### 2019-11-04 paper/paper.tex
began pouring into the introduction nad discussion sections

\documentclass[a4paper,10pt]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\usepackage{amsmath}
\usepackage{amssymb}

\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{grffile}

\usepackage{subcaption}

\usepackage{booktabs}

\newcommand{\important}[1]{\textbf{\color{red} #1}}
\newcommand{\attn}[2]{\textbf{\color{red} #2~\textsuperscript{\textit{[#1]}}}}
\newcommand{\verify}[1]{\attn{verify}{#1}}
\newcommand{\rewrite}[1]{\attn{rewrite}{#1}}
\newcommand{\todo}[1]{{\color{blue} [TODO]} \important{#1}}

\newcommand{\real}{\mathbb{R}}
\newcommand{\cplx}{\mathbb{C}}
\newcommand{\tr}[1]{\mathop{tr}{#1}}

\newcommand{\hop}{{\mkern-1.5mu\dagger}}
\newcommand{\conj}[1]{\overline{#1}}

% \renewcommand{\top}{{\mkern-1.5mu\intercal}}
\renewcommand{\vec}[1]{\overrightarrow{#1}}
\newcommand{\diag}[1]{\mathrm{diag}{#1}}

\title{Bayesian Sparsification of $\cplx$-valued networks}
\author{Ivan Nazarov, and Evgeny Burnaev}

\begin{document}
\maketitle

\section{Introduction} % (fold)
\label{sec:introduction}

Deep neural networks are an integral part of the machine learning and data science set of
tools for practical data-driver problem solving. Despite recent advances in generalization
and optimization theory specific to deep networks, it is challenging to deploy the trained
in actual embedded hardware, due to obvious storage and compute limitations. Many techniques
exist to compress or sparsify the networks: weight pruning \cite{citation_needed}, quantization
from IEEE754 floating point to integer-based arithmetic, and dropout. The key idea is that
the more explicitly zero parameters the model has, the less multiplications the mode needs.

Bayesian Inference is a principled framework of reasoning about uncertainty. The core
principle is updating prior beliefs in accordance with the likelihood of given empirical
observations into posterior belief. Under suitable modelling and prior assumptions, methods
of variational Bayesian inference can be used towards model sparsification: variants of
Bayesian dropout studied in \cite{kingma_variational_2015,molchanov_variational_2017}, and
\cite{kharitonov_variational_2018}.

% section introduction (end)

\section{Bayesian Dropout} % (fold)
\label{sec:bayesian_dropout}

In general, the core of Bayesian Inference can be summarized as follows: given a prior
distribution $\pi(m)$ on models (hypotheses) $\mathcal{M}$, utilize the empirical evidence
$D$ to update the assumptions by considering the likelihood of the observations under each
$m \in \mathcal{M}$. The inference is performed using the Bayes rule to get the exact
posterior belief: $
  p(m \mid D) = \tfrac{p(D \mid m) \pi(m)}{p(D)}
$ with $
  p(D) = \mathbb{E}_{\pi(m)} p(D \mid m)
$.

It is usually assumed that $\mathcal{M}$ is a parametric family indexed by a parameter $\omega$
from some set $\Omega$, that each model is \textit{identified} with its parameter, and that
each $m = m_\omega(\cdot)$ specifies the functional form of the conditional distribution of
the data $D = (z_i)_{i=1}^N$. Unless the data has time-series nature, it is customary to
presume independence of samples $z_i$ conditional on $\omega$.
%
In supervised settings, the nature of the structure of each observation is also conjectured:
$z_i = (x_i, y_i)$ is typically assumed in regression or classification tasks with $
  p(z_i \mid \omega) = p(y_i \mid x_i, \omega) p(x_i)
$, i.e. the inputs $x_i$ are produced by some opaque not particularly interesting process.
%
In unsupervised settings a hierarchical model is usually considered: it is hypothesized that
there are unobserved causal variables $u_i$ with some prior distribution $\pi(u_i \mid \omega)$
and a model of $p(x_i \mid u_i, \omega)$.
% vae x -- indep: q(u \mid x) ~ p(u \mid x, D), q(\omega \mid D) see \cite[eq.~4]{1805.08498}
%
In following we assume that the samples in $D$ are conditionally independent.

The posterior distribution $p(\omega \mid D)$ derived by Bayesian inference from the premise,
can be used to get useful information about yet unobserved data, such as the classification
uncertainty and predictive statistics, to name some examples. These downstream tasks usually
involve iterated or nested integrals over the posterior, e.g. classification uncertainty
evaluates the entropy $
  \mathbb{H}(q) = - \mathbb{E}_{y\sim q} \log{q(y)}
$ of the posterior predictive distribution at $
  p(y \mid x) = \mathbb{E}_{p(\omega \mid D)} p(y \mid x, \omega)
$ for some $x$ of interest, whereas the predictive statistics use
$
  \mathbb{E}_{p(\omega \mid D)} \hat{g}_\omega(x)
$ (by Fubini) for $
  \hat{g}_\omega(x) = \mathbb{E}_{p(y \mid x, \omega)} g(y)
$. These integrals are rarely analytically tractable in practice, and so are approximated
using Monte-Carlo estimators with varying degree of precision, \cite{citation_needed}.

However, despite the modeling assumption being chosen by the practitioner, the posterior
itself can be intractable or scale poorly with the problem size, due to the integral in the
denominator in the Bayes rule. Thus, save for the relatively simple cases \cite{citation_needed},
the exactness of Bayesian Inference is traded for tractability and speed of Variational
Inference.

The main idea of Variational Inference is to recast the posterior inference problem into
optimization framework. Instead of deriving $p(\omega \mid D)$ exactly, we consider a parametric
family $\mathcal{Q}$ of distributions indexed by a variational parameter $\theta \in \Theta$
as potential approximations for the posterior. Here $\theta$ represents a generic composite
parameter of the approximation and is specified whenever necessary.

We seek the closest $Q_\theta(d\omega)$ within the class with respect to some distance or
proximity score $\rho$ on probability measures or densities. Thus the class $\mathcal{Q}$ becomes
part of the modeling assumptions and is usually picked so that its members can be sampled
from, have known and tractable density $
  q_\theta(\omega) d\omega
$ with a tractable score function $
  \omega \mapsto \nabla_\theta \log q_\theta(\omega)
$ for REINFORCE, \cite{citation_needed}, or amenable to the Reparameterization Trick or
its variants, \cite[sec.~2.4]{kingma_auto-encoding_2014}, \cite[sec.~3]{figurnov_implicit_2019}: $
  \omega \sim q_\theta(\omega)
$
is equivalent in distribution to $
  \omega = g_\theta(\varepsilon)
$ for some deterministic differentiable $
  \theta \mapsto g_\theta(\varepsilon)
$ and a non-parametric random variable $
  \varepsilon \sim p_\varepsilon(\varepsilon)
$.
% (reparameterization trick) $q_{\theta}(d\omega)$ is a push-forward of $p(d\varepsilon)$ by a
% differentiable map $g_\theta(\varepsilon)$.

Not every proximity score is practically useful, since finding the variational parameters
$$
\theta^*
  \in \arg \min_{\theta} \rho\bigl(
    q_\theta(\omega), p(\omega \mid D)
  \bigr)
  \,, $$
still requires access to the exact posterior, precisely what variational inference attempts
to avoid. Despite its shortcomings, such as failing to be a metric, and infinite values for
densities with non-nested support, \cite{citation_needed}, the Kullback-Leibler divergence,
defined for $q(\omega) \ll p(\omega)$ as
$$
KL(q\| p)
  = \mathbb{E}_{\omega \sim q}
    \log\frac{q(\omega)}{p(\omega)}
  \,, $$
is commonly used. It circumvents the raised issue, because it satisfies the following identity,
which holds for $q$ and $p$ whenever the divergences are finite:
\begin{equation} \label{eq:kl-div-master}
  \log p(D)
    % = \mathbb{E}_{q(\omega)} \log \frac{p(D, \omega)}{p(\omega \mid D)}
    % = \mathbb{E}_{q(\omega)} \log \frac{
    %   p(D \mid \omega) \pi(\omega)
    % }{p(\omega \mid D)}
    % = \mathbb{E}_{q(\omega)} \log \frac{
    %   p(D \mid \omega) \pi(\omega)
    % }{q(\omega)}
    % + \mathbb{E}_{q(\omega)} \log \frac{q(\omega)}{p(\omega \mid D)}
    % = \mathbb{E}_{q(\omega)} \log{p(D \mid \omega)}
    % - \mathbb{E}_{q(\omega)} \log \frac{q(\omega)}{\pi(\omega)}
    % + \mathbb{E}_{q(\omega)} \log \frac{q(\omega)}{p(\omega \mid D)}
    = \mathbb{E}_{q(\omega)} \log{p(D \mid \omega)}
    - KL(q(\omega) \| \pi(\omega))
    + KL(q(\omega) \| p(\omega \mid D))
    \,.
\end{equation}
This identity implies an equivalent proxy problem for the variational inference -- maximizing
the \textit{evidence lower bound} (ELBO)
\begin{equation} \label{eq:elbo_general}
\begin{aligned}
  & \underset{\theta}{\text{maximize}}
    & \mathcal{L}(\theta; \pi, p)
      & = \mathbb{E}_{\omega \sim q_{\theta}}
          \log p(D \mid \omega)
        - KL(q_{\theta}(\omega) \| \pi(\omega))
        % \mathbb{E}_{\omega \sim q_{\theta}}
          % \log\frac{q_\theta(\omega)}{\pi(\omega)}
  % \\
  % & &
  %     & = \mathbb{E}_{\omega \sim q_{\theta}}
  %         \log{p(D \mid \omega) \pi(\omega)}
  %       + \mathbb{H}(q_{\theta})
  \,,
\end{aligned}
\end{equation}
where the prior and conditional data probability model as listed as arguments, to emphasize
that they can potentially be optimized over (using alternating approach leading to EM-algorithm).
% vae
It is worth noting, that the optimization objective \eqref{eq:elbo_general} requires only $
  p(\omega \mid D)
    \propto p(D \mid \omega) \pi(\omega)
$, i.e. up to its normalizing constant, which is crucial for its practical viability. As
was mentioned above, other objectives for variational approximation can be considered, e.g.
\cite{ranganath_operator_2018} propose an approach that encompasses $f$-divergences, \textbf{...} and
other proximity scores, that depend on $p(\omega\mid D)$ through $p(D \mid \omega)$ and
$\pi(\omega)$.

The Stochastic Gradient Variational Bayes, proposed by \cite{kingma_auto-encoding_2014,citation_needed}, is
an unbiased differentiable Monte-Carlo estimator of the lower bound \eqref{eq:elbo_general}
that allows maximizing ELBO using stochastic gradient-based methods. In deep Bayesian inference
the variational approximation family is defined by deep neural networks, using the stochastic
estimate of ELBO the only viable option. Exploiting independence of observations in $D$ and
the reparameterization trick, the estimator is defined as
\begin{equation} \label{eq:elbo}
  \mathcal{L}^{SGVB}(\theta; \pi, p)
    =
    - KL(q_{\theta}(\omega) \| \pi(\omega))
    % + \frac{N}{\lvert B \rvert} \sum_{i\in B}
        % \log p(z_i \mid \omega_i)
    + N
      \frac1{M} \sum_{i=1}^M
        \frac1{L} \sum_{l=1}^L
          \log p(z_i \mid \omega_{il})
            \Big\vert_{\omega_{il} = g_\theta(\varepsilon_{il})}
    % =
    % - KL(q_{\theta}(\omega) \| \pi(\omega))
    % + N \mathbb{E}_{B \sim \{D\}_M \otimes q_\theta^M}
    %   \hat{\mathbb{E}}_{z,\omega \sim B}
    %     \log p(z \mid \omega)
    \,, 
\end{equation}
where $B = (z_i)_{i=1}^M$ is a minibatch form the dataset $D$ and $
  (\varepsilon_{il})_{l=1}^L \sim p(\varepsilon)
$ are drawn independently per each sample $z_i$. The most commonly used variational
approximations have analytically tractable KL-divergence term, but can be replaced by
an unbiased differentiable estimator.

For a particular family of variational posterior approximation, variational inference
can be used as a regularization method \cite{kingma_variational_2015} and as model sparsification
technique \cite{molchanov_variational_2017}. In \cite{kingma_variational_2015} the Binary
dropout and DropConnect \cite{hinton_improving_2012,dropconnect}, and Gaussian dropout
\cite{srivastava_dropout_2014,wang_fast_2013} were reframed as variational inference methods
by treating the induced parameter distributions as a factorized posterior approximations
of the form $
  q_\theta(\omega) = \prod_j q_{\theta}(\omega_j)
$, where each component $q_{\theta}(\omega_j)$ is defined via $\omega_j = \mu_j \xi_j$
with $\xi_j \sim p(\xi_j)$ iid for some $p(\xi)$. In Binary dropout with rate $p \in (0, 1)$
the mutliplicative noise $\xi$ is distributed like $
  \mathcal{B}\bigl(
      \{0, \tfrac1{1-p}\}, 1-p
    \bigr)
$ whereas in Gaussian dropout $\mathcal{N}(1, \alpha)$ for $\alpha = \tfrac{p}{1-p}$.
Focusing on Gaussian dropout, \cite{kingma_variational_2015} proposed Variational Dropout
technique for Bayesian model regularization: $\alpha$ is treated as a variational parameter,
that enabled its optimization through SGVB. The variational approximation is a fully
factorized Gaussian distribution with components $
  q_{\theta}(\omega_j)
    = \mathcal{N}(\mu_j, \alpha_j \mu_j^2)
$. The flexibility in specifying the dependence of $q_\theta$ on $\alpha$ allows learning
structured dropout rates: global per network, local per layer and even individual, i.e.
specific to each parameter. In the case of a prior with improper log-uniform factors $
  \pi(\omega_j) \propto \lvert \omega_j \rvert^{-1}
$, the KL-divergence term in \eqref{eq:elbo} as computed up to a constant term as a sum of
\begin{equation} \label{eq:improper-kl-div-real}
  KL(q_\theta(\omega) \| \pi(\omega))
    \propto
      \frac12 \mathbb{E}_{\varepsilon \sim \mathcal{N}(0, 1)}
        \log{\Bigl\lvert \tfrac1{\sqrt{\alpha}} + \varepsilon \Bigr\rvert^2}
      % \frac12 \mathbb{E}_{\varepsilon \sim \mathcal{N}(0, 1)}
      %   \log{\bigl\lvert 1 + \sqrt{\alpha} \varepsilon \bigr\rvert^2}
      % - \frac12 \log{\alpha}
  \,.
\end{equation}

Secondary contribution of \cite{kingma_variational_2015} has been the analysis of the local
reparameterization trick as a gradient variance reduction technique for \eqref{eq:elbo},
that is particularly suitable for Variational Dropout. The trick is to translate uncertainty
from the global parameter noise to local noise in intermediate outputs within the network.
Initially, this idea was used in \cite{who-dis-originally-22} for Gaussian dropout,
who employed the closure of Gaussians under affine transformations as a way to inject
regularizing noise. Later in \cite[app.~B]{kingma_variational_2015} it was rigorously shown
that for the case of fully factorized Gaussian dropout posterior approximations, the
gradient estimator $\nabla_\theta \mathcal{L}^{SGVB}$ is more statistically efficient
and computationally fast, when the trick is used in addition to independent per sample
parameter draws, which reduce variance by decorrelating ELBO estimates within the minibatch.

The more recent developments of Bayesian dropout technique with factorized Gaussian
approximations are considered in \cite{molchanov_variational_2017,kharitonov_variational_2018}.
\cite{molchanov_variational_2017}
studies variational dropout from a model sparsification perspective, improve on the results
of \cite{kingma_variational_2015} in two ways: the authors propose a more accurate approximation
to the KL-divergence term, and propose additive noise parameterization for the factors of
$q_\theta(\omega)$, $\omega = W$. Under the original $(\mu, \alpha)$ parameterization the
stochastic output of a linear layer $
  y = W^\top x + b
$ with $
  W \in \mathbb{R}^{n\times m}
$ and independent $
  W_{ij} \sim \mathcal{N}(\mu_{ij}, \alpha_{ij} \mu_{ij}^2)
$ is equivalent in distribution to $
  y \sim \prod_i \mathcal{N}\Bigl(
      \sum_j \mu_{ij} x_j + b_i,
      \sum_j \alpha_{ij} \mu_{ij}^2 x_j^2
  \Bigr)
$. \cite{molchanov_variational_2017} argue that for the purposes of model sparsification this parameterization
should be abandoned in favour of an equivalent $(\mu, \sigma^2)$ with $\alpha$ calculated
using $\tfrac{\sigma^2}{\mu^2}$ when needed. This makes $\nabla_\mu \mathcal{L}^{SGVB}$,
which is particularly important for sparsification, independent of the noise injected by
the trick.

The KL-divergence term \eqref{eq:expect-improper-term-cplx} is half the log-moment of a non-central
$\chi^2$ distribution with shape $1$ and non-centrality $\lambda = \tfrac1{\alpha}$. In general,
there is no analytically tractable expression for log-moment of a $\chi^2_m$ with odd degrees of
freedom. To circumvent this, \cite{kingma_variational_2015} approximate the expectation by a
non-linear polynomial regression for truncated $\alpha \in (0, 1)$. This approximation was
significantly refined in \cite{molchanov_variational_2017}, by considering regression with sigmoid
and soft-plus basis functions fit to the Monte-Carlo estimator of \eqref{eq:improper-kl-div-real}
for $\alpha$ varying over a logarithmic grid. This enabled doing away with the clipping of the
dropout rate (relevance score) $\alpha$. Since gradient based methods rely on unbiased gradient
estimates, in sec.~\ref{sub:real-chisq-grad} we compare the derivative of the approximation
to the exact derivative of \eqref{eq:improper-kl-div-real} with respect to $\log \alpha$ and show
that the approximation in \cite{molchanov_variational_2017} is an adequate.

In another variant of Bayesian dropout, called Automatic Relevance Determination, is developed
in the \cite{molchanov2018}. The key difference from Variational Dropout is the choice of
prior: the log-uniform factor $\pi(\omega_{ij})$ is replaced by a proper Gaussian prior
$\mathcal{N}(0, \tau^{-1}_{ij})$ with learnable precision $\tau_{ij} > 0$. This is knowns as
the Empirical Bayes method, \cite{citation_needed}, which fits a prior distribution while
performing variational inference. The optimal precision parameter is found in the closed form
by minimizing the KL-divergence term holding variational parameters $\theta$ fixed.

% This concludes the section on the foundations of Bayesian dropout techniques.

% section bayesian_dropout (end)

\section{$\cplx$-valued networks} % (fold)
\label{sec:c_valued_networks}

In this section we overview $\mathbb{C}$-valued networks, their motivation and peculiarities.
In out exposition we shall focus mostly on linear layers, keeping in mind that transferring 
the ideas to convolutional layers is straightforward.

The use $\cplx$-valued networks in applications is not new: earliest mentions include
\cite{citation_needed}. More recently they were applied to music transcription and speech
recognition \cite{trabelsi_deep_2017,1910.10202}. The key motivation behind adoption
of $\cplx$-networks is the fact that complex numbers are inherent in digital signal processing
\cite{citation_needed}, acoustic and radio signal analysis \cite{citation_needed}, and
quantum systems modelling \cite{citation_needed} etc. All these applications require
compliance with algebraic operations in field of complex numbers.

The most recent study of complex-valued networks \cite{trabelsi_deep_2017}, provides a set
of building blocks for deep $\cplx$-valued networks. The core of their work is structured
framework for complex-valued operations including representation and linear layers (dense
and convolutional) as well as $\cplx$-valued activations and complex batch-normalization
and weight initialization.

Following \cite{trabelsi_deep_2017} we identify $\cplx$ with $\real^2$ via $
  z_\mathrm{r} + j z_\mathrm{i} \mapsto (z_\mathrm{r}, z_\mathrm{i})
$, storing the real and imaginary parts in interleaved format, and emulate $\cplx$-algebra
using $\real$-valued arithmetic. Thus designed $\cplx$-network is, essentially, a
$\real$-network with \textit{double} the layers' widths to accommodate real and imaginary
parts and with constraints on layers' parameters that make them respect $\cplx$-algebra.
This makes it possible to retrofit $\cplx$-valued networks into the existing $\real$-valued
auto-differentiation libraries.

In particular, common linear layers, such as dense layers and convolutions,
$
  L \colon \cplx^{\mathrm{[in]}}
    \to \cplx^{\mathrm{[out]}}
$ act upon their inputs as follows:
$$
\real^{2 \times \mathrm{[in]}}
  \to \real^{2 \times \mathrm{[out]}}
  \colon (x_r, x_i)
    \mapsto \Bigl(
      L_r x_r - L_i x_i,
      L_r x_i + L_i x_r
    \Bigr)
  \,, $$
where $
  L_r, L_i
    \colon \real^{\mathrm{[in]}}
      \to \real^{\mathrm{[out]}}
$ are the unique $\real$-linear operators that make up $L = L_r + j L_i$ the overall
effect of the layer. For instance, to respect $\cplx$-arithmetic a convolutional layer with
$\cplx$-kernel $W$ can be implemented using two $\real$-convolutions with $\real$-kernels
$\Re{W}$ and $\Im{W}$. Other algebraic operations, such as division and roots in batch
normalization \cite{trabelsi_deep_2017}, are implemented in such a way as to respect
$\cplx$-algebra.
%
Concerning activations, \cite{trabelsi_deep_2017} consider the following: independent
componentwise application of $\real$-valued non-linearities, $
  z = u + j v
    \mapsto \sigma(u) + j \sigma(v)
$; $\cplx$-differentiable exponential and trigonometric activations; and \textit{modRelu}
activation, which preserves the angle and applies soft-thresholding to the modulus: $
  z = r e^{j \phi}
    \mapsto e^{j \phi} (r - \theta)_+
  % z \mapsto z \bigl(
  %     1 - \tfrac\theta{\lvert z \rvert}
  %   \bigr)_+
$ with a learnable parameter $\theta\in \real$.

The question of differentiability of complex-valued networks is tricky, since they usually
use non-differentiable non-linearities. However, a more severe problem stems from the loss
objective being real-valued. Indeed, if $f\colon \cplx \to \cplx$ were $\cplx$-differentiable
(holomorphic), the composition of $f$ with a non-trivial $h \colon \cplx\to \real$ makes it
not $\cplx$-differentiable with respect parameters, since $h$ violates Cauchy-Riemann conditions.
This problem is commonly dealt with by using Wirtinger, or $\cplx\real$ calculus, which subsumes
$\cplx$-calculus, but is also applicable to non-holomorphic functions of $\cplx$-argument, see
\cite{adali_complex-valued_2011} and \cite{trabelsi_deep_2017}. In essence, this approach
regards $f$ as a function of two independent variables $z$ and its conjugate $\conj{z}$ and
symbolically redefines the derivatives appropriately. The resulting derivative operators
satisfy linearity, product and chain rules, and respect complex conjugation. This approach
can be directly reformulated in terms of derivatives with respect to real and imaginary parts,
making it possible to use and apply the rules of $\real$-calculus to the networks represented
in paired $\real$ fashion and use existing $\real$-valued backpropagation in autograd software.

% criticism and discussion
Despite this, $\cplx$-networks remain much less popular than $\real$-networks for several
reasons. One possible reason is that a $\cplx$-layer is identical to a paired $\real$-layer,
based on the algebraic equivalence between $2 \times 2$ real matrices and complex numbers.
Due to this constraint $\cplx$-networks have less expressive power for the same computation
complexity compared to a $\real$-layer with twice as many inputs and outputs.
%
Another one is that a $\cplx$-network is not a true complex-valued function of a complex
argument: common non-linearities are pointwise applications of $\real$-valued activations
\cite{trabelsi_deep_2017}.
%
Third conceptual issue is that a real-valued loss as a $\cplx\to\real$ function fails
Cauchy-Riemann conditions, and so is not $\cplx$-differentiable. Since the network has to
be trained by a gradient-based method (stochastic), this issue is overcome by $\cplx\real$,
or Wirtinger calculus, which treats the complex argument $z$ and its conjugate $\conj{z}$
as explicit independent variables. For non-holomorphic functions this approach makes taking
their derivatives essentially indistinguishable from calculus on $\real^2$.
%
The last reason is the lack of native support by the major deep learning and auto-differentiation
frameworks.

% section c_valued_networks (end)

\section{Dropout for $\cplx$-valued layers} % (fold)
\label{sec:dropout_for_c_valued_layers}

In this section we review the complex Gaussian distribution and discuss its properties. Then
we introduce factorized dropout posterior for complex-valued parameters and the relevant
version of the local reparameterization trick. Then we move on to choosing suitable priors
and then onward to deriving explicit expressions for the divergence penalties in \eqref{eq:elbo}
in terms of special functions.

\subsection{$\cplx$-Gaussian Variational Approximation} % (fold)
\label{sub:c_gaussian_variational_approximation}

A random vector $z\in \cplx^m$ is said to have complex Gaussian distribution, if its
characteristic function is
$$
z \sim \mathcal{N}^{\cplx}_m(z \vert \mu, \Gamma, C)
  \Leftrightarrow
  \mathbb{E}_{z} e^{j \Re{(t^{\hop} z)}}
  = \exp{\{
    j \Re{(t^{\hop} \mu)}
    - \tfrac14 \bigl(
      t^{\hop} \Gamma t + \Re{(t^{\hop} C \conj{t})}
    \bigr)
  \}}
  \,, $$
where $\mu \in \cplx^m$ is the mean, $\Gamma, C \in \cplx^{m\times m}$ are complex covariance
and relation matrices satisfying $C^\top = C$, $\Gamma^{\hop} = \Gamma$, $\Gamma \succeq 0$,
and $
  \conj{\Gamma} \succeq C^{\hop} \Gamma^{-1} C
$. The matrices $\Gamma$ and $C$ correspond to $
  \mathbb{E} (z - \mu)(z - \mu)^{\hop}
$ and $
  \mathbb{E} (z - \mu)(z - \mu)^\top
$, respectively. Here ${\cdot}^{\hop}$ denotes Hermitian conjugate, i.e. $
  A^{\hop} = (\conj{A})^\top
$, ${\cdot}^{\top}$ -- the matrix transpose, and $\conj{\cdot}$ -- the complex conjugation
elementwise.
%
% The intuition behind them is more apparent in the complex univariate case ($m=1$):
% here $\Gamma = \sigma^2 \geq 0$, and $C$ can be represented as $\sigma^2 \rho \in \cplx$ with $
%   \lvert \rho \rvert \leq 1
% $. Therefore $\sigma^2$ affects the overall ``concentration'' of the complex random variable,
% whereas $\rho$ is responsible for the strength and ``direction'' of the linear relation between
% the real and imaginary parts, \cite{lapidoth_capacity_2003}.
% $$
% \frac{\sigma^2}2
%   \begin{pmatrix}
%     1 + \Re{\rho} & \Im{\rho} \\
%     \Im{\rho} & 1 - \Re{\rho}
%   \end{pmatrix}
%   = \frac{\sigma^2}2 I
%   + \frac{\sigma^2 \lvert \rho \rvert}2 
%   \begin{pmatrix}
%     \cos\theta & \sin\theta \\
%     \sin\theta & - \cos\theta
%   \end{pmatrix}
% $$

A characterization of a $\cplx$-Gaussian vector, more useful for the current study, is via the
equivalence with the paired real multivariate Gaussian distribution:
\begin{equation}  \label{eq:cn-paired-real-density}
  z \sim \mathcal{N}^{\cplx}_m(\mu, \Gamma, C)
    \Leftrightarrow
    \begin{pmatrix}
      \Re z \\ \Im z
    \end{pmatrix}
      \sim \mathcal{N}_{2 m}\biggl(
        \begin{pmatrix}
          \Re \mu \\ \Im \mu
        \end{pmatrix},
        \frac12
        \begin{pmatrix}
          \Re{(\Gamma + C)} & - \Im{(\Gamma - C)} \\
          \Im{(\Gamma + C)} &   \Re{(\Gamma - C)}
        \end{pmatrix}
      \biggr)
    \,.
\end{equation}
It is possible to recover the $\cplx$ covariance and relation matrices from a block covariance
matrix $\Sigma$ of a \textit{non-degenerate} paired real Gaussian vector through
$$
\begin{pmatrix}
  \Sigma_{rr} & \Sigma_{ri} \\ 
  \Sigma_{ir} & \Sigma_{ii} 
\end{pmatrix}
  = \frac12
    \begin{pmatrix}
      \Re{(\Gamma + C)} & - \Im{(\Gamma - C)} \\
      \Im{(\Gamma + C)} &   \Re{(\Gamma - C)}
    \end{pmatrix}
  \, \Leftrightarrow
  \,
  \begin{cases}
    \Gamma
      = \Sigma_{rr} + \Sigma_{ii} + j (\Sigma_{ir} - \Sigma_{ri})
    \,, \\
    C = \Sigma_{rr} - \Sigma_{ii} + j (\Sigma_{ir} + \Sigma_{ri}) 
  \end{cases}
  $$

A $\cplx$-Gaussian random vector $z$ is called \textit{proper}, when $C = 0$, i.e. the random
vector $z$ and its conjugate $\conj{z}$ are uncorrelated. This implies that in the paired real
representation $
  \Sigma_{ir} = -\Sigma_{ri} = -\Sigma_{ir}^\top
$ and $\Sigma_{rr} = \Sigma_{ii}$, i.e. real and imaginary component of the same random element
are uncorrelated, since skew-symmetric matrices necessarily have zero-diagonal.

The $\cplx$-Gaussian family of distributions is closed under affine transformations:
if $
  x \sim \mathcal{N}_m^{\cplx}(\mu, \Gamma, C)
$ and $y = A x + b$, for $
  A \in \cplx^{n\times m}
$ and $b \in \cplx^{n}$, then $
  y \sim \mathcal{N}_n^{\cplx}(A\mu + b, A \Gamma A^\hop, A C A^\top)
$. This follows from the effects of the affine transformation on the characteristic
function.

To develop $\cplx$-variational dropout we assume a fully factorized posterior approximation
distribution on the layers' parameters: $\omega = (W, b)$, where a $\cplx$-valued $W$ collects
all weight matrices of linear layers and kernels of convolutional layers, and $b$ represents
all bias term combined. We use a fully factorized Dirac family on the biases, and mean-field
proper $\cplx$-Gaussian variational approximation for the weights: $
  q(W) = \prod_{lij} q(W^{l}_{ij})
$ with each parameter being an independent proper complex Gaussian
\begin{equation} \label{eq:c-gauss-vi}
  W_{ij}
    \sim \mathcal{N}^{\cplx}(\mu_{ij}, \sigma^2_{ij}, 0)
  \,.
\end{equation}
Thus we would like to sparsify the weights in the network and, since the bias terms constitute
a meagre share of network's parameters and are rarely dropped out or pruned, we use Bayesan
MAP estimates for them.

As was demonstrated in \cite{kingma_variational_2015}, local reparameterization trick
provides both faster computations and better statistical efficiency of the SGVB gradient
estimator. We formulate the $\cplx$ version of the local reparameterization trick, which
generalizes \cite{who-dis-originally-22}.

% subsection c_gaussian_variational_approximation (end)

\subsection{Local reparameterization trick} % (fold)
\label{sub:local_reparameterization_trick}

To simplify exposition of the trick, we consider the complex linear dense layer, and afterwards
outline the caveats for $\cplx$-convolutional layers. In both cases we use fully factorized
general $\cplx$-Gaussian distribution for parameters $W$ of the layer.

Consider a $\cplx$-linear layer: $
  W \in \cplx^{n\times m}
$ is a random $\cplx$-Gaussian matrix with independent elements $
  w_{ij} \sim \mathcal{N}^{\cplx}\bigl(
    w_{ij}
    \big \vert
    \mu_{ij}, \sigma^2_{ij}, C_{ij}
  \bigr)
$ with $\mu_{ij}\in cplx$, $\sigma^2_{ij} \geq 0$, $C_{ij}\in \cplx$ and $
  \lvert C_{ij} \rvert^2 \leq \sigma^2_{ij}
$. We begin by observing that the variational approximation of $q(W)$ is a multivariate
$\cplx$-Gaussian: $
  \vec{W}
    \sim \mathcal{N}^{\cplx}_{[n\times m]} \bigl(
      \vec{\mu}, \diag{\vec{\Sigma}}, \diag{\vec{C}}
    \bigr)
$, where $[n\times m]$ denotes lexicographically flattened dimension and $\diag{v}$ is a
diagonal square matrix with $v_i$ on the main diagonal. Here we collected variances and means
into matrices $\Sigma$ and $\mu$, respectively.
%
Now, for any $x \in \cplx^m$ and $b\in \cplx^n$ we have
$$
W x + b
  % = I_n W x + b
  = (I_n \otimes x^\top) \vec{W} + b
  \,, $$
where $\vec{\cdot}$ denotes flattening in lexicographic order of indices (row-major), and
$\otimes$ denotes the Kronecker product, for which we have the identity $
  \vec{P Q R} = (P \otimes R^\top) \vec{Q}
$, \cite{petersen_matrix_2012}.
% It follows from the definition of the Kronecker product
% of $P$ and $R^\top$ and the row-major order vectorization.
%
Structure of the matrices, involved in this expression, and the identity $
  (P \otimes R) (C \otimes S) = P Q \otimes R S
$, \cite{petersen_matrix_2012}, imply
\begin{align*}
  (I \otimes x^\top) \diag{\vec{\Sigma}} (I \otimes x^\top)^\hop
    % &= \sum_{ij} (I \otimes x^\top) e_i \otimes e_j
    %   \sigma^2_{ij} (e_i \otimes e_j)^\top (I \otimes x^\top)^\hop
    % \\
    &
    = \sum_{ij} (e_i \otimes x^\top e_j)
      \sigma^2_{ij} (e_i \otimes x^\top e_j)^\hop
    \notag \\
    % &= \sum_{ij} (e_i \otimes x_j) \sigma^2_{ij} (e_i^\top \otimes \conj{x}_j)
    % \\
    &
    = \sum_i (e_i e_i^\top) \sum_j \sigma^2_{ij} x_j \conj{x}_j
    \,,
\end{align*}
where $e_i$ is the $i$-th real unit vector of dimensionality conforming to the expression it
is involved with. In a similar fashion we obtain the expression for the relation matrix of
the transformation:
\begin{equation*}
  (I \otimes x^\top) \diag{\vec{C}} (I \otimes x^\top)^\top
    % = \sum_{ij} (e_i \otimes x_j) C_{ij} (e_i \otimes x_j)^\top
    = \sum_i e_i e_i^\top \sum_j C_{ij} x_j^2
    \,.
\end{equation*}
The term $
  \sum_i e_i e_i^\top (\ldots)
$ means that the covariance and relation matrices of $y = Wx + b$ are diagonal.

These observations coupled with the closure under affine transformation imply that the
components of $y = W x + b$ are independent univariate $\cplx$-Gaussain random variables
with distributions
\begin{equation} \label{eq:c-gaus-trick}
  y_i
    \sim \mathcal{N}^{\cplx}
      \bigl(
        e_i^\top \mu x + b,
        \, \sum_j \sigma^2_{ij} \lvert x_j \rvert^2,
        \, \sum_j C_{ij} x_j^2
      \bigr)
    \,.
\end{equation}

We can notice, that in \eqref{eq:c-gaus-trick} the mean, variance and relation parameters are,
essentially, matrix-vector operations: $\mu x + b$, $\Sigma \lvert x \rvert^2$ and $C x^2$
with the modulus and power applied elementwise. The local reparameterization trick works
similarly for $\cplx$-convolutions, provided we draw independent weights $W\sim q(W)$ for each
spatial patch in the input: convolve value $x$, amplitude $\lvert x \rvert^2$ and complex
square $x^2$ with the mean, variance, and relation kernels, respectively. The need for
independent resampling stems from kernel weights being shared between patches, which would
make the gradient estimator less efficient due to correlation from overlapping patches.
The argument from \cite{kingma_variational_2015} in favour drawing independent weight per
sample in the minibatch can be applied here to show that this is \verify{indeed the case}.
%
Weight sharing is pushed from weights of the layer to shared variational parameters $\theta$
in the approximation $q_\theta$.

% subsection local_reparameterization_trick (end)

\subsection{The choice of priors and Kullback-Leibler divergence} % (fold)
\label{sub:priors_and_kullback_leibler_divergence}

In this section we consider two different priors, suitable for variational dropout: log-uniform
\cite{kingma_variational_2015,molchanov_variational_2017} and proper $\cplx$-Gaussian analogue
for the empirical Bayes prior in \cite{kharitonov_variational_2018}.

Recall that we use fully factorized variational approximation for the parameters: $
  W \sim q(W)
    = \bigotimes_{ij} q(\omega_{ij})
$ with proper complex Gaussian distributions of each element $
  q(\omega_{ij})
    = \mathcal{N}^{\cplx}\bigl(
      \omega_{ij} \big\vert
      \mu_{ij}, \sigma^2_{ij}, 0
    \bigr)
$. Assuming factorized prior belief $\pi(W)$ on the parameters $W$, the KL-divergence
term in ELBO \eqref{eq:elbo} is
\begin{equation}  \label{eq:elbo-general-kl-div}
KL(q(W) \| \pi(W))
  % = \mathbb{E}_{W \sim q(W)} \log \tfrac{q(W)}{\pi(W)}
  % = \sum_{ij} \mathbb{E}_{\omega_{ij} \sim q(\omega_{ij})}
  %   \log \tfrac{q(\omega_{ij})}{\pi(\omega_{ij})}
  = \sum_{ij} KL\bigl(
    q(\omega_{ij}) \| \pi(\omega_{ij})
  \bigr)
  \,.
\end{equation}
%
We shall omit the subscripts for brevity in the derivations in the next section, which
we begin with a derivation of the entropy of a proper $\cplx$-Gaussian.

The expression of Kullback-Leibler divergence of $q(\omega)$ from an arbitrary prior $\pi(\omega)$
necessarily involves the (differential) entropy of $q$:
\begin{equation*}
  KL\bigl(
    q(\omega) \| \pi(\omega)
  \bigr)
    % = \mathbb{E}_{\omega \sim q} \log{q(\omega)} - \mathbb{E}_{\omega \sim q} \log{\pi(\omega)}
    = - \mathbb{H}(q) - \mathbb{E}_{\omega \sim q} \log{\pi(\omega)}
    \,.
\end{equation*}
The entropy of a real multivariate Gaussian $
  x \sim q(x) = \mathcal{N}_n(x \vert \mu, \Sigma)
$ is
$$
\mathbb{H}(q)
  = - \mathbb{E}_{x\sim q(x)} \log{q(x)}
  % = \tfrac12 \log \det{(2 \pi \Sigma)}
  % + \tfrac12 \mathop{tr}{(
  %     \Sigma^{-1}
  %     \mathbb{E}_{x\sim q(x)}
  %       (x - \mu) (x - \mu)^\top
  %   )}
  = \tfrac12 \log \det{(2 \pi e \Sigma)}
  \,, $$
whence follows the expression for the entropy of a general $\cplx$-Gaussian random vector
$
  z \sim q(z)
    = \mathcal{N}^{\cplx}_n(z\vert \mu, \Gamma, C)
$
\begin{align*} \label{eq:c-gauss-entropy-derivation}
  \mathbb{H}(q)
    &
    % = \tfrac12 \log \det{(2 \pi e \Sigma)}
    = \tfrac12 \log \det{\biggl(
      2 \pi e \tfrac12
      \begin{pmatrix}
        \Re{(\Gamma + C)} & - \Im{(\Gamma - C)} \\
        \Im{(\Gamma + C)} &   \Re{(\Gamma - C)}
      \end{pmatrix}
    \biggr)}
    \notag \\
    % &
    % = \begin{bmatrix}
    %   r_1 + j r_2 \to r_1 \\  % sufficient for C=0 case
    %   j r_1 + r_2 \to r_2     % j conj of transformation for r1, det x 2
    % \end{bmatrix}
    % = \tfrac12 \log \det{\biggl(
    %   % \det{[I & j I \\ j I & I]} = \det{I} \det{I - jI I^{-1} jI} = \det{2 I}
    %   % left apply : thus dividing by \sqrt{2}
    %   \tfrac1{\sqrt{2}} 2 \pi e \tfrac12
    %   \begin{pmatrix}
    %     \Gamma + C & j (\Gamma - C) \\
    %     j (\conj{\Gamma} + \conj{C}) & \conj{\Gamma} - \conj{C}
    %   \end{pmatrix}
    % \biggr)}
      % % Implicitly using the fact that for a non-singular $\Omega$ we have $
      % %   \det{A}
      % %     = \tfrac{\det{(\Omega A)}}{\det{\Omega}}
      % %     = \tfrac{\det{(A \Omega)}}{\det{\Omega}}
      % % $.
    % \notag \\
    % &
    % = \begin{bmatrix}
    %   c_1 - j c_2 \to c_1 \\  % -j conj of transformation for c2
    %   c_2 - j c_1 \to c_2     % sufficient for C=0 case
    % \end{bmatrix}
    % = \tfrac12 \log \det{\biggl(
    %   % \det{[I & - j I \\ - j I & I]} = \det{I} \det{I - (-j)I I^{-1} (-j)I} = \det{2 I}
    %   % right apply : thus dividing by \sqrt{2}
    %   \tfrac12 2 \pi e \tfrac12
    %   \begin{pmatrix}
    %     2 \Gamma     & - 2 j C \\
    %     2 j \conj{C} & 2 \conj{\Gamma}
    %   \end{pmatrix}
    % \biggr)}
    % \notag \\
    % &
    % = \begin{bmatrix}
    %   r_2 - j \conj{C} \Gamma^{-1} r_1 \to r_2
    % \end{bmatrix}
    % = \tfrac12 \log \det{\biggl(
    %   % \det{[I & 0 \\ - j \conj{C} \Gamma^{-1} & I]} = \det{I} = 1
    %   \pi e
    %   \begin{pmatrix}
    %     \Gamma & - j C \\
    %     0 & \conj{\Gamma} - \conj{C} \Gamma^{-1} C
    %   \end{pmatrix}
    % \biggr)}
    % \notag \\
    &
    = \tfrac12 \log \det{(\pi e \Gamma)} \det{(\pi e (\conj{\Gamma} - \conj{C} \Gamma^{-1} C))}
    \,.
\end{align*}
The entropy of a proper $\cplx$-Gaussian random vector ($C = 0$) is therefore 
\begin{equation}  \label{eq:cn-proper-entropy}
  % determinant commutes with complex conjugation, since it is multilinear
  \mathbb{H}(q)
    % = \tfrac12 \log \det{(\pi e \Gamma)} \det{(\pi e (\conj{\Gamma} - \conj{C} \Gamma^{-1} C))}
    = \tfrac12 \log \det{(\pi e \Gamma)} \det{(\pi e \conj{\Gamma})}
    % = \tfrac12 \log \det{(\pi e \Gamma)} \conj{\det{(\pi e \Gamma)}}
  %  = \tfrac12 \log \bigl\lvert \det{(\pi e \Gamma)} \bigr\rvert^2
    = \log \bigl\lvert \det{(\pi e \Gamma)} \bigr\rvert
    \,.
\end{equation}

\subsubsection{Variational dropout} % (fold){}
\label{ssub:variational_dropout}

Let's get the divergence term for the improper prior, that most closely recovers the variational
dropout penalty term in \cite{kingma_variational_2015} and \cite{molchanov_variational_2017}.
If we assume $
  \pi(\omega) \propto \tfrac1{\lvert \omega \rvert^\beta}
$ for some $\beta > 1$, then we formally get the following KL-divergence term (up to an unknown,
or non-existent constant):
\begin{equation}  \label{eq:var-do-kl-div-raw}
KL(q\| \pi)
  \propto
  %   \mathbb{E}_{\omega \sim q(\omega)} \log q(\omega)
  %   + \tfrac{\beta}2 \mathbb{E}_{\omega \sim q(\omega)} \log \lvert \omega \rvert^2
  % =
  %   - \log \lvert \det{(\pi e \sigma^2)} \rvert
  %   + \tfrac{\beta}2 \mathbb{E}_{\omega \sim q(\omega)} \log \lvert \omega \rvert^2
  % =
    - \log{\sigma^2}
    + \tfrac{\beta}2 \mathbb{E}_{\omega \sim q(\omega)} \log \lvert \omega \rvert^2
  \,,
\end{equation}
where we have used \eqref{eq:cn-proper-entropy} with $\Gamma = \sigma^2 \geq 0$. Note
that for $\mu \neq 0$, we have $\omega \sim q(\omega)$ equal in distribution to $\mu \xi$
with $\xi \sim \mathcal{N}^{\cplx}(\xi \vert 1, \alpha, 0)$, whence
\begin{equation}  \label{eq:expect-improper-term-cplx}
\mathbb{E}_{\omega \sim q(\omega)} \log \lvert \omega \rvert^2
  % = \mathbb{E}_{\xi \sim \mathcal{N}^{\cplx}(\xi \vert 1, \alpha, 0)}
  %   \log \lvert \mu \xi \rvert^2
  % = \log \lvert \mu \rvert^2
  %   + \mathbb{E}_{\xi \sim \mathcal{N}^{\cplx}(\xi \vert 1, \alpha, 0)}
  %       \log \lvert \xi \rvert^2
  = \log \alpha \lvert \mu \rvert^2
    + \mathbb{E}_{\xi \sim \mathcal{N}^{\cplx}(\xi \vert 0, 1, 0)}
        \log{\bigl\lvert \tfrac1{\sqrt{\alpha}} + \xi \bigr\rvert^2}
  \,.
\end{equation}
The expectation in \eqref{eq:expect-improper-term-cplx} involves a log-moment of the non-central
$\chi^2_2$ distribution, which has an analytic expression for the gradient, unlike the case
in $\real$-dropout penalty \eqref{eq:improper-kl-div-real}.

Let $(\mu_i)_{i=1}^m \in \cplx$ and $
  (z_i)_{i=1}^m \sim \mathcal{N}^{\cplx}(0, 1, 0)
$ iid. Then $W = \sum_i \lvert \theta_i + z_i \rvert^2$ has a non-central $\chi^2_{2m}$
distribution with non-centrality parameter $s^2 = \sum_i \lvert \theta_i \rvert^2$. The
log-moments of $W$ for general integer $m \geq1$ are given in
\cite[p.~2466]{lapidoth_capacity_2003}.  % in fact Appendix X, Lemma 10.1
In particular, for $m=1$ and $\theta\in \cplx$ we have
\begin{equation}  \label{eq:log-moment-for-chi-2}
\mathbb{E}_{z \sim \mathcal{N}^{\cplx}(0, 1, 0)}
  \log \lvert \theta + z \rvert^2
  = \log \lvert \theta \rvert^2 - \mathop{Ei}( - \lvert \theta \rvert^2)
  \,,
\end{equation}
where $\mathop{Ei}(x) = \int^x_{-\infty} t^{-1} e^t dt$ for $x < 0$ is the exponential integral
function. Note that the limiting value of \eqref{eq:log-moment-for-chi-2} as $
  \lvert \theta \rvert \to 0
$ is $- \gamma$, i.e. negative Euler's constant. Therefore after cancellation the expression
of the KL-divergence in \eqref{eq:var-do-kl-div-raw} becomes
\begin{equation}  \label{eq:var-do-kl-div}
KL(q\| \pi)
  \propto
  %   - \log \lvert \det{(\pi e \sigma^2)} \rvert
  %   + \tfrac{\beta}2 \log \alpha \lvert \mu \rvert^2
  %   + \tfrac{\beta}2 \mathbb{E}_{\xi \sim \mathcal{N}^{\cplx}(\xi \vert 0, 1, 0)}
  %       \log{\bigl\lvert \tfrac1{\sqrt{\alpha}} + \xi \bigr\rvert^2}
  % =
  %   - \log{\sigma^2}  % - \log{\pi e}
  %   + \tfrac{\beta}2 \log \alpha \lvert \mu \rvert^2
  %   + \tfrac{\beta}2 \bigl(
  %     - \log \alpha - \mathop{Ei}( -\tfrac1{\alpha})
  %   \bigr)
  % =
    % \log \tfrac{\lvert \mu \rvert^\beta}{\sigma^2}
    % \log \tfrac{\lvert \mu \rvert^\beta}{\alpha \lvert \mu \rvert^2}
    \tfrac{\beta-2}2 \log{\lvert \mu \rvert^2}
    + \log{\tfrac1{\alpha}}
    - \tfrac{\beta}2 \mathop{Ei}(- \tfrac1{\alpha})
  \,.
\end{equation}

The exponential integral is readily available in most scientific computations packages nowadays,
and, what is especially useful for the stochastic variational Bayes purposes, has a simple
expression for the derivative: $x \mapsto \tfrac{e^x}{x}$ for $x < 0$. This observation enables
embedding it into autograd software by computing the term with bogus output values, yet correct
(on device) gradient, provided no downstream computations depend on the value of the KL-divergence
term itself.

% subsubsection variational_dropout (end)

\subsubsection{Empirical Bayes} % (fold)
\label{ssub:empirical_bayes}

For this model we use an empirical Bayes prior. We assume that our initial belief is that
parameters are independent and each one is proper $\cplx$-Gaussian with its own precision: $
  \pi(\omega)
    \propto \mathcal{N}^{\cplx}\bigl(
      \omega \vert 0, \tau^{-1}, 0
    \bigr)
$. The per element KL-divergence term in the ELBO is computed thus:
\begin{equation}  \label{eq:emp-bayes-kl-div}
KL(q \| \pi_\tau)
  = - 1 - \log{(\tau \sigma^2)}
    + \tau \bigl(
      \sigma^2 + \lvert \mu \rvert^2
    \bigr)
  \,,
\end{equation}
which follows from the KL-divergence expression for two multivariate Gaussians
$$
% \mathbb{E}_{\omega\sim q_1(\omega)} \log \tfrac{q_1(\omega)}{q_2(\omega)}
%   =
KL(q_1\| q_2)
  =
  % - \tfrac12 \log\det{(2\pi e \Sigma_1)} + \tfrac12 \log\det{(2\pi \Sigma_2)}
  - \tfrac12 \log \det{e I}
  + \tfrac12 \log \frac{\det{\Sigma_2}}{\det{\Sigma_1}}
  + \tfrac12 \tr{\bigl( \Sigma_2^{-1} \Sigma_1 \bigr)}
  + \tfrac12 (\mu_1 - \mu_2)^\top \Sigma_2^{-1} (\mu_1 - \mu_2)
  \,. $$

Somewhat counterintuitively, in empirical Bayes we optimize the hyperparameters of the
prior on the observed dataset. Thus the lower bound \eqref{eq:elbo} is optimized w.r.t.
$\tau$ of each weight's prior. \eqref{eq:emp-bayes-kl-div} is optimized (minimized) at
$\tau^\ast = (\sigma^2 + \lvert \mu \rvert^2)^{-1}$, yielding the following penalty in
ELBO:
\begin{equation}  \label{eq:emp-bayes-opt-kl}
KL(q \| \pi_{\tau^\ast})
  % = - 1 - \log{({\tau^\ast} \sigma^2)}
  %   + {\tau^\ast} \sigma^2 + {\tau^\ast} \lvert \mu \rvert^2
  % = \log{((\sigma^2 + \lvert \mu \rvert^2) \tfrac1{\sigma^2})}
  = \log{\bigl(1 + \tfrac{\lvert \mu \rvert^2}{\sigma^2}\bigr)}
  % = \log{\bigl(1 + \tfrac1\alpha \bigr)}
  \,,
\end{equation}
which exactly replicates the term, derived in \cite{kharitonov_variational_2018}.

% subsubsection empirical_bayes (end)

\subsubsection{Bayesian $\cplx$-dropout via $\real$-scaling} % (fold)
\label{ssub:real_scaling_dropout}

Consider the following parameterization of $W$: $
  W = \mu \odot \xi
$ where $
  \xi_{ij} \sim \mathcal{N}(1, \alpha_{ij})
$, yet $\mu \in \cplx^{n \times m}$. This case corresponds to variational inference for the
multiplicative mask $\xi$, distribution of which is approximated using independent $\real$
univariate Gaussians (ordinary dropout posteriors). Here we are actually interested in
inference, regarding the values of $\xi$ after observing the data (and fitting other model
parameters such as $\mu$). Essentially, in \eqref{eq:elbo} we have
$$
\mathbb{E}_{\xi \sim q(\xi)}
  \log p_\theta(z \vert \xi)
  - KL(q(\xi) \| \pi(\xi))
  \approx
    N \hat{\mathbb{E}}_{(z, \xi) \sim B}
      \log p_\theta(z \vert \xi)
    - KL(q(\xi) \| \pi(\xi))
  \,, $$
and by running SGVB, i.e. maximizing stochastic batched ELBO, we minimize the KL-divergence
of the variational approximation $q(\xi)$ from its true posterior $p(\xi\vert D)$. Thus we
run inference on the relevance factors of the parameters, rather than the parameters themselves.

Under this parameterization we have
$$
W_{ij} = \mu_{ij} \odot \xi_{ij}
  \sim \mathcal{N}^{\cplx} \bigl(
    \mu_{ij},
    \, \alpha_{ij} \lvert \mu_{ij} \rvert^2,
    \, \alpha_{ij} \mu_{ij}^2
  \bigr)
  \,, $$
which is a degenerate $\cplx$-Gaussian distribution. The local reparameterization trick for
this distribution implies
$$
y_i
  \sim \mathcal{N}^{\cplx}\bigl(
    e_i^\top \mu x + b,
    \, \sum_j \alpha_{ij} \lvert x_{ij} \mu_{ij}\rvert^2,
    \, \sum_j \alpha_{ij} (x_{ij} \mu_{ij})^2,
    \,
  \bigr)
  \,. $$
This means that it is a little bit more expensive to translate the local parameter noise
to the immediate activation, since we need to take into consideration the covariance between
complex output and its conjugate. Due to this, additive noise reparameterization trick,
\cite{molchanov_variational_2017}, cannot provide its variance reducing benefits, since
it is impossible to do away with dependence of the complex relation of the key parameter
$\mu_{ij}$.

The KL-divergence penalty term in this case follows form the penalty in the real variational
dropout case with the fully factorized Gaussian approximation and an improper prior $
  \pi(\xi)\propto \lvert \xi \rvert^{-\beta}
$:
$$
KL(q(\xi)\| \pi(\xi))
  % = - \tfrac12 \log 2\pi e \alpha
  %   + \tfrac\beta2 \log \alpha
  %   + \tfrac\beta2 \mathbb{E}_{z\sim \mathcal{N}(0, 1)}
  %     \log \lvert z + \tfrac1\sqrt{\alpha} \rvert^2
  \propto \tfrac{\beta-2}2 \log \alpha
    + \tfrac\beta2 \mathbb{E}_{z\sim \mathcal{N}(0, 1)}
      \log \lvert z + \tfrac1{\sqrt{\alpha}} \rvert^2
  \,. $$
Unlike the $\cplx$-valued case, even derivative of the expectation term is analytically
intractable (sec.~\ref{sub:real-chisq-grad}). Thus we use the approximation provided
by \cite{molchanov_variational_2017}.

% subsubsection real_scaling_dropout (end)

% subsection priors_and_kullback_leibler_divergence (end)

% section dropout_for_c_valued_layers (end)

\section{Experiments} % (fold)
\label{sec:experiments}

In this section we will compare the complex variational dropout techniques, discussed
above, on the tasks and datasets, that were studied in prior research on complex-%
valued networks.

\subsection{Tasks and datasets} % (fold)
\label{sub:tasks_and_datasets}

\cite{trabelsi_deep_2017} studies the applicability of complex-valued networks to
image classification (CIFAR-10, CIFAR-100, reduced train of SVHN), music-transcription
(MusicNet), and Speech Spectrum prediction (TIMIT).
\begin{itemize}
  \item 
\end{itemize}

\cite{monning_evaluation_2018}
\cite{jankowski_complex-valued_1996}
\cite{amin_complex-valued_2012}
\cite{sarroff_complex_2018}

% subsection tasks_and_datasets (end)

\subsection{Radio Frequiency Digital Signal Predistortion} % (fold)
\label{sub:radio_freq_dpd}

Radio Frequency power amplifiers, being physical electronic devices, have imperfections such
as parasitic inductance and capacitance. This coupled with them being operated in saturation,
make their gain respond non-linearly to the input signal, adding undesirable interference and
spectral spreading. Although these effects can be minimized by careful circuit design, they
cannot be eliminated entirely \cite{citation_needed}. Digital signal predistortion aims at
linearizing the amplifier, by introducing signal-dependent compensating component to the input.
At the same time the non-linearities should be corrected on-device efficiently and with low
latency in order to reduce cross-channel interference and enable higher bandwidth utilization
in wireless transmitters.

\cite{traverso_low_2019} uses \rewrite{some group delay estimators of something};
\cite{schoukens_obtaining_2017} develops an iterative approach to inference of the predistortion for a given
signal \todo{unclear};

\cite{tarver_design_2019} models the predistorter as a paired real dense shallow neural network and
demonstrates viability and competitiveness of this approach against polynomial based DPD on an
FPGA implementation.

% About rfWEbLab
The ``RFWebLab'' platform is remote RF power amplifier setup with web-based API, that feeds
the user-submitted quadrature signal through a class AB GaN amplifier and sends-back the measured
output \cite{dpdcompetiton2018}. It is maintained by the GHz Centre at Chalmers University of
Technolgy and National Instruments \cite{landin_rfweblab_2015}.

We use a custom-written python interface to the WebLab setup that is compatible with the MATLAB
interface form the setup owner.

% subsection radio_freq_dpd (end)

% section experiments (end)

\section{Discussion and Related Research} % (fold)
\label{sec:discussion_and_related_research}

Bayesian inference is a very rich field of research with a large body of knowledge and techniques
that enable practical quantification of predictive, parameter, or model uncertainty and its
propagation into solutions of the problems of interest. It is not safeguarded against overfitting
and modelling biases: there are quite a handful of assumptions made every time a Bayesian model
is setup for inference. We need to have a prior belief, the model and its interaction with
the data (the likelihood), and even the posterior: although the Bayes formula is explicit in
how the posterior is derived, in all problems of at least some practical significance the
exact posterior inference involves analytically intractable expectations, compelling the use
of approximations. In addition to this, even if the likelihood and prior come from conjugate
families, making the posterior explicit, the questions of interest are usually concerned with
inference using the posterior predictive distribution, which is factorized as the conditional
predictive distribution given the model and new observation, and the posterior of the model
after observing the data.

Practical performance of variational dropout techniques was studied in \cite{citation_needed}
and \cite{citation_needed}. The most fierce critique of Bayesian approach towards model
sparsification was voiced in \cite{gale_state_2019}, where it was show that it yielded
inconsistent results in text translation tasks and systematically underperformed simpler
techniques such as norm pruning and $\ell_0$-regularization, \cite{louizos_learning_2017}.

The latter approach introduces stochastic masks one the parameters, which have hard-concrete
mask distribution. It is closely related to gumbel-softmax reparameterization trick,
\cite{kingma_auto-encoding_2014,jang_categorical_2017}: the mask values are, essentially,
$[0,1]$ clamped scaled sigmoids, that are randomly shifted relative to a learnable location
parameter, that indicates the degree of weight's relevance. The penalty in the objective is
the expected number of nonzero parameters, and is a smooth approximation to $\ell_0$ norm.
This approach is related to stochastic, rather than bayesian networks: it is formulated in
terms of empirical risk minimization of the negative $\log$-likelihood term in \eqref{eq:elbo}.

% section discussion_and_related_research (end)

\section{Conclusion} % (fold)
\label{sec:conclusion}

% section conclusion (end)

\clearpage

\bibliographystyle{amsplain}
\bibliography{references}
\nocite{*}

\clearpage

\section{Appendix} % (fold)
\label{sec:appendix}

\subsection{Gradient of the KL-divergence in $\real$ case} % (fold)
\label{sub:real-chisq-grad}  % gradient_of_the_kl_divergence_in_R_case

In this section we derive the exact gradient of the KL-divergence term \eqref{eq:improper-kl-div-real}
for $\mathbb{R}$-dropout in case of a log-uniform prior. Even though the final expression for
the penalty term itself involves a derivative of a hypergeometric function, and the gradient,
essentially, relies on computing the error function, the following analysis provides independent
verification of the correctness of the approximation, proposed in \cite{molchanov_variational_2017}.
The logic of the derivation follows \cite{lapidoth_capacity_2003}.
% \cite{pav_moments_2015} correctly notice that \cite[p. 2466]{lapidoth_capacity_2003} has a missing $\log{2}$ term.

Let $(z_i)_{i=1}^m \sim \mathcal{N}(0, 1)$ iid and $
  (\mu_i)_{i=1}^m \in \mathbb{R}
$. The random variable $
  W = \sum_i (\mu_i + z_i)^2
$ is said to be $\chi^2_m(\lambda)$, i.e. noncentral $\chi^2$ with shape $m$ and noncentrality
parameter $\lambda = \sum_i \mu_i^2$. Its density is given by, \cite{citation_needed}
$$
f_W(x)
  % = e^{- \tfrac\lambda2} \sum_{n \geq 0} \tfrac{\bigl(\tfrac\lambda2\bigr)^n}{n!}
  %   \tfrac{
  %     x^{n + \tfrac{m}2 - 1} e^{-\tfrac{x}2}
  %   }{
  %     2^{n + \tfrac{m}2} \Gamma(n + \tfrac{m}2)
  %   }
  % = e^{- \tfrac\lambda2} \sum_{n \geq 0} \tfrac{\bigl(\tfrac\lambda2\bigr)^n}{n!}
  %     \tfrac{
  %         \bigl(\tfrac{x}2\bigr)^{n + \tfrac{m}2 - 1} e^{-\tfrac{x}2}
  %     }{
  %         2 \Gamma(n + \tfrac{m}2)
  %     }
  = \frac12 e^{- \tfrac{x + \lambda}2} \bigl(\tfrac{x}2\bigr)^{\tfrac{m}2 - 1}
    \sum_{n \geq 0} \tfrac{
      \bigl(\tfrac{x \lambda}4\bigr)^n
    }{
      n! \Gamma(n + \tfrac{m}2)
    }
  % = \frac12 e^{- \tfrac{x + \lambda}2}
  % \bigl(\tfrac{x}\lambda\bigr)^{\tfrac{m}4 - \tfrac12}
  % \bigl(\tfrac{x \lambda}4\bigr)^{\tfrac{m}4 - \tfrac12}
  % \sum_{n \geq 0} \tfrac{
  %         \bigl(\tfrac{x \lambda}4\bigr)^n
  %     }{
  %         n! \Gamma(n + \tfrac{m}2)
  %     }
  % = \frac12 e^{- \tfrac{x + \lambda}2}
  % \bigl(\tfrac{x}\lambda\bigr)^{\tfrac{m}4 - \tfrac12}
  % \bigl(\tfrac{\sqrt{x \lambda}}2\bigr)^{\tfrac{m}2 - 1}
  % \sum_{n \geq 0} \tfrac{
  %         \bigl(\tfrac{x \lambda}4\bigr)^n
  %     }{
  %         n! \Gamma(n + \tfrac{m}2)
  %     }
  % = \frac12 e^{- \tfrac{x + \lambda}2}
  % \bigl(\tfrac{x}\lambda\bigr)^{\tfrac{m - 2}4}
  % I_{\bigl(\tfrac{m}2 - 1\bigr)}(\sqrt{x \lambda})
  \,. $$
% where $I_k$ is the modified Bessel function of the first kind
% $$
% I_k(s)
%   = \Bigl(\frac{s}2\Bigr)^k
%       \sum_{n \geq 0} \tfrac{
%           \bigl( \tfrac{s}2 \bigr)^{2n}
%       }{n! \Gamma(n + k + 1)}
%   \,. $$

In the real multiplicative noise case we need to compute the kl-divergence penalty, the key
term of which is the expected logarithm of $W$:
\begin{align}
  \mathbb{E}_{W\sim \chi^2_m(\lambda)} \log W
    &= \int_0^\infty f_W(x) \log x dx
    \notag \\
    &= \frac12 e^{- \tfrac\lambda2}
    \int_0^\infty \sum_{n \geq 0} \biggl(
        \tfrac{\bigl(\tfrac\lambda2\bigr)^n}{n!}
        \tfrac{e^{- \tfrac{x}2}}{\Gamma(n + \tfrac{m}2)}
        \bigl(\tfrac{x}2\bigr)^{n + \tfrac{m}2 - 1}
    \biggr) \log x dx
    % = [\text{ absolute summability and Fubini, or any other conv. thm for integrals of non-negative integrals}]
    % = e^{- \tfrac\lambda2} \sum_{n \geq 0}
    %     \tfrac{\bigl(\tfrac\lambda2\bigr)^n}{n!}
    %     \tfrac1{\Gamma(n + \tfrac{m}2)}
    % \int_0^\infty
    %     e^{- \tfrac{x}2} \bigl(\tfrac{x}2\bigr)^{n + \tfrac{m}2 - 1}
    %     (\log2 + \log \tfrac{x}2) \tfrac{dx}2
    % = [u = \tfrac{x}2]
    \notag \\
    &= e^{- \tfrac\lambda2} \sum_{n \geq 0}
        \tfrac{\bigl(\tfrac\lambda2\bigr)^n}{n!}
    \tfrac1{\Gamma(n + \tfrac{m}2)}
    \int_0^\infty
        e^{- u} u^{n + \tfrac{m}2 - 1}
        (\log2 + \log u) du
    % = [\text{definitions:} \Gamma, \psi]
    % = e^{- \tfrac\lambda2} \sum_{n \geq 0}
    %     \tfrac{\bigl(\tfrac\lambda2\bigr)^n}{n!}
    % (\psi(n + \tfrac{m}2) + \log2)
    \notag \\
    &= \log{2}
    + e^{- \tfrac\lambda2} \sum_{n \geq 0}
        \tfrac{\bigl(\tfrac\lambda2\bigr)^n}{n!}
        \psi(n + \tfrac{m}2)
    \,,
\end{align}
where $\psi(x)$ is the digamma function, i.e.
$$
\psi(x)
  = \frac{d}{dx} \log \Gamma(x)
  = \frac1{\Gamma(x)}
    \int_0^\infty
      u^{x-1} e^{-u} \log{u}
    \, du
  \,. $$
The following properties of the digamma function will be used in the our analysis:
$
  \psi(z+1) = \psi(z) + \tfrac1z
$ and $
  \psi(\tfrac12) = -\gamma - 2\log 2
$. If we put
$$
g_m(x)
  % alpha: e^{-x} \sum_{n=0}^{\infty} \frac{x^n}{n!} \psi(n + m / 2)
  % = e^{-x} \sum_{n \geq 0} \frac{x^n}{n! \Gamma(n + \tfrac{m}2)}
  %     \int_0^\infty e^{-t} t^{n + \tfrac{m}2-1} \log{t} dt
  = e^{-x} \sum_{n \geq 0} \frac{x^n}{n!} \psi(n + \tfrac{m}2)
  \,, $$
then the desired expectation $
  \mathbb{E}_{z \sim \mathcal{N}(0, 1)}
    \log{\bigl\lvert z + \tfrac1{\sqrt{\alpha}} \bigr\rvert^2}
$ is equal to $
  \log{2} + g_1(\tfrac1{2\alpha})
$.

We can differentiate the series in $g_m(x)$, since the sum converges everywhere
on $\mathbb{R}$. Indeed, it is a power series featuring nonnegative coefficients,
which is dominated by $
  \sum_{n \geq 1} \tfrac{x^n}{n!} \log{(n+\tfrac{m}2)}
$, because $\psi(x)\leq \log x - \tfrac1{2x}$. By the ratio test, the dominating
series has infinite radius:
$$
\lim_{n\to\infty}
  \biggl\lvert
    \frac{
      n! x^{n+1} \log{(n + 1 + \tfrac{m}2)}
    }{
      x^n \log{(n + \tfrac{m}2)} (n+1)!
    }
  \biggr\rvert
  = \lim_{n\to\infty}
    \lvert x \rvert 
    \biggl\lvert
      \frac{
        \log{(n + 1 + \tfrac{m}2)}
      }{
        \log{(n + \tfrac{m}2)} (n+1)
      }
    \biggr\rvert
  % = \lim_{n\to\infty}
  %   \lvert x \rvert 
  %   \biggl\lvert
  %     \frac{
  %       n + \tfrac{m}2
  %     }{
  %       (n + 1 + \tfrac{m}2)((n+1) + (n + \tfrac{m}2) \log{(n + \tfrac{m}2)})
  %     }
  %   \biggr\rvert
  = 0 < 1
  \,, $$
since
$$
\frac{\log{(x + a + 1)}}{x \log{(x + a)}}
  \sim \frac{\log{(x+1)}}{(x-a) \log{x}}
  \sim \frac{\log{(x+1)}}{x \log{x}}
  \sim \frac{\tfrac1{(x+1)}}{1 + \log{x}}
  \to 0
  \,. $$
A theorem from calculus states, that the formal series derivative (integral)
coincides with the derivative (integral) of the function, corresponding to
the power series (everywhere on the convergence region). And the convergence
regions of derivative (integral) coincide with the region of the original
power series.

Differentiating the series within $g_m$ yields
$$
\frac{d}{d x} g_m(x)
  % = e^{-x} \sum_{n\geq 1} \frac{x^{n-1}}{(n-1)!} \psi(n + \tfrac{m}2) - g_m(x)
  % = e^{-x} \sum_{n\geq 0} \frac{x^n}{n!} \psi(n + \tfrac{m}2 + 1) - g_m(x)
  % = e^{-x} \sum_{n\geq 0} \frac{x^n}{n!} (
  %     \psi(n + \tfrac{m}2 + 1) - \psi(n + \tfrac{m}2)
  % )
  % = e^{-x} \sum_{n\geq 0} \frac{x^n}{n!} \tfrac1{n + \tfrac{m}2}
  = e^{-x} \sum_{n\geq 0} \frac{x^n}{n!} (n + \tfrac{m}2)^{-1}
  = \cdots
  \,. $$
Now, observe that $
    e^t  = \sum_{n\geq 0} \tfrac{t^n}{n!}
$ on $\mathbb{R}$, for $\alpha\neq 0$ we have $
  \int_0^x t^{\alpha-1} dt
    = \tfrac{x^\alpha}{\alpha}
$ and that
$$
\sum_{n\geq 0} \int_0^x \frac{t^{n+\alpha-1}}{n!} dt
  = \int_0^x \sum_{n\geq 0} \frac{t^{n+\alpha-1}}{n!} dt
  = \int_0^x t^{\alpha-1} e^t dt
  \,, $$
by the monotone convergence theorem on $
  ([0, x], \mathcal{B}([0, x]), dx)
$ whence
$$
\cdots
  = x^{-\tfrac{m}2} e^{-x} \sum_{n\geq 0}
      \frac{x^{n + \tfrac{m}2}}{n!} (n + \tfrac{m}2)^{-1}
  % = x^{-\tfrac{m}2} e^{-x} \sum_{n\geq 0}
  %     \frac1{n!} \int_0^x t^{n + \tfrac{m}2 - 1} dt
  % = x^{-\tfrac{m}2} e^{-x}
  %     \int_0^x t^{\tfrac{m}2 - 1} \sum_{n\geq 0} \frac{t^n}{n!} dt
  = x^{-\tfrac{m}2} e^{-x}
      \int_0^x t^{\tfrac{m}2 - 1} e^t dt
  = \cdots
  \,. $$
The substitution $u^2 = t$ on $[0, \infty]$ with $2u du = dt$ results in
$$
\int_0^x t^{\tfrac{m}2 - 1} e^t  dt
  % = \int_0^{\sqrt{x}} u^{m - 2} e^{u^2} 2 u du
  = 2 \int_0^{\sqrt{x}} u^{m - 1} e^{u^2} du
  \,, $$
whence
$$
\frac{d}{d x} g_m(x)
  % = x^{-\tfrac{m}2} e^{-x}
  %     \int_0^x t^{\tfrac{m}2 - 1} e^t dt
  = 2 x^{-\tfrac{m}2} e^{-x}
      \int_0^{\sqrt{x}} u^{m - 1} e^{u^2} du
  \,. $$
In particular, for $m=1$ we get
$$
g_1(x)
  = - \gamma - 2 \log{2}
  + e^{-x} \sum_{n\geq 0} \frac{x^n}{n!} \sum_{p=1}^n \frac2{2p - 1}
  \,, $$
and the derivative of the KL-term can be computed thus 
$$
\frac{d}{d x} g_1(x)
  = 2 \tfrac{F(\sqrt{x})}{\sqrt{x}}
  \,, $$
using Dawson's integral $
  F \colon \mathbb{R} \to \mathbb{R}
  \colon x \mapsto e^{-x^2} \int_0^x e^{u^2} du
$ -- a special function, implemented in most scientific computing libraries, e.g.
``scipy.special.dawsn''.

The derivative wrt $\alpha$ is 
$$
\tfrac{d}{d \alpha} g_1(\tfrac1{2\alpha})
  = -\tfrac1{2 \alpha^2} g_1'(\tfrac1{2\alpha})
  % = -\tfrac1{2 \alpha^2} 2 \tfrac{F(\sqrt{\tfrac1{2\alpha}})}{\sqrt{\tfrac1{2\alpha}}}
  % = -\tfrac1{2 \alpha^2} 2 \tfrac{F(\tfrac1{\sqrt{2\alpha}})}{\tfrac1{\sqrt{2\alpha}}}
  = -\tfrac1{\alpha} \sqrt{\tfrac2{\alpha}} F(\tfrac1{\sqrt{2\alpha}})
  \,. $$
However, since $\alpha$ is nonnegative, it is typically parameterized via its logarithm
and computed when needed. Thus, in particular, the gradient of the divergence penalty w.r.t
$\log \alpha$ is

\begin{equation} \label{eq:real-kl-div-deriv-log}
  \frac{d}{d\log \alpha}
    \tfrac12 \mathbb{E}_{z \sim \mathcal{N}(0,1)}
    \log \lvert z + \tfrac1{\sqrt{\alpha}} \rvert^2
    = \frac12 \frac{d\alpha}{d\log \alpha}
      \frac{d}{d\alpha} \bigl(\mathbb{E}\cdots \bigr)
    % = - \frac\alpha2 \tfrac1{\alpha}
    %   \sqrt{\tfrac2{\alpha}} F(\tfrac1{\sqrt{2\alpha}})
    = - \tfrac1{\sqrt{2\alpha}} F(\tfrac1{\sqrt{2\alpha}})
    \,.
\end{equation}

We replicated the simulation experiment in \cite{molchanov_variational_2017} and recovered
the same nonlinear approximation result reported therein. We sampled $10^7$ draws of  and 
The coefficients are within
$1\%$ relative tolerance of the reported.
$$
- KL(\mathcal{N}(w \mid \mu, \alpha \mu^2) \|
    \tfrac1{\lvert w \rvert})
  % = \tfrac12 \log \alpha
  %   - \mathbb{E}_{\xi \sim \mathcal{N}(1, \alpha)}
  %   \log{\lvert \xi \rvert} + C
  \approx
    k_1 \sigma(k_2 + k_3 \log \alpha) + C \big\vert_{C = -k1}
    - \tfrac12 \log (1 + e^{-\log \alpha})
  \,. $$
% in parctial implementations we suggest using softplus to numerically comptue the last
% term, since it is typically implemented in a floating-point stable fashion.
The numerically estimated derivative of the penalty term wrt $\log \alpha$ using forward
differences seems to be following \eqref{eq:real-kl-div-deriv-log} very closely (up to
sampling error) see fig.~\ref{fig:molchanov-derivative-replica}.

\begin{figure}[!ht]
  \centering
  \begin{subfigure}[b]{0.47\textwidth}
    \includegraphics[draft]{../notebooks/assets/curve_fit.pdf}
  \end{subfigure}%\hspace{-2.em}
  \begin{subfigure}[b]{0.47\textwidth}
    \includegraphics[draft]{../notebooks/assets/grad_log.pdf}
  \end{subfigure}
  \caption{Fit of the regression \cite{molchanov_variational_2017}, and the accuracy of
  the derivative wrt $\log{\alpha}$.}
  \label{fig:molchanov-derivative-replica}
\end{figure}

Now in SGD (and specifically in SGVB) we are concerned more with the gradient field, induced
by the potential (which is the loss function), rather than the value itself. Thus, as far as
the regularizing penalty term is concerned, which is used to regularize the loss objective,
we can essentially ignore it's forward pass value (level) and just compute its gradient
(subgradient, normal cone) with respect the parameter of interest in sgd. (unless it is a
part of a constraint, ie. downstream computation)

% subsection real-chisq-grad (end)

\subsection{Backpropagation through $\cplx$-networks} % (fold)
\label{sub:wirtinger_calculus}

TLDR: we use Wirtinger calculus!

% essential intro into Wirtinger calculus (CR)
Take $f\colon \cplx \to \cplx$ and identify it with $F\colon \real^2 \to \cplx$ function
via $F(u, v) = f(z)\vert_{z=u + j v}$. Wirtinger calculus introduces two formal derivative
operators \rewrite{(this seems to be very verbatim)}
$
  \tfrac{\partial}{\partial z}
    = \tfrac12 \bigl(
      \tfrac{\partial}{\partial u}
      - j \tfrac{\partial}{\partial v}
    \bigr)
$ and $
  \tfrac{\partial}{\partial \conj{z}}
    = \tfrac12 \bigl(
      \tfrac{\partial}{\partial u}
      + j \tfrac{\partial}{\partial v}
    \bigr)
$, defines $dz = du + j dv$, $d\conj{z} = du - j dv$, and the differential of $f$ as
$$
df = \tfrac{\partial f}{\partial z} dz
    + \tfrac{\partial f}{\partial \conj{z}} d\conj{z}
   % = \tfrac12\bigl(
   %    \tfrac{\partial}{\partial u}
   %    - j \tfrac{\partial}{\partial v}
   % \bigr) F (du - j dv)
   % + \tfrac12\bigl(
   %    \tfrac{\partial}{\partial u}
   %    + j \tfrac{\partial}{\partial v}
   % \bigr) F (du - j dv)
   % = \tfrac12 \bigl(
   %    \tfrac{\partial F}{\partial u} du - j \tfrac{\partial F}{\partial v} du
   %    + j \tfrac{\partial F}{\partial u} dv + \tfrac{\partial F}{\partial v} dv
   % \bigr)
   % + \tfrac12 \bigl(
   %    \tfrac{\partial F}{\partial u} du + j \tfrac{\partial F}{\partial v} du
   %    - j \tfrac{\partial F}{\partial u} dv + \tfrac{\partial F}{\partial v} dv
   % \bigr)
   = \tfrac{\partial F}{\partial u} du
     + \tfrac{\partial F}{\partial v} dv
   = dF
  \,. $$
Thus the complex value and its conjugate are treated as independent variables. In this notation
Cauchy-Riemann conditions are expressed as $
  \tfrac{\partial f}{\partial \conj{z}} = 0
$, or $
  -j\tfrac{\partial F}{\partial v} = \tfrac{\partial F}{\partial v}
$. These conditions impose a rigid structure on real and imaginary parts of $F(u, v)$, namely $
  \tfrac{\partial F_{\Re }}{\partial u} = \tfrac{\partial F_{\Im }}{\partial v}
$ and $
  \tfrac{\partial F_{\Re }}{\partial v} = - \tfrac{\partial F_{\Im }}{\partial u}
$. Thus Wirtinger calculus subsumes the usual $\cplx$-calculus, when $
  \tfrac{\partial f}{\partial \conj{z}} = 0
$, i.e. $
  f(z)
    % = g(z, \conj{z})
    = F(\tfrac12 (z + \conj{z}), \tfrac1{j 2} (z - \conj{z}))
$ does not depend on $\conj{z}$.

For a real-valued $f\colon \cplx \to \real$ we have $\conj{f} = f$, whence $
  \tfrac{\partial f}{\partial \conj{z}}
    = \tfrac{\partial \conj{f}}{\partial \conj{z}}
    = \conj{\tfrac{\partial f}{\partial z}}
$. Hence
$$
df
  = \tfrac{\partial f}{\partial z} dz
    + \tfrac{\partial f}{\partial \conj{z}} d\conj{z}
  % = \conj{\tfrac{\partial \conj{f}}{\partial \conj{z}}} dz
  % + \conj{\conj{\tfrac{\partial f}{\partial \conj{z}}} dz}
  = 2 \Re \Bigl(
    \conj{\tfrac{\partial f}{\partial \conj{z}}} dz
  \Bigr)
  = 2 \Re \bigl(
    \tfrac{\partial f}{\partial z} dz
  \bigr)
  \,. $$
Hence the gradient, being the direction of \rewrite{maximal growth} of $f$ at $z$ is given by $
  \tfrac{\partial f}{\partial \conj{z}}
    = \tfrac{\partial F}{\partial u}
      + j \tfrac{\partial F}{\partial v}
$. Thus under Wirtinger calculus it is possible to reuse $\real$-backpropagation.

% Show that $dh(z) = df(g(z)) dg(z)$.
% $h(z) = f(g(z)) = F(G_r(u, v), G_i(u, v)) = H(u, v)$
% $$
% dH
%   = \tfrac{\partial F}{\partial x} \tfrac{\partial G_r}{\partial u} du
%   + \tfrac{\partial F}{\partial x} \tfrac{\partial G_r}{\partial v} dv
%   + \tfrac{\partial F}{\partial y} \tfrac{\partial G_i}{\partial u} du
%   + \tfrac{\partial F}{\partial y} \tfrac{\partial G_i}{\partial v} dv
%   = \tfrac{\partial F}{\partial r} d\Re g(z)
%   + \tfrac{\partial F}{\partial i} d\Im g(z)
%   = df(\Re g(z) + j\Im g(z)) d g(z)
%   = df(g(z)) d g(z)
%   \,. $$

% subsection wirtinger_calculus (end)

\subsection{$\cplx$-Linear operator representation} % (fold)
\label{sub:c-linear_operator_representation}

% proof that such operators exist and are unique (well this is an obvious statement)
Consider $L \colon \cplx^m \to \cplx^n$ -- linear in $\cplx$. Then $
  L(u + jv) = L u + j L v
$ for any $u, v \in \real^m$, which implies that the effect of $L$ as $\cplx$-linear
operator is determined by its restriction onto $\real^n$. Let $
  F = L\vert_{\real^m}
  \colon \real^m \to \cplx^n
$ and observe that $F_r = \Re \circ F$ and $F_i = \Im \circ F$ are $\real$-linear operators
such that $F = F_r + j F_i$ (pointwise). Indeed,
$$
  F_r(a + \lambda b)
  % = \Re F(a + \lambda b)
  = \Re L(a + \lambda b)
  % = \Re \bigl( L a + \lambda L b \bigr)
  = \Re L a + \lambda \Re L b
  % = \Re F a + \lambda \Re F b
  = F_r a + \lambda F_r b
  \,. $$
Therefore for any $\cplx$-linear operator $L$ there are $\real$-linear operators $U, V$
such that
$$
L z 
  = (U + j V) (\Re z + j \Im z)
  % = (U + j V) \Re z + j (U + j V) \Im z
  % = U \Re z + j V \Re z + j \bigl(U \Im z + j V \Im z \bigr)
  = U \Re z - V \Im z + j \bigl( V \Re z + U \Im z \bigr)
  % = (U + j V) z
  \,. $$
Uniqueness of these operators follows, if this decomposition is applied to any $z$ with
$\Im z = 0$.

% subsection c-linear_operator_representation (end)

\subsubsection{MGF of a noncentral $\chi^2$} % (fold)
\label{ssub:mgf_of_a_noncentral_chi}

Consider the mgf of $W$:
$$
M_W(t)
  = \mathbb{E}(e^{Wt})
  = \prod_i \mathbb{E}(e^{(\mu_i + z_i)^2 t})
  \,, $$
by independence. Now for $z \sim \mathcal{N}(\mu, 1)$
$$
\mathbb{E}(e^{z^2 t})
  = \tfrac1{\sqrt{2\pi}}
  \int_{-\infty}^{+\infty}
      e^{z^2 t} e^{-\tfrac{(z-\mu)^2}2}
  dz
  \,. $$
Now, for $t < \tfrac12$
$$
z^2 t - \tfrac{(z - \mu)^2}2
  = - \tfrac12 (1 - 2t) z^2 + z \mu - \tfrac{\mu^2}2
  % = - \tfrac12 (1 - 2t) \bigl(
  %   z^2 - 2 z \tfrac\mu{1 - 2t} + \tfrac{\mu^2}{1 - 2t}
  % \bigr)
  % = - \tfrac12 (1 - 2t) \bigl( z - \tfrac\mu{1 - 2t} \bigr)^2
  % - \tfrac12 (1 - 2t) \bigl(
  %   \tfrac{\mu^2}{1 - 2t}
  %   - \tfrac{\mu^2}{(1 - 2t)^2}
  % \bigr)
  % = - \tfrac12 (1 - 2t) \bigl( z - \tfrac\mu{1 - 2t} \bigr)^2
  %   - \tfrac{\mu^2}2 \bigl(
  %   \tfrac{1 - 2t}{1 - 2t} - \tfrac1{1 - 2t}
  % \bigr)
  % = - \tfrac12 (1 - 2t) \bigl( z - \tfrac\mu{1 - 2t} \bigr)^2
  %   + \tfrac{\mu^2}2 \tfrac{2t}{1 - 2t}
  = - \tfrac12 (1 - 2t) \bigl( z - \tfrac\mu{1 - 2t} \bigr)^2
    + \mu^2 \tfrac{t}{1 - 2t}
  \,, $$
whence
\begin{multline}
  \mathbb{E}(e^{z^2 t})
    = \tfrac1{\sqrt{2\pi}}
      \int_{-\infty}^{+\infty}
        e^{z^2 t} e^{-\tfrac{(z-\mu)^2}2}
      \, dz
    % = e^{\mu^2 \tfrac{t}{1 - 2t}}
    %   \tfrac1{\sqrt{2\pi}}
    %   \int_{-\infty}^{+\infty}
    %     e^{- \tfrac12 (1 - 2t) \bigl( z - \tfrac\mu{1 - 2t} \bigr)^2}
    %   \, dz
    \\= e^{\mu^2 \tfrac{t}{1 - 2t}}
      \tfrac1{\sqrt{2\pi}}
      \int_{-\infty}^{+\infty}
        e^{- \tfrac12 (1 - 2t) z^2}
      \, dz
    % = [u = \sqrt{1 - 2t} z]
    % = e^{\mu^2 \tfrac{t}{1 - 2t}}
    %   \tfrac1{\sqrt{2\pi}}
    %   \int_{-\infty}^{+\infty}
    %     e^{- \tfrac12 u^2}
    %   \, \tfrac{du}{\sqrt{1 - 2t}}
    = \tfrac{
        \exp{\{\mu^2 \tfrac{t}{1 - 2t}\}}
    }{\sqrt{1 - 2t}}
    \,.
\end{multline}
Therefore
$$
M_W(t)
  = \mathbb{E}(e^{Wt})
  = \prod_i \tfrac{
      e^{\mu_i^2 \tfrac{t}{1 - 2t}}
    }{\sqrt{1 - 2t}}
  % = e^{\lambda \tfrac{t}{1 - 2t}}
  %   (1 - 2t)^{-\tfrac{m}2}
  % = e^{\lambda \tfrac{- t}{2t - 1}}
  %   (1 - 2t)^{-\tfrac{m}2}
  % = e^{\tfrac\lambda2 \tfrac{1 - 2t - 1}{2t - 1}}
  %   (1 - 2t)^{-\tfrac{m}2}
  % = e^{- \tfrac\lambda2 (1 + \tfrac1{2t - 1})}
  %   (1 - 2t)^{-\tfrac{m}2} 
  = e^{- \tfrac\lambda2} e^{\tfrac\lambda2 \tfrac1{1 - 2t}}
  (1 - 2t)^{-\tfrac{m}2}
  \,. $$
Expanding the exponential as infinite series:
\begin{multline}
  M_W(t)
    = e^{- \tfrac\lambda2} e^{\tfrac\lambda2 \tfrac1{1 - 2t}}
    (1 - 2t)^{-\tfrac{m}2}
    % = e^{- \tfrac\lambda2} (1 - 2t)^{-\tfrac{m}2}
    %   \sum_{n \geq 0} \tfrac{\bigl(\tfrac\lambda2\bigr)^n}{n! (1 - 2t)^n}
    \\= \sum_{n \geq 0} \tfrac{e^{- \tfrac\lambda2} \bigl(\tfrac\lambda2\bigr)^n}{n!}
        (1 - 2t)^{-\tfrac{2n + m}2}
    = \sum_{n \geq 0} \tfrac{e^{- \tfrac\lambda2} \bigl(\tfrac\lambda2\bigr)^n}{n!}
        \mathbb{E}_{x \sim \chi^2_{m + 2n}}(e^{x t})
    \,.
\end{multline}

% subsubsection mgf_of_a_noncentral_chi (end)

% section appendix (end)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\clearpage

\section{Trunk} % (fold)
\label{sec:trunk}

In the case of $\real$-valued variational dropout \cite{kingma_variational_2015} approximate
\eqref{eq:expect-improper-term-cplx} by a non-linear regression, fit to the Monte-Carlo estimates
of the expectation for $\alpha$ varying over a logarithmic grid. This approximation was greatly
refined in \cite{molchanov_variational_2017} -- an improvement that enabled doing away with
the clipping of the dropout rate (relevance score) $\alpha$. In fact in the real case the analogue
of the last term in \eqref{eq:expect-improper-term-cplx} is half the log-moment of a non-central
$\chi^2$ distribution with shape $1$ and non-centrality $\lambda = \tfrac1{\alpha}$. Unfortunately,
there is no known expression (even involving special functions) for this expectation for
$\chi^2_m$ with odd shape parameter $m$ (degrees of freedom) \verify{this}. Quite fortunately
there is one for even degrees of freedom.

%%%%%%%
\todo{why this is better than a general $\cplx$-gaussian? Three parameters?}

\important{``pytorch'' specific}
Otherwise we have to offload the values from the device to cpu, compute the special
function there, and transfer back.

Why sparsity matters, why $\cplx$ networks?

Where are $\cplx$-networks used? and do these applications warrant sparsity?

Gist of the LRP (kingmaetal2015)
translating uncertainty (randomness) from parameters to activations
  adds noise -- helps regularization
  emulates one draw per batch element -- decorrelates gradient within the batch
  reduces computations (memory), leverages batched matmuls (or convos)
  decreases variance of the gradient

additive noise reparameterization (molchanov\_variational\_2017) $(\mu, \alpha \mu^2)$:
  less noisy gradient wrt $\mu$, $\alpha$ recomputed on-the-fly

\subsection{$\cplx$-valued networks} % (fold)
\label{sub:c_valued_networks}

In this section i remind the reader what the complex-valued networks are, how
they are implemented and how much of $\cplx$-ness they have. Mention careful
design.

I will describe the linear layers (dense, masked, and convolutions) and
activations borrowed straight from the $\real$-values networks. Then i shall
mention that this has been tried before and list papers that one way or another
address $\cplx$-data processing with neural networks.

It is worth pointing out that the key advantage of
the $\cplx$-constraints is that they permit use of Strassen's $3$M multiplication algorithm,
potentially \verify{saving up} to $25\%$ on floating point multiplications. \todo{
  in contrast to what? to na{\:i}ve (obvious)? to paired-$\real$ ($2 \times 2$-$2\times 1$
  -- 4 fmul)?
}

% subsection c_valued_networks (end)

\section{Complex Variational Dropout} % (fold)
\label{sec:complex_variational_dropout}

In this section we outline and derive the variational dropout technique for complex-%
valued networks, which re-traces the evolution of dropout technique for real-valued
weights.

% a second take on bayesian inference
The core question of Bayesian analysis is concerned with the distribution of the data model
after observing data and given the initial belief about it. The data model is typically a joint
distribution on the sample, which includes assumptions regarding independence and (conditional)
factorization of the distribution of each individual data point. In our case we suppose that
the data $
  \mathcal{D} = (z_i)_{i=1}^m
$, $z_i = (x_i, y_i)$ is independent and identically distributed under our model $m$: $
  p(\mathcal{D}\mid m)
    = \prod_i p(z_i\mid m)
$. The models we  our model $m$ comes from a parametric conditional distribution family, e.g. $
  p(z \mid m)
    = p(y \mid x, m) p(x \mid m)
    = p(y \mid x, m) p(x)
$ and $
  p(y \mid x, m)
    = \mathcal{N}\bigl(
      y\,\mid\, \mu_\omega(x)\,, \sigma^2_\omega(x)
    \bigr)
$, then we can (and do) identify $m$ with its parameters $\omega$. Instead of iid data in
$\mathcal{D}$, we could have assumed a Gaussian Process data model $
  y(x) \sim \mathrm{GP}(\mu, K)
$ for the mean function and covariance kernel $
  \mu
    \colon \mathcal{X} \to \real^d
$ and $
  K \colon \mathcal{X} \times \mathcal{X}
    \to \real^{d\times d}
$.

In the framework of Bayesian Inference we use the Bayes's rule as an exact method for deriving
the posterior parameter distribution from the likelihood of the data model and model's prior:
$
  p(\omega \mid \mathcal{D})
    = \tfrac{
      p(\mathcal{D} \mid \omega) \pi(\omega)
    }{
      p(\mathcal{D})
    }
$. Typically, exact inference involves an analytically intractable integrals, e.g. in the
denominator of the posterior $
  p(\mathcal{D})
    = \int p(\mathcal{D} \mid \omega) \pi(\omega) d\omega
$, or derived distributions, such as the predictive distribution $
  p(y \mid x, \mathcal{D})
    = \int p(y \mid x, \omega) p(\omega \mid \mathcal{D}) d\omega
$.

Variational Inference recasts the problem of posterior derivation into functional optimization
framework. The main idea is to find the closest approximation to the posterior $
  p(\omega \mid \mathcal{D})
$ in some family $
  \mathcal{Q}
$ of approximating distributions $
  q(\omega)
$ on the parameters $\omega$ of the model $m$ (or the model itself). The proximity between
distributions is measured either using MMD metric via embedding into some universal RKHS,
\cite{citation_needed}, Wasserstein \cite{citation_needed} \cite{citation_needed}, total
variation norm \cite{citation_needed}, or $f$-divergences
% $
%   \mathbb{E}_{\omega \sim q(\omega)} f\bigl(
%       \tfrac{p(\omega)}{q(\omega)}
%     \bigr)
% $ for a convex $f$ with $f(1) = 0$
\cite{citation_needed}, specifically Kullback-Leibler divergence. The key trade off in Variational
Inference is the choice of the approximating family that is rich enough to get close to the true
posterior, yet simple enough to sample from or for inferring derived distributions via Bayesian
averaging.

Despite the effort to simplify the bayesian analysis in the most commonly encountered cases
variational inference still requires dealing with analytically intractable expectations,
\cite{citation_needed}. This issue is dealt with by giving up deterministic precision to
gain efficiency from stochastic, since inaccuracies and assumptions are inevitable, especially
when modelling observations.

% a verbatim setion from my mlss2019 bdl notebook
In Bayesian Inference (\textbf{BI}) we \textit{assume} that the observation data $D$ follows a
\textit{model} $m$ with data generating distribution $p(D \mid m, \omega)$ \textit{governed by
unknown parameters} $\omega$. The goal of \textbf{BI} is to reason about the model and/or its
parameters, and new data given the observed data $D$ and our assumptions, i.e to seek the
\textbf{posterior} parameter and predictive distributions:

\begin{align}
p(d \mid D, m)
  &
  % = \mathbb{E}_{
  %   \omega \sim p(\omega \mid D, m)
  % } p(d \mid D, \omega, m)
  = \int p(d \mid D, \omega, m) p(\omega \mid D, m) d\omega
  \,, \\
p(\omega \mid D, m)
  &
  = \frac{p(D \mid \omega, m) \, \pi(\omega \mid m)}{p(D \mid m)}
  \,,
\end{align}
where
\begin{itemize}
  \item the \textbf{prior} distribution $\pi(\omega \mid m)$ reflects our belief before
  having made the observations
  \item the data distribution $p(D \mid \omega, m)$ reflects our assumptions about the data
  generating process, and determines the model \textbf{likelihood} (Gaussian, Categorical,
  Poisson etc.)
\end{itemize}
Unless the distributions and likelihoods are conjugate, posterior in Bayesian inference is
typically intractable and it is common to resort to \textbf{Variational Inference} or
\textbf{Monte Carlo} approximations.

Since inference using the exact posterior is rarely tractable, efficient and unbiased approximation
schemes are typically used. One such scheme is Variational Inference, which casts the inference
task into the domain of optimization problems over some appropriately chosen the posterior
distribution approximation family. The key idea of the former is to seek an approximation
$q(\omega)$ to the intractable posterior $p(\omega \mid D, m)$, via a variational optimization
problem over some parametric family of distributions $\mathcal{Q}$:
$$
q^*(\omega)
    \in \arg \min_{q\in \mathcal{Q}}
      \mathrm{KL}(q(\omega) \| p(\omega \mid D, m))
  \,, $$
where the Kullback-Leibler divergence between $P$ and $Q$ ($P\ll Q$) with densities $p$ and $q$,
respectively, is given by
$$
\mathrm{KL}(q(\omega) \| p(\omega))
  % = \mathbb{E}_{\omega \sim Q} \log \tfrac{dQ}{dP}(\omega)
  = \mathbb{E}_{\omega \sim q(\omega)}
    \log \tfrac{q(\omega)}{p(\omega)}
  \,.
  % \tag{kl-div}
  $$

Note that the family of variational approximations $\mathcal{Q}$ can be structured
\textbf{arbitrarily}: point-mass, products, mixture, dependent on input, having mixed hierarchical
structure, -- any distribution, even unnormalized. Although computing the divergence w.r.t.
the unknown posterior is still hard and intractable, it is possible to do away with it
through the following identity, which is based on the Bayes rule.

For \textbf{any} $q(\omega) \ll p(\omega \mid D; \phi)$ and any model $m$

\begin{align}
\overbrace{
  \log p(D \mid m)
}^{\text{evidence}}
  &= \overbrace{
    \mathbb{E}_{\omega \sim q} \log p(D\mid \omega, m)
  }^{\text{expected conditional likelihood}}
  - \overbrace{
    \mathrm{KL}(q(\omega)\| \pi(\omega \mid m))
  }^{\text{proximity to prior belief}}
  \\
  &+ \underbrace{
    \mathrm{KL}(q(\omega)\| p(\omega \mid D, m))
  }_{\text{posterior approximation}}
\,.
\tag{master-identity}
\end{align}
Instead of minimizing the divergence of the approximation from the posterior, we can maximize
the \textbf{Evidence Lower Bound} with respect to $q(\omega)$:
$$
q^* \in
  \arg\max_{q\in Q}
    \mathcal{L}(q)
    = \mathbb{E}_{\omega \sim q} \log p(D\mid \omega, m)
      - \mathrm{KL}(q(\omega)\| \pi(\omega \mid m))
  \,.
  % \tag{max-ELBO}
  $$
The intuition is that the expected $\log$-likelihood favours $q$ that place their mass on
parameters $\omega$ that explain $D$ under the specified model $m$. At the same time
the negative KL-divergence discourages the approximation $q$ from straying too far away
from to the prior belief $\pi$ under $m$.

We usually consider the following setup (conditioning on model $m$ is omitted):
\begin{itemize}
  \item the likelihood factorizes $
    p(D \mid \omega)
        = \prod_i p(y_i, x_i \mid \omega)
        \propto \prod_i p(y_i \mid x_i, \omega)
  $
  for $D = (x_i, y_i)_{i=1}^N$

  \item the variational posterior approximation is parameterized by $\theta$: $q(\omega \mid \theta)$

  \item the prior on $\omega$ also depends on hyper-parameters $\lambda$, that can be fixed,
  or variable ($\pi(\omega \mid \lambda)$).
\end{itemize}

In this case the variational objective (evidence lower bound)
$$
\log p(D\mid \lambda )
  \geq \mathcal{L}(\theta, \lambda)
    = \mathbb{E}_{\omega \sim q(\omega \mid \theta)}
      \sum_i \log p_\phi(y_i \mid x_i, \omega)
    - KL(q(\omega \mid \theta) \| \pi(\omega \mid \lambda))
  \,, $$
is maximized with respect to $\theta$ (to approximate the posterior).

Priors can be
\begin{itemize}
  \item \textit{subjective}, i.e. reflecting prior beliefs (but not arbitrary)
  \item \textit{objective}, i.e. reflecting our lack of knowledge
  \item \title{empirical}, i.e. learnt from the observed data (optimized over
  hyper-parameters $\lambda$)
\end{itemize}

The stochastic variant of ELBO is formed by randomly batching
the dataset $D$:
$$
\mathcal{L}(\theta, \lambda)
  \approx \mathcal{L}_\mathrm{SGVB}(\theta, \lambda)
  = \lvert D \rvert \biggl(
    \tfrac1{\lvert B \rvert}
      \sum_{b \in B} \mathbb{E}_{\omega \sim q(\omega \mid \theta)}
        \log p(y_b \mid x_b, \omega)
  \biggr)
  - KL(q(\omega \mid \theta) \| \pi(\omega \mid \lambda))
  \,. $$

Stochastic optimization follows noisy unbiased gradient estimates, which are usually cheap and
allow escaping from local optima, but optimize the objective in expectation. In order to get
a gradient of $
  F_\theta = \mathbb{E}_{\omega \sim q(\omega \mid \theta)} f(\omega)
$ w.r.t $\theta$ we use either:
\begin{itemize}
  \item (REINFORCE) $
    \nabla_\theta F_\theta
      = \mathbb{E}_{\omega \sim q(\omega \mid \theta)}
        (f(\omega) - b_\theta) \nabla_\theta \log q(\omega \mid \theta)
  $ for some $b_\theta$ that is used to control variance

  \item (reparameterization) $
    \nabla_\theta F_\theta
      = \nabla_\theta \mathbb{E}_{\varepsilon \sim q(\varepsilon)}
        f(g(\theta; \varepsilon))
      = \mathbb{E}_{\varepsilon \sim q(\varepsilon)}
        \nabla_\theta g(\theta; \varepsilon)
          \nabla_\omega f(\omega) \big\vert_{\omega = g(\theta; \varepsilon)}
    $ when there are $q$ and differentiable $g$, such that sampling from $
      q(\omega \mid \theta)
    $ is equivalent to $
      \omega = g(\theta; \varepsilon)
    $ with $\varepsilon \sim q(\varepsilon)$
\end{itemize}

The variational approximation might yield high dimensional integrals, which are slow/prohibitive
to compute. To make the computations faster without foregoing much of the precision, we may use
Monte Carlo estimator:
$$
\mathbb{E}_{\omega \sim q(\omega\mid \theta)} \, f(\omega)
  \overset{\text{MC}}{\approx}
    \frac1{\lvert \mathcal{W}\rvert}
      \sum_{\omega \in \mathcal{W}} f(\omega)
  \,, $$
where $\mathcal{W} = (\omega_b)_{b=1}^B$ is a sample of independent draws from $
  q(\omega\mid \theta)
$. If we also approximate the expectation wrt model parameters in the gradient of ELBO via Monte
Carlo we get the \textbf{doubly stochastic variational objective}:
$$
\nabla_\theta \mathcal{L}_\mathrm{DSVB}(\theta, \lambda)
  \approx
    \lvert D \rvert \biggl(
      \tfrac1{\lvert B \rvert}
        \sum_{b \in B}
          \mathop{gradient}(x_b, y_b)
    \biggr)
    - \nabla_\theta KL(q(\omega \mid \theta) \| \pi(\omega \mid \lambda))
  \,, $$
where `gradient` is $
  \nabla_\theta
    \mathbb{E}_{\omega \sim q(\omega \mid \theta)}
      \log p(y \mid x, \omega)
$ using one of the approaches above, typically approximated using one independent draw of $\omega$
per $b\in B$. We can use a similar sampling approach to compute the gradient of the divergence term.

We can estimate the divergence term in the ELBO with Monte Carlo, or, for example, for the
predictive distribution we have
\begin{align}
\mathbb{E}_{y\sim p(y\mid x, D, m)} \, g(y)
  &
  \overset{\text{BI}}{=}
    \mathbb{E}_{\omega\sim p(\omega \mid D, m)}
      \mathbb{E}_{y\sim p(y\mid x, \omega, D, m)} \, g(y)
  \\
  &
  \overset{\text{VI}}{\approx}
    \mathbb{E}_{\omega\sim q(\omega)}
      \mathbb{E}_{y\sim p(y\mid x, \omega, D, m)} \, g(y)
  \\
  &
  \overset{\text{MC}}{\approx}
    % \hat{\mathbb{E}}_{\omega \sim \mathcal{W}}
    %   \mathbb{E}_{y\sim p(y\mid x, \omega, D, m)} \, g(y)
    \frac1{\lvert \mathcal{W}\rvert} \sum_{\omega \in \mathcal{W}}
      \mathbb{E}_{y\sim p(y\mid x, \omega, D, m)} \, g(y)
  \,,
\end{align}
where $\mathcal{W} = (\omega_b)_{b=1}^B \sim q(\omega)$ -- iid samples from the variational
approximation.

\bigskip

% on bernoulli dropout
Bernoulli dropout alleviates the problem of overfitting

% on gaussian dropout

% revirew of kingma and lrt
The key contributions of \cite{kingma_variational_2015} are reinterpretation of dropout
as a variational inference method and the analysis of the effects that the local reparameterization
trick has on the efficiency of the gradient estimator in stochastic variational inference,
\cite{citation_needed}.

\cite{kingmaetal2015} argue that Gaussian dropout, being a multiplicative parameter noise,
can be interpreted as variational inference via factorized Gaussian posterior approximation
$q(\omega)$ that optimizes the $\log$-likelihood term from the Evidence Lower Bound. In a fully
Bayesian treatment, the dropout rate $p \in (0, 1)$, which governs the regularization strength,
would appear in the KL-divergence term of ELBO through the corresponding odds $
  \alpha = \tfrac{p}{1-p}
$, which acts a variance scaling factor in the posterior approximation. Having made $\alpha$
a learnable parameter of the variational approximation, \cite{kingmaetal2015} natuallry propose
letting it vary on the per-parameter basis, which allows for even more flexible posterior
approximations. % who proposed sparsification?

The local reparameterization trick, proposed by \cite{citation_wang_menning_2013} in the context
of Bernoulli and Gaussian dropout regularization techniques \cite{citation_needed}, translates
the uncertainty about global parameters to noise in the local intermediate state and utilizes
the closure of Gaussian distribution under affine transformations. Computational advantage of
the trick is that activation noise is cheaper to sample and store for the purposes of backpropagation,
than independently sampling parameters from the posterior approximation individually for each
element of the minibatch. As far as Bayesian inference is concerned, \cite{kingma_variational_2015}
have shown that trick's beneficial effects on minibatch SGD convergence come via two mechanisms
of likelihood gradient estimator's efficiency: decorrelation within the batch (independent noise
draws) and variance reduction through local transfer of parameter uncertainty to activation noise.

\begin{quote}

in practice the performance of stochastic gradient methods depends on the variance of the gradient
field

sampling the activations directly, without the parameter randomness gives a low cost efficient
MC estimator (statistical efficiency).

the gradient in sgvb is unbiased estimate of the $\log$-likelihood part of the elbo

\end{quote}

% a comment on Bernoulli dropout
The key idea of Bernoulli dropout is to randomly mask input features of a layer during
training with in order to learn decorrelated feature maps. In a recent study of network
capacity for multitask learning, \cite{multitask2019}, it was shown, that associating
each dataset (task) with a context, that masks a subset of the parameters, allows non-%
destructive `packing' of the tasks in orthogonal on average `subsets' of a single set
of weights, without much interference between tasks. This lends support for beneficial
effects of Bernulli Dropout on test performance, since, in effect, the network learns
to perform well on identical copies of the same task with different (binary) contexts
with a single parameter set.

% exposition

% plan

A linear layer is parameterized by $W \in\real^{n \times m}$ and bias $b\in \real^n$ and
acts on its input $x\in \real^m$ via $y = W x + b$ with $y\in \real^n$. The key idea of
Bernoulli dropout is to mask elements in the matrix $W$ of the layer
with some given probability $p$: $W = \theta \odot \xi$ with $\theta$ being the learnt
weight matrix, and $
  \xi \sim \mathcal{B}(\{0, \tfrac1{1-p}\}, 1-p)
$ -- an iid Bernoulli mask. During training, a dropout mask $\xi$ is used to compute $W$,
and during evaluation the weights are fixed to the expectation of $W$ which is $\theta$.
The discussion and analysis in \cite{kingma_variational_2015}, suggest that drawing one
common dropout mask for all data in the minibatch reduces statistical efficiency the estimator
of the weights' gradient in the stochastic approximation of the evidence lower bound.

Gaussian dropout works in a similar fashion, except the dropout mask $\xi$ is iid $
  \mathcal{N}(1, \alpha=\tfrac{p}{1-p})
$, i.e. a multiplicative Gaussian noise is injected into the network.

The key idea of Variational Dropout is to assume a Gaussian Mean field variational
approximation of the posterior distribution of linear layer's weights (or convolutional
kernels, with a caveat\footnote).  \footnotetext{
  at each spatial patch of input data the kernel is independently redrawn form the
  VI distribution. This again helps with gradient variance reduction.
}
Weight $W$ are assumed to have independently distributed elements with $
  w_{ij} \sim \mathcal{N}(\theta_{ij}, \sigma^2_{ij})
$.

In fact multiplicative Gaussian dropout on weights $W$ is in fact itself a variational
approximation with variance $\sigma^2_{ij} = \theta_{ij}^2 \tfrac{p}{1-p}$ determined
by the dropout rate.

% set by step we retell the story of kingmaetal2015

Gaussian variational approximation enabled \cite{kingma_variational_2015} propose a
\textit{local reparameterization trick}, which reduces the variance of the gradients
in SGVB and does not resample $W$ per element of a minibatch. It relies the closure
of Gaussian distribution under linear transformations. Indeed, if $W$ is a Gaussian
matrix with independently distributed $
  W_{ij} \sim \mathcal{N}(\theta_{ij}, \sigma^2_{ij})
$, then we have \important{moved}.

and instead
translating the uncertainty from the weights into local output noise of each linear layer.
Without this it would have been necessary to draw new set of random weights per each element
in a mini-batch.

$$
  \mathcal{N}(\theta_{ij}, \alpha \theta^2_{ij})
  \overset{\mathcal{D}}{\sim}
  \theta_{ij} \mathcal{N}(1, \alpha)
  \,, $$

\cite{molchanov_variational_2017} propose additional step in the local reparametrization,
which further reduces the variance of the gradient estimator for each dropped out
weight. Their simple formal change of variables $(\theta, \alpha) \to (\theta, \sigma^2)$
decouples the stochastic component from the weights \rewrite:
$$
  w_{ij} = \theta_{ij} + \theta_{ij} \sqrt{\alpha} \varepsilon_{ij}
  \,\to\,
  w_{ij} = \theta_{ij} + \sigma^2_{ij} \varepsilon_{ij}
  \,, $$
with the appropriate change of variables in the Kullback-Leibler divergence.
($\alpha_{ij} = \tfrac{\sigma_{ij}^2}{\lvert \theta_{ij}\rvert^2}$).

Criticism of \cite{gale_state_2019} implies that $\ell_0$-variational dropout,
proposed by \cite{louizos_learning_2017} and based on the concrete binary distribution
of \cite{maddison_concrete_2016}, works consistently better than the variational
Gaussian dropout.

Maths and related results \cite{pav_moments_2015,taubock_complex-valued_2012},
and \cite{karseras_caution:_2014}

% section complex_variational_dropout (end)

\end{document}

### 2019-11-04 paper/paper.tex
missing reference highlighter
moved cplx review to introduction; restructured and merged the review of kingma2015

@@
 
+\title{Bayesian Sparsification of $\cplx$-valued networks}
+\author{Ivan Nazarov, and Evgeny Burnaev}
+
+%% notation
+\newcommand{\real}{\mathbb{R}}
+\newcommand{\cplx}{\mathbb{C}}
+\newcommand{\tr}[1]{\mathop{tr}{#1}}
+
+\newcommand{\hop}{{\mkern-1.5mu\dagger}}
+\newcommand{\conj}[1]{\overline{#1}}
+
+% \renewcommand{\top}{{\mkern-1.5mu\intercal}}
+\renewcommand{\vec}[1]{\overrightarrow{#1}}
+\newcommand{\diag}[1]{\mathrm{diag}{#1}}
+
+%% drafting macro
 \newcommand{\important}[1]{\textbf{\color{red} #1}}
@@
 
-\newcommand{\real}{\mathbb{R}}
-\newcommand{\cplx}{\mathbb{C}}
-\newcommand{\tr}[1]{\mathop{tr}{#1}}
-
-\newcommand{\hop}{{\mkern-1.5mu\dagger}}
-\newcommand{\conj}[1]{\overline{#1}}
-
-% \renewcommand{\top}{{\mkern-1.5mu\intercal}}
-\renewcommand{\vec}[1]{\overrightarrow{#1}}
-\newcommand{\diag}[1]{\mathrm{diag}{#1}}
-
-\title{Bayesian Sparsification of $\cplx$-valued networks}
-\author{Ivan Nazarov, and Evgeny Burnaev}
+%% red-highlight missing citations
+\usepackage{etoolbox}
+\makeatletter
+\patchcmd{\@citex}{\bfseries ?}{\colorbox{red}{\bfseries ?}}{}{}
+\makeatother
 
@@
 \cite{kharitonov_variational_2018}.
+
+% complex nets and related stuff
+Maths and related results \cite{pav_moments_2015,taubock_complex-valued_2012}, and
+\cite{karseras_caution:_2014}
+
+The use $\cplx$-valued networks in applications is not new: earliest mentions include
+\cite{citation_needed}. More recently they were applied to music transcription and speech
+recognition \cite{trabelsi_deep_2017,yang_complex_2019}. The key motivation behind adoption
+of $\cplx$-networks is the fact that complex numbers are inherent in digital signal processing
+\cite{citation_needed}, acoustic and radio signal analysis \cite{citation_needed}, and
+quantum systems modelling \cite{citation_needed} etc. All these applications require
+compliance with algebraic operations in field of complex numbers.
+
+The paper is structured as follows. In sec.~\ref{sec:bayesian_dropout} we review Bayesian
+dropout techniques, and ins sec.~\ref{sec:c_valued_networks} we provide a brief summary of
+the inner working of complex-valued networks as functions of complex argument. The main
+contribution of this study is presented in sec.~\ref{sec:dropout_for_c_valued_layers},
+where we consider different variational approximations and priors, outline the tricks
+and derive expressions for the divergence term. In sec.~\ref{sec:experiments} we evaluate
+the sparsification rate and compare the resulting performance of various $\cplx$-networks
+proposed in prior work, and discuss the outcomes in sec.~\ref{sec:discussion_and_related_research}.
 
@@
 dropout and DropConnect \cite{hinton_improving_2012,dropconnect}, and Gaussian dropout
-\cite{srivastava_dropout_2014,wang_fast_2013} were reframed as variational inference methods
-by treating the induced parameter distributions as a factorized posterior approximations
-of the form $
+\cite{srivastava_dropout_2014,wang_fast_2013} were reinterpreted as variational inference
+methods. In that study, authors argue that dropout, being multiplicative parameter noise,
+induces parameter distribution equivalent to a fully factorized variational posterior
+approximation of the form $
   q_\theta(\omega) = \prod_j q_{\theta}(\omega_j)
@@
 with $\xi_j \sim p(\xi_j)$ iid for some $p(\xi)$. In Binary dropout with rate $p \in (0, 1)$
-the mutliplicative noise $\xi$ is distributed like $
+the noise $\xi$ is binary and distributed $
   \mathcal{B}\bigl(
@@
     \bigr)
-$ whereas in Gaussian dropout $\mathcal{N}(1, \alpha)$ for $\alpha = \tfrac{p}{1-p}$.
-Focusing on Gaussian dropout, \cite{kingma_variational_2015} proposed Variational Dropout
-technique for Bayesian model regularization: $\alpha$ is treated as a variational parameter,
-that enabled its optimization through SGVB. The variational approximation is a fully
-factorized Gaussian distribution with components $
-  q_{\theta}(\omega_j)
-    = \mathcal{N}(\mu_j, \alpha_j \mu_j^2)
-$. The flexibility in specifying the dependence of $q_\theta$ on $\alpha$ allows learning
-structured dropout rates: global per network, local per layer and even individual, i.e.
-specific to each parameter. In the case of a prior with improper log-uniform factors $
-  \pi(\omega_j) \propto \lvert \omega_j \rvert^{-1}
-$, the KL-divergence term in \eqref{eq:elbo} as computed up to a constant term as a sum of
-\begin{equation} \label{eq:improper-kl-div-real}
-  KL(q_\theta(\omega) \| \pi(\omega))
-    \propto
-      \frac12 \mathbb{E}_{\varepsilon \sim \mathcal{N}(0, 1)}
-        \log{\Bigl\lvert \tfrac1{\sqrt{\alpha}} + \varepsilon \Bigr\rvert^2}
-      % \frac12 \mathbb{E}_{\varepsilon \sim \mathcal{N}(0, 1)}
-      %   \log{\bigl\lvert 1 + \sqrt{\alpha} \varepsilon \bigr\rvert^2}
-      % - \frac12 \log{\alpha}
-  \,.
-\end{equation}
+$, whereas in Gaussian dropout $
+  \xi \sim \mathcal{N}(1, \alpha)
+$ for $\alpha = \tfrac{p}{1-p}$. In the latter case, the \textit{dropout score} $\alpha$ acts
+like a variance scaling factor, making it a natural variational parameter for the posterior
+approximation, which is optimized via SGVB \eqref{eq:elbo}. Thus \cite{kingma_variational_2015}
+propose Variational Dropout technique for Bayesian model regularization. The flexibility in
+specifying dependence of $q_\theta$ on $\alpha$ allows imposing structure on dropout: global
+rate for the whole model network, local per each component and even specific to individual
+parameter.
 
@@
 
-The more recent developments of Bayesian dropout technique with factorized Gaussian
-approximations are considered in \cite{molchanov_variational_2017,kharitonov_variational_2018}.
-\cite{molchanov_variational_2017}
-studies variational dropout from a model sparsification perspective, improve on the results
-of \cite{kingma_variational_2015} in two ways: the authors propose a more accurate approximation
-to the KL-divergence term, and propose additive noise parameterization for the factors of
-$q_\theta(\omega)$, $\omega = W$. Under the original $(\mu, \alpha)$ parameterization the
-stochastic output of a linear layer $
+Bayesian dropout technique with mean field Gaussian variational approximation is further
+developed in \cite{molchanov_variational_2017} and \cite{kharitonov_variational_2018}. The
+first paper studies variational dropout from a model sparsification perspective and improves
+on the results of \cite{kingma_variational_2015} in two directions: the authors propose a
+more accurate approximation to the KL-divergence term in \eqref{eq:elbo}, and introduce
+additive noise parameterization for the factors of $q_\theta(\omega)$, $\omega = W$.
+
+Under the original $(\mu, \alpha)$ parameterization the stochastic output of a linear
+layer $
   y = W^\top x + b
@@
   \Bigr)
-$. \cite{molchanov_variational_2017} argue that for the purposes of model sparsification this parameterization
-should be abandoned in favour of an equivalent $(\mu, \sigma^2)$ with $\alpha$ calculated
-using $\tfrac{\sigma^2}{\mu^2}$ when needed. This makes $\nabla_\mu \mathcal{L}^{SGVB}$,
-which is particularly important for sparsification, independent of the noise injected by
-the trick.
-
-The KL-divergence term \eqref{eq:expect-improper-term-cplx} is half the log-moment of a non-central
+$. \cite{molchanov_variational_2017} argue that for the purposes of model sparsification
+this parameterization should be abandoned in favour of an equivalent $(\mu, \sigma^2)$ with
+the score $\alpha$ calculated using $\tfrac{\sigma^2}{\mu^2}$ when needed. This makes $
+  \nabla_\mu \mathcal{L}^{SGVB}
+$, which is particularly important for sparsification, independent of the noise injected
+by the trick.
+
+\cite{kingma_variational_2015} and \cite{molchanov_variational_2017} consider a factorized
+prior $\pi(\omega)$ with improper log-uniform factors $
+  \pi(\omega_j) \propto \lvert \omega_j \rvert^{-1}
+$. This unravels the divergence term in \eqref{eq:elbo} into a sum of the following terms:
+\begin{equation} \label{eq:improper-kl-div-real}
+  KL(q_\theta(\omega) \| \pi(\omega))
+    \propto
+      \frac12 \mathbb{E}_{\varepsilon \sim \mathcal{N}(0, 1)}
+        \log{\Bigl\lvert \tfrac1{\sqrt{\alpha}} + \varepsilon \Bigr\rvert^2}
+      % \frac12 \mathbb{E}_{\varepsilon \sim \mathcal{N}(0, 1)}
+      %   \log{\bigl\lvert 1 + \sqrt{\alpha} \varepsilon \bigr\rvert^2}
+      % - \frac12 \log{\alpha}
+  \,.
+\end{equation}
+The expectation in \eqref{eq:expect-improper-term-cplx} is half the $\log$-moment of a non-central
 $\chi^2$ distribution with shape $1$ and non-centrality $\lambda = \tfrac1{\alpha}$. In general,
-there is no analytically tractable expression for log-moment of a $\chi^2_m$ with odd degrees of
-freedom. To circumvent this, \cite{kingma_variational_2015} approximate the expectation by a
-non-linear polynomial regression for truncated $\alpha \in (0, 1)$. This approximation was
-significantly refined in \cite{molchanov_variational_2017}, by considering regression with sigmoid
-and soft-plus basis functions fit to the Monte-Carlo estimator of \eqref{eq:improper-kl-div-real}
-for $\alpha$ varying over a logarithmic grid. This enabled doing away with the clipping of the
-dropout rate (relevance score) $\alpha$. Since gradient based methods rely on unbiased gradient
-estimates, in sec.~\ref{sub:real-chisq-grad} we compare the derivative of the approximation
-to the exact derivative of \eqref{eq:improper-kl-div-real} with respect to $\log \alpha$ and show
-that the approximation in \cite{molchanov_variational_2017} is an adequate.
+there is no analytically tractable expression for log-moment of a $\chi^2_m$ with odd degrees
+of freedom. To circumvent this, \cite{kingma_variational_2015} approximate the expectation by
+a non-linear polynomial regression for truncated $\alpha \in (0, 1)$. This approximation was
+substantially refined in \cite{molchanov_variational_2017}, both in term of the domain of scores
+$\alpha$ and accuracy. The paper considered regression with sigmoid and soft-plus basis functions
+fit to the Monte-Carlo estimator of \eqref{eq:improper-kl-div-real} for $\alpha$ varying over
+a fine logarithmic grid. In sec.~\ref{sub:real-chisq-grad} we verify the approximation and
+compare the approximate derivative to the exact derivative of \eqref{eq:improper-kl-div-real}
+with respect to $\log \alpha$.
+% Since gradient based methods rely on unbiased gradient estimates
 
@@
 
-The use $\cplx$-valued networks in applications is not new: earliest mentions include
-\cite{citation_needed}. More recently they were applied to music transcription and speech
-recognition \cite{trabelsi_deep_2017,1910.10202}. The key motivation behind adoption
-of $\cplx$-networks is the fact that complex numbers are inherent in digital signal processing
-\cite{citation_needed}, acoustic and radio signal analysis \cite{citation_needed}, and
-quantum systems modelling \cite{citation_needed} etc. All these applications require
-compliance with algebraic operations in field of complex numbers.
-
 The most recent study of complex-valued networks \cite{trabelsi_deep_2017}, provides a set
@@
 
-Following \cite{trabelsi_deep_2017} we identify $\cplx$ with $\real^2$ via $
+Following \cite{trabelsi_deep_2017}, we naturally identify $\cplx$ with $\real^2$ via $
   z_\mathrm{r} + j z_\mathrm{i} \mapsto (z_\mathrm{r}, z_\mathrm{i})
@@
 equivalence with the paired real multivariate Gaussian distribution:
-\begin{equation}  \label{eq:cn-paired-real-density}
+\begin{multline}  \label{eq:cn-paired-real-density}
   z \sim \mathcal{N}^{\cplx}_m(\mu, \Gamma, C)
-    \Leftrightarrow
+    \\\Leftrightarrow
     \begin{pmatrix}
@@
     \,.
-\end{equation}
+\end{multline}
 It is possible to recover the $\cplx$ covariance and relation matrices from a block covariance
@@
   q(W) = \prod_{lij} q(W^{l}_{ij})
-$ with each parameter being an independent proper complex Gaussian
+$ with each parameter being an independent univariate proper complex Gaussian
+% (we omit the subscript $m=1$ for brevity)
 \begin{equation} \label{eq:c-gauss-vi}
@@
 
-\bibliographystyle{amsplain}
+\bibliographystyle{unsrt}
 \bibliography{references}
-\nocite{*}
+% \nocite{*}
 
@@
 
+In a fully Bayesian treatment, the dropout rate $p$, which governs the regularization strength,
+would appear in the KL-divergence term of ELBO \eqref{eq:elbo} through the corresponding odds 
+ratio $
+  \alpha = \tfrac{p}{1-p}
+$, which.
+
+it vary on the per-parameter basis, which allows for even more flexible posterior
+approximations.
+
+% revirew of kingma and lrt
+The key contributions of \cite{kingma_variational_2015} are reinterpretation of dropout
+as a variational inference method
+
+that optimizes the $\log$-likelihood term from the Evidence Lower Bound.
+
+ % who proposed sparsification?
+
 In the case of $\real$-valued variational dropout \cite{kingma_variational_2015} approximate
@@
 
-Gist of the LRP (kingmaetal2015)
+Gist of the LRP (\cite{kingma_variational_2015})
 translating uncertainty (randomness) from parameters to activations
@@
 
-\section{Complex Variational Dropout} % (fold)
-\label{sec:complex_variational_dropout}
+\section{Bayesian methods} % (fold)
+\label{sec:bayesian_methods}
 
@@
 
+% a comment on Bernoulli dropout
+The key idea of Bernoulli dropout is to randomly mask input features of a layer during
+training with in order to learn decorrelated feature maps. In a recent study of network
+capacity for multitask learning, \cite{multitask2019}, it was shown, that associating
+each dataset (task) with a context, that masks a subset of the parameters, allows non-%
+destructive `packing' of the tasks in orthogonal on average `subsets' of a single set
+of weights, without much interference between tasks. This lends support for beneficial
+effects of Bernulli Dropout on test performance, since, in effect, the network learns
+to perform well on identical copies of the same task with different (binary) contexts
+with a single parameter set.
+
 % on gaussian dropout
-
-% revirew of kingma and lrt
-The key contributions of \cite{kingma_variational_2015} are reinterpretation of dropout
-as a variational inference method and the analysis of the effects that the local reparameterization
-trick has on the efficiency of the gradient estimator in stochastic variational inference,
-\cite{citation_needed}.
-
-\cite{kingmaetal2015} argue that Gaussian dropout, being a multiplicative parameter noise,
-can be interpreted as variational inference via factorized Gaussian posterior approximation
-$q(\omega)$ that optimizes the $\log$-likelihood term from the Evidence Lower Bound. In a fully
-Bayesian treatment, the dropout rate $p \in (0, 1)$, which governs the regularization strength,
-would appear in the KL-divergence term of ELBO through the corresponding odds $
-  \alpha = \tfrac{p}{1-p}
-$, which acts a variance scaling factor in the posterior approximation. Having made $\alpha$
-a learnable parameter of the variational approximation, \cite{kingmaetal2015} natuallry propose
-letting it vary on the per-parameter basis, which allows for even more flexible posterior
-approximations. % who proposed sparsification?
 
@@
 \end{quote}
-
-% a comment on Bernoulli dropout
-The key idea of Bernoulli dropout is to randomly mask input features of a layer during
-training with in order to learn decorrelated feature maps. In a recent study of network
-capacity for multitask learning, \cite{multitask2019}, it was shown, that associating
-each dataset (task) with a context, that masks a subset of the parameters, allows non-%
-destructive `packing' of the tasks in orthogonal on average `subsets' of a single set
-of weights, without much interference between tasks. This lends support for beneficial
-effects of Bernulli Dropout on test performance, since, in effect, the network learns
-to perform well on identical copies of the same task with different (binary) contexts
-with a single parameter set.
-
-% exposition
-
-% plan
 
@@
 
-% set by step we retell the story of kingmaetal2015
-
+% set by step we retell the story of kingma_variational_2015
 Gaussian variational approximation enabled \cite{kingma_variational_2015} propose a
@@
 
-Maths and related results \cite{pav_moments_2015,taubock_complex-valued_2012},
-and \cite{karseras_caution:_2014}
-
-% section complex_variational_dropout (end)
+% section bayesian_methods (end)
 

### 2019-11-04 paper/paper.tex
rewrote sections on CR-calculus; moved cplx criticism to discussion

@@
 % complex nets and related stuff
-Maths and related results \cite{pav_moments_2015,taubock_complex-valued_2012}, and
-\cite{karseras_caution:_2014}
+data that is naturally complex-valued
+studies have shown a potentially richer representation of complex nets
+\cite{hirose2003,fijulamin2009}
+% [3] Akira Hirose, Complex-valued neural networks: theories and applications, vol. 5, World Scientific, 2003.
+% [4] Md Faijul Amin and Kazuyuki Murase, “Single-layered complex-valued neural network for real-valued classification problems,” Neurocomputing, vol. 72, no. 4-6, pp. 945–955, 2009.
+
+the complex version of backpropagation algorithm  was proposed because of
+its richer representational capacity.
+% Nevio Benvenuto and Francesco Piazza, “On the complex backpropagation algorithm,” IEEE Transactions on Signal Processing, vol. 40, no. 4, pp. 967–969, 1992.
+
+\cite{yang_complex_2019} develop complex transformer, with $\cplx$-attention and complex
+encoder-decoder, and apply it to music transcription and wireless signal classification.
+
+that interfaces the rest of
+$\cplx$-valued
+the network with complex numbers
+
+that operates on the Fourier transform input speech, acoustic, of radio signals.
+
+papers related to complex-valued distributions \cite{pav_moments_2015,taubock_complex-valued_2012},
+and \cite{karseras_caution:_2014}
 
@@
 not $\cplx$-differentiable with respect parameters, since $h$ violates Cauchy-Riemann conditions.
-This problem is commonly dealt with by using Wirtinger, or $\cplx\real$ calculus, which subsumes
-$\cplx$-calculus, but is also applicable to non-holomorphic functions of $\cplx$-argument, see
-\cite{adali_complex-valued_2011} and \cite{trabelsi_deep_2017}. In essence, this approach
-regards $f$ as a function of two independent variables $z$ and its conjugate $\conj{z}$ and
-symbolically redefines the derivatives appropriately. The resulting derivative operators
-satisfy linearity, product and chain rules, and respect complex conjugation. This approach
-can be directly reformulated in terms of derivatives with respect to real and imaginary parts,
-making it possible to use and apply the rules of $\real$-calculus to the networks represented
-in paired $\real$ fashion and use existing $\real$-valued backpropagation in autograd software.
-
-% criticism and discussion
-Despite this, $\cplx$-networks remain much less popular than $\real$-networks for several
-reasons. One possible reason is that a $\cplx$-layer is identical to a paired $\real$-layer,
-based on the algebraic equivalence between $2 \times 2$ real matrices and complex numbers.
-Due to this constraint $\cplx$-networks have less expressive power for the same computation
-complexity compared to a $\real$-layer with twice as many inputs and outputs.
-%
-Another one is that a $\cplx$-network is not a true complex-valued function of a complex
-argument: common non-linearities are pointwise applications of $\real$-valued activations
-\cite{trabelsi_deep_2017}.
-%
-Third conceptual issue is that a real-valued loss as a $\cplx\to\real$ function fails
-Cauchy-Riemann conditions, and so is not $\cplx$-differentiable. Since the network has to
-be trained by a gradient-based method (stochastic), this issue is overcome by $\cplx\real$,
-or Wirtinger calculus, which treats the complex argument $z$ and its conjugate $\conj{z}$
-as explicit independent variables. For non-holomorphic functions this approach makes taking
-their derivatives essentially indistinguishable from calculus on $\real^2$.
-%
-The last reason is the lack of native support by the major deep learning and auto-differentiation
-frameworks.
+This problem is dealt with by using Wirtinger, or $\cplx\real$ calculus, which subsumes
+$\cplx$-calculus, and is applicable to non-holomorphic functions of $\cplx$-argument,
+\cite{adali_complex-valued_2011}. As a basis for backpropagation algorithm it was considered
+in \cite{benvenuto_complex_1992} and \cite{trabelsi_deep_2017}.
+
+Basically $\cplx\real$ calculus regard $f(z)$ as a function of two independent variables $z$ 
+and its conjugate $\conj{z}$ and symbolically defines derivative operators $
+  \tfrac{\partial}{\partial z}
+$ and $
+  \tfrac{\partial}{\partial \conj{z}}
+$, that satisfy linearity, product and chain rules, and respect complex conjugation. The important
+property is that, if we identify $f(z) = f(u + jv) = F(u, v)$, then the $\cplx\real$ calculus
+rules differential of $f$ as a $\cplx$ function coincides its differential as an $\real^2$
+function. This makes it possible to use and apply the rules of $\real$-calculus to the networks
+represented in paired $\real$ fashion and use existing $\real$-valued backpropagation in autograd
+software. The key analytic advantage is that computing derivatives is more streamlined, less
+messy, and derivative expressions involving complex variables turn out to be simpler that their
+real-imaginary analogues, \cite{adali_complex-valued_2011}.
 
@@
 
+test on MusicNet, (music transcription [14])
+
+complex high-dimensional time series In-phase Quadrature (IQ)
+
 \cite{monning_evaluation_2018}
@@
 after observing the data.
+
+% criticism and discussion
+Despite this, $\cplx$-networks remain much less popular than $\real$-networks for several
+reasons. One possible reason is that a $\cplx$-layer is identical to a paired $\real$-layer,
+based on the algebraic equivalence between $2 \times 2$ real matrices and complex numbers.
+Due to this constraint $\cplx$-networks have less expressive power for the same computation
+complexity compared to a $\real$-layer with twice as many inputs and outputs.
+%
+Another one is that a $\cplx$-network is not a true complex-valued function of a complex
+argument: common non-linearities are pointwise applications of $\real$-valued activations
+\cite{trabelsi_deep_2017}.
+%
+Third conceptual issue is that a real-valued loss as a $\cplx\to\real$ function fails
+Cauchy-Riemann conditions, and so is not $\cplx$-differentiable. Since the network has to
+be trained by a gradient-based method (stochastic), this issue is overcome by $\cplx\real$,
+or Wirtinger calculus, which treats the complex argument $z$ and its conjugate $\conj{z}$
+as explicit independent variables. For non-holomorphic functions this approach makes taking
+their derivatives essentially indistinguishable from calculus on $\real^2$.
+%
+The last reason is the lack of native support by the major deep learning and auto-differentiation
+frameworks.
 
@@
 
-TLDR: we use Wirtinger calculus!
+% TLDR: we use Wirtinger calculus!
 
 % essential intro into Wirtinger calculus (CR)
-Take $f\colon \cplx \to \cplx$ and identify it with $F\colon \real^2 \to \cplx$ function
-via $F(u, v) = f(z)\vert_{z=u + j v}$. Wirtinger calculus introduces two formal derivative
-operators \rewrite{(this seems to be very verbatim)}
+% https://math.stackexchange.com/a/444493
+Wirtinger calculus relies on the natural identification of $\cplx$ with $\real \times \real$.
+Let's consider $
+  f\colon \cplx \to \cplx
+$ and treat it as an equivalent function $\real^2 \to \cplx$ via $
+  f(z) = f(u + jv) = F(u, v)
+$. Wirtinger calculus defines two formal derivative operators
 $
@@
     \bigr)
-$, defines $dz = du + j dv$, $d\conj{z} = du - j dv$, and the differential of $f$ as
-$$
-df = \tfrac{\partial f}{\partial z} dz
-    + \tfrac{\partial f}{\partial \conj{z}} d\conj{z}
-   % = \tfrac12\bigl(
-   %    \tfrac{\partial}{\partial u}
-   %    - j \tfrac{\partial}{\partial v}
+$ and the differential of $f$ at $z \in \cplx$ as
+$$
+df(z) \big\vert_{z=u + jv}
+  = \frac{\partial f}{\partial z} dz
+    + \frac{\partial f}{\partial \conj{z}} d\conj{z}
+   % = \frac12\bigl(
+   %    \frac{\partial}{\partial u}
+   %    - j \frac{\partial}{\partial v}
    % \bigr) F (du - j dv)
-   % + \tfrac12\bigl(
-   %    \tfrac{\partial}{\partial u}
-   %    + j \tfrac{\partial}{\partial v}
+   % + \frac12\bigl(
+   %    \frac{\partial}{\partial u}
+   %    + j \frac{\partial}{\partial v}
    % \bigr) F (du - j dv)
-   % = \tfrac12 \bigl(
-   %    \tfrac{\partial F}{\partial u} du - j \tfrac{\partial F}{\partial v} du
-   %    + j \tfrac{\partial F}{\partial u} dv + \tfrac{\partial F}{\partial v} dv
+   % = \frac12 \bigl(
+   %    \frac{\partial F}{\partial u} du - j \frac{\partial F}{\partial v} du
+   %    + j \frac{\partial F}{\partial u} dv + \frac{\partial F}{\partial v} dv
    % \bigr)
-   % + \tfrac12 \bigl(
-   %    \tfrac{\partial F}{\partial u} du + j \tfrac{\partial F}{\partial v} du
-   %    - j \tfrac{\partial F}{\partial u} dv + \tfrac{\partial F}{\partial v} dv
+   % + \frac12 \bigl(
+   %    \frac{\partial F}{\partial u} du + j \frac{\partial F}{\partial v} du
+   %    - j \frac{\partial F}{\partial u} dv + \frac{\partial F}{\partial v} dv
    % \bigr)
-   = \tfrac{\partial F}{\partial u} du
-     + \tfrac{\partial F}{\partial v} dv
-   = dF
-  \,. $$
-Thus the complex value and its conjugate are treated as independent variables. In this notation
-Cauchy-Riemann conditions are expressed as $
+   = \frac{\partial F}{\partial u} du
+     + \frac{\partial F}{\partial v} dv
+   = dF(u, v)
+  \,, $$
+where $dz = du + j dv$ and $d\conj{z} = du - j dv$. This implies that the complex argument
+and its conjugate are treated as independent variables. In this notation Cauchy-Riemann
+conditions are expressed as $
   \tfrac{\partial f}{\partial \conj{z}} = 0
 $, or $
-  -j\tfrac{\partial F}{\partial v} = \tfrac{\partial F}{\partial v}
+  -j \tfrac{\partial F}{\partial v} = \tfrac{\partial F}{\partial v}
 $. These conditions impose a rigid structure on real and imaginary parts of $F(u, v)$, namely $
@@
   \tfrac{\partial F_{\Re }}{\partial v} = - \tfrac{\partial F_{\Im }}{\partial u}
-$. Thus Wirtinger calculus subsumes the usual $\cplx$-calculus, when $
+$. Thus Wirtinger calculus subsumes the usual $\cplx$-calculus on holomorphic functions,
+when $
   \tfrac{\partial f}{\partial \conj{z}} = 0
@@
     = F(\tfrac12 (z + \conj{z}), \tfrac1{j 2} (z - \conj{z}))
-$ does not depend on $\conj{z}$.
-
-For a real-valued $f\colon \cplx \to \real$ we have $\conj{f} = f$, whence $
-  \tfrac{\partial f}{\partial \conj{z}}
-    = \tfrac{\partial \conj{f}}{\partial \conj{z}}
-    = \conj{\tfrac{\partial f}{\partial z}}
-$. Hence
-$$
-df
-  = \tfrac{\partial f}{\partial z} dz
-    + \tfrac{\partial f}{\partial \conj{z}} d\conj{z}
-  % = \conj{\tfrac{\partial \conj{f}}{\partial \conj{z}}} dz
-  % + \conj{\conj{\tfrac{\partial f}{\partial \conj{z}}} dz}
-  = 2 \Re \Bigl(
-    \conj{\tfrac{\partial f}{\partial \conj{z}}} dz
-  \Bigr)
-  = 2 \Re \bigl(
-    \tfrac{\partial f}{\partial z} dz
-  \bigr)
+$ does not depend on $\conj{z}$. The usual rules of calculus, like chain and product rules,
+follow directly from the definition of the operators, e.g.
+$$
+  \frac{\partial (f\circ g)}{\partial z}
+    = \frac{\partial f(g(z))}{\partial g} \frac{\partial g(z)}{\partial z}
+    + \frac{\partial f(g(z))}{\partial \conj{g}} \frac{\partial \conj{g(z)}}{\partial z}
+    % = \nabla G \nabla F
   \,. $$
-Hence the gradient, being the direction of \rewrite{maximal growth} of $f$ at $z$ is given by $
-  \tfrac{\partial f}{\partial \conj{z}}
-    = \tfrac{\partial F}{\partial u}
-      + j \tfrac{\partial F}{\partial v}
-$. Thus under Wirtinger calculus it is possible to reuse $\real$-backpropagation.
-
 % Show that $dh(z) = df(g(z)) dg(z)$.
@@
 %   \,. $$
+
+Since in machine learning the target loss is typically an empirical real-valued risk, which
+is minimized, and we let's derive the expression for the gradient and make sure that it is
+compatible with real-valued calculus upon which current auto-differentiation tools are built.
+For a real-valued $f\colon \cplx \to \real$ we have $\conj{f} = f$, whence $
+  \tfrac{\partial f}{\partial \conj{z}}
+    = \tfrac{\partial \conj{f}}{\partial \conj{z}}
+    = \conj{\tfrac{\partial f}{\partial z}}
+$. Hence
+$$
+df
+  = \tfrac{\partial f}{\partial z} dz
+    + \tfrac{\partial f}{\partial \conj{z}} d\conj{z}
+  % = \conj{\tfrac{\partial \conj{f}}{\partial \conj{z}}} dz
+  % + \conj{\conj{\tfrac{\partial f}{\partial \conj{z}}} dz}
+  = 2 \Re \Bigl(
+    \conj{\tfrac{\partial f}{\partial \conj{z}}} dz
+  \Bigr)
+  = 2 \Re \bigl(
+    \tfrac{\partial f}{\partial z} dz
+  \bigr)
+  \,. $$
+Hence the gradient of $f$ at $z$ is given by $
+  \tfrac{\partial f}{\partial \conj{z}}
+    = \tfrac{\partial F}{\partial u}
+      + j \tfrac{\partial F}{\partial v}
+$, meaning that we can use gradients with respect ral and imaginary parts independently. Thus
+using Wirtinger calculus makes it possible to reuse $\real$-backpropagation for $\cplx$-networks.
 

### 2019-11-04 paper/paper.tex
replace otimes with prod

@@
   W \sim q(W)
-    = \bigotimes_{ij} q(\omega_{ij})
+    = \prod_{ij} q(\omega_{ij})
 $ with proper complex Gaussian distributions of each element $

### 2019-11-05 paper/paper.tex
derivation of KL in comment
compressed the section on bayesian methods, located missing citations, fixed the plot in appendix

@@
 
-Deep neural networks are an integral part of the machine learning and data science set of
-tools for practical data-driver problem solving. Despite recent advances in generalization
-and optimization theory specific to deep networks, it is challenging to deploy the trained
-in actual embedded hardware, due to obvious storage and compute limitations. Many techniques
-exist to compress or sparsify the networks: weight pruning \cite{citation_needed}, quantization
-from IEEE754 floating point to integer-based arithmetic, and dropout. The key idea is that
-the more explicitly zero parameters the model has, the less multiplications the mode needs.
-
-Bayesian Inference is a principled framework of reasoning about uncertainty. The core
-principle is updating prior beliefs in accordance with the likelihood of given empirical
-observations into posterior belief. Under suitable modelling and prior assumptions, methods
-of variational Bayesian inference can be used towards model sparsification: variants of
-Bayesian dropout studied in \cite{kingma_variational_2015,molchanov_variational_2017}, and
-\cite{kharitonov_variational_2018}.
+Deep neural networks are an integral part of machine learning and data science toolset
+for practical data-driven problem solving. Despite recent advances in generalization
+and optimization theory specific to deep networks, deploying in actual embedded hardware
+remains a challenge. Solving the storage and compute constraints encourages development
+of model compress and sparsification methods, that focus on favourable tradeoff between
+performance and size. Most popular techniquees include weight pruning \cite{citation_needed},
+model quantization from IEEE754 floating point to integer-based arithmetic \cite{citation_needed},
+and dropout. The key assumption is that the more explicitly zero parameters, the less
+computations is needed.
+
+Bayesian Inference is a principled framework of reasoning about uncertainty. The core principle
+is updating prior beliefs in accordance with the likelihood of empirical observations into
+posterior belief. Under suitable modelling and prior assumptions, Bayesian methods can be
+used towards model sparsification, \cite{kingma_variational_2015,molchanov_variational_2017},
+and \cite{kharitonov_variational_2018}.
 
@@
 $D$ to update the assumptions by considering the likelihood of the observations under each
-$m \in \mathcal{M}$. The inference is performed using the Bayes rule to get the exact
-posterior belief: $
+$m \in \mathcal{M}$. Models are represented by a parametric family indexed by $\omega \in
+\Omega$ and each $m_\omega(\cdot)$ specifies the conditional distribution of the data $
+  D = (z_i)_{i=1}^N
+$. The posterior distribution $p(\omega \mid D)$, derived using the Bayes rule $
   p(m \mid D) = \tfrac{p(D \mid m) \pi(m)}{p(D)}
@@
   p(D) = \mathbb{E}_{\pi(m)} p(D \mid m)
-$.
-
-It is usually assumed that $\mathcal{M}$ is a parametric family indexed by a parameter $\omega$
-from some set $\Omega$, that each model is \textit{identified} with its parameter, and that
-each $m = m_\omega(\cdot)$ specifies the functional form of the conditional distribution of
-the data $D = (z_i)_{i=1}^N$. Unless the data has time-series nature, it is customary to
-presume independence of samples $z_i$ conditional on $\omega$.
-%
-In supervised settings, the nature of the structure of each observation is also conjectured:
-$z_i = (x_i, y_i)$ is typically assumed in regression or classification tasks with $
-  p(z_i \mid \omega) = p(y_i \mid x_i, \omega) p(x_i)
-$, i.e. the inputs $x_i$ are produced by some opaque not particularly interesting process.
-%
-In unsupervised settings a hierarchical model is usually considered: it is hypothesized that
-there are unobserved causal variables $u_i$ with some prior distribution $\pi(u_i \mid \omega)$
-and a model of $p(x_i \mid u_i, \omega)$.
-% vae x -- indep: q(u \mid x) ~ p(u \mid x, D), q(\omega \mid D) see \cite[eq.~4]{1805.08498}
-%
-In following we assume that the samples in $D$ are conditionally independent.
-
-The posterior distribution $p(\omega \mid D)$ derived by Bayesian inference from the premise,
-can be used to get useful information about yet unobserved data, such as the classification
-uncertainty and predictive statistics, to name some examples. These downstream tasks usually
-involve iterated or nested integrals over the posterior, e.g. classification uncertainty
-evaluates the entropy $
-  \mathbb{H}(q) = - \mathbb{E}_{y\sim q} \log{q(y)}
-$ of the posterior predictive distribution at $
-  p(y \mid x) = \mathbb{E}_{p(\omega \mid D)} p(y \mid x, \omega)
-$ for some $x$ of interest, whereas the predictive statistics use
-$
-  \mathbb{E}_{p(\omega \mid D)} \hat{g}_\omega(x)
-$ (by Fubini) for $
-  \hat{g}_\omega(x) = \mathbb{E}_{p(y \mid x, \omega)} g(y)
-$. These integrals are rarely analytically tractable in practice, and so are approximated
-using Monte-Carlo estimators with varying degree of precision, \cite{citation_needed}.
-
-However, despite the modeling assumption being chosen by the practitioner, the posterior
-itself can be intractable or scale poorly with the problem size, due to the integral in the
-denominator in the Bayes rule. Thus, save for the relatively simple cases \cite{citation_needed},
-the exactness of Bayesian Inference is traded for tractability and speed of Variational
-Inference.
-
-The main idea of Variational Inference is to recast the posterior inference problem into
-optimization framework. Instead of deriving $p(\omega \mid D)$ exactly, we consider a parametric
-family $\mathcal{Q}$ of distributions indexed by a variational parameter $\theta \in \Theta$
-as potential approximations for the posterior. Here $\theta$ represents a generic composite
-parameter of the approximation and is specified whenever necessary.
-
-We seek the closest $Q_\theta(d\omega)$ within the class with respect to some distance or
-proximity score $\rho$ on probability measures or densities. Thus the class $\mathcal{Q}$ becomes
-part of the modeling assumptions and is usually picked so that its members can be sampled
-from, have known and tractable density $
-  q_\theta(\omega) d\omega
-$ with a tractable score function $
-  \omega \mapsto \nabla_\theta \log q_\theta(\omega)
-$ for REINFORCE, \cite{citation_needed}, or amenable to the Reparameterization Trick or
-its variants, \cite[sec.~2.4]{kingma_auto-encoding_2014}, \cite[sec.~3]{figurnov_implicit_2019}: $
-  \omega \sim q_\theta(\omega)
-$
-is equivalent in distribution to $
-  \omega = g_\theta(\varepsilon)
-$ for some deterministic differentiable $
-  \theta \mapsto g_\theta(\varepsilon)
-$ and a non-parametric random variable $
-  \varepsilon \sim p_\varepsilon(\varepsilon)
-$.
-% (reparameterization trick) $q_{\theta}(d\omega)$ is a push-forward of $p(d\varepsilon)$ by a
-% differentiable map $g_\theta(\varepsilon)$.
-
-Not every proximity score is practically useful, since finding the variational parameters
-$$
-\theta^*
+$, provides useful information about yet unobserved data and model parameters, e.g
+classification uncertainty, predictive statistics, and parameter relevance.
+
+The posterior itself is computationally intractable, save for the relatively simple cases
+\cite{citation_needed}, and therefore exact inference is traded for tractability and scalability
+of Variational Inference. Instead of deriving $p(\omega \mid D)$ using the rule, this approach
+recasts posterior inference into variational optimization problem
+\begin{equation} \label{eq:variational-progam}
+  q_*
     \in \arg \min_{\theta} \rho\bigl(
@@
     \bigr)
-  \,, $$
-still requires access to the exact posterior, precisely what variational inference attempts
-to avoid. Despite its shortcomings, such as failing to be a metric, and infinite values for
-densities with non-nested support, \cite{citation_needed}, the Kullback-Leibler divergence,
-defined for $q(\omega) \ll p(\omega)$ as
+    \,,
+\end{equation}
+over a tractable parametric family of distributions on the parameter space $
+  \mathcal{Q} = \{Q_\theta(d\omega) \colon \theta \in \Theta\}
+$. The class $\mathcal{Q}$ is picked so that its member have tractable densities $
+  q_\theta(\omega) d\omega
+$, can be sampled from and possess tractable $\log$-derivatives $
+  \omega \mapsto \nabla_\theta \log q_\theta(\omega)
+$, \cite{williams_simple_1992}, or can be represented as differentiable transformations
+of non-parametric noise, \cite{kingma_auto-encoding_2014,figurnov_implicit_2019}.
+% (reparameterization trick, pathwise gradieent) $q_{\theta}(d\omega)$ is a push-forward
+% of $p(d\varepsilon)$ by a differentiable map $g(\varepsilon; \theta)$.
+% % http://stillbreeze.github.io/REINFORCE-vs-Reparameterization-trick/#fn:1
+
+Kullback-Leibler divergence, defined for $q(\omega) \ll p(\omega)$ as
 $$
@@
   \,, $$
-is commonly used. It circumvents the raised issue, because it satisfies the following identity,
-which holds for $q$ and $p$ whenever the divergences are finite:
+is the natural choice for $\rho$, despite it not being a metric and requiring distributions
+with nested support. The main reason is that it satisfies the following identity, which when
+everything works, holds for any $q$ and $p$:
 \begin{equation} \label{eq:kl-div-master}
@@
 \end{equation}
-This identity implies an equivalent proxy problem for the variational inference -- maximizing
-the \textit{evidence lower bound} (ELBO)
+This key identity yield an equivalent problem for \eqref{eq:variational-progam}:
+maximizing the \textit{evidence lower bound} (ELBO)
 \begin{equation} \label{eq:elbo_general}
@@
   & \underset{\theta}{\text{maximize}}
-    & \mathcal{L}(\theta; \pi, p)
+    & \mathcal{L}(\theta; \phi, \lambda)
       & = \mathbb{E}_{\omega \sim q_{\theta}}
-          \log p(D \mid \omega)
-        - KL(q_{\theta}(\omega) \| \pi(\omega))
+          \log p_{\phi}(D \mid \omega)
+        - KL(q_{\theta}(\omega) \| \pi_{\lambda}(\omega))
         % \mathbb{E}_{\omega \sim q_{\theta}}
-          % \log\frac{q_\theta(\omega)}{\pi(\omega)}
+          % \log\frac{q_\theta(\omega)}{\pi_{\lambda}(\omega)}
   % \\
@@
   %     & = \mathbb{E}_{\omega \sim q_{\theta}}
-  %         \log{p(D \mid \omega) \pi(\omega)}
+  %         \log{p_{\phi}(D \mid \omega) \pi_{\lambda}(\omega)}
   %       + \mathbb{H}(q_{\theta})
@@
 \end{equation}
-where the prior and conditional data probability model as listed as arguments, to emphasize
-that they can potentially be optimized over (using alternating approach leading to EM-algorithm).
-% vae
-It is worth noting, that the optimization objective \eqref{eq:elbo_general} requires only $
-  p(\omega \mid D)
-    \propto p(D \mid \omega) \pi(\omega)
-$, i.e. up to its normalizing constant, which is crucial for its practical viability. As
-was mentioned above, other objectives for variational approximation can be considered, e.g.
-\cite{ranganath_operator_2018} propose an approach that encompasses $f$-divergences, \textbf{...} and
-other proximity scores, that depend on $p(\omega\mid D)$ through $p(D \mid \omega)$ and
-$\pi(\omega)$.
-
-The Stochastic Gradient Variational Bayes, proposed by \cite{kingma_auto-encoding_2014,citation_needed}, is
-an unbiased differentiable Monte-Carlo estimator of the lower bound \eqref{eq:elbo_general}
-that allows maximizing ELBO using stochastic gradient-based methods. In deep Bayesian inference
-the variational approximation family is defined by deep neural networks, using the stochastic
-estimate of ELBO the only viable option. Exploiting independence of observations in $D$ and
-the reparameterization trick, the estimator is defined as
-\begin{equation} \label{eq:elbo}
-  \mathcal{L}^{SGVB}(\theta; \pi, p)
-    =
-    - KL(q_{\theta}(\omega) \| \pi(\omega))
+where the prior and likelihood are allowed to depend on explicit parameters. The most
+commonly used algorithm to optimize \eqref{eq:elbo_general} is to use EM-algorithm.
+Other variational objectives are possible, provided $p(\omega \mid D)$ is probed only
+through $\log p(D \mid \omega)$ and $\log \pi(\omega)$, \cite{ranganath_operator_2018}.
+
+Stochastic Gradient Variational Bayes (SGVB), proposed by \cite{kingma_auto-encoding_2014},
+is an differentiable unbiased Monte-Carlo estimator of \eqref{eq:elbo_general}, which makes
+it possible to employ stochastic gradient-based optimization methods. If $
+  \omega \sim q_{\theta}
+$ is equivalent in distribution to $
+  \omega = g(\varepsilon; \theta)
+$ for some non-parametric random variable $
+    \varepsilon \sim p_\varepsilon
+$ and differentiable $
+  g(\varepsilon; \theta)
+$, then the SGVB is
+\begin{equation} \label{eq:sgvb}
+  \widetilde{\mathcal{L}}(\theta; \phi, \lambda)
+    = - KL(q_{\theta}(\omega) \| \pi_{\lambda}(\omega))
       % + \frac{N}{\lvert B \rvert} \sum_{i\in B}
-        % \log p(z_i \mid \omega_i)
-    + N
-      \frac1{M} \sum_{i=1}^M
-        \frac1{L} \sum_{l=1}^L
-          \log p(z_i \mid \omega_{il})
-            \Big\vert_{\omega_{il} = g_\theta(\varepsilon_{il})}
+        % \log p(z_i \mid \omega_i)b
+      + \frac1{L} \sum_{l=1}^L
+        \log p_{\phi}(D \mid \omega_{il})
+          \Big\vert_{\omega_{l} = g(\varepsilon_{l}; \theta)}
       % =
@@
 \end{equation}
-where $B = (z_i)_{i=1}^M$ is a minibatch form the dataset $D$ and $
-  (\varepsilon_{il})_{l=1}^L \sim p(\varepsilon)
-$ are drawn independently per each sample $z_i$. The most commonly used variational
-approximations have analytically tractable KL-divergence term, but can be replaced by
-an unbiased differentiable estimator.
-
-For a particular family of variational posterior approximation, variational inference
-can be used as a regularization method \cite{kingma_variational_2015} and as model sparsification
-technique \cite{molchanov_variational_2017}. In \cite{kingma_variational_2015} the Binary
-dropout and DropConnect \cite{hinton_improving_2012,dropconnect}, and Gaussian dropout
-\cite{srivastava_dropout_2014,wang_fast_2013} were reinterpreted as variational inference
-methods. In that study, authors argue that dropout, being multiplicative parameter noise,
-induces parameter distribution equivalent to a fully factorized variational posterior
-approximation of the form $
+where $
+  (\varepsilon_{l})_{l=1}^L
+$ is an iid sample from $p_\varepsilon$. Intractable KL-divergence terms can be also
+replaced by differentiable unbiased Monte-Carlo estimators, \cite{kingma_auto-encoding_2014}.
+%
+For the purposes of this study, we assume that the observed data is independent, and
+use minibatch version of \eqref{eq:sgvb} with $L=1$:
+\begin{equation} \label{eq:elbo}
+  \widetilde{\mathcal{L}}(\theta; \phi, \lambda)
+    = - KL(q_{\theta}(\omega) \| \pi_{\lambda}(\omega))
+      + \frac{N}{M} \sum_{i=1}^M
+        \log p_{\phi}(z_i \mid g(\varepsilon_i; \theta))
+    \,,
+\end{equation}
+for a random subsample $(z_i)_{i=1}^M$ from $D$ and iid $
+  (\varepsilon_i)_{i=1}^M \sim p_\varepsilon
+$.
+
+\subsection{Dropout} % (fold)
+\label{sub:dropout}
+
+For a particular family of posterior approximation, variational inference can be used
+as a regularization method \cite{kingma_variational_2015} and as model sparsification
+technique \cite{molchanov_variational_2017}. In \cite{kingma_variational_2015} Binary
+dropout, DropConnect and Gaussian dropout, \cite{hinton_improving_2012,wan_regularization_2013},
+\cite{srivastava_dropout_2014}, and \cite{wang_fast_2013} were reinterpreted as variational
+inference methods. That study argues that the multiplicative noise, introduced by dropout,
+induces a distribution equivalent to a fully factorized variational posterior of the form $
   q_\theta(\omega) = \prod_j q_{\theta}(\omega_j)
-$, where each component $q_{\theta}(\omega_j)$ is defined via $\omega_j = \mu_j \xi_j$
-with $\xi_j \sim p(\xi_j)$ iid for some $p(\xi)$. In Binary dropout with rate $p \in (0, 1)$
-the noise $\xi$ is binary and distributed $
-  \mathcal{B}\bigl(
+$, where $q_{\theta}(\omega_j)$ is $\omega_j = \mu_j \xi_j$ with $\xi_j \sim p(\xi_j)$
+iid from some $p_\xi$. In Binary dropout with rate $p \in (0, 1)$ we have $
+  p_\xi
+    = \mathcal{B}\bigl(
         \{0, \tfrac1{1-p}\}, 1-p
@@
 that for the case of fully factorized Gaussian dropout posterior approximations, the
-gradient estimator $\nabla_\theta \mathcal{L}^{SGVB}$ is more statistically efficient
+gradient estimator $\nabla_\theta \tilde{\mathcal{L}}$ is more statistically efficient
 and computationally fast, when the trick is used in addition to independent per sample
@@
 the score $\alpha$ calculated using $\tfrac{\sigma^2}{\mu^2}$ when needed. This makes $
-  \nabla_\mu \mathcal{L}^{SGVB}
+  \nabla_\mu \tilde{\mathcal{L}}
 $, which is particularly important for sparsification, independent of the noise injected
@@
 % This concludes the section on the foundations of Bayesian dropout techniques.
+
+% subsection dropout (end)
 
@@
   % =
+  %   - \log{\sigma^2}
+  %   + \tfrac{\beta}2 \log \alpha \lvert \mu \rvert^2
+  %   - \tfrac{\beta}2 \log \alpha
+  %   - \tfrac{\beta}2 \mathop{Ei}( -\tfrac1{\alpha})
+  % =
     % \log \tfrac{\lvert \mu \rvert^\beta}{\sigma^2}
@@
   \centering
-  \begin{subfigure}[b]{0.47\textwidth}
-    \includegraphics[draft]{../notebooks/assets/curve_fit.pdf}
-  \end{subfigure}%\hspace{-2.em}
-  \begin{subfigure}[b]{0.47\textwidth}
-    \includegraphics[draft]{../notebooks/assets/grad_log.pdf}
-  \end{subfigure}
-  \caption{Fit of the regression \cite{molchanov_variational_2017}, and the accuracy of
-  the derivative wrt $\log{\alpha}$.}
+  \includegraphics[width=1.\linewidth]{../notebooks/assets/grad_log.pdf}
+  \caption{$\tfrac{d f(\alpha)}{d \log{\alpha}}$ of the fit \cite{molchanov_variational_2017},
+  MC estimate, and exact derivative using \eqref{eq:real-kl-div-deriv-log}.}
   \label{fig:molchanov-derivative-replica}

### 2019-11-05 paper/paper.tex
compressing bayesian dropout section

@@
 \begin{aligned}
-  & \underset{\theta}{\text{maximize}}
+  & \underset{\theta, \phi, \lambda}{\text{maximize}}
     & \mathcal{L}(\theta; \phi, \lambda)
@@
 as a regularization method \cite{kingma_variational_2015} and as model sparsification
-technique \cite{molchanov_variational_2017}. In \cite{kingma_variational_2015} Binary
-dropout, DropConnect and Gaussian dropout, \cite{hinton_improving_2012,wan_regularization_2013},
-\cite{srivastava_dropout_2014}, and \cite{wang_fast_2013} were reinterpreted as variational
-inference methods. That study argues that the multiplicative noise, introduced by dropout,
-induces a distribution equivalent to a fully factorized variational posterior of the form $
+technique \cite{molchanov_variational_2017}. \cite{kingma_variational_2015} propose
+Variational Dropout, by studying Binary dropout, DropConnect and Gaussian dropout,
+\cite{hinton_improving_2012,wan_regularization_2013}, \cite{srivastava_dropout_2014},
+and \cite{wang_fast_2013} through the lens of variational inference methods. The study
+argues that the multiplicative noise, introduced by dropout, induces a distribution
+equivalent to a fully factorized variational posterior of the form $
   q_\theta(\omega) = \prod_j q_{\theta}(\omega_j)
 $, where $q_{\theta}(\omega_j)$ is $\omega_j = \mu_j \xi_j$ with $\xi_j \sim p(\xi_j)$
-iid from some $p_\xi$. In Binary dropout with rate $p \in (0, 1)$ we have $
+iid from some $p_\xi$. Binary dropout with rate $p \in (0, 1)$ uses $
   p_\xi
@@
   \xi \sim \mathcal{N}(1, \alpha)
-$ for $\alpha = \tfrac{p}{1-p}$. In the latter case, the \textit{dropout score} $\alpha$ acts
-like a variance scaling factor, making it a natural variational parameter for the posterior
-approximation, which is optimized via SGVB \eqref{eq:elbo}. Thus \cite{kingma_variational_2015}
-propose Variational Dropout technique for Bayesian model regularization. The flexibility in
-specifying dependence of $q_\theta$ on $\alpha$ allows imposing structure on dropout: global
-rate for the whole model network, local per each component and even specific to individual
-parameter.
-
-Secondary contribution of \cite{kingma_variational_2015} has been the analysis of the local
-reparameterization trick as a gradient variance reduction technique for \eqref{eq:elbo},
-that is particularly suitable for Variational Dropout. The trick is to translate uncertainty
-from the global parameter noise to local noise in intermediate outputs within the network.
-Initially, this idea was used in \cite{who-dis-originally-22} for Gaussian dropout,
-who employed the closure of Gaussians under affine transformations as a way to inject
-regularizing noise. Later in \cite[app.~B]{kingma_variational_2015} it was rigorously shown
-that for the case of fully factorized Gaussian dropout posterior approximations, the
-gradient estimator $\nabla_\theta \tilde{\mathcal{L}}$ is more statistically efficient
-and computationally fast, when the trick is used in addition to independent per sample
-parameter draws, which reduce variance by decorrelating ELBO estimates within the minibatch.
-
-Bayesian dropout technique with mean field Gaussian variational approximation is further
-developed in \cite{molchanov_variational_2017} and \cite{kharitonov_variational_2018}. The
-first paper studies variational dropout from a model sparsification perspective and improves
-on the results of \cite{kingma_variational_2015} in two directions: the authors propose a
-more accurate approximation to the KL-divergence term in \eqref{eq:elbo}, and introduce
-additive noise parameterization for the factors of $q_\theta(\omega)$, $\omega = W$.
+$ for $\alpha = \tfrac{p}{1-p}$. This suggests making $\alpha$ a variational parameter
+and optimizing it in \eqref{eq:elbo_general} with an appropriate penalty term. Flexibility
+in dependence of $q_\theta$ on $\alpha$ allows structured dropout with shared $\alpha$
+across groups of parameters or sparsifying dropout, where the rate $\alpha$ is optimized
+for each individual parameter, \cite{molchanov_variational_2017}.
+
+Variational Dropout with mean field Gaussian variational approximation is further developed
+in \cite{molchanov_variational_2017} and \cite{kharitonov_variational_2018}. The first paper
+studies variational dropout from a model sparsification perspective and improves on the
+results of \cite{kingma_variational_2015} in two directions: the authors propose a more
+accurate approximation to the KL-divergence term in \eqref{eq:elbo}, and introduce additive
+noise parameterization for the factors of $q_\theta(\omega)$, $\omega = W$.
 
@@
 In another variant of Bayesian dropout, called Automatic Relevance Determination, is developed
-in the \cite{molchanov2018}. The key difference from Variational Dropout is the choice of
-prior: the log-uniform factor $\pi(\omega_{ij})$ is replaced by a proper Gaussian prior
-$\mathcal{N}(0, \tau^{-1}_{ij})$ with learnable precision $\tau_{ij} > 0$. This is knowns as
-the Empirical Bayes method, \cite{citation_needed}, which fits a prior distribution while
+in the \cite{kharitonov_variational_2018}. The key difference from Variational Dropout is the
+choice of prior: the log-uniform factor $\pi(\omega_{ij})$ is replaced by a proper Gaussian
+prior $\mathcal{N}(0, \tau^{-1}_{ij})$ with learnable precision $\tau_{ij} > 0$. This is knowns
+as the Empirical Bayes method, \cite{citation_needed}, which fits a prior distribution while
 performing variational inference. The optimal precision parameter is found in the closed form
 by minimizing the KL-divergence term holding variational parameters $\theta$ fixed.
+
+Second contribution of \cite{kingma_variational_2015} is the analysis of the \textit{local
+reparameterization trick}, proposed in \cite{wang_fast_2013} to speed up Gaussian dropout,
+as a gradient variance reduction technique for \eqref{eq:elbo}. This trick utilizes the
+closure of Gaussians under affine transformations, thereby translating uncertainty from the
+global parameter noise to local noise in intermediate outputs within the network.
+%
+\cite{kingma_variational_2015} show, that for the case of fully factorized Gaussian
+posterior approximations, the trick decorrelates ELBO estimates within the minibatch,
+making the gradient estimator $\nabla_\theta \tilde{\mathcal{L}}$ more statistically
+efficient.
 
@@
 estimator. We formulate the $\cplx$ version of the local reparameterization trick, which
-generalizes \cite{who-dis-originally-22}.
+generalizes \cite{wang_fast_2013}.
 

### 2019-11-06 paper/paper.tex
compactified the last part of the VD section

@@
 $ for $\alpha = \tfrac{p}{1-p}$. This suggests making $\alpha$ a variational parameter
-and optimizing it in \eqref{eq:elbo_general} with an appropriate penalty term. Flexibility
-in dependence of $q_\theta$ on $\alpha$ allows structured dropout with shared $\alpha$
-across groups of parameters or sparsifying dropout, where the rate $\alpha$ is optimized
-for each individual parameter, \cite{molchanov_variational_2017}.
-
-Variational Dropout with mean field Gaussian variational approximation is further developed
-in \cite{molchanov_variational_2017} and \cite{kharitonov_variational_2018}. The first paper
-studies variational dropout from a model sparsification perspective and improves on the
-results of \cite{kingma_variational_2015} in two directions: the authors propose a more
-accurate approximation to the KL-divergence term in \eqref{eq:elbo}, and introduce additive
-noise parameterization for the factors of $q_\theta(\omega)$, $\omega = W$.
-
-Under the original $(\mu, \alpha)$ parameterization the stochastic output of a linear
-layer $
-  y = W^\top x + b
-$ with $
-  W \in \mathbb{R}^{n\times m}
-$ and independent $
-  W_{ij} \sim \mathcal{N}(\mu_{ij}, \alpha_{ij} \mu_{ij}^2)
-$ is equivalent in distribution to $
-  y \sim \prod_i \mathcal{N}\Bigl(
-      \sum_j \mu_{ij} x_j + b_i,
-      \sum_j \alpha_{ij} \mu_{ij}^2 x_j^2
-  \Bigr)
-$. \cite{molchanov_variational_2017} argue that for the purposes of model sparsification
-this parameterization should be abandoned in favour of an equivalent $(\mu, \sigma^2)$ with
-the score $\alpha$ calculated using $\tfrac{\sigma^2}{\mu^2}$ when needed. This makes $
-  \nabla_\mu \tilde{\mathcal{L}}
-$, which is particularly important for sparsification, independent of the noise injected
-by the trick.
-
-\cite{kingma_variational_2015} and \cite{molchanov_variational_2017} consider a factorized
-prior $\pi(\omega)$ with improper log-uniform factors $
+and optimizing it in \eqref{eq:elbo_general} with an appropriate penalty term. Thus,
+\cite{kingma_variational_2015} propose \textit{Variational Dropout} with mean field Gaussian
+approximation $
+  q_\theta(\omega)
+    = \prod_j \mathcal{N}(\mu_j, \alpha_j \mu_j^2)
+$ and factorized log-uniform prior $\pi(\omega)$ with $
   \pi(\omega_j) \propto \lvert \omega_j \rvert^{-1}
@@
 \end{equation}
-The expectation in \eqref{eq:expect-improper-term-cplx} is half the $\log$-moment of a non-central
-$\chi^2$ distribution with shape $1$ and non-centrality $\lambda = \tfrac1{\alpha}$. In general,
-there is no analytically tractable expression for log-moment of a $\chi^2_m$ with odd degrees
-of freedom. To circumvent this, \cite{kingma_variational_2015} approximate the expectation by
-a non-linear polynomial regression for truncated $\alpha \in (0, 1)$. This approximation was
-substantially refined in \cite{molchanov_variational_2017}, both in term of the domain of scores
-$\alpha$ and accuracy. The paper considered regression with sigmoid and soft-plus basis functions
-fit to the Monte-Carlo estimator of \eqref{eq:improper-kl-div-real} for $\alpha$ varying over
-a fine logarithmic grid. In sec.~\ref{sub:real-chisq-grad} we verify the approximation and
-compare the approximate derivative to the exact derivative of \eqref{eq:improper-kl-div-real}
-with respect to $\log \alpha$.
-% Since gradient based methods rely on unbiased gradient estimates
-
-In another variant of Bayesian dropout, called Automatic Relevance Determination, is developed
-in the \cite{kharitonov_variational_2018}. The key difference from Variational Dropout is the
-choice of prior: the log-uniform factor $\pi(\omega_{ij})$ is replaced by a proper Gaussian
-prior $\mathcal{N}(0, \tau^{-1}_{ij})$ with learnable precision $\tau_{ij} > 0$. This is knowns
-as the Empirical Bayes method, \cite{citation_needed}, which fits a prior distribution while
-performing variational inference. The optimal precision parameter is found in the closed form
-by minimizing the KL-divergence term holding variational parameters $\theta$ fixed.
-
-Second contribution of \cite{kingma_variational_2015} is the analysis of the \textit{local
+In general, there is tractable expression for log-moment of a non-central $\chi^2_m$ random
+variable with odd $m$, that sits under the expectation in \eqref{eq:expect-improper-term-cplx}.
+To circumvent this, \cite{kingma_variational_2015} approximate the expectation by a non-linear
+polynomial regression for truncated $\alpha \in (0, 1)$. This approximation was refined in
+\cite{molchanov_variational_2017}, both in terms of the domain of $\alpha$ and accuracy. The
+paper considered regression with sigmoid and soft-plus basis functions fit to the Monte-Carlo
+estimator of \eqref{eq:improper-kl-div-real} for $\alpha$ varying over a fine logarithmic grid.
+In sec.~\ref{sub:real-chisq-grad} we verify the approximation and confirm its accuracy, by
+comparing its derivative to the exact derivative of \eqref{eq:improper-kl-div-real} with
+respect to $\log \alpha$.
+% (!) good for SGVB: gradient-based methods require unbiased gradient estimates
+
+Flexibility in dependence of $q_\theta$ on $\alpha$ allows structured dropout with shared
+$\alpha$ across groups of parameters $\omega$. \cite{molchanov_variational_2017} study
+Variational Dropout from a model sparsification perspective, optimizing $\alpha$ for each
+individual parameter. Another variant of Bayesian dropout, called Automatic Relevance
+Determination, is developed in \cite{kharitonov_variational_2018}. The key difference from
+Variational Dropout is the choice of prior: the log-uniform factor $\pi(\omega_{ij})$ is
+replaced by a proper Gaussian prior $
+  \mathcal{N}(0, \tau^{-1}_{ij})
+$ with learnable precision $\tau_{ij} > 0$. This is known as the Empirical Bayes method,
+\cite{citation_needed}, which fits a prior distribution while performing variational inference.
+The optimal precision parameter is found in the closed form by minimizing the KL-divergence
+term holding variational parameters $\theta$ fixed.
+
+Another contribution of \cite{kingma_variational_2015} is the analysis of the \textit{local
 reparameterization trick}, proposed in \cite{wang_fast_2013} to speed up Gaussian dropout,
@@
 %
+The stochastic output of a linear layer $
+  y = W^\top x + b
+$ with $
+  W \in \mathbb{R}^{n\times m}
+$ and independent $
+  W_{ij} \sim \mathcal{N}(\mu_{ij}, \alpha_{ij} \mu_{ij}^2)
+$ is equivalent in distribution to
+\begin{equation} \label{eq:r-gauss-trick}
+    y \sim \prod_i \mathcal{N}\Bigl(
+          \sum_j \mu_{ij} x_j + b_i,
+          \sum_j \alpha_{ij} \mu_{ij}^2 x_j^2
+      \Bigr)
+    \,.
+\end{equation}
+%
 \cite{kingma_variational_2015} show, that for the case of fully factorized Gaussian
@@
 making the gradient estimator $\nabla_\theta \tilde{\mathcal{L}}$ more statistically
-efficient.
+efficient. \cite{molchanov_variational_2017} propose an improvement by introducing
+\textit{additive noise parameterization}, which is relevant to model sparsification.
+The paper argues that $(\mu, \alpha)$ parameterization should be abandoned in favour
+of an equivalent $(\mu, \sigma^2)$ with the score $\alpha$ calculated using $
+  \tfrac{\sigma^2}{\mu^2}
+$ when needed. This makes $
+  \nabla_\mu \tilde{\mathcal{L}}
+$, which is shown in \cite{molchanov_variational_2017} to be independent of the noise,
+injected by the trick \eqref{eq:r-gauss-trick}, and further stabilizes gradients in SGVB
+\eqref{eq:elbo}.
 

### 2019-11-06 paper/paper.tex
minor retouching of ARD dropout

@@
   \mathcal{Q} = \{Q_\theta(d\omega) \colon \theta \in \Theta\}
-$. The class $\mathcal{Q}$ is picked so that its member have tractable densities $
+$, $\theta$ -- generic variational parameter. The class $\mathcal{Q}$ is picked so that
+its member have tractable densities $
   q_\theta(\omega) d\omega
@@
 
-Stochastic Gradient Variational Bayes (SGVB), proposed by \cite{kingma_auto-encoding_2014},
+\textit{Stochastic Gradient Variational Bayes} (SGVB), proposed by \cite{kingma_auto-encoding_2014},
 is an differentiable unbiased Monte-Carlo estimator of \eqref{eq:elbo_general}, which makes
@@
 and optimizing it in \eqref{eq:elbo_general} with an appropriate penalty term. Thus,
-\cite{kingma_variational_2015} propose \textit{Variational Dropout} with mean field Gaussian
-approximation $
+\cite{kingma_variational_2015} propose \textit{Variational Dropout} with mean field
+Gaussian approximation $
   q_\theta(\omega)
@@
 Variational Dropout from a model sparsification perspective, optimizing $\alpha$ for each
-individual parameter. Another variant of Bayesian dropout, called Automatic Relevance
-Determination, is developed in \cite{kharitonov_variational_2018}. The key difference from
-Variational Dropout is the choice of prior: the log-uniform factor $\pi(\omega_{ij})$ is
-replaced by a proper Gaussian prior $
+individual parameter. Another variant of Bayesian dropout, called \textit{Automatic Relevance
+Determination}, is developed in \cite{kharitonov_variational_2018}. The key difference is
+that the log-uniform factor $\pi(\omega_{ij})$ is replaced by a proper Gaussian prior $
   \mathcal{N}(0, \tau^{-1}_{ij})
-$ with learnable precision $\tau_{ij} > 0$. This is known as the Empirical Bayes method,
-\cite{citation_needed}, which fits a prior distribution while performing variational inference.
-The optimal precision parameter is found in the closed form by minimizing the KL-divergence
-term holding variational parameters $\theta$ fixed.
+$ with learnable precision $\tau_{ij} > 0$. This method, known as \textit{Empirical Bayes}
+\cite{citation_needed}, fits a prior distribution while performing variational inference.
+Maximizing \eqref{eq:elbo} over $\lambda$, holding other parameters fixed, yields $
+  \tau^* = {(\mu^2 + \sigma^2)}^{-1}
+$, whence
+\begin{equation}  \label{eq:ard-kl-div-real}
+  KL(q_\theta(\omega) \| \pi(\omega))
+    = \log{\bigl(1 + \tfrac1{\alpha} \bigr)}
+    \,.
+\end{equation}
 

### 2019-11-06 paper/paper.tex
compacted KL-div paragraph

@@
 %% drafting macro
-\newcommand{\important}[1]{\textbf{\color{red} #1}}
+\newcommand{\important}[1]{\textbf{\colorbox{red}{#1}}}
 \newcommand{\attn}[2]{\textbf{\color{red} #2~\textsuperscript{\textit{[#1]}}}}
@@
 
-Kullback-Leibler divergence, defined for $q(\omega) \ll p(\omega)$ as
-$$
-KL(q\| p)
+Kullback-Leibler divergence of density $q$ from $p$ is
+\begin{equation} \label{eq:kl-div-def}
+  KL(q \| p)
+    % = \int \frac{dQ}{dP} \log{\frac{dQ}{dP}} P(d\omega)
+    % = \int \frac{q(\omega)}{p(\omega)} \log{\frac{q(\omega)}{p(\omega)}} p(\omega) d\omega
+    % = \mathbb{E}_{\omega \sim q}
+    %   \log\frac{q(\omega)}{p(\omega)}
     = \mathbb{E}_{\omega \sim q}
-    \log\frac{q(\omega)}{p(\omega)}
-  \,, $$
-is the natural choice for $\rho$, despite it not being a metric and requiring distributions
-with nested support. The main reason is that it satisfies the following identity, which when
-everything works, holds for any $q$ and $p$:
+      \log{q(\omega)}
+    - \mathbb{E}_{\omega \sim q}
+      \log{p(\omega)}
+    \,,
+\end{equation}
+% and, despite it not being a metric and requiring distributions with nested support,
+and is the natural choice for $\rho$, the main reason being that it satisfies the following
+identity for well-behaved $q$ and $p$:
 \begin{equation} \label{eq:kl-div-master}
@@
 $.
+%
+\todo{DSVI}
 

### 2019-11-06 paper/paper.tex
edited the cplx-overview section, moved a paragraph (to be edited) into appendix

@@
 In this section we overview $\mathbb{C}$-valued networks, their motivation and peculiarities.
-In out exposition we shall focus mostly on linear layers, keeping in mind that transferring 
+In our exposition we shall focus mostly on linear layers, keeping in mind that transferring 
 the ideas to convolutional layers is straightforward.
 
-The most recent study of complex-valued networks \cite{trabelsi_deep_2017}, provides a set
-of building blocks for deep $\cplx$-valued networks. The core of their work is structured
-framework for complex-valued operations including representation and linear layers (dense
-and convolutional) as well as $\cplx$-valued activations and complex batch-normalization
-and weight initialization.
+The study \cite{trabelsi_deep_2017}, outlines building blocks for deep $\cplx$-valued
+networks and describes suitable representation and operations including linear layers (dense
+and convolutional), $\cplx$-valued activations, complex batch-normalization and suitable
+weight initialization. In fact all papers touching one way or another upon the subject of
+$\cplx$-valued networks, refrain each other, and the current study is no exception.
 
@@
 $, storing the real and imaginary parts in interleaved format, and emulate $\cplx$-algebra
-using $\real$-valued arithmetic. Thus designed $\cplx$-network is, essentially, a
-$\real$-network with \textit{double} the layers' widths to accommodate real and imaginary
-parts and with constraints on layers' parameters that make them respect $\cplx$-algebra.
-This makes it possible to retrofit $\cplx$-valued networks into the existing $\real$-valued
-auto-differentiation libraries.
-
-In particular, common linear layers, such as dense layers and convolutions,
+using $\real$-valued arithmetic. In particular, convolutional and linear layers,
 $
@@
 $ act upon their inputs as follows:
-$$
+\begin{equation} \label{eq:cplx-lin-op}
   \real^{2 \times \mathrm{[in]}}
@@
       \Bigr)
-  \,, $$
+    \,,
+\end{equation}
 where $
@@
       \to \real^{\mathrm{[out]}}
-$ are the unique $\real$-linear operators that make up $L = L_r + j L_i$ the overall
-effect of the layer. For instance, to respect $\cplx$-arithmetic a convolutional layer with
-$\cplx$-kernel $W$ can be implemented using two $\real$-convolutions with $\real$-kernels
-$\Re{W}$ and $\Im{W}$. Other algebraic operations, such as division and roots in batch
-normalization \cite{trabelsi_deep_2017}, are implemented in such a way as to respect
-$\cplx$-algebra.
-%
+$ are unique linear operators that make up $L = L_r + j L_i$. Thus, a $\cplx$-convolutional
+layer with complex kernel $W$ can be implemented as two $\real$-convolutions with kernels
+$\Re{W}$ and $\Im{W}$ using \eqref{eq:cplx-lin-op}. Other algebraic operations, such as
+trigonometric functions, and complex division and roots in batch normalization
+\cite{trabelsi_deep_2017}, are implemented through their counterparts in $\real^2$. This
+makes $\cplx$-valued network into an intricately connected $\real$-valued computational
+graph that respects $\cplx$-algebra.
+
 Concerning activations, \cite{trabelsi_deep_2017} consider the following: independent
@@
 
-The question of differentiability of complex-valued networks is tricky, since they usually
-use non-differentiable non-linearities. However, a more severe problem stems from the loss
-objective being real-valued. Indeed, if $f\colon \cplx \to \cplx$ were $\cplx$-differentiable
-(holomorphic), the composition of $f$ with a non-trivial $h \colon \cplx\to \real$ makes it
-not $\cplx$-differentiable with respect parameters, since $h$ violates Cauchy-Riemann conditions.
-This problem is dealt with by using Wirtinger, or $\cplx\real$ calculus, which subsumes
-$\cplx$-calculus, and is applicable to non-holomorphic functions of $\cplx$-argument,
-\cite{adali_complex-valued_2011}. As a basis for backpropagation algorithm it was considered
-in \cite{benvenuto_complex_1992} and \cite{trabelsi_deep_2017}.
-
-Basically $\cplx\real$ calculus regard $f(z)$ as a function of two independent variables $z$ 
-and its conjugate $\conj{z}$ and symbolically defines derivative operators $
-  \tfrac{\partial}{\partial z}
-$ and $
-  \tfrac{\partial}{\partial \conj{z}}
-$, that satisfy linearity, product and chain rules, and respect complex conjugation. The important
-property is that, if we identify $f(z) = f(u + jv) = F(u, v)$, then the $\cplx\real$ calculus
-rules differential of $f$ as a $\cplx$ function coincides its differential as an $\real^2$
-function. This makes it possible to use and apply the rules of $\real$-calculus to the networks
-represented in paired $\real$ fashion and use existing $\real$-valued backpropagation in autograd
-software. The key analytic advantage is that computing derivatives is more streamlined, less
-messy, and derivative expressions involving complex variables turn out to be simpler that their
-real-imaginary analogues, \cite{adali_complex-valued_2011}.
+Complex networks are, in general, non-holomorphic, i.e. not $\cplx$-differentiable, which is
+exacerbated by the loss being real-valued. Indeed, as implied by Cauchy-Riemann conditions, a
+$\cplx$-differentiable real-valued function is necessarily trivial. This issue is dealt with
+by employing Wirtinger, or $\cplx\real$ calculus, which generalizes holomorphic calculus
+to non-holomorphic functions of $\cplx$-argument, \cite{adali_complex-valued_2011}. It was
+considered as a basis for $\cplx$ version of backpropagation in \cite{benvenuto_complex_1992}
+and \cite{trabelsi_deep_2017} (see sec.~\ref{sub:wirtinger_calculus} for details). The key
+benefit of $\cplx\real$ calculus is straightforward symbolic differentiation, and the fact,
+that this allows retrofiting $\cplx$-valued networks into existing $\real$ deep learning
+auto-differentiation libraries.
+
+\todo{read on holomorphic nets}
 
@@
 % TLDR: we use Wirtinger calculus!
+Basically $\cplx\real$ calculus regard $f(z)$ as a function of two independent variables $z$ 
+and its conjugate $\conj{z}$ and symbolically defines derivative operators $
+  \tfrac{\partial}{\partial z}
+$ and $
+  \tfrac{\partial}{\partial \conj{z}}
+$, that satisfy linearity, product and chain rules, and respect complex conjugation. The important
+property is that, if we identify $f(z) = f(u + jv) = F(u, v)$, then the $\cplx\real$ calculus
+rules differential of $f$ as a $\cplx$ function coincides its differential as an $\real^2$
+function. This makes it possible to use and apply the rules of $\real$-calculus to the networks
+represented in paired $\real$ fashion and use existing $\real$-valued backpropagation in autograd
+software. The key analytic advantage is that computing derivatives is more streamlined, less
+messy, and derivative expressions involving complex variables turn out to be simpler that their
+real-imaginary analogues, \cite{adali_complex-valued_2011}.
 

### 2019-11-06 paper/paper.tex
compressed cplx-real-calculus review in appendix

@@
 Complex networks are, in general, non-holomorphic, i.e. not $\cplx$-differentiable, which is
-exacerbated by the loss being real-valued. Indeed, as implied by Cauchy-Riemann conditions, a
-$\cplx$-differentiable real-valued function is necessarily trivial. This issue is dealt with
-by employing Wirtinger, or $\cplx\real$ calculus, which generalizes holomorphic calculus
-to non-holomorphic functions of $\cplx$-argument, \cite{adali_complex-valued_2011}. It was
-considered as a basis for $\cplx$ version of backpropagation in \cite{benvenuto_complex_1992}
-and \cite{trabelsi_deep_2017} (see sec.~\ref{sub:wirtinger_calculus} for details). The key
-benefit of $\cplx\real$ calculus is straightforward symbolic differentiation, and the fact,
-that this allows retrofiting $\cplx$-valued networks into existing $\real$ deep learning
-auto-differentiation libraries.
+exacerbated by the loss being real-valued. Indeed a $\cplx$-differentiable real-valued function is
+necessarily trivial by Cauchy-Riemann conditions. This issue is dealt with by employing Wirtinger,
+or $\cplx\real$ calculus, which generalizes holomorphic calculus to non-holomorphic functions
+of $\cplx$-argument, \cite{adali_complex-valued_2011}. The rules it defines satisfy intuitive
+linearity, product and chain rules, and respect complex conjugation, but most importantly the
+$\cplx\real$-differential of a function on $\cplx$ coincides with its classical differential as
+a function on $\real^2$. Essentially, it allows straightforward retrofiting of $\cplx$-valued
+networks into existing $\real$ deep learning auto-differentiation frameworks. It was considered
+as a basis for $\cplx$ version of backpropagation in \cite{benvenuto_complex_1992} and
+\cite{trabelsi_deep_2017}, (see sec.~\ref{sub:wirtinger_calculus} for details).
 
@@
 % TLDR: we use Wirtinger calculus!
-Basically $\cplx\real$ calculus regard $f(z)$ as a function of two independent variables $z$ 
-and its conjugate $\conj{z}$ and symbolically defines derivative operators $
-  \tfrac{\partial}{\partial z}
-$ and $
-  \tfrac{\partial}{\partial \conj{z}}
-$, that satisfy linearity, product and chain rules, and respect complex conjugation. The important
-property is that, if we identify $f(z) = f(u + jv) = F(u, v)$, then the $\cplx\real$ calculus
-rules differential of $f$ as a $\cplx$ function coincides its differential as an $\real^2$
-function. This makes it possible to use and apply the rules of $\real$-calculus to the networks
-represented in paired $\real$ fashion and use existing $\real$-valued backpropagation in autograd
-software. The key analytic advantage is that computing derivatives is more streamlined, less
-messy, and derivative expressions involving complex variables turn out to be simpler that their
-real-imaginary analogues, \cite{adali_complex-valued_2011}.
 
@@
 % https://math.stackexchange.com/a/444493
-Wirtinger calculus relies on the natural identification of $\cplx$ with $\real \times \real$.
-Let's consider $
+Wirtinger ($\cplx\real$) calculus relies on the natural identification of $\cplx$ with $
+  \real \times \real
+$, and regards $
   f\colon \cplx \to \cplx
-$ and treat it as an equivalent function $\real^2 \to \cplx$ via $
+$ as an equivalent in algebraic sense function $F\colon \real^2 \to \cplx$ defined $
   f(z) = f(u + jv) = F(u, v)
-$. Wirtinger calculus defines two formal derivative operators
+$. Under this identification, we define two formal derivative operators
 $
@@
 where $dz = du + j dv$ and $d\conj{z} = du - j dv$. This implies that the complex argument
-and its conjugate are treated as independent variables. In this notation Cauchy-Riemann
-conditions are expressed as $
+and its conjugate are treated as independent variables. Cauchy-Riemann conditions $
+  -j \tfrac{\partial F}{\partial v} = \tfrac{\partial F}{\partial u}
+$ impose a rigid structure on real and imaginary parts of $F$ and can be expressed as $
   \tfrac{\partial f}{\partial \conj{z}} = 0
-$, or $
-  -j \tfrac{\partial F}{\partial v} = \tfrac{\partial F}{\partial v}
-$. These conditions impose a rigid structure on real and imaginary parts of $F(u, v)$, namely $
-  \tfrac{\partial F_{\Re }}{\partial u} = \tfrac{\partial F_{\Im }}{\partial v}
-$ and $
-  \tfrac{\partial F_{\Re }}{\partial v} = - \tfrac{\partial F_{\Im }}{\partial u}
-$. Thus Wirtinger calculus subsumes the usual $\cplx$-calculus on holomorphic functions,
-when $
-  \tfrac{\partial f}{\partial \conj{z}} = 0
-$, i.e. $
-  f(z)
-    % = g(z, \conj{z})
-    = F(\tfrac12 (z + \conj{z}), \tfrac1{j 2} (z - \conj{z}))
-$ does not depend on $\conj{z}$. The usual rules of calculus, like chain and product rules,
-follow directly from the definition of the operators, e.g.
+$ in this notation. Thus $\cplx\real$ calculus subsumes the usual $\cplx$-calculus on
+holomorphic functions, when $f(z)$, regarded as $f(z, \conj{z})$, is constant with respect
+to $\conj{z}$. The usual rules of calculus, like chain and product rules, follow directly
+from the definition of the operators, e.g.
 $$
@@
 
-Since in machine learning the target loss is typically an empirical real-valued risk, which
-is minimized, and we let's derive the expression for the gradient and make sure that it is
-compatible with real-valued calculus upon which current auto-differentiation tools are built.
-For a real-valued $f\colon \cplx \to \real$ we have $\conj{f} = f$, whence $
+In machine learning tasks the target objective is typically empirical risk, which has to
+be real-valued to be minimized. Nevertheless, the expression of the $\cplx\real$ gradient
+is compatible with what is expected, when $f$ is treated like a $\real^2$ function. For a
+real-valued $f\colon \cplx \to \real$ we have $\conj{f} = f$, which implies $
   \tfrac{\partial f}{\partial \conj{z}}
@@
     = \conj{\tfrac{\partial f}{\partial z}}
-$. Hence
+$, whence
 $$
@@
   \,. $$
-Hence the gradient of $f$ at $z$ is given by $
-  \tfrac{\partial f}{\partial \conj{z}}
+Thus, the gradient of $f$ at $z$ is given by $
+  \nabla_z f(z)
     = \tfrac{\partial F}{\partial u}
       + j \tfrac{\partial F}{\partial v}
-$, meaning that we can use gradients with respect ral and imaginary parts independently. Thus
-using Wirtinger calculus makes it possible to reuse $\real$-backpropagation for $\cplx$-networks.
+$. Therefore, Wirtinger calculus makes it possible to reuse $\real$-backpropagation.
 

### 2019-11-07 paper/paper.tex
cplx-gaussian overhaul

@@
 
+%notation
+We first clarify some notation: $M^{\top}$ is the matrix transpose, $\conj{M}$ is elementwise
+complex conjugation, and $M^{\hop} = (\conj{M})^\top$ denotes Hermitian conjugate.
+
 \subsection{$\cplx$-Gaussian Variational Approximation} % (fold)
@@
 
-A random vector $z\in \cplx^m$ is said to have complex Gaussian distribution, if its
-characteristic function is
-$$
-z \sim \mathcal{N}^{\cplx}_m(z \vert \mu, \Gamma, C)
-  \Leftrightarrow
-  \mathbb{E}_{z} e^{j \Re{(t^{\hop} z)}}
-  = \exp{\{
-    j \Re{(t^{\hop} \mu)}
-    - \tfrac14 \bigl(
-      t^{\hop} \Gamma t + \Re{(t^{\hop} C \conj{t})}
-    \bigr)
-  \}}
-  \,, $$
-where $\mu \in \cplx^m$ is the mean, $\Gamma, C \in \cplx^{m\times m}$ are complex covariance
-and relation matrices satisfying $C^\top = C$, $\Gamma^{\hop} = \Gamma$, $\Gamma \succeq 0$,
-and $
-  \conj{\Gamma} \succeq C^{\hop} \Gamma^{-1} C
-$. The matrices $\Gamma$ and $C$ correspond to $
-  \mathbb{E} (z - \mu)(z - \mu)^{\hop}
-$ and $
-  \mathbb{E} (z - \mu)(z - \mu)^\top
-$, respectively. Here ${\cdot}^{\hop}$ denotes Hermitian conjugate, i.e. $
-  A^{\hop} = (\conj{A})^\top
-$, ${\cdot}^{\top}$ -- the matrix transpose, and $\conj{\cdot}$ -- the complex conjugation
-elementwise.
-%
-% The intuition behind them is more apparent in the complex univariate case ($m=1$):
-% here $\Gamma = \sigma^2 \geq 0$, and $C$ can be represented as $\sigma^2 \rho \in \cplx$ with $
-%   \lvert \rho \rvert \leq 1
-% $. Therefore $\sigma^2$ affects the overall ``concentration'' of the complex random variable,
-% whereas $\rho$ is responsible for the strength and ``direction'' of the linear relation between
-% the real and imaginary parts, \cite{lapidoth_capacity_2003}.
-% $$
-% \frac{\sigma^2}2
-%   \begin{pmatrix}
-%     1 + \Re{\rho} & \Im{\rho} \\
-%     \Im{\rho} & 1 - \Re{\rho}
-%   \end{pmatrix}
-%   = \frac{\sigma^2}2 I
-%   + \frac{\sigma^2 \lvert \rho \rvert}2 
-%   \begin{pmatrix}
-%     \cos\theta & \sin\theta \\
-%     \sin\theta & - \cos\theta
-%   \end{pmatrix}
-% $$
-
-A characterization of a $\cplx$-Gaussian vector, more useful for the current study, is via the
-equivalence with the paired real multivariate Gaussian distribution:
-\begin{multline}  \label{eq:cn-paired-real-density}
+A random vector $z\in \cplx^m$ has complex Gaussian distribution, $
   z \sim \mathcal{N}^{\cplx}_m(\mu, \Gamma, C)
-    \\\Leftrightarrow
+$, with mean $\mu \in \cplx^m$ and $\cplx^{m\times m}$ covariance and relation
+matrices $\Gamma$ and $C$ are, respectively, if 
+\begin{equation}  \label{eq:cn-paired-real-density}
   \begin{pmatrix}
@@
     \biggr)
-    \,.
-\end{multline}
-It is possible to recover the $\cplx$ covariance and relation matrices from a block covariance
-matrix $\Sigma$ of a \textit{non-degenerate} paired real Gaussian vector through
-$$
-\begin{pmatrix}
-  \Sigma_{rr} & \Sigma_{ri} \\ 
-  \Sigma_{ir} & \Sigma_{ii} 
-\end{pmatrix}
-  = \frac12
-    \begin{pmatrix}
-      \Re{(\Gamma + C)} & - \Im{(\Gamma - C)} \\
-      \Im{(\Gamma + C)} &   \Re{(\Gamma - C)}
-    \end{pmatrix}
-  \, \Leftrightarrow
-  \,
-  \begin{cases}
-    \Gamma
-      = \Sigma_{rr} + \Sigma_{ii} + j (\Sigma_{ir} - \Sigma_{ri})
-    \,, \\
-    C = \Sigma_{rr} - \Sigma_{ii} + j (\Sigma_{ir} + \Sigma_{ri}) 
-  \end{cases}
-  $$
-
-A $\cplx$-Gaussian random vector $z$ is called \textit{proper}, when $C = 0$, i.e. the random
-vector $z$ and its conjugate $\conj{z}$ are uncorrelated. This implies that in the paired real
-representation $
-  \Sigma_{ir} = -\Sigma_{ri} = -\Sigma_{ir}^\top
-$ and $\Sigma_{rr} = \Sigma_{ii}$, i.e. real and imaginary component of the same random element
-are uncorrelated, since skew-symmetric matrices necessarily have zero-diagonal.
-
-The $\cplx$-Gaussian family of distributions is closed under affine transformations:
-if $
-  x \sim \mathcal{N}_m^{\cplx}(\mu, \Gamma, C)
-$ and $y = A x + b$, for $
-  A \in \cplx^{n\times m}
+    \,,
+\end{equation}
+provided they satisfy $\Gamma \succeq 0$, $\Gamma^{\hop} = \Gamma$, $C^\top = C$, and $
+  \conj{\Gamma} \succeq C^{\hop} \Gamma^{-1} C
+$. This distribution possesses the usual properties of $\real$-valued Gaussians, including
+if $y = A z + b$ for $
+  A \in \cplx^{n \times m}
 $ and $b \in \cplx^{n}$, then $
-  y \sim \mathcal{N}_n^{\cplx}(A\mu + b, A \Gamma A^\hop, A C A^\top)
-$. This follows from the effects of the affine transformation on the characteristic
-function.
-
-To develop $\cplx$-variational dropout we assume a fully factorized posterior approximation
-distribution on the layers' parameters: $\omega = (W, b)$, where a $\cplx$-valued $W$ collects
-all weight matrices of linear layers and kernels of convolutional layers, and $b$ represents
-all bias term combined. We use a fully factorized Dirac family on the biases, and mean-field
-proper $\cplx$-Gaussian variational approximation for the weights: $
-  q(W) = \prod_{lij} q(W^{l}_{ij})
-$ with each parameter being an independent univariate proper complex Gaussian
-% (we omit the subscript $m=1$ for brevity)
-\begin{equation} \label{eq:c-gauss-vi}
-  W_{ij}
-    \sim \mathcal{N}^{\cplx}(\mu_{ij}, \sigma^2_{ij}, 0)
-  \,.
-\end{equation}
-Thus we would like to sparsify the weights in the network and, since the bias terms constitute
-a meagre share of network's parameters and are rarely dropped out or pruned, we use Bayesan
-MAP estimates for them.
-
-As was demonstrated in \cite{kingma_variational_2015}, local reparameterization trick
-provides both faster computations and better statistical efficiency of the SGVB gradient
-estimator. We formulate the $\cplx$ version of the local reparameterization trick, which
-generalizes \cite{wang_fast_2013}.
-
-% subsection c_gaussian_variational_approximation (end)
-
-\subsection{Local reparameterization trick} % (fold)
-\label{sub:local_reparameterization_trick}
-
-To simplify exposition of the trick, we consider the complex linear dense layer, and afterwards
-outline the caveats for $\cplx$-convolutional layers. In both cases we use fully factorized
-general $\cplx$-Gaussian distribution for parameters $W$ of the layer.
-
-Consider a $\cplx$-linear layer: $
-  W \in \cplx^{n\times m}
-$ is a random $\cplx$-Gaussian matrix with independent elements $
-  w_{ij} \sim \mathcal{N}^{\cplx}\bigl(
-    w_{ij}
-    \big \vert
-    \mu_{ij}, \sigma^2_{ij}, C_{ij}
+  y \sim \mathcal{N}_n^{\cplx}\bigl(
+      A\mu + b, A \Gamma A^{\hop}, A C A^\top
     \bigr)
-$ with $\mu_{ij}\in cplx$, $\sigma^2_{ij} \geq 0$, $C_{ij}\in \cplx$ and $
-  \lvert C_{ij} \rvert^2 \leq \sigma^2_{ij}
-$. We begin by observing that the variational approximation of $q(W)$ is a multivariate
-$\cplx$-Gaussian: $
-  \vec{W}
-    \sim \mathcal{N}^{\cplx}_{[n\times m]} \bigl(
-      \vec{\mu}, \diag{\vec{\Sigma}}, \diag{\vec{C}}
-    \bigr)
-$, where $[n\times m]$ denotes lexicographically flattened dimension and $\diag{v}$ is a
-diagonal square matrix with $v_i$ on the main diagonal. Here we collected variances and means
-into matrices $\Sigma$ and $\mu$, respectively.
-%
-Now, for any $x \in \cplx^m$ and $b\in \cplx^n$ we have
-$$
-W x + b
-  % = I_n W x + b
-  = (I_n \otimes x^\top) \vec{W} + b
-  \,, $$
-where $\vec{\cdot}$ denotes flattening in lexicographic order of indices (row-major), and
-$\otimes$ denotes the Kronecker product, for which we have the identity $
-  \vec{P Q R} = (P \otimes R^\top) \vec{Q}
-$, \cite{petersen_matrix_2012}.
-% It follows from the definition of the Kronecker product
-% of $P$ and $R^\top$ and the row-major order vectorization.
-%
-Structure of the matrices, involved in this expression, and the identity $
-  (P \otimes R) (C \otimes S) = P Q \otimes R S
-$, \cite{petersen_matrix_2012}, imply
-\begin{align*}
-  (I \otimes x^\top) \diag{\vec{\Sigma}} (I \otimes x^\top)^\hop
-    % &= \sum_{ij} (I \otimes x^\top) e_i \otimes e_j
-    %   \sigma^2_{ij} (e_i \otimes e_j)^\top (I \otimes x^\top)^\hop
-    % \\
+$. The entropy of a $\cplx$-Gaussian distribution $
+  q = \mathcal{N}^{\cplx}_m(\mu, \Gamma, C)
+$ is
+\begin{align} \label{eq:c-gauss-entropy-derivation}
+  \mathbb{H}(q)
+    & = - \mathbb{E}_{z \sim q} \log{q(z)}
+    \notag \\
     &
-    = \sum_{ij} (e_i \otimes x^\top e_j)
-      \sigma^2_{ij} (e_i \otimes x^\top e_j)^\hop
-    \notag \\
-    % &= \sum_{ij} (e_i \otimes x_j) \sigma^2_{ij} (e_i^\top \otimes \conj{x}_j)
-    % \\
-    &
-    = \sum_i (e_i e_i^\top) \sum_j \sigma^2_{ij} x_j \conj{x}_j
-    \,,
-\end{align*}
-where $e_i$ is the $i$-th real unit vector of dimensionality conforming to the expression it
-is involved with. In a similar fashion we obtain the expression for the relation matrix of
-the transformation:
-\begin{equation*}
-  (I \otimes x^\top) \diag{\vec{C}} (I \otimes x^\top)^\top
-    % = \sum_{ij} (e_i \otimes x_j) C_{ij} (e_i \otimes x_j)^\top
-    = \sum_i e_i e_i^\top \sum_j C_{ij} x_j^2
-    \,.
-\end{equation*}
-The term $
-  \sum_i e_i e_i^\top (\ldots)
-$ means that the covariance and relation matrices of $y = Wx + b$ are diagonal.
-
-These observations coupled with the closure under affine transformation imply that the
-components of $y = W x + b$ are independent univariate $\cplx$-Gaussain random variables
-with distributions
-\begin{equation} \label{eq:c-gaus-trick}
-  y_i
-    \sim \mathcal{N}^{\cplx}
-      \bigl(
-        e_i^\top \mu x + b,
-        \, \sum_j \sigma^2_{ij} \lvert x_j \rvert^2,
-        \, \sum_j C_{ij} x_j^2
-      \bigr)
-    \,.
-\end{equation}
-
-We can notice, that in \eqref{eq:c-gaus-trick} the mean, variance and relation parameters are,
-essentially, matrix-vector operations: $\mu x + b$, $\Sigma \lvert x \rvert^2$ and $C x^2$
-with the modulus and power applied elementwise. The local reparameterization trick works
-similarly for $\cplx$-convolutions, provided we draw independent weights $W\sim q(W)$ for each
-spatial patch in the input: convolve value $x$, amplitude $\lvert x \rvert^2$ and complex
-square $x^2$ with the mean, variance, and relation kernels, respectively. The need for
-independent resampling stems from kernel weights being shared between patches, which would
-make the gradient estimator less efficient due to correlation from overlapping patches.
-The argument from \cite{kingma_variational_2015} in favour drawing independent weight per
-sample in the minibatch can be applied here to show that this is \verify{indeed the case}.
-%
-Weight sharing is pushed from weights of the layer to shared variational parameters $\theta$
-in the approximation $q_\theta$.
-
-% subsection local_reparameterization_trick (end)
-
-\subsection{The choice of priors and Kullback-Leibler divergence} % (fold)
-\label{sub:priors_and_kullback_leibler_divergence}
-
-In this section we consider two different priors, suitable for variational dropout: log-uniform
-\cite{kingma_variational_2015,molchanov_variational_2017} and proper $\cplx$-Gaussian analogue
-for the empirical Bayes prior in \cite{kharitonov_variational_2018}.
-
-Recall that we use fully factorized variational approximation for the parameters: $
-  W \sim q(W)
-    = \prod_{ij} q(\omega_{ij})
-$ with proper complex Gaussian distributions of each element $
-  q(\omega_{ij})
-    = \mathcal{N}^{\cplx}\bigl(
-      \omega_{ij} \big\vert
-      \mu_{ij}, \sigma^2_{ij}, 0
-    \bigr)
-$. Assuming factorized prior belief $\pi(W)$ on the parameters $W$, the KL-divergence
-term in ELBO \eqref{eq:elbo} is
-\begin{equation}  \label{eq:elbo-general-kl-div}
-KL(q(W) \| \pi(W))
-  % = \mathbb{E}_{W \sim q(W)} \log \tfrac{q(W)}{\pi(W)}
-  % = \sum_{ij} \mathbb{E}_{\omega_{ij} \sim q(\omega_{ij})}
-  %   \log \tfrac{q(\omega_{ij})}{\pi(\omega_{ij})}
-  = \sum_{ij} KL\bigl(
-    q(\omega_{ij}) \| \pi(\omega_{ij})
-  \bigr)
-  \,.
-\end{equation}
-%
-We shall omit the subscripts for brevity in the derivations in the next section, which
-we begin with a derivation of the entropy of a proper $\cplx$-Gaussian.
-
-The expression of Kullback-Leibler divergence of $q(\omega)$ from an arbitrary prior $\pi(\omega)$
-necessarily involves the (differential) entropy of $q$:
-\begin{equation*}
-  KL\bigl(
-    q(\omega) \| \pi(\omega)
-  \bigr)
-    % = \mathbb{E}_{\omega \sim q} \log{q(\omega)} - \mathbb{E}_{\omega \sim q} \log{\pi(\omega)}
-    = - \mathbb{H}(q) - \mathbb{E}_{\omega \sim q} \log{\pi(\omega)}
-    \,.
-\end{equation*}
-The entropy of a real multivariate Gaussian $
-  x \sim q(x) = \mathcal{N}_n(x \vert \mu, \Sigma)
-$ is
-$$
-\mathbb{H}(q)
-  = - \mathbb{E}_{x\sim q(x)} \log{q(x)}
-  % = \tfrac12 \log \det{(2 \pi \Sigma)}
-  % + \tfrac12 \mathop{tr}{(
-  %     \Sigma^{-1}
-  %     \mathbb{E}_{x\sim q(x)}
-  %       (x - \mu) (x - \mu)^\top
-  %   )}
-  = \tfrac12 \log \det{(2 \pi e \Sigma)}
-  \,, $$
-whence follows the expression for the entropy of a general $\cplx$-Gaussian random vector
-$
-  z \sim q(z)
-    = \mathcal{N}^{\cplx}_n(z\vert \mu, \Gamma, C)
-$
-\begin{align*} \label{eq:c-gauss-entropy-derivation}
-  \mathbb{H}(q)
-    &
+    % entropy of \mathcal{N}_n(\mu, \Sigma)
+    %   % = \tfrac12 \log \det{(2 \pi \Sigma)}
+    %   % + \tfrac12 \mathop{tr}{(
+    %   %     \Sigma^{-1}
+    %   %     \mathbb{E}_{x\sim q(x)}
+    %   %       (x - \mu) (x - \mu)^\top
+    %   %   )}
     %   = \tfrac12 \log \det{(2 \pi e \Sigma)}
@@
     \,.
-\end{align*}
-The entropy of a proper $\cplx$-Gaussian random vector ($C = 0$) is therefore 
+\end{align}
+A $\cplx$-Gaussian random vector $z$ is \textit{proper}, if $z$ and $\conj{z}$ are uncorrelated,
+i.e. $C = 0$, since the matrices $\Gamma$ and $C$ correspond to $
+  \mathbb{E} (z - \mu)(z - \mu)^{\hop}
+$ and $
+  \mathbb{E} (z - \mu)(z - \mu)^{\top}
+$, respectively. From \eqref{eq:c-gauss-entropy-derivation} its entropy is therefore 
 \begin{equation}  \label{eq:cn-proper-entropy}
@@
 \end{equation}
+
+the characteristic function is
+$$
+z \sim \mathcal{N}^{\cplx}_m(z \vert \mu, \Gamma, C)
+  \Leftrightarrow
+  \mathbb{E}_{z} e^{j \Re{(t^{\hop} z)}}
+  = \exp{\{
+    j \Re{(t^{\hop} \mu)}
+    - \tfrac14 \bigl(
+      t^{\hop} \Gamma t + \Re{(t^{\hop} C \conj{t})}
+    \bigr)
+  \}}
+  \,, $$
+
+Not every $\real^{2m}$ Gaussian corresponds to a $\cplx^m$ Gaussian vecor,
+but when it does the covariance and relation can be recovered through
+$$
+\Sigma
+  = \begin{pmatrix}
+    \Sigma_{rr} & \Sigma_{ri} \\ 
+    \Sigma_{ir} & \Sigma_{ii} 
+  \end{pmatrix}
+  \, \Leftrightarrow
+  \,
+  \begin{cases}
+    \Gamma
+      = \Sigma_{rr} + \Sigma_{ii} + j (\Sigma_{ir} - \Sigma_{ri})
+    \,, \\
+    C = \Sigma_{rr} - \Sigma_{ii} + j (\Sigma_{ir} + \Sigma_{ri}) 
+  \end{cases}
+  $$
+
+This implies that $
+  \Sigma_{ir}
+  % = -\Sigma_{ri}
+  = -\Sigma_{ir}^\top
+$ and $\Sigma_{rr} = \Sigma_{ii}$, i.e. real and imaginary component of the same random element
+are uncorrelated, since skew-symmetric matrices necessarily have zero-diagonal.
+
+If $M \in \real^{m\times m}$, $M \succeq 0$ and $M^\top = M$, then
+$$
+  (u - j v)^\top M (u + j v)
+    = u^\top M u + v^\top M v + j (u^\top M v - v^\top M u)
+    % = u^\top M u + v^\top M v + j (u^\top M v - u^\top M^\top v)
+    = u^\top M u + v^\top M v \geq 0
+\,. $$
+if $M^\top = - M$, then
+$$
+  u^\top M v - v^\top M u - j (u^\top M u + v^\top M v)
+  % = u^\top M v - u^\top M^\top v - j (u^\top M u + v^\top M^\top v)
+  = u^\top M v + u^\top M v - j (u^\top M u - v^\top M v)
+  \,. $$
+
+%
+% The intuition behind them is more apparent in the complex univariate case ($m=1$):
+% here $\Gamma = \sigma^2 \geq 0$, and $C$ can be represented as $\sigma^2 \rho \in \cplx$ with $
+%   \lvert \rho \rvert \leq 1
+% $. Therefore $\sigma^2$ affects the overall ``concentration'' of the complex random variable,
+% whereas $\rho$ is responsible for the strength and ``direction'' of the linear relation between
+% the real and imaginary parts, \cite{lapidoth_capacity_2003}.
+% $$
+% \frac{\sigma^2}2
+%   \begin{pmatrix}
+%     1 + \Re{\rho} & \Im{\rho} \\
+%     \Im{\rho} & 1 - \Re{\rho}
+%   \end{pmatrix}
+%   = \frac{\sigma^2}2 I
+%   + \frac{\sigma^2 \lvert \rho \rvert}2 
+%   \begin{pmatrix}
+%     \cos\theta & \sin\theta \\
+%     \sin\theta & - \cos\theta
+%   \end{pmatrix}
+% $$
+
+To develop $\cplx$-variational dropout we assume a fully factorized posterior approximation
+distribution on the layers' parameters: $\omega = (W, b)$, where a $\cplx$-valued $W$ collects
+all weight matrices of linear layers and kernels of convolutional layers, and $b$ represents
+all bias term combined. We use a fully factorized Dirac family on the biases, and mean-field
+proper $\cplx$-Gaussian variational approximation for the weights: $
+  q(W) = \prod_{lij} q(W^{l}_{ij})
+$ with each parameter being an independent univariate proper complex Gaussian
+% (we omit the subscript $m=1$ for brevity)
+\begin{equation} \label{eq:c-gauss-vi}
+  W_{ij}
+    \sim \mathcal{N}^{\cplx}(\mu_{ij}, \sigma^2_{ij}, 0)
+  \,.
+\end{equation}
+Thus we would like to sparsify the weights in the network and, since the bias terms constitute
+a meagre share of network's parameters and are rarely dropped out or pruned, we use Bayesan
+MAP estimates for them.
+
+As was demonstrated in \cite{kingma_variational_2015}, local reparameterization trick
+provides both faster computations and better statistical efficiency of the SGVB gradient
+estimator. We formulate the $\cplx$ version of the local reparameterization trick, which
+generalizes \cite{wang_fast_2013}.
+
+% subsection c_gaussian_variational_approximation (end)
+
+\subsection{Local reparameterization trick} % (fold)
+\label{sub:local_reparameterization_trick}
+
+To simplify exposition of the trick, we consider the complex linear dense layer, and afterwards
+outline the caveats for $\cplx$-convolutional layers. In both cases we use fully factorized
+general $\cplx$-Gaussian distribution for parameters $W$ of the layer.
+
+Consider a $\cplx$-linear layer: $
+  W \in \cplx^{n\times m}
+$ is a random $\cplx$-Gaussian matrix with independent elements $
+  w_{ij} \sim \mathcal{N}^{\cplx}\bigl(
+    w_{ij}
+    \big \vert
+    \mu_{ij}, \sigma^2_{ij}, C_{ij}
+  \bigr)
+$ with $\mu_{ij}\in cplx$, $\sigma^2_{ij} \geq 0$, $C_{ij}\in \cplx$ and $
+  \lvert C_{ij} \rvert^2 \leq \sigma^2_{ij}
+$. We begin by observing that the variational approximation of $q(W)$ is a multivariate
+$\cplx$-Gaussian: $
+  \vec{W}
+    \sim \mathcal{N}^{\cplx}_{[n\times m]} \bigl(
+      \vec{\mu}, \diag{\vec{\Sigma}}, \diag{\vec{C}}
+    \bigr)
+$, where $[n\times m]$ denotes lexicographically flattened dimension and $\diag{v}$ is a
+diagonal square matrix with $v_i$ on the main diagonal. Here we collected variances and means
+into matrices $\Sigma$ and $\mu$, respectively.
+%
+Now, for any $x \in \cplx^m$ and $b\in \cplx^n$ we have
+$$
+W x + b
+  % = I_n W x + b
+  = (I_n \otimes x^\top) \vec{W} + b
+  \,, $$
+where $\vec{\cdot}$ denotes flattening in lexicographic order of indices (row-major), and
+$\otimes$ denotes the Kronecker product, for which we have the identity $
+  \vec{P Q R} = (P \otimes R^\top) \vec{Q}
+$, \cite{petersen_matrix_2012}.
+% It follows from the definition of the Kronecker product
+% of $P$ and $R^\top$ and the row-major order vectorization.
+%
+Structure of the matrices, involved in this expression, and the identity $
+  (P \otimes R) (C \otimes S) = P Q \otimes R S
+$, \cite{petersen_matrix_2012}, imply
+\begin{align*}
+  (I \otimes x^\top) \diag{\vec{\Sigma}} (I \otimes x^\top)^\hop
+    % &= \sum_{ij} (I \otimes x^\top) e_i \otimes e_j
+    %   \sigma^2_{ij} (e_i \otimes e_j)^\top (I \otimes x^\top)^\hop
+    % \\
+    &
+    = \sum_{ij} (e_i \otimes x^\top e_j)
+      \sigma^2_{ij} (e_i \otimes x^\top e_j)^\hop
+    \notag \\
+    % &= \sum_{ij} (e_i \otimes x_j) \sigma^2_{ij} (e_i^\top \otimes \conj{x}_j)
+    % \\
+    &
+    = \sum_i (e_i e_i^\top) \sum_j \sigma^2_{ij} x_j \conj{x}_j
+    \,,
+\end{align*}
+where $e_i$ is the $i$-th real unit vector of dimensionality conforming to the expression it
+is involved with. In a similar fashion we obtain the expression for the relation matrix of
+the transformation:
+\begin{equation*}
+  (I \otimes x^\top) \diag{\vec{C}} (I \otimes x^\top)^\top
+    % = \sum_{ij} (e_i \otimes x_j) C_{ij} (e_i \otimes x_j)^\top
+    = \sum_i e_i e_i^\top \sum_j C_{ij} x_j^2
+    \,.
+\end{equation*}
+The term $
+  \sum_i e_i e_i^\top (\ldots)
+$ means that the covariance and relation matrices of $y = Wx + b$ are diagonal.
+
+These observations coupled with the closure under affine transformation imply that the
+components of $y = W x + b$ are independent univariate $\cplx$-Gaussain random variables
+with distributions
+\begin{equation} \label{eq:c-gaus-trick}
+  y_i
+    \sim \mathcal{N}^{\cplx}
+      \bigl(
+        e_i^\top \mu x + b,
+        \, \sum_j \sigma^2_{ij} \lvert x_j \rvert^2,
+        \, \sum_j C_{ij} x_j^2
+      \bigr)
+    \,.
+\end{equation}
+
+We can notice, that in \eqref{eq:c-gaus-trick} the mean, variance and relation parameters are,
+essentially, matrix-vector operations: $\mu x + b$, $\Sigma \lvert x \rvert^2$ and $C x^2$
+with the modulus and power applied elementwise. The local reparameterization trick works
+similarly for $\cplx$-convolutions, provided we draw independent weights $W\sim q(W)$ for each
+spatial patch in the input: convolve value $x$, amplitude $\lvert x \rvert^2$ and complex
+square $x^2$ with the mean, variance, and relation kernels, respectively. The need for
+independent resampling stems from kernel weights being shared between patches, which would
+make the gradient estimator less efficient due to correlation from overlapping patches.
+The argument from \cite{kingma_variational_2015} in favour drawing independent weight per
+sample in the minibatch can be applied here to show that this is \verify{indeed the case}.
+%
+Weight sharing is pushed from weights of the layer to shared variational parameters $\theta$
+in the approximation $q_\theta$.
+
+% subsection local_reparameterization_trick (end)
+
+\subsection{The choice of priors and Kullback-Leibler divergence} % (fold)
+\label{sub:priors_and_kullback_leibler_divergence}
+
+In this section we consider two different priors, suitable for variational dropout: log-uniform
+\cite{kingma_variational_2015,molchanov_variational_2017} and proper $\cplx$-Gaussian analogue
+for the empirical Bayes prior in \cite{kharitonov_variational_2018}.
+
+Recall that we use fully factorized variational approximation for the parameters: $
+  W \sim q(W)
+    = \prod_{ij} q(\omega_{ij})
+$ with proper complex Gaussian distributions of each element $
+  q(\omega_{ij})
+    = \mathcal{N}^{\cplx}\bigl(
+      \omega_{ij} \big\vert
+      \mu_{ij}, \sigma^2_{ij}, 0
+    \bigr)
+$. Assuming factorized prior belief $\pi(W)$ on the parameters $W$, the KL-divergence
+term in ELBO \eqref{eq:elbo} is
+\begin{equation}  \label{eq:elbo-general-kl-div}
+KL(q(W) \| \pi(W))
+  % = \mathbb{E}_{W \sim q(W)} \log \tfrac{q(W)}{\pi(W)}
+  % = \sum_{ij} \mathbb{E}_{\omega_{ij} \sim q(\omega_{ij})}
+  %   \log \tfrac{q(\omega_{ij})}{\pi(\omega_{ij})}
+  = \sum_{ij} KL\bigl(
+    q(\omega_{ij}) \| \pi(\omega_{ij})
+  \bigr)
+  \,.
+\end{equation}
+%
+We shall omit the subscripts for brevity in the derivations in the next section, which
+we begin with a derivation of the entropy of a proper $\cplx$-Gaussian.
+
+The expression of Kullback-Leibler divergence of $q(\omega)$ from an arbitrary prior $\pi(\omega)$
+necessarily involves the (differential) entropy of $q$:
+\begin{equation*}
+  KL\bigl(
+    q(\omega) \| \pi(\omega)
+  \bigr)
+    % = \mathbb{E}_{\omega \sim q} \log{q(\omega)} - \mathbb{E}_{\omega \sim q} \log{\pi(\omega)}
+    = - \mathbb{H}(q) - \mathbb{E}_{\omega \sim q} \log{\pi(\omega)}
+    \,.
+\end{equation*}
 

### 2019-11-07 paper/paper.tex
formatted labels and edited cplx-gaussian section

@@
 A random vector $z\in \cplx^m$ has complex Gaussian distribution, $
-  z \sim \mathcal{N}^{\cplx}_m(\mu, \Gamma, C)
-$, with mean $\mu \in \cplx^m$ and $\cplx^{m\times m}$ covariance and relation
-matrices $\Gamma$ and $C$ are, respectively, if 
+  z \sim q(z) = \mathcal{N}^{\cplx}_m(\mu, \Gamma, C)
+$, with mean $\mu \in \cplx^m$ and $\cplx^{m\times m}$ covariance and relation matrices
+$\Gamma$ and $C$, respectively, if
 \begin{equation}  \label{eq:cn-paired-real-density}
@@
   \conj{\Gamma} \succeq C^{\hop} \Gamma^{-1} C
-$. This distribution possesses the usual properties of $\real$-valued Gaussians, including
-if $y = A z + b$ for $
-  A \in \cplx^{n \times m}
-$ and $b \in \cplx^{n}$, then $
+$. Matrices $\Gamma$ and $C$ are $
+  \mathbb{E} (z - \mu)(z - \mu)^{\hop}
+$ and $
+  \mathbb{E} (z - \mu)(z - \mu)^{\top}
+$, respectively. $\cplx$-Gaussians are closed under affine transformations: if $y = A z + b$
+for $A \in \cplx^{n \times m}$ and $b \in \cplx^{n}$, then $
   y \sim \mathcal{N}_n^{\cplx}\bigl(
@@
     \bigr)
-$. The entropy of a $\cplx$-Gaussian distribution $
-  q = \mathcal{N}^{\cplx}_m(\mu, \Gamma, C)
-$ is
+$. The entropy of a $\cplx$-Gaussian distribution coincides with the entropy of
+\eqref{eq:cn-paired-real-density}, and in terms of $\Gamma$ and $C$ can be expresed:
 \begin{align}  \label{eq:c-gauss-entropy-derivation}
@@
     \notag \\
-    &
+    % &
     % entropy of \mathcal{N}_n(\mu, \Sigma)
@@
     %   = \tfrac12 \log \det{(2 \pi e \Sigma)}
-    = \tfrac12 \log \det{\biggl(
-      2 \pi e \tfrac12
-      \begin{pmatrix}
-        \Re{(\Gamma + C)} & - \Im{(\Gamma - C)} \\
-        \Im{(\Gamma + C)} &   \Re{(\Gamma - C)}
-      \end{pmatrix}
-    \biggr)}
-    \notag \\
+    % = \tfrac12 \log \det{\biggl(
+    %   2 \pi e \tfrac12
+    %   \begin{pmatrix}
+    %     \Re{(\Gamma + C)} & - \Im{(\Gamma - C)} \\
+    %     \Im{(\Gamma + C)} &   \Re{(\Gamma - C)}
+    %   \end{pmatrix}
+    % \biggr)}
+    % \notag \\
     % &
@@
     &
-    = \tfrac12 \log \det{(\pi e \Gamma)} \det{(\pi e (\conj{\Gamma} - \conj{C} \Gamma^{-1} C))}
+    = \tfrac12 \log \det{(\pi e \Gamma)}
+      \det{(\pi e (\conj{\Gamma} - \conj{C} \Gamma^{-1} C))}
     \,.
 \end{align}
-A $\cplx$-Gaussian random vector $z$ is \textit{proper}, if $z$ and $\conj{z}$ are uncorrelated,
-i.e. $C = 0$, since the matrices $\Gamma$ and $C$ correspond to $
-  \mathbb{E} (z - \mu)(z - \mu)^{\hop}
-$ and $
-  \mathbb{E} (z - \mu)(z - \mu)^{\top}
-$, respectively. From \eqref{eq:c-gauss-entropy-derivation} its entropy is therefore 
+A $\cplx$-Gaussian vector $z$ is \textit{proper}, if $z$ and $\conj{z}$ are uncorrelated, i.e.
+$C = 0$. From \eqref{eq:c-gauss-entropy-derivation} the entropy of a proper $\cplx$-Gaussain is
 \begin{equation}  \label{eq:cn-proper-entropy}
@@
 
-\subsubsection{Variational dropout} % (fold){}
+\subsubsection{Variational dropout} % (fold)
 \label{ssub:variational_dropout}

### 2019-11-07 paper/paper.tex
cplx-gaussian comment edits
moved notation from local-rep-trick, simplified approximation descriptionn

@@
 We first clarify some notation: $M^{\top}$ is the matrix transpose, $\conj{M}$ is elementwise
-complex conjugation, and $M^{\hop} = (\conj{M})^\top$ denotes Hermitian conjugate.
+complex conjugation, and $M^{\hop} = (\conj{M})^\top$ denotes Hermitian conjugate. By $e_i$
+we denote the $i$-th real unit vector of dimensionality \textbf{conforming} to the matrix-vector
+expression it is used in. $\vec{M}$ denotes row-major flattening of $M$ into a vector, i.e.
+in lexicographic order of its indices. $\otimes$ denotes the Kronecker product, for which we
+note the following identities $
+  \vec{P Q R} = (P \otimes R^\top) \vec{Q}
+$, and $
+  (P \otimes R) (C \otimes S) = P Q \otimes R S
+$, \cite{petersen_matrix_2012}.
+% It follows from the definition of the Kronecker product
+% of $P$ and $R^\top$ and the row-major order vectorization.
 
@@
 \end{equation}
-
-the characteristic function is
-$$
-z \sim \mathcal{N}^{\cplx}_m(z \vert \mu, \Gamma, C)
-  \Leftrightarrow
-  \mathbb{E}_{z} e^{j \Re{(t^{\hop} z)}}
-  = \exp{\{
-    j \Re{(t^{\hop} \mu)}
-    - \tfrac14 \bigl(
-      t^{\hop} \Gamma t + \Re{(t^{\hop} C \conj{t})}
-    \bigr)
-  \}}
-  \,, $$
-
-Not every $\real^{2m}$ Gaussian corresponds to a $\cplx^m$ Gaussian vecor,
-but when it does the covariance and relation can be recovered through
-$$
-\Sigma
-  = \begin{pmatrix}
-    \Sigma_{rr} & \Sigma_{ri} \\ 
-    \Sigma_{ir} & \Sigma_{ii} 
-  \end{pmatrix}
-  \, \Leftrightarrow
-  \,
-  \begin{cases}
-    \Gamma
-      = \Sigma_{rr} + \Sigma_{ii} + j (\Sigma_{ir} - \Sigma_{ri})
-    \,, \\
-    C = \Sigma_{rr} - \Sigma_{ii} + j (\Sigma_{ir} + \Sigma_{ri}) 
-  \end{cases}
-  $$
-
-This implies that $
-  \Sigma_{ir}
-  % = -\Sigma_{ri}
-  = -\Sigma_{ir}^\top
-$ and $\Sigma_{rr} = \Sigma_{ii}$, i.e. real and imaginary component of the same random element
-are uncorrelated, since skew-symmetric matrices necessarily have zero-diagonal.
-
-If $M \in \real^{m\times m}$, $M \succeq 0$ and $M^\top = M$, then
-$$
-  (u - j v)^\top M (u + j v)
-    = u^\top M u + v^\top M v + j (u^\top M v - v^\top M u)
-    % = u^\top M u + v^\top M v + j (u^\top M v - u^\top M^\top v)
-    = u^\top M u + v^\top M v \geq 0
-\,. $$
-if $M^\top = - M$, then
-$$
-  u^\top M v - v^\top M u - j (u^\top M u + v^\top M v)
-  % = u^\top M v - u^\top M^\top v - j (u^\top M u + v^\top M^\top v)
-  = u^\top M v + u^\top M v - j (u^\top M u - v^\top M v)
-  \,. $$
-
 %
-% The intuition behind them is more apparent in the complex univariate case ($m=1$):
-% here $\Gamma = \sigma^2 \geq 0$, and $C$ can be represented as $\sigma^2 \rho \in \cplx$ with $
+% The roles of $\Gamma$ and $C$ is more evident in univariate case: here $
+%   \Gamma = \sigma^2 \geq 0
+% $, and $C = \sigma^2 \rho \in \cplx$ with $
 %   \lvert \rho \rvert \leq 1
-% $. Therefore $\sigma^2$ affects the overall ``concentration'' of the complex random variable,
-% whereas $\rho$ is responsible for the strength and ``direction'' of the linear relation between
-% the real and imaginary parts, \cite{lapidoth_capacity_2003}.
+% $. $\sigma^2$ determines the ``dispersion'', whereas $\rho$ is determines the
+% ``strength'' and ``direction'' of the linear relation between real and imaginary
+% parts, \cite{lapidoth_capacity_2003}.
 % $$
@@
 %   \end{pmatrix}
-%   = \frac{\sigma^2}2 I
-%   + \frac{\sigma^2 \lvert \rho \rvert}2 
+%   = \frac{\sigma^2}2 
 %       \begin{pmatrix}
-%     \cos\theta & \sin\theta \\
-%     \sin\theta & - \cos\theta
+%         1 + \lvert \rho \rvert \cos\theta
+%           & \lvert \rho \rvert \sin\theta \\
+%         \lvert \rho \rvert \sin\theta
+%           & 1 - \lvert \rho \rvert \cos\theta
 %       \end{pmatrix}
-% $$
-
-To develop $\cplx$-variational dropout we assume a fully factorized posterior approximation
-distribution on the layers' parameters: $\omega = (W, b)$, where a $\cplx$-valued $W$ collects
-all weight matrices of linear layers and kernels of convolutional layers, and $b$ represents
-all bias term combined. We use a fully factorized Dirac family on the biases, and mean-field
-proper $\cplx$-Gaussian variational approximation for the weights: $
-  q(W) = \prod_{lij} q(W^{l}_{ij})
-$ with each parameter being an independent univariate proper complex Gaussian
+%   \,. $$
+
+In $\cplx$-variational dropout we use mean-field proper $\cplx$-Gaussian variational
+approximation. Specifically, parameters $W \in \cplx^{n\times m}$ of a dense layer follow
+\begin{equation}  \label{eq:c-gauss-vi}
   % (we omit the subscript $m=1$ for brevity)
-\begin{equation}  \label{eq:c-gauss-vi}
-  W_{ij}
-    \sim \mathcal{N}^{\cplx}(\mu_{ij}, \sigma^2_{ij}, 0)
-  \,.
+  W \sim q(W) = \prod_{ij}
+    \mathcal{N}^{\cplx}(W_{ij} \mid \mu_{ij}, \sigma^2_{ij}, 0)
+  \,,
 \end{equation}
-Thus we would like to sparsify the weights in the network and, since the bias terms constitute
-a meagre share of network's parameters and are rarely dropped out or pruned, we use Bayesan
-MAP estimates for them.
+and we use analogous independent proper $\cplx$-Gaussian approximation for convolutional
+kernels. As for bias terms, we propose to use their MAP estimates, i.e. assume an independent
+fully factorized Dirac approximation.
 
@@
   = (I_n \otimes x^\top) \vec{W} + b
-  \,, $$
-where $\vec{\cdot}$ denotes flattening in lexicographic order of indices (row-major), and
-$\otimes$ denotes the Kronecker product, for which we have the identity $
-  \vec{P Q R} = (P \otimes R^\top) \vec{Q}
-$, \cite{petersen_matrix_2012}.
-% It follows from the definition of the Kronecker product
-% of $P$ and $R^\top$ and the row-major order vectorization.
-%
-Structure of the matrices, involved in this expression, and the identity $
-  (P \otimes R) (C \otimes S) = P Q \otimes R S
-$, \cite{petersen_matrix_2012}, imply
+  \,. $$
+Structure of the matrices, involved in this expression, imply
 \begin{align*}
@@
     = \sum_i (e_i e_i^\top) \sum_j \sigma^2_{ij} x_j \conj{x}_j
-    \,,
+    \,.
 \end{align*}
-where $e_i$ is the $i$-th real unit vector of dimensionality conforming to the expression it
-is involved with. In a similar fashion we obtain the expression for the relation matrix of
+In a similar fashion we obtain the expression for the relation matrix of
 the transformation:

### 2019-11-08 paper/paper.tex
finished rewrtiting cplx-lrt

@@
 % of $P$ and $R^\top$ and the row-major order vectorization.
+Finally, $
+  \diag{}
+    \colon \mathbb{K}^n \to \mathbb{K}^{n\times n}
+    \colon v \mapsto (\delta_{ij} v_i)_{ij}
+$ is a diagonal matrix embedding, $\mathbb{K} = \real$ or $\cplx$.
 
@@
   \mathbb{E} (z - \mu)(z - \mu)^{\top}
-$, respectively. $\cplx$-Gaussians are closed under affine transformations: if $y = A z + b$
-for $A \in \cplx^{n \times m}$ and $b \in \cplx^{n}$, then $
-  y \sim \mathcal{N}_n^{\cplx}\bigl(
+$, respectively.
+%
+% $\cplx$-Gaussians are closed under affine transformations: if $y = A z + b$
+% for $A \in \cplx^{n \times m}$ and $b \in \cplx^{n}$, then $
+%   y \sim \mathcal{N}_n^{\cplx}\bigl(
+%       A\mu + b, A \Gamma A^{\hop}, A C A^\top
+%     \bigr)
+% $.
+%
+$\cplx$-Gaussians are closed under affine transformations:
+for $A \in \cplx^{n \times m}$ and $b \in \cplx^{n}$
+\begin{equation}  \label{eq:cn-affine}
+  A z + b \sim \mathcal{N}_n^{\cplx}\bigl(
       A\mu + b, A \Gamma A^{\hop}, A C A^\top
     \bigr)
-$. The entropy of a $\cplx$-Gaussian distribution coincides with the entropy of
+  \,.
+\end{equation}
+%
+The entropy of a $\cplx$-Gaussian distribution coincides with the entropy of
 \eqref{eq:cn-paired-real-density}, and in terms of $\Gamma$ and $C$ can be expresed:
@@
 A $\cplx$-Gaussian vector $z$ is \textit{proper}, if $z$ and $\conj{z}$ are uncorrelated, i.e.
-$C = 0$. From \eqref{eq:c-gauss-entropy-derivation} the entropy of a proper $\cplx$-Gaussain is
+$C = 0$. From \eqref{eq:c-gauss-entropy-derivation} the entropy of a proper $\cplx$-Gaussian is
 \begin{equation}  \label{eq:cn-proper-entropy}
@@
   % (we omit the subscript $m=1$ for brevity)
-  W \sim q(W) = \prod_{ij}
-    \mathcal{N}^{\cplx}(W_{ij} \mid \mu_{ij}, \sigma^2_{ij}, 0)
+  W
+    \sim q(W)
+    = \prod_{ij} q(W_{ij})
+  \,,\,
+    q(W_{ij})
+      = \mathcal{N}^{\cplx}(W_{ij} \mid \mu_{ij}, \sigma^2_{ij}, 0)
   \,,
@@
 
-As was demonstrated in \cite{kingma_variational_2015}, local reparameterization trick
-provides both faster computations and better statistical efficiency of the SGVB gradient
-estimator. We formulate the $\cplx$ version of the local reparameterization trick, which
-generalizes \cite{wang_fast_2013}.
-
 % subsection c_gaussian_variational_approximation (end)
@@
 
-To simplify exposition of the trick, we consider the complex linear dense layer, and afterwards
-outline the caveats for $\cplx$-convolutional layers. In both cases we use fully factorized
-general $\cplx$-Gaussian distribution for parameters $W$ of the layer.
-
-Consider a $\cplx$-linear layer: $
+The local reparameterization trick provides both faster computations, \cite{wang_fast_2013},
+and better statistical efficiency of the SGVB gradient estimator, \cite{kingma_variational_2015}.
+We formulate $\cplx$ version of the local reparameterization trick using a dense linear
+layer as an example, and afterwards outline the caveats for $\cplx$-convolutions.
+
+A general mean field $\cplx$-Gaussian approximation \eqref{eq:c-gauss-vi} for $
   W \in \cplx^{n\times m}
-$ is a random $\cplx$-Gaussian matrix with independent elements $
-  w_{ij} \sim \mathcal{N}^{\cplx}\bigl(
-    w_{ij}
-    \big \vert
-    \mu_{ij}, \sigma^2_{ij}, C_{ij}
-  \bigr)
-$ with $\mu_{ij}\in cplx$, $\sigma^2_{ij} \geq 0$, $C_{ij}\in \cplx$ and $
-  \lvert C_{ij} \rvert^2 \leq \sigma^2_{ij}
-$. We begin by observing that the variational approximation of $q(W)$ is a multivariate
-$\cplx$-Gaussian: $
+$ is
+\begin{equation}  \label{eq:c-gauss-vi-general}
   \vec{W}
-    \sim \mathcal{N}^{\cplx}_{[n\times m]} \bigl(
+    \sim \mathcal{N}^{\cplx}_{nm} \bigl(
       \vec{\mu}, \diag{\vec{\Sigma}}, \diag{\vec{C}}
     \bigr)
-$, where $[n\times m]$ denotes lexicographically flattened dimension and $\diag{v}$ is a
-diagonal square matrix with $v_i$ on the main diagonal. Here we collected variances and means
-into matrices $\Sigma$ and $\mu$, respectively.
-%
-Now, for any $x \in \cplx^m$ and $b\in \cplx^n$ we have
-$$
-W x + b
-  % = I_n W x + b
+  \,,
+\end{equation}
+where mean, \textit{variance} and relation are given by matrices $
+  \mu, \Sigma, C \in \cplx^{n\times m}
+$ with $\Sigma_{ij} \geq 0$, and $
+  \lvert C_{ij} \rvert^2 \leq \Sigma_{ij}
+$. For any $x \in \cplx^m$ and $b\in \cplx^n$ $
+  y = W x + b
     = (I_n \otimes x^\top) \vec{W} + b
-  \,. $$
-Structure of the matrices, involved in this expression, imply
-\begin{align*}
-  (I \otimes x^\top) \diag{\vec{\Sigma}} (I \otimes x^\top)^\hop
-    % &= \sum_{ij} (I \otimes x^\top) e_i \otimes e_j
-    %   \sigma^2_{ij} (e_i \otimes e_j)^\top (I \otimes x^\top)^\hop
-    % \\
-    &
-    = \sum_{ij} (e_i \otimes x^\top e_j)
-      \sigma^2_{ij} (e_i \otimes x^\top e_j)^\hop
-    \notag \\
-    % &= \sum_{ij} (e_i \otimes x_j) \sigma^2_{ij} (e_i^\top \otimes \conj{x}_j)
-    % \\
-    &
-    = \sum_i (e_i e_i^\top) \sum_j \sigma^2_{ij} x_j \conj{x}_j
-    \,.
-\end{align*}
-In a similar fashion we obtain the expression for the relation matrix of
-the transformation:
-\begin{equation*}
+$, whence the covariance and relation matrices of $y$ are
+\begin{align}
+  (I \otimes x^\top) \diag{\vec{\Sigma}} (I \otimes x^\top)^{\hop}
+    % = \sum_{ij} (I \otimes x^\top) e_i \otimes e_j
+    %   \Sigma_{ij} (e_i \otimes e_j)^\top (I \otimes x^\top)^{\hop}
+    % = \sum_{ij} (e_i \otimes x^\top e_j)
+    %   \Sigma_{ij} (e_i \otimes x^\top e_j)^{\hop}
+    % = \sum_{ij} (e_i \otimes x_j) \Sigma_{ij} (e_i^\top \otimes \conj{x}_j)
+    & = \sum_{i=1}^n (e_i e_i^\top) \sum_{j=1}^m \Sigma_{ij} x_j \conj{x}_j
+    \,,  \label{eq:cn-gauss-lrt-cov} \\
   (I \otimes x^\top) \diag{\vec{C}} (I \otimes x^\top)^\top
     % = \sum_{ij} (e_i \otimes x_j) C_{ij} (e_i \otimes x_j)^\top
-    = \sum_i e_i e_i^\top \sum_j C_{ij} x_j^2
-    \,.
-\end{equation*}
-The term $
-  \sum_i e_i e_i^\top (\ldots)
-$ means that the covariance and relation matrices of $y = Wx + b$ are diagonal.
-
-These observations coupled with the closure under affine transformation imply that the
-components of $y = W x + b$ are independent univariate $\cplx$-Gaussain random variables
-with distributions
-\begin{equation}  \label{eq:c-gaus-trick}
+    & = \sum_{i=1}^n (e_i e_i^\top) \sum_{j=1}^m C_{ij} x_j^2
+    \,.  \label{eq:cn-gauss-lrt-rel}
+\end{align}
+Since \eqref{eq:cn-gauss-lrt-cov} and \eqref{eq:cn-gauss-lrt-rel} are diagnal, $(y_i)_{i=1}^n$
+are independent whence \eqref{eq:cn-affine} implies
+\begin{equation}  \label{eq:cplx-gauss-trick}
   y_i
@@
         e_i^\top \mu x + b,
-        \, \sum_j \sigma^2_{ij} \lvert x_j \rvert^2,
-        \, \sum_j C_{ij} x_j^2
+        \, \sum_{j=1}^m \Sigma_{ij} \lvert x_j \rvert^2,
+        \, \sum_{j=1}^m C_{ij} x_j^2
       \bigr)
@@
 \end{equation}
-
-We can notice, that in \eqref{eq:c-gaus-trick} the mean, variance and relation parameters are,
-essentially, matrix-vector operations: $\mu x + b$, $\Sigma \lvert x \rvert^2$ and $C x^2$
-with the modulus and power applied elementwise. The local reparameterization trick works
-similarly for $\cplx$-convolutions, provided we draw independent weights $W\sim q(W)$ for each
-spatial patch in the input: convolve value $x$, amplitude $\lvert x \rvert^2$ and complex
-square $x^2$ with the mean, variance, and relation kernels, respectively. The need for
-independent resampling stems from kernel weights being shared between patches, which would
-make the gradient estimator less efficient due to correlation from overlapping patches.
-The argument from \cite{kingma_variational_2015} in favour drawing independent weight per
-sample in the minibatch can be applied here to show that this is \verify{indeed the case}.
-%
-Weight sharing is pushed from weights of the layer to shared variational parameters $\theta$
-in the approximation $q_\theta$.
+For a proper approximation \eqref{eq:c-gauss-vi} the resulting relation coefficients are zero.
+
+\eqref{eq:cplx-gauss-trick} essentially requires three matrix-vector operations: $\mu x + b$,
+$\Sigma \lvert x \rvert^2$ and $C x^2$ with the modulus and power applied elementwise. Similar
+to $\real$ case, variational dropout for $\cplx$ convolutions draws independent kernel $W$
+for each spatial patch in the input, since a convolution is a matrix product of $W$, unrolled
+into a toeplitz matrix, and flattened intput $\vec{x}$. Weight sharing is essentially pushed
+to shared variational parameters $\theta$ in the approximation $q_\theta$. The rationale
+is to reduce correlation in the gradient estimator stemming from kernel weights being
+shared between overlapping patches, \cite{kingma_variational_2015,citation_needed}. Thus
+\eqref{eq:cplx-gauss-trick} requires computing $\cplx$ convolutions of $x$, complex square
+$x^2$, and amplitude $\lvert x \rvert^2$ with the mean, relation, and variance kernels,
+respectively.
 

### 2019-11-08 paper/paper.tex
merged c-gauss and local rep trick subsections

@@
 \cite{trabelsi_deep_2017}, (see sec.~\ref{sub:wirtinger_calculus} for details).
-
+%
 \todo{read on holomorphic nets}
@@
 We first clarify some notation: $M^{\top}$ is the matrix transpose, $\conj{M}$ is elementwise
-complex conjugation, and $M^{\hop} = (\conj{M})^\top$ denotes Hermitian conjugate. By $e_i$
-we denote the $i$-th real unit vector of dimensionality \textbf{conforming} to the matrix-vector
-expression it is used in. $\vec{M}$ denotes row-major flattening of $M$ into a vector, i.e.
-in lexicographic order of its indices. $\otimes$ denotes the Kronecker product, for which we
-note the following identities $
+complex conjugation, and $M^{\hop} = (\conj{M})^\top$ denotes Hermitian conjugate. By $e_i$ we
+denote the $i$-th real unit vector of dimensionality \textit{conforming} to the matrix-vector
+expression it is used in. $\vec{M}$ denotes \textit{row-major} flattening of $M$ into a vector,
+i.e. in lexicographic order of its indices. $\diag{(\cdot)}$ embeds $\cplx^n$ into $n\times n$
+diagonal matrices. $\otimes$ denotes the Kronecker product, for which we note the following
+identities $
   \vec{P Q R} = (P \otimes R^\top) \vec{Q}
@@
 % of $P$ and $R^\top$ and the row-major order vectorization.
-Finally, $
-  \diag{}
-    \colon \mathbb{K}^n \to \mathbb{K}^{n\times n}
-    \colon v \mapsto (\delta_{ij} v_i)_{ij}
-$ is a diagonal matrix embedding, $\mathbb{K} = \real$ or $\cplx$.
-
-\subsection{$\cplx$-Gaussian Variational Approximation} % (fold)
-\label{sub:c_gaussian_variational_approximation}
+
+\subsection{Complex Gaussians and Local Reparameterization} % (fold)
+\label{sub:c_gauss_and_local_rep}
 
@@
 
-% subsection c_gaussian_variational_approximation (end)
-
-\subsection{Local reparameterization trick} % (fold)
-\label{sub:local_reparameterization_trick}
-
 The local reparameterization trick provides both faster computations, \cite{wang_fast_2013},
@@
 respectively.
-
-% subsection local_reparameterization_trick (end)
+%
+\todo{other reasons for patch-independent weights}
+
+% subsection c_gauss_and_local_rep (end)
 

### 2019-11-08 paper/paper.tex
listed properties of Ei (with proof) compressed improper prior section

@@
   % (we omit the subscript $m=1$ for brevity)
-  W
-    \sim q(W)
+  W \sim q(W)
     = \prod_{ij} q(W_{ij})
@@
 
-In this section we consider two different priors, suitable for variational dropout: log-uniform
-\cite{kingma_variational_2015,molchanov_variational_2017} and proper $\cplx$-Gaussian analogue
-for the empirical Bayes prior in \cite{kharitonov_variational_2018}.
-
-Recall that we use fully factorized variational approximation for the parameters: $
-  W \sim q(W)
-    = \prod_{ij} q(\omega_{ij})
-$ with proper complex Gaussian distributions of each element $
-  q(\omega_{ij})
-    = \mathcal{N}^{\cplx}\bigl(
-      \omega_{ij} \big\vert
-      \mu_{ij}, \sigma^2_{ij}, 0
-    \bigr)
-$. Assuming factorized prior belief $\pi(W)$ on the parameters $W$, the KL-divergence
-term in ELBO \eqref{eq:elbo} is
+We consider two priors for Bayesian dropout: log-uniform and $\cplx$-Gaussian empirical Bayes,
+\cite{kingma_variational_2015,molchanov_variational_2017,kharitonov_variational_2018}. For a 
+fully factorized approximation $q(\omega)$ and factorized prior belief $\pi(\omega)$, the
+divergence term in ELBO \eqref{eq:elbo} is
 \begin{equation}  \label{eq:elbo-general-kl-div}
-KL(q(W) \| \pi(W))
-  % = \mathbb{E}_{W \sim q(W)} \log \tfrac{q(W)}{\pi(W)}
+KL(q(\omega) \| \pi(\omega))
+  % = \mathbb{E}_{\oemga \sim q(\oemga)} \log \tfrac{q(\oemga)}{\pi(\oemga)}
   % = \sum_{ij} \mathbb{E}_{\omega_{ij} \sim q(\omega_{ij})}
   %   \log \tfrac{q(\omega_{ij})}{\pi(\omega_{ij})}
-  = \sum_{ij} KL\bigl(
-    q(\omega_{ij}) \| \pi(\omega_{ij})
-  \bigr)
+  % = \sum_{ij} KL\bigl( q(\omega_{ij}) \| \pi(\omega_{ij}) \bigr)
+  = - \sum_{ij} \mathbb{H}(q(\omega_{ij}))
+    + \mathbb{E}_{\omega_{ij} \sim q(\omega_{ij})} \log{\pi(\omega_{ij})}
   \,.
 \end{equation}
-%
-We shall omit the subscripts for brevity in the derivations in the next section, which
-we begin with a derivation of the entropy of a proper $\cplx$-Gaussian.
-
-The expression of Kullback-Leibler divergence of $q(\omega)$ from an arbitrary prior $\pi(\omega)$
-necessarily involves the (differential) entropy of $q$:
-\begin{equation*}
-  KL\bigl(
-    q(\omega) \| \pi(\omega)
-  \bigr)
-    % = \mathbb{E}_{\omega \sim q} \log{q(\omega)} - \mathbb{E}_{\omega \sim q} \log{\pi(\omega)}
-    = - \mathbb{H}(q) - \mathbb{E}_{\omega \sim q} \log{\pi(\omega)}
-    \,.
-\end{equation*}
+We use approximation \eqref{eq:c-gauss-vi} and omit subscripts ${ij}$ below for brevity.
 
@@
 
-Let's get the divergence term for the improper prior, that most closely recovers the variational
-dropout penalty term in \cite{kingma_variational_2015} and \cite{molchanov_variational_2017}.
-If we assume $
-  \pi(\omega) \propto \tfrac1{\lvert \omega \rvert^\beta}
-$ for some $\beta > 1$, then we formally get the following KL-divergence term (up to an unknown,
-or non-existent constant):
+From \eqref{eq:cn-proper-entropy} the KL-divergence for \verify{log-uniform prior} $
+  \pi(\omega) \propto {\lvert \omega \rvert}^{-\beta}
+$ with $\beta \geq 1$ is
 \begin{equation}  \label{eq:var-do-kl-div-raw}
@@
     + \tfrac{\beta}2 \mathbb{E}_{\omega \sim q(\omega)} \log \lvert \omega \rvert^2
-  \,,
-\end{equation}
-where we have used \eqref{eq:cn-proper-entropy} with $\Gamma = \sigma^2 \geq 0$. Note
-that for $\mu \neq 0$, we have $\omega \sim q(\omega)$ equal in distribution to $\mu \xi$
-with $\xi \sim \mathcal{N}^{\cplx}(\xi \vert 1, \alpha, 0)$, whence
+  \,.
+\end{equation}
+Note that for $\mu \neq 0$ from \eqref{eq:cn-affine} we have $
+  \mathcal{N}^{\cplx}(\mu, \alpha \lvert \mu \rvert^2, 0)
+  \sim \mu \cdot \mathcal{N}^{\cplx}(1, \alpha, 0)
+$, whence
 \begin{equation}  \label{eq:expect-improper-term-cplx}
@@
 \end{equation}
-The expectation in \eqref{eq:expect-improper-term-cplx} involves a log-moment of the non-central
-$\chi^2_2$ distribution, which has an analytic expression for the gradient, unlike the case
-in $\real$-dropout penalty \eqref{eq:improper-kl-div-real}.
-
 Let $(\mu_i)_{i=1}^m \in \cplx$ and $
@@
 \end{equation}
-where $\mathop{Ei}(x) = \int^x_{-\infty} t^{-1} e^t dt$ for $x < 0$ is the exponential integral
-function. Note that the limiting value of \eqref{eq:log-moment-for-chi-2} as $
-  \lvert \theta \rvert \to 0
-$ is $- \gamma$, i.e. negative Euler's constant. Therefore after cancellation the expression
-of the KL-divergence in \eqref{eq:var-do-kl-div-raw} becomes
+where $
+  \mathop{Ei}(x) = \int^x_{-\infty} t^{-1} e^t dt
+$ for $x < 0$ is the Exponential Integral. Note that
+$
+  \tfrac{d}{dx} \mathop{Ei}(x) = \tfrac{e^x}{x}
+$ and $
+  \mathop{Ei}(x) \leq \log{(-x)}
+$ on $x < 0$, asymptotically $
+  \log{(-x)} - \gamma
+$ as $x\to 0-$ and $
+  \mathop{Ei}(x) \geq -e^x
+$ on $x \in (-\infty, -1]$ ($\gamma$ is Euler's constant).
+% 1. by Leibniz rule $Ei(x)$ has -ve derivative on $x < 0$
+% 2. $Ei(x) \leq 0$ on $x < 0$, since $t^{-1} e^t \leq t^{-1} < 0$ on $t < 0$
+% 3. $Ei(x) \leq \log{(-x)}$ on $x < 0$, since on $x \in [-1, 0)$
+% $$
+%   \mathop{Ei}(x)
+%     = \mathop{Ei}(-1) + \int_{-1}^x t^{-1} e^t dt
+%     \leq \mathop{Ei}(-1) + \int_{-1}^x t^{-1} dt
+%     = \mathop{Ei}(-1) + \log{(-x)}
+%     \leq \log{(-x)}
+%   \,. $$
+% 3. by l'H{\^o}pital rule $Ei(x)$ is asymptotically $\log{-x}$ as $x \to 0-$
+% $$
+% % t = -e^{-x} ,  -\log{(-t)} = x
+%   \lim_{x\to 0-} \frac{\mathop{Ei}(x)}{\log{(-x)}}
+%     = \lim_{x\to 0-} \frac{x^{-1} e^x}{x^{-1}}
+%     = 1
+%   \,. $$
+% 4. \cite{lapidoth_capacity_2003} yields $\lim_{x\to 0-} \log{(-x)} - \mathop{Ei}(x) = \gamma$
+% 5. $Ei(x) \geq -e^x$ for any $x < -1$, since $t^{-1} e^t \geq - e^t$ for $t < -1$
+% $$
+% \mathop{Ei}(x)
+%   = \int_{-\infty}^x t^{-1} e^t dt
+%   \geq \int_{-\infty}^x -e^t dt = -e^x
+%   \,. $$
+% 6. $Ei(x) \leq \log{(-x)} - \gamma$ on $x < 0$ and $-e^x \leq Ei(x) \leq 0$ on $x < -1$.
+%
+After cancellation \eqref{eq:var-do-kl-div-raw} becomes
 \begin{equation}  \label{eq:var-do-kl-div}
@@
 \end{equation}
-
-The exponential integral is readily available in most scientific computations packages nowadays,
-and, what is especially useful for the stochastic variational Bayes purposes, has a simple
-expression for the derivative: $x \mapsto \tfrac{e^x}{x}$ for $x < 0$. This observation enables
-embedding it into autograd software by computing the term with bogus output values, yet correct
-(on device) gradient, provided no downstream computations depend on the value of the KL-divergence
-term itself.
+% For $\beta = 2$ we add $\gamma$ to make the right-hand side nonegative. (dubious)
+Gradient-based methods that optimize \eqref{eq:elbo} usually do not rely on the value
+of the objective. Since $\mathop{Ei}$ has simple analytic derivative and downstream
+computations depend \eqref{eq:var-do-kl-div} only additively in\eqref{eq:elbo}, it is
+possible to backpropagate through the divergence without forward evaluation.
 
@@
 
+The expectation in \eqref{eq:expect-improper-term-cplx} involves a log-moment of the non-central
+$\chi^2_2$ distribution, which has an analytic expression for the gradient, unlike the case
+in $\real$-dropout penalty \eqref{eq:improper-kl-div-real}.
+
 % section bayesian_methods (end)

### 2019-11-08 paper/paper.tex
fixed indentation, and shortened cplx-vd

@@
 %
-% The roles of $\Gamma$ and $C$ is more evident in univariate case: here $
+% The roles of $\Gamma$ and $C$ are more evident in univariate case: here $
 %   \Gamma = \sigma^2 \geq 0
@@
 \end{equation}
-Let $(\mu_i)_{i=1}^m \in \cplx$ and $
+Let $
   (z_i)_{i=1}^m \sim \mathcal{N}^{\cplx}(0, 1, 0)
-$ iid. Then $W = \sum_i \lvert \theta_i + z_i \rvert^2$ has a non-central $\chi^2_{2m}$
-distribution with non-centrality parameter $s^2 = \sum_i \lvert \theta_i \rvert^2$. The
-log-moments of $W$ for general integer $m \geq1$ are given in
-\cite[p.~2466]{lapidoth_capacity_2003}.  % in fact Appendix X, Lemma 10.1
+$ iid and $\theta \in \cplx^m$. Then $
+  W
+    = \sum_i \lvert \theta_i + z_i \rvert^2
+    \sim \chi^2_{2m}(s^2)
+$ with $
+  s^2 = \sum_i \lvert \theta_i \rvert^2
+$, i.e. non-central $\chi^2_{2m}$ with parameter $s^2$. The log-moments
+of $W$ for general integer $m \geq1$ are given in \cite[p.~2466]{lapidoth_capacity_2003}.
+% in fact Appendix X, Lemma 10.1
 In particular, for $m=1$ and $\theta\in \cplx$ we have
@@
   \tfrac{d}{dx} \mathop{Ei}(x) = \tfrac{e^x}{x}
-$ and $
+$, $
   \mathop{Ei}(x) \leq \log{(-x)}
-$ on $x < 0$, asymptotically $
-  \log{(-x)} - \gamma
-$ as $x\to 0-$ and $
+$, $
+  \mathop{Ei}(x) \approx \log{(-x)} - \gamma
+$ (Euler's constant) as $x\to 0-$ and $
   \mathop{Ei}(x) \geq -e^x
-$ on $x \in (-\infty, -1]$ ($\gamma$ is Euler's constant).
+$ on $x \in (-\infty, -1]$.
 % 1. by Leibniz rule $Ei(x)$ has -ve derivative on $x < 0$
@@
 %
-After cancellation \eqref{eq:var-do-kl-div-raw} becomes
+Through \eqref{eq:expect-improper-term-cplx} and \eqref{eq:log-moment-for-chi-2} we get
 \begin{equation}  \label{eq:var-do-kl-div}
@@
       - \tfrac{\beta}2 \mathop{Ei}(- \tfrac1{\alpha})
-  \,.
-\end{equation}
-% For $\beta = 2$ we add $\gamma$ to make the right-hand side nonegative. (dubious)
-Gradient-based methods that optimize \eqref{eq:elbo} usually do not rely on the value
-of the objective. Since $\mathop{Ei}$ has simple analytic derivative and downstream
-computations depend \eqref{eq:var-do-kl-div} only additively in\eqref{eq:elbo}, it is
-possible to backpropagate through the divergence without forward evaluation.
+      \tag{\ref{eq:var-do-kl-div-raw}'} \,.
+\end{equation}
+% For $\beta = 2$ we add $\gamma$ to make the right-hand side nonegative. (need proof)
+Since $\mathop{Ei}(x)$ has simple analytic derivative and \eqref{eq:elbo} depends additively
+on \eqref{eq:var-do-kl-div}, it is possible to backpropagate through the divergence without
+forward evaluation.
+% Gradient-based optimiziation of \eqref{eq:elbo} usually does not use the value of the objective.
 

### 2019-11-08 paper/paper.tex
fixed macro, moved -ve sign in (21)
finished empirical bayes

@@
 %% drafting macro
-\newcommand{\important}[1]{\textbf{\colorbox{red}{#1}}}
+\newcommand{\important}[1]{\textbf{\!\colorbox{red}{#1}\!}}
 \newcommand{\attn}[2]{\textbf{\color{red} #2~\textsuperscript{\textit{[#1]}}}}
-\newcommand{\verify}[1]{\attn{verify}{#1}}
+\newcommand{\verify}[1]{\textit{\!\colorbox{red}{#1}\!}}
 \newcommand{\rewrite}[1]{\attn{rewrite}{#1}}
@@
     % = \sum_{ij} KL\bigl( q(\omega_{ij}) \| \pi(\omega_{ij}) \bigr)
-    = - \sum_{ij} \mathbb{H}(q(\omega_{ij}))
-      + \mathbb{E}_{\omega_{ij} \sim q(\omega_{ij})} \log{\pi(\omega_{ij})}
+    = \sum_{ij} \bigl(
+        - \mathbb{H}(q(\omega_{ij}))
+        - \mathbb{E}_{\omega_{ij} \sim q(\omega_{ij})} \log{\pi(\omega_{ij})}
+      \bigr)
     \,.
@@
 \end{equation}
-Note that for $\mu \neq 0$ from \eqref{eq:cn-affine} we have $
-  \mathcal{N}^{\cplx}(\mu, \alpha \lvert \mu \rvert^2, 0)
+\eqref{eq:cn-affine} implies that $
+  \mathcal{N}^{\cplx}(\mu, \sigma^2, 0)
   \sim \mu \cdot \mathcal{N}^{\cplx}(1, \alpha, 0)
+$ for $\mu \neq 0$ and $
+  \sigma^2 = \alpha \lvert \mu \rvert^2
 $, whence
@@
 $, $
+  % as x to 0 from below
   \mathop{Ei}(x) \approx \log{(-x)} - \gamma
-$ (Euler's constant) as $x\to 0-$ and $
+$ as $x\to 0$ ($\gamma$ is Euler's constant) and $
   \mathop{Ei}(x) \geq -e^x
-$ on $x \in (-\infty, -1]$.
+$ for $x \leq -1$.
 % 1. by Leibniz rule $Ei(x)$ has -ve derivative on $x < 0$
@@
 
-For this model we use an empirical Bayes prior. We assume that our initial belief is that
-parameters are independent and each one is proper $\cplx$-Gaussian with its own precision: $
-  \pi(\omega)
+Let's consider fully factorized proper $\cplx$-gaussian prior $
+  \pi_\tau(\omega)
     \propto \mathcal{N}^{\cplx}\bigl(
@@
     \bigr)
-$. The per element KL-divergence term in the ELBO is computed thus:
+$. The per element divergence term in \eqref{eq:elbo-general-kl-div} is
 \begin{equation}  \label{eq:emp-bayes-kl-div}
@@
       \bigr)
-  \,,
-\end{equation}
-which follows from the KL-divergence expression for two multivariate Gaussians
-$$
-% \mathbb{E}_{\omega\sim q_1(\omega)} \log \tfrac{q_1(\omega)}{q_2(\omega)}
+    \,.
+\end{equation}
+%
+% This follows from the KL-divergence expression for two multivariate Gaussians
+% $$
+% % \mathbb{E}_{\omega\sim q_1(\omega)} \log \tfrac{q_1(\omega)}{q_2(\omega)}
+% %   =
+% KL(q_1\| q_2)
 %   =
-KL(q_1\| q_2)
-  =
-  % - \tfrac12 \log\det{(2\pi e \Sigma_1)} + \tfrac12 \log\det{(2\pi \Sigma_2)}
-  - \tfrac12 \log \det{e I}
-  + \tfrac12 \log \frac{\det{\Sigma_2}}{\det{\Sigma_1}}
-  + \tfrac12 \tr{\bigl( \Sigma_2^{-1} \Sigma_1 \bigr)}
-  + \tfrac12 (\mu_1 - \mu_2)^\top \Sigma_2^{-1} (\mu_1 - \mu_2)
-  \,. $$
-
-Somewhat counterintuitively, in empirical Bayes we optimize the hyperparameters of the
-prior on the observed dataset. Thus the lower bound \eqref{eq:elbo} is optimized w.r.t.
-$\tau$ of each weight's prior. \eqref{eq:emp-bayes-kl-div} is optimized (minimized) at
-$\tau^\ast = (\sigma^2 + \lvert \mu \rvert^2)^{-1}$, yielding the following penalty in
-ELBO:
+%   % - \tfrac12 \log\det{(2\pi e \Sigma_1)} + \tfrac12 \log\det{(2\pi \Sigma_2)}
+%   - \tfrac12 \log \det{e I}
+%   + \tfrac12 \log \frac{\det{\Sigma_2}}{\det{\Sigma_1}}
+%   + \tfrac12 \tr{\bigl( \Sigma_2^{-1} \Sigma_1 \bigr)}
+%   + \tfrac12 (\mu_1 - \mu_2)^\top \Sigma_2^{-1} (\mu_1 - \mu_2)
+%   \,. $$
+%
+In empirical Bayes the prior adapts to the observed data, i.e. \eqref{eq:elbo} is optimized
+w.r.t. $\tau$ of each weight's prior. Since divergence sits in \eqref{eq:elbo} with negative
+sign, optimal $
+  \tau^\ast = (\sigma^2 + \lvert \mu \rvert^2)^{-1}
+$ is found by minimizing \eqref{eq:emp-bayes-kl-div}, which gives
 \begin{equation}  \label{eq:emp-bayes-opt-kl}
@@
     % = \log{\bigl(1 + \tfrac1\alpha \bigr)}
-  \,,
-\end{equation}
-which exactly replicates the term, derived in \cite{kharitonov_variational_2018}.
+    \,.
+\end{equation}
 

### 2019-11-11 paper/paper.tex
edited bayesian section

@@
 remains a challenge. Solving the storage and compute constraints encourages development
-of model compress and sparsification methods, that focus on favourable tradeoff between
-performance and size. Most popular techniquees include weight pruning \cite{citation_needed},
+of model compression and sparsification methods, that focus on favourable tradeoff between
+performance and size. Most popular techniques include weight pruning \cite{citation_needed},
 model quantization from IEEE754 floating point to integer-based arithmetic \cite{citation_needed},
-and dropout. The key assumption is that the more explicitly zero parameters, the less
-computations is needed.
+and dropout. The key assumption is that the more explicitly zero parameters there is,
+the less computations is needed.
 
@@
 
-The use $\cplx$-valued networks in applications is not new: earliest mentions include
-\cite{citation_needed}. More recently they were applied to music transcription and speech
-recognition \cite{trabelsi_deep_2017,yang_complex_2019}. The key motivation behind adoption
-of $\cplx$-networks is the fact that complex numbers are inherent in digital signal processing
-\cite{citation_needed}, acoustic and radio signal analysis \cite{citation_needed}, and
-quantum systems modelling \cite{citation_needed} etc. All these applications require
-compliance with algebraic operations in field of complex numbers.
+Application of complex-valued networks is not new, \cite{citation_needed}. More recently
+they were applied to music transcription and speech recognition \cite{trabelsi_deep_2017},
+and \cite{yang_complex_2019}. The key motivation behind adoption of $\cplx$-networks is
+pervasiveness of $\cplx$-valued data in digital signal processing \cite{citation_needed},
+acoustic and radio signal analysis \cite{citation_needed}, and quantum systems modelling
+\cite{citation_needed}, etc. All these applications require compliance with algebraic
+operations in the field of complex numbers.
 
@@
 of Variational Inference. Instead of deriving $p(\omega \mid D)$ using the rule, this approach
-recasts posterior inference into variational optimization problem
+recasts posterior inference into variational optimization problem: finding $q$ that is close
+to $p(\omega \mid D)$ in terms of a proximity score $\rho$
 \begin{equation}  \label{eq:variational-progam}
@@
 $, $\theta$ -- generic variational parameter. The class $\mathcal{Q}$ is picked so that
-its member have tractable densities $
+its members have tractable densities $
   q_\theta(\omega) d\omega
@@
 and is the natural choice for $\rho$, the main reason being that it satisfies the following
-identity for well-behaved $q$ and $p$:
+identity for well-behaved densities:
 \begin{equation}  \label{eq:kl-div-master}
@@
 \end{equation}
-This key identity yield an equivalent problem for \eqref{eq:variational-progam}:
+This identity yields an equivalent problem for \eqref{eq:variational-progam}:
 maximizing the \textit{evidence lower bound} (ELBO)
@@
 where the prior and likelihood are allowed to depend on explicit parameters. The most
-commonly used algorithm to optimize \eqref{eq:elbo_general} is to use EM-algorithm.
-Other variational objectives are possible, provided $p(\omega \mid D)$ is probed only
-through $\log p(D \mid \omega)$ and $\log \pi(\omega)$, \cite{ranganath_operator_2018}.
+commonly used algorithm to optimize \eqref{eq:elbo_general} is EM-algorithm. Other
+variational objectives are possible, provided $p(\omega \mid D)$ is probed only through
+$\log p(D \mid \omega)$ and $\log \pi(\omega)$, \cite{ranganath_operator_2018}.
 
 \textit{Stochastic Gradient Variational Bayes} (SGVB), proposed by \cite{kingma_auto-encoding_2014},
-is an differentiable unbiased Monte-Carlo estimator of \eqref{eq:elbo_general}, which makes
+is a differentiable unbiased Monte-Carlo estimator of \eqref{eq:elbo_general}, which makes
 it possible to employ stochastic gradient-based optimization methods. If $
@@
   (\varepsilon_{l})_{l=1}^L
-$ is an iid sample from $p_\varepsilon$. Intractable KL-divergence terms can be also
-replaced by differentiable unbiased Monte-Carlo estimators, \cite{kingma_auto-encoding_2014}.
+$ is an iid sample from $p_\varepsilon$. Intractable KL-divergence terms can be replaced
+by differentiable unbiased Monte-Carlo estimators, \cite{kingma_auto-encoding_2014}.
 %
@@
 
-For a particular family of posterior approximation, variational inference can be used
-as a regularization method \cite{kingma_variational_2015} and as model sparsification
-technique \cite{molchanov_variational_2017}. \cite{kingma_variational_2015} propose
-Variational Dropout, by studying Binary dropout, DropConnect and Gaussian dropout,
-\cite{hinton_improving_2012,wan_regularization_2013}, \cite{srivastava_dropout_2014},
-and \cite{wang_fast_2013} through the lens of variational inference methods. The study
-argues that the multiplicative noise, introduced by dropout, induces a distribution
-equivalent to a fully factorized variational posterior of the form $
+With special family of posterior approximation, variational inference can be used as
+a regularization method, \cite{kingma_variational_2015}, and as model sparsification
+technique, \cite{molchanov_variational_2017}. The paper \cite{kingma_variational_2015}
+considers Dropout \cite{hinton_improving_2012}, DropConnect, \cite{wan_regularization_2013},
+and Gaussian dropout, \cite{srivastava_dropout_2014,wang_fast_2013} through the lens
+of Bayesian inference methods and proposes \textit{Variational Dropout}. It argues that
+the multiplicative noise introduced by these methods induces a distribution equivalent to
+a fully factorized variational posterior of the form $
   q_\theta(\omega) = \prod_j q_{\theta}(\omega_j)
-$, where $q_{\theta}(\omega_j)$ is $\omega_j = \mu_j \xi_j$ with $\xi_j \sim p(\xi_j)$
-iid from some $p_\xi$. Binary dropout with rate $p \in (0, 1)$ uses $
-  p_\xi
-    = \mathcal{B}\bigl(
-      \{0, \tfrac1{1-p}\}, 1-p
-    \bigr)
-$, whereas in Gaussian dropout $
-  \xi \sim \mathcal{N}(1, \alpha)
-$ for $\alpha = \tfrac{p}{1-p}$. This suggests making $\alpha$ a variational parameter
-and optimizing it in \eqref{eq:elbo_general} with an appropriate penalty term. Thus,
-\cite{kingma_variational_2015} propose \textit{Variational Dropout} with mean field
-Gaussian approximation $
+$, where $q_{\theta}(\omega_j)$ is $\omega_j = \mu_j \xi_j$ with $
+  \xi_j \sim p_\theta(\xi_j)
+$ iid from some $p_\theta(\xi)$.
+%
+% Binary dropout with rate $p \in (0, 1)$ uses $
+%   p_\xi
+%     = \mathcal{B}\bigl(
+%       \{0, \tfrac1{1-p}\}, 1-p
+%     \bigr)
+% $, whereas in Gaussian dropout $
+%   \xi \sim \mathcal{N}(1, \alpha)
+% $ for $\alpha = \tfrac{p}{1-p}$.
+% This suggests making $\alpha$ a variational parameter
+% and optimizing it in \eqref{eq:elbo_general} with an appropriate penalty term. Thus,
+%
+Variational Dropout with assumes mean field Gaussian approximation $
   q_\theta(\omega)
@@
   \pi(\omega_j) \propto \lvert \omega_j \rvert^{-1}
-$. This unravels the divergence term in \eqref{eq:elbo} into a sum of the following terms:
+$. This unravels the divergence term in \eqref{eq:elbo} into a sum of the following
+analytically intractable terms:
 \begin{equation}  \label{eq:improper-kl-div-real}
@@
 \end{equation}
-In general, there is tractable expression for log-moment of a non-central $\chi^2_m$ random
-variable with odd $m$, that sits under the expectation in \eqref{eq:expect-improper-term-cplx}.
-To circumvent this, \cite{kingma_variational_2015} approximate the expectation by a non-linear
-polynomial regression for truncated $\alpha \in (0, 1)$. This approximation was refined in
+\cite{kingma_variational_2015} approximate this expression by a non-linear polynomial
+regression for \verify{truncated} $\alpha \in (0, 1)$. This approximation was refined in
 \cite{molchanov_variational_2017}, both in terms of the domain of $\alpha$ and accuracy. The
@@
 
-Flexibility in dependence of $q_\theta$ on $\alpha$ allows structured dropout with shared
+Flexibility in specification of $q_\theta$ enables structured dropout with shared
 $\alpha$ across groups of parameters $\omega$. \cite{molchanov_variational_2017} study
@@
 
-Another contribution of \cite{kingma_variational_2015} is the analysis of the \textit{local
-reparameterization trick}, proposed in \cite{wang_fast_2013} to speed up Gaussian dropout,
-as a gradient variance reduction technique for \eqref{eq:elbo}. This trick utilizes the
+Another contribution of \cite{kingma_variational_2015} is the analysis of the effects of the
+\textit{local reparameterization trick} on the variance of the gradient of \eqref{eq:elbo}.
+This trick, proposed in \cite{wang_fast_2013} to speed up Gaussian dropout, utilizes the
 closure of Gaussians under affine transformations, thereby translating uncertainty from the

### 2019-11-11 paper/paper.tex
edited the cplx-vd section

@@
 
-% This concludes the section on the foundations of Bayesian dropout techniques.
-
 % subsection dropout (end)
@@
 
-In this section we overview $\mathbb{C}$-valued networks, their motivation and peculiarities.
-In our exposition we shall focus mostly on linear layers, keeping in mind that transferring 
-the ideas to convolutional layers is straightforward.
-
-The study \cite{trabelsi_deep_2017}, outlines building blocks for deep $\cplx$-valued
-networks and describes suitable representation and operations including linear layers (dense
-and convolutional), $\cplx$-valued activations, complex batch-normalization and suitable
-weight initialization. In fact all papers touching one way or another upon the subject of
-$\cplx$-valued networks, refrain each other, and the current study is no exception.
-
-Following \cite{trabelsi_deep_2017}, we naturally identify $\cplx$ with $\real^2$ via $
-  z_\mathrm{r} + j z_\mathrm{i} \mapsto (z_\mathrm{r}, z_\mathrm{i})
-$, storing the real and imaginary parts in interleaved format, and emulate $\cplx$-algebra
-using $\real$-valued arithmetic. In particular, convolutional and linear layers,
+In this section we briefly review $\cplx$-valued networks, their distinction from the
+ordinary $\real$-valued networks.
+
+The study \cite{trabelsi_deep_2017} outlines building blocks for deep $\cplx$-valued
+networks and describes suitable representation and operations including convolutional
+and dense layers, $\cplx$-valued activations, complex batch-normalization and suitable
+weight initialization. Their approach makes a complex-valued network into an intricately
+connected $\real$-valued computational graph that respects $\cplx$-algebra.
+
+In particular, linear layers
 $
@@
       \to \real^{\mathrm{[out]}}
-$ are unique linear operators that make up $L = L_r + j L_i$. Thus, a $\cplx$-convolutional
-layer with complex kernel $W$ can be implemented as two $\real$-convolutions with kernels
-$\Re{W}$ and $\Im{W}$ using \eqref{eq:cplx-lin-op}. Other algebraic operations, such as
-trigonometric functions, and complex division and roots in batch normalization
-\cite{trabelsi_deep_2017}, are implemented through their counterparts in $\real^2$. This
-makes $\cplx$-valued network into an intricately connected $\real$-valued computational
-graph that respects $\cplx$-algebra.
-
-Concerning activations, \cite{trabelsi_deep_2017} consider the following: independent
-componentwise application of $\real$-valued non-linearities, $
+$ are unique operators that make up $L = L_r + j L_i$. A $\cplx$-convolutional layer with
+kernel $W$ can be implemented as two $\real$-convolutions with kernels $\Re{W}$ and $\Im{W}$
+using \eqref{eq:cplx-lin-op}. Algebraic operations, trigonometric functions, are implemented
+through operations in $\real^2$. Activations, considered in \cite{trabelsi_deep_2017} include
+independent componentwise application of $\real$-valued non-linearities, $
   z = u + j v
     \mapsto \sigma(u) + j \sigma(v)
-$; $\cplx$-differentiable exponential and trigonometric activations; and \textit{modRelu}
-activation, which preserves the angle and applies soft-thresholding to the modulus: $
+$, $\cplx$-differentiable exponential and trigonometric activations, and \textit{modRelu}
+activation, which applies soft-thresholding to the modulus and preserves the angle: $
   z = r e^{j \phi}
-    \mapsto e^{j \phi} (r - \theta)_+
+    \mapsto e^{j \phi} (r - b)_+
   % z \mapsto z \bigl(
-  %     1 - \tfrac\theta{\lvert z \rvert}
+  %     1 - \tfracb{\lvert z \rvert}
   %   \bigr)_+
-$ with a learnable parameter $\theta\in \real$.
+$ with a learnable threshold parameter $b \in \real$.
 
@@
 %notation
-We first clarify some notation: $M^{\top}$ is the matrix transpose, $\conj{M}$ is elementwise
+We use the following notation: $M^{\top}$ is the matrix transpose, $\conj{M}$ is elementwise
 complex conjugation, and $M^{\hop} = (\conj{M})^\top$ denotes Hermitian conjugate. By $e_i$ we
@@
 %
-$\cplx$-Gaussians are closed under affine transformations:
-for $A \in \cplx^{n \times m}$ and $b \in \cplx^{n}$
+$\cplx$-Gaussians are closed under affine transformations: for $A \in \cplx^{n \times m}$
+and $b \in \cplx^{n}$
 \begin{equation}  \label{eq:cn-affine}
@@
 %
-The entropy of a $\cplx$-Gaussian distribution coincides with the entropy of
-\eqref{eq:cn-paired-real-density}, and in terms of $\Gamma$ and $C$ can be expresed:
+From \eqref{eq:cn-paired-real-density} the entropy of a $\cplx$-Gaussian in terms of
+$\Gamma$ and $C$ is
 \begin{align}  \label{eq:c-gauss-entropy-derivation}
@@
 \end{equation}
-and we use analogous independent proper $\cplx$-Gaussian approximation for convolutional
-kernels. As for bias terms, we propose to use their MAP estimates, i.e. assume an independent
-fully factorized Dirac approximation.
+and we use similar factorized approximation for convolution. We propose to MAP estimates,
+of the biases i.e. assume an independent fully factorized Dirac approximation.
 
@@
 and better statistical efficiency of the SGVB gradient estimator, \cite{kingma_variational_2015}.
-We formulate $\cplx$ version of the local reparameterization trick using a dense linear
-layer as an example, and afterwards outline the caveats for $\cplx$-convolutions.
-
 A general mean field $\cplx$-Gaussian approximation \eqref{eq:c-gauss-vi} for $
@@
 \end{equation}
-For a proper approximation \eqref{eq:c-gauss-vi} the resulting relation coefficients are zero.
-
-\eqref{eq:cplx-gauss-trick} essentially requires three matrix-vector operations: $\mu x + b$,
-$\Sigma \lvert x \rvert^2$ and $C x^2$ with the modulus and power applied elementwise. Similar
-to $\real$ case, variational dropout for $\cplx$ convolutions draws independent kernel $W$
-for each spatial patch in the input, since a convolution is a matrix product of $W$, unrolled
-into a toeplitz matrix, and flattened intput $\vec{x}$. Weight sharing is essentially pushed
-to shared variational parameters $\theta$ in the approximation $q_\theta$. The rationale
-is to reduce correlation in the gradient estimator stemming from kernel weights being
-shared between overlapping patches, \cite{kingma_variational_2015,citation_needed}. Thus
-\eqref{eq:cplx-gauss-trick} requires computing $\cplx$ convolutions of $x$, complex square
-$x^2$, and amplitude $\lvert x \rvert^2$ with the mean, relation, and variance kernels,
+The trick requires three matrix operations: $\mu x + b$, $\Sigma \lvert x \rvert^2$ and
+$C x^2$ with the modulus and power applied elementwise. For a proper approximation
+\eqref{eq:c-gauss-vi} the relation coefficients are zero.
+
+The trick and dropout can be applied to any layer, the output of which depends linearly
+on its parameters, e.g. convolutional layers, affine and bilinear transformations ($
+  y_j = x^\top W^{(j)} z + b_j
+$). Similar to $\real$ case, variational dropout for $\cplx$ convolutions draws independent
+kernel $W$ for each spatial patch in the input, since a convolution is a matrix product
+of $W$, unrolled into a toeplitz matrix, and flattened intput $\vec{x}$. Weight sharing
+is essentially pushed to shared variational parameters $\theta$ in the approximation $q_\theta$.
+The rationale is to reduce correlation in the gradient estimator stemming from kernel weights
+being shared between overlapping patches, \cite{kingma_variational_2015,citation_needed}.
+Thus \eqref{eq:cplx-gauss-trick} requires computing $\cplx$ convolutions of $x$, complex
+square $x^2$, and amplitude $\lvert x \rvert^2$ with the mean, relation, and variance kernels,
 respectively.
@@
 
-We consider two priors for Bayesian dropout: log-uniform and $\cplx$-Gaussian empirical Bayes,
-\cite{kingma_variational_2015,molchanov_variational_2017,kharitonov_variational_2018}. For a 
-fully factorized approximation $q(\omega)$ and factorized prior belief $\pi(\omega)$, the
-divergence term in ELBO \eqref{eq:elbo} is
+We consider two priors for Bayesian dropout: log-uniform and $\cplx$-Gaussian empirical
+Bayes, \cite{kingma_variational_2015,molchanov_variational_2017,kharitonov_variational_2018}.
+For a fully factorized approximation $q(\omega)$ and factorized prior belief $\pi(\omega)$,
+the divergence term in ELBO \eqref{eq:elbo} is
 \begin{equation}  \label{eq:elbo-general-kl-div}
@@
 $ with $\beta \geq 1$ is
-\begin{equation}  \label{eq:var-do-kl-div-raw}
+\begin{equation}  \label{eq:c-vd-kl-div-raw}
   KL(q\| \pi)
@@
 $ iid and $\theta \in \cplx^m$. Then $
-  W
-    = \sum_i \lvert \theta_i + z_i \rvert^2
+  \sum_i \lvert \theta_i + z_i \rvert^2
     \sim \chi^2_{2m}(s^2)
@@
   s^2 = \sum_i \lvert \theta_i \rvert^2
-$, i.e. non-central $\chi^2_{2m}$ with parameter $s^2$. The log-moments
-of $W$ for general integer $m \geq1$ are given in \cite[p.~2466]{lapidoth_capacity_2003}.
+$, i.e. a non-central $\chi^2_{2m}$ with parameter $s^2$. Its log-moments for general
+integer $m \geq1$ are given in \cite[p.~2466]{lapidoth_capacity_2003}. In particular,
 % in fact Appendix X, Lemma 10.1
-In particular, for $m=1$ and $\theta\in \cplx$ we have
+for $m=1$ and $\theta\in \cplx$ we have
 \begin{equation}  \label{eq:log-moment-for-chi-2}
@@
 Through \eqref{eq:expect-improper-term-cplx} and \eqref{eq:log-moment-for-chi-2} we get
-\begin{equation}  \label{eq:var-do-kl-div}
+\begin{equation}  \label{eq:c-vd-kl-div}
   KL(q\| \pi)
@@
       - \tfrac{\beta}2 \mathop{Ei}(- \tfrac1{\alpha})
-      \tag{\ref{eq:var-do-kl-div-raw}'} \,.
+      \tag{\ref{eq:c-vd-kl-div-raw}'} \,.
 \end{equation}
@@
 Since $\mathop{Ei}(x)$ has simple analytic derivative and \eqref{eq:elbo} depends additively
-on \eqref{eq:var-do-kl-div}, it is possible to backpropagate through the divergence without
+on \eqref{eq:c-vd-kl-div}, it is possible to backpropagate through the divergence without
 forward evaluation.
@@
     = \log{\bigl(1 + \tfrac{\lvert \mu \rvert^2}{\sigma^2}\bigr)}
-    % = \log{\bigl(1 + \tfrac1\alpha \bigr)}
+    = \log{\bigl(1 + \tfrac1\alpha \bigr)}
     \,.
@@
   \xi_{ij} \sim \mathcal{N}(1, \alpha_{ij})
-$, yet $\mu \in \cplx^{n \times m}$. This case corresponds to variational inference for the
-multiplicative mask $\xi$, distribution of which is approximated using independent $\real$
-univariate Gaussians (ordinary dropout posteriors). Here we are actually interested in
-inference, regarding the values of $\xi$ after observing the data (and fitting other model
-parameters such as $\mu$). Essentially, in \eqref{eq:elbo} we have
-$$
-\mathbb{E}_{\xi \sim q(\xi)}
-  \log p_\theta(z \vert \xi)
-  - KL(q(\xi) \| \pi(\xi))
-  \approx
-    N \hat{\mathbb{E}}_{(z, \xi) \sim B}
-      \log p_\theta(z \vert \xi)
-    - KL(q(\xi) \| \pi(\xi))
-  \,, $$
-and by running SGVB, i.e. maximizing stochastic batched ELBO, we minimize the KL-divergence
-of the variational approximation $q(\xi)$ from its true posterior $p(\xi\vert D)$. Thus we
-run inference on the relevance factors of the parameters, rather than the parameters themselves.
-
-Under this parameterization we have
-$$
-W_{ij} = \mu_{ij} \odot \xi_{ij}
+$, yet $\mu \in \cplx^{n \times m}$. This case corresponds to inference regarding
+relevance coefficients $\xi$ rather than the parameters themselves after. Under this
+parameterization
+\begin{equation}  \label{eq:real-scal-gauss-vi}
+  W_{ij}
     \sim \mathcal{N}^{\cplx} \bigl(
@@
     \bigr)
-  \,, $$
-which is a degenerate $\cplx$-Gaussian distribution. The local reparameterization trick for
-this distribution implies
-$$
+  \,,
+\end{equation}
+which is a degenerate $\cplx$-Gaussian distribution. \eqref{eq:cplx-gauss-trick} implies
+\begin{equation}  \label{eq:real-scal-gauss-trick}
   y_i
@@
     \bigr)
-  \,. $$
-This means that it is a little bit more expensive to translate the local parameter noise
-to the immediate activation, since we need to take into consideration the covariance between
-complex output and its conjugate. Due to this, additive noise reparameterization trick,
-\cite{molchanov_variational_2017}, cannot provide its variance reducing benefits, since
-it is impossible to do away with dependence of the complex relation of the key parameter
-$\mu_{ij}$.
-
-The KL-divergence penalty term in this case follows form the penalty in the real variational
-dropout case with the fully factorized Gaussian approximation and an improper prior $
-  \pi(\xi)\propto \lvert \xi \rvert^{-\beta}
-$:
-$$
-KL(q(\xi)\| \pi(\xi))
-  % = - \tfrac12 \log 2\pi e \alpha
-  %   + \tfrac\beta2 \log \alpha
-  %   + \tfrac\beta2 \mathbb{E}_{z\sim \mathcal{N}(0, 1)}
-  %     \log \lvert z + \tfrac1\sqrt{\alpha} \rvert^2
-  \propto \tfrac{\beta-2}2 \log \alpha
-    + \tfrac\beta2 \mathbb{E}_{z\sim \mathcal{N}(0, 1)}
-      \log \lvert z + \tfrac1{\sqrt{\alpha}} \rvert^2
-  \,. $$
-Unlike the $\cplx$-valued case, even derivative of the expectation term is analytically
-intractable (sec.~\ref{sub:real-chisq-grad}). Thus we use the approximation provided
-by \cite{molchanov_variational_2017}.
+    \,.
+\end{equation}
+The KL-divergence term in \eqref{eq:elbo} coincides with \eqref{eq:improper-kl-div-real}.
+We use the approximation provided by \cite{molchanov_variational_2017}. Note that additive
+noise reparameterization, \cite{molchanov_variational_2017}, cannot be used in
+\eqref{eq:real-scal-gauss-trick}.
 
@@
 % TLDR: we use Wirtinger calculus!
+Following \cite{trabelsi_deep_2017}, we naturally identify $\cplx$ with $\real^2$ via $
+  z_\mathrm{r} + j z_\mathrm{i} \mapsto (z_\mathrm{r}, z_\mathrm{i})
+$, storing the real and imaginary parts in interleaved format, and emulate $\cplx$-algebra
+using $\real$-valued arithmetic.
 

### 2019-11-11 paper/paper.tex
finished this editing iteration

@@
 
-Radio Frequency power amplifiers, being physical electronic devices, have imperfections such
-as parasitic inductance and capacitance. This coupled with them being operated in saturation,
-make their gain respond non-linearly to the input signal, adding undesirable interference and
-spectral spreading. Although these effects can be minimized by careful circuit design, they
-cannot be eliminated entirely \cite{citation_needed}. Digital signal predistortion aims at
-linearizing the amplifier, by introducing signal-dependent compensating component to the input.
-At the same time the non-linearities should be corrected on-device efficiently and with low
-latency in order to reduce cross-channel interference and enable higher bandwidth utilization
-in wireless transmitters.
+Radio Frequency Power Amplifiers (PA) are devices used to increase the power of a signal for
+latter transmission via amplitude modulation over radio. One of the most important problems
+in wireless transmission is distortion caused by imperfections the amplifier, which degrades
+the throughput. Although careful circuit design can mitigate undesirable effects, they cannot
+be eliminated entirely \cite{citation_needed}. \textit{Digital Signal Predistortion} (DPD)
+aims at linearizing the amplifier by introducing computed on-the-fly compensation to the
+input that pushes the signal into the linear region of the PA. Practically, the method helps
+reduce cross-channel interference and enables higher bandwidth utilization in wireless
+transmitters, \cite{citation_needed}. The main challenge of DPD methods is efficient
+compensation on-device (with low-latency).
 
@@
 that enable practical quantification of predictive, parameter, or model uncertainty and its
-propagation into solutions of the problems of interest. It is not safeguarded against overfitting
-and modelling biases: there are quite a handful of assumptions made every time a Bayesian model
-is setup for inference. We need to have a prior belief, the model and its interaction with
-the data (the likelihood), and even the posterior: although the Bayes formula is explicit in
-how the posterior is derived, in all problems of at least some practical significance the
-exact posterior inference involves analytically intractable expectations, compelling the use
-of approximations. In addition to this, even if the likelihood and prior come from conjugate
-families, making the posterior explicit, the questions of interest are usually concerned with
-inference using the posterior predictive distribution, which is factorized as the conditional
-predictive distribution given the model and new observation, and the posterior of the model
-after observing the data.
+propagation into solutions of the problems of interest.
 
 % criticism and discussion
-Despite this, $\cplx$-networks remain much less popular than $\real$-networks for several
-reasons. One possible reason is that a $\cplx$-layer is identical to a paired $\real$-layer,
 based on the algebraic equivalence between $2 \times 2$ real matrices and complex numbers.
@@
 %
-Another one is that a $\cplx$-network is not a true complex-valued function of a complex
-argument: common non-linearities are pointwise applications of $\real$-valued activations
-\cite{trabelsi_deep_2017}.
-%
-Third conceptual issue is that a real-valued loss as a $\cplx\to\real$ function fails
-Cauchy-Riemann conditions, and so is not $\cplx$-differentiable. Since the network has to
-be trained by a gradient-based method (stochastic), this issue is overcome by $\cplx\real$,
-or Wirtinger calculus, which treats the complex argument $z$ and its conjugate $\conj{z}$
-as explicit independent variables. For non-holomorphic functions this approach makes taking
-their derivatives essentially indistinguishable from calculus on $\real^2$.
-%
-The last reason is the lack of native support by the major deep learning and auto-differentiation
-frameworks.
-
-Practical performance of variational dropout techniques was studied in \cite{citation_needed}
-and \cite{citation_needed}. The most fierce critique of Bayesian approach towards model
+The most fierce critique of Bayesian approach towards model
 sparsification was voiced in \cite{gale_state_2019}, where it was show that it yielded
@@
 mask distribution. It is closely related to gumbel-softmax reparameterization trick,
-\cite{kingma_auto-encoding_2014,jang_categorical_2017}: the mask values are, essentially,
-$[0,1]$ clamped scaled sigmoids, that are randomly shifted relative to a learnable location
-parameter, that indicates the degree of weight's relevance. The penalty in the objective is
-the expected number of nonzero parameters, and is a smooth approximation to $\ell_0$ norm.
-This approach is related to stochastic, rather than bayesian networks: it is formulated in
-terms of empirical risk minimization of the negative $\log$-likelihood term in \eqref{eq:elbo}.
+\cite{kingma_auto-encoding_2014,jang_categorical_2017}: the mask is a stretched sigmoid,
+clamped to $[0,1]$, that takes random input shifted relative to a learnable location
+parameter, which indicates the degree of relevance. The penalty in the objective is a
+smooth approximation to $\ell_0$ norm, i.e. the expected number of nonzero parameters.
 
@@
 
-In this section we derive the exact gradient of the KL-divergence term \eqref{eq:improper-kl-div-real}
-for $\mathbb{R}$-dropout in case of a log-uniform prior. Even though the final expression for
-the penalty term itself involves a derivative of a hypergeometric function, and the gradient,
-essentially, relies on computing the error function, the following analysis provides independent
-verification of the correctness of the approximation, proposed in \cite{molchanov_variational_2017}.
+In this section we derive the exact gradient of \eqref{eq:improper-kl-div-real}. Even
+though, ultimately, the divergence involves a hypergeometric function \todo{which one},
+and its gradient requires evaluating the Gauss error function, the analysis provides
+independent verification of the approximation, proposed in \cite{molchanov_variational_2017}.
 The logic of the derivation follows \cite{lapidoth_capacity_2003}.
@@
 
-Let $(z_i)_{i=1}^m \sim \mathcal{N}(0, 1)$ iid and $
+For $(z_i)_{i=1}^m \sim \mathcal{N}(0, 1)$ iid and $
   (\mu_i)_{i=1}^m \in \mathbb{R}
-$. The random variable $
-  W = \sum_i (\mu_i + z_i)^2
-$ is said to be $\chi^2_m(\lambda)$, i.e. noncentral $\chi^2$ with shape $m$ and noncentrality
-parameter $\lambda = \sum_i \mu_i^2$. Its density is given by, \cite{citation_needed}
-$$
+$. The random variable $W = \sum_i (\mu_i + z_i)^2$ noncentral $\chi^2$ with shape $m$
+and noncentrality parameter $\lambda = \sum_i \mu_i^2$, i.e. $W\sim \chi^2_m(\lambda)$.
+Its density is
+\begin{equation}. \label{eq:nonchisq-density}
   f_W(x)
@@
     % I_{\bigl(\tfrac{m}2 - 1\bigr)}(\sqrt{x \lambda})
-  \,. $$
+    \,.
+\end{equation}
 % where $I_k$ is the modified Bessel function of the first kind
@@
 %   \,. $$
-
-In the real multiplicative noise case we need to compute the kl-divergence penalty, the key
-term of which is the expected logarithm of $W$:
+In \eqref{eq:ard-kl-div-real} we need the expected logarithm of $W$:
 \begin{align}
@@
 where $\psi(x)$ is the digamma function, i.e.
-$$
+\begin{equation}  \label{eq:digamma}
   \psi(x)
@@
       \, du
-  \,. $$
-The following properties of the digamma function will be used in the our analysis:
-$
+    \,.
+\end{equation}
+Note that $\psi$ satisfies: $
   \psi(z+1) = \psi(z) + \tfrac1z
-$ and $
+$, $
+  \psi(x)\leq \log x - \tfrac1{2x}
+$, and $
   \psi(\tfrac12) = -\gamma - 2\log 2
-$. If we put
-$$
+$ ($\gamma$ is Euler's constant). If we put
+\begin{equation}  \label{eq:g-m-series}
   g_m(x)
@@
     = e^{-x} \sum_{n \geq 0} \frac{x^n}{n!} \psi(n + \tfrac{m}2)
-  \,, $$
-then the desired expectation $
-  \mathbb{E}_{z \sim \mathcal{N}(0, 1)}
-    \log{\bigl\lvert z + \tfrac1{\sqrt{\alpha}} \bigr\rvert^2}
-$ is equal to $
+    \,,
+\end{equation}
+then the desired expectation in \eqref{eq:ard-kl-div-real} equals $
   \log{2} + g_1(\tfrac1{2\alpha})
@@
 
-We can differentiate the series in $g_m(x)$, since the sum converges everywhere
-on $\mathbb{R}$. Indeed, it is a power series featuring nonnegative coefficients,
-which is dominated by $
-  \sum_{n \geq 1} \tfrac{x^n}{n!} \log{(n+\tfrac{m}2)}
-$, because $\psi(x)\leq \log x - \tfrac1{2x}$. By the ratio test, the dominating
-series has infinite radius:
-$$
-\lim_{n\to\infty}
-  \biggl\lvert
-    \frac{
-      n! x^{n+1} \log{(n + 1 + \tfrac{m}2)}
-    }{
-      x^n \log{(n + \tfrac{m}2)} (n+1)!
-    }
-  \biggr\rvert
-  = \lim_{n\to\infty}
-    \lvert x \rvert 
-    \biggl\lvert
-      \frac{
-        \log{(n + 1 + \tfrac{m}2)}
-      }{
-        \log{(n + \tfrac{m}2)} (n+1)
-      }
-    \biggr\rvert
+% We can differentiate the series in $g_m(x)$, since the sum converges on $\mathbb{R}$.
+% Indeed, it is a power series featuring nonnegative coefficients, which is dominated by $
+%   \sum_{n \geq 1} \tfrac{x^n}{n!} \log{(n+\tfrac{m}2)}
+% $. By the ratio test, the dominating
+% series has infinite radius:
+% $$
+% \lim_{n\to\infty}
+%   \biggl\lvert
+%     \frac{
+%       n! x^{n+1} \log{(n + 1 + \tfrac{m}2)}
+%     }{
+%       x^n \log{(n + \tfrac{m}2)} (n+1)!
+%     }
+%   \biggr\rvert
 %   = \lim_{n\to\infty}
@@
 %       \frac{
-  %       n + \tfrac{m}2
+%         \log{(n + 1 + \tfrac{m}2)}
 %       }{
-  %       (n + 1 + \tfrac{m}2)((n+1) + (n + \tfrac{m}2) \log{(n + \tfrac{m}2)})
+%         \log{(n + \tfrac{m}2)} (n+1)
 %       }
 %     \biggr\rvert
-  = 0 < 1
-  \,, $$
-since
-$$
-\frac{\log{(x + a + 1)}}{x \log{(x + a)}}
-  \sim \frac{\log{(x+1)}}{(x-a) \log{x}}
-  \sim \frac{\log{(x+1)}}{x \log{x}}
-  \sim \frac{\tfrac1{(x+1)}}{1 + \log{x}}
-  \to 0
-  \,. $$
-A theorem from calculus states, that the formal series derivative (integral)
-coincides with the derivative (integral) of the function, corresponding to
-the power series (everywhere on the convergence region). And the convergence
-regions of derivative (integral) coincide with the region of the original
-power series.
+%   % = \lim_{n\to\infty}
+%   %   \lvert x \rvert 
+%   %   \biggl\lvert
+%   %     \frac{
+%   %       n + \tfrac{m}2
+%   %     }{
+%   %       (n + 1 + \tfrac{m}2)((n+1) + (n + \tfrac{m}2) \log{(n + \tfrac{m}2)})
+%   %     }
+%   %   \biggr\rvert
+%   = 0 < 1
+%   \,, $$
+% since
+% $$
+% \frac{\log{(x + a + 1)}}{x \log{(x + a)}}
+%   \sim \frac{\log{(x+1)}}{(x-a) \log{x}}
+%   \sim \frac{\log{(x+1)}}{x \log{x}}
+%   \sim \frac{\tfrac1{(x+1)}}{1 + \log{x}}
+%   \to 0
+%   \,. $$
+% A theorem from calculus states, that the formal series derivative (integral)
+% coincides with the derivative (integral) of the function, corresponding to
+% the power series (everywhere on the convergence region). And the convergence
+% regions of derivative (integral) coincide with the region of the original
+% power series.
 
 Differentiating the series within $g_m$ yields
-$$
+\begin{equation*}  \label{eq:g-m-deriv}
   \frac{d}{d x} g_m(x)
@@
     = \cdots
-  \,. $$
-Now, observe that $
+    \,.
+\end{equation*}
+Since $
     e^t  = \sum_{n\geq 0} \tfrac{t^n}{n!}
@@
     = \tfrac{x^\alpha}{\alpha}
-$ and that
-$$
+$ and
+\begin{equation*}  \label{eq:g-m-deriv-int-1}
   \sum_{n\geq 0} \int_0^x \frac{t^{n+\alpha-1}}{n!} dt
@@
     = \int_0^x t^{\alpha-1} e^t dt
-  \,, $$
-by the monotone convergence theorem on $
-  ([0, x], \mathcal{B}([0, x]), dx)
-$ whence
-$$
+    \,,
+  % the MCT ([0, x], \mathcal{B}([0, x]), dx)
+\end{equation*}
+by the monotone convergence theorem, whence
+\begin{equation}  \label{eq:g-m-deriv-int-2}
   \cdots
@@
     = \cdots
-  \,. $$
-The substitution $u^2 = t$ on $[0, \infty]$ with $2u du = dt$ results in
-$$
+    \,.
+\end{equation}
+The substitution $u^2 = t$ on $[0, \infty]$ with $2u du = dt$ yields
+$$
+\frac{d}{d x} g_m(x)
+  = x^{-\tfrac{m}2} e^{-x}
       \int_0^x t^{\tfrac{m}2 - 1} e^t dt
-  % = \int_0^{\sqrt{x}} u^{m - 2} e^{u^2} 2 u du
-  = 2 \int_0^{\sqrt{x}} u^{m - 1} e^{u^2} du
-  \,, $$
-whence
-$$
-\frac{d}{d x} g_m(x)
-  % = x^{-\tfrac{m}2} e^{-x}
-  %     \int_0^x t^{\tfrac{m}2 - 1} e^t dt
   = 2 x^{-\tfrac{m}2} e^{-x}
@@
 In particular, for $m=1$ we get
-$$
+\begin{equation}  \label{eq:g-m-series-one}
   g_1(x)
@@
     + e^{-x} \sum_{n\geq 0} \frac{x^n}{n!} \sum_{p=1}^n \frac2{2p - 1}
-  \,, $$
-and the derivative of the KL-term can be computed thus 
-$$
+    \,,
+\end{equation}
+and the derivative \eqref{eq:g-m-deriv} can be computed thus
+\begin{equation}  \label{eq:g-m-deriv-one}
   \frac{d}{d x} g_1(x)
     = 2 \tfrac{F(\sqrt{x})}{\sqrt{x}}
-  \,, $$
-using Dawson's integral $
+    \,,
+\end{equation}
+using $
   F \colon \mathbb{R} \to \mathbb{R}
   \colon x \mapsto e^{-x^2} \int_0^x e^{u^2} du
-$ -- a special function, implemented in most scientific computing libraries, e.g.
-``scipy.special.dawsn''.
-
-The derivative wrt $\alpha$ is 
+$ (Dawson's integral) a special function.
+
+The derivative of \eqref{eq:ard-kl-div-real} with respect to $\alpha$ is
 $$
@@
 However, since $\alpha$ is nonnegative, it is typically parameterized via its logarithm
-and computed when needed. Thus, in particular, the gradient of the divergence penalty w.r.t
-$\log \alpha$ is
-
+and computed when needed. Thus the gradient w.r.t $\log \alpha$ is
 \begin{equation}  \label{eq:real-kl-div-deriv-log}

### 2019-11-11 paper/paper.tex
removed trunk

@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\clearpage
-
-\section{Trunk} % (fold)
-\label{sec:trunk}
-
-In a fully Bayesian treatment, the dropout rate $p$, which governs the regularization strength,
-would appear in the KL-divergence term of ELBO \eqref{eq:elbo} through the corresponding odds 
-ratio $
-  \alpha = \tfrac{p}{1-p}
-$, which.
-
-it vary on the per-parameter basis, which allows for even more flexible posterior
-approximations.
-
-% revirew of kingma and lrt
-The key contributions of \cite{kingma_variational_2015} are reinterpretation of dropout
-as a variational inference method
-
-that optimizes the $\log$-likelihood term from the Evidence Lower Bound.
-
- % who proposed sparsification?
-
-In the case of $\real$-valued variational dropout \cite{kingma_variational_2015} approximate
-\eqref{eq:expect-improper-term-cplx} by a non-linear regression, fit to the Monte-Carlo estimates
-of the expectation for $\alpha$ varying over a logarithmic grid. This approximation was greatly
-refined in \cite{molchanov_variational_2017} -- an improvement that enabled doing away with
-the clipping of the dropout rate (relevance score) $\alpha$. In fact in the real case the analogue
-of the last term in \eqref{eq:expect-improper-term-cplx} is half the log-moment of a non-central
-$\chi^2$ distribution with shape $1$ and non-centrality $\lambda = \tfrac1{\alpha}$. Unfortunately,
-there is no known expression (even involving special functions) for this expectation for
-$\chi^2_m$ with odd shape parameter $m$ (degrees of freedom) \verify{this}. Quite fortunately
-there is one for even degrees of freedom.
-
-%%%%%%%
-\todo{why this is better than a general $\cplx$-gaussian? Three parameters?}
-
-\important{``pytorch'' specific}
-Otherwise we have to offload the values from the device to cpu, compute the special
-function there, and transfer back.
-
-Why sparsity matters, why $\cplx$ networks?
-
-Where are $\cplx$-networks used? and do these applications warrant sparsity?
-
-Gist of the LRP (\cite{kingma_variational_2015})
-translating uncertainty (randomness) from parameters to activations
-  adds noise -- helps regularization
-  emulates one draw per batch element -- decorrelates gradient within the batch
-  reduces computations (memory), leverages batched matmuls (or convos)
-  decreases variance of the gradient
-
-additive noise reparameterization (molchanov\_variational\_2017) $(\mu, \alpha \mu^2)$:
-  less noisy gradient wrt $\mu$, $\alpha$ recomputed on-the-fly
-
-\subsection{$\cplx$-valued networks} % (fold)
-\label{sub:c_valued_networks}
-
-In this section i remind the reader what the complex-valued networks are, how
-they are implemented and how much of $\cplx$-ness they have. Mention careful
-design.
-
-I will describe the linear layers (dense, masked, and convolutions) and
-activations borrowed straight from the $\real$-values networks. Then i shall
-mention that this has been tried before and list papers that one way or another
-address $\cplx$-data processing with neural networks.
-
-It is worth pointing out that the key advantage of
-the $\cplx$-constraints is that they permit use of Strassen's $3$M multiplication algorithm,
-potentially \verify{saving up} to $25\%$ on floating point multiplications. \todo{
-  in contrast to what? to na{\:i}ve (obvious)? to paired-$\real$ ($2 \times 2$-$2\times 1$
-  -- 4 fmul)?
-}
-
-% subsection c_valued_networks (end)
-
-\section{Bayesian methods} % (fold)
-\label{sec:bayesian_methods}
-
-In this section we outline and derive the variational dropout technique for complex-%
-valued networks, which re-traces the evolution of dropout technique for real-valued
-weights.
-
-% a second take on bayesian inference
-The core question of Bayesian analysis is concerned with the distribution of the data model
-after observing data and given the initial belief about it. The data model is typically a joint
-distribution on the sample, which includes assumptions regarding independence and (conditional)
-factorization of the distribution of each individual data point. In our case we suppose that
-the data $
-  \mathcal{D} = (z_i)_{i=1}^m
-$, $z_i = (x_i, y_i)$ is independent and identically distributed under our model $m$: $
-  p(\mathcal{D}\mid m)
-    = \prod_i p(z_i\mid m)
-$. The models we  our model $m$ comes from a parametric conditional distribution family, e.g. $
-  p(z \mid m)
-    = p(y \mid x, m) p(x \mid m)
-    = p(y \mid x, m) p(x)
-$ and $
-  p(y \mid x, m)
-    = \mathcal{N}\bigl(
-      y\,\mid\, \mu_\omega(x)\,, \sigma^2_\omega(x)
-    \bigr)
-$, then we can (and do) identify $m$ with its parameters $\omega$. Instead of iid data in
-$\mathcal{D}$, we could have assumed a Gaussian Process data model $
-  y(x) \sim \mathrm{GP}(\mu, K)
-$ for the mean function and covariance kernel $
-  \mu
-    \colon \mathcal{X} \to \real^d
-$ and $
-  K \colon \mathcal{X} \times \mathcal{X}
-    \to \real^{d\times d}
-$.
-
-In the framework of Bayesian Inference we use the Bayes's rule as an exact method for deriving
-the posterior parameter distribution from the likelihood of the data model and model's prior:
-$
-  p(\omega \mid \mathcal{D})
-    = \tfrac{
-      p(\mathcal{D} \mid \omega) \pi(\omega)
-    }{
-      p(\mathcal{D})
-    }
-$. Typically, exact inference involves an analytically intractable integrals, e.g. in the
-denominator of the posterior $
-  p(\mathcal{D})
-    = \int p(\mathcal{D} \mid \omega) \pi(\omega) d\omega
-$, or derived distributions, such as the predictive distribution $
-  p(y \mid x, \mathcal{D})
-    = \int p(y \mid x, \omega) p(\omega \mid \mathcal{D}) d\omega
-$.
-
-Variational Inference recasts the problem of posterior derivation into functional optimization
-framework. The main idea is to find the closest approximation to the posterior $
-  p(\omega \mid \mathcal{D})
-$ in some family $
-  \mathcal{Q}
-$ of approximating distributions $
-  q(\omega)
-$ on the parameters $\omega$ of the model $m$ (or the model itself). The proximity between
-distributions is measured either using MMD metric via embedding into some universal RKHS,
-\cite{citation_needed}, Wasserstein \cite{citation_needed} \cite{citation_needed}, total
-variation norm \cite{citation_needed}, or $f$-divergences
-% $
-%   \mathbb{E}_{\omega \sim q(\omega)} f\bigl(
-%       \tfrac{p(\omega)}{q(\omega)}
-%     \bigr)
-% $ for a convex $f$ with $f(1) = 0$
-\cite{citation_needed}, specifically Kullback-Leibler divergence. The key trade off in Variational
-Inference is the choice of the approximating family that is rich enough to get close to the true
-posterior, yet simple enough to sample from or for inferring derived distributions via Bayesian
-averaging.
-
-Despite the effort to simplify the bayesian analysis in the most commonly encountered cases
-variational inference still requires dealing with analytically intractable expectations,
-\cite{citation_needed}. This issue is dealt with by giving up deterministic precision to
-gain efficiency from stochastic, since inaccuracies and assumptions are inevitable, especially
-when modelling observations.
-
-% a verbatim setion from my mlss2019 bdl notebook
-In Bayesian Inference (\textbf{BI}) we \textit{assume} that the observation data $D$ follows a
-\textit{model} $m$ with data generating distribution $p(D \mid m, \omega)$ \textit{governed by
-unknown parameters} $\omega$. The goal of \textbf{BI} is to reason about the model and/or its
-parameters, and new data given the observed data $D$ and our assumptions, i.e to seek the
-\textbf{posterior} parameter and predictive distributions:
-
-\begin{align}
-p(d \mid D, m)
-  &
-  % = \mathbb{E}_{
-  %   \omega \sim p(\omega \mid D, m)
-  % } p(d \mid D, \omega, m)
-  = \int p(d \mid D, \omega, m) p(\omega \mid D, m) d\omega
-  \,, \\
-p(\omega \mid D, m)
-  &
-  = \frac{p(D \mid \omega, m) \, \pi(\omega \mid m)}{p(D \mid m)}
-  \,,
-\end{align}
-where
-\begin{itemize}
-  \item the \textbf{prior} distribution $\pi(\omega \mid m)$ reflects our belief before
-  having made the observations
-  \item the data distribution $p(D \mid \omega, m)$ reflects our assumptions about the data
-  generating process, and determines the model \textbf{likelihood} (Gaussian, Categorical,
-  Poisson etc.)
-\end{itemize}
-Unless the distributions and likelihoods are conjugate, posterior in Bayesian inference is
-typically intractable and it is common to resort to \textbf{Variational Inference} or
-\textbf{Monte Carlo} approximations.
-
-Since inference using the exact posterior is rarely tractable, efficient and unbiased approximation
-schemes are typically used. One such scheme is Variational Inference, which casts the inference
-task into the domain of optimization problems over some appropriately chosen the posterior
-distribution approximation family. The key idea of the former is to seek an approximation
-$q(\omega)$ to the intractable posterior $p(\omega \mid D, m)$, via a variational optimization
-problem over some parametric family of distributions $\mathcal{Q}$:
-$$
-q^*(\omega)
-    \in \arg \min_{q\in \mathcal{Q}}
-      \mathrm{KL}(q(\omega) \| p(\omega \mid D, m))
-  \,, $$
-where the Kullback-Leibler divergence between $P$ and $Q$ ($P\ll Q$) with densities $p$ and $q$,
-respectively, is given by
-$$
-\mathrm{KL}(q(\omega) \| p(\omega))
-  % = \mathbb{E}_{\omega \sim Q} \log \tfrac{dQ}{dP}(\omega)
-  = \mathbb{E}_{\omega \sim q(\omega)}
-    \log \tfrac{q(\omega)}{p(\omega)}
-  \,.
-  % \tag{kl-div}
-  $$
-
-Note that the family of variational approximations $\mathcal{Q}$ can be structured
-\textbf{arbitrarily}: point-mass, products, mixture, dependent on input, having mixed hierarchical
-structure, -- any distribution, even unnormalized. Although computing the divergence w.r.t.
-the unknown posterior is still hard and intractable, it is possible to do away with it
-through the following identity, which is based on the Bayes rule.
-
-For \textbf{any} $q(\omega) \ll p(\omega \mid D; \phi)$ and any model $m$
-
-\begin{align}
-\overbrace{
-  \log p(D \mid m)
-}^{\text{evidence}}
-  &= \overbrace{
-    \mathbb{E}_{\omega \sim q} \log p(D\mid \omega, m)
-  }^{\text{expected conditional likelihood}}
-  - \overbrace{
-    \mathrm{KL}(q(\omega)\| \pi(\omega \mid m))
-  }^{\text{proximity to prior belief}}
-  \\
-  &+ \underbrace{
-    \mathrm{KL}(q(\omega)\| p(\omega \mid D, m))
-  }_{\text{posterior approximation}}
-\,.
-\tag{master-identity}
-\end{align}
-Instead of minimizing the divergence of the approximation from the posterior, we can maximize
-the \textbf{Evidence Lower Bound} with respect to $q(\omega)$:
-$$
-q^* \in
-  \arg\max_{q\in Q}
-    \mathcal{L}(q)
-    = \mathbb{E}_{\omega \sim q} \log p(D\mid \omega, m)
-      - \mathrm{KL}(q(\omega)\| \pi(\omega \mid m))
-  \,.
-  % \tag{max-ELBO}
-  $$
-The intuition is that the expected $\log$-likelihood favours $q$ that place their mass on
-parameters $\omega$ that explain $D$ under the specified model $m$. At the same time
-the negative KL-divergence discourages the approximation $q$ from straying too far away
-from to the prior belief $\pi$ under $m$.
-
-We usually consider the following setup (conditioning on model $m$ is omitted):
-\begin{itemize}
-  \item the likelihood factorizes $
-    p(D \mid \omega)
-        = \prod_i p(y_i, x_i \mid \omega)
-        \propto \prod_i p(y_i \mid x_i, \omega)
-  $
-  for $D = (x_i, y_i)_{i=1}^N$
-
-  \item the variational posterior approximation is parameterized by $\theta$: $q(\omega \mid \theta)$
-
-  \item the prior on $\omega$ also depends on hyper-parameters $\lambda$, that can be fixed,
-  or variable ($\pi(\omega \mid \lambda)$).
-\end{itemize}
-
-In this case the variational objective (evidence lower bound)
-$$
-\log p(D\mid \lambda )
-  \geq \mathcal{L}(\theta, \lambda)
-    = \mathbb{E}_{\omega \sim q(\omega \mid \theta)}
-      \sum_i \log p_\phi(y_i \mid x_i, \omega)
-    - KL(q(\omega \mid \theta) \| \pi(\omega \mid \lambda))
-  \,, $$
-is maximized with respect to $\theta$ (to approximate the posterior).
-
-Priors can be
-\begin{itemize}
-  \item \textit{subjective}, i.e. reflecting prior beliefs (but not arbitrary)
-  \item \textit{objective}, i.e. reflecting our lack of knowledge
-  \item \title{empirical}, i.e. learnt from the observed data (optimized over
-  hyper-parameters $\lambda$)
-\end{itemize}
-
-The stochastic variant of ELBO is formed by randomly batching
-the dataset $D$:
-$$
-\mathcal{L}(\theta, \lambda)
-  \approx \mathcal{L}_\mathrm{SGVB}(\theta, \lambda)
-  = \lvert D \rvert \biggl(
-    \tfrac1{\lvert B \rvert}
-      \sum_{b \in B} \mathbb{E}_{\omega \sim q(\omega \mid \theta)}
-        \log p(y_b \mid x_b, \omega)
-  \biggr)
-  - KL(q(\omega \mid \theta) \| \pi(\omega \mid \lambda))
-  \,. $$
-
-Stochastic optimization follows noisy unbiased gradient estimates, which are usually cheap and
-allow escaping from local optima, but optimize the objective in expectation. In order to get
-a gradient of $
-  F_\theta = \mathbb{E}_{\omega \sim q(\omega \mid \theta)} f(\omega)
-$ w.r.t $\theta$ we use either:
-\begin{itemize}
-  \item (REINFORCE) $
-    \nabla_\theta F_\theta
-      = \mathbb{E}_{\omega \sim q(\omega \mid \theta)}
-        (f(\omega) - b_\theta) \nabla_\theta \log q(\omega \mid \theta)
-  $ for some $b_\theta$ that is used to control variance
-
-  \item (reparameterization) $
-    \nabla_\theta F_\theta
-      = \nabla_\theta \mathbb{E}_{\varepsilon \sim q(\varepsilon)}
-        f(g(\theta; \varepsilon))
-      = \mathbb{E}_{\varepsilon \sim q(\varepsilon)}
-        \nabla_\theta g(\theta; \varepsilon)
-          \nabla_\omega f(\omega) \big\vert_{\omega = g(\theta; \varepsilon)}
-    $ when there are $q$ and differentiable $g$, such that sampling from $
-      q(\omega \mid \theta)
-    $ is equivalent to $
-      \omega = g(\theta; \varepsilon)
-    $ with $\varepsilon \sim q(\varepsilon)$
-\end{itemize}
-
-The variational approximation might yield high dimensional integrals, which are slow/prohibitive
-to compute. To make the computations faster without foregoing much of the precision, we may use
-Monte Carlo estimator:
-$$
-\mathbb{E}_{\omega \sim q(\omega\mid \theta)} \, f(\omega)
-  \overset{\text{MC}}{\approx}
-    \frac1{\lvert \mathcal{W}\rvert}
-      \sum_{\omega \in \mathcal{W}} f(\omega)
-  \,, $$
-where $\mathcal{W} = (\omega_b)_{b=1}^B$ is a sample of independent draws from $
-  q(\omega\mid \theta)
-$. If we also approximate the expectation wrt model parameters in the gradient of ELBO via Monte
-Carlo we get the \textbf{doubly stochastic variational objective}:
-$$
-\nabla_\theta \mathcal{L}_\mathrm{DSVB}(\theta, \lambda)
-  \approx
-    \lvert D \rvert \biggl(
-      \tfrac1{\lvert B \rvert}
-        \sum_{b \in B}
-          \mathop{gradient}(x_b, y_b)
-    \biggr)
-    - \nabla_\theta KL(q(\omega \mid \theta) \| \pi(\omega \mid \lambda))
-  \,, $$
-where `gradient` is $
-  \nabla_\theta
-    \mathbb{E}_{\omega \sim q(\omega \mid \theta)}
-      \log p(y \mid x, \omega)
-$ using one of the approaches above, typically approximated using one independent draw of $\omega$
-per $b\in B$. We can use a similar sampling approach to compute the gradient of the divergence term.
-
-We can estimate the divergence term in the ELBO with Monte Carlo, or, for example, for the
-predictive distribution we have
-\begin{align}
-\mathbb{E}_{y\sim p(y\mid x, D, m)} \, g(y)
-  &
-  \overset{\text{BI}}{=}
-    \mathbb{E}_{\omega\sim p(\omega \mid D, m)}
-      \mathbb{E}_{y\sim p(y\mid x, \omega, D, m)} \, g(y)
-  \\
-  &
-  \overset{\text{VI}}{\approx}
-    \mathbb{E}_{\omega\sim q(\omega)}
-      \mathbb{E}_{y\sim p(y\mid x, \omega, D, m)} \, g(y)
-  \\
-  &
-  \overset{\text{MC}}{\approx}
-    % \hat{\mathbb{E}}_{\omega \sim \mathcal{W}}
-    %   \mathbb{E}_{y\sim p(y\mid x, \omega, D, m)} \, g(y)
-    \frac1{\lvert \mathcal{W}\rvert} \sum_{\omega \in \mathcal{W}}
-      \mathbb{E}_{y\sim p(y\mid x, \omega, D, m)} \, g(y)
-  \,,
-\end{align}
-where $\mathcal{W} = (\omega_b)_{b=1}^B \sim q(\omega)$ -- iid samples from the variational
-approximation.
-
-\bigskip
-
-% on bernoulli dropout
-Bernoulli dropout alleviates the problem of overfitting
-
-% a comment on Bernoulli dropout
-The key idea of Bernoulli dropout is to randomly mask input features of a layer during
-training with in order to learn decorrelated feature maps. In a recent study of network
-capacity for multitask learning, \cite{multitask2019}, it was shown, that associating
-each dataset (task) with a context, that masks a subset of the parameters, allows non-%
-destructive `packing' of the tasks in orthogonal on average `subsets' of a single set
-of weights, without much interference between tasks. This lends support for beneficial
-effects of Bernulli Dropout on test performance, since, in effect, the network learns
-to perform well on identical copies of the same task with different (binary) contexts
-with a single parameter set.
-
-% on gaussian dropout
-
-The local reparameterization trick, proposed by \cite{citation_wang_menning_2013} in the context
-of Bernoulli and Gaussian dropout regularization techniques \cite{citation_needed}, translates
-the uncertainty about global parameters to noise in the local intermediate state and utilizes
-the closure of Gaussian distribution under affine transformations. Computational advantage of
-the trick is that activation noise is cheaper to sample and store for the purposes of backpropagation,
-than independently sampling parameters from the posterior approximation individually for each
-element of the minibatch. As far as Bayesian inference is concerned, \cite{kingma_variational_2015}
-have shown that trick's beneficial effects on minibatch SGD convergence come via two mechanisms
-of likelihood gradient estimator's efficiency: decorrelation within the batch (independent noise
-draws) and variance reduction through local transfer of parameter uncertainty to activation noise.
-
-\begin{quote}
-
-in practice the performance of stochastic gradient methods depends on the variance of the gradient
-field
-
-sampling the activations directly, without the parameter randomness gives a low cost efficient
-MC estimator (statistical efficiency).
-
-the gradient in sgvb is unbiased estimate of the $\log$-likelihood part of the elbo
-
-\end{quote}
-
-A linear layer is parameterized by $W \in\real^{n \times m}$ and bias $b\in \real^n$ and
-acts on its input $x\in \real^m$ via $y = W x + b$ with $y\in \real^n$. The key idea of
-Bernoulli dropout is to mask elements in the matrix $W$ of the layer
-with some given probability $p$: $W = \theta \odot \xi$ with $\theta$ being the learnt
-weight matrix, and $
-  \xi \sim \mathcal{B}(\{0, \tfrac1{1-p}\}, 1-p)
-$ -- an iid Bernoulli mask. During training, a dropout mask $\xi$ is used to compute $W$,
-and during evaluation the weights are fixed to the expectation of $W$ which is $\theta$.
-The discussion and analysis in \cite{kingma_variational_2015}, suggest that drawing one
-common dropout mask for all data in the minibatch reduces statistical efficiency the estimator
-of the weights' gradient in the stochastic approximation of the evidence lower bound.
-
-Gaussian dropout works in a similar fashion, except the dropout mask $\xi$ is iid $
-  \mathcal{N}(1, \alpha=\tfrac{p}{1-p})
-$, i.e. a multiplicative Gaussian noise is injected into the network.
-
-The key idea of Variational Dropout is to assume a Gaussian Mean field variational
-approximation of the posterior distribution of linear layer's weights (or convolutional
-kernels, with a caveat\footnote).  \footnotetext{
-  at each spatial patch of input data the kernel is independently redrawn form the
-  VI distribution. This again helps with gradient variance reduction.
-}
-Weight $W$ are assumed to have independently distributed elements with $
-  w_{ij} \sim \mathcal{N}(\theta_{ij}, \sigma^2_{ij})
-$.
-
-In fact multiplicative Gaussian dropout on weights $W$ is in fact itself a variational
-approximation with variance $\sigma^2_{ij} = \theta_{ij}^2 \tfrac{p}{1-p}$ determined
-by the dropout rate.
-
-% set by step we retell the story of kingma_variational_2015
-Gaussian variational approximation enabled \cite{kingma_variational_2015} propose a
-\textit{local reparameterization trick}, which reduces the variance of the gradients
-in SGVB and does not resample $W$ per element of a minibatch. It relies the closure
-of Gaussian distribution under linear transformations. Indeed, if $W$ is a Gaussian
-matrix with independently distributed $
-  W_{ij} \sim \mathcal{N}(\theta_{ij}, \sigma^2_{ij})
-$, then we have \important{moved}.
-
-and instead
-translating the uncertainty from the weights into local output noise of each linear layer.
-Without this it would have been necessary to draw new set of random weights per each element
-in a mini-batch.
-
-$$
-  \mathcal{N}(\theta_{ij}, \alpha \theta^2_{ij})
-  \overset{\mathcal{D}}{\sim}
-  \theta_{ij} \mathcal{N}(1, \alpha)
-  \,, $$
-
-\cite{molchanov_variational_2017} propose additional step in the local reparametrization,
-which further reduces the variance of the gradient estimator for each dropped out
-weight. Their simple formal change of variables $(\theta, \alpha) \to (\theta, \sigma^2)$
-decouples the stochastic component from the weights \rewrite:
-$$
-  w_{ij} = \theta_{ij} + \theta_{ij} \sqrt{\alpha} \varepsilon_{ij}
-  \,\to\,
-  w_{ij} = \theta_{ij} + \sigma^2_{ij} \varepsilon_{ij}
-  \,, $$
-with the appropriate change of variables in the Kullback-Leibler divergence.
-($\alpha_{ij} = \tfrac{\sigma_{ij}^2}{\lvert \theta_{ij}\rvert^2}$).
-
-Criticism of \cite{gale_state_2019} implies that $\ell_0$-variational dropout,
-proposed by \cite{louizos_learning_2017} and based on the concrete binary distribution
-of \cite{maddison_concrete_2016}, works consistently better than the variational
-Gaussian dropout.
-
-The expectation in \eqref{eq:expect-improper-term-cplx} involves a log-moment of the non-central
-$\chi^2_2$ distribution, which has an analytic expression for the gradient, unlike the case
-in $\real$-dropout penalty \eqref{eq:improper-kl-div-real}.
-
-% section bayesian_methods (end)
-
 \end{document}

### 2019-11-12 paper/paper.tex
in-text and parenthetical citations

@@
 \usepackage[utf8]{inputenc}
+\usepackage[english]{babel}
+\usepackage{natbib}
+% \setcitestyle{authoryear,open={((},close={))}}
 
@@
 of model compression and sparsification methods, that focus on favourable tradeoff between
-performance and size. Most popular techniques include weight pruning \cite{citation_needed},
-model quantization from IEEE754 floating point to integer-based arithmetic \cite{citation_needed},
+performance and size. Most popular techniques include weight pruning \citep{citation_needed},
+model quantization from IEEE754 floating point to integer-based arithmetic \citep{citation_needed},
 and dropout. The key assumption is that the more explicitly zero parameters there is,
@@
 posterior belief. Under suitable modelling and prior assumptions, Bayesian methods can be
-used towards model sparsification, \cite{kingma_variational_2015,molchanov_variational_2017},
-and \cite{kharitonov_variational_2018}.
+used towards model sparsification, \citep{kingma_variational_2015,molchanov_variational_2017},
+and \citep{kharitonov_variational_2018}.
 
@@
 studies have shown a potentially richer representation of complex nets
-\cite{hirose2003,fijulamin2009}
+\citep{hirose2003,fijulamin2009}
 % [3] Akira Hirose, Complex-valued neural networks: theories and applications, vol. 5, World Scientific, 2003.
@@
 
-\cite{yang_complex_2019} develop complex transformer, with $\cplx$-attention and complex
+\citep{yang_complex_2019} develop complex transformer, with $\cplx$-attention and complex
 encoder-decoder, and apply it to music transcription and wireless signal classification.
@@
 
-papers related to complex-valued distributions \cite{pav_moments_2015,taubock_complex-valued_2012},
-and \cite{karseras_caution:_2014}
-
-Application of complex-valued networks is not new, \cite{citation_needed}. More recently
-they were applied to music transcription and speech recognition \cite{trabelsi_deep_2017},
-and \cite{yang_complex_2019}. The key motivation behind adoption of $\cplx$-networks is
-pervasiveness of $\cplx$-valued data in digital signal processing \cite{citation_needed},
-acoustic and radio signal analysis \cite{citation_needed}, and quantum systems modelling
-\cite{citation_needed}, etc. All these applications require compliance with algebraic
+papers related to complex-valued distributions \citep{pav_moments_2015,taubock_complex-valued_2012},
+and \citep{karseras_caution:_2014}
+
+Application of complex-valued networks is not new, \citep{citation_needed}. More recently
+they were applied to music transcription and speech recognition \citep{trabelsi_deep_2017},
+and \citep{yang_complex_2019}. The key motivation behind adoption of $\cplx$-networks is
+pervasiveness of $\cplx$-valued data in digital signal processing \citep{citation_needed},
+acoustic and radio signal analysis \citep{citation_needed}, and quantum systems modelling
+\citep{citation_needed}, etc. All these applications require compliance with algebraic
 operations in the field of complex numbers.
@@
 The posterior itself is computationally intractable, save for the relatively simple cases
-\cite{citation_needed}, and therefore exact inference is traded for tractability and scalability
+\citep{citation_needed}, and therefore exact inference is traded for tractability and scalability
 of Variational Inference. Instead of deriving $p(\omega \mid D)$ using the rule, this approach
@@
   \omega \mapsto \nabla_\theta \log q_\theta(\omega)
-$, \cite{williams_simple_1992}, or can be represented as differentiable transformations
-of non-parametric noise, \cite{kingma_auto-encoding_2014,figurnov_implicit_2019}.
+$, \citep{williams_simple_1992}, or can be represented as differentiable transformations
+of non-parametric noise, \citep{kingma_auto-encoding_2014,figurnov_implicit_2019}.
 % (reparameterization trick, pathwise gradieent) $q_{\theta}(d\omega)$ is a push-forward
@@
 variational objectives are possible, provided $p(\omega \mid D)$ is probed only through
-$\log p(D \mid \omega)$ and $\log \pi(\omega)$, \cite{ranganath_operator_2018}.
-
-\textit{Stochastic Gradient Variational Bayes} (SGVB), proposed by \cite{kingma_auto-encoding_2014},
+$\log p(D \mid \omega)$ and $\log \pi(\omega)$, \citep{ranganath_operator_2018}.
+
+\textit{Stochastic Gradient Variational Bayes} (SGVB), proposed by \citep{kingma_auto-encoding_2014},
 is a differentiable unbiased Monte-Carlo estimator of \eqref{eq:elbo_general}, which makes
@@
 $ is an iid sample from $p_\varepsilon$. Intractable KL-divergence terms can be replaced
-by differentiable unbiased Monte-Carlo estimators, \cite{kingma_auto-encoding_2014}.
+by differentiable unbiased Monte-Carlo estimators, \citep{kingma_auto-encoding_2014}.
 %
@@
 With special family of posterior approximation, variational inference can be used as
-a regularization method, \cite{kingma_variational_2015}, and as model sparsification
-technique, \cite{molchanov_variational_2017}. The paper \cite{kingma_variational_2015}
-considers Dropout \cite{hinton_improving_2012}, DropConnect, \cite{wan_regularization_2013},
-and Gaussian dropout, \cite{srivastava_dropout_2014,wang_fast_2013} through the lens
-of Bayesian inference methods and proposes \textit{Variational Dropout}. It argues that
+a regularization method and as model sparsification technique. \citet{kingma_variational_2015}
+consider Dropout \citep{hinton_improving_2012}, DropConnect, \citep{wan_regularization_2013},
+and Gaussian dropout, \citep{srivastava_dropout_2014,wang_fast_2013} through the lens
+of Bayesian inference methods and proposes \textit{Variational Dropout}. They argue that
 the multiplicative noise introduced by these methods induces a distribution equivalent to
@@
 %
-Variational Dropout with assumes mean field Gaussian approximation $
+Variational Dropout assumes fully factorized Gaussian approximate posterior $
   q_\theta(\omega)
@@
 \end{equation}
-\cite{kingma_variational_2015} approximate this expression by a non-linear polynomial
-regression for \verify{truncated} $\alpha \in (0, 1)$. This approximation was refined in
-\cite{molchanov_variational_2017}, both in terms of the domain of $\alpha$ and accuracy. The
-paper considered regression with sigmoid and soft-plus basis functions fit to the Monte-Carlo
-estimator of \eqref{eq:improper-kl-div-real} for $\alpha$ varying over a fine logarithmic grid.
-In sec.~\ref{sub:real-chisq-grad} we verify the approximation and confirm its accuracy, by
-comparing its derivative to the exact derivative of \eqref{eq:improper-kl-div-real} with
-respect to $\log \alpha$.
+\citet{kingma_variational_2015} approximate this expression by a non-linear polynomial
+regression for \verify{truncated} $\alpha \in (0, 1)$. \citet{molchanov_variational_2017}
+refine the approximation by using sigmoid and soft-plus basis functions.
+%
+In sec.~\ref{sub:real-chisq-grad} we verify the approximation against Monte-Carlo
+estimates of \eqref{eq:improper-kl-div-real} for $\alpha$ varying over a fine logarithmic
+grid, and confirm its accuracy, by comparing its derivative to the exact derivative of
+\eqref{eq:improper-kl-div-real} with respect to $\log \alpha$.
 % (!) good for SGVB: gradient-based methods require unbiased gradient estimates
@@
 Flexibility in specification of $q_\theta$ enables structured dropout with shared
-$\alpha$ across groups of parameters $\omega$. \cite{molchanov_variational_2017} study
+$\alpha$ across groups of parameters $\omega$. \citet{molchanov_variational_2017} study
 Variational Dropout from a model sparsification perspective, optimizing $\alpha$ for each
 individual parameter. Another variant of Bayesian dropout, called \textit{Automatic Relevance
-Determination}, is developed in \cite{kharitonov_variational_2018}. The key difference is
+Determination}, is developed in \citep{kharitonov_variational_2018}. The key difference is
 that the log-uniform factor $\pi(\omega_{ij})$ is replaced by a proper Gaussian prior $
@@
 $ with learnable precision $\tau_{ij} > 0$. This method, known as \textit{Empirical Bayes}
-\cite{citation_needed}, fits a prior distribution while performing variational inference.
+\citep{citation_needed}, fits a prior distribution while performing variational inference.
 Maximizing \eqref{eq:elbo} over $\lambda$, holding other parameters fixed, yields $
@@
 
-Another contribution of \cite{kingma_variational_2015} is the analysis of the effects of the
+Another contribution of \citep{kingma_variational_2015} is the analysis of the effects of the
 \textit{local reparameterization trick} on the variance of the gradient of \eqref{eq:elbo}.
-This trick, proposed in \cite{wang_fast_2013} to speed up Gaussian dropout, utilizes the
+This trick, proposed in \citep{wang_fast_2013} to speed up Gaussian dropout, utilizes the
 closure of Gaussians under affine transformations, thereby translating uncertainty from the
@@
 %
-\cite{kingma_variational_2015} show, that for the case of fully factorized Gaussian
+\citet{kingma_variational_2015} show, that for the case of fully factorized Gaussian
 posterior approximations, the trick decorrelates ELBO estimates within the minibatch,
 making the gradient estimator $\nabla_\theta \tilde{\mathcal{L}}$ more statistically
-efficient. \cite{molchanov_variational_2017} propose an improvement by introducing
+efficient. \citet{molchanov_variational_2017} propose an improvement by introducing
 \textit{additive noise parameterization}, which is relevant to model sparsification.
-The paper argues that $(\mu, \alpha)$ parameterization should be abandoned in favour
-of an equivalent $(\mu, \sigma^2)$ with the score $\alpha$ calculated using $
+They argue that $(\mu, \alpha)$ parameterization should be abandoned in favour of an
+equivalent $(\mu, \sigma^2)$ with the score $\alpha$ calculated using $
   \tfrac{\sigma^2}{\mu^2}
@@
   \nabla_\mu \tilde{\mathcal{L}}
-$, which is shown in \cite{molchanov_variational_2017} to be independent of the noise,
+$, which is shown in \citep{molchanov_variational_2017} to be independent of the noise,
 injected by the trick \eqref{eq:r-gauss-trick}, and further stabilizes gradients in SGVB
@@
 
-The study \cite{trabelsi_deep_2017} outlines building blocks for deep $\cplx$-valued
-networks and describes suitable representation and operations including convolutional
-and dense layers, $\cplx$-valued activations, complex batch-normalization and suitable
-weight initialization. Their approach makes a complex-valued network into an intricately
-connected $\real$-valued computational graph that respects $\cplx$-algebra.
+\citet{trabelsi_deep_2017} outline the building blocks for deep $\cplx$-valued networks
+and describe suitable representation and operations including convolutional and dense layers,
+$\cplx$-valued activations, complex batch-normalization and suitable weight initialization.
+Their approach makes a complex-valued network into an intricately connected $\real$-valued
+computational graph that respects $\cplx$-algebra.
 
@@
 using \eqref{eq:cplx-lin-op}. Algebraic operations, trigonometric functions, are implemented
-through operations in $\real^2$. Activations, considered in \cite{trabelsi_deep_2017} include
+through operations in $\real^2$. Activations, considered in \citep{trabelsi_deep_2017} include
 independent componentwise application of $\real$-valued non-linearities, $
@@
 or $\cplx\real$ calculus, which generalizes holomorphic calculus to non-holomorphic functions
-of $\cplx$-argument, \cite{adali_complex-valued_2011}. The rules it defines satisfy intuitive
+of $\cplx$-argument, \citep{adali_complex-valued_2011}. The rules it defines satisfy intuitive
 linearity, product and chain rules, and respect complex conjugation, but most importantly the
@@
 networks into existing $\real$ deep learning auto-differentiation frameworks. It was considered
-as a basis for $\cplx$ version of backpropagation in \cite{benvenuto_complex_1992} and
-\cite{trabelsi_deep_2017}, (see sec.~\ref{sub:wirtinger_calculus} for details).
+as a basis for $\cplx$ version of backpropagation in \citep{benvenuto_complex_1992} and
+\citep{trabelsi_deep_2017}, (see sec.~\ref{sub:wirtinger_calculus} for details).
 %
@@
   (P \otimes R) (C \otimes S) = P Q \otimes R S
-$, \cite{petersen_matrix_2012}.
+$, \citep{petersen_matrix_2012}.
 % It follows from the definition of the Kronecker product
@@
 % ``strength'' and ``direction'' of the linear relation between real and imaginary
-% parts, \cite{lapidoth_capacity_2003}.
+% parts, \citep{lapidoth_capacity_2003}.
 % $$
@@
 
-The local reparameterization trick provides both faster computations, \cite{wang_fast_2013},
-and better statistical efficiency of the SGVB gradient estimator, \cite{kingma_variational_2015}.
-A general mean field $\cplx$-Gaussian approximation \eqref{eq:c-gauss-vi} for $
+The local reparameterization trick provides both faster computations, and better statistical
+efficiency of the SGVB gradient estimator, \citep{wang_fast_2013,kingma_variational_2015}. A
+general mean field $\cplx$-Gaussian approximation \eqref{eq:c-gauss-vi} for $
   W \in \cplx^{n\times m}
@@
 The rationale is to reduce correlation in the gradient estimator stemming from kernel weights
-being shared between overlapping patches, \cite{kingma_variational_2015,citation_needed}.
+being shared between overlapping patches, \citep{kingma_variational_2015,citation_needed}.
 Thus \eqref{eq:cplx-gauss-trick} requires computing $\cplx$ convolutions of $x$, complex
@@
 We consider two priors for Bayesian dropout: log-uniform and $\cplx$-Gaussian empirical
-Bayes, \cite{kingma_variational_2015,molchanov_variational_2017,kharitonov_variational_2018}.
+Bayes, \citep{kingma_variational_2015,molchanov_variational_2017,kharitonov_variational_2018}.
 For a fully factorized approximation $q(\omega)$ and factorized prior belief $\pi(\omega)$,
@@
 %   \,. $$
-% 4. \cite{lapidoth_capacity_2003} yields $\lim_{x\to 0-} \log{(-x)} - \mathop{Ei}(x) = \gamma$
+% 4. \citep{lapidoth_capacity_2003} yields $\lim_{x\to 0-} \log{(-x)} - \mathop{Ei}(x) = \gamma$
 % 5. $Ei(x) \geq -e^x$ for any $x < -1$, since $t^{-1} e^t \geq - e^t$ for $t < -1$
@@
 The KL-divergence term in \eqref{eq:elbo} coincides with \eqref{eq:improper-kl-div-real}.
-We use the approximation provided by \cite{molchanov_variational_2017}. Note that additive
-noise reparameterization, \cite{molchanov_variational_2017}, cannot be used in
+We use the approximation provided by \citep{molchanov_variational_2017}. Note that additive
+noise reparameterization, \citep{molchanov_variational_2017}, cannot be used in
 \eqref{eq:real-scal-gauss-trick}.
@@
 
-\cite{trabelsi_deep_2017} studies the applicability of complex-valued networks to
-image classification (CIFAR-10, CIFAR-100, reduced train of SVHN), music-transcription
+\citet{trabelsi_deep_2017} study the applicability of complex-valued networks to image
+classification (CIFAR-10, CIFAR-100, reduced train of SVHN), music-transcription
 (MusicNet), and Speech Spectrum prediction (TIMIT).
@@
 
-\cite{monning_evaluation_2018}
-\cite{jankowski_complex-valued_1996}
-\cite{amin_complex-valued_2012}
-\cite{sarroff_complex_2018}
+\citep{monning_evaluation_2018}
+\citep{jankowski_complex-valued_1996}
+\citep{amin_complex-valued_2012}
+\citep{sarroff_complex_2018}
 
@@
 the throughput. Although careful circuit design can mitigate undesirable effects, they cannot
-be eliminated entirely \cite{citation_needed}. \textit{Digital Signal Predistortion} (DPD)
+be eliminated entirely \citep{citation_needed}. \textit{Digital Signal Predistortion} (DPD)
 aims at linearizing the amplifier by introducing computed on-the-fly compensation to the
@@
 reduce cross-channel interference and enables higher bandwidth utilization in wireless
-transmitters, \cite{citation_needed}. The main challenge of DPD methods is efficient
+transmitters, \citep{citation_needed}. The main challenge of DPD methods is efficient
 compensation on-device (with low-latency).
 
-\cite{traverso_low_2019} uses \rewrite{some group delay estimators of something};
-\cite{schoukens_obtaining_2017} develops an iterative approach to inference of the predistortion for a given
-signal \todo{unclear};
-
-\cite{tarver_design_2019} models the predistorter as a paired real dense shallow neural network and
-demonstrates viability and competitiveness of this approach against polynomial based DPD on an
-FPGA implementation.
+\citet{traverso_low_2019} use \rewrite{some group delay estimators of something};
+\citet{schoukens_obtaining_2017} develop an iterative approach to inference of the predistortion
+for a given signal \todo{unclear};
+
+\citet{tarver_design_2019} model the predistorter as a paired real dense shallow neural network
+and demonstrate viability and competitiveness of this approach against polynomial based DPD on
+an FPGA implementation.
 
@@
 the user-submitted quadrature signal through a class AB GaN amplifier and sends-back the measured
-output \cite{dpdcompetiton2018}. It is maintained by the GHz Centre at Chalmers University of
-Technolgy and National Instruments \cite{landin_rfweblab_2015}.
+output \citep{dpdcompetiton2018}. It is maintained by the GHz Centre at Chalmers University of
+Technolgy and National Instruments \citep{landin_rfweblab_2015}.
 
@@
 %
-The most fierce critique of Bayesian approach towards model
-sparsification was voiced in \cite{gale_state_2019}, where it was show that it yielded
+The \verify{most fierce critique} of Bayesian approach towards model
+sparsification was voiced in \citep{gale_state_2019}, where it was show that it yielded
 inconsistent results in text translation tasks and systematically underperformed simpler
-techniques such as norm pruning and $\ell_0$-regularization, \cite{louizos_learning_2017}.
+techniques such as norm pruning and $\ell_0$-regularization, \citep{louizos_learning_2017}.
 
@@
 mask distribution. It is closely related to gumbel-softmax reparameterization trick,
-\cite{kingma_auto-encoding_2014,jang_categorical_2017}: the mask is a stretched sigmoid,
+\citep{kingma_auto-encoding_2014,jang_categorical_2017}: the mask is a stretched sigmoid,
 clamped to $[0,1]$, that takes random input shifted relative to a learnable location
@@
 
-\bibliographystyle{unsrt}
+\bibliographystyle{abbrvnat}
 \bibliography{references}
@@
 and its gradient requires evaluating the Gauss error function, the analysis provides
-independent verification of the approximation, proposed in \cite{molchanov_variational_2017}.
-The logic of the derivation follows \cite{lapidoth_capacity_2003}.
-% \cite{pav_moments_2015} correctly notice that \cite[p. 2466]{lapidoth_capacity_2003} has a missing $\log{2}$ term.
+independent verification of the approximation, proposed in \citep{molchanov_variational_2017}.
+The logic of the derivation follows \citep{lapidoth_capacity_2003}.
+% \citep{pav_moments_2015} correctly notice that \cite[p. 2466]{lapidoth_capacity_2003} has a missing $\log{2}$ term.
 
@@
 
-We replicated the simulation experiment in \cite{molchanov_variational_2017} and recovered
+We replicated the simulation experiment in \citep{molchanov_variational_2017} and recovered
 the same nonlinear approximation result reported therein. We sampled $10^7$ draws of  and 
@@
   \includegraphics[width=1.\linewidth]{../notebooks/assets/grad_log.pdf}
-  \caption{$\tfrac{d f(\alpha)}{d \log{\alpha}}$ of the fit \cite{molchanov_variational_2017},
+  \caption{$\tfrac{d f(\alpha)}{d \log{\alpha}}$ of the fit \citep{molchanov_variational_2017},
   MC estimate, and exact derivative using \eqref{eq:real-kl-div-deriv-log}.}
@@
 % TLDR: we use Wirtinger calculus!
-Following \cite{trabelsi_deep_2017}, we naturally identify $\cplx$ with $\real^2$ via $
+Following \citep{trabelsi_deep_2017}, we naturally identify $\cplx$ with $\real^2$ via $
   z_\mathrm{r} + j z_\mathrm{i} \mapsto (z_\mathrm{r}, z_\mathrm{i})

### 2019-11-12 paper/paper.tex
edits in appendices

@@
 A $\cplx$-Gaussian vector $z$ is \textit{proper}, if $z$ and $\conj{z}$ are uncorrelated, i.e.
-$C = 0$. From \eqref{eq:c-gauss-entropy-derivation} the entropy of a proper $\cplx$-Gaussian is
+$C = 0$. The entropy of proper $\cplx$-Gaussians is
 \begin{equation}  \label{eq:cn-proper-entropy}
@@
     = \log \bigl\lvert \det{(\pi e \Gamma)} \bigr\rvert
-    \,.
+    \tag{\ref{eq:c-gauss-entropy-derivation}'}\,.
 \end{equation}
@@
         - \mathbb{H}(q(\omega_{ij}))
-        - \mathbb{E}_{\omega_{ij} \sim q(\omega_{ij})} \log{\pi(\omega_{ij})}
+        - \mathbb{E}_{q(\omega_{ij})} \log{\pi(\omega_{ij})}
       \bigr)
@@
 Its density is
-\begin{equation}. \label{eq:nonchisq-density}
+\begin{equation}  \label{eq:nonchisq-density}
   f_W(x)
@@
 %   \,. $$
-In \eqref{eq:ard-kl-div-real} we need the expected logarithm of $W$:
+In \eqref{eq:ard-kl-div-real} we need $
+  \mathbb{E}_{W\sim \chi^2_m(\lambda)} \log W
+$:
 \begin{align}
-  \mathbb{E}_{W\sim \chi^2_m(\lambda)} \log W
-    &= \int_0^\infty f_W(x) \log x dx
-    \notag \\
+    % &= \int_0^\infty f_W(x) \log x dx
+    % \notag \\
     &= \frac12 e^{- \tfrac\lambda2}
@@
         \bigl(\tfrac{x}2\bigr)^{n + \tfrac{m}2 - 1}
-    \biggr) \log x dx
+    \biggr) \log{(x)} dx
     % = [\text{ absolute summability and Fubini, or any other conv. thm for integrals of non-negative integrals}]
@@
       \, du
-    \,.
-\end{equation}
-Note that $\psi$ satisfies: $
+    \,,
+\end{equation}
+which satisfies $
   \psi(z+1) = \psi(z) + \tfrac1z
@@
 Differentiating the series within $g_m$ yields
-\begin{equation*}  \label{eq:g-m-deriv}
+\begin{equation}  \label{eq:g-m-deriv}
   \frac{d}{d x} g_m(x)
@@
     = e^{-x} \sum_{n\geq 0} \frac{x^n}{n!} (n + \tfrac{m}2)^{-1}
-    = \cdots
-    \,.
-\end{equation*}
+    \,.
+\end{equation}
 Since $
     e^t  = \sum_{n\geq 0} \tfrac{t^n}{n!}
-$ on $\mathbb{R}$, for $\alpha\neq 0$ we have $
-  \int_0^x t^{\alpha-1} dt
-    = \tfrac{x^\alpha}{\alpha}
-$ and
-\begin{equation*}  \label{eq:g-m-deriv-int-1}
+$ on $\mathbb{R}$, for $\alpha\neq 0$ we have
+% $
+%   \int_0^x t^{\alpha-1} dt
+%     = \tfrac{x^\alpha}{\alpha}
+% $ and
+\begin{equation}  \label{eq:g-m-deriv-int-1}
   \sum_{n\geq 0} \int_0^x \frac{t^{n+\alpha-1}}{n!} dt
-    = \int_0^x \sum_{n\geq 0} \frac{t^{n+\alpha-1}}{n!} dt
+    % = \int_0^x \sum_{n\geq 0} \frac{t^{n+\alpha-1}}{n!} dt
     = \int_0^x t^{\alpha-1} e^t dt
@@
   % the MCT ([0, x], \mathcal{B}([0, x]), dx)
-\end{equation*}
+\end{equation}
 by the monotone convergence theorem, whence
 \begin{equation}  \label{eq:g-m-deriv-int-2}
-  \cdots
+  \eqref{eq:g-m-deriv}
     = x^{-\tfrac{m}2} e^{-x} \sum_{n\geq 0}
@@
         \int_0^x t^{\tfrac{m}2 - 1} e^t dt
-    = \cdots
     \,.
@@
 The substitution $u^2 = t$ on $[0, \infty]$ with $2u du = dt$ yields
-$$
+\begin{equation}  \label{eq:g-m-deriv-int-3}
   \frac{d}{d x} g_m(x)
-  = x^{-\tfrac{m}2} e^{-x}
-      \int_0^x t^{\tfrac{m}2 - 1} e^t dt
+    % = x^{-\tfrac{m}2} e^{-x}
+    %     \int_0^x t^{\tfrac{m}2 - 1} e^t dt
     = 2 x^{-\tfrac{m}2} e^{-x}
         \int_0^{\sqrt{x}} u^{m - 1} e^{u^2} du
-  \,. $$
+    \,.
+\end{equation}
 In particular, for $m=1$ we get
@@
   \colon x \mapsto e^{-x^2} \int_0^x e^{u^2} du
-$ (Dawson's integral) a special function.
+$ Dawson's integral (special function).
 
@@
   \,. $$
-However, since $\alpha$ is nonnegative, it is typically parameterized via its logarithm
-and computed when needed. Thus the gradient w.r.t $\log \alpha$ is
+Since $\alpha$ is nonnegative, it is typically parameterized via its logarithm and computed
+when needed. Thus the gradient of \eqref{eq:ard-kl-div-real} w.r.t $\log \alpha$ is
 \begin{equation}  \label{eq:real-kl-div-deriv-log}
-  \frac{d}{d\log \alpha}
-    \tfrac12 \mathbb{E}_{z \sim \mathcal{N}(0,1)}
-    \log \lvert z + \tfrac1{\sqrt{\alpha}} \rvert^2
-    = \frac12 \frac{d\alpha}{d\log \alpha}
-      \frac{d}{d\alpha} \bigl(\mathbb{E}\cdots \bigr)
+  \frac{d \eqref{eq:ard-kl-div-real}}{d\log \alpha}
+  % \frac{d}{d\log \alpha}
+  %   \frac12 \mathbb{E}_{z \sim \mathcal{N}(0,1)}
+  %     \log \lvert z + \tfrac1{\sqrt{\alpha}} \rvert^2
+    % = \frac12 \frac{d\alpha}{d\log \alpha}
+    %   \frac{d}{d\alpha} \bigl(\mathbb{E}\cdots \bigr)
     % = - \frac\alpha2 \tfrac1{\alpha}
     %   \sqrt{\tfrac2{\alpha}} F(\tfrac1{\sqrt{2\alpha}})
-    = - \tfrac1{\sqrt{2\alpha}} F(\tfrac1{\sqrt{2\alpha}})
+    = - \frac1{\sqrt{2\alpha}} F\bigl(\tfrac1{\sqrt{2\alpha}}\bigr)
     \,.
@@
 the same nonlinear approximation result reported therein. We sampled $10^7$ draws of  and 
-The coefficients are within
-$1\%$ relative tolerance of the reported.
+The coefficients are within $1\%$ relative tolerance of the reported.
 $$
-- KL(\mathcal{N}(w \mid \mu, \alpha \mu^2) \|
-    \tfrac1{\lvert w \rvert})
+  \eqref{eq:ard-kl-div-real}
+% - KL(\mathcal{N}(w \mid \mu, \alpha \mu^2) \|
+%     \tfrac1{\lvert w \rvert})
+%   \approx
+%     k_1 \sigma(k_2 + k_3 \log \alpha)
+%     + C \big\vert_{C = -k1}
+%     - \tfrac12 \log (1 + e^{-\log \alpha})
   % = \tfrac12 \log \alpha
@@
   \approx
-    k_1 \sigma(k_2 + k_3 \log \alpha) + C \big\vert_{C = -k1}
-    - \tfrac12 \log (1 + e^{-\log \alpha})
+    \frac12 \log{\bigl(1 + e^{-\log \alpha}\bigr)}
+    + k_1 \sigma\bigl(- (k_2 + k_3 \log \alpha)\bigr)
+    % - k_1 \bigl(1 - \sigma(k_2 + k_3 \log \alpha)\bigr)
   \,. $$
@@
 % term, since it is typically implemented in a floating-point stable fashion.
-The numerically estimated derivative of the penalty term wrt $\log \alpha$ using forward
-differences seems to be following \eqref{eq:real-kl-div-deriv-log} very closely (up to
-sampling error) see fig.~\ref{fig:molchanov-derivative-replica}.
 
@@
 
+The numerically estimated derivative of the penalty term wrt $\log \alpha$ using forward
+differences seems to be following \eqref{eq:real-kl-div-deriv-log} very closely (up to
+sampling error) see fig.~\ref{fig:molchanov-derivative-replica}.
+
 % subsection real-chisq-grad (end)
@@
 \label{sub:wirtinger_calculus}
-
-% TLDR: we use Wirtinger calculus!
-Following \citep{trabelsi_deep_2017}, we naturally identify $\cplx$ with $\real^2$ via $
-  z_\mathrm{r} + j z_\mathrm{i} \mapsto (z_\mathrm{r}, z_\mathrm{i})
-$, storing the real and imaginary parts in interleaved format, and emulate $\cplx$-algebra
-using $\real$-valued arithmetic.
 
@@
   f(z) = f(u + jv) = F(u, v)
-$. Under this identification, we define two formal derivative operators
-$
-  \tfrac{\partial}{\partial z}
-    = \tfrac12 \bigl(
-      \tfrac{\partial}{\partial u}
-      - j \tfrac{\partial}{\partial v}
-    \bigr)
-$ and $
-  \tfrac{\partial}{\partial \conj{z}}
-    = \tfrac12 \bigl(
-      \tfrac{\partial}{\partial u}
-      + j \tfrac{\partial}{\partial v}
-    \bigr)
-$ and the differential of $f$ at $z \in \cplx$ as
+$. Within this framework the differential of $f$ at $z \in \cplx$ is
 $$
@@
   \,, $$
-where $dz = du + j dv$ and $d\conj{z} = du - j dv$. This implies that the complex argument
-and its conjugate are treated as independent variables. Cauchy-Riemann conditions $
+with formally defined derivatives $
+  \tfrac{\partial}{\partial z}
+    = \tfrac12 \bigl(
+      \tfrac{\partial}{\partial u}
+      - j \tfrac{\partial}{\partial v}
+    \bigr)
+$ and $
+  \tfrac{\partial}{\partial \conj{z}}
+    = \tfrac12 \bigl(
+      \tfrac{\partial}{\partial u}
+      + j \tfrac{\partial}{\partial v}
+    \bigr)
+$, and differentials $dz = du + j dv$ and $d\conj{z} = du - j dv$. This implies that the
+complex argument and its conjugate are treated as independent variables. Cauchy-Riemann
+conditions $
   -j \tfrac{\partial F}{\partial v} = \tfrac{\partial F}{\partial u}
-$ impose a rigid structure on real and imaginary parts of $F$ and can be expressed as $
+$ scan be expressed as $
   \tfrac{\partial f}{\partial \conj{z}} = 0
@@
       + j \tfrac{\partial F}{\partial v}
-$. Therefore, Wirtinger calculus makes it possible to reuse $\real$-backpropagation.
+$.
+
+Natural identification of $\cplx$ with $\real\times \real$, storing the real and imaginary
+parts in interleaved format, emulation of $\cplx$-algebra using $\real$-valued arithmetic,
+and Wirtinger calculus make it possible to reuse $\real$-backpropagation and existing
+auto-differentiation frameworks, \citep{trabelsi_deep_2017}.
 

### 2019-11-12 paper/paper.tex
compressing the analysis in appendix

@@
     = \frac12 e^{- \tfrac{x + \lambda}2} \bigl(\tfrac{x}2\bigr)^{\tfrac{m}2 - 1}
-      \sum_{n \geq 0} \tfrac{
+      \sum_{n \geq 0} \frac{
         \bigl(\tfrac{x \lambda}4\bigr)^n
@@
 %   \,. $$
-In \eqref{eq:ard-kl-div-real} we need $
+The expectation $
   \mathbb{E}_{W\sim \chi^2_m(\lambda)} \log W
-$:
-\begin{align}
+$, needed in \eqref{eq:ard-kl-div-real}, by integrating power series \eqref{eq:nonchisq-density}
+with substitution $x \to 2u$ equals
+\begin{multline}  \label{eq:exp-log-chisq-proof}
     % &= \int_0^\infty f_W(x) \log x dx
     % \notag \\
-    &= \frac12 e^{- \tfrac\lambda2}
-    \int_0^\infty \sum_{n \geq 0} \biggl(
-        \tfrac{\bigl(\tfrac\lambda2\bigr)^n}{n!}
-        \tfrac{e^{- \tfrac{x}2}}{\Gamma(n + \tfrac{m}2)}
-        \bigl(\tfrac{x}2\bigr)^{n + \tfrac{m}2 - 1}
-    \biggr) \log{(x)} dx
+    % &\frac12 e^{- \tfrac\lambda2}
+    % \int_0^\infty \sum_{n \geq 0} \biggl(
+    %     \frac{
+    %       e^{- \tfrac{x}2} \bigl(\tfrac\lambda2\bigr)^n
+    %     }{
+    %       n! \Gamma(n + \tfrac{m}2)
+    %     }
+    %     \bigl(\tfrac{x}2\bigr)^{n + \tfrac{m}2 - 1}
+    % \biggr) \log{(x)} dx
     % = [\text{ absolute summability and Fubini, or any other conv. thm for integrals of non-negative integrals}]
@@
     % = [u = \tfrac{x}2]
-    \notag \\
-    &= e^{- \tfrac\lambda2} \sum_{n \geq 0}
-        \tfrac{\bigl(\tfrac\lambda2\bigr)^n}{n!}
-    \tfrac1{\Gamma(n + \tfrac{m}2)}
+    % \notag \\
+    e^{- \tfrac\lambda2} \sum_{n \geq 0}
+        \frac{\bigl(\tfrac\lambda2\bigr)^n}{
+          n! \Gamma(n + \tfrac{m}2)
+        }
     \int_0^\infty
         e^{- u} u^{n + \tfrac{m}2 - 1}
-        (\log2 + \log u) du
+        \log{(2 u)} du
     % = [\text{definitions:} \Gamma, \psi]
@@
     % (\psi(n + \tfrac{m}2) + \log2)
-    \notag \\
-    &= \log{2}
+    % \notag
+    \\
+    = \log{2}
     + e^{- \tfrac\lambda2} \sum_{n \geq 0}
-        \tfrac{\bigl(\tfrac\lambda2\bigr)^n}{n!}
+        \frac{\bigl(\tfrac\lambda2\bigr)^n}{n!}
         \psi(n + \tfrac{m}2)
     \,,
-\end{align}
+\end{multline}
 where $\psi(x)$ is the digamma function, i.e.
@@
   \psi(x)
-    = \frac{d}{dx} \log \Gamma(x)
+    % = \frac{d}{dx} \log \Gamma(x)
     = \frac1{\Gamma(x)}
@@
 $.
-
+%
 % We can differentiate the series in $g_m(x)$, since the sum converges on $\mathbb{R}$.
@@
 % power series.
-
-Differentiating the series within $g_m$ yields
+%
+Differentiating the power series within $g_m$ yields
 \begin{equation}  \label{eq:g-m-deriv}
@@
     % = e^{-x} \sum_{n\geq 0} \frac{x^n}{n!} \tfrac1{n + \tfrac{m}2}
-    = e^{-x} \sum_{n\geq 0} \frac{x^n}{n!} (n + \tfrac{m}2)^{-1}
-    \,.
-\end{equation}
-Since $
+    % = e^{-x} \sum_{n\geq 0} \frac{x^n}{n!} (n + \tfrac{m}2)^{-1}
+    = x^{-\tfrac{m}2} e^{-x} \sum_{n\geq 0}
+        \frac{x^{n + \tfrac{m}2}}{n!} (n + \tfrac{m}2)^{-1}
+    \,.
+\end{equation}
+From $
     e^t  = \sum_{n\geq 0} \tfrac{t^n}{n!}
-$ on $\mathbb{R}$, for $\alpha\neq 0$ we have
-% $
-%   \int_0^x t^{\alpha-1} dt
-%     = \tfrac{x^\alpha}{\alpha}
-% $ and
+$ on $\mathbb{R}$ and $
+  \tfrac{x^\alpha}{\alpha}
+    = \int_0^x t^{\alpha-1} dt
+$ for $\alpha\neq 0$ we get
 \begin{equation}  \label{eq:g-m-deriv-int-1}
@@
   \eqref{eq:g-m-deriv}
+    % = x^{-\tfrac{m}2} e^{-x} \sum_{n\geq 0}
+    %     \frac{x^{n + \tfrac{m}2}}{n!} (n + \tfrac{m}2)^{-1}
     = x^{-\tfrac{m}2} e^{-x} \sum_{n\geq 0}
-        \frac{x^{n + \tfrac{m}2}}{n!} (n + \tfrac{m}2)^{-1}
-    % = x^{-\tfrac{m}2} e^{-x} \sum_{n\geq 0}
-    %     \frac1{n!} \int_0^x t^{n + \tfrac{m}2 - 1} dt
+        \frac1{n!} \int_0^x t^{n + \tfrac{m}2 - 1} dt
     % = x^{-\tfrac{m}2} e^{-x}
@@
   f(z) = f(u + jv) = F(u, v)
-$. Within this framework the differential of $f$ at $z \in \cplx$ is
+$. Within this framework the differential of $f$ at $z = u + jv \in \cplx$ is
 $$
-df(z) \big\vert_{z=u + jv}
+df(z)
   = \frac{\partial f}{\partial z} dz

### 2019-11-12 paper/paper.tex
finished compressing the appendix on the derivative

@@
 % Gradient-based optimiziation of \eqref{eq:elbo} usually does not use the value of the objective. 
+% In stochastic gradient methods are concerned more with the gradient, induced by the objective
+% function, rather than its value.
 
@@
 $ for $\alpha\neq 0$ we get
-\begin{equation}  \label{eq:g-m-deriv-int-1}
-  \sum_{n\geq 0} \int_0^x \frac{t^{n+\alpha-1}}{n!} dt
-    % = \int_0^x \sum_{n\geq 0} \frac{t^{n+\alpha-1}}{n!} dt
-    = \int_0^x t^{\alpha-1} e^t dt
-    \,,
-  % the MCT ([0, x], \mathcal{B}([0, x]), dx)
-\end{equation}
-by the monotone convergence theorem, whence
+% by the monotone convergence theorem on ([0, x], \mathcal{B}([0, x]), dx)
 \begin{equation}  \label{eq:g-m-deriv-int-2}
@@
 \end{equation}
-The substitution $u^2 = t$ on $[0, \infty]$ with $2u du = dt$ yields
+Substitution $u^2 = t$ on $[0, \infty]$ with $2u du = dt$ yields
 \begin{equation}  \label{eq:g-m-deriv-int-3}
@@
 \end{equation}
-In particular, for $m=1$ we get
-\begin{equation}  \label{eq:g-m-series-one}
-  g_1(x)
-    = - \gamma - 2 \log{2}
-    + e^{-x} \sum_{n\geq 0} \frac{x^n}{n!} \sum_{p=1}^n \frac2{2p - 1}
-    \,,
-\end{equation}
-and the derivative \eqref{eq:g-m-deriv} can be computed thus
+In particular, the derivative of \eqref{eq:g-m-series} for $m=1$ is
 \begin{equation}  \label{eq:g-m-deriv-one}
   \frac{d}{d x} g_1(x)
-    = 2 \tfrac{F(\sqrt{x})}{\sqrt{x}}
+    = 2 \frac{F(\sqrt{x})}{\sqrt{x}}
     \,,
@@
 $ Dawson's integral (special function).
-
-The derivative of \eqref{eq:ard-kl-div-real} with respect to $\alpha$ is
+%
+Hence, the derivative of \eqref{eq:ard-kl-div-real} with respect to $\alpha$ is
 $$
-\tfrac{d}{d \alpha} g_1(\tfrac1{2\alpha})
-  = -\tfrac1{2 \alpha^2} g_1'(\tfrac1{2\alpha})
-  % = -\tfrac1{2 \alpha^2} 2 \tfrac{F(\sqrt{\tfrac1{2\alpha}})}{\sqrt{\tfrac1{2\alpha}}}
-  % = -\tfrac1{2 \alpha^2} 2 \tfrac{F(\tfrac1{\sqrt{2\alpha}})}{\tfrac1{\sqrt{2\alpha}}}
-  = -\tfrac1{\alpha} \sqrt{\tfrac2{\alpha}} F(\tfrac1{\sqrt{2\alpha}})
+\frac{d}{d \alpha} g_1(\tfrac1{2\alpha})
+  = -\frac1{2 \alpha^2} g_1'(\tfrac1{2\alpha})
+  % = -\frac1{2 \alpha^2} 2 \tfrac{F(\sqrt{\tfrac1{2\alpha}})}{\sqrt{\tfrac1{2\alpha}}}
+  % = -\frac1{2 \alpha^2} 2 \tfrac{F(\tfrac1{\sqrt{2\alpha}})}{\tfrac1{\sqrt{2\alpha}}}
+  = -\frac1{\alpha} \sqrt{\frac2{\alpha}} F(\tfrac1{\sqrt{2\alpha}})
   \,. $$
-Since $\alpha$ is nonnegative, it is typically parameterized via its logarithm and computed
-when needed. Thus the gradient of \eqref{eq:ard-kl-div-real} w.r.t $\log \alpha$ is
+Finally, since $\alpha$ is nonnegative, it is typically parameterized via its logarithm.
+The gradient of \eqref{eq:ard-kl-div-real} w.r.t $\log \alpha$ is
 \begin{equation}  \label{eq:real-kl-div-deriv-log}
@@
 
-We replicated the simulation experiment in \citep{molchanov_variational_2017} and recovered
-the same nonlinear approximation result reported therein. We sampled $10^7$ draws of  and 
-The coefficients are within $1\%$ relative tolerance of the reported.
-$$
+We compute the Monte-Carlo estimator of \eqref{eq:ard-kl-div-real} on a sample of $10^7$
+draws over an equally spaced grid of $\log \alpha$ in $[-12, +12]$ of size $4096$. The optimal
+coefficients of the regression, proposed by \citep{molchanov_variational_2017}, are within
+$1\%$ relative tolerance of the reported therein.
+\begin{equation}  \label{eq:ard-kl-div-real-approx}
   \eqref{eq:ard-kl-div-real}
@@
     % - k_1 \bigl(1 - \sigma(k_2 + k_3 \log \alpha)\bigr)
-  \,. $$
+  \,,
+\end{equation}
 % in parctial implementations we suggest using softplus to numerically comptue the last
 % term, since it is typically implemented in a floating-point stable fashion.
+The numerically estimated derivative of the penalty term wrt $\log \alpha$ using forward
+differences seems to be following \eqref{eq:real-kl-div-deriv-log} very closely (up to
+sampling error) see fig.~\ref{fig:molchanov-derivative-replica}. The derivative of
+\eqref{eq:ard-kl-div-real-approx} with respect to $\log \alpha$ appears to be very close
+to \eqref{eq:real-kl-div-deriv-log}.
 
@@
 \end{figure}
-
-Now in SGD (and specifically in SGVB) we are concerned more with the gradient field, induced
-by the potential (which is the loss function), rather than the value itself. Thus, as far as
-the regularizing penalty term is concerned, which is used to regularize the loss objective,
-we can essentially ignore it's forward pass value (level) and just compute its gradient
-(subgradient, normal cone) with respect the parameter of interest in sgd. (unless it is a
-part of a constraint, ie. downstream computation)
-
-The numerically estimated derivative of the penalty term wrt $\log \alpha$ using forward
-differences seems to be following \eqref{eq:real-kl-div-deriv-log} very closely (up to
-sampling error) see fig.~\ref{fig:molchanov-derivative-replica}.
 

### 2019-11-12 paper/paper.tex
split formula 32
compacting formulae
removed useless omega-argument in densities

@@
 identity for well-behaved densities:
-\begin{equation}  \label{eq:kl-div-master}
-  \log p(D)
+\begin{multline}  \label{eq:kl-div-master}
+  % \log p(D)
     % = \mathbb{E}_{q(\omega)} \log \frac{p(D, \omega)}{p(\omega \mid D)}
@@
     % + \mathbb{E}_{q(\omega)} \log \frac{q(\omega)}{p(\omega \mid D)}
+    % - \mathbb{E}_{q(\omega)} \log \frac{q(\omega)}{\pi(\omega)}
     % = \mathbb{E}_{q(\omega)} \log{p(D \mid \omega)}
-    % - \mathbb{E}_{q(\omega)} \log \frac{q(\omega)}{\pi(\omega)}
     % + \mathbb{E}_{q(\omega)} \log \frac{q(\omega)}{p(\omega \mid D)}
-    = \mathbb{E}_{q(\omega)} \log{p(D \mid \omega)}
-    - KL(q(\omega) \| \pi(\omega))
-    + KL(q(\omega) \| p(\omega \mid D))
-    \,.
-\end{equation}
+  \log p(D)
+    - KL(q \| p(\omega \mid D))
+    \\ = \mathbb{E}_{q(\omega)} \log{p(D \mid \omega)}
+    - KL(q \| \pi)
+    \,.
+\end{multline}
 This identity yields an equivalent problem for \eqref{eq:variational-progam}:
@@
 \begin{equation}  \label{eq:elbo_general}
-\begin{aligned}
-  & \underset{\theta, \phi, \lambda}{\text{maximize}}
-    & \mathcal{L}(\theta; \phi, \lambda)
-      & = \mathbb{E}_{\omega \sim q_{\theta}}
+  \mathcal{L}(\theta; \phi, \lambda)
+    = - KL(q_{\theta} \| \pi_{\lambda})
+      + \mathbb{E}_{\omega \sim q_{\theta}}
         \log p_{\phi}(D \mid \omega)
-        - KL(q_{\theta}(\omega) \| \pi_{\lambda}(\omega))
       % \mathbb{E}_{\omega \sim q_{\theta}}
         % \log\frac{q_\theta(\omega)}{\pi_{\lambda}(\omega)}
-  % \\
-  % & &
-  %     & = \mathbb{E}_{\omega \sim q_{\theta}}
+  % = \mathbb{E}_{\omega \sim q_{\theta}}
   %     \log{p_{\phi}(D \mid \omega) \pi_{\lambda}(\omega)}
@@
   \,,
-\end{aligned}
 \end{equation}
@@
   \widetilde{\mathcal{L}}(\theta; \phi, \lambda)
-    = - KL(q_{\theta}(\omega) \| \pi_{\lambda}(\omega))
+    = - KL(q_{\theta} \| \pi_{\lambda})
       % + \frac{N}{\lvert B \rvert} \sum_{i\in B}
@@
       + \frac1{L} \sum_{l=1}^L
-        \log p_{\phi}(D \mid \omega_{il})
-          \Big\vert_{\omega_{l} = g(\varepsilon_{l}; \theta)}
+        \log p_{\phi}(D \mid g(\varepsilon_{l}; \theta))
+        % \log p_{\phi}(D \mid \omega_{l})
+        %   \Big\vert_{\omega_{l} = g(\varepsilon_{l}; \theta)}
       % =
-      % - KL(q_{\theta}(\omega) \| \pi(\omega))
+      % - KL(q_{\theta} \| \pi)
       % + N \mathbb{E}_{B \sim \{D\}_M \otimes q_\theta^M}
@@
   \widetilde{\mathcal{L}}(\theta; \phi, \lambda)
-    = - KL(q_{\theta}(\omega) \| \pi_{\lambda}(\omega))
+    = - KL(q_{\theta} \| \pi_{\lambda})
       + \frac{N}{M} \sum_{i=1}^M
@@
 \begin{equation}  \label{eq:improper-kl-div-real}
-  KL(q_\theta(\omega) \| \pi(\omega))
+  KL(q_\theta \| \pi)
     \propto
@@
 \begin{equation}  \label{eq:ard-kl-div-real}
-  KL(q_\theta(\omega) \| \pi(\omega))
+  KL(q_\theta \| \pi)
     = \log{\bigl(1 + \tfrac1{\alpha} \bigr)}
@@
 \begin{equation}  \label{eq:elbo-general-kl-div}
-  KL(q(\omega) \| \pi(\omega))
+  KL(q \| \pi)
     % = \mathbb{E}_{\oemga \sim q(\oemga)} \log \tfrac{q(\oemga)}{\pi(\oemga)}
@@
 % by the monotone convergence theorem on ([0, x], \mathcal{B}([0, x]), dx)
-\begin{equation}  \label{eq:g-m-deriv-int-2}
+\begin{align}  \label{eq:g-m-deriv-int-2}
   \eqref{eq:g-m-deriv}
@@
     %     \frac{x^{n + \tfrac{m}2}}{n!} (n + \tfrac{m}2)^{-1}
-    = x^{-\tfrac{m}2} e^{-x} \sum_{n\geq 0}
+    &= x^{-\tfrac{m}2} e^{-x} \sum_{n\geq 0}
         \frac1{n!} \int_0^x t^{n + \tfrac{m}2 - 1} dt
@@
     %     \int_0^x t^{\tfrac{m}2 - 1} \sum_{n\geq 0} \frac{t^n}{n!} dt
-    = x^{-\tfrac{m}2} e^{-x}
+    \notag \\
+    &= x^{-\tfrac{m}2} e^{-x}
         \int_0^x t^{\tfrac{m}2 - 1} e^t dt
     \,.
-\end{equation}
+\end{align}
 Substitution $u^2 = t$ on $[0, \infty]$ with $2u du = dt$ yields

### 2019-11-12 paper/paper.tex
fixed formula overflows

@@
 $ is an iid sample from $p_\varepsilon$. Intractable KL-divergence terms can be replaced
-by differentiable unbiased Monte-Carlo estimators, \citep{kingma_auto-encoding_2014}.
+by differentiable unbiased sampling estimators, \citep{kingma_auto-encoding_2014}.
 %
@@
 
-In particular, linear layers
-$
-  L \colon \cplx^{\mathrm{[in]}}
-    \to \cplx^{\mathrm{[out]}}
+In particular, natural identification of $\cplx$ and $\real^2$ implies that linear layers $
+  L \colon \cplx^m \to \cplx^n
 $ act upon their inputs as follows:
 \begin{equation}  \label{eq:cplx-lin-op}
-  \real^{2 \times \mathrm{[in]}}
-    \to \real^{2 \times \mathrm{[out]}}
-    \colon (x_r, x_i)
+  {(\real^n)}^{2}
+    \to {(\real^m)}^{2}
+    \colon (u, v)
       \mapsto \Bigl(
-        L_r x_r - L_i x_i,
-        L_r x_i + L_i x_r
+        P u - Q v,
+        P v + Q u
       \Bigr)
@@
 where $
-  L_r, L_i
-    \colon \real^{\mathrm{[in]}}
-      \to \real^{\mathrm{[out]}}
-$ are unique operators that make up $L = L_r + j L_i$. A $\cplx$-convolutional layer with
-kernel $W$ can be implemented as two $\real$-convolutions with kernels $\Re{W}$ and $\Im{W}$
-using \eqref{eq:cplx-lin-op}. Algebraic operations, trigonometric functions, are implemented
+  P, Q \colon \real^{n} \to \real^{m}
+$ are unique operators such that $L = P + j Q$. A $\cplx$-convolutional layer with kernel
+$W$ can be implemented as two $\real$-convolutions with kernels $\Re{W}$ and $\Im{W}$ using
+\eqref{eq:cplx-lin-op}. Algebraic operations, trigonometric functions, are implemented
 through operations in $\real^2$. Activations, considered in \citep{trabelsi_deep_2017} include
@@
 \begin{equation}  \label{eq:cn-paired-real-density}
-  \begin{pmatrix}
+  \Bigl(
+    \begin{smallmatrix}
       \Re z \\ \Im z
-  \end{pmatrix}
+    \end{smallmatrix}
+  \Bigr)
     \sim \mathcal{N}_{2 m}\biggl(
-      \begin{pmatrix}
+      \Bigl(
+        \begin{smallmatrix}
           \Re \mu \\ \Im \mu
-      \end{pmatrix},
-      \frac12
-      \begin{pmatrix}
-        \Re{(\Gamma + C)} & - \Im{(\Gamma - C)} \\
+        \end{smallmatrix}
+      \Bigr),
+      \tfrac12 \Bigl(
+        \begin{smallmatrix}
+          \Re{(\Gamma + C)} & \Im{(C - \Gamma)} \\
           \Im{(\Gamma + C)} & \Re{(\Gamma - C)}
-      \end{pmatrix}
+        \end{smallmatrix}
+      \Bigr)
     \biggr)
@@
 %
-From \eqref{eq:cn-paired-real-density} the entropy of a $\cplx$-Gaussian in terms of
-$\Gamma$ and $C$ is
+The entropy of a $\cplx$-Gaussian in terms of $\Gamma$ and $C$ is
 \begin{align}  \label{eq:c-gauss-entropy-derivation}
@@
 \end{align}
-A $\cplx$-Gaussian vector $z$ is \textit{proper}, if $z$ and $\conj{z}$ are uncorrelated, i.e.
-$C = 0$. The entropy of proper $\cplx$-Gaussians is
+A $\cplx$-Gaussian vector $z$ is \textit{proper} if $z$ and $\conj{z}$ are uncorrelated, i.e.
+$C = 0$. The entropy of a proper $\cplx$-Gaussian is
 \begin{equation}  \label{eq:cn-proper-entropy}
@@
     = \log \bigl\lvert \det{(\pi e \Gamma)} \bigr\rvert
-    \tag{\ref{eq:c-gauss-entropy-derivation}'}\,.
+    \,.
+    \tag{\ref{eq:c-gauss-entropy-derivation}'}
 \end{equation}
@@
 
-In $\cplx$-variational dropout we use mean-field proper $\cplx$-Gaussian variational
-approximation. Specifically, parameters $W \in \cplx^{n\times m}$ of a dense layer follow
+In $\cplx$-variational dropout we use mean-field proper $\cplx$-Gaussian approximate
+posterior: for a dense linear layer parameters $W \in \cplx^{n\times m}$ follow
 \begin{equation}  \label{eq:c-gauss-vi}
@@
   W \sim q(W)
-    = \prod_{ij} q(W_{ij})
-  \,,\,
-    q(W_{ij})
-      = \mathcal{N}^{\cplx}(W_{ij} \mid \mu_{ij}, \sigma^2_{ij}, 0)
+    % = \prod_{ij} q(W_{ij})
+    = \prod_{ij} \mathcal{N}^{\cplx}(W_{ij} \mid \mu_{ij}, \sigma^2_{ij}, 0)
   \,,
 \end{equation}
-and we use similar factorized approximation for convolution. We propose to MAP estimates,
+and we use similar factorized approximation for convolutions. We propose to MAP estimates,
 of the biases i.e. assume an independent fully factorized Dirac approximation.

### 2019-11-12 paper/paper.tex
moved cplx-rep-trick derivation to appendix

@@
 We use the following notation: $M^{\top}$ is the matrix transpose, $\conj{M}$ is elementwise
-complex conjugation, and $M^{\hop} = (\conj{M})^\top$ denotes Hermitian conjugate. By $e_i$ we
-denote the $i$-th real unit vector of dimensionality \textit{conforming} to the matrix-vector
-expression it is used in. $\vec{M}$ denotes \textit{row-major} flattening of $M$ into a vector,
-i.e. in lexicographic order of its indices. $\diag{(\cdot)}$ embeds $\cplx^n$ into $n\times n$
-diagonal matrices. $\otimes$ denotes the Kronecker product, for which we note the following
-identities $
-  \vec{P Q R} = (P \otimes R^\top) \vec{Q}
-$, and $
-  (P \otimes R) (C \otimes S) = P Q \otimes R S
-$, \citep{petersen_matrix_2012}.
-% It follows from the definition of the Kronecker product
-% of $P$ and $R^\top$ and the row-major order vectorization.
+complex conjugation, and $M^{\hop} = (\conj{M})^\top$ denotes Hermitian conjugate.
 
@@
 
-In $\cplx$-variational dropout we use mean-field proper $\cplx$-Gaussian approximate
-posterior: for a dense linear layer parameters $W \in \cplx^{n\times m}$ follow
-\begin{equation}  \label{eq:c-gauss-vi}
-  % (we omit the subscript $m=1$ for brevity)
-  W \sim q(W)
-    % = \prod_{ij} q(W_{ij})
-    = \prod_{ij} \mathcal{N}^{\cplx}(W_{ij} \mid \mu_{ij}, \sigma^2_{ij}, 0)
-  \,,
-\end{equation}
-and we use similar factorized approximation for convolutions. We propose to MAP estimates,
-of the biases i.e. assume an independent fully factorized Dirac approximation.
-
 The local reparameterization trick provides both faster computations, and better statistical
-efficiency of the SGVB gradient estimator, \citep{wang_fast_2013,kingma_variational_2015}. A
-general mean field $\cplx$-Gaussian approximation \eqref{eq:c-gauss-vi} for $
-  W \in \cplx^{n\times m}
-$ is
+efficiency of the SGVB gradient estimator, \citep{wang_fast_2013,kingma_variational_2015}.
+We assume that weights $W \in \cplx^{n\times m}$ of a dense linear layer are drawn from a
+mean field $\cplx$-Gaussian approximate posterior
 \begin{equation}  \label{eq:c-gauss-vi-general}
-  \vec{W}
-    \sim \mathcal{N}^{\cplx}_{nm} \bigl(
-      \vec{\mu}, \diag{\vec{\Sigma}}, \diag{\vec{C}}
+  W_{ij}
+    \sim \mathcal{N}^{\cplx} \bigl(
+      \mu_{ij}, \Sigma_{ij}, C_{ij}
     \bigr)
@@
 \end{equation}
-where mean, \textit{variance} and relation are given by matrices $
+where mean, \textit{variance} and \textit{relation} are given by matrices $
   \mu, \Sigma, C \in \cplx^{n\times m}
-$ with $\Sigma_{ij} \geq 0$, and $
+$ with $\Sigma_{ij} \in \real$, and $
   \lvert C_{ij} \rvert^2 \leq \Sigma_{ij}
-$. For any $x \in \cplx^m$ and $b\in \cplx^n$ $
-  y = W x + b
-    = (I_n \otimes x^\top) \vec{W} + b
-$, whence the covariance and relation matrices of $y$ are
-\begin{align}
-  (I \otimes x^\top) \diag{\vec{\Sigma}} (I \otimes x^\top)^{\hop}
-    % = \sum_{ij} (I \otimes x^\top) e_i \otimes e_j
-    %   \Sigma_{ij} (e_i \otimes e_j)^\top (I \otimes x^\top)^{\hop}
-    % = \sum_{ij} (e_i \otimes x^\top e_j)
-    %   \Sigma_{ij} (e_i \otimes x^\top e_j)^{\hop}
-    % = \sum_{ij} (e_i \otimes x_j) \Sigma_{ij} (e_i^\top \otimes \conj{x}_j)
-    & = \sum_{i=1}^n (e_i e_i^\top) \sum_{j=1}^m \Sigma_{ij} x_j \conj{x}_j
-    \,,  \label{eq:cn-gauss-lrt-cov} \\
-  (I \otimes x^\top) \diag{\vec{C}} (I \otimes x^\top)^\top
-    % = \sum_{ij} (e_i \otimes x_j) C_{ij} (e_i \otimes x_j)^\top
-    & = \sum_{i=1}^n (e_i e_i^\top) \sum_{j=1}^m C_{ij} x_j^2
-    \,.  \label{eq:cn-gauss-lrt-rel}
-\end{align}
-Since \eqref{eq:cn-gauss-lrt-cov} and \eqref{eq:cn-gauss-lrt-rel} are diagnal, $(y_i)_{i=1}^n$
-are independent whence \eqref{eq:cn-affine} implies
+$. Property \eqref{eq:cn-affine} and independence of $W$ imply that for any $x \in \cplx^m$
+and $b \in \cplx^n$ the output $y = W x + b$ is distributed like
 \begin{equation}  \label{eq:cplx-gauss-trick}
@@
 \todo{other reasons for patch-independent weights}
+
+For $\cplx$-variational dropout we propose using mean-field proper $\cplx$-Gaussian approximate
+posterior, e.g. parameters $W \in \cplx^{n\times m}$ of a dense linear layer follow
+\begin{equation}  \label{eq:c-gauss-vi}
+  % (we omit the subscript $m=1$ for brevity)
+  W \sim q(W)
+    % = \prod_{ij} q(W_{ij})
+    = \prod_{ij} \mathcal{N}^{\cplx}(W_{ij} \mid \mu_{ij}, \sigma^2_{ij}, 0)
+  \,,
+\end{equation}
+and we use similar factorized approximation for convolutions. We propose to MAP estimates,
+of the biases i.e. assume an independent fully factorized Dirac approximation.
 
@@
 \label{sec:appendix}
+
+\subsection{Complex-valued local reparameterization} % (fold)
+\label{sub:complex_valued_local_reparameterization}
+
+%notation
+By $e_i$ we denote the $i$-th real unit vector of dimensionality \textit{conforming} to
+the matrix-vector expression it is used in. $\vec{M}$ denotes \textit{row-major} flattening
+of $M$ into a vector, i.e. in lexicographic order of its indices. $\diag{(\cdot)}$ embeds
+$\cplx^n$ into $n\times n$ diagonal matrices. $\otimes$ denotes the Kronecker product,
+for which we note the following identities $
+  \vec{P Q R} = (P \otimes R^\top) \vec{Q}
+$, and $
+  (P \otimes R) (C \otimes S) = P Q \otimes R S
+$, \citep{petersen_matrix_2012}.
+% It follows from the definition of the Kronecker product
+% of $P$ and $R^\top$ and the row-major order vectorization.
+
+If we assume a mean field $\cplx$-Gaussian approximate posteriror for $
+  W \in \cplx^{n\times m}
+$, then
+\begin{equation}  \label{eq:c-gauss-vi-general}
+  \vec{W}
+    \sim \mathcal{N}^{\cplx}_{nm} \bigl(
+      \vec{\mu}, \diag{\vec{\Sigma}}, \diag{\vec{C}}
+    \bigr)
+  \,,
+\end{equation}
+where mean, \textit{variance} and relation are given by matrices $
+  \mu, \Sigma, C \in \cplx^{n\times m}
+$ with $\Sigma_{ij} \geq 0$, and $
+  \lvert C_{ij} \rvert^2 \leq \Sigma_{ij}
+$. For any $x \in \cplx^m$ and $b\in \cplx^n$ $
+  y = W x + b
+    = (I_n \otimes x^\top) \vec{W} + b
+$, whence the covariance and relation matrices of $y$ are
+\begin{align}
+  (I \otimes x^\top) \diag{\vec{\Sigma}} (I \otimes x^\top)^{\hop}
+    % = \sum_{ij} (I \otimes x^\top) e_i \otimes e_j
+    %   \Sigma_{ij} (e_i \otimes e_j)^\top (I \otimes x^\top)^{\hop}
+    % = \sum_{ij} (e_i \otimes x^\top e_j)
+    %   \Sigma_{ij} (e_i \otimes x^\top e_j)^{\hop}
+    % = \sum_{ij} (e_i \otimes x_j) \Sigma_{ij} (e_i^\top \otimes \conj{x}_j)
+    & = \sum_{i=1}^n (e_i e_i^\top) \sum_{j=1}^m \Sigma_{ij} x_j \conj{x}_j
+    \,,  \label{eq:cn-gauss-lrt-cov} \\
+  (I \otimes x^\top) \diag{\vec{C}} (I \otimes x^\top)^\top
+    % = \sum_{ij} (e_i \otimes x_j) C_{ij} (e_i \otimes x_j)^\top
+    & = \sum_{i=1}^n (e_i e_i^\top) \sum_{j=1}^m C_{ij} x_j^2
+    \,.  \label{eq:cn-gauss-lrt-rel}
+\end{align}
+Since \eqref{eq:cn-gauss-lrt-cov} and \eqref{eq:cn-gauss-lrt-rel} are diagonal, $(y_i)_{i=1}^n$
+are independent whence \eqref{eq:cn-affine} implies
+\begin{equation}  \label{eq:cplx-gauss-trick}
+  y_i
+    \sim \mathcal{N}^{\cplx}
+      \bigl(
+        e_i^\top \mu x + b,
+        \, \sum_{j=1}^m \Sigma_{ij} \lvert x_j \rvert^2,
+        \, \sum_{j=1}^m C_{ij} x_j^2
+      \bigr)
+    \,.
+\end{equation}
+Hence \eqref{eq:cplx-gauss-trick} folows.
+
+% subsection complex_valued_local_reparameterization (end)
 

### 2019-11-12 paper/paper.tex
scattered edits

@@
 
-%notation
-We use the following notation: $M^{\top}$ is the matrix transpose, $\conj{M}$ is elementwise
-complex conjugation, and $M^{\hop} = (\conj{M})^\top$ denotes Hermitian conjugate.
-
 \subsection{Complex Gaussians and Local Reparameterization} % (fold)
@@
 
-A random vector $z\in \cplx^m$ has complex Gaussian distribution, $
-  z \sim q(z) = \mathcal{N}^{\cplx}_m(\mu, \Gamma, C)
-$, with mean $\mu \in \cplx^m$ and $\cplx^{m\times m}$ covariance and relation matrices
+%notation
+In the following $M^{\top}$ is the matrix transpose, $\conj{M}$ is elementwise complex
+conjugation, and $M^{\hop} = (\conj{M})^\top$ denotes Hermitian conjugate.
+
+A vector $z\in \cplx^m$ has complex Gaussian distribution, $
+  q(z) = \mathcal{N}^{\cplx}_m(\mu, \Gamma, C)
+$ with mean $\mu \in \cplx^m$ and $\cplx^{m\times m}$ covariance and relation matrices
 $\Gamma$ and $C$, respectively, if
 \begin{equation}  \label{eq:cn-paired-real-density}
-  \Bigl(
-    \begin{smallmatrix}
+  \begin{pmatrix}
     \Re z \\ \Im z
-    \end{smallmatrix}
-  \Bigr)
+  \end{pmatrix}
     \sim \mathcal{N}_{2 m}\biggl(
@@
 \end{equation}
-provided they satisfy $\Gamma \succeq 0$, $\Gamma^{\hop} = \Gamma$, $C^\top = C$, and $
+provided $\Gamma \succeq 0$, $\Gamma^{\hop} = \Gamma$, $C^\top = C$, and $
   \conj{\Gamma} \succeq C^{\hop} \Gamma^{-1} C
@@
 A $\cplx$-Gaussian vector $z$ is \textit{proper} if $z$ and $\conj{z}$ are uncorrelated, i.e.
-$C = 0$. The entropy of a proper $\cplx$-Gaussian is
+$C = 0$. From \eqref{eq:c-gauss-entropy-derivation} its entropy is
 \begin{equation}  \label{eq:cn-proper-entropy}
@@
 $. Property \eqref{eq:cn-affine} and independence of $W$ imply that for any $x \in \cplx^m$
-and $b \in \cplx^n$ the output $y = W x + b$ is distributed like
+and $b \in \cplx^n$ the components of $y = W x + b$ are independent with
 \begin{equation}  \label{eq:cplx-gauss-trick}
@@
     \sim \mathcal{N}^{\cplx}
-      \bigl(
-        e_i^\top \mu x + b,
+      \Bigl(
+        % e_i^\top \mu x + b_i,
+        b_i + \sum_{j=1}^m \mu_{ij} x_j,
         \, \sum_{j=1}^m \Sigma_{ij} \lvert x_j \rvert^2,
         \, \sum_{j=1}^m C_{ij} x_j^2
-      \bigr)
+      \Bigr)
     \,.
@@
 The trick requires three matrix operations: $\mu x + b$, $\Sigma \lvert x \rvert^2$ and
-$C x^2$ with the modulus and power applied elementwise. For a proper approximation
-\eqref{eq:c-gauss-vi} the relation coefficients are zero.
+$C x^2$ with the modulus and power applied elementwise.
 
 The trick and dropout can be applied to any layer, the output of which depends linearly
-on its parameters, e.g. convolutional layers, affine and bilinear transformations ($
-  y_j = x^\top W^{(j)} z + b_j
-$). Similar to $\real$ case, variational dropout for $\cplx$ convolutions draws independent
+on its parameters, e.g. convolutional layers, affine and bilinear transformations $
+  (x, z) \mapsto x^\top W^{(j)} z + b_j
+$. Similar to $\real$ case, variational dropout for $\cplx$ convolutions draws independent
 kernel $W$ for each spatial patch in the input, since a convolution is a matrix product
-of $W$, unrolled into a toeplitz matrix, and flattened intput $\vec{x}$. Weight sharing
-is essentially pushed to shared variational parameters $\theta$ in the approximation $q_\theta$.
+of $W$, unrolled into a toeplitz matrix, and flattened intput $x$. Weight sharing is
+essentially pushed to shared variational parameters $\theta$ in the approximation $q_\theta$.
 The rationale is to reduce correlation in the gradient estimator stemming from kernel weights
@@
 \todo{other reasons for patch-independent weights}
+
+% subsection c_gauss_and_local_rep (end)
+
+\subsection{The choice of priors and Kullback-Leibler divergence} % (fold)
+\label{sub:priors_and_kullback_leibler_divergence}
 
@@
     % = \prod_{ij} q(W_{ij})
-    = \prod_{ij} \mathcal{N}^{\cplx}(W_{ij} \mid \mu_{ij}, \sigma^2_{ij}, 0)
+    = \prod_{ij} \mathcal{N}^{\cplx}(
+      W_{ij} \mid
+        \mu_{ij},
+        \alpha_{ij} \lvert \mu_{ij} \rvert^2,
+        % \sigma^2_{ij},
+        0
+    )
   \,,
 \end{equation}
-and we use similar factorized approximation for convolutions. We propose to MAP estimates,
-of the biases i.e. assume an independent fully factorized Dirac approximation.
-
-% subsection c_gauss_and_local_rep (end)
-
-\subsection{The choice of priors and Kullback-Leibler divergence} % (fold)
-\label{sub:priors_and_kullback_leibler_divergence}
+and we use similar factorized approximation for convolutions. For this approximation the
+relation coefficients \eqref{eq:cplx-gauss-trick} are zero. We use MAP estimates of bias
+terms, i.e. assume an independent fully factorized Dirac approximation.
 
@@
     \sim \mathcal{N}^{\cplx}\bigl(
-      e_i^\top \mu x + b,
+      % e_i^\top \mu x + b,
+      b_i + \sum_{j=1}^m \mu_{ij} x_j,
       \, \sum_j \alpha_{ij} \lvert x_{ij} \mu_{ij}\rvert^2,
-      \, \sum_j \alpha_{ij} (x_{ij} \mu_{ij})^2,
-      \,
+      \, \sum_j \alpha_{ij} (x_{ij} \mu_{ij})^2
     \bigr)
@@
 %notation
-By $e_i$ we denote the $i$-th real unit vector of dimensionality \textit{conforming} to
-the matrix-vector expression it is used in. $\vec{M}$ denotes \textit{row-major} flattening
+By $e_i$ we denote the $i$-th real unit vector of dimensionality \textit{conforming} to the
+matrix-vector expression it is used in. Let $\vec{M}$ denote \textit{row-major} flattening
 of $M$ into a vector, i.e. in lexicographic order of its indices. $\diag{(\cdot)}$ embeds
-$\cplx^n$ into $n\times n$ diagonal matrices. $\otimes$ denotes the Kronecker product,
+$\cplx^n$ into $n\times n$ diagonal matrices, and $\otimes$ denotes the Kronecker product,
 for which we note the following identities $
@@
       \bigl(
-        e_i^\top \mu x + b,
+        e_i^\top \mu x + b_i,
         \, \sum_{j=1}^m \Sigma_{ij} \lvert x_j \rvert^2,

### 2019-11-14 fragments/gale-elsen-hooker.tex
State-of-sparsity summary

Deep networks achieve state-of-the-art performance on many practical tasks, including
image recognition \citep{citation_needed}, speech synthesis \citep{citation_needed},
automatic translation \citep{citation_needed}. Although performance tends to improve
with the model size, training and deploying large models becomes challenging. Several
aprroaches tackling this are being acitvely developed: model compression \citep{pruning},
distillation \citep{distill} and sparsification. The latter one essentially reduces
the numerical and storage complexity by zeroing as many parameters of the model as
possbile without significant performance loss. This has foremost importance in resource
constrained applications, such as embedded systems and mobile devices.

sparisity inducing methods impose structure on the topology of sparse weights
unstructured -- gives the achievable maximum of the compression-accuracy tradeoff, but
poses challenges in practical implementations (popr chace performance, almost as if
random access model).

Learnt Sparse topology can be trained from scratch to full performance (this is what
we use in train-compressed phase). reinitialization or continuation. But Gale et al.
faield to replicate successfull training from scratch (even for longer training), and
the results were worse than mag-prune. the likely reason is the complexity of the task
and scale of the models.

Sparsification techniques demonstrated deliver sota compression on small models / datasets,
perform inconsistently, and that simple heiristic approaches yield better results with less
computational costs. And provide strong counterexamples to reusability of the learnt sparse
topology.

% their paper
goal: apply sparsity inducing techniques to large-scale models and datasets
\citet{galehooker} raise an important issue that all sparsification techniques have been
propsed and tested on relatively small models, and skew towards convolutional architectures.
Sparsification is like architecture search: the space being the connectivity the computational
graph of the model. Evaluate smooth $\ell_0$ regularization \citep{louizos}, variational
dropout \citep{kingma2015} and magnitude pruning \citep{zhu-gupta2017} \ref{datasets}.

Show that var-dropout and $\ell_0$ demonstrate inconsistent performance on large-scale tasks
in contrast to magnitude pruning, i.e removing small weights $\ell_1$ hard thresholding.

($\ell_0$ regularization) explicitly penalizes the expected number of non-zero parameters
by using multiplicative noise drawn from hard-concrete distribution, that allows differentiating
through sampling.

(var-dropout) var inference over a fully factorized Gaussian posterior over the weights under
log-uniform prior. Local reparameterization to move noise from parameters to intermediate activations
and apply additive noise to further reduce the variance of the gradient. Verify the implementation
by reproducing the results of the original paper \citep{molchanovetal2017}.

(mag-pruning) reactivation of masked weights during training based on grads and sorting schedule.

(random pruning) does not permit reactivation, gives lower bound to sparsity-accuracy trade off.

% datasets and experiment setup
Constant number of training steps, extensive hyperparameter tuning

(random) Benchmark aginst random weight pruning

(resnet) ResNet-50 (He et al. 2016) on ImageNet. 128k iter x 1024 batch 
SGD w. mom; lr ramp-up 5ep. up 0.4, ÷ 10 every 30ep, see TF resnet-50
Sparsify conv and fc layers. Vardropout experimetns used batches of size 32 over 32 accel.

(xformer) Neural Machine Translation Transformer (Vasawi et al.2017) on WMT 2014 Eng-Ger dual corpus
standard procedire from (Vasawi et al.2017) without checkpoint averaging. Sparsify fc (attn) and
embedding layers.

% analysis
per layer sparsity and dependence on the hyperparameters: nonuniform sparsity is key to
high compression (He et al. 2018).

(xformer) More param in embedding, FFN an output of attn, less param in key-value of attn.

(resnet) unenven distribution of sparsity through the network

%% in my paper
We use the following three stage-process: train for better initial weights, sparsify
and then fine tune the sparsified model.

these are the techniques for cplx-sparsification. THey alllow this tradeoff on such and
such models.

### 2019-11-14 fragments/yang-ma-li.tex
cplx-transformer review

Speech recognition, signal processing, audio transcription all use FFT to get
spectral input, which is complex.

cplx-nets have rich represeantaiton

(lit-review)
attn and xfromer gained prominence in seq. modelling especially with long
temporal dependencies [10-13]

cplx-feed forward and cplx-lstm (with unitary matrix constraints) [see. 3-10]
cplx-conv and BN [18]
cplx-recurrent [5-7,9,10] merging FT and seq modelling [8]

(cplx)
natural representation of complex numbers as real pairs
emulate complex algebra and operations using paired reals

(attn)
Q, K, V = X W_Q, X W_K, X W_V
A = Q K^T V

use min-max attn instead of softmax (grad explosion !!)
are matrices W cplx?

% datasets
MusicNet : audio (signal) to symbols (labels), resampling 44khz to 11khz according to
[18], then real signal to cplx via FT

in-phase quadratic (private dataset): classify device by WIFI signal, resample to
balance devices.

### 2019-11-14 fragments/monning-manandhar.tex
capacity comparison of cplx nets summary

the paper studies capacity of simple complex networks
conclude that cplx nets perform not better than real-valued netowrks with similar capacity.
Observe synchronisation of real and imaginary parts in real valued tasks, but observe subpar
performance of cplx netowrks of equal capacity, sensetivity ot initialization. Isues due to 
singularities (poles) -- avoidable by constraining function value, normalizing weights or
gradients. Found that using relus is stabler and allows insight transfer from the vast literature
on real nets to complex domain. Recommend using cplx only if the data naturally or meaningfully
maps into cplx plane. and the net should reflect real-imag interaction

ensure comparability of architectures with respect to model size and capacity: doubling of
the number of parameters implies that one should keep the number of numerical parameters as
close as possible whn comparing real and complex nets. This ensures that performance differences
are due to use of cplx numbers rather than doubling of the number of parameters.
1) fixed number of real-valued parameters per layer
2) fixed budget of real-valued parameters per network

(lit-review) formally described in [8], complex versions of backpropagation in [6, 10, 19],
ides were even extended to quaternions [4, 3], complex valued RNN [5, 29] with unitary matrices
to tackle vanishing/exploding gradient problems. Complex convolutions [26], and complex attention
layers for complex-valeud transformer achitectures [ynag-ma-li]
Complex version of  batch-normalisation and weight initialization [26] (analogue of glorot xavier)

cplx-nets had limited popularity: less intuitive architecutres, increased numerical complexity (in
paired real -- instead of a single up to four multiplications are required, and two additions).
% due to them not being true cplx and just paired real computational graphs

(tasks) processing and analysis of compelx-valued data or data with intuitive mapping to
complex numbers. Images and signals in spectral representation. [15] show superiority of complex
nets to such tasks.

(datasets) MNIST; synthetic-1 (quadrant of the sum of cplx); synthetic-2 (same af synth-1 but for real)

(cplx) activation function can be C->C or C->R. cplx-differentiable -- exists limit in
C-field -- holomorhpic. Wirtinger CR calculus -- chosing a different basis of partial derivatives
CR improves statbility of the training process.

Activations: separate application to real and imaginary part, or more sophisticated, which uses
interaction between cplx and its conjugate, be it polar or paired representation. modReLU, hyperbolic
functions, complex modulus (absolute value), softmax based on squared modulus

simple doubling in insufficient: we also need to duplicate the parameters and enforce skew symmetric
constraint ([[re, -im], [im, re]])

complex-valued loss functions need a notion of ordering (what does it mean to minimize it,
how is it related to ERM and stat learning)

[03] Aizenberg (2007) Multilayer feedfroward network on multi-valued neurons and back prop
[04] Aizenberg (1992) Cnn based on muli-valeud neurons 
[05] Arjovsky, Shah (2015) Unitary evolution recurrent neural networks
[06] Benvenuto, Piazza (1992) complex backprop algorithm
[08] Clarke (1990) Generalization on neural networks to compelx plane
[10] Gergious Koutsougeras (1992) Complex domain backpropagation
[15] Hirose (2009) Cmoplex valued neural networks
[19] Nitta (1993) A back-propagation algorithm for compelx numbered neural networks
[26] Trabelsi (2017) Deep complex networks
[29] Wisdom Powers (2016) Full-capacity unitary recurrent neural networks

### 2019-11-14 fragments/gale-elsen-hooker.tex
typo fixes and references

@@
 with the model size, training and deploying large models becomes challenging. Several
-aprroaches tackling this are being acitvely developed: model compression \citep{pruning},
+aprroaches tackling this are being actively developed: model compression \citep{pruning},
 distillation \citep{distill} and sparsification. The latter one essentially reduces
@@
 unstructured -- gives the achievable maximum of the compression-accuracy tradeoff, but
-poses challenges in practical implementations (popr chace performance, almost as if
+poses challenges in practical implementations (poor cache performance, almost as if
 random access model).
@@
 we use in train-compressed phase). reinitialization or continuation. But Gale et al.
-faield to replicate successfull training from scratch (even for longer training), and
+failed to replicate successful training from scratch (even for longer training), and
 the results were worse than mag-prune. the likely reason is the complexity of the task
@@
 Sparsification techniques demonstrated deliver sota compression on small models / datasets,
-perform inconsistently, and that simple heiristic approaches yield better results with less
+perform inconsistently, and that simple heuristic approaches yield better results with less
 computational costs. And provide strong counterexamples to reusability of the learnt sparse
@@
 \citet{galehooker} raise an important issue that all sparsification techniques have been
-propsed and tested on relatively small models, and skew towards convolutional architectures.
+proposed and tested on relatively small models, and skew towards convolutional architectures.
 Sparsification is like architecture search: the space being the connectivity the computational
@@
 SGD w. mom; lr ramp-up 5ep. up 0.4, ÷ 10 every 30ep, see TF resnet-50
-Sparsify conv and fc layers. Vardropout experimetns used batches of size 32 over 32 accel.
+Sparsify conv and fc layers. Vardropout experiments used batches of size 32 over 32 accel.
 
 (xformer) Neural Machine Translation Transformer (Vasawi et al.2017) on WMT 2014 Eng-Ger dual corpus
-standard procedire from (Vasawi et al.2017) without checkpoint averaging. Sparsify fc (attn) and
+standard procedure from (Vasawi et al.2017) without checkpoint averaging. Sparsify fc (attn) and
 embedding layers.
@@
 
-(resnet) unenven distribution of sparsity through the network
+(resnet) uneven distribution of sparsity through the network
 
@@
 
-these are the techniques for cplx-sparsification. THey alllow this tradeoff on such and
+these are the techniques for cplx-sparsification. THey allow this trade-off on such and
 such models.

### 2019-11-14 fragments/monning-manandhar.tex
typo fixes and references

@@
 the paper studies capacity of simple complex networks
-conclude that cplx nets perform not better than real-valued netowrks with similar capacity.
+conclude that cplx nets perform not better than real-valued networks with similar capacity.
 Observe synchronisation of real and imaginary parts in real valued tasks, but observe subpar
-performance of cplx netowrks of equal capacity, sensetivity ot initialization. Isues due to 
+performance of cplx networks of equal capacity, sensitivity ot initialization. Isues due to 
 singularities (poles) -- avoidable by constraining function value, normalizing weights or
-gradients. Found that using relus is stabler and allows insight transfer from the vast literature
+gradients. Found that using ReLUs is stabler and allows insight transfer from the vast literature
 on real nets to complex domain. Recommend using cplx only if the data naturally or meaningfully
@@
 the number of parameters implies that one should keep the number of numerical parameters as
-close as possible whn comparing real and complex nets. This ensures that performance differences
+close as possible when comparing real and complex nets. This ensures that performance differences
 are due to use of cplx numbers rather than doubling of the number of parameters.
@@
 to tackle vanishing/exploding gradient problems. Complex convolutions [26], and complex attention
-layers for complex-valeud transformer achitectures [ynag-ma-li]
+layers for complex-valued transformer architectures [ynag-ma-li]
 Complex version of  batch-normalisation and weight initialization [26] (analogue of glorot xavier)
 
-cplx-nets had limited popularity: less intuitive architecutres, increased numerical complexity (in
+cplx-nets had limited popularity: less intuitive architectures, increased numerical complexity (in
 paired real -- instead of a single up to four multiplications are required, and two additions).
@@
 
-(tasks) processing and analysis of compelx-valued data or data with intuitive mapping to
+(tasks) processing and analysis of complex-valued data or data with intuitive mapping to
 complex numbers. Images and signals in spectral representation. [15] show superiority of complex
@@
 (cplx) activation function can be C->C or C->R. cplx-differentiable -- exists limit in
-C-field -- holomorhpic. Wirtinger CR calculus -- chosing a different basis of partial derivatives
-CR improves statbility of the training process.
+C-field -- holomorhpic. Wirtinger CR calculus -- choosing a different basis of partial derivatives
+CR improves stability of the training process.
 
@@
 [03] Aizenberg (2007) Multilayer feedfroward network on multi-valued neurons and back prop
-[04] Aizenberg (1992) Cnn based on muli-valeud neurons 
+[04] Aizenberg (1992) Cnn based on muli-valued neurons 
 [05] Arjovsky, Shah (2015) Unitary evolution recurrent neural networks
 [06] Benvenuto, Piazza (1992) complex backprop algorithm
-[08] Clarke (1990) Generalization on neural networks to compelx plane
+[08] Clarke (1990) Generalization on neural networks to complex plane
 [10] Gergious Koutsougeras (1992) Complex domain backpropagation
-[15] Hirose (2009) Cmoplex valued neural networks
-[19] Nitta (1993) A back-propagation algorithm for compelx numbered neural networks
+[15] Hirose (2009) Complex valued neural networks
+[19] Nitta (1993) A back-propagation algorithm for complex numbered neural networks
 [26] Trabelsi (2017) Deep complex networks

### 2019-11-14 fragments/yang-ma-li.tex
typo fixes and references

@@
 balance devices.
+
+[03] Hirose (2003) Cmoplex valued neural networks: theories and applications
+[04] Amin, Murase (2009) single layered complex-valued neural networks for real-valued classification problems
+[05] Arjovsky, Shah (2016) Unitary evolution recurrent neural networks
+[06] Danihelka, Wayne (2016) Associative Long short-term memory
+[07] Wolter, Yao (2018) Complex gatteed recurrent nural network
+[08] Wolter, Yao (2018) Fourier RNNs for sequence prediction
+[09] Hochreiter, Schmidhuber (1997) Long short-term memory
+[10] Cho, Merrienboer (2014) Learning phase representations using RNN encode-decoder for statistical machine translation
+[11] Bahndau, Cho (2014) Neural Machine translation by jointly learning to align and translate
+[12] Vaswani, Shazeer (2017) Attention is all you need
+[13] Yang, Dai (2019) Xlnet: generalized autoregressive pretraining for language understsding
+[18] Trabelsi (2017) Deep complex networks

### 2019-11-15 fragments/titsias-lazaro.tex
dsvi summary

Doubly Stochasticc Variational Bayes for no-conjugate Inference

continuous parameter space

(on bayes) probabilistic framework for inference that combines prior knowledge with observed
data in a principled manner. However apart from simple cases involving conjugate distributions
the Bayesian computations are intractable and approximations are used.

Such approximations are either Markov Chain Monte Carlo methods that sample from the unnormalized
posterior and need to converge or Bayesian variational inference (Jordan et al. 1999), that
cast the inference problem as optimization and finds the best approximation to the posterior
within some parametric family. MCMC samples well, but needs time to converge to the stationary
distribution and VI still has an expectation in the objective (ELBO).

Stochastic approximation (Robbins & Monroe, 1951)

a general (standard) parameter-free source noise distribution $\phi(\varesilon)$, which, coupled
with a parameterized diffeomorphism, induces the used variational posterior approximation.
Flexibility: from the diffeomorphism, from the structure of the standard parameter-free noise
(fully factorized with special univariate marginals for which exact simulation is possible).

Standard var bayes setting is to use KL-divergence (Jordan, 1999) between the var posterior
and the true posterior.

(DSVI) stochasticity from var. distribution and from dataset sub-sampling, internalized the
reparam. trick of (Kingma et al., 2013), and derived (expected wrt var distribution) gradients
for the parameters. Essentially a precursor to SGVB.

The goal is to keep the estimators of the gradients as unbiased as possible.

(lit-review) compare reinforcement trick (score function approach) and reparameterization trick
(path-wise differentiation). Reinf. has undesirable random walk behaviour due to the score
function and does not utilize info form the log-joint density. Can add control variates (depends
on var-param only) to stabilize the variance.

(tricks) TT/TR tensor format for compression (lossy), sampling (w. variance control), importance
weights (direct in expectations and indirect as in Metropolis Hastings), domain/range truncation
and monotone ct, dominated ct, martingale ct applications.

(ard) (Tippping, 2001) uses proper Gaussian prior allows efficiency since some part of the
expectation can be optimized analytically. The optimized kl-div encourages sparsity: shrinks
the var. mean to zero if the dimension is irrelevant.

### 2019-11-18 fragments/srivastava-et-al.tex
dropout and fast dropout summaries

(dropout)
prevents overfitting and provides a way to combine (probabilistically) exponentially
many models with shared weights during training, and a single network at test time.
Stochastic Grad descent accretes brittle co-adaptations that overfit: work well for training
data but fail to generalize. During training sample a thinned network by dropping out
units within each element of the minibatch by zeroing intermediate features. Injecting
noise severs these coadaptations by making features unreliable. On of the drawbacks
is increased training time, though.

(on denoising AE)
noise/ dropout can be injected into intermediate states which effectively accomplishes
a form of model averaging.

In dropout each models (through the distribution on masks) is weighted equally, whereas
in bayesian networks the prior distribution and the likelihood in model-space does the
weighting.

(trick)
constraining weights to within a norm-ball of fixed radius (with projection). This makes
it possible to use huge learning rates without blowup.

max-norm regularization, large decaying learning rates, and high momentum

(Gaussian dropout)
noted that $z\sim \mathcal{N}(1,1)$ works better than Bernoulli; Gaussian has the highest
entropy and Bernoulli -- the lowest.

(on TIMIT)
a benchmark for clean speech recognition

structure 120 dim/frame x 21 frames
train 1.1M frames, test 58K frames

windows of 21-log filter bank frames to predict the label of a central frame

(regression)
$$
\mathbb{E}_{z\sim {Ber}} \|y - (z\odot X) W\|^2
    % = \mathbb{E}_{z\sim {Ber}} \|y - p X W\|^2
    %     + \langel y - p X W, p X W - (z\odot X) W \rangle
    %     + \|p X W - (z\odot X) W\|^2
    = \|y - p X W\|^2
        % + \mathbb{E}_{z\sim {Ber}} \| ((z - p) \odot X) W \|^2
        % + \mathbb{E}_{z\sim {Ber}} \tr D_{z - p}^2 X W W^\top X^\top
        + p(1 - p) \|X W \|^2
    \,. $$

### 2019-11-18 fragments/wang-manning.tex
dropout and fast dropout summaries

(dropout)
dropout randomly zeroes hidden units during training. This prevents co-adaptiation and 
helps regularize by lowering the trust in a feature. It can be viewed as averaging many
netowrks with shared weights.

Propose fast dropout via Gaussian approximation and without sampling. The Gaussian
approximation is justified by the CLT. In addition they derive the gradient of the objective,
and approximate the integrals using logit-probit trick (MacKay; 1992). The shortcoming
of their method in more complicated gradient in the backprop.

(details)
Instead of sampling bernoulli masks for the MC estimate of the gradient, use gaussian
approximation of the outputs within the graident evaluation. They propose a special
gradient estimator that takes into account partial derivatives wrt $\mu$ and $\sigma^2$
of the approximation and uses finite difference approximations for changes in the latter
conditioned on the dropout rvs.

They note that $y_j = e_j^\top W D_z x$ is a weigheted sum of bernoulli rv's with a
unimodal or bounded distributed $x_i w_i$. Then they apply the CLT and argue that if
x-dim is large then $y_j \sim \matcal{N}(...)$  with mean  $e_j^\top W D_p x$ and
variance $\sum_i (W_{ji} x_i)^2 p_i(1 - p_i)$.

(closed form sigmoid approximation)
the Gaussain expected value of a logistic function via scaled probit. See (MacKay; 1992)
$\sigma(x)$ is close to a gaussian integral, i.e. $
  \sigma(x) \approx \Phi(\sqrt{\tfrac\pi8} x)
$ for $
  \phi(x) = \int_{-\infty}^x \tfrac1{\sqrt{2\pi}} e^{-\tfrac{t^2}2} dt
$, and then by fubini and differentiation under the integral, that
$$
\int \Phi(\lambda x) \mathcal{N}(x, \mu, \sigma^2) dx
    = \Phi\bigl(
        \tfrac\mu{\sqrt{\lambda^{-2} + \sigma^4}}
    \bigr)
    \,. $$

(augmetnation as noise) Transformation can be locally approximated by its Lie derivative
(Simard et al.; 1996) as a weighted matrix operationd (plus identity) with gaussian weights.
The authors argue thet the techniques they offer can be used to speed up this.

(other)
in dropout framework uncertainty comes form the dropout mask, in Bayesian models -- form
weight uncertainty.

Their analysis resembles derivation of the SGVB (DSVI): they differentialte the log-likeihood
loss.

Argue that using approximation makes it obvious that dropout approximates the ELBO for
approximate posteriors of the form $
  q(w) = \mathcal{N}(w\mid \mu, \alpha^\mu^2)
$.

### 2019-11-21 paper/paper.tex
some intro on dropout: used srivastava-et-al and wang-manning

@@
 
+% general intro text with motivation
 Deep neural networks are an integral part of machine learning and data science toolset
@@
 
-Bayesian Inference is a principled framework of reasoning about uncertainty. The core principle
-is updating prior beliefs in accordance with the likelihood of empirical observations into
-posterior belief. Under suitable modelling and prior assumptions, Bayesian methods can be
-used towards model sparsification, \citep{kingma_variational_2015,molchanov_variational_2017},
+% on dropout
+Dropout, \citep{hinton_improving_2012}, prevents overfitting by injecting multiplicative
+binary noise into layer's weights, thereby breaking up co-adaptations that could occur
+during training. \citet{wang_fast_2013} argue that the overall effect of binary dropout
+on the intermediate outputs via the Central Limit Theorem can be approximated by a Gaussian
+with weight-input dependent mean and variance. \citet{srivastava_dropout_2014} propse
+using independent $\mathcal{N}(1,1)$ noise, arguing that higher entroy of a Gaussian has
+better regularizing effect. In multitask learning \citet{cheung_superposition_2019}
+has shown the possiblity of storing task-specific parameters in non-destructive superposition
+within a single network. Their argument implies that if the single task setting is viewed
+as replicated mutlitask learning, then by sampling uncorrelated weight masks dropout acts
+as superposition method, which better utilizes the learnig capacity of the network.
+% many identical copies of the same task; \cite[Appendix A.1]{cheung_superposition_2019}
+
+% segue into bayesian inference
+Dropout resembles averaging models with shared parameters: each model is weighted equally
+since masks are randomly sampled, unlike bayesian model averaging, which weighs accoring to
+the posterior distribution. \citet{kingma_variational_2015} specifically consider dropout
+as a Bayesian inference technique. Bayesian Inference as a principled framework of reasoning
+about uncertainty, updates prior beliefs in accordance with the likelihood of empirical
+observations into posterior belief. Under suitable modelling and prior assumptions, Bayesian
+methods can be used towards model sparsification, \citep{kingma_variational_2015,molchanov_variational_2017},
 and \citep{kharitonov_variational_2018}.

### 2019-11-21 paper/paper.tex
somewhat improved introduction, still no cplx review tho

@@
 Deep neural networks are an integral part of machine learning and data science toolset
-for practical data-driven problem solving. Despite recent advances in generalization
+for practical data-driven problem solving. With continual miniaturization ever more
+applications can be found in embeded systems. Common embedded applications include
+on-device image recognition and signal processing. Despite recent advances in generalization
 and optimization theory specific to deep networks, deploying in actual embedded hardware
-remains a challenge. Solving the storage and compute constraints encourages development
-of model compression and sparsification methods, that focus on favourable tradeoff between
-performance and size. Most popular techniques include weight pruning \citep{citation_needed},
-model quantization from IEEE754 floating point to integer-based arithmetic \citep{citation_needed},
+remains a challenge due to storage, real-time throughput, and numerical computational
+compelexity restrictions.
+
+These applications establish a need for sparsification and model compression techniques.
+However audio or radio frequiency signal analysis is inherently complex-valued, yet
+$\cplx$-valued models and neural networks and, in particular, comprssion methods tailored
+to $\cplx$-networks remain a niche field of research. Although computational efficiency
+reduction methods such as quantization and integer-based arithmetic appear to be directly
+transferrable to $\cplx$-field, \citep{citation_needed}, the most promising methods,
+\citep{gale_state_2019} such as weight pruning \citep{zuo_compression_2019}, bayesian 
+dropout \citep{kingma_variational_2015}, and \citep{louizos_learning_2017} require
+additional considerations.
+
+% on sparsification
+Solving the storage and compute constraints encourages development of model compression
+and sparsification methods, that focus on favourable tradeoff between performance and size.
+%
+Most popular techniques include
+model quantization from IEEE754,
 and dropout. The key assumption is that the more explicitly zero parameters there is,
 the less computations is needed.
+
+\citet{monning_evaluation_2018} state,
+that $\cplx$-networks have less intuitive architectures, inherently higher numerical
+complexity due to multiplication in $\cplx$, that requires 3-4 floating point multiplications,
+dependening on the implementation.
+
+% due to them not being true cplx and just paired real computational graphs
 
@@
 and \citep{kharitonov_variational_2018}.
+
+% out contribution
+Inspired by variational sparsification techniques we develop bayesian dropout for $\cplx$-vlaued
+networks.
+
+\citep{yang_complex_2019,monning_evaluation_2018}
 
@@
 \todo{DSVI}
+\citep{titsias_doubly_2014}
 

### 2019-11-22 paper/paper.tex
intro: gale-et-al review, some motivation for cplx-vd

@@
 for practical data-driven problem solving. With continual miniaturization ever more
-applications can be found in embeded systems. Common embedded applications include
+applications can be found in embedded systems. Common embedded applications include
 on-device image recognition and signal processing. Despite recent advances in generalization
@@
 remains a challenge due to storage, real-time throughput, and numerical computational
-compelexity restrictions.
-
-These applications establish a need for sparsification and model compression techniques.
-However audio or radio frequiency signal analysis is inherently complex-valued, yet
-$\cplx$-valued models and neural networks and, in particular, comprssion methods tailored
-to $\cplx$-networks remain a niche field of research. Although computational efficiency
-reduction methods such as quantization and integer-based arithmetic appear to be directly
-transferrable to $\cplx$-field, \citep{citation_needed}, the most promising methods,
-\citep{gale_state_2019} such as weight pruning \citep{zuo_compression_2019}, bayesian 
-dropout \citep{kingma_variational_2015}, and \citep{louizos_learning_2017} require
-additional considerations.
+complexity restrictions. Therefore compression methods for achieving high model sparsity
+and numerical efficiency without losing much in performance are especially relevant.
+
+Signal processing, specifically, audio or radio frequency signal analysis is inherently
+complex-valued, yet $\cplx$-valued models and neural networks, and, in particular, compression
+methods tailored to $\cplx$-domain remain a niche field of research. Computational efficiency
+reduction methods such as quantization, integer-based arithmetic \citep{citation_needed},
+and distillation \citep{distillation} appear to be immediately applicable to $\cplx$-field.
+%
+Some model sparsification methods, e.g. magnitude pruning \citep{zuo_compression_2019}, which
+reactivates zeroed parameters based on gradients, and sparsity inducing regularizers, can be
+adapted directly to $\cplx$-valued models. Other methods -- require additional considerations.
+
+\citet{gale_state_2019} compare variational dropout \citep{kingma_variational_2015}, $\ell_0$
+regularization \citep{louizos_learning_2017} and magnitude pruning on large-scale models.
+Their results suggest that although var-dropout may achieve good accuracy-sparsity balance
+and outperform pruning on the studied architectures, overall pruning is preferable due to
+simplicity and speed. They also conclude that, although dropout and $\ell_0$ yield less
+consistent performance and are more complex, they induce non-uniform sparsity throughout
+the model, which is essential for better compression \verify{(He et al., 2018)}.
+%
+% Magnitude pruning induces user-specified sparsity distributions.
+%
+% L0 and dropout work in the low-to-mid sparsity range, variational dropout consistently
+% ranked behind L0 on Transformer, and was bested by magnitude pruning for sparsity
+% levels of 80\% and up. Variational dropout consistently produces models on-par or better
+% than magnitude pruning on ResNet-50, and l0 fails to produce sparse models at all.
+%
+Therefore it appears that Bayesian and stochastic sparsification techniques can be useful
+for models in $\cplx$ domain. \verify{$\ell_0$ -- stoch?}
 
@@
 model quantization from IEEE754,
-and dropout. The key assumption is that the more explicitly zero parameters there is,
+and dropout.
+
+The key assumption is that the more explicitly zero parameters there is,
 the less computations is needed.
@@
 on the intermediate outputs via the Central Limit Theorem can be approximated by a Gaussian
-with weight-input dependent mean and variance. \citet{srivastava_dropout_2014} propse
-using independent $\mathcal{N}(1,1)$ noise, arguing that higher entroy of a Gaussian has
+with weight-input dependent mean and variance. \citet{srivastava_dropout_2014} propose
+using independent $\mathcal{N}(1,1)$ noise, arguing that higher entropy of a Gaussian has
 better regularizing effect. In multitask learning \citet{cheung_superposition_2019}
-has shown the possiblity of storing task-specific parameters in non-destructive superposition
+has shown the possibility of storing task-specific parameters in non-destructive superposition
 within a single network. Their argument implies that if the single task setting is viewed
 as replicated mutlitask learning, then by sampling uncorrelated weight masks dropout acts
-as superposition method, which better utilizes the learnig capacity of the network.
+as superposition method, which better utilizes the learning capacity of the network.
 % many identical copies of the same task; \cite[Appendix A.1]{cheung_superposition_2019}
@@
 Dropout resembles averaging models with shared parameters: each model is weighted equally
-since masks are randomly sampled, unlike bayesian model averaging, which weighs accoring to
+since masks are randomly sampled, unlike bayesian model averaging, which weighs according to
 the posterior distribution. \citet{kingma_variational_2015} specifically consider dropout

### 2019-11-22 paper/paper.tex
reshuffle in the introduction

@@
 and numerical efficiency without losing much in performance are especially relevant.
+% Solving the storage and compute constraints encourages development of model compression
+% and sparsification methods, that focus on favourable tradeoff between performance and size.
 
@@
 reactivates zeroed parameters based on gradients, and sparsity inducing regularizers, can be
-adapted directly to $\cplx$-valued models. Other methods -- require additional considerations.
-
-\citet{gale_state_2019} compare variational dropout \citep{kingma_variational_2015}, $\ell_0$
-regularization \citep{louizos_learning_2017} and magnitude pruning on large-scale models.
-Their results suggest that although var-dropout may achieve good accuracy-sparsity balance
-and outperform pruning on the studied architectures, overall pruning is preferable due to
-simplicity and speed. They also conclude that, although dropout and $\ell_0$ yield less
-consistent performance and are more complex, they induce non-uniform sparsity throughout
-the model, which is essential for better compression \verify{(He et al., 2018)}.
-%
-% Magnitude pruning induces user-specified sparsity distributions.
-%
-% L0 and dropout work in the low-to-mid sparsity range, variational dropout consistently
-% ranked behind L0 on Transformer, and was bested by magnitude pruning for sparsity
-% levels of 80\% and up. Variational dropout consistently produces models on-par or better
-% than magnitude pruning on ResNet-50, and l0 fails to produce sparse models at all.
-%
-Therefore it appears that Bayesian and stochastic sparsification techniques can be useful
-for models in $\cplx$ domain. \verify{$\ell_0$ -- stoch?}
-
-% on sparsification
-Solving the storage and compute constraints encourages development of model compression
-and sparsification methods, that focus on favourable tradeoff between performance and size.
-%
-Most popular techniques include
-model quantization from IEEE754,
-and dropout.
-
-The key assumption is that the more explicitly zero parameters there is,
-the less computations is needed.
-
+adapted directly to $\cplx$-valued models. Other methods require additional considerations.
+% the more explicitly zero parameters there is, the less computations is needed.
+
+%%% >>>> (cplx)
+% complex nets and related stuff
+% cplx domain models
+% (cplx-transformer) yang-ma-li.tex
+% (cplx capacity) monning-manandhar.tex
 \citet{monning_evaluation_2018} state,
@@
 dependening on the implementation.
-
 % due to them not being true cplx and just paired real computational graphs
+
+\citep{yang_complex_2019,monning_evaluation_2018}
+
+data that is naturally complex-valued
+studies have shown a potentially richer representation of complex nets
+\citep{hirose2003,fijulamin2009}
+% [3] Akira Hirose, Complex-valued neural networks: theories and applications, vol. 5, World Scientific, 2003.
+% [4] Md Faijul Amin and Kazuyuki Murase, “Single-layered complex-valued neural network for real-valued classification problems,” Neurocomputing, vol. 72, no. 4-6, pp. 945–955, 2009.
+
+the complex version of backpropagation algorithm  was proposed because of
+its richer representational capacity.
+% Nevio Benvenuto and Francesco Piazza, “On the complex backpropagation algorithm,” IEEE Transactions on Signal Processing, vol. 40, no. 4, pp. 967–969, 1992.
+
+\citep{yang_complex_2019} develop complex transformer, with $\cplx$-attention and complex
+encoder-decoder, and apply it to music transcription and wireless signal classification.
+
+that interfaces the rest of
+$\cplx$-valued
+the network with complex numbers
+
+that operates on the Fourier transform input speech, acoustic, of radio signals.
+
+papers related to complex-valued distributions \citep{pav_moments_2015,taubock_complex-valued_2012},
+and \citep{karseras_caution:_2014}
+
+Application of complex-valued networks is not new, \citep{citation_needed}. More recently
+they were applied to music transcription and speech recognition \citep{trabelsi_deep_2017},
+and \citep{yang_complex_2019}. The key motivation behind adoption of $\cplx$-networks is
+pervasiveness of $\cplx$-valued data in digital signal processing \citep{citation_needed},
+acoustic and radio signal analysis \citep{citation_needed}, and quantum systems modelling
+\citep{citation_needed}, etc. All these applications require compliance with algebraic
+operations in the field of complex numbers.
+%%% <<<< (cplx)
 
@@
 % many identical copies of the same task; \cite[Appendix A.1]{cheung_superposition_2019}
+% (fast dropout gauss-approx) wang-manning.tex
+% (gauss dropout) srivastava-et-al.tex
 
@@
 
-% out contribution
-Inspired by variational sparsification techniques we develop bayesian dropout for $\cplx$-vlaued
+% (sparsity tech large-scale models) gale-elsen-hooker.tex
+\citet{gale_state_2019} compare variational dropout \citep{kingma_variational_2015}, $\ell_0$
+regularization \citep{louizos_learning_2017} and magnitude pruning on large-scale models.
+Their results suggest that although var-dropout may achieve good accuracy-sparsity balance
+and outperform pruning on the studied architectures, overall pruning is preferable due to
+simplicity and speed. They also conclude that, although dropout and $\ell_0$ yield less
+consistent performance and are more complex, they induce non-uniform sparsity throughout
+the model, which is essential for better compression \verify{(He et al., 2018)}.
+%
+% Magnitude pruning induces user-specified sparsity distributions.
+%
+% L0 and dropout work in the low-to-mid sparsity range, variational dropout consistently
+% ranked behind L0 on Transformer, and was bested by magnitude pruning for sparsity
+% levels of 80\% and up. Variational dropout consistently produces models on-par or better
+% than magnitude pruning on ResNet-50, and l0 fails to produce sparse models at all.
+%
+Therefore it appears that Bayesian and stochastic sparsification techniques can be useful
+for models in $\cplx$ domain. \verify{$\ell_0$ -- stoch?}
+
+% our contribution
+Inspired by variational sparsification we develop bayesian dropout for $\cplx$-valued
 networks.
-
-\citep{yang_complex_2019,monning_evaluation_2018}
-
-% complex nets and related stuff
-data that is naturally complex-valued
-studies have shown a potentially richer representation of complex nets
-\citep{hirose2003,fijulamin2009}
-% [3] Akira Hirose, Complex-valued neural networks: theories and applications, vol. 5, World Scientific, 2003.
-% [4] Md Faijul Amin and Kazuyuki Murase, “Single-layered complex-valued neural network for real-valued classification problems,” Neurocomputing, vol. 72, no. 4-6, pp. 945–955, 2009.
-
-the complex version of backpropagation algorithm  was proposed because of
-its richer representational capacity.
-% Nevio Benvenuto and Francesco Piazza, “On the complex backpropagation algorithm,” IEEE Transactions on Signal Processing, vol. 40, no. 4, pp. 967–969, 1992.
-
-\citep{yang_complex_2019} develop complex transformer, with $\cplx$-attention and complex
-encoder-decoder, and apply it to music transcription and wireless signal classification.
-
-that interfaces the rest of
-$\cplx$-valued
-the network with complex numbers
-
-that operates on the Fourier transform input speech, acoustic, of radio signals.
-
-papers related to complex-valued distributions \citep{pav_moments_2015,taubock_complex-valued_2012},
-and \citep{karseras_caution:_2014}
-
-Application of complex-valued networks is not new, \citep{citation_needed}. More recently
-they were applied to music transcription and speech recognition \citep{trabelsi_deep_2017},
-and \citep{yang_complex_2019}. The key motivation behind adoption of $\cplx$-networks is
-pervasiveness of $\cplx$-valued data in digital signal processing \citep{citation_needed},
-acoustic and radio signal analysis \citep{citation_needed}, and quantum systems modelling
-\citep{citation_needed}, etc. All these applications require compliance with algebraic
-operations in the field of complex numbers.
 
@@
 %
+% (DSVI) titsias-lazaro.tex
 \todo{DSVI}

### 2019-11-22 paper/paper.tex
He et al. 2018 reference

@@
 consistent performance and are more complex, they induce non-uniform sparsity throughout
-the model, which is essential for better compression \verify{(He et al., 2018)}.
+the model, which is essential for better compression \citep{he_amc:_2018}.
+\todo{read (He et al., 2018)}
 %

### 2019-11-22 paper/paper.tex
proper citation in the intro

@@
 remains a challenge due to storage, real-time throughput, and numerical computational
-complexity restrictions. Therefore compression methods for achieving high model sparsity
-and numerical efficiency without losing much in performance are especially relevant.
+complexity restrictions \citep{he_amc:_2018}. Therefore compression methods for achieving
+high model sparsity and numerical efficiency without losing much in performance are
+especially relevant.
 % Solving the storage and compute constraints encourages development of model compression

### 2019-11-25 notebooks/utils/musicnet.py
switched label lookup to Nested Containment List

@@ -10,6 +10,7 @@ import torch.utils.data
 
 # from functools import lru_cache
 
+from ncls import NCLS64
 from intervaltree import IntervalTree
 from resampy import resample
 
@@ -66,31 +67,30 @@ class MuscNetHDF5(torch.utils.data.Dataset):
 
         # build data lookup and label tree (O(n log n))
         self.intervals, self.labels, self.total = IntervalTree(), {}, 0
-        for key, group in tqdm.tqdm(hdf5.items(), desc="building lookup",
-                                    disable=not verbose):
+        for key, group in tqdm.tqdm(hdf5.items(), disable=not verbose,
+                                    desc="building lookup"):
             obj, lab = group["data"], group["labels"]
 
             # cache hdf5 group objects (stores references to hdf5 objects!)
             strided_size = ((len(obj) - window + 1) + stride - 1) // stride
             self.intervals[self.total:self.total + strided_size] = key, obj
-
             self.total += strided_size
 
             # collect notes
             note_ids.update(lab["note_id"])
 
-            # expensive construction (rebuilding is faster than pickling)
-            tree = IntervalTree.from_tuples(lab["start_time", "end_time", "note_id"])
-
-            # all covering empty-class
-            tree.addi(0, len(obj), None)  # (float("-inf"), float("+inf"), None)
-            self.labels[key] = tree
+            # construct a fast lookup of music notes: a Nested Containment List
+            #  is much faster than Interval Tree.
+            self.labels[key] = NCLS64(
+                np.array(lab["start_time"], dtype=np.int64),  # start
+                np.array(lab["end_time"], dtype=np.int64),    # end
+                np.array(lab["note_id"], dtype=np.int64))     # payload id
 
         # preallocate `note_id` one-hots
-        n_classes = max(note_ids) - min(note_ids) + 1
-        self.onehots = {None: np.zeros((1, n_classes))}
+        self.onehots, self.n_classes = {}, max(note_ids) - min(note_ids) + 1
+        eye = np.eye(self.n_classes, dtype=np.float32)
         for j, note in enumerate(sorted(note_ids)):
-            self.onehots[note] = np.eye(1, n_classes, k=j, dtype=np.float32)
+            self.onehots[note] = eye[j]
 
         self.hdf5, self.window, self.stride = hdf5, window, stride
 
@@ -105,10 +105,12 @@ class MuscNetHDF5(torch.utils.data.Dataset):
         key, obj = interval.data
[…]

### 2019-11-25 notebooks/utils/__init__.py
fixed class name, NCL for waveform as well

@@ -1,1 +1,1 @@
-from .musicnet import MuscNetHDF5
+from .musicnet import MusicNetHDF5

### 2019-11-25 notebooks/utils/musicnet.py

@@ -43,7 +43,7 @@ def resample_h5(file_in, file_out, frame_rate_in, frame_rate_out):
     return file_out
 
 
-class MuscNetHDF5(torch.utils.data.Dataset):
+class MusicNetHDF5(torch.utils.data.Dataset):
     """Dataset access to MusicNet sotred in HDF5 file.
 
     Parameters
@@ -65,26 +65,33 @@ class MuscNetHDF5(torch.utils.data.Dataset):
         # has to get note_ids from somewhere
         note_ids = set()  # OVERRIDE!
 
-        # build data lookup and label tree (O(n log n))
-        self.intervals, self.labels, self.total = IntervalTree(), {}, 0
-        for key, group in tqdm.tqdm(hdf5.items(), disable=not verbose,
-                                    desc="building lookup"):
-            obj, lab = group["data"], group["labels"]
-
-            # cache hdf5 group objects (stores references to hdf5 objects!)
-            strided_size = ((len(obj) - window + 1) + stride - 1) // stride
-            self.intervals[self.total:self.total + strided_size] = key, obj
-            self.total += strided_size
+        # build object and label lookup
+        intervals, n_samples = [], 0
+        groups = tqdm.tqdm(hdf5.items(), disable=not verbose,
+                           desc="building lookup")
+        for ix, (key, group) in enumerate(groups):
+            obj, label = group["data"], group["labels"]
 
             # collect notes
-            note_ids.update(lab["note_id"])
+            note_ids.update(label["note_id"])
 
-            # construct a fast lookup of music notes: a Nested Containment List
-            #  is much faster than Interval Tree.
-            self.labels[key] = NCLS64(
-                np.array(lab["start_time"], dtype=np.int64),  # start
-                np.array(lab["end_time"], dtype=np.int64),    # end
-                np.array(lab["note_id"], dtype=np.int64))     # payload id
+            # construct a fast lookup of music notes: a Nested
+            #  Containment List is much faster than Interval Tree.
+            tree = NCLS64(np.int64(label["start_time"]),  # start
+                          np.int64(label["end_time"]),    # end
+                          np.int64(label["note_id"]))     # payload
+
+            # cache hdf5 objects (stores references to hdf5 objects!)
+            strided_size = ((len(obj) - window + 1) + stride - 1) // stride
+            intervals.append((n_samples, n_samples + strided_size, obj, tree))
+
+            n_samples += strided_size
+
+        # build the object lookup
[…]

### 2019-11-25 notebooks/utils/musicnet.py
default fp32, removed unused imports, boolean target

@@ -8,10 +8,7 @@ import numpy as np
 import torch
 import torch.utils.data
 
-# from functools import lru_cache
-
 from ncls import NCLS64
-from intervaltree import IntervalTree
 from resampy import resample
 
 
@@ -58,7 +55,7 @@ class MusicNetHDF5(torch.utils.data.Dataset):
     stride : int, default=1
         The stride of the sliding window.
     """
-    def __init__(self, hdf5, window=4096, stride=512, verbose=False):
+    def __init__(self, hdf5, window=4096, stride=512):
         # ensure an open HDF5 handle
         assert isinstance(hdf5, h5py.File) and hdf5.id
 
@@ -67,9 +64,7 @@ class MusicNetHDF5(torch.utils.data.Dataset):
 
         # build object and label lookup
         intervals, n_samples = [], 0
-        groups = tqdm.tqdm(hdf5.items(), disable=not verbose,
-                           desc="building lookup")
-        for ix, (key, group) in enumerate(groups):
+        for ix, (key, group) in enumerate(hdf5.items()):
             obj, label = group["data"], group["labels"]
 
             # collect notes
@@ -95,7 +90,7 @@ class MusicNetHDF5(torch.utils.data.Dataset):
 
         # preallocate `note_id` one-hots
         self.onehots, self.n_classes = {}, max(note_ids) - min(note_ids) + 1
-        eye = np.eye(self.n_classes, dtype=np.float32)
+        eye = np.eye(self.n_classes, dtype=np.bool)
         for j, note in enumerate(sorted(note_ids)):
             self.onehots[note] = eye[j]
 
@@ -112,14 +107,14 @@ class MusicNetHDF5(torch.utils.data.Dataset):
 
         # fetch data and construct labels: random access is slow
         obj, lab = self.objects[key], self.labels[key]
-        data = obj[ix:ix + self.window]
+        data = obj[ix:ix + self.window].astype(np.float32)
 
         midp = ix + self.window // 2
         labels = lab.find_overlap(midp, midp + 1)
         onehot = sum((self.onehots[note_id] for a, b, note_id in labels),
-                     np.zeros(self.n_classes, dtype=np.float32))
+                     np.zeros(self.n_classes, dtype=np.bool))
 
-        return data, onehot
+        return data, onehot.astype(np.int32)
 
     def __len__(self):
         return self.n_samples

### 2019-11-25 notebooks/utils/musicnet.py
train-valid-test split for musicnet, key choice in resample

@@ -12,7 +12,7 @@ from ncls import NCLS64
 from resampy import resample
 
 
-def resample_h5(file_in, file_out, frame_rate_in, frame_rate_out):
+def resample_h5(file_in, file_out, frame_rate_in, frame_rate_out, keys=None):
     # Authors: Dmitriy Serdyuk
     # (2019-11-24) changed to hdf5 supports
     print(f""".. resampling {file_in} ({frame_rate_in}Hz) """
@@ -24,7 +24,11 @@ def resample_h5(file_in, file_out, frame_rate_in, frame_rate_out):
         ratio = frame_rate_out / float(frame_rate_in)
 
         # pour from h5_in to h5_out
-        for key, group in tqdm.tqdm(h5_in.items()):
+        items = h5_in.items()
+        if keys is not None:
+            items = [(k, h5_in[k]) for k in keys]
+
+        for key, group in tqdm.tqdm(items):
 
             # resample the waveform
             data = resample(np.array(group["data"]),

### 2019-11-26 notebooks/utils/musicnet.py
fixed note labelling

@@ -58,23 +58,18 @@ class MusicNetHDF5(torch.utils.data.Dataset):
     def __init__(self, hdf5, window=4096, stride=512):
         # ensure an open HDF5 handle
         assert isinstance(hdf5, h5py.File) and hdf5.id
-
-        # has to get note_ids from somewhere
-        note_ids = set()  # OVERRIDE!
+        # assumes note_ids 21..105, i.e. 84 class labels
 
         # build object and label lookup
         intervals, n_samples = [], 0
         for ix, (key, group) in enumerate(hdf5.items()):
             obj, label = group["data"], group["labels"]
 
-            # collect notes
-            note_ids.update(label["note_id"])
-
             # construct a fast lookup of music notes: a Nested
             #  Containment List is much faster than Interval Tree.
-            tree = NCLS64(np.int64(label["start_time"]),  # start
-                          np.int64(label["end_time"]),    # end
-                          np.int64(label["note_id"]))     # payload
+            tree = NCLS64(np.int64(label["start_time"]),    # start
+                          np.int64(label["end_time"]),      # end
+                          np.int64(label["note_id"] - 21))  # note - 21 (base)
 
             # cache hdf5 objects (stores references to hdf5 objects!)
             strided_size = ((len(obj) - window + 1) + stride - 1) // stride
@@ -88,21 +83,15 @@ class MusicNetHDF5(torch.utils.data.Dataset):
                                 np.int64(np.r_[:len(self.objects)]))
         self.n_samples = n_samples
 
-        # preallocate `note_id` one-hots
-        self.onehots, self.n_classes = {}, max(note_ids) - min(note_ids) + 1
-        eye = np.eye(self.n_classes, dtype=np.bool)
-        for j, note in enumerate(sorted(note_ids)):
-            self.onehots[note] = eye[j]
-
         self.hdf5, self.window, self.stride = hdf5, window, stride
 
     def __getitem__(self, index):
         index = self.n_samples + index if index < 0 else index
-        intervals = self.intervals.find_overlap(index, index + 1)
-        if not intervals:
+        interval = next(self.intervals.find_overlap(index, index + 1), None)
+        if interval is None:
             raise KeyError
 
-        beg, end, key = next(intervals)
+        beg, _, key = interval
         ix = (index - beg) * self.stride
 
         # fetch data and construct labels: random access is slow
[…]

### 2019-11-26 experiments/musicnet/__init__.py
path fixes

@@ -1,1 +1,1 @@
-from .musicnet import MusicNetHDF5
+from .dataset import MusicNetHDF5

### 2019-11-26 experiments/musicnet/models/trabelsi2019.py
models from (Trabelsi et al., 2019)

@@ -1,0 +1,108 @@
+"""Reimplementation of model used by Trabelsi et al. (2019)
+"""
+import torch
+
+from collections import OrderedDict
+from torch.nn import init
+
+
+def reset_bias(mod):
+    if hasattr(mod, "bias"):
+        init.constant_(mod.bias, -5)
+
+
+class Flatten(torch.nn.Module):
+    def __init__(self, start_dim=0, end_dim=-1):
+        super().__init__()
+        self.start_dim, self.end_dim = start_dim, end_dim
+
+    def forward(self, input):
+        return input.flatten(self.start_dim, self.end_dim)
+
+
+class BodyMixin(torch.nn.Module):
+    def forward(self, input):
+        # just delegate to self.body
+        return self.body(input)
+
+
+class TwoLayerDense(BodyMixin, torch.nn.Module):
+    Linear = torch.nn.Linear
+
+    def __init__(self, n_seq=4096, n_channels=2, n_outputs=84):
+        super().__init__()
+        # assume zero-th batch dimension
+        self.body = torch.nn.Sequential(OrderedDict([
+            ("flatten", Flatten(1, -1)),
+            ("dense00", self.Linear(n_seq * n_channels, 2048)),
+            ("activ01", torch.nn.ReLU()),
+            ("dense01", self.Linear(2048, n_outputs)),
+            # do not use sigmoids: outputs are fed into BCEwithLogits
+        ]))
+
+        reset_bias(self.body[-1])
+
+
+class ShallowConvNet(BodyMixin, torch.nn.Module):
+    Linear = torch.nn.Linear
+    Conv1d = torch.nn.Conv1d
+
+    def __init__(self, n_seq=4096, n_channels=2, n_outputs=84):
+        super().__init__()
+        # keras's dynamic input dependent construction is neat.
+
+        n_seq = (n_seq - 512 + 1 + 16 - 1) // 16  # tailored to `cnv1d00`
+        n_seq = (n_seq -   4 + 1 +  2 - 1) //  2  # tailored to `max1d01`
+        self.body = torch.nn.Sequential(OrderedDict([
+            ("cnv1d00", self.Conv1d(n_channels, 64, 512, stride=16)),
+            ("activ01", torch.nn.ReLU()),
+            ("max1d01", torch.nn.MaxPool1d(4, stride=2)),
+            ("flatten", Flatten(1, -1)),
+            ("dense02", self.Linear(n_seq * 64, 2048)),
[…]

### 2019-11-26 experiments/musicnet/models/trabelsi2019.py
n_channels fix

@@ -93,7 +93,8 @@ class DeepConvNet(BodyMixin, torch.nn.Module):
                 n_seq = (n_seq - 2 + 1 + 2 - 1) // 2
 
         self.body = torch.nn.Sequential(OrderedDict([
-            ("block00", self.one_block(  2,  64, n_ker[0], n_str[0],  True)),
+            ("block00", self.one_block(
+                                n_channels,  64, n_ker[0], n_str[0],  True)),
             ("block01", self.one_block( 64,  64, n_ker[1], n_str[1],  True)),
             ("block02", self.one_block( 64, 128, n_ker[2], n_str[2],  True)),
             ("block03", self.one_block(128, 128, n_ker[3], n_str[3],  True)),

### 2019-12-01 experiments/auto/auto.py
minor cleanup

@@ -1,7 +1,5 @@
 import os
 import copy
-import time
-import gzip
 import tqdm
 import math
 import json
@@ -11,39 +9,15 @@ import numpy as np
 
 from setuptools._vendor.packaging.version import Version
 
-from .delayed import DelayedKeyboardInterrupt
-from .utils import get_instance
 
-
-__version__ = "0.1s"
-
-
-def save_snapshot(filename, **kwargs):
-    with gzip.open(filename, "wb", compresslevel=5) as fout:
-        torch.save(dict(kwargs, **{
-            "__version__": __version__,
-            "__timestamp__": time.strftime("%Y%m%d-%H%M%S"),
-        }), fout, pickle_protocol=3)
-
-    return filename
-
-
-def get_optimizer(parameters, *, lr, **options):
-    return get_instance(parameters, lr=lr, **options)
-
-
-def get_scheduler(optimizer, **options):
-    return get_instance(optimizer, **options)
-
-
-def get_criterion(**options):
-    return get_instance(**options)
+__version__ = "0.1"
 
 
 def fit(model, objective, feed, optim, sched=None, n_epochs=100,
         grad_clip=0., verbose=True):
     from torch.optim.lr_scheduler import ReduceLROnPlateau
     from torch.nn.utils import clip_grad_norm_
+    from .delayed import DelayedKeyboardInterrupt
 
     history, abort = [], False
     with tqdm.tqdm(range(n_epochs), disable=not verbose) as bar, \

### 2019-12-01 experiments/auto/utils.py

@@ -6,34 +6,33 @@ import torch
 import importlib
 
 
-def recipe_param(recipe, **defaults):
-    param = {}
-    if recipe and isinstance(recipe[-1], dict):
-        *recipe, param = recipe
+def save_snapshot(filename, **kwargs):
+    with gzip.open(filename, "wb", compresslevel=5) as fout:
+        torch.save(dict(kwargs, **{
+            "__timestamp__": time.strftime("%Y%m%d-%H%M%S"),
+        }), fout, pickle_protocol=3)
 
-    return recipe, {**defaults, **param}
+    return filename
 
 
-def recipe_param_apply(recipe, **mapper):
-    def apply(param):
-        return {
-            name: mapper.get(name, lambda v: v)(value) or value
-            for name, value in param.items()
-        }
+def param_apply(param, **mapper):
+    result = {}
+    for name, value in param.items():
+        if value is not None:
+            fn = mapper.get(name)
+            retvalue = fn(value) if callable(fn) else value
+            value = value if retvalue is None else retvalue
 
-    def walk(recipe):
-        if isinstance(recipe, (tuple, list)) and recipe:
-            param = {}
-            if isinstance(recipe[-1], dict):
-                *recipe, param = recipe
+        result[name] = value
 
-            return (*map(walk, recipe), apply(param))
-        return recipe
-
-    return walk(recipe)
+    return result
 
 
 def get_class(klass):
+    """Parse the specified type-string, import it and return the type."""
+    if isinstance(klass, type):
+        return klass
+
     if not isinstance(klass, str):
         return None
 
@@ -47,20 +46,6 @@ def get_class(klass):
     return getattr(importlib.import_module(module), klass)
 
 
-def get_instance(*args, **options):
-    factory = get_class(options.pop("class"))
-    return factory(*args, **options)
-
-
-def get_model_factory(**options):
-    from functools import partial
-    from .. import models
-
-    options.pop("repr", None)
-
-    klass = options.pop("class")
-    factory = get_class(klass) or getattr(models, klass)
-
-    recipe = recipe_param_apply(
-        options.pop("recipe", []), activation=get_class)
-    return partial(factory, *recipe, **options)
+def get_instance(*args, cls, **options):
+    """Locate and create a `cls` instance."""
+    return get_class(cls)(*args, **options)

### 2019-12-01 experiments/auto/utils.py
Feature preprocessor from (Trabesli et al., 2017), feed wrappers: mover and limiter

@@ -5,6 +5,59 @@ import gzip
 import torch
 import importlib
 
+from torch.utils.data import DataLoader
+
+
+def feed_mover(feed, **kwargs):
+    """Transfer to device and type cast the batches from the feed on the fly.
+
+    Parameters
+    ----------
+    feed : torch.utils.data.DataLoader
+        The data loader instance draw batches from.
+
+    **kwargs : keyword arguments
+        The keyword arguments for the method `torch.Tensor.to()`.
+
+    Yields
+    ------
+    batch : iterable
+        An iterable that consitutes the batch.
+    """
+
+    if not kwargs:
+        yield from feed
+        return
+
+    for batch in feed:
+        yield [b.to(**kwargs) for b in batch]
+
+
+def feed_limiter(feed, max=-1):
+    """Limit the number of batches requested from the feed.
+
+    Parameters
+    ----------
+    feed : torch.utils.data.DataLoader
+        The data loader instance draw batches from.
+
+    max : int, default=-1
+        The limit on the number of batches generated.
+        Disabled if `max` is negative.
+
+    Yields
+    ------
+    batch : iterable
+        An iterable that consitutes the batch.
+    """
+
+    if max < 0:
+        yield from feed
+        return
+
+    for batch, _ in zip(feed, range(max)):
+        yield batch
+
 
 def save_snapshot(filename, **kwargs):
     with gzip.open(filename, "wb", compresslevel=5) as fout:

### 2019-12-01 experiments/auto/wrappers.py

@@ -1,30 +1,0 @@
-import torch
-from torch.utils.data import DataLoader
-
-
-class FeedWrapper(object):
-    """A wrapper for a dataLoader that puts batches on device on the fly.
-
-    Parameters
-    ----------
-    feed : torch.utils.data.DataLoader
-        The data loader instance to be wrapped.
-
-    **kwargs : keyword arguments
-        The keyword arguments to be passed to `torch.Tensor.to()`.
-    """
-    def __init__(self, feed, **kwargs):
-        assert isinstance(feed, DataLoader)
-        self.feed, self.kwargs = feed, kwargs
-
-    def __len__(self):
-        return len(self.feed)
-
-    def __iter__(self):
-        if not self.kwargs:
-            yield from iter(self.feed)
-
-        else:
-            for batch in iter(self.feed):
-                yield tuple(b.to(**self.kwargs)
-                            for b in batch)

### 2019-12-01 experiments/musicnet/dataset.py

@@ -9,6 +9,9 @@ from bisect import bisect_right
 
 from numpy.lib.stride_tricks import as_strided
 
+from scipy.fftpack import fft  # Fourier features
+from scipy.signal import stft  # Short-time Fourtier Transform
+
 
 class MusicNetHDF5(torch.utils.data.Dataset):
     """Dataset access to MusicNet stored in HDF5 file.
@@ -172,3 +175,78 @@ class MusicNetHDF5(torch.utils.data.Dataset):
 
     def __repr__(self):
         return repr(self.hdf5)
+
+
+class MusicNetWaveformCollation(object):
+    """Batch collation with on-the-fly feature processing transforms.
+
+    Parameters
+    ----------
+    kind : str, default='fft'
+        The kind of features to compute: 'raw' -- the raw signal waveform,
+        'fft' -- fourier trasnform, 'stft' -- short time fourier transform.
+        'stft-swap' is same as 'stft', but has freq and times axes swapped
+        for compatibility with the original experiments of Trabesli et al.
+        (2017), where the frequencies and times are swapped in Keras.
+
+    cplx : bool, default=True
+        Whether to return complex features in re-im format stacked along
+        the 2nd to last axis, or return real valued features. The nature
+        of the latter depend on the `kind` parameter: if `kind` is 'raw'
+        then the waveform is just returned as is, otherwise the magnitude
+        of complex numbers is returned.
+    """
+
+    def __init__(self, kind="fft", cplx=True):
+        assert kind in ("raw", "fft", "stft", "stft-swap")
+        self.kind, self.cplx = kind, cplx
+
+    def __call__(self, batch):
+        """Arrange each piece into a tensor with batch in the zeroth dimension.
+
+        Details
+        -------
+        Expects numpy ndarray(s) in batch. Feature generation was put here to
+        streamline fourier feature generation, albeit in numpy.
+        """
+
+        # collate in numpy (on CPU) by stacking along axis 0
+        signal, *rest = map(np.stack, zip(*batch))
+
+        # produce features fft/stft/raw
+        if self.kind == "raw":
+            z = signal[..., np.newaxis, :]
+
+        elif self.kind == "fft":
+            # z is complex64 B x 1 x [window]
+            z = fft(signal[..., np.newaxis, :], axis=-1)
+
+        else:  # self.kind in ("stft", "stft-swap")
+            # z is complex64 B x [freq] x [times] (window 4096 -> 70 times)
[…]

### 2019-12-01 experiments/musicnet/dataset.py
moved reasmpling to a special script, since it is a one-time procedure

@@ -1,7 +1,3 @@
-#!/usr/bin/env python
-# -*- coding: utf-8 -*-
-
-import tqdm
 import h5py
 import numpy as np
 
@@ -9,42 +5,9 @@ import torch
 import torch.utils.data
 
 from ncls import NCLS64
-from resampy import resample
 from bisect import bisect_right
 
 from numpy.lib.stride_tricks import as_strided
-
-
-def resample_h5(file_in, file_out, frame_rate_in, frame_rate_out, keys=None):
-    # Authors: Dmitriy Serdyuk
-    # (2019-11-24) changed to hdf5 supports
-    print(f""".. resampling {file_in} ({frame_rate_in}Hz) """
-          f"""into {file_out} ({frame_rate_out}Hz)""", flush=True)
-
-    with h5py.File(file_in, "r") as h5_in, \
-            h5py.File(file_out, "w") as h5_out:
-
-        ratio = frame_rate_out / float(frame_rate_in)
-
-        # pour from h5_in to h5_out
-        items = h5_in.items()
-        if keys is not None:
-            items = [(k, h5_in[k]) for k in keys]
-
-        for key, group in tqdm.tqdm(items):
-
-            # resample the waveform
-            data = resample(np.array(group["data"]),
-                            frame_rate_in, frame_rate_out)
-            h5_out.create_dataset(f"{key}/data", data=data)
-
-            # change start-end times
-            labels = np.array(group["labels"])
-            labels["start_time"] = (labels["start_time"] * ratio).astype(int)
-            labels["end_time"] = (labels["end_time"] * ratio).astype(int)
-            h5_out.create_dataset(f"{key}/labels", data=labels)
-
-    return file_out
 
 
 class MusicNetHDF5(torch.utils.data.Dataset):

### 2019-12-01 experiments/auto/auto.py
partial scaffolding of the experiment runner

@@ -1,3 +1,4 @@
+__version__ = "0.1"
 import os
 import copy
 import tqdm
@@ -8,9 +9,116 @@ import torch
 import numpy as np
 
 from setuptools._vendor.packaging.version import Version
+from .utils import feed_limiter, feed_mover
 
 
-__version__ = "0.1"
+def defaults(options):
+    # currently no defaults
+    return copy.deepcopy(options)
+
+
+def get_datasets(factory, recipe):
+    """Get dataset instances from the factory specification and recipe."""
+    # "dataset", "dataset_sources"
+    raise NotImplementedError
+
+
+def get_collate_fn(recipe):
+    """Get collation function responsible for batch-feature generation."""
+    # "features"
+    raise NotImplementedError
+
+
+def get_feeds(datasets, collate_fn, recipe):
+    """Get instances of data loaders from the datasets and collate function."""
+    # <datasets>, <collate_fn>, "feeds"
+    raise NotImplementedError
+
+
+def get_objective_terms(recipe):
+    """Gather the components of the objective function."""
+    # "objective_terms"
+    raise NotImplementedError
+
+
+def get_model_factory(recipe):
+    """Partial constructor of the model. Assumes a particual common API."""
+    # "model"
+    raise NotImplementedError
+
+
+def get_model(factory, recipe):
+    """Partial constructor of the model. Assumes a particual common API."""
+    # <factory>, "stages__*__model"
+    raise NotImplementedError
+
+
+def get_objective(objective_terms, recipe):
+    """Construct the objective function from the recipe and components."""
+    # <objective_terms>, "stages__*__objective"
+    raise NotImplementedError
+
+
+def get_optimizer(module, *, lr, **kwargs):
+    """Get the optimizer for the module from explicit lr and kwargs."""
+    raise NotImplementedError
+
+
+def get_scheduler(optimizer, **kwargs):
+    """Get scheduler for the optimizer and kwargs."""
+    raise NotImplementedError
+
+
+class FeedWrapper(object):
+    def __init__(self, feed, max=1000, **kwargs):
+        self.feed, self.max, self.kwargs = feed, max, kwargs
+
+    def __iter__(self):
+        feed = feed_limiter(self.feed, self.max)
+        yield from feed_mover(feed, **self.kwargs)
+
+    def __len__(self):
+        return len(self.feed)
+
+
+def run(options, verbose=True):
+    options = defaults(options)
+
+    # placement (dtype / device) and sparsity settings
[…]

### 2019-12-01 experiments/auto/auto.py
bit more fleshed out scaffolding, extra utilities

@@ -10,6 +10,8 @@ import numpy as np
 
 from setuptools._vendor.packaging.version import Version
 from .utils import feed_limiter, feed_mover
+from .utils import save_snapshot, load_snapshot
+from .utils import join, deploy_optimizer
 
 
 def defaults(options):
@@ -81,8 +83,9 @@ class FeedWrapper(object):
         return len(self.feed)
 
 
-def run(options, verbose=True):
+def run(options, folder, suffix, verbose=True):
     options = defaults(options)
+    options_backup = copy.deepcopy(options)
 
     # placement (dtype / device) and sparsity settings
     threshold = options["threshold"]  # log(p/(1-p)), p=dropout rate
@@ -98,13 +101,56 @@ def run(options, verbose=True):
 
     model_factory = get_model_factory(options["model"])
 
-    model, optim = None, None
-    for stage, settings in options["stages"].itmes():
+    stages = options["stages"]
+    model, optim, mapper = None, None, {}
+    for n_stage, stage in enumerate(options["stage-order"]):
+        settings = stages[stage]
+        stage_backup = stage, copy.deepcopy(settings)
+
+        # `.load_state_dict()` automatically moves to device and casts
         new_model = get_model(model_factory, settings["model"]).to(**devtype)
+
+        # base lr is specified in the optimizer settings
         new_optim = get_optimizer(new_model, **settings["optimizer"])
 
+        # name-id mapping for copying optimizer states
+        new_mapper = {k: id(p) for k, p in new_model.named_parameters()}
+
+        # check optimizer class and restart flag (`new_optim` exists anyway)
+        restart = settings["restart"] or not isinstance(optim, new_optim.__class__)
+
         # <stage continuation>
-        model, optim = new_model, new_optim
+        optim_state = {}
+        if settings["snapshot"] is not None:
+            # Cold: parameters and buffers are loaded from some snapshot
+            state = load_snapshot(settings["snapshot"])
+
+            state_dict = state["model"]
+            mapper = state.get("mapper", {})
+            optim_state = state.get("optimizer", {})
+
+            new_model.load_state_dict(state_dict, strict=True)
+
+            del state
+
+        elif model is not None:
+            # Warm: the previous model provides the parameters
+            raise NotImplementedError
+
+        else:
+            raise NotImplementedError
+
+        # pass on the state of the optimizer
+        if optim_state and not restart:
+            # construct a map of id-s from `source` (left) to `target` (right)
[…]

### 2019-12-01 experiments/auto/utils.py

@@ -68,6 +68,15 @@ def save_snapshot(filename, **kwargs):
     return filename
 
 
+def load_snapshot(filename):
+    with gzip.open(filename, "rb") as fin:
+        state = torch.load(fin, map_location=torch.device("cpu"))
+
+    # verify
+
+    return state
+
+
 def param_apply(param, **mapper):
     result = {}
     for name, value in param.items():
@@ -102,3 +111,50 @@ def get_class(klass):
 def get_instance(*args, cls, **options):
     """Locate and create a `cls` instance."""
     return get_class(cls)(*args, **options)
+
+
+def join(*, left, right, how="inner", f=None):
+    assert isinstance(left, dict) and isinstance(right, dict)
+
+    if how == "left":
+        key = left.keys()
+
+    elif how == "right":
+        key = right.keys()
+
+    elif how == "inner":
+        key = left.keys() & right.keys()
+
+    else:
+        key = left.keys() | right.keys()
+
+    def f_or_none(x):
+        return None if x is None else (x if not callable(f) else f(x))
+
+    return {k: (f_or_none(left.get(k)), f_or_none(right.get(k))) for k in key}
+
+
+def deploy_optimizer(mapper, *, target, source=None, copy_lr=False):
+    if source is None:
+        return target
+
+    if isinstance(source, torch.optim.Optimizer):
+        d_source = source.state_dict()
+    elif isinstance(source, dict):
+        d_source = source
+    else:
+        raise TypeError(f"`source` must be a dict or an oprimizer. "
+                        f"Got {type(source).__name__}.")
+
+    d_target = target.state_dict()
+
+    # transfer the state
+    d_target["state"].update({
+        mapper[k]: v for k, v in d_source["state"].items() if k in mapper
+    })
+
+    # copy the learning rate
+    assert not copy_lr
+
+    target.load_state_dict(d_target)
+    return target

### 2019-12-01 experiments/auto/auto.py
added state inheritance logic

@@ -8,6 +8,9 @@ import json
 import torch
 import numpy as np
 
+from cplxmodule.relevance import compute_ard_masks
+from cplxmodule.masks import binarize_masks
+
 from setuptools._vendor.packaging.version import Version
 from .utils import feed_limiter, feed_mover
 from .utils import save_snapshot, load_snapshot
@@ -119,23 +122,39 @@ def run(options, folder, suffix, verbose=True):
         # check optimizer class and restart flag (`new_optim` exists anyway)
         restart = settings["restart"] or not isinstance(optim, new_optim.__class__)
 
-        # <stage continuation>
+        # continuation: inherit optimizer state and model parametrs either form
+        #  the previous (hot) state or from a (cold) storage.
         optim_state = {}
         if settings["snapshot"] is not None:
             # Cold: parameters and buffers are loaded from some snapshot
-            state = load_snapshot(settings["snapshot"])
+            model, optim, mapper = None, None, {}
+            snapshot = load_snapshot(settings["snapshot"])
 
-            state_dict = state["model"]
-            mapper = state.get("mapper", {})
-            optim_state = state.get("optimizer", {})
+            # overwrite the parameters and buffers of the model
+            new_model.load_state_dict(snapshot["model"], strict=True)
 
-            new_model.load_state_dict(state_dict, strict=True)
+            # get the saved state of the optimizer and a name-id map
+            optim_state = snapshot.get("optimizer", {})
+            mapper = snapshot.get("mapper", {})
 
-            del state
+            del snapshot
 
         elif model is not None:
             # Warm: the previous model provides the parameters
-            raise NotImplementedError
+            optim_state = optim.state_dict()
+
+            # harvest and binarize masks, and clean the related parameters
+            masks = compute_ard_masks(model, hard=True, threshold=threshold)
+            state_dict, masks = binarize_masks(model.state_dict(), masks)
+            state_dict.update(masks)
+
+            # Models in each stage are instances of the same underlying
+            #  architecture just with differnt traits. Hence only here
+            #  we allow missing or unexpected parameters when deploying
+            #  the state
+            new_model.load_state_dict(state_dict, strict=False)
+
+            del state_dict, masks
 
         else:
             raise NotImplementedError
@@ -145,8 +164,7 @@ def run(options, folder, suffix, verbose=True):
             # construct a map of id-s from `source` (left) to `target` (right)
             mapping = join(right=new_mapper, left=mapper, how="inner")
             deploy_optimizer(dict(mapping.values()),
[…]

### 2019-12-01 experiments/auto/utils.py
simple docstrings for join ad deploy

@@ -114,6 +114,7 @@ def get_instance(*args, cls, **options):
 
 
 def join(*, left, right, how="inner", f=None):
+    """SQL-like join of two dictionaries."""
     assert isinstance(left, dict) and isinstance(right, dict)
 
     if how == "left":
@@ -125,7 +126,7 @@ def join(*, left, right, how="inner", f=None):
     elif how == "inner":
         key = left.keys() & right.keys()
 
-    else:
+    else:  # how == "outer"
         key = left.keys() | right.keys()
 
     def f_or_none(x):
@@ -134,7 +135,13 @@ def join(*, left, right, how="inner", f=None):
     return {k: (f_or_none(left.get(k)), f_or_none(right.get(k))) for k in key}
 
 
-def deploy_optimizer(mapper, *, target, source=None, copy_lr=False):
+def deploy_optimizer(mapper, *, target, source=None):
+    """Copy common state from the `source` to the `target` optimizer.
+
+    Note
+    ----
+    Neither learning rate settings nor parameter groups are compied.
+    """
     if source is None:
         return target
 
@@ -152,9 +159,6 @@ def deploy_optimizer(mapper, *, target, source=None, copy_lr=False):
     d_target["state"].update({
         mapper[k]: v for k, v in d_source["state"].items() if k in mapper
     })
-
-    # copy the learning rate
-    assert not copy_lr
 
     target.load_state_dict(d_target)
     return target

### 2019-12-01 experiments/auto/auto.py
factored out stage state from the main loop

@@ -9,12 +9,17 @@ import torch
 import numpy as np
 
 from cplxmodule.relevance import compute_ard_masks
-from cplxmodule.masks import binarize_masks
+from cplxmodule.masked import binarize_masks
 
 from setuptools._vendor.packaging.version import Version
+
+from .utils import get_class
 from .utils import feed_limiter, feed_mover
 from .utils import save_snapshot, load_snapshot
 from .utils import join, deploy_optimizer
+
+from collections import namedtuple
+State = namedtuple("State", ["model", "optim", "mapper"])
 
 
 def defaults(options):
@@ -47,13 +52,13 @@ def get_objective_terms(recipe):
 
 
 def get_model_factory(recipe):
-    """Partial constructor of the model. Assumes a particual common API."""
+    """Partial constructor of the model. Assumes a particular common API."""
     # "model"
     raise NotImplementedError
 
 
 def get_model(factory, recipe):
-    """Partial constructor of the model. Assumes a particual common API."""
+    """Partial constructor of the model. Assumes a particular common API."""
     # <factory>, "stages__*__model"
     raise NotImplementedError
 
@@ -75,6 +80,7 @@ def get_scheduler(optimizer, **kwargs):
 
 
 class FeedWrapper(object):
+    """A class that combines the limiter and the mover."""
     def __init__(self, feed, max=1000, **kwargs):
         self.feed, self.max, self.kwargs = feed, max, kwargs
 
@@ -86,13 +92,94 @@ class FeedWrapper(object):
         return len(self.feed)
 
 
+def state_create(factory, settings, devtype):
+    """Create a new state, i.e. model, optimizer and name-id mapper (for state
+    inheritance below), from the settings and model factory.
+    """
+
+    # (note) `.load_state_dict()` automatically moves to device and casts
+    model = get_model(factory, settings["model"]).to(**devtype)
+
+    # base lr is specified in the optimizer settings
+    optim = get_optimizer(model, **settings["optimizer"])
+
+    # name-id mapping for copying optimizer states
+    mapper = {k: id(p) for k, p in model.named_parameters()}
+
+    return State(model, optim, mapper)
+
+
+def state_inherit(state, options, *, old=None, **sparsity_kwargs):
+    """Inherit optimizer state and model parameters either form
+    the previous (hot) state or from a (cold) storage.
+    """
+    # model state is inherited anyway, optimizer is conditional.
+    optim_state, source_mapper, inheritable = {}, {}, False
[…]

### 2019-12-02 experiments/musicnet/dataset.py
waveform data resident in ram

@@ -11,7 +11,7 @@ from numpy.lib.stride_tricks import as_strided
 
 
 class MusicNetHDF5(torch.utils.data.Dataset):
-    """Dataset access to MusicNet sotred in HDF5 file.
+    """Dataset access to MusicNet stored in HDF5 file.
 
     Parameters
     ----------
@@ -31,11 +31,15 @@ class MusicNetHDF5(torch.utils.data.Dataset):
         of the window by default (None).
 
     dtype : np.dtype, default=np.float32
-        The data typee of the waveform windows and targets. Defautls ot float32
+        The data type of the waveform windows and targets. Defaults to float32
         for easier compatibility with torch.
+
+    resident : bool, default=False
+        Wheter to cache the raw waveform data into ram on init.
     """
 
-    def __init__(self, hdf5, window=4096, stride=512, at=None, dtype=np.float32):
+    def __init__(self, hdf5, window=4096, stride=512, at=None,
+                 dtype=np.float32, resident=False):
         # ensure an open HDF5 handle
         assert isinstance(hdf5, h5py.File) and hdf5.id
         # assumes note_ids 21..105, i.e. 84 class labels
@@ -61,6 +65,8 @@ class MusicNetHDF5(torch.utils.data.Dataset):
             self.probability[ix] = counts / float(len(obj))
 
             # cache hdf5 objects (stores references to hdf5 objects!)
+            if resident:
+                obj = obj[:].astype(dtype, copy=True)  # read the data
             references.append((obj, tree))
 
             # the number of full valid windows fitting into the signal
@@ -97,7 +103,7 @@ class MusicNetHDF5(torch.utils.data.Dataset):
 
         # fetch data and construct labels: random access is slow
         obj, lab = self.objects[key], self.labels[key]
-        data = obj[ix:ix + self.window].astype(self.dtype)
+        data = obj[ix:ix + self.window].astype(self.dtype, copy=False)
 
         notes = np.zeros(self.n_outputs, self.dtype)
         for b, e, j in lab.find_overlap(ix + self.at, ix + self.at + 1):
@@ -152,7 +158,7 @@ class MusicNetHDF5(torch.utils.data.Dataset):
             raise KeyError(f"`{key}` not found")
 
         key = self.keys[key]
-        data = self.objects[key][:].astype(self.dtype)
+        data = self.objects[key][:].astype(self.dtype, copy=False)
 
         *head, stride = data.strides
         stride = *head, self.stride * stride, stride

### 2019-12-02 paper/paper.tex
path fixes
added references for cplx network overview

@@
 or $\cplx\real$ calculus, which generalizes holomorphic calculus to non-holomorphic functions
-of $\cplx$-argument, \citep{adali_complex-valued_2011}. The rules it defines satisfy intuitive
-linearity, product and chain rules, and respect complex conjugation, but most importantly the
+of $\cplx$-argument, \citep{adali_complex-valued_2011,boeddeker_computation_2019}. It satisfies
+product and chain rules, respects complex conjugation and linearity, but most importantly the
 $\cplx\real$-differential of a function on $\cplx$ coincides with its classical differential as

### 2019-12-02 experiments/auto/utils.py
factory maker and default parameter setter

@@ -5,6 +5,8 @@ import gzip
 import torch
 import importlib
 
+from functools import partial
+
 from torch.utils.data import DataLoader
 
 
@@ -77,6 +79,10 @@ def load_snapshot(filename):
     return state
 
 
+def param_defaults(param, **defaults):
+    return {**defaults, **param}
+
+
 def param_apply(param, **mapper):
     result = {}
     for name, value in param.items():
@@ -111,6 +117,11 @@ def get_class(klass):
 def get_instance(*args, cls, **options):
     """Locate and create a `cls` instance."""
     return get_class(cls)(*args, **options)
+
+
+def get_factory(*args, cls, **options):
+    """Locate and create a partial `cls` constructor."""
+    return partial(get_class(cls), *args, **options)
 
 
 def join(*, left, right, how="inner", f=None):

### 2019-12-02 experiments/auto/auto.py
obective components might depend on the dataset (sample weight, label weights)

@@ -45,7 +45,7 @@ def get_feeds(datasets, collate_fn, recipe):
     raise NotImplementedError
 
 
-def get_objective_terms(recipe):
+def get_objective_terms(datasets, recipe):
     """Gather the components of the objective function."""
     # "objective_terms"
     raise NotImplementedError
@@ -187,7 +187,7 @@ def run(options, folder, suffix, verbose=True):
 
     feeds = get_feeds(datasets, collate_fn, options["feeds"])
 
-    objective_terms = get_objective_terms(options["objective_terms"])
+    objective_terms = get_objective_terms(datasets, options["objective_terms"])
 
     model_factory = get_model_factory(options["model"])
 

### 2019-12-02 experiments/auto/utils.py
paramter defaults, and depth-first nested dictionary mapper

@@ -80,20 +80,81 @@ def load_snapshot(filename):
 
 
 def param_defaults(param, **defaults):
+    """Add keys with default values if absent.
+
+    Parameters
+    ----------
+    param : dict
+        The dictionary of parameters.
+
+    **defaults : keyword arguments
+        The default values of the missing keys.
+
+    Returns
+    -------
+    out : dict
+        A shallow copy of the parameters with specified (shallow) defaults.
+    """
     return {**defaults, **param}
 
 
-def param_apply(param, **mapper):
-    result = {}
-    for name, value in param.items():
-        if value is not None:
-            fn = mapper.get(name)
-            retvalue = fn(value) if callable(fn) else value
-            value = value if retvalue is None else retvalue
+def param_apply_map(param, deep=True, memo=None, **map):
+    """Recurively re-map the values within the nested dictionary.
 
-        result[name] = value
+    Parameters
+    ----------
+    param : dict
+        The dictionary of parameters.
 
-    return result
+    deep : bool, default=True
+        Whether to recursevely copy the nested dictionaries.
+
+    memo : set, default=None
+        Service set to keep track of visited nested dictionaries.
+
+    **map : keyworded functions
+        The key-function mapping, applied to non-dictionary elements.
+
+    Returns
+    -------
+    out : dict
+        A shallow or deep modified copy of the original parameter dictionary.
+
+    Details
+    -------
+    If `map` is provided, then produces a modified copy of the original
+    dictionary, maintaining is key ordering.
+    """
+
+    if not map:
+        return param
+
+    # keep track of visited nested dictionaries by their `id(...)`
+    if memo is None:
+        memo = set()
+
+    if id(param) in memo:
+        # nested self reference : return the dictinoary as it is.
+        return param
+    memo.add(id(param))
+
+    out = dict()
+    # make an elementwise copy of the dictionary
+    for key in param:
+        value = param[key]
+        if not isinstance(value, dict):
+            # map a non None value using the supplied map
+            if key in map and value is not None:
+                retvalue = map[key](value)
+                if retvalue is not None:
+                    value = retvalue
+
+        elif deep:  # value is dict
+            value = param_apply_map(value, memo=memo, deep=True, **map)
+
+        out[key] = value
+
+    return out
 
 
 def get_class(klass):

### 2019-12-02 experiments/auto/utils.py
prioritize applying to nested dicts, instead of recursing

@@ -142,14 +142,14 @@ def param_apply_map(param, deep=True, memo=None, **map):
     # make an elementwise copy of the dictionary
     for key in param:
         value = param[key]
-        if not isinstance(value, dict):
-            # map a non None value using the supplied map
-            if key in map and value is not None:
-                retvalue = map[key](value)
-                if retvalue is not None:
-                    value = retvalue
+        # map a non None value using the supplied map
+        if key in map and value is not None:
+            retvalue = map[key](value)
+            if retvalue is not None:
+                value = retvalue
 
-        elif deep:  # value is dict
+        elif deep and isinstance(value, dict):
+            # key not in map and value is dict and deep
             value = param_apply_map(value, memo=memo, deep=True, **map)
 
         out[key] = value

### 2019-12-02 experiments/auto/auto.py
fleshed out dataset handling

@@ -13,7 +13,9 @@ from cplxmodule.masked import binarize_masks
 
 from setuptools._vendor.packaging.version import Version
 
-from .utils import get_class
+from .utils import get_class, get_factory, get_instance
+from .utils import param_apply_map, param_defaults
+
 from .utils import feed_limiter, feed_mover
 from .utils import save_snapshot, load_snapshot
 from .utils import join, deploy_optimizer
@@ -30,19 +32,28 @@ def defaults(options):
 def get_datasets(factory, recipe):
     """Get dataset instances from the factory specification and recipe."""
     # "dataset", "dataset_sources"
-    raise NotImplementedError
+    factory = get_factory(**factory)
+    return {name: factory(**source)
+            for name, source in recipe.items()}
 
 
 def get_collate_fn(recipe):
     """Get collation function responsible for batch-feature generation."""
     # "features"
-    raise NotImplementedError
+    return get_instance(**recipe)
 
 
 def get_feeds(datasets, collate_fn, recipe):
     """Get instances of data loaders from the datasets and collate function."""
     # <datasets>, <collate_fn>, "feeds"
-    raise NotImplementedError
+    recipe = param_apply_map(recipe, dataset=datasets.__getitem__)
+
+    feeds = {}
+    for name, par in recipe.items():
+        par = param_defaults(par, pin_memory=True)
+        feeds[name] = torch.utils.data.DataLoader(**par, collate_fn=collate_fn)
+
+    return feeds
 
 
 def get_objective_terms(datasets, recipe):

### 2019-12-02 experiments/auto/auto.py
implemented constructor of composite objective terms

@@ -11,6 +11,7 @@ import numpy as np
 from cplxmodule.relevance import compute_ard_masks
 from cplxmodule.masked import binarize_masks
 
+from scipy.special import logit
 from setuptools._vendor.packaging.version import Version
 
 from .utils import get_class, get_factory, get_instance
@@ -56,10 +57,37 @@ def get_feeds(datasets, collate_fn, recipe):
     return feeds
 
 
+def compute_positive_weight(recipe):
+    """Compute the +ve label weights to ensure balance given in the recipe."""
+    # "pos_weight" (with mapped dataset)
+    recipe = param_defaults(recipe, alpha=0.5, max=1e2)
+
+    # average across pieces of data (axis 0 in probabilities)
+    proba_hat = recipe["dataset"].probability.mean(axis=0)
+
+    # clip to within (0, 1) to prevent saturation
+    proba_hat_clipped = proba_hat.clip(1e-6, 1 - 1e-6)
+
+    # w_+ = \alpha (\tfrac{m}{n_+} - 1) = \alpha \tfrac{1 - p_+}{p_+}
+    pos_weight = np.exp(- logit(proba_hat_clipped)) * recipe["alpha"]
+
+    # clip weights to avoid overflows
+    pos_weight_clipped = pos_weight.clip(max=recipe["max"])
+
+    return torch.from_numpy(pos_weight_clipped).float()
+
+
 def get_objective_terms(datasets, recipe):
     """Gather the components of the objective function."""
-    # "objective_terms"
-    raise NotImplementedError
+    # <datasets>, "objective_terms"
+    recipe = param_apply_map(recipe, dataset=datasets.__getitem__)
+
+    objectives = {}
+    for name, par in recipe.items():
+        par = param_apply_map(par, pos_weight=compute_positive_weight)
+        objectives[name] = get_instance(**par)
+
+    return objectives
 
 
 def get_model_factory(recipe):

### 2019-12-02 experiments/auto/auto.py
changed optimizer and scheduler creation interface, fixed doctsring typos, nop-ed else-clause in state_inherit

@@ -108,13 +108,15 @@ def get_objective(objective_terms, recipe):
     raise NotImplementedError
 
 
-def get_optimizer(module, *, lr, **kwargs):
-    """Get the optimizer for the module from explicit lr and kwargs."""
+def get_optimizer(module, recipe):
+    """Get the optimizer for the module from the recipe."""
+    # <module>, "stages__*__optimizer"
     raise NotImplementedError
 
 
-def get_scheduler(optimizer, **kwargs):
-    """Get scheduler for the optimizer and kwargs."""
+def get_scheduler(optimizer, recipe):
+    """Get scheduler for the optimizer and recipe."""
+    # <optimizer>, "stages__*__lr_scheduler"
     raise NotImplementedError
 
 
@@ -140,7 +142,7 @@ def state_create(factory, settings, devtype):
     model = get_model(factory, settings["model"]).to(**devtype)
 
     # base lr is specified in the optimizer settings
-    optim = get_optimizer(model, **settings["optimizer"])
+    optim = get_optimizer(model, settings["optimizer"])
 
     # name-id mapping for copying optimizer states
     mapper = {k: id(p) for k, p in model.named_parameters()}
@@ -189,9 +191,8 @@ def state_inherit(state, options, *, old=None, **sparsity_kwargs):
 
         del state_dict, masks
 
-    else:
-        # no snapshot, or old is None, or old is State, but old.model is None
-        raise NotImplementedError
+    else:  # snapshot is None and old.model is None
+        pass
 
     # check optimizer inheritance and restart flag, and deploy the state
     if (optim_state and inheritable) and not options["restart"]:
@@ -243,7 +244,7 @@ def run(options, folder, suffix, verbose=True):
 
         objective = get_objective(objective_terms, settings["objective"]).to(**devtype)
         feed = FeedWrapper(feeds[stage], max=settings["n_batches_per_epoch"], **devtype)
-        sched = get_scheduler(optim, **settings["lr_scheduler"])
+        sched = get_scheduler(optim, settings["lr_scheduler"])
 
         model.train()
         model, success, history = fit(

### 2019-12-02 experiments/auto/utils.py

@@ -7,15 +7,13 @@ import importlib
 
 from functools import partial
 
-from torch.utils.data import DataLoader
-
 
 def feed_mover(feed, **kwargs):
     """Transfer to device and type cast the batches from the feed on the fly.
 
     Parameters
     ----------
-    feed : torch.utils.data.DataLoader
+    feed : iterable
         The data loader instance draw batches from.
 
     **kwargs : keyword arguments
@@ -24,7 +22,7 @@ def feed_mover(feed, **kwargs):
     Yields
     ------
     batch : iterable
-        An iterable that consitutes the batch.
+        An iterable that constitutes the batch.
     """
 
     if not kwargs:
@@ -40,7 +38,7 @@ def feed_limiter(feed, max=-1):
 
     Parameters
     ----------
-    feed : torch.utils.data.DataLoader
+    feed : iterable
         The data loader instance draw batches from.
 
     max : int, default=-1
@@ -50,7 +48,7 @@ def feed_limiter(feed, max=-1):
     Yields
     ------
     batch : iterable
-        An iterable that consitutes the batch.
+        An iterable that constitutes the batch.
     """
 
     if max < 0:
@@ -99,7 +97,7 @@ def param_defaults(param, **defaults):
 
 
 def param_apply_map(param, deep=True, memo=None, **map):
-    """Recurively re-map the values within the nested dictionary.
+    """Recursively re-map the values within the nested dictionary.
 
     Parameters
     ----------
@@ -107,7 +105,7 @@ def param_apply_map(param, deep=True, memo=None, **map):
         The dictionary of parameters.
 
     deep : bool, default=True
-        Whether to recursevely copy the nested dictionaries.
+        Whether to recursively copy the nested dictionaries.
 
     memo : set, default=None
         Service set to keep track of visited nested dictionaries.
@@ -134,7 +132,7 @@ def param_apply_map(param, deep=True, memo=None, **map):
         memo = set()
 
     if id(param) in memo:
-        # nested self reference : return the dictinoary as it is.
+        # nested self reference : return the dictionary as it is.
         return param
     memo.add(id(param))
 
@@ -170,7 +168,7 @@ def get_class(klass):
     if match is None:
         return None
 
-    # import from builtins if no module is specified
+    # import from built-ins if no module is specified
     module, klass = (match.group(1) or "builtins"), match.group(2)
     return getattr(importlib.import_module(module), klass)
 
@@ -212,17 +210,19 @@ def deploy_optimizer(mapper, *, target, source=None):
[…]

### 2019-12-02 experiments/auto/utils.py
prioritize dfs in apply-map

@@ -107,8 +107,9 @@ def param_apply_map(param, deep=True, memo=None, **map):
     deep : bool, default=True
         Whether to recursively copy the nested dictionaries.
 
-    memo : set, default=None
-        Service set to keep track of visited nested dictionaries.
+    memo : dict, default=None
+        Internally used service dictionary to keep track of visited nested
+        dictionaries.
 
     **map : keyworded functions
         The key-function mapping, applied to non-dictionary elements.
@@ -129,26 +130,27 @@ def param_apply_map(param, deep=True, memo=None, **map):
 
     # keep track of visited nested dictionaries by their `id(...)`
     if memo is None:
-        memo = set()
+        memo = {}
 
+    # nested self reference: return the previously computed dictionary
     if id(param) in memo:
-        # nested self reference : return the dictionary as it is.
-        return param
-    memo.add(id(param))
+        return memo[id(param)]
 
-    out = dict()
+    out = {}
+    memo[id(param)] = out  # reference the dynamically created dictionary
+
     # make an elementwise copy of the dictionary
     for key in param:
         value = param[key]
+        # prioritize dfs, then pass the nested result through the map
+        if isinstance(value, dict) and deep:
+            value = param_apply_map(value, deep=True, memo=memo, **map)
+
         # map a non None value using the supplied map
         if key in map and value is not None:
             retvalue = map[key](value)
             if retvalue is not None:
                 value = retvalue
-
-        elif deep and isinstance(value, dict):
-            # key not in map and value is dict and deep
-            value = param_apply_map(value, memo=memo, deep=True, **map)
 
         out[key] = value
 

### 2019-12-02 experiments/auto/auto.py
fixed stage feed source

@@ -242,8 +242,10 @@ def run(options, folder, suffix, verbose=True):
         # unpack the state, initialize objective and scheduler, and train
         model, optim = state.model, state.optim
 
-        objective = get_objective(objective_terms, settings["objective"]).to(**devtype)
-        feed = FeedWrapper(feeds[stage], max=settings["n_batches_per_epoch"], **devtype)
+        feed = FeedWrapper(feeds[settings["feed"]],
+                           max=settings["n_batches_per_epoch"], **devtype)
+        objective = get_objective(objective_terms,
+                                  settings["objective"]).to(**devtype)
         sched = get_scheduler(optim, settings["lr_scheduler"])
 
         model.train()

### 2019-12-02 experiments/auto/auto.py
FIX: explicit conversion of DelayedINterrupt to bool

@@ -317,10 +317,10 @@ def fit(model, objective, feed, optim, sched=None, n_epochs=100,
 
                 # abort on nan -- no need to waste compute
                 abort = np.isnan(epoch_loss[-1])
-                if abort or stop:
+                if abort or bool(stop):
                     break
 
-            if abort or stop:
+            if abort or bool(stop):
                 break
 
             if sched is not None:
@@ -340,4 +340,4 @@ def fit(model, objective, feed, optim, sched=None, n_epochs=100,
     history = dict(zip(objective.terms, term_values))
     history.update({"|g|": grad_norms})
 
-    return model.eval(), bool(abort or stop), history
+    return model.eval(), not (abort or bool(stop)), history

### 2019-12-02 experiments/musicnet/dataset.py
Special class for ram-resident musicnet

@@ -177,6 +177,40 @@ class MusicNetHDF5(torch.utils.data.Dataset):
         return repr(self.hdf5)
 
 
+class MusicNetRAM(MusicNetHDF5):
+    """Entirely RAM resident MusicNet dataset from an HDF5 file.
+
+    Parameters
+    ----------
+    filename : str
+        Path to an HDF5 file with the MusicNet dataset (special structure).
+
+    window : int, or tuple
+        The size of the window. If tuple, then specifies the number of samples
+        before `t` and after.
+
+    stride : int, default=1
+        The stride of the sliding window.
+
+    at : int, or None, default=None
+        The index within the `window` at which the targets are collected.
+        Should be thought of as the offset to time `t` in the window. Midpoint
+        of the window by default (None).
+
+    dtype : np.dtype, default=np.float32
+        The data type of the waveform windows and targets. Defaults to float32
+        for easier compatibility with torch.
+    """
+    def __init__(self, filename, window=4096, stride=512,
+                 at=None, dtype=np.float32):
+        super().__init__(h5py.File(filename, "r"), window=window,
+                         stride=stride, at=at, dtype=dtype,
+                         resident=True)
+
+    def __del__(self):
+        self.hdf5.close()
+
+
 class MusicNetWaveformCollation(object):
     """Batch collation with on-the-fly feature processing transforms.
 

### 2019-12-02 experiments/auto/auto.py
eliminated model factory, finished composite objective constructor, optim and sched getters

@@ -21,6 +21,8 @@ from .utils import feed_limiter, feed_mover
 from .utils import save_snapshot, load_snapshot
 from .utils import join, deploy_optimizer
 
+from .objective import ExpressionObjective, WeightedObjective
+
 from collections import namedtuple
 State = namedtuple("State", ["model", "optim", "mapper"])
 
@@ -90,34 +92,32 @@ def get_objective_terms(datasets, recipe):
     return objectives
 
 
-def get_model_factory(recipe):
-    """Partial constructor of the model. Assumes a particular common API."""
-    # "model"
-    raise NotImplementedError
-
-
 def get_model(factory, recipe):
-    """Partial constructor of the model. Assumes a particular common API."""
-    # <factory>, "stages__*__model"
-    raise NotImplementedError
+    """Construct the instance of a model from a two-part specification."""
+    # "model", "stages__*__model"
+    return get_instance(**factory, **recipe)
 
 
 def get_objective(objective_terms, recipe):
     """Construct the objective function from the recipe and components."""
     # <objective_terms>, "stages__*__objective"
-    raise NotImplementedError
+    if isinstance(recipe, dict):
+        return WeightedObjective(recipe, **objective_terms)
+
+    if isinstance(recipe, str):
+        return ExpressionObjective(recipe, **objective_terms)
 
 
 def get_optimizer(module, recipe):
     """Get the optimizer for the module from the recipe."""
     # <module>, "stages__*__optimizer"
-    raise NotImplementedError
+    return get_instance(module.parameters(), **recipe)
 
 
 def get_scheduler(optimizer, recipe):
     """Get scheduler for the optimizer and recipe."""
     # <optimizer>, "stages__*__lr_scheduler"
-    raise NotImplementedError
+    return get_instance(optimizer, **recipe)
 
 
 class FeedWrapper(object):
@@ -229,15 +229,13 @@ def run(options, folder, suffix, verbose=True):
 
     objective_terms = get_objective_terms(datasets, options["objective_terms"])
 
-    model_factory = get_model_factory(options["model"])
-
     stages, state = options["stages"], State(None, None, {})
     for n_stage, stage in enumerate(options["stage-order"]):
         settings = stages[stage]
         stage_backup = stage, copy.deepcopy(settings)
 
-        state = state_inherit(state_create(model_factory, settings, devtype),
-                              settings, old=state, **sparsity)
+        new = state_create(options["model"], settings, devtype)
[…]

### 2019-12-06 experiments/auto/auto.py
less strict special feed name filtering

@@ -71,7 +71,7 @@ def get_special_feeds(feeds, devtype, special):
     """Prepare feeds for special activities, like testing performance."""
     special_feeds = {}
     for name, feed in feeds.items():
-        if name in special:
+        if any(map(name.startswith, special)):
             special_feeds[name] = wrap_feed(feed, max_iter=-1, **devtype)
 
     # may be empty

### 2019-12-06 paper/paper.tex
abstract stub

@@
 \maketitle
+
+\begin{abstract}
+With continual miniaturization ever more applications of deep learning can be found in
+embedded systems. Common embedded applications include on-device image recognition and
+signal processing (audio and radio). We investigate complex-domain deep neural networks
+and complex-valued Bayesian compression thereof. To this end we conduct a large scale
+numerical study of complex-valued networks to assess quality - compression rate trade-off.
+The results of this study have direct implications for real-time signal processing
+throughput of embedded systems.
+\end{abstract}
 

### 2019-12-07 experiments/auto/auto.py
Special loader, sampler classes

@@ -56,8 +56,9 @@ def get_feeds(datasets, collate_fn, recipe):
 
     feeds = {}
     for name, par in recipe.items():
-        par = param_defaults(par, pin_memory=True)
-        feeds[name] = torch.utils.data.DataLoader(**par, collate_fn=collate_fn)
+        par = param_defaults(par, cls=str(torch.utils.data.DataLoader),
+                             pin_memory=True)
+        feeds[name] = get_instance(**par, collate_fn=collate_fn)
 
     return feeds
 

### 2019-12-07 experiments/musicnet/dataset.py

@@ -1,3 +1,4 @@
+import math
 import h5py
 import numpy as np
 
@@ -284,3 +285,45 @@ class MusicNetWaveformCollation(object):
             data = np.abs(z)
 
         return [*map(torch.from_numpy, (data, *rest))]
+
+
+class MusicNetRandomBatchSampler(object):
+    """Random batch sampler for MusicNet."""
+    def __init__(self, dataset, pregen=128):
+        assert isinstance(dataset, MusicNetHDF5)
+        self.dataset, self.pregen = dataset, pregen
+
+    def __iter__(self):
+        """Generate random indices within the range of each windowed waveform.
+        """
+        n_batches = (len(self) + self.pregen - 1) // self.pregen
+        for i in range(n_batches):
+            # construct a dict of keys and window indices
+            obj_ind = {}
+            for k, lim in self.dataset.limits.items():
+                # generate a sequence of samples indices for this object
+                obj_ind[k] = torch.randint(*lim, (self.pregen,)).tolist()
+
+            # take the next index from every object (pregen times)
+            yield from zip(*obj_ind.values())
+
+    def __len__(self):
+        # length by the longest key
+        return max(b - a for a, b in self.dataset.limits.values())
+
+
+class MusicNetDataLoader(torch.utils.data.DataLoader):
+    """A special DataLoader to avoid pre-populating memory (~10 Gb) with coslty
+    random permutaions, which are performed on __iter__ of the base sampler
+    class `torch.utils.data.sampler.RandomSampler`
+    """
+    def __init__(self, dataset, collate_fn, pin_memory=False, num_workers=0,
+                 timeout=0, worker_init_fn=None):
+        super().__init__(
+            dataset,
+            batch_sampler=MusicNetRandomBatchSampler(dataset),
+            num_workers=num_workers,
+            collate_fn=collate_fn,
+            pin_memory=pin_memory,
+            timeout=timeout,
+            worker_init_fn=worker_init_fn)

### 2019-12-09 experiments/auto/fit.py
backup prior to fit-on-epoch, handling fp-error in except calue, simpler formatting in verbose and checkoing eraly stopping before each fit

@@ -127,28 +127,27 @@ def fit(model, objective, feed, optim, sched=None, early=None,
     into `eval` mode afterwards.
     """
     model.train()
-    history, epoch_checkpoint = [], {}
+    history, model_backup = [], {}
     with tqdm.tqdm(range(n_epochs), disable=not verbose) as bar:
         def history_append(values):
             history.append(values)
             if verbose:
                 # format the components of the loss objective
-                *terms, grad_norm = values
-                terms = map("{:.2e}".format, terms)
-                status = repr(tuple(terms)).replace("'", "")
-                bar.set_postfix_str(f"{status} |g| {grad_norm:.1e}")
+                *terms, grad_norm = map("{:.2e}".format, values)
+                status = repr(terms).replace("'", "")
+                bar.set_postfix_str(f"{status} |g| {grad_norm}")
 
         # try-catch for graceful return
         try:
             for epoch in bar:
+                # checkpointer and early stopper steps
+                if early is not None:
+                    raise NotImplementedError
+
+                model_backup = state_dict_to_cpu(model.state_dict())
                 epoch_loss = fit_one_epoch(model, objective, feed, optim,
                                            grad_clip=grad_clip,
                                            callback=history_append)
-
-                # checkpointer and early stopper steps
-                epoch_checkpoint = state_dict_to_cpu(model.state_dict())
-                if early is not None:
-                    raise NotImplementedError
 
                 # scheduler step: the `.step` api isn't standardized
                 if sched is not None:
@@ -158,7 +157,8 @@ def fit(model, objective, feed, optim, sched=None, early=None,
                     else:
                         sched.step()
 
-        except FloatingPointError as e:
+        except FloatingPointError as e:  # thrown by fit_one_epoch
+            model.load_state_dict(model_backup)
             emergency = e
 
         except KeyboardInterrupt as e:
@@ -166,10 +166,6 @@ def fit(model, objective, feed, optim, sched=None, early=None,
 
         else:  # no exception raised, no loop broken out of -- no emergency
             emergency = None
-
-    if isinstance(emergency, FloatingPointError):
-        if epoch_checkpoint:
-            model.load_state_dict(epoch_checkpoint)
 
     # Collect histories of objective's components and the norm of the gradient
     *term_values, grad_norms = [np.empty(0)] * (len(objective.terms) + 1)

### 2019-12-09 paper/paper.tex
use term 'arithmetic complexity'; fixed the use of intractable

@@
 and optimization theory specific to deep networks, deploying in actual embedded hardware
-remains a challenge due to storage, real-time throughput, and numerical computational
+remains a challenge due to storage, real-time throughput, and arithmetic (computational)
 complexity restrictions \citep{he_amc:_2018}. Therefore compression methods for achieving
@@
 especially relevant.
-% Solving the storage and compute constraints encourages development of model compression
+% Solving the storage and artihmetic constraints encourages development of model compression
 % and sparsification methods, that focus on favourable tradeoff between performance and size.
@@
 methods tailored to $\cplx$-domain remain a niche field of research. Computational efficiency
-reduction methods such as quantization, integer-based arithmetic \citep{citation_needed},
+improvement methods such as quantization, integer-based arithmetic \citep{citation_needed},
 and distillation \citep{distillation} appear to be immediately applicable to $\cplx$-field.
@@
 \citet{monning_evaluation_2018} state,
-that $\cplx$-networks have less intuitive architectures, inherently higher numerical
+that $\cplx$-networks have less intuitive architectures, inherently higher arithmetic
 complexity due to multiplication in $\cplx$, that requires 3-4 floating point multiplications,
@@
 
-The posterior itself is computationally intractable, save for the relatively simple cases
-\citep{citation_needed}, and therefore exact inference is traded for tractability and scalability
-of Variational Inference. Instead of deriving $p(\omega \mid D)$ using the rule, this approach
-recasts posterior inference into variational optimization problem: finding $q$ that is close
-to $p(\omega \mid D)$ in terms of a proximity score $\rho$
+The posterior itself is intractable, save for the relatively simple cases \citep{citation_needed},
+and therefore exact inference is traded for tractability and scalability of Variational
+Inference. Instead of deriving $p(\omega \mid D)$ using the rule, this approach recasts
+posterior inference into variational optimization problem: finding $q$ that is close to
+$p(\omega \mid D)$ in terms of a proximity score $\rho$
 \begin{equation}  \label{eq:variational-progam}
@@
 based on the algebraic equivalence between $2 \times 2$ real matrices and complex numbers.
-Due to this constraint $\cplx$-networks have less expressive power for the same computation
+Due to this constraint $\cplx$-networks have less expressive power for the same arithmetic
 complexity compared to a $\real$-layer with twice as many inputs and outputs.

### 2019-12-09 experiments/auto/performance.py
early stopper prototype

@@ -5,6 +5,8 @@ This module is exceptionally task-specific, except for, probabily,
 """
 import math
 import numpy as np
+import torch
+import warnings
 
 from scipy.special import expit as sigmoid
 
@@ -78,18 +80,18 @@ def evaluate(model, feed, curves=False):
     out["precision"] = tp / np.maximum(tp + fp, 1)  # ~ P(y=1 \mid \hat{y}=1)
     out["recall"] = tp / np.maximum(tp + fn, 1)     # ~ P(\hat{y}=1 \mid y=1)
 
-    # Raw per output average precision (actually logits should suffice)
-    y_prob = sigmoid(logits)
+    # Raw per output average precision
     out["average_precision"] = average_precision_score(
-        y_true, y_prob, pos_label=1, average=None)
+        y_true, logits, pos_label=1, average=None)
 
     # Pooled AP (treating different outputs as one -- good?) -- slow
     out["pooled_average_precision"] = average_precision_score(
-        y_true.ravel(), y_prob.ravel(), pos_label=1, average=None)
+        y_true.ravel(), logits.ravel(), pos_label=1, average=None)
 
     # compute the curves
     out["ap_curves"] = {}
     if curves:
+        y_prob = sigmoid(logits)
         out["ap_curves"]["pooled"] = precision_recall_curve(
             y_true.ravel(), y_prob.ravel())
 
@@ -135,6 +137,10 @@ class ValueTracker(object):
         self.best_ = -math.inf if self.mode == "max" else math.inf
         self.wait_, self.hits_, self.history_ = 0, 0, []
 
+    @property
+    def is_waiting(self):
+        return self.wait_ < self.patience
+
     def is_worse(self, a, b):
         r"""Check if `a` is outside of the allowed tolerance of `b`."""
         delta = (a - b) if self.mode == "max" else (b - a)
@@ -153,5 +159,43 @@ class ValueTracker(object):
 
         self.history_.append(value)
 
+        # indicate reset ot the caller
+        return self.wait_ == 0
+
     def __bool__(self):
-        return self.wait_ >= self.patience
+        return not self.is_waiting
+
+
+class PooledAveragePrecisionEarlyStopper(ValueTracker):
+    """Raise StopIteration if the metric stops improving for several epochs
+    in a row.
+    """
+    def __init__(self, model, feed, cooldown=1, patience=10):
+        super().__init__(patience=patience, mode="max", rtol=1e-3, atol=1e-4)
+        self.model, self.feed, self.cooldown = model, feed, cooldown
+
[…]

### 2019-12-09 experiments/auto/auto.py
api calls to early stopper and early init

@@ -15,6 +15,7 @@ from scipy.special import logit
 from setuptools._vendor.packaging.version import Version
 
 from .performance import evaluate
+from .performance import PooledAveragePrecisionEarlyStopper
 
 from .utils import get_class, get_factory, get_instance
 from .utils import param_apply_map, param_defaults
@@ -140,6 +141,10 @@ def get_scheduler(optimizer, recipe):
     return get_instance(optimizer, **recipe)
 
 
+def get_early_stopper(model, special_feeds, recipe):
+    raise NotImplementedError
+
+
 def state_create(factory, settings, devtype):
     """Create a new state, i.e. model, optimizer and name-id mapper (for state
     inheritance below), from the settings and model factory.
@@ -263,10 +268,11 @@ def run(options, folder, suffix, verbose=True):
 
         # setup checkpointing and fit-time validation for early stopping
         # checkpointer, early_stopper = Checkpointer(...), EarlyStopper(...)
+        early = get_early_stopper(model, special_feeds, settings["early"])
 
         model.train()
         model, emergency, history = fit(
-            model, objective, feed, optim, sched,
+            model, objective, feed, optim, sched, early,
             n_epochs=settings["n_epochs"], grad_clip=settings["grad_clip"],
             verbose=verbose)
 

### 2019-12-09 experiments/auto/fit.py

@@ -144,7 +144,7 @@ def fit(model, objective, feed, optim, sched=None, early=None,
             for epoch in bar:
                 # checkpointer and early stopper steps
                 if early is not None:
-                    raise NotImplementedError
+                    early.step(epoch)
 
                 model_backup = state_dict_to_cpu(model.state_dict())
                 epoch_loss = fit_one_epoch(model, objective, feed, optim,
@@ -164,6 +164,9 @@ def fit(model, objective, feed, optim, sched=None, early=None,
             emergency = e
 
         except KeyboardInterrupt as e:
+            emergency = e
+
+        except StopIteration as e:  # thrown by early stopper
             emergency = e
 
         else:  # no exception raised, no loop broken out of -- no emergency

### 2019-12-09 experiments/auto/fit.py
keyworded sched and early

@@ -73,7 +73,7 @@ def fit_one_epoch(model, objective, feed, optim, grad_clip=0., callback=None):
     return losses
 
 
-def fit(model, objective, feed, optim, sched=None, early=None,
+def fit(model, objective, feed, optim, *, sched=None, early=None,
         n_epochs=100, grad_clip=0., verbose=True):
     """Fit a model to the objective on the data feed for specified number of
     epochs with optimizer, lr-schedule and gradient clipping.

### 2019-12-09 experiments/auto/auto.py
fleshed out early stopper instantiation

@@ -141,8 +141,11 @@ def get_scheduler(optimizer, recipe):
     return get_instance(optimizer, **recipe)
 
 
-def get_early_stopper(model, special_feeds, recipe):
-    raise NotImplementedError
+def get_early_stopper(model, feeds, recipe):
+    """Get scheduler for the optimizer and recipe."""
+    # <model>, <feeds>, "stages__*__early"
+    recipe = param_apply_map(recipe, feed=feeds.__getitem__)
+    return PooledAveragePrecisionEarlyStopper(model, **recipe)
 
 
 def state_create(factory, settings, devtype):
@@ -268,11 +271,13 @@ def run(options, folder, suffix, verbose=True):
 
         # setup checkpointing and fit-time validation for early stopping
         # checkpointer, early_stopper = Checkpointer(...), EarlyStopper(...)
-        early = get_early_stopper(model, special_feeds, settings["early"])
+        early = None
+        if "early" in settings:
+            early = get_early_stopper(model, special_feeds, settings["early"])
 
         model.train()
         model, emergency, history = fit(
-            model, objective, feed, optim, sched, early,
+            model, objective, feed, optim, sched=sched, early=early,
             n_epochs=settings["n_epochs"], grad_clip=settings["grad_clip"],
             verbose=verbose)
 

### 2019-12-09 experiments/auto/fit.py
lr history tracker

@@ -62,7 +62,9 @@ def fit_one_epoch(model, objective, feed, optim, grad_clip=0., callback=None):
 
         losses.append(float(loss))
         if callable(callback):
-            callback((*objective.component_values_, grad_norm))
+            # track zero-th parameter group's learning rate
+            lrs = [group.get("lr", np.nan) for group in optim.param_groups]
+            callback((*objective.component_values_, grad_norm, lrs[0]))
 
         # abort on nan -- no need to waste compute
         if np.isnan(losses[-1]):
@@ -133,9 +135,9 @@ def fit(model, objective, feed, optim, sched=None, early=None,
             history.append(values)
             if verbose:
                 # format the components of the loss objective
-                *terms, grad_norm = map("{:.2e}".format, values)
+                *terms, grad_norm, lr = map("{:.2e}".format, values)
                 status = repr(terms).replace("'", "")
-                bar.set_postfix_str(f"{status} |g| {grad_norm}")
+                bar.set_postfix_str(f"{status} |g| {grad_norm} lr {lr}")
 
         # try-catch for graceful return
         try:
@@ -168,12 +170,12 @@ def fit(model, objective, feed, optim, sched=None, early=None,
             emergency = None
 
     # Collect histories of objective's components and the norm of the gradient
-    *term_values, grad_norms = [np.empty(0)] * (len(objective.terms) + 1)
+    *term_values, grad_norms, lr = [np.empty(0)] * (len(objective.terms) + 2)
     if history:
-        *term_values, grad_norms = map(np.array, zip(*history))
+        *term_values, grad_norms, lr = map(np.array, zip(*history))
 
     history = dict(zip(objective.terms, term_values))
-    history.update({"|g|": grad_norms})
+    history.update({"|g|": grad_norms, "lr": lr})
 
     model.eval()
     return model, emergency, history

### 2019-12-09 experiments/auto/performance.py
saving history of values in tracker

@@ -133,7 +133,7 @@ class ValueTracker(object):
 
     def reset(self):
         self.best_ = -math.inf if self.mode == "max" else math.inf
-        self.wait_, self.hits_ = 0, 0
+        self.wait_, self.hits_, self.history_ = 0, 0, []
 
     def is_worse(self, a, b):
         r"""Check if `a` is outside of the allowed tolerance of `b`."""
@@ -150,6 +150,8 @@ class ValueTracker(object):
 
         else:
             self.best_, self.wait_, self.hits_ = current, 0, self.hits_ + 1
+
+        self.history_.append(value)
 
     def __bool__(self):
         return self.wait_ >= self.patience

### 2019-12-09 experiments/auto/auto.py
check if early is None in the manifest

@@ -272,7 +272,7 @@ def run(options, folder, suffix, verbose=True):
         # setup checkpointing and fit-time validation for early stopping
         # checkpointer, early_stopper = Checkpointer(...), EarlyStopper(...)
         early = None
-        if "early" in settings:
+        if "early" in settings and settings["early"] is not None:
             early = get_early_stopper(model, special_feeds, settings["early"])
 
         model.train()

### 2019-12-10 experiments/auto/auto.py
made early stopping not an emergency, saving validation history

@@ -306,6 +306,7 @@ def run(options, folder, suffix, verbose=True):
             # meta data
             history=history,
             performance=performance,
+            early_history=np.array(getattr(early, "history_")),
             options=options_backup,
             stage=stage_backup,
 

### 2019-12-10 experiments/auto/fit.py

@@ -167,7 +167,7 @@ def fit(model, objective, feed, optim, *, sched=None, early=None,
             emergency = e
 
         except StopIteration as e:  # thrown by early stopper
-            emergency = e
+            emergency = None  # e  # Early Stopping is not an emergency
 
         else:  # no exception raised, no loop broken out of -- no emergency
             emergency = None

### 2019-12-27 fragments/wolter_yao_2018.tex
excerpts from Wolter, Yao (2018)

(experiment)
For musicnet they use FFT features from a sliding window of size 2048 with stirde
512 and perform 128-multioutput classification (unlike Trabelsi who predicct 84).

They study various gating functions on neural addition problem.

(on complex networks)
They refrain the general sentiment that the key advantage of complex-valued networks
against paired (double-dim) real networks, is the intrinsic regularization induced by
complex arithemtic operations.

A complex number $z\in \mathbb{C}$ as represented as $z = u + j v$ for reals $u, v$
with $u = \Re z$ and $v = \Im z$. The complex conjugate $\overline{z} = u - j v$, and
polar representation of $z = \lvert z \rvert e^{j \theta}$ where the $\theta$ is the
phase (argument $\arg z$, angle $\angle z$) and $\lvert z \rvert$ is the modulus
(magnitude).

The nonlinearities proposed in the earlier literature are known as the split-complex
approach, whereby a function is appled to real and imaginary components, or phase and
magnitude of a complex number separately. \citet{hirose_complex_2009} proposed 
$$
\sigma_b(z)
    = \tanh{\Bigl(\frac{\lvert z \rvert}{b}\Bigr)}
        \frac{\overline{z}}{\lvert z \rvert}  % why do they use conjugate?
\,, $$
and \citet{arjovsky_unitary_2016} used a ReLU varinot of Hirose's activation: modRelU
$$
\sigma_b(z)
    = \max{\bigl\{0, \lvert z \rvert + b\bigr\}}
        \frac{\overline{z}}{\lvert z \rvert}
\,. $$
To transform outputs from $\mathbb{C}$ to $\mathbb{R}$, \citet{wolter_complex_2018}
propose to use
$$
\mathbb{C}^n \to \mathbb{R}^m
    \colon z \mapsto W_r \Re z + W_i \Im z + b
    \,, $$
with $W_r, W_i \in \mathbb{R}^{m \times n}$.

(on rnns)
Propose novel complex-valued gating mechanism to unitary-RNN of Wisdom et al. (2016).
Investigate the effects of different gating mechanisms and conduct experiments on human
motion prediction adn MusicNet. End up getting 53\% AP in the latter.

Study gating mechanisms since they are one of the common heuristics, employed to
stabilize RNN training (vanishing or exploding grads). Gates adaptively protect the
cell state from bad updates, tha may cause instability. Besides gating, there are
gradient clipping, norm-preserving state transition matrices (unitary / orthogonal).

The studied gates include 
$$
\sigma_b(z)
    = \sigma(\alpha \Re z + \beta \Im z)
    \,, \alpha,\beta \in [0, 1] 
\,. $$
% Vanishing gradients are disrtibuted over a sum, exploding are clipped.

(on norm-preservation)
they cite \citep{arjovsky_unitary_2016}, 
Observe that for a scalar-valued function $f \colon \mathbb{C}^{n\times k} \to \mathbb{R}$
with $J_z = \nabla_z f$ and $J_{\overline{z}} f =  \nabla_{\overline{z}} f$, and
$W \in \mathbb{C}^{d \times k}$ by $\mathbb{CR}$-calculus we have
$$
\partial f
    = \mathop{tr} J_z^H \bigl((\partial x) W + x \partial W\bigr)
    + \mathop{tr} J_{\overline{z}}^H \bigl(
        (\partial \overline{x}) \overline{W}
        + \overline{x} \partial \overline{W}
    \bigr)
    \,, $$
whence
$$ 
\tfrac{\partial f(x W)}{\partial x}
    = J_{\overline{z}} W^H \Big\vert_{z = xW}
    \,, \tfrac{\partial f(x W)}{\partial \overline{x}}
        = J_{z} W^\top \Big\vert_{z = xW}
    \,. $$

Thus to preserve backwards gradinets and ensure forward stability in the case of $d=k$
the operator norm of $W$ should be $1$.

### 2019-12-27 experiments/auto/auto.py
weight reset option in state_inherit

@@ -9,7 +9,7 @@ import torch
 import numpy as np
 
 from cplxmodule.nn.relevance import compute_ard_masks
-from cplxmodule.nn.masked import binarize_masks
+from cplxmodule.nn.masked import binarize_masks, deploy_masks
 
 from scipy.special import logit
 from setuptools._vendor.packaging.version import Version
@@ -259,11 +259,19 @@ def state_inherit(state, options, *, old=None, **sparsity_kwargs):
         state_dict, masks = binarize_masks(old.model.state_dict(), masks)
         state_dict.update(masks)
 
-        # Models in each stage are instances of the same underlying
-        #  architecture just with different traits. Hence only here
-        #  we allow missing or unexpected parameters when deploying
-        #  the state
-        state.model.load_state_dict(state_dict, strict=False)
+        if options["reset"]:
+            # Explicitly instructed to transfer masks only (if available).
+            #  `reset=True` makes sure that every mask in the receiving
+            #  model is initialized. A forward pass thorugh a model with
+            #  an uninitialized mask would raise a RuntimeError.
+            deploy_masks(state.model, state_dict=masks, reset=True)
+
+        else:
+            # Models in each stage are instances of the same underlying
+            #  architecture just with different traits. Hence only here
+            #  we allow missing or unexpected parameters when deploying
+            #  the state
+            state.model.load_state_dict(state_dict, strict=False)
 
         del state_dict, masks
 

### 2019-12-27 experiments/auto/auto.py
default reset settings

@@ -90,12 +90,13 @@ def defaults(options):
                 "amsgrad": False
             },
             "restart": False,
+            "reset": False,
             **settings
         })
         assert all(key in settings for key in [
             "model", "n_epochs", "objective", "feed",
             "grad_clip", "snapshot", "lr_scheduler",
-            "optimizer", "restart", "early"
+            "optimizer", "restart", "early", "reset"
         ])
 
     return options

### 2019-12-27 experiments/auto/auto.py
careful fit emergency handling

@@ -31,6 +31,8 @@ from .objective import ExpressionObjective, WeightedObjective
 from collections import namedtuple
 State = namedtuple("State", ["model", "optim", "mapper"])
 
+benign_emergencies = (StopIteration, type(None))
+
 
 def defaults(options):
     options = copy.deepcopy(options)
@@ -360,7 +362,9 @@ def run(options, folder, suffix, verbose=True):
                                for name, feed in special_feeds.items()}
 
         # save snapshot
-        status = "TERMINATED " if emergency else ""
+        status = "" if emergency is None else type(emergency).__name__
+        is_benign = isinstance(emergency, benign_emergencies)
+
         final_snapshot = save_snapshot(
             os.path.join(folder, f"{status}{n_stage}-{stage} {suffix}.gz"),
 
@@ -369,8 +373,8 @@ def run(options, folder, suffix, verbose=True):
             optim=dict(
                 cls=str(type(state.optim)),
                 state=state.optim.state_dict()
-            ) if emergency is None else None,
-            mapper=state.mapper if emergency is None else None,
+            ) if is_benign else None,
+            mapper=state.mapper if is_benign else None,
 
             # meta data
             history=history,
@@ -387,7 +391,7 @@ def run(options, folder, suffix, verbose=True):
         snapshots.append(final_snapshot)
 
         # emergency termination: cannot continue
-        if emergency:
+        if not is_benign:
             break
 
     return snapshots

### 2019-12-27 experiments/auto/fit.py

@@ -161,13 +161,13 @@ def fit(model, objective, feed, optim, *, sched=None, early=None,
 
         except FloatingPointError as e:  # thrown by fit_one_epoch
             model.load_state_dict(model_backup)
-            emergency = e
+            emergency = e  # encountered wild model instability
 
         except KeyboardInterrupt as e:
-            emergency = e
+            emergency = e  # user requested fit loop termination
 
         except StopIteration as e:  # thrown by early stopper
-            emergency = None  # e  # Early Stopping is not an emergency
+            emergency = e  # Early Stopping is a benign `emergency`
 
         else:  # no exception raised, no loop broken out of -- no emergency
             emergency = None

### 2019-12-27 setup.py
restructured and setup for easier deployment

@@ -1,0 +1,20 @@
+from distutils.core import setup, Extension
+
+setup(
+    name="cplxpaper",
+    version="0.1",
+    description="""Package for Bayesian Sparsification """
+                """of Complex Valued Networks.""",
+    license="MIT License",
+    author="Ivan Nazarov",
+    author_email="ivan.nazarov@skolkovotech.ru",
+    packages=[
+        "cplxpaper",
+        "cplxpaper.auto",
+        "cplxpaper.musicnet"
+    ],
+    requires=["torch", "numpy", "pandas", "cplxmodule"],
+    # install_requires=[  # uncomment for publishing
+    #     "cplxmodule @ git+https://github.com/ivannz/cplxmodule.git"
+    # ]
+)

### 2019-12-27 cplxpaper/auto/__init__.py
expose auto.run

@@ -1,2 +1,3 @@
+from .auto import run
 from .fit import fit
 from .delayed import DelayedKeyboardInterrupt

### 2019-12-27 cplxpaper/auto/__main__.py
experiment runner as main of .auto

@@ -1,0 +1,119 @@
+import os
+import json
+
+import argparse
+
+from multiprocessing import Process, JoinableQueue, Array
+
+
+def acquire(array):
+    """Acquire resources from a budget."""
+    while True:
+        with array.get_lock():
+            # get the largest counter
+            ix = max(range(len(array)), key=array.__getitem__)
+            if array[ix] > 0:
+                # acquire the index and decrease the counter
+                array[ix] -= 1
+                break
+
+        # Busy wait on a next nonzero counter. This works fine if jobs are
+        #  few and long. But there should be a better way with `asyncio`!
+        pass
+    return ix
+
+
+def release(array, ix):
+    """Release resources to the budget."""
+    with array.get_lock():
+        array[ix] += 1
+
+
+def one_experiment(wid, device, manifest):
+    # Import torch inside this function, because it is called in a subprocess.
+    # This makes sure that torch's RNG context is initialized afresh.
+    import torch
+
+    from cplxpaper.auto import run
+
+    # open manifest
+    options = json.load(open(manifest, "r"))
+    options["device"] = device
+
+    # create the target folder
+    path = os.path.dirname(manifest)
+    name = os.path.basename(manifest)
+
+    name, ext = os.path.splitext(name)
+    target = os.path.join(path, name)
+
+    # run the experiment
+    if not os.path.exists(target):
+        print(f">>> {wid:03d}-{device} {name}")
+#         run(options, target, time.strftime("%Y%m%d-%H%M%S"), verbose=False)
+
+
+def worker(wid, jobs, devarray, devices):
+    """Poll the job queue and dispatch to a device."""
+    job = jobs.get()
+    while job is not None:
+        # Acquire the next free device for this job and make sure the
+        #  resources are released.
+        devid = acquire(devarray)
+        try:
+            one_experiment(wid, devices[devid], job)
+
+        finally:
+            release(devarray, devid)
+            jobs.task_done()
+
+        job = jobs.get()
+
+    jobs.task_done()
+
+
+def main(path, devices=("cuda:1", "cuda:3"), n_per_device=2):
+    # create a pool of workers and a device availability array
+    workers, manifests = [], JoinableQueue()
+    devarray = Array("i", len(devices) * [n_per_device])
+    for device in n_per_device * devices:
+        p = Process(target=worker, args=(
+            len(workers), manifests, devarray, devices))
+        p.start()
+        workers.append(p)
+
[…]

### 2019-12-27 cplxpaper/auto/__main__.py
uncomment runner

@@ -1,4 +1,5 @@
 import os
+import time
 import json
 
 import argparse
@@ -33,7 +34,6 @@ def one_experiment(wid, device, manifest):
     # Import torch inside this function, because it is called in a subprocess.
     # This makes sure that torch's RNG context is initialized afresh.
     import torch
-
     from cplxpaper.auto import run
 
     # open manifest
@@ -50,7 +50,7 @@ def one_experiment(wid, device, manifest):
     # run the experiment
     if not os.path.exists(target):
         print(f">>> {wid:03d}-{device} {name}")
-#         run(options, target, time.strftime("%Y%m%d-%H%M%S"), verbose=False)
+        run(options, target, time.strftime("%Y%m%d-%H%M%S"), verbose=False)
 
 
 def worker(wid, jobs, devarray, devices):
@@ -72,13 +72,14 @@ def worker(wid, jobs, devarray, devices):
     jobs.task_done()
 
 
-def main(path, devices=("cuda:1", "cuda:3"), n_per_device=2):
+def main(path, devices=("cuda:1", "cuda:3"), n_per_device=1):
     # create a pool of workers and a device availability array
     workers, manifests = [], JoinableQueue()
     devarray = Array("i", len(devices) * [n_per_device])
     for device in n_per_device * devices:
         p = Process(target=worker, args=(
-            len(workers), manifests, devarray, devices))
+            len(workers), manifests, devarray, devices
+        ))
         p.start()
         workers.append(p)
 
@@ -106,11 +107,13 @@ def main(path, devices=("cuda:1", "cuda:3"), n_per_device=2):
     print(">>> complete")
 
 
-parser = argparse.ArgumentParser(add_help=True, description='Auto experiment runner')
+parser = argparse.ArgumentParser(description='Auto experiment runner',
+                                 add_help=True)
 parser.add_argument('path', type=str, help='the path to all manifests')
-parser.add_argument('--devices', default=("cuda:1", "cuda:3"),
-                    type=str, nargs='+', help='allowed devices', required=False)
-parser.add_argument('--per-device', default='2', type=int, required=False)
+parser.add_argument('--devices', type=str, nargs='+',
+                    default=("cuda:1", "cuda:3"), required=False,
+                    help='allowed devices')
+parser.add_argument('--per-device', type=int, default=1, required=False)
 
 args = parser.parse_args()
 

### 2019-12-27 cplxpaper/auto/__main__.py
create target folder

@@ -49,6 +49,8 @@ def one_experiment(wid, device, manifest):
 
     # run the experiment
     if not os.path.exists(target):
+        os.makedirs(target, exist_ok=False)
+
         print(f">>> {wid:03d}-{device} {name}")
         run(options, target, time.strftime("%Y%m%d-%H%M%S"), verbose=False)
 

### 2019-12-27 cplxpaper/auto/auto.py
fixed imported objects, and snapshot naming

@@ -363,10 +363,12 @@ def run(options, folder, suffix, verbose=True):
 
         # save snapshot
         status = "" if emergency is None else type(emergency).__name__
+        status += " " if status else ""
+
         is_benign = isinstance(emergency, benign_emergencies)
 
         final_snapshot = save_snapshot(
-            os.path.join(folder, f"{status}{n_stage}-{stage} {suffix}.gz"),
+            os.path.join(folder, f"{n_stage}-{stage} {status}{suffix}.gz"),
 
             # state
             model=state.model.state_dict(),

### 2019-12-27 cplxpaper/auto/auto.py
fix -- absent early stopper

@@ -381,7 +381,7 @@ def run(options, folder, suffix, verbose=True):
             # meta data
             history=history,
             performance=performance,
-            early_history=np.array(getattr(early, "history_")),
+            early_history=np.array(getattr(early, "history_", [])),
             options=options_backup,
             stage=stage_backup,
 

### 2019-12-27 cplxpaper/auto/auto.py
handle missing optimizer state in inherit()

@@ -241,11 +241,12 @@ def state_inherit(state, options, *, old=None, **sparsity_kwargs):
 
         # get the saved state of the optimizer and a name-id map
         saved = snapshot.get("optim", {})
-        optim_state = saved.get("state", {})
-        source_mapper = snapshot.get("mapper", {})
+        if saved is not None:
+            optim_state = saved.get("state", {})
+            source_mapper = snapshot.get("mapper", {})
 
-        # see if stored state an state.optim's state are compatible
-        inheritable = isinstance(state.optim, get_class(saved.get("cls")))
+            # see if stored state an state.optim's state are compatible
+            inheritable = isinstance(state.optim, get_class(saved.get("cls")))
 
         # overwrite the parameters and buffers of the model
         state.model.load_state_dict(snapshot["model"], strict=True)

### 2019-12-27 cplxpaper/auto/__main__.py
option to disable saving optimizer state

@@ -117,6 +117,10 @@ parser.add_argument('--devices', type=str, nargs='+',
                     help='allowed devices')
 parser.add_argument('--per-device', type=int, default=1, required=False)
 
+# parser.add_argument('--save-optim', dest='save_optim', action='store_true')
+# parser.add_argument('--no-save-optim', dest='save_optim', action='store_false')
+# parser.set_defaults(save_optim=True)
+
 args = parser.parse_args()
 
 path = args.path

### 2019-12-27 cplxpaper/auto/auto.py

@@ -295,7 +295,7 @@ def state_inherit(state, options, *, old=None, **sparsity_kwargs):
     return state
 
 
-def run(options, folder, suffix, verbose=True):
+def run(options, folder, suffix, verbose=True, save_optim=False):
     """The main procedure that choreographs staged training.
 
     Parameters
@@ -376,8 +376,8 @@ def run(options, folder, suffix, verbose=True):
             optim=dict(
                 cls=str(type(state.optim)),
                 state=state.optim.state_dict()
-            ) if is_benign else None,
-            mapper=state.mapper if is_benign else None,
+            ) if (is_benign and save_optim) else None,
+            mapper=state.mapper if (is_benign and save_optim) else None,
 
             # meta data
             history=history,

### 2019-12-28 cplxpaper/auto/auto.py
can still evaluate performance in case of benign emergency

@@ -353,10 +353,12 @@ def run(options, folder, suffix, verbose=True, save_optim=False):
             n_epochs=settings["n_epochs"], grad_clip=settings["grad_clip"],
             verbose=verbose)
 
-        # Evaluate the performance on the reserved feeds, e.g. `test`.
+        is_benign_emergency = isinstance(emergency, benign_emergencies)
+
+        # Evaluate the performance on the reserved feeds, e.g. 'test*'.
         model.eval()
         performance = {}
-        if emergency is None:
+        if is_benign_emergency:
             # Ignore warnings: no need to `.filter()` when `record=True`
             with warnings.catch_warnings(record=True):
                 performance = {name: evaluate(model, feed, curves=False)
@@ -365,9 +367,6 @@ def run(options, folder, suffix, verbose=True, save_optim=False):
         # save snapshot
         status = "" if emergency is None else type(emergency).__name__
         status += " " if status else ""
-
-        is_benign = isinstance(emergency, benign_emergencies)
-
         final_snapshot = save_snapshot(
             os.path.join(folder, f"{n_stage}-{stage} {status}{suffix}.gz"),
 
@@ -376,8 +375,8 @@ def run(options, folder, suffix, verbose=True, save_optim=False):
             optim=dict(
                 cls=str(type(state.optim)),
                 state=state.optim.state_dict()
-            ) if (is_benign and save_optim) else None,
-            mapper=state.mapper if (is_benign and save_optim) else None,
+            ) if (is_benign_emergency and save_optim) else None,
+            mapper=state.mapper if (is_benign_emergency and save_optim) else None,
 
             # meta data
             history=history,
@@ -394,7 +393,7 @@ def run(options, folder, suffix, verbose=True, save_optim=False):
         snapshots.append(final_snapshot)
 
         # emergency termination: cannot continue
-        if not is_benign:
+        if not is_benign_emergency:
             break
 
     return snapshots

### 2020-01-13 fragments/hirose_2009.tex
sumary of Hirose (2009)

Discussion and motivation of CVNN in comparison to double real networks

(Hirose 2009)
Features extensive list of applications of CVNNs (complex valued neural networks):
- ultrasonic fault detection in materials, sonar data, voice processing
- filtering and time-sequential signal processing
- frequency domain mutliplexed microwave signal processing
- pulse beam forming in ultra-wideband communications
- satellite imaging
- image processing
- ground penetrating radar system for landmine detection (buried shallowly)

(merits of CVNN)
Hirose argues that the key merit of CVNN is the built-in (embedded) regularization from
complex arithmetic, esp. multiplication, which does simultaneous phase rotation and amplitude
amplification/attenuation. This reduces ineffective degrees of freedom in comparison
with double-dimensional (paired) real-valued network.

(nature of non-linearities)
argue that cplx non-differentiability is not an issue

Depend on the nature of the signal to be treated wave-related complex signals.
Amplitude-phase type non-linearities

conformal mapping nature of the holomorphic function (mapping structure itself, rather than a combination with some non-linearity)

the non-linearities most promising candidates in CVNNs are usually split, i.e. applied independently to the components of a
complex number, be it real and imaginary (in planar), or phase and amplitude (in polar).

### 2020-01-13 fragments/wisdom_et_al_2016.tex
minor review of Wisdom-etal2016

(wisdom_full-capacity_2016)
Recurrent nn suffer from vanishing/exploding gradients due to repeated use of the parameter matrix
which affects forward pass and backprop via layers' input gradients.

remedies included gradient clipping, orthogonal initializations, novel architectures with
gated, residual, or attention based pathways.

unitary recurrent weight matrices make the gradient inherently stable \citep{arjovsky_unitary_2016}
Illustrate on pixel-by-pixel mnist

This paper shows the limitations of Arjovsky's parameterization and argues in favour of fully fledged
optimization on the Stiefel manifold, i.e. the differentiable manifold of $\cplx^{n \times n}$ unitary
matrices.

### 2020-01-13 fragments/wisdom_et_al_2016.tex
merged in fragments of arjovsky et al 2016

@@
 matrices.
+
+(arjovsky_unitary_2016)
+vanishing gradients adversely affect credit assignment function of backpropagation
+explicitly derive the upper bound on the norm of the gradient wrt intermediate recurrent outputs
+as a a function of depth (through extensive use of the chain-rule, and the definition of the
+operator norm of a square matrix; and if intermediate output grads die/explode, then the grad wrt
+the weight of the layers tends to die/explode). Thus they motivate the use of unitary (orthogonal)
+weight matrices.
+
+Note that in their experiments, split-re-im ReLU adversely affected the performance by
+``brutally'' destroying the pahse, and so the decision was made to use modReLU, that applies
+the rectifier to the amplitude of a complex number.
+
+Finally, they use a mixing layer to transform complex to real outputs as in \cite{wolter_yao_2018}.

### 2020-01-15 paper/paper.tex
proof read the text, reworded some phrases

@@
 Dropout, \citep{hinton_improving_2012}, prevents overfitting by injecting multiplicative
-binary noise into layer's weights, thereby breaking up co-adaptations that could occur
+binary noise into layer's weights, which breaks up co-adaptations that could occur
 during training. \citet{wang_fast_2013} argue that the overall effect of binary dropout
@@
 the posterior distribution. \citet{kingma_variational_2015} specifically consider dropout
-as a Bayesian inference technique. Bayesian Inference as a principled framework of reasoning
-about uncertainty, updates prior beliefs in accordance with the likelihood of empirical
-observations into posterior belief. Under suitable modelling and prior assumptions, Bayesian
-methods can be used towards model sparsification, \citep{kingma_variational_2015,molchanov_variational_2017},
+as a Bayesian Inference technique: a principled framework of reasoning about uncertainty,
+whihc updates prior beliefs in accordance with the likelihood of empirical observations
+into posterior belief. Under suitable modelling and prior assumptions, Bayesian methods
+can be used towards model sparsification, \citep{kingma_variational_2015,molchanov_variational_2017},
 and \citep{kharitonov_variational_2018}.
@@
 Therefore it appears that Bayesian and stochastic sparsification techniques can be useful
-for models in $\cplx$ domain. \verify{$\ell_0$ -- stoch?}
+for models in $\cplx$ domain. \verify{$\ell_0$ -- stoch? yes}
 
@@
 The paper is structured as follows. In sec.~\ref{sec:bayesian_dropout} we review Bayesian
-dropout techniques, and ins sec.~\ref{sec:c_valued_networks} we provide a brief summary of
+dropout techniques, and in sec.~\ref{sec:c_valued_networks} we provide a brief summary of
 the inner working of complex-valued networks as functions of complex argument. The main
@@
 $D$ to update the assumptions by considering the likelihood of the observations under each
-$m \in \mathcal{M}$. Models are represented by a parametric family indexed by $\omega \in
-\Omega$ and each $m_\omega(\cdot)$ specifies the conditional distribution of the data $
+$m \in \mathcal{M}$. Models are represented by a parametric family indexed by parameters
+$\omega \in \Omega$ and each $m_\omega(\cdot)$ specifies the conditional distribution of
+the data $
   D = (z_i)_{i=1}^N
@@
 The posterior itself is intractable, save for the relatively simple cases \citep{citation_needed},
-and therefore exact inference is traded for tractability and scalability of Variational
+and therefore exact inference is traded for tractability and scalability offered by Variational
 Inference. Instead of deriving $p(\omega \mid D)$ using the rule, this approach recasts
@@
 % % http://stillbreeze.github.io/REINFORCE-vs-Reparameterization-trick/#fn:1
-
-Kullback-Leibler divergence of density $q$ from $p$ is
+%
+The natural choice for $\rho$ is Kullback-Leibler divergence of density $q$ from $p$,
 \begin{equation}  \label{eq:kl-div-def}
@@
 % and, despite it not being a metric and requiring distributions with nested support,
-and is the natural choice for $\rho$, the main reason being that it satisfies the following
-identity for well-behaved densities:
+the main reason being that it satisfies the following identity for well-behaved densities:
+% $(q, p, \pi)$
 \begin{multline}  \label{eq:kl-div-master}
@@
 \textit{Stochastic Gradient Variational Bayes} (SGVB), proposed by \citep{kingma_auto-encoding_2014},
-is a differentiable unbiased Monte-Carlo estimator of \eqref{eq:elbo_general}, which makes
-it possible to employ stochastic gradient-based optimization methods. If $
+is a differentiable unbiased Monte-Carlo estimator of \eqref{eq:elbo_general}, which
+makes it possible to employ stochastic gradient-based optimization methods to solve
+\eqref{eq:variational-progam}. If $
   \omega \sim q_{\theta}
@@
 
-With special family of posterior approximation, variational inference can be used as
+With a special family of posterior approximation, variational inference can be used as
 a regularization method and as model sparsification technique. \citet{kingma_variational_2015}
-consider Dropout \citep{hinton_improving_2012}, DropConnect, \citep{wan_regularization_2013},
-and Gaussian dropout, \citep{srivastava_dropout_2014,wang_fast_2013} through the lens
+consider Dropout \citep{hinton_improving_2012}, DropConnect \citep{wan_regularization_2013},
+and Gaussian dropout \citep{srivastava_dropout_2014,wang_fast_2013} through the lens
 of Bayesian inference methods and proposes \textit{Variational Dropout}. They argue that
@@
   \pi(\omega_j) \propto \lvert \omega_j \rvert^{-1}
-$. This unravels the divergence term in \eqref{eq:elbo} into a sum of the following
+$. The divergence term in \eqref{eq:elbo} unravels into a sum of the following
 analytically intractable terms:
@@
 \citet{kingma_variational_2015} approximate this expression by a non-linear polynomial
-regression for \verify{truncated} $\alpha \in (0, 1)$. \citet{molchanov_variational_2017}
-refine the approximation by using sigmoid and soft-plus basis functions.
+regression for truncated $\alpha \in (0, 1)$. \citet{molchanov_variational_2017}
+refine the approximation by using a nonlinear regression based on sigmoid and soft-plus.
+% see p.6 sec 3.4 of kingma_variational_2015
 %
@@
 
-Flexibility in specification of $q_\theta$ enables structured dropout with shared
-$\alpha$ across groups of parameters $\omega$. \citet{molchanov_variational_2017} study
-Variational Dropout from a model sparsification perspective, optimizing $\alpha$ for each
-individual parameter. Another variant of Bayesian dropout, called \textit{Automatic Relevance
-Determination}, is developed in \citep{kharitonov_variational_2018}. The key difference is
-that the log-uniform factor $\pi(\omega_{ij})$ is replaced by a proper Gaussian prior $
+Being the ratio of the squared mean to the effective variance, $\alpha_j$ regulates the
+relevance of the parameter $\omega_j$ it is associated to. Thus \citet{molchanov_variational_2017}
+focus on the model sparsification capabilities of Variational Dropout, optimizing $\alpha$
+for each individual parameter. Flexibility in specification of $q_\theta$ enables structured
+dropout with shared $\alpha$ across groups of parameters $\omega$. Another variant of Bayesian
+dropout, called \textit{Automatic Relevance Determination}, is developed in \citep{kharitonov_variational_2018}.
+The key difference is that the log-uniform factor $\pi(\omega_{ij})$ is replaced by a proper
+Gaussian prior $
   \mathcal{N}(0, \tau^{-1}_{ij})
@@
 efficient. \citet{molchanov_variational_2017} propose an improvement by introducing
-\textit{additive noise parameterization}, which is relevant to model sparsification.
-They argue that $(\mu, \alpha)$ parameterization should be abandoned in favour of an
-equivalent $(\mu, \sigma^2)$ with the score $\alpha$ calculated using $
+\textit{additive noise parameterization}. They argue in favour of abandoning the
+$(\mu, \alpha)$ parameterization in favour of an equivalent $(\mu, \sigma^2)$, since
+the latter renders $
+  \nabla_\mu \tilde{\mathcal{L}}
+$ independent from the local output noise, injected by the trick \eqref{eq:r-gauss-trick},
+and further stabilizes gradients in SGVB \eqref{eq:elbo}. The relevance $\alpha$ is
+calculated using $
   \tfrac{\sigma^2}{\mu^2}
-$ when needed. This makes $
-  \nabla_\mu \tilde{\mathcal{L}}
-$, which is shown in \citep{molchanov_variational_2017} to be independent of the noise,
-injected by the trick \eqref{eq:r-gauss-trick}, and further stabilizes gradients in SGVB
-\eqref{eq:elbo}.
+$ when needed.
 
@@
 Their approach makes a complex-valued network into an intricately connected $\real$-valued
-computational graph that respects $\cplx$-algebra.
-
+computational graph that respects $\cplx$-arithmetic.
+%
 In particular, natural identification of $\cplx$ and $\real^2$ implies that linear layers $
@@
 \eqref{eq:cplx-lin-op}. Algebraic operations, trigonometric functions, are implemented
-through operations in $\real^2$. Activations, considered in \citep{trabelsi_deep_2017} include
-independent componentwise application of $\real$-valued non-linearities, $
+through operations in $\real^2$, \citep{hirose_complex-valued_2009}. Activations, considered
+in \citep{trabelsi_deep_2017} include independent componentwise application of $\real$-valued
+non-linearities, $
   z = u + j v
@@
 %
-$\cplx$-Gaussians are closed under affine transformations: for $A \in \cplx^{n \times m}$
-and $b \in \cplx^{n}$
+$\cplx$-Gaussian random variables are closed under affine transformations: for $
+  A \in \cplx^{n \times m}
+$ and $b \in \cplx^{n}$
 \begin{equation}  \label{eq:cn-affine}
@@
 $. Similar to $\real$ case, variational dropout for $\cplx$ convolutions draws independent
-kernel $W$ for each spatial patch in the input, since a convolution is a matrix product
-of $W$, unrolled into a toeplitz matrix, and flattened intput $x$. Weight sharing is
-essentially pushed to shared variational parameters $\theta$ in the approximation $q_\theta$.
-The rationale is to reduce correlation in the gradient estimator stemming from kernel weights
-being shared between overlapping patches, \citep{kingma_variational_2015,citation_needed}.
-Thus \eqref{eq:cplx-gauss-trick} requires computing $\cplx$ convolutions of $x$, complex
-square $x^2$, and amplitude $\lvert x \rvert^2$ with the mean, relation, and variance kernels,
-respectively.
-%
-\todo{other reasons for patch-independent weights}
+kernel $W$ for each spatial patch in the input. The rationale is simpler computations and
+variance reduction. Reduced variance stems from decorrelated gradient estimates from
+overlapping patches, \citep{kingma_variational_2015}, which allows \eqref{eq:cplx-gauss-trick}
+to use $\cplx$ convolutions of elementwise complex squares $x^2$ and amplitudes $\lvert x \rvert^2$
+with the relation and variance kernels.
+% Weight sharing is essentially pushed to shared variational parameters $\theta$ in the approximation $q_\theta$.
+% A convolution is a matrix product of $W$, unrolled into a toeplitz matrix, and im-to-col
+% flattened intput $x$
 
@@
 \end{equation}
-and we use similar factorized approximation for convolutions. For this approximation the
-relation coefficients \eqref{eq:cplx-gauss-trick} are zero. We use MAP estimates of bias
-terms, i.e. assume an independent fully factorized Dirac approximation.
+and we use similar factorized approximation for convolutions and other, effectively, linear
+layers. For this approximation the relation coefficients \eqref{eq:cplx-gauss-trick} are
+zero. We use MAP estimates of bias terms, i.e. assume an independent fully factorized Dirac
+approximation.
 
@@
 \end{equation}
-% For $\beta = 2$ we add $\gamma$ to make the right-hand side nonegative. (need proof)
+% For $\beta = 2$ we add $\gamma$ to make the right-hand side nonegative. (proof needed)
 Since $\mathop{Ei}(x)$ has simple analytic derivative and \eqref{eq:elbo} depends additively
@@
 %   \,. $$
-The expectation $
+By integrating the power series \eqref{eq:nonchisq-density} with substitution $x \to 2u$,
+the expectation $
   \mathbb{E}_{W\sim \chi^2_m(\lambda)} \log W
-$, needed in \eqref{eq:ard-kl-div-real}, by integrating power series \eqref{eq:nonchisq-density}
-with substitution $x \to 2u$ equals
+$, needed in \eqref{eq:improper-kl-div-real}, equals
 \begin{multline}  \label{eq:exp-log-chisq-proof}
@@
 %
-Differentiating the power series within $g_m$ yields
+Formally differentiating the convergent power series within $g_m$ yields
 \begin{equation}  \label{eq:g-m-deriv}
@@
 \end{equation}
-using $
-  F \colon \mathbb{R} \to \mathbb{R}
+using Dawson's integral $
+  F
+  % \colon \mathbb{R} \to \mathbb{R}
   \colon x \mapsto e^{-x^2} \int_0^x e^{u^2} du
-$ Dawson's integral (special function).
+$.
 %
@@
   \includegraphics[width=1.\linewidth]{../notebooks/assets/grad_log.pdf}
-  \caption{$\tfrac{d f(\alpha)}{d \log{\alpha}}$ of the fit \citep{molchanov_variational_2017},
-  MC estimate, and exact derivative using \eqref{eq:real-kl-div-deriv-log}.}
+  \caption{$\tfrac{d f(\alpha)}{d \log{\alpha}}$ of the fit in \citep{molchanov_variational_2017},
+  MC estimate of \eqref{eq:improper-kl-div-real}, and exact derivative using
+  \eqref{eq:real-kl-div-deriv-log}.}
   \label{fig:molchanov-derivative-replica}
@@
   -j \tfrac{\partial F}{\partial v} = \tfrac{\partial F}{\partial u}
-$ scan be expressed as $
+$ can be expressed as $
   \tfrac{\partial f}{\partial \conj{z}} = 0

### 2020-01-15 paper/paper.tex
removed chunks: on predistortion, since no experiments are expected moved chunks from deiscussion to intro, deleted 'criticism of gale et al.'

@@
 for models in $\cplx$ domain. \verify{$\ell_0$ -- stoch? yes}
+
+Bayesian inference is a very rich field of research with a large body of knowledge and techniques
+that enable practical quantification of predictive, parameter, or model uncertainty and its
+propagation into solutions of the problems of interest.
+
+The latter approach introduces stochastic masks one the parameters, which have hard-concrete
+mask distribution. It is closely related to gumbel-softmax reparameterization trick,
+\citep{kingma_auto-encoding_2014,jang_categorical_2017}: the mask is a stretched sigmoid,
+clamped to $[0,1]$, that takes random input shifted relative to a learnable location
+parameter, which indicates the degree of relevance. The penalty in the objective is a
+smooth approximation to $\ell_0$ norm, i.e. the expected number of nonzero parameters.
 
@@
 
-\subsection{Radio Frequiency Digital Signal Predistortion} % (fold)
-\label{sub:radio_freq_dpd}
-
-Radio Frequency Power Amplifiers (PA) are devices used to increase the power of a signal for
-latter transmission via amplitude modulation over radio. One of the most important problems
-in wireless transmission is distortion caused by imperfections the amplifier, which degrades
-the throughput. Although careful circuit design can mitigate undesirable effects, they cannot
-be eliminated entirely \citep{citation_needed}. \textit{Digital Signal Predistortion} (DPD)
-aims at linearizing the amplifier by introducing computed on-the-fly compensation to the
-input that pushes the signal into the linear region of the PA. Practically, the method helps
-reduce cross-channel interference and enables higher bandwidth utilization in wireless
-transmitters, \citep{citation_needed}. The main challenge of DPD methods is efficient
-compensation on-device (with low-latency).
-
-\citet{traverso_low_2019} use \rewrite{some group delay estimators of something};
-\citet{schoukens_obtaining_2017} develop an iterative approach to inference of the predistortion
-for a given signal \todo{unclear};
-
-\citet{tarver_design_2019} model the predistorter as a paired real dense shallow neural network
-and demonstrate viability and competitiveness of this approach against polynomial based DPD on
-an FPGA implementation.
-
-% About rfWEbLab
-The ``RFWebLab'' platform is remote RF power amplifier setup with web-based API, that feeds
-the user-submitted quadrature signal through a class AB GaN amplifier and sends-back the measured
-output \citep{dpdcompetiton2018}. It is maintained by the GHz Centre at Chalmers University of
-Technolgy and National Instruments \citep{landin_rfweblab_2015}.
-
-We use a custom-written python interface to the WebLab setup that is compatible with the MATLAB
-interface form the setup owner.
-
-% subsection radio_freq_dpd (end)
-
 % section experiments (end)
-
-\section{Discussion and Related Research} % (fold)
-\label{sec:discussion_and_related_research}
-
-Bayesian inference is a very rich field of research with a large body of knowledge and techniques
-that enable practical quantification of predictive, parameter, or model uncertainty and its
-propagation into solutions of the problems of interest.
-
-% criticism and discussion
-based on the algebraic equivalence between $2 \times 2$ real matrices and complex numbers.
-Due to this constraint $\cplx$-networks have less expressive power for the same arithmetic
-complexity compared to a $\real$-layer with twice as many inputs and outputs.
-%
-The \verify{most fierce critique} of Bayesian approach towards model
-sparsification was voiced in \citep{gale_state_2019}, where it was show that it yielded
-inconsistent results in text translation tasks and systematically underperformed simpler
-techniques such as norm pruning and $\ell_0$-regularization, \citep{louizos_learning_2017}.
-
-The latter approach introduces stochastic masks one the parameters, which have hard-concrete
-mask distribution. It is closely related to gumbel-softmax reparameterization trick,
-\citep{kingma_auto-encoding_2014,jang_categorical_2017}: the mask is a stretched sigmoid,
-clamped to $[0,1]$, that takes random input shifted relative to a learnable location
-parameter, which indicates the degree of relevance. The penalty in the objective is a
-smooth approximation to $\ell_0$ norm, i.e. the expected number of nonzero parameters.
-
-% section discussion_and_related_research (end)
 
@@
 
-\subsubsection{MGF of a noncentral $\chi^2$} % (fold)
-\label{ssub:mgf_of_a_noncentral_chi}
-
-Consider the mgf of $W$:
-$$
-M_W(t)
-  = \mathbb{E}(e^{Wt})
-  = \prod_i \mathbb{E}(e^{(\mu_i + z_i)^2 t})
-  \,, $$
-by independence. Now for $z \sim \mathcal{N}(\mu, 1)$
-$$
-\mathbb{E}(e^{z^2 t})
-  = \tfrac1{\sqrt{2\pi}}
-  \int_{-\infty}^{+\infty}
-      e^{z^2 t} e^{-\tfrac{(z-\mu)^2}2}
-  dz
-  \,. $$
-Now, for $t < \tfrac12$
-$$
-z^2 t - \tfrac{(z - \mu)^2}2
-  = - \tfrac12 (1 - 2t) z^2 + z \mu - \tfrac{\mu^2}2
-  % = - \tfrac12 (1 - 2t) \bigl(
-  %   z^2 - 2 z \tfrac\mu{1 - 2t} + \tfrac{\mu^2}{1 - 2t}
-  % \bigr)
-  % = - \tfrac12 (1 - 2t) \bigl( z - \tfrac\mu{1 - 2t} \bigr)^2
-  % - \tfrac12 (1 - 2t) \bigl(
-  %   \tfrac{\mu^2}{1 - 2t}
-  %   - \tfrac{\mu^2}{(1 - 2t)^2}
-  % \bigr)
-  % = - \tfrac12 (1 - 2t) \bigl( z - \tfrac\mu{1 - 2t} \bigr)^2
-  %   - \tfrac{\mu^2}2 \bigl(
-  %   \tfrac{1 - 2t}{1 - 2t} - \tfrac1{1 - 2t}
-  % \bigr)
-  % = - \tfrac12 (1 - 2t) \bigl( z - \tfrac\mu{1 - 2t} \bigr)^2
-  %   + \tfrac{\mu^2}2 \tfrac{2t}{1 - 2t}
-  = - \tfrac12 (1 - 2t) \bigl( z - \tfrac\mu{1 - 2t} \bigr)^2
-    + \mu^2 \tfrac{t}{1 - 2t}
-  \,, $$
-whence
-\begin{multline}
-  \mathbb{E}(e^{z^2 t})
-    = \tfrac1{\sqrt{2\pi}}
-      \int_{-\infty}^{+\infty}
-        e^{z^2 t} e^{-\tfrac{(z-\mu)^2}2}
-      \, dz
-    % = e^{\mu^2 \tfrac{t}{1 - 2t}}
-    %   \tfrac1{\sqrt{2\pi}}
-    %   \int_{-\infty}^{+\infty}
-    %     e^{- \tfrac12 (1 - 2t) \bigl( z - \tfrac\mu{1 - 2t} \bigr)^2}
-    %   \, dz
-    \\= e^{\mu^2 \tfrac{t}{1 - 2t}}
-      \tfrac1{\sqrt{2\pi}}
-      \int_{-\infty}^{+\infty}
-        e^{- \tfrac12 (1 - 2t) z^2}
-      \, dz
-    % = [u = \sqrt{1 - 2t} z]
-    % = e^{\mu^2 \tfrac{t}{1 - 2t}}
-    %   \tfrac1{\sqrt{2\pi}}
-    %   \int_{-\infty}^{+\infty}
-    %     e^{- \tfrac12 u^2}
-    %   \, \tfrac{du}{\sqrt{1 - 2t}}
-    = \tfrac{
-        \exp{\{\mu^2 \tfrac{t}{1 - 2t}\}}
-    }{\sqrt{1 - 2t}}
-    \,.
-\end{multline}
-Therefore
-$$
-M_W(t)
-  = \mathbb{E}(e^{Wt})
-  = \prod_i \tfrac{
-      e^{\mu_i^2 \tfrac{t}{1 - 2t}}
-    }{\sqrt{1 - 2t}}
-  % = e^{\lambda \tfrac{t}{1 - 2t}}
-  %   (1 - 2t)^{-\tfrac{m}2}
-  % = e^{\lambda \tfrac{- t}{2t - 1}}
-  %   (1 - 2t)^{-\tfrac{m}2}
-  % = e^{\tfrac\lambda2 \tfrac{1 - 2t - 1}{2t - 1}}
-  %   (1 - 2t)^{-\tfrac{m}2}
-  % = e^{- \tfrac\lambda2 (1 + \tfrac1{2t - 1})}
-  %   (1 - 2t)^{-\tfrac{m}2} 
-  = e^{- \tfrac\lambda2} e^{\tfrac\lambda2 \tfrac1{1 - 2t}}
-  (1 - 2t)^{-\tfrac{m}2}
-  \,. $$
-Expanding the exponential as infinite series:
-\begin{multline}
-  M_W(t)
-    = e^{- \tfrac\lambda2} e^{\tfrac\lambda2 \tfrac1{1 - 2t}}
-    (1 - 2t)^{-\tfrac{m}2}
-    % = e^{- \tfrac\lambda2} (1 - 2t)^{-\tfrac{m}2}
-    %   \sum_{n \geq 0} \tfrac{\bigl(\tfrac\lambda2\bigr)^n}{n! (1 - 2t)^n}
-    \\= \sum_{n \geq 0} \tfrac{e^{- \tfrac\lambda2} \bigl(\tfrac\lambda2\bigr)^n}{n!}
-        (1 - 2t)^{-\tfrac{2n + m}2}
-    = \sum_{n \geq 0} \tfrac{e^{- \tfrac\lambda2} \bigl(\tfrac\lambda2\bigr)^n}{n!}
-        \mathbb{E}_{x \sim \chi^2_{m + 2n}}(e^{x t})
-    \,.
-\end{multline}
-
-% subsubsection mgf_of_a_noncentral_chi (end)
-
 % section appendix (end)

### 2020-01-17 paper/paper.tex
read he at al. (2018), merged ell-0, and added citations

@@
 complex-valued, yet $\cplx$-valued models and neural networks, and, in particular, compression
-methods tailored to $\cplx$-domain remain a niche field of research. Computational efficiency
-improvement methods such as quantization, integer-based arithmetic \citep{citation_needed},
-and distillation \citep{distillation} appear to be immediately applicable to $\cplx$-field.
-%
-Some model sparsification methods, e.g. magnitude pruning \citep{zuo_compression_2019}, which
-reactivates zeroed parameters based on gradients, and sparsity inducing regularizers, can be
-adapted directly to $\cplx$-valued models. Other methods require additional considerations.
-% the more explicitly zero parameters there is, the less computations is needed.
+methods tailored to $\cplx$-domain remain a niche field of research.
 
@@
 \citep{hirose2003,fijulamin2009}
-% [3] Akira Hirose, Complex-valued neural networks: theories and applications, vol. 5, World Scientific, 2003.
 % [4] Md Faijul Amin and Kazuyuki Murase, “Single-layered complex-valued neural network for real-valued classification problems,” Neurocomputing, vol. 72, no. 4-6, pp. 945–955, 2009.
@@
 % Nevio Benvenuto and Francesco Piazza, “On the complex backpropagation algorithm,” IEEE Transactions on Signal Processing, vol. 40, no. 4, pp. 967–969, 1992.
-
-\citep{yang_complex_2019} develop complex transformer, with $\cplx$-attention and complex
-encoder-decoder, and apply it to music transcription and wireless signal classification.
-
-that interfaces the rest of
-$\cplx$-valued
-the network with complex numbers
-
 that operates on the Fourier transform input speech, acoustic, of radio signals.
-
-papers related to complex-valued distributions \citep{pav_moments_2015,taubock_complex-valued_2012},
-and \citep{karseras_caution:_2014}
 
@@
 operations in the field of complex numbers.
+
+\citep{yang_complex_2019} develop complex transformer, with $\cplx$-attention and complex
+encoder-decoder, and apply it to music transcription and wireless signal classification.
+
+papers related to complex-valued distributions \citep{pav_moments_2015,taubock_complex-valued_2012},
+and \citep{karseras_caution:_2014}
+
 %%% <<<< (cplx)
+
+% motivation and other methods
+Computational efficiency improvement and model compression methods such as quantization
+\citep{uhlich_differentiable_2019}, integer-based arithmetic \citep{lin_fixed_2016,chen_fxpnet_2017},
+and knowledge distillation \citep{hinton_distilling_2015} appear to be directly applicable
+to $\cplx$-valued networks.
+%
+Certain model sparsification methods, e.g. sparsity inducing regularizers, and magnitude
+pruning \citep{zuo_compression_2019}, which reactivates zeroed parameters based on gradients,
+can be adapted directly to $\cplx$-valued models. Other methods require additional considerations.
+% the more explicitly zero parameters there is, the less computations is needed.
 
@@
 better regularizing effect. In multitask learning \citet{cheung_superposition_2019}
-has shown the possibility of storing task-specific parameters in non-destructive superposition
+have shown the possibility of storing task-specific parameters in non-destructive superposition
 within a single network. Their argument implies that if the single task setting is viewed
-as replicated mutlitask learning, then by sampling uncorrelated weight masks dropout acts
+as replicated multitask learning, then by sampling uncorrelated weight masks dropout acts
 as superposition method, which better utilizes the learning capacity of the network.
@@
 % segue into bayesian inference
+Bayesian inference is a very rich field of research with a large body of research and
+techniques that enable practical quantification of predictive, parameter, or model
+uncertainty and its propagation into solutions of the problems of interest.
+%
 Dropout resembles averaging models with shared parameters: each model is weighted equally
@@
 as a Bayesian Inference technique: a principled framework of reasoning about uncertainty,
-whihc updates prior beliefs in accordance with the likelihood of empirical observations
+which updates prior beliefs in accordance with the likelihood of empirical observations
 into posterior belief. Under suitable modelling and prior assumptions, Bayesian methods
@@
 % (sparsity tech large-scale models) gale-elsen-hooker.tex
-\citet{gale_state_2019} compare variational dropout \citep{kingma_variational_2015}, $\ell_0$
-regularization \citep{louizos_learning_2017} and magnitude pruning on large-scale models.
+\citet{gale_state_2019} compare variational dropout \citep{kingma_variational_2015},
+magnitude pruning, and $\ell_0$ regularization \citep{louizos_learning_2017} on large-scale
+models. The latter is a probabilistic regularization method, which penalizes the expected
+number of non-zero entries in $[0, 1]$-valued stochastic parameter masks with learnable
+hard-concrete distribution with an atom at $0$, \citep{maddison_concrete_2016,jang_categorical_2017}.
 Their results suggest that although var-dropout may achieve good accuracy-sparsity balance
-and outperform pruning on the studied architectures, overall pruning is preferable due to
-simplicity and speed. They also conclude that, although dropout and $\ell_0$ yield less
-consistent performance and are more complex, they induce non-uniform sparsity throughout
-the model, which is essential for better compression \citep{he_amc:_2018}.
-\todo{read (He et al., 2018)}
-%
+and outperform pruning and $\ell_0$ on the studied architectures, pruning is preferable for
+its simplicity and speed. They also observe that despite dropout showing more variable
+performance, than magnitude pruning, it nevertheless induces non-uniform sparsity throughout
+the model, which is essential for superior compression \citep{he_amc:_2018}.
 % Magnitude pruning induces user-specified sparsity distributions.
@@
 %
-Therefore it appears that Bayesian and stochastic sparsification techniques can be useful
-for models in $\cplx$ domain. \verify{$\ell_0$ -- stoch? yes}
-
-Bayesian inference is a very rich field of research with a large body of knowledge and techniques
-that enable practical quantification of predictive, parameter, or model uncertainty and its
-propagation into solutions of the problems of interest.
-
-The latter approach introduces stochastic masks one the parameters, which have hard-concrete
-mask distribution. It is closely related to gumbel-softmax reparameterization trick,
-\citep{kingma_auto-encoding_2014,jang_categorical_2017}: the mask is a stretched sigmoid,
-clamped to $[0,1]$, that takes random input shifted relative to a learnable location
-parameter, which indicates the degree of relevance. The penalty in the objective is a
-smooth approximation to $\ell_0$ norm, i.e. the expected number of nonzero parameters.
 
 % our contribution
-Inspired by variational sparsification we develop bayesian dropout for $\cplx$-valued
-networks.
-
+Inspired by variational sparsification and stochastic sparsification techniques we
+develop bayesian dropout for $\cplx$-valued networks.
+%
 The paper is structured as follows. In sec.~\ref{sec:bayesian_dropout} we review Bayesian
@@
 $, then
-\begin{equation}  \label{eq:c-gauss-vi-general}
+\begin{equation}  \label{eq:c-gauss-vi-general-vec}
   \vec{W}
@@
 are independent whence \eqref{eq:cn-affine} implies
-\begin{equation}  \label{eq:cplx-gauss-trick}
+\begin{equation}  \label{eq:cplx-gauss-trick-appendix}
   y_i
@@
 \end{equation}
-Hence \eqref{eq:cplx-gauss-trick} folows.
+Hence \eqref{eq:cplx-gauss-trick-appendix} folows.
 

### 2020-01-17 paper/paper.tex
cplx-network review, fixed an eqref

@@
 
-Signal processing, specifically, audio or radio frequency signal analysis is inherently
-complex-valued, yet $\cplx$-valued models and neural networks, and, in particular, compression
-methods tailored to $\cplx$-domain remain a niche field of research.
-
-%%% >>>> (cplx)
-% complex nets and related stuff
-% cplx domain models
-% (cplx-transformer) yang-ma-li.tex
-% (cplx capacity) monning-manandhar.tex
-\citet{monning_evaluation_2018} state,
-that $\cplx$-networks have less intuitive architectures, inherently higher arithmetic
-complexity due to multiplication in $\cplx$, that requires 3-4 floating point multiplications,
-dependening on the implementation.
-% due to them not being true cplx and just paired real computational graphs
-
-\citep{yang_complex_2019,monning_evaluation_2018}
-
-data that is naturally complex-valued
-studies have shown a potentially richer representation of complex nets
-\citep{hirose2003,fijulamin2009}
-% [4] Md Faijul Amin and Kazuyuki Murase, “Single-layered complex-valued neural network for real-valued classification problems,” Neurocomputing, vol. 72, no. 4-6, pp. 945–955, 2009.
-
-the complex version of backpropagation algorithm  was proposed because of
-its richer representational capacity.
-% Nevio Benvenuto and Francesco Piazza, “On the complex backpropagation algorithm,” IEEE Transactions on Signal Processing, vol. 40, no. 4, pp. 967–969, 1992.
-that operates on the Fourier transform input speech, acoustic, of radio signals.
-
-Application of complex-valued networks is not new, \citep{citation_needed}. More recently
-they were applied to music transcription and speech recognition \citep{trabelsi_deep_2017},
-and \citep{yang_complex_2019}. The key motivation behind adoption of $\cplx$-networks is
-pervasiveness of $\cplx$-valued data in digital signal processing \citep{citation_needed},
-acoustic and radio signal analysis \citep{citation_needed}, and quantum systems modelling
-\citep{citation_needed}, etc. All these applications require compliance with algebraic
-operations in the field of complex numbers.
-
-\citep{yang_complex_2019} develop complex transformer, with $\cplx$-attention and complex
-encoder-decoder, and apply it to music transcription and wireless signal classification.
-
-papers related to complex-valued distributions \citep{pav_moments_2015,taubock_complex-valued_2012},
-and \citep{karseras_caution:_2014}
-
-%%% <<<< (cplx)
+Inherently complex-valued nature of data in signal processing, specifically, acoustic or radio
+frequency signal analysis, has been the key driver behind adoption of $\cplx$-networks.
+%
+\citet{hirose_complex-valued_2009} argues that the key merit of $\cplx$-valued neural
+networks is simultaneous phase rotation and amplitude adjustment, intrinsic to multiplication
+in $\cplx$ field. Despite inherently higher arithmetic complexity, which stems from up to four
+floating point operations per single $\cplx$ multiplication, \citep{monning_evaluation_2018},
+$\cplx$-arithmetic reduces ineffective degrees of freedom in comparison with an analogous
+double-dimensional $\real$-valued network. \citet{hirose_complex-valued_2009} list numerous
+applications related to acoustic and radio signal processing and demonstrate superiority of
+$\cplx$-networks in the task of shallow landmine detection using ground penetrating radar
+imaging. More recently they were applied to music transcription and speech recognition
+\citep{trabelsi_deep_2017}. \citet{arjovsky_unitary_2016} propose $\cplx$-valued unitary-RNNs
+to deal with exploding~/~vanishing gradients and apply the recurrent models to long-term
+dependence prediction tasks. \citet{wisdom_full-capacity_2016} expand on their work by optimizing
+recurrent weights on the $\cplx^{n \times n}$ Stiefel manifold. And \citet{wolter_complex_2018}
+investigate different $\cplx$-valued gating mechanisms unitary-RNNs and conduct experiments
+on human motion prediction and music transcription. \citet{yang_complex_2019} develop complex
+transformer, with $\cplx$-attention and complex encoder-decoder, and apply it to music
+transcription and wireless signal classification.
+
+% complex-valued distributions \citep{pav_moments_2015,taubock_complex-valued_2012},
+% and \citep{karseras_caution:_2014}
 
 % motivation and other methods
+However, in spite of relative success of $\cplx$-valued networks, compression methods tailored
+to $\cplx$-domain remain a niche field of research.
+%
 Computational efficiency improvement and model compression methods such as quantization
@@
 the sparsification rate and compare the resulting performance of various $\cplx$-networks
-proposed in prior work, and discuss the outcomes in sec.~\ref{sec:discussion_and_related_research}.
+proposed in prior work, and discuss the outcomes.
 
@@
 \citep{citation_needed}, fits a prior distribution while performing variational inference.
-Maximizing \eqref{eq:elbo} over $\lambda$, holding other parameters fixed, yields $
+Maximizing \eqref{eq:elbo} over $\tau$, holding other parameters fixed, yields $
   \tau^* = {(\mu^2 + \sigma^2)}^{-1}
@@
 $W$ can be implemented as two $\real$-convolutions with kernels $\Re{W}$ and $\Im{W}$ using
-\eqref{eq:cplx-lin-op}. Algebraic operations, trigonometric functions, are implemented
-through operations in $\real^2$, \citep{hirose_complex-valued_2009}. Activations, considered
-in \citep{trabelsi_deep_2017} include independent componentwise application of $\real$-valued
-non-linearities, $
-  z = u + j v
-    \mapsto \sigma(u) + j \sigma(v)
-$, $\cplx$-differentiable exponential and trigonometric activations, and \textit{modRelu}
-activation, which applies soft-thresholding to the modulus and preserves the angle: $
-  z = r e^{j \phi}
-    \mapsto e^{j \phi} (r - b)_+
-  % z \mapsto z \bigl(
-  %     1 - \tfracb{\lvert z \rvert}
-  %   \bigr)_+
-$ with a learnable threshold parameter $b \in \real$.
+\eqref{eq:cplx-lin-op}. Activations include trigonometric functions and representation-dependent
+non-linearities, \citep{hirose_complex-valued_2009}: polar (phase-amplitude) $
+  z \mapsto \sigma(\lvert z \rvert) e^{j \arg z}
+$ or planar (real-imaginary) $
+  z \mapsto \sigma(\Re z) + j \sigma(\Im z)
+$ for some $\real$-valued non-linearity $\sigma$, possibly with learnable parameters,
+\citep{trabelsi_deep_2017,wolter_complex_2018}.
 
@@
 \end{equation}
-Hence \eqref{eq:cplx-gauss-trick-appendix} folows.
+Hence \eqref{eq:cplx-gauss-trick} folows.
 

### 2020-01-27 paper/paper.tex
oxford comma, minor rewords

@@
 efficiency of the SGVB gradient estimator, \citep{wang_fast_2013,kingma_variational_2015}.
-We assume that weights $W \in \cplx^{n\times m}$ of a dense linear layer are drawn from a
+Suppose that weights $W \in \cplx^{n\times m}$ of a dense linear layer are drawn from a
 mean field $\cplx$-Gaussian approximate posterior
@@
   \lvert C_{ij} \rvert^2 \leq \Sigma_{ij}
-$. Property \eqref{eq:cn-affine} and independence of $W$ imply that for any $x \in \cplx^m$
-and $b \in \cplx^n$ the components of $y = W x + b$ are independent with
+$. The property \eqref{eq:cn-affine} and independence of elements of $W$ imply that for any
+$x \in \cplx^m$ and $b \in \cplx^n$ the components of $y = W x + b$ are independent with
 \begin{equation}  \label{eq:cplx-gauss-trick}
@@
 The trick and dropout can be applied to any layer, the output of which depends linearly
-on its parameters, e.g. convolutional layers, affine and bilinear transformations $
+on its parameters, e.g. convolutional layers, affine, and bilinear transformations $
   (x, z) \mapsto x^\top W^{(j)} z + b_j
 $. Similar to $\real$ case, variational dropout for $\cplx$ convolutions draws independent
-kernel $W$ for each spatial patch in the input. The rationale is simpler computations and
-variance reduction. Reduced variance stems from decorrelated gradient estimates from
+realizations of $W$ for each spatial patch in the input. The rationale is simpler computations
+and variance reduction. The latter effect stems from decorrelated gradient estimates from
 overlapping patches, \citep{kingma_variational_2015}, which allows \eqref{eq:cplx-gauss-trick}
@@
 
-We consider two priors for Bayesian dropout: log-uniform and $\cplx$-Gaussian empirical
+We consider two priors for Bayesian dropout: \verify{log-uniform} and $\cplx$-Gaussian empirical
 Bayes, \citep{kingma_variational_2015,molchanov_variational_2017,kharitonov_variational_2018}.
@@
     % = \sum_{ij} KL\bigl( q(\omega_{ij}) \| \pi(\omega_{ij}) \bigr)
-    = \sum_{ij} \bigl(
-        - \mathbb{H}(q(\omega_{ij}))
-        - \mathbb{E}_{q(\omega_{ij})} \log{\pi(\omega_{ij})}
-      \bigr)
+    = - \sum_{ij}
+        \mathbb{H}(q(\omega_{ij}))
+        + \mathbb{E}_{q(\omega_{ij})} \log{\pi(\omega_{ij})}
     \,.
@@
 
-In this section we will compare the complex variational dropout techniques, discussed
-above, on the tasks and datasets, that were studied in prior research on complex-%
-valued networks.
+In this section we compare the complex variational dropout techniques discussed above
+on the tasks and datasets, that were studied in prior research on complex-valued networks.
 
@@
 
-\citet{trabelsi_deep_2017} study the applicability of complex-valued networks to image
+\citet{trabelsi_deep_2017} study the applicability of $\cplx$-valued networks to image
 classification (CIFAR-10, CIFAR-100, reduced train of SVHN), music-transcription
 (MusicNet), and Speech Spectrum prediction (TIMIT).
-\begin{itemize}
-  \item 
-\end{itemize}
-
-test on MusicNet, (music transcription [14])
-
-complex high-dimensional time series In-phase Quadrature (IQ)
+
+% complex high-dimensional time series In-phase Quadrature (IQ)
 

### 2020-01-28 cplxpaper/musicnet/models/real/__init__.py
renamed extensions to __init__

@@ -1,3 +1,56 @@
+# var-dropout
+from cplxmodule.nn.relevance.extensions import LinearVD
+from cplxmodule.nn.relevance.extensions import Conv1dVD
+
+# automatic relevance determination
+from cplxmodule.nn.relevance.extensions import LinearARD
+from cplxmodule.nn.relevance.extensions import Conv1dARD
+
+from cplxmodule.nn.masked import LinearMasked
+from cplxmodule.nn.masked import Conv1dMasked
+
 from .base import TwoLayerDense
 from .base import ShallowConvNet
 from .base import DeepConvNet
+
+
+class TwoLayerDenseVD(TwoLayerDense):
+    Linear = LinearVD
+
+
+class TwoLayerDenseARD(TwoLayerDense):
+    Linear = LinearARD
+
+
+class TwoLayerDenseMasked(TwoLayerDense):
+    Linear = LinearMasked
+
+
+class ShallowConvNetVD(ShallowConvNet):
+    Linear = LinearVD
+    Conv1d = Conv1dVD
+
+
+class ShallowConvNetARD(ShallowConvNet):
+    Linear = LinearARD
+    Conv1d = Conv1dARD
+
+
+class ShallowConvNetMasked(ShallowConvNet):
+    Linear = LinearMasked
+    Conv1d = Conv1dMasked
+
+
+class DeepConvNetVD(DeepConvNet):
+    Linear = LinearVD
+    Conv1d = Conv1dVD
+
+
+class DeepConvNetARD(DeepConvNet):
+    Linear = LinearARD
+    Conv1d = Conv1dARD
+
+
+class DeepConvNetMasked(DeepConvNet):
+    Linear = LinearMasked
+    Conv1d = Conv1dMasked

### 2020-01-28 cplxpaper/musicnet/models/real/extensions.py

@@ -1,36 +1,0 @@
-from .base import TwoLayerDense
-from .base import ShallowConvNet
-from .base import DeepConvNet
-
-from cplxmodule.nn.relevance import LinearARD
-from cplxmodule.nn.masked import LinearMasked
-from cplxmodule.nn.relevance import Conv1dARD
-from cplxmodule.nn.masked import Conv1dMasked
-
-
-class TwoLayerDenseARD(TwoLayerDense):
-    Linear = LinearARD
-
-
-class TwoLayerDenseMasked(TwoLayerDense):
-    Linear = LinearMasked
-
-
-class ShallowConvNetARD(ShallowConvNet):
-    Linear = LinearARD
-    Conv1d = Conv1dARD
-
-
-class ShallowConvNetMasked(ShallowConvNet):
-    Linear = LinearMasked
-    Conv1d = Conv1dMasked
-
-
-class DeepConvNetARD(DeepConvNet):
-    Linear = LinearARD
-    Conv1d = Conv1dARD
-
-
-class DeepConvNetMasked(DeepConvNet):
-    Linear = LinearMasked
-    Conv1d = Conv1dMasked

### 2020-01-28 cplxpaper/musicnet/models/complex/__init__.py
renamed extensions to __init__

@@ -2,3 +2,55 @@ from .base import CplxTwoLayerDense
 from .base import CplxShallowConvNet
 from .base import CplxDeepConvNet
 
+# var-dropout
+from cplxmodule.nn.relevance.extensions import CplxLinearVDBogus
+from cplxmodule.nn.relevance.extensions import CplxConv1dVDBogus
+
+# automatic relevance determination
+from cplxmodule.nn.relevance.extensions import CplxLinearARD
+from cplxmodule.nn.relevance.extensions import CplxConv1dARD
+
+from cplxmodule.nn.masked import CplxLinearMasked
+from cplxmodule.nn.masked import CplxConv1dMasked
+
+
+class CplxTwoLayerDenseVD(CplxTwoLayerDense):
+    Linear = CplxLinearVDBogus
+
+
+class CplxTwoLayerDenseARD(CplxTwoLayerDense):
+    Linear = CplxLinearARD
+
+
+class CplxTwoLayerDenseMasked(CplxTwoLayerDense):
+    Linear = CplxLinearMasked
+
+
+class CplxShallowConvNetVD(CplxShallowConvNet):
+    Linear = CplxLinearVDBogus
+    Conv1d = CplxConv1dVDBogus
+
+
+class CplxShallowConvNetARD(CplxShallowConvNet):
+    Linear = CplxLinearARD
+    Conv1d = CplxConv1dARD
+
+
+class CplxShallowConvNetMasked(CplxShallowConvNet):
+    Linear = CplxLinearMasked
+    Conv1d = CplxConv1dMasked
+
+
+class CplxDeepConvNetVD(CplxDeepConvNet):
+    Linear = CplxLinearVDBogus
+    Conv1d = CplxConv1dVDBogus
+
+
+class CplxDeepConvNetARD(CplxDeepConvNet):
+    Linear = CplxLinearARD
+    Conv1d = CplxConv1dARD
+
+
+class CplxDeepConvNetMasked(CplxDeepConvNet):
+    Linear = CplxLinearMasked
+    Conv1d = CplxConv1dMasked

### 2020-01-28 cplxpaper/musicnet/models/complex/extensions.py

@@ -1,36 +1,0 @@
-from .base import CplxTwoLayerDense
-from .base import CplxShallowConvNet
-from .base import CplxDeepConvNet
-
-from cplxmodule.nn.relevance.extensions import CplxLinearVDBogus
-from cplxmodule.nn.masked import CplxLinearMasked
-from cplxmodule.nn.relevance.extensions import CplxConv1dVDBogus
-from cplxmodule.nn.masked import CplxConv1dMasked
-
-
-class CplxTwoLayerDenseARD(CplxTwoLayerDense):
-    Linear = CplxLinearVDBogus
-
-
-class CplxTwoLayerDenseMasked(CplxTwoLayerDense):
-    Linear = CplxLinearMasked
-
-
-class CplxShallowConvNetARD(CplxShallowConvNet):
-    Linear = CplxLinearVDBogus
-    Conv1d = CplxConv1dVDBogus
-
-
-class CplxShallowConvNetMasked(CplxShallowConvNet):
-    Linear = CplxLinearMasked
-    Conv1d = CplxConv1dMasked
-
-
-class CplxDeepConvNetARD(CplxDeepConvNet):
-    Linear = CplxLinearVDBogus
-    Conv1d = CplxConv1dVDBogus
-
-
-class CplxDeepConvNetMasked(CplxDeepConvNet):
-    Linear = CplxLinearMasked
-    Conv1d = CplxConv1dMasked

### 2020-01-28 cplxpaper/musicnet/lr_scheduler.py
moved scheduler of Trabelsi (2017) to a separate script

@@ -1,0 +1,24 @@
+from torch.optim.lr_scheduler import LambdaLR
+
+
+class Trabelsi2017LRSchedule(LambdaLR):
+    def __init__(self, optimizer):
+        super().__init__(optimizer, self.lr_lambda)
+
+    @classmethod
+    def lr_lambda(cls, epoch):
+        """Multiplicative LR schedule (for base lr 1e-3)."""
+        if epoch < 10:
+            return 1e-0  # (1e-3)
+
+        elif epoch < 100:
+            return 1e-1  # (1e-4)
+
+        elif epoch < 120:
+            return 5e-2  # (5e-5)
+
+        elif epoch < 150:
+            return 1e-2  # (1e-5)
+
+        else:
+            return 1e-3  # (1e-6)

### 2020-01-28 cplxpaper/musicnet/models/real/base.py

@@ -110,26 +110,3 @@ class DeepConvNet(BodyMixin, torch.nn.Module):
         ]))
 
         reset_bias(self.body[-1])
-
-
-class Trabelsi2017LRSchedule(torch.optim.lr_scheduler.LambdaLR):
-    def __init__(self, optimizer):
-        super().__init__(optimizer, self.lr_lambda)
-
-    @classmethod
-    def lr_lambda(cls, epoch):
-        """Multiplicative LR schedule (for base lr 1e-3)."""
-        if epoch < 10:
-            return 1e-0  # (1e-3)
-
-        elif epoch < 100:
-            return 1e-1  # (1e-4)
-
-        elif epoch < 120:
-            return 5e-2  # (5e-5)
-
-        elif epoch < 150:
-            return 1e-2  # (1e-5)
-
-        else:
-            return 1e-3  # (1e-6)

### 2020-01-28 cplxpaper/musicnet/models/complex/__init__.py
dropped CPLX prefix and fixed Flatten import

@@ -1,7 +1,3 @@
-from .base import CplxTwoLayerDense
-from .base import CplxShallowConvNet
-from .base import CplxDeepConvNet
-
 # var-dropout
 from cplxmodule.nn.relevance.extensions import CplxLinearVDBogus
 from cplxmodule.nn.relevance.extensions import CplxConv1dVDBogus
@@ -13,44 +9,48 @@ from cplxmodule.nn.relevance.extensions import CplxConv1dARD
 from cplxmodule.nn.masked import CplxLinearMasked
 from cplxmodule.nn.masked import CplxConv1dMasked
 
+from .base import TwoLayerDense
+from .base import ShallowConvNet
+from .base import DeepConvNet
 
-class CplxTwoLayerDenseVD(CplxTwoLayerDense):
+
+class TwoLayerDenseVD(TwoLayerDense):
     Linear = CplxLinearVDBogus
 
 
-class CplxTwoLayerDenseARD(CplxTwoLayerDense):
+class TwoLayerDenseARD(TwoLayerDense):
     Linear = CplxLinearARD
 
 
-class CplxTwoLayerDenseMasked(CplxTwoLayerDense):
+class TwoLayerDenseMasked(TwoLayerDense):
     Linear = CplxLinearMasked
 
 
-class CplxShallowConvNetVD(CplxShallowConvNet):
+class ShallowConvNetVD(ShallowConvNet):
     Linear = CplxLinearVDBogus
     Conv1d = CplxConv1dVDBogus
 
 
-class CplxShallowConvNetARD(CplxShallowConvNet):
+class ShallowConvNetARD(ShallowConvNet):
     Linear = CplxLinearARD
     Conv1d = CplxConv1dARD
 
 
-class CplxShallowConvNetMasked(CplxShallowConvNet):
+class ShallowConvNetMasked(ShallowConvNet):
     Linear = CplxLinearMasked
     Conv1d = CplxConv1dMasked
 
 
-class CplxDeepConvNetVD(CplxDeepConvNet):
+class DeepConvNetVD(DeepConvNet):
     Linear = CplxLinearVDBogus
     Conv1d = CplxConv1dVDBogus
 
 
-class CplxDeepConvNetARD(CplxDeepConvNet):
+class DeepConvNetARD(DeepConvNet):
     Linear = CplxLinearARD
     Conv1d = CplxConv1dARD
 
 
-class CplxDeepConvNetMasked(CplxDeepConvNet):
[…]

### 2020-01-28 cplxpaper/musicnet/models/complex/base.py

@@ -9,10 +9,10 @@ from cplxmodule.nn.conv import CplxConv1d
 
 from cplxmodule.nn.batchnorm import CplxBatchNorm1d
 
-from ..trabelsi2017.base import Flatten, BodyMixin
+from ..real.base import Flatten, BodyMixin
 
 
-class CplxTwoLayerDense(torch.nn.Module):
+class TwoLayerDense(torch.nn.Module):
     """
     n_channels : int
         number of cplx channels (2 x floats).
@@ -41,7 +41,7 @@ def one_pool(n_seq, cls, kernel, stride):
     return n_seq, CplxToCplx[cls](kernel, stride)
 
 
-class CplxShallowConvNet(torch.nn.Module):
+class ShallowConvNet(torch.nn.Module):
     Linear = CplxLinear
     Conv1d = CplxConv1d
 
@@ -64,7 +64,7 @@ class CplxShallowConvNet(torch.nn.Module):
         ]))
 
 
-class CplxDeepConvNet(torch.nn.Module):
+class DeepConvNet(torch.nn.Module):
     Linear = CplxLinear
     Conv1d = CplxConv1d
 

### 2020-01-28 cplxpaper/mnist/models/complex.py
renamed ARD to VD, and implemented true ARD

@@ -8,13 +8,17 @@ from cplxmodule.nn.layers import CplxReal, AsTypeCplx
 from cplxmodule.nn.layers import ConcatenatedRealToCplx
 from cplxmodule.nn.layers import CplxToConcatenatedReal
 
-# from cplxmodule.nn.relevance import CplxConv2dARD, CplxLinearARD
+# var-dropout
 from cplxmodule.nn.relevance.extensions import CplxLinearVDBogus
 from cplxmodule.nn.relevance.extensions import CplxConv2dVDBogus
 
+# automatic relevance determination
+from cplxmodule.nn.relevance.extensions import CplxLinearARD
+from cplxmodule.nn.relevance.extensions import CplxConv2dARD
+
 from cplxmodule.nn.masked import CplxConv2dMasked, CplxLinearMasked
 
-from ...musicnet.trabelsi2017.base import Flatten
+from ...musicnet.models.real.base import Flatten
 
 
 class SimpleConvModel(object):
@@ -45,9 +49,14 @@ class SimpleConvModel(object):
         return torch.nn.Sequential(OrderedDict(layers))
 
 
-class SimpleConvModelARD(SimpleConvModel):
+class SimpleConvModelVD(SimpleConvModel):
     Linear = CplxLinearVDBogus
     Conv2d = CplxConv2dVDBogus
+
+
+class SimpleConvModelARD(SimpleConvModel):
+    Linear = CplxLinearARD
+    Conv2d = CplxConv2dARD
 
 
 class SimpleConvModelMasked(SimpleConvModel):
@@ -77,8 +86,12 @@ class SimpleDenseModel(object):
         return torch.nn.Sequential(OrderedDict(layers))
 
 
-class SimpleDenseModelARD(SimpleDenseModel):
+class SimpleDenseModelVD(SimpleDenseModel):
     Linear = CplxLinearVDBogus
+
+
+class SimpleDenseModelARD(SimpleDenseModel):
+    Linear = CplxLinearARD
 
 
 class SimpleDenseModelMasked(SimpleDenseModel):
@@ -105,8 +118,12 @@ class TwoLayerDenseModel(object):
         return torch.nn.Sequential(OrderedDict(layers))
 
 
-class TwoLayerDenseModelARD(TwoLayerDenseModel):
+class TwoLayerDenseModelVD(TwoLayerDenseModel):
     Linear = CplxLinearVDBogus
+
+
[…]

### 2020-01-28 cplxpaper/mnist/models/real.py

@@ -1,10 +1,17 @@
 import torch
 from collections import OrderedDict
 
-from cplxmodule.nn.relevance import Conv2dARD, LinearARD
+# var-dropout
+from cplxmodule.nn.relevance.extensions import LinearVD
+from cplxmodule.nn.relevance.extensions import Conv2dVD
+
+# automatic relevance determination
+from cplxmodule.nn.relevance.extensions import LinearARD
+from cplxmodule.nn.relevance.extensions import Conv2dARD
+
 from cplxmodule.nn.masked import Conv2dMasked, LinearMasked
 
-from ...musicnet.trabelsi2017.base import Flatten
+from ...musicnet.models.real.base import Flatten
 
 
 class SimpleConvModel(object):
@@ -31,6 +38,11 @@ class SimpleConvModel(object):
         ]))
 
 
+class SimpleConvModelVD(SimpleConvModel):
+    Linear = LinearVD
+    Conv2d = Conv2dVD
+
+
 class SimpleConvModelARD(SimpleConvModel):
     Linear = LinearARD
     Conv2d = Conv2dARD
@@ -55,6 +67,10 @@ class SimpleDenseModel(object):
         ]))
 
 
+class SimpleDenseModelVD(SimpleDenseModel):
+    Linear = LinearVD
+
+
 class SimpleDenseModelARD(SimpleDenseModel):
     Linear = LinearARD
 
@@ -73,6 +89,10 @@ class TwoLayerDenseModel(object):
             ("relu2", torch.nn.ReLU()),
             ("lin_2", cls.Linear(4096, n_outputs)),
         ]))
+
+
+class TwoLayerDenseModelVD(TwoLayerDenseModel):
+    Linear = LinearVD
 
 
 class TwoLayerDenseModelARD(TwoLayerDenseModel):

### 2020-01-28 cplxpaper/auto/auto.py
fixed imports

@@ -63,7 +63,7 @@ def defaults(options):
             "grad_clip": 0.5,
             "early": None,
             "lr_scheduler": {
-                "cls": "<class 'musicnet.trabelsi2017.base.Trabelsi2017LRSchedule'>"
+                "cls": "<class 'cplxpaper.musicnet.lr_scheduler.Trabelsi2017LRSchedule'>"
             },
             "optimizer": {
                 "cls": "<class 'torch.optim.adam.Adam'>",

### 2020-01-28 setup.py
version bump and subpackage fix

@@ -2,7 +2,7 @@ from distutils.core import setup, Extension
 
 setup(
     name="cplxpaper",
-    version="0.3.2",
+    version="0.3.3",
     description="""Package for Bayesian Sparsification """
                 """of Complex Valued Networks.""",
     license="MIT License",
@@ -12,11 +12,10 @@ setup(
         "cplxpaper",
         "cplxpaper.auto",
         "cplxpaper.musicnet",
-        "cplxpaper.musicnet.complex",
-        "cplxpaper.musicnet.trabelsi2017",
         "cplxpaper.mnist",
-        "cplxpaper.mnist.models",
         "cplxpaper.cifar",
+        "cplxpaper.musicnet.models",
+        "cplxpaper.mnist.models",
         "cplxpaper.cifar.models"
     ],
     requires=["torch", "numpy", "pandas", "cplxmodule", "scikit-learn"],

### 2020-01-28 setup.py
import and setup-requires fix

@@ -18,7 +18,7 @@ setup(
         "cplxpaper.mnist.models",
         "cplxpaper.cifar.models"
     ],
-    requires=["torch", "numpy", "pandas", "cplxmodule", "scikit-learn"],
+    requires=["torch", "numpy", "pandas", "cplxmodule", "sklearn"],
     # install_requires=[  # uncomment for publishing
     #     "cplxmodule @ git+https://github.com/ivannz/cplxmodule.git"
     # ]

### 2020-01-28 cplxpaper/musicnet/models/complex/base.py
had to add a compatibility flag as a permament reminder of my carelessness

@@ -86,9 +86,11 @@ class DeepConvNet(torch.nn.Module):
 
         return n_seq, torch.nn.Sequential(OrderedDict(layers))
 
-    def __new__(cls, n_seq=4096, n_channels=1, n_outputs=84):
+    def __new__(cls, n_seq=4096, n_channels=1, n_outputs=84, legacy=True):
+        k = 3 if legacy else 6  # sigh, a mistake... had to add `legacy` flag
+
         param = [
-            (  1,  16, 3, 2,  True),  # Trabelsi et al. (2017) has kernel=6 (L57)
+            (  1,  16, k, 2,  True),  # Trabelsi et al. (2017) has kernel=6 (L57)
             ( 16,  32, 3, 2,  True),
             ( 32,  64, 3, 1,  True),
             ( 64,  64, 3, 1,  True),

### 2020-01-29 paper/paper.tex
stub version of the experimental section

@@
 on the tasks and datasets, that were studied in prior research on complex-valued networks.
+
+% general training strategy
+The goal of the following experiments to study the sparsity-performance trade-off of the
+proposed Bayesian sparsification methods for $\cplx$-valued networks. To this end we employ
+the following training plan in every experiment. The model is trained in three successive
+stages:
+``dense'' $\to$ ``sparsify'' $\to$ ``fine-tune''
+
+At the first, ``dense'', stage every network retains its original non-bayesian layers
+and is fit ``as-is'' using only the likelihood from \eqref{eq:elbo} without variational
+dropout.
+
+During the second stage ``sparsify'' we make the relevant layers bayesian and apply
+variational dropout sec.~\ref{ssub:variational_dropout} (or sec.~\ref{ssub:empirical_bayes})
+or their $\real$ counterparts. To be able to study the attainable sparsity levels we
+inject a coefficient $C \in (0, 1]$ at the KL divergence term in
+\eqref{eq:elbo}:
+\begin{equation}  \label{eq:elbo_with_coef}
+    - \frac{C}N KL(q_{\theta} \| \pi_{\lambda})
+    + \frac1{M} \sum_{i=1}^M
+        \log p_{\phi}(z_i \mid g(\varepsilon_i; \theta))
+    \,. \tag{\ref{eq:elbo}'}
+\end{equation}
+Increasing $C$ yields increasingly more sparse networks upon termination of this stage.
+
+Before transitioning to the ``fine-tune'' stage we compute the mask of non-zero weights
+in each layer based on the relevance scores $\alpha$ (sec.~\ref{sub:dropout}). Since
+the variational approximation factorizes into univariate distributions, whether a $\cplx$
+or $\real$ parameter is zero or not is determined from its relevance score $
+  \alpha = \tfrac{\sigma^2}{\lvert\mu\rvert^2}
+$: non-zero (relevant) if $\log \alpha \leq \tau$, zero (irrelevant) otherwise.
+In every experiment we set $\tau = -\tfrac12$, which yields extreme levels of sparsity,
+especially considering that the recommended setting in \citep{molchanov_variational_2017}
+was $3$. The rationale behind our choice was twofold: we use an extra fine tuning
+stage, and keep the weights that are away from zero with high probability.
+
+These masks are then used during ``fine-tune'' to train the remaining non-zero parameters
+similar to the ``dense'' stage, i.e. with layers non-bayesian layers, but with fixed
+sparsity masks.
+
+Unless specified otherwise we use ADAM optimizer with the base learning rate of $10^{-3}$
+and the annealing schedule from .
+
+\subsection{MNIST-like datasets} % (fold)
+\label{sub:mnist_like_datasets}
+
+We conduct a moderately sized numerical experiment on MNIST and similar datasets to see
+whether the proposed $\cplx$-var dropout indeed reasonably sparsifies complex-valued networks.
+
+We compare with the studied $\cplx$-valued networks against their classical $\real$-valued
+counterparts both in terms of the resulting sparsity and test performance.
+
+Although image data is not $\cplx$ in nature, we apply two-dimensional Fourier Transform
+in order to get $\cplx$-valued inputs. We concede that this is a rather unnatural representation
+of image data, however the selection of publicly available datasets, which are not artificially
+$\cplx$-valued, is limited to audio, speech and music. Indeed, as is shown by the numerical
+experiments, a real-valued model is trained on the Fourier transformed data underperforms
+relative to its architecturally similar twin fit to on the raw color data.
+
+\citet{trabelsi_deep_2017} study the applicability of $\cplx$-valued networks to image
+classification (CIFAR-10, CIFAR-100, and a subset of SVHN). Their approach is to either
+embed $\real$ in $\cplx$ (by $\Re z = 0$), or train a smaller auxiliary network, that
+synthesizes the imaginary component from the raw channel data. \todo{DO THIS}
+In our experiments we opt to transforming the input $2d$ data with
+
+% subsection mnist_like_datasets (end)
 

### 2020-01-30 paper/paper.tex
on log-relevance distribution

@@
 the following training plan in every experiment. The model is trained in three successive
-stages:
-``dense'' $\to$ ``sparsify'' $\to$ ``fine-tune''
+stages: ``dense'' $\to$ ``sparsify'' $\to$ ``fine-tune''.
+%
+The last two stages are used to compare the .
 
@@
 
-During the second stage ``sparsify'' we make the relevant layers bayesian and apply
-variational dropout sec.~\ref{ssub:variational_dropout} (or sec.~\ref{ssub:empirical_bayes})
-or their $\real$ counterparts. To be able to study the attainable sparsity levels we
-inject a coefficient $C \in (0, 1]$ at the KL divergence term in
-\eqref{eq:elbo}:
+During the ``sparsify'' stage we make the relevant layers bayesian and apply $\cplx$-variational
+dropout sec.~\ref{ssub:variational_dropout} (or sec.~\ref{ssub:empirical_bayes}) or its $\real$
+counterpart. To be able to study the attainable sparsity levels we inject a coefficient $
+  C \in (0, 1]
+$ at the KL divergence term in \eqref{eq:elbo}:
 \begin{equation}  \label{eq:elbo_with_coef}
@@
 \end{equation}
-Increasing $C$ yields increasingly more sparse networks upon termination of this stage.
+Higher $C$ yields increasingly more sparse layers upon termination of this stage.
 
@@
   \alpha = \tfrac{\sigma^2}{\lvert\mu\rvert^2}
-$: non-zero (relevant) if $\log \alpha \leq \tau$, zero (irrelevant) otherwise.
-In every experiment we set $\tau = -\tfrac12$, which yields extreme levels of sparsity,
-especially considering that the recommended setting in \citep{molchanov_variational_2017}
-was $3$. The rationale behind our choice was twofold: we use an extra fine tuning
+$: non-zero (relevant) if $\log \alpha \leq \tau$, zero (irrelevant) otherwise. Figure~%
+\ref{fig:typical_log_alpha_distrib} depicts the distribution of $\log \alpha$ values
+from \textbf{some run}, which exhibits the typical behaviour we noticed in all experiments
+conducted: there always is a single mode within the moderately negative range, and one or
+two modes to the right of $0$. The relative mass of each mode changes with $C$ and the
+higher the coefficient is, the more mass is shifted to the positive half. However, in every
+exepriment the trough between the peaks of the negative mode and the first positive one
+is around zero.
+
+Thus, in every experiment we set $\tau = -\tfrac12$, which is admittedly very low, especially
+considering that the recommended setting in \citep{molchanov_variational_2017} is $3$. This
+yields high levels of sparsity,
+The rationale behind our choice was twofold: we use an extra fine tuning
 stage, and keep the weights that are away from zero with high probability.

### 2020-01-30 paper/paper.tex
-0.5 threshold explanation and a newer abstract

@@
 With continual miniaturization ever more applications of deep learning can be found in
-embedded systems. Common embedded applications include on-device image recognition and
-signal processing (audio and radio). We investigate complex-domain deep neural networks
-and complex-valued Bayesian compression thereof. To this end we conduct a large scale
-numerical study of complex-valued networks to assess quality - compression rate trade-off.
-The results of this study have direct implications for real-time signal processing
-throughput of embedded systems.
+embedded systems, where it is common to encounter data with natural complex domain
+representation. To this end we extend Variational Dropout of \citet{kingma_variational_2015}
+and \citet{kharitonov_variational_2018} to complex-valued neural networks building upon
+the work of \citet{trabelsi_deep_2017}. We verify the proposed Bayesian technique and
+assess the performance-compression trade-off by conducting a large-scale numerical study
+of $\cplx$-valued networks on two tasks: image recognition on MNIST-like and CIFAR10
+datasets and music transcription on MusicNet \citep{thickstun_learning_2017}. We reliably
+replicate the state-of-the-art result for $\cplx$-valued networks on MusicNet with $50-100\times$
+compression rate.
 \end{abstract}
@@
 on the tasks and datasets, that were studied in prior research on complex-valued networks.
-
-% general training strategy
+All experiments share the following settings unless specified otherwise:
+\begin{itemize}
+  \item ADAM optimizer with the base learning rate of $10^{-3}$
+  \item learning rate the annealing schedule from \citep{trabelsi_deep_2017}
+  \item global gradient clipping to within an $\ell_2$-norm ball of radius $0.05$
+\end{itemize}
+
+\subsection{Fitting and compression} % (fold)
+\label{sub:fitting_and_compression}
+
 The goal of the following experiments to study the sparsity-performance trade-off of the
@@
 the following training plan in every experiment. The model is trained in three successive
-stages: ``dense'' $\to$ ``sparsify'' $\to$ ``fine-tune''.
-%
-The last two stages are used to compare the .
-
-At the first, ``dense'', stage every network retains its original non-bayesian layers
-and is fit ``as-is'' using only the likelihood from \eqref{eq:elbo} without variational
-dropout.
-
-During the ``sparsify'' stage we make the relevant layers bayesian and apply $\cplx$-variational
+stages: ``dense'' $\to$ ``sparsify'' $\to$ ``fine-tune''. Parameter values and the internal
+state of the optimizer for similar parameters are kept between stages.
+
+At the \textit{``dense''} stage every network is fit ``as-is'', retaining its original
+non-bayesian architecture and using only the likelihood from \eqref{eq:elbo} without
+variational dropout.
+%
+During the \textit{``sparsify''} stage we make every layer bayesian and apply $\cplx$-variational
 dropout sec.~\ref{ssub:variational_dropout} (or sec.~\ref{ssub:empirical_bayes}) or its $\real$
@@
 Higher $C$ yields increasingly more sparse layers upon termination of this stage.
-
-Before transitioning to the ``fine-tune'' stage we compute the mask of non-zero weights
-in each layer based on the relevance scores $\alpha$ (sec.~\ref{sub:dropout}). Since
+%
+At the \textit{``fine-tune''} stage we deduce sparsity masks from the parameters of the fit
+variational approximation and train the remaining non-zero parameters similarly to the
+``dense'' stage, i.e. with non-bayesian layers, but with fixed sparsity masks.
+
+Between \textit{``sparsify''} and \textit{``fine-tune''} stages we compute masks of non-zero
+weights in each layer based on the relevance scores $\alpha$ (sec.~\ref{sub:dropout}). Since
 the variational approximation factorizes into univariate distributions, whether a $\cplx$
-or $\real$ parameter is zero or not is determined from its relevance score $
+or $\real$ parameter is zero or not is determined from individual relevance scores $
   \alpha = \tfrac{\sigma^2}{\lvert\mu\rvert^2}
-$: non-zero (relevant) if $\log \alpha \leq \tau$, zero (irrelevant) otherwise. Figure~%
-\ref{fig:typical_log_alpha_distrib} depicts the distribution of $\log \alpha$ values
-from \textbf{some run}, which exhibits the typical behaviour we noticed in all experiments
-conducted: there always is a single mode within the moderately negative range, and one or
-two modes to the right of $0$. The relative mass of each mode changes with $C$ and the
-higher the coefficient is, the more mass is shifted to the positive half. However, in every
-exepriment the trough between the peaks of the negative mode and the first positive one
-is around zero.
-
-Thus, in every experiment we set $\tau = -\tfrac12$, which is admittedly very low, especially
-considering that the recommended setting in \citep{molchanov_variational_2017} is $3$. This
-yields high levels of sparsity,
-The rationale behind our choice was twofold: we use an extra fine tuning
-stage, and keep the weights that are away from zero with high probability.
-
-These masks are then used during ``fine-tune'' to train the remaining non-zero parameters
-similar to the ``dense'' stage, i.e. with layers non-bayesian layers, but with fixed
-sparsity masks.
-
-Unless specified otherwise we use ADAM optimizer with the base learning rate of $10^{-3}$
-and the annealing schedule from .
+$: non-zero if $\log \alpha \leq \tau$, zero otherwise. Figure~\ref{fig:log-relevance}
+(top) displays general shape of the distribution of $\log \alpha$ values from the experiment
+in sec.~\ref{sub:mnist_like_datasets}, which depicts the typical behaviour noticed in all
+experiments conducted on every considered dataset: there always is a single mode within the
+moderately negative range, and one or two modes to the right of $0$. The relative mass of
+each mode changes with $C$ and the higher the coefficient is, the more mass is shifted to
+the positive half. In every experiment the trough between the peaks of the negative mode
+and the first positive one is around zero.
+
+\begin{figure}[!ht]
+  \centering
+  \begin{subfigure}[b]{0.9\textwidth}
+    \centering
+    \includegraphics[width=1.\linewidth,draft]{../notebooks/assets/grad_log.pdf}
+    % \caption{} \label{fig:log-relevance-kde}
+  \end{subfigure} \\
+  % \hfill
+  \begin{subfigure}[b]{0.9\textwidth}
+    \centering
+    \includegraphics[width=1.\linewidth,draft]{../notebooks/assets/grad_log.pdf}
+    % \caption{} \label{fig:log-relevance-proba}
+  \end{subfigure}
+  \caption{%
+    \textit{top}: Estimate of $\log\alpha$ density for a convolutional and dense layer
+    from the convolutional model of sec.~\ref{sub:mnist_like_datasets}.
+    \textit{bottom}: The probability of 
+  }
+  \label{fig:log-relevance}
+\end{figure}
+
+We decide if a parameter is \textit{``non-zero''} if it is within $\delta$ relative
+tolerance of its mean with high probability under the approximate posterior. Since
+\eqref{eq:c-gauss-vi} is Gaussian, $
+  \tfrac{\lvert w - \mu \rvert^2}
+        {\alpha \lvert \mu \rvert^2}
+$ is $\chi^2_k$ distributed with shape $k=1$ ($\real$) or $2$ ($\cplx$), whence
+\begin{equation} \label{eq:prob_relevant}
+  \Pr\bigl(
+    \lvert w - \mu \rvert \leq \delta \lvert \mu \rvert
+  \bigr)
+    = \Pr\biggl(
+      \frac{\lvert w - \mu \rvert^2}{\alpha \lvert \mu \rvert^2}
+        \leq \frac{\delta^2}{\alpha}
+    \biggr)
+    = \chi^2_k\biggl(\frac{\delta^2}{\alpha}\biggr)
+  \,.
+\end{equation}
+Figure~\ref{fig:log-relevance} (bottom) shows the probability of a $\real$ (or $\cplx$) 
+parameter being non-zero for various $\delta\in(0, \tfrac12)$ as a function of $\log \alpha$.
+For a reasonably generous $\delta = 25\%$ tolerance all values of $\log \alpha$ below
+$-2.5$ yield a reasonably high chance of a non-zero parameter. Given that $q_\theta$ is
+merely an approximation we opt for a slightly higher $\log \alpha$ threshold, and thus
+set $\tau = -\tfrac12$ in every experiment, despite it being lower than the recommended
+$\tau = 3$ in \citep{molchanov_variational_2017}, but yields much higher levels of sparsity.
+The rationale behind our choice was twofold: we use an extra fine tuning stage, and keep the
+parameters that are away from zero with high probability.
+
+% subsection fitting_and_compression (end)
 

### 2020-01-30 paper/paper.tex
edits and plans

@@
 
-In this section we compare the complex variational dropout techniques discussed above
+In this section we study the complex variational dropout techniques discussed above
 on the tasks and datasets, that were studied in prior research on complex-valued networks.
@@
   \item learning rate the annealing schedule from \citep{trabelsi_deep_2017}
-  \item global gradient clipping to within an $\ell_2$-norm ball of radius $0.05$
+  \item global gradient clipping within an $\ell_2$-norm ball of radius $0.05$
 \end{itemize}
@@
     \centering
-    \includegraphics[width=1.\linewidth,draft]{../notebooks/assets/grad_log.pdf}
+    \includegraphics[width=1.\linewidth,draft]{../notebooks/assets/log-alpha__histograms.pdf}
     % \caption{} \label{fig:log-relevance-kde}
@@
     \centering
-    \includegraphics[width=1.\linewidth,draft]{../notebooks/assets/grad_log.pdf}
+    \includegraphics[width=1.\linewidth,draft]{../notebooks/assets/proba_of_nonzero.pdf}
     % \caption{} \label{fig:log-relevance-proba}
@@
     from the convolutional model of sec.~\ref{sub:mnist_like_datasets}.
-    \textit{bottom}: The probability of 
+    \textit{bottom}: The probability of a parameter being within $\pm \delta$ relative
+    tolerance of its mean.
   }
@@
 For a reasonably generous $\delta = 25\%$ tolerance all values of $\log \alpha$ below
-$-2.5$ yield a reasonably high chance of a non-zero parameter. Given that $q_\theta$ is
-merely an approximation we opt for a slightly higher $\log \alpha$ threshold, and thus
-set $\tau = -\tfrac12$ in every experiment, despite it being lower than the recommended
-$\tau = 3$ in \citep{molchanov_variational_2017}, but yields much higher levels of sparsity.
-The rationale behind our choice was twofold: we use an extra fine tuning stage, and keep the
-parameters that are away from zero with high probability.
+$-2.5$ yield a relatively high chance of a non-zero parameter. Given that $q_\theta$
+is merely an approximation, we opt for a somewhat higher $\log \alpha$ threshold, and
+pick $\tau = -\tfrac12$, which is much lower than $\tau = 3$, recommended by
+\citet{molchanov_variational_2017}. Additional rationale behind this decision is the
+extra fine tuning, which trains the compressed model.
 
@@
 
-We conduct a moderately sized numerical experiment on MNIST and similar datasets to see
-whether the proposed $\cplx$-var dropout indeed reasonably sparsifies complex-valued networks.
-
-We compare with the studied $\cplx$-valued networks against their classical $\real$-valued
-counterparts both in terms of the resulting sparsity and test performance.
-
-Although image data is not $\cplx$ in nature, we apply two-dimensional Fourier Transform
-in order to get $\cplx$-valued inputs. We concede that this is a rather unnatural representation
-of image data, however the selection of publicly available datasets, which are not artificially
-$\cplx$-valued, is limited to audio, speech and music. Indeed, as is shown by the numerical
-experiments, a real-valued model is trained on the Fourier transformed data underperforms
-relative to its architecturally similar twin fit to on the raw color data.
-
-\citet{trabelsi_deep_2017} study the applicability of $\cplx$-valued networks to image
-classification (CIFAR-10, CIFAR-100, and a subset of SVHN). Their approach is to either
-embed $\real$ in $\cplx$ (by $\Re z = 0$), or train a smaller auxiliary network, that
-synthesizes the imaginary component from the raw channel data. \todo{DO THIS}
-In our experiments we opt to transforming the input $2d$ data with
+We conduct a moderately sized numerical experiment on MNIST and similar $28\times 28$
+greyscale image datasets to see whether the proposed $\cplx$-variational dropout indeed
+sparsifies complex-valued networks. We compare with the studied $\cplx$-valued networks
+against their $\real$-valued counterparts both in terms of the resulting sparsity and
+test performance. For a fair comparison, we make the $\cplx$-valued network have
+approximately half as many parameters, \citep{monning_evaluation_2018}.
+
+Although image data is not $\cplx$ in nature \citet{trabelsi_deep_2017} study the applicability
+of $\cplx$-valued networks to image classification (CIFAR-10, CIFAR-100, and a subset of
+SVHN). Their approach is to either embed $\real$ in $\cplx$ (by $\Re z = 0$), or train
+a smaller auxiliary network, that synthesizes the imaginary component from the raw channel
+data. In our experiments we apply the two-dimensional Fourier Transform to get $\cplx$-valued
+inputs. We concede that this is a rather unnatural representation of image data, however
+the selection of publicly available datasets, which are not artificially $\cplx$-valued,
+is limited to audio, speech and music.
+
+Indeed, as is shown by the numerical experiments on MNIST-like datasets and CIFAR10, a
+real-valued model trained on the Fourier transformed data underperforms relative to
+its architectural twin, fit to on the raw color data. At the same time complex-valued
+models
+
+% a copule of plot form mnist and fashion mnist
+% discuss the plots describing how the test -perfromance grows with compression
+% hinting at overfitting/regularization effects of masking and sparsification
 

### 2020-01-30 paper/paper.tex
added some additional plans and fleshed out a conclusion

@@
 
-% a copule of plot form mnist and fashion mnist
-% discuss the plots describing how the test -perfromance grows with compression
+% a couple of plots from MNIST and Fashion-MNIST
+% write a note on the incompressible parameters (bias, batch norm etc.)
+% discuss the plots describing how the test-performance grows with compression and then drops if the model is too sparse
 % hinting at overfitting/regularization effects of masking and sparsification
@@
 
-\subsection{Tasks and datasets} % (fold)
-\label{sub:tasks_and_datasets}
-
-\citet{trabelsi_deep_2017} study the applicability of $\cplx$-valued networks to image
-classification (CIFAR-10, CIFAR-100, reduced train of SVHN), music-transcription
-(MusicNet), and Speech Spectrum prediction (TIMIT).
-
-% complex high-dimensional time series In-phase Quadrature (IQ)
-
-\citep{monning_evaluation_2018}
-\citep{jankowski_complex-valued_1996}
-\citep{amin_complex-valued_2012}
-\citep{sarroff_complex_2018}
-
-% subsection tasks_and_datasets (end)
+\subsection{CIFAR10/100} % (fold)
+\label{sub:cifar10_100}
+
+% mention the same experimental setup as in MNIST
+% describe the VGG16 model and its cplx-valued modification
+% mention that fourier-features perfomed worse than raw image data embeded in to $\cplx$
+% compare compressed cplx-vgg against real-vgg
+% draw some conclusions
+
+% subsection cifar10_100 (end)
+
+\subsection{MusciNet} % (fold)
+\label{sub:muscinet}
+
+\citet{trabelsi_deep_2017} designed a complex-valued network that achieved SOTA results
+on the music-transcription task on MusicNet, \citep{thickstun_learning_2017}.
+
+% describe musicnet as in Trabelsi et al. (2017) also get some hints from thickstun_learning_2017
+
+% mention 44khz to 11khz downsampling and the extraction of the originally recommended test set
+% and the validation set chosen by Trabelsi et al.
+
+% Describe the network by Trabelsi and then present the reslts form then model with kernel size \textbf{6} 
+% the causally mantion that you also conducted a large study of an inferior model with kenrel size 3.
+% (do not mention that this was a mistake, you dummy!)
+
+% subsection muscinet (end)
 
@@
 \label{sec:conclusion}
+
+Despite having higher arithmetic complexity, complex-valued models provide built-in
+joint amplitude-phase transformations and regularization, \citep{hirose_complex-valued_2009},
+and enjoy superior performance on naturally $\cplx$-valued datasets \citep{citation_needed},
+that occur in ultra high-frequency radio communications and audio signal processing. In this
+study we address the issue of excessive the arithmetic complexity of complex-valued networks
+by extending the existing Bayesian compression techniques by \citet{kingma_variational_2015},
+\citet{molchanov_variational_2017} and \citet{kharitonov_variational_2018} to $\cplx$-valued
+model parameters. To this end we have conducted a large scale numerical study of such networks
+to assess the performance-compression rate trade-off and achieved performance, comparable
+to SOTA on the MusicNet dataset.
+
+Much like $\real$-valued variational dropout, the proposed $\cplx$-valued extension can be
+straightforwardly enhanced to provide structured sparsity. The results of this study have
+direct implications for real-time signal processing with embedded deep learning applications
+both in terms of lower storage requirements and higher throughput stemming from fewer
+floating-point multiplications.
 

### 2020-01-31 paper/paper.tex
comment on the error messages
notes on replications and train splits

@@
 \end{itemize}
+Every experiment is replicated several times to take random effects into account, e.g.
+random network initialization prior to ``dense'' stage, randomly ordered batches during
+SGD. Throughout every experiment on MNIST-like datasets (sec.~\ref{sub:mnist_like_datasets},
+we \textit{fixed} a random subset of the train split of each dataset, and used the test
+split to gauge the final performance. Same appriach was applied to CIFAR10 (sec.~%
+\ref{sub:cifar10_100} experiments, which could partly expalin the overall poor test
+perfomrnace we got from the tested VGG16 model ($\real$ and $\cplx$ version).
 
@@
   \centering
-  \begin{subfigure}[b]{0.9\textwidth}
+  \begin{subfigure}[b]{0.9\textwidth}  % imcl2019-style swears at this
     \centering
@@
   % \hfill
-  \begin{subfigure}[b]{0.9\textwidth}
+  \begin{subfigure}[b]{0.9\textwidth}  % imcl2019-style swears at this
     \centering
@@
 % (do not mention that this was a mistake, you dummy!)
+
+The set up of the experiment is thus:
+Each full three-stage run is replicated five times take random effects into account, e.g.
+random network initialization prior to ``dense'' stage, randomly picked $1000$ batches from
+the sample during SGD.
 

### 2020-01-31 paper/paper.tex
slight rewording in the abstract and some typo fixes

@@
 of $\cplx$-valued networks on two tasks: image recognition on MNIST-like and CIFAR10
-datasets and music transcription on MusicNet \citep{thickstun_learning_2017}. We reliably
-replicate the state-of-the-art result for $\cplx$-valued networks on MusicNet with $50-100\times$
-compression rate.
+datasets and music transcription on MusicNet. We reliably replicate the state-of-the-art
+result by \citet{thickstun_learning_2017} for $\cplx$-valued networks on MusicNet with
+$50-100\times$ compression rate.
 \end{abstract}
@@
 we \textit{fixed} a random subset of the train split of each dataset, and used the test
-split to gauge the final performance. Same appriach was applied to CIFAR10 (sec.~%
-\ref{sub:cifar10_100} experiments, which could partly expalin the overall poor test
-perfomrnace we got from the tested VGG16 model ($\real$ and $\cplx$ version).
+split to gauge the final performance. Same approach was applied to CIFAR10 (sec.~%
+\ref{sub:cifar10_100} experiments, which could partly explain the overall poor test
+performance we got from the tested VGG16 model ($\real$ and $\cplx$ version).
 
@@
 variational approximation and train the remaining non-zero parameters similarly to the
-``dense'' stage, i.e. with non-bayesian layers, but with fixed sparsity masks.
+``dense'' stage, i.e. with non-Bayesian layers, but with fixed sparsity masks.
 
@@
 real-valued model trained on the Fourier transformed data underperforms relative to
-its architectural twin, fit to on the raw color data. At the same time complex-valued
+its architectural twin, fit to on the raw colour data. At the same time complex-valued
 models

### 2020-01-31 paper/paper.tex
removed citations from the abstract, added its condensed version into intro, fixed the title

@@
 
-\title{Bayesian Sparsification of $\cplx$-valued networks}
+\title{Bayesian Sparsification of Deep $\cplx$-valued networks}
 \author{Ivan Nazarov, and Evgeny Burnaev}
@@
 \begin{abstract}
-With continual miniaturization ever more applications of deep learning can be found in
-embedded systems, where it is common to encounter data with natural complex domain
-representation. To this end we extend Variational Dropout of \citet{kingma_variational_2015}
-and \citet{kharitonov_variational_2018} to complex-valued neural networks building upon
-the work of \citet{trabelsi_deep_2017}. We verify the proposed Bayesian technique and
-assess the performance-compression trade-off by conducting a large-scale numerical study
-of $\cplx$-valued networks on two tasks: image recognition on MNIST-like and CIFAR10
-datasets and music transcription on MusicNet. We reliably replicate the state-of-the-art
-result by \citet{thickstun_learning_2017} for $\cplx$-valued networks on MusicNet with
-$50-100\times$ compression rate.
+With continual miniaturization ever more applications of deep learning can be found
+in embedded systems, where it is common to encounter data with natural complex domain
+representation. To this end we extend Variational Dropout to complex-valued neural
+networks. We verify the proposed Bayesian technique and assess the performance-compression
+trade-off by conducting a large-scale numerical study of $\cplx$-valued networks on
+two tasks: image recognition on MNIST-like and CIFAR10 datasets and music transcription
+on MusicNet. We reliably replicate the state-of-the-art result by \citet{trabelsi_deep_2017}
+for $\cplx$-valued networks on MusicNet with $50-100\times$ compression rate.
 \end{abstract}
@@
 Inspired by variational sparsification and stochastic sparsification techniques we
-develop bayesian dropout for $\cplx$-valued networks.
-%
+extend Bayesian dropout for $\cplx$-valued networks. We assess the performance-compression
+trade-off of the the proposed Bayesian technique by conducting a large-scale numerical
+study of $\cplx$-valued networks on two tasks: image recognition on MNIST-like and CIFAR10
+datasets and music transcription on MusicNet, \citep{thickstun_learning_2017}. We reproduce
+the state-of-the-art result by \citet{trabelsi_deep_2017} for $\cplx$-valued networks on
+the latter with $\approx 1-2\%$ of remaining non-zero parameters.
+
 The paper is structured as follows. In sec.~\ref{sec:bayesian_dropout} we review Bayesian

### 2020-01-31 paper/paper.tex
placeholders for figures and some edits

@@
 Every experiment is replicated several times to take random effects into account, e.g.
-random network initialization prior to ``dense'' stage, randomly ordered batches during
-SGD. Throughout every experiment on MNIST-like datasets (sec.~\ref{sub:mnist_like_datasets},
+random network initialization prior to training, randomly ordered batches during SGD.
+Throughout every experiment on MNIST-like datasets (sec.~\ref{sub:mnist_like_datasets},
 we \textit{fixed} a random subset of the train split of each dataset, and used the test
-split to gauge the final performance. Same approach was applied to CIFAR10 (sec.~%
+split to gauge the final performance. The same approach was applied to CIFAR10 (sec.~%
 \ref{sub:cifar10_100} experiments, which could partly explain the overall poor test
@@
 stages: ``dense'' $\to$ ``sparsify'' $\to$ ``fine-tune''. Parameter values and the internal
-state of the optimizer for similar parameters are kept between stages.
+state of the optimizer for related parameters are transferred between stages.
 
 At the \textit{``dense''} stage every network is fit ``as-is'', retaining its original
-non-bayesian architecture and using only the likelihood from \eqref{eq:elbo} without
+non-bayesian architecture and using only the likelihood term from \eqref{eq:elbo} without
 variational dropout.
@@
 %
-At the \textit{``fine-tune''} stage we deduce sparsity masks from the parameters of the fit
-variational approximation and train the remaining non-zero parameters similarly to the
-``dense'' stage, i.e. with non-Bayesian layers, but with fixed sparsity masks.
+The \textit{``fine-tune''} stage begins with computing the sparsity masks from the fitted
+approximation $q_\theta(W)$ and proceeds to train the non-zero parameters similarly to
+the ``dense'' stage, i.e. with non-Bayesian layers and fixed sparsity masks. The test
+performance is reported for the model at the start and termination of the final stage.
 
@@
 $: non-zero if $\log \alpha \leq \tau$, zero otherwise. Figure~\ref{fig:log-relevance}
-(top) displays general shape of the distribution of $\log \alpha$ values from the experiment
-in sec.~\ref{sub:mnist_like_datasets}, which depicts the typical behaviour noticed in all
-experiments conducted on every considered dataset: there always is a single mode within the
-moderately negative range, and one or two modes to the right of $0$. The relative mass of
-each mode changes with $C$ and the higher the coefficient is, the more mass is shifted to
-the positive half. In every experiment the trough between the peaks of the negative mode
-and the first positive one is around zero.
+(top) displays the general shape of the distribution of $\log \alpha$ values from all
+experiments in sec.~\ref{sub:mnist_like_datasets}. In fact, this appears to be the typical
+in every experiment conducted in this study: there always is a single mode within the
+moderately negative range, and one or two modes to the right of zero. The relative mass
+of each mode changes with $C$ and the higher the coefficient is, the more mass is shifted
+to the right. In every experiment the trough between the peaks of the negative mode and
+the first positive one is around zero.
 
@@
     \centering
-    \includegraphics[width=1.\linewidth,draft]{../notebooks/assets/log-alpha__histograms.pdf}
+    \includegraphics[width=1.\linewidth,draft]{../assets/log-alpha__histograms.pdf}
     % \caption{} \label{fig:log-relevance-kde}
@@
     \centering
-    \includegraphics[width=1.\linewidth,draft]{../notebooks/assets/proba_of_nonzero.pdf}
+    \includegraphics[width=1.\linewidth,draft]{../assets/proba_of_nonzero.pdf}
     % \caption{} \label{fig:log-relevance-proba}
@@
 the selection of publicly available datasets, which are not artificially $\cplx$-valued,
-is limited to audio, speech and music.
+is limited to audio signals.
 
@@
 its architectural twin, fit to on the raw colour data. At the same time complex-valued
-models
+models.
 
 % a couple of plots from MNIST and Fashion-MNIST
+\begin{figure}[!ht]
+  \centering
+  \begin{subfigure}[b]{0.9\textwidth}  % imcl2019-style swears at this
+    \centering
+    \includegraphics[width=1.\linewidth,draft]{../assets/log-alpha__histograms.pdf}
+    % \caption{} \label{fig:log-relevance-kde}
+  \end{subfigure} \\
+  % \hfill
+  \begin{subfigure}[b]{0.9\textwidth}  % imcl2019-style swears at this
+    \centering
+    \includegraphics[width=1.\linewidth,draft]{../assets/proba_of_nonzero.pdf}
+    % \caption{} \label{fig:log-relevance-proba}
+  \end{subfigure}
+  \caption{%
+    \textit{top}: The performance-compression tradeoff for MNIST \citep{citation_needed}.
+    \textit{bottom}: The performance-compression tradeoff for Fashion MNIST \citep{citation_needed}.
+  }
+  \label{fig:mnist-like_tradeoff}
+\end{figure}
+
 % write a note on the incompressible parameters (bias, batch norm etc.)
@@
 the sample during SGD.
+
+\begin{figure}[!ht]
+  \centering
+  \begin{subfigure}[b]{0.9\textwidth}  % imcl2019-style swears at this
+    \centering
+    \includegraphics[width=1.\linewidth,draft]{../assets/log-alpha__histograms.pdf}
+    % \caption{} \label{fig:log-relevance-kde}
+  \end{subfigure} \\
+  % \hfill
+  \begin{subfigure}[b]{0.9\textwidth}  % imcl2019-style swears at this
+    \centering
+    \includegraphics[width=1.\linewidth,draft]{../assets/proba_of_nonzero.pdf}
+    % \caption{} \label{fig:log-relevance-proba}
+  \end{subfigure}
+  \caption{%
+    \textit{top}: MusicNet for the model of \citep{trabelsi_deep_2017} with kernel size $3$.
+    \textit{bottom}: The performance-compression tradeoff for Fashion MNIST \citep{citation_needed}.
+  }
+  \label{fig:mnist-like_tradeoff}
+\end{figure}
 

### 2020-01-31 paper/paper.tex
fleshed out placeholder figures

@@
     \centering
-    \includegraphics[width=1.\linewidth,draft]{../assets/log-alpha__histograms.pdf}
+    \includegraphics[width=1.\linewidth]{../assets/log-alpha__sum__mnist__20200131-202713.pdf}
     % \caption{} \label{fig:log-relevance-kde}
@@
     \centering
-    \includegraphics[width=1.\linewidth,draft]{../assets/proba_of_nonzero.pdf}
+    \includegraphics[width=1.\linewidth]{../assets/log-alpha__sum__fashion-mnist__20200131-205926.pdf}
     % \caption{} \label{fig:log-relevance-proba}
@@
   \centering
+  \begin{subfigure}[b]{0.95\textwidth}  % imcl2019-style swears at this
+    \centering
+    \includegraphics[width=1.\linewidth]{../assets/sum__mnist__fine-tune.pdf}
+    % \caption{} \label{fig:log-relevance-kde}
+  \end{subfigure} \\%
+  % \hfill
+  \begin{subfigure}[b]{0.95\textwidth}  % imcl2019-style swears at this
+    \centering
+    \includegraphics[width=1.\linewidth]{../assets/sum__fashion-mnist__fine-tune.pdf}
+    % \caption{} \label{fig:log-relevance-proba}
+  \end{subfigure}
+  \caption{%
+    The accuracy-compression tradeoff after ``fine-tune''.
+    \textit{top}: MNIST \citep{citation_needed};
+    \textit{bottom}: Fashion MNIST \citep{citation_needed}.
+  }
+  \label{fig:mnist-like_tradeoff}
+\end{figure}
+
+% write a note on the incompressible parameters (bias, batch norm etc.)
+% discuss the plots describing how the test-performance grows with compression and then drops if the model is too sparse
+% hinting at overfitting/regularization effects of masking and sparsification
+
+% subsection mnist_like_datasets (end)
+
+\subsection{CIFAR10/100} % (fold)
+\label{sub:cifar10_100}
+
+% mention the same experimental setup as in MNIST
+% describe the VGG16 model and its cplx-valued modification
+% mention that fourier-features perfomed worse than raw image data embeded in to $\cplx$
+% compare compressed cplx-vgg against real-vgg
+% draw some conclusions
+
+% subsection cifar10_100 (end)
+
+\subsection{MusciNet} % (fold)
+\label{sub:muscinet}
+
+\citet{trabelsi_deep_2017} designed a complex-valued network that achieved SOTA results
+on the music-transcription task on MusicNet, \citep{thickstun_learning_2017}.
+
+% describe musicnet as in Trabelsi et al. (2017) also get some hints from thickstun_learning_2017
+
+% mention 44khz to 11khz downsampling and the extraction of the originally recommended test set
+% and the validation set chosen by Trabelsi et al.
+
+% Describe the network by Trabelsi and then present the reslts form then model with kernel size \textbf{6} 
+% the causally mantion that you also conducted a large study of an inferior model with kenrel size 3.
+% (do not mention that this was a mistake, you dummy!)
+
+The set up of the experiment is thus:
+Each full three-stage run is replicated five times take random effects into account, e.g.
+random network initialization prior to ``dense'' stage, randomly picked $1000$ batches from
+the sample during SGD.
+
+\begin{figure}[!ht]
+  \centering
   \begin{subfigure}[b]{0.9\textwidth}  % imcl2019-style swears at this
     \centering
-    \includegraphics[width=1.\linewidth,draft]{../assets/log-alpha__histograms.pdf}
+    \includegraphics[width=1.\linewidth]{../assets/grid_cplx_fine_kl_div_v3_fast-fine-tune.pdf}
     % \caption{} \label{fig:log-relevance-kde}
@@
     \centering
-    \includegraphics[width=1.\linewidth,draft]{../assets/proba_of_nonzero.pdf}
+    \includegraphics[width=1.\linewidth]{../assets/grid_cplx_fine_kl_div_v2-fine-tune.pdf}
     % \caption{} \label{fig:log-relevance-proba}
@@
   \caption{%
-    \textit{top}: The performance-compression tradeoff for MNIST \citep{citation_needed}.
-    \textit{bottom}: The performance-compression tradeoff for Fashion MNIST \citep{citation_needed}.
+    Average Percision frontier for the convolutional model of \citet{trabelsi_deep_2017}.
+    Shaded horiontal region represents the $\mu\pm\sigma$ bands for the performance of the
+    uncompressed model.
+    \textit{top}: Original model ($k=6$) compressed with \textbf{\color{orange} VD}
+    (\ref{ssub:variational_dropout}) and \textbf{\color{blue} ARD} (\ref{ssub:empirical_bayes});
+    \textit{bottom}: The model of \citep{trabelsi_deep_2017} with kernel size $3$
+    compressed with \textbf{\color{blue} VD} (\ref{ssub:variational_dropout}).
   }
-  \label{fig:mnist-like_tradeoff}
+  \label{fig:musicnet_tradeoff}
 \end{figure}
-
-% write a note on the incompressible parameters (bias, batch norm etc.)
-% discuss the plots describing how the test-performance grows with compression and then drops if the model is too sparse
-% hinting at overfitting/regularization effects of masking and sparsification
-
-% subsection mnist_like_datasets (end)
-
-\subsection{CIFAR10/100} % (fold)
-\label{sub:cifar10_100}
-
-% mention the same experimental setup as in MNIST
-% describe the VGG16 model and its cplx-valued modification
-% mention that fourier-features perfomed worse than raw image data embeded in to $\cplx$
-% compare compressed cplx-vgg against real-vgg
-% draw some conclusions
-
-% subsection cifar10_100 (end)
-
-\subsection{MusciNet} % (fold)
-\label{sub:muscinet}
-
-\citet{trabelsi_deep_2017} designed a complex-valued network that achieved SOTA results
-on the music-transcription task on MusicNet, \citep{thickstun_learning_2017}.
-
-% describe musicnet as in Trabelsi et al. (2017) also get some hints from thickstun_learning_2017
-
-% mention 44khz to 11khz downsampling and the extraction of the originally recommended test set
-% and the validation set chosen by Trabelsi et al.
-
-% Describe the network by Trabelsi and then present the reslts form then model with kernel size \textbf{6} 
-% the causally mantion that you also conducted a large study of an inferior model with kenrel size 3.
-% (do not mention that this was a mistake, you dummy!)
-
-The set up of the experiment is thus:
-Each full three-stage run is replicated five times take random effects into account, e.g.
-random network initialization prior to ``dense'' stage, randomly picked $1000$ batches from
-the sample during SGD.
 
@@
     \centering
-    \includegraphics[width=1.\linewidth,draft]{../assets/log-alpha__histograms.pdf}
+    \includegraphics[width=1.\linewidth]{../assets/grid_cplx_fine_kl_div_v3_fast-c-ard-tradeoff.pdf}
     % \caption{} \label{fig:log-relevance-kde}
@@
     \centering
-    \includegraphics[width=1.\linewidth,draft]{../assets/proba_of_nonzero.pdf}
+    \includegraphics[width=1.\linewidth]{../assets/grid_cplx_fine_kl_div_v3_fast-c-ard-tradeoff.pdf}
     % \caption{} \label{fig:log-relevance-proba}
@@
   \caption{%
-    \textit{top}: MusicNet for the model of \citep{trabelsi_deep_2017} with kernel size $3$.
-    \textit{bottom}: The performance-compression tradeoff for Fashion MNIST \citep{citation_needed}.
+    Pre ``finte-tune'' performance of the best models from figure \ref{fig:musicnet_tradeoff}
+    compressed with methods of sec.~\ref{sec:dropout_for_c_valued_layers}:
+    (\ref{ssub:variational_dropout} -- \textit{top}, \ref{ssub:empirical_bayes} --  \textit{bottom}).
   }
-  \label{fig:mnist-like_tradeoff}
+  \label{fig:musicnet_tradeoff_pre_fune-tune}
 \end{figure}
-
 % subsection muscinet (end)

### 2020-02-03 cplxpaper/mnist/models/complex.py
support for half-double number of features

@@ -25,23 +25,24 @@ class SimpleConvModel(object):
     Linear = CplxLinear
     Conv2d = CplxConv2d
 
-    def __new__(cls, n_outputs=10, n_inputs=1, upcast=False):
+    def __new__(cls, n_outputs=10, n_inputs=1, upcast=False, half=False):
         if upcast:
             layers = [("cplx", AsTypeCplx())]
         else:
             layers = [("cplx", ConcatenatedRealToCplx(copy=False, dim=-3))]
 
+        n_features = [10, 25, 250] if half else [20, 50, 500]
         layers.extend([
-            ("conv1", cls.Conv2d(n_inputs, 20, 5, 1)),
+            ("conv1", cls.Conv2d(n_inputs, n_features[0], 5, 1)),
             ("relu1", CplxToCplx[torch.nn.ReLU]()),
             ("pool1", CplxToCplx[torch.nn.AvgPool2d](2, 2)),
-            ("conv2", cls.Conv2d(20, 50, 5, 1)),
+            ("conv2", cls.Conv2d(n_features[0], n_features[1], 5, 1)),
             ("relu2", CplxToCplx[torch.nn.ReLU]()),
             ("pool2", CplxToCplx[torch.nn.AvgPool2d](2, 2)),
             ("flat_", CplxToCplx[Flatten](-3, -1)),
-            ("lin_1", cls.Linear(4 * 4 * 50, 500)),
+            ("lin_1", cls.Linear(4 * 4 * n_features[1], n_features[2])),
             ("relu3", CplxToCplx[torch.nn.ReLU]()),
-            ("lin_2", cls.Linear(500, n_outputs)),
+            ("lin_2", cls.Linear(n_features[2], n_outputs)),
             ("real", CplxReal()),
             # ("real", CplxToConcatenatedReal(dim=-1)),
             # ("lin_3", torch.nn.Linear(20, 10)),
@@ -67,19 +68,20 @@ class SimpleConvModelMasked(SimpleConvModel):
 class SimpleDenseModel(object):
     Linear = CplxLinear
 
-    def __new__(cls, n_outputs=10, n_inputs=1, upcast=False):
+    def __new__(cls, n_outputs=10, n_inputs=1, upcast=False, half=False):
         if upcast:
             layers = [("cplx", AsTypeCplx())]
         else:
             layers = [("cplx", ConcatenatedRealToCplx(copy=False, dim=-3))]
 
+        n_features = [256, 256] if half else [512, 512]
[…]

### 2020-02-03 cplxpaper/mnist/models/real.py

@@ -23,18 +23,19 @@ class SimpleConvModel(object):
     Linear = torch.nn.Linear
     Conv2d = torch.nn.Conv2d
 
-    def __new__(cls, n_outputs=10, n_inputs=1):
+    def __new__(cls, n_outputs=10, n_inputs=1, double=False):
+        n_features = [40, 100, 1000] if double else [20, 50, 500]
         return torch.nn.Sequential(OrderedDict([
-            ("conv1", cls.Conv2d(n_inputs, 20, 5, 1)),
+            ("conv1", cls.Conv2d(n_inputs, n_features[0], 5, 1)),
             ("relu1", torch.nn.ReLU()),
             ("pool1", torch.nn.AvgPool2d(2, 2)),
-            ("conv2", cls.Conv2d(20, 50, 5, 1)),
+            ("conv2", cls.Conv2d(n_features[0], n_features[1], 5, 1)),
             ("relu2", torch.nn.ReLU()),
             ("pool2", torch.nn.AvgPool2d(2, 2)),
             ("flat_", Flatten(-3, -1)),
-            ("lin_1", cls.Linear(4 * 4 * 50, 500)),
+            ("lin_1", cls.Linear(4 * 4 * n_features[1], n_features[2])),
             ("relu3", torch.nn.ReLU()),
-            ("lin_2", cls.Linear(500, n_outputs)),
+            ("lin_2", cls.Linear(n_features[2], n_outputs)),
         ]))
 
 
@@ -56,14 +57,15 @@ class SimpleConvModelMasked(SimpleConvModel):
 class SimpleDenseModel(object):
     Linear = torch.nn.Linear
 
-    def __new__(cls, n_outputs=10, n_inputs=1):
+    def __new__(cls, n_outputs=10, n_inputs=1, double=False):
+        n_features = [1024, 1024] if double else [512, 512]
         return torch.nn.Sequential(OrderedDict([
             ("flat_", Flatten(-3, -1)),
-            ("lin_1", cls.Linear(n_inputs * 28 * 28, 512)),
+            ("lin_1", cls.Linear(n_inputs * 28 * 28, n_features[0])),
             ("relu2", torch.nn.ReLU()),
-            ("lin_2", cls.Linear(512, 512)),
+            ("lin_2", cls.Linear(n_features[0], n_features[1])),
             ("relu3", torch.nn.ReLU()),
-            ("lin_3", cls.Linear(512, n_outputs)),
[…]

### 2020-02-03 cplxpaper/musicnet/lr_scheduler.py
link to lr scheduler source

@@ -7,7 +7,12 @@ class Trabelsi2017LRSchedule(LambdaLR):
 
     @classmethod
     def lr_lambda(cls, epoch):
-        """Multiplicative LR schedule (for base lr 1e-3)."""
+        """Multiplicative LR schedule (for base lr 1e-3).
+        
+        Details
+        -------
+        Taken verbatim from https://github.com/ChihebTrabelsi/deep_complex_networks/blob/f7065cea654c8b2a049c40fcc40fd76817c15096/musicnet/scripts/train.py#L32-L53
+        """
         if epoch < 10:
             return 1e-0  # (1e-3)
 

### 2020-02-03 paper/paper.tex
fleshed out mnist section

@@
 % Solving the storage and artihmetic constraints encourages development of model compression
-% and sparsification methods, that focus on favourable tradeoff between performance and size.
+% and sparsification methods, that focus on favourable trade-off between performance and size.
 
@@
 on the tasks and datasets, that were studied in prior research on complex-valued networks.
-All experiments share the following settings unless specified otherwise:
-\begin{itemize}
-  \item ADAM optimizer with the base learning rate of $10^{-3}$
-  \item learning rate the annealing schedule from \citep{trabelsi_deep_2017}
-  \item global gradient clipping within an $\ell_2$-norm ball of radius $0.05$
-\end{itemize}
-Every experiment is replicated several times to take random effects into account, e.g.
-random network initialization prior to training, randomly ordered batches during SGD.
-Throughout every experiment on MNIST-like datasets (sec.~\ref{sub:mnist_like_datasets},
-we \textit{fixed} a random subset of the train split of each dataset, and used the test
-split to gauge the final performance. The same approach was applied to CIFAR10 (sec.~%
-\ref{sub:cifar10_100} experiments, which could partly explain the overall poor test
-performance we got from the tested VGG16 model ($\real$ and $\cplx$ version).
 
@@
 
-The goal of the following experiments to study the sparsity-performance trade-off of the
-proposed Bayesian sparsification methods for $\cplx$-valued networks. To this end we employ
-the following training plan in every experiment. The model is trained in three successive
-stages: ``dense'' $\to$ ``sparsify'' $\to$ ``fine-tune''. Parameter values and the internal
-state of the optimizer for related parameters are transferred between stages.
+The goal of this section to study the compression-performance trade-off of the proposed Bayesian
+sparsification methods for $\cplx$-valued networks. To this end we employ the following training
+plan in every experiment. The model is trained in three successive stages: ``dense'' $\to$
+``sparsify'' $\to$ ``fine-tune''. Parameter values and the internal state of the optimizers
+are transferred between stages.
+
+% write a note on the incompressible parameters (bias, batch norm etc.)
+The compression rate is computed based on the number of floating point values needed
+to specify the model and equals $
+  \frac{n_\mathtt{par}}{n_\mathtt{par} - n_\mathtt{zer}}
+$, where $n_\mathtt{zer}$ is the number of explicit zeros after sparsification, $n_\mathtt{par}$
+is the total number of floats. Thus each parameter is counted once in a $\real$-valued
+network, but twice in a $\cplx$-network, being a pair of real-imaginary floats. Each model
+has incompressible parameters, such as layer biases, and shifts and scalings from $\real$-
+and $\cplx$-batch normalization layers, if present.
 
 At the \textit{``dense''} stage every network is fit ``as-is'', retaining its original
-non-bayesian architecture and using only the likelihood term from \eqref{eq:elbo} without
+non-Bayesian architecture and using only the likelihood term from \eqref{eq:elbo} without
 variational dropout.
 %
-During the \textit{``sparsify''} stage we make every layer bayesian and apply $\cplx$-variational
+During the \textit{``sparsify''} stage we make every layer Bayesian and apply $\cplx$-variational
 dropout sec.~\ref{ssub:variational_dropout} (or sec.~\ref{ssub:empirical_bayes}) or its $\real$
@@
   \alpha = \tfrac{\sigma^2}{\lvert\mu\rvert^2}
-$: non-zero if $\log \alpha \leq \tau$, zero otherwise. Figure~\ref{fig:log-relevance}
-(top) displays the general shape of the distribution of $\log \alpha$ values from all
-experiments in sec.~\ref{sub:mnist_like_datasets}. In fact, this appears to be the typical
-in every experiment conducted in this study: there always is a single mode within the
-moderately negative range, and one or two modes to the right of zero. The relative mass
-of each mode changes with $C$ and the higher the coefficient is, the more mass is shifted
-to the right. In every experiment the trough between the peaks of the negative mode and
-the first positive one is around zero.
-
-\begin{figure}[!ht]
+$: non-zero if $\log \alpha \leq \tau$, zero otherwise. Figure~\ref{fig:log-alpha__mnist-like}
+displays the general shape of the distribution of $\log \alpha$ on the Fashion-MNIST dataset
+in sec.~\ref{sub:mnist_like_datasets}. This shape appears to be typical in every experiment
+conducted in this study: there always is a single mode within the moderately negative
+range, and one or two modes to the right of zero. The relative mass of each mode changes
+with $C$ and the higher the coefficient is, the more mass is shifted to the right. In every
+experiment the trough between the peaks of the negative mode and the first positive one
+is around zero.
+
+\begin{figure}[ht]
   \centering
-  \begin{subfigure}[b]{0.9\textwidth}  % imcl2019-style swears at this
-    \centering
-    \includegraphics[width=1.\linewidth]{../assets/log-alpha__sum__mnist__20200131-202713.pdf}
-    % \caption{} \label{fig:log-relevance-kde}
-  \end{subfigure} \\
-  % \hfill
-  \begin{subfigure}[b]{0.9\textwidth}  % imcl2019-style swears at this
-    \centering
-    \includegraphics[width=1.\linewidth]{../assets/log-alpha__sum__fashion-mnist__20200131-205926.pdf}
-    % \caption{} \label{fig:log-relevance-proba}
-  \end{subfigure}
+  \includegraphics[draft,width=1.\linewidth]{../assets/log-alpha__sum__fashion-mnist.pdf}
   \caption{%
-    \textit{top}: Estimate of $\log\alpha$ density for a convolutional and dense layer
-    from the convolutional model of sec.~\ref{sub:mnist_like_datasets}.
-    \textit{bottom}: The probability of a parameter being within $\pm \delta$ relative
-    tolerance of its mean.
+    Smoothed density of $\log\alpha$ for a convolutional and dense layer from the
+    model in sec.~\ref{sub:mnist_like_datasets}.
   }
-  \label{fig:log-relevance}
+  \label{fig:log-alpha__mnist-like}
 \end{figure}
@@
 \end{equation}
-Figure~\ref{fig:log-relevance} (bottom) shows the probability of a $\real$ (or $\cplx$) 
-parameter being non-zero for various $\delta\in(0, \tfrac12)$ as a function of $\log \alpha$.
+% Figure~\ref{fig:log-alpha__mnist-like} (bottom) shows the probability of a $\real$
+% (or $\cplx$)  parameter being non-zero for various $\delta\in(0, \tfrac12)$ as a function
+% of $\log \alpha$.
 For a reasonably generous $\delta = 25\%$ tolerance all values of $\log \alpha$ below
@@
 
+% common experiment settings
+Every experiment is replicated several times to take random effects into account, e.g.
+random network initialization prior to training, randomly ordered batches during SGD.
+Unless specified otherwise, every experiment uses global gradient clipping within an
+$\ell_2$-norm ball of radius $0.5$, runs SGD with ADAM optimizer with the base learning
+rate of $10^{-3}$ which is scaled after $5$, $10$, and $20$ epochs by $\tfrac1{10}$,
+$\tfrac1{20}$ and $\tfrac1{100}$, respectively.
+
 % subsection fitting_and_compression (end)
@@
 
+We conduct a moderately sized numerical experiment on MNIST and similar $28\times 28$
+greyscale image datasets to study the compression-performance trade-off of the proposed
+$\cplx$-variational dropout on simple architectures. We use classification accuracy as
+the target performance metric. We compare with the $\real$-valued networks against their
+$\cplx$-valued counterparts with approximately half as many parameters, as suggested
+by \citet{monning_evaluation_2018}.
+
+% dataset size
+We deliberately use a {fixed} random subset of $10k$ images from the train split of each
+dataset to fit the networks, and gauge the final performance on the usual test split.
+Limiting the size was done primarily to test the strength of regularization properties
+of variational dropout, and to make experiments quicker.
+% image features
+Since image data is not naturally $\cplx$-valued, we reprocess images by either embedding
+$\real$-data into $\cplx$ assuming $\Re z = 0$ (\texttt{raw}), or applying the two-dimensional
+Fourier Transform (\texttt{fft}), shifting lower frequencies to the centre of the image. We
+do not investigate the option, proposed by \citet{trabelsi_deep_2017}, to train an auxiliary
+model to synthesize the imaginary component from the real data.
+
+% model architectures
+We study the following $\real$/$\cplx$ networks:
+\begin{itemize}
+  \item \textit{SimpleConvModel}: $2d$ convnet with Average pooling ($2\times 2$)
+  with layers $c(n_1, 5, 1) \to c(n_2, 5, 1) \to d(n_3) \to d(n_\mathtt{out})$
+  \item \textit{TwoLayerDenseModel}: wide shallow network with structure
+  $d(n_1) \to d(n_\mathtt{out})$
+\end{itemize}
+where $c(n, k, s)$ denotes a convolution with $n$ output channels, kernel width $k$ and
+stride $s$, and $d(n)$ is a dense layer with $n$ outputs. The values of $n_\cdot$ depend
+on the input features and are summarized in table~\ref{tbl:mnist-like-model-spec}.
+\begin{table}[hb]
+  \centering
+  \caption{Architecture parameters for models studied on MNIST-like datasets.}
+  \label{tbl:mnist-like-model-spec}
+  \begin{tabular}{lrr}
+    \toprule
+    $(n_1, n_2, n_3)$  & $\real$-\textit{SimpleConvModel} & $\cplx$-\textit{SimpleConvModel} \\
+    \midrule
+    (\texttt{raw}) & $20, 50, 500$ & $10, 25, 250$ \\
+    (\texttt{fft}) & $40, 100, 1000$ & $20, 50, 500$ \\
+    \bottomrule
+  \end{tabular}
+  \begin{tabular}{lrr}
+    \toprule
+    $(n_1)$  & $\real$-\textit{TwoLayerDenseModel} & $\cplx$-\textit{TwoLayerDenseModel} \\
+    \midrule
+    (\texttt{raw}) & $4096$ & $2048$ \\
+    (\texttt{fft}) & $8192$ & $4096$ \\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
+% discuss the plots describing how the test-performance grows with compression and then drops if the model is too sparse
+
+% hinting at overfitting/regularization effects of masking and sparsification
+
+% a couple of plots from MNIST and Fashion-MNIST
+\begin{figure}[!ht]
+  \centering
+  \begin{subfigure}[b]{0.95\textwidth}  % imcl2019-style swears at this
+    \centering
+    \includegraphics[draft,width=1.\linewidth]{../assets/sum__mnist__fine-tune.pdf}
+    % \caption{} \label{fig:log-alpha-kde}
+  \end{subfigure} \\%
+  % \hfill
+  \begin{subfigure}[b]{0.95\textwidth}  % imcl2019-style swears at this
+    \centering
+    \includegraphics[draft,width=1.\linewidth]{../assets/sum__fashion-mnist__fine-tune.pdf}
+    % \caption{} \label{fig:log-alpha-proba}
+  \end{subfigure}
+  \caption{%
+    The accuracy-compression trade-off after ``fine-tune''.
+    \textit{top}: MNIST \citep{citation_needed};
+    \textit{bottom}: Fashion MNIST \citep{citation_needed}.
+  }
+  \label{fig:mnist-like_trade-off}
+\end{figure}
+
+The same approach was applied to
+CIFAR10 (sec.~\ref{sub:cifar10_100} experiments, which could partly explain the overall
+poor test performance we got from the tested VGG16 model ($\real$ and $\cplx$ version).
+
+% comparison strategy
 We conduct a moderately sized numerical experiment on MNIST and similar $28\times 28$
@@
 
-% a couple of plots from MNIST and Fashion-MNIST
-\begin{figure}[!ht]
-  \centering
-  \begin{subfigure}[b]{0.95\textwidth}  % imcl2019-style swears at this
-    \centering
-    \includegraphics[width=1.\linewidth]{../assets/sum__mnist__fine-tune.pdf}
-    % \caption{} \label{fig:log-relevance-kde}
-  \end{subfigure} \\%
-  % \hfill
-  \begin{subfigure}[b]{0.95\textwidth}  % imcl2019-style swears at this
-    \centering
-    \includegraphics[width=1.\linewidth]{../assets/sum__fashion-mnist__fine-tune.pdf}
-    % \caption{} \label{fig:log-relevance-proba}
-  \end{subfigure}
-  \caption{%
-    The accuracy-compression tradeoff after ``fine-tune''.
-    \textit{top}: MNIST \citep{citation_needed};
-    \textit{bottom}: Fashion MNIST \citep{citation_needed}.
-  }
-  \label{fig:mnist-like_tradeoff}
-\end{figure}
-
-% write a note on the incompressible parameters (bias, batch norm etc.)
-% discuss the plots describing how the test-performance grows with compression and then drops if the model is too sparse
-% hinting at overfitting/regularization effects of masking and sparsification
-
 % subsection mnist_like_datasets (end)
@@
     \centering
-    \includegraphics[width=1.\linewidth]{../assets/grid_cplx_fine_kl_div_v3_fast-fine-tune.pdf}
-    % \caption{} \label{fig:log-relevance-kde}
+    \includegraphics[draft,width=1.\linewidth]{../assets/grid_cplx_fine_kl_div_v3_fast-fine-tune.pdf}
+    % \caption{} \label{fig:log-alpha-kde}
   \end{subfigure} \\
@@
     \centering
-    \includegraphics[width=1.\linewidth]{../assets/grid_cplx_fine_kl_div_v2-fine-tune.pdf}
-    % \caption{} \label{fig:log-relevance-proba}
+    \includegraphics[draft,width=1.\linewidth]{../assets/grid_cplx_fine_kl_div_v2-fine-tune.pdf}
+    % \caption{} \label{fig:log-alpha-proba}
   \end{subfigure}
@@
   }
-  \label{fig:musicnet_tradeoff}
+  \label{fig:musicnet_trade-off}
 \end{figure}
@@
     \centering
-    \includegraphics[width=1.\linewidth]{../assets/grid_cplx_fine_kl_div_v3_fast-c-ard-tradeoff.pdf}
-    % \caption{} \label{fig:log-relevance-kde}
+    \includegraphics[draft,width=1.\linewidth]{../assets/grid_cplx_fine_kl_div_v3_fast-c-ard-trade-off.pdf}
+    % \caption{} \label{fig:log-alpha-kde}
   \end{subfigure} \\
@@
     \centering
-    \includegraphics[width=1.\linewidth]{../assets/grid_cplx_fine_kl_div_v3_fast-c-ard-tradeoff.pdf}
-    % \caption{} \label{fig:log-relevance-proba}
+    \includegraphics[draft,width=1.\linewidth]{../assets/grid_cplx_fine_kl_div_v3_fast-c-ard-trade-off.pdf}
+    % \caption{} \label{fig:log-alpha-proba}
   \end{subfigure}
   \caption{%
-    Pre ``finte-tune'' performance of the best models from figure \ref{fig:musicnet_tradeoff}
+    Pre ``finte-tune'' performance of the best models from figure \ref{fig:musicnet_trade-off}
     compressed with methods of sec.~\ref{sec:dropout_for_c_valued_layers}:
@@
   }
-  \label{fig:musicnet_tradeoff_pre_fune-tune}
+  \label{fig:musicnet_trade-off_pre_fune-tune}
 \end{figure}

### 2020-02-03 paper/paper.tex
something on cifar10

@@
 % discuss the plots describing how the test-performance grows with compression and then drops if the model is too sparse
-
+Figures~\ref{fig:mnist-like__trade-off__vd} and ~\ref{fig:mnist-like__trade-off__ard} show
+the results on the ``MNIST'' dataset for $\tau\in\{-\tfrac12, \tfrac32\}$ and $
+  C \in \{\tfrac3{2^{k+1}}\colon k=1..16\}
+$ replicated $5$ times using the method from sec.~\ref{ssub:variational_dropout} (VD)
+and~\ref{ssub:empirical_bayes} (ARD), respectively (results for other MNIST-like datasets
+are in the appendix).
+
+% discussion of TwoLayerDenseModel
+% discussion of SimpleConvModel
 % hinting at overfitting/regularization effects of masking and sparsification
@@
     \centering
-    \includegraphics[draft,width=1.\linewidth]{../assets/sum__mnist__fine-tune.pdf}
+    \includegraphics[draft,width=1.\linewidth]{../assets/sum__mnist__fine-tune__TwoLayerDenseModelVD.pdf}
     % \caption{} \label{fig:log-alpha-kde}
@@
     \centering
-    \includegraphics[draft,width=1.\linewidth]{../assets/sum__fashion-mnist__fine-tune.pdf}
+    \includegraphics[draft,width=1.\linewidth]{../assets/sum__mnist__fine-tune__SimpleConvModelVD.pdf}
     % \caption{} \label{fig:log-alpha-proba}
@@
   \caption{%
-    The accuracy-compression trade-off after ``fine-tune''.
-    \textit{top}: MNIST \citep{citation_needed};
-    \textit{bottom}: Fashion MNIST \citep{citation_needed}.
+    The compression-accuracy trade-off after ``fine-tune'' on MNIST of \textit{TwoLayerDenseModel}
+    (top) and \textit{SimpleConvModel} (bottom) for method in sec.~\ref{ssub:variational_dropout}.
   }
-  \label{fig:mnist-like_trade-off}
+  \label{fig:mnist-like__trade-off__vd}
 \end{figure}
 
-The same approach was applied to
-CIFAR10 (sec.~\ref{sub:cifar10_100} experiments, which could partly explain the overall
-poor test performance we got from the tested VGG16 model ($\real$ and $\cplx$ version).
-
-% comparison strategy
-We conduct a moderately sized numerical experiment on MNIST and similar $28\times 28$
-greyscale image datasets to see whether the proposed $\cplx$-variational dropout indeed
-sparsifies complex-valued networks. We compare with the studied $\cplx$-valued networks
-against their $\real$-valued counterparts both in terms of the resulting sparsity and
-test performance. For a fair comparison, we make the $\cplx$-valued network have
-approximately half as many parameters, \citep{monning_evaluation_2018}.
-
-Although image data is not $\cplx$ in nature \citet{trabelsi_deep_2017} study the applicability
-of $\cplx$-valued networks to image classification (CIFAR-10, CIFAR-100, and a subset of
-SVHN). Their approach is to either embed $\real$ in $\cplx$ (by $\Re z = 0$), or train
-a smaller auxiliary network, that synthesizes the imaginary component from the raw channel
-data. In our experiments we apply the two-dimensional Fourier Transform to get $\cplx$-valued
-inputs. We concede that this is a rather unnatural representation of image data, however
-the selection of publicly available datasets, which are not artificially $\cplx$-valued,
-is limited to audio signals.
-
-Indeed, as is shown by the numerical experiments on MNIST-like datasets and CIFAR10, a
-real-valued model trained on the Fourier transformed data underperforms relative to
-its architectural twin, fit to on the raw colour data. At the same time complex-valued
-models.
+\begin{figure}[!ht]
+  \centering
+  \begin{subfigure}[b]{0.95\textwidth}  % imcl2019-style swears at this
+    \centering
+    \includegraphics[draft,width=1.\linewidth]{../assets/sum__mnist__fine-tune__TwoLayerDenseModelARD.pdf}
+    % \caption{} \label{fig:log-alpha-kde}
+  \end{subfigure} \\%
+  % \hfill
+  \begin{subfigure}[b]{0.95\textwidth}  % imcl2019-style swears at this
+    \centering
+    \includegraphics[draft,width=1.\linewidth]{../assets/sum__mnist__fine-tune__SimpleConvModelARD.pdf}
+    % \caption{} \label{fig:log-alpha-proba}
+  \end{subfigure}
+  \caption{%
+    The compression-accuracy trade-off after ``fine-tune'' on MNIST of \textit{TwoLayerDenseModel}
+    (top) and \textit{SimpleConvModel} (bottom) for method in sec.~\ref{ssub:empirical_bayes}.
+  }
+  \label{fig:mnist-like__trade-off__ard}
+\end{figure}
+
+% which is better ARD or VD
+It is worth pointing out that the prior used in ARD models offers slightly more favourable
+compression-accuracy values, matching the established perception that log-uniform prior
+is \todo{too harsh for sparsification tasks}, \citep{kharitonov_variational_2018}.
+
+% hopeful conclusion
+\todo{The numerical experiments on MNIST-like datasets} demonstrate, that models using fourier
+features perform poorly in comparison to models using raw image input.
 
@@
 
-\subsection{CIFAR10/100} % (fold)
-\label{sub:cifar10_100}
+\subsection{CIFAR10} % (fold)
+\label{sub:cifar10}
 
 % mention the same experimental setup as in MNIST
+Experiments on CIFAR10 dataset are set up similarly to MNIST-like experiment, except
+that we study VGG16 model, \citep{citation_needed}, and its $\cplx$-counterpart, fit
+on the full training split of $60k$ colour $32\times32$ images, and use only raw image
+input features (\texttt{raw}).
+
 % describe the VGG16 model and its cplx-valued modification
+The $\cplx$-VGG16 model is architecturally identical to VGG16, except for all layers
+replaced by their $\cplx$-valued versions. To maintain comparability, we half the filter
+sizes of $\cplx$ model.
+
 % mention that fourier-features perfomed worse than raw image data embeded in to $\cplx$
+
 % compare compressed cplx-vgg against real-vgg
+
 % draw some conclusions

### 2020-02-04 cplxpaper/auto/utils.py
locate and load the latest snapshot of a stage

@@ -27,8 +27,36 @@ def load_snapshot(filename):
         state = torch.load(fin, map_location=torch.device("cpu"))
 
     # verify version
+    pass
 
     return state
+
+
+def load_stage_snapshot(stage, folder, mismatch="ignore"):
+    """Load the snapshot of the given phase from the experiment."""
+    if mismatch not in ("ignore", "raise"):
+        raise ValueError(f"`mismatch` must be either 'ignore' or 'raise'.")
+
+    # synchronized with naming format at ./auto.py#L393
+    pat = re.compile(r"^(\d+)-(\S+)\s+.*?(\d{8}-\d{6})\.gz$")
+
+    # list all filenames matching the format
+    folder, _, filenames = next(os.walk(folder))
+    matches = filter(None, map(pat.match, filenames))
+    matches = sorted(matches,
+                     key=lambda m: time.strptime(m.group(3), "%Y%m%d-%H%M%S"))
+    for m in matches:
+        if m.group(2) == stage:
+            # load and validate stage ID
+            snapshot = load_snapshot(os.path.join(folder, m.string))
+
+            # the snapshot is expected to comply with ./auto.py#L392-411
+            if snapshot["stage"][0] == stage:
+                return snapshot
+
+    if mismatch == "ignore":
+        return {}
+    raise RuntimeError(f"'{stage}' not found.")
 
 
 def param_defaults(param, **defaults):
@@ -230,7 +258,7 @@ def filter_prefix(dictionary, *prefixes):
 
 def file_cache(cachename, recompute=False):
     """File-based cache decorator.
-    
+
     Parameters
     ----------
     cachename : str, or None

### 2020-02-04 cplxpaper/auto/utils.py
manifest loader and completion verifier

@@ -1,6 +1,7 @@
 import os
 import re
 import time
+import json
 import gzip
 import pickle
 
@@ -30,6 +31,50 @@ def load_snapshot(filename):
     pass
 
     return state
+
+
+def load_manifest(folder, create=True):
+    """Load the manifest of an experiment, falling back to snapshots if missing."""
+    # check if `config.json` resides at 'folder'
+    manifest = os.path.join(folder, "config.json")
+    if os.path.exists(manifest):
+        with open(manifest, "r") as fin:
+            return json.load(fin)
+
+    # synchronized with naming format at ./auto.py#L393
+    pat = re.compile(r"^\d+-.*\.gz$")
+
+    _, _, filenames = next(os.walk(folder))
+    for match in filter(None, map(pat.match, filenames)):
+        # load the first snapshot and quit
+        snapshot = load_snapshot(os.path.join(folder, match.string))
+        if create:
+            with open(manifest, "w") as fout:
+                json.dump(snapshot["options"], fout, indent=2, sort_keys=False)
+
+        return snapshot["options"]
+
+    raise RuntimeError(f"Could not load config at '{folder}'")
+
+
+def verify_experiment(folder):
+    """Check if the experiment at the specified folder has been completed."""
+    if not os.path.exists(folder):
+        return False
+
+    folder, _, filenames = next(os.walk(folder))
+    manifest = load_manifest(folder, create=True)
+
+    # stage map to check if any one is missing
+    stages = dict.fromkeys(manifest["stage-order"], False)
+    for j, stage in enumerate(stages.keys()):
+        # synchronized with naming format at ./auto.py#L393
+        pat = re.compile(f"^{j}-{stage}\\s+.*\\.gz$")
+
+        match = next(filter(None, map(pat.match, filenames)), None)
+        stages[stage] = match is not None
+
+    return all(stages.values())
 
 
 def load_stage_snapshot(stage, folder, mismatch="ignore"):

### 2020-02-04 paper/paper.tex
some music net description

@@
 Experiments on CIFAR10 dataset are set up similarly to MNIST-like experiment, except
-that we study VGG16 model, \citep{citation_needed}, and its $\cplx$-counterpart, fit
+that we study VGG16 model, \citep{simonyan_very_2015}, and its $\cplx$-counterpart, fit
 on the full training split of $60k$ colour $32\times32$ images, and use only raw image
@@
 
-\citet{trabelsi_deep_2017} designed a complex-valued network that achieved SOTA results
-on the music-transcription task on MusicNet, \citep{thickstun_learning_2017}.
-
 % describe musicnet as in Trabelsi et al. (2017) also get some hints from thickstun_learning_2017
-
-% mention 44khz to 11khz downsampling and the extraction of the originally recommended test set
-% and the validation set chosen by Trabelsi et al.
+MusicNet, \citep{thickstun_learning_2017}, is an annotated audio dataset, consisting of $330$
+compositions from the public domain. Similarly to \citep{trabelsi_deep_2017}, we use this
+dataset for automatic music transcription task and study the $1d$ VGG-like $\cplx$-convent
+proposed therein. Similarly to this study, we downsample the sound from 44.1kHz to 11kHz,
+retaining only $84$ out of $128$ labels, and hold-out the same validation and test splits.
+During each training epoch we sample $1000$ mini-batches of the remaining $321$ compositions
+thus: a random full window of $4096$ samples is picked within each waveform and transformed
+from $\real$ to $\cplx$ with $1d$ FFT. Annotation labels are taken at the mid-point of the
+window.
+
+We use training from sec.~\ref{sub:fitting_and_compression} with epochs lasting for $12$,
+$32$ and $50$ epochs, respectively. Early stopping is used only during the ``fine-tune''
+stage. Preliminary experiments with the model without sparsification have shown that early
+stopping almost always terminated the training process within the first $10-20$ epochs,
+and that the validation performance peaked at about $10-15$ epochs, much sooner than $200$
+in \citep{trabelsi_deep_2017}. Besides staged training and shorter ``dense'' stage, other
+important deviations from their setup include:
+\begin{itemize}
+  \item shifting lower frequencies to the centre of the window to maintain locality after
+  applying FFT (much like in sec.~\ref{sub:mnist_like_datasets})
+  \item clipping $\ell_2$ norm of parameters' gradients to $0.05$
+  \item faster learning rate reduction schedule (sec.~\ref{sub:fitting_and_compression})
+\end{itemize}
+Each full three-stage experiment is replicated five times to take random effects into account,
+e.g. random network initialization prior to ``dense'' stage, randomization of batches within
+each epoch during SGD, and stochasticity of Bayesian forward pass at ``sparsify'' stage.
 
@@
 % (do not mention that this was a mistake, you dummy!)
-
-The set up of the experiment is thus:
-Each full three-stage run is replicated five times take random effects into account, e.g.
-random network initialization prior to ``dense'' stage, randomly picked $1000$ batches from
-the sample during SGD.
 

### 2020-02-04 cplxpaper/cifar/models/vgg/__init__.py
vgg model for cifar10 experiments

@@ -1,0 +1,2 @@
+from . import real
+from . import complex

### 2020-02-04 cplxpaper/cifar/models/vgg/complex.py

@@ -1,0 +1,76 @@
+"""The complex valued VGG model."""
+import math
+import torch
+
+from collections import OrderedDict
+
+from cplxmodule import cplx
+from cplxmodule.nn.layers import CplxToCplx
+from cplxmodule.nn.layers import ConcatenatedRealToCplx
+from cplxmodule.nn.layers import CplxReal, AsTypeCplx
+
+from cplxmodule.nn.layers import CplxLinear
+from cplxmodule.nn.conv import CplxConv2d
+from cplxmodule.nn.batchnorm import CplxBatchNorm2d
+
+# var-dropout
+from cplxmodule.nn.relevance.extensions import CplxLinearVDBogus
+from cplxmodule.nn.relevance.extensions import CplxConv2dVDBogus
+
+# automatic relevance determination
+from cplxmodule.nn.relevance.extensions import CplxLinearARD
+from cplxmodule.nn.relevance.extensions import CplxConv2dARD
+
+from cplxmodule.nn.masked import CplxConv2dMasked, CplxLinearMasked
+
+from ....musicnet.models.real.base import Flatten
+
+from .real import cfg
+
+
+class VGG(torch.nn.Module):
+    Linear = CplxLinear
+    Conv2d = CplxConv2d
+
+    def __new__(cls, vgg_name='VGG16', n_outputs=10, n_channels=3,
+                upcast=False, half=False):
+        if upcast:
+            layers = [AsTypeCplx()]
+        else:
+            layers = [ConcatenatedRealToCplx(copy=False, dim=-3)]
+
+        for x in cfg[vgg_name]:
+            if x == 'M':
+                layers.append(CplxToCplx[torch.nn.MaxPool2d](kernel_size=2, stride=2))
+
+            else:
+                x = (x // 2) if half else x
+                layers.extend([
+                    cls.Conv2d(n_channels, x, kernel_size=3, padding=1),
+                    CplxBatchNorm2d(x),
+                    CplxToCplx[torch.nn.ReLU](),
+                ])
+                n_channels = x
+
+        # the last integer x was 512 (or 256).
+        return torch.nn.Sequential(
+            *layers,
+            CplxToCplx[Flatten](-3, -1),
+            cls.Linear(256 if half else 512, n_outputs),
+            CplxReal()
+        )
+
+
+class VGGVD(VGG):
+    Linear = CplxLinearVDBogus
[…]

### 2020-02-04 cplxpaper/cifar/models/vgg/real.py

@@ -1,0 +1,73 @@
+r"""The real valued VGG model. Adapted from 
+
+https://github.com/kuangliu/pytorch-cifar/blob/master/models/vgg.py
+https://github.com/anokland/local-loss/blob/master/train.py
+"""
+import torch
+
+# var-dropout
+from cplxmodule.nn.relevance.extensions import LinearVD
+from cplxmodule.nn.relevance.extensions import Conv2dVD
+
+# automatic relevance determination
+from cplxmodule.nn.relevance.extensions import LinearARD
+from cplxmodule.nn.relevance.extensions import Conv2dARD
+
+from cplxmodule.nn.masked import Conv2dMasked, LinearMasked
+
+from ....musicnet.models.real.base import Flatten
+
+
+cfg = {
+# 'VGG6a'  : [ 128,                'M', 256,      'M', 512,                'M', 512                                             ],
+# 'VGG6b'  : [ 128,                'M', 256,      'M', 512,                'M', 512,                'M'                         ],
+'VGG8'   : [  64,                'M', 128,      'M', 256,                'M', 512,                'M', 512,                'M'],
+# 'VGG8a'  : [ 128, 256,           'M', 256, 512, 'M', 512,                'M', 512                                             ],
+# 'VGG8b'  : [ 128, 256,           'M', 256, 512, 'M', 512,                'M', 512,                'M'                         ],
+# 'VGG11b' : [ 128, 128, 128, 256, 'M', 256, 512, 'M', 512, 512,           'M', 512,                'M'                         ],
+'VGG11'  : [  64,                'M', 128,      'M', 256, 256,           'M', 512, 512,           'M', 512, 512,           'M'],
+'VGG13'  : [  64,  64,           'M', 128, 128, 'M', 256, 256,           'M', 512, 512,           'M', 512, 512,           'M'],
+'VGG16'  : [  64,  64,           'M', 128, 128, 'M', 256, 256, 256,      'M', 512, 512, 512,      'M', 512, 512, 512,      'M'],
+'VGG19'  : [  64,  64,           'M', 128, 128, 'M', 256, 256, 256, 256, 'M', 512, 512, 512, 512, 'M', 512, 512, 512, 512, 'M'],
+}
+
+
+class VGG(torch.nn.Module):
+    Linear = torch.nn.Linear
+    Conv2d = torch.nn.Conv2d
+
[…]

### 2020-02-04 cplxpaper/cifar/dataset.py
cifar10 augmented by random crop aand hor-flip

@@ -51,3 +51,27 @@ class CIFAR100_Test(object):
 
     def __new__(cls, root):
         return get_dataset(datasets.CIFAR100, root, train=False)
+
+
+class AugmentedCIFAR10_Train(object):
+    """Train sample from the CIFAR10 dataset."""
+
+    def __new__(cls, root):
+        return datasets.CIFAR10(root, transform=transforms.Compose([
+            transforms.RandomCrop(32, padding=4),
+            transforms.RandomHorizontalFlip(),
+            transforms.ToTensor(),
+            transforms.Normalize((0.4914, 0.4822, 0.4465),
+                                 (0.2023, 0.1994, 0.2010)),
+        ]), target_transform=None, train=True, download=True)
+
+
+class AugmentedCIFAR10_Test(object):
+    """Test sample from the CIFAR10 dataset."""
+
+    def __new__(cls, root):
+        return datasets.CIFAR10(root, transform=transforms.Compose([
+            transforms.ToTensor(),
+            transforms.Normalize((0.4914, 0.4822, 0.4465),
+                                 (0.2023, 0.1994, 0.2010)),
+        ]), target_transform=None, train=False, download=True)

### 2020-02-05 cplxpaper/cifar/dataset.py
toggle augmentation

@@ -56,10 +56,18 @@ class CIFAR100_Test(object):
 class AugmentedCIFAR10_Train(object):
     """Train sample from the CIFAR10 dataset."""
 
-    def __new__(cls, root):
+    def __new__(cls, root, disable=False):
+        if not disable:
+            transform = [
+                transforms.RandomCrop(32, padding=4),
+                transforms.RandomHorizontalFlip()
+            ]
+
+        else:
+            transform = []
+
         return datasets.CIFAR10(root, transform=transforms.Compose([
-            transforms.RandomCrop(32, padding=4),
-            transforms.RandomHorizontalFlip(),
+            *transform,
             transforms.ToTensor(),
             transforms.Normalize((0.4914, 0.4822, 0.4465),
                                  (0.2023, 0.1994, 0.2010)),

### 2020-02-05 cplxpaper/auto/utils.py
slightly less io heavy file-caching

@@ -323,16 +323,21 @@ def file_cache(cachename, recompute=False):
     assert cachename is None or isinstance(cachename, str)
 
     def decorator(user_function):
+        cache = None
+        if isinstance(cachename, str) and os.path.exists(cachename):
+            with open(cachename, "rb") as fin:
+                cache = pickle.load(fin)
+
         def wrapper(*args, **kwargs):
+            if cache is None:
+                return user_function(*args, **kwargs)
+
             # dumb stategy: pickle the args and use it as a binary key
-            cache, key = {}, pickle.dumps((args, kwargs))
-            if isinstance(cachename, str) and os.path.exists(cachename):
-                with open(cachename, "rb") as fin:
-                    cache = pickle.load(fin)
+            key = pickle.dumps((args, kwargs), protocol=3)
+            if key in cache and not recompute:
+                return cache[key]
 
-            if key not in cache or recompute:
-                cache[key] = user_function(*args, **kwargs)
-
+            cache[key] = user_function(*args, **kwargs)
             if isinstance(cachename, str):
                 with open(cachename, "wb") as fout:
                     pickle.dump(cache, fout)

### 2020-02-05 paper/paper.tex
edits and improvements in training proc description

@@
 
-\subsection{Fitting and compression} % (fold)
+% common experiment settings
+Every experiment is replicated several times to take random effects into account, e.g.
+random network initialization prior to training, randomly ordered batches during SGD.
+Unless specified otherwise, every experiment uses global gradient clipping within an
+$\ell_2$-norm ball of radius $0.5$, runs SGD with ADAM optimizer with the base learning
+rate of $10^{-3}$ which is scaled after $5$, $10$, and $20$ epochs by $\tfrac1{10}$,
+$\tfrac1{20}$ and $\tfrac1{100}$, respectively.
+
+\subsection{Staged fitting and compression} % (fold)
 \label{sub:fitting_and_compression}
@@
 plan in every experiment. The model is trained in three successive stages: ``dense'' $\to$
-``sparsify'' $\to$ ``fine-tune''. Parameter values and the internal state of the optimizers
-are transferred between stages.
-
-% write a note on the incompressible parameters (bias, batch norm etc.)
-The compression rate is computed based on the number of floating point values needed
-to specify the model and equals $
-  \frac{n_\mathtt{par}}{n_\mathtt{par} - n_\mathtt{zer}}
-$, where $n_\mathtt{zer}$ is the number of explicit zeros after sparsification, $n_\mathtt{par}$
-is the total number of floats. Thus each parameter is counted once in a $\real$-valued
-network, but twice in a $\cplx$-network, being a pair of real-imaginary floats. Each model
-has incompressible parameters, such as layer biases, and shifts and scalings from $\real$-
-and $\cplx$-batch normalization layers, if present.
+``sparsify'' $\to$ ``fine-tune''. Model parameters and the optimizer are copied between
+stages, except before the ``fine-tune'' optimizer's internal state is reset.
 
@@
 approximation $q_\theta(W)$ and proceeds to train the non-zero parameters similarly to
-the ``dense'' stage, i.e. with non-Bayesian layers and fixed sparsity masks. The test
-performance is reported for the model at the start and termination of the final stage.
-
+the ``dense'' stage, i.e. with non-Bayesian layers and fixed sparsity masks.
+
+% on compresssion
 Between \textit{``sparsify''} and \textit{``fine-tune''} stages we compute masks of non-zero
@@
 
-We decide if a parameter is \textit{``non-zero''} if it is within $\delta$ relative
-tolerance of its mean with high probability under the approximate posterior. Since
-\eqref{eq:c-gauss-vi} is Gaussian, $
+% on compression threshold
+The threshold $\tau$ is picked so, that the remaining \textit{``non-zero''} parameters
+are within $\delta$ relative tolerance of their mean with high probability under the
+approximate posterior $q_\theta(W)$. Since \eqref{eq:c-gauss-vi} is Gaussian, $
   \tfrac{\lvert w - \mu \rvert^2}
@@
 pick $\tau = -\tfrac12$, which is much lower than $\tau = 3$, recommended by
-\citet{molchanov_variational_2017}. Additional rationale behind this decision is the
-extra fine tuning, which trains the compressed model.
-
-% common experiment settings
-Every experiment is replicated several times to take random effects into account, e.g.
-random network initialization prior to training, randomly ordered batches during SGD.
-Unless specified otherwise, every experiment uses global gradient clipping within an
-$\ell_2$-norm ball of radius $0.5$, runs SGD with ADAM optimizer with the base learning
-rate of $10^{-3}$ which is scaled after $5$, $10$, and $20$ epochs by $\tfrac1{10}$,
-$\tfrac1{20}$ and $\tfrac1{100}$, respectively.
+\citet{molchanov_variational_2017}.
 
 % subsection fitting_and_compression (end)
+
+\subsection{Metrics and performance} % (fold)
+\label{sub:metrics_and_performance}
+
+% perfromance metrics
+We use accuracy as the performance metric for multi-class image classification on MNIST-like
+and CIFAR10 datasets. Similarly to \citet{trabelsi_deep_2017} the performance in MusicNet
+experiments is measured with (pooled) average precision: predicted scores and target binary
+labels for each output are pooled, and average precision is computed based on the precision-recall
+curve as if the task was single-output.
+
+The test performance is reported befire the beginning and after termination of the ``fine-tune''
+stage. Additional rationale behind this decision is the extra fine tuning, which trains the
+compressed model.
+
+% write a note on the incompressible parameters (bias, batch norm etc.)
+The compression rate is computed based on the number of floating point values needed
+to specify the model and equals $
+  \frac{n_\mathtt{par}}{n_\mathtt{par} - n_\mathtt{zer}}
+$, where $n_\mathtt{zer}$ is the number of explicit zeros after sparsification, $n_\mathtt{par}$
+is the total number of floats. Thus each parameter is counted once in a $\real$-valued
+network, but twice in a $\cplx$-network, being a pair of real-imaginary floats. Each model
+has incompressible parameters, such as layer biases, and shifts and scalings from $\real$-
+and $\cplx$-batch normalization layers, if present.
+
+% subsection metrics_and_performance (end)
 
@@
 greyscale image datasets to study the compression-performance trade-off of the proposed
-$\cplx$-variational dropout on simple architectures. We use classification accuracy as
-the target performance metric. We compare with the $\real$-valued networks against their
-$\cplx$-valued counterparts with approximately half as many parameters, as suggested
-by \citet{monning_evaluation_2018}.
+$\cplx$-variational dropout on simple architectures. We compare with the $\real$-valued
+networks against their $\cplx$-valued counterparts with approximately half as many
+parameters, as suggested by \citet{monning_evaluation_2018}.
 
@@
 dataset to fit the networks, and gauge the final performance on the usual test split.
-Limiting the size was done primarily to test the strength of regularization properties
-of variational dropout, and to make experiments quicker.
+Limiting the size was done primarily to test the regularization strength of sparsification
+performed by variational dropout, and to make bulk experimentation faster.
+
 % image features
-Since image data is not naturally $\cplx$-valued, we reprocess images by either embedding
+Since image data is not naturally $\cplx$-valued, we preprocess images by either embedding
 $\real$-data into $\cplx$ assuming $\Re z = 0$ (\texttt{raw}), or applying the two-dimensional
@@
 \begin{itemize}
-  \item \textit{SimpleConvModel}: $2d$ convnet with Average pooling ($2\times 2$)
+  \item \textit{SimpleConvModel} (SCM): $2d$ convnet with Average pooling ($2\times 2$)
   with layers $c(n_1, 5, 1) \to c(n_2, 5, 1) \to d(n_3) \to d(n_\mathtt{out})$
-  \item \textit{TwoLayerDenseModel}: wide shallow network with structure
+  \item \textit{TwoLayerDenseModel} (TLDM): wide shallow network with structure
   $d(n_1) \to d(n_\mathtt{out})$
@@
     \toprule
-    $(n_1, n_2, n_3)$  & $\real$-\textit{SimpleConvModel} & $\cplx$-\textit{SimpleConvModel} \\
+    $(n_1, n_2, n_3)$  & $\real$-\textit{SCM} & $\cplx$-\textit{SCM} \\
     \midrule
@@
     \toprule
-    $(n_1)$  & $\real$-\textit{TwoLayerDenseModel} & $\cplx$-\textit{TwoLayerDenseModel} \\
+    $(n_1)$  & $\real$-\textit{TLDM} & $\cplx$-\textit{TLDM} \\
     \midrule
@@
 
-% discussion of TwoLayerDenseModel
-% discussion of SimpleConvModel
+% discussion of TwoLayerDenseModel (TLDM) and SimpleConvModel (SCM)
 % hinting at overfitting/regularization effects of masking and sparsification

### 2020-02-05 setup.py
belated dependency update

@@ -18,7 +18,7 @@ setup(
         "cplxpaper.mnist.models",
         "cplxpaper.cifar.models"
     ],
-    requires=["torch", "numpy", "pandas", "cplxmodule", "sklearn"],
+    requires=["torch", "numpy", "pandas", "cplxmodule", "sklearn", "ncls", "resampy", "h5py"],
     # install_requires=[  # uncomment for publishing
     #     "cplxmodule @ git+https://github.com/ivannz/cplxmodule.git"
     # ]

### 2020-02-05 paper/paper.tex
fixed eqref in appendix and incorporated coauthors edits

@@
 in $\cplx$ field. Despite inherently higher arithmetic complexity, which stems from up to four
-floating point operations per single $\cplx$ multiplication, \citep{monning_evaluation_2018},
+floating point operations per single $\cplx$ multiplication \citep{monning_evaluation_2018}
 $\cplx$-arithmetic reduces ineffective degrees of freedom in comparison with an analogous
@@
 % on dropout
-Dropout, \citep{hinton_improving_2012}, prevents overfitting by injecting multiplicative
+Dropout \citep{hinton_improving_2012} prevents overfitting by injecting multiplicative
 binary noise into layer's weights, which breaks up co-adaptations that could occur
@@
 as replicated multitask learning, then by sampling uncorrelated weight masks dropout acts
-as superposition method, which better utilizes the learning capacity of the network.
+as a superposition method, which better utilizes the learning capacity of the network.
 % many identical copies of the same task; \cite[Appendix A.1]{cheung_superposition_2019}
@@
 which updates prior beliefs in accordance with the likelihood of empirical observations
-into posterior belief. Under suitable modelling and prior assumptions, Bayesian methods
-can be used towards model sparsification, \citep{kingma_variational_2015,molchanov_variational_2017},
-and \citep{kharitonov_variational_2018}.
+into posterior belief. Bayesian methods with suitable modelling and prior assumptions, such
+as Variational Dropout, can be used towards model sparsification
+\citep{kingma_variational_2015,molchanov_variational_2017,kharitonov_variational_2018}.
 
@@
 number of non-zero entries in $[0, 1]$-valued stochastic parameter masks with learnable
-hard-concrete distribution with an atom at $0$, \citep{maddison_concrete_2016,jang_categorical_2017}.
+hard-concrete distribution with an atom at $0$ \citep{maddison_concrete_2016,jang_categorical_2017}.
 Their results suggest that although var-dropout may achieve good accuracy-sparsity balance
 and outperform pruning and $\ell_0$ on the studied architectures, pruning is preferable for
-its simplicity and speed. They also observe that despite dropout showing more variable
-performance, than magnitude pruning, it nevertheless induces non-uniform sparsity throughout
-the model, which is essential for superior compression \citep{he_amc:_2018}.
+its simplicity and speed. They also observe that, despite dropout showing more variable
+performance than magnitude pruning, it induces non-uniform sparsity throughout the model,
+which has been shown by \citet{he_amc:_2018} to be essential for superior compression.
 % Magnitude pruning induces user-specified sparsity distributions.
@@
 extend Bayesian dropout for $\cplx$-valued networks. We assess the performance-compression
-trade-off of the the proposed Bayesian technique by conducting a large-scale numerical
-study of $\cplx$-valued networks on two tasks: image recognition on MNIST-like and CIFAR10
-datasets and music transcription on MusicNet, \citep{thickstun_learning_2017}. We reproduce
-the state-of-the-art result by \citet{trabelsi_deep_2017} for $\cplx$-valued networks on
-the latter with $\approx 1-2\%$ of remaining non-zero parameters.
+trade-off of the proposed Bayesian technique by conducting a large-scale numerical study
+of $\cplx$-valued networks on two tasks: image recognition on MNIST-like and CIFAR10 datasets
+and music transcription on MusicNet \citep{thickstun_learning_2017}. We reproduce the
+state-of-the-art result by \citet{trabelsi_deep_2017} for $\cplx$-valued networks on the
+latter with $\approx 5\%$ of remaining non-zero parameters.
 
@@
 and derive expressions for the divergence term. In sec.~\ref{sec:experiments} we evaluate
-the sparsification rate and compare the resulting performance of various $\cplx$-networks
+the sparsification rate, compare the resulting performance of various $\cplx$-networks
 proposed in prior work, and discuss the outcomes.
@@
 
-The posterior itself is intractable, save for the relatively simple cases \citep{citation_needed},
-and therefore exact inference is traded for tractability and scalability offered by Variational
+The posterior distribution itself is intractable, save for the relatively simple cases, and
+therefore exact inference is traded for tractability and scalability offered by Variational
 Inference. Instead of deriving $p(\omega \mid D)$ using the rule, this approach recasts
@@
   \omega \mapsto \nabla_\theta \log q_\theta(\omega)
-$, \citep{williams_simple_1992}, or can be represented as differentiable transformations
-of non-parametric noise, \citep{kingma_auto-encoding_2014,figurnov_implicit_2019}.
+$ \citep{williams_simple_1992} or can be represented as differentiable transformations
+of non-parametric noise \citep{kingma_auto-encoding_2014,figurnov_implicit_2019}.
 % (reparameterization trick, pathwise gradieent) $q_{\theta}(d\omega)$ is a push-forward
@@
 variational objectives are possible, provided $p(\omega \mid D)$ is probed only through
-$\log p(D \mid \omega)$ and $\log \pi(\omega)$, \citep{ranganath_operator_2018}.
-
-\textit{Stochastic Gradient Variational Bayes} (SGVB), proposed by \citep{kingma_auto-encoding_2014},
+$\log p(D \mid \omega)$ and $\log \pi(\omega)$ \citep{ranganath_operator_2018}.
+
+\textit{Stochastic Gradient Variational Bayes} (SGVB), proposed by \citet{kingma_auto-encoding_2014},
 is a differentiable unbiased Monte-Carlo estimator of \eqref{eq:elbo_general}, which
@@
 $ is an iid sample from $p_\varepsilon$. Intractable KL-divergence terms can be replaced
-by differentiable unbiased sampling estimators, \citep{kingma_auto-encoding_2014}.
+by differentiable unbiased sampling estimators \citep{kingma_auto-encoding_2014}.
 %
@@
 %
-% (DSVI) titsias-lazaro.tex
-\todo{DSVI}
-\citep{titsias_doubly_2014}
+% (DSVI) titsias-lazaro.tex \todo{DSVI} \citep{titsias_doubly_2014}
 
@@
 With a special family of posterior approximation, variational inference can be used as
-a regularization method and as model sparsification technique. \citet{kingma_variational_2015}
+a regularization method and as a model sparsification technique. \citet{kingma_variational_2015}
 consider Dropout \citep{hinton_improving_2012}, DropConnect \citep{wan_regularization_2013},
@@
 % see p.6 sec 3.4 of kingma_variational_2015
-%
-In sec.~\ref{sub:real-chisq-grad} we verify the approximation against Monte-Carlo
-estimates of \eqref{eq:improper-kl-div-real} for $\alpha$ varying over a fine logarithmic
-grid, and confirm its accuracy, by comparing its derivative to the exact derivative of
-\eqref{eq:improper-kl-div-real} with respect to $\log \alpha$.
+We independently verify their approximation against Monte-Carlo estimates for $\alpha$
+varying over a fine logarithmic grid and the exact expression for the derivative of
+\eqref{eq:improper-kl-div-real}, which we derive in appendix~\ref{sub:real-chisq-grad}.
 % (!) good for SGVB: gradient-based methods require unbiased gradient estimates
@@
   \mathcal{N}(0, \tau^{-1}_{ij})
-$ with learnable precision $\tau_{ij} > 0$. This method, known as \textit{Empirical Bayes}
-\citep{citation_needed}, fits a prior distribution while performing variational inference.
-Maximizing \eqref{eq:elbo} over $\tau$, holding other parameters fixed, yields $
+$ with learnable precision $\tau_{ij} > 0$. This method, known as \textit{Empirical Bayes},
+fits a prior distribution while performing variational inference. Maximizing \eqref{eq:elbo}
+over $\tau$, holding other parameters fixed, yields $
   \tau^* = {(\mu^2 + \sigma^2)}^{-1}
@@
 efficient. \citet{molchanov_variational_2017} propose an improvement by introducing
-\textit{additive noise parameterization}. They argue in favour of abandoning the
-$(\mu, \alpha)$ parameterization in favour of an equivalent $(\mu, \sigma^2)$, since
-the latter renders $
+\textit{additive noise parameterization}. They argue for rejecting the $(\mu, \alpha)$
+parameterization in favour of the equivalent $(\mu, \sigma^2)$, since the latter renders $
   \nabla_\mu \tilde{\mathcal{L}}
@@
 and further stabilizes gradients in SGVB \eqref{eq:elbo}. The relevance $\alpha$ is
-calculated using $
+calculated using the ratio $
   \tfrac{\sigma^2}{\mu^2}
-$ when needed.
+$ when needed in the divergence term.
 
@@
 \eqref{eq:cplx-lin-op}. Activations include trigonometric functions and representation-dependent
-non-linearities, \citep{hirose_complex-valued_2009}: polar (phase-amplitude) $
+non-linearities \citep{hirose_complex-valued_2009}: polar (phase-amplitude) $
   z \mapsto \sigma(\lvert z \rvert) e^{j \arg z}
@@
   z \mapsto \sigma(\Re z) + j \sigma(\Im z)
-$ for some $\real$-valued non-linearity $\sigma$, possibly with learnable parameters,
+$ for some $\real$-valued non-linearity $\sigma$, possibly with learnable parameters
 \citep{trabelsi_deep_2017,wolter_complex_2018}.
@@
 or $\cplx\real$ calculus, which generalizes holomorphic calculus to non-holomorphic functions
-of $\cplx$-argument, \citep{adali_complex-valued_2011,boeddeker_computation_2019}. It satisfies
+of $\cplx$-argument \citep{adali_complex-valued_2011,boeddeker_computation_2019}. It satisfies
 product and chain rules, respects complex conjugation and linearity, but most importantly the
@@
 networks into existing $\real$ deep learning auto-differentiation frameworks. It was considered
-as a basis for $\cplx$ version of backpropagation in \citep{benvenuto_complex_1992} and
-\citep{trabelsi_deep_2017}, (see sec.~\ref{sub:wirtinger_calculus} for details).
-%
-\todo{read on holomorphic nets}
+as a basis for $\cplx$ version of backpropagation by \citet{benvenuto_complex_1992} and
+\citet{trabelsi_deep_2017}, (see sec.~\ref{sub:wirtinger_calculus} for details).
+% \todo{read on holomorphic nets}
 
@@
 % ``strength'' and ``direction'' of the linear relation between real and imaginary
-% parts, \citep{lapidoth_capacity_2003}.
+% parts \citep{lapidoth_capacity_2003}.
 % $$
@@
 The local reparameterization trick provides both faster computations, and better statistical
-efficiency of the SGVB gradient estimator, \citep{wang_fast_2013,kingma_variational_2015}.
+efficiency of the SGVB gradient estimator \citep{wang_fast_2013,kingma_variational_2015}.
 Suppose that weights $W \in \cplx^{n\times m}$ of a dense linear layer are drawn from a
@@
 and variance reduction. The latter effect stems from decorrelated gradient estimates from
-overlapping patches, \citep{kingma_variational_2015}, which allows \eqref{eq:cplx-gauss-trick}
+overlapping patches \citep{kingma_variational_2015}, which allows \eqref{eq:cplx-gauss-trick}
 to use $\cplx$ convolutions of elementwise complex squares $x^2$ and amplitudes $\lvert x \rvert^2$
@@
 We consider two priors for Bayesian dropout: \verify{log-uniform} and $\cplx$-Gaussian empirical
-Bayes, \citep{kingma_variational_2015,molchanov_variational_2017,kharitonov_variational_2018}.
+Bayes \citep{kingma_variational_2015,molchanov_variational_2017,kharitonov_variational_2018}.
 For a fully factorized approximation $q(\omega)$ and factorized prior belief $\pi(\omega)$,
@@
 \end{equation}
-We use approximation \eqref{eq:c-gauss-vi} and omit subscripts ${ij}$ below for brevity.
+We use approximation \eqref{eq:c-gauss-vi} and omit subscripts ${ij}$ for brevity.
 
@@
 \end{equation}
-\eqref{eq:cn-affine} implies that $
+Property \eqref{eq:cn-affine} implies that $
   \mathcal{N}^{\cplx}(\mu, \sigma^2, 0)
@@
 \end{equation}
-% For $\beta = 2$ we add $\gamma$ to make the right-hand side nonegative. (proof needed)
+We propse settng $\beta = 2$ for $\cplx$ variational dropout, to make the divergence
+term depend only on $\alpha$.
+% For $\beta = 2$ we add $\gamma$ to make the right-hand side nonegative. (proof missing)
+%
 Since $\mathop{Ei}(x)$ has simple analytic derivative and \eqref{eq:elbo} depends additively
@@
 \end{equation}
-which is a degenerate $\cplx$-Gaussian distribution. \eqref{eq:cplx-gauss-trick} implies
+i.e. a degenerate $\cplx$-Gaussian distribution, which implies by \eqref{eq:cplx-gauss-trick}
 \begin{equation}  \label{eq:real-scal-gauss-trick}
@@
 \end{equation}
-The KL-divergence term in \eqref{eq:elbo} coincides with \eqref{eq:improper-kl-div-real}.
-We use the approximation provided by \citep{molchanov_variational_2017}. Note that additive
-noise reparameterization, \citep{molchanov_variational_2017}, cannot be used in
-\eqref{eq:real-scal-gauss-trick}.
+The KL-divergence term for this approximation coincides with \eqref{eq:improper-kl-div-real},
+which is approximated by \citet{molchanov_variational_2017}. The major drawback of this method
+is inapplicability of the additive noise reparameterization in \eqref{eq:real-scal-gauss-trick},
+which disentangles the gradient with respect to $\mu$ from the local Gaussian noise.
 
@@
 compression-accuracy values, matching the established perception that log-uniform prior
-is \todo{too harsh for sparsification tasks}, \citep{kharitonov_variational_2018}.
+is \todo{too harsh for sparsification tasks} \citep{kharitonov_variational_2018}.
 
@@
 Experiments on CIFAR10 dataset are set up similarly to MNIST-like experiment, except
-that we study VGG16 model, \citep{simonyan_very_2015}, and its $\cplx$-counterpart, fit
+that we study VGG16 model \citep{simonyan_very_2015} and its $\cplx$-counterpart, fit
 on the full training split of $60k$ colour $32\times32$ images, and use only raw image
@@
 % describe musicnet as in Trabelsi et al. (2017) also get some hints from thickstun_learning_2017
-MusicNet, \citep{thickstun_learning_2017}, is an annotated audio dataset, consisting of $330$
-compositions from the public domain. Similarly to \citep{trabelsi_deep_2017}, we use this
+MusicNet \citep{thickstun_learning_2017} is an annotated audio dataset, consisting of $330$
+compositions from the public domain. Folowing \citet{trabelsi_deep_2017}, we use this
 dataset for automatic music transcription task and study the $1d$ VGG-like $\cplx$-convent
@@
 and that the validation performance peaked at about $10-15$ epochs, much sooner than $200$
-in \citep{trabelsi_deep_2017}. Besides staged training and shorter ``dense'' stage, other
-important deviations from their setup include:
+epoch, used by \citet{trabelsi_deep_2017}. Besides staged training and shorter ``dense''
+stage, other important deviations from their setup include:
 \begin{itemize}
@@
     (\ref{ssub:variational_dropout}) and \textbf{\color{blue} ARD} (\ref{ssub:empirical_bayes});
-    \textit{bottom}: The model of \citep{trabelsi_deep_2017} with kernel size $3$
+    \textit{bottom}: The model of \citet{trabelsi_deep_2017} with kernel size $3$
     compressed with \textbf{\color{blue} VD} (\ref{ssub:variational_dropout}).
@@
 Despite having higher arithmetic complexity, complex-valued models provide built-in
-joint amplitude-phase transformations and regularization, \citep{hirose_complex-valued_2009},
-and enjoy superior performance on naturally $\cplx$-valued datasets \citep{citation_needed},
+joint amplitude-phase transformations and regularization \citep{hirose_complex-valued_2009}
+and enjoy superior performance on naturally $\cplx$-valued datasets \citep{tarver_design_2019},
 that occur in ultra high-frequency radio communications and audio signal processing. In this
@@
   (P \otimes R) (C \otimes S) = P Q \otimes R S
-$, \citep{petersen_matrix_2012}.
+$ \citep{petersen_matrix_2012}.
 % It follows from the definition of the Kronecker product
@@
 and its gradient requires evaluating the Gauss error function, the analysis provides
-independent verification of the approximation, proposed in \citep{molchanov_variational_2017}.
-The logic of the derivation follows \citep{lapidoth_capacity_2003}.
-% \citep{pav_moments_2015} correctly notice that \cite[p. 2466]{lapidoth_capacity_2003} has a missing $\log{2}$ term.
+independent verification of the approximation, proposed by \citet{molchanov_variational_2017}.
+The logic of the derivation follows \citet{lapidoth_capacity_2003}.
+% \citet{pav_moments_2015} correctly notice that \cite[p. 2466]{lapidoth_capacity_2003} has a missing $\log{2}$ term.
 
@@
 \end{equation}
-then the desired expectation in \eqref{eq:ard-kl-div-real} equals $
+then the desired expectation in \eqref{eq:improper-kl-div-real} equals $
   \log{2} + g_1(\tfrac1{2\alpha})
@@
 %
-Hence, the derivative of \eqref{eq:ard-kl-div-real} with respect to $\alpha$ is
+Hence, the derivative of the expectation in \eqref{eq:improper-kl-div-real} with respect
+to $\alpha$ is
 $$
@@
 Finally, since $\alpha$ is nonnegative, it is typically parameterized via its logarithm.
-The gradient of \eqref{eq:ard-kl-div-real} w.r.t $\log \alpha$ is
+The gradient of \eqref{eq:improper-kl-div-real} w.r.t $\log \alpha$ is
 \begin{equation}  \label{eq:real-kl-div-deriv-log}
-  \frac{d \eqref{eq:ard-kl-div-real}}{d\log \alpha}
+  \frac{d \eqref{eq:improper-kl-div-real}}{d\log \alpha}
   % \frac{d}{d\log \alpha}
@@
 
-We compute the Monte-Carlo estimator of \eqref{eq:ard-kl-div-real} on a sample of $10^7$
+We compute the Monte-Carlo estimator of \eqref{eq:improper-kl-div-real} on a sample of $10^7$
 draws over an equally spaced grid of $\log \alpha$ in $[-12, +12]$ of size $4096$. The optimal
-coefficients of the regression, proposed by \citep{molchanov_variational_2017}, are within
+coefficients of the regression, proposed by \citet{molchanov_variational_2017}, are within
 $1\%$ relative tolerance of the reported therein.
-\begin{equation}  \label{eq:ard-kl-div-real-approx}
-  \eqref{eq:ard-kl-div-real}
+\begin{equation}  \label{eq:improper-kl-div-real-approx}
+  \eqref{eq:improper-kl-div-real}
 % - KL(\mathcal{N}(w \mid \mu, \alpha \mu^2) \|
@@
 sampling error) see fig.~\ref{fig:molchanov-derivative-replica}. The derivative of
-\eqref{eq:ard-kl-div-real-approx} with respect to $\log \alpha$ appears to be very close
-to \eqref{eq:real-kl-div-deriv-log}.
+\eqref{eq:improper-kl-div-real-approx} with respect to $\log \alpha$ appears to be very close
+to \eqref{eq:real-kl-div-deriv-log}. We compute a similar Monte-Carlo estimate for
+$\cplx$ variational dropout KL divergence term in \eqref{eq:c-vd-kl-div} with $\beta = 2$,
+fit the best approximation \eqref{eq:improper-kl-div-real-approx} and compare the derivatives.
 
@@
   \includegraphics[width=1.\linewidth]{../notebooks/assets/grad_log.pdf}
-  \caption{$\tfrac{d f(\alpha)}{d \log{\alpha}}$ of the fit in \citep{molchanov_variational_2017},
-  MC estimate of \eqref{eq:improper-kl-div-real}, and exact derivative using
-  \eqref{eq:real-kl-div-deriv-log}.}
+  \caption{$\tfrac{d f(\alpha)}{d \log{\alpha}}$ of the fit proposed in
+  \citet{molchanov_variational_2017}, MC estimate of \eqref{eq:improper-kl-div-real},
+  and the exact derivative using \eqref{eq:real-kl-div-deriv-log}.}
   \label{fig:molchanov-derivative-replica}
@@
 and Wirtinger calculus make it possible to reuse $\real$-backpropagation and existing
-auto-differentiation frameworks, \citep{trabelsi_deep_2017}.
+auto-differentiation frameworks \citep{trabelsi_deep_2017}.
 

### 2020-02-05 paper/paper.tex
scattered edits

@@
 \end{equation}
-for a random subsample $(z_i)_{i=1}^M$ from $D$ and iid $
-  (\varepsilon_i)_{i=1}^M \sim p_\varepsilon
-$.
+for a random subsample $(z_i)_{i=1}^M$ from $D$ and iid $\varepsilon_i \sim p_\varepsilon$.
 %
@@
 as a basis for $\cplx$ version of backpropagation by \citet{benvenuto_complex_1992} and
-\citet{trabelsi_deep_2017}, (see sec.~\ref{sub:wirtinger_calculus} for details).
+\citet{trabelsi_deep_2017}, (see appendix~\ref{sub:wirtinger_calculus} for details).
 % \todo{read on holomorphic nets}
@@
 efficiency of the SGVB gradient estimator \citep{wang_fast_2013,kingma_variational_2015}.
-Suppose that weights $W \in \cplx^{n\times m}$ of a dense linear layer are drawn from a
-mean field $\cplx$-Gaussian approximate posterior
+Suppose that weights $W \in \cplx^{n\times m}$ of a linear layer are drawn from a mean
+field $\cplx$-Gaussian approximation
 \begin{equation}  \label{eq:c-gauss-vi-general}
@@
 $x \in \cplx^m$ and $b \in \cplx^n$ the components of $y = W x + b$ are independent with
+distributions
 \begin{equation}  \label{eq:cplx-gauss-trick}
@@
 \end{equation}
-We use approximation \eqref{eq:c-gauss-vi} and omit subscripts ${ij}$ for brevity.
+We omit subscripts ${ij}$ for brevity in the next sectons.
 
@@
 $, yet $\mu \in \cplx^{n \times m}$. This case corresponds to inference regarding
-relevance coefficients $\xi$ rather than the parameters themselves after. Under this
-parameterization
+relevance coefficients $\xi$ rather than the parameters themselves after. Each weight
+under this parameterization is an independent degenerate $\cplx$-Gaussian distribution
 \begin{equation}  \label{eq:real-scal-gauss-vi}
@@
 \end{equation}
-i.e. a degenerate $\cplx$-Gaussian distribution, which implies by \eqref{eq:cplx-gauss-trick}
+which implies by \eqref{eq:cplx-gauss-trick} the following:
 \begin{equation}  \label{eq:real-scal-gauss-trick}
@@
 is inapplicability of the additive noise reparameterization in \eqref{eq:real-scal-gauss-trick},
-which disentangles the gradient with respect to $\mu$ from the local Gaussian noise.
+which disentangles the gradient with respect to $\mu$ from the local noise.
 

### 2020-02-05 paper/paper.tex
minor on-char fixes

@@
 % (!) good for SGVB: gradient-based methods require unbiased gradient estimates
+%
+% (in) it is in poor taste to brag about this begin the first time anyone has derived a
+% derivative of an intractable function.
 
@@
   \centering
-  \includegraphics[draft,width=1.\linewidth]{../assets/log-alpha__sum__fashion-mnist.pdf}
+  \includegraphics[draft,width=1.\linewidth]{../assets/kde-histograms-of-log-alpha-distribution.pdf}
   \caption{%
@@
 
-% on compression threshold
+% on chosing the threshold
 The threshold $\tau$ is picked so, that the remaining \textit{``non-zero''} parameters
@@
 is merely an approximation, we opt for a somewhat higher $\log \alpha$ threshold, and
-pick $\tau = -\tfrac12$, which is much lower than $\tau = 3$, recommended by
+pick $\tau \in [-\tfrac12, \tfrac32]$, which is lower than $\tau = 3$, recommended by
 \citet{molchanov_variational_2017}.
@@
 that we study VGG16 model \citep{simonyan_very_2015} and its $\cplx$-counterpart, fit
-on the full training split of $60k$ colour $32\times32$ images, and use only raw image
+on the full training split of $50k$ colour $32\times32$ images, and use only raw image
 input features (\texttt{raw}).
@@
   \caption{%
-    Pre ``finte-tune'' performance of the best models from figure \ref{fig:musicnet_trade-off}
+    Pre ``fine-tune'' performance of the best models from figure \ref{fig:musicnet_trade-off}
     compressed with methods of sec.~\ref{sec:dropout_for_c_valued_layers}:

### 2020-02-05 cplxpaper/auto/utils.py
fixed defect in file caching

@@ -322,23 +322,30 @@ def file_cache(cachename, recompute=False):
     """
     assert cachename is None or isinstance(cachename, str)
 
+    if not isinstance(cachename, str):
+        # no filename given : decorator just passes function through
+        def decorator(user_function):
+            return user_function
+
+        return decorator
+
+    # initialize an empty cache
+    if not os.path.exists(cachename):
+        with open(cachename, "wb") as fout:
+            pickle.dump({}, fout)
+
     def decorator(user_function):
-        cache = None
-        if isinstance(cachename, str) and os.path.exists(cachename):
-            with open(cachename, "rb") as fin:
-                cache = pickle.load(fin)
+        with open(cachename, "rb") as fin:
+            cache = pickle.load(fin)
 
         def wrapper(*args, **kwargs):
-            if cache is None:
-                return user_function(*args, **kwargs)
-
             # dumb stategy: pickle the args and use it as a binary key
             key = pickle.dumps((args, kwargs), protocol=3)
-            if key in cache and not recompute:
-                return cache[key]
 
-            cache[key] = user_function(*args, **kwargs)
-            if isinstance(cachename, str):
+            # no key: call the wrapped function
+            if key not in cache or recompute:
+                cache[key] = user_function(*args, **kwargs)
+
                 with open(cachename, "wb") as fout:
                     pickle.dump(cache, fout)
 

### 2020-02-06 paper/paper.tex
added proper plot placeholders

@@
   \centering
+  \begin{subfigure}[b]{0.95\textwidth}  % imcl2019-style swears at this
+    \centering
     \includegraphics[draft,width=1.\linewidth]{../assets/kde-histograms-of-log-alpha-distribution.pdf}
+  \end{subfigure} \\%
+  % \hfill
+  \begin{subfigure}[b]{0.95\textwidth}  % imcl2019-style swears at this
+    \centering
+    \includegraphics[draft,width=1.\linewidth]{../assets/kde-histograms-of-log-alpha-distribution.pdf}
+  \end{subfigure}
   \caption{%
-    Smoothed density of $\log\alpha$ for a convolutional and dense layer from the
-    model in sec.~\ref{sub:mnist_like_datasets}.
+    Smoothed density of $\log\alpha$ for a convolutional and dense layer from a model
+    in sec.~\ref{sub:mnist_like_datasets}.
   }
@@
 % discuss the plots describing how the test-performance grows with compression and then drops if the model is too sparse
-Figures~\ref{fig:mnist-like__trade-off__vd} and ~\ref{fig:mnist-like__trade-off__ard} show
-the results on the ``MNIST'' dataset for $\tau\in\{-\tfrac12, \tfrac32\}$ and $
+Plots on figure~\ref{fig:mnist-like__trade-off} show the results on the ``MNIST'' dataset for
+$\tau\in\{-\tfrac12, \tfrac32\}$ and $
   C \in \{\tfrac3{2^{k+1}}\colon k=1..16\}
@@
     \centering
-    \includegraphics[draft,width=1.\linewidth]{../assets/sum__mnist__fine-tune__TwoLayerDenseModelVD.pdf}
-    % \caption{} \label{fig:log-alpha-kde}
+    % \includegraphics[width=1.\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__fashionmnist__fft__-0.5.pdf}
+    \includegraphics[width=1.\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__kmnist__fft__-0.5.pdf}
   \end{subfigure} \\%
@@
     \centering
-    \includegraphics[draft,width=1.\linewidth]{../assets/sum__mnist__fine-tune__SimpleConvModelVD.pdf}
-    % \caption{} \label{fig:log-alpha-proba}
-  \end{subfigure}
-  \caption{%
-    The compression-accuracy trade-off after ``fine-tune'' on MNIST of \textit{TwoLayerDenseModel}
-    (top) and \textit{SimpleConvModel} (bottom) for method in sec.~\ref{ssub:variational_dropout}.
-  }
-  \label{fig:mnist-like__trade-off__vd}
-\end{figure}
-
-\begin{figure}[!ht]
-  \centering
+    % \includegraphics[width=1.\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__mnist__fft__-0.5.pdf}
+    \includegraphics[width=1.\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__emnist_letters__fft__-0.5.pdf}
+  \end{subfigure} \\%
   \begin{subfigure}[b]{0.95\textwidth}  % imcl2019-style swears at this
     \centering
-    \includegraphics[draft,width=1.\linewidth]{../assets/sum__mnist__fine-tune__TwoLayerDenseModelARD.pdf}
-    % \caption{} \label{fig:log-alpha-kde}
+    % \includegraphics[width=1.\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__fashionmnist__raw__-0.5.pdf}
+    \includegraphics[width=1.\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__kmnist__raw__-0.5.pdf}
   \end{subfigure} \\%
@@
     \centering
-    \includegraphics[draft,width=1.\linewidth]{../assets/sum__mnist__fine-tune__SimpleConvModelARD.pdf}
-    % \caption{} \label{fig:log-alpha-proba}
+    % \includegraphics[width=1.\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__mnist__raw__-0.5.pdf}
+    \includegraphics[width=1.\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__emnist_letters__raw__-0.5.pdf}
   \end{subfigure}
@@
     The compression-accuracy trade-off after ``fine-tune'' on MNIST of \textit{TwoLayerDenseModel}
-    (top) and \textit{SimpleConvModel} (bottom) for method in sec.~\ref{ssub:empirical_bayes}.
+    (top) and \textit{SimpleConvModel} (bottom) for methods in sections~\ref{ssub:variational_dropout}
+    and~\ref{ssub:empirical_bayes}.
   }
-  \label{fig:mnist-like__trade-off__ard}
+  \label{fig:mnist-like__trade-off}
 \end{figure}
@@
 % compare compressed cplx-vgg against real-vgg
+\begin{figure}[!ht]
+  \centering
+  \begin{subfigure}[b]{0.9\textwidth}  % imcl2019-style swears at this
+    \centering
+    \includegraphics[draft,width=1.\linewidth]{../assets/figure__cifar10__trade-off/musicnetram__fft__-0.5.pdf}
+  \end{subfigure} \\%
+  % \hfill
+  \begin{subfigure}[b]{0.9\textwidth}  % imcl2019-style swears at this
+    \centering
+    \includegraphics[draft,width=1.\linewidth]{../assets/figure__cifar10__threshold/cifar10__threshold.pdf}
+  \end{subfigure}
+  \caption{%
+    Pre ``fine-tune'' performance of the best models from figure \ref{fig:musicnet_trade-off}
+    compressed with methods of sec.~\ref{sec:dropout_for_c_valued_layers}:
+    (\ref{ssub:variational_dropout} -- \textit{top}, \ref{ssub:empirical_bayes} --  \textit{bottom}).
+  }
+  \label{fig:figure__cifar10__trade-off}
+\end{figure}
 
@@
     \centering
-    \includegraphics[draft,width=1.\linewidth]{../assets/grid_cplx_fine_kl_div_v3_fast-fine-tune.pdf}
-    % \caption{} \label{fig:log-alpha-kde}
-  \end{subfigure} \\
+    \includegraphics[width=1.\linewidth]{../assets/figure__musicnet__trade-off/musicnetram__fft__-0.5.pdf}
+  \end{subfigure} \\%
   % \hfill
@@
     \centering
-    \includegraphics[draft,width=1.\linewidth]{../assets/grid_cplx_fine_kl_div_v2-fine-tune.pdf}
-    % \caption{} \label{fig:log-alpha-proba}
+    % \includegraphics[width=1.\linewidth]{../assets/figure__musicnet__trade-off/musicnetram__fft__-0.5.pdf}
+    \includegraphics[draft,width=1.\linewidth]{../assets/figure__musicnet__trade-off/legacy__musicnetram__fft__-0.5.pdf}
+  \end{subfigure} \\%
+  % \hfill
+  \begin{subfigure}[b]{0.9\textwidth}  % imcl2019-style swears at this
+    \centering
+    % \includegraphics[width=1.\linewidth]{../assets/figure__musicnet__trade-off/musicnetram__fft__-0.5.pdf}
+    \includegraphics[draft,width=1.\linewidth]{../assets/figure__musicnet__threshold/threshold.pdf}
   \end{subfigure}
@@
     uncompressed model.
-    \textit{top}: Original model ($k=6$) compressed with \textbf{\color{orange} VD}
-    (\ref{ssub:variational_dropout}) and \textbf{\color{blue} ARD} (\ref{ssub:empirical_bayes});
+    \textit{top}: Original model ($k=6$) compressed with \textbf{\color{blue} VD}
+    (\ref{ssub:variational_dropout}) and \textbf{\color{orange} ARD} (\ref{ssub:empirical_bayes});
     \textit{bottom}: The model of \citet{trabelsi_deep_2017} with kernel size $3$
@@
   }
-  \label{fig:musicnet_trade-off}
+  \label{fig:musicnet__trade-off}
 \end{figure}
 
-\begin{figure}[!ht]
-  \centering
-  \begin{subfigure}[b]{0.9\textwidth}  % imcl2019-style swears at this
-    \centering
-    \includegraphics[draft,width=1.\linewidth]{../assets/grid_cplx_fine_kl_div_v3_fast-c-ard-trade-off.pdf}
-    % \caption{} \label{fig:log-alpha-kde}
-  \end{subfigure} \\
-  % \hfill
-  \begin{subfigure}[b]{0.9\textwidth}  % imcl2019-style swears at this
-    \centering
-    \includegraphics[draft,width=1.\linewidth]{../assets/grid_cplx_fine_kl_div_v3_fast-c-ard-trade-off.pdf}
-    % \caption{} \label{fig:log-alpha-proba}
-  \end{subfigure}
-  \caption{%
-    Pre ``fine-tune'' performance of the best models from figure \ref{fig:musicnet_trade-off}
-    compressed with methods of sec.~\ref{sec:dropout_for_c_valued_layers}:
-    (\ref{ssub:variational_dropout} -- \textit{top}, \ref{ssub:empirical_bayes} --  \textit{bottom}).
-  }
-  \label{fig:musicnet_trade-off_pre_fune-tune}
-\end{figure}
 % subsection muscinet (end)

### 2020-02-06 paper/paper.tex
plot and proper Trabelsi citation

@@
   \alpha = \tfrac{\sigma^2}{\lvert\mu\rvert^2}
-$: non-zero if $\log \alpha \leq \tau$, zero otherwise. Figure~\ref{fig:log-alpha__mnist-like}
+$: non-zero if $\log \alpha \leq \tau$, zero otherwise. Figure~\ref{fig:hist__and__threshold__tradeoff}
 displays the general shape of the distribution of $\log \alpha$ on the Fashion-MNIST dataset
@@
     \centering
-    \includegraphics[draft,width=1.\linewidth]{../assets/kde-histograms-of-log-alpha-distribution.pdf}
+    \includegraphics[width=1.\linewidth]{../assets/figure__musicnet__threshold.pdf}
   \end{subfigure}
@@
   }
-  \label{fig:log-alpha__mnist-like}
+  \label{fig:hist__and__threshold__tradeoff}
 \end{figure}
@@
 \end{equation}
-% Figure~\ref{fig:log-alpha__mnist-like} (bottom) shows the probability of a $\real$
+% Figure~\ref{fig:hist__and__threshold__tradeoff} (bottom) shows the probability of a $\real$
 % (or $\cplx$)  parameter being non-zero for various $\delta\in(0, \tfrac12)$ as a function
@@
     \includegraphics[draft,width=1.\linewidth]{../assets/figure__musicnet__trade-off/legacy__musicnetram__fft__-0.5.pdf}
-  \end{subfigure} \\%
-  % \hfill
-  \begin{subfigure}[b]{0.9\textwidth}  % imcl2019-style swears at this
-    \centering
-    % \includegraphics[width=1.\linewidth]{../assets/figure__musicnet__trade-off/musicnetram__fft__-0.5.pdf}
-    \includegraphics[draft,width=1.\linewidth]{../assets/figure__musicnet__threshold/threshold.pdf}
   \end{subfigure}

### 2020-02-07 paper/paper.tex
editing the experimental section

@@
 $\ell_2$-norm ball of radius $0.5$, runs SGD with ADAM optimizer with the base learning
-rate of $10^{-3}$ which is scaled after $5$, $10$, and $20$ epochs by $\tfrac1{10}$,
-$\tfrac1{20}$ and $\tfrac1{100}$, respectively.
-
-\subsection{Staged fitting and compression} % (fold)
+rate of $10^{-3}$. We note that since our experiments are on classification tasks,
+$\cplx$-valued networks ultimately have to output a real-valued logit score. Following
+\citet{wolter_complex_2018} and \citet{trabelsi_deep_2017}, the class scores are taken
+as the real part of the $\cplx$ output.
+
+\subsection{Stagewise fitting and compression} % (fold)
 \label{sub:fitting_and_compression}
@@
 The goal of this section to study the compression-performance trade-off of the proposed Bayesian
-sparsification methods for $\cplx$-valued networks. To this end we employ the following training
-plan in every experiment. The model is trained in three successive stages: ``dense'' $\to$
-``sparsify'' $\to$ ``fine-tune''. Model parameters and the optimizer are copied between
-stages, except before the ``fine-tune'' optimizer's internal state is reset.
+sparsification methods for $\cplx$-valued networks. To this end we trained each network in
+three successive stages in every experiment: ``dense'' $\to$ ``sparsify'' $\to$ ``fine-tune''.
+Model parameters and the optimizer are copied between stages, except before the final stage
+optimizer's internal state is reset.
 
@@
 Higher $C$ yields increasingly more sparse layers upon termination of this stage.
-%
+
 The \textit{``fine-tune''} stage begins with computing the sparsity masks from the fitted
@@
 the ``dense'' stage, i.e. with non-Bayesian layers and fixed sparsity masks.
+%
+\todo{reword}
+We observe dual effect of ``fine-tune'' stage: it improves performance of highly compressed
+models since they are more regularized (by poking holes) and thus serves as further fitting.
+At the same time, undercompressed models, behave as if they were over parameterized
+and the fine tune stage overfits.
 
@@
 is around zero.
+%
+The bottom plot on figure~\ref{fig:hist__and__threshold__tradeoff} is constructed without
+running the ``fine-tune'' stage for $C=\tfrac1{2000}$, $\tfrac1{20}$, and $\frac1{200}$.
+The latter setting yields one of the better performing models on the validation split in
+sec.~\ref{sub:musicnet}. We can observe that by choosing $\tau > 0$ we end up in the
+saturation region of the performance and gain only marginal improvement, while losing
+in compression. Relative position compression curves shows that $C$ has much more substantial
+impact on the target sparsity and performance, than the choice of $\tau$.
 
@@
     \centering
-    \includegraphics[draft,width=1.\linewidth]{../assets/kde-histograms-of-log-alpha-distribution.pdf}
+    \includegraphics[width=\linewidth]{../assets/log-alpha__sum__fashion-mnist__20200131-205926.pdf}
   \end{subfigure} \\%
@@
     \centering
-    \includegraphics[width=1.\linewidth]{../assets/figure__musicnet__threshold.pdf}
+    \includegraphics[width=\linewidth]{../assets/figure__musicnet__threshold.pdf}
   \end{subfigure}
   \caption{%
-    Smoothed density of $\log\alpha$ for a convolutional and dense layer from a model
-    in sec.~\ref{sub:mnist_like_datasets}.
+    (\textit{top}) Smoothed density of $\log\alpha$ for some convolutional and dense layer
+    from a model in sec.~\ref{sub:mnist_like_datasets};
+    (\textit{bottom}) Test split performance and compression rate for $\cplx$-valued net
+    by \citet{trabelsi_deep_2017} on MusicNet.
   }
@@
 \end{equation}
-% Figure~\ref{fig:hist__and__threshold__tradeoff} (bottom) shows the probability of a $\real$
-% (or $\cplx$)  parameter being non-zero for various $\delta\in(0, \tfrac12)$ as a function
-% of $\log \alpha$.
 For a reasonably generous $\delta = 25\%$ tolerance all values of $\log \alpha$ below
-$-2.5$ yield a relatively high chance of a non-zero parameter. Given that $q_\theta$
-is merely an approximation, we opt for a somewhat higher $\log \alpha$ threshold, and
-pick $\tau \in [-\tfrac12, \tfrac32]$, which is lower than $\tau = 3$, recommended by
-\citet{molchanov_variational_2017}.
+$-2.5$ yield a relatively high chance of a non-zero parameter. Setting $\tau = 3$
+\citep{molchanov_variational_2017,kingma_variational_2015} is, in our opinion, detrimental
+since it retains parameters $W \sim q_\theta$, standard deviation of which significantly
+exceeds the magnitude of $\mu$, which is typically used as a stand-in for $W$ when the
+network is run in inference mode. Given that $q_\theta$ is merely an approximation,
+we pick $\tau = -\tfrac12$ as the sparsification threshold for $\log \alpha$ in our
+experiments.
 
@@
 labels for each output are pooled, and average precision is computed based on the precision-recall
-curve as if the task was single-output.
-
-The test performance is reported befire the beginning and after termination of the ``fine-tune''
-stage. Additional rationale behind this decision is the extra fine tuning, which trains the
-compressed model.
+curve as if the task was single-output. The evaluation is done after ``dense'' stage, before
+the beginning and upon termination of the ``fine-tune'' stage.
 
@@
 network, but twice in a $\cplx$-network, being a pair of real-imaginary floats. Each model
-has incompressible parameters, such as layer biases, and shifts and scalings from $\real$-
-and $\cplx$-batch normalization layers, if present.
+has incompressible parameters, such as layer biases, shift and scaling from $\real$-and
+$\cplx$-batch normalization layers, if present.
 
@@
 greyscale image datasets to study the compression-performance trade-off of the proposed
-$\cplx$-variational dropout on simple architectures. We compare with the $\real$-valued
-networks against their $\cplx$-valued counterparts with approximately half as many
-parameters, as suggested by \citet{monning_evaluation_2018}.
+$\cplx$-variational dropout on simple architectures.
 
@@
 % model architectures
-We study the following $\real$/$\cplx$ networks:
+% discussion of TwoLayerDenseModel (TLDM) and SimpleConvModel (SCM)
+ the following :
+To compactly describe the $\real$/$\cplx$ networks we study in this experiment we use
+the following notation: $c(n, k, s)$ is a convolution with $n$ output channels, kernel
+width $k$ and stride $s$, and $d(n)$ is a dense layer with $n$ outputs. The values of
+$n_\cdot$ depend on the input features and are summarized in table~\ref{tbl:mnist-like-model-spec}.
 \begin{itemize}
@@
 \end{itemize}
-where $c(n, k, s)$ denotes a convolution with $n$ output channels, kernel width $k$ and
-stride $s$, and $d(n)$ is a dense layer with $n$ outputs. The values of $n_\cdot$ depend
-on the input features and are summarized in table~\ref{tbl:mnist-like-model-spec}.
+
 \begin{table}[hb]
@@
 
+% first experiment: 40-75-40 with fast scheduler
+First we try to compare the $\real$-valued networks against their $\cplx$-valued counterparts
+with approximately half as many parameters, as suggested by \citet{monning_evaluation_2018}.
+In this experiment, ``dense'', ``sparsify'' and ``fine-tune'' stages last for $40$, $75$
+and $40$ epochs, respectively. The base learning rate is scaled after $5$, $10$, and $20$
+epochs by $\tfrac1{10}$, $\tfrac1{20}$ and $\tfrac1{100}$, respectively.
+
 % discuss the plots describing how the test-performance grows with compression and then drops if the model is too sparse
@@
 
-% discussion of TwoLayerDenseModel (TLDM) and SimpleConvModel (SCM)
+% which is better ARD or VD
+It is worth pointing out that the prior used in ARD models offers slightly more favourable
+compression-accuracy values, matching the established perception that log-uniform prior
+is too harsh for sparsification tasks \citep{kharitonov_variational_2018}.
+
+Nevertheless, it is clear form the results depicted in \ref{where}, that VD and ARD
+methods yield very similar compression-performance frontiers.
+
+% second experiment: use scheduler Trabelsi et al. (2018) and show them plotz!
+In the second experiment we use a much slower learning rate scheduler and study only the 
+VD method.
+
 % hinting at overfitting/regularization effects of masking and sparsification
+
+% hopeful conclusion
+\todo{The numerical experiments on MNIST-like datasets} demonstrate, that models using fourier
+features perform poorly in comparison to models using raw image input.
 
@@
   \centering
-  \begin{subfigure}[b]{0.95\textwidth}  % imcl2019-style swears at this
+  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
     \centering
-    % \includegraphics[width=1.\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__fashionmnist__fft__-0.5.pdf}
-    \includegraphics[width=1.\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__kmnist__fft__-0.5.pdf}
+    % \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__fashionmnist__fft__-0.5.pdf}
+    \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__kmnist__fft__-0.5.pdf}
+    % \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/VD__kmnist__fft__-0.5.pdf}
   \end{subfigure} \\%
   % \hfill
-  \begin{subfigure}[b]{0.95\textwidth}  % imcl2019-style swears at this
+  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
     \centering
-    % \includegraphics[width=1.\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__mnist__fft__-0.5.pdf}
-    \includegraphics[width=1.\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__emnist_letters__fft__-0.5.pdf}
+    % \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__mnist__fft__-0.5.pdf}
+    \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__emnist_letters__fft__-0.5.pdf}
+    % \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/ARD__kmnist__fft__-0.5.pdf}
   \end{subfigure} \\%
-  \begin{subfigure}[b]{0.95\textwidth}  % imcl2019-style swears at this
+  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
     \centering
-    % \includegraphics[width=1.\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__fashionmnist__raw__-0.5.pdf}
-    \includegraphics[width=1.\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__kmnist__raw__-0.5.pdf}
+    % \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__fashionmnist__raw__-0.5.pdf}
+    \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__kmnist__raw__-0.5.pdf}
+    % \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/VD__kmnist__raw__-0.5.pdf}
   \end{subfigure} \\%
   % \hfill
-  \begin{subfigure}[b]{0.95\textwidth}  % imcl2019-style swears at this
+  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
     \centering
-    % \includegraphics[width=1.\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__mnist__raw__-0.5.pdf}
-    \includegraphics[width=1.\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__emnist_letters__raw__-0.5.pdf}
+    % \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__mnist__raw__-0.5.pdf}
+    \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__emnist_letters__raw__-0.5.pdf}
+    % \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/VD__emnist_letters__raw__-0.5.pdf}
   \end{subfigure}
@@
 
-% which is better ARD or VD
-It is worth pointing out that the prior used in ARD models offers slightly more favourable
-compression-accuracy values, matching the established perception that log-uniform prior
-is \todo{too harsh for sparsification tasks} \citep{kharitonov_variational_2018}.
-
-% hopeful conclusion
-\todo{The numerical experiments on MNIST-like datasets} demonstrate, that models using fourier
-features perform poorly in comparison to models using raw image input.
-
 % subsection mnist_like_datasets (end)
@@
 Experiments on CIFAR10 dataset are set up similarly to MNIST-like experiment, except
-that we study VGG16 model \citep{simonyan_very_2015} and its $\cplx$-counterpart, fit
-on the full training split of $50k$ colour $32\times32$ images, and use only raw image
-input features (\texttt{raw}).
+that we study VGG16 model \citep{simonyan_very_2015} and its $\cplx$-counterpart. Each
+network is trained stagewise for $20$, $40$, and $20$ epochs on the full training split
+of $50k$ colour $32\times32$ images. We use only raw colour features (\texttt{raw}), since
+the results of the experiments on MNIST left us sceptical about the utility of the Fourier
+features for image recognition. We use fast learning rate scheduler from sec.~\ref{sub:mnist_like_datasets}.
+
+% mention that fourier-features perfomed worse than raw image data embeded in to $\cplx$
 
@@
 The $\cplx$-VGG16 model is architecturally identical to VGG16, except for all layers
-replaced by their $\cplx$-valued versions. To maintain comparability, we half the filter
-sizes of $\cplx$ model.
-
-% mention that fourier-features perfomed worse than raw image data embeded in to $\cplx$
+replaced by their $\cplx$-valued versions. To maintain comparability, we halve the
+filter sizes of $\cplx$ model \citep{monning_evaluation_2018}.
 
@@
     \centering
-    \includegraphics[draft,width=1.\linewidth]{../assets/figure__cifar10__trade-off/musicnetram__fft__-0.5.pdf}
+    \includegraphics[draft,width=\linewidth]{../assets/figure__cifar10__trade-off/musicnetram__fft__-0.5.pdf}
   \end{subfigure} \\%
@@
     \centering
-    \includegraphics[draft,width=1.\linewidth]{../assets/figure__cifar10__threshold/cifar10__threshold.pdf}
+    \includegraphics[draft,width=\linewidth]{../assets/figure__cifar10__threshold/cifar10__threshold.pdf}
   \end{subfigure}
@@
 % draw some conclusions
+The halved $\cplx$ network significantly underperforms in comparison with its $\real$ counterpart
 
@@
 \subsection{MusciNet} % (fold)
-\label{sub:muscinet}
+\label{sub:musicnet}
 
@@
 and that the validation performance peaked at about $10-15$ epochs, much sooner than $200$
-epoch, used by \citet{trabelsi_deep_2017}. Besides staged training and shorter ``dense''
+epoch, used by \citet{trabelsi_deep_2017}. Besides stagewise training and shorter ``dense''
 stage, other important deviations from their setup include:
@@
   \centering
-  \begin{subfigure}[b]{0.9\textwidth}  % imcl2019-style swears at this
+  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
     \centering
-    \includegraphics[width=1.\linewidth]{../assets/figure__musicnet__trade-off/musicnetram__fft__-0.5.pdf}
-  \end{subfigure} \\%
-  % \hfill
-  \begin{subfigure}[b]{0.9\textwidth}  % imcl2019-style swears at this
-    \centering
-    % \includegraphics[width=1.\linewidth]{../assets/figure__musicnet__trade-off/musicnetram__fft__-0.5.pdf}
-    \includegraphics[draft,width=1.\linewidth]{../assets/figure__musicnet__trade-off/legacy__musicnetram__fft__-0.5.pdf}
+    \includegraphics[width=\linewidth]{../assets/figure__musicnet__trade-off/musicnetram__fft__-0.5.pdf}
   \end{subfigure}
@@
   \centering
-  \includegraphics[width=1.\linewidth]{../notebooks/assets/grad_log.pdf}
+  \includegraphics[width=\linewidth]{../notebooks/assets/grad_log.pdf}
   \caption{$\tfrac{d f(\alpha)}{d \log{\alpha}}$ of the fit proposed in

### 2020-02-07 paper/paper.tex
found proof for adding euler const, corrected proba estimate, reworded the netwroks description in mnist-like

@@
 \end{equation}
-We propse settng $\beta = 2$ for $\cplx$ variational dropout, to make the divergence
-term depend only on $\alpha$.
-% For $\beta = 2$ we add $\gamma$ to make the right-hand side nonegative. (proof missing)
+We set $\beta = 2$ to make the divergence term depend only on $\alpha$ and add $\gamma$
+so that the right-hand side is nonegative \citep[eq.(84)]{lapidoth_capacity_2003}.
 %
@@
 
-\subsection{Stagewise fitting and compression} % (fold)
-\label{sub:fitting_and_compression}
+\subsection{Stagewise fitting and sparsification} % (fold)
+\label{sub:fitting_and_sparsification}
 
@@
 weights in each layer based on the relevance scores $\alpha$ (sec.~\ref{sub:dropout}). Since
-the variational approximation factorizes into univariate distributions, whether a $\cplx$
-or $\real$ parameter is zero or not is determined from individual relevance scores $
-  \alpha = \tfrac{\sigma^2}{\lvert\mu\rvert^2}
-$: non-zero if $\log \alpha \leq \tau$, zero otherwise. Figure~\ref{fig:hist__and__threshold__tradeoff}
-displays the general shape of the distribution of $\log \alpha$ on the Fashion-MNIST dataset
-in sec.~\ref{sub:mnist_like_datasets}. This shape appears to be typical in every experiment
-conducted in this study: there always is a single mode within the moderately negative
-range, and one or two modes to the right of zero. The relative mass of each mode changes
-with $C$ and the higher the coefficient is, the more mass is shifted to the right. In every
-experiment the trough between the peaks of the negative mode and the first positive one
-is around zero.
-%
-The bottom plot on figure~\ref{fig:hist__and__threshold__tradeoff} is constructed without
-running the ``fine-tune'' stage for $C=\tfrac1{2000}$, $\tfrac1{20}$, and $\frac1{200}$.
-The latter setting yields one of the better performing models on the validation split in
-sec.~\ref{sub:musicnet}. We can observe that by choosing $\tau > 0$ we end up in the
-saturation region of the performance and gain only marginal improvement, while losing
-in compression. Relative position compression curves shows that $C$ has much more substantial
-impact on the target sparsity and performance, than the choice of $\tau$.
+the $q_\theta$ factorizes into univariate distributions, whether a $\cplx$ or $\real$ parameter
+is zero or not is determined from $\alpha = \tfrac{\sigma^2}{\lvert\mu\rvert^2}$: non-zero
+if $\log \alpha \leq \tau$, zero otherwise. Figure~\ref{fig:hist__and__threshold__tradeoff}
+(top) displays the general shape of the distribution of $\log \alpha$ on the Fashion-MNIST
+dataset in sec.~\ref{sub:mnist_like_datasets}. This shape appears to be typical in every
+experiment conducted in this study: there always is a single mode within the moderately
+negative range, and one or two modes to the right of zero. In every experiment the trough
+between the peaks of the negative mode and the first positive one is around zero. The
+relative mass of each mode changes with $C$ and the higher the coefficient is, the more
+mass is shifted to the right.
+%
+The bottom graph on figure~\ref{fig:hist__and__threshold__tradeoff} is constructed for
+$C \in \{\tfrac1{20}, \frac1{200}\}$ before running the ``fine-tune'' stage. From the
+relative positions of the compression curves on this plot and from the results of other
+experiments we conclude that $C$ has much more substantial impact on the sparsity and
+performance, than the choice of $\tau$. Furthermore, for $\tau > 0$ the performance quickly
+saturates and while compression continues to drop.
 
@@
 are within $\delta$ relative tolerance of their mean with high probability under the
-approximate posterior $q_\theta(W)$. Since \eqref{eq:c-gauss-vi} is Gaussian, $
-  \tfrac{\lvert w - \mu \rvert^2}
+approximate posterior $q_\theta(W)$. Since $W$ is $\real$- or a proper $\cplx$-Gaussian,
+the random variable $
+  \tfrac{k \lvert W - \mu \rvert^2}
         {\alpha \lvert \mu \rvert^2}
-$ is $\chi^2_k$ distributed with shape $k=1$ ($\real$) or $2$ ($\cplx$), whence
+$ is $\chi^2_k$ distributed with $k=1$ ($\real$) or $2$ ($\cplx$), whence
 \begin{equation} \label{eq:prob_relevant}
@@
     = \Pr\biggl(
-      \frac{\lvert w - \mu \rvert^2}{\alpha \lvert \mu \rvert^2}
-        \leq \frac{\delta^2}{\alpha}
+      \frac{k \lvert w - \mu \rvert^2}{\alpha \lvert \mu \rvert^2}
+        \leq \frac{\delta^2 k}{\alpha}
     \biggr)
-    = \chi^2_k\biggl(\frac{\delta^2}{\alpha}\biggr)
-  \,.
-\end{equation}
-For a reasonably generous $\delta = 25\%$ tolerance all values of $\log \alpha$ below
-$-2.5$ yield a relatively high chance of a non-zero parameter. Setting $\tau = 3$
-\citep{molchanov_variational_2017,kingma_variational_2015} is, in our opinion, detrimental
-since it retains parameters $W \sim q_\theta$, standard deviation of which significantly
-exceeds the magnitude of $\mu$, which is typically used as a stand-in for $W$ when the
-network is run in inference mode. Given that $q_\theta$ is merely an approximation,
-we pick $\tau = -\tfrac12$ as the sparsification threshold for $\log \alpha$ in our
-experiments.
-
-% subsection fitting_and_compression (end)
-
-\subsection{Metrics and performance} % (fold)
-\label{sub:metrics_and_performance}
+    = \chi^2_k\biggl(\frac{\delta^2 k}{\alpha}\biggr)
+  \,.
+\end{equation}
+For a generous $\delta = 50\%$ tolerance all values of $\log \alpha$ below $-2.5$ yield
+at least $90\%$ chance of a non-zero $\real$/$\cplx$ parameter. In our opinion, $\tau = 3$
+\citep{molchanov_variational_2017,kingma_variational_2015} retains parameters with randomness
+that significantly exceeds the magnitude of the mean, although $\mu$ is typically used as
+a stand-in for $W$ when the network runs in inference mode. Given that $q_\theta$ is merely
+an approximation, we pick $\tau = -\tfrac12$ to exclude noisy parameters and encourage
+higher sparsity.
+
+% subsection fitting_and_sparsification (end)
+
+\subsection{Metrics and compression} % (fold)
+\label{sub:metrics_and_compression}
 
@@
 We use accuracy as the performance metric for multi-class image classification on MNIST-like
-and CIFAR10 datasets. Similarly to \citet{trabelsi_deep_2017} the performance in MusicNet
-experiments is measured with (pooled) average precision: predicted scores and target binary
-labels for each output are pooled, and average precision is computed based on the precision-recall
+and CIFAR10 datasets. Similarly to \citet{trabelsi_deep_2017} performance in experiments with
+MusicNet is measured with (pooled) average precision: predicted scores and target binary labels
+for each output are pooled, and average precision is computed based on the precision-recall
 curve as if the task was single-output. The evaluation is done after ``dense'' stage, before
@@
 
-% subsection metrics_and_performance (end)
+% subsection metrics_and_compression (end)
 
@@
 % discussion of TwoLayerDenseModel (TLDM) and SimpleConvModel (SCM)
- the following :
-To compactly describe the $\real$/$\cplx$ networks we study in this experiment we use
-the following notation: $c(n, k, s)$ is a convolution with $n$ output channels, kernel
-width $k$ and stride $s$, and $d(n)$ is a dense layer with $n$ outputs. The values of
-$n_\cdot$ depend on the input features and are summarized in table~\ref{tbl:mnist-like-model-spec}.
-\begin{itemize}
-  \item \textit{SimpleConvModel} (SCM): $2d$ convnet with Average pooling ($2\times 2$)
-  with layers $c(n_1, 5, 1) \to c(n_2, 5, 1) \to d(n_3) \to d(n_\mathtt{out})$
-  \item \textit{TwoLayerDenseModel} (TLDM): wide shallow network with structure
-  $d(n_1) \to d(n_\mathtt{out})$
-\end{itemize}
+The $\real$/$\cplx$ networks, studied in this experiment, have been chosen for the purpose 
+of illustrating the compression and understanding the effects of experiment parameters.
+\textit{SimpleConvModel} (SCM) is $2d$ ReLU convolutional networks with average pooling
+($2\times 2$) after non-linearities with two convolutions (kernel $5\times 5$, stride $1$)
+with filters $n_1 \to n_2$ followed by dense layers $n_3 \to n_\mathtt{out}$. The second
+network, \textit{TwoLayerDenseModel} (TLDM), is a wide dense network $n_1 \to n_\mathtt{out}$.
+The values of $n_\cdot$ depend on the input features and are summarized in table~\ref{tbl:mnist-like-model-spec}.
 
@@
     (\texttt{fft}) & $40, 100, 1000$ & $20, 50, 500$ \\
-    \bottomrule
-  \end{tabular}
-  \begin{tabular}{lrr}
+  %   \bottomrule
+  % \end{tabular}
+  % \begin{tabular}{lrr}
     \toprule
@@
 
-We use training from sec.~\ref{sub:fitting_and_compression} with epochs lasting for $12$,
+We use training from sec.~\ref{sub:fitting_and_sparsification} with epochs lasting for $12$,
 $32$ and $50$ epochs, respectively. Early stopping is used only during the ``fine-tune''
@@
   \item clipping $\ell_2$ norm of parameters' gradients to $0.05$
-  \item faster learning rate reduction schedule (sec.~\ref{sub:fitting_and_compression})
+  \item faster learning rate reduction schedule (sec.~\ref{sub:fitting_and_sparsification})
 \end{itemize}

### 2020-02-07 paper/paper.tex
some edits in mnist-like

@@
   \bigr)
-    = \Pr\biggl(
-      \frac{k \lvert w - \mu \rvert^2}{\alpha \lvert \mu \rvert^2}
-        \leq \frac{\delta^2 k}{\alpha}
-    \biggr)
+    % = \Pr\biggl(
+    %   \frac{k \lvert w - \mu \rvert^2}{\alpha \lvert \mu \rvert^2}
+    %     \leq \frac{\delta^2 k}{\alpha}
+    % \biggr)
     = \chi^2_k\biggl(\frac{\delta^2 k}{\alpha}\biggr)
@@
 
-We conduct a moderately sized numerical experiment on MNIST and similar $28\times 28$
-greyscale image datasets to study the compression-performance trade-off of the proposed
-$\cplx$-variational dropout on simple architectures.
-
+We conduct a moderately sized experiment on MNIST and similar $28\times 28$ greyscale
+image datasets to study the compression-performance trade-off of the proposed $\cplx$-variational
+dropout on simple architectures.
 % dataset size
@@
 dataset to fit the networks, and gauge the final performance on the usual test split.
-Limiting the size was done primarily to test the regularization strength of sparsification
-performed by variational dropout, and to make bulk experimentation faster.
-
-% image features
-Since image data is not naturally $\cplx$-valued, we preprocess images by either embedding
-$\real$-data into $\cplx$ assuming $\Re z = 0$ (\texttt{raw}), or applying the two-dimensional
-Fourier Transform (\texttt{fft}), shifting lower frequencies to the centre of the image. We
-do not investigate the option, proposed by \citet{trabelsi_deep_2017}, to train an auxiliary
-model to synthesize the imaginary component from the real data.
+Limiting the size was done primarily to test the regularization strength of compression,
+and to make bulk experimentation faster.
 
@@
 
+% image features
+Since image data is not naturally $\cplx$-valued, we preprocess images by either embedding
+$\real$-data into $\cplx$ assuming $\Re z = 0$ (\texttt{raw}), or applying the two-dimensional
+Fourier Transform (\texttt{fft}), shifting lower frequencies to the centre of the image. We
+do not investigate the option, proposed by \citet{trabelsi_deep_2017}, to train an auxiliary
+model to synthesize the imaginary component from the real data.
+
 % first experiment: 40-75-40 with fast scheduler
-First we try to compare the $\real$-valued networks against their $\cplx$-valued counterparts
-with approximately half as many parameters, as suggested by \citet{monning_evaluation_2018}.
-In this experiment, ``dense'', ``sparsify'' and ``fine-tune'' stages last for $40$, $75$
-and $40$ epochs, respectively. The base learning rate is scaled after $5$, $10$, and $20$
-epochs by $\tfrac1{10}$, $\tfrac1{20}$ and $\tfrac1{100}$, respectively.
+First we compare the $\real$-valued networks against their $\cplx$-valued counterparts with
+approximately half as many parameters as suggested by \citet{monning_evaluation_2018}. In
+this experiment stages last for $40$, $75$ and $40$ epochs, respectively, and the base learning
+rate is scaled after $5$, $10$, and $20$-th epoch by $\tfrac1{10}$, $\tfrac1{20}$ and $\tfrac1{100}$,
+respectively.
 

### 2020-02-07 paper/paper.tex
scattered typo fixes, and edits

@@
 Dropout resembles averaging models with shared parameters: each model is weighted equally
-since masks are randomly sampled, unlike bayesian model averaging, which weighs according to
+since masks are randomly sampled, unlike Bayesian model averaging, which weighs according to
 the posterior distribution. \citet{kingma_variational_2015} specifically consider dropout
@@
 hard-concrete distribution with an atom at $0$ \citep{maddison_concrete_2016,jang_categorical_2017}.
-Their results suggest that although var-dropout may achieve good accuracy-sparsity balance
+Their results suggest that although variational dropout may achieve good accuracy-sparsity balance
 and outperform pruning and $\ell_0$ on the studied architectures, pruning is preferable for
@@
 % our contribution
-Inspired by variational sparsification and stochastic sparsification techniques we
-extend Bayesian dropout for $\cplx$-valued networks. We assess the performance-compression
-trade-off of the proposed Bayesian technique by conducting a large-scale numerical study
-of $\cplx$-valued networks on two tasks: image recognition on MNIST-like and CIFAR10 datasets
-and music transcription on MusicNet \citep{thickstun_learning_2017}. We reproduce the
-state-of-the-art result by \citet{trabelsi_deep_2017} for $\cplx$-valued networks on the
-latter with $\approx 5\%$ of remaining non-zero parameters.
+Inspired by variational and stochastic sparsification techniques we extend Bayesian dropout
+for $\cplx$-valued networks. We assess the performance-compression trade-off of the proposed
+Bayesian technique by conducting a large-scale numerical study of $\cplx$-valued networks
+on two tasks: image recognition on MNIST-like and CIFAR10 datasets and music transcription
+on MusicNet \citep{thickstun_learning_2017}. We reproduce the state-of-the-art result by
+\citet{trabelsi_deep_2017} for $\cplx$-valued networks on the latter with $\approx 5\%$
+of remaining non-zero parameters.
 
@@
 for each individual parameter. Flexibility in specification of $q_\theta$ enables structured
-dropout with shared $\alpha$ across groups of parameters $\omega$. Another variant of Bayesian
-dropout, called \textit{Automatic Relevance Determination}, is developed in \citep{kharitonov_variational_2018}.
+dropout with shared $\alpha$ across groups of parameters $\omega$. Another Bayesian dropout
+method, called \textit{Automatic Relevance Determination}, is developed in \citep{kharitonov_variational_2018}.
 The key difference is that the log-uniform factor $\pi(\omega_{ij})$ is replaced by a proper
@@
 networks into existing $\real$ deep learning auto-differentiation frameworks. It was considered
-as a basis for $\cplx$ version of backpropagation by \citet{benvenuto_complex_1992} and
+as a basis for $\cplx$ version of back-propagation by \citet{benvenuto_complex_1992} and
 \citet{trabelsi_deep_2017}, (see appendix~\ref{sub:wirtinger_calculus} for details).
@@
 
-The trick and dropout can be applied to any layer, the output of which depends linearly
-on its parameters, e.g. convolutional layers, affine, and bilinear transformations $
+The trick and dropout can be applied to any layer, the output of which depends linearly on
+its parameters, e.g. convolutional layers, affine, and bilinear transformations $
   (x, z) \mapsto x^\top W^{(j)} z + b_j
@@
 \end{equation}
-We omit subscripts ${ij}$ for brevity in the next sectons.
+We omit subscripts ${ij}$ for brevity in the next sections.
 
@@
 Since $\mathop{Ei}(x)$ has simple analytic derivative and \eqref{eq:elbo} depends additively
-on \eqref{eq:c-vd-kl-div}, it is possible to backpropagate through the divergence without
+on \eqref{eq:c-vd-kl-div}, it is possible to back-propagate through the divergence without
 forward evaluation.
@@
 
-Let's consider fully factorized proper $\cplx$-gaussian prior $
+Let's consider fully factorized proper $\cplx$-Gaussian prior $
   \pi_\tau(\omega)
@@
 %
-In empirical Bayes the prior adapts to the observed data, i.e. \eqref{eq:elbo} is optimized
+In Empirical Bayes the prior adapts to the observed data, i.e. \eqref{eq:elbo} is optimized
 w.r.t. $\tau$ of each weight's prior. Since divergence sits in \eqref{eq:elbo} with negative
@@
 \citet{wolter_complex_2018} and \citet{trabelsi_deep_2017}, the class scores are taken
-as the real part of the $\cplx$ output.
+as real parts of the $\cplx$ output.
 
@@
 weights in each layer based on the relevance scores $\alpha$ (sec.~\ref{sub:dropout}). Since
-the $q_\theta$ factorizes into univariate distributions, whether a $\cplx$ or $\real$ parameter
-is zero or not is determined from $\alpha = \tfrac{\sigma^2}{\lvert\mu\rvert^2}$: non-zero
-if $\log \alpha \leq \tau$, zero otherwise. Figure~\ref{fig:hist__and__threshold__tradeoff}
-(top) displays the general shape of the distribution of $\log \alpha$ on the Fashion-MNIST
-dataset in sec.~\ref{sub:mnist_like_datasets}. This shape appears to be typical in every
-experiment conducted in this study: there always is a single mode within the moderately
-negative range, and one or two modes to the right of zero. In every experiment the trough
-between the peaks of the negative mode and the first positive one is around zero. The
-relative mass of each mode changes with $C$ and the higher the coefficient is, the more
-mass is shifted to the right.
-%
-The bottom graph on figure~\ref{fig:hist__and__threshold__tradeoff} is constructed for
-$C \in \{\tfrac1{20}, \frac1{200}\}$ before running the ``fine-tune'' stage. From the
-relative positions of the compression curves on this plot and from the results of other
-experiments we conclude that $C$ has much more substantial impact on the sparsity and
-performance, than the choice of $\tau$. Furthermore, for $\tau > 0$ the performance quickly
-saturates and while compression continues to drop.
+the $q_\theta$ factorizes into univariate distributions, a $\cplx$ or $\real$ parameter is
+considered non-zero if $\log \alpha \leq \tau$ for $
+  \alpha = \tfrac{\sigma^2}{\lvert\mu\rvert^2}
+$, or zero otherwise. Figure~\ref{fig:hist__and__threshold__tradeoff} (top) displays
+the general shape of the distribution of $\log \alpha$ on the Fashion-MNIST dataset in
+sec.~\ref{sub:mnist_like_datasets}. There always is a single mode within the moderately
+negative range, and one or two modes to the right of zero, and the trough between the
+peaks of the negative mode and the first positive one is around zero. The relative mass
+of each mode changes with $C$ and the higher the coefficient is, the more mass is shifted
+to the right.
+%
+The bottom graph on figure~\ref{fig:hist__and__threshold__tradeoff} is constructed
+for $C \in \{\tfrac1{20}, \frac1{200}\}$ before running the ``fine-tune'' stage. From
+\eqref{eq:elbo_with_coef}, the relative positions of the compression curves on this
+plot and the results of other experiments, it can be concluded that $C$ has much more
+substantial impact on the sparsity and performance, than the choice of $\tau$. Furthermore,
+for $\tau > 0$ the performance quickly saturates and while compression continues to
+drop.
 
@@
 are within $\delta$ relative tolerance of their mean with high probability under the
-approximate posterior $q_\theta(W)$. Since $W$ is $\real$- or a proper $\cplx$-Gaussian,
-the random variable $
+approximate posterior $q_\theta(W)$. This ensures that stochastic parameters are sufficiently
+concentrated around $\mu$, which is used as a stand-in value for $W$, when the network
+is used in inference mode. Since $W$ is $\real$- or a proper $\cplx$-Gaussian, the random
+variable $
   \tfrac{k \lvert W - \mu \rvert^2}
@@
 For a generous $\delta = 50\%$ tolerance all values of $\log \alpha$ below $-2.5$ yield
-at least $90\%$ chance of a non-zero $\real$/$\cplx$ parameter. In our opinion, $\tau = 3$
-\citep{molchanov_variational_2017,kingma_variational_2015} retains parameters with randomness
-that significantly exceeds the magnitude of the mean, although $\mu$ is typically used as
-a stand-in for $W$ when the network runs in inference mode. Given that $q_\theta$ is merely
-an approximation, we pick $\tau = -\tfrac12$ to exclude noisy parameters and encourage
-higher sparsity.
+at least $90\%$ chance of a non-zero $\real$/$\cplx$ parameter. We pick $\tau = -\tfrac12$
+to exclude noisy parameters and encourage higher sparsity, at the same time staying aware
+that $q_\theta$ is merely an approximation. In comparison, $\tau = 3$ is commonly used as
+the threshold \citep{molchanov_variational_2017,kingma_variational_2015}.
 
@@
 network, but twice in a $\cplx$-network, being a pair of real-imaginary floats. Each model
-has incompressible parameters, such as layer biases, shift and scaling from $\real$-and
+has incompressible parameters, such as layers' biases, shift and scaling from $\real$-and
 $\cplx$-batch normalization layers, if present.
@@
 respectively.
+%
+Plots~\ref{fig:mnist-like__trade-off} depict performance-compression curve on MNIST-like
+datasets for the studied models and methods from sec.~\ref{ssub:variational_dropout} (VD)
+and~\ref{ssub:empirical_bayes} (ARD). Besides that we tried \texttt{raw} or \texttt{fft}
+input features, varied $
+  C \in \{\tfrac3{2^{k+1}}\colon k=1..16\}
+$, and repeated the experiment $4$ times.
+
+% observation: raw features -- alright
+
+fft features with wide dense network exhibit improving performance with the compression rate
+up to a certain limit.
 
 % discuss the plots describing how the test-performance grows with compression and then drops if the model is too sparse
-Plots on figure~\ref{fig:mnist-like__trade-off} show the results on the ``MNIST'' dataset for
-$\tau\in\{-\tfrac12, \tfrac32\}$ and $
-  C \in \{\tfrac3{2^{k+1}}\colon k=1..16\}
-$ replicated $5$ times using the method from sec.~\ref{ssub:variational_dropout} (VD)
-and~\ref{ssub:empirical_bayes} (ARD), respectively (results for other MNIST-like datasets
-are in the appendix).
-
 % which is better ARD or VD
@@
   \caption{%
-    Average Percision frontier for the convolutional model of \citet{trabelsi_deep_2017}.
-    Shaded horiontal region represents the $\mu\pm\sigma$ bands for the performance of the
-    uncompressed model.
-    \textit{top}: Original model ($k=6$) compressed with \textbf{\color{blue} VD}
-    (\ref{ssub:variational_dropout}) and \textbf{\color{orange} ARD} (\ref{ssub:empirical_bayes});
-    \textit{bottom}: The model of \citet{trabelsi_deep_2017} with kernel size $3$
-    compressed with \textbf{\color{blue} VD} (\ref{ssub:variational_dropout}).
+    Performance-compression frontier for the deep network of \citet{trabelsi_deep_2017}.
+    Shaded horizontal region represents the $\mu\pm\sigma$ bands for the performance of the
+    uncompressed model. \textbf{\color{blue} VD} and \textbf{\color{orange} ARD} denote
+    methods \ref{ssub:variational_dropout}) ans \ref{ssub:empirical_bayes}, respectively.
+    The \textbf{\color{pink} version} of the network with kernel $3$ in every convolution compressed with VD
+    is (\ref{ssub:variational_dropout}).
   }
@@
 
-If we assume a mean field $\cplx$-Gaussian approximate posteriror for $
+If we assume a mean field $\cplx$-Gaussian approximate posterior for $
   W \in \cplx^{n\times m}
@@
 \end{equation}
-Hence \eqref{eq:cplx-gauss-trick} folows.
+Hence \eqref{eq:cplx-gauss-trick} follows.
 
@@
 parts in interleaved format, emulation of $\cplx$-algebra using $\real$-valued arithmetic,
-and Wirtinger calculus make it possible to reuse $\real$-backpropagation and existing
+and Wirtinger calculus make it possible to reuse $\real$ back-propagation and existing
 auto-differentiation frameworks \citep{trabelsi_deep_2017}.

### 2020-02-07 paper/paper.tex
finalized musicnet description

@@
 
-We use training from sec.~\ref{sub:fitting_and_sparsification} with epochs lasting for $12$,
-$32$ and $50$ epochs, respectively. Early stopping is used only during the ``fine-tune''
-stage. Preliminary experiments with the model without sparsification have shown that early
-stopping almost always terminated the training process within the first $10-20$ epochs,
-and that the validation performance peaked at about $10-15$ epochs, much sooner than $200$
-epoch, used by \citet{trabelsi_deep_2017}. Besides stagewise training and shorter ``dense''
-stage, other important deviations from their setup include:
-\begin{itemize}
-  \item shifting lower frequencies to the centre of the window to maintain locality after
-  applying FFT (much like in sec.~\ref{sub:mnist_like_datasets})
-  \item clipping $\ell_2$ norm of parameters' gradients to $0.05$
-  \item faster learning rate reduction schedule (sec.~\ref{sub:fitting_and_sparsification})
-\end{itemize}
-Each full three-stage experiment is replicated five times to take random effects into account,
-e.g. random network initialization prior to ``dense'' stage, randomization of batches within
-each epoch during SGD, and stochasticity of Bayesian forward pass at ``sparsify'' stage.
-
-% Describe the network by Trabelsi and then present the reslts form then model with kernel size \textbf{6} 
-% the causally mantion that you also conducted a large study of an inferior model with kenrel size 3.
-% (do not mention that this was a mistake, you dummy!)
+Preliminary experiments with the model without sparsification have shown that early stopping
+almost always terminated the training process within the first $10-20$ epochs, and that the
+validation performance peaked at about $10-15$ epochs, much sooner than $200$ epochs used by
+\citet{trabelsi_deep_2017}. Thus we adopt shorter lasting stages: $12$, $32$ and $50$ epochs,
+which essentially turns the ``dense'' stage into pretraining step. Early stopping, tracking
+the validation split performance, is used only during the ``fine-tune'' stage. To keep the
+learning rate schedule synchronised with such abbreviated training, we allow the base rate
+of $10^{-3}$ to be scaled after $5$, $10$, and $20$-th epoch by $\tfrac1{10}$, $\tfrac1{20}$
+and $\tfrac1{100}$, respectively. Other key deviations from the setup used by \citet{trabelsi_deep_2017}
+include: shifting lower frequencies to the centre of the window to maintain locality after
+applying FFT (sec.~\ref{sub:mnist_like_datasets}), and clipping $\ell_2$ norm of parameters'
+gradients to $0.05$.
+
+In each experiment we varied the method and the value $C$, while keeping $\tau$ at $-\tfrac12$.
+Each full experiment is replicated five times to take random effects from network initialization
+before ``dense'', stochastic batch sequence during SGD, and randomness of Bayesian forward
+pass at ``sparsify'' stage.
+
+Figure~\ref{fig:musicnet__trade-off} shows the resulting performance-compression frontier
+for the deep network of \citet{trabelsi_deep_2017} and its version, in which we purposefully
+halve the spatial size of the first $1d$ convolution kernel from $6$ to $3$ (denoted by
+suffix \textit{k}$3$). The motivation is to test if the performance handicap introduced be
+the forced compression of the most upstream layer can be alleviated through non-uniform
+compression, induced by variational dropout. We test only VD (sec.~\ref{ssub:variational_dropout})
+method in this sub-experiment, since prior results have not demonstrated significant difference
+in performance-compression trade-off between VD and ARD (sec.~\ref{ssub:empirical_bayes}).
 
@@
   \caption{%
-    Performance-compression frontier for the deep network of \citet{trabelsi_deep_2017}.
-    Shaded horizontal region represents the $\mu\pm\sigma$ bands for the performance of the
-    uncompressed model. \textbf{\color{blue} VD} and \textbf{\color{orange} ARD} denote
-    methods \ref{ssub:variational_dropout}) ans \ref{ssub:empirical_bayes}, respectively.
+    \textbf{\color{blue} VD} and \textbf{\color{orange} ARD}
+    denote
+    methods \ref{ssub:variational_dropout}) and \ref{ssub:empirical_bayes}, respectively.
     The \textbf{\color{pink} version} of the network with kernel $3$ in every convolution compressed with VD
@@
 \end{figure}
+
+Shaded horizontal bands represent the min-max spread of the performance of the uncompressed
+network upon termination of ``dense'' stage. Each point represents a precision-compression
+value attained by a network after ``fine-tune'' stage. The end of the tail of each point
+represents the performance gain or loss from the ``fine-tune'' stage itself.
+%
+For compression levels lower than $50$, the final stage overfits the network, since
+undercompresed remain overparameterized. For rates higher than $\approx 100$ the ``fine-tune''
+stage serves its purpose, essentially, due to the network's being sufficiently regularized
+though sparsity. There is evidence in favour of achievability of the SOTA average precision
+of \citet{trabelsi_deep_2017} within the $50$-$100$ compression region with $\cplx$-valued
+automatic relevance derivative (sec.~\ref{ssub:empirical_bayes}).
 

### 2020-02-07 paper/paper.tex
resolved bad wording and added a cifar10 figure

@@
 %
-\todo{reword}
-We observe dual effect of ``fine-tune'' stage: it improves performance of highly compressed
-models since they are more regularized (by poking holes) and thus serves as further fitting.
-At the same time, undercompressed models, behave as if they were over parameterized
-and the fine tune stage overfits.
+The benefit of the ``fine-tune'' stage appears to be strongly influenced by the compression
+rate. In this experiment and more prominently in MusicNet (sec.~\ref{sub:musicnet}), we
+can observe that the more ``holes'' Bayesian dropout poked in the model, the more regularized
+it becomes, the less capacity it maintains for overfitting and the more ``fine-tune'' serves
+as extended training.
 
@@
   \alpha = \tfrac{\sigma^2}{\lvert\mu\rvert^2}
-$, or zero otherwise. Figure~\ref{fig:hist__and__threshold__tradeoff} (top) displays
-the general shape of the distribution of $\log \alpha$ on the Fashion-MNIST dataset in
-sec.~\ref{sub:mnist_like_datasets}. There always is a single mode within the moderately
-negative range, and one or two modes to the right of zero, and the trough between the
-peaks of the negative mode and the first positive one is around zero. The relative mass
-of each mode changes with $C$ and the higher the coefficient is, the more mass is shifted
-to the right.
+$, or zero otherwise. Figure~\ref{fig:hist__and__threshold__tradeoff} (top) displays the
+general shape of the distribution of $\log \alpha$ on the Fashion-MNIST dataset in
+sec.~\ref{sub:mnist_like_datasets}. There always appears to be a mode in the moderately
+negative range, a valley through zero between the peaks of the negative mode and the next
+positive one. The relative mass of each mode changes with $C$ and the higher the coefficient
+is, the more mass is shifted to the right.
 %
@@
 \eqref{eq:elbo_with_coef}, the relative positions of the compression curves on this
-plot and the results of other experiments, it can be concluded that $C$ has much more
+plot and the results of experiments below, it can be concluded that $C$ has much more
 substantial impact on the sparsity and performance, than the choice of $\tau$. Furthermore,
-for $\tau > 0$ the performance quickly saturates and while compression continues to
-drop.
+for $\tau > 0$ the performance quickly saturates while compression creeps downwards.
 
@@
     from a model in sec.~\ref{sub:mnist_like_datasets};
-    (\textit{bottom}) Test split performance and compression rate for $\cplx$-valued net
-    by \citet{trabelsi_deep_2017} on MusicNet.
+    (\textit{bottom}) Test split performance and compression rate for a $\cplx$-valued
+    net on MusicNet.
   }
@@
 approximate posterior $q_\theta(W)$. This ensures that stochastic parameters are sufficiently
-concentrated around $\mu$, which is used as a stand-in value for $W$, when the network
-is used in inference mode. Since $W$ is $\real$- or a proper $\cplx$-Gaussian, the random
-variable $
+concentrated around $\mu$, which are used as stand-in values for network weights $W$,
+when it runs in inference mode. Since $W$ is $\real$- or a proper $\cplx$-Gaussian, the
+random variable $
   \tfrac{k \lvert W - \mu \rvert^2}
@@
 at least $90\%$ chance of a non-zero $\real$/$\cplx$ parameter. We pick $\tau = -\tfrac12$
-to exclude noisy parameters and encourage higher sparsity, at the same time staying aware
+to exclude noisy parameters and encourage higher sparsity, at the same time being aware
 that $q_\theta$ is merely an approximation. In comparison, $\tau = 3$ is commonly used as
@@
 % write a note on the incompressible parameters (bias, batch norm etc.)
-The compression rate is computed based on the number of floating point values needed
-to specify the model and equals $
-  \frac{n_\mathtt{par}}{n_\mathtt{par} - n_\mathtt{zer}}
+The compression rate is computed based on the number of floating point values needed to
+specify the model and equals $
+  \tfrac{n_\mathtt{par}}{n_\mathtt{par} - n_\mathtt{zer}}
 $, where $n_\mathtt{zer}$ is the number of explicit zeros after sparsification, $n_\mathtt{par}$
@@
 
-We conduct a moderately sized experiment on MNIST and similar $28\times 28$ greyscale
-image datasets to study the compression-performance trade-off of the proposed $\cplx$-variational
+We conduct a moderately sized experiment on MNIST and similar $28\times 28$ greyscale image
+datasets to study the compression-performance trade-off of the proposed $\cplx$-variational
 dropout on simple architectures.
@@
 % a couple of plots from MNIST and Fashion-MNIST
-\begin{figure}[!ht]
+\begin{figure}[!h]
   \centering
@@
 the results of the experiments on MNIST left us sceptical about the utility of the Fourier
-features for image recognition. We use fast learning rate scheduler from sec.~\ref{sub:mnist_like_datasets}.
-
-% mention that fourier-features perfomed worse than raw image data embeded in to $\cplx$
+features for image recognition. We use fast learning rate scheduler from sec.~\ref{sub:mnist_like_datasets}
+and apply random crop and horizontal flips as augmentation.
 
 % describe the VGG16 model and its cplx-valued modification
-The $\cplx$-VGG16 model is architecturally identical to VGG16, except for all layers
-replaced by their $\cplx$-valued versions. To maintain comparability, we halve the
-filter sizes of $\cplx$ model \citep{monning_evaluation_2018}.
+The $\cplx$-VGG16 model is architecturally identical to VGG16, except for all layers are
+replaced by their $\cplx$-valued versions. To maintain comparability, we halve the filter
+sizes of $\cplx$ model \citep{monning_evaluation_2018}.
+
+% draw some conclusions
+The halved $\cplx$ network significantly underperforms in comparison with its $\real$ counterpart
 
 % compare compressed cplx-vgg against real-vgg
-\begin{figure}[!ht]
+\begin{figure}[!h]
   \centering
@@
     \centering
-    \includegraphics[draft,width=\linewidth]{../assets/figure__cifar10__trade-off/musicnetram__fft__-0.5.pdf}
-  \end{subfigure} \\%
-  % \hfill
-  \begin{subfigure}[b]{0.9\textwidth}  % imcl2019-style swears at this
-    \centering
-    \includegraphics[draft,width=\linewidth]{../assets/figure__cifar10__threshold/cifar10__threshold.pdf}
+    \includegraphics[width=\linewidth]{../assets/figure__cifar__trade-off/augmentedcifar10__raw__-0.5.pdf}
   \end{subfigure}
   \caption{%
-    Pre ``fine-tune'' performance of the best models from figure \ref{fig:musicnet_trade-off}
-    compressed with methods of sec.~\ref{sec:dropout_for_c_valued_layers}:
-    (\ref{ssub:variational_dropout} -- \textit{top}, \ref{ssub:empirical_bayes} --  \textit{bottom}).
+    Compression-accuracy frontier for $\real$ and $\tfrac12 \cplx$ versions of VGG16 on CIFAR10.
   }
@@
 
-% draw some conclusions
-The halved $\cplx$ network significantly underperforms in comparison with its $\real$ counterpart
+\begin{figure}[!h]
+  \centering
+  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
+    \centering
+    \includegraphics[width=\linewidth]{../assets/figure__musicnet__trade-off/musicnetram__fft__-0.5.pdf}
+  \end{subfigure}
+  \caption{%
+    Performance-compression trade-off using \textbf{\color{blue} VD} and \textbf{\color{orange} ARD}.
+    The \textbf{\color{pink} version} of the network with kernel $3$ in the first convolution is
+    compressed with VD only.
+  }
+  \label{fig:musicnet__trade-off}
+\end{figure}
 
@@
 dataset for automatic music transcription task and study the $1d$ VGG-like $\cplx$-convent
-proposed therein. Similarly to this study, we downsample the sound from 44.1kHz to 11kHz,
+proposed therein. Similarly to this study, we downsample the audio from 44.1kHz to 11kHz,
 retaining only $84$ out of $128$ labels, and hold-out the same validation and test splits.
@@
 in performance-compression trade-off between VD and ARD (sec.~\ref{ssub:empirical_bayes}).
-
-\begin{figure}[!ht]
-  \centering
-  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
-    \centering
-    \includegraphics[width=\linewidth]{../assets/figure__musicnet__trade-off/musicnetram__fft__-0.5.pdf}
-  \end{subfigure}
-  \caption{%
-    \textbf{\color{blue} VD} and \textbf{\color{orange} ARD}
-    denote
-    methods \ref{ssub:variational_dropout}) and \ref{ssub:empirical_bayes}, respectively.
-    The \textbf{\color{pink} version} of the network with kernel $3$ in every convolution compressed with VD
-    is (\ref{ssub:variational_dropout}).
-  }
-  \label{fig:musicnet__trade-off}
-\end{figure}
 
@@
 
-\begin{figure}[!ht]
+\begin{figure}[!h]
   \centering

### 2020-02-07 paper/paper.tex
split mnist figure

@@
     \centering
+    % \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__fashionmnist__raw__-0.5.pdf}
+    \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__kmnist__raw__-0.5.pdf}
+    % \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/VD__kmnist__raw__-0.5.pdf}
+  \end{subfigure}
+  \caption{%
+    The compression-accuracy trade-off on KMNIST dataset.
+    (\textit{top}) \texttt{fft} features, (\textit{bottom}) \texttt{raw} features.
+  }
+  \label{fig:mnist-like__trade-off__kmnist}
+\end{figure}
+
+\begin{figure}[!h]
+  \centering
+  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
+    \centering
     % \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__mnist__fft__-0.5.pdf}
@@
     % \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/ARD__kmnist__fft__-0.5.pdf}
-  \end{subfigure} \\%
-  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
-    \centering
-    % \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__fashionmnist__raw__-0.5.pdf}
-    \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__kmnist__raw__-0.5.pdf}
-    % \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/VD__kmnist__raw__-0.5.pdf}
   \end{subfigure} \\%
@@
   \caption{%
-    The compression-accuracy trade-off after ``fine-tune'' on MNIST of \textit{TwoLayerDenseModel}
-    (top) and \textit{SimpleConvModel} (bottom) for methods in sections~\ref{ssub:variational_dropout}
-    and~\ref{ssub:empirical_bayes}.
+    The compression-accuracy trade-off on the letters part of the Extended MNIST dataset.
+    (\textit{top}) \texttt{fft} features, (\textit{bottom}) \texttt{raw} features.
   }
-  \label{fig:mnist-like__trade-off}
+  \label{fig:mnist-like__trade-off__emnist}
 \end{figure}

### 2020-02-07 paper/paper.tex
carved out the c-2r and 0.5c-r comparison

@@
 network, \textit{TwoLayerDenseModel} (TLDM), is a wide dense network $n_1 \to n_\mathtt{out}$.
-The values of $n_\cdot$ depend on the input features and are summarized in table~\ref{tbl:mnist-like-model-spec}.
-
-\begin{table}[hb]
-  \centering
-  \caption{Architecture parameters for models studied on MNIST-like datasets.}
-  \label{tbl:mnist-like-model-spec}
-  \begin{tabular}{lrr}
-    \toprule
-    $(n_1, n_2, n_3)$  & $\real$-\textit{SCM} & $\cplx$-\textit{SCM} \\
-    \midrule
-    (\texttt{raw}) & $20,  50,  500$ & $10, 25, 250$ \\
-    (\texttt{fft}) & $40, 100, 1000$ & $20, 50, 500$ \\
-  %   \bottomrule
-  % \end{tabular}
-  % \begin{tabular}{lrr}
-    \toprule
-    $(n_1)$  & $\real$-\textit{TLDM} & $\cplx$-\textit{TLDM} \\
-    \midrule
-    (\texttt{raw}) & $4096$ & $2048$ \\
-    (\texttt{fft}) & $8192$ & $4096$ \\
-    \bottomrule
-  \end{tabular}
-\end{table}
+For SCM model $n_1, n_2, n_3$ are $20, 50, 500$, respectively, and for TLDM model $
+  n_1 = 4096
+$ regardless of their type ($\real$ or $\cplx$), although \citet{monning_evaluation_2018}
+argues that this renders models incomparable.
 
@@
 % first experiment: 40-75-40 with fast scheduler
-First we compare the $\real$-valued networks against their $\cplx$-valued counterparts with
-approximately half as many parameters as suggested by \citet{monning_evaluation_2018}. In
-this experiment stages last for $40$, $75$ and $40$ epochs, respectively, and the base learning
-rate is scaled after $5$, $10$, and $20$-th epoch by $\tfrac1{10}$, $\tfrac1{20}$ and $\tfrac1{100}$,
-respectively.
-%
-Plots~\ref{fig:mnist-like__trade-off} depict performance-compression curve on MNIST-like
-datasets for the studied models and methods from sec.~\ref{ssub:variational_dropout} (VD)
-and~\ref{ssub:empirical_bayes} (ARD). Besides that we tried \texttt{raw} or \texttt{fft}
-input features, varied $
+In this experiment stages last for $40$, $75$ and $40$ epochs, respectively, and the base
+learning rate of ${10}^{-3}$ is reduced after the $10$-th epoch to ${10}^{-4}$.
+%
+Plots~\ref{fig:mnist-like__trade-off__kmnist} and \ref{fig:mnist-like__trade-off__emnist}
+depict samples from the performance-compression curve on KMNIST and EMNIST-Letters datasets
+for the studied models and VD compression method (sec.~\ref{ssub:variational_dropout}).
+Besides that we tried \texttt{raw} or \texttt{fft} input features, varied $
   C \in \{\tfrac3{2^{k+1}}\colon k=1..16\}
-$, and repeated the experiment $4$ times.
-
-% observation: raw features -- alright
-
-fft features with wide dense network exhibit improving performance with the compression rate
-up to a certain limit.
-
-% discuss the plots describing how the test-performance grows with compression and then drops if the model is too sparse
-% which is better ARD or VD
-It is worth pointing out that the prior used in ARD models offers slightly more favourable
-compression-accuracy values, matching the established perception that log-uniform prior
-is too harsh for sparsification tasks \citep{kharitonov_variational_2018}.
-
-Nevertheless, it is clear form the results depicted in \ref{where}, that VD and ARD
-methods yield very similar compression-performance frontiers.
-
-% second experiment: use scheduler Trabelsi et al. (2018) and show them plotz!
-In the second experiment we use a much slower learning rate scheduler and study only the 
-VD method.
-
-% hinting at overfitting/regularization effects of masking and sparsification
-
-% hopeful conclusion
-\todo{The numerical experiments on MNIST-like datasets} demonstrate, that models using fourier
-features perform poorly in comparison to models using raw image input.
+$, and repeated the experiment $5$ times.
+
+We make a couple of observations based on these results. First, Fourier features appear to
+perform on par with raw colour channel data in the convolutional networks across most
+compression rates, but require high compression to make wide shallow dense network work
+as well. The upward trend in manifests itself in MNIST and Fashion MNIST experiments as well
+(see appendix~\ref{sub:other_mnist_like_datasets}). Finally, overall $\cplx$ variational
+dropout methods seems to compress network adequately well, without much loss in performance.
 
@@
 Experiments on CIFAR10 dataset are set up similarly to MNIST-like experiment, except
-that we study VGG16 model \citep{simonyan_very_2015} and its $\cplx$-counterpart. Each
-network is trained stagewise for $20$, $40$, and $20$ epochs on the full training split
-of $50k$ colour $32\times32$ images. We use only raw colour features (\texttt{raw}), since
-the results of the experiments on MNIST left us sceptical about the utility of the Fourier
-features for image recognition. We use fast learning rate scheduler from sec.~\ref{sub:mnist_like_datasets}
-and apply random crop and horizontal flips as augmentation.
+that we study VGG16 model \citep{simonyan_very_2015} and its $\cplx$-counterpart and
+replicate each experiment only twice. Each network is trained stagewise for $20$, $40$,
+and $20$ epochs on the full training split of $50k$ colour $32\times32$ images. We use
+only raw colour features (\texttt{raw}). We use fast learning rate scheduler and apply
+random crop and horizontal flips as augmentation. The scheduler scales the base learning
+rate after $5$, $10$, and $20$-th epoch by $\tfrac1{10}$, $\tfrac1{20}$ and $\tfrac1{100}$,
+respectively.
 
@@
 % draw some conclusions
-The halved $\cplx$ network significantly underperforms in comparison with its $\real$ counterpart
+Figure~\ref{fig:figure__cifar10__trade-off} shows that although the prior used in ARD method
+offers slightly less compression, it makes up for it by equally slightly better accuracy.
+Furthermore, the results imply that that the halved $\cplx$ network visibly underperforms
+in comparison with its $\real$ counterpart, although in MNIST-like experiment $\cplx$-valued
+network with the same inner feature dimensions performed on close to $\real$-valued, which
+is half the size of the former.
 
@@
 In this section we derive the exact gradient of \eqref{eq:improper-kl-div-real}. Even
-though, ultimately, the divergence involves a hypergeometric function \todo{which one},
-and its gradient requires evaluating the Gauss error function, the analysis provides
-independent verification of the approximation, proposed by \citet{molchanov_variational_2017}.
-The logic of the derivation follows \citet{lapidoth_capacity_2003}.
+though, ultimately, the divergence involves a hypergeometric function, and its gradient
+requires evaluating the Gauss error function, the analysis provides independent verification
+of the approximation, proposed by \citet{molchanov_variational_2017}. The logic of the
+derivation follows \citet{lapidoth_capacity_2003}.
 % \citet{pav_moments_2015} correctly notice that \cite[p. 2466]{lapidoth_capacity_2003} has a missing $\log{2}$ term.
@@
 
+\subsection{Other MNIST-like datasets} % (fold)
+\label{sub:other_mnist_like_datasets}
+
+We provide the figures of the MNIST-like experiments, omitted from the main paper
+due to size limitations.
+
+\begin{figure}[!h]
+  \centering
+  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
+    \centering
+    \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__fashionmnist__fft__-0.5.pdf}
+  \end{subfigure} \\%
+  % \hfill
+  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
+    \centering
+    \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__fashionmnist__raw__-0.5.pdf}
+  \end{subfigure}
+  \caption{%
+    The compression-accuracy trade-off on the letters part of the Fashion MNIST dataset.
+    (\textit{top}) \texttt{fft} features, (\textit{bottom}) \texttt{raw} features.
+  }
+  \label{fig:mnist-like__trade-off__fashionmnist}
+\end{figure}
+
+\begin{figure}[!h]
+  \centering
+  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
+    \centering
+    \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__mnist__fft__-0.5.pdf}
+  \end{subfigure} \\%
+  % \hfill
+  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
+    \centering
+    \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__mnist__raw__-0.5.pdf}
+  \end{subfigure}
+  \caption{%
+    The compression-accuracy trade-off on the letters part of the MNIST dataset.
+    (\textit{top}) \texttt{fft} features, (\textit{bottom}) \texttt{raw} features.
+  }
+  \label{fig:mnist-like__trade-off__mnist}
+\end{figure}
+
+% subsection other_mnist_like_datasets (end)
+
 % section appendix (end)

### 2020-02-08 cplxpaper/auto/__main__.py
added flag to indicate if incomplete

@@ -48,11 +48,14 @@ def one_experiment(wid, device, manifest):
     target = os.path.join(path, name)
 
     # run the experiment
-    if not os.path.exists(target):
-        os.makedirs(target, exist_ok=False)
+    flag = os.path.join(target, "INCOMPLETE")
+    if not os.path.isdir(target) or os.path.isfile(flag):
+        os.makedirs(target, exist_ok=True)  # once created it is kept
 
+        open(flag, "wb").close()  # set busy flag
         print(f">>> {wid:03d}-{device} {name}")
         run(options, target, time.strftime("%Y%m%d-%H%M%S"), verbose=False)
+        os.remove(flag)  # if run raises the flag is not reset
 
 
 def worker(wid, jobs, devarray, devices):

### 2020-02-19 cplxpaper/auto/reports/tradeoff.py
pin-memory patch

@@ -1,5 +1,6 @@
 import re
 import gc
+import copy
 import torch
 
 from functools import partial
@@ -63,6 +64,17 @@ def load_experiment(folder):
     return options, models
 
 
+def patch_feed(feed):
+    feed = copy.deepcopy(feed)
+
+    # force disable feed, if it is specified in the recipe
+    if feed.get("pin_memory", False):
+        # pinnig wastes memory on gpu 0 by allocating extra device context
+        feed["pin_memory"] = False
+
+    return feed
+
+
 def get_scorers(options, **devtype):
     """Creat scoring objects suitable for the experiment.
 
@@ -76,7 +88,8 @@ def get_scorers(options, **devtype):
     threshold = options["threshold"]
 
     # remove any feed that is tagged as train
-    feeds_recipes = {tag: feed for tag, feed in options["feeds"].items()
+    feeds_recipes = {tag: patch_feed(feed)
+                     for tag, feed in options["feeds"].items()
                      if "train" not in tag}
 
     dataset_tags = set(feed["dataset"] for feed in feeds_recipes.values())

### 2020-02-19 paper/appendix.tex
an embarassing typo and extended the appendix on mnist-like

\documentclass[a4paper]{extarticle}

% \usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{natbib}

\usepackage{geometry}

\usepackage{subcaption}
\usepackage[mathcal]{euscript}

\usepackage{graphicx, url}

\usepackage{amsmath, amsfonts, amssymb, amsthm}
\usepackage{mathptmx}

\usepackage{grffile}

\graphicspath{{../assets/appendix/}}

\title{Bayesian Sparsification of Deep $\cplx$-valued networks -- Extendeed appendix}
\author{Ivan Nazarov, and Evgeny Burnaev}

%% notation
\newcommand{\real}{\mathbb{R}}
\newcommand{\cplx}{\mathbb{C}}
\newcommand{\tr}[1]{\mathop{tr}{#1}}

\newcommand{\hop}{{\mkern-1.5mu\dagger}}
\newcommand{\conj}[1]{\overline{#1}}

% \renewcommand{\top}{{\mkern-1.5mu\intercal}}
\renewcommand{\vec}[1]{\overrightarrow{#1}}
\newcommand{\diag}[1]{\mathrm{diag}{#1}}

\begin{document}
\maketitle
\tableofcontents
\listoffigures
\clearpage

\section{MNIST-like experiments} % (fold)
\label{sec:mnist_like_experiments}

The following scatter plots depict the samples from the compression-performance trade off
curve of simple networks studied in the experiments on the MNIST-like datasets. Transparent
horizontal bands on each plot represent min-max performance spread of an uncompressed
network on the test split. The points illustrate the final trade-off of the compressed
networks after fine-tuning, while their tails show the performance gain or loss due to
the fine-tuning.

We recap the set up of each experiment on MNIST-like:
\begin{itemize}
  \item staged training, with weight transfer
  \item $40$, $75$, and $40$ epochs for ``dense'', ``sparsify'', and ``fine-tune'' stagers, respectively
  \item ADAM optimizer with learning rate $10^{-3}$ before the $10$-th, and $10^{-4}$
  afterwards
  \item $\ell_2$-norm global gradient clipping at $\tfrac12$
  \item training batches of size $128$ from a fixed randomly subset ($10^4$ images) of the training split
  \item the multiplier of the Kullback-Leibler term in ELBO varies over $
    C \in \{
      \tfrac32 2^{-\tfrac{k}2} \colon k=2, \cdots, 38
    \}
  $
  \item the sparsification threshold $\tau$ is set to $-\tfrac12$
\end{itemize}

Each figure shows the compression-accuracy trade-off of a particular method and input features
for \textit{SimpleConvModel} and \textit{TwoLayerDenseModel} models for all four of the studied
datasets (described in the main text): \emph{top-left} EMNIST-Letters, \emph{top-right} KMNIST,
\emph{bottom-left} Fashion MNIST, and \emph{bottom-right} MNIST.

Figures \ref{fig:appendix__mnist-like__trade-off__ARD__fft}, \ref{fig:appendix__mnist-like__trade-off__VD__fft},
\ref{fig:appendix__mnist-like__trade-off__ARD__raw}, and \ref{fig:appendix__mnist-like__trade-off__VD__raw}
compare $\real$ models against $\cplx$ with \emph{the same architecture}, i.e. incomparable
according to \citet{monning_evaluation_2018}. We also report the trade-off comparison, when
their argument for higher intrinsic capacity of $\cplx$-valued networks has been taken
into account.
%
We compare $\real$ networks against $\tfrac12 \cplx$ with half the number of parameters
for raw input features on figures \ref{fig:appendix__cmp__mnist-like__trade-off__ARD__raw},
and \ref{fig:appendix__cmp__mnist-like__trade-off__VD__raw}, and $2 \real$ with
double the number of parameters against $\cplx$ for Fourier input features on figures
\ref{fig:appendix__cmp__mnist-like__trade-off__ARD__fft} and
\ref{fig:appendix__cmp__mnist-like__trade-off__VD__fft}.

The experimental yield the following observations
\begin{itemize}
  \item $\cplx$-valued networks do not have as much spare capacity as $2 \real$ due to
  constants imposed by multiplication in $\cplx$ numbers (\ref{fig:appendix__cmp__mnist-like__trade-off__ARD__raw},
  \ref{fig:appendix__cmp__mnist-like__trade-off__VD__raw})
  \item Variational Dropout and Automatic Relevance Determination offer similar compression-performance
  trade-off, with negligibly lower compression by the latter (both $\real$ and $\cplx$ versions,
  e.g. figures \ref{fig:appendix__mnist-like__trade-off__ARD__raw} and \ref{fig:appendix__mnist-like__trade-off__VD__raw})
  \item smaller networks tend to be less compressible (figures \ref{fig:appendix__cmp__mnist-like__trade-off__ARD__fft},
\ref{fig:appendix__cmp__mnist-like__trade-off__VD__fft})
\end{itemize}

results lend evidence to the following generally accepted rules:

\begin{figure}[ht]
  \centering
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__emnist_letters__fft__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__kmnist__fft__-0.5.pdf}
  \end{subfigure} \\ %
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__fashionmnist__fft__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__mnist__fft__-0.5.pdf}
  \end{subfigure}
  \caption{%
    The compression-accuracy trade-off of ARD method for $\real$ and $\cplx$ models using Fourier features.
  }
  \label{fig:appendix__mnist-like__trade-off__ARD__fft}
\end{figure}

\begin{figure}[ht]
  \centering
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__emnist_letters__fft__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__kmnist__fft__-0.5.pdf}
  \end{subfigure} \\ %
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__fashionmnist__fft__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__mnist__fft__-0.5.pdf}
  \end{subfigure}
  \caption{%
    The compression-accuracy trade-off of VD method for $\real$ and $\cplx$ models using Fourier features.
  }
  \label{fig:appendix__mnist-like__trade-off__VD__fft}
\end{figure}

\begin{figure}[ht]
  \centering
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__emnist_letters__raw__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__kmnist__raw__-0.5.pdf}
  \end{subfigure} \\%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__fashionmnist__raw__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__mnist__raw__-0.5.pdf}
  \end{subfigure}
  \caption{%
    The compression-accuracy trade-off of ARD method for $\real$ and $\cplx$ models using raw features.
  }
  \label{fig:appendix__mnist-like__trade-off__ARD__raw}
\end{figure}

\begin{figure}[ht]
  \centering
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__emnist_letters__raw__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__kmnist__raw__-0.5.pdf}
  \end{subfigure} \\%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__fashionmnist__raw__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__mnist__raw__-0.5.pdf}
  \end{subfigure}
  \caption{%
    The compression-accuracy trade-off of VD method for $\real$ and $\cplx$ models using raw features.
  }
  \label{fig:appendix__mnist-like__trade-off__VD__raw}
\end{figure}

\begin{figure}[ht]
  \centering
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__emnist_letters__fft__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__kmnist__fft__-0.5.pdf}
  \end{subfigure} \\ %
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__fashionmnist__fft__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__mnist__fft__-0.5.pdf}
  \end{subfigure}
  \caption{%
    The compression-accuracy trade-off of ARD method for $2\real$ and $\cplx$ models using Fourier features.
  }
  \label{fig:appendix__cmp__mnist-like__trade-off__ARD__fft}
\end{figure}

\begin{figure}[ht]
  \centering
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__emnist_letters__fft__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__kmnist__fft__-0.5.pdf}
  \end{subfigure} \\ %
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__fashionmnist__fft__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__mnist__fft__-0.5.pdf}
  \end{subfigure}
  \caption{%
    The compression-accuracy trade-off of VD method for $2\real$ and $\cplx$ models using Fourier features.
  }
  \label{fig:appendix__cmp__mnist-like__trade-off__VD__fft}
\end{figure}

\begin{figure}[ht]
  \centering
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__emnist_letters__raw__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__kmnist__raw__-0.5.pdf}
  \end{subfigure} \\%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__fashionmnist__raw__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__mnist__raw__-0.5.pdf}
  \end{subfigure}
  \caption{%
    The compression-accuracy trade-off of ARD method for $\real$ and $\tfrac12\cplx$ models using raw features.
  }
  \label{fig:appendix__cmp__mnist-like__trade-off__ARD__raw}
\end{figure}

\begin{figure}[ht]
  \centering
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__emnist_letters__raw__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__kmnist__raw__-0.5.pdf}
  \end{subfigure} \\%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__fashionmnist__raw__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__mnist__raw__-0.5.pdf}
  \end{subfigure}
  \caption{%
    The compression-accuracy trade-off of VD method for $\real$ and $\tfrac12\cplx$ models using raw features.
  }
  \label{fig:appendix__cmp__mnist-like__trade-off__VD__raw}
\end{figure}

% section mnist_like_experiments (end)

\section{CIFAR10 experiments} % (fold)
\label{sec:cifar_experiments}

% section cifar_experiments (end)

\section{MusicNet experiments} % (fold)
\label{sec:muscinet_experiments}

% section muscinet_experiments (end)

\clearpage

\bibliographystyle{abbrvnat}
\bibliography{references}

\end{document}

### 2020-02-19 paper/appendix.tex
added cifar description, fixed typos

@@
 
-\title{Bayesian Sparsification of Deep $\cplx$-valued networks -- Extendeed appendix}
+\title{Bayesian Sparsification of Deep $\cplx$-valued networks -- Extended appendix}
 \author{Ivan Nazarov, and Evgeny Burnaev}
@@
 \begin{itemize}
-  \item staged training, with weight transfer
+  \item staged training, with weight and optimizer state transfer
   \item $40$, $75$, and $40$ epochs for ``dense'', ``sparsify'', and ``fine-tune'' stagers, respectively
@@
 \end{itemize}
+Each experiment was performed $5$ times to obtain a small sample of performance-compression
+values for each setting of $C$. By reevaluating each setting several times we can account
+for randomness in initialization of the uncompressed network at ``dense'', stochasticity of
+variational dropout layers, and randomness of batch sequences during SDG, and non-determinism
+of computations on GPUs.
 
@@
 \emph{bottom-left} Fashion MNIST, and \emph{bottom-right} MNIST.
-
+%
 Figures \ref{fig:appendix__mnist-like__trade-off__ARD__fft}, \ref{fig:appendix__mnist-like__trade-off__VD__fft},
@@
 
-The experimental yield the following observations
+The following observations could be made from the conducted experiment:
 \begin{itemize}
@@
 \end{itemize}
-
-results lend evidence to the following generally accepted rules:
 
@@
 
+\clearpage
+
 \section{CIFAR10 experiments} % (fold)
@@
 
+For the CIFAR10 experiment we reuse the setup of the MNIST-like experiment with the
+following exceptions:
+\begin{itemize}
+  \item we allocate $20$, $40$, and $20$ epochs to each stage
+  \item the weight of the KL divergence term varies over a smaller grid $
+    C \in \{
+      \tfrac32 2^{-\tfrac{k}2} \colon k=7, \cdots, 15
+    \}
+  $
+  \item we use full $50$k training split of the CIFAR10 dataset for training and raw color
+  features only
+  \item dataset is randomly augmented: every image within a batch of size $128$ is randomly
+  cropped and flipped horizontally
+\end{itemize}
+Random cropping is done by zero-padding each side of a $32\times 32$ image by four pixels
+and then a extracting a random $32\times 32$ patch from the $40\times 40$ intermediate image.
+
+We experiment with $\real$ VGG16 network \citep{simonyan_very_2015} and its $\cplx$-valued
+variant, which straightforwardly replaces $\real$ layers with their $\cplx$ counterparts.
+
+\begin{figure}[!ht]
+  \centering
+  \includegraphics[width=\linewidth]{figure__cifar__trade-off/appendix__augmentedcifar10__raw__-0.5.pdf}
+  \caption{%
+    The compression-accuracy trade-off for $\real$ and $\cplx$ VGG16 using raw input features.
+  }
+  \label{fig:appendix__cifar__trade-off__VGG16__raw}
+\end{figure}
+
 % section cifar_experiments (end)
-
-\section{MusicNet experiments} % (fold)
-\label{sec:muscinet_experiments}
-
-% section muscinet_experiments (end)
 

### 2020-02-19 paper/appendix.tex
added some conclusion to the appendix

@@
 
+To supplement the results, reported in the main text (figures \ref{fig:paper__mnist-like__trade-off__VD__fft}
+and \ref{fig:paper__mnist-like__trade-off__VD__raw}), we conduct additional experiments
+with the same basic setup, but over a finer grid of KL-divergence term coefficients.
+%
+These experiments lend further evidence in supporting the conclusions, draw in the main
+paper, namely that the $\cplx$-valued extension of the $\real$-valued variational dropout
+can offer significant compression levels without much loss in performance. At the same
+time, the test performance of both $\real$ and $\cplx$ compressed networks benefits from
+an extra fine-tuning stage, during which sparsity masks are fixed.
+
+One intriguing observation, is that on MNIST-like images the dense network taking Fourier
+features on input, exhibits gradually improving test-split performance. This is in stark
+contrast to raw image input, where the performance stays at the one level in the small
+compression regime, and then gradually decays at high compression levels. Noteworthy is
+the presence of a trough in the pre fine-tuning stage performance in the small compression
+regime on figures
+\ref{fig:appendix__mnist-like__trade-off__ARD__raw},
+\ref{fig:appendix__mnist-like__trade-off__VD__raw},
+\ref{fig:appendix__cmp__mnist-like__trade-off__ARD__raw},
+and \ref{fig:appendix__cmp__mnist-like__trade-off__VD__raw}, which then slowly disappears
+as compression increases.
+
 The following scatter plots depict the samples from the compression-performance trade off
@@
 
-We recap the set up of each experiment on MNIST-like:
+We recap the set up of each additional experiment on MNIST-like datasets:
 \begin{itemize}
@@
   afterwards
-  \item $\ell_2$-norm global gradient clipping at $\tfrac12$
+  \item global $\ell_2$-norm gradient clipping set at $\tfrac12$
   \item training batches of size $128$ from a fixed randomly subset ($10^4$ images) of the training split
@@
   \caption{%
-    The compression-accuracy trade-off of ARD method for $\real$ and $\cplx$ models using Fourier features.
+    The trade-off of ARD method for $\real$ and $\cplx$ models using Fourier features.
   }
@@
   \caption{%
-    The compression-accuracy trade-off of VD method for $\real$ and $\cplx$ models using Fourier features.
+    The trade-off of VD method for $\real$ and $\cplx$ models using Fourier features.
   }
@@
   \caption{%
-    The compression-accuracy trade-off of ARD method for $\real$ and $\cplx$ models using raw features.
+    The trade-off of ARD method for $\real$ and $\cplx$ models using raw features.
   }
@@
   \caption{%
-    The compression-accuracy trade-off of VD method for $\real$ and $\cplx$ models using raw features.
+    The trade-off of VD method for $\real$ and $\cplx$ models using raw features.
   }
@@
   \caption{%
-    The compression-accuracy trade-off of ARD method for $2\real$ and $\cplx$ models using Fourier features.
+    The trade-off of ARD method for $2\real$ and $\cplx$ models using Fourier features.
   }
@@
   \caption{%
-    The compression-accuracy trade-off of VD method for $2\real$ and $\cplx$ models using Fourier features.
+    The trade-off of VD method for $2\real$ and $\cplx$ models using Fourier features.
   }
@@
   \caption{%
-    The compression-accuracy trade-off of ARD method for $\real$ and $\tfrac12\cplx$ models using raw features.
+    The trade-off of ARD method for $\real$ and $\tfrac12\cplx$ models using raw features.
   }
@@
   \caption{%
-    The compression-accuracy trade-off of VD method for $\real$ and $\tfrac12\cplx$ models using raw features.
+    The trade-off of VD method for $\real$ and $\tfrac12\cplx$ models using raw features.
   }
   \label{fig:appendix__cmp__mnist-like__trade-off__VD__raw}
+\end{figure}
+
+\begin{figure}[ht]
+  \centering
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{../figure__mnist-like__trade-off/legacy__VD__emnist_letters__fft__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{../figure__mnist-like__trade-off/legacy__VD__kmnist__fft__-0.5.pdf}
+  \end{subfigure} \\%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{../figure__mnist-like__trade-off/legacy__VD__fashionmnist__fft__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{../figure__mnist-like__trade-off/legacy__VD__mnist__fft__-0.5.pdf}
+  \end{subfigure}
+  \caption{%
+    The trade-off of VD method for $\real$ and $\cplx$ models using Fourier features (main text).
+  }
+  \label{fig:paper__mnist-like__trade-off__VD__fft}
+\end{figure}
+
+\begin{figure}[ht]
+  \centering
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{../figure__mnist-like__trade-off/legacy__VD__emnist_letters__raw__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{../figure__mnist-like__trade-off/legacy__VD__kmnist__raw__-0.5.pdf}
+  \end{subfigure} \\%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{../figure__mnist-like__trade-off/legacy__VD__fashionmnist__raw__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{../figure__mnist-like__trade-off/legacy__VD__mnist__raw__-0.5.pdf}
+  \end{subfigure}
+  \caption{%
+    The trade-off of VD method for $\real$ and $\cplx$ models using raw features (main text).
+  }
+  \label{fig:paper__mnist-like__trade-off__VD__raw}
 \end{figure}
@@
 
-For the CIFAR10 experiment we reuse the setup of the MNIST-like experiment with the
-following exceptions:
+In addition to the results reported in the main paper, we conduct additional experiment
+on CIFAR10 and VGG16 with a much more slowly annealed learning rate. Similar to MNIST-like
+experiments, we start with rate set to $10^{-3}$ and then reduce it by $10$ after the
+$10$-the epoch. In summary, for the CIFAR10 experiment we reuse the setup with the following
+changes:
 \begin{itemize}

### 2020-03-14 paper/paper.tex
an embarassing typo and extended the appendix on mnist-like
edits after independent proofreading

@@
 remains a challenge due to storage, real-time throughput, and arithmetic (computational)
-complexity restrictions \citep{he_amc:_2018}. Therefore compression methods for achieving
+complexity restrictions \citep{he_amc:_2018}. Therefore, compression methods for achieving
 high model sparsity and numerical efficiency without losing much in performance are
@@
 Inherently complex-valued nature of data in signal processing, specifically, acoustic or radio
-frequency signal analysis, has been the key driver behind adoption of $\cplx$-networks.
+frequency signal analysis, has been the key driver behind the adoption of $\cplx$-networks.
 %
@@
 $\cplx$-arithmetic reduces ineffective degrees of freedom in comparison with an analogous
-double-dimensional $\real$-valued network. \citet{hirose_complex-valued_2009} list numerous
-applications related to acoustic and radio signal processing and demonstrate superiority of
+double-dimensional $\real$-valued network. \citet{hirose_complex-valued_2009} lists numerous
+applications related to acoustic and radio signal processing and demonstrates superiority of
 $\cplx$-networks in the task of shallow landmine detection using ground penetrating radar
-imaging. More recently they were applied to music transcription and speech recognition
+imaging. More recently they have been applied to music transcription and speech recognition
 \citep{trabelsi_deep_2017}. \citet{arjovsky_unitary_2016} propose $\cplx$-valued unitary-RNNs
@@
 recurrent weights on the $\cplx^{n \times n}$ Stiefel manifold. And \citet{wolter_complex_2018}
-investigate different $\cplx$-valued gating mechanisms unitary-RNNs and conduct experiments
+investigate different $\cplx$-valued gating mechanisms for unitary-RNNs and conduct experiments
 on human motion prediction and music transcription. \citet{yang_complex_2019} develop complex
@@
 % segue into bayesian inference
-Bayesian inference is a very rich field of research with a large body of research and
-techniques that enable practical quantification of predictive, parameter, or model
-uncertainty and its propagation into solutions of the problems of interest.
+Bayesian inference is a very rich field with a large body of research and techniques that
+enable practical quantification of predictive, parameter, or model uncertainty and its 
+propagation into solutions of the problems of interest.
 %
@@
 therefore exact inference is traded for tractability and scalability offered by Variational
-Inference. Instead of deriving $p(\omega \mid D)$ using the rule, this approach recasts
+Inference. Instead of deriving $p(\omega \mid D)$ using the Bayes rule, this approach recasts
 posterior inference into variational optimization problem: finding $q$ that is close to
@@
   q_\theta(\omega) d\omega
-$, can be sampled from and possess tractable $\log$-derivatives $
+$, can be sampled from and have either tractable $\log$-derivatives $
   \omega \mapsto \nabla_\theta \log q_\theta(\omega)
@@
 and Gaussian dropout \citep{srivastava_dropout_2014,wang_fast_2013} through the lens
-of Bayesian inference methods and proposes \textit{Variational Dropout}. They argue that
+of Bayesian inference methods and propose \textit{Variational Dropout}. They argue that
 the multiplicative noise introduced by these methods induces a distribution equivalent to
@@
 \citet{kingma_variational_2015} approximate this expression by a non-linear polynomial
-regression for truncated $\alpha \in (0, 1)$. \citet{molchanov_variational_2017}
-refine the approximation by using a nonlinear regression based on sigmoid and soft-plus.
+regression over $\alpha \in (0, 1)$. \citet{molchanov_variational_2017} refine the
+approximation by using a nonlinear regression based on sigmoid and soft-plus.
 % see p.6 sec 3.4 of kingma_variational_2015
@@
 Being the ratio of the squared mean to the effective variance, $\alpha_j$ regulates the
-relevance of the parameter $\omega_j$ it is associated to. Thus \citet{molchanov_variational_2017}
+relevance of the parameter $\omega_j$ it is associated to. Thus, \citet{molchanov_variational_2017}
 focus on the model sparsification capabilities of Variational Dropout, optimizing $\alpha$
@@
 dropout with shared $\alpha$ across groups of parameters $\omega$. Another Bayesian dropout
-method, called \textit{Automatic Relevance Determination}, is developed in \citep{kharitonov_variational_2018}.
+method, called \textit{Automatic Relevance Determination}, has been developed in \citep{kharitonov_variational_2018}.
 The key difference is that the log-uniform factor $\pi(\omega_{ij})$ is replaced by a proper
-Gaussian prior $
+ARD Gaussian prior $
   \mathcal{N}(0, \tau^{-1}_{ij})
@@
 
-In this section we briefly review $\cplx$-valued networks, their distinction from the
+In this section we briefly review $\cplx$-valued networks, and their distinction from the
 ordinary $\real$-valued networks.
@@
 $\cplx$-valued activations, complex batch-normalization and suitable weight initialization.
-Their approach makes a complex-valued network into an intricately connected $\real$-valued
+Their approach transforms a complex-valued network into an intricately connected $\real$-valued
 computational graph that respects $\cplx$-arithmetic.
@@
 of $\cplx$-argument \citep{adali_complex-valued_2011,boeddeker_computation_2019}. It satisfies
-product and chain rules, respects complex conjugation and linearity, but most importantly the
+the product and chain rules, respects complex conjugation and linearity, but most importantly the
 $\cplx\real$-differential of a function on $\cplx$ coincides with its classical differential as
@@
 For $\cplx$-variational dropout we propose using mean-field proper $\cplx$-Gaussian approximate
-posterior, e.g. parameters $W \in \cplx^{n\times m}$ of a dense linear layer follow
+posterior and MAP estimates of bias terms, i.e. parameters $W \in \cplx^{n\times m}$ of a dense
+linear layer follow
+% We use MAP estimates of bias terms, i.e. assume an independent fully factorized Dirac approximation.
 \begin{equation}  \label{eq:c-gauss-vi}
@@
 layers. For this approximation the relation coefficients \eqref{eq:cplx-gauss-trick} are
-zero. We use MAP estimates of bias terms, i.e. assume an independent fully factorized Dirac
-approximation.
+zero.
 
@@
 which is approximated by \citet{molchanov_variational_2017}. The major drawback of this method
-is inapplicability of the additive noise reparameterization in \eqref{eq:real-scal-gauss-trick},
-which disentangles the gradient with respect to $\mu$ from the local noise.
+is that the additive noise reparameterization in \eqref{eq:real-scal-gauss-trick}, which
+disentangles the gradient with respect to $\mu$ from the local noise, cannot be applied.
 
@@
 In this section we study the complex variational dropout techniques discussed above
-on the tasks and datasets, that were studied in prior research on complex-valued networks.
+on the tasks and datasets, that have been studied in prior research on complex-valued networks.
 
@@
 The benefit of the ``fine-tune'' stage appears to be strongly influenced by the compression
-rate. In this experiment and more prominently in MusicNet (sec.~\ref{sub:musicnet}), we
-can observe that the more ``holes'' Bayesian dropout poked in the model, the more regularized
-it becomes, the less capacity it maintains for overfitting and the more ``fine-tune'' serves
-as extended training.
+rate. We can observe in this and, more prominently, in MusicNet experiment (sec.~\ref{sub:musicnet})
+that higher compression rate render the model more regularized, leaving less capacity for
+overfitting.
+% more ``holes'' Bayesian dropout ``poked'' makes the ``fine-tune'' serve as extended training.
 
@@
 \eqref{eq:elbo_with_coef}, the relative positions of the compression curves on this
-plot and the results of experiments below, it can be concluded that $C$ has much more
+plot, and the results of experiments below it can be concluded that $C$ has much more
 substantial impact on the sparsity and performance, than the choice of $\tau$. Furthermore,
@@
     \centering
-    \includegraphics[width=\linewidth]{../assets/log-alpha__sum__fashion-mnist__20200131-205926.pdf}
+    \includegraphics[width=\linewidth,draft]{../assets/log-alpha__sum__fashion-mnist__20200131-205926.pdf}
   \end{subfigure} \\%
@@
 $, where $n_\mathtt{zer}$ is the number of explicit zeros after sparsification, $n_\mathtt{par}$
-is the total number of floats. Thus each parameter is counted once in a $\real$-valued
+is the total number of floats. Thus, each parameter is counted once in a $\real$-valued
 network, but twice in a $\cplx$-network, being a pair of real-imaginary floats. Each model
@@
 of illustrating the compression and understanding the effects of experiment parameters.
-\textit{SimpleConvModel} (SCM) is $2d$ ReLU convolutional networks with average pooling
+\textit{SimpleConvModel} (SCM) is a $2d$ ReLU convolutional network with average pooling
 ($2\times 2$) after non-linearities with two convolutions (kernel $5\times 5$, stride $1$)
@@
 $ regardless of their type ($\real$ or $\cplx$), although \citet{monning_evaluation_2018}
-argues that this renders models incomparable.
+argue that this renders models incomparable.
 
@@
 perform on par with raw colour channel data in the convolutional networks across most
-compression rates, but require high compression to make wide shallow dense network work
+compression rates, but require high compression rate to make wide shallow dense network work
 as well. The upward trend in manifests itself in MNIST and Fashion MNIST experiments as well
@@
 and $20$ epochs on the full training split of $50k$ colour $32\times32$ images. We use
-only raw colour features (\texttt{raw}). We use fast learning rate scheduler and apply
-random crop and horizontal flips as augmentation. The scheduler scales the base learning
+only raw colour features (\texttt{raw}). We apply random crop and horizontal flips as
+data augmentation and use a learning rate scheduler in SGD, which scales the base learning
 rate after $5$, $10$, and $20$-th epoch by $\tfrac1{10}$, $\tfrac1{20}$ and $\tfrac1{100}$,
@@
 % describe the VGG16 model and its cplx-valued modification
-The $\cplx$-VGG16 model is architecturally identical to VGG16, except for all layers are
+The $\cplx$-VGG16 model is architecturally identical to VGG16, except for all layers being
 replaced by their $\cplx$-valued versions. To maintain comparability, we halve the filter
@@
     \centering
-    \includegraphics[width=\linewidth]{../assets/figure__cifar__trade-off/augmentedcifar10__raw__-0.5.pdf}
+    \includegraphics[width=\linewidth]{../assets/figure__cifar__trade-off/legacy__augmentedcifar10__raw__-0.5.pdf}
   \end{subfigure}
@@
     \centering
-    \includegraphics[width=\linewidth]{../assets/figure__musicnet__trade-off/musicnetram__fft__-0.5.pdf}
+    \includegraphics[width=\linewidth]{../assets/figure__musicnet__trade-off/paper__musicnetram__fft__-0.5.pdf}
   \end{subfigure}
@@
 
-\subsection{MusciNet} % (fold)
+\subsection{musicNet} % (fold)
 \label{sub:musicnet}
@@
 retaining only $84$ out of $128$ labels, and hold-out the same validation and test splits.
-During each training epoch we sample $1000$ mini-batches of the remaining $321$ compositions
-thus: a random full window of $4096$ samples is picked within each waveform and transformed
-from $\real$ to $\cplx$ with $1d$ FFT. Annotation labels are taken at the mid-point of the
-window.
+During each training epoch we sample $1000$ mini-batches of the remaining $321$ compositions,
+each mini-batch comprised of a random full window of $4096$ samples picked from each waveform
+and transformed from $\real$ to $\cplx$ with $1d$ FFT. Annotation labels are taken at the
+mid-point of the window.
 
 Preliminary experiments with the model without sparsification have shown that early stopping
-almost always terminated the training process within the first $10-20$ epochs, and that the
-validation performance peaked at about $10-15$ epochs, much sooner than $200$ epochs used by
+almost always terminates the training process within the first $10-20$ epochs, and that the
+validation performance peakeing at about $10-15$ epochs, much sooner than $200$ epochs used by
 \citet{trabelsi_deep_2017}. Thus we adopt shorter lasting stages: $12$, $32$ and $50$ epochs,
@@
 of $10^{-3}$ to be scaled after $5$, $10$, and $20$-th epoch by $\tfrac1{10}$, $\tfrac1{20}$
-and $\tfrac1{100}$, respectively. Other key deviations from the setup used by \citet{trabelsi_deep_2017}
+and $\tfrac1{100}$, respectively. Other key deviations from the set-up used by \citet{trabelsi_deep_2017}
 include: shifting lower frequencies to the centre of the window to maintain locality after
@@
 In each experiment we varied the method and the value $C$, while keeping $\tau$ at $-\tfrac12$.
-Each full experiment is replicated five times to take random effects from network initialization
-before ``dense'', stochastic batch sequence during SGD, and randomness of Bayesian forward
-pass at ``sparsify'' stage.
+Each full experiment is replicated five times to take into account random effects from network
+initialization before ``dense'', randomness of the mini-batch sequence during SGD, and
+stochasticity of intermediate layers on forward pass at ``sparsify'' stage.
 
@@
 For compression levels lower than $50$, the final stage overfits the network, since
-undercompresed remain overparameterized. For rates higher than $\approx 100$ the ``fine-tune''
-stage serves its purpose, essentially, due to the network's being sufficiently regularized
-though sparsity. There is evidence in favour of achievability of the SOTA average precision
-of \citet{trabelsi_deep_2017} within the $50$-$100$ compression region with $\cplx$-valued
-automatic relevance derivative (sec.~\ref{ssub:empirical_bayes}).
-
-% subsection muscinet (end)
+it sill remains overparameterized. For rates higher than $\approx 100$ the ``fine-tune''
+stage serves its purpose, essentially, due regularization effects if high sparsity. There
+is evidence in favour of achievability of the SOTA average precision of \citet{trabelsi_deep_2017}
+within the $50$-$100$ compression region with $\cplx$-valued variational dropout with ARD
+prior (sec.~\ref{ssub:empirical_bayes}).
+
+% subsection musicnet (end)
 
@@
 model parameters. To this end we have conducted a large scale numerical study of such networks
-to assess the performance-compression rate trade-off and achieved performance, comparable
+to assess the performance-compression rate trade-off and have achieved performance, comparable
 to SOTA on the MusicNet dataset.
@@
   (\mu_i)_{i=1}^m \in \mathbb{R}
-$. The random variable $W = \sum_i (\mu_i + z_i)^2$ noncentral $\chi^2$ with shape $m$
+$, the random variable $W = \sum_i (\mu_i + z_i)^2$ is noncentral $\chi^2$ with shape $m$
 and noncentrality parameter $\lambda = \sum_i \mu_i^2$, i.e. $W\sim \chi^2_m(\lambda)$.
@@
 % term, since it is typically implemented in a floating-point stable fashion.
-The numerically estimated derivative of the penalty term wrt $\log \alpha$ using forward
-differences seems to be following \eqref{eq:real-kl-div-deriv-log} very closely (up to
-sampling error) see fig.~\ref{fig:molchanov-derivative-replica}. The derivative of
+The numerically estimated derivative of the penalty term with respect to $\log \alpha$ using
+forward differences seems to be following \eqref{eq:real-kl-div-deriv-log} very closely (up to
+sampling error), see fig.~\ref{fig:molchanov-derivative-replica}. The derivative of
 \eqref{eq:improper-kl-div-real-approx} with respect to $\log \alpha$ appears to be very close
@@
 $\cplx$ variational dropout KL divergence term in \eqref{eq:c-vd-kl-div} with $\beta = 2$,
-fit the best approximation \eqref{eq:improper-kl-div-real-approx} and compare the derivatives.
+fit the best approximation \eqref{eq:improper-kl-div-real-approx}, and compare the derivatives.
 
@@
   \includegraphics[width=\linewidth]{../notebooks/assets/grad_log.pdf}
-  \caption{$\tfrac{d f(\alpha)}{d \log{\alpha}}$ of the fit proposed in
+  \caption{$\tfrac{d f(\alpha)}{d \log{\alpha}}$ of the fit proposed by
   \citet{molchanov_variational_2017}, MC estimate of \eqref{eq:improper-kl-div-real},

### 2020-03-14 cplxpaper/auto/auto.py
added some docstrings

@@ -34,6 +34,7 @@ benign_emergencies = (StopIteration, type(None))
 
 
 def defaults(options):
+    """Fill in the omitted specifications."""
     options = copy.deepcopy(options)
 
     # add defaults: device, threshold, and objective terms
@@ -88,23 +89,87 @@ def defaults(options):
 
 
 def get_datasets(recipe):
-    """Get dataset instances from the recipe."""
+    """Get dataset instances from the recipe.
+
+    Parameters
+    ----------
+    recipe : dict of dict
+        The specifications of the core datasets.
+
+    Returns
+    -------
+    datasets : dict of datasets
+        A dictionary of dataset instances, compatible with torch's
+        DataLoader objects.
+    """
     # "datasets"
     return {dataset: get_instance(**par) for dataset, par in recipe.items()}
 
 
 def wrap_feed(feed, max_iter=-1, **devtype):
-    """Return a feed that combines the limiter and the mover."""
+    """Return a feed that combines the limiter and the mover.
+
+    Parameters
+    ----------
+    feed : DataLoader-like object
+        The data feed, the batches of which should be moved to the device.
+
+    max_iter : int, default=-1
+        The upper limit on the number of data batches provided by the feed.
+
+    **devtype : dict
+        The dictionary specifying the device and dtype conversion for pytorch.
+
+    Returns
+    -------
+    feed : DataLoader-like object
+        A wrapped feed.
+    """
     return FeedMover(FeedLimiter(feed, max_iter), **devtype)
 
 
 def get_feature_generator(feed, recipe):
-    """Create feature generator (last step before feeeding into fit)."""
+    """Create feature generator (last step before feeding into fit).
+
+    Parameters
+    ----------
+    feed : torch.optim
+        The data feed to create the specified feature transformation for.
+
+    recipe : dict
+        The specifications of the feature transformation.
+
+    Returns
+    -------
+    feed : object
+        A wrapped feed.
+    """
     return get_instance(feed, **recipe)
 
 
 def get_feeds(datasets, devtype, features, recipe):
-    """Get instances of data feeds (loader with feature geenrator)."""
+    """Get instances of data feeds (loader with feature generator).
+
+    Parameters
+    ----------
+    datasets : dict of Dataset objects
+        The source datasets over which to construct and package data loaders.
+
+    devtype : dict
+        The dictionary specifying the device and dtype conversion for pytorch.
+
+    features : dict
+        Teh dictionary, specifying the feature transformations.
+
[…]

### 2020-03-16 paper/paper.tex
manually incorporated edits from the icml branch

@@
 three successive stages in every experiment: ``dense'' $\to$ ``sparsify'' $\to$ ``fine-tune''.
-Model parameters and the optimizer are copied between stages, except before the final stage
-optimizer's internal state is reset.
 
@@
   \alpha = \tfrac{\sigma^2}{\lvert\mu\rvert^2}
-$, or zero otherwise. Figure~\ref{fig:hist__and__threshold__tradeoff} (top) displays the
-general shape of the distribution of $\log \alpha$ on the Fashion-MNIST dataset in
-sec.~\ref{sub:mnist_like_datasets}. There always appears to be a mode in the moderately
-negative range, a valley through zero between the peaks of the negative mode and the next
-positive one. The relative mass of each mode changes with $C$ and the higher the coefficient
-is, the more mass is shifted to the right.
-%
-The bottom graph on figure~\ref{fig:hist__and__threshold__tradeoff} is constructed
+$, or zero otherwise. Figure~\ref{fig:hist__and__threshold__tradeoff} is constructed
 for $C \in \{\tfrac1{20}, \frac1{200}\}$ before running the ``fine-tune'' stage. From
@@
 
-\begin{figure}[ht]
+\begin{figure}[!t]
   \centering
@@
     \centering
-    \includegraphics[width=\linewidth,draft]{../assets/log-alpha__sum__fashion-mnist__20200131-205926.pdf}
-  \end{subfigure} \\%
-  % \hfill
-  \begin{subfigure}[b]{0.95\textwidth}  % imcl2019-style swears at this
-    \centering
-    \includegraphics[width=\linewidth]{../assets/figure__musicnet__threshold.pdf}
+    \includegraphics[width=\columnwidth]{../assets/figure__musicnet__threshold.pdf}
   \end{subfigure}
   \caption{%
-    (\textit{top}) Smoothed density of $\log\alpha$ for some convolutional and dense layer
-    from a model in sec.~\ref{sub:mnist_like_datasets};
-    (\textit{bottom}) Test split performance and compression rate for a $\cplx$-valued
-    net on MusicNet.
+    Test split performance and compression rate for a $\cplx$-valued net on MusicNet.
   }
@@
         {\alpha \lvert \mu \rvert^2}
-$ is $\chi^2_k$ distributed with $k=1$ ($\real$) or $2$ ($\cplx$), whence
-\begin{equation} \label{eq:prob_relevant}
-  \Pr\bigl(
-    \lvert w - \mu \rvert \leq \delta \lvert \mu \rvert
-  \bigr)
-    % = \Pr\biggl(
-    %   \frac{k \lvert w - \mu \rvert^2}{\alpha \lvert \mu \rvert^2}
-    %     \leq \frac{\delta^2 k}{\alpha}
-    % \biggr)
-    = \chi^2_k\biggl(\frac{\delta^2 k}{\alpha}\biggr)
-  \,.
-\end{equation}
+$ is $\chi^2_k$ distributed with $k=1$ ($\real$) or $2$ ($\cplx$).
+%
 For a generous $\delta = 50\%$ tolerance all values of $\log \alpha$ below $-2.5$ yield
@@
 and CIFAR10 datasets. Similarly to \citet{trabelsi_deep_2017} performance in experiments with
-MusicNet is measured with (pooled) average precision: predicted scores and target binary labels
-for each output are pooled, and average precision is computed based on the precision-recall
-curve as if the task was single-output. The evaluation is done after ``dense'' stage, before
-the beginning and upon termination of the ``fine-tune'' stage.
+MusicNet is measured with (pooled) average precision. The evaluation is done after ``dense''
+stage, before the beginning and upon termination of the ``fine-tune'' stage.
 
@@
 The compression rate is computed based on the number of floating point values needed to
-specify the model and equals $
+store the model and equals $
   \tfrac{n_\mathtt{par}}{n_\mathtt{par} - n_\mathtt{zer}}
-$, where $n_\mathtt{zer}$ is the number of explicit zeros after sparsification, $n_\mathtt{par}$
-is the total number of floats. Thus, each parameter is counted once in a $\real$-valued
-network, but twice in a $\cplx$-network, being a pair of real-imaginary floats. Each model
-has incompressible parameters, such as layers' biases, shift and scaling from $\real$-and
-$\cplx$-batch normalization layers, if present.
+$, where $n_\mathtt{zer}$ is the number of explicit zeros, $n_\mathtt{par}$ is the total
+number of floats. Thus each parameter is counted once in a $\real$-valued network, but twice
+in a $\cplx$-network. Each model has compression limit, set by layers' biases, shift
+and scaling from $\real$-and $\cplx$-batch normalization.
 
@@
 datasets to study the compression-performance trade-off of the proposed $\cplx$-variational
-dropout on simple architectures.
+dropout.
 % dataset size
 We deliberately use a {fixed} random subset of $10k$ images from the train split of each
-dataset to fit the networks, and gauge the final performance on the usual test split.
-Limiting the size was done primarily to test the regularization strength of compression,
-and to make bulk experimentation faster.
+dataset to fit the networks and gauge the final performance on the usual test split.
+Limiting the size was done primarily to test the regularization strength of compression.
 
@@
 % discussion of TwoLayerDenseModel (TLDM) and SimpleConvModel (SCM)
-The $\real$/$\cplx$ networks, studied in this experiment, have been chosen for the purpose 
-of illustrating the compression and understanding the effects of experiment parameters.
-\textit{SimpleConvModel} (SCM) is a $2d$ ReLU convolutional network with average pooling
-($2\times 2$) after non-linearities with two convolutions (kernel $5\times 5$, stride $1$)
-with filters $n_1 \to n_2$ followed by dense layers $n_3 \to n_\mathtt{out}$. The second
-network, \textit{TwoLayerDenseModel} (TLDM), is a wide dense network $n_1 \to n_\mathtt{out}$.
-For SCM model $n_1, n_2, n_3$ are $20, 50, 500$, respectively, and for TLDM model $
-  n_1 = 4096
-$ regardless of their type ($\real$ or $\cplx$), although \citet{monning_evaluation_2018}
-argue that this renders models incomparable.
+The $\real$/$\cplx$ networks have been chosen for the purpose of illustrating the compression
+and understanding the effects of experiment parameters. \textit{SimpleConvModel} (SCM) is a $2d$
+ReLU convolutional network with average pooling ($2\times 2$) after non-linearities with
+two convolutions (kernel $5\times 5$, stride $1$) with filters $n_1 \to n_2$ followed by
+dense layers $n_3 \to n_\mathtt{out}$. The second network, \textit{TwoLayerDenseModel} (TLDM),
+is a wide dense network $n_1 \to n_\mathtt{out}$. For SCM model $n_1, n_2, n_3$ are $20, 50, 500$,
+respectively, and for TLDM model $n_1 = 4096$ regardless of their type ($\real$ or $\cplx$),
+although \citet{monning_evaluation_2018} argue that this renders models incomparable.
 
@@
 %
-Plots~\ref{fig:mnist-like__trade-off__kmnist} and \ref{fig:mnist-like__trade-off__emnist}
-depict samples from the performance-compression curve on KMNIST and EMNIST-Letters datasets
-for the studied models and VD compression method (sec.~\ref{ssub:variational_dropout}).
-Besides that we tried \texttt{raw} or \texttt{fft} input features, varied $
+Plots~\ref{fig:mnist-like__trade-off} depict samples from the performance-compression curve
+on KMNIST and EMNIST-Letters datasets for the studied models and VD compression method
+(sec.~\ref{ssub:variational_dropout}). Besides that we try \texttt{raw} or \texttt{fft}
+input features, vary $
   C \in \{\tfrac3{2^{k+1}}\colon k=1..16\}
-$, and repeated the experiment $5$ times.
-
-We make a couple of observations based on these results. First, Fourier features appear to
-perform on par with raw colour channel data in the convolutional networks across most
+$, and repeat the experiment $5$ times.
+
+Shaded horizontal bands reflect the spread of the performance of the uncompressed network
+after ``dense'' stage. Each point represents a precision-compression value attained by the
+network after ``fine-tune'' stage. The end of each point's tail represents the performance
+gain or loss from running the ``fine-tune'' stage.
+%
+We make a couple of observations based on the results of these plots. First, \texttt{fft}
+features perform on par with raw colour channel data in the convolutional networks across most
 compression rates, but require high compression rate to make wide shallow dense network work
-as well. The upward trend in manifests itself in MNIST and Fashion MNIST experiments as well
+as well. The upward trend manifests itself in MNIST and Fashion MNIST experiments as well
 (see appendix~\ref{sub:other_mnist_like_datasets}). Finally, overall $\cplx$ variational
-dropout methods seems to compress network adequately well, without much loss in performance.
+dropout methods seem to compress networks adequately well without much loss in performance.
 
 % a couple of plots from MNIST and Fashion-MNIST
-\begin{figure}[!h]
+\begin{figure}[!t]
   \centering
@@
     % \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__fashionmnist__fft__-0.5.pdf}
-    \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__kmnist__fft__-0.5.pdf}
+    \includegraphics[width=0.8\columnwidth]{../assets/figure__mnist-like__trade-off/legacy__VD__kmnist__fft__-0.5.pdf}
     % \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/VD__kmnist__fft__-0.5.pdf}
@@
     % \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__fashionmnist__raw__-0.5.pdf}
-    \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__kmnist__raw__-0.5.pdf}
+    \includegraphics[width=0.8\columnwidth]{../assets/figure__mnist-like__trade-off/legacy__VD__kmnist__raw__-0.5.pdf}
     % \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/VD__kmnist__raw__-0.5.pdf}
-  \end{subfigure}
-  \caption{%
-    The compression-accuracy trade-off on KMNIST dataset.
-    (\textit{top}) \texttt{fft} features, (\textit{bottom}) \texttt{raw} features.
-  }
-  \label{fig:mnist-like__trade-off__kmnist}
-\end{figure}
-
-\begin{figure}[!h]
-  \centering
+  \end{subfigure} \\%
   \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
@@
     % \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__mnist__fft__-0.5.pdf}
-    \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__emnist_letters__fft__-0.5.pdf}
+    \includegraphics[width=0.8\columnwidth]{../assets/figure__mnist-like__trade-off/legacy__VD__emnist_letters__fft__-0.5.pdf}
     % \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/ARD__kmnist__fft__-0.5.pdf}
@@
     % \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__mnist__raw__-0.5.pdf}
-    \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__emnist_letters__raw__-0.5.pdf}
+    \includegraphics[width=0.8\columnwidth]{../assets/figure__mnist-like__trade-off/legacy__VD__emnist_letters__raw__-0.5.pdf}
     % \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/VD__emnist_letters__raw__-0.5.pdf}
@@
   \caption{%
-    The compression-accuracy trade-off on the letters part of the Extended MNIST dataset.
+    The compression-accuracy trade-off on KMNIST and the letters of the Extended MNIST datasets.
     (\textit{top}) \texttt{fft} features, (\textit{bottom}) \texttt{raw} features.
   }
-  \label{fig:mnist-like__trade-off__emnist}
+  \label{fig:mnist-like__trade-off}
 \end{figure}
@@
 that we study VGG16 model \citep{simonyan_very_2015} and its $\cplx$-counterpart and
-replicate each experiment only twice. Each network is trained stagewise for $20$, $40$,
+replicate each experiment only twice.
+%
+% describe the VGG16 model and its cplx-valued modification
+The $\cplx$-VGG16 model is architecturally identical to VGG16, except for all layers being
+replaced by their $\cplx$-valued versions. To maintain comparability, we halve the filter
+sizes of $\cplx$ model \citep{monning_evaluation_2018}.
+%
+Each network is trained stagewise for $20$, $40$,
 and $20$ epochs on the full training split of $50k$ colour $32\times32$ images. We use
@@
 respectively.
-
-% describe the VGG16 model and its cplx-valued modification
-The $\cplx$-VGG16 model is architecturally identical to VGG16, except for all layers being
-replaced by their $\cplx$-valued versions. To maintain comparability, we halve the filter
-sizes of $\cplx$ model \citep{monning_evaluation_2018}.
 
@@
 % compare compressed cplx-vgg against real-vgg
-\begin{figure}[!h]
+\begin{figure}[!t]
   \centering
@@
     \centering
-    \includegraphics[width=\linewidth]{../assets/figure__cifar__trade-off/legacy__augmentedcifar10__raw__-0.5.pdf}
+    \includegraphics[width=\columnwidth]{../assets/figure__cifar__trade-off/legacy__augmentedcifar10__raw__-0.5.pdf}
   \end{subfigure}
@@
 
+% subsection cifar10_100 (end)
+
+\subsection{musicNet} % (fold)
+\label{sub:musicnet}
+
+% describe musicnet as in Trabelsi et al. (2017) also get some hints from thickstun_learning_2017
+MusicNet \citep{thickstun_learning_2017} is an annotated audio dataset, consisting of $330$
+musical compositions. Folowing \citet{trabelsi_deep_2017}, we use it for automatic music
+transcription task and study the $1d$ VGG-like $\cplx$-convent proposed therein. Similarly to
+the study, we downsample the audio from 44.1kHz to 11kHz, retain only $84$ out of $128$ labels,
+and hold-out the same validation and test splits. During each training epoch we sample $1000$
+mini-batches of the remaining $321$ compositions, with each mini-batch comprised of a random
+full window of $4096$ samples picked from each waveform and transformed from $\real$ to
+$\cplx$ with $1d$ FFT. Annotation labels are taken at the mid-point of the window.
+
+Preliminary experiments with the model without sparsification have shown that early stopping
+almost always terminates the training process within the first $10-20$ epochs with the validation
+performance peaking at $10-15$ epochs, much sooner than $200$ epochs used by \citet{trabelsi_deep_2017}.
+Thus we adopt shorter lasting stages: $12$, $32$ and $50$ epochs, which essentially turn the
+``dense'' stage into pretraining. Early stopping is used only during the ``fine-tune'' stage.
+To keep the learning rate schedule consistent, we allow the base rate of $10^{-3}$ to be scaled
+after $5$, $10$, and $20$-th epoch by $\tfrac1{10}$, $\tfrac1{20}$ and $\tfrac1{100}$, respectively.
+Other key deviations from the set-up used by \citet{trabelsi_deep_2017} include: shifting lower
+frequencies to the centre of the window to maintain locality after applying the FFT
+(sec.~\ref{sub:mnist_like_datasets}), and clipping $\ell_2$ norm of the gradients to $0.05$.
+
 \begin{figure}[!h]
@@
     \centering
-    \includegraphics[width=\linewidth]{../assets/figure__musicnet__trade-off/paper__musicnetram__fft__-0.5.pdf}
+    \includegraphics[width=\columnwidth]{../assets/figure__musicnet__trade-off/paper__musicnetram__fft__-0.5.pdf}
   \end{subfigure}
@@
 
-% subsection cifar10_100 (end)
-
-\subsection{musicNet} % (fold)
-\label{sub:musicnet}
-
-% describe musicnet as in Trabelsi et al. (2017) also get some hints from thickstun_learning_2017
-MusicNet \citep{thickstun_learning_2017} is an annotated audio dataset, consisting of $330$
-compositions from the public domain. Folowing \citet{trabelsi_deep_2017}, we use this
-dataset for automatic music transcription task and study the $1d$ VGG-like $\cplx$-convent
-proposed therein. Similarly to this study, we downsample the audio from 44.1kHz to 11kHz,
-retaining only $84$ out of $128$ labels, and hold-out the same validation and test splits.
-During each training epoch we sample $1000$ mini-batches of the remaining $321$ compositions,
-each mini-batch comprised of a random full window of $4096$ samples picked from each waveform
-and transformed from $\real$ to $\cplx$ with $1d$ FFT. Annotation labels are taken at the
-mid-point of the window.
-
-Preliminary experiments with the model without sparsification have shown that early stopping
-almost always terminates the training process within the first $10-20$ epochs, and that the
-validation performance peakeing at about $10-15$ epochs, much sooner than $200$ epochs used by
-\citet{trabelsi_deep_2017}. Thus we adopt shorter lasting stages: $12$, $32$ and $50$ epochs,
-which essentially turns the ``dense'' stage into pretraining step. Early stopping, tracking
-the validation split performance, is used only during the ``fine-tune'' stage. To keep the
-learning rate schedule synchronised with such abbreviated training, we allow the base rate
-of $10^{-3}$ to be scaled after $5$, $10$, and $20$-th epoch by $\tfrac1{10}$, $\tfrac1{20}$
-and $\tfrac1{100}$, respectively. Other key deviations from the set-up used by \citet{trabelsi_deep_2017}
-include: shifting lower frequencies to the centre of the window to maintain locality after
-applying FFT (sec.~\ref{sub:mnist_like_datasets}), and clipping $\ell_2$ norm of parameters'
-gradients to $0.05$.
-
-In each experiment we varied the method and the value $C$, while keeping $\tau$ at $-\tfrac12$.
-Each full experiment is replicated five times to take into account random effects from network
-initialization before ``dense'', randomness of the mini-batch sequence during SGD, and
-stochasticity of intermediate layers on forward pass at ``sparsify'' stage.
+In each experiment we vary the method and the value $C$, while keeping $\tau$ at $-\tfrac12$.
+Every experiment is replicated five times to take into account the random effects from
+initialization, batch sequence during SGD, and stochasticity of intermediate layers on
+forward pass at ``sparsify'' stage.
 
@@
 halve the spatial size of the first $1d$ convolution kernel from $6$ to $3$ (denoted by
-suffix \textit{k}$3$). The motivation is to test if the performance handicap introduced be
-the forced compression of the most upstream layer can be alleviated through non-uniform
-compression, induced by variational dropout. We test only VD (sec.~\ref{ssub:variational_dropout})
-method in this sub-experiment, since prior results have not demonstrated significant difference
-in performance-compression trade-off between VD and ARD (sec.~\ref{ssub:empirical_bayes}).
-
-Shaded horizontal bands represent the min-max spread of the performance of the uncompressed
-network upon termination of ``dense'' stage. Each point represents a precision-compression
-value attained by a network after ``fine-tune'' stage. The end of the tail of each point
-represents the performance gain or loss from the ``fine-tune'' stage itself.
-%
-For compression levels lower than $50$, the final stage overfits the network, since
-it sill remains overparameterized. For rates higher than $\approx 100$ the ``fine-tune''
-stage serves its purpose, essentially, due regularization effects if high sparsity. There
-is evidence in favour of achievability of the SOTA average precision of \citet{trabelsi_deep_2017}
-within the $50$-$100$ compression region with $\cplx$-valued variational dropout with ARD
-prior (sec.~\ref{ssub:empirical_bayes}).
+suffix \textit{k}$3$). The motivation is to test if the handicap introduced by the forced
+compression of the most upstream layer can be alleviated through non-uniform compression,
+induced by variational dropout. We test only VD (sec.~\ref{ssub:variational_dropout}) this
+sub-experiment, since prior results have not demonstrated significant superiority of one method
+over another (sec.~\ref{ssub:empirical_bayes}).
+
+For compression levels lower than $50$, the final stage overfits the network, since it still
+remains overparameterized. For the rates higher than $\approx 100$ the ``fine-tune'' stage
+serves its purpose, essentially, due regularizing effects of high sparsity. There is evidence
+in favour of achievability of the SOTA average precision of \citet{trabelsi_deep_2017} within
+the $50$-$100$ compression region with $\cplx$-valued variational dropout with ARD prior
+(sec.~\ref{ssub:empirical_bayes}).
 
@@
 Despite having higher arithmetic complexity, complex-valued models provide built-in
-joint amplitude-phase transformations and regularization \citep{hirose_complex-valued_2009}
-and enjoy superior performance on naturally $\cplx$-valued datasets \citep{tarver_design_2019},
-that occur in ultra high-frequency radio communications and audio signal processing. In this
-study we address the issue of excessive the arithmetic complexity of complex-valued networks
-by extending the existing Bayesian compression techniques by \citet{kingma_variational_2015},
+amplitude-phase transformations and regularization \citep{hirose_complex-valued_2009}
+and enjoy superior performance on naturally $\cplx$-valued datasets \citep{tarver_design_2019}.
+In this study we address the issue of excessive arithmetic complexity of complex-valued
+networks by extending the existing Bayesian compression techniques by \citet{kingma_variational_2015},
 \citet{molchanov_variational_2017} and \citet{kharitonov_variational_2018} to $\cplx$-valued
-model parameters. To this end we have conducted a large scale numerical study of such networks
-to assess the performance-compression rate trade-off and have achieved performance, comparable
-to SOTA on the MusicNet dataset.
+parameters. To this end we have conducted a large numerical study of such networks to assess
+the performance-compression rate trade-off and have achieved performance comparable to
+the state-of-the-art in $\cplx$-valued networks on the MusicNet dataset.
 
@@
   \centering
-  \includegraphics[width=\linewidth]{../notebooks/assets/grad_log.pdf}
+  \includegraphics[width=\linewidth]{../assets/grad_log.pdf}
   \caption{$\tfrac{d f(\alpha)}{d \log{\alpha}}$ of the fit proposed by

### 2020-03-16 paper/paper.tex
scattered lagunage fixes

@@
 %
-For a generous $\delta = 50\%$ tolerance all values of $\log \alpha$ below $-2.5$ yield
+For a generous tolerance $\delta = 50\%$ all values of $\log \alpha$ below $-2.5$ yield
 at least $90\%$ chance of a non-zero $\real$/$\cplx$ parameter. We pick $\tau = -\tfrac12$
@@
 The $\cplx$-VGG16 model is architecturally identical to VGG16, except for all layers being
-replaced by their $\cplx$-valued versions. To maintain comparability, we halve the filter
-sizes of $\cplx$ model \citep{monning_evaluation_2018}.
+replaced by their $\cplx$-valued versions. We halve the sizes of intermediate layers in
+$\cplx$ model to assess comparability \citep{monning_evaluation_2018}.
 %
@@
 in comparison with its $\real$ counterpart, although in MNIST-like experiment $\cplx$-valued
-network with the same inner feature dimensions performed on close to $\real$-valued, which
-is half the size of the former.
+network with the same inner feature dimensions demonstrates trade-off very similar to
+$\real$-network, which has half the number of real parameters than the former.
 
@@
 MusicNet \citep{thickstun_learning_2017} is an annotated audio dataset, consisting of $330$
-musical compositions. Folowing \citet{trabelsi_deep_2017}, we use it for automatic music
+musical compositions. Folowing \citet{trabelsi_deep_2017}, we use it in automatic music
 transcription task and study the $1d$ VGG-like $\cplx$-convent proposed therein. Similarly to

### 2020-03-16 paper/paper.tex
appendix -> paper

--- 2020-03-16 paper/paper.tex
@@
-\documentclass[a4paper,10pt]{article}
+\documentclass[a4paper]{extarticle}
 
-\usepackage[T1]{fontenc}
+% \usepackage[T1]{fontenc}
 \usepackage[utf8]{inputenc}
@@
 \usepackage{natbib}
-% \setcitestyle{authoryear,open={((},close={))}}
 
-\usepackage{amsmath}
-\usepackage{amssymb}
+\usepackage{geometry}
 
-\usepackage{xcolor}
-\usepackage{graphicx}
+\usepackage{subcaption}
+\usepackage[mathcal]{euscript}
+
+\usepackage{graphicx, url}
+
+\usepackage{amsmath, amsfonts, amssymb, amsthm}
+\usepackage{mathptmx}
+
 \usepackage{grffile}
 
-\usepackage{subcaption}
+\graphicspath{{../assets/}}
 
-\usepackage{booktabs}
-
-\title{Bayesian Sparsification of Deep $\cplx$-valued networks}
+\title{Bayesian Sparsification of Deep $\cplx$-valued networks -- Extended appendix}
 \author{Ivan Nazarov, and Evgeny Burnaev}
@@
 
-%% drafting macro
-\newcommand{\important}[1]{\textbf{\!\colorbox{red}{#1}\!}}
-\newcommand{\attn}[2]{\textbf{\color{red} #2~\textsuperscript{\textit{[#1]}}}}
-\newcommand{\verify}[1]{\textit{\!\colorbox{red}{#1}\!}}
-\newcommand{\rewrite}[1]{\attn{rewrite}{#1}}
-\newcommand{\todo}[1]{{\color{blue} [TODO]} \important{#1}}
-
-%% red-highlight missing citations
-\usepackage{etoolbox}
-\makeatletter
-\patchcmd{\@citex}{\bfseries ?}{\colorbox{red}{\bfseries ?}}{}{}
-\makeatother
-
 \begin{document}
 \maketitle
+\tableofcontents
+\listoffigures
+\clearpage
 
-\begin{abstract}
-With continual miniaturization ever more applications of deep learning can be found
-in embedded systems, where it is common to encounter data with natural complex domain
-representation. To this end we extend Variational Dropout to complex-valued neural
-networks. We verify the proposed Bayesian technique and assess the performance-compression
-trade-off by conducting a large-scale numerical study of $\cplx$-valued networks on
-two tasks: image recognition on MNIST-like and CIFAR10 datasets and music transcription
-on MusicNet. We reliably replicate the state-of-the-art result by \citet{trabelsi_deep_2017}
-for $\cplx$-valued networks on MusicNet with $50-100\times$ compression rate.
-\end{abstract}
+\section{MNIST-like experiments} % (fold)
+\label{sec:mnist_like_experiments}
 
-\section{Introduction} % (fold)
-\label{sec:introduction}
+To supplement the results, reported in the main text (figures \ref{fig:paper__mnist-like__trade-off__VD__fft}
+and \ref{fig:paper__mnist-like__trade-off__VD__raw}), we conduct additional experiments
+with the same basic set-up, but over a finer grid of KL-divergence term coefficients.
+%
+These experiments lend further evidence in support of the conclusions, drawn in the main
+paper, namely, that the $\cplx$-valued extension of the $\real$-valued variational dropout
+can offer significant compression levels without much loss in performance. At the same
+time, the test performance of both $\real$ and $\cplx$ compressed networks benefits from
+an extra fine-tuning stage, during which sparsity masks are fixed.
 
-% general intro text with motivation
-Deep neural networks are an integral part of machine learning and data science toolset
-for practical data-driven problem solving. With continual miniaturization ever more
-applications can be found in embedded systems. Common embedded applications include
-on-device image recognition and signal processing. Despite recent advances in generalization
-and optimization theory specific to deep networks, deploying in actual embedded hardware
-remains a challenge due to storage, real-time throughput, and arithmetic (computational)
-complexity restrictions \citep{he_amc:_2018}. Therefore, compression methods for achieving
-high model sparsity and numerical efficiency without losing much in performance are
-especially relevant.
-% Solving the storage and artihmetic constraints encourages development of model compression
-% and sparsification methods, that focus on favourable trade-off between performance and size.
+One intriguing observation, is that on MNIST-like images the dense network, taking Fourier
+features on input, exhibits gradually improving test-split performance. This is in stark
+contrast to raw image input, where the performance stays at one level in the small compression
+regime, and then gradually decays at high compression levels. Noteworthy is the presence
+of a trough in the pre fine-tuning stage performance in the small compression regime on figures
+\ref{fig:appendix__mnist-like__trade-off__ARD__raw},
+\ref{fig:appendix__mnist-like__trade-off__VD__raw},
+\ref{fig:appendix__cmp__mnist-like__trade-off__ARD__raw},
+and \ref{fig:appendix__cmp__mnist-like__trade-off__VD__raw}, which then slowly disappears
+as compression increases.
 
-Inherently complex-valued nature of data in signal processing, specifically, acoustic or radio
-frequency signal analysis, has been the key driver behind the adoption of $\cplx$-networks.
+The following scatter plots depict the samples from the compression-performance trade-off
+curve of simple networks studied in the experiments on the MNIST-like datasets. Transparent
+horizontal bands on each plot represent min-max performance spread of an uncompressed
+network on the test split. The points illustrate the final trade-off of the compressed
+networks after fine-tuning, while their tails show the performance gain or loss due to
+the fine-tuning.
+
+We recap the set-up of each additional experiment on MNIST-like datasets:
+\begin{itemize}
+  \item staged training, with weight and optimizer state transfer
+  \item $40$, $75$, and $40$ epochs for ``dense'', ``sparsify'', and ``fine-tune'' stagers, respectively
+  \item ADAM optimizer with learning rate $10^{-3}$ before the $10$-th, and $10^{-4}$
+  afterwards
+  \item global $\ell_2$-norm gradient clipping set at $\tfrac12$
+  \item training batches of size $128$ from a fixed randomly subset ($10^4$ images) of the training split
+  \item the multiplier of the Kullback-Leibler term in ELBO varies over $
+    C \in \{
+      \tfrac32 2^{-\tfrac{k}2} \colon k=2, \cdots, 38
+    \}
+  $
+  \item the sparsification threshold $\tau$ is set to $-\tfrac12$
+\end{itemize}
+Each experiment has been performed $5$ times to obtain a small sample of performance-compression
+values for each setting of $C$. By reevaluating each setting several times we can account
+for randomness in initialization of the uncompressed network at ``dense'', stochasticity of
+variational dropout layers, randomness of batch sequences during SDG, and non-determinism
+of computations on GPUs.
+
+Each figure shows the compression-accuracy trade-off of a particular method and input features
+for \textit{SimpleConvModel} and \textit{TwoLayerDenseModel} models for all four of the studied
+datasets (described in the main text): \emph{top-left} EMNIST-Letters, \emph{top-right} KMNIST,
+\emph{bottom-left} Fashion MNIST, and \emph{bottom-right} MNIST.
 %
-\citet{hirose_complex-valued_2009} argues that the key merit of $\cplx$-valued neural
-networks is simultaneous phase rotation and amplitude adjustment, intrinsic to multiplication
-in $\cplx$ field. Despite inherently higher arithmetic complexity, which stems from up to four
-floating point operations per single $\cplx$ multiplication \citep{monning_evaluation_2018}
-$\cplx$-arithmetic reduces ineffective degrees of freedom in comparison with an analogous
-double-dimensional $\real$-valued network. \citet{hirose_complex-valued_2009} lists numerous
-applications related to acoustic and radio signal processing and demonstrates superiority of
-$\cplx$-networks in the task of shallow landmine detection using ground penetrating radar
-imaging. More recently they have been applied to music transcription and speech recognition
-\citep{trabelsi_deep_2017}. \citet{arjovsky_unitary_2016} propose $\cplx$-valued unitary-RNNs
-to deal with exploding~/~vanishing gradients and apply the recurrent models to long-term
-dependence prediction tasks. \citet{wisdom_full-capacity_2016} expand on their work by optimizing
-recurrent weights on the $\cplx^{n \times n}$ Stiefel manifold. And \citet{wolter_complex_2018}
-investigate different $\cplx$-valued gating mechanisms for unitary-RNNs and conduct experiments
-on human motion prediction and music transcription. \citet{yang_complex_2019} develop complex
-transformer, with $\cplx$-attention and complex encoder-decoder, and apply it to music
-transcription and wireless signal classification.
+Figures \ref{fig:appendix__mnist-like__trade-off__ARD__fft}, \ref{fig:appendix__mnist-like__trade-off__VD__fft},
+\ref{fig:appendix__mnist-like__trade-off__ARD__raw}, and \ref{fig:appendix__mnist-like__trade-off__VD__raw}
+present $\real$ and $\cplx$ models with \emph{the same architecture}. We also report the
+trade-off comparison, when the argument by \citet{monning_evaluation_2018} for higher intrinsic
+capacity of $\cplx$-valued networks has been taken into account.
+%
+We compare $\real$ networks against $\tfrac12 \cplx$ with half the number of parameters
+for raw input features on figures \ref{fig:appendix__cmp__mnist-like__trade-off__ARD__raw},
+and \ref{fig:appendix__cmp__mnist-like__trade-off__VD__raw}, and $2 \real$ with
+double the number of parameters against $\cplx$ for Fourier input features on figures
+\ref{fig:appendix__cmp__mnist-like__trade-off__ARD__fft} and
+\ref{fig:appendix__cmp__mnist-like__trade-off__VD__fft}.
 
-% complex-valued distributions \citep{pav_moments_2015,taubock_complex-valued_2012},
-% and \citep{karseras_caution:_2014}
+The following observations can be made from the conducted experiment:
+\begin{itemize}
+  \item $\cplx$-valued networks do not have as much spare capacity as $2 \real$ due to
+  constants imposed by multiplication in $\cplx$ numbers (\ref{fig:appendix__cmp__mnist-like__trade-off__ARD__raw},
+  \ref{fig:appendix__cmp__mnist-like__trade-off__VD__raw})
+  \item Variational Dropout and Automatic Relevance Determination offer similar compression-performance
+  trade-off, with negligibly lower compression by the latter (both $\real$ and $\cplx$ versions,
+  e.g. figures \ref{fig:appendix__mnist-like__trade-off__ARD__raw} and \ref{fig:appendix__mnist-like__trade-off__VD__raw})
+  \item smaller networks tend to be less compressible (figures \ref{fig:appendix__cmp__mnist-like__trade-off__ARD__fft},
+  \ref{fig:appendix__cmp__mnist-like__trade-off__VD__fft})
+\end{itemize}
 
-% motivation and other methods
-However, in spite of relative success of $\cplx$-valued networks, compression methods tailored
-to $\cplx$-domain remain a niche field of research.
-%
-Computational efficiency improvement and model compression methods such as quantization
-\citep{uhlich_differentiable_2019}, integer-based arithmetic \citep{lin_fixed_2016,chen_fxpnet_2017},
-and knowledge distillation \citep{hinton_distilling_2015} appear to be directly applicable
-to $\cplx$-valued networks.
-%
-Certain model sparsification methods, e.g. sparsity inducing regularizers, and magnitude
-pruning \citep{zuo_compression_2019}, which reactivates zeroed parameters based on gradients,
-can be adapted directly to $\cplx$-valued models. Other methods require additional considerations.
-% the more explicitly zero parameters there is, the less computations is needed.
-
-% on dropout
-Dropout \citep{hinton_improving_2012} prevents overfitting by injecting multiplicative
-binary noise into layer's weights, which breaks up co-adaptations that could occur
-during training. \citet{wang_fast_2013} argue that the overall effect of binary dropout
-on the intermediate outputs via the Central Limit Theorem can be approximated by a Gaussian
-with weight-input dependent mean and variance. \citet{srivastava_dropout_2014} propose
-using independent $\mathcal{N}(1,1)$ noise, arguing that higher entropy of a Gaussian has
-better regularizing effect. In multitask learning \citet{cheung_superposition_2019}
-have shown the possibility of storing task-specific parameters in non-destructive superposition
-within a single network. Their argument implies that if the single task setting is viewed
-as replicated multitask learning, then by sampling uncorrelated weight masks dropout acts
-as a superposition method, which better utilizes the learning capacity of the network.
-% many identical copies of the same task; \cite[Appendix A.1]{cheung_superposition_2019}
-% (fast dropout gauss-approx) wang-manning.tex
-% (gauss dropout) srivastava-et-al.tex
-
-% segue into bayesian inference
-Bayesian inference is a very rich field with a large body of research and techniques that
-enable practical quantification of predictive, parameter, or model uncertainty and its 
-propagation into solutions of the problems of interest.
-%
-Dropout resembles averaging models with shared parameters: each model is weighted equally
-since masks are randomly sampled, unlike Bayesian model averaging, which weighs according to
-the posterior distribution. \citet{kingma_variational_2015} specifically consider dropout
-as a Bayesian Inference technique: a principled framework of reasoning about uncertainty,
-which updates prior beliefs in accordance with the likelihood of empirical observations
-into posterior belief. Bayesian methods with suitable modelling and prior assumptions, such
-as Variational Dropout, can be used towards model sparsification
-\citep{kingma_variational_2015,molchanov_variational_2017,kharitonov_variational_2018}.
-
-% (sparsity tech large-scale models) gale-elsen-hooker.tex
-\citet{gale_state_2019} compare variational dropout \citep{kingma_variational_2015},
-magnitude pruning, and $\ell_0$ regularization \citep{louizos_learning_2017} on large-scale
-models. The latter is a probabilistic regularization method, which penalizes the expected
-number of non-zero entries in $[0, 1]$-valued stochastic parameter masks with learnable
-hard-concrete distribution with an atom at $0$ \citep{maddison_concrete_2016,jang_categorical_2017}.
-Their results suggest that although variational dropout may achieve good accuracy-sparsity balance
-and outperform pruning and $\ell_0$ on the studied architectures, pruning is preferable for
-its simplicity and speed. They also observe that, despite dropout showing more variable
-performance than magnitude pruning, it induces non-uniform sparsity throughout the model,
-which has been shown by \citet{he_amc:_2018} to be essential for superior compression.
-% Magnitude pruning induces user-specified sparsity distributions.
-%
-% L0 and dropout work in the low-to-mid sparsity range, variational dropout consistently
-% ranked behind L0 on Transformer, and was bested by magnitude pruning for sparsity
-% levels of 80\% and up. Variational dropout consistently produces models on-par or better
-% than magnitude pruning on ResNet-50, and l0 fails to produce sparse models at all.
-%
-
-% our contribution
-Inspired by variational and stochastic sparsification techniques we extend Bayesian dropout
-for $\cplx$-valued networks. We assess the performance-compression trade-off of the proposed
-Bayesian technique by conducting a large-scale numerical study of $\cplx$-valued networks
-on two tasks: image recognition on MNIST-like and CIFAR10 datasets and music transcription
-on MusicNet \citep{thickstun_learning_2017}. We reproduce the state-of-the-art result by
-\citet{trabelsi_deep_2017} for $\cplx$-valued networks on the latter with $\approx 5\%$
-of remaining non-zero parameters.
-
-The paper is structured as follows. In sec.~\ref{sec:bayesian_dropout} we review Bayesian
-dropout techniques, and in sec.~\ref{sec:c_valued_networks} we provide a brief summary of
-the inner working of complex-valued networks as functions of complex argument. The main
-contribution of this study is presented in sec.~\ref{sec:dropout_for_c_valued_layers},
-where we consider different variational approximations and priors, outline the tricks
-and derive expressions for the divergence term. In sec.~\ref{sec:experiments} we evaluate
-the sparsification rate, compare the resulting performance of various $\cplx$-networks
-proposed in prior work, and discuss the outcomes.
-
-% section introduction (end)
-
-\section{Bayesian Dropout} % (fold)
-\label{sec:bayesian_dropout}
-
-In general, the core of Bayesian Inference can be summarized as follows: given a prior
-distribution $\pi(m)$ on models (hypotheses) $\mathcal{M}$, utilize the empirical evidence
-$D$ to update the assumptions by considering the likelihood of the observations under each
-$m \in \mathcal{M}$. Models are represented by a parametric family indexed by parameters
-$\omega \in \Omega$ and each $m_\omega(\cdot)$ specifies the conditional distribution of
-the data $
-  D = (z_i)_{i=1}^N
-$. The posterior distribution $p(\omega \mid D)$, derived using the Bayes rule $
-  p(m \mid D) = \tfrac{p(D \mid m) \pi(m)}{p(D)}
-$ with $
-  p(D) = \mathbb{E}_{\pi(m)} p(D \mid m)
-$, provides useful information about yet unobserved data and model parameters, e.g
-classification uncertainty, predictive statistics, and parameter relevance.
-
-The posterior distribution itself is intractable, save for the relatively simple cases, and
-therefore exact inference is traded for tractability and scalability offered by Variational
-Inference. Instead of deriving $p(\omega \mid D)$ using the Bayes rule, this approach recasts
-posterior inference into variational optimization problem: finding $q$ that is close to
-$p(\omega \mid D)$ in terms of a proximity score $\rho$
-\begin{equation}  \label{eq:variational-progam}
-  q_*
-    \in \arg \min_{\theta} \rho\bigl(
-      q_\theta(\omega), p(\omega \mid D)
-    \bigr)
-    \,,
-\end{equation}
-over a tractable parametric family of distributions on the parameter space $
-  \mathcal{Q} = \{Q_\theta(d\omega) \colon \theta \in \Theta\}
-$, $\theta$ -- generic variational parameter. The class $\mathcal{Q}$ is picked so that
-its members have tractable densities $
-  q_\theta(\omega) d\omega
-$, can be sampled from and have either tractable $\log$-derivatives $
-  \omega \mapsto \nabla_\theta \log q_\theta(\omega)
-$ \citep{williams_simple_1992} or can be represented as differentiable transformations
-of non-parametric noise \citep{kingma_auto-encoding_2014,figurnov_implicit_2019}.
-% (reparameterization trick, pathwise gradieent) $q_{\theta}(d\omega)$ is a push-forward
-% of $p(d\varepsilon)$ by a differentiable map $g(\varepsilon; \theta)$.
-% % http://stillbreeze.github.io/REINFORCE-vs-Reparameterization-trick/#fn:1
-%
-The natural choice for $\rho$ is Kullback-Leibler divergence of density $q$ from $p$,
-\begin{equation}  \label{eq:kl-div-def}
-  KL(q \| p)
-    % = \int \frac{dQ}{dP} \log{\frac{dQ}{dP}} P(d\omega)
-    % = \int \frac{q(\omega)}{p(\omega)} \log{\frac{q(\omega)}{p(\omega)}} p(\omega) d\omega
-    % = \mathbb{E}_{\omega \sim q}
-    %   \log\frac{q(\omega)}{p(\omega)}
-    = \mathbb{E}_{\omega \sim q}
-      \log{q(\omega)}
-    - \mathbb{E}_{\omega \sim q}
-      \log{p(\omega)}
-    \,,
-\end{equation}
-% and, despite it not being a metric and requiring distributions with nested support,
-the main reason being that it satisfies the following identity for well-behaved densities:
-% $(q, p, \pi)$
-\begin{multline}  \label{eq:kl-div-master}
-  % \log p(D)
-    % = \mathbb{E}_{q(\omega)} \log \frac{p(D, \omega)}{p(\omega \mid D)}
-    % = \mathbb{E}_{q(\omega)} \log \frac{
-    %   p(D \mid \omega) \pi(\omega)
-    % }{p(\omega \mid D)}
-    % = \mathbb{E}_{q(\omega)} \log \frac{
-    %   p(D \mid \omega) \pi(\omega)
-    % }{q(\omega)}
-    % + \mathbb{E}_{q(\omega)} \log \frac{q(\omega)}{p(\omega \mid D)}
-    % - \mathbb{E}_{q(\omega)} \log \frac{q(\omega)}{\pi(\omega)}
-    % = \mathbb{E}_{q(\omega)} \log{p(D \mid \omega)}
-    % + \mathbb{E}_{q(\omega)} \log \frac{q(\omega)}{p(\omega \mid D)}
-  \log p(D)
-    - KL(q \| p(\omega \mid D))
-    \\ = \mathbb{E}_{q(\omega)} \log{p(D \mid \omega)}
-    - KL(q \| \pi)
-    \,.
-\end{multline}
-This identity yields an equivalent problem for \eqref{eq:variational-progam}:
-maximizing the \textit{evidence lower bound} (ELBO)
-\begin{equation}  \label{eq:elbo_general}
-  \mathcal{L}(\theta; \phi, \lambda)
-    = - KL(q_{\theta} \| \pi_{\lambda})
-      + \mathbb{E}_{\omega \sim q_{\theta}}
-        \log p_{\phi}(D \mid \omega)
-      % \mathbb{E}_{\omega \sim q_{\theta}}
-        % \log\frac{q_\theta(\omega)}{\pi_{\lambda}(\omega)}
-  % = \mathbb{E}_{\omega \sim q_{\theta}}
-  %     \log{p_{\phi}(D \mid \omega) \pi_{\lambda}(\omega)}
-  %   + \mathbb{H}(q_{\theta})
-  \,,
-\end{equation}
-where the prior and likelihood are allowed to depend on explicit parameters. The most
-commonly used algorithm to optimize \eqref{eq:elbo_general} is EM-algorithm. Other
-variational objectives are possible, provided $p(\omega \mid D)$ is probed only through
-$\log p(D \mid \omega)$ and $\log \pi(\omega)$ \citep{ranganath_operator_2018}.
-
-\textit{Stochastic Gradient Variational Bayes} (SGVB), proposed by \citet{kingma_auto-encoding_2014},
-is a differentiable unbiased Monte-Carlo estimator of \eqref{eq:elbo_general}, which
-makes it possible to employ stochastic gradient-based optimization methods to solve
-\eqref{eq:variational-progam}. If $
-  \omega \sim q_{\theta}
-$ is equivalent in distribution to $
-  \omega = g(\varepsilon; \theta)
-$ for some non-parametric random variable $
-    \varepsilon \sim p_\varepsilon
-$ and differentiable $
-  g(\varepsilon; \theta)
-$, then the SGVB is
-\begin{equation}  \label{eq:sgvb}
-  \widetilde{\mathcal{L}}(\theta; \phi, \lambda)
-    = - KL(q_{\theta} \| \pi_{\lambda})
-      % + \frac{N}{\lvert B \rvert} \sum_{i\in B}
-        % \log p(z_i \mid \omega_i)b
-      + \frac1{L} \sum_{l=1}^L
-        \log p_{\phi}(D \mid g(\varepsilon_{l}; \theta))
-        % \log p_{\phi}(D \mid \omega_{l})
-        %   \Big\vert_{\omega_{l} = g(\varepsilon_{l}; \theta)}
-      % =
-      % - KL(q_{\theta} \| \pi)
-      % + N \mathbb{E}_{B \sim \{D\}_M \otimes q_\theta^M}
-        % \hat{\mathbb{E}}_{z,\omega \sim B}
-          % \log p(z \mid \omega)
-    \,, 
-\end{equation}
-where $
-  (\varepsilon_{l})_{l=1}^L
-$ is an iid sample from $p_\varepsilon$. Intractable KL-divergence terms can be replaced
-by differentiable unbiased sampling estimators \citep{kingma_auto-encoding_2014}.
-%
-For the purposes of this study, we assume that the observed data is independent, and
-use minibatch version of \eqref{eq:sgvb} with $L=1$:
-\begin{equation}  \label{eq:elbo}
-  \widetilde{\mathcal{L}}(\theta; \phi, \lambda)
-    = - KL(q_{\theta} \| \pi_{\lambda})
-      + \frac{N}{M} \sum_{i=1}^M
-        \log p_{\phi}(z_i \mid g(\varepsilon_i; \theta))
-    \,,
-\end{equation}
-for a random subsample $(z_i)_{i=1}^M$ from $D$ and iid $\varepsilon_i \sim p_\varepsilon$.
-%
-% (DSVI) titsias-lazaro.tex \todo{DSVI} \citep{titsias_doubly_2014}
-
-\subsection{Dropout} % (fold)
-\label{sub:dropout}
-
-With a special family of posterior approximation, variational inference can be used as
-a regularization method and as a model sparsification technique. \citet{kingma_variational_2015}
-consider Dropout \citep{hinton_improving_2012}, DropConnect \citep{wan_regularization_2013},
-and Gaussian dropout \citep{srivastava_dropout_2014,wang_fast_2013} through the lens
-of Bayesian inference methods and propose \textit{Variational Dropout}. They argue that
-the multiplicative noise introduced by these methods induces a distribution equivalent to
-a fully factorized variational posterior of the form $
-  q_\theta(\omega) = \prod_j q_{\theta}(\omega_j)
-$, where $q_{\theta}(\omega_j)$ is $\omega_j = \mu_j \xi_j$ with $
-  \xi_j \sim p_\theta(\xi_j)
-$ iid from some $p_\theta(\xi)$.
-%
-% Binary dropout with rate $p \in (0, 1)$ uses $
-%   p_\xi
-%     = \mathcal{B}\bigl(
-%       \{0, \tfrac1{1-p}\}, 1-p
-%     \bigr)
-% $, whereas in Gaussian dropout $
-%   \xi \sim \mathcal{N}(1, \alpha)
-% $ for $\alpha = \tfrac{p}{1-p}$.
-% This suggests making $\alpha$ a variational parameter
-% and optimizing it in \eqref{eq:elbo_general} with an appropriate penalty term. Thus,
-%
-Variational Dropout assumes fully factorized Gaussian approximate posterior $
-  q_\theta(\omega)
-    = \prod_j \mathcal{N}(\mu_j, \alpha_j \mu_j^2)
-$ and factorized log-uniform prior $\pi(\omega)$ with $
-  \pi(\omega_j) \propto \lvert \omega_j \rvert^{-1}
-$. The divergence term in \eqref{eq:elbo} unravels into a sum of the following
-analytically intractable terms:
-\begin{equation}  \label{eq:improper-kl-div-real}
-  KL(q_\theta \| \pi)
-    \propto
-      \frac12 \mathbb{E}_{\varepsilon \sim \mathcal{N}(0, 1)}
-        \log{\Bigl\lvert \tfrac1{\sqrt{\alpha}} + \varepsilon \Bigr\rvert^2}
-      % \frac12 \mathbb{E}_{\varepsilon \sim \mathcal{N}(0, 1)}
-      %   \log{\bigl\lvert 1 + \sqrt{\alpha} \varepsilon \bigr\rvert^2}
-      % - \frac12 \log{\alpha}
-  \,.
-\end{equation}
-\citet{kingma_variational_2015} approximate this expression by a non-linear polynomial
-regression over $\alpha \in (0, 1)$. \citet{molchanov_variational_2017} refine the
-approximation by using a nonlinear regression based on sigmoid and soft-plus.
-% see p.6 sec 3.4 of kingma_variational_2015
-We independently verify their approximation against Monte-Carlo estimates for $\alpha$
-varying over a fine logarithmic grid and the exact expression for the derivative of
-\eqref{eq:improper-kl-div-real}, which we derive in appendix~\ref{sub:real-chisq-grad}.
-% (!) good for SGVB: gradient-based methods require unbiased gradient estimates
-%
-% (in) it is in poor taste to brag about this begin the first time anyone has derived a
-% derivative of an intractable function.
-
-Being the ratio of the squared mean to the effective variance, $\alpha_j$ regulates the
-relevance of the parameter $\omega_j$ it is associated to. Thus, \citet{molchanov_variational_2017}
-focus on the model sparsification capabilities of Variational Dropout, optimizing $\alpha$
-for each individual parameter. Flexibility in specification of $q_\theta$ enables structured
-dropout with shared $\alpha$ across groups of parameters $\omega$. Another Bayesian dropout
-method, called \textit{Automatic Relevance Determination}, has been developed in \citep{kharitonov_variational_2018}.
-The key difference is that the log-uniform factor $\pi(\omega_{ij})$ is replaced by a proper
-ARD Gaussian prior $
-  \mathcal{N}(0, \tau^{-1}_{ij})
-$ with learnable precision $\tau_{ij} > 0$. This method, known as \textit{Empirical Bayes},
-fits a prior distribution while performing variational inference. Maximizing \eqref{eq:elbo}
-over $\tau$, holding other parameters fixed, yields $
-  \tau^* = {(\mu^2 + \sigma^2)}^{-1}
-$, whence
-\begin{equation}  \label{eq:ard-kl-div-real}
-  KL(q_\theta \| \pi)
-    = \log{\bigl(1 + \tfrac1{\alpha} \bigr)}
-    \,.
-\end{equation}
-
-Another contribution of \citep{kingma_variational_2015} is the analysis of the effects of the
-\textit{local reparameterization trick} on the variance of the gradient of \eqref{eq:elbo}.
-This trick, proposed in \citep{wang_fast_2013} to speed up Gaussian dropout, utilizes the
-closure of Gaussians under affine transformations, thereby translating uncertainty from the
-global parameter noise to local noise in intermediate outputs within the network.
-%
-The stochastic output of a linear layer $
-  y = W^\top x + b
-$ with $
-  W \in \mathbb{R}^{n\times m}
-$ and independent $
-  W_{ij} \sim \mathcal{N}(\mu_{ij}, \alpha_{ij} \mu_{ij}^2)
-$ is equivalent in distribution to
-\begin{equation}  \label{eq:r-gauss-trick}
-    y \sim \prod_i \mathcal{N}\Bigl(
-          \sum_j \mu_{ij} x_j + b_i,
-          \sum_j \alpha_{ij} \mu_{ij}^2 x_j^2
-      \Bigr)
-    \,.
-\end{equation}
-%
-\citet{kingma_variational_2015} show, that for the case of fully factorized Gaussian
-posterior approximations, the trick decorrelates ELBO estimates within the minibatch,
-making the gradient estimator $\nabla_\theta \tilde{\mathcal{L}}$ more statistically
-efficient. \citet{molchanov_variational_2017} propose an improvement by introducing
-\textit{additive noise parameterization}. They argue for rejecting the $(\mu, \alpha)$
-parameterization in favour of the equivalent $(\mu, \sigma^2)$, since the latter renders $
-  \nabla_\mu \tilde{\mathcal{L}}
-$ independent from the local output noise, injected by the trick \eqref{eq:r-gauss-trick},
-and further stabilizes gradients in SGVB \eqref{eq:elbo}. The relevance $\alpha$ is
-calculated using the ratio $
-  \tfrac{\sigma^2}{\mu^2}
-$ when needed in the divergence term.
-
-% subsection dropout (end)
-
-% section bayesian_dropout (end)
-
-\section{$\cplx$-valued networks} % (fold)
-\label{sec:c_valued_networks}
-
-In this section we briefly review $\cplx$-valued networks, and their distinction from the
-ordinary $\real$-valued networks.
-
-\citet{trabelsi_deep_2017} outline the building blocks for deep $\cplx$-valued networks
-and describe suitable representation and operations including convolutional and dense layers,
-$\cplx$-valued activations, complex batch-normalization and suitable weight initialization.
-Their approach transforms a complex-valued network into an intricately connected $\real$-valued
-computational graph that respects $\cplx$-arithmetic.
-%
-In particular, natural identification of $\cplx$ and $\real^2$ implies that linear layers $
-  L \colon \cplx^m \to \cplx^n
-$ act upon their inputs as follows:
-\begin{equation}  \label{eq:cplx-lin-op}
-  {(\real^n)}^{2}
-    \to {(\real^m)}^{2}
-    \colon (u, v)
-      \mapsto \Bigl(
-        P u - Q v,
-        P v + Q u
-      \Bigr)
-    \,,
-\end{equation}
-where $
-  P, Q \colon \real^{n} \to \real^{m}
-$ are unique operators such that $L = P + j Q$. A $\cplx$-convolutional layer with kernel
-$W$ can be implemented as two $\real$-convolutions with kernels $\Re{W}$ and $\Im{W}$ using
-\eqref{eq:cplx-lin-op}. Activations include trigonometric functions and representation-dependent
-non-linearities \citep{hirose_complex-valued_2009}: polar (phase-amplitude) $
-  z \mapsto \sigma(\lvert z \rvert) e^{j \arg z}
-$ or planar (real-imaginary) $
-  z \mapsto \sigma(\Re z) + j \sigma(\Im z)
-$ for some $\real$-valued non-linearity $\sigma$, possibly with learnable parameters
-\citep{trabelsi_deep_2017,wolter_complex_2018}.
-
-Complex networks are, in general, non-holomorphic, i.e. not $\cplx$-differentiable, which is
-exacerbated by the loss being real-valued. Indeed a $\cplx$-differentiable real-valued function is
-necessarily trivial by Cauchy-Riemann conditions. This issue is dealt with by employing Wirtinger,
-or $\cplx\real$ calculus, which generalizes holomorphic calculus to non-holomorphic functions
-of $\cplx$-argument \citep{adali_complex-valued_2011,boeddeker_computation_2019}. It satisfies
-the product and chain rules, respects complex conjugation and linearity, but most importantly the
-$\cplx\real$-differential of a function on $\cplx$ coincides with its classical differential as
-a function on $\real^2$. Essentially, it allows straightforward retrofiting of $\cplx$-valued
-networks into existing $\real$ deep learning auto-differentiation frameworks. It was considered
-as a basis for $\cplx$ version of back-propagation by \citet{benvenuto_complex_1992} and
-\citet{trabelsi_deep_2017}, (see appendix~\ref{sub:wirtinger_calculus} for details).
-% \todo{read on holomorphic nets}
-
-% section c_valued_networks (end)
-
-\section{Dropout for $\cplx$-valued layers} % (fold)
-\label{sec:dropout_for_c_valued_layers}
-
-In this section we review the complex Gaussian distribution and discuss its properties. Then
-we introduce factorized dropout posterior for complex-valued parameters and the relevant
-version of the local reparameterization trick. Then we move on to choosing suitable priors
-and then onward to deriving explicit expressions for the divergence penalties in \eqref{eq:elbo}
-in terms of special functions.
-
-\subsection{Complex Gaussians and Local Reparameterization} % (fold)
-\label{sub:c_gauss_and_local_rep}
-
-%notation
-In the following $M^{\top}$ is the matrix transpose, $\conj{M}$ is elementwise complex
-conjugation, and $M^{\hop} = (\conj{M})^\top$ denotes Hermitian conjugate.
-
-A vector $z\in \cplx^m$ has complex Gaussian distribution, $
-  q(z) = \mathcal{N}^{\cplx}_m(\mu, \Gamma, C)
-$ with mean $\mu \in \cplx^m$ and $\cplx^{m\times m}$ covariance and relation matrices
-$\Gamma$ and $C$, respectively, if
-\begin{equation}  \label{eq:cn-paired-real-density}
-  \begin{pmatrix}
-    \Re z \\ \Im z
-  \end{pmatrix}
-    \sim \mathcal{N}_{2 m}\biggl(
-      \Bigl(
-        \begin{smallmatrix}
-          \Re \mu \\ \Im \mu
-        \end{smallmatrix}
-      \Bigr),
-      \tfrac12 \Bigl(
-        \begin{smallmatrix}
-          \Re{(\Gamma + C)} & \Im{(C - \Gamma)} \\
-          \Im{(\Gamma + C)} & \Re{(\Gamma - C)}
-        \end{smallmatrix}
-      \Bigr)
-    \biggr)
-    \,,
-\end{equation}
-provided $\Gamma \succeq 0$, $\Gamma^{\hop} = \Gamma$, $C^\top = C$, and $
-  \conj{\Gamma} \succeq C^{\hop} \Gamma^{-1} C
-$. Matrices $\Gamma$ and $C$ are $
-  \mathbb{E} (z - \mu)(z - \mu)^{\hop}
-$ and $
-  \mathbb{E} (z - \mu)(z - \mu)^{\top}
-$, respectively.
-%
-% $\cplx$-Gaussians are closed under affine transformations: if $y = A z + b$
-% for $A \in \cplx^{n \times m}$ and $b \in \cplx^{n}$, then $
-%   y \sim \mathcal{N}_n^{\cplx}\bigl(
-%       A\mu + b, A \Gamma A^{\hop}, A C A^\top
-%     \bigr)
-% $.
-%
-$\cplx$-Gaussian random variables are closed under affine transformations: for $
-  A \in \cplx^{n \times m}
-$ and $b \in \cplx^{n}$
-\begin{equation}  \label{eq:cn-affine}
-  A z + b \sim \mathcal{N}_n^{\cplx}\bigl(
-      A\mu + b, A \Gamma A^{\hop}, A C A^\top
-    \bigr)
-  \,.
-\end{equation}
-%
-The entropy of a $\cplx$-Gaussian in terms of $\Gamma$ and $C$ is
-\begin{align}  \label{eq:c-gauss-entropy-derivation}
-  \mathbb{H}(q)
-    & = - \mathbb{E}_{z \sim q} \log{q(z)}
-    \notag \\
-    % &
-    % entropy of \mathcal{N}_n(\mu, \Sigma)
-    %   % = \tfrac12 \log \det{(2 \pi \Sigma)}
-    %   % + \tfrac12 \mathop{tr}{(
-    %   %     \Sigma^{-1}
-    %   %     \mathbb{E}_{x\sim q(x)}
-    %   %       (x - \mu) (x - \mu)^\top
-    %   %   )}
-    %   = \tfrac12 \log \det{(2 \pi e \Sigma)}
-    % = \tfrac12 \log \det{\biggl(
-    %   2 \pi e \tfrac12
-    %   \begin{pmatrix}
-    %     \Re{(\Gamma + C)} & - \Im{(\Gamma - C)} \\
-    %     \Im{(\Gamma + C)} &   \Re{(\Gamma - C)}
-    %   \end{pmatrix}
-    % \biggr)}
-    % \notag \\
-    % &
-    % = \begin{bmatrix}
-    %   r_1 + j r_2 \to r_1 \\  % sufficient for C=0 case
-    %   j r_1 + r_2 \to r_2     % j conj of transformation for r1, det x 2
-    % \end{bmatrix}
-    % = \tfrac12 \log \det{\biggl(
-    %   % \det{[I & j I \\ j I & I]} = \det{I} \det{I - jI I^{-1} jI} = \det{2 I}
-    %   % left apply : thus dividing by \sqrt{2}
-    %   \tfrac1{\sqrt{2}} 2 \pi e \tfrac12
-    %   \begin{pmatrix}
-    %     \Gamma + C & j (\Gamma - C) \\
-    %     j (\conj{\Gamma} + \conj{C}) & \conj{\Gamma} - \conj{C}
-    %   \end{pmatrix}
-    % \biggr)}
-      % % Implicitly using the fact that for a non-singular $\Omega$ we have $
-      % %   \det{A}
-      % %     = \tfrac{\det{(\Omega A)}}{\det{\Omega}}
-      % %     = \tfrac{\det{(A \Omega)}}{\det{\Omega}}
-      % % $.
-    % \notag \\
-    % &
-    % = \begin{bmatrix}
-    %   c_1 - j c_2 \to c_1 \\  % -j conj of transformation for c2
-    %   c_2 - j c_1 \to c_2     % sufficient for C=0 case
-    % \end{bmatrix}
-    % = \tfrac12 \log \det{\biggl(
-    %   % \det{[I & - j I \\ - j I & I]} = \det{I} \det{I - (-j)I I^{-1} (-j)I} = \det{2 I}
-    %   % right apply : thus dividing by \sqrt{2}
-    %   \tfrac12 2 \pi e \tfrac12
-    %   \begin{pmatrix}
-    %     2 \Gamma     & - 2 j C \\
-    %     2 j \conj{C} & 2 \conj{\Gamma}
-    %   \end{pmatrix}
-    % \biggr)}
-    % \notag \\
-    % &
-    % = \begin{bmatrix}
-    %   r_2 - j \conj{C} \Gamma^{-1} r_1 \to r_2
-    % \end{bmatrix}
-    % = \tfrac12 \log \det{\biggl(
-    %   % \det{[I & 0 \\ - j \conj{C} \Gamma^{-1} & I]} = \det{I} = 1
-    %   \pi e
-    %   \begin{pmatrix}
-    %     \Gamma & - j C \\
-    %     0 & \conj{\Gamma} - \conj{C} \Gamma^{-1} C
-    %   \end{pmatrix}
-    % \biggr)}
-    % \notag \\
-    &
-    = \tfrac12 \log \det{(\pi e \Gamma)}
-      \det{(\pi e (\conj{\Gamma} - \conj{C} \Gamma^{-1} C))}
-    \,.
-\end{align}
-A $\cplx$-Gaussian vector $z$ is \textit{proper} if $z$ and $\conj{z}$ are uncorrelated, i.e.
-$C = 0$. From \eqref{eq:c-gauss-entropy-derivation} its entropy is
-\begin{equation}  \label{eq:cn-proper-entropy}
-  % determinant commutes with complex conjugation, since it is multilinear
-  \mathbb{H}(q)
-    % = \tfrac12 \log \det{(\pi e \Gamma)} \det{(\pi e (\conj{\Gamma} - \conj{C} \Gamma^{-1} C))}
-    = \tfrac12 \log \det{(\pi e \Gamma)} \det{(\pi e \conj{\Gamma})}
-    % = \tfrac12 \log \det{(\pi e \Gamma)} \conj{\det{(\pi e \Gamma)}}
-    % = \tfrac12 \log \bigl\lvert \det{(\pi e \Gamma)} \bigr\rvert^2
-    = \log \bigl\lvert \det{(\pi e \Gamma)} \bigr\rvert
-    \,.
-    \tag{\ref{eq:c-gauss-entropy-derivation}'}
-\end{equation}
-%
-% The roles of $\Gamma$ and $C$ are more evident in univariate case: here $
-%   \Gamma = \sigma^2 \geq 0
-% $, and $C = \sigma^2 \rho \in \cplx$ with $
-%   \lvert \rho \rvert \leq 1
-% $. $\sigma^2$ determines the ``dispersion'', whereas $\rho$ is determines the
-% ``strength'' and ``direction'' of the linear relation between real and imaginary
-% parts \citep{lapidoth_capacity_2003}.
-% $$
-% \frac{\sigma^2}2
-%   \begin{pmatrix}
-%     1 + \Re{\rho} & \Im{\rho} \\
-%     \Im{\rho} & 1 - \Re{\rho}
-%   \end{pmatrix}
-%   = \frac{\sigma^2}2 
-%       \begin{pmatrix}
-%         1 + \lvert \rho \rvert \cos\theta
-%           & \lvert \rho \rvert \sin\theta \\
-%         \lvert \rho \rvert \sin\theta
-%           & 1 - \lvert \rho \rvert \cos\theta
-%       \end{pmatrix}
-%   \,. $$
-
-The local reparameterization trick provides both faster computations, and better statistical
-efficiency of the SGVB gradient estimator \citep{wang_fast_2013,kingma_variational_2015}.
-Suppose that weights $W \in \cplx^{n\times m}$ of a linear layer are drawn from a mean
-field $\cplx$-Gaussian approximation
-\begin{equation}  \label{eq:c-gauss-vi-general}
-  W_{ij}
-    \sim \mathcal{N}^{\cplx} \bigl(
-      \mu_{ij}, \Sigma_{ij}, C_{ij}
-    \bigr)
-  \,,
-\end{equation}
-where mean, \textit{variance} and \textit{relation} are given by matrices $
-  \mu, \Sigma, C \in \cplx^{n\times m}
-$ with $\Sigma_{ij} \in \real$, and $
-  \lvert C_{ij} \rvert^2 \leq \Sigma_{ij}
-$. The property \eqref{eq:cn-affine} and independence of elements of $W$ imply that for any
-$x \in \cplx^m$ and $b \in \cplx^n$ the components of $y = W x + b$ are independent with
-distributions
-\begin{equation}  \label{eq:cplx-gauss-trick}
-  y_i
-    \sim \mathcal{N}^{\cplx}
-      \Bigl(
-        % e_i^\top \mu x + b_i,
-        b_i + \sum_{j=1}^m \mu_{ij} x_j,
-        \, \sum_{j=1}^m \Sigma_{ij} \lvert x_j \rvert^2,
-        \, \sum_{j=1}^m C_{ij} x_j^2
-      \Bigr)
-    \,.
-\end{equation}
-The trick requires three matrix operations: $\mu x + b$, $\Sigma \lvert x \rvert^2$ and
-$C x^2$ with the modulus and power applied elementwise.
-
-The trick and dropout can be applied to any layer, the output of which depends linearly on
-its parameters, e.g. convolutional layers, affine, and bilinear transformations $
-  (x, z) \mapsto x^\top W^{(j)} z + b_j
-$. Similar to $\real$ case, variational dropout for $\cplx$ convolutions draws independent
-realizations of $W$ for each spatial patch in the input. The rationale is simpler computations
-and variance reduction. The latter effect stems from decorrelated gradient estimates from
-overlapping patches \citep{kingma_variational_2015}, which allows \eqref{eq:cplx-gauss-trick}
-to use $\cplx$ convolutions of elementwise complex squares $x^2$ and amplitudes $\lvert x \rvert^2$
-with the relation and variance kernels.
-% Weight sharing is essentially pushed to shared variational parameters $\theta$ in the approximation $q_\theta$.
-% A convolution is a matrix product of $W$, unrolled into a toeplitz matrix, and im-to-col
-% flattened intput $x$
-
-% subsection c_gauss_and_local_rep (end)
-
-\subsection{The choice of priors and Kullback-Leibler divergence} % (fold)
-\label{sub:priors_and_kullback_leibler_divergence}
-
-For $\cplx$-variational dropout we propose using mean-field proper $\cplx$-Gaussian approximate
-posterior and MAP estimates of bias terms, i.e. parameters $W \in \cplx^{n\times m}$ of a dense
-linear layer follow
-% We use MAP estimates of bias terms, i.e. assume an independent fully factorized Dirac approximation.
-\begin{equation}  \label{eq:c-gauss-vi}
-  % (we omit the subscript $m=1$ for brevity)
-  W \sim q(W)
-    % = \prod_{ij} q(W_{ij})
-    = \prod_{ij} \mathcal{N}^{\cplx}(
-      W_{ij} \mid
-        \mu_{ij},
-        \alpha_{ij} \lvert \mu_{ij} \rvert^2,
-        % \sigma^2_{ij},
-        0
-    )
-  \,,
-\end{equation}
-and we use similar factorized approximation for convolutions and other, effectively, linear
-layers. For this approximation the relation coefficients \eqref{eq:cplx-gauss-trick} are
-zero.
-
-We consider two priors for Bayesian dropout: \verify{log-uniform} and $\cplx$-Gaussian empirical
-Bayes \citep{kingma_variational_2015,molchanov_variational_2017,kharitonov_variational_2018}.
-For a fully factorized approximation $q(\omega)$ and factorized prior belief $\pi(\omega)$,
-the divergence term in ELBO \eqref{eq:elbo} is
-\begin{equation}  \label{eq:elbo-general-kl-div}
-  KL(q \| \pi)
-    % = \mathbb{E}_{\oemga \sim q(\oemga)} \log \tfrac{q(\oemga)}{\pi(\oemga)}
-    % = \sum_{ij} \mathbb{E}_{\omega_{ij} \sim q(\omega_{ij})}
-    %   \log \tfrac{q(\omega_{ij})}{\pi(\omega_{ij})}
-    % = \sum_{ij} KL\bigl( q(\omega_{ij}) \| \pi(\omega_{ij}) \bigr)
-    = - \sum_{ij}
-        \mathbb{H}(q(\omega_{ij}))
-        + \mathbb{E}_{q(\omega_{ij})} \log{\pi(\omega_{ij})}
-    \,.
-\end{equation}
-We omit subscripts ${ij}$ for brevity in the next sections.
-
-\subsubsection{Variational dropout} % (fold)
-\label{ssub:variational_dropout}
-
-From \eqref{eq:cn-proper-entropy} the KL-divergence for \verify{log-uniform prior} $
-  \pi(\omega) \propto {\lvert \omega \rvert}^{-\beta}
-$ with $\beta \geq 1$ is
-\begin{equation}  \label{eq:c-vd-kl-div-raw}
-  KL(q\| \pi)
-    \propto
-    %   \mathbb{E}_{\omega \sim q(\omega)} \log q(\omega)
-    %   + \tfrac{\beta}2 \mathbb{E}_{\omega \sim q(\omega)} \log \lvert \omega \rvert^2
-    % =
-    %   - \log \lvert \det{(\pi e \sigma^2)} \rvert
-    %   + \tfrac{\beta}2 \mathbb{E}_{\omega \sim q(\omega)} \log \lvert \omega \rvert^2
-    % =
-      - \log{\sigma^2}
-      + \tfrac{\beta}2 \mathbb{E}_{\omega \sim q(\omega)} \log \lvert \omega \rvert^2
-    \,.
-\end{equation}
-Property \eqref{eq:cn-affine} implies that $
-  \mathcal{N}^{\cplx}(\mu, \sigma^2, 0)
-  \sim \mu \cdot \mathcal{N}^{\cplx}(1, \alpha, 0)
-$ for $\mu \neq 0$ and $
-  \sigma^2 = \alpha \lvert \mu \rvert^2
-$, whence
-\begin{equation}  \label{eq:expect-improper-term-cplx}
-  \mathbb{E}_{\omega \sim q(\omega)} \log \lvert \omega \rvert^2
-    % = \mathbb{E}_{\xi \sim \mathcal{N}^{\cplx}(\xi \vert 1, \alpha, 0)}
-    %   \log \lvert \mu \xi \rvert^2
-    % = \log \lvert \mu \rvert^2
-    %   + \mathbb{E}_{\xi \sim \mathcal{N}^{\cplx}(\xi \vert 1, \alpha, 0)}
-    %       \log \lvert \xi \rvert^2
-    = \log \alpha \lvert \mu \rvert^2
-      + \mathbb{E}_{\xi \sim \mathcal{N}^{\cplx}(\xi \vert 0, 1, 0)}
-          \log{\bigl\lvert \tfrac1{\sqrt{\alpha}} + \xi \bigr\rvert^2}
-    \,.
-\end{equation}
-Let $
-  (z_i)_{i=1}^m \sim \mathcal{N}^{\cplx}(0, 1, 0)
-$ iid and $\theta \in \cplx^m$. Then $
-  \sum_i \lvert \theta_i + z_i \rvert^2
-    \sim \chi^2_{2m}(s^2)
-$ with $
-  s^2 = \sum_i \lvert \theta_i \rvert^2
-$, i.e. a non-central $\chi^2_{2m}$ with parameter $s^2$. Its log-moments for general
-integer $m \geq1$ are given in \cite[p.~2466]{lapidoth_capacity_2003}. In particular,
-% in fact Appendix X, Lemma 10.1
-for $m=1$ and $\theta\in \cplx$ we have
-\begin{equation}  \label{eq:log-moment-for-chi-2}
-  \mathbb{E}_{z \sim \mathcal{N}^{\cplx}(0, 1, 0)}
-    \log \lvert \theta + z \rvert^2
-    = \log \lvert \theta \rvert^2 - \mathop{Ei}( - \lvert \theta \rvert^2)
-    \,,
-\end{equation}
-where $
-  \mathop{Ei}(x) = \int^x_{-\infty} t^{-1} e^t dt
-$ for $x < 0$ is the Exponential Integral. Note that
-$
-  \tfrac{d}{dx} \mathop{Ei}(x) = \tfrac{e^x}{x}
-$, $
-  \mathop{Ei}(x) \leq \log{(-x)}
-$, $
-  % as x to 0 from below
-  \mathop{Ei}(x) \approx \log{(-x)} - \gamma
-$ as $x\to 0$ ($\gamma$ is Euler's constant) and $
-  \mathop{Ei}(x) \geq -e^x
-$ for $x \leq -1$.
-% 1. by Leibniz rule $Ei(x)$ has -ve derivative on $x < 0$
-% 2. $Ei(x) \leq 0$ on $x < 0$, since $t^{-1} e^t \leq t^{-1} < 0$ on $t < 0$
-% 3. $Ei(x) \leq \log{(-x)}$ on $x < 0$, since on $x \in [-1, 0)$
-% $$
-%   \mathop{Ei}(x)
-%     = \mathop{Ei}(-1) + \int_{-1}^x t^{-1} e^t dt
-%     \leq \mathop{Ei}(-1) + \int_{-1}^x t^{-1} dt
-%     = \mathop{Ei}(-1) + \log{(-x)}
-%     \leq \log{(-x)}
-%   \,. $$
-% 3. by l'H{\^o}pital rule $Ei(x)$ is asymptotically $\log{-x}$ as $x \to 0-$
-% $$
-% % t = -e^{-x} ,  -\log{(-t)} = x
-%   \lim_{x\to 0-} \frac{\mathop{Ei}(x)}{\log{(-x)}}
-%     = \lim_{x\to 0-} \frac{x^{-1} e^x}{x^{-1}}
-%     = 1
-%   \,. $$
-% 4. \citep{lapidoth_capacity_2003} yields $\lim_{x\to 0-} \log{(-x)} - \mathop{Ei}(x) = \gamma$
-% 5. $Ei(x) \geq -e^x$ for any $x < -1$, since $t^{-1} e^t \geq - e^t$ for $t < -1$
-% $$
-% \mathop{Ei}(x)
-%   = \int_{-\infty}^x t^{-1} e^t dt
-%   \geq \int_{-\infty}^x -e^t dt = -e^x
-%   \,. $$
-% 6. $Ei(x) \leq \log{(-x)} - \gamma$ on $x < 0$ and $-e^x \leq Ei(x) \leq 0$ on $x < -1$.
-%
-Through \eqref{eq:expect-improper-term-cplx} and \eqref{eq:log-moment-for-chi-2} we get
-\begin{equation}  \label{eq:c-vd-kl-div}
-  KL(q\| \pi)
-    \propto
-    %   - \log \lvert \det{(\pi e \sigma^2)} \rvert
-    %   + \tfrac{\beta}2 \log \alpha \lvert \mu \rvert^2
-    %   + \tfrac{\beta}2 \mathbb{E}_{\xi \sim \mathcal{N}^{\cplx}(\xi \vert 0, 1, 0)}
-    %       \log{\bigl\lvert \tfrac1{\sqrt{\alpha}} + \xi \bigr\rvert^2}
-    % =
-    %   - \log{\sigma^2}  % - \log{\pi e}
-    %   + \tfrac{\beta}2 \log \alpha \lvert \mu \rvert^2
-    %   + \tfrac{\beta}2 \bigl(
-    %     - \log \alpha - \mathop{Ei}( -\tfrac1{\alpha})
-    %   \bigr)
-    % =
-    %   - \log{\sigma^2}
-    %   + \tfrac{\beta}2 \log \alpha \lvert \mu \rvert^2
-    %   - \tfrac{\beta}2 \log \alpha
-    %   - \tfrac{\beta}2 \mathop{Ei}( -\tfrac1{\alpha})
-    % =
-      % \log \tfrac{\lvert \mu \rvert^\beta}{\sigma^2}
-      % \log \tfrac{\lvert \mu \rvert^\beta}{\alpha \lvert \mu \rvert^2}
-      \tfrac{\beta-2}2 \log{\lvert \mu \rvert^2}
-      + \log{\tfrac1{\alpha}}
-      - \tfrac{\beta}2 \mathop{Ei}(- \tfrac1{\alpha})
-      \tag{\ref{eq:c-vd-kl-div-raw}'} \,.
-\end{equation}
-We set $\beta = 2$ to make the divergence term depend only on $\alpha$ and add $\gamma$
-so that the right-hand side is nonegative \citep[eq.(84)]{lapidoth_capacity_2003}.
-%
-Since $\mathop{Ei}(x)$ has simple analytic derivative and \eqref{eq:elbo} depends additively
-on \eqref{eq:c-vd-kl-div}, it is possible to back-propagate through the divergence without
-forward evaluation.
-% Gradient-based optimiziation of \eqref{eq:elbo} usually does not use the value of the objective. 
-% In stochastic gradient methods are concerned more with the gradient, induced by the objective
-% function, rather than its value.
-
-% subsubsection variational_dropout (end)
-
-\subsubsection{Empirical Bayes} % (fold)
-\label{ssub:empirical_bayes}
-
-Let's consider fully factorized proper $\cplx$-Gaussian prior $
-  \pi_\tau(\omega)
-    \propto \mathcal{N}^{\cplx}\bigl(
-      \omega \vert 0, \tau^{-1}, 0
-    \bigr)
-$. The per element divergence term in \eqref{eq:elbo-general-kl-div} is
-\begin{equation}  \label{eq:emp-bayes-kl-div}
-  KL(q \| \pi_\tau)
-    = - 1 - \log{(\tau \sigma^2)}
-      + \tau \bigl(
-        \sigma^2 + \lvert \mu \rvert^2
-      \bigr)
-    \,.
-\end{equation}
-%
-% This follows from the KL-divergence expression for two multivariate Gaussians
-% $$
-% % \mathbb{E}_{\omega\sim q_1(\omega)} \log \tfrac{q_1(\omega)}{q_2(\omega)}
-% %   =
-% KL(q_1\| q_2)
-%   =
-%   % - \tfrac12 \log\det{(2\pi e \Sigma_1)} + \tfrac12 \log\det{(2\pi \Sigma_2)}
-%   - \tfrac12 \log \det{e I}
-%   + \tfrac12 \log \frac{\det{\Sigma_2}}{\det{\Sigma_1}}
-%   + \tfrac12 \tr{\bigl( \Sigma_2^{-1} \Sigma_1 \bigr)}
-%   + \tfrac12 (\mu_1 - \mu_2)^\top \Sigma_2^{-1} (\mu_1 - \mu_2)
-%   \,. $$
-%
-In Empirical Bayes the prior adapts to the observed data, i.e. \eqref{eq:elbo} is optimized
-w.r.t. $\tau$ of each weight's prior. Since divergence sits in \eqref{eq:elbo} with negative
-sign, optimal $
-  \tau^\ast = (\sigma^2 + \lvert \mu \rvert^2)^{-1}
-$ is found by minimizing \eqref{eq:emp-bayes-kl-div}, which gives
-\begin{equation}  \label{eq:emp-bayes-opt-kl}
-  KL(q \| \pi_{\tau^\ast})
-    % = - 1 - \log{({\tau^\ast} \sigma^2)}
-    %   + {\tau^\ast} \sigma^2 + {\tau^\ast} \lvert \mu \rvert^2
-    % = \log{((\sigma^2 + \lvert \mu \rvert^2) \tfrac1{\sigma^2})}
-    = \log{\bigl(1 + \tfrac{\lvert \mu \rvert^2}{\sigma^2}\bigr)}
-    = \log{\bigl(1 + \tfrac1\alpha \bigr)}
-    \,.
-\end{equation}
-
-% subsubsection empirical_bayes (end)
-
-\subsubsection{Bayesian $\cplx$-dropout via $\real$-scaling} % (fold)
-\label{ssub:real_scaling_dropout}
-
-Consider the following parameterization of $W$: $
-  W = \mu \odot \xi
-$ where $
-  \xi_{ij} \sim \mathcal{N}(1, \alpha_{ij})
-$, yet $\mu \in \cplx^{n \times m}$. This case corresponds to inference regarding
-relevance coefficients $\xi$ rather than the parameters themselves after. Each weight
-under this parameterization is an independent degenerate $\cplx$-Gaussian distribution
-\begin{equation}  \label{eq:real-scal-gauss-vi}
-  W_{ij}
-    \sim \mathcal{N}^{\cplx} \bigl(
-      \mu_{ij},
-      \, \alpha_{ij} \lvert \mu_{ij} \rvert^2,
-      \, \alpha_{ij} \mu_{ij}^2
-    \bigr)
-  \,,
-\end{equation}
-which implies by \eqref{eq:cplx-gauss-trick} the following:
-\begin{equation}  \label{eq:real-scal-gauss-trick}
-  y_i
-    \sim \mathcal{N}^{\cplx}\bigl(
-      % e_i^\top \mu x + b,
-      b_i + \sum_{j=1}^m \mu_{ij} x_j,
-      \, \sum_j \alpha_{ij} \lvert x_{ij} \mu_{ij}\rvert^2,
-      \, \sum_j \alpha_{ij} (x_{ij} \mu_{ij})^2
-    \bigr)
-    \,.
-\end{equation}
-The KL-divergence term for this approximation coincides with \eqref{eq:improper-kl-div-real},
-which is approximated by \citet{molchanov_variational_2017}. The major drawback of this method
-is that the additive noise reparameterization in \eqref{eq:real-scal-gauss-trick}, which
-disentangles the gradient with respect to $\mu$ from the local noise, cannot be applied.
-
-% subsubsection real_scaling_dropout (end)
-
-% subsection priors_and_kullback_leibler_divergence (end)
-
-% section dropout_for_c_valued_layers (end)
-
-\section{Experiments} % (fold)
-\label{sec:experiments}
-
-In this section we study the complex variational dropout techniques discussed above
-on the tasks and datasets, that have been studied in prior research on complex-valued networks.
-
-% common experiment settings
-Every experiment is replicated several times to take random effects into account, e.g.
-random network initialization prior to training, randomly ordered batches during SGD.
-Unless specified otherwise, every experiment uses global gradient clipping within an
-$\ell_2$-norm ball of radius $0.5$, runs SGD with ADAM optimizer with the base learning
-rate of $10^{-3}$. We note that since our experiments are on classification tasks,
-$\cplx$-valued networks ultimately have to output a real-valued logit score. Following
-\citet{wolter_complex_2018} and \citet{trabelsi_deep_2017}, the class scores are taken
-as real parts of the $\cplx$ output.
-
-\subsection{Stagewise fitting and sparsification} % (fold)
-\label{sub:fitting_and_sparsification}
-
-The goal of this section to study the compression-performance trade-off of the proposed Bayesian
-sparsification methods for $\cplx$-valued networks. To this end we trained each network in
-three successive stages in every experiment: ``dense'' $\to$ ``sparsify'' $\to$ ``fine-tune''.
-
-At the \textit{``dense''} stage every network is fit ``as-is'', retaining its original
-non-Bayesian architecture and using only the likelihood term from \eqref{eq:elbo} without
-variational dropout.
-%
-During the \textit{``sparsify''} stage we make every layer Bayesian and apply $\cplx$-variational
-dropout sec.~\ref{ssub:variational_dropout} (or sec.~\ref{ssub:empirical_bayes}) or its $\real$
-counterpart. To be able to study the attainable sparsity levels we inject a coefficient $
-  C \in (0, 1]
-$ at the KL divergence term in \eqref{eq:elbo}:
-\begin{equation}  \label{eq:elbo_with_coef}
-    - \frac{C}N KL(q_{\theta} \| \pi_{\lambda})
-    + \frac1{M} \sum_{i=1}^M
-        \log p_{\phi}(z_i \mid g(\varepsilon_i; \theta))
-    \,. \tag{\ref{eq:elbo}'}
-\end{equation}
-Higher $C$ yields increasingly more sparse layers upon termination of this stage.
-
-The \textit{``fine-tune''} stage begins with computing the sparsity masks from the fitted
-approximation $q_\theta(W)$ and proceeds to train the non-zero parameters similarly to
-the ``dense'' stage, i.e. with non-Bayesian layers and fixed sparsity masks. 
-%
-The benefit of the ``fine-tune'' stage appears to be strongly influenced by the compression
-rate. We can observe in this and, more prominently, in MusicNet experiment (sec.~\ref{sub:musicnet})
-that higher compression rate render the model more regularized, leaving less capacity for
-overfitting.
-% more ``holes'' Bayesian dropout ``poked'' makes the ``fine-tune'' serve as extended training.
-
-% on compresssion
-Between \textit{``sparsify''} and \textit{``fine-tune''} stages we compute masks of non-zero
-weights in each layer based on the relevance scores $\alpha$ (sec.~\ref{sub:dropout}). Since
-the $q_\theta$ factorizes into univariate distributions, a $\cplx$ or $\real$ parameter is
-considered non-zero if $\log \alpha \leq \tau$ for $
-  \alpha = \tfrac{\sigma^2}{\lvert\mu\rvert^2}
-$, or zero otherwise. Figure~\ref{fig:hist__and__threshold__tradeoff} is constructed
-for $C \in \{\tfrac1{20}, \frac1{200}\}$ before running the ``fine-tune'' stage. From
-\eqref{eq:elbo_with_coef}, the relative positions of the compression curves on this
-plot, and the results of experiments below it can be concluded that $C$ has much more
-substantial impact on the sparsity and performance, than the choice of $\tau$. Furthermore,
-for $\tau > 0$ the performance quickly saturates while compression creeps downwards.
-
-\begin{figure}[!t]
+\begin{figure}[b]
   \centering
-  \begin{subfigure}[b]{0.95\textwidth}  % imcl2019-style swears at this
+  \begin{subfigure}[b]{0.5\textwidth}
     \centering
-    \includegraphics[width=\columnwidth]{../assets/figure__musicnet__threshold.pdf}
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__emnist_letters__fft__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__kmnist__fft__-0.5.pdf}
+  \end{subfigure} \\ %
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__fashionmnist__fft__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__mnist__fft__-0.5.pdf}
   \end{subfigure}
   \caption{%
-    Test split performance and compression rate for a $\cplx$-valued net on MusicNet.
+    The trade-off of ARD method for $\real$ and $\cplx$ models using Fourier features.
   }
-  \label{fig:hist__and__threshold__tradeoff}
+  \label{fig:appendix__mnist-like__trade-off__ARD__fft}
 \end{figure}
 
-% on chosing the threshold
-The threshold $\tau$ is picked so, that the remaining \textit{``non-zero''} parameters
-are within $\delta$ relative tolerance of their mean with high probability under the
-approximate posterior $q_\theta(W)$. This ensures that stochastic parameters are sufficiently
-concentrated around $\mu$, which are used as stand-in values for network weights $W$,
-when it runs in inference mode. Since $W$ is $\real$- or a proper $\cplx$-Gaussian, the
-random variable $
-  \tfrac{k \lvert W - \mu \rvert^2}
-        {\alpha \lvert \mu \rvert^2}
-$ is $\chi^2_k$ distributed with $k=1$ ($\real$) or $2$ ($\cplx$).
-%
-For a generous $\delta = 50\%$ tolerance all values of $\log \alpha$ below $-2.5$ yield
-at least $90\%$ chance of a non-zero $\real$/$\cplx$ parameter. We pick $\tau = -\tfrac12$
-to exclude noisy parameters and encourage higher sparsity, at the same time being aware
-that $q_\theta$ is merely an approximation. In comparison, $\tau = 3$ is commonly used as
-the threshold \citep{molchanov_variational_2017,kingma_variational_2015}.
-
-% subsection fitting_and_sparsification (end)
-
-\subsection{Metrics and compression} % (fold)
-\label{sub:metrics_and_compression}
-
-% perfromance metrics
-We use accuracy as the performance metric for multi-class image classification on MNIST-like
-and CIFAR10 datasets. Similarly to \citet{trabelsi_deep_2017} performance in experiments with
-MusicNet is measured with (pooled) average precision. The evaluation is done after ``dense''
-stage, before the beginning and upon termination of the ``fine-tune'' stage.
-
-% write a note on the incompressible parameters (bias, batch norm etc.)
-The compression rate is computed based on the number of floating point values needed to
-store the model and equals $
-  \tfrac{n_\mathtt{par}}{n_\mathtt{par} - n_\mathtt{zer}}
-$, where $n_\mathtt{zer}$ is the number of explicit zeros, $n_\mathtt{par}$ is the total
-number of floats. Thus each parameter is counted once in a $\real$-valued network, but twice
-in a $\cplx$-network. Each model has compression limit, set by layers' biases, shift
-and scaling from $\real$-and $\cplx$-batch normalization.
-
-% subsection metrics_and_compression (end)
-
-\subsection{MNIST-like datasets} % (fold)
-\label{sub:mnist_like_datasets}
-
-We conduct a moderately sized experiment on MNIST and similar $28\times 28$ greyscale image
-datasets to study the compression-performance trade-off of the proposed $\cplx$-variational
-dropout.
-% dataset size
-We deliberately use a {fixed} random subset of $10k$ images from the train split of each
-dataset to fit the networks and gauge the final performance on the usual test split.
-Limiting the size was done primarily to test the regularization strength of compression.
-
-% model architectures
-% discussion of TwoLayerDenseModel (TLDM) and SimpleConvModel (SCM)
-The $\real$/$\cplx$ networks have been chosen for the purpose of illustrating the compression
-and understanding the effects of experiment parameters. \textit{SimpleConvModel} (SCM) is a $2d$
-ReLU convolutional network with average pooling ($2\times 2$) after non-linearities with
-two convolutions (kernel $5\times 5$, stride $1$) with filters $n_1 \to n_2$ followed by
-dense layers $n_3 \to n_\mathtt{out}$. The second network, \textit{TwoLayerDenseModel} (TLDM),
-is a wide dense network $n_1 \to n_\mathtt{out}$. For SCM model $n_1, n_2, n_3$ are $20, 50, 500$,
-respectively, and for TLDM model $n_1 = 4096$ regardless of their type ($\real$ or $\cplx$),
-although \citet{monning_evaluation_2018} argue that this renders models incomparable.
-
-% image features
-Since image data is not naturally $\cplx$-valued, we preprocess images by either embedding
-$\real$-data into $\cplx$ assuming $\Re z = 0$ (\texttt{raw}), or applying the two-dimensional
-Fourier Transform (\texttt{fft}), shifting lower frequencies to the centre of the image. We
-do not investigate the option, proposed by \citet{trabelsi_deep_2017}, to train an auxiliary
-model to synthesize the imaginary component from the real data.
-
-% first experiment: 40-75-40 with fast scheduler
-In this experiment stages last for $40$, $75$ and $40$ epochs, respectively, and the base
-learning rate of ${10}^{-3}$ is reduced after the $10$-th epoch to ${10}^{-4}$.
-%
-Plots~\ref{fig:mnist-like__trade-off} depict samples from the performance-compression curve
-on KMNIST and EMNIST-Letters datasets for the studied models and VD compression method
-(sec.~\ref{ssub:variational_dropout}). Besides that we try \texttt{raw} or \texttt{fft}
-input features, vary $
-  C \in \{\tfrac3{2^{k+1}}\colon k=1..16\}
-$, and repeat the experiment $5$ times.
-
-Shaded horizontal bands reflect the spread of the performance of the uncompressed network
-after ``dense'' stage. Each point represents a precision-compression value attained by the
-network after ``fine-tune'' stage. The end of each point's tail represents the performance
-gain or loss from running the ``fine-tune'' stage.
-%
-We make a couple of observations based on the results of these plots. First, \texttt{fft}
-features perform on par with raw colour channel data in the convolutional networks across most
-compression rates, but require high compression rate to make wide shallow dense network work
-as well. The upward trend manifests itself in MNIST and Fashion MNIST experiments as well
-(see appendix~\ref{sub:other_mnist_like_datasets}). Finally, overall $\cplx$ variational
-dropout methods seem to compress networks adequately well without much loss in performance.
-
-% a couple of plots from MNIST and Fashion-MNIST
-\begin{figure}[!t]
+\begin{figure}[b]
   \centering
-  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
+  \begin{subfigure}[b]{0.5\textwidth}
     \centering
-    % \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__fashionmnist__fft__-0.5.pdf}
-    \includegraphics[width=0.8\columnwidth]{../assets/figure__mnist-like__trade-off/legacy__VD__kmnist__fft__-0.5.pdf}
-    % \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/VD__kmnist__fft__-0.5.pdf}
-  \end{subfigure} \\%
-  % \hfill
-  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__emnist_letters__fft__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
     \centering
-    % \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__fashionmnist__raw__-0.5.pdf}
-    \includegraphics[width=0.8\columnwidth]{../assets/figure__mnist-like__trade-off/legacy__VD__kmnist__raw__-0.5.pdf}
-    % \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/VD__kmnist__raw__-0.5.pdf}
-  \end{subfigure} \\%
-  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__kmnist__fft__-0.5.pdf}
+  \end{subfigure} \\ %
+  \begin{subfigure}[b]{0.5\textwidth}
     \centering
-    % \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__mnist__fft__-0.5.pdf}
-    \includegraphics[width=0.8\columnwidth]{../assets/figure__mnist-like__trade-off/legacy__VD__emnist_letters__fft__-0.5.pdf}
-    % \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/ARD__kmnist__fft__-0.5.pdf}
-  \end{subfigure} \\%
-  % \hfill
-  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__fashionmnist__fft__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
     \centering
-    % \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__mnist__raw__-0.5.pdf}
-    \includegraphics[width=0.8\columnwidth]{../assets/figure__mnist-like__trade-off/legacy__VD__emnist_letters__raw__-0.5.pdf}
-    % \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/VD__emnist_letters__raw__-0.5.pdf}
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__mnist__fft__-0.5.pdf}
   \end{subfigure}
   \caption{%
-    The compression-accuracy trade-off on KMNIST and the letters of the Extended MNIST datasets.
-    (\textit{top}) \texttt{fft} features, (\textit{bottom}) \texttt{raw} features.
+    The trade-off of VD method for $\real$ and $\cplx$ models using Fourier features.
   }
-  \label{fig:mnist-like__trade-off}
+  \label{fig:appendix__mnist-like__trade-off__VD__fft}
 \end{figure}
 
-% subsection mnist_like_datasets (end)
-
-\subsection{CIFAR10} % (fold)
-\label{sub:cifar10}
-
-% mention the same experimental setup as in MNIST
-Experiments on CIFAR10 dataset are set up similarly to MNIST-like experiment, except
-that we study VGG16 model \citep{simonyan_very_2015} and its $\cplx$-counterpart and
-replicate each experiment only twice.
-%
-% describe the VGG16 model and its cplx-valued modification
-The $\cplx$-VGG16 model is architecturally identical to VGG16, except for all layers being
-replaced by their $\cplx$-valued versions. To maintain comparability, we halve the filter
-sizes of $\cplx$ model \citep{monning_evaluation_2018}.
-%
-Each network is trained stagewise for $20$, $40$,
-and $20$ epochs on the full training split of $50k$ colour $32\times32$ images. We use
-only raw colour features (\texttt{raw}). We apply random crop and horizontal flips as
-data augmentation and use a learning rate scheduler in SGD, which scales the base learning
-rate after $5$, $10$, and $20$-th epoch by $\tfrac1{10}$, $\tfrac1{20}$ and $\tfrac1{100}$,
-respectively.
-
-% draw some conclusions
-Figure~\ref{fig:figure__cifar10__trade-off} shows that although the prior used in ARD method
-offers slightly less compression, it makes up for it by equally slightly better accuracy.
-Furthermore, the results imply that that the halved $\cplx$ network visibly underperforms
-in comparison with its $\real$ counterpart, although in MNIST-like experiment $\cplx$-valued
-network with the same inner feature dimensions performed on close to $\real$-valued, which
-is half the size of the former.
-
-% compare compressed cplx-vgg against real-vgg
-\begin{figure}[!t]
+\begin{figure}[b]
   \centering
-  \begin{subfigure}[b]{0.9\textwidth}  % imcl2019-style swears at this
+  \begin{subfigure}[b]{0.5\textwidth}
     \centering
-    \includegraphics[width=\columnwidth]{../assets/figure__cifar__trade-off/legacy__augmentedcifar10__raw__-0.5.pdf}
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__emnist_letters__raw__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__kmnist__raw__-0.5.pdf}
+  \end{subfigure} \\%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__fashionmnist__raw__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__mnist__raw__-0.5.pdf}
   \end{subfigure}
   \caption{%
-    Compression-accuracy frontier for $\real$ and $\tfrac12 \cplx$ versions of VGG16 on CIFAR10.
+    The trade-off of ARD method for $\real$ and $\cplx$ models using raw features.
   }
-  \label{fig:figure__cifar10__trade-off}
+  \label{fig:appendix__mnist-like__trade-off__ARD__raw}
 \end{figure}
 
-% subsection cifar10_100 (end)
-
-\subsection{musicNet} % (fold)
-\label{sub:musicnet}
-
-% describe musicnet as in Trabelsi et al. (2017) also get some hints from thickstun_learning_2017
-MusicNet \citep{thickstun_learning_2017} is an annotated audio dataset, consisting of $330$
-musical compositions. Folowing \citet{trabelsi_deep_2017}, we use it for automatic music
-transcription task and study the $1d$ VGG-like $\cplx$-convent proposed therein. Similarly to
-the study, we downsample the audio from 44.1kHz to 11kHz, retain only $84$ out of $128$ labels,
-and hold-out the same validation and test splits. During each training epoch we sample $1000$
-mini-batches of the remaining $321$ compositions, with each mini-batch comprised of a random
-full window of $4096$ samples picked from each waveform and transformed from $\real$ to
-$\cplx$ with $1d$ FFT. Annotation labels are taken at the mid-point of the window.
-
-Preliminary experiments with the model without sparsification have shown that early stopping
-almost always terminates the training process within the first $10-20$ epochs with the validation
-performance peaking at $10-15$ epochs, much sooner than $200$ epochs used by \citet{trabelsi_deep_2017}.
-Thus we adopt shorter lasting stages: $12$, $32$ and $50$ epochs, which essentially turn the
-``dense'' stage into pretraining. Early stopping is used only during the ``fine-tune'' stage.
-To keep the learning rate schedule consistent, we allow the base rate of $10^{-3}$ to be scaled
-after $5$, $10$, and $20$-th epoch by $\tfrac1{10}$, $\tfrac1{20}$ and $\tfrac1{100}$, respectively.
-Other key deviations from the set-up used by \citet{trabelsi_deep_2017} include: shifting lower
-frequencies to the centre of the window to maintain locality after applying the FFT
-(sec.~\ref{sub:mnist_like_datasets}), and clipping $\ell_2$ norm of the gradients to $0.05$.
-
-\begin{figure}[!h]
+\begin{figure}[b]
   \centering
-  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
+  \begin{subfigure}[b]{0.5\textwidth}
     \centering
-    \includegraphics[width=\columnwidth]{../assets/figure__musicnet__trade-off/paper__musicnetram__fft__-0.5.pdf}
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__emnist_letters__raw__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__kmnist__raw__-0.5.pdf}
+  \end{subfigure} \\%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__fashionmnist__raw__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__mnist__raw__-0.5.pdf}
   \end{subfigure}
   \caption{%
-    Performance-compression trade-off using \textbf{\color{blue} VD} and \textbf{\color{orange} ARD}.
-    The \textbf{\color{pink} version} of the network with kernel $3$ in the first convolution is
-    compressed with VD only.
+    The trade-off of VD method for $\real$ and $\cplx$ models using raw features.
   }
-  \label{fig:musicnet__trade-off}
+  \label{fig:appendix__mnist-like__trade-off__VD__raw}
 \end{figure}
 
-In each experiment we vary the method and the value $C$, while keeping $\tau$ at $-\tfrac12$.
-Every experiment is replicated five times to take into account the random effects from
-initialization, batch sequence during SGD, and stochasticity of intermediate layers on
-forward pass at ``sparsify'' stage.
+\begin{figure}[b]
+  \centering
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__emnist_letters__fft__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__kmnist__fft__-0.5.pdf}
+  \end{subfigure} \\ %
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__fashionmnist__fft__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__mnist__fft__-0.5.pdf}
+  \end{subfigure}
+  \caption{%
+    The trade-off of ARD method for $2\real$ and $\cplx$ models using Fourier features.
+  }
+  \label{fig:appendix__cmp__mnist-like__trade-off__ARD__fft}
+\end{figure}
 
-Figure~\ref{fig:musicnet__trade-off} shows the resulting performance-compression frontier
-for the deep network of \citet{trabelsi_deep_2017} and its version, in which we purposefully
-halve the spatial size of the first $1d$ convolution kernel from $6$ to $3$ (denoted by
-suffix \textit{k}$3$). The motivation is to test if the handicap introduced by the forced
-compression of the most upstream layer can be alleviated through non-uniform compression,
-induced by variational dropout. We test only VD (sec.~\ref{ssub:variational_dropout}) this
-sub-experiment, since prior results have not demonstrated significant superiority of one method
-over another (sec.~\ref{ssub:empirical_bayes}).
+\begin{figure}[b]
+  \centering
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__emnist_letters__fft__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__kmnist__fft__-0.5.pdf}
+  \end{subfigure} \\ %
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__fashionmnist__fft__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__mnist__fft__-0.5.pdf}
+  \end{subfigure}
+  \caption{%
+    The trade-off of VD method for $2\real$ and $\cplx$ models using Fourier features.
+  }
+  \label{fig:appendix__cmp__mnist-like__trade-off__VD__fft}
+\end{figure}
 
-For compression levels lower than $50$, the final stage overfits the network, since it still
-remains overparameterized. For the rates higher than $\approx 100$ the ``fine-tune'' stage
-serves its purpose, essentially, due regularizing effects of high sparsity. There is evidence
-in favour of achievability of the SOTA average precision of \citet{trabelsi_deep_2017} within
-the $50$-$100$ compression region with $\cplx$-valued variational dropout with ARD prior
-(sec.~\ref{ssub:empirical_bayes}).
+\begin{figure}[b]
+  \centering
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__emnist_letters__raw__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__kmnist__raw__-0.5.pdf}
+  \end{subfigure} \\%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__fashionmnist__raw__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__mnist__raw__-0.5.pdf}
+  \end{subfigure}
+  \caption{%
+    The trade-off of ARD method for $\real$ and $\tfrac12\cplx$ models using raw features.
+  }
+  \label{fig:appendix__cmp__mnist-like__trade-off__ARD__raw}
+\end{figure}
 
-% subsection musicnet (end)
+\begin{figure}[b]
+  \centering
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__emnist_letters__raw__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__kmnist__raw__-0.5.pdf}
+  \end{subfigure} \\%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__fashionmnist__raw__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__mnist__raw__-0.5.pdf}
+  \end{subfigure}
+  \caption{%
+    The trade-off of VD method for $\real$ and $\tfrac12\cplx$ models using raw features.
+  }
+  \label{fig:appendix__cmp__mnist-like__trade-off__VD__raw}
+\end{figure}
 
-% section experiments (end)
+\begin{figure}[b]
+  \centering
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/legacy__VD__emnist_letters__fft__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/legacy__VD__kmnist__fft__-0.5.pdf}
+  \end{subfigure} \\%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/legacy__VD__fashionmnist__fft__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/legacy__VD__mnist__fft__-0.5.pdf}
+  \end{subfigure}
+  \caption{%
+    The trade-off of VD method for $\real$ and $\cplx$ models using Fourier features (main text).
+  }
+  \label{fig:paper__mnist-like__trade-off__VD__fft}
+\end{figure}
 
-\section{Conclusion} % (fold)
-\label{sec:conclusion}
+\begin{figure}[b]
+  \centering
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/legacy__VD__emnist_letters__raw__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/legacy__VD__kmnist__raw__-0.5.pdf}
+  \end{subfigure} \\%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/legacy__VD__fashionmnist__raw__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/legacy__VD__mnist__raw__-0.5.pdf}
+  \end{subfigure}
+  \caption{%
+    The trade-off of VD method for $\real$ and $\cplx$ models using raw features (main text).
+  }
+  \label{fig:paper__mnist-like__trade-off__VD__raw}
+\end{figure}
 
-Despite having higher arithmetic complexity, complex-valued models provide built-in
-amplitude-phase transformations and regularization \citep{hirose_complex-valued_2009}
-and enjoy superior performance on naturally $\cplx$-valued datasets \citep{tarver_design_2019}.
-In this study we address the issue of excessive arithmetic complexity of complex-valued
-networks by extending the existing Bayesian compression techniques by \citet{kingma_variational_2015},
-\citet{molchanov_variational_2017} and \citet{kharitonov_variational_2018} to $\cplx$-valued
-parameters. To this end we have conducted a large numerical study of such networks to assess
-the performance-compression rate trade-off and have achieved performance comparable to
-the state-of-the-art in $\cplx$-valued networks on the MusicNet dataset.
+% section mnist_like_experiments (end)
 
-Much like $\real$-valued variational dropout, the proposed $\cplx$-valued extension can be
-straightforwardly enhanced to provide structured sparsity. The results of this study have
-direct implications for real-time signal processing with embedded deep learning applications
-both in terms of lower storage requirements and higher throughput stemming from fewer
-floating-point multiplications.
+\clearpage
 
-% section conclusion (end)
+\section{CIFAR10 experiments} % (fold)
+\label{sec:cifar_experiments}
+
+In addition to the results reported in the main paper, we conduct additional experiment
+on CIFAR10 and VGG16 with a much more slowly annealed learning rate. Similar to MNIST-like
+experiments, we start with the rate set to $10^{-3}$ and then reduce it by $10$ after the
+$10$-the epoch. In summary, for the CIFAR10 experiments we reuse the set-up with the following
+changes:
+\begin{itemize}
+  \item we allocate $20$, $40$, and $20$ epochs to each stage
+  \item the weight of the KL divergence term varies over a smaller grid $
+    C \in \{
+      \tfrac32 2^{-\tfrac{k}2} \colon k=7, \cdots, 15
+    \}
+  $
+  \item we use full $50$k training split of the CIFAR10 dataset for training and raw color
+  features only
+  \item dataset is randomly augmented: every image within a batch of size $128$ is randomly
+  cropped and flipped horizontally
+\end{itemize}
+Random cropping is done by zero-padding each side of a $32\times 32$ image by four pixels
+and then a extracting a random $32\times 32$ patch from the $40\times 40$ intermediate image.
+
+We experiment with $\real$ VGG16 network \citep{simonyan_very_2015} and its $\cplx$-valued
+variant, which straightforwardly replaces $\real$ layers with their $\cplx$ counterparts.
+
+\begin{figure}[htb]
+  \centering
+  \includegraphics[width=\linewidth]{figure__cifar__trade-off/appendix__augmentedcifar10__raw__-0.5.pdf}
+  \caption{%
+    The compression-accuracy trade-off for $\real$ and $\cplx$ VGG16 using raw input features.
+  }
+  \label{fig:appendix__cifar__trade-off__VGG16__raw}
+\end{figure}
+
+% section cifar_experiments (end)
 
@@
 \bibliography{references}
-% \nocite{*}
-
-\clearpage
-
-\section{Appendix} % (fold)
-\label{sec:appendix}
-
-\subsection{Complex-valued local reparameterization} % (fold)
-\label{sub:complex_valued_local_reparameterization}
-
-%notation
-By $e_i$ we denote the $i$-th real unit vector of dimensionality \textit{conforming} to the
-matrix-vector expression it is used in. Let $\vec{M}$ denote \textit{row-major} flattening
-of $M$ into a vector, i.e. in lexicographic order of its indices. $\diag{(\cdot)}$ embeds
-$\cplx^n$ into $n\times n$ diagonal matrices, and $\otimes$ denotes the Kronecker product,
-for which we note the following identities $
-  \vec{P Q R} = (P \otimes R^\top) \vec{Q}
-$, and $
-  (P \otimes R) (C \otimes S) = P Q \otimes R S
-$ \citep{petersen_matrix_2012}.
-% It follows from the definition of the Kronecker product
-% of $P$ and $R^\top$ and the row-major order vectorization.
-
-If we assume a mean field $\cplx$-Gaussian approximate posterior for $
-  W \in \cplx^{n\times m}
-$, then
-\begin{equation}  \label{eq:c-gauss-vi-general-vec}
-  \vec{W}
-    \sim \mathcal{N}^{\cplx}_{nm} \bigl(
-      \vec{\mu}, \diag{\vec{\Sigma}}, \diag{\vec{C}}
-    \bigr)
-  \,,
-\end{equation}
-where mean, \textit{variance} and relation are given by matrices $
-  \mu, \Sigma, C \in \cplx^{n\times m}
-$ with $\Sigma_{ij} \geq 0$, and $
-  \lvert C_{ij} \rvert^2 \leq \Sigma_{ij}
-$. For any $x \in \cplx^m$ and $b\in \cplx^n$ $
-  y = W x + b
-    = (I_n \otimes x^\top) \vec{W} + b
-$, whence the covariance and relation matrices of $y$ are
-\begin{align}
-  (I \otimes x^\top) \diag{\vec{\Sigma}} (I \otimes x^\top)^{\hop}
-    % = \sum_{ij} (I \otimes x^\top) e_i \otimes e_j
-    %   \Sigma_{ij} (e_i \otimes e_j)^\top (I \otimes x^\top)^{\hop}
-    % = \sum_{ij} (e_i \otimes x^\top e_j)
-    %   \Sigma_{ij} (e_i \otimes x^\top e_j)^{\hop}
-    % = \sum_{ij} (e_i \otimes x_j) \Sigma_{ij} (e_i^\top \otimes \conj{x}_j)
-    & = \sum_{i=1}^n (e_i e_i^\top) \sum_{j=1}^m \Sigma_{ij} x_j \conj{x}_j
-    \,,  \label{eq:cn-gauss-lrt-cov} \\
-  (I \otimes x^\top) \diag{\vec{C}} (I \otimes x^\top)^\top
-    % = \sum_{ij} (e_i \otimes x_j) C_{ij} (e_i \otimes x_j)^\top
-    & = \sum_{i=1}^n (e_i e_i^\top) \sum_{j=1}^m C_{ij} x_j^2
-    \,.  \label{eq:cn-gauss-lrt-rel}
-\end{align}
-Since \eqref{eq:cn-gauss-lrt-cov} and \eqref{eq:cn-gauss-lrt-rel} are diagonal, $(y_i)_{i=1}^n$
-are independent whence \eqref{eq:cn-affine} implies
-\begin{equation}  \label{eq:cplx-gauss-trick-appendix}
-  y_i
-    \sim \mathcal{N}^{\cplx}
-      \bigl(
-        e_i^\top \mu x + b_i,
-        \, \sum_{j=1}^m \Sigma_{ij} \lvert x_j \rvert^2,
-        \, \sum_{j=1}^m C_{ij} x_j^2
-      \bigr)
-    \,.
-\end{equation}
-Hence \eqref{eq:cplx-gauss-trick} follows.
-
-% subsection complex_valued_local_reparameterization (end)
-
-\subsection{Gradient of the KL-divergence in $\real$ case} % (fold)
-\label{sub:real-chisq-grad}  % gradient_of_the_kl_divergence_in_R_case
-
-In this section we derive the exact gradient of \eqref{eq:improper-kl-div-real}. Even
-though, ultimately, the divergence involves a hypergeometric function, and its gradient
-requires evaluating the Gauss error function, the analysis provides independent verification
-of the approximation, proposed by \citet{molchanov_variational_2017}. The logic of the
-derivation follows \citet{lapidoth_capacity_2003}.
-% \citet{pav_moments_2015} correctly notice that \cite[p. 2466]{lapidoth_capacity_2003} has a missing $\log{2}$ term.
-
-For $(z_i)_{i=1}^m \sim \mathcal{N}(0, 1)$ iid and $
-  (\mu_i)_{i=1}^m \in \mathbb{R}
-$, the random variable $W = \sum_i (\mu_i + z_i)^2$ is noncentral $\chi^2$ with shape $m$
-and noncentrality parameter $\lambda = \sum_i \mu_i^2$, i.e. $W\sim \chi^2_m(\lambda)$.
-Its density is
-\begin{equation}  \label{eq:nonchisq-density}
-  f_W(x)
-    % = e^{- \tfrac\lambda2} \sum_{n \geq 0} \tfrac{\bigl(\tfrac\lambda2\bigr)^n}{n!}
-    %   \tfrac{
-    %     x^{n + \tfrac{m}2 - 1} e^{-\tfrac{x}2}
-    %   }{
-    %     2^{n + \tfrac{m}2} \Gamma(n + \tfrac{m}2)
-    %   }
-    % = e^{- \tfrac\lambda2} \sum_{n \geq 0} \tfrac{\bigl(\tfrac\lambda2\bigr)^n}{n!}
-    %     \tfrac{
-    %         \bigl(\tfrac{x}2\bigr)^{n + \tfrac{m}2 - 1} e^{-\tfrac{x}2}
-    %     }{
-    %         2 \Gamma(n + \tfrac{m}2)
-    %     }
-    = \frac12 e^{- \tfrac{x + \lambda}2} \bigl(\tfrac{x}2\bigr)^{\tfrac{m}2 - 1}
-      \sum_{n \geq 0} \frac{
-        \bigl(\tfrac{x \lambda}4\bigr)^n
-      }{
-        n! \Gamma(n + \tfrac{m}2)
-      }
-    % = \frac12 e^{- \tfrac{x + \lambda}2}
-    % \bigl(\tfrac{x}\lambda\bigr)^{\tfrac{m}4 - \tfrac12}
-    % \bigl(\tfrac{x \lambda}4\bigr)^{\tfrac{m}4 - \tfrac12}
-    % \sum_{n \geq 0} \tfrac{
-    %         \bigl(\tfrac{x \lambda}4\bigr)^n
-    %     }{
-    %         n! \Gamma(n + \tfrac{m}2)
-    %     }
-    % = \frac12 e^{- \tfrac{x + \lambda}2}
-    % \bigl(\tfrac{x}\lambda\bigr)^{\tfrac{m}4 - \tfrac12}
-    % \bigl(\tfrac{\sqrt{x \lambda}}2\bigr)^{\tfrac{m}2 - 1}
-    % \sum_{n \geq 0} \tfrac{
-    %         \bigl(\tfrac{x \lambda}4\bigr)^n
-    %     }{
-    %         n! \Gamma(n + \tfrac{m}2)
-    %     }
-    % = \frac12 e^{- \tfrac{x + \lambda}2}
-    % \bigl(\tfrac{x}\lambda\bigr)^{\tfrac{m - 2}4}
-    % I_{\bigl(\tfrac{m}2 - 1\bigr)}(\sqrt{x \lambda})
-    \,.
-\end{equation}
-% where $I_k$ is the modified Bessel function of the first kind
-% $$
-% I_k(s)
-%   = \Bigl(\frac{s}2\Bigr)^k
-%       \sum_{n \geq 0} \tfrac{
-%           \bigl( \tfrac{s}2 \bigr)^{2n}
-%       }{n! \Gamma(n + k + 1)}
-%   \,. $$
-By integrating the power series \eqref{eq:nonchisq-density} with substitution $x \to 2u$,
-the expectation $
-  \mathbb{E}_{W\sim \chi^2_m(\lambda)} \log W
-$, needed in \eqref{eq:improper-kl-div-real}, equals
-\begin{multline}  \label{eq:exp-log-chisq-proof}
-    % &= \int_0^\infty f_W(x) \log x dx
-    % \notag \\
-    % &\frac12 e^{- \tfrac\lambda2}
-    % \int_0^\infty \sum_{n \geq 0} \biggl(
-    %     \frac{
-    %       e^{- \tfrac{x}2} \bigl(\tfrac\lambda2\bigr)^n
-    %     }{
-    %       n! \Gamma(n + \tfrac{m}2)
-    %     }
-    %     \bigl(\tfrac{x}2\bigr)^{n + \tfrac{m}2 - 1}
-    % \biggr) \log{(x)} dx
-    % = [\text{ absolute summability and Fubini, or any other conv. thm for integrals of non-negative integrals}]
-    % = e^{- \tfrac\lambda2} \sum_{n \geq 0}
-    %     \tfrac{\bigl(\tfrac\lambda2\bigr)^n}{n!}
-    %     \tfrac1{\Gamma(n + \tfrac{m}2)}
-    % \int_0^\infty
-    %     e^{- \tfrac{x}2} \bigl(\tfrac{x}2\bigr)^{n + \tfrac{m}2 - 1}
-    %     (\log2 + \log \tfrac{x}2) \tfrac{dx}2
-    % = [u = \tfrac{x}2]
-    % \notag \\
-    e^{- \tfrac\lambda2} \sum_{n \geq 0}
-        \frac{\bigl(\tfrac\lambda2\bigr)^n}{
-          n! \Gamma(n + \tfrac{m}2)
-        }
-    \int_0^\infty
-        e^{- u} u^{n + \tfrac{m}2 - 1}
-        \log{(2 u)} du
-    % = [\text{definitions:} \Gamma, \psi]
-    % = e^{- \tfrac\lambda2} \sum_{n \geq 0}
-    %     \tfrac{\bigl(\tfrac\lambda2\bigr)^n}{n!}
-    % (\psi(n + \tfrac{m}2) + \log2)
-    % \notag
-    \\
-    = \log{2}
-    + e^{- \tfrac\lambda2} \sum_{n \geq 0}
-        \frac{\bigl(\tfrac\lambda2\bigr)^n}{n!}
-        \psi(n + \tfrac{m}2)
-    \,,
-\end{multline}
-where $\psi(x)$ is the digamma function, i.e.
-\begin{equation}  \label{eq:digamma}
-  \psi(x)
-    % = \frac{d}{dx} \log \Gamma(x)
-    = \frac1{\Gamma(x)}
-      \int_0^\infty
-        u^{x-1} e^{-u} \log{u}
-      \, du
-    \,,
-\end{equation}
-which satisfies $
-  \psi(z+1) = \psi(z) + \tfrac1z
-$, $
-  \psi(x)\leq \log x - \tfrac1{2x}
-$, and $
-  \psi(\tfrac12) = -\gamma - 2\log 2
-$ ($\gamma$ is Euler's constant). If we put
-\begin{equation}  \label{eq:g-m-series}
-  g_m(x)
-    % alpha: e^{-x} \sum_{n=0}^{\infty} \frac{x^n}{n!} \psi(n + m / 2)
-    % = e^{-x} \sum_{n \geq 0} \frac{x^n}{n! \Gamma(n + \tfrac{m}2)}
-    %     \int_0^\infty e^{-t} t^{n + \tfrac{m}2-1} \log{t} dt
-    = e^{-x} \sum_{n \geq 0} \frac{x^n}{n!} \psi(n + \tfrac{m}2)
-    \,,
-\end{equation}
-then the desired expectation in \eqref{eq:improper-kl-div-real} equals $
-  \log{2} + g_1(\tfrac1{2\alpha})
-$.
-%
-% We can differentiate the series in $g_m(x)$, since the sum converges on $\mathbb{R}$.
-% Indeed, it is a power series featuring nonnegative coefficients, which is dominated by $
-%   \sum_{n \geq 1} \tfrac{x^n}{n!} \log{(n+\tfrac{m}2)}
-% $. By the ratio test, the dominating
-% series has infinite radius:
-% $$
-% \lim_{n\to\infty}
-%   \biggl\lvert
-%     \frac{
-%       n! x^{n+1} \log{(n + 1 + \tfrac{m}2)}
-%     }{
-%       x^n \log{(n + \tfrac{m}2)} (n+1)!
-%     }
-%   \biggr\rvert
-%   = \lim_{n\to\infty}
-%     \lvert x \rvert 
-%     \biggl\lvert
-%       \frac{
-%         \log{(n + 1 + \tfrac{m}2)}
-%       }{
-%         \log{(n + \tfrac{m}2)} (n+1)
-%       }
-%     \biggr\rvert
-%   % = \lim_{n\to\infty}
-%   %   \lvert x \rvert 
-%   %   \biggl\lvert
-%   %     \frac{
-%   %       n + \tfrac{m}2
-%   %     }{
-%   %       (n + 1 + \tfrac{m}2)((n+1) + (n + \tfrac{m}2) \log{(n + \tfrac{m}2)})
-%   %     }
-%   %   \biggr\rvert
-%   = 0 < 1
-%   \,, $$
-% since
-% $$
-% \frac{\log{(x + a + 1)}}{x \log{(x + a)}}
-%   \sim \frac{\log{(x+1)}}{(x-a) \log{x}}
-%   \sim \frac{\log{(x+1)}}{x \log{x}}
-%   \sim \frac{\tfrac1{(x+1)}}{1 + \log{x}}
-%   \to 0
-%   \,. $$
-% A theorem from calculus states, that the formal series derivative (integral)
-% coincides with the derivative (integral) of the function, corresponding to
-% the power series (everywhere on the convergence region). And the convergence
-% regions of derivative (integral) coincide with the region of the original
-% power series.
-%
-Formally differentiating the convergent power series within $g_m$ yields
-\begin{equation}  \label{eq:g-m-deriv}
-  \frac{d}{d x} g_m(x)
-    % = e^{-x} \sum_{n\geq 1} \frac{x^{n-1}}{(n-1)!} \psi(n + \tfrac{m}2) - g_m(x)
-    % = e^{-x} \sum_{n\geq 0} \frac{x^n}{n!} \psi(n + \tfrac{m}2 + 1) - g_m(x)
-    % = e^{-x} \sum_{n\geq 0} \frac{x^n}{n!} (
-    %     \psi(n + \tfrac{m}2 + 1) - \psi(n + \tfrac{m}2)
-    % )
-    % = e^{-x} \sum_{n\geq 0} \frac{x^n}{n!} \tfrac1{n + \tfrac{m}2}
-    % = e^{-x} \sum_{n\geq 0} \frac{x^n}{n!} (n + \tfrac{m}2)^{-1}
-    = x^{-\tfrac{m}2} e^{-x} \sum_{n\geq 0}
-        \frac{x^{n + \tfrac{m}2}}{n!} (n + \tfrac{m}2)^{-1}
-    \,.
-\end{equation}
-From $
-    e^t  = \sum_{n\geq 0} \tfrac{t^n}{n!}
-$ on $\mathbb{R}$ and $
-  \tfrac{x^\alpha}{\alpha}
-    = \int_0^x t^{\alpha-1} dt
-$ for $\alpha\neq 0$ we get
-% by the monotone convergence theorem on ([0, x], \mathcal{B}([0, x]), dx)
-\begin{align}  \label{eq:g-m-deriv-int-2}
-  \eqref{eq:g-m-deriv}
-    % = x^{-\tfrac{m}2} e^{-x} \sum_{n\geq 0}
-    %     \frac{x^{n + \tfrac{m}2}}{n!} (n + \tfrac{m}2)^{-1}
-    &= x^{-\tfrac{m}2} e^{-x} \sum_{n\geq 0}
-        \frac1{n!} \int_0^x t^{n + \tfrac{m}2 - 1} dt
-    % = x^{-\tfrac{m}2} e^{-x}
-    %     \int_0^x t^{\tfrac{m}2 - 1} \sum_{n\geq 0} \frac{t^n}{n!} dt
-    \notag \\
-    &= x^{-\tfrac{m}2} e^{-x}
-        \int_0^x t^{\tfrac{m}2 - 1} e^t dt
-    \,.
-\end{align}
-Substitution $u^2 = t$ on $[0, \infty]$ with $2u du = dt$ yields
-\begin{equation}  \label{eq:g-m-deriv-int-3}
-  \frac{d}{d x} g_m(x)
-    % = x^{-\tfrac{m}2} e^{-x}
-    %     \int_0^x t^{\tfrac{m}2 - 1} e^t dt
-    = 2 x^{-\tfrac{m}2} e^{-x}
-        \int_0^{\sqrt{x}} u^{m - 1} e^{u^2} du
-    \,.
-\end{equation}
-In particular, the derivative of \eqref{eq:g-m-series} for $m=1$ is
-\begin{equation}  \label{eq:g-m-deriv-one}
-  \frac{d}{d x} g_1(x)
-    = 2 \frac{F(\sqrt{x})}{\sqrt{x}}
-    \,,
-\end{equation}
-using Dawson's integral $
-  F
-  % \colon \mathbb{R} \to \mathbb{R}
-  \colon x \mapsto e^{-x^2} \int_0^x e^{u^2} du
-$.
-%
-Hence, the derivative of the expectation in \eqref{eq:improper-kl-div-real} with respect
-to $\alpha$ is
-$$
-\frac{d}{d \alpha} g_1(\tfrac1{2\alpha})
-  = -\frac1{2 \alpha^2} g_1'(\tfrac1{2\alpha})
-  % = -\frac1{2 \alpha^2} 2 \tfrac{F(\sqrt{\tfrac1{2\alpha}})}{\sqrt{\tfrac1{2\alpha}}}
-  % = -\frac1{2 \alpha^2} 2 \tfrac{F(\tfrac1{\sqrt{2\alpha}})}{\tfrac1{\sqrt{2\alpha}}}
-  = -\frac1{\alpha} \sqrt{\frac2{\alpha}} F(\tfrac1{\sqrt{2\alpha}})
-  \,. $$
-Finally, since $\alpha$ is nonnegative, it is typically parameterized via its logarithm.
-The gradient of \eqref{eq:improper-kl-div-real} w.r.t $\log \alpha$ is
-\begin{equation}  \label{eq:real-kl-div-deriv-log}
-  \frac{d \eqref{eq:improper-kl-div-real}}{d\log \alpha}
-  % \frac{d}{d\log \alpha}
-  %   \frac12 \mathbb{E}_{z \sim \mathcal{N}(0,1)}
-  %     \log \lvert z + \tfrac1{\sqrt{\alpha}} \rvert^2
-    % = \frac12 \frac{d\alpha}{d\log \alpha}
-    %   \frac{d}{d\alpha} \bigl(\mathbb{E}\cdots \bigr)
-    % = - \frac\alpha2 \tfrac1{\alpha}
-    %   \sqrt{\tfrac2{\alpha}} F(\tfrac1{\sqrt{2\alpha}})
-    = - \frac1{\sqrt{2\alpha}} F\bigl(\tfrac1{\sqrt{2\alpha}}\bigr)
-    \,.
-\end{equation}
-
-We compute the Monte-Carlo estimator of \eqref{eq:improper-kl-div-real} on a sample of $10^7$
-draws over an equally spaced grid of $\log \alpha$ in $[-12, +12]$ of size $4096$. The optimal
-coefficients of the regression, proposed by \citet{molchanov_variational_2017}, are within
-$1\%$ relative tolerance of the reported therein.
-\begin{equation}  \label{eq:improper-kl-div-real-approx}
-  \eqref{eq:improper-kl-div-real}
-% - KL(\mathcal{N}(w \mid \mu, \alpha \mu^2) \|
-%     \tfrac1{\lvert w \rvert})
-%   \approx
-%     k_1 \sigma(k_2 + k_3 \log \alpha)
-%     + C \big\vert_{C = -k1}
-%     - \tfrac12 \log (1 + e^{-\log \alpha})
-  % = \tfrac12 \log \alpha
-  %   - \mathbb{E}_{\xi \sim \mathcal{N}(1, \alpha)}
-  %   \log{\lvert \xi \rvert} + C
-  \approx
-    \frac12 \log{\bigl(1 + e^{-\log \alpha}\bigr)}
-    + k_1 \sigma\bigl(- (k_2 + k_3 \log \alpha)\bigr)
-    % - k_1 \bigl(1 - \sigma(k_2 + k_3 \log \alpha)\bigr)
-  \,,
-\end{equation}
-% in parctial implementations we suggest using softplus to numerically comptue the last
-% term, since it is typically implemented in a floating-point stable fashion.
-The numerically estimated derivative of the penalty term with respect to $\log \alpha$ using
-forward differences seems to be following \eqref{eq:real-kl-div-deriv-log} very closely (up to
-sampling error), see fig.~\ref{fig:molchanov-derivative-replica}. The derivative of
-\eqref{eq:improper-kl-div-real-approx} with respect to $\log \alpha$ appears to be very close
-to \eqref{eq:real-kl-div-deriv-log}. We compute a similar Monte-Carlo estimate for
-$\cplx$ variational dropout KL divergence term in \eqref{eq:c-vd-kl-div} with $\beta = 2$,
-fit the best approximation \eqref{eq:improper-kl-div-real-approx}, and compare the derivatives.
-
-\begin{figure}[!h]
-  \centering
-  \includegraphics[width=\linewidth]{../assets/grad_log.pdf}
-  \caption{$\tfrac{d f(\alpha)}{d \log{\alpha}}$ of the fit proposed by
-  \citet{molchanov_variational_2017}, MC estimate of \eqref{eq:improper-kl-div-real},
-  and the exact derivative using \eqref{eq:real-kl-div-deriv-log}.}
-  \label{fig:molchanov-derivative-replica}
-\end{figure}
-
-% subsection real-chisq-grad (end)
-
-\subsection{Backpropagation through $\cplx$-networks} % (fold)
-\label{sub:wirtinger_calculus}
-
-% essential intro into Wirtinger calculus (CR)
-% https://math.stackexchange.com/a/444493
-Wirtinger ($\cplx\real$) calculus relies on the natural identification of $\cplx$ with $
-  \real \times \real
-$, and regards $
-  f\colon \cplx \to \cplx
-$ as an equivalent in algebraic sense function $F\colon \real^2 \to \cplx$ defined $
-  f(z) = f(u + jv) = F(u, v)
-$. Within this framework the differential of $f$ at $z = u + jv \in \cplx$ is
-$$
-df(z)
-  = \frac{\partial f}{\partial z} dz
-    + \frac{\partial f}{\partial \conj{z}} d\conj{z}
-   % = \frac12\bigl(
-   %    \frac{\partial}{\partial u}
-   %    - j \frac{\partial}{\partial v}
-   % \bigr) F (du - j dv)
-   % + \frac12\bigl(
-   %    \frac{\partial}{\partial u}
-   %    + j \frac{\partial}{\partial v}
-   % \bigr) F (du - j dv)
-   % = \frac12 \bigl(
-   %    \frac{\partial F}{\partial u} du - j \frac{\partial F}{\partial v} du
-   %    + j \frac{\partial F}{\partial u} dv + \frac{\partial F}{\partial v} dv
-   % \bigr)
-   % + \frac12 \bigl(
-   %    \frac{\partial F}{\partial u} du + j \frac{\partial F}{\partial v} du
-   %    - j \frac{\partial F}{\partial u} dv + \frac{\partial F}{\partial v} dv
-   % \bigr)
-   = \frac{\partial F}{\partial u} du
-     + \frac{\partial F}{\partial v} dv
-   = dF(u, v)
-  \,, $$
-with formally defined derivatives $
-  \tfrac{\partial}{\partial z}
-    = \tfrac12 \bigl(
-      \tfrac{\partial}{\partial u}
-      - j \tfrac{\partial}{\partial v}
-    \bigr)
-$ and $
-  \tfrac{\partial}{\partial \conj{z}}
-    = \tfrac12 \bigl(
-      \tfrac{\partial}{\partial u}
-      + j \tfrac{\partial}{\partial v}
-    \bigr)
-$, and differentials $dz = du + j dv$ and $d\conj{z} = du - j dv$. This implies that the
-complex argument and its conjugate are treated as independent variables. Cauchy-Riemann
-conditions $
-  -j \tfrac{\partial F}{\partial v} = \tfrac{\partial F}{\partial u}
-$ can be expressed as $
-  \tfrac{\partial f}{\partial \conj{z}} = 0
-$ in this notation. Thus $\cplx\real$ calculus subsumes the usual $\cplx$-calculus on
-holomorphic functions, when $f(z)$, regarded as $f(z, \conj{z})$, is constant with respect
-to $\conj{z}$. The usual rules of calculus, like chain and product rules, follow directly
-from the definition of the operators, e.g.
-$$
-  \frac{\partial (f\circ g)}{\partial z}
-    = \frac{\partial f(g(z))}{\partial g} \frac{\partial g(z)}{\partial z}
-    + \frac{\partial f(g(z))}{\partial \conj{g}} \frac{\partial \conj{g(z)}}{\partial z}
-    % = \nabla G \nabla F
-  \,. $$
-% Show that $dh(z) = df(g(z)) dg(z)$.
-% $h(z) = f(g(z)) = F(G_r(u, v), G_i(u, v)) = H(u, v)$
-% $$
-% dH
-%   = \tfrac{\partial F}{\partial x} \tfrac{\partial G_r}{\partial u} du
-%   + \tfrac{\partial F}{\partial x} \tfrac{\partial G_r}{\partial v} dv
-%   + \tfrac{\partial F}{\partial y} \tfrac{\partial G_i}{\partial u} du
-%   + \tfrac{\partial F}{\partial y} \tfrac{\partial G_i}{\partial v} dv
-%   = \tfrac{\partial F}{\partial r} d\Re g(z)
-%   + \tfrac{\partial F}{\partial i} d\Im g(z)
-%   = df(\Re g(z) + j\Im g(z)) d g(z)
-%   = df(g(z)) d g(z)
-%   \,. $$
-
-In machine learning tasks the target objective is typically empirical risk, which has to
-be real-valued to be minimized. Nevertheless, the expression of the $\cplx\real$ gradient
-is compatible with what is expected, when $f$ is treated like a $\real^2$ function. For a
-real-valued $f\colon \cplx \to \real$ we have $\conj{f} = f$, which implies $
-  \tfrac{\partial f}{\partial \conj{z}}
-    = \tfrac{\partial \conj{f}}{\partial \conj{z}}
-    = \conj{\tfrac{\partial f}{\partial z}}
-$, whence
-$$
-df
-  = \tfrac{\partial f}{\partial z} dz
-    + \tfrac{\partial f}{\partial \conj{z}} d\conj{z}
-  % = \conj{\tfrac{\partial \conj{f}}{\partial \conj{z}}} dz
-  % + \conj{\conj{\tfrac{\partial f}{\partial \conj{z}}} dz}
-  = 2 \Re \Bigl(
-    \conj{\tfrac{\partial f}{\partial \conj{z}}} dz
-  \Bigr)
-  = 2 \Re \bigl(
-    \tfrac{\partial f}{\partial z} dz
-  \bigr)
-  \,. $$
-Thus, the gradient of $f$ at $z$ is given by $
-  \nabla_z f(z)
-    = \tfrac{\partial F}{\partial u}
-      + j \tfrac{\partial F}{\partial v}
-$.
-
-Natural identification of $\cplx$ with $\real\times \real$, storing the real and imaginary
-parts in interleaved format, emulation of $\cplx$-algebra using $\real$-valued arithmetic,
-and Wirtinger calculus make it possible to reuse $\real$ back-propagation and existing
-auto-differentiation frameworks \citep{trabelsi_deep_2017}.
-
-% subsection wirtinger_calculus (end)
-
-\subsection{$\cplx$-Linear operator representation} % (fold)
-\label{sub:c-linear_operator_representation}
-
-% proof that such operators exist and are unique (well this is an obvious statement)
-Consider $L \colon \cplx^m \to \cplx^n$ -- linear in $\cplx$. Then $
-  L(u + jv) = L u + j L v
-$ for any $u, v \in \real^m$, which implies that the effect of $L$ as $\cplx$-linear
-operator is determined by its restriction onto $\real^n$. Let $
-  F = L\vert_{\real^m}
-  \colon \real^m \to \cplx^n
-$ and observe that $F_r = \Re \circ F$ and $F_i = \Im \circ F$ are $\real$-linear operators
-such that $F = F_r + j F_i$ (pointwise). Indeed,
-$$
-  F_r(a + \lambda b)
-  % = \Re F(a + \lambda b)
-  = \Re L(a + \lambda b)
-  % = \Re \bigl( L a + \lambda L b \bigr)
-  = \Re L a + \lambda \Re L b
-  % = \Re F a + \lambda \Re F b
-  = F_r a + \lambda F_r b
-  \,. $$
-Therefore for any $\cplx$-linear operator $L$ there are $\real$-linear operators $U, V$
-such that
-$$
-L z 
-  = (U + j V) (\Re z + j \Im z)
-  % = (U + j V) \Re z + j (U + j V) \Im z
-  % = U \Re z + j V \Re z + j \bigl(U \Im z + j V \Im z \bigr)
-  = U \Re z - V \Im z + j \bigl( V \Re z + U \Im z \bigr)
-  % = (U + j V) z
-  \,. $$
-Uniqueness of these operators follows, if this decomposition is applied to any $z$ with
-$\Im z = 0$.
-
-% subsection c-linear_operator_representation (end)
-
-\subsection{Other MNIST-like datasets} % (fold)
-\label{sub:other_mnist_like_datasets}
-
-We provide the figures of the MNIST-like experiments, omitted from the main paper
-due to size limitations.
-
-\begin{figure}[!h]
-  \centering
-  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
-    \centering
-    \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__fashionmnist__fft__-0.5.pdf}
-  \end{subfigure} \\%
-  % \hfill
-  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
-    \centering
-    \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__fashionmnist__raw__-0.5.pdf}
-  \end{subfigure}
-  \caption{%
-    The compression-accuracy trade-off on the letters part of the Fashion MNIST dataset.
-    (\textit{top}) \texttt{fft} features, (\textit{bottom}) \texttt{raw} features.
-  }
-  \label{fig:mnist-like__trade-off__fashionmnist}
-\end{figure}
-
-\begin{figure}[!h]
-  \centering
-  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
-    \centering
-    \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__mnist__fft__-0.5.pdf}
-  \end{subfigure} \\%
-  % \hfill
-  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
-    \centering
-    \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__mnist__raw__-0.5.pdf}
-  \end{subfigure}
-  \caption{%
-    The compression-accuracy trade-off on the letters part of the MNIST dataset.
-    (\textit{top}) \texttt{fft} features, (\textit{bottom}) \texttt{raw} features.
-  }
-  \label{fig:mnist-like__trade-off__mnist}
-\end{figure}
-
-% subsection other_mnist_like_datasets (end)
-
-% section appendix (end)
 

### 2020-03-16 paper/paper.tex
tmp -> paper

--- 2020-03-16 paper/paper.tex
@@
 \usepackage{xcolor}
-\usepackage{graphicx}
+\usepackage{graphicx, url}
 \usepackage{grffile}
+
+\graphicspath{{../assets/}}
 
@@
     \centering
-    \includegraphics[width=\columnwidth]{../assets/figure__musicnet__threshold.pdf}
+    \includegraphics[width=\columnwidth]{figure__musicnet__threshold.pdf}
   \end{subfigure}
@@
     \centering
-    % \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__fashionmnist__fft__-0.5.pdf}
-    \includegraphics[width=0.8\columnwidth]{../assets/figure__mnist-like__trade-off/legacy__VD__kmnist__fft__-0.5.pdf}
-    % \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/VD__kmnist__fft__-0.5.pdf}
+    % \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/legacy__VD__fashionmnist__fft__-0.5.pdf}
+    \includegraphics[width=0.8\columnwidth]{figure__mnist-like__trade-off/legacy__VD__kmnist__fft__-0.5.pdf}
+    % \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/VD__kmnist__fft__-0.5.pdf}
   \end{subfigure} \\%
@@
     \centering
-    % \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__fashionmnist__raw__-0.5.pdf}
-    \includegraphics[width=0.8\columnwidth]{../assets/figure__mnist-like__trade-off/legacy__VD__kmnist__raw__-0.5.pdf}
-    % \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/VD__kmnist__raw__-0.5.pdf}
+    % \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/legacy__VD__fashionmnist__raw__-0.5.pdf}
+    \includegraphics[width=0.8\columnwidth]{figure__mnist-like__trade-off/legacy__VD__kmnist__raw__-0.5.pdf}
+    % \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/VD__kmnist__raw__-0.5.pdf}
   \end{subfigure} \\%
@@
     \centering
-    % \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__mnist__fft__-0.5.pdf}
-    \includegraphics[width=0.8\columnwidth]{../assets/figure__mnist-like__trade-off/legacy__VD__emnist_letters__fft__-0.5.pdf}
-    % \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/ARD__kmnist__fft__-0.5.pdf}
+    % \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/legacy__VD__mnist__fft__-0.5.pdf}
+    \includegraphics[width=0.8\columnwidth]{figure__mnist-like__trade-off/legacy__VD__emnist_letters__fft__-0.5.pdf}
+    % \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/ARD__kmnist__fft__-0.5.pdf}
   \end{subfigure} \\%
@@
     \centering
-    % \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__mnist__raw__-0.5.pdf}
-    \includegraphics[width=0.8\columnwidth]{../assets/figure__mnist-like__trade-off/legacy__VD__emnist_letters__raw__-0.5.pdf}
-    % \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/VD__emnist_letters__raw__-0.5.pdf}
+    % \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/legacy__VD__mnist__raw__-0.5.pdf}
+    \includegraphics[width=0.8\columnwidth]{figure__mnist-like__trade-off/legacy__VD__emnist_letters__raw__-0.5.pdf}
+    % \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/VD__emnist_letters__raw__-0.5.pdf}
   \end{subfigure}
@@
     \centering
-    \includegraphics[width=\columnwidth]{../assets/figure__cifar__trade-off/legacy__augmentedcifar10__raw__-0.5.pdf}
+    \includegraphics[width=\columnwidth]{figure__cifar__trade-off/legacy__augmentedcifar10__raw__-0.5.pdf}
   \end{subfigure}
@@
     \centering
-    \includegraphics[width=\columnwidth]{../assets/figure__musicnet__trade-off/paper__musicnetram__fft__-0.5.pdf}
+    \includegraphics[width=\columnwidth]{figure__musicnet__trade-off/paper__musicnetram__fft__-0.5.pdf}
   \end{subfigure}
@@
   \centering
-  \includegraphics[width=\linewidth]{../assets/grad_log.pdf}
+  \includegraphics[width=\columnwidth]{grad_log.pdf}
   \caption{$\tfrac{d f(\alpha)}{d \log{\alpha}}$ of the fit proposed by
@@
     \centering
-    \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__fashionmnist__fft__-0.5.pdf}
+    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/legacy__VD__fashionmnist__fft__-0.5.pdf}
   \end{subfigure} \\%
@@
     \centering
-    \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__fashionmnist__raw__-0.5.pdf}
+    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/legacy__VD__fashionmnist__raw__-0.5.pdf}
   \end{subfigure}
@@
     \centering
-    \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__mnist__fft__-0.5.pdf}
+    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/legacy__VD__mnist__fft__-0.5.pdf}
   \end{subfigure} \\%
@@
     \centering
-    \includegraphics[width=\linewidth]{../assets/figure__mnist-like__trade-off/legacy__VD__mnist__raw__-0.5.pdf}
+    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/legacy__VD__mnist__raw__-0.5.pdf}
   \end{subfigure}

### 2020-03-16 paper/paper.tex

@@
 
+\clearpage
+
+\subsection{MNIST-like experiments} % (fold)
+\label{sub:mnist_like_experiments}
+
+To supplement the results, reported in the main text (figures \ref{fig:paper__mnist-like__trade-off__VD__fft}
+and \ref{fig:paper__mnist-like__trade-off__VD__raw}), we conduct additional experiments
+with the same basic set-up, but over a finer grid of KL-divergence term coefficients.
+%
+These experiments lend further evidence in support of the conclusions, drawn in the main
+paper, namely, that the $\cplx$-valued extension of the $\real$-valued variational dropout
+can offer significant compression levels without much loss in performance. At the same
+time, the test performance of both $\real$ and $\cplx$ compressed networks benefits from
+an extra fine-tuning stage, during which sparsity masks are fixed.
+
+One intriguing observation, is that on MNIST-like images the dense network, taking Fourier
+features on input, exhibits gradually improving test-split performance. This is in stark
+contrast to raw image input, where the performance stays at one level in the small compression
+regime, and then gradually decays at high compression levels. Noteworthy is the presence
+of a trough in the pre fine-tuning stage performance in the small compression regime on figures
+\ref{fig:appendix__mnist-like__trade-off__ARD__raw},
+\ref{fig:appendix__mnist-like__trade-off__VD__raw},
+\ref{fig:appendix__cmp__mnist-like__trade-off__ARD__raw},
+and \ref{fig:appendix__cmp__mnist-like__trade-off__VD__raw}, which then slowly disappears
+as compression increases.
+
+The following scatter plots depict the samples from the compression-performance trade-off
+curve of simple networks studied in the experiments on the MNIST-like datasets. Transparent
+horizontal bands on each plot represent min-max performance spread of an uncompressed
+network on the test split. The points illustrate the final trade-off of the compressed
+networks after fine-tuning, while their tails show the performance gain or loss due to
+the fine-tuning.
+
+We recap the set-up of each additional experiment on MNIST-like datasets:
+\begin{itemize}
+  \item staged training, with weight and optimizer state transfer
+  \item $40$, $75$, and $40$ epochs for ``dense'', ``sparsify'', and ``fine-tune'' stagers, respectively
+  \item ADAM optimizer with learning rate $10^{-3}$ before the $10$-th, and $10^{-4}$
+  afterwards
+  \item global $\ell_2$-norm gradient clipping set at $\tfrac12$
+  \item training batches of size $128$ from a fixed randomly subset ($10^4$ images) of the training split
+  \item the multiplier of the Kullback-Leibler term in ELBO varies over $
+    C \in \{
+      \tfrac32 2^{-\tfrac{k}2} \colon k=2, \cdots, 38
+    \}
+  $
+  \item the sparsification threshold $\tau$ is set to $-\tfrac12$
+\end{itemize}
+Each experiment has been performed $5$ times to obtain a small sample of performance-compression
+values for each setting of $C$. By reevaluating each setting several times we can account
+for randomness in initialization of the uncompressed network at ``dense'', stochasticity of
+variational dropout layers, randomness of batch sequences during SDG, and non-determinism
+of computations on GPUs.
+
+Each figure shows the compression-accuracy trade-off of a particular method and input features
+for \textit{SimpleConvModel} and \textit{TwoLayerDenseModel} models for all four of the studied
+datasets (described in the main text): \emph{top-left} EMNIST-Letters, \emph{top-right} KMNIST,
+\emph{bottom-left} Fashion MNIST, and \emph{bottom-right} MNIST.
+%
+Figures \ref{fig:appendix__mnist-like__trade-off__ARD__fft}, \ref{fig:appendix__mnist-like__trade-off__VD__fft},
+\ref{fig:appendix__mnist-like__trade-off__ARD__raw}, and \ref{fig:appendix__mnist-like__trade-off__VD__raw}
+present $\real$ and $\cplx$ models with \emph{the same architecture}. We also report the
+trade-off comparison, when the argument by \citet{monning_evaluation_2018} for higher intrinsic
+capacity of $\cplx$-valued networks has been taken into account.
+%
+We compare $\real$ networks against $\tfrac12 \cplx$ with half the number of parameters
+for raw input features on figures \ref{fig:appendix__cmp__mnist-like__trade-off__ARD__raw},
+and \ref{fig:appendix__cmp__mnist-like__trade-off__VD__raw}, and $2 \real$ with
+double the number of parameters against $\cplx$ for Fourier input features on figures
+\ref{fig:appendix__cmp__mnist-like__trade-off__ARD__fft} and
+\ref{fig:appendix__cmp__mnist-like__trade-off__VD__fft}.
+
+The following observations can be made from the conducted experiment:
+\begin{itemize}
+  \item $\cplx$-valued networks do not have as much spare capacity as $2 \real$ due to
+  constants imposed by multiplication in $\cplx$ numbers (\ref{fig:appendix__cmp__mnist-like__trade-off__ARD__raw},
+  \ref{fig:appendix__cmp__mnist-like__trade-off__VD__raw})
+  \item Variational Dropout and Automatic Relevance Determination offer similar compression-performance
+  trade-off, with negligibly lower compression by the latter (both $\real$ and $\cplx$ versions,
+  e.g. figures \ref{fig:appendix__mnist-like__trade-off__ARD__raw} and \ref{fig:appendix__mnist-like__trade-off__VD__raw})
+  \item smaller networks tend to be less compressible (figures \ref{fig:appendix__cmp__mnist-like__trade-off__ARD__fft},
+  \ref{fig:appendix__cmp__mnist-like__trade-off__VD__fft})
+\end{itemize}
+
+\begin{figure}[b]
+  \centering
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__emnist_letters__fft__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__kmnist__fft__-0.5.pdf}
+  \end{subfigure} \\ %
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__fashionmnist__fft__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__mnist__fft__-0.5.pdf}
+  \end{subfigure}
+  \caption{%
+    The trade-off of ARD method for $\real$ and $\cplx$ models using Fourier features.
+  }
+  \label{fig:appendix__mnist-like__trade-off__ARD__fft}
+\end{figure}
+
+\begin{figure}[b]
+  \centering
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__emnist_letters__fft__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__kmnist__fft__-0.5.pdf}
+  \end{subfigure} \\ %
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__fashionmnist__fft__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__mnist__fft__-0.5.pdf}
+  \end{subfigure}
+  \caption{%
+    The trade-off of VD method for $\real$ and $\cplx$ models using Fourier features.
+  }
+  \label{fig:appendix__mnist-like__trade-off__VD__fft}
+\end{figure}
+
+\begin{figure}[b]
+  \centering
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__emnist_letters__raw__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__kmnist__raw__-0.5.pdf}
+  \end{subfigure} \\%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__fashionmnist__raw__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__mnist__raw__-0.5.pdf}
+  \end{subfigure}
+  \caption{%
+    The trade-off of ARD method for $\real$ and $\cplx$ models using raw features.
+  }
+  \label{fig:appendix__mnist-like__trade-off__ARD__raw}
+\end{figure}
+
+\begin{figure}[b]
+  \centering
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__emnist_letters__raw__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__kmnist__raw__-0.5.pdf}
+  \end{subfigure} \\%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__fashionmnist__raw__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__mnist__raw__-0.5.pdf}
+  \end{subfigure}
+  \caption{%
+    The trade-off of VD method for $\real$ and $\cplx$ models using raw features.
+  }
+  \label{fig:appendix__mnist-like__trade-off__VD__raw}
+\end{figure}
+
+\begin{figure}[b]
+  \centering
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__emnist_letters__fft__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__kmnist__fft__-0.5.pdf}
+  \end{subfigure} \\ %
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__fashionmnist__fft__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__mnist__fft__-0.5.pdf}
+  \end{subfigure}
+  \caption{%
+    The trade-off of ARD method for $2\real$ and $\cplx$ models using Fourier features.
+  }
+  \label{fig:appendix__cmp__mnist-like__trade-off__ARD__fft}
+\end{figure}
+
+\begin{figure}[b]
+  \centering
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__emnist_letters__fft__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__kmnist__fft__-0.5.pdf}
+  \end{subfigure} \\ %
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__fashionmnist__fft__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__mnist__fft__-0.5.pdf}
+  \end{subfigure}
+  \caption{%
+    The trade-off of VD method for $2\real$ and $\cplx$ models using Fourier features.
+  }
+  \label{fig:appendix__cmp__mnist-like__trade-off__VD__fft}
+\end{figure}
+
+\begin{figure}[b]
+  \centering
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__emnist_letters__raw__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__kmnist__raw__-0.5.pdf}
+  \end{subfigure} \\%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__fashionmnist__raw__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__mnist__raw__-0.5.pdf}
+  \end{subfigure}
+  \caption{%
+    The trade-off of ARD method for $\real$ and $\tfrac12\cplx$ models using raw features.
+  }
+  \label{fig:appendix__cmp__mnist-like__trade-off__ARD__raw}
+\end{figure}
+
+\begin{figure}[b]
+  \centering
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__emnist_letters__raw__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__kmnist__raw__-0.5.pdf}
+  \end{subfigure} \\%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__fashionmnist__raw__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__mnist__raw__-0.5.pdf}
+  \end{subfigure}
+  \caption{%
+    The trade-off of VD method for $\real$ and $\tfrac12\cplx$ models using raw features.
+  }
+  \label{fig:appendix__cmp__mnist-like__trade-off__VD__raw}
+\end{figure}
+
+\begin{figure}[b]
+  \centering
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/legacy__VD__emnist_letters__fft__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/legacy__VD__kmnist__fft__-0.5.pdf}
+  \end{subfigure} \\%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/legacy__VD__fashionmnist__fft__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/legacy__VD__mnist__fft__-0.5.pdf}
+  \end{subfigure}
+  \caption{%
+    The trade-off of VD method for $\real$ and $\cplx$ models using Fourier features (main text).
+  }
+  \label{fig:paper__mnist-like__trade-off__VD__fft}
+\end{figure}
+
+\begin{figure}[b]
+  \centering
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/legacy__VD__emnist_letters__raw__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/legacy__VD__kmnist__raw__-0.5.pdf}
+  \end{subfigure} \\%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/legacy__VD__fashionmnist__raw__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/legacy__VD__mnist__raw__-0.5.pdf}
+  \end{subfigure}
+  \caption{%
+    The trade-off of VD method for $\real$ and $\cplx$ models using raw features (main text).
+  }
+  \label{fig:paper__mnist-like__trade-off__VD__raw}
+\end{figure}
+
+% subsection mnist_like_experiments (end)
+
+\clearpage
+
+\subsection{CIFAR10 experiments} % (fold)
+\label{sub:cifar_experiments}
+
+In addition to the results reported in the main paper, we conduct additional experiment
+on CIFAR10 and VGG16 with a much more slowly annealed learning rate. Similar to MNIST-like
+experiments, we start with the rate set to $10^{-3}$ and then reduce it by $10$ after the
+$10$-the epoch. In summary, for the CIFAR10 experiments we reuse the set-up with the following
+changes:
+\begin{itemize}
+  \item we allocate $20$, $40$, and $20$ epochs to each stage
+  \item the weight of the KL divergence term varies over a smaller grid $
+    C \in \{
+      \tfrac32 2^{-\tfrac{k}2} \colon k=7, \cdots, 15
+    \}
+  $
+  \item we use full $50$k training split of the CIFAR10 dataset for training and raw color
+  features only
+  \item dataset is randomly augmented: every image within a batch of size $128$ is randomly
+  cropped and flipped horizontally
+\end{itemize}
+Random cropping is done by zero-padding each side of a $32\times 32$ image by four pixels
+and then a extracting a random $32\times 32$ patch from the $40\times 40$ intermediate image.
+
+We experiment with $\real$ VGG16 network \citep{simonyan_very_2015} and its $\cplx$-valued
+variant, which straightforwardly replaces $\real$ layers with their $\cplx$ counterparts.
+
+\begin{figure}[htb]
+  \centering
+  \includegraphics[width=\linewidth]{figure__cifar__trade-off/appendix__augmentedcifar10__raw__-0.5.pdf}
+  \caption{%
+    The compression-accuracy trade-off for $\real$ and $\cplx$ VGG16 using raw input features.
+  }
+  \label{fig:appendix__cifar__trade-off__VGG16__raw}
+\end{figure}
+
+% subsection cifar_experiments (end)
+
 % section appendix (end)

### 2020-03-16 paper/paper.tex
removed the now redundant other-mnist-like section; moved cplx-backprop and linear operator to the back

@@
 as well. The upward trend manifests itself in MNIST and Fashion MNIST experiments as well
-(see appendix~\ref{sub:other_mnist_like_datasets}). Finally, overall $\cplx$ variational
-dropout methods seem to compress networks adequately well without much loss in performance.
+(see appendix~\ref{sub:mnist_like_experiments}). Finally, overall $\cplx$ variational dropout
+methods seem to compress networks adequately well without much loss in performance.
 
@@
 % subsection real-chisq-grad (end)
+
+\subsection{MNIST-like experiments} % (fold)
+\label{sub:mnist_like_experiments}
+
+To supplement the results, reported in the main text (figures \ref{fig:paper__mnist-like__trade-off__VD__fft}
+and \ref{fig:paper__mnist-like__trade-off__VD__raw}), we conduct additional experiments
+with the same basic set-up, but over a finer grid of KL-divergence term coefficients.
+%
+These experiments lend further evidence in support of the conclusions, drawn in the main
+paper, namely, that the $\cplx$-valued extension of the $\real$-valued variational dropout
+can offer significant compression levels without much loss in performance. At the same
+time, the test performance of both $\real$ and $\cplx$ compressed networks benefits from
+an extra fine-tuning stage, during which sparsity masks are fixed.
+
+One intriguing observation, is that on MNIST-like images the dense network, taking Fourier
+features on input, exhibits gradually improving test-split performance. This is in stark
+contrast to raw image input, where the performance stays at one level in the small compression
+regime, and then gradually decays at high compression levels. Noteworthy is the presence
+of a trough in the pre fine-tuning stage performance in the small compression regime on figures
+\ref{fig:appendix__mnist-like__trade-off__ARD__raw},
+\ref{fig:appendix__mnist-like__trade-off__VD__raw},
+\ref{fig:appendix__cmp__mnist-like__trade-off__ARD__raw},
+and \ref{fig:appendix__cmp__mnist-like__trade-off__VD__raw}, which then slowly disappears
+as compression increases.
+
+The following scatter plots depict the samples from the compression-performance trade-off
+curve of simple networks studied in the experiments on the MNIST-like datasets. Transparent
+horizontal bands on each plot represent min-max performance spread of an uncompressed
+network on the test split. The points illustrate the final trade-off of the compressed
+networks after fine-tuning, while their tails show the performance gain or loss due to
+the fine-tuning.
+
+We recap the set-up of each additional experiment on MNIST-like datasets:
+\begin{itemize}
+  \item staged training, with weight and optimizer state transfer
+  \item $40$, $75$, and $40$ epochs for ``dense'', ``sparsify'', and ``fine-tune'' stagers, respectively
+  \item ADAM optimizer with learning rate $10^{-3}$ before the $10$-th, and $10^{-4}$
+  afterwards
+  \item global $\ell_2$-norm gradient clipping set at $\tfrac12$
+  \item training batches of size $128$ from a fixed randomly subset ($10^4$ images) of the training split
+  \item the multiplier of the Kullback-Leibler term in ELBO varies over $
+    C \in \{
+      \tfrac32 2^{-\tfrac{k}2} \colon k=2, \cdots, 38
+    \}
+  $
+  \item the sparsification threshold $\tau$ is set to $-\tfrac12$
+\end{itemize}
+Each experiment has been performed $5$ times to obtain a small sample of performance-compression
+values for each setting of $C$. By reevaluating each setting several times we can account
+for randomness in initialization of the uncompressed network at ``dense'', stochasticity of
+variational dropout layers, randomness of batch sequences during SDG, and non-determinism
+of computations on GPUs.
+
+Each figure shows the compression-accuracy trade-off of a particular method and input features
+for \textit{SimpleConvModel} and \textit{TwoLayerDenseModel} models for all four of the studied
+datasets (described in the main text): \emph{top-left} EMNIST-Letters, \emph{top-right} KMNIST,
+\emph{bottom-left} Fashion MNIST, and \emph{bottom-right} MNIST.
+%
+Figures \ref{fig:appendix__mnist-like__trade-off__ARD__fft}, \ref{fig:appendix__mnist-like__trade-off__VD__fft},
+\ref{fig:appendix__mnist-like__trade-off__ARD__raw}, and \ref{fig:appendix__mnist-like__trade-off__VD__raw}
+present $\real$ and $\cplx$ models with \emph{the same architecture}. We also report the
+trade-off comparison, when the argument by \citet{monning_evaluation_2018} for higher intrinsic
+capacity of $\cplx$-valued networks has been taken into account.
+%
+We compare $\real$ networks against $\tfrac12 \cplx$ with half the number of parameters
+for raw input features on figures \ref{fig:appendix__cmp__mnist-like__trade-off__ARD__raw},
+and \ref{fig:appendix__cmp__mnist-like__trade-off__VD__raw}, and $2 \real$ with
+double the number of parameters against $\cplx$ for Fourier input features on figures
+\ref{fig:appendix__cmp__mnist-like__trade-off__ARD__fft} and
+\ref{fig:appendix__cmp__mnist-like__trade-off__VD__fft}.
+
+The following observations can be made from the conducted experiment:
+\begin{itemize}
+  \item $\cplx$-valued networks do not have as much spare capacity as $2 \real$ due to
+  constants imposed by multiplication in $\cplx$ numbers (\ref{fig:appendix__cmp__mnist-like__trade-off__ARD__raw},
+  \ref{fig:appendix__cmp__mnist-like__trade-off__VD__raw})
+  \item Variational Dropout and Automatic Relevance Determination offer similar compression-performance
+  trade-off, with negligibly lower compression by the latter (both $\real$ and $\cplx$ versions,
+  e.g. figures \ref{fig:appendix__mnist-like__trade-off__ARD__raw} and \ref{fig:appendix__mnist-like__trade-off__VD__raw})
+  \item smaller networks tend to be less compressible (figures \ref{fig:appendix__cmp__mnist-like__trade-off__ARD__fft},
+  \ref{fig:appendix__cmp__mnist-like__trade-off__VD__fft})
+\end{itemize}
+
+\begin{figure}[b]
+  \centering
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__emnist_letters__fft__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__kmnist__fft__-0.5.pdf}
+  \end{subfigure} \\ %
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__fashionmnist__fft__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__mnist__fft__-0.5.pdf}
+  \end{subfigure}
+  \caption{%
+    The trade-off of ARD method for $\real$ and $\cplx$ models using Fourier features.
+  }
+  \label{fig:appendix__mnist-like__trade-off__ARD__fft}
+\end{figure}
+
+\begin{figure}[b]
+  \centering
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__emnist_letters__fft__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__kmnist__fft__-0.5.pdf}
+  \end{subfigure} \\ %
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__fashionmnist__fft__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__mnist__fft__-0.5.pdf}
+  \end{subfigure}
+  \caption{%
+    The trade-off of VD method for $\real$ and $\cplx$ models using Fourier features.
+  }
+  \label{fig:appendix__mnist-like__trade-off__VD__fft}
+\end{figure}
+
+\begin{figure}[b]
+  \centering
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__emnist_letters__raw__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__kmnist__raw__-0.5.pdf}
+  \end{subfigure} \\%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__fashionmnist__raw__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__mnist__raw__-0.5.pdf}
+  \end{subfigure}
+  \caption{%
+    The trade-off of ARD method for $\real$ and $\cplx$ models using raw features.
+  }
+  \label{fig:appendix__mnist-like__trade-off__ARD__raw}
+\end{figure}
+
+\begin{figure}[b]
+  \centering
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__emnist_letters__raw__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__kmnist__raw__-0.5.pdf}
+  \end{subfigure} \\%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__fashionmnist__raw__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__mnist__raw__-0.5.pdf}
+  \end{subfigure}
+  \caption{%
+    The trade-off of VD method for $\real$ and $\cplx$ models using raw features.
+  }
+  \label{fig:appendix__mnist-like__trade-off__VD__raw}
+\end{figure}
+
+\begin{figure}[b]
+  \centering
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__emnist_letters__fft__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__kmnist__fft__-0.5.pdf}
+  \end{subfigure} \\ %
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__fashionmnist__fft__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__mnist__fft__-0.5.pdf}
+  \end{subfigure}
+  \caption{%
+    The trade-off of ARD method for $2\real$ and $\cplx$ models using Fourier features.
+  }
+  \label{fig:appendix__cmp__mnist-like__trade-off__ARD__fft}
+\end{figure}
+
+\begin{figure}[b]
+  \centering
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__emnist_letters__fft__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__kmnist__fft__-0.5.pdf}
+  \end{subfigure} \\ %
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__fashionmnist__fft__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__mnist__fft__-0.5.pdf}
+  \end{subfigure}
+  \caption{%
+    The trade-off of VD method for $2\real$ and $\cplx$ models using Fourier features.
+  }
+  \label{fig:appendix__cmp__mnist-like__trade-off__VD__fft}
+\end{figure}
+
+\begin{figure}[b]
+  \centering
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__emnist_letters__raw__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__kmnist__raw__-0.5.pdf}
+  \end{subfigure} \\%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__fashionmnist__raw__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__mnist__raw__-0.5.pdf}
+  \end{subfigure}
+  \caption{%
+    The trade-off of ARD method for $\real$ and $\tfrac12\cplx$ models using raw features.
+  }
+  \label{fig:appendix__cmp__mnist-like__trade-off__ARD__raw}
+\end{figure}
+
+\begin{figure}[b]
+  \centering
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__emnist_letters__raw__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__kmnist__raw__-0.5.pdf}
+  \end{subfigure} \\%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__fashionmnist__raw__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__mnist__raw__-0.5.pdf}
+  \end{subfigure}
+  \caption{%
+    The trade-off of VD method for $\real$ and $\tfrac12\cplx$ models using raw features.
+  }
+  \label{fig:appendix__cmp__mnist-like__trade-off__VD__raw}
+\end{figure}
+
+\begin{figure}[b]
+  \centering
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/legacy__VD__emnist_letters__fft__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/legacy__VD__kmnist__fft__-0.5.pdf}
+  \end{subfigure} \\%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/legacy__VD__fashionmnist__fft__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/legacy__VD__mnist__fft__-0.5.pdf}
+  \end{subfigure}
+  \caption{%
+    The trade-off of VD method for $\real$ and $\cplx$ models using Fourier features (main text).
+  }
+  \label{fig:paper__mnist-like__trade-off__VD__fft}
+\end{figure}
+
+\begin{figure}[b]
+  \centering
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/legacy__VD__emnist_letters__raw__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/legacy__VD__kmnist__raw__-0.5.pdf}
+  \end{subfigure} \\%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/legacy__VD__fashionmnist__raw__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/legacy__VD__mnist__raw__-0.5.pdf}
+  \end{subfigure}
+  \caption{%
+    The trade-off of VD method for $\real$ and $\cplx$ models using raw features (main text).
+  }
+  \label{fig:paper__mnist-like__trade-off__VD__raw}
+\end{figure}
+
+% subsection mnist_like_experiments (end)
+
+\clearpage
+
+\subsection{CIFAR10 experiments} % (fold)
+\label{sub:cifar_experiments}
+
+In addition to the results reported in the main paper, we conduct additional experiment
+on CIFAR10 and VGG16 with a much more slowly annealed learning rate. Similar to MNIST-like
+experiments, we start with the rate set to $10^{-3}$ and then reduce it by $10$ after the
+$10$-the epoch. In summary, for the CIFAR10 experiments we reuse the set-up with the following
+changes:
+\begin{itemize}
+  \item we allocate $20$, $40$, and $20$ epochs to each stage
+  \item the weight of the KL divergence term varies over a smaller grid $
+    C \in \{
+      \tfrac32 2^{-\tfrac{k}2} \colon k=7, \cdots, 15
+    \}
+  $
+  \item we use full $50$k training split of the CIFAR10 dataset for training and raw color
+  features only
+  \item dataset is randomly augmented: every image within a batch of size $128$ is randomly
+  cropped and flipped horizontally
+\end{itemize}
+Random cropping is done by zero-padding each side of a $32\times 32$ image by four pixels
+and then a extracting a random $32\times 32$ patch from the $40\times 40$ intermediate image.
+
+We experiment with $\real$ VGG16 network \citep{simonyan_very_2015} and its $\cplx$-valued
+variant, which straightforwardly replaces $\real$ layers with their $\cplx$ counterparts.
+
+\begin{figure}[htb]
+  \centering
+  \includegraphics[width=\linewidth]{figure__cifar__trade-off/appendix__augmentedcifar10__raw__-0.5.pdf}
+  \caption{%
+    The compression-accuracy trade-off for $\real$ and $\cplx$ VGG16 using raw input features.
+  }
+  \label{fig:appendix__cifar__trade-off__VGG16__raw}
+\end{figure}
+
+% subsection cifar_experiments (end)
 
@@
 
-\subsection{Other MNIST-like datasets} % (fold)
-\label{sub:other_mnist_like_datasets}
-
-We provide the figures of the MNIST-like experiments, omitted from the main paper
-due to size limitations.
-
-\begin{figure}[!h]
-  \centering
-  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
-    \centering
-    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/legacy__VD__fashionmnist__fft__-0.5.pdf}
-  \end{subfigure} \\%
-  % \hfill
-  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
-    \centering
-    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/legacy__VD__fashionmnist__raw__-0.5.pdf}
-  \end{subfigure}
-  \caption{%
-    The compression-accuracy trade-off on the letters part of the Fashion MNIST dataset.
-    (\textit{top}) \texttt{fft} features, (\textit{bottom}) \texttt{raw} features.
-  }
-  \label{fig:mnist-like__trade-off__fashionmnist}
-\end{figure}
-
-\begin{figure}[!h]
-  \centering
-  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
-    \centering
-    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/legacy__VD__mnist__fft__-0.5.pdf}
-  \end{subfigure} \\%
-  % \hfill
-  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
-    \centering
-    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/legacy__VD__mnist__raw__-0.5.pdf}
-  \end{subfigure}
-  \caption{%
-    The compression-accuracy trade-off on the letters part of the MNIST dataset.
-    (\textit{top}) \texttt{fft} features, (\textit{bottom}) \texttt{raw} features.
-  }
-  \label{fig:mnist-like__trade-off__mnist}
-\end{figure}
-
-% subsection other_mnist_like_datasets (end)
-
-\clearpage
-
-\subsection{MNIST-like experiments} % (fold)
-\label{sub:mnist_like_experiments}
-
-To supplement the results, reported in the main text (figures \ref{fig:paper__mnist-like__trade-off__VD__fft}
-and \ref{fig:paper__mnist-like__trade-off__VD__raw}), we conduct additional experiments
-with the same basic set-up, but over a finer grid of KL-divergence term coefficients.
-%
-These experiments lend further evidence in support of the conclusions, drawn in the main
-paper, namely, that the $\cplx$-valued extension of the $\real$-valued variational dropout
-can offer significant compression levels without much loss in performance. At the same
-time, the test performance of both $\real$ and $\cplx$ compressed networks benefits from
-an extra fine-tuning stage, during which sparsity masks are fixed.
-
-One intriguing observation, is that on MNIST-like images the dense network, taking Fourier
-features on input, exhibits gradually improving test-split performance. This is in stark
-contrast to raw image input, where the performance stays at one level in the small compression
-regime, and then gradually decays at high compression levels. Noteworthy is the presence
-of a trough in the pre fine-tuning stage performance in the small compression regime on figures
-\ref{fig:appendix__mnist-like__trade-off__ARD__raw},
-\ref{fig:appendix__mnist-like__trade-off__VD__raw},
-\ref{fig:appendix__cmp__mnist-like__trade-off__ARD__raw},
-and \ref{fig:appendix__cmp__mnist-like__trade-off__VD__raw}, which then slowly disappears
-as compression increases.
-
-The following scatter plots depict the samples from the compression-performance trade-off
-curve of simple networks studied in the experiments on the MNIST-like datasets. Transparent
-horizontal bands on each plot represent min-max performance spread of an uncompressed
-network on the test split. The points illustrate the final trade-off of the compressed
-networks after fine-tuning, while their tails show the performance gain or loss due to
-the fine-tuning.
-
-We recap the set-up of each additional experiment on MNIST-like datasets:
-\begin{itemize}
-  \item staged training, with weight and optimizer state transfer
-  \item $40$, $75$, and $40$ epochs for ``dense'', ``sparsify'', and ``fine-tune'' stagers, respectively
-  \item ADAM optimizer with learning rate $10^{-3}$ before the $10$-th, and $10^{-4}$
-  afterwards
-  \item global $\ell_2$-norm gradient clipping set at $\tfrac12$
-  \item training batches of size $128$ from a fixed randomly subset ($10^4$ images) of the training split
-  \item the multiplier of the Kullback-Leibler term in ELBO varies over $
-    C \in \{
-      \tfrac32 2^{-\tfrac{k}2} \colon k=2, \cdots, 38
-    \}
-  $
-  \item the sparsification threshold $\tau$ is set to $-\tfrac12$
-\end{itemize}
-Each experiment has been performed $5$ times to obtain a small sample of performance-compression
-values for each setting of $C$. By reevaluating each setting several times we can account
-for randomness in initialization of the uncompressed network at ``dense'', stochasticity of
-variational dropout layers, randomness of batch sequences during SDG, and non-determinism
-of computations on GPUs.
-
-Each figure shows the compression-accuracy trade-off of a particular method and input features
-for \textit{SimpleConvModel} and \textit{TwoLayerDenseModel} models for all four of the studied
-datasets (described in the main text): \emph{top-left} EMNIST-Letters, \emph{top-right} KMNIST,
-\emph{bottom-left} Fashion MNIST, and \emph{bottom-right} MNIST.
-%
-Figures \ref{fig:appendix__mnist-like__trade-off__ARD__fft}, \ref{fig:appendix__mnist-like__trade-off__VD__fft},
-\ref{fig:appendix__mnist-like__trade-off__ARD__raw}, and \ref{fig:appendix__mnist-like__trade-off__VD__raw}
-present $\real$ and $\cplx$ models with \emph{the same architecture}. We also report the
-trade-off comparison, when the argument by \citet{monning_evaluation_2018} for higher intrinsic
-capacity of $\cplx$-valued networks has been taken into account.
-%
-We compare $\real$ networks against $\tfrac12 \cplx$ with half the number of parameters
-for raw input features on figures \ref{fig:appendix__cmp__mnist-like__trade-off__ARD__raw},
-and \ref{fig:appendix__cmp__mnist-like__trade-off__VD__raw}, and $2 \real$ with
-double the number of parameters against $\cplx$ for Fourier input features on figures
-\ref{fig:appendix__cmp__mnist-like__trade-off__ARD__fft} and
-\ref{fig:appendix__cmp__mnist-like__trade-off__VD__fft}.
-
-The following observations can be made from the conducted experiment:
-\begin{itemize}
-  \item $\cplx$-valued networks do not have as much spare capacity as $2 \real$ due to
-  constants imposed by multiplication in $\cplx$ numbers (\ref{fig:appendix__cmp__mnist-like__trade-off__ARD__raw},
-  \ref{fig:appendix__cmp__mnist-like__trade-off__VD__raw})
-  \item Variational Dropout and Automatic Relevance Determination offer similar compression-performance
-  trade-off, with negligibly lower compression by the latter (both $\real$ and $\cplx$ versions,
-  e.g. figures \ref{fig:appendix__mnist-like__trade-off__ARD__raw} and \ref{fig:appendix__mnist-like__trade-off__VD__raw})
-  \item smaller networks tend to be less compressible (figures \ref{fig:appendix__cmp__mnist-like__trade-off__ARD__fft},
-  \ref{fig:appendix__cmp__mnist-like__trade-off__VD__fft})
-\end{itemize}
-
-\begin{figure}[b]
-  \centering
-  \begin{subfigure}[b]{0.5\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__emnist_letters__fft__-0.5.pdf}
-  \end{subfigure}%
-  \begin{subfigure}[b]{0.5\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__kmnist__fft__-0.5.pdf}
-  \end{subfigure} \\ %
-  \begin{subfigure}[b]{0.5\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__fashionmnist__fft__-0.5.pdf}
-  \end{subfigure}%
-  \begin{subfigure}[b]{0.5\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__mnist__fft__-0.5.pdf}
-  \end{subfigure}
-  \caption{%
-    The trade-off of ARD method for $\real$ and $\cplx$ models using Fourier features.
-  }
-  \label{fig:appendix__mnist-like__trade-off__ARD__fft}
-\end{figure}
-
-\begin{figure}[b]
-  \centering
-  \begin{subfigure}[b]{0.5\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__emnist_letters__fft__-0.5.pdf}
-  \end{subfigure}%
-  \begin{subfigure}[b]{0.5\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__kmnist__fft__-0.5.pdf}
-  \end{subfigure} \\ %
-  \begin{subfigure}[b]{0.5\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__fashionmnist__fft__-0.5.pdf}
-  \end{subfigure}%
-  \begin{subfigure}[b]{0.5\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__mnist__fft__-0.5.pdf}
-  \end{subfigure}
-  \caption{%
-    The trade-off of VD method for $\real$ and $\cplx$ models using Fourier features.
-  }
-  \label{fig:appendix__mnist-like__trade-off__VD__fft}
-\end{figure}
-
-\begin{figure}[b]
-  \centering
-  \begin{subfigure}[b]{0.5\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__emnist_letters__raw__-0.5.pdf}
-  \end{subfigure}%
-  \begin{subfigure}[b]{0.5\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__kmnist__raw__-0.5.pdf}
-  \end{subfigure} \\%
-  \begin{subfigure}[b]{0.5\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__fashionmnist__raw__-0.5.pdf}
-  \end{subfigure}%
-  \begin{subfigure}[b]{0.5\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__mnist__raw__-0.5.pdf}
-  \end{subfigure}
-  \caption{%
-    The trade-off of ARD method for $\real$ and $\cplx$ models using raw features.
-  }
-  \label{fig:appendix__mnist-like__trade-off__ARD__raw}
-\end{figure}
-
-\begin{figure}[b]
-  \centering
-  \begin{subfigure}[b]{0.5\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__emnist_letters__raw__-0.5.pdf}
-  \end{subfigure}%
-  \begin{subfigure}[b]{0.5\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__kmnist__raw__-0.5.pdf}
-  \end{subfigure} \\%
-  \begin{subfigure}[b]{0.5\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__fashionmnist__raw__-0.5.pdf}
-  \end{subfigure}%
-  \begin{subfigure}[b]{0.5\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__mnist__raw__-0.5.pdf}
-  \end{subfigure}
-  \caption{%
-    The trade-off of VD method for $\real$ and $\cplx$ models using raw features.
-  }
-  \label{fig:appendix__mnist-like__trade-off__VD__raw}
-\end{figure}
-
-\begin{figure}[b]
-  \centering
-  \begin{subfigure}[b]{0.5\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__emnist_letters__fft__-0.5.pdf}
-  \end{subfigure}%
-  \begin{subfigure}[b]{0.5\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__kmnist__fft__-0.5.pdf}
-  \end{subfigure} \\ %
-  \begin{subfigure}[b]{0.5\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__fashionmnist__fft__-0.5.pdf}
-  \end{subfigure}%
-  \begin{subfigure}[b]{0.5\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__mnist__fft__-0.5.pdf}
-  \end{subfigure}
-  \caption{%
-    The trade-off of ARD method for $2\real$ and $\cplx$ models using Fourier features.
-  }
-  \label{fig:appendix__cmp__mnist-like__trade-off__ARD__fft}
-\end{figure}
-
-\begin{figure}[b]
-  \centering
-  \begin{subfigure}[b]{0.5\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__emnist_letters__fft__-0.5.pdf}
-  \end{subfigure}%
-  \begin{subfigure}[b]{0.5\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__kmnist__fft__-0.5.pdf}
-  \end{subfigure} \\ %
-  \begin{subfigure}[b]{0.5\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__fashionmnist__fft__-0.5.pdf}
-  \end{subfigure}%
-  \begin{subfigure}[b]{0.5\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__mnist__fft__-0.5.pdf}
-  \end{subfigure}
-  \caption{%
-    The trade-off of VD method for $2\real$ and $\cplx$ models using Fourier features.
-  }
-  \label{fig:appendix__cmp__mnist-like__trade-off__VD__fft}
-\end{figure}
-
-\begin{figure}[b]
-  \centering
-  \begin{subfigure}[b]{0.5\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__emnist_letters__raw__-0.5.pdf}
-  \end{subfigure}%
-  \begin{subfigure}[b]{0.5\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__kmnist__raw__-0.5.pdf}
-  \end{subfigure} \\%
-  \begin{subfigure}[b]{0.5\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__fashionmnist__raw__-0.5.pdf}
-  \end{subfigure}%
-  \begin{subfigure}[b]{0.5\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__mnist__raw__-0.5.pdf}
-  \end{subfigure}
-  \caption{%
-    The trade-off of ARD method for $\real$ and $\tfrac12\cplx$ models using raw features.
-  }
-  \label{fig:appendix__cmp__mnist-like__trade-off__ARD__raw}
-\end{figure}
-
-\begin{figure}[b]
-  \centering
-  \begin{subfigure}[b]{0.5\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__emnist_letters__raw__-0.5.pdf}
-  \end{subfigure}%
-  \begin{subfigure}[b]{0.5\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__kmnist__raw__-0.5.pdf}
-  \end{subfigure} \\%
-  \begin{subfigure}[b]{0.5\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__fashionmnist__raw__-0.5.pdf}
-  \end{subfigure}%
-  \begin{subfigure}[b]{0.5\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__mnist__raw__-0.5.pdf}
-  \end{subfigure}
-  \caption{%
-    The trade-off of VD method for $\real$ and $\tfrac12\cplx$ models using raw features.
-  }
-  \label{fig:appendix__cmp__mnist-like__trade-off__VD__raw}
-\end{figure}
-
-\begin{figure}[b]
-  \centering
-  \begin{subfigure}[b]{0.5\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/legacy__VD__emnist_letters__fft__-0.5.pdf}
-  \end{subfigure}%
-  \begin{subfigure}[b]{0.5\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/legacy__VD__kmnist__fft__-0.5.pdf}
-  \end{subfigure} \\%
-  \begin{subfigure}[b]{0.5\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/legacy__VD__fashionmnist__fft__-0.5.pdf}
-  \end{subfigure}%
-  \begin{subfigure}[b]{0.5\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/legacy__VD__mnist__fft__-0.5.pdf}
-  \end{subfigure}
-  \caption{%
-    The trade-off of VD method for $\real$ and $\cplx$ models using Fourier features (main text).
-  }
-  \label{fig:paper__mnist-like__trade-off__VD__fft}
-\end{figure}
-
-\begin{figure}[b]
-  \centering
-  \begin{subfigure}[b]{0.5\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/legacy__VD__emnist_letters__raw__-0.5.pdf}
-  \end{subfigure}%
-  \begin{subfigure}[b]{0.5\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/legacy__VD__kmnist__raw__-0.5.pdf}
-  \end{subfigure} \\%
-  \begin{subfigure}[b]{0.5\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/legacy__VD__fashionmnist__raw__-0.5.pdf}
-  \end{subfigure}%
-  \begin{subfigure}[b]{0.5\textwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/legacy__VD__mnist__raw__-0.5.pdf}
-  \end{subfigure}
-  \caption{%
-    The trade-off of VD method for $\real$ and $\cplx$ models using raw features (main text).
-  }
-  \label{fig:paper__mnist-like__trade-off__VD__raw}
-\end{figure}
-
-% subsection mnist_like_experiments (end)
-
-\clearpage
-
-\subsection{CIFAR10 experiments} % (fold)
-\label{sub:cifar_experiments}
-
-In addition to the results reported in the main paper, we conduct additional experiment
-on CIFAR10 and VGG16 with a much more slowly annealed learning rate. Similar to MNIST-like
-experiments, we start with the rate set to $10^{-3}$ and then reduce it by $10$ after the
-$10$-the epoch. In summary, for the CIFAR10 experiments we reuse the set-up with the following
-changes:
-\begin{itemize}
-  \item we allocate $20$, $40$, and $20$ epochs to each stage
-  \item the weight of the KL divergence term varies over a smaller grid $
-    C \in \{
-      \tfrac32 2^{-\tfrac{k}2} \colon k=7, \cdots, 15
-    \}
-  $
-  \item we use full $50$k training split of the CIFAR10 dataset for training and raw color
-  features only
-  \item dataset is randomly augmented: every image within a batch of size $128$ is randomly
-  cropped and flipped horizontally
-\end{itemize}
-Random cropping is done by zero-padding each side of a $32\times 32$ image by four pixels
-and then a extracting a random $32\times 32$ patch from the $40\times 40$ intermediate image.
-
-We experiment with $\real$ VGG16 network \citep{simonyan_very_2015} and its $\cplx$-valued
-variant, which straightforwardly replaces $\real$ layers with their $\cplx$ counterparts.
-
-\begin{figure}[htb]
-  \centering
-  \includegraphics[width=\linewidth]{figure__cifar__trade-off/appendix__augmentedcifar10__raw__-0.5.pdf}
-  \caption{%
-    The compression-accuracy trade-off for $\real$ and $\cplx$ VGG16 using raw input features.
-  }
-  \label{fig:appendix__cifar__trade-off__VGG16__raw}
-\end{figure}
-
-% subsection cifar_experiments (end)
-
 % section appendix (end)

### 2020-03-16 paper/paper.tex
minor typos

@@
 We set $\beta = 2$ to make the divergence term depend only on $\alpha$ and add $\gamma$
-so that the right-hand side is nonegative \citep[eq.(84)]{lapidoth_capacity_2003}.
+so that the right-hand side is nonnegative \citep[eq.(84)]{lapidoth_capacity_2003}.
 %
@@
 MusicNet \citep{thickstun_learning_2017} is an annotated audio dataset, consisting of $330$
-musical compositions. Folowing \citet{trabelsi_deep_2017}, we use it in automatic music
+musical compositions. Following \citet{trabelsi_deep_2017}, we use it in automatic music
 transcription task and study the $1d$ VGG-like $\cplx$-convent proposed therein. Similarly to
@@
     % \biggr) \log{(x)} dx
-    % = [\text{ absolute summability and Fubini, or any other conv. thm for integrals of non-negative integrals}]
+    % = [\text{ absolute summability and Fubini, or any other conv. thm for integrals of nonnegative integrals}]
     % = e^{- \tfrac\lambda2} \sum_{n \geq 0}

### 2020-03-17 paper/paper.tex
thorough proofread 1 (sections 1-3) * renamed section dropout -> Variational Dropout * fixed real-ard kl-div eq (8), cleaned out dubious and imprecise statements (em-algo) * removed excessive citations and repeated rewordings in intro and VB * improved language and coherence in Bayes-related narrative (VI, VB, estimator etc.), reworded and rearranged paragraphs for clearer exposition

@@
 and optimization theory specific to deep networks, deploying in actual embedded hardware
-remains a challenge due to storage, real-time throughput, and arithmetic (computational)
-complexity restrictions \citep{he_amc:_2018}. Therefore, compression methods for achieving
-high model sparsity and numerical efficiency without losing much in performance are
-especially relevant.
+remains a challenge due to storage, real-time throughput, and arithmetic complexity
+restrictions \citep{he_amc:_2018}. Therefore, compression methods for achieving high
+model sparsity and numerical efficiency without losing much in performance are especially
+relevant.
 % Solving the storage and artihmetic constraints encourages development of model compression
@@
 in $\cplx$ field. Despite inherently higher arithmetic complexity, which stems from up to four
-floating point operations per single $\cplx$ multiplication \citep{monning_evaluation_2018}
+floating point operations per single $\cplx$ multiplication
 $\cplx$-arithmetic reduces ineffective degrees of freedom in comparison with an analogous
@@
 
-% on dropout
-Dropout \citep{hinton_improving_2012} prevents overfitting by injecting multiplicative
-binary noise into layer's weights, which breaks up co-adaptations that could occur
-during training. \citet{wang_fast_2013} argue that the overall effect of binary dropout
-on the intermediate outputs via the Central Limit Theorem can be approximated by a Gaussian
-with weight-input dependent mean and variance. \citet{srivastava_dropout_2014} propose
-using independent $\mathcal{N}(1,1)$ noise, arguing that higher entropy of a Gaussian has
-better regularizing effect. In multitask learning \citet{cheung_superposition_2019}
-have shown the possibility of storing task-specific parameters in non-destructive superposition
-within a single network. Their argument implies that if the single task setting is viewed
-as replicated multitask learning, then by sampling uncorrelated weight masks dropout acts
-as a superposition method, which better utilizes the learning capacity of the network.
-% many identical copies of the same task; \cite[Appendix A.1]{cheung_superposition_2019}
-% (fast dropout gauss-approx) wang-manning.tex
-% (gauss dropout) srivastava-et-al.tex
-
 % segue into bayesian inference
-Bayesian inference is a very rich field with a large body of research and techniques that
-enable practical quantification of predictive, parameter, or model uncertainty and its 
-propagation into solutions of the problems of interest.
-%
-Dropout resembles averaging models with shared parameters: each model is weighted equally
-since masks are randomly sampled, unlike Bayesian model averaging, which weighs according to
-the posterior distribution. \citet{kingma_variational_2015} specifically consider dropout
-as a Bayesian Inference technique: a principled framework of reasoning about uncertainty,
-which updates prior beliefs in accordance with the likelihood of empirical observations
-into posterior belief. Bayesian methods with suitable modelling and prior assumptions, such
-as Variational Dropout, can be used towards model sparsification
-\citep{kingma_variational_2015,molchanov_variational_2017,kharitonov_variational_2018}.
+Bayesian Inference is a principled framework of reasoning about uncertainty, which updates
+prior beliefs in accordance with the likelihood of empirical observations into posterior
+belief. Under suitable modelling and distributional assumptions, Bayesian methods can be
+used towards model sparsification, e.g. Variational Dropout \citep{kingma_variational_2015,molchanov_variational_2017}.
 
 % (sparsity tech large-scale models) gale-elsen-hooker.tex
-\citet{gale_state_2019} compare variational dropout \citep{kingma_variational_2015},
-magnitude pruning, and $\ell_0$ regularization \citep{louizos_learning_2017} on large-scale
-models. The latter is a probabilistic regularization method, which penalizes the expected
-number of non-zero entries in $[0, 1]$-valued stochastic parameter masks with learnable
-hard-concrete distribution with an atom at $0$ \citep{maddison_concrete_2016,jang_categorical_2017}.
-Their results suggest that although variational dropout may achieve good accuracy-sparsity balance
-and outperform pruning and $\ell_0$ on the studied architectures, pruning is preferable for
-its simplicity and speed. They also observe that, despite dropout showing more variable
-performance than magnitude pruning, it induces non-uniform sparsity throughout the model,
-which has been shown by \citet{he_amc:_2018} to be essential for superior compression.
+\citet{gale_state_2019} compare Variational Dropout, magnitude pruning, and $\ell_0$
+regularization \citep{louizos_learning_2017} on large-scale models. The latter is a
+probabilistic regularization method, which penalizes the expected number of non-zero
+entries in $[0, 1]$-valued stochastic parameter masks with learnable hard-concrete
+distribution with atoms at $0$ and $1$ \citep{maddison_concrete_2016,jang_categorical_2017}.
+Their results suggest that Variational Dropout may achieve good accuracy-sparsity balance
+and outperform pruning and $\ell_0$ in deep architectures, although pruning is prefered for
+simplicity, stability and speed. They also observe that dropout induces non-uniform sparsity
+throughout the model, which \citet{he_amc:_2018} has shown to be essential for superior
+compression.
 % Magnitude pruning induces user-specified sparsity distributions.
@@
 Inspired by variational and stochastic sparsification techniques we extend Bayesian dropout
-for $\cplx$-valued networks. We assess the performance-compression trade-off of the proposed
+to $\cplx$-valued networks. We assess the performance-compression trade-off of the proposed
 Bayesian technique by conducting a large-scale numerical study of $\cplx$-valued networks
 on two tasks: image recognition on MNIST-like and CIFAR10 datasets and music transcription
-on MusicNet \citep{thickstun_learning_2017}. We reproduce the state-of-the-art result by
-\citet{trabelsi_deep_2017} for $\cplx$-valued networks on the latter with $\approx 5\%$
-of remaining non-zero parameters.
+on MusicNet \citep{thickstun_learning_2017}.
 
@@
 where we consider different variational approximations and priors, outline the tricks
-and derive expressions for the divergence term. In sec.~\ref{sec:experiments} we evaluate
-the sparsification rate, compare the resulting performance of various $\cplx$-networks
+and derive the penalty terms in the evidence lower bound. In sec.~\ref{sec:experiments}
+we evaluate the sparsification rate, compare the resulting performance of various $\cplx$-networks
 proposed in prior work, and discuss the outcomes.
@@
 
-The posterior distribution itself is intractable, save for the relatively simple cases, and
-therefore exact inference is traded for tractability and scalability offered by Variational
-Inference. Instead of deriving $p(\omega \mid D)$ using the Bayes rule, this approach recasts
-posterior inference into variational optimization problem: finding $q$ that is close to
-$p(\omega \mid D)$ in terms of a proximity score $\rho$
+Save for the relatively simple cases, the posterior distribution is intractable, and
+therefore exactness Bayesian Inference is traded for tractability and scalability of
+Variational Bayesian Inference. Instead of deriving the posterior $p(\omega \mid D)$,
+this approach postulates an optimization problem for finding an approximation $q$,
+which is close to $p(\omega \mid D)$ in terms of a proximity score $\rho$
 \begin{equation}  \label{eq:variational-progam}
@@
   \mathcal{Q} = \{Q_\theta(d\omega) \colon \theta \in \Theta\}
-$, $\theta$ -- generic variational parameter. The class $\mathcal{Q}$ is picked so that
-its members have tractable densities $
+$, $\theta$ -- generic variational parameter. The variational approximation class
+$\mathcal{Q}$ is chosen so that its members have tractable densities $
   q_\theta(\omega) d\omega
@@
   \omega \mapsto \nabla_\theta \log q_\theta(\omega)
-$ \citep{williams_simple_1992} or can be represented as differentiable transformations
-of non-parametric noise \citep{kingma_auto-encoding_2014,figurnov_implicit_2019}.
-% (reparameterization trick, pathwise gradieent) $q_{\theta}(d\omega)$ is a push-forward
+$ or can be represented as differentiable transformations of non-parametric noise
+\citep{williams_simple_1992,kingma_auto-encoding_2014,figurnov_implicit_2019}.
+% (reparameterization trick, pathwise gradient) $q_{\theta}(d\omega)$ is a push-forward
 % of $p(d\varepsilon)$ by a differentiable map $g(\varepsilon; \theta)$.
@@
 %
-The natural choice for $\rho$ is Kullback-Leibler divergence of density $q$ from $p$,
+The most common choice for $\rho$ is Kullback-Leibler divergence of density $q$ from $p$,
 \begin{equation}  \label{eq:kl-div-def}
@@
 \end{multline}
-This identity yields an equivalent problem for \eqref{eq:variational-progam}:
-maximizing the \textit{evidence lower bound} (ELBO)
+This leads to an equivalent problem for \eqref{eq:variational-progam} of maximizing
+the \textit{evidence lower bound} (ELBO)
 \begin{equation}  \label{eq:elbo_general}
@@
 \end{equation}
-where the prior and likelihood are allowed to depend on explicit parameters. The most
-commonly used algorithm to optimize \eqref{eq:elbo_general} is EM-algorithm. Other
-variational objectives are possible, provided $p(\omega \mid D)$ is probed only through
-$\log p(D \mid \omega)$ and $\log \pi(\omega)$ \citep{ranganath_operator_2018}.
+where $\lambda$, $\theta$ and $\phi$ are optimization parameters of the prior $\pi$,
+approximation $q$ and the likelihood $p(D\mid \omega)$, respectively. Other objectives
+are possible, besides \eqref{eq:elbo_general}, provided $p(\omega \mid D)$ is evaluated
+only through $\log p(D \mid \omega)$ and $\log \pi(\omega)$, \citep{ranganath_operator_2018}.
 
 \textit{Stochastic Gradient Variational Bayes} (SGVB), proposed by \citet{kingma_auto-encoding_2014},
-is a differentiable unbiased Monte-Carlo estimator of \eqref{eq:elbo_general}, which
-makes it possible to employ stochastic gradient-based optimization methods to solve
-\eqref{eq:variational-progam}. If $
+replaces the Variational objective \eqref{eq:elbo_general} by its unbiased differentiable
+Monte-Carlo estimator, which makes it possible to employ stochastic gradient optimization
+methods to solve \eqref{eq:variational-progam}. If $
   \omega \sim q_{\theta}
@@
   \omega = g(\varepsilon; \theta)
-$ for some non-parametric random variable $
+$ for some differentiable $
+  g(\varepsilon; \theta)
+$ and non-parametric random variable $
     \varepsilon \sim p_\varepsilon
-$ and differentiable $
-  g(\varepsilon; \theta)
-$, then the SGVB is
-\begin{equation}  \label{eq:sgvb}
+$, then the SGVB objective is
+\begin{equation}  \label{eq:sgvb_objective}
   \widetilde{\mathcal{L}}(\theta; \phi, \lambda)
@@
   (\varepsilon_{l})_{l=1}^L
-$ is an iid sample from $p_\varepsilon$. Intractable KL-divergence terms can be replaced
-by differentiable unbiased sampling estimators \citep{kingma_auto-encoding_2014}.
-%
-For the purposes of this study, we assume that the observed data is independent, and
-use minibatch version of \eqref{eq:sgvb} with $L=1$:
+$ is an iid sample from $p_\varepsilon$, the KL-divergence term replaced by unbiased
+differentiable finite sample estimator if it is intractable.
+%
+For the purposes of this study, we assume that the likelihood satisfies $
+  \log p_\phi(D\mid \omega)
+    = \sum_i \log p_\phi(z_i \mid \omega)
+$, i.e. the observed data $
+  D = (z_i)_{i=1}^N
+$ is conditionally independent, and consider \eqref{eq:sgvb_objective} with $L=1$
+and random mini-batches from $D$:
 \begin{equation}  \label{eq:elbo}
@@
     = - KL(q_{\theta} \| \pi_{\lambda})
-      + \frac{N}{M} \sum_{i=1}^M
-        \log p_{\phi}(z_i \mid g(\varepsilon_i; \theta))
+      + \frac{N}{M} \sum_{k=1}^M
+        \log p_{\phi}(z_{i_k} \mid g(\varepsilon_k; \theta))
     \,,
 \end{equation}
-for a random subsample $(z_i)_{i=1}^M$ from $D$ and iid $\varepsilon_i \sim p_\varepsilon$.
+for a random subsample $(z_{i_k})_{k=1}^M$ and iid $\varepsilon_k \sim p_\varepsilon$.
 %
@@
 
-\subsection{Dropout} % (fold)
-\label{sub:dropout}
-
-With a special family of posterior approximation, variational inference can be used as
-a regularization method and as a model sparsification technique. \citet{kingma_variational_2015}
-consider Dropout \citep{hinton_improving_2012}, DropConnect \citep{wan_regularization_2013},
-and Gaussian dropout \citep{srivastava_dropout_2014,wang_fast_2013} through the lens
-of Bayesian inference methods and propose \textit{Variational Dropout}. They argue that
+\subsection{Variational Dropout} % (fold)
+\label{sub:variational_dropout}
+
+With a special family of posterior approximation, Variational Inference can be used as
+a regularization method and as a model sparsification technique.
+
+% on dropout
+Dropout \citep{hinton_improving_2012} prevents overfitting by injecting multiplicative
+binary noise into layer's weights, which breaks up co-adaptations that could occur
+during training. \citet{wang_fast_2013} argue that the overall effect of binary dropout
+on the intermediate outputs via the Central Limit Theorem can be approximated by a Gaussian
+with weight-input dependent mean and variance. \citet{srivastava_dropout_2014} propose
+using independent $\mathcal{N}(1,1)$ noise, arguing that higher entropy of a Gaussian has
+better regularizing effect. In a recent study concerning multitask learning
+\citet{cheung_superposition_2019} have shown the possibility of storing task-specific
+parameters in non-destructive superposition within a single network. In particular, their
+argument implies that if the single task setting is viewed as multitask learning with
+replicated task, then by sampling uncorrelated binary masks Dropout acts as a superposition
+method, utilizing the learning capacity of the network better.
+% many identical copies of the same task; \cite[Appendix A.1]{cheung_superposition_2019}
+% (fast dropout gauss-approx) wang-manning.tex
+% (gauss dropout) srivastava-et-al.tex
+
+Dropout can be viewed as a Bayesian model averaging method, where models share parameters
+and are weighted equally. Thus, \citet{kingma_variational_2015} consider Dropout, DropConnect
+\citep{wan_regularization_2013}, and Gaussian dropout \citep{wang_fast_2013} through the
+lens of Bayesian Inference methods and propose \textit{Variational Dropout}. They argue that
 the multiplicative noise introduced by these methods induces a distribution equivalent to
@@
 $ iid from some $p_\theta(\xi)$.
-%
+
 % Binary dropout with rate $p \in (0, 1)$ uses $
@@
 % see p.6 sec 3.4 of kingma_variational_2015
-We independently verify their approximation against Monte-Carlo estimates for $\alpha$
-varying over a fine logarithmic grid and the exact expression for the derivative of
-\eqref{eq:improper-kl-div-real}, which we derive in appendix~\ref{sub:real-chisq-grad}.
+In appendix~\ref{sub:real-chisq-grad} we verify the value and the derivative of their
+approximation against the Monte-Carlo estimate of \eqref{eq:improper-kl-div-real} for $\alpha$
+varying over a fine logarithmic grid and the gradient of \eqref{eq:improper-kl-div-real},
+for which we obtain an exact expression.
 % (!) good for SGVB: gradient-based methods require unbiased gradient estimates
@@
 % derivative of an intractable function.
-
-Being the ratio of the squared mean to the effective variance, $\alpha_j$ regulates the
-relevance of the parameter $\omega_j$ it is associated to. Thus, \citet{molchanov_variational_2017}
-focus on the model sparsification capabilities of Variational Dropout, optimizing $\alpha$
-for each individual parameter. Flexibility in specification of $q_\theta$ enables structured
-dropout with shared $\alpha$ across groups of parameters $\omega$. Another Bayesian dropout
-method, called \textit{Automatic Relevance Determination}, has been developed in \citep{kharitonov_variational_2018}.
-The key difference is that the log-uniform factor $\pi(\omega_{ij})$ is replaced by a proper
-ARD Gaussian prior $
+The key role in the factorization is played by $\alpha_j$, which reflects the relevance
+of the parameter $\omega_j$ it is associated to, by being the ratio of its squared mean
+to its variance. Thus, \citet{molchanov_variational_2017} focus on the model sparsification
+capabilities of Variational Dropout, optimizing $\alpha$ for each individual parameter.
+\citet{kharitonov_variational_2018} address theoretical issues with improper priors and
+propose an alternative Bayesian Dropout method based on \textit{Automatic Relevance
+Determination} procedure. In essence, the log-uniform factor $\pi(\omega_{ij})$ is replaced by
+a proper ARD Gaussian prior $
   \mathcal{N}(0, \tau^{-1}_{ij})
 $ with learnable precision $\tau_{ij} > 0$. This method, known as \textit{Empirical Bayes},
-fits a prior distribution while performing variational inference. Maximizing \eqref{eq:elbo}
+fits a prior distribution while performing Variational Inference. Maximizing \eqref{eq:elbo}
 over $\tau$, holding other parameters fixed, yields $
@@
   KL(q_\theta \| \pi)
-    = \log{\bigl(1 + \tfrac1{\alpha} \bigr)}
+    = \tfrac12 \log{\bigl(1 + \tfrac1{\alpha} \bigr)}
     \,.
 \end{equation}
+Flexibility in specification of $q_\theta$ enables developing structured dropout with
+shared $\alpha$ across groups of parameters $\omega$.
 
@@
 \textit{local reparameterization trick} on the variance of the gradient of \eqref{eq:elbo}.
-This trick, proposed in \citep{wang_fast_2013} to speed up Gaussian dropout, utilizes the
-closure of Gaussians under affine transformations, thereby translating uncertainty from the
-global parameter noise to local noise in intermediate outputs within the network.
-%
-The stochastic output of a linear layer $
-  y = W^\top x + b
+Proposed by \citet{wang_fast_2013} to speed up Gaussian dropout, this trick translates
+uncertainty from parameters of the model to intermediate outputs within the network:
+the stochasticity of $
+  W \sim \prod_{ij} \mathcal{N}(\mu_{ij}, \alpha_{ij} \mu_{ij}^2)
+$ in a linear layer $
+  y = b + W^\top x
 $ with $
   W \in \mathbb{R}^{n\times m}
-$ and independent $
-  W_{ij} \sim \mathcal{N}(\mu_{ij}, \alpha_{ij} \mu_{ij}^2)
-$ is equivalent in distribution to
+$ is pushed to its output
 \begin{equation}  \label{eq:r-gauss-trick}
     y \sim \prod_i \mathcal{N}\Bigl(
-          \sum_j \mu_{ij} x_j + b_i,
+          b_i + \sum_j \mu_{ij} x_j,
           \sum_j \alpha_{ij} \mu_{ij}^2 x_j^2
@@
 \citet{kingma_variational_2015} show, that for the case of fully factorized Gaussian
-posterior approximations, the trick decorrelates ELBO estimates within the minibatch,
-making the gradient estimator $\nabla_\theta \tilde{\mathcal{L}}$ more statistically
-efficient. \citet{molchanov_variational_2017} propose an improvement by introducing
-\textit{additive noise parameterization}. They argue for rejecting the $(\mu, \alpha)$
-parameterization in favour of the equivalent $(\mu, \sigma^2)$, since the latter renders $
+posterior approximations, using \eqref{eq:r-gauss-trick} decorrelates the estimators
+\eqref{eq:elbo} within the mini-batch and makes the gradient estimator $
+  \nabla_\theta \tilde{\mathcal{L}}
+$ more statistically efficient. Specifically for the problem of selecting relevant parameters
+\citet{molchanov_variational_2017} further improve the efficiency of the estimator of the $
   \nabla_\mu \tilde{\mathcal{L}}
-$ independent from the local output noise, injected by the trick \eqref{eq:r-gauss-trick},
-and further stabilizes gradients in SGVB \eqref{eq:elbo}. The relevance $\alpha$ is
+$ by introducing \textit{additive noise parameterization}. They revert the $(\mu, \alpha)$
+parameterization back to the equivalent $(\mu, \sigma^2)$, since it stabilizes gradients
+of SGVB \eqref{eq:elbo}, by rendering the gradient with respect to $\mu$ independent from
+the local output noise, injected by \eqref{eq:r-gauss-trick}. The relevance $\alpha$ is
 calculated using the ratio $
@@
 
-In this section we briefly review $\cplx$-valued networks, and their distinction from the
-ordinary $\real$-valued networks.
-
-\citet{trabelsi_deep_2017} outline the building blocks for deep $\cplx$-valued networks
-and describe suitable representation and operations including convolutional and dense layers,
-$\cplx$-valued activations, complex batch-normalization and suitable weight initialization.
-Their approach transforms a complex-valued network into an intricately connected $\real$-valued
-computational graph that respects $\cplx$-arithmetic.
+Complex networks are, in general, non-holomorphic, i.e. not $\cplx$-differentiable, which is
+exacerbated by the loss being real-valued. Indeed a $\cplx$-differentiable real-valued function is
+necessarily trivial by Cauchy-Riemann conditions. This issue is dealt with by employing Wirtinger,
+or $\cplx\real$ calculus, which generalizes holomorphic calculus to non-holomorphic functions
+of $\cplx$-argument \citep{adali_complex-valued_2011,boeddeker_computation_2019}. It satisfies
+the product and chain rules, respects complex conjugation and linearity, but most importantly the
+$\cplx\real$-differential of a function on $\cplx$ coincides with its classical differential as
+a function on $\real^2$. Essentially, it allows straightforward retrofiting of $\cplx$-valued
+networks into existing $\real$ deep learning auto-differentiation frameworks. It was considered
+as a basis for $\cplx$ version of back-propagation by \citet{benvenuto_complex_1992}, (see
+appendix~\ref{sub:wirtinger_calculus}).
+% \todo{read on holomorphic nets}
+
+More recently general development of $\cplx$-valued networks has been continued by
+\citet{trabelsi_deep_2017}, who outline the essential building blocks for deep $\cplx$-valued
+networks and describe suitable representation and operations, including convolutional and
+dense layers, $\cplx$-valued activations, complex batch-normalization and weight initialization.
+Their approach coupled with $\cplx\real$ calculus for backprop transforms a $\cplx$-valued
+network into an intricately connected $\real$-valued computational graph, constructured
+to respects $\cplx$-arithmetic.
 %
@@
 \citep{trabelsi_deep_2017,wolter_complex_2018}.
-
-Complex networks are, in general, non-holomorphic, i.e. not $\cplx$-differentiable, which is
-exacerbated by the loss being real-valued. Indeed a $\cplx$-differentiable real-valued function is
-necessarily trivial by Cauchy-Riemann conditions. This issue is dealt with by employing Wirtinger,
-or $\cplx\real$ calculus, which generalizes holomorphic calculus to non-holomorphic functions
-of $\cplx$-argument \citep{adali_complex-valued_2011,boeddeker_computation_2019}. It satisfies
-the product and chain rules, respects complex conjugation and linearity, but most importantly the
-$\cplx\real$-differential of a function on $\cplx$ coincides with its classical differential as
-a function on $\real^2$. Essentially, it allows straightforward retrofiting of $\cplx$-valued
-networks into existing $\real$ deep learning auto-differentiation frameworks. It was considered
-as a basis for $\cplx$ version of back-propagation by \citet{benvenuto_complex_1992} and
-\citet{trabelsi_deep_2017}, (see appendix~\ref{sub:wirtinger_calculus} for details).
-% \todo{read on holomorphic nets}
 
@@
 Between \textit{``sparsify''} and \textit{``fine-tune''} stages we compute masks of non-zero
-weights in each layer based on the relevance scores $\alpha$ (sec.~\ref{sub:dropout}). Since
+weights in each layer based on the relevance scores $\alpha$ (sec.~\ref{sub:variational_dropout}). Since
 the $q_\theta$ factorizes into univariate distributions, a $\cplx$ or $\real$ parameter is

### 2020-03-18 paper/paper.tex
thorough proofread 2 (section 4) * added one-two column option to the docclass * improved the language a bit and compactified the narrative, removed duplicate comments * terminology: dropped log-uniform references, changed linear to dense linear * fixed eqns (5, 6), removed eqns (13', 16, 23, 24), swapped eqn 12 and 13 * verified ARD kl-div expressions

@@
-\documentclass[a4paper,10pt]{article}
+\documentclass[a4paper,10pt,onecolumn]{article}
 
@@
 \begin{equation}  \label{eq:sgvb_objective}
-  \widetilde{\mathcal{L}}(\theta; \phi, \lambda)
+  \widetilde{\mathcal{L}} %(\theta; \phi, \lambda)
     = - KL(q_{\theta} \| \pi_{\lambda})
@@
 \begin{equation}  \label{eq:elbo}
-  \widetilde{\mathcal{L}}(\theta; \phi, \lambda)
+  \widetilde{\mathcal{L}} %(\theta; \phi, \lambda)
     = - KL(q_{\theta} \| \pi_{\lambda})
@@
 %
-In particular, natural identification of $\cplx$ and $\real^2$ implies that linear layers $
+In particular, natural identification of $\cplx$ and $\real^2$ implies that dense linear
+layers $
   L \colon \cplx^m \to \cplx^n
@@
 version of the local reparameterization trick. Then we move on to choosing suitable priors
-and then onward to deriving explicit expressions for the divergence penalties in \eqref{eq:elbo}
-in terms of special functions.
+and then to deriving explicit expressions for the divergence penalties in \eqref{eq:elbo}
+in terms of \verify{special} functions.
 
@@
 \label{sub:c_gauss_and_local_rep}
-
-%notation
-In the following $M^{\top}$ is the matrix transpose, $\conj{M}$ is elementwise complex
-conjugation, and $M^{\hop} = (\conj{M})^\top$ denotes Hermitian conjugate.
 
@@
   \conj{\Gamma} \succeq C^{\hop} \Gamma^{-1} C
-$. Matrices $\Gamma$ and $C$ are $
+$.
+% notation
+Here, $M^{\top}$ is the matrix transpose, $\conj{M}$ is elementwise complex
+conjugation, and $M^{\hop} = (\conj{M})^\top$ denotes Hermitian conjugate.
+%
+Matrices $\Gamma$ and $C$ are given by $
   \mathbb{E} (z - \mu)(z - \mu)^{\hop}
@@
   \mathbb{E} (z - \mu)(z - \mu)^{\top}
-$, respectively.
-%
-% $\cplx$-Gaussians are closed under affine transformations: if $y = A z + b$
-% for $A \in \cplx^{n \times m}$ and $b \in \cplx^{n}$, then $
-%   y \sim \mathcal{N}_n^{\cplx}\bigl(
-%       A\mu + b, A \Gamma A^{\hop}, A C A^\top
-%     \bigr)
-% $.
-%
-$\cplx$-Gaussian random variables are closed under affine transformations: for $
-  A \in \cplx^{n \times m}
-$ and $b \in \cplx^{n}$
-\begin{equation}  \label{eq:cn-affine}
-  A z + b \sim \mathcal{N}_n^{\cplx}\bigl(
-      A\mu + b, A \Gamma A^{\hop}, A C A^\top
-    \bigr)
-  \,.
-\end{equation}
-%
-The entropy of a $\cplx$-Gaussian in terms of $\Gamma$ and $C$ is
-\begin{align}  \label{eq:c-gauss-entropy-derivation}
+$, respectively, and $z$ is a \textit{proper} $\cplx$-Gaussian vector if $z$ and
+$\conj{z}$ are uncorrelated, i.e. $C = 0$.
+%
+The entropy of $z$ terms of $\Gamma$ and $C$ is
+\begin{align}
   \mathbb{H}(q)
@@
     % \notag \\
+  % \label{eq:c-gauss-entropy-derivation}
     &
@@
       \det{(\pi e (\conj{\Gamma} - \conj{C} \Gamma^{-1} C))}
+    \notag \\
+  \label{eq:cn-proper-entropy}
+    &
+    % determinant commutes with complex conjugation, since it is multilinear
+    % = \tfrac12 \log \det{(\pi e \Gamma)} \det{(\pi e (\conj{\Gamma} - \conj{C} \Gamma^{-1} C))}
+    % = \tfrac12 \log \det{(\pi e \Gamma)} \det{(\pi e \conj{\Gamma})}
+    % = \tfrac12 \log \det{(\pi e \Gamma)} \conj{\det{(\pi e \Gamma)}}
+    % = \tfrac12 \log \bigl\lvert \det{(\pi e \Gamma)} \bigr\rvert^2
+    \Bigl[
+    = \log \bigl\lvert \det{(\pi e \Gamma)} \bigr\rvert
+    \quad \text{for } C = 0
+    \Bigr]
     \,.
 \end{align}
-A $\cplx$-Gaussian vector $z$ is \textit{proper} if $z$ and $\conj{z}$ are uncorrelated, i.e.
-$C = 0$. From \eqref{eq:c-gauss-entropy-derivation} its entropy is
-\begin{equation}  \label{eq:cn-proper-entropy}
-  % determinant commutes with complex conjugation, since it is multilinear
-  \mathbb{H}(q)
-    % = \tfrac12 \log \det{(\pi e \Gamma)} \det{(\pi e (\conj{\Gamma} - \conj{C} \Gamma^{-1} C))}
-    = \tfrac12 \log \det{(\pi e \Gamma)} \det{(\pi e \conj{\Gamma})}
-    % = \tfrac12 \log \det{(\pi e \Gamma)} \conj{\det{(\pi e \Gamma)}}
-    % = \tfrac12 \log \bigl\lvert \det{(\pi e \Gamma)} \bigr\rvert^2
-    = \log \bigl\lvert \det{(\pi e \Gamma)} \bigr\rvert
-    \,.
-    \tag{\ref{eq:c-gauss-entropy-derivation}'}
-\end{equation}
 %
@@
 
-The local reparameterization trick provides both faster computations, and better statistical
-efficiency of the SGVB gradient estimator \citep{wang_fast_2013,kingma_variational_2015}.
-Suppose that weights $W \in \cplx^{n\times m}$ of a linear layer are drawn from a mean
-field $\cplx$-Gaussian approximation
+The $\cplx$-variant of the local reparameterization trick utilizes the fact that Gaussian
+vectors are closed under affine transformations:
+% $\cplx$-Gaussians are closed under affine transformations
+\begin{equation}  \label{eq:cn-affine}
+  b + A z \sim \mathcal{N}_n^{\cplx}\bigl(
+      b + A\mu, A \Gamma A^{\hop}, A C A^\top
+    \bigr)
+  \,,
+\end{equation}
+for $A \in \cplx^{n \times m}$ and $b \in \cplx^{n}$. Therefore, if $W \in \cplx^{n\times m}$
+is drawn from a fully factorized approximation
 \begin{equation}  \label{eq:c-gauss-vi-general}
-  W_{ij}
-    \sim \mathcal{N}^{\cplx} \bigl(
+  W \sim q(W)
+    = \prod_{ij} \mathcal{N}^{\cplx} \bigl(
       \mu_{ij}, \Sigma_{ij}, C_{ij}
@@
 \end{equation}
-where mean, \textit{variance} and \textit{relation} are given by matrices $
-  \mu, \Sigma, C \in \cplx^{n\times m}
-$ with $\Sigma_{ij} \in \real$, and $
+with $
+  \mu, C \in \cplx^{n\times m}
+$, $\Sigma \in \real^{n\times m}$, and $
   \lvert C_{ij} \rvert^2 \leq \Sigma_{ij}
-$. The property \eqref{eq:cn-affine} and independence of elements of $W$ imply that for any
-$x \in \cplx^m$ and $b \in \cplx^n$ the components of $y = W x + b$ are independent with
-distributions
+$, then for $x \in \cplx^m$ and $b \in \cplx^n$ the vector $y = b + W x$ has independent
+components with
 \begin{equation}  \label{eq:cplx-gauss-trick}
@@
 \end{equation}
-The trick requires three matrix operations: $\mu x + b$, $\Sigma \lvert x \rvert^2$ and
-$C x^2$ with the modulus and power applied elementwise.
-
-The trick and dropout can be applied to any layer, the output of which depends linearly on
-its parameters, e.g. convolutional layers, affine, and bilinear transformations $
+The trick requires three operations, i.e. $b + \mu x$, $\Sigma \lvert x \rvert^2$ and
+$C x^2$ with the complex modulus and square applied elementwise, and can be applied to
+any layer, the output of which depends linearly on its parameters, such as convolutional,
+affine, and bilinear transformations ($
   (x, z) \mapsto x^\top W^{(j)} z + b_j
-$. Similar to $\real$ case, variational dropout for $\cplx$ convolutions draws independent
-realizations of $W$ for each spatial patch in the input. The rationale is simpler computations
-and variance reduction. The latter effect stems from decorrelated gradient estimates from
-overlapping patches \citep{kingma_variational_2015}, which allows \eqref{eq:cplx-gauss-trick}
-to use $\cplx$ convolutions of elementwise complex squares $x^2$ and amplitudes $\lvert x \rvert^2$
-with the relation and variance kernels.
+$). Similar to $\real$ case, Variational Dropout for $\cplx$ convolutions draws independent
+realizations of $W$ for each spatial patch in the input \citep{molchanov_variational_2017}.
+This provides faster computations and better statistical efficiency of the SGVB gradient
+estimator stemming from decorrelated gradient estimates from overlapping patches
+\citep{kingma_variational_2015}, allowing \eqref{eq:cplx-gauss-trick} to leverage $\cplx$
+convolutions of the relation and variance kernels with elementwise complex squares $x^2$
+and amplitudes $\lvert x \rvert^2$.
 % Weight sharing is essentially pushed to shared variational parameters $\theta$ in the approximation $q_\theta$.
@@
 
-For $\cplx$-variational dropout we propose using mean-field proper $\cplx$-Gaussian approximate
-posterior and MAP estimates of bias terms, i.e. parameters $W \in \cplx^{n\times m}$ of a dense
-linear layer follow
-% We use MAP estimates of bias terms, i.e. assume an independent fully factorized Dirac approximation.
-\begin{equation}  \label{eq:c-gauss-vi}
-  % (we omit the subscript $m=1$ for brevity)
-  W \sim q(W)
-    % = \prod_{ij} q(W_{ij})
-    = \prod_{ij} \mathcal{N}^{\cplx}(
-      W_{ij} \mid
-        \mu_{ij},
-        \alpha_{ij} \lvert \mu_{ij} \rvert^2,
-        % \sigma^2_{ij},
-        0
-    )
-  \,,
-\end{equation}
-and we use similar factorized approximation for convolutions and other, effectively, linear
-layers. For this approximation the relation coefficients \eqref{eq:cplx-gauss-trick} are
-zero.
-
-We consider two priors for Bayesian dropout: \verify{log-uniform} and $\cplx$-Gaussian empirical
-Bayes \citep{kingma_variational_2015,molchanov_variational_2017,kharitonov_variational_2018}.
-For a fully factorized approximation $q(\omega)$ and factorized prior belief $\pi(\omega)$,
+For $\cplx$-Bayesian Dropout we propose to use fully factorized proper $\cplx$-Gaussian
+approximation \eqref{eq:c-gauss-vi-general} for weights and point estimates of biases in
+dense linear, convolutional and other, effectively, affine layers, i.e. we let $
+  \Sigma_{ij} = \alpha_{ij} \lvert \mu_{ij} \rvert^2
+$ and fix $C_{ij} = 0$. Under this approximation the relation coefficients in \eqref{eq:cplx-gauss-trick}
+are zero.
+%
+For a fully factorized approximation $q(\omega)$ and factorized prior belief $
+  \pi(\omega) = \prod_{ij} \pi(\omega_{ij})
+$,
 the divergence term in ELBO \eqref{eq:elbo} is
@@
 \end{equation}
-We omit subscripts ${ij}$ for brevity in the next sections.
-
-\subsubsection{Variational dropout} % (fold)
-\label{ssub:variational_dropout}
-
-From \eqref{eq:cn-proper-entropy} the KL-divergence for \verify{log-uniform prior} $
+We consider two fully factorized priors: an improper prior for Variational Dropout and
+$\cplx$-Gaussian ARD prior. We omit subscripts ${ij}$ for brevity in the next sections.
+
+\subsubsection{VD prior} % (fold)
+\label{ssub:vd_prior}
+
+From \eqref{eq:cn-proper-entropy} the KL-divergence for an improper prior $
   \pi(\omega) \propto {\lvert \omega \rvert}^{-\beta}
@@
       - \log{\sigma^2}
-      + \tfrac{\beta}2 \mathbb{E}_{\omega \sim q(\omega)} \log \lvert \omega \rvert^2
+      + \tfrac{\beta}2 \Bigl(
+        \mathbb{E}_{\omega \sim q(\omega)} \log \lvert \omega \rvert^2
+      \Bigr)
     \,.
@@
   \sigma^2 = \alpha \lvert \mu \rvert^2
-$, whence
+$, whence the expectation in brackets is given by
 \begin{equation}  \label{eq:expect-improper-term-cplx}
-  \mathbb{E}_{\omega \sim q(\omega)} \log \lvert \omega \rvert^2
-    % = \mathbb{E}_{\xi \sim \mathcal{N}^{\cplx}(\xi \vert 1, \alpha, 0)}
-    %   \log \lvert \mu \xi \rvert^2
-    % = \log \lvert \mu \rvert^2
-    %   + \mathbb{E}_{\xi \sim \mathcal{N}^{\cplx}(\xi \vert 1, \alpha, 0)}
-    %       \log \lvert \xi \rvert^2
-    = \log \alpha \lvert \mu \rvert^2
+  % \mathbb{E}_{\omega \sim q(\omega)} \log \lvert \omega \rvert^2
+  %   % = \mathbb{E}_{\xi \sim \mathcal{N}^{\cplx}(\xi \vert 1, \alpha, 0)}
+  %   %   \log \lvert \mu \xi \rvert^2
+  %   % = \log \lvert \mu \rvert^2
+  %   %   + \mathbb{E}_{\xi \sim \mathcal{N}^{\cplx}(\xi \vert 1, \alpha, 0)}
+  %   %       \log \lvert \xi \rvert^2
+  %   =
+    \log \alpha \lvert \mu \rvert^2
       + \mathbb{E}_{\xi \sim \mathcal{N}^{\cplx}(\xi \vert 0, 1, 0)}
@@
 \end{equation}
-Let $
-  (z_i)_{i=1}^m \sim \mathcal{N}^{\cplx}(0, 1, 0)
-$ iid and $\theta \in \cplx^m$. Then $
+If $
+  (z_i)_{i=1}^m
+    \sim \mathcal{N}^{\cplx}(0, 1, 0)
+$ iid and $\theta \in \cplx^m$, then $
   \sum_i \lvert \theta_i + z_i \rvert^2
@@
 $, i.e. a non-central $\chi^2_{2m}$ with parameter $s^2$. Its log-moments for general
-integer $m \geq1$ are given in \cite[p.~2466]{lapidoth_capacity_2003}. In particular,
+integer $m \geq1$ have been derived by \citet[p.~2466]{lapidoth_capacity_2003}.
 % in fact Appendix X, Lemma 10.1
-for $m=1$ and $\theta\in \cplx$ we have
+In particular, for $m=1$ and $\theta\in \cplx$ we have
 \begin{equation}  \label{eq:log-moment-for-chi-2}
@@
   \mathop{Ei}(x) = \int^x_{-\infty} t^{-1} e^t dt
-$ for $x < 0$ is the Exponential Integral. Note that
-$
-  \tfrac{d}{dx} \mathop{Ei}(x) = \tfrac{e^x}{x}
-$, $
+$ for $x < 0$ is the Exponential Integral, which satisfies $
   \mathop{Ei}(x) \leq \log{(-x)}
@@
 %
-Through \eqref{eq:expect-improper-term-cplx} and \eqref{eq:log-moment-for-chi-2} we get
+Although $\mathop{Ei}$ is an intractable integral, requiring numerical approximations to
+compute, its derivative is exact: $
+  \tfrac{d}{dx} \mathop{Ei}(x) = \tfrac{e^x}{x}
+$ at $x < 0$.
+
+From \eqref{eq:expect-improper-term-cplx} and \eqref{eq:log-moment-for-chi-2}, the terms of
+the divergence that depend on the parameters are given by
 \begin{equation}  \label{eq:c-vd-kl-div}
@@
       - \tfrac{\beta}2 \mathop{Ei}(- \tfrac1{\alpha})
-      \tag{\ref{eq:c-vd-kl-div-raw}'} \,.
+      \,.
+      \tag{\ref{eq:c-vd-kl-div-raw}'}
 \end{equation}
@@
 on \eqref{eq:c-vd-kl-div}, it is possible to back-propagate through the divergence without
-forward evaluation.
+forward evaluation, which speeds up gradient updates.
 % Gradient-based optimiziation of \eqref{eq:elbo} usually does not use the value of the objective. 
@@
 
-\subsubsection{Empirical Bayes} % (fold)
-\label{ssub:empirical_bayes}
-
-Let's consider fully factorized proper $\cplx$-Gaussian prior $
+\subsubsection{ARD prior} % (fold)
+\label{ssub:ard_prior}
+
+We consider the fully factorized proper $\cplx$-Gaussian ARD prior with $
   \pi_\tau(\omega)
@@
 %   + \tfrac12 (\mu_1 - \mu_2)^\top \Sigma_2^{-1} (\mu_1 - \mu_2)
+%   =
+%   - \log\lvert\det{\pi e \Gamma}\rvert
+%   + \log\lvert\det{\pi \tau^{-1} I} \rvert
+%   + \tau \Re \tr{\Gamma} + \tau \mu^\hop \mu
+%   =
+%   - n - \log \lvert\det{\tau \Gamma}\rvert
+%   + \tau \Re \tr{\Gamma} + \tau \mu^\hop \mu
 %   \,. $$
@@
     \,.
+    \tag{\ref{eq:emp-bayes-kl-div}'}
 \end{equation}
@@
 
-\subsubsection{Bayesian $\cplx$-dropout via $\real$-scaling} % (fold)
+\subsubsection{$\cplx$-Bayesian Dropout via $\real$-scaling} % (fold)
 \label{ssub:real_scaling_dropout}
@@
 Consider the following parameterization of $W$: $
-  W = \mu \odot \xi
-$ where $
+  W_{ij} = \mu_{ij} \xi_{ij}
+$, $\xi_{ij} \in \real$ with $
   \xi_{ij} \sim \mathcal{N}(1, \alpha_{ij})
 $, yet $\mu \in \cplx^{n \times m}$. This case corresponds to inference regarding
-relevance coefficients $\xi$ rather than the parameters themselves after. Each weight
-under this parameterization is an independent degenerate $\cplx$-Gaussian distribution
-\begin{equation}  \label{eq:real-scal-gauss-vi}
-  W_{ij}
-    \sim \mathcal{N}^{\cplx} \bigl(
-      \mu_{ij},
-      \, \alpha_{ij} \lvert \mu_{ij} \rvert^2,
-      \, \alpha_{ij} \mu_{ij}^2
-    \bigr)
-  \,,
-\end{equation}
-which implies by \eqref{eq:cplx-gauss-trick} the following:
-\begin{equation}  \label{eq:real-scal-gauss-trick}
-  y_i
-    \sim \mathcal{N}^{\cplx}\bigl(
-      % e_i^\top \mu x + b,
-      b_i + \sum_{j=1}^m \mu_{ij} x_j,
-      \, \sum_j \alpha_{ij} \lvert x_{ij} \mu_{ij}\rvert^2,
-      \, \sum_j \alpha_{ij} (x_{ij} \mu_{ij})^2
-    \bigr)
-    \,.
-\end{equation}
+relevance multipliers $\xi$ rather than the parameters themselves. Under this parameterization
+the weight distribution is fully factorized degenerate $\cplx$-Gaussian approximation
+\eqref{eq:c-gauss-vi-general} with $
+  \Sigma_{ij} = \alpha_{ij} \lvert \mu_{ij} \rvert^2
+$ and $
+  C_{ij} = \alpha_{ij} \mu_{ij}^2
+$. Unlike proper $\cplx$-Gaussian approximation, the complex relation parameter in
+\eqref{eq:cplx-gauss-trick} is nonzero in this case and equals $
+  \sum_j \alpha_{ij} (x_{ij} \mu_{ij})^2
+$.
+%
 The KL-divergence term for this approximation coincides with \eqref{eq:improper-kl-div-real},
-which is approximated by \citet{molchanov_variational_2017}. The major drawback of this method
-is that the additive noise reparameterization in \eqref{eq:real-scal-gauss-trick}, which
-disentangles the gradient with respect to $\mu$ from the local noise, cannot be applied.
+however the major drawback of this approximation is that the additive noise reparameterization,
+which disentangles the gradient with respect to $\mu$ from the local output noise, cannot be
+applied.
 
@@
 During the \textit{``sparsify''} stage we make every layer Bayesian and apply $\cplx$-variational
-dropout sec.~\ref{ssub:variational_dropout} (or sec.~\ref{ssub:empirical_bayes}) or its $\real$
+dropout sec.~\ref{ssub:vd_prior} (or sec.~\ref{ssub:ard_prior}) or its $\real$
 counterpart. To be able to study the attainable sparsity levels we inject a coefficient $
@@
         \log p_{\phi}(z_i \mid g(\varepsilon_i; \theta))
-    \,. \tag{\ref{eq:elbo}'}
+    \,.
+    \tag{\ref{eq:elbo}'}
 \end{equation}
@@
 on KMNIST and EMNIST-Letters datasets for the studied models and VD compression method
-(sec.~\ref{ssub:variational_dropout}). Besides that we try \texttt{raw} or \texttt{fft}
+(sec.~\ref{ssub:vd_prior}). Besides that we try \texttt{raw} or \texttt{fft}
 input features, vary $
@@
 compression of the most upstream layer can be alleviated through non-uniform compression,
-induced by variational dropout. We test only VD (sec.~\ref{ssub:variational_dropout}) this
+induced by variational dropout. We test only VD (sec.~\ref{ssub:vd_prior}) this
 sub-experiment, since prior results have not demonstrated significant superiority of one method
-over another (sec.~\ref{ssub:empirical_bayes}).
+over another (sec.~\ref{ssub:ard_prior}).
 
@@
 the $50$-$100$ compression region with $\cplx$-valued variational dropout with ARD prior
-(sec.~\ref{ssub:empirical_bayes}).
+(sec.~\ref{ssub:ard_prior}).
 

### 2020-03-18 paper/paper.tex
repalced textwidth with columnwidth; used LaTeX builtin appendix command
Some minor changes * proper citation for ARD prior (Neal, 1996); added sums to kl-div * use rv-pipe-par notation, to emphasize conditional dependence * reverted to sections in appendix

@@
   q_\theta(\omega)
-    = \prod_j \mathcal{N}(\mu_j, \alpha_j \mu_j^2)
+    = \prod_j \mathcal{N}(\omega_j \vert\, \mu_j, \alpha_j \mu_j^2)
 $ and factorized log-uniform prior $\pi(\omega)$ with $
   \pi(\omega_j) \propto \lvert \omega_j \rvert^{-1}
-$. The divergence term in \eqref{eq:elbo} unravels into a sum of the following
-analytically intractable terms:
+$. The divergence term in \eqref{eq:elbo} unravels into the following sum:
 \begin{equation}  \label{eq:improper-kl-div-real}
@@
     \propto
-      \frac12 \mathbb{E}_{\varepsilon \sim \mathcal{N}(0, 1)}
-        \log{\Bigl\lvert \tfrac1{\sqrt{\alpha}} + \varepsilon \Bigr\rvert^2}
+      \frac12 \sum_j \mathbb{E}_{\varepsilon \sim \mathcal{N}(0, 1)}
+        \log{\Bigl\lvert \tfrac1{\sqrt{\alpha_j}} + \varepsilon \Bigr\rvert^2}
       % \frac12 \mathbb{E}_{\varepsilon \sim \mathcal{N}(0, 1)}
@@
 % see p.6 sec 3.4 of kingma_variational_2015
-In appendix~\ref{sub:real-chisq-grad} we verify the value and the derivative of their
+In appendix~\ref{sec:real-chisq-grad} we verify the value and the derivative of their
 approximation against the Monte-Carlo estimate of \eqref{eq:improper-kl-div-real} for $\alpha$
@@
 % (!) good for SGVB: gradient-based methods require unbiased gradient estimates
-%
-% (in) it is in poor taste to brag about this begin the first time anyone has derived a
+% (in) it is in poor taste to brag about this beign the first time anyone has derived a
 % derivative of an intractable function.
+
 The key role in the factorization is played by $\alpha_j$, which reflects the relevance
@@
 to its variance. Thus, \citet{molchanov_variational_2017} focus on the model sparsification
-capabilities of Variational Dropout, optimizing $\alpha$ for each individual parameter.
-\citet{kharitonov_variational_2018} address theoretical issues with improper priors and
-propose an alternative Bayesian Dropout method based on \textit{Automatic Relevance
-Determination} procedure. In essence, the log-uniform factor $\pi(\omega_{ij})$ is replaced by
-a proper ARD Gaussian prior $
-  \mathcal{N}(0, \tau^{-1}_{ij})
-$ with learnable precision $\tau_{ij} > 0$. This method, known as \textit{Empirical Bayes},
-fits a prior distribution while performing Variational Inference. Maximizing \eqref{eq:elbo}
-over $\tau$, holding other parameters fixed, yields $
-  \tau^* = {(\mu^2 + \sigma^2)}^{-1}
+capabilities of Variational Dropout, optimizing $\alpha_j$ for each individual parameter,
+or across groups of parameters for structured sparsity. \citet{kharitonov_variational_2018}
+address theoretical issues with improper priors and propose a method based on \textit{
+Automatic Relevance Determination} procedure, which falls under \textit{Empirical Bayes}
+approach that fits a prior distribution while performing Variational Inference. In this
+method the log-uniform factor $\pi(\omega_j)$ is replaced by a proper Gaussian ARD
+prior $
+  \mathcal{N}(\omega_j \vert\, 0, \tau^{-1}_j)
+$ with learnable precision $\tau_j > 0$, \citep{neal_bayesian_1996}. Maximizing
+\eqref{eq:elbo} over $\tau$, holding other parameters fixed, yields $
+  \tau^*_j = {(\mu_j^2 + \sigma^2_j)}^{-1}
 $, whence
@@
   KL(q_\theta \| \pi)
-    = \tfrac12 \log{\bigl(1 + \tfrac1{\alpha} \bigr)}
+    = \frac12 \sum_j \log{\bigl(1 + \tfrac1{\alpha_j} \bigr)}
     \,.
 \end{equation}
-Flexibility in specification of $q_\theta$ enables developing structured dropout with
-shared $\alpha$ across groups of parameters $\omega$.
 
@@
 the stochasticity of $
-  W \sim \prod_{ij} \mathcal{N}(\mu_{ij}, \alpha_{ij} \mu_{ij}^2)
-$ in a linear layer $
+  W \in \mathbb{R}^{n\times m}
+$ with $
+  q(W) = \prod_{ij}
+    \mathcal{N}(w_{ij}\vert\, \mu_{ij}, \alpha_{ij} \mu_{ij}^2)
+$ in a linear layer is pushed to its output $
   y = b + W^\top x
-$ with $
-  W \in \mathbb{R}^{n\times m}
-$ is pushed to its output
+$,
 \begin{equation}  \label{eq:r-gauss-trick}
-    y \sim \prod_i \mathcal{N}\Bigl(
+    q(y) = \prod_i \mathcal{N}\Bigl(
+          y_i \big\vert\,
           b_i + \sum_j \mu_{ij} x_j,
@@
     = \prod_{ij} \mathcal{N}^{\cplx} \bigl(
-      \mu_{ij}, \Sigma_{ij}, C_{ij}
+      w_{ij} \vert\, \mu_{ij}, \Sigma_{ij}, C_{ij}
     \bigr)
@@
   \centering
-  \begin{subfigure}[b]{0.95\textwidth}  % imcl2019-style swears at this
+  \begin{subfigure}[b]{1.\columnwidth}  % imcl2019-style swears at this
     \centering
@@
 as well. The upward trend manifests itself in MNIST and Fashion MNIST experiments as well
-(see appendix~\ref{sub:mnist_like_experiments}). Finally, overall $\cplx$ variational dropout
+(see appendix~\ref{sec:mnist_like_experiments}). Finally, overall $\cplx$ variational dropout
 methods seem to compress networks adequately well without much loss in performance.
@@
   \centering
-  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
+  \begin{subfigure}[b]{1.\columnwidth}  % imcl2019-style swears at this
     \centering
@@
   % \hfill
-  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
+  \begin{subfigure}[b]{1.\columnwidth}  % imcl2019-style swears at this
     \centering
@@
   \end{subfigure} \\%
-  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
+  \begin{subfigure}[b]{1.\columnwidth}  % imcl2019-style swears at this
     \centering
@@
   \centering
-  \begin{subfigure}[b]{0.9\textwidth}  % imcl2019-style swears at this
+  \begin{subfigure}[b]{1.\columnwidth}  % imcl2019-style swears at this
     \centering
@@
 
-\begin{figure}[!h]
-  \centering
-  \begin{subfigure}[b]{1.\textwidth}  % imcl2019-style swears at this
+\begin{figure}[!t]
+  \centering
+  \begin{subfigure}[b]{1.\columnwidth}  % imcl2019-style swears at this
     \centering
@@
 
-\clearpage
+% \clearpage
 
@@
 
-\clearpage
-
-\section{Appendix} % (fold)
-\label{sec:appendix}
-
-\subsection{Complex-valued local reparameterization} % (fold)
-\label{sub:complex_valued_local_reparameterization}
+% \clearpage
+
+\appendix
+\onecolumn
+
+\section{Complex-valued local reparameterization} % (fold)
+\label{sec:complex_valued_local_reparameterization}
 
@@
 
-% subsection complex_valued_local_reparameterization (end)
-
-\subsection{Gradient of the KL-divergence in $\real$ case} % (fold)
-\label{sub:real-chisq-grad}  % gradient_of_the_kl_divergence_in_R_case
+% section complex_valued_local_reparameterization (end)
+
+\section{Gradient of the KL-divergence in $\real$ case} % (fold)
+\label{sec:real-chisq-grad}  % gradient_of_the_kl_divergence_in_R_case
 
@@
 
-% subsection real-chisq-grad (end)
-
-\subsection{MNIST-like experiments} % (fold)
-\label{sub:mnist_like_experiments}
+% section real-chisq-grad (end)
+
+\section{MNIST-like experiments} % (fold)
+\label{sec:mnist_like_experiments}
 
@@
 
-% subsection mnist_like_experiments (end)
+% section mnist_like_experiments (end)
 
@@
 
-\subsection{CIFAR10 experiments} % (fold)
-\label{sub:cifar_experiments}
+\section{CIFAR10 experiments} % (fold)
+\label{sec:cifar_experiments}
 
@@
 
-% subsection cifar_experiments (end)
-
-\subsection{Backpropagation through $\cplx$-networks} % (fold)
+% section cifar_experiments (end)
+
+\section{Backpropagation through $\cplx$-networks} % (fold)
 \label{sub:wirtinger_calculus}
@@
 
-% subsection wirtinger_calculus (end)
-
-\subsection{$\cplx$-Linear operator representation} % (fold)
-\label{sub:c-linear_operator_representation}
+% section wirtinger_calculus (end)
+
+\section{$\cplx$-Linear operator representation} % (fold)
+\label{sec:c-linear_operator_representation}
 
@@
 
-% subsection c-linear_operator_representation (end)
+% section c-linear_operator_representation (end)
 

### 2020-03-19 cplxpaper/auto/utils.py
factored out snapshot path locator from load-stage

@@ -81,11 +81,9 @@ def verify_experiment(folder):
     return all(stages.values())
 
 
-def load_stage_snapshot(stage, folder, mismatch="ignore"):
-    """Load the snapshot of the given phase from the experiment."""
-    if mismatch not in ("ignore", "raise"):
-        raise ValueError(f"`mismatch` must be either 'ignore' or 'raise'.")
-
+def get_stage_snapshot(stage, folder):
+    """Get the filename of the snapshot of the given phase from the experiment.
+    """
     # synchronized with naming format at ./auto.py#L393
     pat = re.compile(r"^(\d+)-(\S+)\s+.*?(\d{8}-\d{6})\.gz$")
 
@@ -98,16 +96,29 @@ def load_stage_snapshot(stage, folder, mismatch="ignore"):
                      key=lambda m: time.strptime(m.group(3), "%Y%m%d-%H%M%S"))
     for m in matches:
         if m.group(2) == stage:
-            # load and validate stage ID
-            snapshot = load_snapshot(os.path.join(folder, m.string))
+            return os.path.join(folder, m.string)
 
-            # the snapshot is expected to comply with ./auto.py#L392-411
-            if snapshot["stage"][0] == stage:
-                return snapshot
-
-    if mismatch == "ignore":
-        return {}
     raise RuntimeError(f"'{stage}' not found.")
+
+
+def load_stage_snapshot(stage, folder, mismatch="ignore"):
+    """Load the snapshot of the given phase from the experiment."""
+    if mismatch not in ("ignore", "raise"):
+        raise ValueError(f"`mismatch` must be either 'ignore' or 'raise'.")
+
+    try:
+        # load and validate stage ID
+        snapshot = load_snapshot(get_stage_snapshot(stage, folder))
+
+        # the snapshot is expected to comply with ./auto.py#L392-411
+        if snapshot["stage"][0] == stage:
+            return snapshot
+
+    except RuntimeError:
+        if mismatch != "ignore":
+            raise
+
+    return {}
 
 
 def param_defaults(param, **defaults):

### 2020-03-19 cplxpaper/auto/reports/tradeoff.py
make dense satge optional in trade-off

@@ -43,19 +43,24 @@ def load_experiment(folder):
     the model that existed just before the `fine-tune` stage from `sparsify`
     and the sparsity `threshold`, specified in the experiment.
     """
-    options = load_manifest(folder)
+    options, models = load_manifest(folder), {}
 
-    # load 'dense'
-    models = {"dense": load_model(load_stage_snapshot("dense", folder))}
+    # load 'dense' (ignore if unavailable)
+    try:
+        snapshot = load_stage_snapshot("dense", folder, mismatch="raise")
+        models["dense"] = load_model(snapshot)
+
+    except RuntimeError:
+        pass
 
     # "post-fine-tune"
-    snapshot = load_stage_snapshot("fine-tune", folder)
+    snapshot = load_stage_snapshot("fine-tune", folder, mismatch="raise")
     models["post-fine-tune"] = load_model(snapshot)
 
     # "pre-fine-tune": load model from `fine-tune` and deploy the masks
     #  and weights onto it from `sparsify` using the prescribed threshold.
     state_dict, masks = auto.state_dict_with_masks(
-        load_model(load_stage_snapshot("sparsify", folder)),
+        load_model(load_stage_snapshot("sparsify", folder, mismatch="raise")),
         hard=True, threshold=options["threshold"])
 
     models["pre-fine-tune"] = load_model(snapshot)

### 2020-03-19 cplxpaper/auto/auto.py
evaluate only if trained

@@ -644,6 +644,7 @@ def run(options, folder, suffix, verbose=True, save_optim=False):
         sched = get_scheduler(optim, settings["lr_scheduler"])
 
         feed = feeds[settings["feed"]]
+        n_epochs = settings["n_epochs"]
 
         formula = settings["objective"]
         objective = get_objective(objective_terms, formula).to(**devtype)
@@ -657,7 +658,7 @@ def run(options, folder, suffix, verbose=True, save_optim=False):
         model.train()
         model, emergency, history = fit(
             model, objective, feed, optim, sched=sched, early=early,
-            n_epochs=settings["n_epochs"], grad_clip=settings["grad_clip"],
+            n_epochs=n_epochs, grad_clip=settings["grad_clip"],
             verbose=verbose)
 
         is_benign_emergency = isinstance(emergency, benign_emergencies)
@@ -665,7 +666,7 @@ def run(options, folder, suffix, verbose=True, save_optim=False):
         # Evaluate the performance on the reserved feeds, e.g. 'test*'.
         model.eval()
         performance = {}
-        if is_benign_emergency:
+        if is_benign_emergency and n_epochs > 0:
             # Ignore warnings: no need to `.filter()` when `record=True`
             with warnings.catch_warnings(record=True):
                 performance = {name: scorer(model)

### 2020-03-21 paper/paper.tex
thorough proofread 3 (beginning of section 5) * sorted and reworded common experiment setup * removed repeating pieces about replication * renamed and shortened a little bit the `stageswise` section

@@
-\documentclass[a4paper,10pt,onecolumn]{article}
+\documentclass[a4paper,10pt,twocolumn]{article}
 
@@
 
-In this section we study the complex variational dropout techniques discussed above
-on the tasks and datasets, that have been studied in prior research on complex-valued networks.
-
-% common experiment settings
-Every experiment is replicated several times to take random effects into account, e.g.
-random network initialization prior to training, randomly ordered batches during SGD.
+We study the compression-performance trade-off of the proposed Bayesian sparsification
+methods for $\cplx$-valued networks presented above on the datasets, that have been
+studied in prior research on complex-valued networks.
+
+% setup and common experiment settings
+For each dataset we conduct a set of experiments in which we try out all combinations of
+model kinds ($\real$ or $\cplx$), sparsification methods (VD or ARD) and input features.
+Where reasonable, we also study the effects of halving ($\cplx$) or doubling ($\real$)
+of the size of intermediate layers in each network \citep{monning_evaluation_2018}.
+%
+Each network within every experiment passes through three successive stages of training:
+pre-training, sparsification, and fine-tuning (sec.~\ref{sub:fitting_and_sparsification}).
+%
+Each experiment is replicated \textit{five} times to take into account random initialization,
+random order of the mini-batch during SGD, stochastic outputs of the intermediate layers,
+and non-determinism of single-precision computations on GPUs.
+
 Unless specified otherwise, every experiment uses global gradient clipping within an
-$\ell_2$-norm ball of radius $0.5$, runs SGD with ADAM optimizer with the base learning
+$\ell_2$-norm ball of radius $0.5$, employs SGD with ADAM optimizer with the base learning
 rate of $10^{-3}$. We note that since our experiments are on classification tasks,
@@
 
-\subsection{Stagewise fitting and sparsification} % (fold)
+% write a note on the incompressible parameters (bias, batch norm etc.)
+The compression rate is computed based on the number of IEEE754 floating point values
+needed to store the model and equals $
+  \tfrac{n_\mathtt{par}}{n_\mathtt{par} - n_\mathtt{zer}}
+$, where $n_\mathtt{zer}$ is the number of explicit zeros, $n_\mathtt{par}$ is the total
+number of floats. In particular, each parameter is counted once in a $\real$-valued network,
+but twice in a $\cplx$-network. Each model has a compression limit, determined by its
+layers' biases, shift and scaling from $\real$-and $\cplx$-batch normalization.
+
+\subsection{Stagewise training} % (fold)
 \label{sub:fitting_and_sparsification}
 
-The goal of this section to study the compression-performance trade-off of the proposed Bayesian
-sparsification methods for $\cplx$-valued networks. To this end we trained each network in
-three successive stages in every experiment: ``dense'' $\to$ ``sparsify'' $\to$ ``fine-tune''.
+% The training consists of three successive stages: ``dense'' $\to$ ``sparsify'' $\to$ ``fine-tune''.
 
 At the \textit{``dense''} stage every network is fit ``as-is'', retaining its original
-non-Bayesian architecture and using only the likelihood term from \eqref{eq:elbo} without
+non-Bayesian architecture, and using only the likelihood term from \eqref{eq:elbo} without
 variational dropout.
-%
+
 During the \textit{``sparsify''} stage we make every layer Bayesian and apply $\cplx$-variational
-dropout sec.~\ref{ssub:vd_prior} (or sec.~\ref{ssub:ard_prior}) or its $\real$
-counterpart. To be able to study the attainable sparsity levels we inject a coefficient $
+dropout sec.~\ref{ssub:vd_prior} (or sec.~\ref{ssub:ard_prior}) or its $\real$ counterpart.
+We inject a coefficient $
   C \in (0, 1]
-$ at the KL divergence term in \eqref{eq:elbo}:
+$ at the KL divergence term in \eqref{eq:elbo} to study the attainable sparsity levels:
 \begin{equation}  \label{eq:elbo_with_coef}
   - \frac{C}N KL(q_{\theta} \| \pi_{\lambda})
-    + \frac1{M} \sum_{i=1}^M
-        \log p_{\phi}(z_i \mid g(\varepsilon_i; \theta))
+  + \frac1{M} \sum_{k=1}^M
+      \log p_{\phi}(z_{i_k} \mid g(\varepsilon_k; \theta))
   \,.
@@
 \end{equation}
-Higher $C$ yields increasingly more sparse layers upon termination of this stage.
-
-The \textit{``fine-tune''} stage begins with computing the sparsity masks from the fitted
-approximation $q_\theta(W)$ and proceeds to train the non-zero parameters similarly to
-the ``dense'' stage, i.e. with non-Bayesian layers and fixed sparsity masks. 
-%
-The benefit of the ``fine-tune'' stage appears to be strongly influenced by the compression
+By varying $C$ we adjust the importance of the sparsifying prior in learning $q_\theta(W)$,
+meaning that higher value yields more irrelevant parameters during in inference and makes
+layers sparser upon termination of this stage.
+
+% on compresssion
+Between \textit{``sparsify''} and \textit{``fine-tune''} stages we compute masks of non-zero
+weights in each layer based on the relevance scores $\alpha$ (sec.~\ref{sub:variational_dropout}).
+Since the $q_\theta$ factorizes into univariate distributions, a $\cplx$ or $\real$ parameter
+is considered non-zero if $\log \alpha \leq \tau$ for $
+  \alpha = \tfrac{\sigma^2}{\lvert\mu\rvert^2}
+$, or zero otherwise.
+
+The \textit{``fine-tune''} stage reverts the network back to non-Bayesian layers, applies
+sparsity masks to its parameters and proceeds with training the kept parameters as during
+the ``dense'' stage. Unless specified otherwise the network is initialized to the mode
+of the learnt $q_\theta(W)$.
+
+% on chosing the threshold
+The threshold $\tau$ is picked so, that the remaining non-zero parameters are within
+$\delta$ relative tolerance of their mode with high probability under the approximate
+posterior. Since $q_\theta$ is fully factorized $\real$- or a proper $\cplx$-Gaussian,
+the random variable $
+  \tfrac{k \lvert w - \mu \rvert^2}
+        {\alpha \lvert \mu \rvert^2}
+$ is $\chi^2_k$ distributed with $k=1$ ($\real$) or $2$ ($\cplx$).
+%
+For a generous tolerance $\delta = 50\%$ all values of $\log \alpha$ below $-2.5$ yield
+at least $90\%$ chance of a non-zero $\real$/$\cplx$ parameter. We pick $\tau = -\tfrac12$
+to retain parameters sufficiently concentrated around their mode, and encourage higher
+sparsity, at the same time being aware that $q_\theta$ is merely an approximation.
+In comparison, $\tau = 3$ is commonly used as the threshold
+\citep{molchanov_variational_2017,kingma_variational_2015}.
+
+% subsection fitting_and_sparsification (end)
+
+\subsection{Metrics and compression} % (fold)
+\label{sub:metrics_and_compression}
+
+% conlcusions
+The impact of the ``fine-tune'' stage appears to be strongly influenced by the compression
 rate. We can observe in this and, more prominently, in MusicNet experiment (sec.~\ref{sub:musicnet})
@@
 
-% on compresssion
-Between \textit{``sparsify''} and \textit{``fine-tune''} stages we compute masks of non-zero
-weights in each layer based on the relevance scores $\alpha$ (sec.~\ref{sub:variational_dropout}). Since
-the $q_\theta$ factorizes into univariate distributions, a $\cplx$ or $\real$ parameter is
-considered non-zero if $\log \alpha \leq \tau$ for $
-  \alpha = \tfrac{\sigma^2}{\lvert\mu\rvert^2}
-$, or zero otherwise. Figure~\ref{fig:hist__and__threshold__tradeoff} is constructed
+% effects of extra training epochs and the impact of tau
+Figure~\ref{fig:hist__and__threshold__tradeoff} is constructed
 for $C \in \{\tfrac1{20}, \frac1{200}\}$ before running the ``fine-tune'' stage. From
@@
 
-% on chosing the threshold
-The threshold $\tau$ is picked so, that the remaining \textit{``non-zero''} parameters
-are within $\delta$ relative tolerance of their mean with high probability under the
-approximate posterior $q_\theta(W)$. This ensures that stochastic parameters are sufficiently
-concentrated around $\mu$, which are used as stand-in values for network weights $W$,
-when it runs in inference mode. Since $W$ is $\real$- or a proper $\cplx$-Gaussian, the
-random variable $
-  \tfrac{k \lvert W - \mu \rvert^2}
-        {\alpha \lvert \mu \rvert^2}
-$ is $\chi^2_k$ distributed with $k=1$ ($\real$) or $2$ ($\cplx$).
-%
-For a generous tolerance $\delta = 50\%$ all values of $\log \alpha$ below $-2.5$ yield
-at least $90\%$ chance of a non-zero $\real$/$\cplx$ parameter. We pick $\tau = -\tfrac12$
-to exclude noisy parameters and encourage higher sparsity, at the same time being aware
-that $q_\theta$ is merely an approximation. In comparison, $\tau = 3$ is commonly used as
-the threshold \citep{molchanov_variational_2017,kingma_variational_2015}.
-
-% subsection fitting_and_sparsification (end)
-
-\subsection{Metrics and compression} % (fold)
-\label{sub:metrics_and_compression}
-
 % perfromance metrics
@@
 stage, before the beginning and upon termination of the ``fine-tune'' stage.
-
-% write a note on the incompressible parameters (bias, batch norm etc.)
-The compression rate is computed based on the number of floating point values needed to
-store the model and equals $
-  \tfrac{n_\mathtt{par}}{n_\mathtt{par} - n_\mathtt{zer}}
-$, where $n_\mathtt{zer}$ is the number of explicit zeros, $n_\mathtt{par}$ is the total
-number of floats. Thus each parameter is counted once in a $\real$-valued network, but twice
-in a $\cplx$-network. Each model has compression limit, set by layers' biases, shift
-and scaling from $\real$-and $\cplx$-batch normalization.
 
@@
 In each experiment we vary the method and the value $C$, while keeping $\tau$ at $-\tfrac12$.
-Every experiment is replicated five times to take into account the random effects from
-initialization, batch sequence during SGD, and stochasticity of intermediate layers on
-forward pass at ``sparsify'' stage.
 
@@
 
-\begin{figure}[!h]
+\begin{figure}[!t]
   \centering
@@
 Each experiment has been performed $5$ times to obtain a small sample of performance-compression
-values for each setting of $C$. By reevaluating each setting several times we can account
-for randomness in initialization of the uncompressed network at ``dense'', stochasticity of
-variational dropout layers, randomness of batch sequences during SDG, and non-determinism
-of computations on GPUs.
+values for each setting of $C$.
 

### 2020-03-21 paper/paper.tex
thorough proofread 4 (scattered) * merged sub 2.1 into sec 2 * improved names of c-valued dropout section, and rewritten its intro * reworded paragraph on non-overlapping patches * moved the first piece from `priors` sub to `c-gaussian` sub * scattered edits

@@
 
-The paper is structured as follows. In sec.~\ref{sec:bayesian_dropout} we review Bayesian
+The paper is structured as follows. In sec.~\ref{sec:variational_dropout} we review Bayesian
 dropout techniques, and in sec.~\ref{sec:c_valued_networks} we provide a brief summary of
 the inner working of complex-valued networks as functions of complex argument. The main
-contribution of this study is presented in sec.~\ref{sec:dropout_for_c_valued_layers},
+contribution of this study is presented in sec.~\ref{sec:c_variational_dropout},
 where we consider different variational approximations and priors, outline the tricks
@@
 
-\section{Bayesian Dropout} % (fold)
-\label{sec:bayesian_dropout}
+\section{Variational Dropout} % (fold)
+\label{sec:variational_dropout}
 
@@
 
-\subsection{Variational Dropout} % (fold)
-\label{sub:variational_dropout}
-
 With a special family of posterior approximation, Variational Inference can be used as
@@
 
-% subsection dropout (end)
-
 % section bayesian_dropout (end)
@@
 
-\section{Dropout for $\cplx$-valued layers} % (fold)
-\label{sec:dropout_for_c_valued_layers}
-
-In this section we review the complex Gaussian distribution and discuss its properties. Then
-we introduce factorized dropout posterior for complex-valued parameters and the relevant
-version of the local reparameterization trick. Then we move on to choosing suitable priors
-and then to deriving explicit expressions for the divergence penalties in \eqref{eq:elbo}
-in terms of \verify{special} functions.
-
-\subsection{Complex Gaussians and Local Reparameterization} % (fold)
+\section{$\cplx$-Variational Dropout} % (fold)
+\label{sec:c_variational_dropout}
+
+We propose to use fully factorized complex Gaussian posterior approximation and $\cplx$
+variant of the local reparameterization trick to extend Bayesian Dropout techniques to
+$\cplx$-valued networks. In this section we describe the approximation and derive the
+divergence penalties in \eqref{eq:elbo}.
+
+\subsection{$\cplx$-Gaussian Distribution} % (fold)
 \label{sub:c_gauss_and_local_rep}
@@
 This provides faster computations and better statistical efficiency of the SGVB gradient
-estimator stemming from decorrelated gradient estimates from overlapping patches
-\citep{kingma_variational_2015}, allowing \eqref{eq:cplx-gauss-trick} to leverage $\cplx$
-convolutions of the relation and variance kernels with elementwise complex squares $x^2$
-and amplitudes $\lvert x \rvert^2$.
+estimator by eliminating correlation from overlapping patches \citep{kingma_variational_2015}
+and allowing \eqref{eq:cplx-gauss-trick} to leverage $\cplx$ convolutions of the relation
+and variance kernels with elementwise complex squares $x^2$ and amplitudes $\lvert x \rvert^2$.
 % Weight sharing is essentially pushed to shared variational parameters $\theta$ in the approximation $q_\theta$.
@@
 
-% subsection c_gauss_and_local_rep (end)
-
-\subsection{The choice of priors and Kullback-Leibler divergence} % (fold)
-\label{sub:priors_and_kullback_leibler_divergence}
-
 For $\cplx$-Bayesian Dropout we propose to use fully factorized proper $\cplx$-Gaussian
 approximation \eqref{eq:c-gauss-vi-general} for weights and point estimates of biases in
-dense linear, convolutional and other, effectively, affine layers, i.e. we let $
+dense linear, convolutional and other, effectively, affine layers, i.e. $
   \Sigma_{ij} = \alpha_{ij} \lvert \mu_{ij} \rvert^2
-$ and fix $C_{ij} = 0$. Under this approximation the relation coefficients in \eqref{eq:cplx-gauss-trick}
-are zero.
-%
+$ and $C_{ij} = 0$. This forces the relation coefficients in \eqref{eq:cplx-gauss-trick}
+to be zero.
+
+% subsection c_gauss_and_local_rep (end)
+
+\subsection{The priors} % (fold)
+\label{sub:the_priors}
+
 For a fully factorized approximation $q(\omega)$ and factorized prior belief $
   \pi(\omega) = \prod_{ij} \pi(\omega_{ij})
-$,
-the divergence term in ELBO \eqref{eq:elbo} is
+$, the divergence term in ELBO \eqref{eq:elbo} is
 \begin{equation}  \label{eq:elbo-general-kl-div}
@@
 
-% section dropout_for_c_valued_layers (end)
+% section c_variational_dropout (end)
 
@@
 but twice in a $\cplx$-network. Each model has a compression limit, determined by its
-layers' biases, shift and scaling from $\real$-and $\cplx$-batch normalization.
+layers' biases, shift and scaling from $\real$- and $\cplx$-valued batch normalization.
 
@@
 Between \textit{``sparsify''} and \textit{``fine-tune''} stages we compute masks of non-zero
-weights in each layer based on the relevance scores $\alpha$ (sec.~\ref{sub:variational_dropout}).
+weights in each layer based on the relevance scores $\alpha$ (sec.~\ref{sec:variational_dropout}).
 Since the $q_\theta$ factorizes into univariate distributions, a $\cplx$ or $\real$ parameter

### 2020-03-21 paper/paper.tex
thorough proofread 5 (intro to sec 5) * compactified the intro, moved compression and fourier fatures into to it

@@
 We study the compression-performance trade-off of the proposed Bayesian sparsification
-methods for $\cplx$-valued networks presented above on the datasets, that have been
-studied in prior research on complex-valued networks.
+method for $\cplx$-valued networks presented above on image classification and music
+annotation tasks.
+%
+Following \citet{wolter_complex_2018} and \citet{trabelsi_deep_2017}, the class logit scores
+are taken as real part of the complex-valued output of a network.
+%
+% image features
+Since image data is not naturally $\cplx$-valued, we preprocess it by either embedding
+$\real$-data into $\cplx$ assuming $\Im z = 0$ (\texttt{raw}), or applying the two-dimensional
+Fourier Transform (\texttt{fft}), shifting lower frequencies to the centre of the image.
+We do not investigate the option to train an auxiliary model to synthesize the imaginary
+component from the real data, proposed by \citet{trabelsi_deep_2017}.
 
@@
 model kinds ($\real$ or $\cplx$), sparsification methods (VD or ARD) and input features.
-Where reasonable, we also study the effects of halving ($\cplx$) or doubling ($\real$)
+Where reasonable, we also study the effects of halving ($\tfrac12\cplx$) and doubling ($2\real$)
 of the size of intermediate layers in each network \citep{monning_evaluation_2018}.
-%
-Each network within every experiment passes through three successive stages of training:
-pre-training, sparsification, and fine-tuning (sec.~\ref{sub:fitting_and_sparsification}).
 %
@@
 
+Each network within every experiment passes through three successive stages of training:
+pre-training, sparsification, and fine-tuning (sec.~\ref{sub:fitting_and_sparsification}).
+%
 Unless specified otherwise, every experiment uses global gradient clipping within an
-$\ell_2$-norm ball of radius $0.5$, employs SGD with ADAM optimizer with the base learning
-rate of $10^{-3}$. We note that since our experiments are on classification tasks,
-$\cplx$-valued networks ultimately have to output a real-valued logit score. Following
-\citet{wolter_complex_2018} and \citet{trabelsi_deep_2017}, the class scores are taken
-as real parts of the $\cplx$ output.
+$\ell_2$-norm ball of radius $0.5$ and uses ADAM optimizer with the base learning rate
+of $10^{-3}$.
 
@@
 although \citet{monning_evaluation_2018} argue that this renders models incomparable.
-
-% image features
-Since image data is not naturally $\cplx$-valued, we preprocess images by either embedding
-$\real$-data into $\cplx$ assuming $\Re z = 0$ (\texttt{raw}), or applying the two-dimensional
-Fourier Transform (\texttt{fft}), shifting lower frequencies to the centre of the image. We
-do not investigate the option, proposed by \citet{trabelsi_deep_2017}, to train an auxiliary
-model to synthesize the imaginary component from the real data.
 

### 2020-03-23 paper/paper.tex
thorough proofread 6 (sec 5.2 appendix C) * almost done with mnist: awfully many incorrect and invalid observations were made * compacted the text in mnist-like intro and split mnist-like figure in two * reduced the volume of text in the mnist-related appendix * reworded the cplx-netowrk section * moved compression-threshold figure to musicnet * replaced textwidth with columnwidth

@@
 
-Complex networks are, in general, non-holomorphic, i.e. not $\cplx$-differentiable, which is
+Complex-valued networks are, in general, non-holomorphic, i.e. not $\cplx$-differentiable, which is
 exacerbated by the loss being real-valued. Indeed a $\cplx$-differentiable real-valued function is
@@
 %
-The KL-divergence term for this approximation coincides with \eqref{eq:improper-kl-div-real},
-however the major drawback of this approximation is that the additive noise reparameterization,
-which disentangles the gradient with respect to $\mu$ from the local output noise, cannot be
-applied.
+The KL-divergence term coincides with \eqref{eq:improper-kl-div-real}, however the major
+drawback of this approximation is that the gradient of the loss with respect to $\mu$ cannot
+be disentangled from the local output noise by additive reparameterization.
 
@@
 $\real$-data into $\cplx$ assuming $\Im z = 0$ (\texttt{raw}), or applying the two-dimensional
-Fourier Transform (\texttt{fft}), shifting lower frequencies to the centre of the image.
-We do not investigate the option to train an auxiliary model to synthesize the imaginary
-component from the real data, proposed by \citet{trabelsi_deep_2017}.
+Fourier Transform (\texttt{fft}), centering the lower frequencies. We do not train an
+auxiliary model to synthesize the imaginary component from the real data, proposed by
+\citet{trabelsi_deep_2017}.
 
@@
 Each network within every experiment passes through three successive stages of training:
-pre-training, sparsification, and fine-tuning (sec.~\ref{sub:fitting_and_sparsification}).
-%
-Unless specified otherwise, every experiment uses global gradient clipping within an
-$\ell_2$-norm ball of radius $0.5$ and uses ADAM optimizer with the base learning rate
-of $10^{-3}$.
+pre-training (\textit{``dense''}), sparsification (\textit{``sparsify''}), and fine-tuning
+(\textit{``fine-tune''}) (sec.~\ref{sub:staging}). The parameters and optimizer state are
+passed between stages, except for last one, which inherits just the parameters.
+%
+Every experiment uses ADAM optimizer, resets the learning rate to $10^{-3}$ before each
+stage, and applies global $\ell_2$-norm gradient clipping at $0.5$.
 
 % write a note on the incompressible parameters (bias, batch norm etc.)
-The compression rate is computed based on the number of IEEE754 floating point values
+The compression rate is calculated based on the number of IEEE754 floating point values
 needed to store the model and equals $
@@
 number of floats. In particular, each parameter is counted once in a $\real$-valued network,
-but twice in a $\cplx$-network. Each model has a compression limit, determined by its
-layers' biases, shift and scaling from $\real$- and $\cplx$-valued batch normalization.
+but twice in a $\cplx$-network. Each model has a compression limit, determined by biases,
+shift and scaling in $\real$- and $\cplx$-valued batch normalization layers.
 
 \subsection{Stagewise training} % (fold)
-\label{sub:fitting_and_sparsification}
+\label{sub:staging}
 
@@
 
-\subsection{Metrics and compression} % (fold)
-\label{sub:metrics_and_compression}
-
-% conlcusions
-The impact of the ``fine-tune'' stage appears to be strongly influenced by the compression
-rate. We can observe in this and, more prominently, in MusicNet experiment (sec.~\ref{sub:musicnet})
-that higher compression rate render the model more regularized, leaving less capacity for
-overfitting.
-% more ``holes'' Bayesian dropout ``poked'' makes the ``fine-tune'' serve as extended training.
-
-% effects of extra training epochs and the impact of tau
-Figure~\ref{fig:hist__and__threshold__tradeoff} is constructed
-for $C \in \{\tfrac1{20}, \frac1{200}\}$ before running the ``fine-tune'' stage. From
-\eqref{eq:elbo_with_coef}, the relative positions of the compression curves on this
-plot, and the results of experiments below it can be concluded that $C$ has much more
-substantial impact on the sparsity and performance, than the choice of $\tau$. Furthermore,
-for $\tau > 0$ the performance quickly saturates while compression creeps downwards.
-
-\begin{figure}[!t]
-  \centering
-  \begin{subfigure}[b]{1.\columnwidth}  % imcl2019-style swears at this
-    \centering
-    \includegraphics[width=\columnwidth]{figure__musicnet__threshold.pdf}
-  \end{subfigure}
-  \caption{%
-    Test split performance and compression rate for a $\cplx$-valued net on MusicNet.
-  }
-  \label{fig:hist__and__threshold__tradeoff}
-\end{figure}
-
-% perfromance metrics
-We use accuracy as the performance metric for multi-class image classification on MNIST-like
-and CIFAR10 datasets. Similarly to \citet{trabelsi_deep_2017} performance in experiments with
-MusicNet is measured with (pooled) average precision. The evaluation is done after ``dense''
-stage, before the beginning and upon termination of the ``fine-tune'' stage.
-
-% subsection metrics_and_compression (end)
-
 \subsection{MNIST-like datasets} % (fold)
@@
 
-We conduct a moderately sized experiment on MNIST and similar $28\times 28$ greyscale image
-datasets to study the compression-performance trade-off of the proposed $\cplx$-variational
-dropout.
+We conduct a moderately sized experiment on MNIST-like datasets of $28\times 28$ greyscale
+images to study the compression-performance trade-off of the proposed $\cplx$-variational
+dropout: MNIST \citep{lecun_gradient-based_1998}, KMNIST \citep{clanuwat_deep_2018},
+EMNIST \citep{cohen_emnist_2017} and Fashion-MNIST \citep{xiao_fashion-mnist_2017}.
+%
 % dataset size
 We deliberately use a {fixed} random subset of $10k$ images from the train split of each
-dataset to fit the networks and gauge the final performance on the usual test split.
-Limiting the size was done primarily to test the regularization strength of compression.
+dataset to fit the networks and measure the performance with classification \textit{accuracy}
+score on the usual test split.
+% Limiting the size was done primarily to test the regularization strength of compression
+% and to facilitate quicker experiments.
 
 % model architectures
-% discussion of TwoLayerDenseModel (TLDM) and SimpleConvModel (SCM)
-The $\real$/$\cplx$ networks have been chosen for the purpose of illustrating the compression
-and understanding the effects of experiment parameters. \textit{SimpleConvModel} (SCM) is a $2d$
-ReLU convolutional network with average pooling ($2\times 2$) after non-linearities with
-two convolutions (kernel $5\times 5$, stride $1$) with filters $n_1 \to n_2$ followed by
-dense layers $n_3 \to n_\mathtt{out}$. The second network, \textit{TwoLayerDenseModel} (TLDM),
-is a wide dense network $n_1 \to n_\mathtt{out}$. For SCM model $n_1, n_2, n_3$ are $20, 50, 500$,
-respectively, and for TLDM model $n_1 = 4096$ regardless of their type ($\real$ or $\cplx$),
-although \citet{monning_evaluation_2018} argue that this renders models incomparable.
-
-% first experiment: 40-75-40 with fast scheduler
-In this experiment stages last for $40$, $75$ and $40$ epochs, respectively, and the base
-learning rate of ${10}^{-3}$ is reduced after the $10$-th epoch to ${10}^{-4}$.
-%
-Plots~\ref{fig:mnist-like__trade-off} depict samples from the performance-compression curve
-on KMNIST and EMNIST-Letters datasets for the studied models and VD compression method
-(sec.~\ref{ssub:vd_prior}). Besides that we try \texttt{raw} or \texttt{fft}
-input features, vary $
-  C \in \{\tfrac3{2^{k+1}}\colon k=1..16\}
-$, and repeat the experiment $5$ times.
-
-Shaded horizontal bands reflect the spread of the performance of the uncompressed network
-after ``dense'' stage. Each point represents a precision-compression value attained by the
-network after ``fine-tune'' stage. The end of each point's tail represents the performance
-gain or loss from running the ``fine-tune'' stage.
-%
-We make a couple of observations based on the results of these plots. First, \texttt{fft}
-features perform on par with raw colour channel data in the convolutional networks across most
-compression rates, but require high compression rate to make wide shallow dense network work
-as well. The upward trend manifests itself in MNIST and Fashion MNIST experiments as well
-(see appendix~\ref{sec:mnist_like_experiments}). Finally, overall $\cplx$ variational dropout
-methods seem to compress networks adequately well without much loss in performance.
+% (fft) C - R - C / 2
+% (raw) R - C - 2 * R
+We consider two simple architectures for $\real$ and $\cplx$ networks in this experiment,
+which have been chosen for the purpose of illustrating the compression and understanding
+the effects of experiment parameters. \textit{TwoLayerDenseModel} is a wide dense ReLU
+network $784 \to 4096 \to n_\mathtt{out}$, and \textit{SimpleConvModel} is a ReLU net with
+two $2d$ $k_5 s_1$ convolutions with filters $20 \to 50$, two $k_2 s_2$ average pooling steps,
+and a dense classifier network $800 \to 500 \to n_\mathtt{out}$. The number of intermediate
+feature is as specified in $\real$ and $\cplx$ models, is halved in complex models tagged
+$\tfrac12\cplx$, and doubled in real models labelled $2\real$.
+
+% experiment setup
+Stages (sec.~\ref{sub:staging}) last for $40$, $75$ and $40$ epochs, respectively, in each
+experiment. The sparsification threshold $\tau$ is fixed at $-\tfrac12$, the training batch
+size is set to $128$ and the base learning rate ${10}^{-3}$ is reduced after the $10$-th epoch
+to ${10}^{-4}$ at every stage.
+%
+% grid specs
+We let $
+  C \in \{
+    \tfrac32 2^{-\tfrac{k}2} \colon k=2, \cdots, 38
+  \}
+$ in \eqref{eq:elbo_with_coef}, test VD and ARD methods, try \texttt{raw} or \texttt{fft}
+input features, and repeat each experiment $5$ times to get a sample of compression-accuracy
+pairs.
 
 % a couple of plots from MNIST and Fashion-MNIST
-\begin{figure}[!t]
+\begin{figure}[!ht]
   \centering
@@
     \centering
-    % \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/legacy__VD__fashionmnist__fft__-0.5.pdf}
-    \includegraphics[width=0.8\columnwidth]{figure__mnist-like__trade-off/legacy__VD__kmnist__fft__-0.5.pdf}
-    % \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/VD__kmnist__fft__-0.5.pdf}
+    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__VD__mnist__fft__-0.5.pdf}
   \end{subfigure} \\%
@@
     \centering
-    % \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/legacy__VD__fashionmnist__raw__-0.5.pdf}
-    \includegraphics[width=0.8\columnwidth]{figure__mnist-like__trade-off/legacy__VD__kmnist__raw__-0.5.pdf}
-    % \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/VD__kmnist__raw__-0.5.pdf}
-  \end{subfigure} \\%
+    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__VD__mnist__fft__-0.5.pdf}
+  \end{subfigure}
+  \caption{%
+    The compression-accuracy curve (VD, \texttt{fft}, MNIST):
+    $2 \real / \cplx$ (\textit{top}) and $\real / \cplx$ (\textit{bottom}).
+  }
+  \label{fig:mnist-like__trade-off__fft}
+\end{figure}
+
+\begin{figure}[!ht]
+  \centering
   \begin{subfigure}[b]{1.\columnwidth}  % imcl2019-style swears at this
     \centering
-    % \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/legacy__VD__mnist__fft__-0.5.pdf}
-    \includegraphics[width=0.8\columnwidth]{figure__mnist-like__trade-off/legacy__VD__emnist_letters__fft__-0.5.pdf}
-    % \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/ARD__kmnist__fft__-0.5.pdf}
+    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__ARD__mnist__raw__-0.5.pdf}
   \end{subfigure} \\%
@@
     \centering
-    % \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/legacy__VD__mnist__raw__-0.5.pdf}
-    \includegraphics[width=0.8\columnwidth]{figure__mnist-like__trade-off/legacy__VD__emnist_letters__raw__-0.5.pdf}
-    % \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/VD__emnist_letters__raw__-0.5.pdf}
+    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__mnist__raw__-0.5.pdf}
   \end{subfigure}
   \caption{%
-    The compression-accuracy trade-off on KMNIST and the letters of the Extended MNIST datasets.
-    (\textit{top}) \texttt{fft} features, (\textit{bottom}) \texttt{raw} features.
+    The compression-accuracy curve (ARD, \texttt{raw}, MNIST):
+    $\real / \cplx$ (\textit{top}) and $\real / \tfrac12 \cplx$ (\textit{bottom}).
   }
-  \label{fig:mnist-like__trade-off}
+  \label{fig:mnist-like__trade-off__raw}
 \end{figure}
+
+% observations
+Figures~\ref{fig:mnist-like__trade-off__fft} and~\ref{fig:mnist-like__trade-off__raw}
+depict the resulting compression-accuracy trade-off on MNIST for the simple models
+described above (other datasets are in appendix~\ref{sec:mnist_like_experiments}).
+%
+The points represent the trade-off of the compressed networks after fine-tuning, while their
+tails illustrate the impact of this stage on the accuracy. Transparent horizontal bands on
+each plot represent min-max performance spread of an uncompressed network on the test split.
+
+The overarching pattern in all experiments on MNIST-like datasets is that both ARD and VD yield
+compress similarly and ARD offers marginal advantage in terms of performance after fine-tuning.
+Fourier features perform marginally worse than raw image data for each model across all
+compression rates, and their trade-off for the dense network has a hat-like shape, contrasting
+the raw image features, for which the accuracy stays at one level for moderate rates,
+and then abruptly decays in high compression regime.
+
+The impact of ``fine-tune'' is mixed, and depends on the dataset and features, although it
+frequently improves accuracy in high compression $\times50+$ (high $C$ in \eqref{eq:elbo_with_coef})
+for raw image input. On EMNIST Letters and MNIST datasets in the small compression regime the
+dense network exhibits a trough in accuracy before fine-tuning stage.
+
+% conclusions
+These experiments demonstrate that $\cplx$ Variational Dropout can offer adequate compression
+without much loss in performance for $\cplx$-valued networks. Although ARD performs on par
+with VD, unlike VD, it uses a proper prior and has a tractable analytic expression for the
+KL-divergence \eqref{eq:emp-bayes-kl-div} in both $\real$ and $\cplx$ cases.
+% fft: $2\real$ convolutional model trade-off overall better than $\real$, dense -- on par.
+% raw: $\cplx$ models trade-off overall better than $\tfrac12\cplx$.
+Wider $\real$ and $\cplx$ networks appear to have more favourable trade-off between
+compression and accuracy.
+% fft: any-$\real$ dense model compresses better than $\cplx$
+However, it seems that due to more intrinsic degrees of freedom, $\real$-valued models
+perform and compress better than $\cplx$, even when the former uses the same number of
+features as the latter.
+% $\cplx$-valued networks do not have as much spare capacity as $2 \real$ due to
+%  constraints imposed by multiplication in $\cplx$ numbers
 
@@
 \label{sub:cifar10}
+
+We use accuracy as the performance metric for multi-class image classification on CIFAR10 datasets.
 
@@
 
+% perfromance metrics
+Similarly to \citet{trabelsi_deep_2017} performance in experiments with
+MusicNet is measured with (pooled) average precision. The evaluation is done after ``dense''
+stage, before the beginning and upon termination of the ``fine-tune'' stage.
+
 \begin{figure}[!t]
@@
 (sec.~\ref{ssub:ard_prior}).
+
+% conlcusions
+The impact of the ``fine-tune'' stage appears to be strongly influenced by the compression
+rate. We can observe in this and, more prominently, in MusicNet experiment (sec.~\ref{sub:musicnet})
+that higher compression rate render the model more regularized, leaving less capacity for
+overfitting.
+% more ``holes'' Bayesian dropout ``poked'' makes the ``fine-tune'' serve as extended training.
+
+\begin{figure}[!t]
+  \centering
+  \begin{subfigure}[b]{1.\columnwidth}  % imcl2019-style swears at this
+    \centering
+    \includegraphics[width=\columnwidth]{figure__musicnet__threshold.pdf}
+  \end{subfigure}
+  \caption{%
+    Test split performance and compression rate for a $\cplx$-valued net on MusicNet.
+  }
+  \label{fig:hist__and__threshold__tradeoff}
+\end{figure}
+
+% effects of extra training epochs and the impact of tau
+Figure~\ref{fig:hist__and__threshold__tradeoff} is constructed
+for $C \in \{\tfrac1{20}, \frac1{200}\}$ before running the ``fine-tune'' stage. From
+\eqref{eq:elbo_with_coef}, the relative positions of the compression curves on this
+plot, and the results of experiments below it can be concluded that $C$ has much more
+substantial impact on the sparsity and performance, than the choice of $\tau$. Furthermore,
+for $\tau > 0$ the performance quickly saturates while compression creeps downwards.
 
@@
 
-To supplement the results, reported in the main text (figures \ref{fig:paper__mnist-like__trade-off__VD__fft}
-and \ref{fig:paper__mnist-like__trade-off__VD__raw}), we conduct additional experiments
-with the same basic set-up, but over a finer grid of KL-divergence term coefficients.
-%
-These experiments lend further evidence in support of the conclusions, drawn in the main
-paper, namely, that the $\cplx$-valued extension of the $\real$-valued variational dropout
-can offer significant compression levels without much loss in performance. At the same
-time, the test performance of both $\real$ and $\cplx$ compressed networks benefits from
-an extra fine-tuning stage, during which sparsity masks are fixed.
-
-One intriguing observation, is that on MNIST-like images the dense network, taking Fourier
-features on input, exhibits gradually improving test-split performance. This is in stark
-contrast to raw image input, where the performance stays at one level in the small compression
-regime, and then gradually decays at high compression levels. Noteworthy is the presence
-of a trough in the pre fine-tuning stage performance in the small compression regime on figures
-\ref{fig:appendix__mnist-like__trade-off__ARD__raw},
-\ref{fig:appendix__mnist-like__trade-off__VD__raw},
-\ref{fig:appendix__cmp__mnist-like__trade-off__ARD__raw},
-and \ref{fig:appendix__cmp__mnist-like__trade-off__VD__raw}, which then slowly disappears
-as compression increases.
-
-The following scatter plots depict the samples from the compression-performance trade-off
-curve of simple networks studied in the experiments on the MNIST-like datasets. Transparent
-horizontal bands on each plot represent min-max performance spread of an uncompressed
-network on the test split. The points illustrate the final trade-off of the compressed
-networks after fine-tuning, while their tails show the performance gain or loss due to
-the fine-tuning.
-
-We recap the set-up of each additional experiment on MNIST-like datasets:
-\begin{itemize}
-  \item staged training, with weight and optimizer state transfer
-  \item $40$, $75$, and $40$ epochs for ``dense'', ``sparsify'', and ``fine-tune'' stagers, respectively
-  \item ADAM optimizer with learning rate $10^{-3}$ before the $10$-th, and $10^{-4}$
-  afterwards
-  \item global $\ell_2$-norm gradient clipping set at $\tfrac12$
-  \item training batches of size $128$ from a fixed randomly subset ($10^4$ images) of the training split
-  \item the multiplier of the Kullback-Leibler term in ELBO varies over $
-    C \in \{
-      \tfrac32 2^{-\tfrac{k}2} \colon k=2, \cdots, 38
-    \}
-  $
-  \item the sparsification threshold $\tau$ is set to $-\tfrac12$
-\end{itemize}
-Each experiment has been performed $5$ times to obtain a small sample of performance-compression
-values for each setting of $C$.
-
 Each figure shows the compression-accuracy trade-off of a particular method and input features
@@
 
-The following observations can be made from the conducted experiment:
-\begin{itemize}
-  \item $\cplx$-valued networks do not have as much spare capacity as $2 \real$ due to
-  constants imposed by multiplication in $\cplx$ numbers (\ref{fig:appendix__cmp__mnist-like__trade-off__ARD__raw},
-  \ref{fig:appendix__cmp__mnist-like__trade-off__VD__raw})
-  \item Variational Dropout and Automatic Relevance Determination offer similar compression-performance
-  trade-off, with negligibly lower compression by the latter (both $\real$ and $\cplx$ versions,
-  e.g. figures \ref{fig:appendix__mnist-like__trade-off__ARD__raw} and \ref{fig:appendix__mnist-like__trade-off__VD__raw})
-  \item smaller networks tend to be less compressible (figures \ref{fig:appendix__cmp__mnist-like__trade-off__ARD__fft},
-  \ref{fig:appendix__cmp__mnist-like__trade-off__VD__fft})
-\end{itemize}
-
 \begin{figure}[b]
   \centering
-  \begin{subfigure}[b]{0.5\textwidth}
-    \centering
+  \begin{subfigure}[b]{0.5\columnwidth}
+    \centering
+    % used in main text
     \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__emnist_letters__fft__-0.5.pdf}
   \end{subfigure}%
-  \begin{subfigure}[b]{0.5\textwidth}
+  \begin{subfigure}[b]{0.5\columnwidth}
     \centering
@@
   \end{subfigure} \\ %
-  \begin{subfigure}[b]{0.5\textwidth}
+  \begin{subfigure}[b]{0.5\columnwidth}
     \centering
@@
   \end{subfigure}%
-  \begin{subfigure}[b]{0.5\textwidth}
+  \begin{subfigure}[b]{0.5\columnwidth}
     \centering
@@
   \centering
-  \begin{subfigure}[b]{0.5\textwidth}
-    \centering
+  \begin{subfigure}[b]{0.5\columnwidth}
+    \centering
+    % used in main text
     \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__emnist_letters__fft__-0.5.pdf}
   \end{subfigure}%
-  \begin{subfigure}[b]{0.5\textwidth}
+  \begin{subfigure}[b]{0.5\columnwidth}
     \centering
@@
   \centering
-  \begin{subfigure}[b]{0.5\textwidth}
-    \centering
+  \begin{subfigure}[b]{0.5\columnwidth}
+    \centering
+    % used in main text
     \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__emnist_letters__raw__-0.5.pdf}
   \end{subfigure}%
-  \begin{subfigure}[b]{0.5\textwidth}
+  \begin{subfigure}[b]{0.5\columnwidth}
     \centering
@@
   \end{subfigure} \\%
-  \begin{subfigure}[b]{0.5\textwidth}
+  \begin{subfigure}[b]{0.5\columnwidth}
     \centering
@@
   \centering
-  \begin{subfigure}[b]{0.5\textwidth}
-    \centering
+  \begin{subfigure}[b]{0.5\columnwidth}
+    \centering
+    % used in main text
     \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__emnist_letters__raw__-0.5.pdf}
   \end{subfigure}%
-  \begin{subfigure}[b]{0.5\textwidth}
+  \begin{subfigure}[b]{0.5\columnwidth}
     \centering
@@
   \centering
-  \begin{subfigure}[b]{0.5\textwidth}
+  \begin{subfigure}[b]{0.5\columnwidth}
     \centering
@@
   \centering
-  \includegraphics[width=\linewidth]{figure__cifar__trade-off/appendix__augmentedcifar10__raw__-0.5.pdf}
+  \includegraphics[width=\columnwidth]{figure__cifar__trade-off/appendix__augmentedcifar10__raw__-0.5.pdf}
   \caption{%

### 2020-03-23 paper/paper.tex
thorough proofread 7 (sec 5.3 appendix D) * modified positioning in minst figures * moved CIFAR10 from appendix into main text, dropped old 2x replicated results * properly cite CIFAR10

@@
 % a couple of plots from MNIST and Fashion-MNIST
-\begin{figure}[!ht]
+\begin{figure}[!t]
   \centering
@@
 
-\begin{figure}[!ht]
+\begin{figure}[!t]
   \centering
@@
 
-We use accuracy as the performance metric for multi-class image classification on CIFAR10 datasets.
-
-% mention the same experimental setup as in MNIST
-Experiments on CIFAR10 dataset are set up similarly to MNIST-like experiment, except
-that we study VGG16 model \citep{simonyan_very_2015} and its $\cplx$-counterpart and
-replicate each experiment only twice.
-%
-% describe the VGG16 model and its cplx-valued modification
-The $\cplx$-VGG16 model is architecturally identical to VGG16, except for all layers being
-replaced by their $\cplx$-valued versions. We halve the sizes of intermediate layers in
-$\cplx$ model to assess comparability \citep{monning_evaluation_2018}.
-%
-Each network is trained stagewise for $20$, $40$,
-and $20$ epochs on the full training split of $50k$ colour $32\times32$ images. We use
-only raw colour features (\texttt{raw}). We apply random crop and horizontal flips as
-data augmentation and use a learning rate scheduler in SGD, which scales the base learning
-rate after $5$, $10$, and $20$-th epoch by $\tfrac1{10}$, $\tfrac1{20}$ and $\tfrac1{100}$,
-respectively.
-
-% draw some conclusions
-Figure~\ref{fig:figure__cifar10__trade-off} shows that although the prior used in ARD method
-offers slightly less compression, it makes up for it by equally slightly better accuracy.
-Furthermore, the results imply that that the halved $\cplx$ network visibly underperforms
-in comparison with its $\real$ counterpart, although in MNIST-like experiment $\cplx$-valued
-network with the same inner feature dimensions demonstrates trade-off very similar to
-$\real$-network, which has half the number of real parameters than the former.
+We conduct an experiment on the CIFAR10 classification dataset \citep{krizhevsky_learning_2009}
+comprising $32\times 32$ color images of $10$ classes to study the compression-performance
+trade-off of a moderately large deep network.
+% same experimental setup as in MNIST, describe the VGG16 model and its cplx-valued modification
+The experiment is set up similarly to MNIST-like experiment, except that we train $\real$
+VGG16 network \citep{simonyan_very_2015} and its $\cplx$ variant, in which we have replaced
+$\real$-valued layers with their $\cplx$-valued counterparts. $\real$ and $\cplx$ VGG16 have
+the same feature sizes in intermediate layers.
+
+% differences with mnist
+Unlike experiment in sec.~\ref{sub:mnist_like_datasets}, we consider the raw features only,
+use full training split, and allocate $20$, $40$, and $20$ epochs to each stage. During training
+the mini-batch of $128$ samples is randomly augmented by randomly flipping horizontally and
+cropping. Random cropping is done by zero-padding each side by four pixels and extracting a
+random $32\times 32$ patch from the $40\times 40$ intermediate image.
+%
+We vary $C$ in \eqref{eq:elbo_with_coef} over $
+  \{\tfrac32 2^{-\tfrac{k}2} \colon k=7, \cdots, 15\}
+$, compare VD and ARD methods, and measure accuracy on CIFAR10 test split.
 
@@
   \begin{subfigure}[b]{1.\columnwidth}  % imcl2019-style swears at this
-    \centering
-    \includegraphics[width=\columnwidth]{figure__cifar__trade-off/legacy__augmentedcifar10__raw__-0.5.pdf}
+    % \includegraphics[width=\columnwidth]{figure__cifar__trade-off/legacy__augmentedcifar10__raw__-0.5.pdf}
+    \includegraphics[width=\columnwidth]{figure__cifar__trade-off/appendix__augmentedcifar10__raw__-0.5.pdf}
   \end{subfigure}
   \caption{%
-    Compression-accuracy frontier for $\real$ and $\tfrac12 \cplx$ versions of VGG16 on CIFAR10.
+    The compression-accuracy frontier for VGG16 ($\real$ and $\cplx$) on CIFAR10.
   }
@@
 \end{figure}
+
+% draw some conclusions
+Figure~\ref{fig:figure__cifar10__trade-off} shows that, although ARD method offers slightly
+less compression, it makes up for it by marginally better accuracy post fine-tune. VGG16 and
+$\cplx$-VGG16 exhibit similar declining compression-accuracy trade-off, but due to higher
+capacity $\cplx$-valued network yields higher accuracy \citep{monning_evaluation_2018}. Unlike
+MNIST, fine-tuning stage significantly improves the test performance, which, we speculate, might
+be due to dataset augmentation and deeper model.
 
@@
 % section mnist_like_experiments (end)
-
-\clearpage
-
-\section{CIFAR10 experiments} % (fold)
-\label{sec:cifar_experiments}
-
-In addition to the results reported in the main paper, we conduct additional experiment
-on CIFAR10 and VGG16 with a much more slowly annealed learning rate. Similar to MNIST-like
-experiments, we start with the rate set to $10^{-3}$ and then reduce it by $10$ after the
-$10$-the epoch. In summary, for the CIFAR10 experiments we reuse the set-up with the following
-changes:
-\begin{itemize}
-  \item we allocate $20$, $40$, and $20$ epochs to each stage
-  \item the weight of the KL divergence term varies over a smaller grid $
-    C \in \{
-      \tfrac32 2^{-\tfrac{k}2} \colon k=7, \cdots, 15
-    \}
-  $
-  \item we use full $50$k training split of the CIFAR10 dataset for training and raw color
-  features only
-  \item dataset is randomly augmented: every image within a batch of size $128$ is randomly
-  cropped and flipped horizontally
-\end{itemize}
-Random cropping is done by zero-padding each side of a $32\times 32$ image by four pixels
-and then a extracting a random $32\times 32$ patch from the $40\times 40$ intermediate image.
-
-We experiment with $\real$ VGG16 network \citep{simonyan_very_2015} and its $\cplx$-valued
-variant, which straightforwardly replaces $\real$ layers with their $\cplx$ counterparts.
-
-\begin{figure}[htb]
-  \centering
-  \includegraphics[width=\columnwidth]{figure__cifar__trade-off/appendix__augmentedcifar10__raw__-0.5.pdf}
-  \caption{%
-    The compression-accuracy trade-off for $\real$ and $\cplx$ VGG16 using raw input features.
-  }
-  \label{fig:appendix__cifar__trade-off__VGG16__raw}
-\end{figure}
-
-% section cifar_experiments (end)
 

### 2020-03-24 paper/paper.tex
thorough proofread 8 (sec 5.4) * rewritten musicnet section * added investigation into why undercompressed models suffer from fine-tuning

@@
 
-\subsection{musicNet} % (fold)
+\subsection{MusicNet} % (fold)
 \label{sub:musicnet}
@@
 % describe musicnet as in Trabelsi et al. (2017) also get some hints from thickstun_learning_2017
-MusicNet \citep{thickstun_learning_2017} is an annotated audio dataset, consisting of $330$
-musical compositions. Following \citet{trabelsi_deep_2017}, we use it in automatic music
-transcription task and study the $1d$ VGG-like $\cplx$-convent proposed therein. Similarly to
-the study, we downsample the audio from 44.1kHz to 11kHz, retain only $84$ out of $128$ labels,
-and hold-out the same validation and test splits. During each training epoch we sample $1000$
-mini-batches of the remaining $321$ compositions, with each mini-batch comprised of a random
-full window of $4096$ samples picked from each waveform and transformed from $\real$ to
-$\cplx$ with $1d$ FFT. Annotation labels are taken at the mid-point of the window.
-
-Preliminary experiments with the model without sparsification have shown that early stopping
-almost always terminates the training process within the first $10-20$ epochs with the validation
-performance peaking at $10-15$ epochs, much sooner than $200$ epochs used by \citet{trabelsi_deep_2017}.
-Thus we adopt shorter lasting stages: $12$, $32$ and $50$ epochs, which essentially turn the
-``dense'' stage into pretraining. Early stopping is used only during the ``fine-tune'' stage.
-To keep the learning rate schedule consistent, we allow the base rate of $10^{-3}$ to be scaled
-after $5$, $10$, and $20$-th epoch by $\tfrac1{10}$, $\tfrac1{20}$ and $\tfrac1{100}$, respectively.
-Other key deviations from the set-up used by \citet{trabelsi_deep_2017} include: shifting lower
-frequencies to the centre of the window to maintain locality after applying the FFT
-(sec.~\ref{sub:mnist_like_datasets}), and clipping $\ell_2$ norm of the gradients to $0.05$.
-
-% perfromance metrics
-Similarly to \citet{trabelsi_deep_2017} performance in experiments with
-MusicNet is measured with (pooled) average precision. The evaluation is done after ``dense''
-stage, before the beginning and upon termination of the ``fine-tune'' stage.
+We use MusicNet \citep{thickstun_learning_2017}, an audio dataset of $330$ annotated
+musical compositions, to investigate compressibility of the $1d$ VGG-like $\cplx$-convent
+proposed by \citet{trabelsi_deep_2017}. Similarly to the study, we downsample the audio
+from 44.1kHz to 11kHz, retain only $84$ out of $128$ labels, and hold-out the same validation
+and test compositions, on which we score the models with the pooled average precision.
+Each epoch lasts for $1000$ random mini-batches of the remaining $321$ pieces. The input
+features are $\cplx$-valued Fourier transformed windows of $4096$ samples from each waveform.
+The label vectors are taken from annotations at the middle of the window.
+
+Experiments with the uncompressed model aimed at replicating the result of \citet{trabelsi_deep_2017}
+have shown that early stopping almost always terminates much sooner, than $200$ epochs used
+in their study: within the first $10-20$ epochs with the validation performance peaking at
+$10-15$ epochs and steadily declining afterwards.
+%
+Thus we opt to use shorter stages: $12$, $32$ and $50$ epochs (sec.~\ref{sub:staging}), with
+early stopping activated only during the ``fine-tune'' stage. To keep the learning rate schedule
+consistent, we scale the learning rate of $10^{-3}$ after $5$, $10$, and $20$-th epoch by
+$\tfrac1{10}$, $\tfrac1{20}$ and $\tfrac1{100}$, respectively.
+
+We deviate from the set-up used by \citet{trabelsi_deep_2017} by clipping $\ell_2$ norm of the
+gradients to $0.05$ and shifting the low frequencies of the input to the centre to maintain
+spatial locality for convolutions.
+
+We test complex ARD (sec.~\ref{ssub:ard_prior}) and VD (sec.~\ref{ssub:vd_prior}) methods
+and vary $
+  C \in \{\tfrac14, \tfrac12, \tfrac34, 1\} \cdot 10^{-k}
+$ for $k=1, 2, 3$, while keeping $\tau$ at $-\tfrac12$. The performance is measured after
+``dense'' stage, before the beginning and upon termination of fine-tuning.
+%
+Additionally, we test the model of \citet{trabelsi_deep_2017}, in which we purposefully
+halve the receptive field of the first convolution from $6$ to $3$ (denoted by suffix $k_3$).
+The motivation is to test if the handicap introduced by the forced compression of the most
+upstream layer can be alleviated by non-uniform compression, induced by variational dropout.
+We test only complex VD in this sub-experiment, since prior results have not demonstrated
+significant superiority of one method over another.  % it should've been ARD
 
@@
   \caption{%
-    Performance-compression trade-off using \textbf{\color{blue} VD} and \textbf{\color{orange} ARD}.
-    The \textbf{\color{pink} version} of the network with kernel $3$ in the first convolution is
-    compressed with VD only.
+    Performance-compression curve for \textbf{\color{blue} VD}, \textbf{\color{orange} ARD},
+    and the ${\color{pink} k_3}$ version compressed with VD.
   }
@@
 
-In each experiment we vary the method and the value $C$, while keeping $\tau$ at $-\tfrac12$.
-
-Figure~\ref{fig:musicnet__trade-off} shows the resulting performance-compression frontier
-for the deep network of \citet{trabelsi_deep_2017} and its version, in which we purposefully
-halve the spatial size of the first $1d$ convolution kernel from $6$ to $3$ (denoted by
-suffix \textit{k}$3$). The motivation is to test if the handicap introduced by the forced
-compression of the most upstream layer can be alleviated through non-uniform compression,
-induced by variational dropout. We test only VD (sec.~\ref{ssub:vd_prior}) this
-sub-experiment, since prior results have not demonstrated significant superiority of one method
-over another (sec.~\ref{ssub:ard_prior}).
-
-For compression levels lower than $50$, the final stage overfits the network, since it still
-remains overparameterized. For the rates higher than $\approx 100$ the ``fine-tune'' stage
-serves its purpose, essentially, due regularizing effects of high sparsity. There is evidence
-in favour of achievability of the SOTA average precision of \citet{trabelsi_deep_2017} within
-the $50$-$100$ compression region with $\cplx$-valued variational dropout with ARD prior
-(sec.~\ref{ssub:ard_prior}).
-
-% conlcusions
-The impact of the ``fine-tune'' stage appears to be strongly influenced by the compression
-rate. We can observe in this and, more prominently, in MusicNet experiment (sec.~\ref{sub:musicnet})
-that higher compression rate render the model more regularized, leaving less capacity for
-overfitting.
-% more ``holes'' Bayesian dropout ``poked'' makes the ``fine-tune'' serve as extended training.
-
+Figure~\ref{fig:musicnet__trade-off} shows the resulting performance-compression frontier.
+ARD slightly outperforms VD in terms of performance, but both deliver similar compression
+rates. The trade-off demonstrates that with the proposed $\cplx$-valued variational dropout
+methods (sec.~\ref{sec:c_variational_dropout}) and post-sparsification fine-tuning it is
+possible to achieve average precision level comparable to the result of \citet{trabelsi_deep_2017}
+with a model compressed $50\times$-$200\times$. Furthermore, the $k_3$ model, compressed
+$110 \times$ with $\cplx$ VD, outperforms its uncompressed baseline, but yields lower
+performance than the full model.
+
+\begin{figure}[!t]
+  \centering
+  \begin{subfigure}[b]{1.\columnwidth}  % imcl2019-style swears at this
+    \centering
+    \includegraphics[width=\columnwidth]{figure__fine-tune_fx__early.pdf}
+  \end{subfigure}
+  \caption{%
+    Early stopping epoch at fine-tuning stage.
+  }
+  \label{fig:musicnet__early_stopping}
+\end{figure}
+
+% why is there such a dramamtic difference in impact of ``fine-tune''?
+We provide the following interpretation of the apparent difference in performance impact
+of the ``fine-tune'' stage between less than $50\times$ and higher than $100\times$ compression
+regimes in figure~\ref{fig:musicnet__trade-off}, also observed in sec.~\ref{sub:mnist_like_datasets}.
+%
+% * early stopping kick in at around 10-20 epoch
+% * performance peaks at 10-15 epoch and then gradually declines
+The value of $C$ in \eqref{eq:elbo_with_coef} is a good proxy for the ranking of the final
+compression rate since it directly affects the feedback from sparsifying prior. So, with
+low $C$ models get less compressed during $50$ epoch allotted for ``sparsify'' stage, which
+appears to be insufficient to move model away from the parameters after the dense stage.
+It is reasonable therefore to expect that for undercompressed models the fine-tuning stage
+acts essentially as a continuation of the pre-training stage. Since we have observed that
+longer training invariably deteriorates the validation performance, the ``fine-tune'' stage
+leads to overfitting. Figure~\ref{fig:musicnet__early_stopping}, which shows that the models,
+which have been sparsified with $C$ less than $\tfrac1{400}$ and have $50\times$ compression,
+need considerably less training epochs before early stopping terminates the process.
+
+% testing the fx of the threshold
 \begin{figure}[!t]
@@
 % effects of extra training epochs and the impact of tau
-Figure~\ref{fig:hist__and__threshold__tradeoff} is constructed
-for $C \in \{\tfrac1{20}, \frac1{200}\}$ before running the ``fine-tune'' stage. From
-\eqref{eq:elbo_with_coef}, the relative positions of the compression curves on this
-plot, and the results of experiments below it can be concluded that $C$ has much more
-substantial impact on the sparsity and performance, than the choice of $\tau$. Furthermore,
-for $\tau > 0$ the performance quickly saturates while compression creeps downwards.
+We take the models from experiments with $C \in \{\tfrac1{20}, \frac1{200}\}$ and plot
+the compression and performance metrics before fine-tuning for various threshold levels
+on figure~\ref{fig:hist__and__threshold__tradeoff}. From \eqref{eq:elbo_with_coef} and
+the relative positions of the compression curves it can be concluded that $C$ has much
+more substantial impact on the sparsity and performance, than the choice of $\tau$.
+Furthermore, for $\tau > 0$ the performance quickly saturates while compression creeps
+downwards.
+
+% (pending) threshold and fune-tuning?
+% By reducing the excess degrees of freedom, high compression rates could act as a regularizer,
+% leaving less capacity for overfitting. Which seems sufficient enough for models in higher
+% compression regime
+% more ``holes'' Bayesian dropout ``poked'' makes the ``fine-tune'' serve as extended training.
 

### 2020-03-24 paper/paper.tex
thorough proofread 9 (into and outro) * reworded clunky paragraph on cplx-networks in the intro * rewritten the conclusion section

@@
 %
-\citet{hirose_complex-valued_2009} argues that the key merit of $\cplx$-valued neural
-networks is simultaneous phase rotation and amplitude adjustment, intrinsic to multiplication
-in $\cplx$ field. Despite inherently higher arithmetic complexity, which stems from up to four
-floating point operations per single $\cplx$ multiplication
-$\cplx$-arithmetic reduces ineffective degrees of freedom in comparison with an analogous
-double-dimensional $\real$-valued network. \citet{hirose_complex-valued_2009} lists numerous
-applications related to acoustic and radio signal processing and demonstrates superiority of
-$\cplx$-networks in the task of shallow landmine detection using ground penetrating radar
-imaging. More recently they have been applied to music transcription and speech recognition
-\citep{trabelsi_deep_2017}. \citet{arjovsky_unitary_2016} propose $\cplx$-valued unitary-RNNs
-to deal with exploding~/~vanishing gradients and apply the recurrent models to long-term
-dependence prediction tasks. \citet{wisdom_full-capacity_2016} expand on their work by optimizing
-recurrent weights on the $\cplx^{n \times n}$ Stiefel manifold. And \citet{wolter_complex_2018}
-investigate different $\cplx$-valued gating mechanisms for unitary-RNNs and conduct experiments
-on human motion prediction and music transcription. \citet{yang_complex_2019} develop complex
+\citet{hirose_complex-valued_2009} argues that $\cplx$-valued networks merit from the
+simultaneous phase rotation and amplitude adjustment, intrinsic to $\cplx$ arithmetic,
+which reduce ineffective degrees of freedom in comparison with an double-dimensional
+$\real$-valued networks. Their study lists numerous applications related to acoustic
+and radio signal processing and demonstrates superiority of $\cplx$-networks in the
+task of shallow landmine detection using ground penetrating radar imaging, in spite of
+inherently higher arithmetic complexity of $\cplx$-networks, stemming from $3-4$ floating
+point operations per single $\cplx$ multiplication. More recently $\cplx$-networks have
+been applied to music transcription and speech recognition \citep{trabelsi_deep_2017}.
+\citet{arjovsky_unitary_2016} propose $\cplx$-valued unitary-RNNs to deal with exploding~/~vanishing
+gradients and apply the recurrent models to long-term dependence prediction tasks.
+\citet{wisdom_full-capacity_2016} expand on their work by optimizing recurrent weights on
+the $\cplx^{n \times n}$ Stiefel manifold. And \citet{wolter_complex_2018} investigate
+different $\cplx$-valued gating mechanisms for unitary-RNNs and conduct experiments on
+motion prediction and music transcription. \citet{yang_complex_2019} develop complex
 transformer, with $\cplx$-attention and complex encoder-decoder, and apply it to music
-transcription and wireless signal classification.
+transcription and wireless signal classification. \citet{tarver_design_2019} achieve
+significantly lower out-of-band performance with a $\cplx$-valued network in Digital Signal
+Predistortion task.
 
@@
 $\cplx$-valued networks. In this section we describe the approximation and derive the
-divergence penalties in \eqref{eq:elbo}.
+divergence penalties in \eqref{eq:elbo}. Similarly to $\real$-valued Variational Dropout,
+the proposed $\cplx$-valued extension can be straightforwardly enhanced to provide
+structured sparsity.
 
@@
 
-We study the compression-performance trade-off of the proposed Bayesian sparsification
+We study the performance-compression trade-off of the proposed Bayesian sparsification
 method for $\cplx$-valued networks presented above on image classification and music
@@
 We conduct a moderately sized experiment on MNIST-like datasets of $28\times 28$ greyscale
-images to study the compression-performance trade-off of the proposed $\cplx$-variational
+images to study the performance-compression trade-off of the proposed $\cplx$-variational
 dropout: MNIST \citep{lecun_gradient-based_1998}, KMNIST \citep{clanuwat_deep_2018},
@@
 We conduct an experiment on the CIFAR10 classification dataset \citep{krizhevsky_learning_2009}
-comprising $32\times 32$ color images of $10$ classes to study the compression-performance
+comprising $32\times 32$ color images of $10$ classes to study the performance-compression
 trade-off of a moderately large deep network.
@@
 
-Despite having higher arithmetic complexity, complex-valued models provide built-in
-amplitude-phase transformations and regularization \citep{hirose_complex-valued_2009}
-and enjoy superior performance on naturally $\cplx$-valued datasets \citep{tarver_design_2019}.
-In this study we address the issue of excessive arithmetic complexity of complex-valued
-networks by extending the existing Bayesian compression techniques by \citet{kingma_variational_2015},
+In this study we have extended Variational Dropout methods of \citet{kingma_variational_2015},
 \citet{molchanov_variational_2017} and \citet{kharitonov_variational_2018} to $\cplx$-valued
-parameters. To this end we have conducted a large numerical study of such networks to assess
-the performance-compression rate trade-off and have achieved performance comparable to
-the state-of-the-art in $\cplx$-valued networks on the MusicNet dataset.
-
-Much like $\real$-valued variational dropout, the proposed $\cplx$-valued extension can be
-straightforwardly enhanced to provide structured sparsity. The results of this study have
-direct implications for real-time signal processing with embedded deep learning applications
-both in terms of lower storage requirements and higher throughput stemming from fewer
-floating-point multiplications.
+Bayesian networks. To validate the proposed technique we have conducted a large numerical
+study of complex-valued networks with simple architectures in image recognition tasks to
+assess the feasible performance-compression trade-off. At the cost of marginally lower performance,
+we have achieved $50-100\times$ compression of the state-of-the-art deep $\cplx$-valued network
+of \citet{trabelsi_deep_2017} on the MusicNet.
+
+The results of this study have direct implications for real-time signal processing with
+embedded deep learning applications both in terms of lower storage requirements and higher
+throughput stemming from fewer floating-point multiplications, despite higher arithmetic
+complexity of $\cplx$-valued networks.
 

### 2020-03-24 paper/paper.tex
thorough proofread X (appendix) * move section A after sectiion C * reverted back to onecolumn format

@@
-\documentclass[a4paper,10pt,twocolumn]{article}
+\documentclass[a4paper,10pt,onecolumn]{article}
 
@@
 
-\section{Complex-valued local reparameterization} % (fold)
-\label{sec:complex_valued_local_reparameterization}
-
-%notation
-By $e_i$ we denote the $i$-th real unit vector of dimensionality \textit{conforming} to the
-matrix-vector expression it is used in. Let $\vec{M}$ denote \textit{row-major} flattening
-of $M$ into a vector, i.e. in lexicographic order of its indices. $\diag{(\cdot)}$ embeds
-$\cplx^n$ into $n\times n$ diagonal matrices, and $\otimes$ denotes the Kronecker product,
-for which we note the following identities $
-  \vec{P Q R} = (P \otimes R^\top) \vec{Q}
-$, and $
-  (P \otimes R) (C \otimes S) = P Q \otimes R S
-$ \citep{petersen_matrix_2012}.
-% It follows from the definition of the Kronecker product
-% of $P$ and $R^\top$ and the row-major order vectorization.
-
-If we assume a mean field $\cplx$-Gaussian approximate posterior for $
-  W \in \cplx^{n\times m}
-$, then
-\begin{equation}  \label{eq:c-gauss-vi-general-vec}
-  \vec{W}
-    \sim \mathcal{N}^{\cplx}_{nm} \bigl(
-      \vec{\mu}, \diag{\vec{\Sigma}}, \diag{\vec{C}}
-    \bigr)
-  \,,
-\end{equation}
-where mean, \textit{variance} and relation are given by matrices $
-  \mu, \Sigma, C \in \cplx^{n\times m}
-$ with $\Sigma_{ij} \geq 0$, and $
-  \lvert C_{ij} \rvert^2 \leq \Sigma_{ij}
-$. For any $x \in \cplx^m$ and $b\in \cplx^n$ $
-  y = W x + b
-    = (I_n \otimes x^\top) \vec{W} + b
-$, whence the covariance and relation matrices of $y$ are
-\begin{align}
-  (I \otimes x^\top) \diag{\vec{\Sigma}} (I \otimes x^\top)^{\hop}
-    % = \sum_{ij} (I \otimes x^\top) e_i \otimes e_j
-    %   \Sigma_{ij} (e_i \otimes e_j)^\top (I \otimes x^\top)^{\hop}
-    % = \sum_{ij} (e_i \otimes x^\top e_j)
-    %   \Sigma_{ij} (e_i \otimes x^\top e_j)^{\hop}
-    % = \sum_{ij} (e_i \otimes x_j) \Sigma_{ij} (e_i^\top \otimes \conj{x}_j)
-    & = \sum_{i=1}^n (e_i e_i^\top) \sum_{j=1}^m \Sigma_{ij} x_j \conj{x}_j
-    \,,  \label{eq:cn-gauss-lrt-cov} \\
-  (I \otimes x^\top) \diag{\vec{C}} (I \otimes x^\top)^\top
-    % = \sum_{ij} (e_i \otimes x_j) C_{ij} (e_i \otimes x_j)^\top
-    & = \sum_{i=1}^n (e_i e_i^\top) \sum_{j=1}^m C_{ij} x_j^2
-    \,.  \label{eq:cn-gauss-lrt-rel}
-\end{align}
-Since \eqref{eq:cn-gauss-lrt-cov} and \eqref{eq:cn-gauss-lrt-rel} are diagonal, $(y_i)_{i=1}^n$
-are independent whence \eqref{eq:cn-affine} implies
-\begin{equation}  \label{eq:cplx-gauss-trick-appendix}
-  y_i
-    \sim \mathcal{N}^{\cplx}
-      \bigl(
-        e_i^\top \mu x + b_i,
-        \, \sum_{j=1}^m \Sigma_{ij} \lvert x_j \rvert^2,
-        \, \sum_{j=1}^m C_{ij} x_j^2
-      \bigr)
-    \,.
-\end{equation}
-Hence \eqref{eq:cplx-gauss-trick} follows.
-
-% section complex_valued_local_reparameterization (end)
-
 \section{Gradient of the KL-divergence in $\real$ case} % (fold)
@@
 
-Each figure shows the compression-accuracy trade-off of a particular method and input features
-for \textit{SimpleConvModel} and \textit{TwoLayerDenseModel} models for all four of the studied
-datasets (described in the main text): \emph{top-left} EMNIST-Letters, \emph{top-right} KMNIST,
-\emph{bottom-left} Fashion MNIST, and \emph{bottom-right} MNIST.
+The plots presented in this appendix support the conclusions made in the main text and
+provide an overview of the experiments conducted on MNIST-like datasets.
+
+Each figure shows the compression-accuracy trade-off of a particular method and input
+features for \textit{SimpleConvModel} and \textit{TwoLayerDenseModel} models for all four
+of the studied datasets (described in the main text): EMNIST-Letters on the \textit{top-left},
+KMNIST -- \textit{top-right}, Fashion MNIST -- \textit{bottom-left}, and MNIST on the
+\textit{bottom-right}.
 %
@@
 \ref{fig:appendix__mnist-like__trade-off__ARD__raw}, and \ref{fig:appendix__mnist-like__trade-off__VD__raw}
-present $\real$ and $\cplx$ models with \emph{the same architecture}. We also report the
-trade-off comparison, when the argument by \citet{monning_evaluation_2018} for higher intrinsic
-capacity of $\cplx$-valued networks has been taken into account.
+present $\real$ and $\cplx$ models with \textit{the same intermediate feature sizes}.
+
+We also report the trade-off comparison, when the argument by \citet{monning_evaluation_2018}
+for higher intrinsic capacity of $\cplx$-valued networks has been taken into account.
 %
@@
 
+% \clearpage
+
 % section mnist_like_experiments (end)
+
+\section{Complex-valued local reparameterization} % (fold)
+\label{sec:complex_valued_local_reparameterization}
+
+%notation
+By $e_i$ we denote the $i$-th real unit vector of dimensionality \textit{conforming} to the
+matrix-vector expression it is used in. Let $\vec{M}$ denote \textit{row-major} flattening
+of $M$ into a vector, i.e. in lexicographic order of its indices. $\diag{(\cdot)}$ embeds
+$\cplx^n$ into $n\times n$ diagonal matrices, and $\otimes$ denotes the Kronecker product,
+for which we note the following identities $
+  \vec{P Q R} = (P \otimes R^\top) \vec{Q}
+$, and $
+  (P \otimes R) (C \otimes S) = P Q \otimes R S
+$ \citep{petersen_matrix_2012}.
+% It follows from the definition of the Kronecker product
+% of $P$ and $R^\top$ and the row-major order vectorization.
+
+If we assume a mean field $\cplx$-Gaussian approximate posterior for $
+  W \in \cplx^{n\times m}
+$, then
+\begin{equation}  \label{eq:c-gauss-vi-general-vec}
+  \vec{W}
+    \sim \mathcal{N}^{\cplx}_{nm} \bigl(
+      \vec{\mu}, \diag{\vec{\Sigma}}, \diag{\vec{C}}
+    \bigr)
+  \,,
+\end{equation}
+where mean, \textit{variance} and relation are given by matrices $
+  \mu, \Sigma, C \in \cplx^{n\times m}
+$ with $\Sigma_{ij} \geq 0$, and $
+  \lvert C_{ij} \rvert^2 \leq \Sigma_{ij}
+$. For any $x \in \cplx^m$ and $b\in \cplx^n$ $
+  y = W x + b
+    = (I_n \otimes x^\top) \vec{W} + b
+$, whence the covariance and relation matrices of $y$ are
+\begin{align}
+  (I \otimes x^\top) \diag{\vec{\Sigma}} (I \otimes x^\top)^{\hop}
+    % = \sum_{ij} (I \otimes x^\top) e_i \otimes e_j
+    %   \Sigma_{ij} (e_i \otimes e_j)^\top (I \otimes x^\top)^{\hop}
+    % = \sum_{ij} (e_i \otimes x^\top e_j)
+    %   \Sigma_{ij} (e_i \otimes x^\top e_j)^{\hop}
+    % = \sum_{ij} (e_i \otimes x_j) \Sigma_{ij} (e_i^\top \otimes \conj{x}_j)
+    & = \sum_{i=1}^n (e_i e_i^\top) \sum_{j=1}^m \Sigma_{ij} x_j \conj{x}_j
+    \,,  \label{eq:cn-gauss-lrt-cov} \\
+  (I \otimes x^\top) \diag{\vec{C}} (I \otimes x^\top)^\top
+    % = \sum_{ij} (e_i \otimes x_j) C_{ij} (e_i \otimes x_j)^\top
+    & = \sum_{i=1}^n (e_i e_i^\top) \sum_{j=1}^m C_{ij} x_j^2
+    \,.  \label{eq:cn-gauss-lrt-rel}
+\end{align}
+Since \eqref{eq:cn-gauss-lrt-cov} and \eqref{eq:cn-gauss-lrt-rel} are diagonal, $(y_i)_{i=1}^n$
+are independent whence \eqref{eq:cn-affine} implies
+\begin{equation}  \label{eq:cplx-gauss-trick-appendix}
+  y_i
+    \sim \mathcal{N}^{\cplx}
+      \bigl(
+        e_i^\top \mu x + b_i,
+        \, \sum_{j=1}^m \Sigma_{ij} \lvert x_j \rvert^2,
+        \, \sum_{j=1}^m C_{ij} x_j^2
+      \bigr)
+    \,.
+\end{equation}
+Hence \eqref{eq:cplx-gauss-trick} follows.
+
+% section complex_valued_local_reparameterization (end)
 

### 2020-03-24 paper/paper.tex
synchronised the in-text color to the plot

@@
     Performance-compression curve for \textbf{\color{blue} VD}, \textbf{\color{orange} ARD},
-    and the ${\color{pink} k_3}$ version compressed with VD.
+    and the ${\color{gray} k_3}$ version compressed with VD.
   }

### 2020-03-25 paper/paper.tex
rewroded abstract, added urls to repositories

@@
 in embedded systems, where it is common to encounter data with natural complex domain
-representation. To this end we extend Variational Dropout to complex-valued neural
-networks. We verify the proposed Bayesian technique and assess the performance-compression
-trade-off by conducting a large-scale numerical study of $\cplx$-valued networks on
-two tasks: image recognition on MNIST-like and CIFAR10 datasets and music transcription
-on MusicNet. We reliably replicate the state-of-the-art result by \citet{trabelsi_deep_2017}
-for $\cplx$-valued networks on MusicNet with $50-100\times$ compression rate.
+representation. To this end we extend Sparse Variational Dropout to complex-valued neural
+networks and verify the proposed Bayesian technique by conducting a large numerical
+study of the performance-compression trade-off of $\cplx$-valued networks on two tasks:
+image recognition on MNIST-like and CIFAR10 datasets and music transcription on MusicNet.
+We replicate the state-of-the-art result by \citet{trabelsi_deep_2017} on MusicNet with
+a $\cplx$-valued network compressed $50-100\times$ at a small performance peanlty.
 \end{abstract}
@@
 
+Source code for the experiments conducted in this study and figures is available at
+\url{https://github.com/ivannz/complex_paper}.
+%
+Source code for a PyTorch extension which implements $\cplx$-valued Variational Dropout and
+ARD layers, and provides basic layers for $\cplx$-valued networks, including maskable
+sparsified layers, is available at
+\url{https://github.com/ivannz/cplxmodule}.
+\smallskip
+
 We study the performance-compression trade-off of the proposed Bayesian sparsification

### 2020-03-25 setup.py
title update and version bump

@@ -2,7 +2,7 @@ from distutils.core import setup, Extension
 
 setup(
     name="cplxpaper",
-    version="0.5",
+    version="2020.3",
     description="""Backend for experiments presented in Bayesian"""
                 """ Sparsification of Deep Complex-valued Networks.""",
     license="MIT License",

### 2020-03-25 paper/paper.tex
update title, fix git repo release
typos in abstract, what a shame

@@
 
-\title{Bayesian Sparsification of Deep $\cplx$-valued networks}
+\title{Bayesian Sparsification Methods for Deep Complex-valued Networks}
 \author{Ivan Nazarov, and Evgeny Burnaev}
@@
 We replicate the state-of-the-art result by \citet{trabelsi_deep_2017} on MusicNet with
-a $\cplx$-valued network compressed $50-100\times$ at a small performance peanlty.
+a complex-valued network compressed by $50-100\times$ at a small performance penalty.
 \end{abstract}
@@
 Source code for the experiments conducted in this study and figures is available at
-\url{https://github.com/ivannz/complex_paper}.
+\url{https://github.com/ivannz/complex_paper/tree/v2020.3}.
 %

### 2020-03-27 paper/paper.tex
cited and added Louizos et al. (2017) for hierarchical priors and group sparsity

@@
 capabilities of Variational Dropout, optimizing $\alpha_j$ for each individual parameter,
-or across groups of parameters for structured sparsity. \citet{kharitonov_variational_2018}
+or across groups of parameters for structured sparsity.
+%
+\citet{louizos_bayesian_2017} consider hierarchical prior and approximation, which couples
+the parameters $\omega_j$ within a group $J$ through shared scaling $z_J$ and enables
+pruning entire input features in each layer.
+% {louizos_bayesian_2017} eq. (11) variance -> gaussian entropy -> informative bits 
+%
+\citet{kharitonov_variational_2018}
 address theoretical issues with improper priors and propose a method based on \textit{
@@
 \end{equation}
+% \begin{align}
+%   \pi(\omega)
+%     &
+%     = \prod_J \pi(s_J)
+%       \prod_{j\in J} \pi(\omega_j \vert s_J)
+%     \propto \prod_J \frac1{\lvert s_J \rvert}
+%       \prod_{j\in J} \mathcal{N}(\omega_j \vert 0, s_J^2)
+%     \,, \\
+%   q_\theta(\omega)
+%     &
+%     % = \prod_J q_\theta(s_J)
+%     %   \prod_{j\in J} q_\theta(\omega_j \vert s_J)
+%     = \prod_J \mathcal{N}(s_J \vert \mu_J, \alpha_J \mu_J^2)
+%       \prod_{j\in J} \mathcal{N}(\omega_j \vert \mu_j s_J, \sigma_j^2 s_J^2)
+%     \,.
+% \end{align}
 
@@
 Their approach coupled with $\cplx\real$ calculus for backprop transforms a $\cplx$-valued
-network into an intricately connected $\real$-valued computational graph, constructured
+network into an intricately connected $\real$-valued computational graph, constructed
 to respects $\cplx$-arithmetic.

### 2020-03-29 paper/paper.tex
late night comit of the finished additional experiment with fune-tuning

@@
     \includegraphics[width=\columnwidth]{figure__musicnet__threshold.pdf}
+  \end{subfigure} \\
+  \begin{subfigure}[b]{1.\columnwidth}  % imcl2019-style swears at this
+    \centering
+    \includegraphics[width=\columnwidth]{figure__musicnet__threshold__fine-tune.pdf}
   \end{subfigure}
   \caption{%
-    Test split performance and compression rate for a $\cplx$-valued net on MusicNet.
+    Performance (smooth curve) and compression (curve with markers) of select experiments
+    before (\textit{top}) and after (\textit{bottom}) fine-tuning.
   }
@@
 the compression and performance metrics before fine-tuning for various threshold levels
-on figure~\ref{fig:hist__and__threshold__tradeoff}. From \eqref{eq:elbo_with_coef} and
+on figure~\ref{fig:hist__and__threshold__tradeoff} (top). From \eqref{eq:elbo_with_coef} and
 the relative positions of the compression curves it can be concluded that $C$ has much
@@
 
-% (pending) threshold and fune-tuning?
-% By reducing the excess degrees of freedom, high compression rates could act as a regularizer,
-% leaving less capacity for overfitting. Which seems sufficient enough for models in higher
-% compression regime
-% more ``holes'' Bayesian dropout ``poked'' makes the ``fine-tune'' serve as extended training.
+% (pending) threshold and fune-tuning? BETTER text
+Bottom plot in figure~\ref{fig:hist__and__threshold__tradeoff} show improved performance
+for thresholds below $-\tfrac12$ after fine-tuning. For higher $\tau$ the final stage
+improves performance of a highly compressed model ($C=0.05$), while leaving moderately
+compressed model ($C=0.005$) unaffected. This behaviour can be explained by the regularizing
+effect of high compression rates, which servely reduce the excess degrees of freedom,
+leaving less capacity for overfitting.
+% coarser grid than in top plot in order not to wait for 20 compute days, but 9.5 on
+% 4 x Geforce 1080Ti, 256 Gb, core-i7 machine, running 4*2 experiments in parallel
+
+% takeaway: fine tune seems to improve performance for highly compressed models, but
+% within a limit. Worth a try for moderately compressed models, but willl must likely
+% overfit for undercompressed models. Varying $C$ in \eqref{eq:elbo_with_coef} affects
+% sparsity more strongly, than varying $\tau$. But this is only observational.
 

### 2020-04-11 paper/paper.tex
slightly better conclusion from the fine-tuned threshold experiment

@@
 downwards.
-
-% (pending) threshold and fune-tuning? BETTER text
-Bottom plot in figure~\ref{fig:hist__and__threshold__tradeoff} show improved performance
-for thresholds below $-\tfrac12$ after fine-tuning. For higher $\tau$ the final stage
-improves performance of a highly compressed model ($C=0.05$), while leaving moderately
-compressed model ($C=0.005$) unaffected. This behaviour can be explained by the regularizing
-effect of high compression rates, which servely reduce the excess degrees of freedom,
-leaving less capacity for overfitting.
+%
+The bottom plot in figure~\ref{fig:hist__and__threshold__tradeoff} shows the effect of
+the ``fine-tune'' stage: for $\tau \leq -1$ it improves the test performance, while leaving
+it mostly unaffected for positive $\tau$. We attrbute this behaviour to regularization
+effect of high compression rate, which limits the capacity for overfitting by significantly
+reducing the excess degrees of freedom.
 % coarser grid than in top plot in order not to wait for 20 compute days, but 9.5 on

### 2020-04-11 paper/paper.tex
fixed mag-pruning misattribution

@@
 Certain model sparsification methods, e.g. sparsity inducing regularizers, and magnitude
-pruning \citep{zuo_compression_2019}, which reactivates zeroed parameters based on gradients,
+pruning \citep{zhu_prune_2017}, which reactivates zeroed parameters based on gradients,
 can be adapted directly to $\cplx$-valued models. Other methods require additional considerations.

### 2020-04-19 paper/paper.tex
fixed arxiv citations

@@
 Certain model sparsification methods, e.g. sparsity inducing regularizers, and magnitude
-pruning \citep{zhu_prune_2017}, which reactivates zeroed parameters based on gradients,
+pruning \citep{zhu_prune_2018}, which reactivates zeroed parameters based on gradients,
 can be adapted directly to $\cplx$-valued models. Other methods require additional considerations.
@@
 \citet{gale_state_2019} compare Variational Dropout, magnitude pruning, and $\ell_0$
-regularization \citep{louizos_learning_2017} on large-scale models. The latter is a
+regularization \citep{louizos_learning_2018} on large-scale models. The latter is a
 probabilistic regularization method, which penalizes the expected number of non-zero

### 2020-06-01 paper/paper.tex
minor typo fixes

@@
 simultaneous phase rotation and amplitude adjustment, intrinsic to $\cplx$ arithmetic,
-which reduce ineffective degrees of freedom in comparison with an double-dimensional
+which reduce ineffective degrees of freedom in comparison with double-dimensional
 $\real$-valued networks. Their study lists numerous applications related to acoustic
@@
     - \mathbb{E}_{\omega \sim q}
-      \log{p(\omega)}
+      \log{p(\omega \mid D)}
     \,,
@@
 By varying $C$ we adjust the importance of the sparsifying prior in learning $q_\theta(W)$,
-meaning that higher value yields more irrelevant parameters during in inference and makes
+meaning that higher value yields more irrelevant parameters during inference and makes
 layers sparser upon termination of this stage.
+% RFC: citation needed fot this "trick". Cite $\beta$-VAE maybe?
 
@@
 
-The overarching pattern in all experiments on MNIST-like datasets is that both ARD and VD yield
+The overarching pattern in all experiments on MNIST-like datasets is that both ARD and VD
 compress similarly and ARD offers marginal advantage in terms of performance after fine-tuning.
@@
 be due to dataset augmentation and deeper model.
+% reword this sentence
 
@@
     \centering
-    \includegraphics[width=\columnwidth]{figure__fine-tune_fx__early.pdf}
+    \includegraphics[width=\columnwidth]{figure__fine-tune_fx__early__compression.pdf}
   \end{subfigure}

### 2020-06-06 paper/rebuttal/rebuttal.tex
end of april rebuttal

\documentclass[10pt,a4paper,draft]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

\bibliographystyle{amsplain}

\usepackage{amsmath}
\usepackage{amssymb}

\usepackage{xcolor}
\usepackage{url}

\usepackage{dialogue}

\title{Rebuttal}
\author{Anonymous Authors}

\begin{document}
% \maketitle

Dear reviewers, we would like to thank you for your valuable comments, however space
limitations compelled us to respond to them altogether and not individually. We will
fix the mistakes you found, and shall make available the code for the experiments and
a library for C-valued Variational Dropout after the review process, regardless of its
outcome.
\medskip

% (rev 1, 5)
The fundamental motivation for C-valued networks is that there is evidence from signal
processing, which hints at them performing better both for R-valued and C-valued signals,
\cite{tarver_design_2019,sivachitra_planning_2015} and \cite{hu_initial_2016}. In terms
of arithmetic complexity, doubly-real networks require 4x more multiplications, while
C-valued require only 3x, due to the skew symmetric parameter constraint embedded in them
when viewed as a doubly-real to emulates C arithmetic. At the same time, higher redundancy
generally offers higher compression rates, and may enjoy better test performance for some
hyperparameters. Therefore, we conjecture that there would be no compressibility advantage
to C-networks. Thus the main reason to use C-valued networks is whether the domain knowledge
dictates that C-consistent transformations be used, i.g. with acoustic or radio
telecommunications' data, or MRI.

% (rev 3, 5)
Concerning the novelty of the study, it is the first application of Variational Inference
to C-valued networks, based on thorough analysis of the related work. The most closely
related study has been done by \cite{popa_complex-valued_2018}, who introduce C-valued Botlzmann
Machine and maximize ELBO over a fully-factorized posterior of Bernoulli distributions on
the hidden states of the machine. At the same time this is not the first attempt at compressing
C-valued networks. For instance, \cite{wu_compressing_2019} consider several compression
approaches, among which is fixed threshold-based pruning; and \cite{vecchi_compressing_2020}
apply sparsity-inducing regularization (LASSO) to quaternion-valued networks, which are
generalizations of complex numbers.

% (rev 3) on kl-scaling
For variational autoencoders scaling the KL term has been motivated by the need to control
the capacity and statistical independence of the latent information through a constraint on
the KL-divergence of the encoding variational posterior from the prior, \cite{higgins_beta-vae_2017}.
In Variational Dropout methods scaling is used to balance the gradient feedback of the loss
and the prior-matching terms of ELBO. In \cite{molchanov_variational_2017,kharitonov_variational_2018,gale_state_2019}
the coefficient C is linearly annealed from 0 to 1 during training. Unlike these studies,
we use constant C during `sparsify` stage in order to directly control the balance and explore
performance-compression trade-off by varying the weight of the complexity penalty of the
variational posterior distribution.

% (rev 3)
Variational Dropout permits non-uniform sparsity and as a Bayesian approach, allows estimation
of parameter uncertainty, which is useful for selecting sufficient bit precision level
\cite{louizos_bayesian_2017}. However, as a compression method, VD is more computationally
costly, than pruning, which has less arithmetic complexity and smaller memory footprint,
since it is not necessary to backpropagate through variational approximation's parameters.
We expect the conclusion of \cite{gale_state_2019} to carry over to C-valued models, since
pruning of \cite{zhu_prune_2018} masks parameters based on their ranking by absolute value,
$l_0$-based pruning \cite{louizos_learning_2018} learns a multiplicative mask, and there is
nothing fundamentally different in C-valued Variational Dropout.

% (rev 1)
Concerning the staged training procedure, the second step in
\cite{havasi_minimal_2018}
% [(Havasi et al. 2018)](https://openreview.net/forum?id=r1f0YiCctm)
is aimed at encoding parameters as indices in a shared lookup table, whereas our fine-tuning
stage trains the weights on the sparse pathways discovered by Variational Dropout methods.
Albeit their argument exhibits much more rigour, regrettably, it cannot be used to motivate
or `fine-tune` stage. However, this study is very relevant to Bayesian sparsification shall
be included in the text.

The recommended study \cite{havasi_minimal_2018} proposes KL-divergence targeting for reducing
communication complexity, motivated by the bits-back coding argument. The authors partition
parameters into groups and use KL-targeted $\beta$-VAE SGVB method split into pre-training
and random group-wise encoding phase. Targeting is done by adjusting the scaling coefficient
if the divergence deviates from the allotted `coding goal' for the group. The coding goal
specifies the amount of bits allocated to communicating the index in the shared procedurally
generated weight lookup table specific to that group, and therefore explicitly controls the
compression rate.

This method does not necessarily reduce arithmetic complexity, since a deterministic
non-zero parameter requires zero bits to be communicated given the assumed shared lookup
table, but cannot be excluded from the computation. The current study, on the other hand,
retains arithmetically significant parameters, those which are away from zero with high
confidence with respect to the variational posterior. Here compression is conflated with
sparsification, since implicit zeros reduce arithmetic and communication complexity.

% (rev 5)
Overall our experiment results are in line with empirical evidence that, other things being
equal, VD provides marginally stronger compression than ARD, but both show statistically similar
performance \cite[tab.1]{kharitonov_variational_2018}. Although there is no rigorous result
that would imply pareto-dominance of one method over the other, VD can be considered
theoretically flawed, since it uses the log-uniform prior which is improper and cannot be
normalized to a probability density. Both methods' KL-divergence terms provide similar
gradient feedback, which would imply certain uniformity in terms of convergence and stability,
but there has been no study addressing this directly.

% (rev 3, 5)
Concerning poor performance of undercompressed models on MusicNet, we strongly suspect
that the reason is overfitting. In our preliminary attempts at verbatim replication of
\cite{trabelsi_deep_2018}, we could not reach 72\% AP. However, we noticed that the validation
score had been consistently peaking at about the 15-th epoch and then steadily declining.
This lead us to believe that on this dataset (train-valid-test split) the undercompressed
models tends to overfit and for them the fine-tuning stage only exacerbates it. Analysis
of the compression rate and the number of epochs until early-stopping at the fine-tune
stage confirmed that undercompressed models start to overfit on validation very early.

Disregarding compression, our average best result of 72\% AP is modest compared to the current
state of the art on this task. First, \cite{trabelsi_deep_2018} report 72.9\% AP and show
that their deep architecture is superior to its R-valued variant (69.6\%). \cite{wolter_complex_2018}
use complex gated RNN but achieve 53\% AP. \cite{yang_complex_2019} use C-valued transformer
and achieve 74.2\% AP. Finally, \cite{thickstun_invariances_2018} use translation-invariant
R-valued network to achieve 77.3\% AP. Concerning compression, there seems no study concerning
compression of classifiers for MusicNet.

\bibliography{rebuttal}

\end{document}

### 2020-06-06 paper/rebuttal/rebuttal.tex
reflect concise rebuttal sent to reviews

@@
 % \maketitle
+% this is unabrdiged version of the rebuttal: the actual one uses more abbreviations and newspaper style
 
 Dear reviewers, we would like to thank you for your valuable comments, however space
-limitations compelled us to respond to them altogether and not individually. We will
-fix the mistakes you found, and shall make available the code for the experiments and
-a library for C-valued Variational Dropout after the review process, regardless of its
-outcome.
+limitations compel us to respond to them altogether and not individually. We shall make
+available the code for the experiments and a library for C-valued Variational Dropout
+after the review process, regardless of its outcome.
 \medskip
@@
 % (rev 1, 5)
-The fundamental motivation for C-valued networks is that there is evidence from signal
-processing, which hints at them performing better both for R-valued and C-valued signals,
+The fundamental motivation for C-valued networks is whether the domain knowledge
+dictates that C-consistent transformations be used, e.g. with acoustic, radio, or MRI
+data. In addition to discussion in the paper, there is scattered evidence from signal
+processing, hinting at them performing better both for R-valued and C-valued signals,
 \cite{tarver_design_2019,sivachitra_planning_2015} and \cite{hu_initial_2016}. In terms
 of arithmetic complexity, doubly-real networks require 4x more multiplications, while
-C-valued require only 3x, due to the skew symmetric parameter constraint embedded in them
-when viewed as a doubly-real to emulates C arithmetic. At the same time, higher redundancy
-generally offers higher compression rates, and may enjoy better test performance for some
-hyperparameters. Therefore, we conjecture that there would be no compressibility advantage
-to C-networks. Thus the main reason to use C-valued networks is whether the domain knowledge
-dictates that C-consistent transformations be used, i.g. with acoustic or radio
-telecommunications' data, or MRI.
+C-networks require only 3x, due to the skew symmetric constraint needed to emulate C
+arithmetic with R2. Finally, higher redundancy generally offers higher compression
+rates, and may enjoy better test performance for some hyperparameters, whence we
+believe that there is no compressibility advantage to C-networks.
 
 % (rev 3, 5)
-Concerning the novelty of the study, it is the first application of Variational Inference
-to C-valued networks, based on thorough analysis of the related work. The most closely
-related study has been done by \cite{popa_complex-valued_2018}, who introduce C-valued Botlzmann
-Machine and maximize ELBO over a fully-factorized posterior of Bernoulli distributions on
-the hidden states of the machine. At the same time this is not the first attempt at compressing
-C-valued networks. For instance, \cite{wu_compressing_2019} consider several compression
-approaches, among which is fixed threshold-based pruning; and \cite{vecchi_compressing_2020}
-apply sparsity-inducing regularization (LASSO) to quaternion-valued networks, which are
-generalizations of complex numbers.
+This study is the first application of Variational Inference to C-valued networks,
+based on thorough survey of the related work. The most closely related study has
+been done by \cite{popa_complex-valued_2018}, who introduces C-valued Botlzmann Machine
+and maximizes ELBO over a fully-factorized posterior of Bernoulli distributions on
+the hidden states of the machine. At the same time this is not the first attempt at
+compressing C-valued networks. For instance, \cite{wu_compressing_2019} consider
+several compression approaches, among which is fixed threshold-based pruning; and
+\cite{vecchi_compressing_2020} apply LASSO regularization to quaternion-valued networks,
+which are generalizations of complex numbers.
 
 % (rev 3) on kl-scaling
-For variational autoencoders scaling the KL term has been motivated by the need to control
-the capacity and statistical independence of the latent information through a constraint on
-the KL-divergence of the encoding variational posterior from the prior, \cite{higgins_beta-vae_2017}.
-In Variational Dropout methods scaling is used to balance the gradient feedback of the loss
-and the prior-matching terms of ELBO. In \cite{molchanov_variational_2017,kharitonov_variational_2018,gale_state_2019}
-the coefficient C is linearly annealed from 0 to 1 during training. Unlike these studies,
-we use constant C during `sparsify` stage in order to directly control the balance and explore
-performance-compression trade-off by varying the weight of the complexity penalty of the
-variational posterior distribution.
+In Variational Autoencoders KL-divergence scaling allows to control the capacity and
+statistical independence of the latent information through a constraint on the divergence
+of the encoding variational posterior from the prior, \cite{higgins_beta-vae_2017}.
+In Variational Dropout methods scaling balances the gradient feedback of the loss
+and the prior-matching terms of ELBO. In contrast to \cite{molchanov_variational_2017},
+\cite{kharitonov_variational_2018}, and \cite{gale_state_2019}, who linearly anneal
+the scale from 0 to 1 during training, we use constant C during `sparsify` stage in
+order to directly control the balance and explore performance-compression trade-off
+by varying the weight of the complexity penalty of the variational posterior distribution.
 
 % (rev 3)
-Variational Dropout permits non-uniform sparsity and as a Bayesian approach, allows estimation
-of parameter uncertainty, which is useful for selecting sufficient bit precision level
+Variational Dropout permits non-uniform sparsity and, as a Bayesian approach, can estimate
+parameter uncertainty, which is useful for selecting bit precision sufficient for it,
 \cite{louizos_bayesian_2017}. However, as a compression method, VD is more computationally
-costly, than pruning, which has less arithmetic complexity and smaller memory footprint,
+costly than pruning, which has less arithmetic complexity and smaller memory footprint,
 since it is not necessary to backpropagate through variational approximation's parameters.
 We expect the conclusion of \cite{gale_state_2019} to carry over to C-valued models, since
-pruning of \cite{zhu_prune_2018} masks parameters based on their ranking by absolute value,
-$l_0$-based pruning \cite{louizos_learning_2018} learns a multiplicative mask, and there is
-nothing fundamentally different in C-valued Variational Dropout.
+the pruning method of \cite{zhu_prune_2018} masks parameters based on their ranking by
+absolute value, the probabilistic $l_0$ regularization of \cite{louizos_learning_2018}
+learns a multiplicative mask, and there is nothing fundamentally different in C-valued
+Variational Dropout.
 
 % (rev 1)
-Concerning the staged training procedure, the second step in
-\cite{havasi_minimal_2018}
+Concerning the staged training procedure, regrettably, the study by \cite{havasi_minimal_2018}
 % [(Havasi et al. 2018)](https://openreview.net/forum?id=r1f0YiCctm)
-is aimed at encoding parameters as indices in a shared lookup table, whereas our fine-tuning
-stage trains the weights on the sparse pathways discovered by Variational Dropout methods.
-Albeit their argument exhibits much more rigour, regrettably, it cannot be used to motivate
-or `fine-tune` stage. However, this study is very relevant to Bayesian sparsification shall
-be included in the text.
+cannot motivate our `fine-tune` stage, albeit their argument exhibits much more rigour.
+Their second step uses Bayesian compression to encode parameters as indices in a shared
+lookup table, whereas our fine-tuning stage trains the weights on the sparse pathways
+discovered by Variational Dropout. However, the suggested study is very relevant to Bayesian
+sparsification and shall be covered in the text.
 
@@
 % (rev 5)
-Overall our experiment results are in line with empirical evidence that, other things being
-equal, VD provides marginally stronger compression than ARD, but both show statistically similar
-performance \cite[tab.1]{kharitonov_variational_2018}. Although there is no rigorous result
-that would imply pareto-dominance of one method over the other, VD can be considered
-theoretically flawed, since it uses the log-uniform prior which is improper and cannot be
-normalized to a probability density. Both methods' KL-divergence terms provide similar
-gradient feedback, which would imply certain uniformity in terms of convergence and stability,
-but there has been no study addressing this directly.
+Overall our experiment results are in line with empirical evidence that, other things
+equal, VD provides marginally stronger compression than ARD, but both show statistically
+similar performance \cite[tab.1]{kharitonov_variational_2018}. Both methods' KL-divergence
+terms provide similar gradient feedback, which would imply certain uniformity in terms
+of convergence and stability, but there has been no study addressing this directly.
+Although there is no rigorous result that would imply Pareto-dominance of one method
+over the other, VD can be considered theoretically flawed, since it uses the log-uniform
+prior which is improper and cannot be normalized to a probability density.
 
 % (rev 3, 5)
-Concerning poor performance of undercompressed models on MusicNet, we strongly suspect
-that the reason is overfitting. In our preliminary attempts at verbatim replication of
-\cite{trabelsi_deep_2018}, we could not reach 72\% AP. However, we noticed that the validation
-score had been consistently peaking at about the 15-th epoch and then steadily declining.
-This lead us to believe that on this dataset (train-valid-test split) the undercompressed
-models tends to overfit and for them the fine-tuning stage only exacerbates it. Analysis
-of the compression rate and the number of epochs until early-stopping at the fine-tune
-stage confirmed that undercompressed models start to overfit on validation very early.
+We suspect the reason for poor performance of under-compressed models on MusicNet is
+overfitting. In our preliminary attempts at verbatim replication of \cite{trabelsi_deep_2018},
+we could not surpass 72\% AP, and noticed that the validation score had been consistently
+peaking around the 15-th epoch and then declining afterwards. This lead us to believe
+that the under-compressed models tend to overfit and for them fine-tuning only exacerbates
+it. Analysis of the compression rate and the number of epochs until early-stopping at
+the final stage showed that undercompressed models start to overfit on validation very early.
 
 Disregarding compression, our average best result of 72\% AP is modest compared to the current
-state of the art on this task. First, \cite{trabelsi_deep_2018} report 72.9\% AP and show
-that their deep architecture is superior to its R-valued variant (69.6\%). \cite{wolter_complex_2018}
-use complex gated RNN but achieve 53\% AP. \cite{yang_complex_2019} use C-valued transformer
-and achieve 74.2\% AP. Finally, \cite{thickstun_invariances_2018} use translation-invariant
-R-valued network to achieve 77.3\% AP. Concerning compression, there seems no study concerning
-compression of classifiers for MusicNet.
+state of the art on this task. \cite{trabelsi_deep_2018} report 72.9\% AP and show that their
+deep C-network is superior to its R-valued variant (69.6\%). \cite{yang_complex_2019} use
+C-valued transformer and achieve 74.2\% AP. Finally, \cite{thickstun_invariances_2018} use
+translation-invariant R-valued network to achieve 77.3\% AP. Concerning compression, there
+seems no study concerning compression of classifiers for MusicNet.
 

### 2020-06-10 paper/paper.tex
fixed Molchanov's approximation sign confusion

@@
 We compute the Monte-Carlo estimator of \eqref{eq:improper-kl-div-real} on a sample of $10^7$
-draws over an equally spaced grid of $\log \alpha$ in $[-12, +12]$ of size $4096$. The optimal
-coefficients of the regression, proposed by \citet{molchanov_variational_2017}, are within
-$1\%$ relative tolerance of the reported therein.
+draws over an equally spaced grid of $\log \alpha$ in $[-12, +12]$ of size $4096$. The
+coefficients of the approximation, proposed by \citet{molchanov_variational_2017}, are
+within $1\%$ relative tolerance of the reported therein. An equivalent expression of the
+approximation is given in \eqref{eq:improper-kl-div-real-approx}.
+% see eq.~(14): flit overall sign, use $C = -k_1$, $1-\sigma(x) = \sigma(-x)$
 \begin{equation}  \label{eq:improper-kl-div-real-approx}
@@
   \includegraphics[width=\columnwidth]{grad_log.pdf}
-  \caption{$\tfrac{d f(\alpha)}{d \log{\alpha}}$ of the fit proposed by
-  \citet{molchanov_variational_2017}, MC estimate of \eqref{eq:improper-kl-div-real},
+  \caption{$\tfrac{d f(\alpha)}{d \log{\alpha}}$ of the approximation
+  \eqref{eq:improper-kl-div-real-approx}, MC estimate of \eqref{eq:improper-kl-div-real},
   and the exact derivative using \eqref{eq:real-kl-div-deriv-log}.}

### 2020-06-16 paper/paper.tex
replaced two plots with single  better one

@@
   \centering
-  \begin{subfigure}[b]{1.\columnwidth}  % imcl2019-style swears at this
-    \centering
-    \includegraphics[width=\columnwidth]{figure__musicnet__threshold.pdf}
-  \end{subfigure} \\
-  \begin{subfigure}[b]{1.\columnwidth}  % imcl2019-style swears at this
-    \centering
-    \includegraphics[width=\columnwidth]{figure__musicnet__threshold__fine-tune.pdf}
-  \end{subfigure}
+  \includegraphics[width=1\columnwidth]{figure__musicnet__threshold__C__DeepConvNet.pdf}
   \caption{%
-    Performance (smooth curve) and compression (curve with markers) of select experiments
-    before (\textit{top}) and after (\textit{bottom}) fine-tuning.
+    Effects of finetunig on performance-compression curves parametrized by $
+      \tau\in \{\tfrac{k}2\colon k=-8..+8 \}
+    $ for $
+      C\in \{\tfrac1{20}, \frac1{200}\}
+    $ in \eqref{eq:elbo_with_coef} during sparsification (sec.~\ref{sub:staging}).
   }

### 2020-06-16 paper/plots__kind-compression.tex
helper docs for making sense of the results

\documentclass[a4paper,10pt,onecolumn]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{a4paper,margin=10mm}
\usepackage[english]{babel}
\usepackage{natbib}
% \setcitestyle{authoryear,open={((},close={))}}

\usepackage{amsmath}
\usepackage{amssymb}

\usepackage{xcolor}
\usepackage{graphicx, url}
\usepackage{grffile}

\graphicspath{{../assets/}}

\usepackage{subcaption}

\usepackage{booktabs}

\title{Bayesian Sparsification of Deep $\cplx$-valued networks}
\author{Ivan Nazarov, and Evgeny Burnaev}

%% notation
\newcommand{\real}{\mathbb{R}}
\newcommand{\cplx}{\mathbb{C}}

\begin{document}
\maketitle
\listoffigures

\clearpage

\begin{figure}[b]
  \centering
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__emnist_letters__fft__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__VD__emnist_letters__fft__-0.5.pdf}
  \end{subfigure} \\ %
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    % used in main text
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__ARD__emnist_letters__fft__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__VD__emnist_letters__fft__-0.5.pdf}
  \end{subfigure} \\ %
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__ARD__emnist_letters__raw__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__VD__emnist_letters__raw__-0.5.pdf}
  \end{subfigure} \\ %
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__emnist_letters__raw__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__VD__emnist_letters__raw__-0.5.pdf}
  \end{subfigure}
  \caption{%
    \texttt{emnist\_letters}: (row 1) $2\real / \cplx$, (rows 2, 3) $\real / \cplx$, (row 4) $\real / \tfrac12\cplx$.
    % ARD method for $\real$ and $\cplx$ models using Fourier features.
  }
  % \label{fig:appendix__mnist-like__trade-off__emnist_letters}
\end{figure}

\begin{figure}[b]
  \centering
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__kmnist__fft__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__VD__kmnist__fft__-0.5.pdf}
  \end{subfigure} \\ %
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    % used in main text
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__ARD__kmnist__fft__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__VD__kmnist__fft__-0.5.pdf}
  \end{subfigure} \\ %
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__ARD__kmnist__raw__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__VD__kmnist__raw__-0.5.pdf}
  \end{subfigure} \\ %
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__kmnist__raw__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__VD__kmnist__raw__-0.5.pdf}
  \end{subfigure}
  \caption{%
    \texttt{kmnist}: (row 1) $2\real / \cplx$, (rows 2, 3) $\real / \cplx$, (row 4) $\real / \tfrac12\cplx$.
    % VD method for $\real$ and $\cplx$ models using Fourier features.
  }
  % \label{fig:appendix__mnist-like__trade-off__kmnist}
\end{figure}

\begin{figure}[b]
  \centering
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__fashionmnist__fft__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__VD__fashionmnist__fft__-0.5.pdf}
  \end{subfigure} \\%
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    % used in main text
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__ARD__fashionmnist__fft__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__VD__fashionmnist__fft__-0.5.pdf}
  \end{subfigure} \\%
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__ARD__fashionmnist__raw__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__VD__fashionmnist__raw__-0.5.pdf}
  \end{subfigure} \\ %
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__fashionmnist__raw__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__VD__fashionmnist__raw__-0.5.pdf}
  \end{subfigure}
  \caption{%
    \texttt{fashionmnist}: (row 1) $2\real / \cplx$, (rows 2, 3) $\real / \cplx$, (row 4) $\real / \tfrac12\cplx$.
    % ARD method for $\real$ and $\cplx$ models using raw features.
  }
  % \label{fig:appendix__mnist-like__trade-off__fashionmnist}
\end{figure}

\begin{figure}[b]
  \centering
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__mnist__fft__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__VD__mnist__fft__-0.5.pdf}
  \end{subfigure} \\%
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    % used in main text
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__ARD__mnist__fft__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__VD__mnist__fft__-0.5.pdf}
  \end{subfigure} \\%
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__ARD__mnist__raw__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__VD__mnist__raw__-0.5.pdf}
  \end{subfigure} \\ %
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__mnist__raw__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__VD__mnist__raw__-0.5.pdf}
  \end{subfigure}
  \caption{%
    \texttt{mnist}: (row 1) $2\real / \cplx$, (rows 2, 3) $\real / \cplx$, (row 4) $\real / \tfrac12\cplx$.
    % VD method for $\real$ and $\cplx$ models using raw features.
  }
  % \label{fig:appendix__mnist-like__trade-off__mnist}
\end{figure}

% judging features
\begin{figure}[b]
  \centering
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__ARD__emnist_letters__raw__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__VD__emnist_letters__raw__-0.5.pdf}
  \end{subfigure} \\ %
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    % used in main text
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__emnist_letters__raw__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__VD__emnist_letters__raw__-0.5.pdf}
  \end{subfigure} \\ %
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__ARD__kmnist__raw__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__VD__kmnist__raw__-0.5.pdf}
  \end{subfigure} \\ %
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__kmnist__raw__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__VD__kmnist__raw__-0.5.pdf}
  \end{subfigure}
  \caption{%
    \texttt{emnist\_letters}: (row 1) $2\real / \cplx$, (rows 2, 3) $\real / \cplx$, (row 4) $\real / \tfrac12\cplx$.
    % ARD method for $\real$ and $\cplx$ models using Fourier features.
  }
  % \label{fig:appendix__mnist-like__trade-off__emnist_letters}
\end{figure}

\begin{figure}[b]
  \centering
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__ARD__fashionmnist__raw__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__VD__fashionmnist__raw__-0.5.pdf}
  \end{subfigure} \\ %
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    % used in main text
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__fashionmnist__raw__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__VD__fashionmnist__raw__-0.5.pdf}
  \end{subfigure} \\ %
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__ARD__mnist__raw__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__VD__mnist__raw__-0.5.pdf}
  \end{subfigure} \\ %
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__mnist__raw__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__VD__mnist__raw__-0.5.pdf}
  \end{subfigure}
  \caption{%
    \texttt{kmnist}: (row 1) $2\real / \cplx$, (rows 2, 3) $\real / \cplx$, (row 4) $\real / \tfrac12\cplx$.
    % VD method for $\real$ and $\cplx$ models using Fourier features.
  }
  % \label{fig:appendix__mnist-like__trade-off__kmnist}
\end{figure}

\begin{figure}[b]
  \centering
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__emnist_letters__fft__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__VD__emnist_letters__fft__-0.5.pdf}
  \end{subfigure} \\%
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    % used in main text
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__ARD__emnist_letters__fft__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__VD__emnist_letters__fft__-0.5.pdf}
  \end{subfigure} \\%
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__kmnist__fft__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__VD__kmnist__fft__-0.5.pdf}
  \end{subfigure} \\ %
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__ARD__kmnist__fft__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__VD__kmnist__fft__-0.5.pdf}
  \end{subfigure}
  \caption{%
    \texttt{fashionmnist}: (row 1) $2\real / \cplx$, (rows 2, 3) $\real / \cplx$, (row 4) $\real / \tfrac12\cplx$.
    % ARD method for $\real$ and $\cplx$ models using raw features.
  }
  % \label{fig:appendix__mnist-like__trade-off__fashionmnist}
\end{figure}

\begin{figure}[b]
  \centering
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__fashionmnist__fft__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__VD__fashionmnist__fft__-0.5.pdf}
  \end{subfigure} \\%
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    % used in main text
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__ARD__fashionmnist__fft__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__VD__fashionmnist__fft__-0.5.pdf}
  \end{subfigure} \\%
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__mnist__fft__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__VD__mnist__fft__-0.5.pdf}
  \end{subfigure} \\ %
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__ARD__mnist__fft__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__VD__mnist__fft__-0.5.pdf}
  \end{subfigure}
  \caption{%
    \texttt{mnist}: (row 1) $2\real / \cplx$, (rows 2, 3) $\real / \cplx$, (row 4) $\real / \tfrac12\cplx$.
    % VD method for $\real$ and $\cplx$ models using raw features.
  }
  % \label{fig:appendix__mnist-like__trade-off__mnist}
\end{figure}

\end{document}

### 2020-06-16 paper/plots__method-profile.tex
helper docs for making sense of the results

\documentclass[a4paper,10pt,onecolumn]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{a4paper,margin=10mm}
\usepackage[english]{babel}
\usepackage{natbib}
% \setcitestyle{authoryear,open={((},close={))}}

\usepackage{amsmath}
\usepackage{amssymb}

\usepackage{xcolor}
\usepackage{graphicx, url}
\usepackage{grffile}

\graphicspath{{../assets/}}

\usepackage{subcaption}

\usepackage{booktabs}

\title{Bayesian Sparsification of Deep $\cplx$-valued networks}
\author{Ivan Nazarov, and Evgeny Burnaev}

%% notation
\newcommand{\real}{\mathbb{R}}
\newcommand{\cplx}{\mathbb{C}}

\begin{document}
\maketitle
\listoffigures

\clearpage

\begin{figure}[b]
  \centering
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__method_comparison/appendix__SimpleConvModel__emnist_letters__fft__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__method_comparison/appendix__SimpleConvModel__emnist_letters__raw__-0.5.pdf}
  \end{subfigure} \\ %
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    % used in main text
    \includegraphics[width=\columnwidth]{figure__mnist-like__method_comparison/appendix__SimpleConvModel__fashionmnist__fft__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__method_comparison/appendix__SimpleConvModel__fashionmnist__raw__-0.5.pdf}
  \end{subfigure} \\ %
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__method_comparison/appendix__SimpleConvModel__kmnist__fft__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__method_comparison/appendix__SimpleConvModel__kmnist__raw__-0.5.pdf}
  \end{subfigure} \\ %
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__method_comparison/appendix__SimpleConvModel__mnist__fft__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__method_comparison/appendix__SimpleConvModel__mnist__raw__-0.5.pdf}
  \end{subfigure}
  \caption{%
    \texttt{SimpleConvModel}: (row 1) EMNIST, (rows 2) Fashion-MNIST, (row 3) KMNIST, (row 4) MNIST.
  }
  % \label{fig:appendix__mnist-like__trade-off__emnist_letters}
\end{figure}

\begin{figure}[b]
  \centering
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__method_comparison/appendix__TwoLayerDenseModel__emnist_letters__fft__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__method_comparison/appendix__TwoLayerDenseModel__emnist_letters__raw__-0.5.pdf}
  \end{subfigure} \\ %
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    % used in main text
    \includegraphics[width=\columnwidth]{figure__mnist-like__method_comparison/appendix__TwoLayerDenseModel__fashionmnist__fft__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__method_comparison/appendix__TwoLayerDenseModel__fashionmnist__raw__-0.5.pdf}
  \end{subfigure} \\ %
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__method_comparison/appendix__TwoLayerDenseModel__kmnist__fft__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__method_comparison/appendix__TwoLayerDenseModel__kmnist__raw__-0.5.pdf}
  \end{subfigure} \\ %
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__method_comparison/appendix__TwoLayerDenseModel__mnist__fft__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\columnwidth}
    \centering
    \includegraphics[width=\columnwidth]{figure__mnist-like__method_comparison/appendix__TwoLayerDenseModel__mnist__raw__-0.5.pdf}
  \end{subfigure}
  \caption{%
    \texttt{TwoLayerDenseModel}: (row 1) EMNIST, (rows 2) Fashion-MNIST, (row 3) KMNIST, (row 4) MNIST.
  }
  % \label{fig:appendix__mnist-like__trade-off__kmnist}
\end{figure}

\end{document}

### 2020-06-18 paper/paper.tex
1- Major overhaul of the inroduction:  * more coherent story on the intro:    CVNN are promising, but niche; R compression method abound, some can be adpated to CVNN, but overall CVNN have much less compression results; Gale et al. (2018) compare R-valeud methods, sparse vd is alright; this, the rarity of compression and bayesian inference methods applied to cvnn, inspired this work.  * more comprehensive lit-review of CVNN results and R-valued compression methods  * dropped citations that served no purpose or seemed to be execssive

@@
 \usepackage[english]{babel}
-\usepackage{natbib}
+\usepackage[sort&compress]{natbib}
 % \setcitestyle{authoryear,open={((},close={))}}
@@
 image recognition on MNIST-like and CIFAR10 datasets and music transcription on MusicNet.
-We replicate the state-of-the-art result by \citet{trabelsi_deep_2017} on MusicNet with
+We replicate the state-of-the-art result by \citet{trabelsi_deep_2018} on MusicNet with
 a complex-valued network compressed by $50-100\times$ at a small performance penalty.
@@
 
-Inherently complex-valued nature of data in signal processing, specifically, acoustic or radio
-frequency signal analysis, has been the key driver behind the adoption of $\cplx$-networks.
-%
-\citet{hirose_complex-valued_2009} argues that $\cplx$-valued networks merit from the
-simultaneous phase rotation and amplitude adjustment, intrinsic to $\cplx$ arithmetic,
-which reduce ineffective degrees of freedom in comparison with double-dimensional
-$\real$-valued networks. Their study lists numerous applications related to acoustic
-and radio signal processing and demonstrates superiority of $\cplx$-networks in the
-task of shallow landmine detection using ground penetrating radar imaging, in spite of
-inherently higher arithmetic complexity of $\cplx$-networks, stemming from $3-4$ floating
-point operations per single $\cplx$ multiplication. More recently $\cplx$-networks have
-been applied to music transcription and speech recognition \citep{trabelsi_deep_2017}.
-\citet{arjovsky_unitary_2016} propose $\cplx$-valued unitary-RNNs to deal with exploding~/~vanishing
-gradients and apply the recurrent models to long-term dependence prediction tasks.
-\citet{wisdom_full-capacity_2016} expand on their work by optimizing recurrent weights on
-the $\cplx^{n \times n}$ Stiefel manifold. And \citet{wolter_complex_2018} investigate
-different $\cplx$-valued gating mechanisms for unitary-RNNs and conduct experiments on
-motion prediction and music transcription. \citet{yang_complex_2019} develop complex
-transformer, with $\cplx$-attention and complex encoder-decoder, and apply it to music
-transcription and wireless signal classification. \citet{tarver_design_2019} achieve
-significantly lower out-of-band performance with a $\cplx$-valued network in Digital Signal
-Predistortion task.
-
-% complex-valued distributions \citep{pav_moments_2015,taubock_complex-valued_2012},
-% and \citep{karseras_caution:_2014}
+% applications of cvnn
+Complex-valued nature of the data in acoustic and radio signal processing has been
+the main driver behind the adoption of $\cplx$-valued neural networks ($\cplx$VNN).
+\citet{hirose_complex-valued_2009} argues that the combined phase-magnitude effect of
+$\cplx$-valued transformations reduces removes the excess degrees of freedom, that cause
+degenerate transformation in $\real$-valued networks with twice the feature dimensions.
+Their study demonstrates superiority of $\cplx$VNN in landmine detection using ground
+penetrating radar imaging. Other examples, where $\cplx$-valued networks have outperformed
+$\real$-valued networks include magnetic resonance \citep{hui_mri_1995,wang_deepcomplexmri_2020}
+and radar imaging \citep{haensch_complex-valued_2010,zhang_complex-valued_2017}, music
+transcription and spectral speech modelling \citep{wisdom_full-capacity_2016,trabelsi_deep_2018},
+and wireless signal classification \citep{yang_complex_2019}. \citet{tarver_design_2019}
+have lowered the out-of-band power leakage with a $\cplx$-valued network for digital
+signal predistortion. The networks have also been applied to non $\cplx$-valued domains,
+such as image classification \citep{popa_complex-valued_2017}, sequence modelling
+\citep{danihelka_associative_2016}, and motion prediction \citep{wolter_complex_2018},
+and for stabilizing back-propagation in RNN \citep{wisdom_full-capacity_2016}.
 
 % motivation and other methods
-However, in spite of relative success of $\cplx$-valued networks, compression methods tailored
-to $\cplx$-domain remain a niche field of research.
-%
-Computational efficiency improvement and model compression methods such as quantization
-\citep{uhlich_differentiable_2019}, integer-based arithmetic \citep{lin_fixed_2016,chen_fxpnet_2017},
-and knowledge distillation \citep{hinton_distilling_2015} appear to be directly applicable
-to $\cplx$-valued networks.
-%
-Certain model sparsification methods, e.g. sparsity inducing regularizers, and magnitude
-pruning \citep{zhu_prune_2018}, which reactivates zeroed parameters based on gradients,
-can be adapted directly to $\cplx$-valued models. Other methods require additional considerations.
+Despite promising results for embedded signal processing applications, $\cplx$-valued
+networks remain a niche in deep learning, and as such little attention has been paid
+to compression methods specific to $\cplx$VNN. \citet{wu_compressing_2019} adapt $k$-means
+quantization to $\cplx \simeq \real^2$ parameters and successfully compress $\cplx$VNN
+with the ``prune-quantize-code'' procedure of \citet{han_deep_2016}.
+
+Yet there is an abundance of research related to real-valued network compression, and
+many results can be applied to $\cplx$VNN. Methods such as knowledge distillation
+\citep{hinton_distilling_2015}, which trains a small network to replicate a large
+well-trained teacher, low-rank matrix \citep{denton_exploiting_2014} and tensor decomposition
+\citep{novikov_tensorizing_2015}, or magnitude-based parameter pruning \citep{zhu_prune_2018}
+can be adapted to $\cplx$VNN without modifications. Parameter quantization and conversion
+from floating to fixed point arithmetic \citep{courbariaux_training_2015,uhlich_mixed_2020},
+appear to be readily applicable as well. \citet{louizos_learning_2018} propose probabilistic
+$\ell_0$ regularization through multiplicative $[0, 1]$-valued stochastic masks with
+distribution having an atom at $0$, yet differentiable via the reparameterization trick
+\citep{kingma_auto-encoding_2014}. By sharing a single mask value within a group of
+parameters their approach can be adapted to $\cplx$ parameters. However, methods such
+as Hessian-based parameter pruning \citep{lecun_optimal_1990} or Sparse Variational Dropout
+\citep{molchanov_variational_2017} require additional considerations.
 % the more explicitly zero parameters there is, the less computations is needed.
 
-% segue into bayesian inference
-Bayesian Inference is a principled framework of reasoning about uncertainty, which updates
-prior beliefs in accordance with the likelihood of empirical observations into posterior
-belief. Under suitable modelling and distributional assumptions, Bayesian methods can be
-used towards model sparsification, e.g. Variational Dropout \citep{kingma_variational_2015,molchanov_variational_2017}.
-
+% segue into why we chose sparse VD rather than anything else
 % (sparsity tech large-scale models) gale-elsen-hooker.tex
-\citet{gale_state_2019} compare Variational Dropout, magnitude pruning, and $\ell_0$
-regularization \citep{louizos_learning_2018} on large-scale models. The latter is a
-probabilistic regularization method, which penalizes the expected number of non-zero
-entries in $[0, 1]$-valued stochastic parameter masks with learnable hard-concrete
-distribution with atoms at $0$ and $1$ \citep{maddison_concrete_2016,jang_categorical_2017}.
-Their results suggest that Variational Dropout may achieve good accuracy-sparsity balance
-and outperform pruning and $\ell_0$ in deep architectures, although pruning is prefered for
-simplicity, stability and speed. They also observe that dropout induces non-uniform sparsity
-throughout the model, which \citet{he_amc:_2018} has shown to be essential for superior
-compression.
+\citet{gale_state_2019} compare magnitude pruning, $\ell_0$ regularization and Sparse
+Variational Dropout (VD) on large-scale models. Their results suggest that VD may achieve
+good accuracy-sparsity balance and outperform pruning and $\ell_0$ in deep architectures,
+although pruning is preferred for simplicity, stability and speed. They also observe that
+VD induces non-uniform sparsity throughout the model, which \citet{he_amc:_2018} have shown
+to be essential for superior compression.
 % Magnitude pruning induces user-specified sparsity distributions.
@@
 % than magnitude pruning on ResNet-50, and l0 fails to produce sparse models at all.
-%
+We expect the overall conclusion of \citet{gale_state_2019} to carry over to $\cplx$VNN,
+since there is nothing fundamentally different in $\cplx$-valued versions of the methods
+they study, except for the need to operate on pairs of parameters.
+
+% with noting that compression and sparsification techniques serve dual purpose as model
+% regularization. and can be regarded as a Bayesian network pruning method
 
 % our contribution
-Inspired by variational and stochastic sparsification techniques we extend Bayesian dropout
-to $\cplx$-valued networks. We assess the performance-compression trade-off of the proposed
-Bayesian technique by conducting a large-scale numerical study of $\cplx$-valued networks
-on two tasks: image recognition on MNIST-like and CIFAR10 datasets and music transcription
-on MusicNet \citep{thickstun_learning_2017}.
-
-The paper is structured as follows. In sec.~\ref{sec:variational_dropout} we review Bayesian
-dropout techniques, and in sec.~\ref{sec:c_valued_networks} we provide a brief summary of
-the inner working of complex-valued networks as functions of complex argument. The main
-contribution of this study is presented in sec.~\ref{sec:c_variational_dropout},
-where we consider different variational approximations and priors, outline the tricks
-and derive the penalty terms in the evidence lower bound. In sec.~\ref{sec:experiments}
-we evaluate the sparsification rate, compare the resulting performance of various $\cplx$-networks
-proposed in prior work, and discuss the outcomes.
+Sparse Variational Dropout is a Bayesian Variational Inference method with automatic
+parameter relevance determination effect. In this study we extend this technique to
+$\cplx$VNN, inspired by the results of \citet{gale_state_2019}, and motivated by seldom
+application of Bayesian Inference to $\cplx$-valued networks \citep{popa_complex-valued_2018}
+and apparent scarcity of compression methods specific to them. We assess the performance-%
+compression trade-off of the extension by conducting a large-scale numerical study on
+image classification on MNIST-like and CIFAR10 datasets and music transcription on MusicNet.
+
+The paper is structured as follows. Sec.~\ref{sec:variational_dropout} reviews Bayesian
+dropout techniques, and sec.~\ref{sec:c_valued_networks} provides a brief summary of
+the inner working of complex-valued networks. The main contribution of this study is
+presented in sec.~\ref{sec:c_variational_dropout}, where we outline the details of
+different variational approximations and priors and derive the penalty terms in the
+evidence lower bound. In sec.~\ref{sec:experiments} we evaluate the sparsification rate,
+compare the resulting performance of various $\cplx$-networks proposed in prior work,
+and discuss the outcomes.
 
@@
 \label{sec:variational_dropout}
+
+% segue into bayesian inference
+  % \speak{R 1}
+  % In the first paragraph of section 2: Although the Bayesian prior over weights can indeed
+  % be interpreted as a prior over models, the inclusion of this notation in the first
+  % paragraph of section 2 seems unnecessary. Especially considering that the authors refer
+  % to weights, and not models, for the remainder of the paper.
+
+Bayesian Inference is a principled framework of reasoning about uncertainty, and in broad
+terms Bayesian methods are used to update prior assumptions in accordance with their
+likelihood based on empirical evidence into posterior beliefs. Under suitable modelling
+and distributional assumptions, Bayesian methods can be used towards model regularization,
+e.g. Variational Dropout \citep{kingma_variational_2015}.
+% Bayesian perspective on dropout model regularization proposed by Kingma at al. (2015)
+% repurposed for sparsification by Molchanov et al. (2017) and Kharitonov et al. (2018)
 
@@
 on the intermediate outputs via the Central Limit Theorem can be approximated by a Gaussian
-with weight-input dependent mean and variance. \citet{srivastava_dropout_2014} propose
+with weight-input dependent mean and variance. \citet{srivastava_dropout:_2014} propose
 using independent $\mathcal{N}(1,1)$ noise, arguing that higher entropy of a Gaussian has
@@
 
+% Although $\cplx$-valued dense layers and back-propagation have been around since early
+% 1990-s, one of the earliest accounts
+
+Development of deep $\cplx$-valued networks has been active. \citet{haensch_complex-valued_2010}
+put forward $\cplx$-valued convolutional networks, \citet{guberman_complex_2016} and
+\citet{popa_complex-valued_2017} developed modifications of pooling, \citet{arjovsky_unitary_2016}
+and \citet{wisdom_full-capacity_2016} proposed $\cplx$-valued RNNs with unitary recurrent
+transition matrices, and \citet{danihelka_associative_2016} developed $\cplx$-valued
+holographic representations for LSTMs. More recently \citet{trabelsi_deep_2018} proposed
+$\cplx$-valued batch-normalization and weight initialization, \citet{wolter_complex_2018}
+investigated different $\cplx$-valued gating mechanisms for RNNs, \citet{yang_complex_2019}
+proposed $\cplx$-valued self-attention and complex transformer architecture. It merits
+noting that \citet{gaudet_deep_2018} generalized $\cplx$VNN further to deep quaternion-valued
+networks, and \citet{vecchi_compressing_2020} studied sparsity inducing regularizers for
+them.
+
+% Nonlinearities used in $\cplx$VNN are of two classes: split that operate on equivalent
+% planar or polar representations of $\cplx$, of full which consider the complex number
+% as a whole. Split planar $
+%   z \mapsto g(\Re{z}) + \iu g(\Im{z}) % split
+% $, \citep{benvenuto_complex_1992,hirose_generalization_2012,haensch_complex-valued_2010},
+% or polar $
+%   z \mapsto g(\lvert z\rvert) e^{\iu \arg{\!(z)}}
+% $, \citep{wolter_complex_2018,arjovsky_unitary_2016}. Full trigonometric, holomorphic, 
+% % \citet{hirose_generalization_2012} polar (tanh)
+% % \citet{savitha_2011} trig (sinh)
+% % \citet{arjovsky_unitary_2016} polar (modReLU)
+% % \citet{guberman_complex_2016} polar (zRelU)
+% % \citet{wolter_complex_2018} gating for $\cplx$-RNN
+
+% % complex-valued distributions \citep{pav_moments_2015,taubock_complex-valued_2012},
+% % and \citep{karseras_caution:_2014}
+
 Complex-valued networks are, in general, non-holomorphic, i.e. not $\cplx$-differentiable, which is
@@
 More recently general development of $\cplx$-valued networks has been continued by
-\citet{trabelsi_deep_2017}, who outline the essential building blocks for deep $\cplx$-valued
+\citet{trabelsi_deep_2018}, who outline the essential building blocks for deep $\cplx$-valued
 networks and describe suitable representation and operations, including convolutional and
@@
 $ for some $\real$-valued non-linearity $\sigma$, possibly with learnable parameters
-\citep{trabelsi_deep_2017,wolter_complex_2018}.
+\citep{trabelsi_deep_2018,wolter_complex_2018}.
 
@@
 %
-Following \citet{wolter_complex_2018} and \citet{trabelsi_deep_2017}, the class logit scores
+Following \citet{wolter_complex_2018} and \citet{trabelsi_deep_2018}, the class logit scores
 are taken as real part of the complex-valued output of a network.
@@
 auxiliary model to synthesize the imaginary component from the real data, proposed by
-\citet{trabelsi_deep_2017}.
+\citet{trabelsi_deep_2018}.
 
@@
 musical compositions, to investigate compressibility of the $1d$ VGG-like $\cplx$-convent
-proposed by \citet{trabelsi_deep_2017}. Similarly to the study, we downsample the audio
+proposed by \citet{trabelsi_deep_2018}. Similarly to the study, we downsample the audio
 from 44.1kHz to 11kHz, retain only $84$ out of $128$ labels, and hold-out the same validation
@@
 
-Experiments with the uncompressed model aimed at replicating the result of \citet{trabelsi_deep_2017}
+Experiments with the uncompressed model aimed at replicating the result of \citet{trabelsi_deep_2018}
 have shown that early stopping almost always terminates much sooner, than $200$ epochs used
@@
 
-We deviate from the set-up used by \citet{trabelsi_deep_2017} by clipping $\ell_2$ norm of the
+We deviate from the set-up used by \citet{trabelsi_deep_2018} by clipping $\ell_2$ norm of the
 gradients to $0.05$ and shifting the low frequencies of the input to the centre to maintain
@@
 %
-Additionally, we test the model of \citet{trabelsi_deep_2017}, in which we purposefully
+Additionally, we test the model of \citet{trabelsi_deep_2018}, in which we purposefully
 halve the receptive field of the first convolution from $6$ to $3$ (denoted by suffix $k_3$).
@@
 methods (sec.~\ref{sec:c_variational_dropout}) and post-sparsification fine-tuning it is
-possible to achieve average precision level comparable to the result of \citet{trabelsi_deep_2017}
+possible to achieve average precision level comparable to the result of \citet{trabelsi_deep_2018}
 with a model compressed $50\times$-$200\times$. Furthermore, the $k_3$ model, compressed
@@
 we have achieved $50-100\times$ compression of the state-of-the-art deep $\cplx$-valued network
-of \citet{trabelsi_deep_2017} on the MusicNet.
+of \citet{trabelsi_deep_2018} on the MusicNet.
 
@@
 and Wirtinger calculus make it possible to reuse $\real$ back-propagation and existing
-auto-differentiation frameworks \citep{trabelsi_deep_2017}.
+auto-differentiation frameworks \citep{trabelsi_deep_2018}.
 

### 2020-06-18 paper/paper.tex
icml2020 header

@@
-\documentclass[a4paper,10pt,twocolumn]{article}
+\documentclass{article}
 
@@
 \usepackage{amssymb}
+\usepackage{cancel}
 
@@
 
-\usepackage{subcaption}
+\usepackage{subfigure}
 
@@
 
-\title{Bayesian Sparsification Methods for Deep Complex-valued Networks}
-\author{Ivan Nazarov, and Evgeny Burnaev}
+\usepackage{microtype}
+\usepackage{hyperref}
+
+\usepackage[accepted]{icml2020/icml2020}
+
+% \title{Bayesian Sparsification Methods for Deep Complex-valued Networks}
+% \author{Ivan Nazarov, and Evgeny Burnaev}
+
+\icmltitlerunning{Bayesian Sparsification of Deep $\mathbb{C}$-valued networks}
 
@@
 \newcommand{\cplx}{\mathbb{C}}
+\newcommand{\iu}{{\jmath}}
 \newcommand{\tr}[1]{\mathop{tr}{#1}}
 
-\newcommand{\hop}{{\mkern-1.5mu\dagger}}
 \newcommand{\conj}[1]{\overline{#1}}
@@
 
-%% drafting macro
-\newcommand{\important}[1]{\textbf{\!\colorbox{red}{#1}\!}}
-\newcommand{\attn}[2]{\textbf{\color{red} #2~\textsuperscript{\textit{[#1]}}}}
-\newcommand{\verify}[1]{\textit{\!\colorbox{red}{#1}\!}}
-\newcommand{\rewrite}[1]{\attn{rewrite}{#1}}
-\newcommand{\todo}[1]{{\color{blue} [TODO]} \important{#1}}
-
-%% red-highlight missing citations
-\usepackage{etoolbox}
-\makeatletter
-\patchcmd{\@citex}{\bfseries ?}{\colorbox{red}{\bfseries ?}}{}{}
-\makeatother
-
 \begin{document}
-\maketitle
+\twocolumn[
+\icmltitle{Bayesian Sparsification of Deep $\mathbb{C}$-valued Networks}
+
+\icmlsetsymbol{equal}{*}
+
+\begin{icmlauthorlist}
+  \icmlauthor{Ivan Nazarov}{sk}
+  \icmlauthor{Evgeny Burnaev}{sk}
+\end{icmlauthorlist}
+
+\icmlaffiliation{sk}{
+  Centre for Data Intensive Sciecne and Engineering,
+  Skolkovo Insitiute of Science and Technology, Msocow, Russia
+}
+\icmlcorrespondingauthor{Ivan Nazarov}{ivan.nazarov@skolkovotech.ru}
+
+% the "keywords" metadata in the PDF but will not be shown in the document
+\icmlkeywords{complex-valued neural networks, Variational Dropout, network compression}
+
+\vskip 0.3in
+]
+\printAffiliationsAndNotice{}  % leave blank if no need to mention equal contribution
+% \printAffiliationsAndNotice{\icmlEqualContribution} % otherwise use the standard text.
 
@@
 With continual miniaturization ever more applications of deep learning can be found
-in embedded systems, where it is common to encounter data with natural complex domain
-representation. To this end we extend Sparse Variational Dropout to complex-valued neural
-networks and verify the proposed Bayesian technique by conducting a large numerical
+in embedded systems, where it is common to encounter data with natural representation
+in the complex domain. To this end we extend Sparse Variational Dropout to complex-valued
+neural networks and verify the proposed Bayesian technique by conducting a large numerical
 study of the performance-compression trade-off of $\cplx$-valued networks on two tasks:
@@
 remains a challenge due to storage, real-time throughput, and arithmetic complexity
-restrictions \citep{he_amc:_2018}. Therefore, compression methods for achieving high
+restrictions \citep{han_learning_2015}. Therefore, compression methods for achieving high
 model sparsity and numerical efficiency without losing much in performance are especially
@@
 \citet{hirose_complex-valued_2009} argues that the combined phase-magnitude effect of
-$\cplx$-valued transformations reduces removes the excess degrees of freedom, that cause
-degenerate transformation in $\real$-valued networks with twice the feature dimensions.
+$\cplx$-valued transformations removes the excess degrees of freedom, that cause
+degenerate transformations in $\real$-valued networks with twice the feature dimensions.
 Their study demonstrates superiority of $\cplx$VNN in landmine detection using ground
 penetrating radar imaging. Other examples, where $\cplx$-valued networks have outperformed
-$\real$-valued networks include magnetic resonance \citep{hui_mri_1995,wang_deepcomplexmri_2020}
+$\real$-valued networks, include magnetic resonance \citep{hui_mri_1995,wang_deepcomplexmri_2020}
 and radar imaging \citep{haensch_complex-valued_2010,zhang_complex-valued_2017}, music
 transcription and spectral speech modelling \citep{wisdom_full-capacity_2016,trabelsi_deep_2018},
-and wireless signal classification \citep{yang_complex_2019}. \citet{tarver_design_2019}
+and wireless signal classification \citep{yang_complex_2020}. \citet{tarver_design_2019}
 have lowered the out-of-band power leakage with a $\cplx$-valued network for digital
-signal predistortion. The networks have also been applied to non $\cplx$-valued domains,
+signal predistortion. The networks have also been applied to non-$\cplx$-valued domains,
 such as image classification \citep{popa_complex-valued_2017}, sequence modelling
@@
 networks remain a niche in deep learning, and as such little attention has been paid
-to compression methods specific to $\cplx$VNN. \citet{wu_compressing_2019} adapt $k$-means
-quantization to $\cplx \simeq \real^2$ parameters and successfully compress $\cplx$VNN
-with the ``prune-quantize-code'' procedure of \citet{han_deep_2016}.
-
+to compression methods specific to $\cplx$VNN.
+%
 Yet there is an abundance of research related to real-valued network compression, and
@@
 from floating to fixed point arithmetic \citep{courbariaux_training_2015,uhlich_mixed_2020},
-appear to be readily applicable as well. \citet{louizos_learning_2018} propose probabilistic
-$\ell_0$ regularization through multiplicative $[0, 1]$-valued stochastic masks with
-distribution having an atom at $0$, yet differentiable via the reparameterization trick
-\citep{kingma_auto-encoding_2014}. By sharing a single mask value within a group of
-parameters their approach can be adapted to $\cplx$ parameters. However, methods such
-as Hessian-based parameter pruning \citep{lecun_optimal_1990} or Sparse Variational Dropout
-\citep{molchanov_variational_2017} require additional considerations.
+appear to be readily applicable as well. For example, \citet{wu_compressing_2019} adapt
+$k$-means quantization to $\cplx \simeq \real^2$ parameters and successfully compress
+$\cplx$VNN with the ``prune-quantize-code'' procedure of \citet{han_deep_2016}.
+
+Other methods cannot be translated to $\cplx$VNN this straightforwardly. Probabilistic
+$\ell_0$ regularization of \citet{louizos_learning_2018} prune networks using multiplicative
+$[0, 1]$-valued stochastic masks with distributions having an atom at $0$, yet differentiable
+via the reparameterization trick \citep{kingma_auto-encoding_2014}. By sharing a single mask
+value within a group of parameters their approach can be adapted to $\cplx$ parameters.
+However, methods such as Hessian-based parameter pruning \citep{lecun_optimal_1990}
+or Sparse Variational Dropout \citep{molchanov_variational_2017} require additional
+considerations.
 % the more explicitly zero parameters there is, the less computations is needed.
@@
 % Magnitude pruning induces user-specified sparsity distributions.
-%
-% L0 and dropout work in the low-to-mid sparsity range, variational dropout consistently
-% ranked behind L0 on Transformer, and was bested by magnitude pruning for sparsity
-% levels of 80\% and up. Variational dropout consistently produces models on-par or better
-% than magnitude pruning on ResNet-50, and l0 fails to produce sparse models at all.
-We expect the overall conclusion of \citet{gale_state_2019} to carry over to $\cplx$VNN,
-since there is nothing fundamentally different in $\cplx$-valued versions of the methods
-they study, except for the need to operate on pairs of parameters.
-
-% with noting that compression and sparsification techniques serve dual purpose as model
-% regularization. and can be regarded as a Bayesian network pruning method
 
@@
 Sparse Variational Dropout is a Bayesian Variational Inference method with automatic
-parameter relevance determination effect. In this study we extend this technique to
+parameter relevance determination effect. In this study we extend \emph{Sparse VD} to
 $\cplx$VNN, inspired by the results of \citet{gale_state_2019}, and motivated by seldom
-application of Bayesian Inference to $\cplx$-valued networks \citep{popa_complex-valued_2018}
+application of Bayesian Inference to $\cplx$-valued networks \citep{popa_complex-valued_2017}
 and apparent scarcity of compression methods specific to them. We assess the performance-%
@@
 
-The paper is structured as follows. Sec.~\ref{sec:variational_dropout} reviews Bayesian
-dropout techniques, and sec.~\ref{sec:c_valued_networks} provides a brief summary of
-the inner working of complex-valued networks. The main contribution of this study is
-presented in sec.~\ref{sec:c_variational_dropout}, where we outline the details of
-different variational approximations and priors and derive the penalty terms in the
-evidence lower bound. In sec.~\ref{sec:experiments} we evaluate the sparsification rate,
-compare the resulting performance of various $\cplx$-networks proposed in prior work,
-and discuss the outcomes.
+The paper is structured as follows. Sec.~\ref{sec:variational_dropout} reviews Variational
+Dropout, and sec.~\ref{sec:c_valued_networks} provides a brief summary of the inner
+workings of complex-valued networks. The main contribution of this study is presented
+in sec.~\ref{sec:c_variational_dropout}, where we provide the details of $\cplx$-valued
+variational sparsification methods. In sec.~\ref{sec:experiments} we estimate the compression
+and performance trade-off on shallow and deep $\cplx$-valued networks, and discuss the
+outcomes.
 
@@
 
-% segue into bayesian inference
-  % \speak{R 1}
-  % In the first paragraph of section 2: Although the Bayesian prior over weights can indeed
-  % be interpreted as a prior over models, the inclusion of this notation in the first
-  % paragraph of section 2 seems unnecessary. Especially considering that the authors refer
-  % to weights, and not models, for the remainder of the paper.
-
-Bayesian Inference is a principled framework of reasoning about uncertainty, and in broad
-terms Bayesian methods are used to update prior assumptions in accordance with their
-likelihood based on empirical evidence into posterior beliefs. Under suitable modelling
-and distributional assumptions, Bayesian methods can be used towards model regularization,
-e.g. Variational Dropout \citep{kingma_variational_2015}.
-% Bayesian perspective on dropout model regularization proposed by Kingma at al. (2015)
-% repurposed for sparsification by Molchanov et al. (2017) and Kharitonov et al. (2018)
-
-In general, the core of Bayesian Inference can be summarized as follows: given a prior
-distribution $\pi(m)$ on models (hypotheses) $\mathcal{M}$, utilize the empirical evidence
-$D$ to update the assumptions by considering the likelihood of the observations under each
-$m \in \mathcal{M}$. Models are represented by a parametric family indexed by parameters
-$\omega \in \Omega$ and each $m_\omega(\cdot)$ specifies the conditional distribution of
-the data $
-  D = (z_i)_{i=1}^N
-$. The posterior distribution $p(\omega \mid D)$, derived using the Bayes rule $
-  p(m \mid D) = \tfrac{p(D \mid m) \pi(m)}{p(D)}
-$ with $
-  p(D) = \mathbb{E}_{\pi(m)} p(D \mid m)
-$, provides useful information about yet unobserved data and model parameters, e.g
-classification uncertainty, predictive statistics, and parameter relevance.
-
-Save for the relatively simple cases, the posterior distribution is intractable, and
-therefore exactness Bayesian Inference is traded for tractability and scalability of
-Variational Bayesian Inference. Instead of deriving the posterior $p(\omega \mid D)$,
-this approach postulates an optimization problem for finding an approximation $q$,
-which is close to $p(\omega \mid D)$ in terms of a proximity score $\rho$
-\begin{equation}  \label{eq:variational-progam}
-  q_*
-    \in \arg \min_{\theta} \rho\bigl(
-      q_\theta(\omega), p(\omega \mid D)
-    \bigr)
-    \,,
-\end{equation}
-over a tractable parametric family of distributions on the parameter space $
-  \mathcal{Q} = \{Q_\theta(d\omega) \colon \theta \in \Theta\}
-$, $\theta$ -- generic variational parameter. The variational approximation class
-$\mathcal{Q}$ is chosen so that its members have tractable densities $
-  q_\theta(\omega) d\omega
-$, can be sampled from and have either tractable $\log$-derivatives $
-  \omega \mapsto \nabla_\theta \log q_\theta(\omega)
-$ or can be represented as differentiable transformations of non-parametric noise
-\citep{williams_simple_1992,kingma_auto-encoding_2014,figurnov_implicit_2019}.
-% (reparameterization trick, pathwise gradient) $q_{\theta}(d\omega)$ is a push-forward
-% of $p(d\varepsilon)$ by a differentiable map $g(\varepsilon; \theta)$.
-% % http://stillbreeze.github.io/REINFORCE-vs-Reparameterization-trick/#fn:1
-%
-The most common choice for $\rho$ is Kullback-Leibler divergence of density $q$ from $p$,
-\begin{equation}  \label{eq:kl-div-def}
-  KL(q \| p)
+\subsection{Variational Inference} % (fold)
+\label{sub:variational_inference}
+
+% overview
+In broad terms Bayesian Inference is a principled framework for reasoning about uncertainty
+and updating prior beliefs about model's parameters in accordance with evidence or
+empirical data into a posterior distribution. The posterior is useful for inference
+regarding unobserved data, predictive statistics, parameter confidence regions, and
+model's uncertainty.
+% intuitive definition of  of model given data is the same as probability of data under hypothesis (model)
+% KL-div min & VI -- \citep{jordan_introduction_1999} approximate Bayesian inference
+% SVI -- \citep{hoffman_stochastic_2013} scalable stochastic variant
+% SGVB -- \citep{kingma_auto-encoding_2014} differentiable MCMC estimator of the evidence lower bound for SVI
+
+For an observed dataset $
+  D = (x_i)_{i=1}^N
+$ and statistical model $
+  p(D \mid \omega)
+    = \prod_i p(x_i \mid \omega)
+    % $D$ conditional independence given parameters $\omega$
+$ with parameters $\omega$ the Bayes rule transforms prior hypotheses $\pi(\omega)$
+about the unknown distribution of model's parameters into the posterior distribution: $
+  p(\omega \mid D) = \tfrac{p(D \mid \omega) \pi(\omega)}{p(D)}
+$.
+%
+% In general the marginal likelihood of the dataset is intractable $
+%   p(D) = \mathbb{E}_{\pi(\omega)} p(D \mid \omega)
+% $.
+Save for the relatively simple set-ups, either the posterior distribution itself or the
+mathematical expectations it is involved in are analytically intractable or impractical
+to compute numerically. Variational Inference (VI), proposed by \citet{jordan_introduction_1999},
+can be used in such cases to make approximate inference. The approach finds an approximation
+within some distribution family $q_\theta(\omega)$, which is closest to the true posterior
+distribution in terms of Kullback-Leibler divergence: $
+  KL(q_\theta(\omega) \| p(\omega \mid D))
     % = \int \frac{dQ}{dP} \log{\frac{dQ}{dP}} P(d\omega)
@@
     %   \log\frac{q(\omega)}{p(\omega)}
-    = \mathbb{E}_{\omega \sim q}
-      \log{q(\omega)}
-    - \mathbb{E}_{\omega \sim q}
-      \log{p(\omega \mid D)}
-    \,,
-\end{equation}
-% and, despite it not being a metric and requiring distributions with nested support,
-the main reason being that it satisfies the following identity for well-behaved densities:
-% $(q, p, \pi)$
-\begin{multline}  \label{eq:kl-div-master}
-  % \log p(D)
-    % = \mathbb{E}_{q(\omega)} \log \frac{p(D, \omega)}{p(\omega \mid D)}
-    % = \mathbb{E}_{q(\omega)} \log \frac{
-    %   p(D \mid \omega) \pi(\omega)
-    % }{p(\omega \mid D)}
-    % = \mathbb{E}_{q(\omega)} \log \frac{
-    %   p(D \mid \omega) \pi(\omega)
-    % }{q(\omega)}
-    % + \mathbb{E}_{q(\omega)} \log \frac{q(\omega)}{p(\omega \mid D)}
-    % - \mathbb{E}_{q(\omega)} \log \frac{q(\omega)}{\pi(\omega)}
-    % = \mathbb{E}_{q(\omega)} \log{p(D \mid \omega)}
-    % + \mathbb{E}_{q(\omega)} \log \frac{q(\omega)}{p(\omega \mid D)}
-  \log p(D)
-    - KL(q \| p(\omega \mid D))
-    \\ = \mathbb{E}_{q(\omega)} \log{p(D \mid \omega)}
-    - KL(q \| \pi)
-    \,.
-\end{multline}
-This leads to an equivalent problem for \eqref{eq:variational-progam} of maximizing
-the \textit{evidence lower bound} (ELBO)
+    = \mathbb{E}_{\omega \sim q_\theta}
+      \log \tfrac{q_\theta(\omega)}{p(\omega \mid D)}
+$. % The approximation family is chosen so that the expectations become tractable.
+%
+\citet{jordan_introduction_1999} show that this problem is equivalent to variational
+\emph{maximization} of the \emph{Evidence Lower Bound} (ELBO)
 \begin{equation}  \label{eq:elbo_general}
-  \mathcal{L}(\theta; \phi, \lambda)
+  \mathcal{L}(\theta; \lambda)
     = - KL(q_{\theta} \| \pi_{\lambda})
-      + \mathbb{E}_{\omega \sim q_{\theta}}
-        \log p_{\phi}(D \mid \omega)
+      + \sum_{i=1}^N \mathbb{E}_{\omega \sim q_{\theta}}
+        \log p(x_i \mid \omega)
       % \mathbb{E}_{\omega \sim q_{\theta}}
@@
 \end{equation}
-where $\lambda$, $\theta$ and $\phi$ are optimization parameters of the prior $\pi$,
-approximation $q$ and the likelihood $p(D\mid \omega)$, respectively. Other objectives
-are possible, besides \eqref{eq:elbo_general}, provided $p(\omega \mid D)$ is evaluated
-only through $\log p(D \mid \omega)$ and $\log \pi(\omega)$, \citep{ranganath_operator_2018}.
-
-\textit{Stochastic Gradient Variational Bayes} (SGVB), proposed by \citet{kingma_auto-encoding_2014},
-replaces the Variational objective \eqref{eq:elbo_general} by its unbiased differentiable
-Monte-Carlo estimator, which makes it possible to employ stochastic gradient optimization
-methods to solve \eqref{eq:variational-progam}. If $
-  \omega \sim q_{\theta}
+where the variational parameters $\theta$ and $\lambda$ parameterize the approximation
+and the prior, respectively.
+%
+Kullback-Leibler and, by proxy, ELBO are standard objectives in VI, however it is possible
+to use other objectives, provided the true posterior $p(\omega \mid D)$ is evaluated only
+through $\log p(D \mid \omega)$ and $\log \pi(\omega)$, \citep{ranganath_operator_2016}.
+
+% speed, scale, variance, family of suitable Var approximations
+In subsequent years several improvements to Variational Inference approach were introduced.
+To make VI able to handle large-scale datasets \citet{hoffman_stochastic_2013} proposed
+\emph{Stochastic Variational Inference}, which uses stochastic gradient optimization of
+\eqref{eq:elbo_general} based on noisy unbiased gradient estimates of ELBO
+computed on random mini-batches from the dataset. \citet{titsias_doubly_2014} translated
+the dependence on location–scale parameters of $q_{\theta}$ to the function inside its
+expectation and proposed \emph{Doubly Stochastic Variational Inference}. DSVI constructs
+an unbiased finite-sample estimator of the gradient of \eqref{eq:elbo_general} by both
+subsampling the dataset and sampling from $q_{\theta}$, without forfeiting convergence
+of SVI.
+
+% The variance of the stochastic gradient directly affects convergence of SVI.
+Independently, \citet{kingma_auto-encoding_2014} proposed \emph{Stochastic Gradient
+Variational Bayes}, which is an alternative efficient doubly stochastic estimator
+applicable to models with parameters $\omega$ that are continuous random variables
+amenable to the \emph{reparameterization trick}, i.e. $
+  \omega \sim q_{\theta}(\omega)
 $ is equivalent in distribution to $
-  \omega = g(\varepsilon; \theta)
-$ for some differentiable $
+  \omega = g_{\theta}(\varepsilon)
+$ for some non-parametric random variable $
+  \varepsilon \sim p(\varepsilon)
+$ and $
   g(\varepsilon; \theta)
-$ and non-parametric random variable $
-    \varepsilon \sim p_\varepsilon
-$, then the SGVB objective is
-\begin{equation}  \label{eq:sgvb_objective}
-  \widetilde{\mathcal{L}} %(\theta; \phi, \lambda)
+$ differentiable with respect to $\theta$. The estimator of \eqref{eq:elbo_general}
+with $L$ reparameterized draws per element in the mini-batch of size $M$ is given by
+\begin{equation}  \label{eq:sgvb_estimator}
+  \widetilde{\mathcal{L}}(\theta; \lambda)
     = - KL(q_{\theta} \| \pi_{\lambda})
       % + \frac{N}{\lvert B \rvert} \sum_{i\in B}
-        % \log p(z_i \mid \omega_i)b
-      + \frac1{L} \sum_{l=1}^L
-        \log p_{\phi}(D \mid g(\varepsilon_{l}; \theta))
-        % \log p_{\phi}(D \mid \omega_{l})
+        % \log p(x_i \mid \omega_i)b
+      + \frac{N}{M L} \sum_{k,l}
+        \log p(x_{i_k} \mid g(\varepsilon_{lk}; \theta))
+      % + \frac{N}{M L} \sum_{k=1}^M \sum_{l=1}^L
+      %   \log p(x_{i_k} \mid g(\varepsilon_{lk}; \theta))
+        % \log p(D \mid \omega_{l})
         %   \Big\vert_{\omega_{l} = g(\varepsilon_{l}; \theta)}
@@
       % + N \mathbb{E}_{B \sim \{D\}_M \otimes q_\theta^M}
-        % \hat{\mathbb{E}}_{z,\omega \sim B}
-          % \log p(z \mid \omega)
+        % \hat{\mathbb{E}}_{x,\omega \sim B}
+          % \log p(x \mid \omega)
     \,,
 \end{equation}
-where $
-  (\varepsilon_{l})_{l=1}^L
-$ is an iid sample from $p_\varepsilon$, the KL-divergence term replaced by unbiased
-differentiable finite sample estimator if it is intractable.
-%
-For the purposes of this study, we assume that the likelihood satisfies $
-  \log p_\phi(D\mid \omega)
-    = \sum_i \log p_\phi(z_i \mid \omega)
-$, i.e. the observed data $
-  D = (z_i)_{i=1}^N
-$ is conditionally independent, and consider \eqref{eq:sgvb_objective} with $L=1$
-and random mini-batches from $D$:
-\begin{equation}  \label{eq:elbo}
-  \widetilde{\mathcal{L}} %(\theta; \phi, \lambda)
-    = - KL(q_{\theta} \| \pi_{\lambda})
-      + \frac{N}{M} \sum_{k=1}^M
-        \log p_{\phi}(z_{i_k} \mid g(\varepsilon_k; \theta))
-    \,,
-\end{equation}
-for a random subsample $(z_{i_k})_{k=1}^M$ and iid $\varepsilon_k \sim p_\varepsilon$.
-%
-% (DSVI) titsias-lazaro.tex \todo{DSVI} \citep{titsias_doubly_2014}
-
-With a special family of posterior approximation, Variational Inference can be used as
-a regularization method and as a model sparsification technique.
+where $(x_{i_k})_{k=1}^M$ is a random subsample from $D$ and $
+  (\varepsilon_{lk})_{l=1}^L
+$ are $k=1..M$ independent iid samples from $p_\varepsilon$. \citet{figurnov_implicit_2018}
+extended the scope of the reparameterization gradients to include continuous distributions
+such as Gamma and von Mises. To handle the case of non-reparameterizable $\omega$ in
+doubly stochastic VI, e.g. discrete random parameters, \citet{titsias_local_2015} proposed
+\emph{local expectation gradients}, which is a version of REINFORCE gradient estimator
+\citep{williams_simple_1992} with variance reduced by careful use of dependence
+structures in the model.
+% (reparameterization trick, pathwise gradient) $q_{\theta}(d\omega)$ is a push-forward
+% of $p(d\varepsilon)$ by a differentiable map $g(\varepsilon; \theta)$.
+% % http://stillbreeze.github.io/REINFORCE-vs-Reparameterization-trick/#fn:1
+% rao-blackwellization (http://pyro.ai/examples/svi_part_iii.html)
+
+% The Local Reparameterization Trick reduces the variance of SGVB
+% even further by sampling independent weight matrices for
+% each data-point inside mini-batch. So we need both original SGVB
+% (per sample randomness) and local reparameterization (that is an
+% efficient and less noisy equivalent to per-sample weight sampling)
+% SGVB is specifically for VAE (local latent variables per data-point)
+% what Kingma propose is SGVB for global shared latent variables aka
+% WEIGHTS!!
+In this study we use the SGVB estimator \eqref{eq:sgvb_estimator} with $L=1$ and the
+\emph{local reparameterization trick} proposed by \citet{kingma_variational_2015}. They
+argued that this gradient estimator can be made more statistically and computationally
+efficient, if the structure of the model permits translating global stochasticity of
+$\omega$ down to local intermediate states of computation.
+%
+The class of models that allow this include non-recurrent computational graphs,
+exemplified by neural networks with parameters $\omega \sim q_\theta$. In their case,
+\eqref{eq:sgvb_estimator} would require that the \emph{entire} set of network's parameters
+$\omega$ be independently drawn for each element in the mini-batch. Since the parameters
+in a network naturally split into subsets with non-overlapping layer-wise effects, it is
+standard to assume that the approximation $
+  q_\theta(\omega)
+$ is factorized over layers. Furthermore, if $
+  % \omega =
+  W \in \mathbb{R}^{n\times m}
+$ in a linear layer $
+  y = b + W^\top x
+$ with $
+  q_\theta(W)
+    = \prod_{ij}
+      \mathcal{N}(w_{ij} \vert\, \mu_{ij}, \sigma_{ij}^2)
+$, then by virtue of $y$ being a linear transformation of $W$, we get
+\begin{equation}  \label{eq:r-gauss-trick}
+  q(y) = \prod_i \mathcal{N}\Bigl(
+        y_i \big\vert\,
+        b_i + \sum_j \mu_{ij} x_j,
+        \sum_j \sigma^2_{ij} x_j^2
+    \Bigr)
+  \,.
+\end{equation}
+This yields outputs equivalent in distribution to sampling $W$ for each element in
+the mini-batch, which produces the SGVB estimator with smaller variance, as demonstrated
+by \citet{kingma_variational_2015}.
+% Similar idea to \eqref{eq:r-gauss-trick} was proposed by \citet{wang_fast_2013} to speed
+% up Gaussian dropout.
+
+% subsection variational_inference (end)
+
+\subsection{Dropout} % (fold)
+\label{sub:dropout}
+
+Variational Inference can be used as model regularization and sparsification method
+for certain posterior approximation $q_\theta$ and prior $\pi$.
 
 % on dropout
-Dropout \citep{hinton_improving_2012} prevents overfitting by injecting multiplicative
-binary noise into layer's weights, which breaks up co-adaptations that could occur
-during training. \citet{wang_fast_2013} argue that the overall effect of binary dropout
-on the intermediate outputs via the Central Limit Theorem can be approximated by a Gaussian
-with weight-input dependent mean and variance. \citet{srivastava_dropout:_2014} propose
-using independent $\mathcal{N}(1,1)$ noise, arguing that higher entropy of a Gaussian has
-better regularizing effect. In a recent study concerning multitask learning
-\citet{cheung_superposition_2019} have shown the possibility of storing task-specific
-parameters in non-destructive superposition within a single network. In particular, their
-argument implies that if the single task setting is viewed as multitask learning with
-replicated task, then by sampling uncorrelated binary masks Dropout acts as a superposition
-method, utilizing the learning capacity of the network better.
+Dropout, proposed by \citet{hinton_improving_2012}, prevents overfitting by injecting
+multiplicative binary noise into layer's weights, which breaks up co-adaptations that
+could occur during training. \citet{wang_fast_2013} argued that the overall effect of
+binary Dropout on the intermediate outputs can be approximated by a Gaussian with weight-input
+dependent mean and variance via the Central Limit Theorem. \citet{srivastava_dropout_2014}
+proposed using independent $\mathcal{N}(1, 1)$ multiplicative noise, arguing that higher
+entropy of a Gaussian has better regularizing effect. \citet{gal_dropout_2016} showed
+that Dropout is a Bayesian approximation method with close ties to deep Gaussian Processes
+that yields inexpensive model uncertainty estimates. In a study concerning multitask learning
+\citet{cheung_superposition_2019} demonstrated the possibility of storing task-specific
+parameters in non-destructive superposition within a single network. Regarding Dropout
+their argument implies that if the single task setting is viewed as multitask learning
+with replicated task, then by sampling uncorrelated binary masks Dropout acts as a
+superposition method, utilizing the learning capacity of the network better.
 % many identical copies of the same task; \cite[Appendix A.1]{cheung_superposition_2019}
@@
 
-Dropout can be viewed as a Bayesian model averaging method, where models share parameters
-and are weighted equally. Thus, \citet{kingma_variational_2015} consider Dropout, DropConnect
-\citep{wan_regularization_2013}, and Gaussian dropout \citep{wang_fast_2013} through the
-lens of Bayesian Inference methods and propose \textit{Variational Dropout}. They argue that
-the multiplicative noise introduced by these methods induces a distribution equivalent to
-a fully factorized variational posterior of the form $
+% VD is a Bayesian perspective on dropout regularization \citep{hinton_improving_2012} offered
+% by \citet{kingma_variational_2015} and repurposed for sparsification by \citet{molchanov_variational_2017}.
+%
+\citet{kingma_variational_2015} provided a unifying perspective on Dropout, DropConnect
+\citep{wan_regularization_2013}, and Gaussian Dropout \citep{wang_fast_2013} through
+the lens of Variational Inference and propose \emph{Variational Dropout}. They argued
+that the multiplicative noise introduced by Dropout methods induces a distribution
+equivalent to a fully factorized variational posterior $
   q_\theta(\omega) = \prod_j q_{\theta}(\omega_j)
-$, where $q_{\theta}(\omega_j)$ is $\omega_j = \mu_j \xi_j$ with $
-  \xi_j \sim p_\theta(\xi_j)
-$ iid from some $p_\theta(\xi)$.
-
+$, where $q_{\theta}(\omega_j)$ is $\omega_j = \mu_j \eta_j$ with $
+  \eta_j \sim p_\theta(\eta_j)
+$ iid from some $p_\theta(\eta)$.
+%
 % Binary dropout with rate $p \in (0, 1)$ uses $
-%   p_\xi
+%   p_\eta
 %     = \mathcal{B}\bigl(
@@
 % $, whereas in Gaussian dropout $
-%   \xi \sim \mathcal{N}(1, \alpha)
+%   \eta \sim \mathcal{N}(1, \alpha)
 % $ for $\alpha = \tfrac{p}{1-p}$.
@@
 % and optimizing it in \eqref{eq:elbo_general} with an appropriate penalty term. Thus,
-%
-Variational Dropout assumes fully factorized Gaussian approximate posterior $
+
+Variational Dropout uses \emph{fully factorized Gaussian} approximation $
   q_\theta(\omega)
     = \prod_j \mathcal{N}(\omega_j \vert\, \mu_j, \alpha_j \mu_j^2)
-$ and factorized log-uniform prior $\pi(\omega)$ with $
+$ and factorized scale invariant log-uniform prior $\pi(\omega)$ with $
   \pi(\omega_j) \propto \lvert \omega_j \rvert^{-1}
-$. The divergence term in \eqref{eq:elbo} unravels into the following sum:
+$. \citet{molchanov_variational_2017} noticed that $\alpha_j$ reflects the relevance of the
+parameter $\omega_j$ it is associated to by being the ratio of its squared mean to its
+effective variance. Based on this observation they proposed \emph{Sparse Variational Dropout},
+a modification that enables automatic model sparsification by optimizing $\alpha_j$ for each
+individual parameter. \citet{louizos_bayesian_2017} extended the idea to structured sparsity
+by considering hierarchical prior and variational approximation. They grouped the parameters
+$\omega_j$ and coupled them within each one through a shared latent variable, which on the
+whole enabled pruning entire input features in each layer.
+% {louizos_bayesian_2017} eq. (11) variance -> gaussian entropy -> informative bits
+% They also proposed to estiamte bit precision for quantization based on parameter's
+% estimated uncertainty (variance or entropy).
+
+Due to factorization assumption, the term $KL(q_\theta \| \pi)$ in \eqref{eq:sgvb_estimator}
+for Sparse VD unravels into $
+  \sum_j K(\tfrac{\sigma^2_{j}}{\mu_{j}^2})
+$ with
 \begin{equation}  \label{eq:improper-kl-div-real}
-  KL(q_\theta \| \pi)
-    \propto
-      \frac12 \sum_j \mathbb{E}_{\varepsilon \sim \mathcal{N}(0, 1)}
-        \log{\Bigl\lvert \tfrac1{\sqrt{\alpha_j}} + \varepsilon \Bigr\rvert^2}
+  K(\alpha)
+    \propto \frac12 \mathbb{E}_{\varepsilon \sim \mathcal{N}(0, 1)}
+        \log{\Bigl\lvert \tfrac1{\sqrt{\alpha}} + \varepsilon \Bigr\rvert^2}
       % \frac12 \mathbb{E}_{\varepsilon \sim \mathcal{N}(0, 1)}
@@
 \end{equation}
-\citet{kingma_variational_2015} approximate this expression by a non-linear polynomial
-regression over $\alpha \in (0, 1)$. \citet{molchanov_variational_2017} refine the
-approximation by using a nonlinear regression based on sigmoid and soft-plus.
+\citet{kingma_variational_2015} approximated $K(\alpha)$ over $\alpha \in (0, 1)$ by a
+polynomial with a logarithmic term, and later \citet{molchanov_variational_2017} refined
+the approximation of \eqref{eq:improper-kl-div-real} by weighted sum of a sigmoid and a
+soft-plus term.
 % see p.6 sec 3.4 of kingma_variational_2015
-In appendix~\ref{sec:real-chisq-grad} we verify the value and the derivative of their
-approximation against the Monte-Carlo estimate of \eqref{eq:improper-kl-div-real} for $\alpha$
-varying over a fine logarithmic grid and the gradient of \eqref{eq:improper-kl-div-real},
-for which we obtain an exact expression.
+In appendix~\ref{sec:real-chisq-grad} we verify the derivative of their approximation
+against a Monte-Carlo estimate for $\alpha$ varying over a fine $\log$-scale grid and
+the exact expression for gradient of \eqref{eq:improper-kl-div-real}.
 % (!) good for SGVB: gradient-based methods require unbiased gradient estimates
@@
 
-The key role in the factorization is played by $\alpha_j$, which reflects the relevance
-of the parameter $\omega_j$ it is associated to, by being the ratio of its squared mean
-to its variance. Thus, \citet{molchanov_variational_2017} focus on the model sparsification
-capabilities of Variational Dropout, optimizing $\alpha_j$ for each individual parameter,
-or across groups of parameters for structured sparsity.
-%
-\citet{louizos_bayesian_2017} consider hierarchical prior and approximation, which couples
-the parameters $\omega_j$ within a group $J$ through shared scaling $z_J$ and enables
-pruning entire input features in each layer.
-% {louizos_bayesian_2017} eq. (11) variance -> gaussian entropy -> informative bits 
-%
-\citet{kharitonov_variational_2018}
-address theoretical issues with improper priors and propose a method based on \textit{
-Automatic Relevance Determination} procedure, which falls under \textit{Empirical Bayes}
-approach that fits a prior distribution while performing Variational Inference. In this
-method the log-uniform factor $\pi(\omega_j)$ is replaced by a proper Gaussian ARD
-prior $
-  \mathcal{N}(\omega_j \vert\, 0, \tau^{-1}_j)
-$ with learnable precision $\tau_j > 0$, \citep{neal_bayesian_1996}. Maximizing
-\eqref{eq:elbo} over $\tau$, holding other parameters fixed, yields $
+\citet{kharitonov_variational_2018} addressed theoretical issues with improper prior
+$\pi$ in Sparse VD, emphasized by \citet{hron_variational_2018}, and proposed
+\emph{Automatic Relevance Determination} Variational Dropout, by replacing $\pi(\omega_j)$
+with a proper Gaussian prior $
+  \pi_\lambda(\omega_j) = \mathcal{N}(\omega_j \vert\, 0, \tau_j^{-1})
+$ with learnable precision $\tau_j > 0$ \citep{neal_bayesian_1996}. This recast the VD
+as the \emph{Empirical Bayes} approach, which performs Bayesian Inference over $\omega$,
+but uses Maximum Likelihood estimates for the hyper-parameters $\lambda$,
+\citep{mackay_bayesian_1994}. Maximizing \eqref{eq:sgvb_estimator} over $\tau$, holding
+other parameters fixed, yields $
   \tau^*_j = {(\mu_j^2 + \sigma^2_j)}^{-1}
@@
 \begin{equation}  \label{eq:ard-kl-div-real}
-  KL(q_\theta \| \pi)
-    = \frac12 \sum_j \log{\bigl(1 + \tfrac1{\alpha_j} \bigr)}
+  K(\alpha)
+    = \frac12 \log{\bigl(1 + \tfrac1{\alpha} \bigr)}
     \,.
@@
 
-Another contribution of \citep{kingma_variational_2015} is the analysis of the effects of the
-\textit{local reparameterization trick} on the variance of the gradient of \eqref{eq:elbo}.
-Proposed by \citet{wang_fast_2013} to speed up Gaussian dropout, this trick translates
-uncertainty from parameters of the model to intermediate outputs within the network:
-the stochasticity of $
-  W \in \mathbb{R}^{n\times m}
-$ with $
-  q(W) = \prod_{ij}
-    \mathcal{N}(w_{ij}\vert\, \mu_{ij}, \alpha_{ij} \mu_{ij}^2)
-$ in a linear layer is pushed to its output $
-  y = b + W^\top x
-$,
-\begin{equation}  \label{eq:r-gauss-trick}
-  q(y) = \prod_i \mathcal{N}\Bigl(
-        y_i \big\vert\,
-        b_i + \sum_j \mu_{ij} x_j,
-        \sum_j \alpha_{ij} \mu_{ij}^2 x_j^2
-    \Bigr)
-  \,.
-\end{equation}
-%
-\citet{kingma_variational_2015} show, that for the case of fully factorized Gaussian
-posterior approximations, using \eqref{eq:r-gauss-trick} decorrelates the estimators
-\eqref{eq:elbo} within the mini-batch and makes the gradient estimator $
-  \nabla_\theta \tilde{\mathcal{L}}
-$ more statistically efficient. Specifically for the problem of selecting relevant parameters
-\citet{molchanov_variational_2017} further improve the efficiency of the estimator of the $
-  \nabla_\mu \tilde{\mathcal{L}}
-$ by introducing \textit{additive noise parameterization}. They revert the $(\mu, \alpha)$
-parameterization back to the equivalent $(\mu, \sigma^2)$, since it stabilizes gradients
-of SGVB \eqref{eq:elbo}, by rendering the gradient with respect to $\mu$ independent from
-the local output noise, injected by \eqref{eq:r-gauss-trick}. The relevance $\alpha$ is
-calculated using the ratio $
-  \tfrac{\sigma^2}{\mu^2}
-$ when needed in the divergence term.
-
-% section bayesian_dropout (end)
+% practical difference between them?
+
+Simultaneously the method \citet{molchanov_variational_2017} proposed to use \emph{additive
+noise parameterization} in the factorized Gaussian $q_\theta(\omega)$ in conjunction with
+the local reparameterization trick. They reverted the $(\mu, \alpha)$ parameterization in
+$q_\theta(\omega)$ back to $(\mu, \sigma^2)$, arguing that it reduces the variance of the
+SGVB \eqref{eq:sgvb_estimator}, by rendering the gradient with respect to $\mu$ independent
+from the local noise, injected by \eqref{eq:r-gauss-trick}. This modification is important
+for pruning, since $\mu$ of a relevant parameter serves as the estimate of its value.
+
+% subsection dropout (end)
+
+% section variational_dropout (end)
 
@@
 
+% implementation
+$\cplx$-valued neural networks are networks that rely on the arithmetic in the complex
+domain. To achieve this implementations of $\cplx$VNN use the geometric representation
+of a complex number as paired \emph{real} and \emph{imaginary} values, $\cplx \simeq \real^2$,
+ensuring that the resulting $\real$-valued computational graph respects $\cplx$-arithmetic.
+For example, $
+  f\colon \cplx^n \to \cplx^m
+$ is identified with a real vector-valued function $
+  F\colon \real^{2 m} \to \real^{2 m}
+$ defined via $
+  F(u, v) = (\Re f(u + \iu v), \Im f(u + \iu v))
+$, $\Re$ and $\Im$ denoting the real and imaginary parts, respectively. When $f$ is
+a $\cplx$-valued linear transformation, the computations are ``wired'' so that
+\begin{equation}  \label{eq:cplx-lin-op}
+  % F\colon
+  %   (u, v)
+  %     \mapsto \Bigl(
+  %       P u - Q v,
+  %       P v + Q u
+  %     \Bigr)
+  F(u, v)
+    =
+    \begin{pmatrix}
+      P u - Q v \\
+      P v + Q u
+    \end{pmatrix}
+    = \begin{pmatrix}
+      P & - Q \\ Q & P
+    \end{pmatrix} \begin{pmatrix}
+      u \\ v
+    \end{pmatrix}
+    \,,
+\end{equation}
+with $
+  P, Q \colon \real^{n} \to \real^{m}
+$ given by $P = \Re f$ and $Q = \Im f$ restricted to $\real^{n}$.
+% The downside is that, for instance, one $\cplx$-valued convolution requires up to
+% four $\real$-valued convolution operations.
+%
+Non-linearities in $\cplx$VNN can be hyperbolic functions or maps that operate on
+$\cplx$ numbers in planar form, $
+  z \mapsto \sigma(\Re{z}) + \iu \sigma(\Im{z}) % split
+$, or polar form $
+  % z \mapsto \sigma(\lvert z\rvert, \arg{\!(z)})
+  r e^{\iu \phi} \mapsto \sigma(r, \phi)
+$.
+% \citep{savitha_2011,hirose_generalization_2012,arjovsky_unitary_2016,guberman_complex_2016}
+
+This $\cplx \simeq \real^2$ identification allows straightforward retrofitting of $\cplx$VNN
+into existing $\real$-valued auto-differentiation frameworks for deep learning. This
+act is backed by Wirtinger ($\cplx\real$) calculus, which enables generalized treatment
+of functions of complex argument, by regarding $z$ and its \emph{complex conjugate}
+$\conj{z}$ as independent variables and defining derivative operators with respect to
+them through partial derivatives with respect to real and imaginary parts. These definitions
+simplify manual analysis of $\cplx$ derivatives and satisfy the product and chain rules, respect
+complex conjugation and linearity for $\cplx \to \cplx$ maps, and as such were used to define
+$\cplx$ version of back-propagation, \citep{benvenuto_complex_1992,guberman_complex_2016}.
+However, since auto-differentiation frameworks can algorithmically handle computational
+graphs of arbitrary complexity, explicit use of Wirtinger derivatives is not required,
+especially considering the fact that the direction of the steepest ascent of a $
+  \cplx \to \real
+$ function is given by complex conjugate gradient $\nabla_{\conj{z}}$, which coincides
+with the classical gradient of the same function viewed as $\real^2 \to \real$,
+(see appendix~\ref{sub:wirtinger_calculus}).
+%
+% in natively $\cplx$-valued backprop it would be necessary to modify the existing sgd
+% to explicitly use $\nabla_{\conj{z}} f(z)$, while no such modification is necessary
+% in re-im. If some inner activation of a $\cplx$VNN is holomorphic, i.e. satisfies
+% Cauchy-Riemann conditions, then that particular step of in the chain rule that is
+% backprop can be simplified by assuming one piece of the tracked gradient to be exact
+% zero. But other wise it is necessary to track both $\partial_{\conj{z}}$ and $\partial_{z}$.
+%
+% Training a $\cplx$VNN involves optimizing a real-valued objective with respect to
+% complex valued arguments.
+%
+% The computed gradients are theoretically justified
+% - CR dictates the it is necessary to track both $z$ and $\conj{z}$ derivatives
+% - the direction of largest increase in f: C-R is given by the gradient with
+% respect to the conjugate, which coincides in the re-im representation with 
+% the ordinary gradient wrt u and v
+% - the Chain Rule in CR holds and when a holomorphic C-C function is backproped
+% the autodiff just wastes cycles on computing its conj-derivative (rather than assuming
+% it to be zero)
+
 % Although $\cplx$-valued dense layers and back-propagation have been around since early
 % 1990-s, one of the earliest accounts
-
 Development of deep $\cplx$-valued networks has been active. \citet{haensch_complex-valued_2010}
@@
 $\cplx$-valued batch-normalization and weight initialization, \citet{wolter_complex_2018}
-investigated different $\cplx$-valued gating mechanisms for RNNs, \citet{yang_complex_2019}
+investigated different $\cplx$-valued gating mechanisms for RNNs, and \citet{yang_complex_2020}
 proposed $\cplx$-valued self-attention and complex transformer architecture. It merits
@@
 them.
-
-% Nonlinearities used in $\cplx$VNN are of two classes: split that operate on equivalent
-% planar or polar representations of $\cplx$, of full which consider the complex number
-% as a whole. Split planar $
-%   z \mapsto g(\Re{z}) + \iu g(\Im{z}) % split
-% $, \citep{benvenuto_complex_1992,hirose_generalization_2012,haensch_complex-valued_2010},
-% or polar $
-%   z \mapsto g(\lvert z\rvert) e^{\iu \arg{\!(z)}}
-% $, \citep{wolter_complex_2018,arjovsky_unitary_2016}. Full trigonometric, holomorphic, 
-% % \citet{hirose_generalization_2012} polar (tanh)
-% % \citet{savitha_2011} trig (sinh)
-% % \citet{arjovsky_unitary_2016} polar (modReLU)
-% % \citet{guberman_complex_2016} polar (zRelU)
-% % \citet{wolter_complex_2018} gating for $\cplx$-RNN
-
-% % complex-valued distributions \citep{pav_moments_2015,taubock_complex-valued_2012},
-% % and \citep{karseras_caution:_2014}
-
-Complex-valued networks are, in general, non-holomorphic, i.e. not $\cplx$-differentiable, which is
-exacerbated by the loss being real-valued. Indeed a $\cplx$-differentiable real-valued function is
-necessarily trivial by Cauchy-Riemann conditions. This issue is dealt with by employing Wirtinger,
-or $\cplx\real$ calculus, which generalizes holomorphic calculus to non-holomorphic functions
-of $\cplx$-argument \citep{adali_complex-valued_2011,boeddeker_computation_2019}. It satisfies
-the product and chain rules, respects complex conjugation and linearity, but most importantly the
-$\cplx\real$-differential of a function on $\cplx$ coincides with its classical differential as
-a function on $\real^2$. Essentially, it allows straightforward retrofiting of $\cplx$-valued
-networks into existing $\real$ deep learning auto-differentiation frameworks. It was considered
-as a basis for $\cplx$ version of back-propagation by \citet{benvenuto_complex_1992}, (see
-appendix~\ref{sub:wirtinger_calculus}).
+% complex-valued distributions \citep{pav_moments_2015,taubock_complex-valued_2012},
+% and \citep{karseras_caution:_2014}
+
+% This is too abrupt: first intro into what Cplx- valued nets are, then the representation 
+% and how it dictates the architecture, and ultimately bioils down to representation
+% u(x, y) + j v(x, y) as a R2->R2 map.
+
 % \todo{read on holomorphic nets}
-
-More recently general development of $\cplx$-valued networks has been continued by
-\citet{trabelsi_deep_2018}, who outline the essential building blocks for deep $\cplx$-valued
-networks and describe suitable representation and operations, including convolutional and
-dense layers, $\cplx$-valued activations, complex batch-normalization and weight initialization.
-Their approach coupled with $\cplx\real$ calculus for backprop transforms a $\cplx$-valued
-network into an intricately connected $\real$-valued computational graph, constructed
-to respects $\cplx$-arithmetic.
-%
-In particular, natural identification of $\cplx$ and $\real^2$ implies that dense linear
-layers $
-  L \colon \cplx^m \to \cplx^n
-$ act upon their inputs as follows:
-\begin{equation}  \label{eq:cplx-lin-op}
-  {(\real^n)}^{2}
-    \to {(\real^m)}^{2}
-    \colon (u, v)
-      \mapsto \Bigl(
-        P u - Q v,
-        P v + Q u
-      \Bigr)
-    \,,
-\end{equation}
-where $
-  P, Q \colon \real^{n} \to \real^{m}
-$ are unique operators such that $L = P + j Q$. A $\cplx$-convolutional layer with kernel
-$W$ can be implemented as two $\real$-convolutions with kernels $\Re{W}$ and $\Im{W}$ using
-\eqref{eq:cplx-lin-op}. Activations include trigonometric functions and representation-dependent
-non-linearities \citep{hirose_complex-valued_2009}: polar (phase-amplitude) $
-  z \mapsto \sigma(\lvert z \rvert) e^{j \arg z}
-$ or planar (real-imaginary) $
-  z \mapsto \sigma(\Re z) + j \sigma(\Im z)
-$ for some $\real$-valued non-linearity $\sigma$, possibly with learnable parameters
-\citep{trabelsi_deep_2018,wolter_complex_2018}.
 
@@
 
-We propose to use fully factorized complex Gaussian posterior approximation and $\cplx$
-variant of the local reparameterization trick to extend Bayesian Dropout techniques to
-$\cplx$-valued networks. In this section we describe the approximation and derive the
-divergence penalties in \eqref{eq:elbo}. Similarly to $\real$-valued Variational Dropout,
-the proposed $\cplx$-valued extension can be straightforwardly enhanced to provide
-structured sparsity.
+In this section we develop Sparse Variational Dropout for $\cplx$VNN by using a fully
+factorized complex Gaussian posterior approximation. We outline the $\cplx$ version of
+the local reparameterization trick and derive the divergence penalties in \eqref{eq:sgvb_estimator}.
+The proposed $\cplx$-valued extension can readily be a part of a hierarchical variational
+approximation for structured sparsity \citep{louizos_bayesian_2017}.
 
@@
 A vector $z\in \cplx^m$ has complex Gaussian distribution, $
-  q(z) = \mathcal{N}^{\cplx}_m(\mu, \Gamma, C)
-$ with mean $\mu \in \cplx^m$ and $\cplx^{m\times m}$ covariance and relation matrices
-$\Gamma$ and $C$, respectively, if
+  q(z) = \mathcal{C}\mathcal{N}_m(\mu, \Gamma, C)
+$ with mean $\mu \in \cplx^m$, complex covariance and relation matrices $\Gamma$ and $C$,
+respectively, if
 \begin{equation}  \label{eq:cn-paired-real-density}
@@
 \end{equation}
-provided $\Gamma \succeq 0$, $\Gamma^{\hop} = \Gamma$, $C^\top = C$, and $
-  \conj{\Gamma} \succeq C^{\hop} \Gamma^{-1} C
+provided $\Gamma$ is positive definite Hermitian matrix, $C^\top = C$, and $
+  \conj{\Gamma} \succeq \conj{C} \Gamma^{-1} C
 $.
+% $\Gamma \succeq 0$, $\conj{\Gamma^\top} = \Gamma$
 % notation
-Here, $M^{\top}$ is the matrix transpose, $\conj{M}$ is elementwise complex
-conjugation, and $M^{\hop} = (\conj{M})^\top$ denotes Hermitian conjugate.
+% Here, $M^{\top}$ is the matrix transpose, $\conj{M}$ is elementwise complex
+% conjugation, and $M^{\hop} = (\conj{M})^\top$ denotes Hermitian conjugate.
 %
 Matrices $\Gamma$ and $C$ are given by $
-  \mathbb{E} (z - \mu)(z - \mu)^{\hop}
+  \mathbb{E} (z - \mu)\conj{(z - \mu)^\top}
 $ and $
   \mathbb{E} (z - \mu)(z - \mu)^{\top}
-$, respectively, and $z$ is a \textit{proper} $\cplx$-Gaussian vector if $z$ and
-$\conj{z}$ are uncorrelated, i.e. $C = 0$.
+$, respectively, and the random vector $z$ is a \emph{circularly symmetric} $\cplx$-Gaussian
+vector if $z$ and $\conj{z}$ are uncorrelated, i.e. $C = 0$.
 %
 The entropy of $z$ terms of $\Gamma$ and $C$ is
-\begin{align}
+\begin{eqnarray} \label{eq:c-gauss-entropy}
   \mathbb{H}(q)
-    & = - \mathbb{E}_{z \sim q} \log{q(z)}
-    \notag \\
+    &=&
+      - \mathbb{E}_{z \sim q} \log{q(z)}
+      \\
     % &
@@
   % \label{eq:c-gauss-entropy-derivation}
-    &
-    = \tfrac12 \log \det{(\pi e \Gamma)}
+    &=&
+      \tfrac12 \log \det{(\pi e \Gamma)}
       \det{(\pi e (\conj{\Gamma} - \conj{C} \Gamma^{-1} C))}
     \notag \\
-  \label{eq:cn-proper-entropy}
-    &
     % determinant commutes with complex conjugation, since it is multilinear
@@
     % = \tfrac12 \log \bigl\lvert \det{(\pi e \Gamma)} \bigr\rvert^2
-    \Bigl[
-    = \log \bigl\lvert \det{(\pi e \Gamma)} \bigr\rvert
-    \quad \text{for } C = 0
-    \Bigr]
+    &=&
+      \log \bigl\lvert \det{(\pi e \Gamma)} \bigr\rvert
+      \,, \quad \text{ for } C = 0
     \,.
-\end{align}
+    \notag
+\end{eqnarray}
 %
@@
 %   \,. $$
-
-The $\cplx$-variant of the local reparameterization trick utilizes the fact that Gaussian
-vectors are closed under affine transformations:
+Parameterization of a univariate $\cplx$-Gaussian distribution is simpler: $
+  \mathcal{CN}(\mu, \sigma^2, \sigma^2 \xi)
+$ with $\xi \in \cplx$ such that $\lvert \xi \rvert \leq 1$ and $\sigma^2 \geq 0$.
+By \eqref{eq:c-gauss-entropy} its entropy is $
+  \log \pi e \sigma^2 \sqrt{1 - \lvert \xi \rvert^2}
+$.
+
 % $\cplx$-Gaussians are closed under affine transformations
+$\cplx$-Gaussianity is preserved under linear transformations, i.e. for $
+  A \in \cplx^{n \times m}
+$ and $b \in \cplx^{n}$
 \begin{equation}  \label{eq:cn-affine}
-  b + A z \sim \mathcal{N}_n^{\cplx}\bigl(
-      b + A\mu, A \Gamma A^{\hop}, A C A^\top
+  b + A z \sim \mathcal{C}\mathcal{N}_n\bigl(
+      b + A\mu, A \Gamma \conj{A^\top}, A C A^\top
     \bigr)
+  \,.
+\end{equation}
+Therefore, if we have a $\cplx^{n\times m}$ matrix $W$ with \emph{independent}
+$\cplx$-Gaussian entries, i.e.
+\begin{equation}  \label{eq:c-gauss-vi-general}
+  q(W)
+    = \prod_{ij} \mathcal{CN}(
+      % W_{ij} \mid
+      \mu_{ij}, \Sigma_{ij}, \Sigma_{ij} \xi_{ij}
+    )
   \,,
 \end{equation}
-for $A \in \cplx^{n \times m}$ and $b \in \cplx^{n}$. Therefore, if $W \in \cplx^{n\times m}$
-is drawn from a fully factorized approximation
-\begin{equation}  \label{eq:c-gauss-vi-general}
-  W \sim q(W)
-    = \prod_{ij} \mathcal{N}^{\cplx} \bigl(
-      w_{ij} \vert\, \mu_{ij}, \Sigma_{ij}, C_{ij}
-    \bigr)
-  \,,
-\end{equation}
 with $
-  \mu, C \in \cplx^{n\times m}
-$, $\Sigma \in \real^{n\times m}$, and $
-  \lvert C_{ij} \rvert^2 \leq \Sigma_{ij}
-$, then for $x \in \cplx^m$ and $b \in \cplx^n$ the vector $y = b + W x$ has independent
-components with
+  \mu, \xi \in \cplx^{n\times m}
+$, $\Sigma \in [0, +\infty)^{n\times m}$ and $
+  \lvert \xi_{ij} \rvert \leq 1
+$, then for $x \in \cplx^m$ and $b \in \cplx^n$ each component $y_i$ of $y = b + W x$
+is independent univariate $\cplx$-Gaussian
 \begin{equation}  \label{eq:cplx-gauss-trick}
   y_i
-    \sim \mathcal{N}^{\cplx}
+    \sim \mathcal{C}\mathcal{N}
       \Bigl(
-        % e_i^\top \mu x + b_i,
         b_i + \sum_{j=1}^m \mu_{ij} x_j,
         \, \sum_{j=1}^m \Sigma_{ij} \lvert x_j \rvert^2,
-        \, \sum_{j=1}^m C_{ij} x_j^2
+        \, \sum_{j=1}^m \Sigma_{ij} x_j^2 \xi_{ij}
       \Bigr)
@@
 \end{equation}
-The trick requires three operations, i.e. $b + \mu x$, $\Sigma \lvert x \rvert^2$ and
-$C x^2$ with the complex modulus and square applied elementwise, and can be applied to
-any layer, the output of which depends linearly on its parameters, such as convolutional,
-affine, and bilinear transformations ($
-  (x, z) \mapsto x^\top W^{(j)} z + b_j
-$). Similar to $\real$ case, Variational Dropout for $\cplx$ convolutions draws independent
-realizations of $W$ for each spatial patch in the input \citep{molchanov_variational_2017}.
-This provides faster computations and better statistical efficiency of the SGVB gradient
-estimator by eliminating correlation from overlapping patches \citep{kingma_variational_2015}
-and allowing \eqref{eq:cplx-gauss-trick} to leverage $\cplx$ convolutions of the relation
-and variance kernels with elementwise complex squares $x^2$ and amplitudes $\lvert x \rvert^2$.
+This is the $\cplx$-Gaussian version of the local reparameterization trick \eqref{eq:r-gauss-trick}.
+It requires three matrix-vector operations: $\cplx$-valued $b + \mu x$ and $C x^2$,
+and $\real$-valued $
+  \Sigma \lvert x \rvert^2
+$, where $C_{ij} = \Sigma_{ij} \xi_{ij}$ and the complex modulus and square are applied
+elementwise. Equation \eqref{eq:cplx-gauss-trick} can be applied to any layer, the output
+of which depends linearly on its parameters, such as convolutional, affine, and bilinear
+transformations ($
+  (x, z) \mapsto b_j + x^\top W^{(j)} z
+$). Similar to the $\real$ case, $\cplx$ convolutions draw independent realizations of $W$
+for each spatial patch in the input \citep{molchanov_variational_2017}. This provides
+faster computations and better statistical efficiency of the SGVB gradient estimator
+by eliminating correlation from overlapping patches \citep{kingma_variational_2015} and
+allowing \eqref{eq:cplx-gauss-trick} to efficiently leverage $\cplx$ convolutions of
+the relation and variance kernels with elementwise complex squares $x^2$ and amplitudes
+$\lvert x \rvert^2$.
 % Weight sharing is essentially pushed to shared variational parameters $\theta$ in the approximation $q_\theta$.
@@
 
-For $\cplx$-Bayesian Dropout we propose to use fully factorized proper $\cplx$-Gaussian
-approximation \eqref{eq:c-gauss-vi-general} for weights and point estimates of biases in
-dense linear, convolutional and other, effectively, affine layers, i.e. $
-  \Sigma_{ij} = \alpha_{ij} \lvert \mu_{ij} \rvert^2
-$ and $C_{ij} = 0$. This forces the relation coefficients in \eqref{eq:cplx-gauss-trick}
-to be zero.
+For $\cplx$-Sparse Variational Dropout we propose to use fully factorized $\cplx$-Gaussian
+approximation \eqref{eq:c-gauss-vi-general} with $\xi_{ij} = 0$ and additive noise
+parameterization ($
+  \alpha_{ij} = \tfrac{\Sigma_{ij}}{\lvert \mu_{ij} \rvert^2}
+$) for weights in dense linear, convolutional and other effectively parameter-affine
+layers. Point estimates are used for biases.
+% This forces the relation coefficient in \eqref{eq:cplx-gauss-trick} to be zero.
 
@@
 
-For a fully factorized approximation $q(\omega)$ and factorized prior belief $
+For a fully factorized approximation $q(\omega)$ and factorized prior $
   \pi(\omega) = \prod_{ij} \pi(\omega_{ij})
-$, the divergence term in ELBO \eqref{eq:elbo} is
+$, the divergence term \eqref{eq:sgvb_estimator} is
 \begin{equation}  \label{eq:elbo-general-kl-div}
@@
 \end{equation}
-We consider two fully factorized priors: an improper prior for Variational Dropout and
-$\cplx$-Gaussian ARD prior. We omit subscripts ${ij}$ for brevity in the next sections.
+We consider two fully factorized priors: an improper prior, resembling VD, and $\cplx$-Gaussian
+ARD prior. We omit subscripts ${ij}$ for brevity in this section.
 
@@
 
-From \eqref{eq:cn-proper-entropy} the KL-divergence for an improper prior $
+From \eqref{eq:c-gauss-entropy} and $\xi = 0$ the KL-divergence for an improper prior $
   \pi(\omega) \propto {\lvert \omega \rvert}^{-\beta}
@@
 \end{equation}
-Property \eqref{eq:cn-affine} implies that $
-  \mathcal{N}^{\cplx}(\mu, \sigma^2, 0)
-  \sim \mu \cdot \mathcal{N}^{\cplx}(1, \alpha, 0)
-$ for $\mu \neq 0$ and $
+For $\mu \neq 0$ and $
   \sigma^2 = \alpha \lvert \mu \rvert^2
+$ property \eqref{eq:cn-affine} implies $
+  \mathcal{CN}(\mu, \sigma^2, 0)
+    \sim \mu \cdot \mathcal{CN}(1, \alpha, 0)
 $, whence the expectation in brackets is given by
@@
   % \mathbb{E}_{\omega \sim q(\omega)} \log \lvert \omega \rvert^2
-  %   % = \mathbb{E}_{\xi \sim \mathcal{N}^{\cplx}(\xi \vert 1, \alpha, 0)}
-  %   %   \log \lvert \mu \xi \rvert^2
+  %   % = \mathbb{E}_{\varepsilon \sim \mathcal{CN}(\varepsilon \vert 1, \alpha, 0)}
+  %   %   \log \lvert \mu \varepsilon \rvert^2
   %   % = \log \lvert \mu \rvert^2
-  %   %   + \mathbb{E}_{\xi \sim \mathcal{N}^{\cplx}(\xi \vert 1, \alpha, 0)}
-  %   %       \log \lvert \xi \rvert^2
+  %   %   + \mathbb{E}_{\varepsilon \sim \mathcal{CN}(\varepsilon \vert 1, \alpha, 0)}
+  %   %       \log \lvert \varepsilon \rvert^2
   %   =
     \log \alpha \lvert \mu \rvert^2
-      + \mathbb{E}_{\xi \sim \mathcal{N}^{\cplx}(\xi \vert 0, 1, 0)}
-          \log{\bigl\lvert \tfrac1{\sqrt{\alpha}} + \xi \bigr\rvert^2}
+      + \mathbb{E}_{\varepsilon \sim \mathcal{CN}(0, 1, 0)}
+          \log{\bigl\lvert \tfrac1{\sqrt{\alpha}} + \varepsilon \bigr\rvert^2}
     \,.
@@
   (z_i)_{i=1}^m
-    \sim \mathcal{N}^{\cplx}(0, 1, 0)
+    \sim \mathcal{CN}(0, 1, 0)
 $ iid and $\theta \in \cplx^m$, then $
@@
 \begin{equation}  \label{eq:log-moment-for-chi-2}
-  \mathbb{E}_{z \sim \mathcal{N}^{\cplx}(0, 1, 0)}
+  \mathbb{E}_{z \sim \mathcal{CN}(0, 1, 0)}
     \log \lvert \theta + z \rvert^2
@@
     %   + \tfrac{\beta}2 \log \alpha \lvert \mu \rvert^2
-    %   + \tfrac{\beta}2 \mathbb{E}_{\xi \sim \mathcal{N}^{\cplx}(\xi \vert 0, 1, 0)}
-    %       \log{\bigl\lvert \tfrac1{\sqrt{\alpha}} + \xi \bigr\rvert^2}
+    %   + \tfrac{\beta}2 \mathbb{E}_{\varepsilon \sim \mathcal{CN}(\varepsilon \vert 0, 1, 0)}
+    %       \log{\bigl\lvert \tfrac1{\sqrt{\alpha}} + \varepsilon \bigr\rvert^2}
     % =
@@
 We set $\beta = 2$ to make the divergence term depend only on $\alpha$ and add $\gamma$
-so that the right-hand side is nonnegative \citep[eq.(84)]{lapidoth_capacity_2003}.
-%
-Since $\mathop{Ei}(x)$ has simple analytic derivative and \eqref{eq:elbo} depends additively
+so that the right-hand side is non-negative \citep[eq.(84)]{lapidoth_capacity_2003}.
+%
+Since $\mathop{Ei}(x)$ has simple analytic derivative and \eqref{eq:sgvb_estimator} depends additively
 on \eqref{eq:c-vd-kl-div}, it is possible to back-propagate through the divergence without
 forward evaluation, which speeds up gradient updates.
-% Gradient-based optimiziation of \eqref{eq:elbo} usually does not use the value of the objective. 
-% In stochastic gradient methods are concerned more with the gradient, induced by the objective
-% function, rather than its value.
+% Gradient-based optimiziation of \eqref{eq:sgvb_estimator} usually does not use the value
+% of the objective.  In stochastic gradient methods are concerned more with the gradient,
+% induced by the objective function, rather than its value.
 
@@
 
-We consider the fully factorized proper $\cplx$-Gaussian ARD prior with $
+We consider the fully factorized circularly symmetric $\cplx$-Gaussian ARD prior $
   \pi_\tau(\omega)
-    \propto \mathcal{N}^{\cplx}\bigl(
+    = \mathcal{CN}\bigl(
       \omega \vert 0, \tau^{-1}, 0
     \bigr)
-$. The per element divergence term in \eqref{eq:elbo-general-kl-div} is
+$ with $\tau > 0$. The per element divergence term in \eqref{eq:elbo-general-kl-div} is
 \begin{equation}  \label{eq:emp-bayes-kl-div}
@@
 %
-In Empirical Bayes the prior adapts to the observed data, i.e. \eqref{eq:elbo} is optimized
-w.r.t. $\tau$ of each weight's prior. Since divergence sits in \eqref{eq:elbo} with negative
-sign, optimal $
+In Empirical Bayes the prior adapts to the observed data, i.e. \eqref{eq:sgvb_estimator}
+is optimized w.r.t. $\tau$ of each weight's prior. The Maximum Likelihood estimator
+of $\tau$ is given by the minimizer \eqref{eq:emp-bayes-kl-div}, i.e. $
   \tau^\ast = (\sigma^2 + \lvert \mu \rvert^2)^{-1}
-$ is found by minimizing \eqref{eq:emp-bayes-kl-div}, which gives
+$, thereby giving
 \begin{equation}  \label{eq:emp-bayes-opt-kl}
@@
 \end{equation}
+Thus in both $\real$ and $\cplx$ cases ARD produces a tractable analytic expression for
+the KL-divergence term in \eqref{eq:sgvb_estimator}.
 
@@
 
-\subsubsection{$\cplx$-Bayesian Dropout via $\real$-scaling} % (fold)
+\subsubsection{$\cplx$-Variational Dropout via $\real$-scaling} % (fold)
 \label{ssub:real_scaling_dropout}
 
-Consider the following parameterization of $W$: $
-  W_{ij} = \mu_{ij} \xi_{ij}
-$, $\xi_{ij} \in \real$ with $
-  \xi_{ij} \sim \mathcal{N}(1, \alpha_{ij})
+We consider the following parameterization of $W$: $
+  W_{ij} = \mu_{ij} \varepsilon_{ij}
+$, $\varepsilon_{ij} \in \real$ with $
+  \varepsilon_{ij} \sim \mathcal{N}(1, \alpha_{ij})
 $, yet $\mu \in \cplx^{n \times m}$. This case corresponds to inference regarding
-relevance multipliers $\xi$ rather than the parameters themselves. Under this parameterization
-the weight distribution is fully factorized degenerate $\cplx$-Gaussian approximation
+multiplicative noise $\varepsilon$ rather than the parameters themselves. Under
+this parameterization $q(W_{ij})$ is effectively degenerate univariate $\cplx$-Gaussian
 \eqref{eq:c-gauss-vi-general} with $
@@
 $ and $
-  C_{ij} = \alpha_{ij} \mu_{ij}^2
-$. Unlike proper $\cplx$-Gaussian approximation, the complex relation parameter in
-\eqref{eq:cplx-gauss-trick} is nonzero in this case and equals $
+  \xi_{ij} = e^{\iu \phi_{ij}}
+  % \xi_{ij} = \bigl(\tfrac{\mu_{ij}}{\lvert \mu_{ij} \rvert}\bigr)^2
+$ with $\phi_{ij} = \arg \mu_{ij}$, thereby making the complex relation parameter
+in \eqref{eq:cplx-gauss-trick} equal $
   \sum_j \alpha_{ij} (x_{ij} \mu_{ij})^2
-$.
+$, which is non-zero.
 %
@@
 
-Source code for the experiments conducted in this study and figures is available at
-\url{https://github.com/ivannz/complex_paper/tree/v2020.3}.
-%
-Source code for a PyTorch extension which implements $\cplx$-valued Variational Dropout and
-ARD layers, and provides basic layers for $\cplx$-valued networks, including maskable
-sparsified layers, is available at
-\url{https://github.com/ivannz/cplxmodule}.
-\smallskip
-
-We study the performance-compression trade-off of the proposed Bayesian sparsification
-method for $\cplx$-valued networks presented above on image classification and music
-annotation tasks.
-%
-Following \citet{wolter_complex_2018} and \citet{trabelsi_deep_2018}, the class logit scores
-are taken as real part of the complex-valued output of a network.
-%
+To verify the proposed $\cplx$-valued variational sparsification methods presented
+above and explore their compression-performance trade-off we carry out a numerical
+study of $\cplx$VNN for image classification and music transcription.
+
 % image features
-Since image data is not naturally $\cplx$-valued, we preprocess it by either embedding
-$\real$-data into $\cplx$ assuming $\Im z = 0$ (\texttt{raw}), or applying the two-dimensional
-Fourier Transform (\texttt{fft}), centering the lower frequencies. We do not train an
-auxiliary model to synthesize the imaginary component from the real data, proposed by
-\citet{trabelsi_deep_2018}.
+Since image data is not naturally $\cplx$-valued, we preprocess it using the natural
+inclusion $\real \hookrightarrow \cplx$ (\texttt{raw}, $\Im z = 0$) or applying the
+two-dimensional Fourier Transform (\texttt{fft}), centering the lower frequencies. We
+do not train an auxiliary network that synthesizes the imaginary component from $\real$
+input data \citep{trabelsi_deep_2018}.
+%
+Following \citet{wolter_complex_2018} and \citet{trabelsi_deep_2018}, the class logit
+scores are taken as real part of the complex-valued output of a network.
 
 % setup and common experiment settings
-For each dataset we conduct a set of experiments in which we try out all combinations of
-model kinds ($\real$ or $\cplx$), sparsification methods (VD or ARD) and input features.
-Where reasonable, we also study the effects of halving ($\tfrac12\cplx$) and doubling ($2\real$)
-of the size of intermediate layers in each network \citep{monning_evaluation_2018}.
-%
-Each experiment is replicated \textit{five} times to take into account random initialization,
-random order of the mini-batch during SGD, stochastic outputs of the intermediate layers,
-and non-determinism of single-precision computations on GPUs.
-
-Each network within every experiment passes through three successive stages of training:
-pre-training (\textit{``dense''}), sparsification (\textit{``sparsify''}), and fine-tuning
-(\textit{``fine-tune''}) (sec.~\ref{sub:staging}). The parameters and optimizer state are
-passed between stages, except for last one, which inherits just the parameters.
-%
-Every experiment uses ADAM optimizer, resets the learning rate to $10^{-3}$ before each
-stage, and applies global $\ell_2$-norm gradient clipping at $0.5$.
+The networks are trained in three successive stages in every experiment: the \emph{``pre-train''}
+stage for pre-training the network, the \emph{``sparsify''} stage to determine parameter
+relevance using Variational Dropout, and the \emph{``fine-tune''} to train the pruned
+network (sec.~\ref{sub:staging}). Network's parameters are initialized with values from
+the previous stage.
+%
+Networks are trained with ADAM optimizer, with the learning rate reset to $10^{-3}$ before
+each stage and global $\ell_2$-norm gradient clipping at $0.5$.
+% https://pytorch.org/docs/master/_modules/torch/nn/utils/clip_grad.html#clip_grad_norm_
+
+Each experiment is replicated \emph{five} times to account for random effects from
+initialization, stochastic gradient optimization, noisy output from intermediate layers,
+and non-determinism of computations on GPU.
+% experiments took about three weeks on 4 node GTX1080Ti GPUs in fp32
 
 % write a note on the incompressible parameters (bias, batch norm etc.)
-The compression rate is calculated based on the number of IEEE754 floating point values
-needed to store the model and equals $
+The compression rate is calculated based on the number of floating point values needed
+to store the network and equals $
   \tfrac{n_\mathtt{par}}{n_\mathtt{par} - n_\mathtt{zer}}
-$, where $n_\mathtt{zer}$ is the number of explicit zeros, $n_\mathtt{par}$ is the total
-number of floats. In particular, each parameter is counted once in a $\real$-valued network,
-but twice in a $\cplx$-network. Each model has a compression limit, determined by biases,
-shift and scaling in $\real$- and $\cplx$-valued batch normalization layers.
+$, where $n_\mathtt{zer}$ is the number of explicit zeros at the ``fine-tune'' stage
+and $n_\mathtt{par}$ is the total number of values. In a $\real$-valued network each
+parameter counts as \emph{one} value and as \emph{two} values in a $\cplx$VNN. Each
+model has a compression limit, determined by biases, shift and scaling in $\real$-
+and $\cplx$-valued batch normalization layers.
+% variace parameters in q_\theta are completely ignored.
 
@@
 
-% The training consists of three successive stages: ``dense'' $\to$ ``sparsify'' $\to$ ``fine-tune''.
-
-At the \textit{``dense''} stage every network is fit ``as-is'', retaining its original
-non-Bayesian architecture, and using only the likelihood term from \eqref{eq:elbo} without
-variational dropout.
-
-During the \textit{``sparsify''} stage we make every layer Bayesian and apply $\cplx$-variational
-dropout sec.~\ref{ssub:vd_prior} (or sec.~\ref{ssub:ard_prior}) or its $\real$ counterpart.
+% The training consists of three successive stages: ``pre-train'' $\to$ ``sparsify'' $\to$ ``fine-tune''.
+At the \emph{``pre-train''} stage every network is fit ``as-is'' using deterministic layers
+and only the likelihood term from \eqref{eq:sgvb_estimator}.
+
+During the \emph{``sparsify''} stage we make every layer stochastic and apply variational
+sparsification (sec.~\ref{ssub:vd_prior}, ~\ref{ssub:ard_prior}, or their $\real$ versions).
 We inject a coefficient $
   C \in (0, 1]
-$ at the KL divergence term in \eqref{eq:elbo} to study the attainable sparsity levels:
+$ at the KL divergence term in \eqref{eq:sgvb_estimator}:
 \begin{equation}  \label{eq:elbo_with_coef}
@@
   + \frac1{M} \sum_{k=1}^M
-      \log p_{\phi}(z_{i_k} \mid g(\varepsilon_k; \theta))
+      \log p_{\phi}(x_{i_k} \mid g(\varepsilon_k; \theta))
   \,.
-  \tag{\ref{eq:elbo}'}
-\end{equation}
-By varying $C$ we adjust the importance of the sparsifying prior in learning $q_\theta(W)$,
-meaning that higher value yields more irrelevant parameters during inference and makes
-layers sparser upon termination of this stage.
+  \tag{\ref{eq:sgvb_estimator}'}
+\end{equation}
+In contrast to \cite{molchanov_variational_2017}, who anneal $C$ from zero to one during
+training, we use constant $C$ and vary it between runs. This allows us to explore the
+compression-performance profile by balancing model's likelihood and posterior's penalty
+for diverging form the sparsifying prior in \eqref{eq:elbo_with_coef}. In particular,
+higher $C$ implies higher sparsity.
 % RFC: citation needed fot this "trick". Cite $\beta$-VAE maybe?
@@
 % on compresssion
-Between \textit{``sparsify''} and \textit{``fine-tune''} stages we compute masks of non-zero
-weights in each layer based on the relevance scores $\alpha$ (sec.~\ref{sec:variational_dropout}).
-Since the $q_\theta$ factorizes into univariate distributions, a $\cplx$ or $\real$ parameter
-is considered non-zero if $\log \alpha \leq \tau$ for $
-  \alpha = \tfrac{\sigma^2}{\lvert\mu\rvert^2}
-$, or zero otherwise.
-
-The \textit{``fine-tune''} stage reverts the network back to non-Bayesian layers, applies
-sparsity masks to its parameters and proceeds with training the kept parameters as during
-the ``dense'' stage. Unless specified otherwise the network is initialized to the mode
-of the learnt $q_\theta(W)$.
-
+Between \emph{``sparsify''} and \emph{``fine-tune''} stages we compute masks of non-zero
+weights in each layer based on the relevance scores $\alpha$ (sec.~\ref{sub:dropout}).
+Since $q_\theta$ factorizes into univariate distributions, a $\cplx$ or $\real$ parameter
+is considered non-zero iff $\log \alpha \leq \tau$ for $
+  \alpha = \tfrac{\sigma^2}{\lvert \mu \rvert^2}
+$.
 % on chosing the threshold
-The threshold $\tau$ is picked so, that the remaining non-zero parameters are within
+The threshold $\tau$ is picked so that the remaining non-zero parameters are within
 $\delta$ relative tolerance of their mode with high probability under the approximate
-posterior. Since $q_\theta$ is fully factorized $\real$- or a proper $\cplx$-Gaussian,
-the random variable $
+posterior. For a univariate $\real$- or a circularly symmetric $\cplx$-Gaussian random
+variable $w$, $
   \tfrac{k \lvert w - \mu \rvert^2}
@@
 %
-For a generous tolerance $\delta = 50\%$ all values of $\log \alpha$ below $-2.5$ yield
-at least $90\%$ chance of a non-zero $\real$/$\cplx$ parameter. We pick $\tau = -\tfrac12$
-to retain parameters sufficiently concentrated around their mode, and encourage higher
-sparsity, at the same time being aware that $q_\theta$ is merely an approximation.
-In comparison, $\tau = 3$ is commonly used as the threshold
+For a tolerance $\delta = 50\%$ values $\log \alpha$ below $-2.5$ yield at least $90\%$
+chance of a non-zero $\real$/$\cplx$ parameter. We pick $\tau = -\tfrac12$ to retain
+parameters sufficiently concentrated around their mode and encourage higher sparsity,
+at the same time being aware that $q_\theta$ is merely an approximation. In comparison,
+$\tau = 3$ is commonly used as the threshold
 \citep{molchanov_variational_2017,kingma_variational_2015}.
+
+At the \emph{``fine-tune''} stage the network reverts back to deterministic architecture
+and proceeds the same way as the ``pre-train'' stage, except for training only those
+parameters, which are specified by sparsity masks.
 
@@
 We conduct a moderately sized experiment on MNIST-like datasets of $28\times 28$ greyscale
-images to study the performance-compression trade-off of the proposed $\cplx$-variational
-dropout: MNIST \citep{lecun_gradient-based_1998}, KMNIST \citep{clanuwat_deep_2018},
+images to study the performance-compression trade-off of the proposed $\cplx$-valued Sparse
+Variational Dropout: MNIST \citep{lecun_gradient-based_1998}, KMNIST \citep{clanuwat_deep_2018},
 EMNIST \citep{cohen_emnist_2017} and Fashion-MNIST \citep{xiao_fashion-mnist_2017}.
@@
 % dataset size
-We deliberately use a {fixed} random subset of $10k$ images from the train split of each
-dataset to fit the networks and measure the performance with classification \textit{accuracy}
-score on the usual test split.
+We deliberately use a \emph{fixed} random subset of \emph{ten thousand} images from the train
+split of each dataset to fit the networks and measure the performance with classification
+\emph{accuracy} score on the usual test split.
 % Limiting the size was done primarily to test the regularization strength of compression
@@
 % (raw) R - C - 2 * R
-We consider two simple architectures for $\real$ and $\cplx$ networks in this experiment,
-which have been chosen for the purpose of illustrating the compression and understanding
-the effects of experiment parameters. \textit{TwoLayerDenseModel} is a wide dense ReLU
-network $784 \to 4096 \to n_\mathtt{out}$, and \textit{SimpleConvModel} is a ReLU net with
-two $2d$ $k_5 s_1$ convolutions with filters $20 \to 50$, two $k_2 s_2$ average pooling steps,
-and a dense classifier network $800 \to 500 \to n_\mathtt{out}$. The number of intermediate
-feature is as specified in $\real$ and $\cplx$ models, is halved in complex models tagged
-$\tfrac12\cplx$, and doubled in real models labelled $2\real$.
+We consider two simple architectures in this experiment, which have been chosen for
+the purpose of illustrating the compression and understanding the effects of experiment
+parameters. \emph{TwoLayerDenseModel} is a wide dense ReLU network $
+  784 \to 4096 \to n_\mathtt{out}
+$, and \emph{SimpleConvModel} is a ReLU net with two $2d$ $k_5 s_1$ convolutions with
+filters $20 \to 50$, two $k_2 s_2$ average pooling steps, and a classifier head
+$800 \to 500 \to n_\mathtt{out}$.
+%
+For each dataset we experiment with all combinations of model kinds ($\real$ or $\cplx$)
+and sparsification methods (VD or ARD). To take into account potential differences in
+the capacity of $\cplx$VNN we consider halving or doubling the number of features in
+the intermediate layers \citep{monning_evaluation_2018}. Halved $\cplx$VNN are tagged
+$\tfrac12\cplx$, and doubled $\real$-valued networks are labelled $2\real$. For \texttt{fft}
+we compare $\{\real, \cplx, 2\real\}$ and for \texttt{raw} -- $\{\tfrac12\cplx, \real, \cplx\}$.
 
@@
 experiment. The sparsification threshold $\tau$ is fixed at $-\tfrac12$, the training batch
-size is set to $128$ and the base learning rate ${10}^{-3}$ is reduced after the $10$-th epoch
-to ${10}^{-4}$ at every stage.
+size is set to $128$ and the base learning rate ${10}^{-3}$ is reduced after the $10$-th
+epoch to ${10}^{-4}$ at every stage.
 %
 % grid specs
-We let $
+We vary $
   C \in \{
@@
   \}
-$ in \eqref{eq:elbo_with_coef}, test VD and ARD methods, try \texttt{raw} or \texttt{fft}
-input features, and repeat each experiment $5$ times to get a sample of compression-accuracy
-pairs.
+$ in \eqref{eq:elbo_with_coef} and repeat each experiment $5$ times to get a sample
+of compression-accuracy pairs.
 
@@
   \centering
-  \begin{subfigure}[b]{1.\columnwidth}  % imcl2019-style swears at this
+  \begin{subfigure}  % [b]{1.\columnwidth}  % imcl2019-style swears at this
     \centering
@@
   % \hfill
-  \begin{subfigure}[b]{1.\columnwidth}  % imcl2019-style swears at this
+  \begin{subfigure}  % [b]{1.\columnwidth}  % imcl2019-style swears at this
     \centering
@@
 Figures~\ref{fig:mnist-like__trade-off__fft} and~\ref{fig:mnist-like__trade-off__raw}
-depict the resulting compression-accuracy trade-off on MNIST for the simple models
-described above (other datasets are in appendix~\ref{sec:mnist_like_experiments}).
-%
-The points represent the trade-off of the compressed networks after fine-tuning, while their
-tails illustrate the impact of this stage on the accuracy. Transparent horizontal bands on
-each plot represent min-max performance spread of an uncompressed network on the test split.
-
-The overarching pattern in all experiments on MNIST-like datasets is that both ARD and VD
-compress similarly and ARD offers marginal advantage in terms of performance after fine-tuning.
-Fourier features perform marginally worse than raw image data for each model across all
-compression rates, and their trade-off for the dense network has a hat-like shape, contrasting
-the raw image features, for which the accuracy stays at one level for moderate rates,
-and then abruptly decays in high compression regime.
-
-The impact of ``fine-tune'' is mixed, and depends on the dataset and features, although it
-frequently improves accuracy in high compression $\times50+$ (high $C$ in \eqref{eq:elbo_with_coef})
-for raw image input. On EMNIST Letters and MNIST datasets in the small compression regime the
-dense network exhibits a trough in accuracy before fine-tuning stage.
-
-% conclusions
-These experiments demonstrate that $\cplx$ Variational Dropout can offer adequate compression
-without much loss in performance for $\cplx$-valued networks. Although ARD performs on par
-with VD, unlike VD, it uses a proper prior and has a tractable analytic expression for the
-KL-divergence \eqref{eq:emp-bayes-kl-div} in both $\real$ and $\cplx$ cases.
+depict the resulting compression-accuracy trade-off on MNIST for the models described
+above.
+%
+Each point represents the trade-off of the compressed network after fine-tuning, while
+its tail illustrates the impact of this stage on the performance. Transparent horizontal
+bands on each plot represent min-max performance spread of the pre-trained uncompressed
+network on the test split.
+%
+Results for other MNIST-like dataset are presented appendix~\ref{sec:mnist_like_experiments}.
+
+% observations and conclusions
+The overarching conclusion from the conducted experiments is that both $\cplx$-ARD and
+$\cplx$-VD methods compress similarly to each other, but for the same value of $C$ in
+\eqref{eq:elbo_with_coef} ARD yields marginally lower compression and slightly higher
+performance post fine-tuning. For each fixed $C$ the compression rates after ``sparsify''
+stage are roughly identical.
+% a table for mean comparison against C and compression-performance?
+%
 % fft: $2\real$ convolutional model trade-off overall better than $\real$, dense -- on par.
 % raw: $\cplx$ models trade-off overall better than $\tfrac12\cplx$.
-Wider $\real$ and $\cplx$ networks appear to have more favourable trade-off between
-compression and accuracy.
 % fft: any-$\real$ dense model compresses better than $\cplx$
-However, it seems that due to more intrinsic degrees of freedom, $\real$-valued models
-perform and compress better than $\cplx$, even when the former uses the same number of
-features as the latter.
 % $\cplx$-valued networks do not have as much spare capacity as $2 \real$ due to
 %  constraints imposed by multiplication in $\cplx$ numbers
+%
+At the same time, ``fine-tune'' stage almost always improves performance in high compression
+regime ($\times50+$ high $C$ in \eqref{eq:elbo_with_coef}), likely due to regularization from
+high sparsity.
+% On EMNIST Letters and MNIST datasets in the small compression regime the dense network
+% exhibits a trough in accuracy before fine-tuning stage.
+Fourier features catch up to the raw data in terms of performance at high compression
+rates $\times100+$ only for the \emph{TwoLayerDenseModel}.
+% spectral feature useful residual information?
+% For it the compression-performance profile exhibits a ramp-like shape, in contrast
+% to the raw features, for which the accuracy stays level for moderate rates, but then
+% abruptly drops at high rates.
+%
+Comparison of $\real$ and $\cplx$ networks with matching architecture, i.e. same effective
+layer widths in $2\real$ vs. $\cplx$ and $\real$ vs. $\tfrac12\cplx$, shows that doubled
+$\real$ networks perform and compress better than $\cplx$, due to higher intrinsic redundancy
+unchecked by $\cplx$-arithmetic constraint.
+% Convolutional network compress worse because they have less redundant parameters
 
@@
 
-We conduct an experiment on the CIFAR10 classification dataset \citep{krizhevsky_learning_2009}
-comprising $32\times 32$ color images of $10$ classes to study the performance-compression
-trade-off of a moderately large deep network.
+Having verified the $\cplx$ variational sparsification method on MNIST-like datasets
+and simple models, we turn to the CIFAR10 dataset comprising $32\times 32$ colour
+images of $10$ classes \citep{krizhevsky_learning_2009} and focus on the VGG16 network
+\citep{simonyan_very_2015}.
+%
 % same experimental setup as in MNIST, describe the VGG16 model and its cplx-valued modification
-The experiment is set up similarly to MNIST-like experiment, except that we train $\real$
-VGG16 network \citep{simonyan_very_2015} and its $\cplx$ variant, in which we have replaced
-$\real$-valued layers with their $\cplx$-valued counterparts. $\real$ and $\cplx$ VGG16 have
-the same feature sizes in intermediate layers.
-
+We train the VGG16 network and its $\cplx$ variant, in which we have replaced $\real$-valued
+layers with their $\cplx$-valued counterparts. We do not halve or double the features
+in any network, since the goal of this experiment is to assess the trade-off for a deep
+convolutional network.
+%
 % differences with mnist
-Unlike experiment in sec.~\ref{sub:mnist_like_datasets}, we consider the raw features only,
-use full training split, and allocate $20$, $40$, and $20$ epochs to each stage. During training
-the mini-batch of $128$ samples is randomly augmented by randomly flipping horizontally and
-cropping. Random cropping is done by zero-padding each side by four pixels and extracting a
-random $32\times 32$ patch from the $40\times 40$ intermediate image.
-%
-We vary $C$ in \eqref{eq:elbo_with_coef} over $
-  \{\tfrac32 2^{-\tfrac{k}2} \colon k=7, \cdots, 15\}
-$, compare VD and ARD methods, and measure accuracy on CIFAR10 test split.
+Unlike experiment in sec.~\ref{sub:mnist_like_datasets}, we consider the raw features
+only, use full training split, measure accuracy on the usual test split, and allocate
+$20$, $40$, and $20$ epochs to each stage.
+During training every mini-batch of $128$ samples is augmented by random horizontal flipping
+and random cropping, which is done by zero-padding the image with four pixels and extracting
+a $32\times 32$ patch from the $40\times 40$ intermediate image.
 
@@
   \centering
-  \begin{subfigure}[b]{1.\columnwidth}  % imcl2019-style swears at this
   % \includegraphics[width=\columnwidth]{figure__cifar__trade-off/legacy__augmentedcifar10__raw__-0.5.pdf}
   \includegraphics[width=\columnwidth]{figure__cifar__trade-off/appendix__augmentedcifar10__raw__-0.5.pdf}
-  \end{subfigure}
   \caption{%
-    The compression-accuracy frontier for VGG16 ($\real$ and $\cplx$) on CIFAR10.
+    The compression-accuracy profile for the $\real$ and $\cplx$ VGG16.
   }
@@
 % draw some conclusions
-Figure~\ref{fig:figure__cifar10__trade-off} shows that, although ARD method offers slightly
-less compression, it makes up for it by marginally better accuracy post fine-tune. VGG16 and
-$\cplx$-VGG16 exhibit similar declining compression-accuracy trade-off, but due to higher
-capacity $\cplx$-valued network yields higher accuracy \citep{monning_evaluation_2018}. Unlike
-MNIST, fine-tuning stage significantly improves the test performance, which, we speculate, might
-be due to dataset augmentation and deeper model.
-% reword this sentence
+The compression-accuracy curve in figure~\ref{fig:figure__cifar10__trade-off}, constructed
+for $C = \tfrac32 2^{-\tfrac{k}2}$ with $k=7, \cdots, 15$, shows that
+it is possible to confidently achieve around $\times100$ compression of a deep $\cplx$VNN
+without losing accuracy, provided the network is fine-tuned after undergoing Variational
+sparsification. Regarding methods themselves, $\cplx$-VD and $\cplx$-ARD follow the same
+declining compression-accuracy pattern, but for the same setting $C$ the latter provides
+slightly less compression with marginally better accuracy.
 
@@
 % describe musicnet as in Trabelsi et al. (2017) also get some hints from thickstun_learning_2017
-We use MusicNet \citep{thickstun_learning_2017}, an audio dataset of $330$ annotated
-musical compositions, to investigate compressibility of the $1d$ VGG-like $\cplx$-convent
-proposed by \citet{trabelsi_deep_2018}. Similarly to the study, we downsample the audio
-from 44.1kHz to 11kHz, retain only $84$ out of $128$ labels, and hold-out the same validation
-and test compositions, on which we score the models with the pooled average precision.
-Each epoch lasts for $1000$ random mini-batches of the remaining $321$ pieces. The input
-features are $\cplx$-valued Fourier transformed windows of $4096$ samples from each waveform.
-The label vectors are taken from annotations at the middle of the window.
-
-Experiments with the uncompressed model aimed at replicating the result of \citet{trabelsi_deep_2018}
-have shown that early stopping almost always terminates much sooner, than $200$ epochs used
-in their study: within the first $10-20$ epochs with the validation performance peaking at
+
+% The experimental results of the experiments in previous sections indicate that the proposed
+% $\cplx$-valued Sparse Variational Dropout achieves the goal of network compression.
+% Inspired by this we set out to investigate its effects on in the domain where it has
+% been shown that CVNN outperform rvnn.
+
+% Prior experiments demonstrated that the $\cplx$-valued variational sparsification
+% what can be expected from prior research.
+MusicNet is a corpus of $330$ annotated classical music recordings used for learning
+feature representations for music transcription tasks \citep{thickstun_learning_2017}.
+\citet{trabelsi_deep_2018} have proposed a $1d$ VGG-like $\cplx$-valued network that
+surpassed a similar $\real$-valued network and achieved $72.9\%$ pooled \emph{Average
+Precision} on this dataset. Recently \citet{yang_complex_2020} have reported $74.2\%$
+AP with a $\cplx$-valued transformer, \citet{thickstun_invariances_2018} have achieved
+$77.3\%$ with a four-layer $\real$-valued network on $\log$-spaced spectrogram, and
+\citet{draguns_residual_2020} report $78.0\%$ with a residual-shuffle-exchange network.
+
+In this experiment we seek to compress of the $\cplx$VNN proposed by \citet{trabelsi_deep_2018}.
+%
+The dataset is split into the same validation and test samples and handled identically
+to their study. The input features are $\cplx$-valued Fourier transforms of $4096$-sample
+windows from each waveform, and the label vectors are taken from annotations at the middle
+of the window. Each epoch lasts for $1000$ random mini-batches of the musical pieces.
+% downsample the audio from 44.1kHz to 11kHz, retain only $84$ out of $128$ labels,
+% and hold-out the same validation and test compositions
+% 
+However, we deviate from the set-up used by \citet{trabelsi_deep_2018} by clipping $\ell_2$
+norm of the gradients to $0.05$ and shifting the low frequencies of the input to the centre
+to maintain spatial locality for convolutions.
+
+Experiments with the uncompressed model aimed at replicating the original result have
+shown that early stopping almost always terminates within the first $10-20$ epochs of
+the $200$ epochs used in their study, due to the validation performance peaking at
 $10-15$ epochs and steadily declining afterwards.
 %
-Thus we opt to use shorter stages: $12$, $32$ and $50$ epochs (sec.~\ref{sub:staging}), with
-early stopping activated only during the ``fine-tune'' stage. To keep the learning rate schedule
-consistent, we scale the learning rate of $10^{-3}$ after $5$, $10$, and $20$-th epoch by
-$\tfrac1{10}$, $\tfrac1{20}$ and $\tfrac1{100}$, respectively.
-
-We deviate from the set-up used by \citet{trabelsi_deep_2018} by clipping $\ell_2$ norm of the
-gradients to $0.05$ and shifting the low frequencies of the input to the centre to maintain
-spatial locality for convolutions.
-
-We test complex ARD (sec.~\ref{ssub:ard_prior}) and VD (sec.~\ref{ssub:vd_prior}) methods
-and vary $
-  C \in \{\tfrac14, \tfrac12, \tfrac34, 1\} \cdot 10^{-k}
-$ for $k=1, 2, 3$, while keeping $\tau$ at $-\tfrac12$. The performance is measured after
-``dense'' stage, before the beginning and upon termination of fine-tuning.
+Thus we opt to use shorter stages: $12$, $32$ and $50$ epochs (sec.~\ref{sub:staging}),
+with early stopping activated only during the ``fine-tune'' stage. To keep the learning
+rate schedule consistent, we scale the learning rate of $10^{-3}$ after $5$, $10$, and
+$20$-th epoch by $\tfrac1{10}$, $\tfrac1{20}$ and $\tfrac1{100}$, respectively.
+
+We explore the $\cplx$-VD and $\cplx$-ARD methods by varying $C$ over the grid $
+  \{\tfrac14, \tfrac12, \tfrac34, 1\} \cdot 10^{-k}
+$ with $k=1, 2, 3$, while keeping $\tau$ at $-\tfrac12$. The performance is measured after
+``pre-train'' stage, just before and upon termination of fine-tuning.
 %
@@
 The motivation is to test if the handicap introduced by the forced compression of the most
-upstream layer can be alleviated by non-uniform compression, induced by variational dropout.
-We test only complex VD in this sub-experiment, since prior results have not demonstrated
+upstream layer can be alleviated by non-uniform compression, induced by Variational Dropout.
+We test only $\cplx$-VD in this sub-experiment, since prior results have not demonstrated
 significant superiority of one method over another.  % it should've been ARD
@@
   \centering
-  \begin{subfigure}[b]{1.\columnwidth}  % imcl2019-style swears at this
-    \centering
   \includegraphics[width=\columnwidth]{figure__musicnet__trade-off/paper__musicnetram__fft__-0.5.pdf}
-  \end{subfigure}
   \caption{%
@@
 
-Figure~\ref{fig:musicnet__trade-off} shows the resulting performance-compression frontier.
-ARD slightly outperforms VD in terms of performance, but both deliver similar compression
-rates. The trade-off demonstrates that with the proposed $\cplx$-valued variational dropout
-methods (sec.~\ref{sec:c_variational_dropout}) and post-sparsification fine-tuning it is
-possible to achieve average precision level comparable to the result of \citet{trabelsi_deep_2018}
-with a model compressed $50\times$-$200\times$. Furthermore, the $k_3$ model, compressed
-$110 \times$ with $\cplx$ VD, outperforms its uncompressed baseline, but yields lower
-performance than the full model.
-
+The performance-compression frontier in figure~\ref{fig:musicnet__trade-off} shows that
+VD and ARD deliver similar compression rates, but ARD slightly outperforms in terms of
+the average precision at the cost of marginally lower compression.
+%
+At $\times100$ compression level the $k_3$ model outperforms its
+uncompressed baseline, but yields lower AP score than the full model. In conjunction with
+post-pruning fine-tuning, both $\cplx$-valued variational sparsification methods achieve
+average precision level comparable to the result of \citet{trabelsi_deep_2018} with a
+network having $50$-$200$ times less parameters.
+% any conclusions related to k_3???
+
+% testing the fx of the threshold
 \begin{figure}[!t]
   \centering
-  \begin{subfigure}[b]{1.\columnwidth}  % imcl2019-style swears at this
-    \centering
-    \includegraphics[width=\columnwidth]{figure__fine-tune_fx__early__compression.pdf}
-  \end{subfigure}
+  \includegraphics[width=1\columnwidth]{figure__musicnet__threshold__C__DeepConvNet.pdf}
+  \caption{%
+    The effect of fine-tuning on performance-compression curves for $
+      C\in \{\tfrac1{20}, \frac1{200}\}
+    $ in \eqref{eq:elbo_with_coef}.
+  }
+  \label{fig:hist__and__threshold__tradeoff}
+\end{figure}
+
+% effects of extra training epochs and the impact of tau
+We take the full models compressed with $C \in \{\tfrac1{20}, \frac1{200}\}$ and re-run
+only the fine-tuning stage for various pruning thresholds $
+  \tau \in \{\tfrac{k}2\colon k=-8\cdots+8\}
+$. The performance-compression curves depicted in figure~\ref{fig:hist__and__threshold__tradeoff}
+are parameterized by decreasing $\tau$ from left to right, since models are not re-compressed
+which makes $\tau$ monotonically affect the compression rate. From \eqref{eq:elbo_with_coef}
+and the relative positions of the curves it can be concluded that $C$ has a much more
+substantial impact on the compression profile of each method, than the choice of the
+pruning threshold.
+% coarser grid than in top plot in order not to wait for 20 compute days, but 9.5 on
+% 4 x Geforce 1080Ti, 256 Gb, core-i7 machine, running 4*2 experiments in parallel
+
+% takeaway: fine tune seems to improve performance for highly compressed models, but
+% within a limit. Worth a try for moderately compressed models, but willl must likely
+% overfit for undercompressed models. Varying $C$ in \eqref{eq:elbo_with_coef} affects
+% sparsity more strongly, than varying $\tau$. But this is only observational.
+
+% why is there such a dramamtic difference in impact of ``fine-tune''?
+We provide the following interpretation of the apparent contrast in performance impact
+borne by fine-tuning between less than $\times50$ and higher than $\times100$ compression
+regimes in figure~\ref{fig:musicnet__trade-off}, also observed in sec.~\ref{sub:mnist_like_datasets}.
+%
+% * early stopping kick in at around 10-20 epoch
+% * performance peaks at 10-15 epoch and then gradually declines
+The value of $C$ in \eqref{eq:elbo_with_coef} is a good proxy for the ranking of the
+final compression rate since it directly affects the feedback from sparsifying prior.
+So, during the $50$ epoch allotted for ``sparsify'' stage, low $C$ prevents the sparsity
+inducing prior from pulling the posterior sufficiently away from the likelihood-maximizing
+parameters inherited from the ``pre-train'' stage. It is reasonable, therefore, to expect
+that for undercompressed models the fine-tuning stage acts essentially as a continuation
+of pre-training. And, since we have observed that longer training invariably deteriorates
+the validation performance, the ``fine-tune'' stage should lead to overfitting for small
+$C$.
+%
+Figure~\ref{fig:musicnet__early_stopping} shows that the models, which have been sparsified
+with $C$ less than $\tfrac1{400}$, have less than $50\times$ compression and need considerably
+less training epochs before early stopping terminates the process.
+
+\begin{figure}[!t]
+  \centering
+  \includegraphics[width=\columnwidth]{figure__fine-tune_fx__early.pdf}
   \caption{%
@@
 
-% why is there such a dramamtic difference in impact of ``fine-tune''?
-We provide the following interpretation of the apparent difference in performance impact
-of the ``fine-tune'' stage between less than $50\times$ and higher than $100\times$ compression
-regimes in figure~\ref{fig:musicnet__trade-off}, also observed in sec.~\ref{sub:mnist_like_datasets}.
-%
-% * early stopping kick in at around 10-20 epoch
-% * performance peaks at 10-15 epoch and then gradually declines
-The value of $C$ in \eqref{eq:elbo_with_coef} is a good proxy for the ranking of the final
-compression rate since it directly affects the feedback from sparsifying prior. So, with
-low $C$ models get less compressed during $50$ epoch allotted for ``sparsify'' stage, which
-appears to be insufficient to move model away from the parameters after the dense stage.
-It is reasonable therefore to expect that for undercompressed models the fine-tuning stage
-acts essentially as a continuation of the pre-training stage. Since we have observed that
-longer training invariably deteriorates the validation performance, the ``fine-tune'' stage
-leads to overfitting. Figure~\ref{fig:musicnet__early_stopping}, which shows that the models,
-which have been sparsified with $C$ less than $\tfrac1{400}$ and have $50\times$ compression,
-need considerably less training epochs before early stopping terminates the process.
-
-% testing the fx of the threshold
-\begin{figure}[!t]
-  \centering
-  \includegraphics[width=1\columnwidth]{figure__musicnet__threshold__C__DeepConvNet.pdf}
-  \caption{%
-    Effects of finetunig on performance-compression curves parametrized by $
-      \tau\in \{\tfrac{k}2\colon k=-8..+8 \}
-    $ for $
-      C\in \{\tfrac1{20}, \frac1{200}\}
-    $ in \eqref{eq:elbo_with_coef} during sparsification (sec.~\ref{sub:staging}).
-  }
-  \label{fig:hist__and__threshold__tradeoff}
-\end{figure}
-
-% effects of extra training epochs and the impact of tau
-We take the models from experiments with $C \in \{\tfrac1{20}, \frac1{200}\}$ and plot
-the compression and performance metrics before fine-tuning for various threshold levels
-on figure~\ref{fig:hist__and__threshold__tradeoff} (top). From \eqref{eq:elbo_with_coef} and
-the relative positions of the compression curves it can be concluded that $C$ has much
-more substantial impact on the sparsity and performance, than the choice of $\tau$.
-Furthermore, for $\tau > 0$ the performance quickly saturates while compression creeps
-downwards.
-%
-The bottom plot in figure~\ref{fig:hist__and__threshold__tradeoff} shows the effect of
-the ``fine-tune'' stage: for $\tau \leq -1$ it improves the test performance, while leaving
-it mostly unaffected for positive $\tau$. We attrbute this behaviour to regularization
-effect of high compression rate, which limits the capacity for overfitting by significantly
-reducing the excess degrees of freedom.
-% coarser grid than in top plot in order not to wait for 20 compute days, but 9.5 on
-% 4 x Geforce 1080Ti, 256 Gb, core-i7 machine, running 4*2 experiments in parallel
-
-% takeaway: fine tune seems to improve performance for highly compressed models, but
-% within a limit. Worth a try for moderately compressed models, but willl must likely
-% overfit for undercompressed models. Varying $C$ in \eqref{eq:elbo_with_coef} affects
-% sparsity more strongly, than varying $\tau$. But this is only observational.
-
 % subsection musicnet (end)
@@
 
-In this study we have extended Variational Dropout methods of \citet{kingma_variational_2015},
-\citet{molchanov_variational_2017} and \citet{kharitonov_variational_2018} to $\cplx$-valued
-Bayesian networks. To validate the proposed technique we have conducted a large numerical
-study of complex-valued networks with simple architectures in image recognition tasks to
-assess the feasible performance-compression trade-off. At the cost of marginally lower performance,
-we have achieved $50-100\times$ compression of the state-of-the-art deep $\cplx$-valued network
-of \citet{trabelsi_deep_2018} on the MusicNet.
-
-The results of this study have direct implications for real-time signal processing with
-embedded deep learning applications both in terms of lower storage requirements and higher
-throughput stemming from fewer floating-point multiplications, despite higher arithmetic
+In this study we have presented $\cplx$-valued variational sparsification methods to
+the ever growing set of tools for learning deep $\cplx$-valued neural networks. To
+validate these methods we have carried out a large numerical study of $\cplx$VNN with
+simple architectures to assess the feasible performance-compression trade-off, and
+studied compression of two deep convolutional $\cplx$VNN. At the cost of marginally
+lower performance, we have achieved $\times50$-$\times100$ compression of the deep
+$\cplx$VNN of \citet{trabelsi_deep_2018} on the MusicNet.
+% CVNN capacity grows by \sqrt{2}, compute grows by 2 % RVNN caption by 2 compute by 2.
+
+Experimental results show that $\cplx$-VD (sec.~\ref{ssub:vd_prior}) and $\cplx$-ARD
+(sec.~\ref{ssub:ard_prior}) exhibit trade-off profiles matching their $\real$-valued
+counterparts. This makes us confident that the overall conclusion of \citet{gale_state_2019}
+is applicable to $\cplx$VNN and the proposed $\cplx$-valued variational sparsification
+methods.
+% L0 and dropout work in the low-to-mid sparsity range, variational dropout consistently
+% ranked behind L0 on Transformer, and was bested by magnitude pruning for sparsity
+% levels of 80\% and up. Variational dropout consistently produces models on-par or better
+% than magnitude pruning on ResNet-50, and l0 fails to produce sparse models at all.
+Furthermore our findings indicate that between each other under similar circumstances
+the methods yield comparable compression and performance results, which echoes earlier
+results by \citet{kharitonov_variational_2018}.
+
+This study has direct implications for embedded deep learning applications
+both in terms of lower storage requirements and higher throughput stemming from fewer
+floating point multiplications due to sparsity, despite somewhat higher arithmetic
 complexity of $\cplx$-valued networks.
@@
 % section conclusion (end)
+
+\section*{Software and Data} % (fold)
+\label{sec:software_and_data}
+
+% we strongly encourage the publication of software and data with the camera-ready version
+% of the paper whenever appropriate. This can be done by including a URL in the copy.
+% do not include URLs that reveal your institution or identity in your submission for review
+% * provide an anonymous URL or upload the material as ``Supplementary Material'' into the CMT
+
+The source code for a package based on PyTorch \citep{paszke_pytorch_2019}, which
+implements $\cplx$-valued Sparse Variational Dropout and ARD layers and provides other
+basic layers for $\cplx$VNN is available at
+\url{https://github.com/ivannz/cplxmodule}.
+%
+The source code for the experiments and the figures in this study is available at
+\url{https://github.com/ivannz/complex_paper/tree/v2020.6}.
+
+% section* software_and_data (end)
+
+% Acknowledgements should only appear in the accepted version.
+\section*{Acknowledgements} % (fold)
+\label{sec:acknowledgements}
+
+% Do not include acknowledgements in the initial version of the paper submitted for blind review.
+
+% the final camera-ready version can (and probably should) include acknowledgements
+% Typically, this will include thanks to reviewers who gave useful comments, to colleagues
+% who contributed to the ideas, and to funding agencies and corporate sponsors that provided
+% financial support.
+We would like to thank the anonymous reviewers, Evgenii Egorov, Ruslan Kostoev (ADASE)
+and Danila Doroshin (Huawei) for their useful comments.
+% We thank Skoltech CDISE HPC Zhores cluster staff for providing computational infrastructure.
+The authors acknowledge the use of the Skoltech CDISE HPC cluster ``Zhores'' for obtaining
+the results presented in this paper.
+
+% section* acknowledgements (end)
 
@@
 
-\section{Gradient of the KL-divergence in $\real$ case} % (fold)
-\label{sec:real-chisq-grad}  % gradient_of_the_kl_divergence_in_R_case
-
-In this section we derive the exact gradient of \eqref{eq:improper-kl-div-real}. Even
-though, ultimately, the divergence involves a hypergeometric function, and its gradient
-requires evaluating the Gauss error function, the analysis provides independent verification
-of the approximation, proposed by \citet{molchanov_variational_2017}. The logic of the
-derivation follows \citet{lapidoth_capacity_2003}.
-% \citet{pav_moments_2015} correctly notice that \cite[p. 2466]{lapidoth_capacity_2003} has a missing $\log{2}$ term.
-
-For $(z_i)_{i=1}^m \sim \mathcal{N}(0, 1)$ iid and $
-  (\mu_i)_{i=1}^m \in \mathbb{R}
-$, the random variable $W = \sum_i (\mu_i + z_i)^2$ is noncentral $\chi^2$ with shape $m$
-and noncentrality parameter $\lambda = \sum_i \mu_i^2$, i.e. $W\sim \chi^2_m(\lambda)$.
-Its density is
-\begin{equation}  \label{eq:nonchisq-density}
-  f_W(x)
-    % = e^{- \tfrac\lambda2} \sum_{n \geq 0} \tfrac{\bigl(\tfrac\lambda2\bigr)^n}{n!}
-    %   \tfrac{
-    %     x^{n + \tfrac{m}2 - 1} e^{-\tfrac{x}2}
-    %   }{
-    %     2^{n + \tfrac{m}2} \Gamma(n + \tfrac{m}2)
-    %   }
-    % = e^{- \tfrac\lambda2} \sum_{n \geq 0} \tfrac{\bigl(\tfrac\lambda2\bigr)^n}{n!}
-    %     \tfrac{
-    %         \bigl(\tfrac{x}2\bigr)^{n + \tfrac{m}2 - 1} e^{-\tfrac{x}2}
-    %     }{
-    %         2 \Gamma(n + \tfrac{m}2)
-    %     }
-    = \frac12 e^{- \tfrac{x + \lambda}2} \bigl(\tfrac{x}2\bigr)^{\tfrac{m}2 - 1}
-      \sum_{n \geq 0} \frac{
-        \bigl(\tfrac{x \lambda}4\bigr)^n
-      }{
-        n! \Gamma(n + \tfrac{m}2)
-      }
-    % = \frac12 e^{- \tfrac{x + \lambda}2}
-    % \bigl(\tfrac{x}\lambda\bigr)^{\tfrac{m}4 - \tfrac12}
-    % \bigl(\tfrac{x \lambda}4\bigr)^{\tfrac{m}4 - \tfrac12}
-    % \sum_{n \geq 0} \tfrac{
-    %         \bigl(\tfrac{x \lambda}4\bigr)^n
-    %     }{
-    %         n! \Gamma(n + \tfrac{m}2)
-    %     }
-    % = \frac12 e^{- \tfrac{x + \lambda}2}
-    % \bigl(\tfrac{x}\lambda\bigr)^{\tfrac{m}4 - \tfrac12}
-    % \bigl(\tfrac{\sqrt{x \lambda}}2\bigr)^{\tfrac{m}2 - 1}
-    % \sum_{n \geq 0} \tfrac{
-    %         \bigl(\tfrac{x \lambda}4\bigr)^n
-    %     }{
-    %         n! \Gamma(n + \tfrac{m}2)
-    %     }
-    % = \frac12 e^{- \tfrac{x + \lambda}2}
-    % \bigl(\tfrac{x}\lambda\bigr)^{\tfrac{m - 2}4}
-    % I_{\bigl(\tfrac{m}2 - 1\bigr)}(\sqrt{x \lambda})
-    \,.
-\end{equation}
-% where $I_k$ is the modified Bessel function of the first kind
-% $$
-% I_k(s)
-%   = \Bigl(\frac{s}2\Bigr)^k
-%       \sum_{n \geq 0} \tfrac{
-%           \bigl( \tfrac{s}2 \bigr)^{2n}
-%       }{n! \Gamma(n + k + 1)}
-%   \,. $$
-By integrating the power series \eqref{eq:nonchisq-density} with substitution $x \to 2u$,
-the expectation $
-  \mathbb{E}_{W\sim \chi^2_m(\lambda)} \log W
-$, needed in \eqref{eq:improper-kl-div-real}, equals
-\begin{multline}  \label{eq:exp-log-chisq-proof}
-    % &= \int_0^\infty f_W(x) \log x dx
-    % \notag \\
-    % &\frac12 e^{- \tfrac\lambda2}
-    % \int_0^\infty \sum_{n \geq 0} \biggl(
-    %     \frac{
-    %       e^{- \tfrac{x}2} \bigl(\tfrac\lambda2\bigr)^n
-    %     }{
-    %       n! \Gamma(n + \tfrac{m}2)
-    %     }
-    %     \bigl(\tfrac{x}2\bigr)^{n + \tfrac{m}2 - 1}
-    % \biggr) \log{(x)} dx
-    % = [\text{ absolute summability and Fubini, or any other conv. thm for integrals of nonnegative integrals}]
-    % = e^{- \tfrac\lambda2} \sum_{n \geq 0}
-    %     \tfrac{\bigl(\tfrac\lambda2\bigr)^n}{n!}
-    %     \tfrac1{\Gamma(n + \tfrac{m}2)}
-    % \int_0^\infty
-    %     e^{- \tfrac{x}2} \bigl(\tfrac{x}2\bigr)^{n + \tfrac{m}2 - 1}
-    %     (\log2 + \log \tfrac{x}2) \tfrac{dx}2
-    % = [u = \tfrac{x}2]
-    % \notag \\
-    e^{- \tfrac\lambda2} \sum_{n \geq 0}
-        \frac{\bigl(\tfrac\lambda2\bigr)^n}{
-          n! \Gamma(n + \tfrac{m}2)
-        }
-    \int_0^\infty
-        e^{- u} u^{n + \tfrac{m}2 - 1}
-        \log{(2 u)} du
-    % = [\text{definitions:} \Gamma, \psi]
-    % = e^{- \tfrac\lambda2} \sum_{n \geq 0}
-    %     \tfrac{\bigl(\tfrac\lambda2\bigr)^n}{n!}
-    % (\psi(n + \tfrac{m}2) + \log2)
-    % \notag
-    \\
-    = \log{2}
-    + e^{- \tfrac\lambda2} \sum_{n \geq 0}
-        \frac{\bigl(\tfrac\lambda2\bigr)^n}{n!}
-        \psi(n + \tfrac{m}2)
-    \,,
-\end{multline}
-where $\psi(x)$ is the digamma function, i.e.
-\begin{equation}  \label{eq:digamma}
-  \psi(x)
-    % = \frac{d}{dx} \log \Gamma(x)
-    = \frac1{\Gamma(x)}
-      \int_0^\infty
-        u^{x-1} e^{-u} \log{u}
-      \, du
-    \,,
-\end{equation}
-which satisfies $
-  \psi(z+1) = \psi(z) + \tfrac1z
-$, $
-  \psi(x)\leq \log x - \tfrac1{2x}
-$, and $
-  \psi(\tfrac12) = -\gamma - 2\log 2
-$ ($\gamma$ is Euler's constant). If we put
-\begin{equation}  \label{eq:g-m-series}
-  g_m(x)
-    % alpha: e^{-x} \sum_{n=0}^{\infty} \frac{x^n}{n!} \psi(n + m / 2)
-    % = e^{-x} \sum_{n \geq 0} \frac{x^n}{n! \Gamma(n + \tfrac{m}2)}
-    %     \int_0^\infty e^{-t} t^{n + \tfrac{m}2-1} \log{t} dt
-    = e^{-x} \sum_{n \geq 0} \frac{x^n}{n!} \psi(n + \tfrac{m}2)
-    \,,
-\end{equation}
-then the desired expectation in \eqref{eq:improper-kl-div-real} equals $
-  \log{2} + g_1(\tfrac1{2\alpha})
-$.
-%
-% We can differentiate the series in $g_m(x)$, since the sum converges on $\mathbb{R}$.
-% Indeed, it is a power series featuring nonnegative coefficients, which is dominated by $
-%   \sum_{n \geq 1} \tfrac{x^n}{n!} \log{(n+\tfrac{m}2)}
-% $. By the ratio test, the dominating
-% series has infinite radius:
-% $$
-% \lim_{n\to\infty}
-%   \biggl\lvert
-%     \frac{
-%       n! x^{n+1} \log{(n + 1 + \tfrac{m}2)}
-%     }{
-%       x^n \log{(n + \tfrac{m}2)} (n+1)!
-%     }
-%   \biggr\rvert
-%   = \lim_{n\to\infty}
-%     \lvert x \rvert 
-%     \biggl\lvert
-%       \frac{
-%         \log{(n + 1 + \tfrac{m}2)}
-%       }{
-%         \log{(n + \tfrac{m}2)} (n+1)
-%       }
-%     \biggr\rvert
-%   % = \lim_{n\to\infty}
-%   %   \lvert x \rvert 
-%   %   \biggl\lvert
-%   %     \frac{
-%   %       n + \tfrac{m}2
-%   %     }{
-%   %       (n + 1 + \tfrac{m}2)((n+1) + (n + \tfrac{m}2) \log{(n + \tfrac{m}2)})
-%   %     }
-%   %   \biggr\rvert
-%   = 0 < 1
-%   \,, $$
-% since
-% $$
-% \frac{\log{(x + a + 1)}}{x \log{(x + a)}}
-%   \sim \frac{\log{(x+1)}}{(x-a) \log{x}}
-%   \sim \frac{\log{(x+1)}}{x \log{x}}
-%   \sim \frac{\tfrac1{(x+1)}}{1 + \log{x}}
-%   \to 0
-%   \,. $$
-% A theorem from calculus states, that the formal series derivative (integral)
-% coincides with the derivative (integral) of the function, corresponding to
-% the power series (everywhere on the convergence region). And the convergence
-% regions of derivative (integral) coincide with the region of the original
-% power series.
-%
-Formally differentiating the convergent power series within $g_m$ yields
-\begin{equation}  \label{eq:g-m-deriv}
-  \frac{d}{d x} g_m(x)
-    % = e^{-x} \sum_{n\geq 1} \frac{x^{n-1}}{(n-1)!} \psi(n + \tfrac{m}2) - g_m(x)
-    % = e^{-x} \sum_{n\geq 0} \frac{x^n}{n!} \psi(n + \tfrac{m}2 + 1) - g_m(x)
-    % = e^{-x} \sum_{n\geq 0} \frac{x^n}{n!} (
-    %     \psi(n + \tfrac{m}2 + 1) - \psi(n + \tfrac{m}2)
-    % )
-    % = e^{-x} \sum_{n\geq 0} \frac{x^n}{n!} \tfrac1{n + \tfrac{m}2}
-    % = e^{-x} \sum_{n\geq 0} \frac{x^n}{n!} (n + \tfrac{m}2)^{-1}
-    = x^{-\tfrac{m}2} e^{-x} \sum_{n\geq 0}
-        \frac{x^{n + \tfrac{m}2}}{n!} (n + \tfrac{m}2)^{-1}
-    \,.
-\end{equation}
-From $
-    e^t  = \sum_{n\geq 0} \tfrac{t^n}{n!}
-$ on $\mathbb{R}$ and $
-  \tfrac{x^\alpha}{\alpha}
-    = \int_0^x t^{\alpha-1} dt
-$ for $\alpha\neq 0$ we get
-% by the monotone convergence theorem on ([0, x], \mathcal{B}([0, x]), dx)
-\begin{align}  \label{eq:g-m-deriv-int-2}
-  \eqref{eq:g-m-deriv}
-    % = x^{-\tfrac{m}2} e^{-x} \sum_{n\geq 0}
-    %     \frac{x^{n + \tfrac{m}2}}{n!} (n + \tfrac{m}2)^{-1}
-    &= x^{-\tfrac{m}2} e^{-x} \sum_{n\geq 0}
-        \frac1{n!} \int_0^x t^{n + \tfrac{m}2 - 1} dt
-    % = x^{-\tfrac{m}2} e^{-x}
-    %     \int_0^x t^{\tfrac{m}2 - 1} \sum_{n\geq 0} \frac{t^n}{n!} dt
-    \notag \\
-    &= x^{-\tfrac{m}2} e^{-x}
-        \int_0^x t^{\tfrac{m}2 - 1} e^t dt
-    \,.
-\end{align}
-Substitution $u^2 = t$ on $[0, \infty]$ with $2u du = dt$ yields
-\begin{equation}  \label{eq:g-m-deriv-int-3}
-  \frac{d}{d x} g_m(x)
-    % = x^{-\tfrac{m}2} e^{-x}
-    %     \int_0^x t^{\tfrac{m}2 - 1} e^t dt
-    = 2 x^{-\tfrac{m}2} e^{-x}
-        \int_0^{\sqrt{x}} u^{m - 1} e^{u^2} du
-    \,.
-\end{equation}
-In particular, the derivative of \eqref{eq:g-m-series} for $m=1$ is
-\begin{equation}  \label{eq:g-m-deriv-one}
-  \frac{d}{d x} g_1(x)
-    = 2 \frac{F(\sqrt{x})}{\sqrt{x}}
-    \,,
-\end{equation}
-using Dawson's integral $
-  F
-  % \colon \mathbb{R} \to \mathbb{R}
-  \colon x \mapsto e^{-x^2} \int_0^x e^{u^2} du
-$.
-%
-Hence, the derivative of the expectation in \eqref{eq:improper-kl-div-real} with respect
-to $\alpha$ is
-$$
-\frac{d}{d \alpha} g_1(\tfrac1{2\alpha})
-  = -\frac1{2 \alpha^2} g_1'(\tfrac1{2\alpha})
-  % = -\frac1{2 \alpha^2} 2 \tfrac{F(\sqrt{\tfrac1{2\alpha}})}{\sqrt{\tfrac1{2\alpha}}}
-  % = -\frac1{2 \alpha^2} 2 \tfrac{F(\tfrac1{\sqrt{2\alpha}})}{\tfrac1{\sqrt{2\alpha}}}
-  = -\frac1{\alpha} \sqrt{\frac2{\alpha}} F(\tfrac1{\sqrt{2\alpha}})
-  \,. $$
-Finally, since $\alpha$ is nonnegative, it is typically parameterized via its logarithm.
-The gradient of \eqref{eq:improper-kl-div-real} w.r.t $\log \alpha$ is
-\begin{equation}  \label{eq:real-kl-div-deriv-log}
-  \frac{d \eqref{eq:improper-kl-div-real}}{d\log \alpha}
-  % \frac{d}{d\log \alpha}
-  %   \frac12 \mathbb{E}_{z \sim \mathcal{N}(0,1)}
-  %     \log \lvert z + \tfrac1{\sqrt{\alpha}} \rvert^2
-    % = \frac12 \frac{d\alpha}{d\log \alpha}
-    %   \frac{d}{d\alpha} \bigl(\mathbb{E}\cdots \bigr)
-    % = - \frac\alpha2 \tfrac1{\alpha}
-    %   \sqrt{\tfrac2{\alpha}} F(\tfrac1{\sqrt{2\alpha}})
-    = - \frac1{\sqrt{2\alpha}} F\bigl(\tfrac1{\sqrt{2\alpha}}\bigr)
-    \,.
-\end{equation}
-
-We compute the Monte-Carlo estimator of \eqref{eq:improper-kl-div-real} on a sample of $10^7$
-draws over an equally spaced grid of $\log \alpha$ in $[-12, +12]$ of size $4096$. The
-coefficients of the approximation, proposed by \citet{molchanov_variational_2017}, are
-within $1\%$ relative tolerance of the reported therein. An equivalent expression of the
-approximation is given in \eqref{eq:improper-kl-div-real-approx}.
-% see eq.~(14): flit overall sign, use $C = -k_1$, $1-\sigma(x) = \sigma(-x)$
-\begin{equation}  \label{eq:improper-kl-div-real-approx}
-  \eqref{eq:improper-kl-div-real}
-% - KL(\mathcal{N}(w \mid \mu, \alpha \mu^2) \|
-%     \tfrac1{\lvert w \rvert})
-%   \approx
-%     k_1 \sigma(k_2 + k_3 \log \alpha)
-%     + C \big\vert_{C = -k1}
-%     - \tfrac12 \log (1 + e^{-\log \alpha})
-  % = \tfrac12 \log \alpha
-  %   - \mathbb{E}_{\xi \sim \mathcal{N}(1, \alpha)}
-  %   \log{\lvert \xi \rvert} + C
-  \approx
-    \frac12 \log{\bigl(1 + e^{-\log \alpha}\bigr)}
-    + k_1 \sigma\bigl(- (k_2 + k_3 \log \alpha)\bigr)
-    % - k_1 \bigl(1 - \sigma(k_2 + k_3 \log \alpha)\bigr)
-  \,,
-\end{equation}
-% in parctial implementations we suggest using softplus to numerically comptue the last
-% term, since it is typically implemented in a floating-point stable fashion.
-The numerically estimated derivative of the penalty term with respect to $\log \alpha$ using
-forward differences seems to be following \eqref{eq:real-kl-div-deriv-log} very closely (up to
-sampling error), see fig.~\ref{fig:molchanov-derivative-replica}. The derivative of
-\eqref{eq:improper-kl-div-real-approx} with respect to $\log \alpha$ appears to be very close
-to \eqref{eq:real-kl-div-deriv-log}. We compute a similar Monte-Carlo estimate for
-$\cplx$ variational dropout KL divergence term in \eqref{eq:c-vd-kl-div} with $\beta = 2$,
-fit the best approximation \eqref{eq:improper-kl-div-real-approx}, and compare the derivatives.
-
-\begin{figure}[!t]
-  \centering
-  \includegraphics[width=\columnwidth]{grad_log.pdf}
-  \caption{$\tfrac{d f(\alpha)}{d \log{\alpha}}$ of the approximation
-  \eqref{eq:improper-kl-div-real-approx}, MC estimate of \eqref{eq:improper-kl-div-real},
-  and the exact derivative using \eqref{eq:real-kl-div-deriv-log}.}
-  \label{fig:molchanov-derivative-replica}
-\end{figure}
-
-% section real-chisq-grad (end)
-
 \section{MNIST-like experiments} % (fold)
@@
 Each figure shows the compression-accuracy trade-off of a particular method and input
-features for \textit{SimpleConvModel} and \textit{TwoLayerDenseModel} models for all four
-of the studied datasets (described in the main text): EMNIST-Letters on the \textit{top-left},
-KMNIST -- \textit{top-right}, Fashion MNIST -- \textit{bottom-left}, and MNIST on the
-\textit{bottom-right}.
+features for \emph{SimpleConvModel} and \emph{TwoLayerDenseModel} models for all four
+of the studied datasets (described in the main text): EMNIST-Letters on the \emph{top-left},
+KMNIST -- \emph{top-right}, Fashion MNIST -- \emph{bottom-left}, and MNIST on the
+\emph{bottom-right}.
 %
@@
 \ref{fig:appendix__mnist-like__trade-off__ARD__raw}, and \ref{fig:appendix__mnist-like__trade-off__VD__raw}
-present $\real$ and $\cplx$ models with \textit{the same intermediate feature sizes}.
-
-We also report the trade-off comparison, when the argument by \citet{monning_evaluation_2018}
-for higher intrinsic capacity of $\cplx$-valued networks has been taken into account.
-%
+present $\real$ and $\cplx$ models with \emph{the same intermediate feature sizes}.
+
 We compare $\real$ networks against $\tfrac12 \cplx$ with half the number of parameters
@@
   \centering
-  \begin{subfigure}[b]{0.5\columnwidth}
+  \begin{subfigure}  % [b]{0.5\columnwidth}
     \centering
     % used in main text
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__emnist_letters__fft__-0.5.pdf}
+    \includegraphics[width=0.47\linewidth]{figure__mnist-like__trade-off/appendix__ARD__emnist_letters__fft__-0.5.pdf}
   \end{subfigure}%
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__kmnist__fft__-0.5.pdf}
+  \begin{subfigure}  % [b]{0.5\columnwidth}
+    \centering
+    \includegraphics[width=0.47\linewidth]{figure__mnist-like__trade-off/appendix__ARD__kmnist__fft__-0.5.pdf}
   \end{subfigure} \\ %
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__fashionmnist__fft__-0.5.pdf}
+  \begin{subfigure}  % [b]{0.5\columnwidth}
+    \centering
+    \includegraphics[width=0.47\linewidth]{figure__mnist-like__trade-off/appendix__ARD__fashionmnist__fft__-0.5.pdf}
   \end{subfigure}%
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__mnist__fft__-0.5.pdf}
+  \begin{subfigure}  % [b]{0.5\columnwidth}
+    \centering
+    \includegraphics[width=0.47\linewidth]{figure__mnist-like__trade-off/appendix__ARD__mnist__fft__-0.5.pdf}
   \end{subfigure}
@@
   \centering
-  \begin{subfigure}[b]{0.5\columnwidth}
+  \begin{subfigure}  % [b]{0.5\columnwidth}
     \centering
     % used in main text
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__emnist_letters__fft__-0.5.pdf}
+    \includegraphics[width=0.47\linewidth]{figure__mnist-like__trade-off/appendix__VD__emnist_letters__fft__-0.5.pdf}
   \end{subfigure}%
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__kmnist__fft__-0.5.pdf}
+  \begin{subfigure}  % [b]{0.5\columnwidth}
+    \centering
+    \includegraphics[width=0.47\linewidth]{figure__mnist-like__trade-off/appendix__VD__kmnist__fft__-0.5.pdf}
   \end{subfigure} \\ %
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__fashionmnist__fft__-0.5.pdf}
+  \begin{subfigure}  % [b]{0.5\columnwidth}
+    \centering
+    \includegraphics[width=0.47\linewidth]{figure__mnist-like__trade-off/appendix__VD__fashionmnist__fft__-0.5.pdf}
   \end{subfigure}%
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__mnist__fft__-0.5.pdf}
+  \begin{subfigure}  % [b]{0.5\columnwidth}
+    \centering
+    \includegraphics[width=0.47\linewidth]{figure__mnist-like__trade-off/appendix__VD__mnist__fft__-0.5.pdf}
   \end{subfigure}
@@
   \centering
-  \begin{subfigure}[b]{0.5\columnwidth}
+  \begin{subfigure}  % [b]{0.5\columnwidth}
     \centering
     % used in main text
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__emnist_letters__raw__-0.5.pdf}
+    \includegraphics[width=0.47\linewidth]{figure__mnist-like__trade-off/appendix__ARD__emnist_letters__raw__-0.5.pdf}
   \end{subfigure}%
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__kmnist__raw__-0.5.pdf}
+  \begin{subfigure}  % [b]{0.5\columnwidth}
+    \centering
+    \includegraphics[width=0.47\linewidth]{figure__mnist-like__trade-off/appendix__ARD__kmnist__raw__-0.5.pdf}
   \end{subfigure} \\%
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__fashionmnist__raw__-0.5.pdf}
+  \begin{subfigure}  % [b]{0.5\columnwidth}
+    \centering
+    \includegraphics[width=0.47\linewidth]{figure__mnist-like__trade-off/appendix__ARD__fashionmnist__raw__-0.5.pdf}
   \end{subfigure}%
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__mnist__raw__-0.5.pdf}
+  \begin{subfigure}  % [b]{0.5\columnwidth}
+    \centering
+    \includegraphics[width=0.47\linewidth]{figure__mnist-like__trade-off/appendix__ARD__mnist__raw__-0.5.pdf}
   \end{subfigure}
@@
   \centering
-  \begin{subfigure}[b]{0.5\columnwidth}
+  \begin{subfigure}  % [b]{0.5\columnwidth}
     \centering
     % used in main text
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__emnist_letters__raw__-0.5.pdf}
+    \includegraphics[width=0.47\linewidth]{figure__mnist-like__trade-off/appendix__VD__emnist_letters__raw__-0.5.pdf}
   \end{subfigure}%
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__kmnist__raw__-0.5.pdf}
+  \begin{subfigure}  % [b]{0.5\columnwidth}
+    \centering
+    \includegraphics[width=0.47\linewidth]{figure__mnist-like__trade-off/appendix__VD__kmnist__raw__-0.5.pdf}
   \end{subfigure} \\%
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__fashionmnist__raw__-0.5.pdf}
+  \begin{subfigure}  % [b]{0.5\columnwidth}
+    \centering
+    \includegraphics[width=0.47\linewidth]{figure__mnist-like__trade-off/appendix__VD__fashionmnist__raw__-0.5.pdf}
   \end{subfigure}%
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__mnist__raw__-0.5.pdf}
+  \begin{subfigure}  % [b]{0.5\columnwidth}
+    \centering
+    \includegraphics[width=0.47\linewidth]{figure__mnist-like__trade-off/appendix__VD__mnist__raw__-0.5.pdf}
   \end{subfigure}
@@
   \centering
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__emnist_letters__fft__-0.5.pdf}
+  \begin{subfigure}  % [b]{0.5\columnwidth}
+    \centering
+    \includegraphics[width=0.47\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__emnist_letters__fft__-0.5.pdf}
   \end{subfigure}%
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__kmnist__fft__-0.5.pdf}
+  \begin{subfigure}  % [b]{0.5\columnwidth}
+    \centering
+    \includegraphics[width=0.47\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__kmnist__fft__-0.5.pdf}
   \end{subfigure} \\ %
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__fashionmnist__fft__-0.5.pdf}
+  \begin{subfigure}  % [b]{0.5\columnwidth}
+    \centering
+    \includegraphics[width=0.47\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__fashionmnist__fft__-0.5.pdf}
   \end{subfigure}%
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__mnist__fft__-0.5.pdf}
+  \begin{subfigure}  % [b]{0.5\columnwidth}
+    \centering
+    \includegraphics[width=0.47\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__mnist__fft__-0.5.pdf}
   \end{subfigure}
@@
   \centering
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__emnist_letters__fft__-0.5.pdf}
+  \begin{subfigure}  % [b]{0.5\columnwidth}
+    \centering
+    \includegraphics[width=0.47\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__emnist_letters__fft__-0.5.pdf}
   \end{subfigure}%
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__kmnist__fft__-0.5.pdf}
+  \begin{subfigure}  % [b]{0.5\columnwidth}
+    \centering
+    \includegraphics[width=0.47\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__kmnist__fft__-0.5.pdf}
   \end{subfigure} \\ %
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__fashionmnist__fft__-0.5.pdf}
+  \begin{subfigure}  % [b]{0.5\columnwidth}
+    \centering
+    \includegraphics[width=0.47\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__fashionmnist__fft__-0.5.pdf}
   \end{subfigure}%
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__mnist__fft__-0.5.pdf}
+  \begin{subfigure}  % [b]{0.5\columnwidth}
+    \centering
+    \includegraphics[width=0.47\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__mnist__fft__-0.5.pdf}
   \end{subfigure}
@@
   \centering
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__emnist_letters__raw__-0.5.pdf}
+  \begin{subfigure}  % [b]{0.5\columnwidth}
+    \centering
+    \includegraphics[width=0.47\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__emnist_letters__raw__-0.5.pdf}
   \end{subfigure}%
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__kmnist__raw__-0.5.pdf}
+  \begin{subfigure}  % [b]{0.5\columnwidth}
+    \centering
+    \includegraphics[width=0.47\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__kmnist__raw__-0.5.pdf}
   \end{subfigure} \\%
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__fashionmnist__raw__-0.5.pdf}
+  \begin{subfigure}  % [b]{0.5\columnwidth}
+    \centering
+    \includegraphics[width=0.47\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__fashionmnist__raw__-0.5.pdf}
   \end{subfigure}%
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__mnist__raw__-0.5.pdf}
+  \begin{subfigure}  % [b]{0.5\columnwidth}
+    \centering
+    \includegraphics[width=0.47\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__mnist__raw__-0.5.pdf}
   \end{subfigure}
@@
   \centering
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__emnist_letters__raw__-0.5.pdf}
+  \begin{subfigure}  % [b]{0.5\columnwidth}
+    \centering
+    \includegraphics[width=0.47\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__emnist_letters__raw__-0.5.pdf}
   \end{subfigure}%
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__kmnist__raw__-0.5.pdf}
+  \begin{subfigure}  % [b]{0.5\columnwidth}
+    \centering
+    \includegraphics[width=0.47\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__kmnist__raw__-0.5.pdf}
   \end{subfigure} \\%
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__fashionmnist__raw__-0.5.pdf}
+  \begin{subfigure}  % [b]{0.5\columnwidth}
+    \centering
+    \includegraphics[width=0.47\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__fashionmnist__raw__-0.5.pdf}
   \end{subfigure}%
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__mnist__raw__-0.5.pdf}
+  \begin{subfigure}  % [b]{0.5\columnwidth}
+    \centering
+    \includegraphics[width=0.47\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__mnist__raw__-0.5.pdf}
   \end{subfigure}
@@
 
-\begin{figure}[b]
-  \centering
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/legacy__VD__emnist_letters__fft__-0.5.pdf}
-  \end{subfigure}%
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/legacy__VD__kmnist__fft__-0.5.pdf}
-  \end{subfigure} \\%
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/legacy__VD__fashionmnist__fft__-0.5.pdf}
-  \end{subfigure}%
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/legacy__VD__mnist__fft__-0.5.pdf}
-  \end{subfigure}
-  \caption{%
-    The trade-off of VD method for $\real$ and $\cplx$ models using Fourier features (main text).
-  }
-  \label{fig:paper__mnist-like__trade-off__VD__fft}
-\end{figure}
-
-\begin{figure}[b]
-  \centering
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/legacy__VD__emnist_letters__raw__-0.5.pdf}
-  \end{subfigure}%
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/legacy__VD__kmnist__raw__-0.5.pdf}
-  \end{subfigure} \\%
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/legacy__VD__fashionmnist__raw__-0.5.pdf}
-  \end{subfigure}%
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/legacy__VD__mnist__raw__-0.5.pdf}
-  \end{subfigure}
-  \caption{%
-    The trade-off of VD method for $\real$ and $\cplx$ models using raw features (main text).
-  }
-  \label{fig:paper__mnist-like__trade-off__VD__raw}
-\end{figure}
-
 % \clearpage
@@
 
+% Why does this warrant an extra section in the appendix?
+In this section we show \eqref{eq:cplx-gauss-trick}.
+
 %notation
-By $e_i$ we denote the $i$-th real unit vector of dimensionality \textit{conforming} to the
-matrix-vector expression it is used in. Let $\vec{M}$ denote \textit{row-major} flattening
-of $M$ into a vector, i.e. in lexicographic order of its indices. $\diag{(\cdot)}$ embeds
-$\cplx^n$ into $n\times n$ diagonal matrices, and $\otimes$ denotes the Kronecker product,
-for which we note the following identities $
-  \vec{P Q R} = (P \otimes R^\top) \vec{Q}
+By $e_i\in \real \hookrightarrow \cplx$ we denote the $i$-th unit vector of dimensionality
+\emph{conforming} to the matrix-vector expression it is used in, $[M]$ denotes \emph{row-major}
+flattening of a matrix $M$ into a vector, i.e. in lexicographic order of its indices.
+Furthermore $\diag{(\cdot)}$ embeds vectors into matrices with zeros everywhere except
+the diagonal, and $\otimes$ is the Kronecker product, for which we note the following
+identities $
+  [P Q R] = (P \otimes R^\top) [Q]
+$, $
+  (P \otimes Q)^\top = (P^\top \otimes Q^\top)
 $, and $
@@
 
-If we assume a mean field $\cplx$-Gaussian approximate posterior for $
+If we assume a factorized $\cplx$-Gaussian approximation \eqref{eq:c-gauss-vi-general}
+for $
   W \in \cplx^{n\times m}
-$, then
+$, then $[W]$ is $\cplx$-Gaussian vector with
 \begin{equation}  \label{eq:c-gauss-vi-general-vec}
-  \vec{W}
-    \sim \mathcal{N}^{\cplx}_{nm} \bigl(
-      \vec{\mu}, \diag{\vec{\Sigma}}, \diag{\vec{C}}
+  [W]
+    \sim \mathcal{C}\mathcal{N}_{nm} \bigl(
+      [\mu], \diag{[\Sigma]}, \diag{[C]}
     \bigr)
@@
 \end{equation}
-where mean, \textit{variance} and relation are given by matrices $
-  \mu, \Sigma, C \in \cplx^{n\times m}
-$ with $\Sigma_{ij} \geq 0$, and $
+where with $C_{ij} = \Sigma_{ij} \xi_{ij}$, $\Sigma_{ij} \geq 0$, and $
   \lvert C_{ij} \rvert^2 \leq \Sigma_{ij}
-$. For any $x \in \cplx^m$ and $b\in \cplx^n$ $
+$. Then for any $x \in \cplx^m$ and $b\in \cplx^n$ we have $
   y = W x + b
-    = (I_n \otimes x^\top) \vec{W} + b
+    = (I_n \otimes x^\top) [W] + b
 $, whence the covariance and relation matrices of $y$ are
-\begin{align}
-  (I \otimes x^\top) \diag{\vec{\Sigma}} (I \otimes x^\top)^{\hop}
-    % = \sum_{ij} (I \otimes x^\top) e_i \otimes e_j
-    %   \Sigma_{ij} (e_i \otimes e_j)^\top (I \otimes x^\top)^{\hop}
-    % = \sum_{ij} (e_i \otimes x^\top e_j)
-    %   \Sigma_{ij} (e_i \otimes x^\top e_j)^{\hop}
-    % = \sum_{ij} (e_i \otimes x_j) \Sigma_{ij} (e_i^\top \otimes \conj{x}_j)
-    & = \sum_{i=1}^n (e_i e_i^\top) \sum_{j=1}^m \Sigma_{ij} x_j \conj{x}_j
+\begin{eqnarray}
+  \bigl(I_n \otimes x^\top\bigr)
+    \diag{[\Sigma]}
+  \conj{\bigl(I_n \otimes x^\top\bigr)^\top}
+    &=& \sum_{ij}
+      \bigl(I_n \otimes x^\top\bigr)
+      \biggl(
+        (e_i \otimes e_j)
+          \Sigma_{ij}
+        (e_i \otimes e_j)^\top
+      \biggr)
+      \conj{\bigl(I_n \otimes x^\top\bigr)^\top}
+    \notag \\
+    &=& \sum_{ij}
+      \bigl(e_i \otimes x^\top e_j \bigr)
+        \Sigma_{ij}
+      \conj{\bigl(e_i \otimes x^\top e_j \bigr)^\top}
+    \notag \\
+    % &=& \sum_{ij}
+    %     \Sigma_{ij}
+    %   \bigl(e_i e_i^\top \otimes (x^\top e_j) \conj{(x^\top e_j)^\top} \bigr)
+    % \notag \\
+    % &=& \sum_{i} (e_i e_i^\top) \sum_{j}
+    %     \Sigma_{ij} (x^\top e_j)(e_j^\top \conj{x})
+    % \notag \\
+    &=&
+    %   \sum_{i} (e_i e_i^\top) \sum_{j}
+    %     \Sigma_{ij} (x_j \conj{x_j})
+    % =
+      \sum_{i=1}^n (e_i e_i^\top)
+        \biggl\{
+          \sum_{j=1}^m \Sigma_{ij} \lvert x_j \rvert^2
+        \biggr\}
     \,,  \label{eq:cn-gauss-lrt-cov} \\
-  (I \otimes x^\top) \diag{\vec{C}} (I \otimes x^\top)^\top
-    % = \sum_{ij} (e_i \otimes x_j) C_{ij} (e_i \otimes x_j)^\top
-    & = \sum_{i=1}^n (e_i e_i^\top) \sum_{j=1}^m C_{ij} x_j^2
+  \bigl(I_n \otimes x^\top\bigr)
+    \diag{[C]}
+  \bigl(I_n \otimes x^\top\bigr)^\top
+    &=& \sum_{ij}
+      \bigl(I_n \otimes x^\top\bigr)
+      \biggl(
+        (e_i \otimes e_j)
+          C_{ij}
+        (e_i \otimes e_j)^\top
+      \biggr)
+      \bigl(I_n \otimes x^\top\bigr)^\top
+    \notag \\
+    % &=& \sum_{ij}
+    %   \bigl(e_i \otimes x^\top e_j \bigr)
+    %     C_{ij}
+    %   \bigl(e_i \otimes x^\top e_j \bigr)^\top
+    % \notag \\
+    % &=& \sum_{ij}
+    %     C_{ij}
+    %   \bigl(e_i e_i^\top \otimes (x^\top e_j) (x^\top e_j)^\top \bigr)
+    % \notag \\
+    % &=& \sum_{i} (e_i e_i^\top) \sum_{j}
+    %     C_{ij} (x^\top e_j)(e_j^\top x)
+    % \notag \\
+    &=&
+    %   \sum_{i} (e_i e_i^\top) \sum_{j}
+    %     C_{ij} (x_j x_j)
+    % =
+      \sum_{i=1}^n (e_i e_i^\top)
+        \biggl\{
+          \sum_{j=1}^m C_{ij} x_j^2
+        \biggr\}
     \,.  \label{eq:cn-gauss-lrt-rel}
-\end{align}
-Since \eqref{eq:cn-gauss-lrt-cov} and \eqref{eq:cn-gauss-lrt-rel} are diagonal, $(y_i)_{i=1}^n$
-are independent whence \eqref{eq:cn-affine} implies
-\begin{equation}  \label{eq:cplx-gauss-trick-appendix}
-  y_i
-    \sim \mathcal{N}^{\cplx}
-      \bigl(
-        e_i^\top \mu x + b_i,
-        \, \sum_{j=1}^m \Sigma_{ij} \lvert x_j \rvert^2,
-        \, \sum_{j=1}^m C_{ij} x_j^2
-      \bigr)
-    \,.
-\end{equation}
-Hence \eqref{eq:cplx-gauss-trick} follows.
+\end{eqnarray}
+Since \eqref{eq:cn-gauss-lrt-cov} and \eqref{eq:cn-gauss-lrt-rel} are diagonal, the
+vector $y$ has independent univariate $\cplx$-Gaussian components, whence
+\eqref{eq:cplx-gauss-trick} follows.
 
@@
 Wirtinger ($\cplx\real$) calculus relies on the natural identification of $\cplx$ with $
-  \real \times \real
+  \real^2
 $, and regards $
   f\colon \cplx \to \cplx
-$ as an equivalent in algebraic sense function $F\colon \real^2 \to \cplx$ defined $
-  f(z) = f(u + jv) = F(u, v)
-$. Within this framework the differential of $f$ at $z = u + jv \in \cplx$ is
-$$
-df(z)
-  = \frac{\partial f}{\partial z} dz
-    + \frac{\partial f}{\partial \conj{z}} d\conj{z}
-   % = \frac12\bigl(
-   %    \frac{\partial}{\partial u}
-   %    - j \frac{\partial}{\partial v}
-   % \bigr) F (du - j dv)
-   % + \frac12\bigl(
-   %    \frac{\partial}{\partial u}
-   %    + j \frac{\partial}{\partial v}
-   % \bigr) F (du - j dv)
-   % = \frac12 \bigl(
-   %    \frac{\partial F}{\partial u} du - j \frac{\partial F}{\partial v} du
-   %    + j \frac{\partial F}{\partial u} dv + \frac{\partial F}{\partial v} dv
-   % \bigr)
-   % + \frac12 \bigl(
-   %    \frac{\partial F}{\partial u} du + j \frac{\partial F}{\partial v} du
-   %    - j \frac{\partial F}{\partial u} dv + \frac{\partial F}{\partial v} dv
-   % \bigr)
-   = \frac{\partial F}{\partial u} du
-     + \frac{\partial F}{\partial v} dv
-   = dF(u, v)
-  \,, $$
-with formally defined derivatives $
+$ as an algebraically equivalent function $F\colon \real^2 \to \cplx$ defined $
+  f(z) = f(u + \iu v) = F(u, v)
+$. It enables general treatment of functions of vector $\cplx$-argument that possess partial
+derivatives with respect to real and imaginary parts, yet are not required to satisfy
+Cauchy-Riemann conditions. In $\cplx\real$ calculus the complex argument $z$ and its
+conjugate $\conj{z}$ act as independent variables and $f(z)$ is treated as $f(z, \conj{z})$
+by way of geometric transformations $z = u + \iu v$ and $\conj{z} = u - \iu v$.
+
+Wirtinger partial derivative operators are formally defined as $
   \tfrac{\partial}{\partial z}
@@
       \tfrac{\partial}{\partial u}
-      - j \tfrac{\partial}{\partial v}
+      - \iu \tfrac{\partial}{\partial v}
     \bigr)
@@
       \tfrac{\partial}{\partial u}
-      + j \tfrac{\partial}{\partial v}
+      + \iu \tfrac{\partial}{\partial v}
     \bigr)
-$, and differentials $dz = du + j dv$ and $d\conj{z} = du - j dv$. This implies that the
-complex argument and its conjugate are treated as independent variables. Cauchy-Riemann
-conditions $
-  -j \tfrac{\partial F}{\partial v} = \tfrac{\partial F}{\partial u}
-$ can be expressed as $
-  \tfrac{\partial f}{\partial \conj{z}} = 0
-$ in this notation. Thus $\cplx\real$ calculus subsumes the usual $\cplx$-calculus on
-holomorphic functions, when $f(z)$, regarded as $f(z, \conj{z})$, is constant with respect
-to $\conj{z}$. The usual rules of calculus, like chain and product rules, follow directly
+$ and differentials are $dz = du + \iu dv$ and $d\conj{z} = du - \iu dv$. In this paradigm
+The usual rules of calculus, like chain and product rules, follow directly
 from the definition of the operators, e.g.
-$$
+\begin{equation}
     \frac{\partial (f\circ g)}{\partial z}
@@
     % = \nabla G \nabla F
-  \,. $$
+  \,.  \notag
+\end{equation}
+The total differential of $f$ at $z = u + \iu v \in \cplx$ is
+\begin{eqnarray}  
+df(z)
+  &=& \frac{\partial f}{\partial z} dz
+    + \frac{\partial f}{\partial \conj{z}} d\conj{z}
+  \notag \\
+  % &=& \frac12\biggl(
+  %    \frac{\partial F}{\partial u}
+  %    - \iu \frac{\partial F}{\partial v}
+  % \biggr) (du + \iu dv)
+  % + \frac12\biggl(
+  %    \frac{\partial F}{\partial u}
+  %    + \iu \frac{\partial F}{\partial v}
+  % \biggr) (du - \iu dv)
+  % \notag \\
+  &=& \frac12 \biggl(
+     \frac{\partial F}{\partial u} du
+     - \cancel{\iu \frac{\partial F}{\partial v} du}
+     + \cancel{\iu \frac{\partial F}{\partial u} dv}
+     + \frac{\partial F}{\partial v} dv
+  \biggr)
+  + \frac12 \biggl(
+     \frac{\partial F}{\partial u} du
+     + \cancel{\iu \frac{\partial F}{\partial v} du}
+     - \cancel{\iu \frac{\partial F}{\partial u} dv}
+     + \frac{\partial F}{\partial v} dv
+  \biggr)
+  \notag \\
+  % &=& \frac{\partial F}{\partial u} du
+  %    + \frac{\partial F}{\partial v} dv
+  % \notag \\
+  &=& dF(u, v)
+  \,,  \notag
+\end{eqnarray}
+% \begin{eqnarray}
+%   d(f\circ g)
+%     &=&
+%       \frac{\partial f(g(z))}{\partial g}
+%       dg
+%     + \frac{\partial f(g(z))}{\partial \conj{g}}
+%       d\conj{g}
+%     \notag \\
+%     &=&
+%       \frac{\partial f(g(z))}{\partial g}
+%       \biggl\{
+%         \frac{\partial g}{\partial z}
+%         dz
+%       + \frac{\partial g}{\partial \conj{z}}
+%         d\conj{z}
+%       \biggr\}
+%     + \frac{\partial f(g(z))}{\partial \conj{g}}
+%       \biggl\{
+%         \frac{\partial \conj{g}}{\partial z}
+%         dz
+%       + \frac{\partial \conj{g}}{\partial \conj{z}}
+%         d\conj{z}
+%       \biggr\}
+%     \notag \\
+%     &=&
+%         \frac{\partial f(g(z))}{\partial g} \frac{\partial g}{\partial z}
+%         dz
+%       + \frac{\partial f(g(z))}{\partial g} \frac{\partial g}{\partial \conj{z}}
+%         d\conj{z}
+%       + \frac{\partial f(g(z))}{\partial \conj{g}} \frac{\partial \conj{g}}{\partial z}
+%         dz
+%       + \frac{\partial f(g(z))}{\partial \conj{g}} \frac{\partial \conj{g}}{\partial \conj{z}}
+%         d\conj{z}
+%     \notag \\
+%     &=&
+%       \biggl\{
+%         \frac{\partial f(g(z))}{\partial g} \frac{\partial g}{\partial z}
+%         + \frac{\partial f(g(z))}{\partial \conj{g}} \conj{\frac{\partial g}{\partial \conj{z}}}
+%       \biggr\} dz
+%       + \biggl\{
+%         \frac{\partial f(g(z))}{\partial g} \frac{\partial g}{\partial \conj{z}}
+%         + \frac{\partial f(g(z))}{\partial \conj{g}} \conj{\frac{\partial g}{\partial z}}
+%       \biggr\}
+%         d\conj{z}
+%     \,.
+% \end{eqnarray}
 % Show that $dh(z) = df(g(z)) dg(z)$.
@@
 %   \,. $$
-
-In machine learning tasks the target objective is typically empirical risk, which has to
-be real-valued to be minimized. Nevertheless, the expression of the $\cplx\real$ gradient
-is compatible with what is expected, when $f$ is treated like a $\real^2$ function. For a
-real-valued $f\colon \cplx \to \real$ we have $\conj{f} = f$, which implies $
+At the same time the Cauchy-Riemann conditions $
+  -\iu \tfrac{\partial F}{\partial v} = \tfrac{\partial F}{\partial u}
+$ can be expressed as $
+  \tfrac{\partial f}{\partial \conj{z}} = 0
+$. Thus $\cplx\real$ calculus subsumes the usual $\cplx$-calculus of holomorphic functions,
+since $f(z) = f(z, \conj{z})$ is constant with respect to $\conj{z}$ in the latter.
+
+In optimization-related tasks the objective is $
+  f\colon \cplx\to \real
+$, meaning that if it were to satisfy the Cauchy-Riemann conditions, then it necessarily
+should have been constant. Nevertheless, the expression of the $\cplx\real$ gradient is
+compatible with what is expected, when $f$ is treated like a $\real^2$ function. For such
+$f$ we have $\conj{f} = f$, which implies $
   \tfrac{\partial f}{\partial \conj{z}}
@@
 $, whence
-$$
+\begin{equation*}
   df
@@
       + \tfrac{\partial f}{\partial \conj{z}} d\conj{z}
-  % = \conj{\tfrac{\partial \conj{f}}{\partial \conj{z}}} dz
-  % + \conj{\conj{\tfrac{\partial f}{\partial \conj{z}}} dz}
-  = 2 \Re \Bigl(
-    \conj{\tfrac{\partial f}{\partial \conj{z}}} dz
-  \Bigr)
-  = 2 \Re \bigl(
+    % = \tfrac{\partial f}{\partial z} dz
+    %   + \conj{\tfrac{\partial f}{\partial z}} d\conj{z}
+    = \tfrac{\partial f}{\partial z} dz
+      + \conj{\tfrac{\partial f}{\partial z} dz}
+    % = 2 \Re
+    %   \Bigl(
+    %     \conj{\tfrac{\partial f}{\partial \conj{z}}} dz
+    %   \Bigr)
+    = 2 \Re
+      \bigl(
         \tfrac{\partial f}{\partial z} dz
       \bigr)
-  \,. $$
-Thus, the gradient of $f$ at $z$ is given by $
-  \nabla_z f(z)
+    \,.
+\end{equation*}
+Therefore the gradient of $f$ at $z$ is given by $
+  \nabla_{\conj{z}} f(z)
+    = \conj{\tfrac{\partial f}{\partial z}}
     = \tfrac{\partial F}{\partial u}
-      + j \tfrac{\partial F}{\partial v}
+    + \iu \tfrac{\partial F}{\partial v}
+$. The identification $\cplx \simeq \real^2$, backed by Wirtinger calculus, and emulation
+of $\cplx$-arithmetic in computational graphs with $\real$-valued operations makes it
+possible to reuse $\real$ back-propagation and existing auto-differentiation frameworks.
+
+% section wirtinger_calculus (end)
+
+\section{Gradient of the KL-divergence in $\real$ case} % (fold)
+\label{sec:real-chisq-grad}  % gradient_of_the_kl_divergence_in_R_case
+
+In this appendix we study the approximation proposed by \citet{molchanov_variational_2017}
+for the KL divergence term \eqref{eq:improper-kl-div-real} for $\real$ Sparse Variational
+Dropout. Following the logic of \citet{lapidoth_capacity_2003} we derive the expression
+for $
+  \tfrac{d}{d\log \alpha} K(\alpha)
+$. Acknowledging that the same result was obtained by \citet[eq.~(5)]{hron_variational_2018},
+we provide this appendix for the sake of completeness.
+% The derivation in this section different from \citet{lapidoth_capacity_2003}.
+% The results are identical: they use DCT to establish interchangeability of limits
+% (sum-integral-derivative), whilst we allude to calculus theorems on differentiation
+% and integration of power series within the radius of their convergence (which are
+% essentially corollaries to the DCT).
+
+% \citet{pav_moments_2015} correctly notice that \cite[p. 2466]{lapidoth_capacity_2003} has a missing $\log{2}$ term.
+
+For $(z_i)_{i=1}^m \sim \mathcal{N}(0, 1)$ iid and $
+  (\mu_i)_{i=1}^m \in \mathbb{R}
+$, the random variable $W = \sum_i (\mu_i + z_i)^2$ has non-central $\chi^2$ distribution
+with shape $m$ and non-centrality parameter $\lambda = \sum_i \mu_i^2$, i.e. $
+  W\sim \chi^2_m(\lambda)
+$. Therefore, the divergence \eqref{eq:improper-kl-div-real} has the form
+\begin{equation}  \label{eq:kl-div-appendix}
+  K(\alpha)
+    \propto \frac12 \mathbb{E}_{
+        W\sim \chi^2_1\bigl(\tfrac1{\alpha}\bigr)
+      } \log W
+    \tag{\ref{eq:improper-kl-div-real}'}
+  \,.
+\end{equation}
+$W$ can alternatively be represented as a Poisson mixture of ordinary $\chi^2$
+distributions: if $Z_{\mid J} \sim \chi^2_{m + 2J}$ for $
+  J \sim \mathcal{P}ois(\tfrac{\lambda}2)
+$ then $W \sim Z$. Therefore, expanding the conditional expectation gives
+\begin{equation}  \label{eq:cond_exp_expansion}
+  \mathbb{E}_{W\sim \chi^2_m(\lambda)} \log W
+    = \mathbb{E}\Bigl(
+        \mathbb{E} \bigl( \log W \mid J)
+      \Bigr)
+    = \mathbb{E}_{J\sim {\mathcal{P}ois}(\tfrac\lambda2)}
+      \Bigl(
+        \mathbb{E}_{W\sim \chi^2_{m + 2 J}} \log W
+      \Bigr)
+    \,.
+\end{equation}
+Since $\chi^2_\nu$ is Gamma distribution $\Gamma(\tfrac\nu2, \tfrac12)$, it can be shown
+that the logarithmic moment $
+  \mathbb{E}_{W\sim \chi^2_\nu} \log W
+$ is $
+  \psi\bigl(\tfrac\nu{2}\bigr) - \log \tfrac12
+$, where $\psi$ is the digamma function ($\psi(x) = \tfrac{d}{dx} \log \Gamma(x)$).
+% \begin{equation}  \label{eq:digamma}
+%   \psi(x)
+%     % = \frac{d}{dx} \log \Gamma(x)
+%     = \frac1{\Gamma(x)}
+%       \int_0^\infty
+%         u^{x-1} e^{-u} \log{u}
+%       \, du
+%     \,.
+% \end{equation}
+By expanding expectation of a Poisson random variable we get $
+  \mathbb{E}_{W\sim \chi^2_m(\lambda)} \log W
+    = \log2 + g_m\bigl(\tfrac\lambda2\bigr)
+$, where
+\begin{equation}  \label{eq:exp_digamma}
+  g_m(x)
+    % = \mathbb{E}_{J\sim {\mathcal{P}ois}(x)}
+    %   \psi\bigl(\tfrac{m + 2 J}{2}\bigr)
+    = e^{- x} \sum_{j\geq 0}
+        \frac{x^j}{j!}
+          \psi\bigl(\tfrac{m + 2 J}{2}\bigr)
+    \,.
+\end{equation}
+Making use of the property $
+  \psi(z + 1) = \psi(z) + \tfrac1z
+  % \psi(1 + J + \tfrac{m}2) = \tfrac2{m + 2J} + \psi(J + \tfrac{m}2)
+$ of the digamma funciton for $z > 0$, we conclude that the power series in \eqref{eq:exp_digamma}
+converges for any $x \geq 0$. Therefore the derivative of \eqref{eq:exp_digamma} is
+given by
+\begin{equation}  \label{eq:g_m_series}
+  \frac{d}{dx} g_m(x)
+    % = \mathbb{E}_{J\sim {\mathcal{P}ois}(x)}
+    %     \bigl( \tfrac{J}x - 1 \bigr)
+    %   \psi\bigl(\tfrac{m + 2 J}{2}\bigr)
+    = - g_m(x)
+      + e^{- x} \sum_{j \geq 0}
+          \frac{x^j}{j!}
+        \biggl(
+          \psi\bigl(\tfrac{m + 2 j}{2}\bigr)
+          + \frac{2}{m + 2 j}
+        \biggr)
+    % = e^{- x} \sum_{j \geq 0}
+    %     \frac{x^j}{j!} \frac{2}{m + 2 j}
+    \,.
+\end{equation}
+By manipulating the partial sums within \eqref{eq:g_m_series} we get
+\begin{equation}  \label{eq:g_m_series_int}
+  \frac{d}{dx} g_m(x)
+    = e^{- x} \sum_{j \geq 0}
+      \frac{x^j}{j!} \frac1{j + \tfrac{m}2}
+    % = e^{- x} x^{- \tfrac{m}2} \sum_{j \geq 0}
+    %   \frac1{j!}
+    %   \frac{x^{j + \tfrac{m}2}}{j + \tfrac{m}2}
+    = e^{- x} x^{- \tfrac{m}2} \sum_{j \geq 0}
+      \frac1{j!} \int_0^x t^{j + \tfrac{m}2 - 1} dt
+    \,.
+\end{equation}
+Furthermore, the functions $
+  t \mapsto \sum_{j=0}^J \frac1{j!} t^{j + \tfrac{m}2 - 1}
+$ are non-decreasing on $(0, x)$ with growing $J$ and converge to $
+  t^{\tfrac{m}2 - 1} e^t
+$, which implies by the Monotone Convergence Theorem that
+\begin{equation}  \label{eq:g_m_integral}
+  \frac{d}{dx} g_m(x)
+    = e^{- x} x^{- \tfrac{m}2}
+      \int_0^x \sum_{j \geq 0}
+        \frac1{j!} t^{j + \tfrac{m}2 - 1} dt
+    = e^{- x} x^{- \tfrac{m}2}
+      \int_0^x t^{\bigl(\tfrac{m}2 - 1\bigr)} e^t dt
+    \,.
+\end{equation}
+Substituting $u^2 = t$ on $[0, \infty]$ with $2u du = dt$ and letting $
+  I_m
+  % \colon \mathbb{R} \to \mathbb{R}
+  \colon x \mapsto e^{-x^2} \int_0^x u^{m - 1} e^{u^2} du
+$ yields
+\begin{equation}  \label{eq:g_m_integral-sub}
+  \frac{d \eqref{eq:cond_exp_expansion}}{d \lambda}
+    = \frac12 \frac{d}{dx} g_m(x)
+        \bigg\vert_{x=\tfrac\lambda2}
+    % = x^{-\tfrac{m}2} e^{-x}
+    %     \int_0^x t^{\tfrac{m}2 - 1} e^t dt
+    = e^{-x}
+      x^{-\tfrac{m}2}
+      \int_0^{\sqrt{x}} u^{m - 1} e^{u^2} du
+        \bigg\vert_{x=\tfrac\lambda2}
+    % = e^{-x}
+    %   \frac1{\sqrt{x}}
+    %   \int_0^{\sqrt{x}} e^{u^2} du
+    %     \bigg\vert_{x=\tfrac\lambda2}
+    = \Bigl(\sqrt{\tfrac2\lambda}\Bigr)^m I_m\Bigl(\sqrt{\tfrac\lambda2}\Bigr)
+    \,.
+\end{equation}
+Since $\alpha$ is non-negative, it is typically parameterized via its logarithm, whence
+the derivative of \eqref{eq:kl-div-appendix} with respect to $\log\alpha$ follows from
+\eqref{eq:g_m_integral-sub} for $m=1$ and $\lambda = \tfrac1\alpha$:
+\begin{equation}  \label{eq:real-kl-div-deriv-log}
+  \frac{d K(\alpha)}{d\log \alpha}
+    % = \tfrac12 \sqrt{\tfrac2\lambda} F\Bigl(\sqrt{\tfrac\lambda2}\Bigr)
+    % for \lambda = \tfrac1\alpha
+    %   \tfrac{d\lambda}{d\alpha} = - \alpha^{-2}
+    %   \tfrac{d\alpha}{d\log \alpha} = \alpha
+    % = - \alpha \frac1{\alpha\sqrt{2\alpha}} F\Bigl(\tfrac1{\sqrt{2\alpha}}\Bigr)
+    = - \frac1{\sqrt{2\alpha}} I_1\bigl(\tfrac1{\sqrt{2\alpha}}\bigr)
+    \,.
+\end{equation}
+
+We compute the Monte-Carlo estimate of \eqref{eq:improper-kl-div-real} on a sample
+of $10^7$ draws over an equally spaced grid of $\log \alpha$ in $[-12, +12]$ of size
+$4096$. The approximation proposed by \citet{molchanov_variational_2017} is given in
+\eqref{eq:improper-kl-div-real-approx}, with coefficients $
+  k_1 = 0.63576
+$, $
+  k_2 = 1.8732
+$, and $
+  k_3 = 1.48695
+$. The derivative of the approximation with respect to $\log \alpha$ follows
+\eqref{eq:real-kl-div-deriv-log} within $4\%$ of relative tolerance, see
+fig.~\ref{fig:molchanov-derivative-replica}. 
+% see eq.~(14): flit overall sign, use $C = -k_1$, $1-\sigma(x) = \sigma(-x)$
+\begin{equation}  \label{eq:improper-kl-div-real-approx}
+  \eqref{eq:improper-kl-div-real}
+% - KL(\mathcal{N}(w \mid \mu, \alpha \mu^2) \|
+%     \tfrac1{\lvert w \rvert})
+%   \approx
+%     k_1 \sigma(k_2 + k_3 \log \alpha)
+%     + C \big\vert_{C = -k1}
+%     - \tfrac12 \log (1 + e^{-\log \alpha})
+  % = \tfrac12 \log \alpha
+  %   - \mathbb{E}_{\varepsilon \sim \mathcal{N}(1, \alpha)}
+  %   \log{\lvert \varepsilon \rvert} + C
+  \approx
+    \frac12 \log{\bigl(1 + e^{-\log \alpha}\bigr)}
+    + k_1 \sigma\bigl(- (k_2 + k_3 \log \alpha)\bigr)
+    % - k_1 \bigl(1 - \sigma(k_2 + k_3 \log \alpha)\bigr)
+  \,,
+\end{equation}
+% in parctial implementations we suggest using softplus to numerically comptue the last
+% term, since it is typically implemented in a floating-point stable fashion.
+Similarly, the forward difference estimate of the derivative \eqref{eq:real-kl-div-deriv-log}
+very closely (up to sampling error). For sake of completeness, we compute a similar
+Monte-Carlo estimate for the KL divergence term in \eqref{eq:c-vd-kl-div} for $\cplx$-valued
+Variational Dropout with $\beta = 2$, fit the best approximation \eqref{eq:improper-kl-div-real-approx},
+and compare it against the exact $\log \alpha$ derivative $
+  \frac{d \eqref{eq:c-vd-kl-div}}{d\log \alpha}
+    % = \frac{d \alpha}{d\log \alpha} \frac{d}{d\alpha} \bigl(
+    %   \log \tfrac1\alpha - \mathop{Ei}\bigl(-\tfrac1\alpha\bigr)
+    % = \alpha \bigl(
+    %   - \tfrac1\alpha
+    %   - \tfrac{e^x}{x} \bigg\vert_{x=-\tfrac1\alpha} \alpha^{-2}
+    % \bigr)
+    = e^{-\tfrac1\alpha} - 1
 $.
 
-Natural identification of $\cplx$ with $\real\times \real$, storing the real and imaginary
-parts in interleaved format, emulation of $\cplx$-algebra using $\real$-valued arithmetic,
-and Wirtinger calculus make it possible to reuse $\real$ back-propagation and existing
-auto-differentiation frameworks \citep{trabelsi_deep_2018}.
-
-% section wirtinger_calculus (end)
+\begin{figure}[!t]
+  \centering
+  \includegraphics[width=\columnwidth]{grad_log.pdf}
+  \caption{$\tfrac{d K(\alpha)}{d \log{\alpha}}$ of the approximation
+  \eqref{eq:improper-kl-div-real-approx}, MC estimate of \eqref{eq:improper-kl-div-real},
+  and the exact derivative using \eqref{eq:real-kl-div-deriv-log}.}
+  \label{fig:molchanov-derivative-replica}
+\end{figure}
+
+% section real-chisq-grad (end)
 
@@
 Consider $L \colon \cplx^m \to \cplx^n$ -- linear in $\cplx$. Then $
-  L(u + jv) = L u + j L v
+  L(u + jv) = L u + \iu L v
 $ for any $u, v \in \real^m$, which implies that the effect of $L$ as $\cplx$-linear
@@
 $ and observe that $F_r = \Re \circ F$ and $F_i = \Im \circ F$ are $\real$-linear operators
-such that $F = F_r + j F_i$ (pointwise). Indeed,
+such that $F = F_r + \iu F_i$ (pointwise). Indeed,
 $$
@@
 L z 
-  = (U + j V) (\Re z + j \Im z)
-  % = (U + j V) \Re z + j (U + j V) \Im z
-  % = U \Re z + j V \Re z + j \bigl(U \Im z + j V \Im z \bigr)
-  = U \Re z - V \Im z + j \bigl( V \Re z + U \Im z \bigr)
-  % = (U + j V) z
+  = (U + \iu V) (\Re z + \iu \Im z)
+  % = (U + \iu V) \Re z + \iu (U + \iu V) \Im z
+  % = U \Re z + \iu V \Re z + \iu \bigl(U \Im z + \iu V \Im z \bigr)
+  = U \Re z - V \Im z + \iu \bigl( V \Re z + U \Im z \bigr)
+  % = (U + \iu V) z
   \,. $$

### 2020-06-18 paper/paper.tex
icml2020 header

@@
 \eqref{eq:sgvb_estimator} would require that the \emph{entire} set of network's parameters
-$\omega$ be independently drawn for each element in the mini-batch. Since the parameters
-in a network naturally split into subsets with non-overlapping layer-wise effects, it is
-standard to assume that the approximation $
+$\omega$ be independently drawn for each element in the mini-batch. Since that the
+parameters in a network naturally split into subsets with non-overlapping layer-wise
+effects, it is standard to assume that the approximation $
   q_\theta(\omega)
@@
 $, where $C_{ij} = \Sigma_{ij} \xi_{ij}$ and the complex modulus and square are applied
-elementwise. Equation \eqref{eq:cplx-gauss-trick} can be applied to any layer, the output
+elementwise. \eqref{sub:c_gauss_and_local_rep} can be applied to any layer, the output
 of which depends linearly on its parameters, such as convolutional, affine, and bilinear

### 2020-06-18 paper/paper.tex
2 Overhauled the beginning of the Bayesian section  * more thorough exposition of the transition from Bayesian inference to SGVB  * added useful comments about SGVB versus local reparameterization trick  * cleaned up citations

--- 2020-06-18 paper/paper.tex
@@
 % Magnitude pruning induces user-specified sparsity distributions.
+
+% our contribution
+Sparse Variational Dropout is a Bayesian Variational Inference method with automatic
+parameter relevance determination effect. In this study we extend \emph{Sparse VD} to
+$\cplx$VNN, inspired by the results of \citet{gale_state_2019}, and motivated by seldom
+application of Bayesian Inference to $\cplx$-valued networks \citep{popa_complex-valued_2018}
+and apparent scarcity of compression methods specific to them. We assess the performance-%
+compression trade-off of the extension by conducting a large-scale numerical study on
+image classification on MNIST-like and CIFAR10 datasets and music transcription on MusicNet.
+%
+% THIS SHOULD GO TO CONCLUSIONS!
 %
@@
 
-% with noting that compression and sparsification techniques serve dual purpose as model
-% regularization. and can be regarded as a Bayesian network pruning method
-
-% our contribution
-Sparse Variational Dropout is a Bayesian Variational Inference method with automatic
-parameter relevance determination effect. In this study we extend this technique to
-$\cplx$VNN, inspired by the results of \citet{gale_state_2019}, and motivated by seldom
-application of Bayesian Inference to $\cplx$-valued networks \citep{popa_complex-valued_2018}
-and apparent scarcity of compression methods specific to them. We assess the performance-%
-compression trade-off of the extension by conducting a large-scale numerical study on
-image classification on MNIST-like and CIFAR10 datasets and music transcription on MusicNet.
-
-The paper is structured as follows. Sec.~\ref{sec:variational_dropout} reviews Bayesian
-dropout techniques, and sec.~\ref{sec:c_valued_networks} provides a brief summary of
-the inner working of complex-valued networks. The main contribution of this study is
-presented in sec.~\ref{sec:c_variational_dropout}, where we outline the details of
-different variational approximations and priors and derive the penalty terms in the
-evidence lower bound. In sec.~\ref{sec:experiments} we evaluate the sparsification rate,
-compare the resulting performance of various $\cplx$-networks proposed in prior work,
-and discuss the outcomes.
+The paper is structured as follows. Sec.~\ref{sec:variational_dropout} reviews Variational
+Dropout, and sec.~\ref{sec:c_valued_networks} provides a brief summary of the inner
+working of complex-valued networks. The main contribution of this study is presented in
+sec.~\ref{sec:c_variational_dropout}, where we outline the details of different variational
+approximations and priors and derive the penalty terms in the evidence lower bound.
+In sec.~\ref{sec:experiments} we evaluate the sparsification rate, compare the resulting
+performance of various $\cplx$-networks proposed in prior work, and discuss the outcomes.
 
@@
 
-% segue into bayesian inference
-  % \speak{R 1}
-  % In the first paragraph of section 2: Although the Bayesian prior over weights can indeed
-  % be interpreted as a prior over models, the inclusion of this notation in the first
-  % paragraph of section 2 seems unnecessary. Especially considering that the authors refer
-  % to weights, and not models, for the remainder of the paper.
-
-Bayesian Inference is a principled framework of reasoning about uncertainty, and in broad
-terms Bayesian methods are used to update prior assumptions in accordance with their
-likelihood based on empirical evidence into posterior beliefs. Under suitable modelling
-and distributional assumptions, Bayesian methods can be used towards model regularization,
-e.g. Variational Dropout \citep{kingma_variational_2015}.
-% Bayesian perspective on dropout model regularization proposed by Kingma at al. (2015)
-% repurposed for sparsification by Molchanov et al. (2017) and Kharitonov et al. (2018)
-
-In general, the core of Bayesian Inference can be summarized as follows: given a prior
-distribution $\pi(m)$ on models (hypotheses) $\mathcal{M}$, utilize the empirical evidence
-$D$ to update the assumptions by considering the likelihood of the observations under each
-$m \in \mathcal{M}$. Models are represented by a parametric family indexed by parameters
-$\omega \in \Omega$ and each $m_\omega(\cdot)$ specifies the conditional distribution of
-the data $
+% overview
+In broad terms Bayesian Inference is a principled framework of reasoning about uncertainty
+and a tool to update prior beliefs about model's parameters in accordance with evidence or
+empirical data into a posterior distribution. The posterior is useful for inference
+regarding unobserved data, predictive statistics, parameter confidence regions, and
+model's uncertainty.
+% intuitive definition of  of model given data is the same as probability of data under hypothesis (model)
+% KL-div min & VI -- \citep{jordan_introduction_1999} approximate Bayesian inference
+% SVI -- \citep{hoffman_stochastic_2013} scalable stochastic variant
+% SGVB -- \citep{kingma_auto-encoding_2014} differentiable MCMC estimator of the evidence lower bound for SVI
+
+For an observed dataset $
   D = (z_i)_{i=1}^N
-$. The posterior distribution $p(\omega \mid D)$, derived using the Bayes rule $
-  p(m \mid D) = \tfrac{p(D \mid m) \pi(m)}{p(D)}
-$ with $
-  p(D) = \mathbb{E}_{\pi(m)} p(D \mid m)
-$, provides useful information about yet unobserved data and model parameters, e.g
-classification uncertainty, predictive statistics, and parameter relevance.
-
-Save for the relatively simple cases, the posterior distribution is intractable, and
-therefore exactness Bayesian Inference is traded for tractability and scalability of
-Variational Bayesian Inference. Instead of deriving the posterior $p(\omega \mid D)$,
-this approach postulates an optimization problem for finding an approximation $q$,
-which is close to $p(\omega \mid D)$ in terms of a proximity score $\rho$
-\begin{equation}  \label{eq:variational-progam}
-  q_*
-    \in \arg \min_{\theta} \rho\bigl(
-      q_\theta(\omega), p(\omega \mid D)
-    \bigr)
-    \,,
-\end{equation}
-over a tractable parametric family of distributions on the parameter space $
-  \mathcal{Q} = \{Q_\theta(d\omega) \colon \theta \in \Theta\}
-$, $\theta$ -- generic variational parameter. The variational approximation class
-$\mathcal{Q}$ is chosen so that its members have tractable densities $
-  q_\theta(\omega) d\omega
-$, can be sampled from and have either tractable $\log$-derivatives $
-  \omega \mapsto \nabla_\theta \log q_\theta(\omega)
-$ or can be represented as differentiable transformations of non-parametric noise
-\citep{williams_simple_1992,kingma_auto-encoding_2014,figurnov_implicit_2019}.
-% (reparameterization trick, pathwise gradient) $q_{\theta}(d\omega)$ is a push-forward
-% of $p(d\varepsilon)$ by a differentiable map $g(\varepsilon; \theta)$.
-% % http://stillbreeze.github.io/REINFORCE-vs-Reparameterization-trick/#fn:1
-%
-The most common choice for $\rho$ is Kullback-Leibler divergence of density $q$ from $p$,
-\begin{equation}  \label{eq:kl-div-def}
-  KL(q \| p)
+$ with parametric statistical model (likelihood) $
+  p(D \mid \omega)
+    = \prod_i \log p(z_i \mid \omega)
+    % $D$ conditional independence given parameters $\omega$
+$ the Bayes rule $
+  p(\omega \mid D) = \tfrac{p(D \mid \omega) \pi(\omega)}{p(D)}
+$ transforms prior hypotheses $\pi(\omega)$ about the unknown distribution of model's
+parameters $\omega$ into the posterior distribution $p(\omega \mid D)$.
+%
+% In general the marginal likelihood of the dataset is intractable $
+%   p(D) = \mathbb{E}_{\pi(\omega)} p(D \mid \omega)
+% $.
+Save for the relatively simple set-ups, either the posterior distribution itself or the
+mathematical expectations it is involved in are analytically intractable or impractical
+to compute numerically. Thus, Variational Inference (VI), an approximate inference method
+proposed by \citet{jordan_introduction_1999}, is used to find an approximation within
+a parametric distribution family with densities $q_\theta(\omega)$, that is closest
+in terms of Kullback-Leibler (KL) divergence to the true posterior distribution, $
+  KL(q_\theta(\omega) \| p(\omega \mid D))
     % = \int \frac{dQ}{dP} \log{\frac{dQ}{dP}} P(d\omega)
@@
     = \mathbb{E}_{\omega \sim q}
-      \log{q(\omega)}
-    - \mathbb{E}_{\omega \sim q}
-      \log{p(\omega \mid D)}
-    \,,
-\end{equation}
-% and, despite it not being a metric and requiring distributions with nested support,
-the main reason being that it satisfies the following identity for well-behaved densities:
-% $(q, p, \pi)$
-\begin{multline}  \label{eq:kl-div-master}
-  % \log p(D)
-    % = \mathbb{E}_{q(\omega)} \log \frac{p(D, \omega)}{p(\omega \mid D)}
-    % = \mathbb{E}_{q(\omega)} \log \frac{
-    %   p(D \mid \omega) \pi(\omega)
-    % }{p(\omega \mid D)}
-    % = \mathbb{E}_{q(\omega)} \log \frac{
-    %   p(D \mid \omega) \pi(\omega)
-    % }{q(\omega)}
-    % + \mathbb{E}_{q(\omega)} \log \frac{q(\omega)}{p(\omega \mid D)}
-    % - \mathbb{E}_{q(\omega)} \log \frac{q(\omega)}{\pi(\omega)}
-    % = \mathbb{E}_{q(\omega)} \log{p(D \mid \omega)}
-    % + \mathbb{E}_{q(\omega)} \log \frac{q(\omega)}{p(\omega \mid D)}
-  \log p(D)
-    - KL(q \| p(\omega \mid D))
-    \\ = \mathbb{E}_{q(\omega)} \log{p(D \mid \omega)}
-    - KL(q \| \pi)
-    \,.
-\end{multline}
-This leads to an equivalent problem for \eqref{eq:variational-progam} of maximizing
-the \textit{evidence lower bound} (ELBO)
+      \log \tfrac{q_\theta(\omega)}{p(\omega \mid D)}
+$. The approximation family is chosen so that the expectations become tractable.
+%
+\citet{jordan_introduction_1999} showed that this problem is equivalent to \emph{maximizing}
+the \emph{Evidence Lower Bound} (ELBO)
 \begin{equation}  \label{eq:elbo_general}
@@
     = - KL(q_{\theta} \| \pi_{\lambda})
-      + \mathbb{E}_{\omega \sim q_{\theta}}
-        \log p_{\phi}(D \mid \omega)
+      + \sum_{i=1}^N \mathbb{E}_{\omega \sim q_{\theta}}
+        \log p_{\phi}(z_i \mid \omega)
       % \mathbb{E}_{\omega \sim q_{\theta}}
@@
 \end{equation}
-where $\lambda$, $\theta$ and $\phi$ are optimization parameters of the prior $\pi$,
-approximation $q$ and the likelihood $p(D\mid \omega)$, respectively. Other objectives
-are possible, besides \eqref{eq:elbo_general}, provided $p(\omega \mid D)$ is evaluated
-only through $\log p(D \mid \omega)$ and $\log \pi(\omega)$, \citep{ranganath_operator_2018}.
-
-\textit{Stochastic Gradient Variational Bayes} (SGVB), proposed by \citet{kingma_auto-encoding_2014},
-replaces the Variational objective \eqref{eq:elbo_general} by its unbiased differentiable
-Monte-Carlo estimator, which makes it possible to employ stochastic gradient optimization
-methods to solve \eqref{eq:variational-progam}. If $
+where $\lambda$ and $\phi$ parameterize the prior and the likelihood, respectively.
+%
+It is possible to use other objectives, besides \eqref{eq:elbo_general}, provided $
+  p(\omega \mid D)
+$ is evaluated only through $\log p(D \mid \omega)$ and $\log \pi(\omega)$,
+\citep{ranganath_operator_2018}.
+
+To make VI able to handle large-scale datasets \citet{hoffman_stochastic_2013} proposed
+\emph{Stochastic Variational Inference}, which uses stochastic gradient optimization over
+mini-batches from $D$ to solve \eqref{eq:elbo_general} with exponential families of
+distributions. To allow for efficient inference with non-conjugate distributions
+in large-scale setting \citet{titsias_doubly_2014} proposed \emph{Doubly Stochastic
+Variational Bayes} that uses unbiased Monte-Carlo estimate of the gradient of ELBO
+and requires that $q_\theta$ can be efficiently sampled from and have tractable
+$\nabla_\theta \log q_\theta(\omega)$.
+%
+Independently, \citet{kingma_auto-encoding_2014} proposed \emph{Stochastic Gradient
+Variational Bayes} estimator for ELBO and its gradient \eqref{eq:elbo_general} with
+respect to parameters via an unbiased differentiable Monte-Carlo estimator, provided
+the density $q_\theta(\omega)$ is amenable to the \emph{reparameterization trick},
+i.e. $
   \omega \sim q_{\theta}
@@
   \omega = g(\varepsilon; \theta)
-$ for some differentiable $
-  g(\varepsilon; \theta)
-$ and non-parametric random variable $
+$ for some non-parametric random variable $
     \varepsilon \sim p_\varepsilon
-$, then the SGVB objective is
+$ and $g(\varepsilon; \theta)$ differentiable with respect to $\theta$.
+
+% HERE
+% The Local Reparameterization Trick reduces the variance of SGVB
+% even further by sampling independent weight matrices for
+% each data-point inside mini-batch. So we need both original SGVB
+% (per sample randomness) and local reparameterization (that is an
+% efficient and less noisy equivalent to per-sample weight sampling)
+%
+The SGVB objective is
 \begin{equation}  \label{eq:sgvb_objective}
@@
         % \log p(z_i \mid \omega_i)b
-      + \frac1{L} \sum_{l=1}^L
-        \log p_{\phi}(D \mid g(\varepsilon_{l}; \theta))
+      + \frac1{L} \sum_{i=1}^N \sum_{l=1}^L
+        \log p_{\phi}(z_i \mid g(\varepsilon_{il}; \theta))
         % \log p_{\phi}(D \mid \omega_{l})
@@
   (\varepsilon_{l})_{l=1}^L
-$ is an iid sample from $p_\varepsilon$, the KL-divergence term replaced by unbiased
-differentiable finite sample estimator if it is intractable.
-%
-For the purposes of this study, we assume that the likelihood satisfies $
-  \log p_\phi(D\mid \omega)
-    = \sum_i \log p_\phi(z_i \mid \omega)
-$, i.e. the observed data $
-  D = (z_i)_{i=1}^N
-$ is conditionally independent, and consider \eqref{eq:sgvb_objective} with $L=1$
-and random mini-batches from $D$:
+$ is an iid sample from $p_\varepsilon$. The KL divergence term can replaced by an
+unbiased differentiable finite sample estimator if it is intractable.
+
+For the purposes of this study, we follow \citet{kingma_auto-encoding_2014} and use
+\eqref{eq:sgvb_objective} with random batches of size $M$ from $D$ and $L=1$ $\varepsilon$
+samples per datapoint in the mini-batch:
 \begin{equation}  \label{eq:elbo}
@@
     \,,
-\end{equation}
+\end{equation}  % \citet{kingma_auto-encoding_2014}
 for a random subsample $(z_{i_k})_{k=1}^M$ and iid $\varepsilon_k \sim p_\varepsilon$.
-%
-% (DSVI) titsias-lazaro.tex \todo{DSVI} \citep{titsias_doubly_2014}
-
-With a special family of posterior approximation, Variational Inference can be used as
-a regularization method and as a model sparsification technique.
+
+\medskip
+With a special posterior approximation family and suitable prior assumptions, Variational
+Inference can be used as model regularization and sparsification technique.
 
@@
 
+% VD is a Bayesian perspective on dropout regularization \citep{hinton_improving_2012} offered
+% by \citet{kingma_variational_2015} and repurposed for sparsification by \citet{molchanov_variational_2017}.
+%
 Dropout can be viewed as a Bayesian model averaging method, where models share parameters
@@
   \caption{%
-    Effects of finetunig on performance-compression curves parametrized by $
+    Effects of finetunig on performance-compression curves parameterized by $
       \tau\in \{\tfrac{k}2\colon k=-8..+8 \}

### 2020-06-20 paper/paper.tex
SGVB is efficient for local latents; for global shared latents we had better use use LRP of Kingma et al. (2015)
3 Finalized the Variational Inference section  * gradully introduced the SGVB estimator used in this study  * cleaned up the exposition, carefully researched the ideas behind var bayes developemnts

@@
 
+\subsection{Variational Inference} % (fold)
+\label{sub:variational_inference}
+
 % overview
 In broad terms Bayesian Inference is a principled framework of reasoning about uncertainty
-and a tool to update prior beliefs about model's parameters in accordance with evidence or
-empirical data into a posterior distribution. The posterior is useful for inference
+and a tool to update prior beliefs about model's parameters in accordance with evidence
+or empirical data into a posterior distribution. The posterior is useful for inference
 regarding unobserved data, predictive statistics, parameter confidence regions, and
@@
 For an observed dataset $
-  D = (z_i)_{i=1}^N
-$ with parametric statistical model (likelihood) $
+  D = (x_i)_{i=1}^N
+$ and statistical model $
   p(D \mid \omega)
-    = \prod_i \log p(z_i \mid \omega)
+    = \prod_i \log p(x_i \mid \omega)
     % $D$ conditional independence given parameters $\omega$
-$ the Bayes rule $
+$ with parameters $\omega$ the Bayes rule transforms prior hypotheses $\pi(\omega)$
+about the unknown distribution of model's parameters into the posterior distribution: $
   p(\omega \mid D) = \tfrac{p(D \mid \omega) \pi(\omega)}{p(D)}
-$ transforms prior hypotheses $\pi(\omega)$ about the unknown distribution of model's
-parameters $\omega$ into the posterior distribution $p(\omega \mid D)$.
+$.
 %
@@
 mathematical expectations it is involved in are analytically intractable or impractical
-to compute numerically. Thus, Variational Inference (VI), an approximate inference method
-proposed by \citet{jordan_introduction_1999}, is used to find an approximation within
-a parametric distribution family with densities $q_\theta(\omega)$, that is closest
-in terms of Kullback-Leibler (KL) divergence to the true posterior distribution, $
+to compute numerically. Variational Inference (VI), proposed by \citet{jordan_introduction_1999},
+can be used in such cases to make approximate inference. The approach finds an approximation
+within some distribution family $q_\theta(\omega)$, which is closest to the true posterior
+distribution in terms of Kullback-Leibler divergence: $
   KL(q_\theta(\omega) \| p(\omega \mid D))
@@
     %   \log\frac{q(\omega)}{p(\omega)}
-    = \mathbb{E}_{\omega \sim q}
+    = \mathbb{E}_{\omega \sim q_\theta}
       \log \tfrac{q_\theta(\omega)}{p(\omega \mid D)}
-$. The approximation family is chosen so that the expectations become tractable.
-%
-\citet{jordan_introduction_1999} showed that this problem is equivalent to \emph{maximizing}
-the \emph{Evidence Lower Bound} (ELBO)
+$. % The approximation family is chosen so that the expectations become tractable.
+%
+\citet{jordan_introduction_1999} show that this problem is equivalent to variational
+\emph{maximization} of the \emph{Evidence Lower Bound} (ELBO)
 \begin{equation}  \label{eq:elbo_general}
-  \mathcal{L}(\theta; \phi, \lambda)
+  \mathcal{L}(\theta; \lambda)
     = - KL(q_{\theta} \| \pi_{\lambda})
       + \sum_{i=1}^N \mathbb{E}_{\omega \sim q_{\theta}}
-        \log p_{\phi}(z_i \mid \omega)
+        \log p(x_i \mid \omega)
       % \mathbb{E}_{\omega \sim q_{\theta}}
@@
 \end{equation}
-where $\lambda$ and $\phi$ parameterize the prior and the likelihood, respectively.
-%
-It is possible to use other objectives, besides \eqref{eq:elbo_general}, provided $
-  p(\omega \mid D)
-$ is evaluated only through $\log p(D \mid \omega)$ and $\log \pi(\omega)$,
-\citep{ranganath_operator_2018}.
-
+where the variational parameters $\theta$ and $\lambda$ parameterize the approximation
+and the prior, respectively.
+%
+Kullback-Leibler and, by proxy, ELBO are standard objectives in VI, however it is possible
+to use other objectives, provided the true posterior $p(\omega \mid D)$ is evaluated only
+through $\log p(D \mid \omega)$ and $\log \pi(\omega)$, \citep{ranganath_operator_2018}.
+
+% speed, scale, variance, family of suitable Var approximations
+In subsequent years several improvements to Variational Inference approach were introduced.
 To make VI able to handle large-scale datasets \citet{hoffman_stochastic_2013} proposed
-\emph{Stochastic Variational Inference}, which uses stochastic gradient optimization over
-mini-batches from $D$ to solve \eqref{eq:elbo_general} with exponential families of
-distributions. To allow for efficient inference with non-conjugate distributions
-in large-scale setting \citet{titsias_doubly_2014} proposed \emph{Doubly Stochastic
-Variational Bayes} that uses unbiased Monte-Carlo estimate of the gradient of ELBO
-and requires that $q_\theta$ can be efficiently sampled from and have tractable
-$\nabla_\theta \log q_\theta(\omega)$.
-%
+\emph{Stochastic Variational Inference}, which uses stochastic gradient optimization of
+\eqref{eq:elbo_general} based on inexpensive noisy unbiased gradient estimates of ELBO
+computed on random mini-batches from the dataset. \citet{titsias_doubly_2014} translated
+dependence on $\theta$ from $q_{\theta}$ to the functions inside the expectations of ELBO
+and propose \emph{Doubly Stochastic Variational Inference}, which computes unbiased gradient
+estimator based on both dataset subsampling and random draws from variational distribution
+$q_{\theta}$. Note, that the KL divergence term can replaced by its unbiased differentiable
+finite-sample estimator without forfeiting convergence of (doubly) SVI.
+
+% The variance of the stochastic gradient directly affects convergence of SVI. 
 Independently, \citet{kingma_auto-encoding_2014} proposed \emph{Stochastic Gradient
-Variational Bayes} estimator for ELBO and its gradient \eqref{eq:elbo_general} with
-respect to parameters via an unbiased differentiable Monte-Carlo estimator, provided
-the density $q_\theta(\omega)$ is amenable to the \emph{reparameterization trick},
-i.e. $
-  \omega \sim q_{\theta}
+Variational Bayes}, which is an alternative efficient doubly stochastic estimator
+applicable to models with parameters $\omega$ that are continuous random variables
+amenable to the \emph{reparameterization trick}, i.e. $
+  \omega \sim q_{\theta}(\omega)
 $ is equivalent in distribution to $
-  \omega = g(\varepsilon; \theta)
+  \omega = g_{\theta}(\varepsilon)
 $ for some non-parametric random variable $
-    \varepsilon \sim p_\varepsilon
-$ and $g(\varepsilon; \theta)$ differentiable with respect to $\theta$.
-
-% HERE
+  \varepsilon \sim p(\varepsilon)
+$ and $
+  g(\varepsilon; \theta)
+$ differentiable with respect to $\theta$. The estimator of \eqref{eq:elbo_general}
+for $L$ reparameterized draws per datapoint in mini-batch of size $M$, is given by
+\begin{equation}  \label{eq:sgvb_estimator}
+  \widetilde{\mathcal{L}}(\theta; \lambda)
+    = - KL(q_{\theta} \| \pi_{\lambda})
+      % + \frac{N}{\lvert B \rvert} \sum_{i\in B}
+        % \log p(x_i \mid \omega_i)b
+      + \frac{N}{M L} \sum_{k,l}
+        \log p(x_{i_k} \mid g(\varepsilon_{lk}; \theta))
+      % + \frac{N}{M L} \sum_{k=1}^M \sum_{l=1}^L
+      %   \log p(x_{i_k} \mid g(\varepsilon_{lk}; \theta))
+        % \log p(D \mid \omega_{l})
+        %   \Big\vert_{\omega_{l} = g(\varepsilon_{l}; \theta)}
+      % =
+      % - KL(q_{\theta} \| \pi)
+      % + N \mathbb{E}_{B \sim \{D\}_M \otimes q_\theta^M}
+        % \hat{\mathbb{E}}_{x,\omega \sim B}
+          % \log p(x \mid \omega)
+    \,,
+\end{equation}
+where $(x_{i_k})_{k=1}^M$ is a random mini-batch from $D$ and $
+  (\varepsilon_{lk})_{l=1}^L
+$ are $M$ independent iid samples from $p_\varepsilon$. \citet{figurnov_implicit_2019}
+extended the scope of the reparameterization gradients to include continuous distributions
+such as Gamma and von Mises. To handle the case of non-reparameterizable $\omega$ in
+doubly stochastic VI, e.g. discrete random parameters, \citet{titsias_local_2015} proposed
+\emph{local expectation gradients}, which is a version of REINFORCE gradient estimator
+\citep{williams_simple_1992} with variance reduced by careful use of dependence
+structures in the model.
+% (reparameterization trick, pathwise gradient) $q_{\theta}(d\omega)$ is a push-forward
+% of $p(d\varepsilon)$ by a differentiable map $g(\varepsilon; \theta)$.
+% % http://stillbreeze.github.io/REINFORCE-vs-Reparameterization-trick/#fn:1
+% rao-blackwellization (http://pyro.ai/examples/svi_part_iii.html)
+
 % The Local Reparameterization Trick reduces the variance of SGVB
@@
 % efficient and less noisy equivalent to per-sample weight sampling)
-%
-The SGVB objective is
-\begin{equation}  \label{eq:sgvb_objective}
-  \widetilde{\mathcal{L}} %(\theta; \phi, \lambda)
-    = - KL(q_{\theta} \| \pi_{\lambda})
-      % + \frac{N}{\lvert B \rvert} \sum_{i\in B}
-        % \log p(z_i \mid \omega_i)b
-      + \frac1{L} \sum_{i=1}^N \sum_{l=1}^L
-        \log p_{\phi}(z_i \mid g(\varepsilon_{il}; \theta))
-        % \log p_{\phi}(D \mid \omega_{l})
-        %   \Big\vert_{\omega_{l} = g(\varepsilon_{l}; \theta)}
-      % =
-      % - KL(q_{\theta} \| \pi)
-      % + N \mathbb{E}_{B \sim \{D\}_M \otimes q_\theta^M}
-        % \hat{\mathbb{E}}_{z,\omega \sim B}
-          % \log p(z \mid \omega)
-    \,,
-\end{equation}
-where $
-  (\varepsilon_{l})_{l=1}^L
-$ is an iid sample from $p_\varepsilon$. The KL divergence term can replaced by an
-unbiased differentiable finite sample estimator if it is intractable.
-
-For the purposes of this study, we follow \citet{kingma_auto-encoding_2014} and use
-\eqref{eq:sgvb_objective} with random batches of size $M$ from $D$ and $L=1$ $\varepsilon$
-samples per datapoint in the mini-batch:
-\begin{equation}  \label{eq:elbo}
-  \widetilde{\mathcal{L}} %(\theta; \phi, \lambda)
-    = - KL(q_{\theta} \| \pi_{\lambda})
-      + \frac{N}{M} \sum_{k=1}^M
-        \log p_{\phi}(z_{i_k} \mid g(\varepsilon_k; \theta))
-    \,,
-\end{equation}  % \citet{kingma_auto-encoding_2014}
-for a random subsample $(z_{i_k})_{k=1}^M$ and iid $\varepsilon_k \sim p_\varepsilon$.
-
-\medskip
+% SGVB is specifically for VAE (local latent varaibles per data-point)
+% what Kingma propose is SGVB for global shared latent varaibles aka
+% WEIGHTS!!
+In this study we use the SGVB estimator \eqref{eq:sgvb_estimator} with $L=1$ and the
+\emph{local reparameterization trick} proposed by \citet{kingma_variational_2015}. They
+argued that this gradient estimator can be made more statistically and computationally
+efficient, if the structure of the model permits translating global stochasticity of
+$\omega$ down to local intermediate states of computation.
+%
+The class of models that are allow this include non-recurrent computational graphs,
+exemplified by neural networks with parameters $\omega \sim q_\theta$. In this case
+\eqref{eq:sgvb_estimator} would require that the \emph{entire} set of network's parameters
+$\omega$ be independently drawn for each element in the mini-batch. However, noting
+that the parameters in a network naturally decompose into subsets with non-overlapping
+layer-wise effects, it is standard to assume that the approximation $
+  q_\theta(\omega)
+$ is factorized over layers. Furthermore, if $
+  \omega = W \in \mathbb{R}^{n\times m}
+$ in a linear layer $
+  y = b + W^\top x
+$ with $
+  q_\theta(W)
+    = \prod_{ij}
+      \mathcal{N}(w_{ij} \vert\, \mu_{ij}, \sigma_{ij}^2)
+$, then by virtue of $y$ being a linear transformation of $W$, we get
+\begin{equation}  \label{eq:r-gauss-trick}
+  q(y) = \prod_i \mathcal{N}\Bigl(
+        y_i \big\vert\,
+        b_i + \sum_j \mu_{ij} x_j,
+        \sum_j \sigma^2_{ij} x_j^2
+    \Bigr)
+  \,.
+\end{equation}
+This yields outputs equivalent in distribution to sampling $W$ for each element in
+the mini-batch, which produces the SGVB estimator with smaller variance, as demonstrated
+by \citet{kingma_variational_2015}.
+
+% subsection variational_inference (end)
+
+\subsection{Dropout} % (fold)
+\label{sub:dropout}
+
 With a special posterior approximation family and suitable prior assumptions, Variational
@@
   \pi(\omega_j) \propto \lvert \omega_j \rvert^{-1}
-$. The divergence term in \eqref{eq:elbo} unravels into the following sum:
+$. The divergence term in \eqref{eq:sgvb_estimator} unravels into the following sum:
 \begin{equation}  \label{eq:improper-kl-div-real}
@@
 $ with learnable precision $\tau_j > 0$, \citep{neal_bayesian_1996}. Maximizing
-\eqref{eq:elbo} over $\tau$, holding other parameters fixed, yields $
+\eqref{eq:sgvb_estimator} over $\tau$, holding other parameters fixed, yields $
   \tau^*_j = {(\mu_j^2 + \sigma^2_j)}^{-1}
@@
 
+% Similar idea to \eqref{eq:r-gauss-trick} was proposed by \citet{wang_fast_2013} to speed
+% up Gaussian dropout.
+
+% , that for the case of fully factorized Gaussian
+% posterior approximations, using \eqref{eq:r-gauss-trick} decorrelates the estimators
+% \eqref{eq:sgvb_estimator} within the mini-batch and makes the gradient estimator $
+%   \nabla_\theta \tilde{\mathcal{L}}
+% $ more statistically efficient. Specifically for the problem of selecting relevant parameters
+% \citet{molchanov_variational_2017} further improve the efficiency of the estimator of the $
+%   \nabla_\mu \tilde{\mathcal{L}}
+% $ by introducing \textit{additive noise parameterization}.
+
 Another contribution of \citep{kingma_variational_2015} is the analysis of the effects of the
-\textit{local reparameterization trick} on the variance of the gradient of \eqref{eq:elbo}.
+\textit{local reparameterization trick} on the variance of the gradient of \eqref{eq:sgvb_estimator}.
 Proposed by \citet{wang_fast_2013} to speed up Gaussian dropout, this trick translates
@@
 $,
-\begin{equation}  \label{eq:r-gauss-trick}
+\begin{equation}  % \label{eq:r-gauss-trick}
   q(y) = \prod_i \mathcal{N}\Bigl(
@@
 posterior approximations, using \eqref{eq:r-gauss-trick} decorrelates the estimators
-\eqref{eq:elbo} within the mini-batch and makes the gradient estimator $
+\eqref{eq:sgvb_estimator} within the mini-batch and makes the gradient estimator $
   \nabla_\theta \tilde{\mathcal{L}}
@@
 parameterization back to the equivalent $(\mu, \sigma^2)$, since it stabilizes gradients
-of SGVB \eqref{eq:elbo}, by rendering the gradient with respect to $\mu$ independent from
+of SGVB \eqref{eq:sgvb_estimator}, by rendering the gradient with respect to $\mu$ independent from
 the local output noise, injected by \eqref{eq:r-gauss-trick}. The relevance $\alpha$ is
@@
 
-% section bayesian_dropout (end)
+% subsection dropout (end)
+
+% section variational_dropout (end)
 
@@
 $\cplx$-valued networks. In this section we describe the approximation and derive the
-divergence penalties in \eqref{eq:elbo}. Similarly to $\real$-valued Variational Dropout,
+divergence penalties in \eqref{eq:sgvb_estimator}. Similarly to $\real$-valued Variational Dropout,
 the proposed $\cplx$-valued extension can be straightforwardly enhanced to provide
@@
   \pi(\omega) = \prod_{ij} \pi(\omega_{ij})
-$, the divergence term in ELBO \eqref{eq:elbo} is
+$, the divergence term in ELBO \eqref{eq:sgvb_estimator} is
 \begin{equation}  \label{eq:elbo-general-kl-div}
@@
 %
-Since $\mathop{Ei}(x)$ has simple analytic derivative and \eqref{eq:elbo} depends additively
+Since $\mathop{Ei}(x)$ has simple analytic derivative and \eqref{eq:sgvb_estimator} depends additively
 on \eqref{eq:c-vd-kl-div}, it is possible to back-propagate through the divergence without
 forward evaluation, which speeds up gradient updates.
-% Gradient-based optimiziation of \eqref{eq:elbo} usually does not use the value of the objective. 
+% Gradient-based optimiziation of \eqref{eq:sgvb_estimator} usually does not use the value of the objective. 
 % In stochastic gradient methods are concerned more with the gradient, induced by the objective
@@
 %
-In Empirical Bayes the prior adapts to the observed data, i.e. \eqref{eq:elbo} is optimized
-w.r.t. $\tau$ of each weight's prior. Since divergence sits in \eqref{eq:elbo} with negative
+In Empirical Bayes the prior adapts to the observed data, i.e. \eqref{eq:sgvb_estimator} is optimized
+w.r.t. $\tau$ of each weight's prior. Since divergence sits in \eqref{eq:sgvb_estimator} with negative
 sign, optimal $
@@
 At the \textit{``dense''} stage every network is fit ``as-is'', retaining its original
-non-Bayesian architecture, and using only the likelihood term from \eqref{eq:elbo} without
+non-Bayesian architecture, and using only the likelihood term from \eqref{eq:sgvb_estimator} without
 variational dropout.
@@
   C \in (0, 1]
-$ at the KL divergence term in \eqref{eq:elbo} to study the attainable sparsity levels:
+$ at the KL divergence term in \eqref{eq:sgvb_estimator} to study the attainable sparsity levels:
 \begin{equation}  \label{eq:elbo_with_coef}
@@
   \,.
-  \tag{\ref{eq:elbo}'}
+  \tag{\ref{eq:sgvb_estimator}'}
 \end{equation}

### 2020-06-20 paper/paper.tex
4 reshuffled the order of the narration in the section related to dropout   * Dropout connects to Bayes and VD, and VD connects to sparsification   * discuss molchanov's parameterization in connection to SGVB   * finish with KL divergences and their approximations

@@
 % efficient and less noisy equivalent to per-sample weight sampling)
-% SGVB is specifically for VAE (local latent varaibles per data-point)
-% what Kingma propose is SGVB for global shared latent varaibles aka
+% SGVB is specifically for VAE (local latent variables per data-point)
+% what Kingma propose is SGVB for global shared latent variables aka
 % WEIGHTS!!
@@
 by \citet{kingma_variational_2015}.
+% Similar idea to \eqref{eq:r-gauss-trick} was proposed by \citet{wang_fast_2013} to speed
+% up Gaussian dropout.
 
@@
 
-With a special posterior approximation family and suitable prior assumptions, Variational
-Inference can be used as model regularization and sparsification technique.
+With a special posterior approximation family $q_\theta$ and suitable prior $\pi$,
+Variational Inference can be used as model regularization and sparsification technique.
 
 % on dropout
-Dropout \citep{hinton_improving_2012} prevents overfitting by injecting multiplicative
-binary noise into layer's weights, which breaks up co-adaptations that could occur
-during training. \citet{wang_fast_2013} argue that the overall effect of binary dropout
-on the intermediate outputs via the Central Limit Theorem can be approximated by a Gaussian
-with weight-input dependent mean and variance. \citet{srivastava_dropout:_2014} propose
-using independent $\mathcal{N}(1,1)$ noise, arguing that higher entropy of a Gaussian has
-better regularizing effect. In a recent study concerning multitask learning
-\citet{cheung_superposition_2019} have shown the possibility of storing task-specific
-parameters in non-destructive superposition within a single network. In particular, their
-argument implies that if the single task setting is viewed as multitask learning with
-replicated task, then by sampling uncorrelated binary masks Dropout acts as a superposition
-method, utilizing the learning capacity of the network better.
+Dropout, proposed by \citet{hinton_improving_2012}, prevents overfitting by injecting
+multiplicative binary noise into layer's weights, which breaks up co-adaptations that
+could occur during training. \citet{wang_fast_2013} argued that the overall effect of
+binary dropout on the intermediate outputs can be approximated by a Gaussian with weight-input
+dependent mean and variance via the Central Limit Theorem. \citet{srivastava_dropout:_2014}
+proposed using independent $\mathcal{N}(1, 1)$ multiplicative noise, arguing that higher
+entropy of a Gaussian has better regularizing effect. \citet{gal_dropout_2016} showed
+that Dropout is a Bayesian approximation method with close ties to deep Gaussian Processes
+that yields inexpensive model uncertainty estimates. In a study concerning multitask learning
+\citet{cheung_superposition_2019} demonstrated the possibility of storing task-specific
+parameters in non-destructive superposition within a single network. Regarding Dropout
+their argument implies that if the single task setting is viewed as multitask learning
+with replicated task, then by sampling uncorrelated binary masks Dropout acts as a
+superposition method, utilizing the learning capacity of the network better.
 % many identical copies of the same task; \cite[Appendix A.1]{cheung_superposition_2019}
@@
 %
-Dropout can be viewed as a Bayesian model averaging method, where models share parameters
-and are weighted equally. Thus, \citet{kingma_variational_2015} consider Dropout, DropConnect
-\citep{wan_regularization_2013}, and Gaussian dropout \citep{wang_fast_2013} through the
-lens of Bayesian Inference methods and propose \textit{Variational Dropout}. They argue that
-the multiplicative noise introduced by these methods induces a distribution equivalent to
-a fully factorized variational posterior of the form $
+\citet{kingma_variational_2015} provided a unifying perspective on Dropout, DropConnect
+\citep{wan_regularization_2013}, and Gaussian dropout \citep{wang_fast_2013} through
+the lens of Variational Inference methods and propose \emph{Variational Dropout}. They
+argued that the multiplicative noise introduced by Dropout methods induces a distribution
+equivalent to a fully factorized variational posterior of the form $
   q_\theta(\omega) = \prod_j q_{\theta}(\omega_j)
@@
 $ iid from some $p_\theta(\xi)$.
-
+%
 % Binary dropout with rate $p \in (0, 1)$ uses $
@@
     = \prod_j \mathcal{N}(\omega_j \vert\, \mu_j, \alpha_j \mu_j^2)
-$ and factorized log-uniform prior $\pi(\omega)$ with $
+$ and factorized scale invariant log-uniform prior $\pi(\omega)$ with $
   \pi(\omega_j) \propto \lvert \omega_j \rvert^{-1}
-$. The divergence term in \eqref{eq:sgvb_estimator} unravels into the following sum:
+$. \citet{molchanov_variational_2017} noticed that $\alpha_j$ reflect the relevance of the
+parameter $\omega_j$ it is associated to by being the ratio of its squared mean to its
+effective variance. Based on this observation they proposed \emph{Sparse Variational Dropout},
+a modification that enables automatic model sparsification by optimizing $\alpha_j$ for each
+individual parameter. \citet{louizos_bayesian_2017} extended the idea to structured sparsity
+by considering hierarchical prior and variational approximation. They grouped the parameters
+$\omega_j$ and coupled them within each one through a shared latent variable, which on the
+whole enabled pruning entire input features in each layer.
+% {louizos_bayesian_2017} eq. (11) variance -> gaussian entropy -> informative bits
+%
+
+Simultaneously \citet{molchanov_variational_2017} proposed to use \emph{Additive Noise
+Parameterization} in the factorized Gaussian $q_\theta(\omega)$ in conjunction with the
+Local Reparameterization Trick. They reverted the $(\mu, \alpha)$ parameterization back
+to the equivalent $(\mu, \sigma^2)$, arguing that it reduces the variance of the SGVB
+\eqref{eq:sgvb_estimator}, by rendering the gradient with respect to $\mu_{ij}$ independent
+from the local output noise, injected by \eqref{eq:r-gauss-trick}. This improvement is
+especially important for model pruning, since $\mu_{ij}$ of relevant parameters are used
+as point estimates of their values.
+
+Due to factorization alternative parameterization, the term $KL(q_\theta \| \pi)$ in
+\eqref{eq:sgvb_estimator} of Sparse VD unravels into $
+  \sum_j K(\tfrac{\sigma^2_{j}}{\mu_{j}^2})
+$ with
 \begin{equation}  \label{eq:improper-kl-div-real}
-  KL(q_\theta \| \pi)
-    \propto
-      \frac12 \sum_j \mathbb{E}_{\varepsilon \sim \mathcal{N}(0, 1)}
-        \log{\Bigl\lvert \tfrac1{\sqrt{\alpha_j}} + \varepsilon \Bigr\rvert^2}
+  K(\alpha)
+    \propto \frac12 \mathbb{E}_{\varepsilon \sim \mathcal{N}(0, 1)}
+        \log{\Bigl\lvert \tfrac1{\sqrt{\alpha}} + \varepsilon \Bigr\rvert^2}
       % \frac12 \mathbb{E}_{\varepsilon \sim \mathcal{N}(0, 1)}
@@
 \end{equation}
-\citet{kingma_variational_2015} approximate this expression by a non-linear polynomial
-regression over $\alpha \in (0, 1)$. \citet{molchanov_variational_2017} refine the
-approximation by using a nonlinear regression based on sigmoid and soft-plus.
+\citet{kingma_variational_2015} approximated $K(\alpha)$ over $\alpha \in (0, 1)$ by
+a non-linear polynomial, and later \citet{molchanov_variational_2017} refined the
+approximation of \eqref{eq:improper-kl-div-real} by a nonlinear regression based on
+sigmoid and soft-plus.
 % see p.6 sec 3.4 of kingma_variational_2015
 In appendix~\ref{sec:real-chisq-grad} we verify the value and the derivative of their
-approximation against the Monte-Carlo estimate of \eqref{eq:improper-kl-div-real} for $\alpha$
-varying over a fine logarithmic grid and the gradient of \eqref{eq:improper-kl-div-real},
+approximation against the Monte-Carlo estimate of \eqref{eq:improper-kl-div-real} for
+$\alpha$ varying over a fine logarithmic grid and the gradient of \eqref{eq:improper-kl-div-real},
 for which we obtain an exact expression.
@@
 
-The key role in the factorization is played by $\alpha_j$, which reflects the relevance
-of the parameter $\omega_j$ it is associated to, by being the ratio of its squared mean
-to its variance. Thus, \citet{molchanov_variational_2017} focus on the model sparsification
-capabilities of Variational Dropout, optimizing $\alpha_j$ for each individual parameter,
-or across groups of parameters for structured sparsity.
-%
-\citet{louizos_bayesian_2017} consider hierarchical prior and approximation, which couples
-the parameters $\omega_j$ within a group $J$ through shared scaling $z_J$ and enables
-pruning entire input features in each layer.
-% {louizos_bayesian_2017} eq. (11) variance -> gaussian entropy -> informative bits 
-%
-\citet{kharitonov_variational_2018}
-address theoretical issues with improper priors and propose a method based on \textit{
-Automatic Relevance Determination} procedure, which falls under \textit{Empirical Bayes}
-approach that fits a prior distribution while performing Variational Inference. In this
-method the log-uniform factor $\pi(\omega_j)$ is replaced by a proper Gaussian ARD
-prior $
-  \mathcal{N}(\omega_j \vert\, 0, \tau^{-1}_j)
-$ with learnable precision $\tau_j > 0$, \citep{neal_bayesian_1996}. Maximizing
-\eqref{eq:sgvb_estimator} over $\tau$, holding other parameters fixed, yields $
+\citet{kharitonov_variational_2018} addressed theoretical issues with improper prior
+$\pi$, emphasized by \citet{hron_variational_2018}, and proposed Sparse VD based on
+\textit{Automatic Relevance Determination} procedure. ARD replaces $\pi(\omega_j)$ by
+a proper Gaussian ARD prior $
+  \pi_\lambda(\omega_j) = \mathcal{N}(\omega_j \vert\, 0, \tau_j^{-1})
+$ with learnable precision $\tau_j > 0$ \citep{neal_bayesian_1996}, thereby recasting
+the VD as the \textit{Empirical Bayes} approach, which performs Bayesian Inference over
+$\omega$, but uses Maximum Likelihood point-estimates for the hyper-parameters $\lambda$,
+\citep{mackay_bayesian_1994}. Maximizing \eqref{eq:sgvb_estimator} over $\tau$, holding
+other parameters fixed, yields $
   \tau^*_j = {(\mu_j^2 + \sigma^2_j)}^{-1}
@@
 \begin{equation}  \label{eq:ard-kl-div-real}
-  KL(q_\theta \| \pi)
-    = \frac12 \sum_j \log{\bigl(1 + \tfrac1{\alpha_j} \bigr)}
+  K(\alpha)
+    = \frac12 \sum_j \log{\bigl(1 + \tfrac1{\alpha} \bigr)}
     \,.
@@
 % \end{align}
-
-% Similar idea to \eqref{eq:r-gauss-trick} was proposed by \citet{wang_fast_2013} to speed
-% up Gaussian dropout.
-
-% , that for the case of fully factorized Gaussian
-% posterior approximations, using \eqref{eq:r-gauss-trick} decorrelates the estimators
-% \eqref{eq:sgvb_estimator} within the mini-batch and makes the gradient estimator $
-%   \nabla_\theta \tilde{\mathcal{L}}
-% $ more statistically efficient. Specifically for the problem of selecting relevant parameters
-% \citet{molchanov_variational_2017} further improve the efficiency of the estimator of the $
-%   \nabla_\mu \tilde{\mathcal{L}}
-% $ by introducing \textit{additive noise parameterization}.
-
-Another contribution of \citep{kingma_variational_2015} is the analysis of the effects of the
-\textit{local reparameterization trick} on the variance of the gradient of \eqref{eq:sgvb_estimator}.
-Proposed by \citet{wang_fast_2013} to speed up Gaussian dropout, this trick translates
-uncertainty from parameters of the model to intermediate outputs within the network:
-the stochasticity of $
-  W \in \mathbb{R}^{n\times m}
-$ with $
-  q(W) = \prod_{ij}
-    \mathcal{N}(w_{ij}\vert\, \mu_{ij}, \alpha_{ij} \mu_{ij}^2)
-$ in a linear layer is pushed to its output $
-  y = b + W^\top x
-$,
-\begin{equation}  % \label{eq:r-gauss-trick}
-  q(y) = \prod_i \mathcal{N}\Bigl(
-        y_i \big\vert\,
-        b_i + \sum_j \mu_{ij} x_j,
-        \sum_j \alpha_{ij} \mu_{ij}^2 x_j^2
-    \Bigr)
-  \,.
-\end{equation}
-%
-\citet{kingma_variational_2015} show, that for the case of fully factorized Gaussian
-posterior approximations, using \eqref{eq:r-gauss-trick} decorrelates the estimators
-\eqref{eq:sgvb_estimator} within the mini-batch and makes the gradient estimator $
-  \nabla_\theta \tilde{\mathcal{L}}
-$ more statistically efficient. Specifically for the problem of selecting relevant parameters
-\citet{molchanov_variational_2017} further improve the efficiency of the estimator of the $
-  \nabla_\mu \tilde{\mathcal{L}}
-$ by introducing \textit{additive noise parameterization}. They revert the $(\mu, \alpha)$
-parameterization back to the equivalent $(\mu, \sigma^2)$, since it stabilizes gradients
-of SGVB \eqref{eq:sgvb_estimator}, by rendering the gradient with respect to $\mu$ independent from
-the local output noise, injected by \eqref{eq:r-gauss-trick}. The relevance $\alpha$ is
-calculated using the ratio $
-  \tfrac{\sigma^2}{\mu^2}
-$ when needed in the divergence term.
 

### 2020-06-20 paper/paper.tex
11 (5) condensed the edits for redoing the proof of the log-alpha grad in the appendix

@@
 \citet{hirose_complex-valued_2009} argues that the combined phase-magnitude effect of
-$\cplx$-valued transformations reduces removes the excess degrees of freedom, that cause
-degenerate transformation in $\real$-valued networks with twice the feature dimensions.
+$\cplx$-valued transformations removes the excess degrees of freedom, that cause
+degenerate transformations in $\real$-valued networks with twice the feature dimensions.
 Their study demonstrates superiority of $\cplx$VNN in landmine detection using ground
 penetrating radar imaging. Other examples, where $\cplx$-valued networks have outperformed
-$\real$-valued networks include magnetic resonance \citep{hui_mri_1995,wang_deepcomplexmri_2020}
+$\real$-valued networks, include magnetic resonance \citep{hui_mri_1995,wang_deepcomplexmri_2020}
 and radar imaging \citep{haensch_complex-valued_2010,zhang_complex-valued_2017}, music
@@
 have lowered the out-of-band power leakage with a $\cplx$-valued network for digital
-signal predistortion. The networks have also been applied to non $\cplx$-valued domains,
+signal predistortion. The networks have also been applied to non-$\cplx$-valued domains,
 such as image classification \citep{popa_complex-valued_2017}, sequence modelling
@@
 $\cplx$VNN, inspired by the results of \citet{gale_state_2019}, and motivated by seldom
-application of Bayesian Inference to $\cplx$-valued networks \citep{popa_complex-valued_2018}
+application of Bayesian Inference to $\cplx$-valued networks \citep{popa_complex-valued_2017}
 and apparent scarcity of compression methods specific to them. We assess the performance-%
@@
 image classification on MNIST-like and CIFAR10 datasets and music transcription on MusicNet.
-%
-% THIS SHOULD GO TO CONCLUSIONS!
-%
-% L0 and dropout work in the low-to-mid sparsity range, variational dropout consistently
-% ranked behind L0 on Transformer, and was bested by magnitude pruning for sparsity
-% levels of 80\% and up. Variational dropout consistently produces models on-par or better
-% than magnitude pruning on ResNet-50, and l0 fails to produce sparse models at all.
-We expect the overall conclusion of \citet{gale_state_2019} to carry over to $\cplx$VNN,
-since there is nothing fundamentally different in $\cplx$-valued versions of the methods
-they study, except for the need to operate on pairs of parameters.
 
@@
 Dropout, and sec.~\ref{sec:c_valued_networks} provides a brief summary of the inner
-working of complex-valued networks. The main contribution of this study is presented in
-sec.~\ref{sec:c_variational_dropout}, where we outline the details of different variational
-approximations and priors and derive the penalty terms in the evidence lower bound.
-In sec.~\ref{sec:experiments} we evaluate the sparsification rate, compare the resulting
-performance of various $\cplx$-networks proposed in prior work, and discuss the outcomes.
+workings of complex-valued networks. The main contribution of this study is presented
+in sec.~\ref{sec:c_variational_dropout}, where we provide the details of $\cplx$-valued
+variational sparsification method. In sec.~\ref{sec:experiments} we estimate the compression
+and performance trade-off on shallow and deep $\cplx$-valued networks, and discuss the
+outcomes.
 
@@
 % overview
-In broad terms Bayesian Inference is a principled framework of reasoning about uncertainty
-and a tool to update prior beliefs about model's parameters in accordance with evidence
-or empirical data into a posterior distribution. The posterior is useful for inference
+In broad terms Bayesian Inference is a principled framework for reasoning about uncertainty
+and updating prior beliefs about model's parameters in accordance with evidence or
+empirical data into a posterior distribution. The posterior is useful for inference
 regarding unobserved data, predictive statistics, parameter confidence regions, and
@@
   p(D \mid \omega)
-    = \prod_i \log p(x_i \mid \omega)
+    = \prod_i p(x_i \mid \omega)
     % $D$ conditional independence given parameters $\omega$
@@
 to use other objectives, provided the true posterior $p(\omega \mid D)$ is evaluated only
-through $\log p(D \mid \omega)$ and $\log \pi(\omega)$, \citep{ranganath_operator_2018}.
+through $\log p(D \mid \omega)$ and $\log \pi(\omega)$, \citep{ranganath_operator_2016}.
 
@@
 \emph{Stochastic Variational Inference}, which uses stochastic gradient optimization of
-\eqref{eq:elbo_general} based on inexpensive noisy unbiased gradient estimates of ELBO
+\eqref{eq:elbo_general} based on noisy unbiased gradient estimates of ELBO
 computed on random mini-batches from the dataset. \citet{titsias_doubly_2014} translated
-dependence on $\theta$ from $q_{\theta}$ to the functions inside the expectations of ELBO
-and propose \emph{Doubly Stochastic Variational Inference}, which computes unbiased gradient
-estimator based on both dataset subsampling and random draws from variational distribution
-$q_{\theta}$. Note, that the KL divergence term can replaced by its unbiased differentiable
-finite-sample estimator without forfeiting convergence of (doubly) SVI.
+the dependence on location–scale parameters of $q_{\theta}$ to the function inside its
+expectation and proposed \emph{Doubly Stochastic Variational Inference}. DSVI constructs
+an unbiased finite-sample estimator of the gradient of \eqref{eq:elbo_general} by both
+subsampling the dataset and sampling from $q_{\theta}$, without forfeiting convergence
+of SVI.
 
@@
 $ differentiable with respect to $\theta$. The estimator of \eqref{eq:elbo_general}
-for $L$ reparameterized draws per datapoint in mini-batch of size $M$, is given by
+with $L$ reparameterized draws per element in the mini-batch of size $M$ is given by
 \begin{equation}  \label{eq:sgvb_estimator}
@@
 \end{equation}
-where $(x_{i_k})_{k=1}^M$ is a random mini-batch from $D$ and $
+where $(x_{i_k})_{k=1}^M$ is a random subsample from $D$ and $
   (\varepsilon_{lk})_{l=1}^L
-$ are $M$ independent iid samples from $p_\varepsilon$. \citet{figurnov_implicit_2019}
+$ are $k=1..M$ independent iid samples from $p_\varepsilon$. \citet{figurnov_implicit_2018}
 extended the scope of the reparameterization gradients to include continuous distributions
@@
 %
-The class of models that are allow this include non-recurrent computational graphs,
-exemplified by neural networks with parameters $\omega \sim q_\theta$. In this case
+The class of models that allow this include non-recurrent computational graphs,
+exemplified by neural networks with parameters $\omega \sim q_\theta$. In their case,
 \eqref{eq:sgvb_estimator} would require that the \emph{entire} set of network's parameters
-$\omega$ be independently drawn for each element in the mini-batch. However, noting
-that the parameters in a network naturally decompose into subsets with non-overlapping
-layer-wise effects, it is standard to assume that the approximation $
+$\omega$ be independently drawn for each element in the mini-batch. Since that the
+parameters in a network naturally split into subsets with non-overlapping layer-wise
+effects, it is standard to assume that the approximation $
   q_\theta(\omega)
 $ is factorized over layers. Furthermore, if $
-  \omega = W \in \mathbb{R}^{n\times m}
+  % \omega =
+  W \in \mathbb{R}^{n\times m}
 $ in a linear layer $
@@
 could occur during training. \citet{wang_fast_2013} argued that the overall effect of
-binary dropout on the intermediate outputs can be approximated by a Gaussian with weight-input
-dependent mean and variance via the Central Limit Theorem. \citet{srivastava_dropout:_2014}
+binary Dropout on the intermediate outputs can be approximated by a Gaussian with weight-input
+dependent mean and variance via the Central Limit Theorem. \citet{srivastava_dropout_2014}
 proposed using independent $\mathcal{N}(1, 1)$ multiplicative noise, arguing that higher
@@
 \citet{kingma_variational_2015} provided a unifying perspective on Dropout, DropConnect
-\citep{wan_regularization_2013}, and Gaussian dropout \citep{wang_fast_2013} through
-the lens of Variational Inference methods and propose \emph{Variational Dropout}. They
-argued that the multiplicative noise introduced by Dropout methods induces a distribution
-equivalent to a fully factorized variational posterior of the form $
+\citep{wan_regularization_2013}, and Gaussian Dropout \citep{wang_fast_2013} through
+the lens of Variational Inference and propose \emph{Variational Dropout}. They argued
+that the multiplicative noise introduced by Dropout methods induces a distribution
+equivalent to a fully factorized variational posterior $
   q_\theta(\omega) = \prod_j q_{\theta}(\omega_j)
-$, where $q_{\theta}(\omega_j)$ is $\omega_j = \mu_j \xi_j$ with $
-  \xi_j \sim p_\theta(\xi_j)
-$ iid from some $p_\theta(\xi)$.
+$, where $q_{\theta}(\omega_j)$ is $\omega_j = \mu_j \eta_j$ with $
+  \eta_j \sim p_\theta(\eta_j)
+$ iid from some $p_\theta(\eta)$.
 %
 % Binary dropout with rate $p \in (0, 1)$ uses $
-%   p_\xi
+%   p_\eta
 %     = \mathcal{B}\bigl(
@@
 % and optimizing it in \eqref{eq:elbo_general} with an appropriate penalty term. Thus,
-%
-Variational Dropout assumes fully factorized Gaussian approximate posterior $
+
+Variational Dropout uses \emph{fully factorized Gaussian} approximation $
   q_\theta(\omega)
@@
   \pi(\omega_j) \propto \lvert \omega_j \rvert^{-1}
-$. \citet{molchanov_variational_2017} noticed that $\alpha_j$ reflect the relevance of the
+$. \citet{molchanov_variational_2017} noticed that $\alpha_j$ reflects the relevance of the
 parameter $\omega_j$ it is associated to by being the ratio of its squared mean to its
@@
 % {louizos_bayesian_2017} eq. (11) variance -> gaussian entropy -> informative bits
-%
-
-Simultaneously \citet{molchanov_variational_2017} proposed to use \emph{Additive Noise
-Parameterization} in the factorized Gaussian $q_\theta(\omega)$ in conjunction with the
-Local Reparameterization Trick. They reverted the $(\mu, \alpha)$ parameterization back
-to the equivalent $(\mu, \sigma^2)$, arguing that it reduces the variance of the SGVB
-\eqref{eq:sgvb_estimator}, by rendering the gradient with respect to $\mu_{ij}$ independent
-from the local output noise, injected by \eqref{eq:r-gauss-trick}. This improvement is
-especially important for model pruning, since $\mu_{ij}$ of relevant parameters are used
-as point estimates of their values.
-
-Due to factorization alternative parameterization, the term $KL(q_\theta \| \pi)$ in
-\eqref{eq:sgvb_estimator} of Sparse VD unravels into $
+% They also proposed to estiamte bit precision for quantization based on parameter's
+% estimated uncertainty (variance or entropy).
+
+Simultaneously \citet{molchanov_variational_2017} proposed to use \emph{additive noise
+parameterization} in the factorized Gaussian $q_\theta(\omega)$ in conjunction with the
+local reparameterization trick. They reverted the $(\mu, \alpha)$ parameterization in
+$q_\theta(\omega)$ back to $(\mu, \sigma^2)$, arguing that it reduces the variance of the
+SGVB \eqref{eq:sgvb_estimator}, by rendering the gradient with respect to $\mu$ independent
+from the local noise, injected by \eqref{eq:r-gauss-trick}. This modification is important
+for pruning, since $\mu$ of a relevant parameter serves as the estimate of its value.
+
+Due factorization assumption, the term $KL(q_\theta \| \pi)$ in \eqref{eq:sgvb_estimator}
+for Sparse VD unravels into $
   \sum_j K(\tfrac{\sigma^2_{j}}{\mu_{j}^2})
@@
 \end{equation}
-\citet{kingma_variational_2015} approximated $K(\alpha)$ over $\alpha \in (0, 1)$ by
-a non-linear polynomial, and later \citet{molchanov_variational_2017} refined the
-approximation of \eqref{eq:improper-kl-div-real} by a nonlinear regression based on
-sigmoid and soft-plus.
+\citet{kingma_variational_2015} approximated $K(\alpha)$ over $\alpha \in (0, 1)$ by a
+polynomial with a logarithmic term, and later \citet{molchanov_variational_2017} refined
+the approximation of \eqref{eq:improper-kl-div-real} by weighted sum of a sigmoid and a
+soft-plus term.
 % see p.6 sec 3.4 of kingma_variational_2015
-In appendix~\ref{sec:real-chisq-grad} we verify the value and the derivative of their
-approximation against the Monte-Carlo estimate of \eqref{eq:improper-kl-div-real} for
-$\alpha$ varying over a fine logarithmic grid and the gradient of \eqref{eq:improper-kl-div-real},
-for which we obtain an exact expression.
+In appendix~\ref{sec:real-chisq-grad} we verify the derivative of their approximation
+against a Monte-Carlo estimate for $\alpha$ varying over a fine $\log$-scale grid and
+the exact expression for gradient of \eqref{eq:improper-kl-div-real}.
 % (!) good for SGVB: gradient-based methods require unbiased gradient estimates
@@
 \citet{kharitonov_variational_2018} addressed theoretical issues with improper prior
-$\pi$, emphasized by \citet{hron_variational_2018}, and proposed Sparse VD based on
-\textit{Automatic Relevance Determination} procedure. ARD replaces $\pi(\omega_j)$ by
-a proper Gaussian ARD prior $
+$\pi$ in Sparse VD, emphasized by \citet{hron_variational_2018}, and proposed
+\emph{Automatic Relevance Determination} Variational Dropout, by replacing $\pi(\omega_j)$
+with a proper Gaussian prior $
   \pi_\lambda(\omega_j) = \mathcal{N}(\omega_j \vert\, 0, \tau_j^{-1})
-$ with learnable precision $\tau_j > 0$ \citep{neal_bayesian_1996}, thereby recasting
-the VD as the \textit{Empirical Bayes} approach, which performs Bayesian Inference over
-$\omega$, but uses Maximum Likelihood point-estimates for the hyper-parameters $\lambda$,
+$ with learnable precision $\tau_j > 0$ \citep{neal_bayesian_1996}. This recast the VD
+as the \emph{Empirical Bayes} approach, which performs Bayesian Inference over $\omega$,
+but uses Maximum Likelihood estimates for the hyper-parameters $\lambda$,
 \citep{mackay_bayesian_1994}. Maximizing \eqref{eq:sgvb_estimator} over $\tau$, holding
@@
   K(\alpha)
-    = \frac12 \sum_j \log{\bigl(1 + \tfrac1{\alpha} \bigr)}
+    = \frac12 \log{\bigl(1 + \tfrac1{\alpha} \bigr)}
     \,.
@@
 
+% practical difference between them?
+
 % subsection dropout (end)
@@
 
+% implementation
+$\cplx$-valued neural networks are networks that rely on the arithmetic in the complex
+domain. To achieve this implementations of $\cplx$VNN use the geometric representation
+of a complex number as paired \emph{real} and \emph{imaginary} values, $\cplx \simeq \real^2$,
+ensuring that the resulting $\real$-valued computational graph respects $\cplx$-arithmetic.
+For example, $
+  f\colon \cplx^n \to \cplx^m
+$ is identified with a real vector-valued function $
+  F\colon \real^{2 m} \to \real^{2 m}
+$ defined via $
+  F(u, v) = (\Re f(u + \iu v), \Im f(u + \iu v))
+$, $\Re$ and $\Im$ denoting the real and imaginary parts, respectively. When $f$ is
+a $\cplx$-valued linear transformation, the computations are ``wired'' so that
+\begin{equation}  \label{eq:cplx-lin-op}
+  % F\colon
+  %   (u, v)
+  %     \mapsto \Bigl(
+  %       P u - Q v,
+  %       P v + Q u
+  %     \Bigr)
+  F(u, v)
+    =
+    \begin{pmatrix}
+      P u - Q v \\
+      P v + Q u
+    \end{pmatrix}
+    = \begin{pmatrix}
+      P & - Q \\ Q & P
+    \end{pmatrix} \begin{pmatrix}
+      u \\ v
+    \end{pmatrix}
+    \,,
+\end{equation}
+with $
+  P, Q \colon \real^{n} \to \real^{m}
+$ given by $P = \Re f$ and $Q = \Im f$ restricted to $\real^{n}$.
+% The downside is that, for instance, one $\cplx$-valued convolution requires up to
+% four $\real$-valued convolution operations.
+%
+Non-linearities in $\cplx$VNN can be hyperbolic functions or maps that operate on
+$\cplx$ numbers in planar form, $
+  z \mapsto \sigma(\Re{z}) + \iu \sigma(\Im{z}) % split
+$, or polar form $
+  % z \mapsto \sigma(\lvert z\rvert, \arg{\!(z)})
+  r e^{\iu \phi} \mapsto \sigma(r, \phi)
+$.
+% \citep{savitha_2011,hirose_generalization_2012,arjovsky_unitary_2016,guberman_complex_2016}
+
+This $\cplx \simeq \real^2$ identification allows straightforward retrofitting of $\cplx$VNN
+into existing $\real$-valued auto-differentiation frameworks for deep learning. This
+act is backed by Wirtinger ($\cplx\real$) calculus, which enables generalized treatment
+of functions of complex argument, by regarding $z$ and its \emph{complex conjugate}
+$\conj{z}$ as independent variables and defining derivative operators with respect to
+them through partial derivatives with respect to real and imaginary parts. These definitions
+simplify manual analysis of $\cplx$ derivatives and satisfy the product and chain rules, respect
+complex conjugation and linearity for $\cplx \to \cplx$ maps, and such were used to define
+$\cplx$ version of back-propagation, \citep{benvenuto_complex_1992,guberman_complex_2016}.
+However, since auto-differentiation frameworks can algorithmically handle computational
+graphs of arbitrary complexity, explicit use of Wirtinger derivatives is not required,
+especially considering the fact that the direction of the steepest ascent of a $
+  \cplx \to \real
+$ function is given by complex conjugate gradient $\nabla_{\conj{z}}$, which coincides
+with the classical gradient of the same function viewed as $\real^2 \to \real$,
+(see appendix~\ref{sub:wirtinger_calculus}).
+%
+% in natively $\cplx$-valued backprop it would be necessary to modify the existing sgd
+% to explicitly use $\nabla_{\conj{z}} f(z)$, while no such modification is necessary
+% in re-im. If some inner activation of a $\cplx$VNN is holomorphic, i.e. satisfies
+% Cauchy-Riemann conditions, then that particular step of in the chain rule that is
+% backprop can be simplified by assuming one piece of the tracked gradient to be exact
+% zero. But other wise it is necessary to track both $\partial_{\conj{z}}$ and $\partial_{z}$.
+%
+% Training a $\cplx$VNN involves optimizing a real-valued objective with respect to
+% complex valued arguments.
+%
+% The computed gradients are theoretically justified
+% - CR dictates the it is necessary to track both $z$ and $\conj{z}$ derivatives
+% - the direction of largest increase in f: C-R is given by the gradient with
+% respect to the conjugate, which coincides in the re-im representation with 
+% the ordinary gradient wrt u and v
+% - the Chain Rule in CR holds and when a holomorphic C-C function is backproped
+% the autodiff just wastes cycles on computing its conj-derivative (rather than assuming
+% it to be zero)
+
 % Although $\cplx$-valued dense layers and back-propagation have been around since early
 % 1990-s, one of the earliest accounts
-
 Development of deep $\cplx$-valued networks has been active. \citet{haensch_complex-valued_2010}
@@
 $\cplx$-valued batch-normalization and weight initialization, \citet{wolter_complex_2018}
-investigated different $\cplx$-valued gating mechanisms for RNNs, \citet{yang_complex_2019}
+investigated different $\cplx$-valued gating mechanisms for RNNs, and \citet{yang_complex_2019}
 proposed $\cplx$-valued self-attention and complex transformer architecture. It merits
@@
 
-We propose to use fully factorized complex Gaussian posterior approximation and $\cplx$
-variant of the local reparameterization trick to extend Bayesian Dropout techniques to
-$\cplx$-valued networks. In this section we describe the approximation and derive the
-divergence penalties in \eqref{eq:sgvb_estimator}. Similarly to $\real$-valued Variational Dropout,
-the proposed $\cplx$-valued extension can be straightforwardly enhanced to provide
-structured sparsity.
+In this section we develop Sparse Variational Dropout for $\cplx$VNN by using a fully
+factorized complex Gaussian posterior approximation. We outline the $\cplx$ version of
+the local reparameterization trick and derive the divergence penalties in \eqref{eq:sgvb_estimator}.
+The proposed $\cplx$-valued extension can readily be a part of a hierarchical variational
+approximation for structured sparsity \citep{louizos_bayesian_2017}.
 
@@
 \end{equation}
-The trick requires three operations, i.e. $b + \mu x$, $\Sigma \lvert x \rvert^2$ and
-$C x^2$ with the complex modulus and square applied elementwise, and can be applied to
-any layer, the output of which depends linearly on its parameters, such as convolutional,
-affine, and bilinear transformations ($
-  (x, z) \mapsto x^\top W^{(j)} z + b_j
-$). Similar to $\real$ case, Variational Dropout for $\cplx$ convolutions draws independent
-realizations of $W$ for each spatial patch in the input \citep{molchanov_variational_2017}.
-This provides faster computations and better statistical efficiency of the SGVB gradient
-estimator by eliminating correlation from overlapping patches \citep{kingma_variational_2015}
-and allowing \eqref{eq:cplx-gauss-trick} to leverage $\cplx$ convolutions of the relation
-and variance kernels with elementwise complex squares $x^2$ and amplitudes $\lvert x \rvert^2$.
+This is the $\cplx$-Gaussian version of the local reparameterization trick \eqref{eq:r-gauss-trick}.
+It requires three matrix-vector operations: $\cplx$-valued $b + \mu x$ and $C x^2$,
+and $\real$-valued $
+  \Sigma \lvert x \rvert^2
+$, where $C_{ij} = \Sigma_{ij} \xi_{ij}$ and the complex modulus and square are applied
+elementwise. \eqref{sub:c_gauss_and_local_rep} can be applied to any layer, the output
+of which depends linearly on its parameters, such as convolutional, affine, and bilinear
+transformations ($
+  (x, z) \mapsto b_j + x^\top W^{(j)} z
+$). Similar to the $\real$ case, $\cplx$ convolutions draw independent realizations of $W$
+for each spatial patch in the input \citep{molchanov_variational_2017}. This provides
+faster computations and better statistical efficiency of the SGVB gradient estimator
+by eliminating correlation from overlapping patches \citep{kingma_variational_2015} and
+allowing \eqref{eq:cplx-gauss-trick} to efficiently leverage $\cplx$ convolutions of
+the relation and variance kernels with elementwise complex squares $x^2$ and amplitudes
+$\lvert x \rvert^2$.
 % Weight sharing is essentially pushed to shared variational parameters $\theta$ in the approximation $q_\theta$.
@@
 
-For a fully factorized approximation $q(\omega)$ and factorized prior belief $
+For a fully factorized approximation $q(\omega)$ and factorized prior $
   \pi(\omega) = \prod_{ij} \pi(\omega_{ij})
-$, the divergence term in ELBO \eqref{eq:sgvb_estimator} is
+$, the divergence term \eqref{eq:sgvb_estimator} is
 \begin{equation}  \label{eq:elbo-general-kl-div}
@@
 We set $\beta = 2$ to make the divergence term depend only on $\alpha$ and add $\gamma$
-so that the right-hand side is nonnegative \citep[eq.(84)]{lapidoth_capacity_2003}.
+so that the right-hand side is non-negative \citep[eq.(84)]{lapidoth_capacity_2003}.
 %
@@
 forward evaluation, which speeds up gradient updates.
-% Gradient-based optimiziation of \eqref{eq:sgvb_estimator} usually does not use the value of the objective. 
-% In stochastic gradient methods are concerned more with the gradient, induced by the objective
-% function, rather than its value.
+% Gradient-based optimiziation of \eqref{eq:sgvb_estimator} usually does not use the value
+% of the objective.  In stochastic gradient methods are concerned more with the gradient,
+% induced by the objective function, rather than its value.
 
@@
 %
-In Empirical Bayes the prior adapts to the observed data, i.e. \eqref{eq:sgvb_estimator} is optimized
-w.r.t. $\tau$ of each weight's prior. Since divergence sits in \eqref{eq:sgvb_estimator} with negative
-sign, optimal $
+In Empirical Bayes the prior adapts to the observed data, i.e. \eqref{eq:sgvb_estimator}
+is optimized w.r.t. $\tau$ of each weight's prior. The Maximum Likelihood estimator
+of $\tau$ is given by the minimizer \eqref{eq:emp-bayes-kl-div}, i.e. $
   \tau^\ast = (\sigma^2 + \lvert \mu \rvert^2)^{-1}
-$ is found by minimizing \eqref{eq:emp-bayes-kl-div}, which gives
+$, thereby giving
 \begin{equation}  \label{eq:emp-bayes-opt-kl}
@@
 
-% The training consists of three successive stages: ``dense'' $\to$ ``sparsify'' $\to$ ``fine-tune''.
-
-At the \textit{``dense''} stage every network is fit ``as-is'', retaining its original
-non-Bayesian architecture, and using only the likelihood term from \eqref{eq:sgvb_estimator} without
-variational dropout.
-
-During the \textit{``sparsify''} stage we make every layer Bayesian and apply $\cplx$-variational
-dropout sec.~\ref{ssub:vd_prior} (or sec.~\ref{ssub:ard_prior}) or its $\real$ counterpart.
-We inject a coefficient $
+% The training consists of three successive stages: ``pre-train'' $\to$ ``sparsify'' $\to$ ``fine-tune''.
+At the \emph{``pre-train''} stage every network is fit ``as-is'' using deterministic layers
+and only the likelihood term from \eqref{eq:sgvb_estimator}.
+
+During the \emph{``sparsify''} stage we make every layer stochastic and apply $\cplx$-valued
+variational sparsification (sec.~\ref{ssub:vd_prior}, ~\ref{ssub:ard_prior}) or its $\real$
+counterpart. We inject a coefficient $
   C \in (0, 1]
-$ at the KL divergence term in \eqref{eq:sgvb_estimator} to study the attainable sparsity levels:
+$ at the KL divergence term in \eqref{eq:sgvb_estimator}:
 \begin{equation}  \label{eq:elbo_with_coef}
@@
   + \frac1{M} \sum_{k=1}^M
-      \log p_{\phi}(z_{i_k} \mid g(\varepsilon_k; \theta))
+      \log p_{\phi}(x_{i_k} \mid g(\varepsilon_k; \theta))
   \,.
@@
 \end{equation}
-By varying $C$ we adjust the importance of the sparsifying prior in learning $q_\theta(W)$,
-meaning that higher value yields more irrelevant parameters during inference and makes
-layers sparser upon termination of this stage.
+In contrast to \cite{molchanov_variational_2017}, who anneal $C$ from zero to one during
+training, we use constant $C$ and vary it between runs. This allows us to explore the
+compression-performance profile by balancing model's likelihood and posterior's penalty
+for diverging form the sparsifying prior in \eqref{eq:elbo_with_coef}. In particular,
+higher $C$ implies higher sparsity.
 % RFC: citation needed fot this "trick". Cite $\beta$-VAE maybe?
@@
 
-We conduct an experiment on the CIFAR10 classification dataset \citep{krizhevsky_learning_2009}
-comprising $32\times 32$ color images of $10$ classes to study the performance-compression
-trade-off of a moderately large deep network.
+Having verified the $\cplx$ variational sparsification method on MNIST-like datasets
+and simple models, we turn to the CIFAR10 dataset comprising $32\times 32$ colour
+images of $10$ classes \citep{krizhevsky_learning_2009} and focus on the VGG16 network
+\citep{simonyan_very_2015}.
+%
 % same experimental setup as in MNIST, describe the VGG16 model and its cplx-valued modification
-The experiment is set up similarly to MNIST-like experiment, except that we train $\real$
-VGG16 network \citep{simonyan_very_2015} and its $\cplx$ variant, in which we have replaced
-$\real$-valued layers with their $\cplx$-valued counterparts. $\real$ and $\cplx$ VGG16 have
-the same feature sizes in intermediate layers.
-
+We train the VGG16 network and its $\cplx$ variant, in which we have replaced $\real$-valued
+layers with their $\cplx$-valued counterparts. We do not halve or double the features
+in any network, since the goal of this experiment is to assess the trade-off for a deep
+convolutional network.
+%
 % differences with mnist
-Unlike experiment in sec.~\ref{sub:mnist_like_datasets}, we consider the raw features only,
-use full training split, and allocate $20$, $40$, and $20$ epochs to each stage. During training
-the mini-batch of $128$ samples is randomly augmented by randomly flipping horizontally and
-cropping. Random cropping is done by zero-padding each side by four pixels and extracting a
-random $32\times 32$ patch from the $40\times 40$ intermediate image.
+Unlike experiment in sec.~\ref{sub:mnist_like_datasets}, we consider the raw features
+only, use full training split and allocate $20$, $40$, and $20$ epochs to each stage.
+During training every mini-batch of $128$ samples is augmented by random horizontal flipping
+and random cropping, which is done by zero-padding the image with four pixels and extracting
+a $32\times 32$ patch from the $40\times 40$ intermediate image.
 %
@@
   \{\tfrac32 2^{-\tfrac{k}2} \colon k=7, \cdots, 15\}
-$, compare VD and ARD methods, and measure accuracy on CIFAR10 test split.
+$, compare $\real / \cplx$ VD and ARD methods and measure accuracy on the usual test split.
 
@@
   \caption{%
-    The compression-accuracy frontier for VGG16 ($\real$ and $\cplx$) on CIFAR10.
+    The compression-accuracy profile for the $\real$ and $\cplx$ VGG16.
   }
@@
 % draw some conclusions
-Figure~\ref{fig:figure__cifar10__trade-off} shows that, although ARD method offers slightly
-less compression, it makes up for it by marginally better accuracy post fine-tune. VGG16 and
-$\cplx$-VGG16 exhibit similar declining compression-accuracy trade-off, but due to higher
-capacity $\cplx$-valued network yields higher accuracy \citep{monning_evaluation_2018}. Unlike
-MNIST, fine-tuning stage significantly improves the test performance, which, we speculate, might
-be due to dataset augmentation and deeper model.
-% reword this sentence
+The compression-accuracy curve in figure~\ref{fig:figure__cifar10__trade-off} shows that
+it is possible to confidently achieve around $\times100$ compression of a deep $\cplx$VNN
+without losing accuracy, provided the network is fine-tuned after undergoing Variational
+sparsification. Regarding methods themselves, $\cplx$-VD and $\cplx$-ARD follow the same
+declining compression-accuracy pattern, but for the same setting $C$ the latter provides
+slightly less compression with marginally better accuracy.
 
@@
 % describe musicnet as in Trabelsi et al. (2017) also get some hints from thickstun_learning_2017
-We use MusicNet \citep{thickstun_learning_2017}, an audio dataset of $330$ annotated
-musical compositions, to investigate compressibility of the $1d$ VGG-like $\cplx$-convent
-proposed by \citet{trabelsi_deep_2018}. Similarly to the study, we downsample the audio
-from 44.1kHz to 11kHz, retain only $84$ out of $128$ labels, and hold-out the same validation
-and test compositions, on which we score the models with the pooled average precision.
-Each epoch lasts for $1000$ random mini-batches of the remaining $321$ pieces. The input
-features are $\cplx$-valued Fourier transformed windows of $4096$ samples from each waveform.
-The label vectors are taken from annotations at the middle of the window.
-
-Experiments with the uncompressed model aimed at replicating the result of \citet{trabelsi_deep_2018}
-have shown that early stopping almost always terminates much sooner, than $200$ epochs used
-in their study: within the first $10-20$ epochs with the validation performance peaking at
+
+% The experimental results of the experiments in previous sections indicate that the proposed
+% $\cplx$-valued Sparse Variational Dropout achieves the goal of network compression.
+% Inspired by this we set out to investigate its effects on in the domain where it has
+% been shown that CVNN outperform rvnn.
+
+% Prior experiments demonstrated that the $\cplx$-valued variational sparsification
+% what can be expected from prior research.
+MusicNet is a corpus of $330$ annotated classical music recordings used for learning
+feature representations for music transcription tasks \citep{thickstun_learning_2017}.
+\citet{trabelsi_deep_2018} have proposed a $1d$ VGG-like $\cplx$-valued network that
+surpassed a similar $\real$-valued network and achieved $72.9\%$ pooled \emph{Average
+Precision} on this dataset. Recently \citet{yang_complex_2019} have reported $74.2\%$
+AP with a $\cplx$-valued transformer, \citet{thickstun_invariances_2018} have achieved
+$77.3\%$ with a four-layer $\real$-valued network on $\log$-spaced spectrogram, and
+\citet{draguns_residual_2020} report $78.0\%$ with a residual-shuffle-exchange network.
+
+In this experiment we seek to compress of the $\cplx$VNN proposed by \citet{trabelsi_deep_2018}.
+%
+The dataset is split into the same validation and test samples and handled identically
+to their study. The input features are $\cplx$-valued Fourier transforms of $4096$-sample
+windows from each waveform, and the label vectors are taken from annotations at the middle
+of the window. Each epoch lasts for $1000$ random mini-batches of the musical pieces.
+% downsample the audio from 44.1kHz to 11kHz, retain only $84$ out of $128$ labels,
+% and hold-out the same validation and test compositions
+% 
+However, we deviate from the set-up used by \citet{trabelsi_deep_2018} by clipping $\ell_2$
+norm of the gradients to $0.05$ and shifting the low frequencies of the input to the centre
+to maintain spatial locality for convolutions.
+
+Experiments with the uncompressed model aimed at replicating the original result have
+shown that early stopping almost always terminates within the first $10-20$ epochs of
+the $200$ epochs used in their study, due to the validation performance peaking at
 $10-15$ epochs and steadily declining afterwards.
 %
-Thus we opt to use shorter stages: $12$, $32$ and $50$ epochs (sec.~\ref{sub:staging}), with
-early stopping activated only during the ``fine-tune'' stage. To keep the learning rate schedule
-consistent, we scale the learning rate of $10^{-3}$ after $5$, $10$, and $20$-th epoch by
-$\tfrac1{10}$, $\tfrac1{20}$ and $\tfrac1{100}$, respectively.
-
-We deviate from the set-up used by \citet{trabelsi_deep_2018} by clipping $\ell_2$ norm of the
-gradients to $0.05$ and shifting the low frequencies of the input to the centre to maintain
-spatial locality for convolutions.
-
-We test complex ARD (sec.~\ref{ssub:ard_prior}) and VD (sec.~\ref{ssub:vd_prior}) methods
-and vary $
-  C \in \{\tfrac14, \tfrac12, \tfrac34, 1\} \cdot 10^{-k}
-$ for $k=1, 2, 3$, while keeping $\tau$ at $-\tfrac12$. The performance is measured after
-``dense'' stage, before the beginning and upon termination of fine-tuning.
+Thus we opt to use shorter stages: $12$, $32$ and $50$ epochs (sec.~\ref{sub:staging}),
+with early stopping activated only during the ``fine-tune'' stage. To keep the learning
+rate schedule consistent, we scale the learning rate of $10^{-3}$ after $5$, $10$, and
+$20$-th epoch by $\tfrac1{10}$, $\tfrac1{20}$ and $\tfrac1{100}$, respectively.
+
+We explore the $\cplx$-VD and $\cplx$-ARD methods by varying $C$ over the grid $
+  \{\tfrac14, \tfrac12, \tfrac34, 1\} \cdot 10^{-k}
+$ with $k=1, 2, 3$, while keeping $\tau$ at $-\tfrac12$. The performance is measured after
+``pre-train'' stage, just before and upon termination of fine-tuning.
 %
@@
 
-Figure~\ref{fig:musicnet__trade-off} shows the resulting performance-compression frontier.
-ARD slightly outperforms VD in terms of performance, but both deliver similar compression
-rates. The trade-off demonstrates that with the proposed $\cplx$-valued variational dropout
-methods (sec.~\ref{sec:c_variational_dropout}) and post-sparsification fine-tuning it is
-possible to achieve average precision level comparable to the result of \citet{trabelsi_deep_2018}
-with a model compressed $50\times$-$200\times$. Furthermore, the $k_3$ model, compressed
-$110 \times$ with $\cplx$ VD, outperforms its uncompressed baseline, but yields lower
-performance than the full model.
-
+The performance-compression frontier in figure~\ref{fig:musicnet__trade-off} shows that
+VD and ARD deliver similar compression rates, but ARD slightly outperforms in terms of
+the average precision at the cost of marginally lower compression.
+%
+At $\times100$ compression level the $k_3$ model outperforms its
+uncompressed baseline, but yields lower AP score than the full model. In conjunction with
+post-pruning fine-tuning, both $\cplx$-valued variational sparsification methods achieve
+average precision level comparable to the result of \citet{trabelsi_deep_2018} with a
+network having $50$-$200$ times less parameters.
+% any conclusions related to k_3???
+
+% testing the fx of the threshold
 \begin{figure}[!t]
   \centering
+  \includegraphics[width=1\columnwidth]{figure__musicnet__threshold__C__DeepConvNet.pdf}
+  \caption{%
+    The effect of fine-tuning on performance-compression curves for $
+      C\in \{\tfrac1{20}, \frac1{200}\}
+    $ in \eqref{eq:elbo_with_coef}.
+  }
+  \label{fig:hist__and__threshold__tradeoff}
+\end{figure}
+
+% effects of extra training epochs and the impact of tau
+We take the full models compressed with $C \in \{\tfrac1{20}, \frac1{200}\}$ and re-run
+only the fine-tuning stage for various pruning thresholds $
+  \tau \in \{\tfrac{k}2\colon k=-8\cdots+8\}
+$. The performance-compression curves depicted in figure~\ref{fig:hist__and__threshold__tradeoff}
+are parameterized by decreasing $\tau$ from left to right, since models are not re-compressed
+which makes $\tau$ monotonically affect the compression rate. From \eqref{eq:elbo_with_coef}
+and the relative positions of the curves it can be concluded that $C$ has a much more
+substantial impact on the compression profile of each method, than the choice of the
+pruning threshold.
+% coarser grid than in top plot in order not to wait for 20 compute days, but 9.5 on
+% 4 x Geforce 1080Ti, 256 Gb, core-i7 machine, running 4*2 experiments in parallel
+
+% takeaway: fine tune seems to improve performance for highly compressed models, but
+% within a limit. Worth a try for moderately compressed models, but willl must likely
+% overfit for undercompressed models. Varying $C$ in \eqref{eq:elbo_with_coef} affects
+% sparsity more strongly, than varying $\tau$. But this is only observational.
+
+% why is there such a dramamtic difference in impact of ``fine-tune''?
+We provide the following interpretation of the apparent contrast in performance impact
+borne by fine-tuning between less than $\times50$ and higher than $\times100$ compression
+regimes in figure~\ref{fig:musicnet__trade-off}, also observed in sec.~\ref{sub:mnist_like_datasets}.
+%
+% * early stopping kick in at around 10-20 epoch
+% * performance peaks at 10-15 epoch and then gradually declines
+The value of $C$ in \eqref{eq:elbo_with_coef} is a good proxy for the ranking of the
+final compression rate since it directly affects the feedback from sparsifying prior.
+So, during the $50$ epoch allotted for ``sparsify'' stage, low $C$ prevents the sparsity
+inducing prior from pulling the posterior sufficiently away from the likelihood-maximizing
+parameters inherited from the ``pre-train'' stage. It is reasonable, therefore, to expect
+that for undercompressed models the fine-tuning stage acts essentially as a continuation
+of pre-training. And, since we have observed that longer training invariably deteriorates
+the validation performance, the ``fine-tune'' stage should lead to overfitting for small
+$C$.
+%
+Figure~\ref{fig:musicnet__early_stopping} shows that the models, which have been sparsified
+with $C$ less than $\tfrac1{400}$, have less than $50\times$ compression and need considerably
+less training epochs before early stopping terminates the process.
+
+\begin{figure}[!t]
+  \centering
   \begin{subfigure}[b]{1.\columnwidth}  % imcl2019-style swears at this
     \centering
-    \includegraphics[width=\columnwidth]{figure__fine-tune_fx__early__compression.pdf}
+    \includegraphics[width=\columnwidth]{figure__fine-tune_fx__early.pdf}
   \end{subfigure}
@@
 
-% why is there such a dramamtic difference in impact of ``fine-tune''?
-We provide the following interpretation of the apparent difference in performance impact
-of the ``fine-tune'' stage between less than $50\times$ and higher than $100\times$ compression
-regimes in figure~\ref{fig:musicnet__trade-off}, also observed in sec.~\ref{sub:mnist_like_datasets}.
-%
-% * early stopping kick in at around 10-20 epoch
-% * performance peaks at 10-15 epoch and then gradually declines
-The value of $C$ in \eqref{eq:elbo_with_coef} is a good proxy for the ranking of the final
-compression rate since it directly affects the feedback from sparsifying prior. So, with
-low $C$ models get less compressed during $50$ epoch allotted for ``sparsify'' stage, which
-appears to be insufficient to move model away from the parameters after the dense stage.
-It is reasonable therefore to expect that for undercompressed models the fine-tuning stage
-acts essentially as a continuation of the pre-training stage. Since we have observed that
-longer training invariably deteriorates the validation performance, the ``fine-tune'' stage
-leads to overfitting. Figure~\ref{fig:musicnet__early_stopping}, which shows that the models,
-which have been sparsified with $C$ less than $\tfrac1{400}$ and have $50\times$ compression,
-need considerably less training epochs before early stopping terminates the process.
-
-% testing the fx of the threshold
-\begin{figure}[!t]
-  \centering
-  \includegraphics[width=1\columnwidth]{figure__musicnet__threshold__C__DeepConvNet.pdf}
-  \caption{%
-    Effects of finetunig on performance-compression curves parameterized by $
-      \tau\in \{\tfrac{k}2\colon k=-8..+8 \}
-    $ for $
-      C\in \{\tfrac1{20}, \frac1{200}\}
-    $ in \eqref{eq:elbo_with_coef} during sparsification (sec.~\ref{sub:staging}).
-  }
-  \label{fig:hist__and__threshold__tradeoff}
-\end{figure}
-
-% effects of extra training epochs and the impact of tau
-We take the models from experiments with $C \in \{\tfrac1{20}, \frac1{200}\}$ and plot
-the compression and performance metrics before fine-tuning for various threshold levels
-on figure~\ref{fig:hist__and__threshold__tradeoff} (top). From \eqref{eq:elbo_with_coef} and
-the relative positions of the compression curves it can be concluded that $C$ has much
-more substantial impact on the sparsity and performance, than the choice of $\tau$.
-Furthermore, for $\tau > 0$ the performance quickly saturates while compression creeps
-downwards.
-%
-The bottom plot in figure~\ref{fig:hist__and__threshold__tradeoff} shows the effect of
-the ``fine-tune'' stage: for $\tau \leq -1$ it improves the test performance, while leaving
-it mostly unaffected for positive $\tau$. We attrbute this behaviour to regularization
-effect of high compression rate, which limits the capacity for overfitting by significantly
-reducing the excess degrees of freedom.
-% coarser grid than in top plot in order not to wait for 20 compute days, but 9.5 on
-% 4 x Geforce 1080Ti, 256 Gb, core-i7 machine, running 4*2 experiments in parallel
-
-% takeaway: fine tune seems to improve performance for highly compressed models, but
-% within a limit. Worth a try for moderately compressed models, but willl must likely
-% overfit for undercompressed models. Varying $C$ in \eqref{eq:elbo_with_coef} affects
-% sparsity more strongly, than varying $\tau$. But this is only observational.
-
 % subsection musicnet (end)
@@
 
-In this study we have extended Variational Dropout methods of \citet{kingma_variational_2015},
-\citet{molchanov_variational_2017} and \citet{kharitonov_variational_2018} to $\cplx$-valued
-Bayesian networks. To validate the proposed technique we have conducted a large numerical
-study of complex-valued networks with simple architectures in image recognition tasks to
-assess the feasible performance-compression trade-off. At the cost of marginally lower performance,
-we have achieved $50-100\times$ compression of the state-of-the-art deep $\cplx$-valued network
-of \citet{trabelsi_deep_2018} on the MusicNet.
+In this study we have presented $\cplx$-valued Variational sparsification methods to
+the ever growing set of tools for learning deep $\cplx$-valued neural networks. To
+validate the proposed $\cplx$-valued extensions of the Variational Dropout methods
+\citep{molchanov_variational_2017,kharitonov_variational_2018} we have conducted a
+large numerical study of $\cplx$VNN with simple architectures to assess the feasible
+performance-compression trade-off. At the cost of marginally lower performance, we have
+achieved $\times50$-$\times100$ compression of the deep $\cplx$VNN of \citet{trabelsi_deep_2018}
+on the MusicNet.
+
+Analysis of experimental findings has shown that $\cplx$-VD, sec.~\ref{ssub:vd_prior},
+and $\cplx$-ARD, sec.~\ref{ssub:ard_prior} offer adequate compression with controllable
+performance degradation in $\cplx$VNN and have trade-off profile similar to their $\real$
+counterparts.
+% L0 and dropout work in the low-to-mid sparsity range, variational dropout consistently
+% ranked behind L0 on Transformer, and was bested by magnitude pruning for sparsity
+% levels of 80\% and up. Variational dropout consistently produces models on-par or better
+% than magnitude pruning on ResNet-50, and l0 fails to produce sparse models at all.
+Therefore, we expect the overall conclusion of \citet{gale_state_2019} to carry over to
+$\cplx$VNN, since there is nothing fundamentally different in the proposed $\cplx$-valued
+variational sparsification methods.
 
@@
 complexity of $\cplx$-valued networks.
+% CVNN capacity grows by \sqrt{2}, compute grows by 2 % RVNN caption by 2 compute by 2.
 
 % section conclusion (end)
+
+\section*{Software and Data} % (fold)
+\label{sec:software_and_data}
+
+% we strongly encourage the publication of software and data with the camera-ready version
+% of the paper whenever appropriate. This can be done by including a URL in the copy.
+% do not include URLs that reveal your institution or identity in your submission for review
+% * provide an anonymous URL or upload the material as ``Supplementary Material'' into the CMT
+
+The source code for a package based on PyTorch \citep{paszke_pytorch_2019}, which
+implements $\cplx$-valued Sparse Variational Dropout and ARD layers and provides other
+basic layers for $\cplx$VNN is available at
+\url{https://github.com/ivannz/cplxmodule}.
+%
+The source code for the experiments and the figures in this study is available at
+\url{https://github.com/ivannz/complex_paper/tree/v2020.6}.
+
+% section* software_and_data (end)
+
+% Acknowledgements should only appear in the accepted version.
+\section*{Acknowledgements} % (fold)
+\label{sec:acknowledgements}
+
+% Do not include acknowledgements in the initial version of the paper submitted for blind review.
+
+% the final camera-ready version can (and probably should) include acknowledgements
+% Typically, this will include thanks to reviewers who gave useful comments, to colleagues
+% who contributed to the ideas, and to funding agencies and corporate sponsors that provided
+% financial support.
+We would like to thank the anonymous reviewers for their useful comments, and Evgenii
+Egorov, Ruslan Kostoev (ADASE) and Danila Doroshin (Huawei) for fruitfull discussions.
+% We thank Skoltech CDISE HPC Zhores cluster staff for providing computational infrastructure.
+The authors acknowledge the use of the Skoltech CDISE HPC cluster ``Zhores'' for obtaining
+the results presented in this paper.
+
+% section* acknowledgements (end)
 
@@
 
-In this section we derive the exact gradient of \eqref{eq:improper-kl-div-real}. Even
-though, ultimately, the divergence involves a hypergeometric function, and its gradient
-requires evaluating the Gauss error function, the analysis provides independent verification
-of the approximation, proposed by \citet{molchanov_variational_2017}. The logic of the
-derivation follows \citet{lapidoth_capacity_2003}.
+In this appendix we study the approximation proposed by \citet{molchanov_variational_2017}
+for the KL divergence term \eqref{eq:improper-kl-div-real}. We show empirically that
+the gradient feedback provided by the approximation is sufficiently close to $
+  \tfrac{d}{d\log \alpha} K(\alpha)
+$, making it a viable alternative to exact gradients, computed in \citet{hron_variational_2018}.
+% The derivation in this section different from \citet{lapidoth_capacity_2003}.
+% The results are identical: they use DCT to establish interchangeability of limits
+% (sum-integral-derivative), whilst we allude to calculus theorems on differentiation
+% and integration of power series within the radius of their convergence (which are
+% essentially corollaries to the DCT).
+
 % \citet{pav_moments_2015} correctly notice that \cite[p. 2466]{lapidoth_capacity_2003} has a missing $\log{2}$ term.
@@
   (\mu_i)_{i=1}^m \in \mathbb{R}
-$, the random variable $W = \sum_i (\mu_i + z_i)^2$ is noncentral $\chi^2$ with shape $m$
-and noncentrality parameter $\lambda = \sum_i \mu_i^2$, i.e. $W\sim \chi^2_m(\lambda)$.
-Its density is
-\begin{equation}  \label{eq:nonchisq-density}
-  f_W(x)
-    % = e^{- \tfrac\lambda2} \sum_{n \geq 0} \tfrac{\bigl(\tfrac\lambda2\bigr)^n}{n!}
-    %   \tfrac{
-    %     x^{n + \tfrac{m}2 - 1} e^{-\tfrac{x}2}
-    %   }{
-    %     2^{n + \tfrac{m}2} \Gamma(n + \tfrac{m}2)
-    %   }
-    % = e^{- \tfrac\lambda2} \sum_{n \geq 0} \tfrac{\bigl(\tfrac\lambda2\bigr)^n}{n!}
-    %     \tfrac{
-    %         \bigl(\tfrac{x}2\bigr)^{n + \tfrac{m}2 - 1} e^{-\tfrac{x}2}
-    %     }{
-    %         2 \Gamma(n + \tfrac{m}2)
-    %     }
-    = \frac12 e^{- \tfrac{x + \lambda}2} \bigl(\tfrac{x}2\bigr)^{\tfrac{m}2 - 1}
-      \sum_{n \geq 0} \frac{
-        \bigl(\tfrac{x \lambda}4\bigr)^n
-      }{
-        n! \Gamma(n + \tfrac{m}2)
-      }
-    % = \frac12 e^{- \tfrac{x + \lambda}2}
-    % \bigl(\tfrac{x}\lambda\bigr)^{\tfrac{m}4 - \tfrac12}
-    % \bigl(\tfrac{x \lambda}4\bigr)^{\tfrac{m}4 - \tfrac12}
-    % \sum_{n \geq 0} \tfrac{
-    %         \bigl(\tfrac{x \lambda}4\bigr)^n
-    %     }{
-    %         n! \Gamma(n + \tfrac{m}2)
-    %     }
-    % = \frac12 e^{- \tfrac{x + \lambda}2}
-    % \bigl(\tfrac{x}\lambda\bigr)^{\tfrac{m}4 - \tfrac12}
-    % \bigl(\tfrac{\sqrt{x \lambda}}2\bigr)^{\tfrac{m}2 - 1}
-    % \sum_{n \geq 0} \tfrac{
-    %         \bigl(\tfrac{x \lambda}4\bigr)^n
-    %     }{
-    %         n! \Gamma(n + \tfrac{m}2)
-    %     }
-    % = \frac12 e^{- \tfrac{x + \lambda}2}
-    % \bigl(\tfrac{x}\lambda\bigr)^{\tfrac{m - 2}4}
-    % I_{\bigl(\tfrac{m}2 - 1\bigr)}(\sqrt{x \lambda})
+$, the random variable $W = \sum_i (\mu_i + z_i)^2$ has non-central $\chi^2$ distribution
+with shape $m$ and non-centrality parameter $\lambda = \sum_i \mu_i^2$, i.e. $
+  W\sim \chi^2_m(\lambda)
+$. The divergence \eqref{eq:improper-kl-div-real} has the form
+\begin{equation}  \label{eq:kl-div-appendix}
+  K(\alpha)
+    \propto \frac12 \mathbb{E}_{
+        W\sim \chi^2_1\bigl(\tfrac1{\alpha}\bigr)
+      } \log W
+    \tag{\ref{eq:improper-kl-div-real}'}
+  \,,
+\end{equation}
+$W$ can alternatively be represented as a Poisson mixture of ordinary $\chi^2$
+distributions: if $Z_{\mid J} \sim \chi^2_{k + 2J}$ for $
+  J \sim \mathcal{P}ois(\tfrac{\lambda}2)
+$ then $W \sim Z$. Therefore, expanding the conditional expectation gives
+\begin{equation}  \label{eq:cond_exp_expansion}
+  \mathbb{E}_{W\sim \chi^2_k(\lambda)} \log W
+    = \mathbb{E}\Bigl(
+        \mathbb{E} \bigl( \log W \mid J)
+      \Bigr)
+    = \mathbb{E}_{J\sim {\mathcal{P}ois}(\tfrac\lambda2)}
+      \Bigl(
+        \mathbb{E}_{W\sim \chi^2_{m + 2 J}} \log W
+      \Bigr)
     \,.
 \end{equation}
-% where $I_k$ is the modified Bessel function of the first kind
-% $$
-% I_k(s)
-%   = \Bigl(\frac{s}2\Bigr)^k
-%       \sum_{n \geq 0} \tfrac{
-%           \bigl( \tfrac{s}2 \bigr)^{2n}
-%       }{n! \Gamma(n + k + 1)}
-%   \,. $$
-By integrating the power series \eqref{eq:nonchisq-density} with substitution $x \to 2u$,
-the expectation $
-  \mathbb{E}_{W\sim \chi^2_m(\lambda)} \log W
-$, needed in \eqref{eq:improper-kl-div-real}, equals
-\begin{multline}  \label{eq:exp-log-chisq-proof}
-    % &= \int_0^\infty f_W(x) \log x dx
-    % \notag \\
-    % &\frac12 e^{- \tfrac\lambda2}
-    % \int_0^\infty \sum_{n \geq 0} \biggl(
-    %     \frac{
-    %       e^{- \tfrac{x}2} \bigl(\tfrac\lambda2\bigr)^n
-    %     }{
-    %       n! \Gamma(n + \tfrac{m}2)
-    %     }
-    %     \bigl(\tfrac{x}2\bigr)^{n + \tfrac{m}2 - 1}
-    % \biggr) \log{(x)} dx
-    % = [\text{ absolute summability and Fubini, or any other conv. thm for integrals of nonnegative integrals}]
-    % = e^{- \tfrac\lambda2} \sum_{n \geq 0}
-    %     \tfrac{\bigl(\tfrac\lambda2\bigr)^n}{n!}
-    %     \tfrac1{\Gamma(n + \tfrac{m}2)}
-    % \int_0^\infty
-    %     e^{- \tfrac{x}2} \bigl(\tfrac{x}2\bigr)^{n + \tfrac{m}2 - 1}
-    %     (\log2 + \log \tfrac{x}2) \tfrac{dx}2
-    % = [u = \tfrac{x}2]
-    % \notag \\
-    e^{- \tfrac\lambda2} \sum_{n \geq 0}
-        \frac{\bigl(\tfrac\lambda2\bigr)^n}{
-          n! \Gamma(n + \tfrac{m}2)
-        }
-    \int_0^\infty
-        e^{- u} u^{n + \tfrac{m}2 - 1}
-        \log{(2 u)} du
-    % = [\text{definitions:} \Gamma, \psi]
-    % = e^{- \tfrac\lambda2} \sum_{n \geq 0}
-    %     \tfrac{\bigl(\tfrac\lambda2\bigr)^n}{n!}
-    % (\psi(n + \tfrac{m}2) + \log2)
-    % \notag
-    \\
-    = \log{2}
-    + e^{- \tfrac\lambda2} \sum_{n \geq 0}
-        \frac{\bigl(\tfrac\lambda2\bigr)^n}{n!}
-        \psi(n + \tfrac{m}2)
+Since $\chi^2_\nu$ is Gamma distribution $\Gamma(\tfrac\nu2, \tfrac12)$, its logarithmic
+moment $
+  \mathbb{E}_{W\sim \chi^2_\nu} \log W
+$ is $
+  \psi\bigl(\tfrac\nu{2}\bigr) - \log \tfrac12
+$, where $\psi(x)$ is the digamma function. Hence
+\begin{equation}  \label{eq:exp_digamma}
+  \mathbb{E}_{W\sim \chi^2_k(\lambda)} \log W
+    = \log2 + \mathbb{E}_{J\sim {\mathcal{P}ois}(\tfrac\lambda2)}
+      \psi\bigl(\tfrac{m + 2 J}{2}\bigr)
+    % = \log2
+    % + \sum_{j\geq 0}
+    %     e^{- \tfrac{\lambda}2}
+    %     \frac{\bigl(\tfrac{\lambda}2\bigr)^j}{j!}
+    %   \psi\bigl(\tfrac{m+2J}{2}\bigr)
+    \,.
+\end{equation}
+We can use REINFORCE method to compute the derivative of \eqref{eq:exp_digamma} with respect
+to $\lambda$ \citep{williams_simple_1992}. Since Poisson $\log$-probability is $
+  \log p_\lambda(J)
+    = - \tfrac{\lambda}2
+      + J \log \tfrac{\lambda}2
+      - \log J!
+$, we get
+\begin{equation}  \label{eq:exp_reinforce}
+  \frac{d \eqref{eq:exp_digamma}}{d \lambda}
+    =
+    \mathbb{E}_{J\sim {\mathcal{P}ois}(\tfrac\lambda2)}
+      \psi\bigl(\tfrac{m + 2 J}{2}\bigr)
+      \tfrac{d}{d \lambda} \log p_\lambda(J)
+    % = \mathbb{E}_{J}
+    %   \bigl(
+    %     \tfrac2\lambda J - 1
+    %   \bigr)
+    %   \frac{\psi\bigl(\tfrac{m + 2 J}{2}\bigr)}2
+    = \frac12 g_m\bigl(\tfrac\lambda2\bigr)
     \,,
-\end{multline}
-where $\psi(x)$ is the digamma function, i.e.
-\begin{equation}  \label{eq:digamma}
-  \psi(x)
-    % = \frac{d}{dx} \log \Gamma(x)
-    = \frac1{\Gamma(x)}
-      \int_0^\infty
-        u^{x-1} e^{-u} \log{u}
-      \, du
-    \,,
-\end{equation}
-which satisfies $
-  \psi(z+1) = \psi(z) + \tfrac1z
-$, $
-  \psi(x)\leq \log x - \tfrac1{2x}
-$, and $
-  \psi(\tfrac12) = -\gamma - 2\log 2
-$ ($\gamma$ is Euler's constant). If we put
-\begin{equation}  \label{eq:g-m-series}
+\end{equation}
+where
+\begin{equation}  \label{eq:g_m_series}
   g_m(x)
-    % alpha: e^{-x} \sum_{n=0}^{\infty} \frac{x^n}{n!} \psi(n + m / 2)
-    % = e^{-x} \sum_{n \geq 0} \frac{x^n}{n! \Gamma(n + \tfrac{m}2)}
-    %     \int_0^\infty e^{-t} t^{n + \tfrac{m}2-1} \log{t} dt
-    = e^{-x} \sum_{n \geq 0} \frac{x^n}{n!} \psi(n + \tfrac{m}2)
-    \,,
-\end{equation}
-then the desired expectation in \eqref{eq:improper-kl-div-real} equals $
-  \log{2} + g_1(\tfrac1{2\alpha})
-$.
-%
-% We can differentiate the series in $g_m(x)$, since the sum converges on $\mathbb{R}$.
-% Indeed, it is a power series featuring nonnegative coefficients, which is dominated by $
-%   \sum_{n \geq 1} \tfrac{x^n}{n!} \log{(n+\tfrac{m}2)}
-% $. By the ratio test, the dominating
-% series has infinite radius:
-% $$
-% \lim_{n\to\infty}
-%   \biggl\lvert
-%     \frac{
-%       n! x^{n+1} \log{(n + 1 + \tfrac{m}2)}
-%     }{
-%       x^n \log{(n + \tfrac{m}2)} (n+1)!
-%     }
-%   \biggr\rvert
-%   = \lim_{n\to\infty}
-%     \lvert x \rvert 
-%     \biggl\lvert
-%       \frac{
-%         \log{(n + 1 + \tfrac{m}2)}
-%       }{
-%         \log{(n + \tfrac{m}2)} (n+1)
-%       }
-%     \biggr\rvert
-%   % = \lim_{n\to\infty}
-%   %   \lvert x \rvert 
-%   %   \biggl\lvert
-%   %     \frac{
-%   %       n + \tfrac{m}2
-%   %     }{
-%   %       (n + 1 + \tfrac{m}2)((n+1) + (n + \tfrac{m}2) \log{(n + \tfrac{m}2)})
-%   %     }
-%   %   \biggr\rvert
-%   = 0 < 1
-%   \,, $$
-% since
-% $$
-% \frac{\log{(x + a + 1)}}{x \log{(x + a)}}
-%   \sim \frac{\log{(x+1)}}{(x-a) \log{x}}
-%   \sim \frac{\log{(x+1)}}{x \log{x}}
-%   \sim \frac{\tfrac1{(x+1)}}{1 + \log{x}}
-%   \to 0
-%   \,. $$
-% A theorem from calculus states, that the formal series derivative (integral)
-% coincides with the derivative (integral) of the function, corresponding to
-% the power series (everywhere on the convergence region). And the convergence
-% regions of derivative (integral) coincide with the region of the original
-% power series.
-%
-Formally differentiating the convergent power series within $g_m$ yields
-\begin{equation}  \label{eq:g-m-deriv}
-  \frac{d}{d x} g_m(x)
-    % = e^{-x} \sum_{n\geq 1} \frac{x^{n-1}}{(n-1)!} \psi(n + \tfrac{m}2) - g_m(x)
-    % = e^{-x} \sum_{n\geq 0} \frac{x^n}{n!} \psi(n + \tfrac{m}2 + 1) - g_m(x)
-    % = e^{-x} \sum_{n\geq 0} \frac{x^n}{n!} (
-    %     \psi(n + \tfrac{m}2 + 1) - \psi(n + \tfrac{m}2)
-    % )
-    % = e^{-x} \sum_{n\geq 0} \frac{x^n}{n!} \tfrac1{n + \tfrac{m}2}
-    % = e^{-x} \sum_{n\geq 0} \frac{x^n}{n!} (n + \tfrac{m}2)^{-1}
-    = x^{-\tfrac{m}2} e^{-x} \sum_{n\geq 0}
-        \frac{x^{n + \tfrac{m}2}}{n!} (n + \tfrac{m}2)^{-1}
+    =
+    \mathbb{E}_{J\sim {\mathcal{P}ois}(x)}
+      \bigl( \tfrac{J}x - 1 \bigr)
+      \psi\bigl(\tfrac{m + 2 J}{2}\bigr)
+    =
+    e^{- x} \sum_{j \geq 0}
+      \frac{x^j}{j!} \bigl( \tfrac{J}x - 1 \bigr)
+      \psi\bigl(\tfrac{m + 2 j}{2}\bigr)
     \,.
 \end{equation}
-From $
-    e^t  = \sum_{n\geq 0} \tfrac{t^n}{n!}
-$ on $\mathbb{R}$ and $
-  \tfrac{x^\alpha}{\alpha}
-    = \int_0^x t^{\alpha-1} dt
-$ for $\alpha\neq 0$ we get
-% by the monotone convergence theorem on ([0, x], \mathcal{B}([0, x]), dx)
-\begin{align}  \label{eq:g-m-deriv-int-2}
-  \eqref{eq:g-m-deriv}
-    % = x^{-\tfrac{m}2} e^{-x} \sum_{n\geq 0}
-    %     \frac{x^{n + \tfrac{m}2}}{n!} (n + \tfrac{m}2)^{-1}
-    &= x^{-\tfrac{m}2} e^{-x} \sum_{n\geq 0}
-        \frac1{n!} \int_0^x t^{n + \tfrac{m}2 - 1} dt
-    % = x^{-\tfrac{m}2} e^{-x}
-    %     \int_0^x t^{\tfrac{m}2 - 1} \sum_{n\geq 0} \frac{t^n}{n!} dt
-    \notag \\
-    &= x^{-\tfrac{m}2} e^{-x}
-        \int_0^x t^{\tfrac{m}2 - 1} e^t dt
+By manipulating the partial sums within $g_m(x)$ and making use of the property $
+  \psi(x + 1) = \psi(x) + \tfrac1x
+  % \psi(1 + J + \tfrac{m}2) = \tfrac2{m + 2J} + \psi(J + \tfrac{m}2)
+$ of the digamma funciton for $x > 0$, we get
+\begin{equation}  \label{eq:g_m_series_int}
+  g_m(x)
+    = e^{- x} \sum_{j \geq 0}
+      \frac{x^j}{j!} \frac1{j + \tfrac{m}2}
+    = e^{- x} x^{- \tfrac{m}2} \sum_{j \geq 0}
+      \frac1{j!}
+      \frac{x^{j + \tfrac{m}2}}{j + \tfrac{m}2}
+    = e^{- x} x^{- \tfrac{m}2} \sum_{j \geq 0}
+      \frac1{j!} \int_0^x t^{j + \tfrac{m}2 - 1} dt
     \,.
-\end{align}
-Substitution $u^2 = t$ on $[0, \infty]$ with $2u du = dt$ yields
-\begin{equation}  \label{eq:g-m-deriv-int-3}
-  \frac{d}{d x} g_m(x)
+\end{equation}
+Since for any $J$ the functions $
+  t \mapsto \sum_{j=0}^J \frac1{j!} t^{j + \tfrac{m}2 - 1}
+$ are positive on $(0, x)$ and upper bounded by integrable $
+  t^{\tfrac{m}2 - 1} e^t
+$, which turns out to be the limit of the partial sums, the Dominated Convergence
+theorem implies
+\begin{equation}  \label{eq:g_m_integral}
+  g_m(x)
+    = e^{- x} x^{- \tfrac{m}2}
+      \int_0^x \sum_{j \geq 0}
+        \frac1{j!} t^{j + \tfrac{m}2 - 1} dt
+    = e^{- x} x^{- \tfrac{m}2}
+      \int_0^x e^t t^{(\tfrac{m}2 - 1)} dt
+    \,.
+\end{equation}
+Substituting $u^2 = t$ on $[0, \infty]$ with $2u du = dt$ and letting $
+  F_m
+  % \colon \mathbb{R} \to \mathbb{R}
+  \colon x \mapsto e^{-x^2} \int_0^x u^{m - 1} e^{u^2} du
+$ yields
+\begin{equation}  \label{eq:g_m_integral-sub}
+  \frac{d \eqref{eq:exp_digamma}}{d \lambda}
+    = \frac12 g_m\bigl(\tfrac\lambda2\bigr)
     % = x^{-\tfrac{m}2} e^{-x}
     %     \int_0^x t^{\tfrac{m}2 - 1} e^t dt
-    = 2 x^{-\tfrac{m}2} e^{-x}
+    = e^{-x}
+      x^{-\tfrac{m}2}
       \int_0^{\sqrt{x}} u^{m - 1} e^{u^2} du
+        \bigg\vert_{x=\tfrac\lambda2}
+    % = e^{-x}
+    %   \frac1{\sqrt{x}}
+    %   \int_0^{\sqrt{x}} e^{u^2} du
+    %     \bigg\vert_{x=\tfrac\lambda2}
+    = \Bigl(\sqrt{\tfrac2\lambda}\Bigr)^m F\Bigl(\sqrt{\tfrac\lambda2}\Bigr)
     \,.
 \end{equation}
-In particular, the derivative of \eqref{eq:g-m-series} for $m=1$ is
-\begin{equation}  \label{eq:g-m-deriv-one}
-  \frac{d}{d x} g_1(x)
-    = 2 \frac{F(\sqrt{x})}{\sqrt{x}}
-    \,,
-\end{equation}
-using Dawson's integral $
-  F
-  % \colon \mathbb{R} \to \mathbb{R}
-  \colon x \mapsto e^{-x^2} \int_0^x e^{u^2} du
-$.
-%
-Hence, the derivative of the expectation in \eqref{eq:improper-kl-div-real} with respect
-to $\alpha$ is
-$$
-\frac{d}{d \alpha} g_1(\tfrac1{2\alpha})
-  = -\frac1{2 \alpha^2} g_1'(\tfrac1{2\alpha})
-  % = -\frac1{2 \alpha^2} 2 \tfrac{F(\sqrt{\tfrac1{2\alpha}})}{\sqrt{\tfrac1{2\alpha}}}
-  % = -\frac1{2 \alpha^2} 2 \tfrac{F(\tfrac1{\sqrt{2\alpha}})}{\tfrac1{\sqrt{2\alpha}}}
-  = -\frac1{\alpha} \sqrt{\frac2{\alpha}} F(\tfrac1{\sqrt{2\alpha}})
-  \,. $$
-Finally, since $\alpha$ is nonnegative, it is typically parameterized via its logarithm.
-The gradient of \eqref{eq:improper-kl-div-real} w.r.t $\log \alpha$ is
+Since $\alpha$ is non-negative, it is typically parameterized via its logarithm, whence
+the derivative of \eqref{eq:kl-div-appendix} with respect to $\log\alpha$ follows from
+\eqref{eq:g_m_integral-sub} for $m=1$ and $\lambda = \tfrac1\alpha$:
 \begin{equation}  \label{eq:real-kl-div-deriv-log}
-  \frac{d \eqref{eq:improper-kl-div-real}}{d\log \alpha}
-  % \frac{d}{d\log \alpha}
-  %   \frac12 \mathbb{E}_{z \sim \mathcal{N}(0,1)}
-  %     \log \lvert z + \tfrac1{\sqrt{\alpha}} \rvert^2
-    % = \frac12 \frac{d\alpha}{d\log \alpha}
-    %   \frac{d}{d\alpha} \bigl(\mathbb{E}\cdots \bigr)
-    % = - \frac\alpha2 \tfrac1{\alpha}
-    %   \sqrt{\tfrac2{\alpha}} F(\tfrac1{\sqrt{2\alpha}})
+  \frac{d K(\alpha)}{d\log \alpha}
+    % = \tfrac12 \sqrt{\tfrac2\lambda} F\Bigl(\sqrt{\tfrac\lambda2}\Bigr)
+    % for \lambda = \tfrac1\alpha
+    %   \tfrac{d\lambda}{d\alpha} = - \alpha^{-2}
+    %   \tfrac{d\alpha}{d\log \alpha} = \alpha
+    % = - \alpha \frac1{\alpha\sqrt{2\alpha}} F\Bigl(\tfrac1{\sqrt{2\alpha}}\Bigr)
     = - \frac1{\sqrt{2\alpha}} F\bigl(\tfrac1{\sqrt{2\alpha}}\bigr)
@@
   % = \tfrac12 \log \alpha
-  %   - \mathbb{E}_{\xi \sim \mathcal{N}(1, \alpha)}
-  %   \log{\lvert \xi \rvert} + C
+  %   - \mathbb{E}_{\varepsilon \sim \mathcal{N}(1, \alpha)}
+  %   \log{\lvert \varepsilon \rvert} + C
   \approx
@@
 sampling error), see fig.~\ref{fig:molchanov-derivative-replica}. The derivative of
-\eqref{eq:improper-kl-div-real-approx} with respect to $\log \alpha$ appears to be very close
-to \eqref{eq:real-kl-div-deriv-log}. We compute a similar Monte-Carlo estimate for
-$\cplx$ variational dropout KL divergence term in \eqref{eq:c-vd-kl-div} with $\beta = 2$,
-fit the best approximation \eqref{eq:improper-kl-div-real-approx}, and compare the derivatives.
+\eqref{eq:improper-kl-div-real-approx} with respect to $\log \alpha$ appears to be very
+close to \eqref{eq:real-kl-div-deriv-log}. For sake of completeness, we compute a similar
+Monte-Carlo estimate for $\cplx$ variational dropout KL divergence term in \eqref{eq:c-vd-kl-div}
+with $\beta = 2$, fit the best approximation \eqref{eq:improper-kl-div-real-approx}, and
+compare it against the exact $\log \alpha$ derivative $
+  \frac{d \eqref{eq:c-vd-kl-div}}{d\log \alpha}
+    % = \frac{d \alpha}{d\log \alpha} \frac{d}{d\alpha} \bigl(
+    %   \log \tfrac1\alpha - \mathop{Ei}\bigl(-\tfrac1\alpha\bigr)
+    % = \alpha \bigl(
+    %   - \tfrac1\alpha
+    %   - \tfrac{e^x}{x} \bigg\vert_{x=-\tfrac1\alpha} \alpha^{-2}
+    % \bigr)
+    = e^{-\tfrac1\alpha} - 1
+$.
 
@@
   \includegraphics[width=\columnwidth]{grad_log.pdf}
-  \caption{$\tfrac{d f(\alpha)}{d \log{\alpha}}$ of the approximation
+  \caption{$\tfrac{d K(\alpha)}{d \log{\alpha}}$ of the approximation
   \eqref{eq:improper-kl-div-real-approx}, MC estimate of \eqref{eq:improper-kl-div-real},
@@
       + \tfrac{\partial f}{\partial \conj{z}} d\conj{z}
-  % = \conj{\tfrac{\partial \conj{f}}{\partial \conj{z}}} dz
-  % + \conj{\conj{\tfrac{\partial f}{\partial \conj{z}}} dz}
-  = 2 \Re \Bigl(
-    \conj{\tfrac{\partial f}{\partial \conj{z}}} dz
-  \Bigr)
-  = 2 \Re \bigl(
+    % = \tfrac{\partial f}{\partial z} dz
+    %   + \conj{\tfrac{\partial f}{\partial z}} d\conj{z}
+    = \tfrac{\partial f}{\partial z} dz
+      + \conj{\tfrac{\partial f}{\partial z} dz}
+    % = 2 \Re
+    %   \Bigl(
+    %     \conj{\tfrac{\partial f}{\partial \conj{z}}} dz
+    %   \Bigr)
+    = 2 \Re
+      \bigl(
         \tfrac{\partial f}{\partial z} dz
       \bigr)
-  \,. $$
-Thus, the gradient of $f$ at $z$ is given by $
-  \nabla_z f(z)
+    \,.
+\end{equation*}
+Therefore the gradient of $f$ at $z$ is given by $
+  \nabla_{\conj{z}} f(z)
+    = \conj{\tfrac{\partial f}{\partial z}}
     = \tfrac{\partial F}{\partial u}
-      + j \tfrac{\partial F}{\partial v}
-$.
-
-Natural identification of $\cplx$ with $\real\times \real$, storing the real and imaginary
-parts in interleaved format, emulation of $\cplx$-algebra using $\real$-valued arithmetic,
-and Wirtinger calculus make it possible to reuse $\real$ back-propagation and existing
-auto-differentiation frameworks \citep{trabelsi_deep_2018}.
+    + \iu \tfrac{\partial F}{\partial v}
+$. The identification $\cplx \simeq \real^2$, backed by Wirtinger calculus, and emulation
+of $\cplx$-arithmetic in computational graphs with $\real$-valued operations makes it
+possible to reuse $\real$ back-propagation and existing auto-differentiation frameworks.
 

### 2020-06-21 paper/paper.tex
minor edits in vardropout section

--- 2020-06-20 paper/paper.tex
@@
 \newcommand{\cplx}{\mathbb{C}}
+\newcommand{\iu}{{\jmath}}
 \newcommand{\tr}[1]{\mathop{tr}{#1}}
@@
 $ is factorized over layers. Furthermore, if $
-  \omega = W \in \mathbb{R}^{n\times m}
+  % \omega =
+  W \in \mathbb{R}^{n\times m}
 $ in a linear layer $
@@
 to the equivalent $(\mu, \sigma^2)$, arguing that it reduces the variance of the SGVB
-\eqref{eq:sgvb_estimator}, by rendering the gradient with respect to $\mu_{ij}$ independent
+\eqref{eq:sgvb_estimator}, by rendering the gradient with respect to $\mu$ independent
 from the local output noise, injected by \eqref{eq:r-gauss-trick}. This improvement is
-especially important for model pruning, since $\mu_{ij}$ of relevant parameters are used
+especially important for model pruning, since $\mu$ of relevant parameters are used
 as point estimates of their values.
 
-Due to factorization alternative parameterization, the term $KL(q_\theta \| \pi)$ in
-\eqref{eq:sgvb_estimator} of Sparse VD unravels into $
+Due factorization assumption, the term $KL(q_\theta \| \pi)$ in \eqref{eq:sgvb_estimator}
+for Sparse VD unravels into $
   \sum_j K(\tfrac{\sigma^2_{j}}{\mu_{j}^2})

### 2020-06-21 paper/paper.tex
replaced textit-s with emph

@@
   \mathbb{E} (z - \mu)(z - \mu)^{\top}
-$, respectively, and $z$ is a \textit{proper} $\cplx$-Gaussian vector if $z$ and
+$, respectively, and $z$ is a \emph{proper} $\cplx$-Gaussian vector if $z$ and
 $\conj{z}$ are uncorrelated, i.e. $C = 0$.
@@
 %
-Each experiment is replicated \textit{five} times to take into account random initialization,
+Each experiment is replicated \emph{five} times to take into account random initialization,
 random order of the mini-batch during SGD, stochastic outputs of the intermediate layers,
@@
 Each network within every experiment passes through three successive stages of training:
-pre-training (\textit{``dense''}), sparsification (\textit{``sparsify''}), and fine-tuning
-(\textit{``fine-tune''}) (sec.~\ref{sub:staging}). The parameters and optimizer state are
+pre-training (\emph{``dense''}), sparsification (\emph{``sparsify''}), and fine-tuning
+(\emph{``fine-tune''}) (sec.~\ref{sub:staging}). The parameters and optimizer state are
 passed between stages, except for last one, which inherits just the parameters.
@@
 
-At the \textit{``dense''} stage every network is fit ``as-is'', retaining its original
+At the \emph{``dense''} stage every network is fit ``as-is'', retaining its original
 non-Bayesian architecture, and using only the likelihood term from \eqref{eq:sgvb_estimator} without
@@
 
-During the \textit{``sparsify''} stage we make every layer Bayesian and apply $\cplx$-variational
+During the \emph{``sparsify''} stage we make every layer Bayesian and apply $\cplx$-variational
 dropout sec.~\ref{ssub:vd_prior} (or sec.~\ref{ssub:ard_prior}) or its $\real$ counterpart.
@@
 % on compresssion
-Between \textit{``sparsify''} and \textit{``fine-tune''} stages we compute masks of non-zero
+Between \emph{``sparsify''} and \emph{``fine-tune''} stages we compute masks of non-zero
 weights in each layer based on the relevance scores $\alpha$ (sec.~\ref{sec:variational_dropout}).
@@
 
-The \textit{``fine-tune''} stage reverts the network back to non-Bayesian layers, applies
+The \emph{``fine-tune''} stage reverts the network back to non-Bayesian layers, applies
 sparsity masks to its parameters and proceeds with training the kept parameters as during
@@
 We deliberately use a {fixed} random subset of $10k$ images from the train split of each
-dataset to fit the networks and measure the performance with classification \textit{accuracy}
+dataset to fit the networks and measure the performance with classification \emph{accuracy}
 score on the usual test split.
@@
 which have been chosen for the purpose of illustrating the compression and understanding
-the effects of experiment parameters. \textit{TwoLayerDenseModel} is a wide dense ReLU
-network $784 \to 4096 \to n_\mathtt{out}$, and \textit{SimpleConvModel} is a ReLU net with
+the effects of experiment parameters. \emph{TwoLayerDenseModel} is a wide dense ReLU
+network $784 \to 4096 \to n_\mathtt{out}$, and \emph{SimpleConvModel} is a ReLU net with
 two $2d$ $k_5 s_1$ convolutions with filters $20 \to 50$, two $k_2 s_2$ average pooling steps,
@@
 \ref{fig:appendix__mnist-like__trade-off__ARD__raw}, and \ref{fig:appendix__mnist-like__trade-off__VD__raw}
-present $\real$ and $\cplx$ models with \textit{the same intermediate feature sizes}.
+present $\real$ and $\cplx$ models with \emph{the same intermediate feature sizes}.
 
@@
 %notation
-By $e_i$ we denote the $i$-th real unit vector of dimensionality \textit{conforming} to the
-matrix-vector expression it is used in. Let $\vec{M}$ denote \textit{row-major} flattening
+By $e_i$ we denote the $i$-th real unit vector of dimensionality \emph{conforming} to the
+matrix-vector expression it is used in. Let $\vec{M}$ denote \emph{row-major} flattening
 of $M$ into a vector, i.e. in lexicographic order of its indices. $\diag{(\cdot)}$ embeds
@@
 \end{equation}
-where mean, \textit{variance} and relation are given by matrices $
+where mean, \emph{variance} and relation are given by matrices $
   \mu, \Sigma, C \in \cplx^{n\times m}

### 2020-06-21 paper/paper.tex
compatcified paragraph of additive noise parameterization

@@
 Parameterization} in the factorized Gaussian $q_\theta(\omega)$ in conjunction with the
-Local Reparameterization Trick. They reverted the $(\mu, \alpha)$ parameterization back
-to the equivalent $(\mu, \sigma^2)$, arguing that it reduces the variance of the SGVB
-\eqref{eq:sgvb_estimator}, by rendering the gradient with respect to $\mu$ independent
-from the local output noise, injected by \eqref{eq:r-gauss-trick}. This improvement is
-especially important for model pruning, since $\mu$ of relevant parameters are used
-as point estimates of their values.
+Local Reparameterization Trick. They reverted the $(\mu, \alpha)$ parameterization in
+$q_\theta(\omega)$ back to $(\mu, \sigma^2)$, arguing that it reduces the variance of the
+SGVB \eqref{eq:sgvb_estimator}, by rendering the gradient with respect to $\mu$ independent
+from the local noise, injected by \eqref{eq:r-gauss-trick}. This modification is important
+for pruning, since $\mu$ of relevant parameters are used as estimates of their values.
 
@@
 % \end{align}
+
+% practical difference between them?
 

### 2020-06-21 paper/paper.tex
6  clearer story in the CVNN section  * what CVNN are and how they work  * how to back-propagate though them  * and what were the major developments in their niche

@@
 
+% implementation
+$\cplx$-valued neural networks are networks that rely on the arithmetic in the complex
+domain. To achieve this implementations of $\cplx$VNN use the geometric (planar) representation
+of a complex number as paired \emph{real} and \emph{imaginary} values, $\cplx \simeq \real^2$,
+ensuring that the resulting $\real$-valued computational graph respects $\cplx$-arithmetic.
+For example, $
+  f\colon \cplx^n \to \cplx^m
+$ is identified with a real vector-valued function $
+  F\colon \real^{2 m} \to \real^{2 m}
+$ defined via $
+  F(u, v) = (\Re f(u + \iu v), \Im f(u + \iu v))
+$, $\Re$ and $\Im$ denoting the real and imaginary parts, respectively. When $f$ is
+a $\cplx$-valued linear transformation, the computations are ``wired'' so that
+\begin{equation}  \label{eq:cplx-lin-op}
+  % F\colon
+  %   (u, v)
+  %     \mapsto \Bigl(
+  %       P u - Q v,
+  %       P v + Q u
+  %     \Bigr)
+  F(u, v)
+    =
+    \begin{pmatrix}
+      P u - Q v \\
+      P v + Q u
+    \end{pmatrix}
+    = \begin{pmatrix}
+      P & - Q \\ Q & P
+    \end{pmatrix} \begin{pmatrix}
+      u \\ v
+    \end{pmatrix}
+    \,,
+\end{equation}
+with $
+  P, Q \colon \real^{n} \to \real^{m}
+$ given by $P = \Re f$ and $Q = \Im f$ restricted to $\real^{n}$.
+% The downside is that, for instance, one $\cplx$-valued convolution requires up to
+% four $\real$-valued convolution operations.
+%
+Nonlinearities in $\cplx$VNN can be hyperbolic functions or maps that operate on
+$\cplx$ numbers in planar form, $
+  z \mapsto \sigma(\Re{z}) + \iu \sigma(\Im{z}) % split
+$, or polar form $
+  % z \mapsto \sigma(\lvert z\rvert, \arg{\!(z)})
+  r e^{\iu \phi} \mapsto \sigma(r, \phi)
+$.
+% \citep{savitha_2011,hirose_generalization_2012,arjovsky_unitary_2016,guberman_complex_2016}
+
+This $\cplx \simeq \real^2$ identification allows straightforward retrofitting of $\cplx$VNN
+into existing $\real$-valued auto-differentiation frameworks for deep learning. This
+act is backed by Wirtinger ($\cplx\real$) calculus, which enables generalized treatment
+of functions of complex argument, by regarding $z$ and $\conj{z}$ as independent variables
+and defining derivatives with respect to them through partial derivatives with respect
+to real and imaginary parts of each argument. These definitions simplify manual calculations
+of $\cplx$ derivatives and satisfy the product and chain rules, respect complex conjugation
+and linearity for $\cplx \to \cplx$ maps. $\cplx\real$ calculus was used to define $\cplx$
+version of back-propagation, \citep{benvenuto_complex_1992,guberman_complex_2016}. However,
+since auto-differentiation frameworks can algorithmically handle computational graphs
+of arbitrary complexity, explicit use of Wirtinger derivatives is not required, especially
+considering the fact that the direction of the steepest ascent of a $\cplx\to \real$
+function is given by complex conjugate gradient $\nabla_{\conj{z}}$, which coincides
+with the classical gradient of the same function viewed as $\real^2 \to \real$,
+(see appendix~\ref{sub:wirtinger_calculus}).
+%
+% in natively $\cplx$-valued backprop it would be necessary to modify the existing sgd
+% to explicitly use $\nabla_{\conj{z}} f(z)$, while no such modification is necessary
+% in re-im. If some inner activation of a $\cplx$VNN is holomorphic, i.e. satisfies
+% Cauchy-Riemann conditions, then that particular step of in the chain rule that is
+% backprop can be simplified by assuming one piece of the tracked gradient to be exact
+% zero. But other wise it is necessary to track both $\partial_{\conj{z}}$ and $\partial_{z}$.
+%
+% Training a $\cplx$VNN involves optimizing a real-valued objective with respect to
+% complex valued arguments.
+%
+% The computed gradients are theoretically justified
+% - CR dictates the it is necessary to track both $z$ and $\conj{z}$ derivatives
+% - the direction of largest increase in f: C-R is given by the gradient with
+% respect to the conjugate, which coincides in the re-im representation with 
+% the ordinary gradient wrt u and v
+% - the Chain Rule in CR holds and when a holomorphic C-C function is backproped
+% the autodiff just wastes cycles on computing its conj-derivative (rather than assuming
+% it to be zero)
+
 % Although $\cplx$-valued dense layers and back-propagation have been around since early
 % 1990-s, one of the earliest accounts
-
 Development of deep $\cplx$-valued networks has been active. \citet{haensch_complex-valued_2010}

### 2020-06-21 paper/paper.tex
minor cosmetics in the cvnn section

@@
 act is backed by Wirtinger ($\cplx\real$) calculus, which enables generalized treatment
-of functions of complex argument, by regarding $z$ and $\conj{z}$ as independent variables
-and defining derivatives with respect to them through partial derivatives with respect
-to real and imaginary parts of each argument. These definitions simplify manual calculations
-of $\cplx$ derivatives and satisfy the product and chain rules, respect complex conjugation
-and linearity for $\cplx \to \cplx$ maps. $\cplx\real$ calculus was used to define $\cplx$
-version of back-propagation, \citep{benvenuto_complex_1992,guberman_complex_2016}. However,
-since auto-differentiation frameworks can algorithmically handle computational graphs
-of arbitrary complexity, explicit use of Wirtinger derivatives is not required, especially
-considering the fact that the direction of the steepest ascent of a $\cplx\to \real$
-function is given by complex conjugate gradient $\nabla_{\conj{z}}$, which coincides
+of functions of complex argument, by regarding $z$ and its \emph{complex conjugate}
+$\conj{z}$ as independent variables and defining derivatives with respect to them through
+partial derivatives with respect to real and imaginary parts. These definitions simplify
+manual calculations of $\cplx$ derivatives and satisfy the product and chain rules, respect
+complex conjugation and linearity for $\cplx \to \cplx$ maps. $\cplx\real$ calculus was
+used to define $\cplx$ version of back-propagation,
+\citep{benvenuto_complex_1992,guberman_complex_2016}.
+However, since auto-differentiation frameworks can algorithmically handle computational
+graphs of arbitrary complexity, explicit use of Wirtinger derivatives is not required,
+especially considering the fact that the direction of the steepest ascent of a $
+  \cplx \to \real
+$ function is given by complex conjugate gradient $\nabla_{\conj{z}}$, which coincides
 with the classical gradient of the same function viewed as $\real^2 \to \real$,

### 2020-06-21 paper/paper.tex
7  cleaned up the methodological section  * explicitly written a univariate cplx-Gaussian with entropy (full-c-ard)  * reworded the cplx-valued LRP  * edited the section on R-scaling a bit and verified its claims Also  * added hyphes to `non-`  * reworded the approximatinos for K-alpha in section 2

@@
   q_\theta(\omega) = \prod_j q_{\theta}(\omega_j)
-$, where $q_{\theta}(\omega_j)$ is $\omega_j = \mu_j \xi_j$ with $
-  \xi_j \sim p_\theta(\xi_j)
-$ iid from some $p_\theta(\xi)$.
+$, where $q_{\theta}(\omega_j)$ is $\omega_j = \mu_j \eta_j$ with $
+  \eta_j \sim p_\theta(\eta_j)
+$ iid from some $p_\theta(\eta)$.
 %
 % Binary dropout with rate $p \in (0, 1)$ uses $
-%   p_\xi
+%   p_\eta
 %     = \mathcal{B}\bigl(
@@
 \citet{kingma_variational_2015} approximated $K(\alpha)$ over $\alpha \in (0, 1)$ by
-a non-linear polynomial, and later \citet{molchanov_variational_2017} refined the
-approximation of \eqref{eq:improper-kl-div-real} by a nonlinear regression based on
-sigmoid and soft-plus.
+a polynomial with $\log$-term, and later \citet{molchanov_variational_2017} refined the
+approximation of \eqref{eq:improper-kl-div-real} by weighted sum of a sigmoid and a
+soft-plus term.
 % see p.6 sec 3.4 of kingma_variational_2015
@@
 %
-Nonlinearities in $\cplx$VNN can be hyperbolic functions or maps that operate on
+Non-linearities in $\cplx$VNN can be hyperbolic functions or maps that operate on
 $\cplx$ numbers in planar form, $
@@
 
-We propose to use fully factorized complex Gaussian posterior approximation and $\cplx$
-variant of the local reparameterization trick to extend Bayesian Dropout techniques to
-$\cplx$-valued networks. In this section we describe the approximation and derive the
-divergence penalties in \eqref{eq:sgvb_estimator}. Similarly to $\real$-valued Variational Dropout,
-the proposed $\cplx$-valued extension can be straightforwardly enhanced to provide
-structured sparsity.
+Below we develop Sparse Variational Dropout for $\cplx$VNN by using fully factorized
+complex Gaussian posterior approximation, outline the $\cplx$ variant of the Local
+Reparameterization Trick and derive the divergence penalties in \eqref{eq:sgvb_estimator}.
+The proposed $\cplx$-valued extension can readily be a part of a hierarchical variational
+approximation for structured sparsity \citep{louizos_bayesian_2017}.
 
@@
 \end{equation}
-provided $\Gamma \succeq 0$, $\Gamma^{\hop} = \Gamma$, $C^\top = C$, and $
-  \conj{\Gamma} \succeq C^{\hop} \Gamma^{-1} C
+provided $\Gamma$ is positive definite Hermitian matrix, $C^\top = C$, and $
+  \conj{\Gamma} \succeq \conj{C} \Gamma^{-1} C
 $.
+% $\Gamma \succeq 0$, $\conj{\Gamma^\top} = \Gamma$
 % notation
-Here, $M^{\top}$ is the matrix transpose, $\conj{M}$ is elementwise complex
-conjugation, and $M^{\hop} = (\conj{M})^\top$ denotes Hermitian conjugate.
+% Here, $M^{\top}$ is the matrix transpose, $\conj{M}$ is elementwise complex
+% conjugation, and $M^{\hop} = (\conj{M})^\top$ denotes Hermitian conjugate.
 %
 Matrices $\Gamma$ and $C$ are given by $
-  \mathbb{E} (z - \mu)(z - \mu)^{\hop}
+  \mathbb{E} (z - \mu)\conj{(z - \mu)^\top}
 $ and $
   \mathbb{E} (z - \mu)(z - \mu)^{\top}
-$, respectively, and $z$ is a \emph{proper} $\cplx$-Gaussian vector if $z$ and
-$\conj{z}$ are uncorrelated, i.e. $C = 0$.
+$, respectively, and $z$ is a \emph{circularly symmetric} $\cplx$-Gaussian vector
+if $z$ and $\conj{z}$ are uncorrelated, i.e. $C = 0$.
 %
 The entropy of $z$ terms of $\Gamma$ and $C$ is
-\begin{align}
+\begin{eqnarray} \label{eq:c-gauss-entropy}
   \mathbb{H}(q)
-    & = - \mathbb{E}_{z \sim q} \log{q(z)}
-    \notag \\
+    &=&
+      - \mathbb{E}_{z \sim q} \log{q(z)}
+      \\
     % &
@@
 %   \,. $$
-
-The $\cplx$-variant of the local reparameterization trick utilizes the fact that Gaussian
-vectors are closed under affine transformations:
+Parameterization of a univariate $\cplx$-Gaussian distribution is simpler: $
+  \mathcal{CN}(\mu, \sigma^2, \sigma^2 \xi)
+$ with $\xi \in \cplx$ such that $\lvert \xi \rvert \leq 1$ and $\sigma^2 \geq 0$.
+By \eqref{eq:c-gauss-entropy} its entropy is $
+  \log \pi e \sigma^2 \sqrt{1 - \lvert \xi \rvert^2}
+$.
+
 % $\cplx$-Gaussians are closed under affine transformations
+$\cplx$-Gaussianity is preserved under linear transformations, i.e. for $
+  A \in \cplx^{n \times m}
+$ and $b \in \cplx^{n}$
 \begin{equation}  \label{eq:cn-affine}
-  b + A z \sim \mathcal{N}_n^{\cplx}\bigl(
+  b + A z \sim \mathcal{C}\mathcal{N}_n\bigl(
       b + A\mu, A \Gamma A^{\hop}, A C A^\top
     \bigr)
+  \,.
+\end{equation}
+Therefore, if we have a $\cplx^{n\times m}$ matrix $W$ with \emph{independent}
+$\cplx$-Gaussian entries, i.e.
+\begin{equation}  \label{eq:c-gauss-vi-general}
+  q(W)
+    = \prod_{ij} \mathcal{CN}(
+      % W_{ij} \mid
+      \mu_{ij}, \Sigma_{ij}, \Sigma_{ij} \xi_{ij}
+    )
   \,,
 \end{equation}
-for $A \in \cplx^{n \times m}$ and $b \in \cplx^{n}$. Therefore, if $W \in \cplx^{n\times m}$
-is drawn from a fully factorized approximation
-\begin{equation}  \label{eq:c-gauss-vi-general}
-  W \sim q(W)
-    = \prod_{ij} \mathcal{N}^{\cplx} \bigl(
-      w_{ij} \vert\, \mu_{ij}, \Sigma_{ij}, C_{ij}
-    \bigr)
-  \,,
-\end{equation}
 with $
-  \mu, C \in \cplx^{n\times m}
-$, $\Sigma \in \real^{n\times m}$, and $
-  \lvert C_{ij} \rvert^2 \leq \Sigma_{ij}
-$, then for $x \in \cplx^m$ and $b \in \cplx^n$ the vector $y = b + W x$ has independent
-components with
+  \mu, \xi \in \cplx^{n\times m}
+$, $\Sigma \in [0, +\infty)^{n\times m}$ and $
+  \lvert \xi_{ij} \rvert \leq 1
+$, then for $x \in \cplx^m$ and $b \in \cplx^n$ each component $y_i$ of $y = b + W x$
+is independent univariate $\cplx$-Gaussian
 \begin{equation}  \label{eq:cplx-gauss-trick}
   y_i
-    \sim \mathcal{N}^{\cplx}
+    \sim \mathcal{C}\mathcal{N}
       \Bigl(
-        % e_i^\top \mu x + b_i,
         b_i + \sum_{j=1}^m \mu_{ij} x_j,
         \, \sum_{j=1}^m \Sigma_{ij} \lvert x_j \rvert^2,
-        \, \sum_{j=1}^m C_{ij} x_j^2
+        \, \sum_{j=1}^m \Sigma_{ij} x_j^2 \xi_{ij}
       \Bigr)
@@
 \end{equation}
-The trick requires three operations, i.e. $b + \mu x$, $\Sigma \lvert x \rvert^2$ and
-$C x^2$ with the complex modulus and square applied elementwise, and can be applied to
-any layer, the output of which depends linearly on its parameters, such as convolutional,
-affine, and bilinear transformations ($
-  (x, z) \mapsto x^\top W^{(j)} z + b_j
-$). Similar to $\real$ case, Variational Dropout for $\cplx$ convolutions draws independent
-realizations of $W$ for each spatial patch in the input \citep{molchanov_variational_2017}.
-This provides faster computations and better statistical efficiency of the SGVB gradient
-estimator by eliminating correlation from overlapping patches \citep{kingma_variational_2015}
-and allowing \eqref{eq:cplx-gauss-trick} to leverage $\cplx$ convolutions of the relation
+This is the $\cplx$-gaussian version of the Local Reparameterization Trick \eqref{eq:r-gauss-trick}.
+It requires three operations $b + \mu x$, $\Sigma \lvert x \rvert^2$ and $C x^2$ for
+$C_{ij} = \Sigma_{ij} \xi_{ij}$ with the complex modulus and square applied elementwise,
+and can be applied to any layer, the output of which depends linearly on its parameters,
+such as convolutional, affine, and bilinear transformations ($
+  (x, z) \mapsto b_j + x^\top W^{(j)} z
+$). Similar to $\real$ case, $\cplx$ convolutions draw independent realizations of $W$
+for each spatial patch in the input \citep{molchanov_variational_2017}. This provides
+faster computations and better statistical efficiency of the SGVB gradient estimator
+by eliminating correlation from overlapping patches \citep{kingma_variational_2015} and
+allowing \eqref{eq:cplx-gauss-trick} to leverage $\cplx$ convolutions of the relation
 and variance kernels with elementwise complex squares $x^2$ and amplitudes $\lvert x \rvert^2$.
@@
 
-For $\cplx$-Bayesian Dropout we propose to use fully factorized proper $\cplx$-Gaussian
-approximation \eqref{eq:c-gauss-vi-general} for weights and point estimates of biases in
-dense linear, convolutional and other, effectively, affine layers, i.e. $
+For $\cplx$-Sparse Variational Dropout we propose to use fully factorized $\cplx$-Gaussian
+approximation \eqref{eq:c-gauss-vi-general} with $
   \Sigma_{ij} = \alpha_{ij} \lvert \mu_{ij} \rvert^2
-$ and $C_{ij} = 0$. This forces the relation coefficients in \eqref{eq:cplx-gauss-trick}
-to be zero.
+$ and $\xi_{ij} = 0$ for weights in dense linear, convolutional and other, effectively,
+affine layers. Point estimates are used for biases.
+% This forces the relation coefficient in \eqref{eq:cplx-gauss-trick} to be zero.
 
@@
 
-For a fully factorized approximation $q(\omega)$ and factorized prior belief $
+For a fully factorized approximation $q(\omega)$ and factorized prior $
   \pi(\omega) = \prod_{ij} \pi(\omega_{ij})
@@
 \end{equation}
-We consider two fully factorized priors: an improper prior for Variational Dropout and
-$\cplx$-Gaussian ARD prior. We omit subscripts ${ij}$ for brevity in the next sections.
+We consider two fully factorized priors: an improper VD prior and $\cplx$-Gaussian
+ARD prior. We omit subscripts ${ij}$ for brevity in this section.
 
@@
   % \mathbb{E}_{\omega \sim q(\omega)} \log \lvert \omega \rvert^2
-  %   % = \mathbb{E}_{\xi \sim \mathcal{N}^{\cplx}(\xi \vert 1, \alpha, 0)}
-  %   %   \log \lvert \mu \xi \rvert^2
+  %   % = \mathbb{E}_{\varepsilon \sim \mathcal{N}^{\cplx}(\varepsilon \vert 1, \alpha, 0)}
+  %   %   \log \lvert \mu \varepsilon \rvert^2
   %   % = \log \lvert \mu \rvert^2
-  %   %   + \mathbb{E}_{\xi \sim \mathcal{N}^{\cplx}(\xi \vert 1, \alpha, 0)}
-  %   %       \log \lvert \xi \rvert^2
+  %   %   + \mathbb{E}_{\varepsilon \sim \mathcal{N}^{\cplx}(\varepsilon \vert 1, \alpha, 0)}
+  %   %       \log \lvert \varepsilon \rvert^2
   %   =
     \log \alpha \lvert \mu \rvert^2
-      + \mathbb{E}_{\xi \sim \mathcal{N}^{\cplx}(\xi \vert 0, 1, 0)}
-          \log{\bigl\lvert \tfrac1{\sqrt{\alpha}} + \xi \bigr\rvert^2}
+      + \mathbb{E}_{\varepsilon \sim \mathcal{CN}(0, 1, 0)}
+          \log{\bigl\lvert \tfrac1{\sqrt{\alpha}} + \varepsilon \bigr\rvert^2}
     \,.
@@
     %   + \tfrac{\beta}2 \log \alpha \lvert \mu \rvert^2
-    %   + \tfrac{\beta}2 \mathbb{E}_{\xi \sim \mathcal{N}^{\cplx}(\xi \vert 0, 1, 0)}
-    %       \log{\bigl\lvert \tfrac1{\sqrt{\alpha}} + \xi \bigr\rvert^2}
+    %   + \tfrac{\beta}2 \mathbb{E}_{\varepsilon \sim \mathcal{N}^{\cplx}(\varepsilon \vert 0, 1, 0)}
+    %       \log{\bigl\lvert \tfrac1{\sqrt{\alpha}} + \varepsilon \bigr\rvert^2}
     % =
@@
 %
-In Empirical Bayes the prior adapts to the observed data, i.e. \eqref{eq:sgvb_estimator} is optimized
-w.r.t. $\tau$ of each weight's prior. Since divergence sits in \eqref{eq:sgvb_estimator} with negative
-sign, optimal $
+In Empirical Bayes the prior adapts to the observed data, i.e. \eqref{eq:sgvb_estimator}
+is optimized w.r.t. $\tau$ of each weight's prior. The Maximimum Likelihood estimator
+of $\tau$ is given by the minimizer \eqref{eq:emp-bayes-kl-div}, i.e. $
   \tau^\ast = (\sigma^2 + \lvert \mu \rvert^2)^{-1}
-$ is found by minimizing \eqref{eq:emp-bayes-kl-div}, which gives
+$, thereby giving
 \begin{equation}  \label{eq:emp-bayes-opt-kl}
@@
 
-\subsubsection{$\cplx$-Bayesian Dropout via $\real$-scaling} % (fold)
+\subsubsection{$\cplx$-Variational Dropout via $\real$-scaling} % (fold)
 \label{ssub:real_scaling_dropout}
@@
 Consider the following parameterization of $W$: $
-  W_{ij} = \mu_{ij} \xi_{ij}
-$, $\xi_{ij} \in \real$ with $
-  \xi_{ij} \sim \mathcal{N}(1, \alpha_{ij})
+  W_{ij} = \mu_{ij} \varepsilon_{ij}
+$, $\varepsilon_{ij} \in \real$ with $
+  \varepsilon_{ij} \sim \mathcal{N}(1, \alpha_{ij})
 $, yet $\mu \in \cplx^{n \times m}$. This case corresponds to inference regarding
-relevance multipliers $\xi$ rather than the parameters themselves. Under this parameterization
-the weight distribution is fully factorized degenerate $\cplx$-Gaussian approximation
+multiplicative noise $\varepsilon$ rather than the parameters themselves. Under
+this parameterization $q(W)$ is effectively factorized degenerate $\cplx$-Gaussian
 \eqref{eq:c-gauss-vi-general} with $

### 2020-06-21 paper/paper.tex
finished replacing N-C with CN
cite pytorch

@@
   % \mathbb{E}_{\omega \sim q(\omega)} \log \lvert \omega \rvert^2
-  %   % = \mathbb{E}_{\varepsilon \sim \mathcal{N}^{\cplx}(\varepsilon \vert 1, \alpha, 0)}
+  %   % = \mathbb{E}_{\varepsilon \sim \mathcal{CN}(\varepsilon \vert 1, \alpha, 0)}
   %   %   \log \lvert \mu \varepsilon \rvert^2
   %   % = \log \lvert \mu \rvert^2
-  %   %   + \mathbb{E}_{\varepsilon \sim \mathcal{N}^{\cplx}(\varepsilon \vert 1, \alpha, 0)}
+  %   %   + \mathbb{E}_{\varepsilon \sim \mathcal{CN}(\varepsilon \vert 1, \alpha, 0)}
   %   %       \log \lvert \varepsilon \rvert^2
@@
     %   + \tfrac{\beta}2 \log \alpha \lvert \mu \rvert^2
-    %   + \tfrac{\beta}2 \mathbb{E}_{\varepsilon \sim \mathcal{N}^{\cplx}(\varepsilon \vert 0, 1, 0)}
+    %   + \tfrac{\beta}2 \mathbb{E}_{\varepsilon \sim \mathcal{CN}(\varepsilon \vert 0, 1, 0)}
     %       \log{\bigl\lvert \tfrac1{\sqrt{\alpha}} + \varepsilon \bigr\rvert^2}
@@
 
-Source code for the experiments conducted in this study and figures is available at
-\url{https://github.com/ivannz/complex_paper/tree/v2020.3}.
-%
-Source code for a PyTorch extension which implements $\cplx$-valued Variational Dropout and
-ARD layers, and provides basic layers for $\cplx$-valued networks, including maskable
-sparsified layers, is available at
+The source code for the experiments and the figures in this study is available at
+\url{https://github.com/ivannz/complex_paper/tree/v2020.6}.
+%
+The source code for a package based on PyTorch \citep{paszke_pytorch_2019}, which
+implements $\cplx$-valued Sparse Variational Dropout and ARD layers, and provides
+other basic layers for $\cplx$VNN, including maskable sparsified layers, is available at
 \url{https://github.com/ivannz/cplxmodule}.
@@
 %
-Following \citet{wolter_complex_2018} and \citet{trabelsi_deep_2018}, the class logit scores
-are taken as real part of the complex-valued output of a network.
+Following \citet{wolter_complex_2018} and \citet{trabelsi_deep_2018}, the class logit
+scores are taken as real part of the complex-valued output of a network.
 %
@@
 Since image data is not naturally $\cplx$-valued, we preprocess it by either embedding
+% $\real \hookrightarrow \cplx$
 $\real$-data into $\cplx$ assuming $\Im z = 0$ (\texttt{raw}), or applying the two-dimensional
@@
   \vec{W}
-    \sim \mathcal{N}^{\cplx}_{nm} \bigl(
+    \sim \mathcal{C}\mathcal{N}_{nm} \bigl(
       \vec{\mu}, \diag{\vec{\Sigma}}, \diag{\vec{C}}
@@
   y_i
-    \sim \mathcal{N}^{\cplx}
+    \sim \mathcal{CN}
       \bigl(

### 2020-06-22 paper/paper.tex
scattered targeted edits

@@
 \emph{Stochastic Variational Inference}, which uses stochastic gradient optimization of
-\eqref{eq:elbo_general} based on inexpensive noisy unbiased gradient estimates of ELBO
+\eqref{eq:elbo_general} based on noisy unbiased gradient estimates of ELBO
 computed on random mini-batches from the dataset. \citet{titsias_doubly_2014} translated
@@
 \end{equation}
-where $(x_{i_k})_{k=1}^M$ is a random mini-batch from $D$ and $
+where $(x_{i_k})_{k=1}^M$ is a random subsample from $D$ and $
   (\varepsilon_{lk})_{l=1}^L
-$ are $M$ independent iid samples from $p_\varepsilon$. \citet{figurnov_implicit_2019}
+$ are $k=1..M$ independent iid samples from $p_\varepsilon$. \citet{figurnov_implicit_2019}
 extended the scope of the reparameterization gradients to include continuous distributions
@@
 %
-The class of models that are allow this include non-recurrent computational graphs,
+The class of models that allow this include non-recurrent computational graphs,
 exemplified by neural networks with parameters $\omega \sim q_\theta$. In this case
@@
 \citep{wan_regularization_2013}, and Gaussian dropout \citep{wang_fast_2013} through
-the lens of Variational Inference methods and propose \emph{Variational Dropout}. They
+the lens of Variational Inference and propose \emph{Variational Dropout}. They
 argued that the multiplicative noise introduced by Dropout methods induces a distribution
@@
 from the local noise, injected by \eqref{eq:r-gauss-trick}. This modification is important
-for pruning, since $\mu$ of relevant parameters are used as estimates of their values.
+for pruning, since $\mu$ of a relevant parameter serves as the estimate of its value.
 
@@
 In appendix~\ref{sec:real-chisq-grad} we verify the value and the derivative of their
-approximation against the Monte-Carlo estimate of \eqref{eq:improper-kl-div-real} for
+approximation against a Monte-Carlo estimate for
 $\alpha$ varying over a fine logarithmic grid and the gradient of \eqref{eq:improper-kl-div-real},
@@
 $\cplx$-valued neural networks are networks that rely on the arithmetic in the complex
-domain. To achieve this implementations of $\cplx$VNN use the geometric (planar) representation
+domain. To achieve this implementations of $\cplx$VNN use a geometric representation
 of a complex number as paired \emph{real} and \emph{imaginary} values, $\cplx \simeq \real^2$,
@@
 For $\cplx$-Sparse Variational Dropout we propose to use fully factorized $\cplx$-Gaussian
-approximation \eqref{eq:c-gauss-vi-general} with $
-  \Sigma_{ij} = \alpha_{ij} \lvert \mu_{ij} \rvert^2
-$ and $\xi_{ij} = 0$ for weights in dense linear, convolutional and other, effectively,
-affine layers. Point estimates are used for biases.
+approximation \eqref{eq:c-gauss-vi-general} with Additive Noise Parameterization $
+  \alpha_{ij} = \tfrac{\Sigma_{ij}}{\lvert \mu_{ij} \rvert^2}
+$ and $\xi_{ij} = 0$ for weights in dense linear, convolutional and other effectively
+parameter-affine layers. Point estimates are used for biases.
 % This forces the relation coefficient in \eqref{eq:cplx-gauss-trick} to be zero.

### 2020-06-22 paper/plots__feature.tex
feature comparison helper file

--- 2020-06-16 paper/plots__kind-compression.tex
@@
 \usepackage{geometry}
-\geometry{a4paper,margin=10mm}
+% \geometry{a4paper,margin=10mm}
 \usepackage[english]{babel}
@@
 \maketitle
+
+The purspose of this supplementary file is to compare the preformance-compression
+profiles of diffenret input features: $\real \hookrightarrow \cplx$ (\texttt{raw}),
+and $2$d Fourier transformed (\texttt{fft}).
+
+\bigskip
+\noindent
+\textbf{Conclusion}: fourier features do not outperform unprocessed iinput, but their
+proflie exhibits ramp-like shape, when in two-layer-dense $\cplx$/$\real$ -valued
+neural networks.
+
 \listoffigures
@@
     \centering
-    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__VD__emnist_letters__fft__-0.5.pdf}
+    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__emnist_letters__raw__-0.5.pdf}
   \end{subfigure} \\ %
@@
     % used in main text
+    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__VD__emnist_letters__fft__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\columnwidth}
+    \centering
+    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__VD__emnist_letters__raw__-0.5.pdf}
+  \end{subfigure} \\ %
+  \begin{subfigure}[b]{0.5\columnwidth}
+    \centering
     \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__ARD__emnist_letters__fft__-0.5.pdf}
@@
     \centering
-    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__VD__emnist_letters__fft__-0.5.pdf}
+    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__ARD__emnist_letters__raw__-0.5.pdf}
   \end{subfigure} \\ %
@@
     \centering
-    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__ARD__emnist_letters__raw__-0.5.pdf}
+    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__VD__emnist_letters__fft__-0.5.pdf}
   \end{subfigure}%
@@
     \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__VD__emnist_letters__raw__-0.5.pdf}
-  \end{subfigure} \\ %
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__emnist_letters__raw__-0.5.pdf}
-  \end{subfigure}%
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__VD__emnist_letters__raw__-0.5.pdf}
   \end{subfigure}
   \caption{%
-    \texttt{emnist\_letters}: (row 1) $2\real / \cplx$, (rows 2, 3) $\real / \cplx$, (row 4) $\real / \tfrac12\cplx$.
+    \texttt{emnist\_letters}:
+      \texttt{fft} (left), \texttt{raw} (right).
+      Models on rows 1 \& 2 are incomparable: (left $2\real / \cplx$), (right $\real / \tfrac12\cplx$).
+      Rows 3 \& 4 feature $\real / \cplx$ models.
     % ARD method for $\real$ and $\cplx$ models using Fourier features.
@@
     \centering
-    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__VD__kmnist__fft__-0.5.pdf}
+    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__kmnist__raw__-0.5.pdf}
   \end{subfigure} \\ %
@@
     % used in main text
+    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__VD__kmnist__fft__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\columnwidth}
+    \centering
+    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__VD__kmnist__raw__-0.5.pdf}
+  \end{subfigure} \\ %
+  \begin{subfigure}[b]{0.5\columnwidth}
+    \centering
     \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__ARD__kmnist__fft__-0.5.pdf}
@@
     \centering
-    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__VD__kmnist__fft__-0.5.pdf}
+    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__ARD__kmnist__raw__-0.5.pdf}
   \end{subfigure} \\ %
@@
     \centering
-    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__ARD__kmnist__raw__-0.5.pdf}
+    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__VD__kmnist__fft__-0.5.pdf}
   \end{subfigure}%
@@
     \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__VD__kmnist__raw__-0.5.pdf}
-  \end{subfigure} \\ %
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__kmnist__raw__-0.5.pdf}
-  \end{subfigure}%
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__VD__kmnist__raw__-0.5.pdf}
   \end{subfigure}
   \caption{%
-    \texttt{kmnist}: (row 1) $2\real / \cplx$, (rows 2, 3) $\real / \cplx$, (row 4) $\real / \tfrac12\cplx$.
+    \texttt{kmnist}:
+      \texttt{fft} (left), \texttt{raw} (right).
+      Models on rows 1 \& 2 are incomparable: (left $2\real / \cplx$), (right $\real / \tfrac12\cplx$).
+      Rows 3 \& 4 feature $\real / \cplx$ models.
     % VD method for $\real$ and $\cplx$ models using Fourier features.
@@
     \centering
-    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__VD__fashionmnist__fft__-0.5.pdf}
+    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__fashionmnist__raw__-0.5.pdf}
   \end{subfigure} \\%
@@
     % used in main text
+    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__VD__fashionmnist__fft__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\columnwidth}
+    \centering
+    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__VD__fashionmnist__raw__-0.5.pdf}
+  \end{subfigure} \\%
+  \begin{subfigure}[b]{0.5\columnwidth}
+    \centering
     \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__ARD__fashionmnist__fft__-0.5.pdf}
@@
     \centering
-    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__VD__fashionmnist__fft__-0.5.pdf}
-  \end{subfigure} \\%
+    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__ARD__fashionmnist__raw__-0.5.pdf}
+  \end{subfigure} \\ %
   \begin{subfigure}[b]{0.5\columnwidth}
     \centering
-    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__ARD__fashionmnist__raw__-0.5.pdf}
+    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__VD__fashionmnist__fft__-0.5.pdf}
   \end{subfigure}%
@@
     \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__VD__fashionmnist__raw__-0.5.pdf}
-  \end{subfigure} \\ %
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__fashionmnist__raw__-0.5.pdf}
-  \end{subfigure}%
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__VD__fashionmnist__raw__-0.5.pdf}
   \end{subfigure}
   \caption{%
-    \texttt{fashionmnist}: (row 1) $2\real / \cplx$, (rows 2, 3) $\real / \cplx$, (row 4) $\real / \tfrac12\cplx$.
+    \texttt{fashionmnist}:
+      \texttt{fft} (left), \texttt{raw} (right).
+      Models on rows 1 \& 2 are incomparable: (left $2\real / \cplx$), (right $\real / \tfrac12\cplx$).
+      Rows 3 \& 4 feature $\real / \cplx$ models.
     % ARD method for $\real$ and $\cplx$ models using raw features.
@@
     \centering
-    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__VD__mnist__fft__-0.5.pdf}
+    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__mnist__raw__-0.5.pdf}
   \end{subfigure} \\%
@@
     % used in main text
-    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__ARD__mnist__fft__-0.5.pdf}
-  \end{subfigure}%
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__VD__mnist__fft__-0.5.pdf}
-  \end{subfigure} \\%
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__ARD__mnist__raw__-0.5.pdf}
-  \end{subfigure}%
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__VD__mnist__raw__-0.5.pdf}
-  \end{subfigure} \\ %
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__mnist__raw__-0.5.pdf}
+    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__VD__mnist__fft__-0.5.pdf}
   \end{subfigure}%
@@
     \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__VD__mnist__raw__-0.5.pdf}
-  \end{subfigure}
-  \caption{%
-    \texttt{mnist}: (row 1) $2\real / \cplx$, (rows 2, 3) $\real / \cplx$, (row 4) $\real / \tfrac12\cplx$.
-    % VD method for $\real$ and $\cplx$ models using raw features.
-  }
-  % \label{fig:appendix__mnist-like__trade-off__mnist}
-\end{figure}
-
-% judging features
-\begin{figure}[b]
-  \centering
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__ARD__emnist_letters__raw__-0.5.pdf}
-  \end{subfigure}%
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__VD__emnist_letters__raw__-0.5.pdf}
-  \end{subfigure} \\ %
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    % used in main text
-    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__emnist_letters__raw__-0.5.pdf}
-  \end{subfigure}%
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__VD__emnist_letters__raw__-0.5.pdf}
-  \end{subfigure} \\ %
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__ARD__kmnist__raw__-0.5.pdf}
-  \end{subfigure}%
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__VD__kmnist__raw__-0.5.pdf}
-  \end{subfigure} \\ %
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__kmnist__raw__-0.5.pdf}
-  \end{subfigure}%
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__VD__kmnist__raw__-0.5.pdf}
-  \end{subfigure}
-  \caption{%
-    \texttt{emnist\_letters}: (row 1) $2\real / \cplx$, (rows 2, 3) $\real / \cplx$, (row 4) $\real / \tfrac12\cplx$.
-    % ARD method for $\real$ and $\cplx$ models using Fourier features.
-  }
-  % \label{fig:appendix__mnist-like__trade-off__emnist_letters}
-\end{figure}
-
-\begin{figure}[b]
-  \centering
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__ARD__fashionmnist__raw__-0.5.pdf}
-  \end{subfigure}%
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__VD__fashionmnist__raw__-0.5.pdf}
-  \end{subfigure} \\ %
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    % used in main text
-    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__fashionmnist__raw__-0.5.pdf}
-  \end{subfigure}%
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__VD__fashionmnist__raw__-0.5.pdf}
-  \end{subfigure} \\ %
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__ARD__mnist__raw__-0.5.pdf}
-  \end{subfigure}%
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__VD__mnist__raw__-0.5.pdf}
-  \end{subfigure} \\ %
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__mnist__raw__-0.5.pdf}
-  \end{subfigure}%
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__VD__mnist__raw__-0.5.pdf}
-  \end{subfigure}
-  \caption{%
-    \texttt{kmnist}: (row 1) $2\real / \cplx$, (rows 2, 3) $\real / \cplx$, (row 4) $\real / \tfrac12\cplx$.
-    % VD method for $\real$ and $\cplx$ models using Fourier features.
-  }
-  % \label{fig:appendix__mnist-like__trade-off__kmnist}
-\end{figure}
-
-\begin{figure}[b]
-  \centering
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__emnist_letters__fft__-0.5.pdf}
-  \end{subfigure}%
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__VD__emnist_letters__fft__-0.5.pdf}
   \end{subfigure} \\%
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    % used in main text
-    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__ARD__emnist_letters__fft__-0.5.pdf}
-  \end{subfigure}%
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__VD__emnist_letters__fft__-0.5.pdf}
-  \end{subfigure} \\%
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__kmnist__fft__-0.5.pdf}
-  \end{subfigure}%
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__VD__kmnist__fft__-0.5.pdf}
-  \end{subfigure} \\ %
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__ARD__kmnist__fft__-0.5.pdf}
-  \end{subfigure}%
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__VD__kmnist__fft__-0.5.pdf}
-  \end{subfigure}
-  \caption{%
-    \texttt{fashionmnist}: (row 1) $2\real / \cplx$, (rows 2, 3) $\real / \cplx$, (row 4) $\real / \tfrac12\cplx$.
-    % ARD method for $\real$ and $\cplx$ models using raw features.
-  }
-  % \label{fig:appendix__mnist-like__trade-off__fashionmnist}
-\end{figure}
-
-\begin{figure}[b]
-  \centering
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__fashionmnist__fft__-0.5.pdf}
-  \end{subfigure}%
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__VD__fashionmnist__fft__-0.5.pdf}
-  \end{subfigure} \\%
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    % used in main text
-    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__ARD__fashionmnist__fft__-0.5.pdf}
-  \end{subfigure}%
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__VD__fashionmnist__fft__-0.5.pdf}
-  \end{subfigure} \\%
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__mnist__fft__-0.5.pdf}
-  \end{subfigure}%
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__cmp__VD__mnist__fft__-0.5.pdf}
-  \end{subfigure} \\ %
   \begin{subfigure}[b]{0.5\columnwidth}
@@
     \centering
+    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__ARD__mnist__raw__-0.5.pdf}
+  \end{subfigure} \\ %
+  \begin{subfigure}[b]{0.5\columnwidth}
+    \centering
     \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__VD__mnist__fft__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\columnwidth}
+    \centering
+    \includegraphics[width=\columnwidth]{figure__mnist-like__trade-off/appendix__VD__mnist__raw__-0.5.pdf}
   \end{subfigure}
   \caption{%
-    \texttt{mnist}: (row 1) $2\real / \cplx$, (rows 2, 3) $\real / \cplx$, (row 4) $\real / \tfrac12\cplx$.
+    \texttt{mnist}:
+      \texttt{fft} (left), \texttt{raw} (right).
+      Models on rows 1 \& 2 are incomparable: (left $2\real / \cplx$), (right $\real / \tfrac12\cplx$).
+      Rows 3 \& 4 feature $\real / \cplx$ models.
     % VD method for $\real$ and $\cplx$ models using raw features.

### 2020-06-22 paper/paper.tex
8 improving the presentation of the findings  * moved expected outcome from intro section to conclusions  * compressed the preliminaries of the experimental methodology  * wrote up the findings of the MNIST-like section better  * condensed CIFAR10 section and drew clearer conclusions  * added some thought stubs to conclusion

@@
 % {louizos_bayesian_2017} eq. (11) variance -> gaussian entropy -> informative bits
+% They also proposed to estiamte bit precision for quantization based on parameter's
+% estimated uncertainty (variance or entropy).
 %
@@
 
-We study the performance-compression trade-off of the proposed Bayesian sparsification
-method for $\cplx$-valued networks presented above on image classification and music
-annotation tasks.
+To verify the proposed $\cplx$-valued variational sparsification methods presented
+above and explore their compression-performance trade-off we carry out a numerical
+study of $\cplx$VNN for image classification and music transcription.
+
+% image features
+Since image data is not naturally $\cplx$-valued, we preprocess it using the natural
+inclusion $\real \hookrightarrow \cplx$ (\texttt{raw}, $\Im z = 0$) or applying the
+two-dimensional Fourier Transform (\texttt{fft}), centering the lower frequencies. We
+do not train an auxiliary network that synthesizes the imaginary component from $\real$
+input data \citep{trabelsi_deep_2018}.
 %
@@
 scores are taken as real part of the complex-valued output of a network.
-%
-% image features
-Since image data is not naturally $\cplx$-valued, we preprocess it by either embedding
-% $\real \hookrightarrow \cplx$
-$\real$-data into $\cplx$ assuming $\Im z = 0$ (\texttt{raw}), or applying the two-dimensional
-Fourier Transform (\texttt{fft}), centering the lower frequencies. We do not train an
-auxiliary model to synthesize the imaginary component from the real data, proposed by
-\citet{trabelsi_deep_2018}.
 
 % setup and common experiment settings
-For each dataset we conduct a set of experiments in which we try out all combinations of
-model kinds ($\real$ or $\cplx$), sparsification methods (VD or ARD) and input features.
-Where reasonable, we also study the effects of halving ($\tfrac12\cplx$) and doubling ($2\real$)
-of the size of intermediate layers in each network \citep{monning_evaluation_2018}.
-%
-Each experiment is replicated \emph{five} times to take into account random initialization,
-random order of the mini-batch during SGD, stochastic outputs of the intermediate layers,
-and non-determinism of single-precision computations on GPUs.
-
-Each network within every experiment passes through three successive stages of training:
-pre-training (\emph{``dense''}), sparsification (\emph{``sparsify''}), and fine-tuning
-(\emph{``fine-tune''}) (sec.~\ref{sub:staging}). The parameters and optimizer state are
-passed between stages, except for last one, which inherits just the parameters.
-%
-Every experiment uses ADAM optimizer, resets the learning rate to $10^{-3}$ before each
-stage, and applies global $\ell_2$-norm gradient clipping at $0.5$.
+The networks are trained in three successive stages in every experiment: the \emph{``pre-train''}
+stage for pre-training the network, the \emph{``sparsify''} stage to determine parameter
+relevance using Variational Dropout, and the \emph{``fine-tune''} to train the pruned
+network (sec.~\ref{sub:staging}). Network's parameters are initialized with values from
+the previous stage.
+%
+Networks are trained with ADAM optimizer, with the learning rate reset to $10^{-3}$ before
+each stage and global $\ell_2$-norm gradient clipping at $0.5$.
+% https://pytorch.org/docs/master/_modules/torch/nn/utils/clip_grad.html#clip_grad_norm_
+
+Each experiment is replicated \emph{five} times to account for random effects from
+initialization, stochastic gradient optimization, noisy output from intermediate layers,
+and non-determinism of computations on GPU.
+% experiments took about three weeks on 4 node GTX1080Ti GPUs in fp32
 
 % write a note on the incompressible parameters (bias, batch norm etc.)
-The compression rate is calculated based on the number of IEEE754 floating point values
-needed to store the model and equals $
+The compression rate is calculated based on the number of floating point values needed
+to store the network and equals $
   \tfrac{n_\mathtt{par}}{n_\mathtt{par} - n_\mathtt{zer}}
-$, where $n_\mathtt{zer}$ is the number of explicit zeros, $n_\mathtt{par}$ is the total
-number of floats. In particular, each parameter is counted once in a $\real$-valued network,
-but twice in a $\cplx$-network. Each model has a compression limit, determined by biases,
-shift and scaling in $\real$- and $\cplx$-valued batch normalization layers.
+$, where $n_\mathtt{zer}$ is the number of explicit zeros at the ``fine-tune'' stage
+and $n_\mathtt{par}$ is the total number of values. In a $\real$-valued network each
+parameter counts as \emph{one} value and as \emph{two} values in a $\cplx$VNN. Each
+model has a compression limit, determined by biases, shift and scaling in $\real$-
+and $\cplx$-valued batch normalization layers.
 
@@
 
-% The training consists of three successive stages: ``dense'' $\to$ ``sparsify'' $\to$ ``fine-tune''.
-
-At the \emph{``dense''} stage every network is fit ``as-is'', retaining its original
-non-Bayesian architecture, and using only the likelihood term from \eqref{eq:sgvb_estimator} without
-variational dropout.
-
-During the \emph{``sparsify''} stage we make every layer Bayesian and apply $\cplx$-variational
-dropout sec.~\ref{ssub:vd_prior} (or sec.~\ref{ssub:ard_prior}) or its $\real$ counterpart.
-We inject a coefficient $
+% The training consists of three successive stages: ``pre-train'' $\to$ ``sparsify'' $\to$ ``fine-tune''.
+At the \emph{``pre-train''} stage every network is fit ``as-is'', retaining its original
+deterministic architecture and using only the likelihood term from \eqref{eq:sgvb_estimator}.
+
+During the \emph{``sparsify''} stage we make every layer Bayesian and apply $\cplx$-valued
+variational sparsification (sec.~\ref{ssub:vd_prior}, ~\ref{ssub:ard_prior}) or its $\real$
+counterpart. We inject a coefficient $
   C \in (0, 1]
-$ at the KL divergence term in \eqref{eq:sgvb_estimator} to study the attainable sparsity levels:
+$ at the KL divergence term in \eqref{eq:sgvb_estimator}:
 \begin{equation}  \label{eq:elbo_with_coef}
@@
 Between \emph{``sparsify''} and \emph{``fine-tune''} stages we compute masks of non-zero
-weights in each layer based on the relevance scores $\alpha$ (sec.~\ref{sec:variational_dropout}).
-Since the $q_\theta$ factorizes into univariate distributions, a $\cplx$ or $\real$ parameter
-is considered non-zero if $\log \alpha \leq \tau$ for $
-  \alpha = \tfrac{\sigma^2}{\lvert\mu\rvert^2}
-$, or zero otherwise.
-
-The \emph{``fine-tune''} stage reverts the network back to non-Bayesian layers, applies
-sparsity masks to its parameters and proceeds with training the kept parameters as during
-the ``dense'' stage. Unless specified otherwise the network is initialized to the mode
-of the learnt $q_\theta(W)$.
-
+weights in each layer based on the relevance scores $\alpha$ (sec.~\ref{sub:dropout}).
+Since $q_\theta$ factorizes into univariate distributions, a $\cplx$ or $\real$ parameter
+is considered non-zero iff $\log \alpha \leq \tau$ for $
+  \alpha = \tfrac{\sigma^2}{\lvert \mu \rvert^2}
+$.
 % on chosing the threshold
-The threshold $\tau$ is picked so, that the remaining non-zero parameters are within
+The threshold $\tau$ is picked so that the remaining non-zero parameters are within
 $\delta$ relative tolerance of their mode with high probability under the approximate
-posterior. Since $q_\theta$ is fully factorized $\real$- or a proper $\cplx$-Gaussian,
-the random variable $
+posterior. For a univariate $\real$- or a circularly symmetric $\cplx$-Gaussian random
+variable $w$, $
   \tfrac{k \lvert w - \mu \rvert^2}
@@
 %
-For a generous tolerance $\delta = 50\%$ all values of $\log \alpha$ below $-2.5$ yield
-at least $90\%$ chance of a non-zero $\real$/$\cplx$ parameter. We pick $\tau = -\tfrac12$
-to retain parameters sufficiently concentrated around their mode, and encourage higher
-sparsity, at the same time being aware that $q_\theta$ is merely an approximation.
-In comparison, $\tau = 3$ is commonly used as the threshold
+For a tolerance $\delta = 50\%$ values $\log \alpha$ below $-2.5$ yield at least $90\%$
+chance of a non-zero $\real$/$\cplx$ parameter. We pick $\tau = -\tfrac12$ to retain
+parameters sufficiently concentrated around their mode and encourage higher sparsity,
+at the same time being aware that $q_\theta$ is merely an approximation. In comparison,
+$\tau = 3$ is commonly used as the threshold
 \citep{molchanov_variational_2017,kingma_variational_2015}.
+
+The \emph{``fine-tune''} stage reverts the network back to deterministic layers,
+initializes the parameters to the mode of $q_\theta(\omega)$ and proceeds as the
+``pre-train'' stage, except for training only the parameters specified by sparsity
+masks.
 
@@
 % dataset size
-We deliberately use a {fixed} random subset of $10k$ images from the train split of each
-dataset to fit the networks and measure the performance with classification \emph{accuracy}
-score on the usual test split.
+We deliberately use a \emph{fixed} random subset of $10k$ images from the train split
+of each dataset to fit the networks and measure the performance with classification
+\emph{accuracy} score on the usual test split.
 % Limiting the size was done primarily to test the regularization strength of compression
@@
 % (raw) R - C - 2 * R
-We consider two simple architectures for $\real$ and $\cplx$ networks in this experiment,
-which have been chosen for the purpose of illustrating the compression and understanding
-the effects of experiment parameters. \emph{TwoLayerDenseModel} is a wide dense ReLU
-network $784 \to 4096 \to n_\mathtt{out}$, and \emph{SimpleConvModel} is a ReLU net with
-two $2d$ $k_5 s_1$ convolutions with filters $20 \to 50$, two $k_2 s_2$ average pooling steps,
-and a dense classifier network $800 \to 500 \to n_\mathtt{out}$. The number of intermediate
-feature is as specified in $\real$ and $\cplx$ models, is halved in complex models tagged
-$\tfrac12\cplx$, and doubled in real models labelled $2\real$.
+We consider two simple architectures in this experiment, which have been chosen for
+the purpose of illustrating the compression and understanding the effects of experiment
+parameters. \emph{TwoLayerDenseModel} is a wide dense ReLU network $
+  784 \to 4096 \to n_\mathtt{out}
+$, and \emph{SimpleConvModel} is a ReLU net with two $2d$ $k_5 s_1$ convolutions with
+filters $20 \to 50$, two $k_2 s_2$ average pooling steps, and a classifier head
+$800 \to 500 \to n_\mathtt{out}$.
+%
+For each dataset we experiment with all combinations of model kinds ($\real$ or $\cplx$)
+and sparsification methods (VD or ARD). To take into account potential differences in
+capacity we consider halving or doubling the number of features in the intermediate layers
+\citep{monning_evaluation_2018}. Halved $\cplx$VNN are tagged $\tfrac12\cplx$, and
+doubled $\real$-valued networks are labelled $2\real$. For \texttt{fft} we compare
+$\{\real, \cplx, 2\real\}$ and for \texttt{raw} -- $\{\tfrac12\cplx, \real, \cplx\}$.
 
@@
 % grid specs
-We let $
+We vary $
   C \in \{
@@
 Figures~\ref{fig:mnist-like__trade-off__fft} and~\ref{fig:mnist-like__trade-off__raw}
-depict the resulting compression-accuracy trade-off on MNIST for the simple models
-described above (other datasets are in appendix~\ref{sec:mnist_like_experiments}).
-%
-The points represent the trade-off of the compressed networks after fine-tuning, while their
-tails illustrate the impact of this stage on the accuracy. Transparent horizontal bands on
-each plot represent min-max performance spread of an uncompressed network on the test split.
-
-The overarching pattern in all experiments on MNIST-like datasets is that both ARD and VD
-compress similarly and ARD offers marginal advantage in terms of performance after fine-tuning.
-Fourier features perform marginally worse than raw image data for each model across all
-compression rates, and their trade-off for the dense network has a hat-like shape, contrasting
-the raw image features, for which the accuracy stays at one level for moderate rates,
-and then abruptly decays in high compression regime.
-
-The impact of ``fine-tune'' is mixed, and depends on the dataset and features, although it
-frequently improves accuracy in high compression $\times50+$ (high $C$ in \eqref{eq:elbo_with_coef})
-for raw image input. On EMNIST Letters and MNIST datasets in the small compression regime the
-dense network exhibits a trough in accuracy before fine-tuning stage.
-
-% conclusions
-These experiments demonstrate that $\cplx$ Variational Dropout can offer adequate compression
-without much loss in performance for $\cplx$-valued networks. Although ARD performs on par
-with VD, unlike VD, it uses a proper prior and has a tractable analytic expression for the
-KL-divergence \eqref{eq:emp-bayes-kl-div} in both $\real$ and $\cplx$ cases.
+depict the resulting compression-accuracy trade-off on MNIST for the models described
+above (see appendix~\ref{sec:mnist_like_experiments}).
+%
+Each point represents the trade-off of the compressed network after fine-tuning, while
+its tail illustrates the impact of this stage on the performance. Transparent horizontal
+bands on each plot represent min-max performance spread of the pre-trained uncompressed
+network on the test split.
+
+% observations and conclusions
+At the same time, ``fine-tune'' stage almost always improves performance in high compression
+regime ($\times50+$ high $C$ in \eqref{eq:elbo_with_coef}), likely due to regularization from
+high sparsity.
+% On EMNIST Letters and MNIST datasets in the small compression regime the dense network
+% exhibits a trough in accuracy before fine-tuning stage.
+Fourier features catch up to the raw data in terms of performance at high compression
+rates $\times100+$ only for the \emph{TwoLayerDenseModel}.
+% spectral feature useful residual information?
+% For it the compression-performance profile exhibits a ramp-like shape, in contrast
+% to the raw features, for which the accuracy stays level for moderate rates, but then
+% abruptly drops at high rates.
+%
+Comparison of $\real$ and $\cplx$ networks with matching architecture, i.e. same effective
+layer widths in $2\real$ vs. $\cplx$ and $\real$ vs. $\tfrac12\cplx$, shows that doubled
+$\real$ networks perform and compress better than $\cplx$, due higher intrinsic redundancy
+unchecked by $\cplx$-arithmetic constraint.
+% Convolutional network compress worse because they have less redundant parameters
+
+% a table for mean comparison against C and compression-performance?
+%
 % fft: $2\real$ convolutional model trade-off overall better than $\real$, dense -- on par.
 % raw: $\cplx$ models trade-off overall better than $\tfrac12\cplx$.
-Wider $\real$ and $\cplx$ networks appear to have more favourable trade-off between
-compression and accuracy.
 % fft: any-$\real$ dense model compresses better than $\cplx$
-However, it seems that due to more intrinsic degrees of freedom, $\real$-valued models
-perform and compress better than $\cplx$, even when the former uses the same number of
-features as the latter.
 % $\cplx$-valued networks do not have as much spare capacity as $2 \real$ due to
@@
 
-We conduct an experiment on the CIFAR10 classification dataset \citep{krizhevsky_learning_2009}
-comprising $32\times 32$ color images of $10$ classes to study the performance-compression
-trade-off of a moderately large deep network.
+Having verified the $\cplx$ variational sparsification method on MNIST-like datasets
+and simple models, we turn to the CIFAR10 dataset comprising $32\times 32$ colour
+images of $10$ classes \citep{krizhevsky_learning_2009} and focus on the VGG16 network
+\citep{simonyan_very_2015}.
+%
 % same experimental setup as in MNIST, describe the VGG16 model and its cplx-valued modification
-The experiment is set up similarly to MNIST-like experiment, except that we train $\real$
-VGG16 network \citep{simonyan_very_2015} and its $\cplx$ variant, in which we have replaced
-$\real$-valued layers with their $\cplx$-valued counterparts. $\real$ and $\cplx$ VGG16 have
-the same feature sizes in intermediate layers.
-
+We train the VGG16 network and its $\cplx$ variant, in which we have replaced $\real$-valued
+layers with their $\cplx$-valued counterparts. We do not halve or double the features
+in any network, since the goal of this experiment is to assess the trade-off for a deep
+convolutional network.
+%
 % differences with mnist
-Unlike experiment in sec.~\ref{sub:mnist_like_datasets}, we consider the raw features only,
-use full training split, and allocate $20$, $40$, and $20$ epochs to each stage. During training
-the mini-batch of $128$ samples is randomly augmented by randomly flipping horizontally and
-cropping. Random cropping is done by zero-padding each side by four pixels and extracting a
-random $32\times 32$ patch from the $40\times 40$ intermediate image.
+Unlike experiment in sec.~\ref{sub:mnist_like_datasets}, we consider the raw features
+only, use full training split and allocate $20$, $40$, and $20$ epochs to each stage.
+During training the mini-batch of $128$ samples is augmented by random horizontal flipping
+and random cropping, which is done by zero-padding the image with four pixels and extracting
+a $32\times 32$ patch from the $40\times 40$ intermediate image.
 %
@@
   \{\tfrac32 2^{-\tfrac{k}2} \colon k=7, \cdots, 15\}
-$, compare VD and ARD methods, and measure accuracy on CIFAR10 test split.
+$, compare $\real / \cplx$ VD and ARD methods and measure accuracy on CIFAR10 test split.
 
@@
 % draw some conclusions
-Figure~\ref{fig:figure__cifar10__trade-off} shows that, although ARD method offers slightly
-less compression, it makes up for it by marginally better accuracy post fine-tune. VGG16 and
-$\cplx$-VGG16 exhibit similar declining compression-accuracy trade-off, but due to higher
-capacity $\cplx$-valued network yields higher accuracy \citep{monning_evaluation_2018}. Unlike
-MNIST, fine-tuning stage significantly improves the test performance, which, we speculate, might
-be due to dataset augmentation and deeper model.
-% reword this sentence
+The compression-accuracy curve in figure~\ref{fig:figure__cifar10__trade-off} shows that
+it is possible to confidently achieve $\approx100\times$ compression of a deep $\cplx$VNN
+without losing accuracy, provided the network is fine-tuned after undergoing Variational
+sparsification. Regarding methods themselves, $\cplx$-VD and $\cplx$-ARD follow the same
+declining compression-accuracy pattern, but for the same setting $C$ the latter provides
+slightly less compression with marginally better accuracy.
 
@@
 $ for $k=1, 2, 3$, while keeping $\tau$ at $-\tfrac12$. The performance is measured after
-``dense'' stage, before the beginning and upon termination of fine-tuning.
+``pre-train'' stage, before the beginning and upon termination of fine-tuning.
 %
@@
 low $C$ models get less compressed during $50$ epoch allotted for ``sparsify'' stage, which
-appears to be insufficient to move model away from the parameters after the dense stage.
+appears to be insufficient to move model away from the parameters after the ``pre-train'' stage.
 It is reasonable therefore to expect that for undercompressed models the fine-tuning stage
@@
 \label{sec:conclusion}
+
+The overarching conclusion from the conducted experiments is that both $\cplx$-ARD and
+$\cplx$-VD methods compress similarly to each other, but for the same value of $C$ in
+\eqref{eq:elbo_with_coef} ARD yields slightly higher performance post fine-tuning at
+the cost of marginally lower compression.
+
+The results of this experiment and previous ones indicate that the $\cplx$ Variational
+Dropout offers adequate compression with controllable loss in performance in $\cplx$VNN
+and has trade-off profile similar to the $\real$ counterpart. Although ARD performs on
+par with VD, unlike it, it uses a proper prior and has a tractable analytic expression
+for the KL-divergence \eqref{eq:emp-bayes-kl-div} in both $\real$ and $\cplx$ cases.%
+%
+% L0 and dropout work in the low-to-mid sparsity range, variational dropout consistently
+% ranked behind L0 on Transformer, and was bested by magnitude pruning for sparsity
+% levels of 80\% and up. Variational dropout consistently produces models on-par or better
+% than magnitude pruning on ResNet-50, and l0 fails to produce sparse models at all.
+We expect the overall conclusion of \citet{gale_state_2019} to carry over to $\cplx$VNN,
+since there is nothing fundamentally different in $\cplx$-valued versions of the methods
+they study, except for the need to operate on pairs of parameters.
 

### 2020-06-22 paper/paper.tex
9 Finished editing  * changed to times-number format  * re-written the paragraph about the fx of fine-tuning  * updated the conclusions

@@
 % estimated uncertainty (variance or entropy).
-%
 
@@
 
+The overarching conclusion from the conducted experiments is that both $\cplx$-ARD and
+$\cplx$-VD methods compress similarly to each other, but for the same value of $C$ in
+\eqref{eq:elbo_with_coef} ARD yields marginally lower compression and slightly
+higher performance post fine-tuning.
 % a table for mean comparison against C and compression-performance?
@@
 The compression-accuracy curve in figure~\ref{fig:figure__cifar10__trade-off} shows that
-it is possible to confidently achieve $\approx100\times$ compression of a deep $\cplx$VNN
+it is possible to confidently achieve around $\times100$ compression of a deep $\cplx$VNN
 without losing accuracy, provided the network is fine-tuned after undergoing Variational
@@
 % describe musicnet as in Trabelsi et al. (2017) also get some hints from thickstun_learning_2017
-We use MusicNet \citep{thickstun_learning_2017}, an audio dataset of $330$ annotated
-musical compositions, to investigate compressibility of the $1d$ VGG-like $\cplx$-convent
-proposed by \citet{trabelsi_deep_2018}. Similarly to the study, we downsample the audio
-from 44.1kHz to 11kHz, retain only $84$ out of $128$ labels, and hold-out the same validation
-and test compositions, on which we score the models with the pooled average precision.
-Each epoch lasts for $1000$ random mini-batches of the remaining $321$ pieces. The input
-features are $\cplx$-valued Fourier transformed windows of $4096$ samples from each waveform.
-The label vectors are taken from annotations at the middle of the window.
-
-Experiments with the uncompressed model aimed at replicating the result of \citet{trabelsi_deep_2018}
-have shown that early stopping almost always terminates much sooner, than $200$ epochs used
-in their study: within the first $10-20$ epochs with the validation performance peaking at
+
+% The experimental results of the experiments in previous sections indicate that the proposed
+% $\cplx$-valued Sparse Variational Dropout achieves the goal of network compression.
+% Inspired by this we set out to investigate its effects on in the domain where it has
+% been shown that CVNN outperform rvnn.
+
+MusicNet is a dataset of $330$ classical music recordings with note annotations
+\citep{thickstun_learning_2017}. \citet{trabelsi_deep_2018} proposed a $1d$ VGG-like
+$\cplx$-valued network that surpassed a similar $\real$-valued network and achieved
+$72.9\%$ pooled \emph{Average Precision} on the music transcription task.
+%
+Recently \citet{thickstun_invariances_2018} have achieved $77.3\%$ with a four-layer
+$\real$-valued network on $\log$-spaced STFT features, and \citet{draguns_residual_2020}
+are reporting $78.0\%$ with a residual-shuffle-exchange network.
+
+% Prior experiments demonstrated that the $\cplx$-valued variational sparsification
+% what can be expected from prior research.
+In this experiment we seek to compress of the $\cplx$VNN proposed by \citet{trabelsi_deep_2018}.
+The dataset is split into the same validation and test samples and handled identically
+to their study. The input features are $\cplx$-valued Fourier transforms of $4096$-sample
+windows from each waveform, and the label vectors are taken from annotations at the middle
+of the window. Each epoch lasts for $1000$ random mini-batches of the musical pieces.
+% downsample the audio from 44.1kHz to 11kHz, retain only $84$ out of $128$ labels,
+% and hold-out the same validation and test compositions
+% 
+However, we deviate from the set-up used by \citet{trabelsi_deep_2018} by clipping $\ell_2$
+norm of the gradients to $0.05$ and shifting the low frequencies of the input to the centre
+to maintain spatial locality for convolutions.
+
+Experiments with the uncompressed model aimed at replicating the original result have
+shown that early stopping almost always terminates within the first $10-20$ epochs of
+the $200$ epochs used in their study, due to the validation performance peaking at
 $10-15$ epochs and steadily declining afterwards.
 %
-Thus we opt to use shorter stages: $12$, $32$ and $50$ epochs (sec.~\ref{sub:staging}), with
-early stopping activated only during the ``fine-tune'' stage. To keep the learning rate schedule
-consistent, we scale the learning rate of $10^{-3}$ after $5$, $10$, and $20$-th epoch by
-$\tfrac1{10}$, $\tfrac1{20}$ and $\tfrac1{100}$, respectively.
-
-We deviate from the set-up used by \citet{trabelsi_deep_2018} by clipping $\ell_2$ norm of the
-gradients to $0.05$ and shifting the low frequencies of the input to the centre to maintain
-spatial locality for convolutions.
-
-We test complex ARD (sec.~\ref{ssub:ard_prior}) and VD (sec.~\ref{ssub:vd_prior}) methods
-and vary $
-  C \in \{\tfrac14, \tfrac12, \tfrac34, 1\} \cdot 10^{-k}
-$ for $k=1, 2, 3$, while keeping $\tau$ at $-\tfrac12$. The performance is measured after
-``pre-train'' stage, before the beginning and upon termination of fine-tuning.
+Thus we opt to use shorter stages: $12$, $32$ and $50$ epochs (sec.~\ref{sub:staging}),
+with early stopping activated only during the ``fine-tune'' stage. To keep the learning
+rate schedule consistent, we scale the learning rate of $10^{-3}$ after $5$, $10$, and
+$20$-th epoch by $\tfrac1{10}$, $\tfrac1{20}$ and $\tfrac1{100}$, respectively.
+
+We explore the $\cplx$-VD and $\cplx$-ARD methods by varying $C$ over the grid $
+  \{\tfrac14, \tfrac12, \tfrac34, 1\} \cdot 10^{-k}
+$ with $k=1, 2, 3$, while keeping $\tau$ at $-\tfrac12$. The performance is measured after
+``pre-train'' stage, just before and upon termination of fine-tuning.
 %
@@
 
-Figure~\ref{fig:musicnet__trade-off} shows the resulting performance-compression frontier.
-ARD slightly outperforms VD in terms of performance, but both deliver similar compression
-rates. The trade-off demonstrates that with the proposed $\cplx$-valued variational dropout
-methods (sec.~\ref{sec:c_variational_dropout}) and post-sparsification fine-tuning it is
-possible to achieve average precision level comparable to the result of \citet{trabelsi_deep_2018}
-with a model compressed $50\times$-$200\times$. Furthermore, the $k_3$ model, compressed
-$110 \times$ with $\cplx$ VD, outperforms its uncompressed baseline, but yields lower
-performance than the full model.
+The performance-compression frontier in figure~\ref{fig:musicnet__trade-off} shows that
+VD and ARD deliver similar compression rates, but ARD slightly outperforms in terms of
+the average precision. At $\times100$ compression level the $k_3$ model outperforms its
+uncompressed baseline, but yields lower AP score than the full model. In conjunction with
+post-pruning fine-tuning, both $\cplx$-valued variational sparsification methods achieve
+average precision level comparable to the result of \citet{trabelsi_deep_2018} with a
+network compressed $\times50$-$\times200$.
+% any coclusions related to k_3???
+
+% testing the fx of the threshold
+\begin{figure}[!t]
+  \centering
+  \includegraphics[width=1\columnwidth]{figure__musicnet__threshold__C__DeepConvNet.pdf}
+  \caption{%
+    The effect of fine-tuning on performance-compression curves for $
+      C\in \{\tfrac1{20}, \frac1{200}\}
+    $ in \eqref{eq:elbo_with_coef}.
+  }
+  \label{fig:hist__and__threshold__tradeoff}
+\end{figure}
+
+% effects of extra training epochs and the impact of tau
+We take the models compressed with $C \in \{\tfrac1{20}, \frac1{200}\}$ and re-run only
+the fine-tuning stage for various pruning thresholds $
+  \tau \in \{\tfrac{k}2\colon k=-8\cdots+8\}
+$. The performance-compression curves depicted in figure~\ref{fig:hist__and__threshold__tradeoff}
+are parameterized by decreasing $\tau$ from left to right, since models are not re-compressed
+and making $\tau$ monotonically influence the compression rate. From \eqref{eq:elbo_with_coef}
+and the relative positions of the curves it can be concluded that $C$ has a much more
+substantial impact on the compression profile of each method, than the choice of the
+pruning threshold.
+% coarser grid than in top plot in order not to wait for 20 compute days, but 9.5 on
+% 4 x Geforce 1080Ti, 256 Gb, core-i7 machine, running 4*2 experiments in parallel
+
+% takeaway: fine tune seems to improve performance for highly compressed models, but
+% within a limit. Worth a try for moderately compressed models, but willl must likely
+% overfit for undercompressed models. Varying $C$ in \eqref{eq:elbo_with_coef} affects
+% sparsity more strongly, than varying $\tau$. But this is only observational.
+
+% why is there such a dramamtic difference in impact of ``fine-tune''?
+We provide the following interpretation of the apparent contrast in performance impact
+borne by fine-tuning between less than $\times50$ and higher than $\times100$ compression
+regimes in figure~\ref{fig:musicnet__trade-off}, also observed in sec.~\ref{sub:mnist_like_datasets}.
+%
+% * early stopping kick in at around 10-20 epoch
+% * performance peaks at 10-15 epoch and then gradually declines
+The value of $C$ in \eqref{eq:elbo_with_coef} is a good proxy for the ranking of the
+final compression rate since it directly affects the feedback from sparsifying prior.
+So, during the $50$ epoch allotted for ``sparsify'' stage, low $C$ prevents the sparsity
+inducing prior from pulling the posterior sufficiently away from the likelihood-maximizing
+parameters inherited from the ``pre-train'' stage. It is reasonable, therefore, to expect
+that for undercompressed models the fine-tuning stage acts essentially as a continuation
+of pre-training. And, since we have observed that longer training invariably deteriorates
+the validation performance, the ``fine-tune'' stage should leads to overfitting for small
+$C$.
+%
+Figure~\ref{fig:musicnet__early_stopping} shows that the models, which have been
+sparsified with $C$ less than $\tfrac1{400}$ and have $50\times$ compression, need
+considerably less training epochs before early stopping terminates the process.
 
@@
 
-% why is there such a dramamtic difference in impact of ``fine-tune''?
-We provide the following interpretation of the apparent difference in performance impact
-of the ``fine-tune'' stage between less than $50\times$ and higher than $100\times$ compression
-regimes in figure~\ref{fig:musicnet__trade-off}, also observed in sec.~\ref{sub:mnist_like_datasets}.
-%
-% * early stopping kick in at around 10-20 epoch
-% * performance peaks at 10-15 epoch and then gradually declines
-The value of $C$ in \eqref{eq:elbo_with_coef} is a good proxy for the ranking of the final
-compression rate since it directly affects the feedback from sparsifying prior. So, with
-low $C$ models get less compressed during $50$ epoch allotted for ``sparsify'' stage, which
-appears to be insufficient to move model away from the parameters after the ``pre-train'' stage.
-It is reasonable therefore to expect that for undercompressed models the fine-tuning stage
-acts essentially as a continuation of the pre-training stage. Since we have observed that
-longer training invariably deteriorates the validation performance, the ``fine-tune'' stage
-leads to overfitting. Figure~\ref{fig:musicnet__early_stopping}, which shows that the models,
-which have been sparsified with $C$ less than $\tfrac1{400}$ and have $50\times$ compression,
-need considerably less training epochs before early stopping terminates the process.
-
-% testing the fx of the threshold
-\begin{figure}[!t]
-  \centering
-  \includegraphics[width=1\columnwidth]{figure__musicnet__threshold__C__DeepConvNet.pdf}
-  \caption{%
-    Effects of finetunig on performance-compression curves parameterized by $
-      \tau\in \{\tfrac{k}2\colon k=-8..+8 \}
-    $ for $
-      C\in \{\tfrac1{20}, \frac1{200}\}
-    $ in \eqref{eq:elbo_with_coef} during sparsification (sec.~\ref{sub:staging}).
-  }
-  \label{fig:hist__and__threshold__tradeoff}
-\end{figure}
-
-% effects of extra training epochs and the impact of tau
-We take the models from experiments with $C \in \{\tfrac1{20}, \frac1{200}\}$ and plot
-the compression and performance metrics before fine-tuning for various threshold levels
-on figure~\ref{fig:hist__and__threshold__tradeoff} (top). From \eqref{eq:elbo_with_coef} and
-the relative positions of the compression curves it can be concluded that $C$ has much
-more substantial impact on the sparsity and performance, than the choice of $\tau$.
-Furthermore, for $\tau > 0$ the performance quickly saturates while compression creeps
-downwards.
-%
-The bottom plot in figure~\ref{fig:hist__and__threshold__tradeoff} shows the effect of
-the ``fine-tune'' stage: for $\tau \leq -1$ it improves the test performance, while leaving
-it mostly unaffected for positive $\tau$. We attrbute this behaviour to regularization
-effect of high compression rate, which limits the capacity for overfitting by significantly
-reducing the excess degrees of freedom.
-% coarser grid than in top plot in order not to wait for 20 compute days, but 9.5 on
-% 4 x Geforce 1080Ti, 256 Gb, core-i7 machine, running 4*2 experiments in parallel
-
-% takeaway: fine tune seems to improve performance for highly compressed models, but
-% within a limit. Worth a try for moderately compressed models, but willl must likely
-% overfit for undercompressed models. Varying $C$ in \eqref{eq:elbo_with_coef} affects
-% sparsity more strongly, than varying $\tau$. But this is only observational.
-
 % subsection musicnet (end)
@@
 
-The overarching conclusion from the conducted experiments is that both $\cplx$-ARD and
-$\cplx$-VD methods compress similarly to each other, but for the same value of $C$ in
-\eqref{eq:elbo_with_coef} ARD yields slightly higher performance post fine-tuning at
-the cost of marginally lower compression.
-
-The results of this experiment and previous ones indicate that the $\cplx$ Variational
-Dropout offers adequate compression with controllable loss in performance in $\cplx$VNN
-and has trade-off profile similar to the $\real$ counterpart. Although ARD performs on
-par with VD, unlike it, it uses a proper prior and has a tractable analytic expression
-for the KL-divergence \eqref{eq:emp-bayes-kl-div} in both $\real$ and $\cplx$ cases.%
-%
+In this study we have presented $\cplx$-valued Variational sparsification methods to
+the ever growing set of tools for learning deep $\cplx$-valued neural networks. To
+validate the proposed $\cplx$-valued extensions of the Variational Dropout methods
+of \citet{molchanov_variational_2017} and \citet{kharitonov_variational_2018} we have
+conducted a large numerical study of $\cplx$VNN with simple architectures to assess
+the feasible performance-compression trade-off. At the cost of marginally lower performance,
+we have achieved $\times50$-$\times100$ compression of the state-of-the-art deep
+$\cplx$VNN of \citet{trabelsi_deep_2018} on the MusicNet.
+
+Analysis of experimental findings has shown that $\cplx$-VD, sec.~\ref{ssub:vd_prior},
+and $\cplx$-ARD, sec.~\ref{ssub:ard_prior} offer adequate compression with controllable
+performance degradation in $\cplx$VNN and have trade-off profile similar to their $\real$
+counterparts.
 % L0 and dropout work in the low-to-mid sparsity range, variational dropout consistently
@@
 since there is nothing fundamentally different in $\cplx$-valued versions of the methods
-they study, except for the need to operate on pairs of parameters.
-
-In this study we have extended Variational Dropout methods of \citet{kingma_variational_2015},
-\citet{molchanov_variational_2017} and \citet{kharitonov_variational_2018} to $\cplx$-valued
-Bayesian networks. To validate the proposed technique we have conducted a large numerical
-study of complex-valued networks with simple architectures in image recognition tasks to
-assess the feasible performance-compression trade-off. At the cost of marginally lower performance,
-we have achieved $50-100\times$ compression of the state-of-the-art deep $\cplx$-valued network
-of \citet{trabelsi_deep_2018} on the MusicNet.
+they study.
+%
 

### 2020-06-23 paper/paper.tex
removed hop macro
scattered de-capitalizations and edits

@@
 
-\newcommand{\hop}{{\mkern-1.5mu\dagger}}
 \newcommand{\conj}[1]{\overline{#1}}
@@
 could occur during training. \citet{wang_fast_2013} argued that the overall effect of
-binary dropout on the intermediate outputs can be approximated by a Gaussian with weight-input
+binary Dropout on the intermediate outputs can be approximated by a Gaussian with weight-input
 dependent mean and variance via the Central Limit Theorem. \citet{srivastava_dropout:_2014}
@@
 \citet{kingma_variational_2015} provided a unifying perspective on Dropout, DropConnect
-\citep{wan_regularization_2013}, and Gaussian dropout \citep{wang_fast_2013} through
-the lens of Variational Inference and propose \emph{Variational Dropout}. They
-argued that the multiplicative noise introduced by Dropout methods induces a distribution
+\citep{wan_regularization_2013}, and Gaussian Dropout \citep{wang_fast_2013} through
+the lens of Variational Inference and propose \emph{Variational Dropout}. They argued
+that the multiplicative noise introduced by Dropout methods induces a distribution
 equivalent to a fully factorized variational posterior of the form $
@@
 
-Simultaneously \citet{molchanov_variational_2017} proposed to use \emph{Additive Noise
-Parameterization} in the factorized Gaussian $q_\theta(\omega)$ in conjunction with the
-Local Reparameterization Trick. They reverted the $(\mu, \alpha)$ parameterization in
+Simultaneously \citet{molchanov_variational_2017} proposed to use \emph{additive noise
+parameterization} in the factorized Gaussian $q_\theta(\omega)$ in conjunction with the
+local reparameterization trick. They reverted the $(\mu, \alpha)$ parameterization in
 $q_\theta(\omega)$ back to $(\mu, \sigma^2)$, arguing that it reduces the variance of the
@@
 Below we develop Sparse Variational Dropout for $\cplx$VNN by using fully factorized
-complex Gaussian posterior approximation, outline the $\cplx$ variant of the Local
-Reparameterization Trick and derive the divergence penalties in \eqref{eq:sgvb_estimator}.
+complex Gaussian posterior approximation, outline the $\cplx$ version of the local
+reparameterization trick and derive the divergence penalties in \eqref{eq:sgvb_estimator}.
 The proposed $\cplx$-valued extension can readily be a part of a hierarchical variational
@@
   b + A z \sim \mathcal{C}\mathcal{N}_n\bigl(
-      b + A\mu, A \Gamma A^{\hop}, A C A^\top
+      b + A\mu, A \Gamma \conj{A^\top}, A C A^\top
     \bigr)
@@
 \end{equation}
-This is the $\cplx$-gaussian version of the Local Reparameterization Trick \eqref{eq:r-gauss-trick}.
+This is the $\cplx$-Gaussian version of the local reparameterization trick \eqref{eq:r-gauss-trick}.
 It requires three operations $b + \mu x$, $\Sigma \lvert x \rvert^2$ and $C x^2$ for
@@
 For $\cplx$-Sparse Variational Dropout we propose to use fully factorized $\cplx$-Gaussian
-approximation \eqref{eq:c-gauss-vi-general} with Additive Noise Parameterization $
+approximation \eqref{eq:c-gauss-vi-general} with additive noise parameterization $
   \alpha_{ij} = \tfrac{\Sigma_{ij}}{\lvert \mu_{ij} \rvert^2}
@@
 \end{equation}
-We consider two fully factorized priors: an improper VD prior and $\cplx$-Gaussian
+We consider two fully factorized priors: an improper prior resembling VD and $\cplx$-Gaussian
 ARD prior. We omit subscripts ${ij}$ for brevity in this section.
@@
 In Empirical Bayes the prior adapts to the observed data, i.e. \eqref{eq:sgvb_estimator}
-is optimized w.r.t. $\tau$ of each weight's prior. The Maximimum Likelihood estimator
+is optimized w.r.t. $\tau$ of each weight's prior. The Maximum Likelihood estimator
 of $\tau$ is given by the minimizer \eqref{eq:emp-bayes-kl-div}, i.e. $
@@
 The source code for a package based on PyTorch \citep{paszke_pytorch_2019}, which
-implements $\cplx$-valued Sparse Variational Dropout and ARD layers, and provides
-other basic layers for $\cplx$VNN, including maskable sparsified layers, is available at
+implements $\cplx$-valued Sparse Variational Dropout and ARD layers and provides other
+basic layers for $\cplx$VNN is available at
 \url{https://github.com/ivannz/cplxmodule}.
@@
 % dataset size
-We deliberately use a \emph{fixed} random subset of $10k$ images from the train split
-of each dataset to fit the networks and measure the performance with classification
+We deliberately use a \emph{fixed} random subset of $10$ thousand images from the train
+split of each dataset to fit the networks and measure the performance with classification
 \emph{accuracy} score on the usual test split.
@@
 and sparsification methods (VD or ARD). To take into account potential differences in
-capacity we consider halving or doubling the number of features in the intermediate layers
-\citep{monning_evaluation_2018}. Halved $\cplx$VNN are tagged $\tfrac12\cplx$, and
-doubled $\real$-valued networks are labelled $2\real$. For \texttt{fft} we compare
-$\{\real, \cplx, 2\real\}$ and for \texttt{raw} -- $\{\tfrac12\cplx, \real, \cplx\}$.
+the capacity of $\cplx$VNN we consider halving or doubling the number of features in
+the intermediate layers \citep{monning_evaluation_2018}. Halved $\cplx$VNN are tagged
+$\tfrac12\cplx$, and doubled $\real$-valued networks are labelled $2\real$. For \texttt{fft}
+we compare $\{\real, \cplx, 2\real\}$ and for \texttt{raw} -- $\{\tfrac12\cplx, \real, \cplx\}$.
 
@@
 experiment. The sparsification threshold $\tau$ is fixed at $-\tfrac12$, the training batch
-size is set to $128$ and the base learning rate ${10}^{-3}$ is reduced after the $10$-th epoch
-to ${10}^{-4}$ at every stage.
+size is set to $128$ and the base learning rate ${10}^{-3}$ is reduced after the $10$-th
+epoch to ${10}^{-4}$ at every stage.
 %
@@
 
-MusicNet is a dataset of $330$ classical music recordings with note annotations
-\citep{thickstun_learning_2017}. \citet{trabelsi_deep_2018} proposed a $1d$ VGG-like
-$\cplx$-valued network that surpassed a similar $\real$-valued network and achieved
-$72.9\%$ pooled \emph{Average Precision} on the music transcription task.
-%
-Recently \citet{thickstun_invariances_2018} have achieved $77.3\%$ with a four-layer
-$\real$-valued network on $\log$-spaced STFT features, and \citet{draguns_residual_2020}
-are reporting $78.0\%$ with a residual-shuffle-exchange network.
-
 % Prior experiments demonstrated that the $\cplx$-valued variational sparsification
 % what can be expected from prior research.
+MusicNet is a corpus of $330$ classical music recordings with note annotations used for
+learning feature representations for music transcription tasks \citep{thickstun_learning_2017}.
+\citet{trabelsi_deep_2018} have proposed a $1d$ VGG-like $\cplx$-valued network that
+surpassed a similar $\real$-valued network and achieved $72.9\%$ pooled \emph{Average
+Precision} on this dataset. Recently \citet{yang_complex_2019} have reported $74.2\%$
+AP with a $\cplx$-valued transformer, \citet{thickstun_invariances_2018} have achieved
+$77.3\%$ with a four-layer $\real$-valued network on $\log$-spaced spectrogram, and
+\citet{draguns_residual_2020} report $78.0\%$ with a residual-shuffle-exchange network.
+
 In this experiment we seek to compress of the $\cplx$VNN proposed by \citet{trabelsi_deep_2018}.
+%
 The dataset is split into the same validation and test samples and handled identically
@@
 network compressed $\times50$-$\times200$.
-% any coclusions related to k_3???
+% any conclusions related to k_3???
 
@@
 validate the proposed $\cplx$-valued extensions of the Variational Dropout methods
-of \citet{molchanov_variational_2017} and \citet{kharitonov_variational_2018} we have
-conducted a large numerical study of $\cplx$VNN with simple architectures to assess
-the feasible performance-compression trade-off. At the cost of marginally lower performance,
-we have achieved $\times50$-$\times100$ compression of the state-of-the-art deep
-$\cplx$VNN of \citet{trabelsi_deep_2018} on the MusicNet.
+\citep{molchanov_variational_2017,kharitonov_variational_2018} we have conducted a
+large numerical study of $\cplx$VNN with simple architectures to assess the feasible
+performance-compression trade-off. At the cost of marginally lower performance, we have
+achieved $\times50$-$\times100$ compression of the deep $\cplx$VNN of \citet{trabelsi_deep_2018}
+on the MusicNet.
 
@@
 We expect the overall conclusion of \citet{gale_state_2019} to carry over to $\cplx$VNN,
-since there is nothing fundamentally different in $\cplx$-valued versions of the methods
-they study.
-%
+since there is nothing fundamentally different in the proposed $\cplx$-valued variational
+sparsification methods.
 
@@
 
-We also report the trade-off comparison, when the argument by \citet{monning_evaluation_2018}
-for higher intrinsic capacity of $\cplx$-valued networks has been taken into account.
-%
 We compare $\real$ networks against $\tfrac12 \cplx$ with half the number of parameters
@@
 \begin{align}
-  (I \otimes x^\top) \diag{\vec{\Sigma}} (I \otimes x^\top)^{\hop}
+  (I \otimes x^\top) \diag{\vec{\Sigma}} \conj{(I \otimes x^\top)^\top}
     % = \sum_{ij} (I \otimes x^\top) e_i \otimes e_j

### 2020-06-23 paper/paper.tex
fixed citations

@@
   (\varepsilon_{lk})_{l=1}^L
-$ are $k=1..M$ independent iid samples from $p_\varepsilon$. \citet{figurnov_implicit_2019}
+$ are $k=1..M$ independent iid samples from $p_\varepsilon$. \citet{figurnov_implicit_2018}
 extended the scope of the reparameterization gradients to include continuous distributions
@@
 binary Dropout on the intermediate outputs can be approximated by a Gaussian with weight-input
-dependent mean and variance via the Central Limit Theorem. \citet{srivastava_dropout:_2014}
+dependent mean and variance via the Central Limit Theorem. \citet{srivastava_dropout_2014}
 proposed using independent $\mathcal{N}(1, 1)$ multiplicative noise, arguing that higher

### 2020-06-23 paper/paper.tex
10 added acknowledgements and software sections
edited appendix-C

@@
 
-The source code for the experiments and the figures in this study is available at
-\url{https://github.com/ivannz/complex_paper/tree/v2020.6}.
-%
-The source code for a package based on PyTorch \citep{paszke_pytorch_2019}, which
-implements $\cplx$-valued Sparse Variational Dropout and ARD layers and provides other
-basic layers for $\cplx$VNN is available at
-\url{https://github.com/ivannz/cplxmodule}.
-\smallskip
-
 To verify the proposed $\cplx$-valued variational sparsification methods presented
@@
 % section conclusion (end)
+
+\section*{Software and Data} % (fold)
+\label{sec:software_and_data}
+
+% we strongly encourage the publication of software and data with the camera-ready version
+% of the paper whenever appropriate. This can be done by including a URL in the copy.
+% do not include URLs that reveal your institution or identity in your submission for review
+% * provide an anonymous URL or upload the material as ``Supplementary Material'' into the CMT
+
+The source code for a package based on PyTorch \citep{paszke_pytorch_2019}, which
+implements $\cplx$-valued Sparse Variational Dropout and ARD layers and provides other
+basic layers for $\cplx$VNN is available at
+\url{https://github.com/ivannz/cplxmodule}.
+%
+The source code for the experiments and the figures in this study is available at
+\url{https://github.com/ivannz/complex_paper/tree/v2020.6}.
+
+% section* software_and_data (end)
+
+% Acknowledgements should only appear in the accepted version.
+\section*{Acknowledgements} % (fold)
+\label{sec:acknowledgements}
+
+% Do not include acknowledgements in the initial version of the paper submitted for blind review.
+
+% the final camera-ready version can (and probably should) include acknowledgements
+% Typically, this will include thanks to reviewers who gave useful comments, to colleagues
+% who contributed to the ideas, and to funding agencies and corporate sponsors that provided
+% financial support.
+We would like to thank the anonymous reviewers for their useful comments, and Evgenii
+Egorov, Ruslan Kostoev (ADASE) and Danila Doroshin (Huawei) for fruitfull discussions.
+% We thank Skoltech CDISE HPC Zhores cluster staff for providing computational infrastructure.
+The authors acknowledge the use of the Skoltech CDISE HPC cluster ``Zhores'' for obtaining
+the results presented in this paper.
+
+% section* acknowledgements (end)
 
@@
 
+% Why does this warrant an extra section in the appendix?
+In this section we show \eqref{eq:cplx-gauss-trick}.
+
 %notation
-By $e_i$ we denote the $i$-th real unit vector of dimensionality \emph{conforming} to the
-matrix-vector expression it is used in. Let $\vec{M}$ denote \emph{row-major} flattening
-of $M$ into a vector, i.e. in lexicographic order of its indices. $\diag{(\cdot)}$ embeds
-$\cplx^n$ into $n\times n$ diagonal matrices, and $\otimes$ denotes the Kronecker product,
-for which we note the following identities $
-  \vec{P Q R} = (P \otimes R^\top) \vec{Q}
+By $e_i\in \real \hookrightarrow \cplx$ we denote the $i$-th unit vector of dimensionality
+\emph{conforming} to the matrix-vector expression it is used in, $[M]$ denotes \emph{row-major}
+flattening of a matrix $M$ into a vector, i.e. in lexicographic order of its indices.
+Furthermore $\diag{(\cdot)}$ embeds vectors into matrices with zeros everywhere except
+the diagonal, and $\otimes$ is the Kronecker product, for which we note the following
+identities $
+  [P Q R] = (P \otimes R^\top) [Q]
+$, $
+  (P \otimes Q)^\top = (P^\top \otimes Q^\top)
 $, and $
@@
 
-If we assume a mean field $\cplx$-Gaussian approximate posterior for $
+If we assume a factorized $\cplx$-Gaussian approximation \eqref{eq:c-gauss-vi-general}
+for $
   W \in \cplx^{n\times m}
-$, then
+$, then $[W]$ is $\cplx$-Gaussian vector with
 \begin{equation}  \label{eq:c-gauss-vi-general-vec}
-  \vec{W}
+  [W]
     \sim \mathcal{C}\mathcal{N}_{nm} \bigl(
-      \vec{\mu}, \diag{\vec{\Sigma}}, \diag{\vec{C}}
+      [\mu], \diag{[\Sigma]}, \diag{[C]}
     \bigr)
@@
 \end{equation}
-where mean, \emph{variance} and relation are given by matrices $
-  \mu, \Sigma, C \in \cplx^{n\times m}
-$ with $\Sigma_{ij} \geq 0$, and $
+where with $C_{ij} = \Sigma_{ij} \xi_{ij}$, $\Sigma_{ij} \geq 0$, and $
   \lvert C_{ij} \rvert^2 \leq \Sigma_{ij}
-$. For any $x \in \cplx^m$ and $b\in \cplx^n$ $
+$. Then for any $x \in \cplx^m$ and $b\in \cplx^n$ we have $
   y = W x + b
-    = (I_n \otimes x^\top) \vec{W} + b
+    = (I_n \otimes x^\top) [W] + b
 $, whence the covariance and relation matrices of $y$ are
-\begin{align}
-  (I \otimes x^\top) \diag{\vec{\Sigma}} \conj{(I \otimes x^\top)^\top}
-    % = \sum_{ij} (I \otimes x^\top) e_i \otimes e_j
-    %   \Sigma_{ij} (e_i \otimes e_j)^\top (I \otimes x^\top)^{\hop}
-    % = \sum_{ij} (e_i \otimes x^\top e_j)
-    %   \Sigma_{ij} (e_i \otimes x^\top e_j)^{\hop}
-    % = \sum_{ij} (e_i \otimes x_j) \Sigma_{ij} (e_i^\top \otimes \conj{x}_j)
-    & = \sum_{i=1}^n (e_i e_i^\top) \sum_{j=1}^m \Sigma_{ij} x_j \conj{x}_j
+\begin{eqnarray}
+  \bigl(I_n \otimes x^\top\bigr)
+    \diag{[\Sigma]}
+  \conj{\bigl(I_n \otimes x^\top\bigr)^\top}
+    &=& \sum_{ij}
+      \bigl(I_n \otimes x^\top\bigr)
+      \biggl(
+        (e_i \otimes e_j)
+          \Sigma_{ij}
+        (e_i \otimes e_j)^\top
+      \biggr)
+      \conj{\bigl(I_n \otimes x^\top\bigr)^\top}
+    \notag \\
+    &=& \sum_{ij}
+      \bigl(e_i \otimes x^\top e_j \bigr)
+        \Sigma_{ij}
+      \conj{\bigl(e_i \otimes x^\top e_j \bigr)^\top}
+    \notag \\
+    % &=& \sum_{ij}
+    %     \Sigma_{ij}
+    %   \bigl(e_i e_i^\top \otimes (x^\top e_j) \conj{(x^\top e_j)^\top} \bigr)
+    % \notag \\
+    % &=& \sum_{i} (e_i e_i^\top) \sum_{j}
+    %     \Sigma_{ij} (x^\top e_j)(e_j^\top \conj{x})
+    % \notag \\
+    &=&
+    %   \sum_{i} (e_i e_i^\top) \sum_{j}
+    %     \Sigma_{ij} (x_j \conj{x_j})
+    % =
+      \sum_{i=1}^n (e_i e_i^\top)
+        \biggl\{
+          \sum_{j=1}^m \Sigma_{ij} \lvert x_j \rvert^2
+        \biggr\}
     \,,  \label{eq:cn-gauss-lrt-cov} \\
-  (I \otimes x^\top) \diag{\vec{C}} (I \otimes x^\top)^\top
-    % = \sum_{ij} (e_i \otimes x_j) C_{ij} (e_i \otimes x_j)^\top
-    & = \sum_{i=1}^n (e_i e_i^\top) \sum_{j=1}^m C_{ij} x_j^2
+  \bigl(I_n \otimes x^\top\bigr)
+    \diag{[C]}
+  \bigl(I_n \otimes x^\top\bigr)^\top
+    &=& \sum_{ij}
+      \bigl(I_n \otimes x^\top\bigr)
+      \biggl(
+        (e_i \otimes e_j)
+          C_{ij}
+        (e_i \otimes e_j)^\top
+      \biggr)
+      \bigl(I_n \otimes x^\top\bigr)^\top
+    \notag \\
+    % &=& \sum_{ij}
+    %   \bigl(e_i \otimes x^\top e_j \bigr)
+    %     C_{ij}
+    %   \bigl(e_i \otimes x^\top e_j \bigr)^\top
+    % \notag \\
+    % &=& \sum_{ij}
+    %     C_{ij}
+    %   \bigl(e_i e_i^\top \otimes (x^\top e_j) (x^\top e_j)^\top \bigr)
+    % \notag \\
+    % &=& \sum_{i} (e_i e_i^\top) \sum_{j}
+    %     C_{ij} (x^\top e_j)(e_j^\top x)
+    % \notag \\
+    &=&
+    %   \sum_{i} (e_i e_i^\top) \sum_{j}
+    %     C_{ij} (x_j x_j)
+    % =
+      \sum_{i=1}^n (e_i e_i^\top)
+        \biggl\{
+          \sum_{j=1}^m C_{ij} x_j^2
+        \biggr\}
     \,.  \label{eq:cn-gauss-lrt-rel}
-\end{align}
-Since \eqref{eq:cn-gauss-lrt-cov} and \eqref{eq:cn-gauss-lrt-rel} are diagonal, $(y_i)_{i=1}^n$
-are independent whence \eqref{eq:cn-affine} implies
-\begin{equation}  \label{eq:cplx-gauss-trick-appendix}
-  y_i
-    \sim \mathcal{CN}
-      \bigl(
-        e_i^\top \mu x + b_i,
-        \, \sum_{j=1}^m \Sigma_{ij} \lvert x_j \rvert^2,
-        \, \sum_{j=1}^m C_{ij} x_j^2
-      \bigr)
-    \,.
-\end{equation}
-Hence \eqref{eq:cplx-gauss-trick} follows.
+\end{eqnarray}
+Since \eqref{eq:cn-gauss-lrt-cov} and \eqref{eq:cn-gauss-lrt-rel} are diagonal, the
+vector $y$ has independent univariate $\cplx$-Gaussian components, whence
+\eqref{eq:cplx-gauss-trick} follows.
 

### 2020-06-23 paper/paper.tex
edited appendix-D on cplx stuff

@@
 Wirtinger ($\cplx\real$) calculus relies on the natural identification of $\cplx$ with $
-  \real \times \real
+  \real^2
 $, and regards $
   f\colon \cplx \to \cplx
-$ as an equivalent in algebraic sense function $F\colon \real^2 \to \cplx$ defined $
-  f(z) = f(u + jv) = F(u, v)
-$. Within this framework the differential of $f$ at $z = u + jv \in \cplx$ is
-$$
-df(z)
-  = \frac{\partial f}{\partial z} dz
-    + \frac{\partial f}{\partial \conj{z}} d\conj{z}
-   % = \frac12\bigl(
-   %    \frac{\partial}{\partial u}
-   %    - j \frac{\partial}{\partial v}
-   % \bigr) F (du - j dv)
-   % + \frac12\bigl(
-   %    \frac{\partial}{\partial u}
-   %    + j \frac{\partial}{\partial v}
-   % \bigr) F (du - j dv)
-   % = \frac12 \bigl(
-   %    \frac{\partial F}{\partial u} du - j \frac{\partial F}{\partial v} du
-   %    + j \frac{\partial F}{\partial u} dv + \frac{\partial F}{\partial v} dv
-   % \bigr)
-   % + \frac12 \bigl(
-   %    \frac{\partial F}{\partial u} du + j \frac{\partial F}{\partial v} du
-   %    - j \frac{\partial F}{\partial u} dv + \frac{\partial F}{\partial v} dv
-   % \bigr)
-   = \frac{\partial F}{\partial u} du
-     + \frac{\partial F}{\partial v} dv
-   = dF(u, v)
-  \,, $$
-with formally defined derivatives $
+$ as an algebraically equivalent function $F\colon \real^2 \to \cplx$ defined $
+  f(z) = f(u + \iu v) = F(u, v)
+$. It enables general treatment of functions of vector $\cplx$-argument that possess partial
+derivatives with respect to real and imaginary parts, yet do are not required to satisfy
+Cauchy-Riemann conditions. In $\cplx\real$ calculus the complex argument $z$ and its
+conjugate $\conj{z}$ act as independent variables and $f(z)$ is treated as $f(z, \conj{z})$
+by way of geometric transformations $z = u + \iu v$ and $\conj{z} = u - \iu v$.
+
+Wirtinger partial derivative operators are formally defined as $
   \tfrac{\partial}{\partial z}
@@
       + \tfrac{\partial f}{\partial \conj{z}} d\conj{z}
-  % = \conj{\tfrac{\partial \conj{f}}{\partial \conj{z}}} dz
-  % + \conj{\conj{\tfrac{\partial f}{\partial \conj{z}}} dz}
-  = 2 \Re \Bigl(
-    \conj{\tfrac{\partial f}{\partial \conj{z}}} dz
-  \Bigr)
-  = 2 \Re \bigl(
+    % = \tfrac{\partial f}{\partial z} dz
+    %   + \conj{\tfrac{\partial f}{\partial z}} d\conj{z}
+    = \tfrac{\partial f}{\partial z} dz
+      + \conj{\tfrac{\partial f}{\partial z} dz}
+    % = 2 \Re
+    %   \Bigl(
+    %     \conj{\tfrac{\partial f}{\partial \conj{z}}} dz
+    %   \Bigr)
+    = 2 \Re
+      \bigl(
         \tfrac{\partial f}{\partial z} dz
       \bigr)
-  \,. $$
-Thus, the gradient of $f$ at $z$ is given by $
-  \nabla_z f(z)
+    \,.
+\end{equation*}
+Therefore the gradient the direction of greatest ascent of $f$ at $z$ is given by $
+  \nabla_{\conj{z}} f(z)
+    = \conj{\tfrac{\partial f}{\partial z}}
     = \tfrac{\partial F}{\partial u}
-      + j \tfrac{\partial F}{\partial v}
+    + \iu \tfrac{\partial F}{\partial v}
 $.
-
-Natural identification of $\cplx$ with $\real\times \real$, storing the real and imaginary
-parts in interleaved format, emulation of $\cplx$-algebra using $\real$-valued arithmetic,
-and Wirtinger calculus make it possible to reuse $\real$ back-propagation and existing
-auto-differentiation frameworks \citep{trabelsi_deep_2018}.
+Natural identification $\cplx \simeq \real^2$, backed by Wirtinger calculus, and emulation
+of $\cplx$-arithmetic in computational graphs with $\real$-valued operations makes it
+possible to reuse $\real$ back-propagation and existing auto-differentiation frameworks.
 

### 2020-06-23 paper/paper.tex
proofread the paper

@@
 The class of models that allow this include non-recurrent computational graphs,
-exemplified by neural networks with parameters $\omega \sim q_\theta$. In this case
+exemplified by neural networks with parameters $\omega \sim q_\theta$. In their case,
 \eqref{eq:sgvb_estimator} would require that the \emph{entire} set of network's parameters
-$\omega$ be independently drawn for each element in the mini-batch. However, noting
-that the parameters in a network naturally decompose into subsets with non-overlapping
-layer-wise effects, it is standard to assume that the approximation $
+$\omega$ be independently drawn for each element in the mini-batch. Since that the
+parameters in a network naturally split into subsets with non-overlapping layer-wise
+effects, it is standard to assume that the approximation $
   q_\theta(\omega)
@@
 \end{equation}
-\citet{kingma_variational_2015} approximated $K(\alpha)$ over $\alpha \in (0, 1)$ by
-a polynomial with $\log$-term, and later \citet{molchanov_variational_2017} refined the
-approximation of \eqref{eq:improper-kl-div-real} by weighted sum of a sigmoid and a
+\citet{kingma_variational_2015} approximated $K(\alpha)$ over $\alpha \in (0, 1)$ by a
+polynomial with a logarithmic term, and later \citet{molchanov_variational_2017} refined
+the approximation of \eqref{eq:improper-kl-div-real} by weighted sum of a sigmoid and a
 soft-plus term.
@@
 In appendix~\ref{sec:real-chisq-grad} we verify the value and the derivative of their
-approximation against a Monte-Carlo estimate for
-$\alpha$ varying over a fine logarithmic grid and the gradient of \eqref{eq:improper-kl-div-real},
-for which we obtain an exact expression.
+approximation against a Monte-Carlo estimate for $\alpha$ varying over a fine logarithmic
+grid and the exact expression for gradient of \eqref{eq:improper-kl-div-real}.
 % (!) good for SGVB: gradient-based methods require unbiased gradient estimates
@@
 $\cplx$-valued neural networks are networks that rely on the arithmetic in the complex
-domain. To achieve this implementations of $\cplx$VNN use a geometric representation
+domain. To achieve this implementations of $\cplx$VNN use the geometric representation
 of a complex number as paired \emph{real} and \emph{imaginary} values, $\cplx \simeq \real^2$,
@@
 of functions of complex argument, by regarding $z$ and its \emph{complex conjugate}
-$\conj{z}$ as independent variables and defining derivatives with respect to them through
-partial derivatives with respect to real and imaginary parts. These definitions simplify
-manual calculations of $\cplx$ derivatives and satisfy the product and chain rules, respect
-complex conjugation and linearity for $\cplx \to \cplx$ maps. $\cplx\real$ calculus was
-used to define $\cplx$ version of back-propagation,
-\citep{benvenuto_complex_1992,guberman_complex_2016}.
+$\conj{z}$ as independent variables and defining derivative operators with respect to
+them through partial derivatives with respect to real and imaginary parts. These definitions
+simplify manual analysis of $\cplx$ derivatives and satisfy the product and chain rules, respect
+complex conjugation and linearity for $\cplx \to \cplx$ maps, and such were used to define
+$\cplx$ version of back-propagation, \citep{benvenuto_complex_1992,guberman_complex_2016}.
 However, since auto-differentiation frameworks can algorithmically handle computational
@@
 
-Below we develop Sparse Variational Dropout for $\cplx$VNN by using fully factorized
-complex Gaussian posterior approximation, outline the $\cplx$ version of the local
-reparameterization trick and derive the divergence penalties in \eqref{eq:sgvb_estimator}.
+In this section we develop Sparse Variational Dropout for $\cplx$VNN by using a fully
+factorized complex Gaussian posterior approximation. We outline the $\cplx$ version of
+the local reparameterization trick and derive the divergence penalties in \eqref{eq:sgvb_estimator}.
 The proposed $\cplx$-valued extension can readily be a part of a hierarchical variational
@@
   \mathbb{E} (z - \mu)(z - \mu)^{\top}
-$, respectively, and $z$ is a \emph{circularly symmetric} $\cplx$-Gaussian vector
-if $z$ and $\conj{z}$ are uncorrelated, i.e. $C = 0$.
+$, respectively, and the random vector $z$ is a \emph{circularly symmetric} $\cplx$-Gaussian
+vector if $z$ and $\conj{z}$ are uncorrelated, i.e. $C = 0$.
 %
@@
 This is the $\cplx$-Gaussian version of the local reparameterization trick \eqref{eq:r-gauss-trick}.
-It requires three operations $b + \mu x$, $\Sigma \lvert x \rvert^2$ and $C x^2$ for
-$C_{ij} = \Sigma_{ij} \xi_{ij}$ with the complex modulus and square applied elementwise,
-and can be applied to any layer, the output of which depends linearly on its parameters,
-such as convolutional, affine, and bilinear transformations ($
+It requires three matrix-vector operations: $\cplx$-valued $b + \mu x$ and $C x^2$,
+and $\real$-valued $
+  \Sigma \lvert x \rvert^2
+$, where $C_{ij} = \Sigma_{ij} \xi_{ij}$ and the complex modulus and square are applied
+elementwise. \eqref{sub:c_gauss_and_local_rep} can be applied to any layer, the output
+of which depends linearly on its parameters, such as convolutional, affine, and bilinear
+transformations ($
   (x, z) \mapsto b_j + x^\top W^{(j)} z
-$). Similar to $\real$ case, $\cplx$ convolutions draw independent realizations of $W$
+$). Similar to the $\real$ case, $\cplx$ convolutions draw independent realizations of $W$
 for each spatial patch in the input \citep{molchanov_variational_2017}. This provides
@@
 by eliminating correlation from overlapping patches \citep{kingma_variational_2015} and
-allowing \eqref{eq:cplx-gauss-trick} to leverage $\cplx$ convolutions of the relation
-and variance kernels with elementwise complex squares $x^2$ and amplitudes $\lvert x \rvert^2$.
+allowing \eqref{eq:cplx-gauss-trick} to efficiently leverage $\cplx$ convolutions of
+the relation and variance kernels with elementwise complex squares $x^2$ and amplitudes
+$\lvert x \rvert^2$.
 % Weight sharing is essentially pushed to shared variational parameters $\theta$ in the approximation $q_\theta$.
@@
 For $\cplx$-Sparse Variational Dropout we propose to use fully factorized $\cplx$-Gaussian
-approximation \eqref{eq:c-gauss-vi-general} with additive noise parameterization $
+approximation \eqref{eq:c-gauss-vi-general} with $\xi_{ij} = 0$ and additive noise
+parameterization ($
   \alpha_{ij} = \tfrac{\Sigma_{ij}}{\lvert \mu_{ij} \rvert^2}
-$ and $\xi_{ij} = 0$ for weights in dense linear, convolutional and other effectively
-parameter-affine layers. Point estimates are used for biases.
+$) for weights in dense linear, convolutional and other effectively parameter-affine
+layers. Point estimates are used for biases.
 % This forces the relation coefficient in \eqref{eq:cplx-gauss-trick} to be zero.
@@
 \end{equation}
-We consider two fully factorized priors: an improper prior resembling VD and $\cplx$-Gaussian
+We consider two fully factorized priors: an improper prior, resembling VD, and $\cplx$-Gaussian
 ARD prior. We omit subscripts ${ij}$ for brevity in this section.
@@
 
-Consider the following parameterization of $W$: $
+We consider the following parameterization of $W$: $
   W_{ij} = \mu_{ij} \varepsilon_{ij}
@@
 multiplicative noise $\varepsilon$ rather than the parameters themselves. Under
-this parameterization $q(W)$ is effectively factorized degenerate $\cplx$-Gaussian
+this parameterization $q(W_{ij})$ is effectively degenerate univariate $\cplx$-Gaussian
 \eqref{eq:c-gauss-vi-general} with $
@@
 and $\cplx$-valued batch normalization layers.
+% variace parameters in q_\theta are completely ignored.
 
@@
 initializes the parameters to the mode of $q_\theta(\omega)$ and proceeds as the
-``pre-train'' stage, except for training only the parameters specified by sparsity
-masks.
+``pre-train'' stage, except for training only those parameters, which are specified
+by sparsity masks.
 
@@
 % dataset size
-We deliberately use a \emph{fixed} random subset of $10$ thousand images from the train
+We deliberately use a \emph{fixed} random subset of \emph{ten thousand} images from the train
 split of each dataset to fit the networks and measure the performance with classification
@@
 depict the resulting compression-accuracy trade-off on MNIST for the models described
-above (see appendix~\ref{sec:mnist_like_experiments}).
+above.
 %
@@
 network on the test split.
+%
+Results for other MNIST-like dataset are presented appendix~\ref{sec:mnist_like_experiments}.
 
 % observations and conclusions
+The overarching conclusion from the conducted experiments is that both $\cplx$-ARD and
+$\cplx$-VD methods compress similarly to each other, but for the same value of $C$ in
+\eqref{eq:elbo_with_coef} ARD yields marginally lower compression and slightly higher
+performance post fine-tuning. For each fixed $C$ the compression rates after ``sparsify''
+stage are roughly identical.
+% a table for mean comparison against C and compression-performance?
+%
+% fft: $2\real$ convolutional model trade-off overall better than $\real$, dense -- on par.
+% raw: $\cplx$ models trade-off overall better than $\tfrac12\cplx$.
+% fft: any-$\real$ dense model compresses better than $\cplx$
+% $\cplx$-valued networks do not have as much spare capacity as $2 \real$ due to
+%  constraints imposed by multiplication in $\cplx$ numbers
+%
 At the same time, ``fine-tune'' stage almost always improves performance in high compression
@@
 layer widths in $2\real$ vs. $\cplx$ and $\real$ vs. $\tfrac12\cplx$, shows that doubled
-$\real$ networks perform and compress better than $\cplx$, due higher intrinsic redundancy
+$\real$ networks perform and compress better than $\cplx$, due to higher intrinsic redundancy
 unchecked by $\cplx$-arithmetic constraint.
 % Convolutional network compress worse because they have less redundant parameters
-
-The overarching conclusion from the conducted experiments is that both $\cplx$-ARD and
-$\cplx$-VD methods compress similarly to each other, but for the same value of $C$ in
-\eqref{eq:elbo_with_coef} ARD yields marginally lower compression and slightly
-higher performance post fine-tuning.
-% a table for mean comparison against C and compression-performance?
-%
-% fft: $2\real$ convolutional model trade-off overall better than $\real$, dense -- on par.
-% raw: $\cplx$ models trade-off overall better than $\tfrac12\cplx$.
-% fft: any-$\real$ dense model compresses better than $\cplx$
-% $\cplx$-valued networks do not have as much spare capacity as $2 \real$ due to
-%  constraints imposed by multiplication in $\cplx$ numbers
 
@@
 only, use full training split and allocate $20$, $40$, and $20$ epochs to each stage.
-During training the mini-batch of $128$ samples is augmented by random horizontal flipping
+During training every mini-batch of $128$ samples is augmented by random horizontal flipping
 and random cropping, which is done by zero-padding the image with four pixels and extracting
@@
 % what can be expected from prior research.
-MusicNet is a corpus of $330$ classical music recordings with note annotations used for
-learning feature representations for music transcription tasks \citep{thickstun_learning_2017}.
+MusicNet is a corpus of $330$ annotated classical music recordings used for learning
+feature representations for music transcription tasks \citep{thickstun_learning_2017}.
 \citet{trabelsi_deep_2018} have proposed a $1d$ VGG-like $\cplx$-valued network that
@@
 VD and ARD deliver similar compression rates, but ARD slightly outperforms in terms of
-the average precision. At $\times100$ compression level the $k_3$ model outperforms its
+the average precision at the cost of marginally lower compression.
+%
+At $\times100$ compression level the $k_3$ model outperforms its
 uncompressed baseline, but yields lower AP score than the full model. In conjunction with
@@
 average precision level comparable to the result of \citet{trabelsi_deep_2018} with a
-network compressed $\times50$-$\times200$.
+network having $50$-$200$ times less parameters.
 % any conclusions related to k_3???
@@
 are parameterized by decreasing $\tau$ from left to right, since models are not re-compressed
-and making $\tau$ monotonically influence the compression rate. From \eqref{eq:elbo_with_coef}
+which makes $\tau$ monotonically affect the compression rate. From \eqref{eq:elbo_with_coef}
 and the relative positions of the curves it can be concluded that $C$ has a much more
@@
 of pre-training. And, since we have observed that longer training invariably deteriorates
-the validation performance, the ``fine-tune'' stage should leads to overfitting for small
+the validation performance, the ``fine-tune'' stage should lead to overfitting for small
 $C$.
@@
 % than magnitude pruning on ResNet-50, and l0 fails to produce sparse models at all.
-We expect the overall conclusion of \citet{gale_state_2019} to carry over to $\cplx$VNN,
-since there is nothing fundamentally different in the proposed $\cplx$-valued variational
-sparsification methods.
+Therefore, we expect the overall conclusion of \citet{gale_state_2019} to carry over to
+$\cplx$VNN, since there is nothing fundamentally different in the proposed $\cplx$-valued
+variational sparsification methods.
 
@@
 $. It enables general treatment of functions of vector $\cplx$-argument that possess partial
-derivatives with respect to real and imaginary parts, yet do are not required to satisfy
+derivatives with respect to real and imaginary parts, yet are not required to satisfy
 Cauchy-Riemann conditions. In $\cplx\real$ calculus the complex argument $z$ and its
@@
 \end{equation*}
-Therefore the gradient the direction of greatest ascent of $f$ at $z$ is given by $
+Therefore the gradient of $f$ at $z$ is given by $
   \nabla_{\conj{z}} f(z)
@@
     + \iu \tfrac{\partial F}{\partial v}
-$.
-Natural identification $\cplx \simeq \real^2$, backed by Wirtinger calculus, and emulation
+$. The identification $\cplx \simeq \real^2$, backed by Wirtinger calculus, and emulation
 of $\cplx$-arithmetic in computational graphs with $\real$-valued operations makes it

### 2020-06-23 paper/paper.tex
cite han-learning for mebedded motivation and shoretn certain paragraphs

@@
 computed on random mini-batches from the dataset. \citet{titsias_doubly_2014} translated
-dependence on $\theta$ from $q_{\theta}$ to the functions inside the expectations of ELBO
-and propose \emph{Doubly Stochastic Variational Inference}, which computes unbiased gradient
-estimator based on both dataset subsampling and random draws from variational distribution
-$q_{\theta}$. Note, that the KL divergence term can replaced by its unbiased differentiable
-finite-sample estimator without forfeiting convergence of (doubly) SVI.
+the dependence on location–scale parameters of $q_{\theta}$ to the function inside its
+expectation and proposed \emph{Doubly Stochastic Variational Inference}. DSVI constructs
+an unbiased finite-sample estimator of the gradient of \eqref{eq:elbo_general} by both
+subsampling the dataset and sampling from $q_{\theta}$, without forfeiting convergence
+of SVI.
 
@@
 that the multiplicative noise introduced by Dropout methods induces a distribution
-equivalent to a fully factorized variational posterior of the form $
+equivalent to a fully factorized variational posterior $
   q_\theta(\omega) = \prod_j q_{\theta}(\omega_j)
@@
 % see p.6 sec 3.4 of kingma_variational_2015
-In appendix~\ref{sec:real-chisq-grad} we verify the value and the derivative of their
-approximation against a Monte-Carlo estimate for $\alpha$ varying over a fine logarithmic
-grid and the exact expression for gradient of \eqref{eq:improper-kl-div-real}.
+In appendix~\ref{sec:real-chisq-grad} we verify the derivative of their approximation
+against a Monte-Carlo estimate for $\alpha$ varying over a fine $\log$-scale grid and
+the exact expression for gradient of \eqref{eq:improper-kl-div-real}.
 % (!) good for SGVB: gradient-based methods require unbiased gradient estimates
@@
   \pi(\omega) = \prod_{ij} \pi(\omega_{ij})
-$, the divergence term in ELBO \eqref{eq:sgvb_estimator} is
+$, the divergence term \eqref{eq:sgvb_estimator} is
 \begin{equation}  \label{eq:elbo-general-kl-div}
@@
 % The training consists of three successive stages: ``pre-train'' $\to$ ``sparsify'' $\to$ ``fine-tune''.
-At the \emph{``pre-train''} stage every network is fit ``as-is'', retaining its original
-deterministic architecture and using only the likelihood term from \eqref{eq:sgvb_estimator}.
-
-During the \emph{``sparsify''} stage we make every layer Bayesian and apply $\cplx$-valued
+At the \emph{``pre-train''} stage every network is fit ``as-is'' using deterministic layers
+and only the likelihood term from \eqref{eq:sgvb_estimator}.
+
+During the \emph{``sparsify''} stage we make every layer stochastic and apply $\cplx$-valued
 variational sparsification (sec.~\ref{ssub:vd_prior}, ~\ref{ssub:ard_prior}) or its $\real$
@@
 
-The \emph{``fine-tune''} stage reverts the network back to deterministic layers,
-initializes the parameters to the mode of $q_\theta(\omega)$ and proceeds as the
-``pre-train'' stage, except for training only those parameters, which are specified
-by sparsity masks.
+At the \emph{``fine-tune''} stage the network reverts back to deterministic architecture
+and proceeds the same way as the ``pre-train'' stage, except for training only those
+parameters, which are specified by sparsity masks.
 
@@
   \{\tfrac32 2^{-\tfrac{k}2} \colon k=7, \cdots, 15\}
-$, compare $\real / \cplx$ VD and ARD methods and measure accuracy on CIFAR10 test split.
+$, compare $\real / \cplx$ VD and ARD methods and measure accuracy on the usual test split.
 
@@
 % effects of extra training epochs and the impact of tau
-We take the models compressed with $C \in \{\tfrac1{20}, \frac1{200}\}$ and re-run only
-the fine-tuning stage for various pruning thresholds $
+We take the full models compressed with $C \in \{\tfrac1{20}, \frac1{200}\}$ and re-run
+only the fine-tuning stage for various pruning thresholds $
   \tau \in \{\tfrac{k}2\colon k=-8\cdots+8\}
@@
 %
-Figure~\ref{fig:musicnet__early_stopping} shows that the models, which have been
-sparsified with $C$ less than $\tfrac1{400}$ and have $50\times$ compression, need
-considerably less training epochs before early stopping terminates the process.
+Figure~\ref{fig:musicnet__early_stopping} shows that the models, which have been sparsified
+with $C$ less than $\tfrac1{400}$, have less than $50\times$ compression and need considerably
+less training epochs before early stopping terminates the process.
 
@@
     \centering
-    \includegraphics[width=\columnwidth]{figure__fine-tune_fx__early__compression.pdf}
+    \includegraphics[width=\columnwidth]{figure__fine-tune_fx__early.pdf}
   \end{subfigure}
@@
 complexity of $\cplx$-valued networks.
+% CVNN capacity grows by \sqrt{2}, compute grows by 2 % RVNN caption by 2 compute by 2.
 

### 2020-06-23 paper/paper.tex
updated references

@@
 transcription and spectral speech modelling \citep{wisdom_full-capacity_2016,trabelsi_deep_2018},
-and wireless signal classification \citep{yang_complex_2019}. \citet{tarver_design_2019}
+and wireless signal classification \citep{yang_complex_2020}. \citet{tarver_design_2019}
 have lowered the out-of-band power leakage with a $\cplx$-valued network for digital
@@
 $\cplx$-valued batch-normalization and weight initialization, \citet{wolter_complex_2018}
-investigated different $\cplx$-valued gating mechanisms for RNNs, and \citet{yang_complex_2019}
+investigated different $\cplx$-valued gating mechanisms for RNNs, and \citet{yang_complex_2020}
 proposed $\cplx$-valued self-attention and complex transformer architecture. It merits
@@
 surpassed a similar $\real$-valued network and achieved $72.9\%$ pooled \emph{Average
-Precision} on this dataset. Recently \citet{yang_complex_2019} have reported $74.2\%$
+Precision} on this dataset. Recently \citet{yang_complex_2020} have reported $74.2\%$
 AP with a $\cplx$-valued transformer, \citet{thickstun_invariances_2018} have achieved

### 2020-06-23 paper/paper.tex
better to conclude with additive noise

@@
 % estimated uncertainty (variance or entropy).
-
-Simultaneously \citet{molchanov_variational_2017} proposed to use \emph{additive noise
-parameterization} in the factorized Gaussian $q_\theta(\omega)$ in conjunction with the
-local reparameterization trick. They reverted the $(\mu, \alpha)$ parameterization in
-$q_\theta(\omega)$ back to $(\mu, \sigma^2)$, arguing that it reduces the variance of the
-SGVB \eqref{eq:sgvb_estimator}, by rendering the gradient with respect to $\mu$ independent
-from the local noise, injected by \eqref{eq:r-gauss-trick}. This modification is important
-for pruning, since $\mu$ of a relevant parameter serves as the estimate of its value.
-
-Due factorization assumption, the term $KL(q_\theta \| \pi)$ in \eqref{eq:sgvb_estimator}
+%
+Due to factorization assumption, the term $KL(q_\theta \| \pi)$ in \eqref{eq:sgvb_estimator}
 for Sparse VD unravels into $
@@
 % practical difference between them?
+
+Simultaneously the method \citet{molchanov_variational_2017} proposed to use \emph{additive
+noise parameterization} in the factorized Gaussian $q_\theta(\omega)$ in conjunction with
+the local reparameterization trick. They reverted the $(\mu, \alpha)$ parameterization in
+$q_\theta(\omega)$ back to $(\mu, \sigma^2)$, arguing that it reduces the variance of the
+SGVB \eqref{eq:sgvb_estimator}, by rendering the gradient with respect to $\mu$ independent
+from the local noise, injected by \eqref{eq:r-gauss-trick}. This modification is important
+for pruning, since $\mu$ of a relevant parameter serves as the estimate of its value.
 

### 2020-06-23 paper/paper.tex
12 written the conclusions better

@@
 
-In this study we have presented $\cplx$-valued Variational sparsification methods to
+In this study we have presented $\cplx$-valued variational sparsification methods to
 the ever growing set of tools for learning deep $\cplx$-valued neural networks. To
-validate the proposed $\cplx$-valued extensions of the Variational Dropout methods
-\citep{molchanov_variational_2017,kharitonov_variational_2018} we have conducted a
-large numerical study of $\cplx$VNN with simple architectures to assess the feasible
-performance-compression trade-off. At the cost of marginally lower performance, we have
-achieved $\times50$-$\times100$ compression of the deep $\cplx$VNN of \citet{trabelsi_deep_2018}
-on the MusicNet.
-
-Analysis of experimental findings has shown that $\cplx$-VD, sec.~\ref{ssub:vd_prior},
-and $\cplx$-ARD, sec.~\ref{ssub:ard_prior} offer adequate compression with controllable
-performance degradation in $\cplx$VNN and have trade-off profile similar to their $\real$
-counterparts.
+validate these methods we have carried out a large numerical study of $\cplx$VNN with
+simple architectures to assess the feasible performance-compression trade-off, and
+studied compression of two deep convolutional $\cplx$VNN. At the cost of marginally
+lower performance, we have achieved $\times50$-$\times100$ compression of the deep
+$\cplx$VNN of \citet{trabelsi_deep_2018} on the MusicNet.
+% CVNN capacity grows by \sqrt{2}, compute grows by 2 % RVNN caption by 2 compute by 2.
+
+Experimental results show that $\cplx$-VD (sec.~\ref{ssub:vd_prior}) and $\cplx$-ARD
+(sec.~\ref{ssub:ard_prior}) exhibit trade-off profiles matching their $\real$-valued
+counterparts. This makes us confident that the overall conclusion of \citet{gale_state_2019}
+is applicable to $\cplx$VNN and the proposed $\cplx$-valued variational sparsification
+methods.
 % L0 and dropout work in the low-to-mid sparsity range, variational dropout consistently
@@
 % than magnitude pruning on ResNet-50, and l0 fails to produce sparse models at all.
-Therefore, we expect the overall conclusion of \citet{gale_state_2019} to carry over to
-$\cplx$VNN, since there is nothing fundamentally different in the proposed $\cplx$-valued
-variational sparsification methods.
-
-The results of this study have direct implications for real-time signal processing with
-embedded deep learning applications both in terms of lower storage requirements and higher
-throughput stemming from fewer floating-point multiplications, despite higher arithmetic
+Furthermore our findings indicate that between each other under similar circumstances
+the methods yield comparable compression and performance results, which echoes earlier
+results by \citet{kharitonov_variational_2018}.
+
+The results of this study have direct implications for embedded deep learning applications
+both in terms of lower storage requirements and higher throughput stemming from fewer
+floating point multiplications due to sparsity, despite somewhat higher arithmetic
 complexity of $\cplx$-valued networks.
-% CVNN capacity grows by \sqrt{2}, compute grows by 2 % RVNN caption by 2 compute by 2.
 

### 2020-06-23 paper/paper.tex
12 cut off some text and shrunk acknowledgements piece

@@
 in sec.~\ref{sec:c_variational_dropout}, where we provide the details of $\cplx$-valued
-variational sparsification method. In sec.~\ref{sec:experiments} we estimate the compression
+variational sparsification methods. In sec.~\ref{sec:experiments} we estimate the compression
 and performance trade-off on shallow and deep $\cplx$-valued networks, and discuss the
@@
 
-With a special posterior approximation family $q_\theta$ and suitable prior $\pi$,
-Variational Inference can be used as model regularization and sparsification technique.
+Variational Inference can be used as model regularization and sparsification method
+for certain posterior approximation $q_\theta$ and prior $\pi$.
 
@@
 
-During the \emph{``sparsify''} stage we make every layer stochastic and apply $\cplx$-valued
-variational sparsification (sec.~\ref{ssub:vd_prior}, ~\ref{ssub:ard_prior}) or its $\real$
-counterpart. We inject a coefficient $
+During the \emph{``sparsify''} stage we make every layer stochastic and apply variational
+sparsification (sec.~\ref{ssub:vd_prior}, ~\ref{ssub:ard_prior}, or their $\real$ versions).
+We inject a coefficient $
   C \in (0, 1]
@@
 Unlike experiment in sec.~\ref{sub:mnist_like_datasets}, we consider the raw features
-only, use full training split and allocate $20$, $40$, and $20$ epochs to each stage.
+only, use full training split, measure accuracy on the usual test split, and allocate
+$20$, $40$, and $20$ epochs to each stage.
 During training every mini-batch of $128$ samples is augmented by random horizontal flipping
@@
 a $32\times 32$ patch from the $40\times 40$ intermediate image.
-%
-We vary $C$ in \eqref{eq:elbo_with_coef} over $
-  \{\tfrac32 2^{-\tfrac{k}2} \colon k=7, \cdots, 15\}
-$, compare $\real / \cplx$ VD and ARD methods and measure accuracy on the usual test split.
 
@@
 % draw some conclusions
-The compression-accuracy curve in figure~\ref{fig:figure__cifar10__trade-off} shows that
+The compression-accuracy curve in figure~\ref{fig:figure__cifar10__trade-off}, constructed
+for $C = \tfrac32 2^{-\tfrac{k}2}$ with $k=7, \cdots, 15$, shows that
 it is possible to confidently achieve around $\times100$ compression of a deep $\cplx$VNN
@@
 
-The results of this study have direct implications for embedded deep learning applications
+This study has direct implications for embedded deep learning applications
 both in terms of lower storage requirements and higher throughput stemming from fewer
@@
 % financial support.
-We would like to thank the anonymous reviewers for their useful comments, and Evgenii
-Egorov, Ruslan Kostoev (ADASE) and Danila Doroshin (Huawei) for fruitfull discussions.
+We would like to thank the anonymous reviewers, Evgenii Egorov, Ruslan Kostoev (ADASE)
+and Danila Doroshin (Huawei) for their useful comments.
 % We thank Skoltech CDISE HPC Zhores cluster staff for providing computational infrastructure.

### 2020-06-23 paper/paper.tex
dropped appendix about linearops

@@
 % estimated uncertainty (variance or entropy).
-%
+
 Due to factorization assumption, the term $KL(q_\theta \| \pi)$ in \eqref{eq:sgvb_estimator}
@@
 simplify manual analysis of $\cplx$ derivatives and satisfy the product and chain rules, respect
-complex conjugation and linearity for $\cplx \to \cplx$ maps, and such were used to define
+complex conjugation and linearity for $\cplx \to \cplx$ maps, and as such were used to define
 $\cplx$ version of back-propagation, \citep{benvenuto_complex_1992,guberman_complex_2016}.
@@
   \centering
-  \begin{subfigure}[b]{1.\columnwidth}  % imcl2019-style swears at this
   % \includegraphics[width=\columnwidth]{figure__cifar__trade-off/legacy__augmentedcifar10__raw__-0.5.pdf}
   \includegraphics[width=\columnwidth]{figure__cifar__trade-off/appendix__augmentedcifar10__raw__-0.5.pdf}
-  \end{subfigure}
   \caption{%
@@
   \centering
-  \begin{subfigure}[b]{1.\columnwidth}  % imcl2019-style swears at this
-    \centering
   \includegraphics[width=\columnwidth]{figure__fine-tune_fx__early.pdf}
-  \end{subfigure}
   \caption{%
@@
 
-\section{Gradient of the KL-divergence in $\real$ case} % (fold)
-\label{sec:real-chisq-grad}  % gradient_of_the_kl_divergence_in_R_case
-
-In this appendix we study the approximation proposed by \citet{molchanov_variational_2017}
-for the KL divergence term \eqref{eq:improper-kl-div-real}. We show empirically that
-the gradient feedback provided by the approximation is sufficiently close to $
-  \tfrac{d}{d\log \alpha} K(\alpha)
-$, making it a viable alternative to exact gradients, computed in \citet{hron_variational_2018}.
-% The derivation in this section different from \citet{lapidoth_capacity_2003}.
-% The results are identical: they use DCT to establish interchangeability of limits
-% (sum-integral-derivative), whilst we allude to calculus theorems on differentiation
-% and integration of power series within the radius of their convergence (which are
-% essentially corollaries to the DCT).
-
-% \citet{pav_moments_2015} correctly notice that \cite[p. 2466]{lapidoth_capacity_2003} has a missing $\log{2}$ term.
-
-For $(z_i)_{i=1}^m \sim \mathcal{N}(0, 1)$ iid and $
-  (\mu_i)_{i=1}^m \in \mathbb{R}
-$, the random variable $W = \sum_i (\mu_i + z_i)^2$ has non-central $\chi^2$ distribution
-with shape $m$ and non-centrality parameter $\lambda = \sum_i \mu_i^2$, i.e. $
-  W\sim \chi^2_m(\lambda)
-$. The divergence \eqref{eq:improper-kl-div-real} has the form
-\begin{equation}  \label{eq:kl-div-appendix}
-  K(\alpha)
-    \propto \frac12 \mathbb{E}_{
-        W\sim \chi^2_1\bigl(\tfrac1{\alpha}\bigr)
-      } \log W
-    \tag{\ref{eq:improper-kl-div-real}'}
-  \,,
-\end{equation}
-$W$ can alternatively be represented as a Poisson mixture of ordinary $\chi^2$
-distributions: if $Z_{\mid J} \sim \chi^2_{k + 2J}$ for $
-  J \sim \mathcal{P}ois(\tfrac{\lambda}2)
-$ then $W \sim Z$. Therefore, expanding the conditional expectation gives
-\begin{equation}  \label{eq:cond_exp_expansion}
-  \mathbb{E}_{W\sim \chi^2_k(\lambda)} \log W
-    = \mathbb{E}\Bigl(
-        \mathbb{E} \bigl( \log W \mid J)
-      \Bigr)
-    = \mathbb{E}_{J\sim {\mathcal{P}ois}(\tfrac\lambda2)}
-      \Bigl(
-        \mathbb{E}_{W\sim \chi^2_{m + 2 J}} \log W
-      \Bigr)
-    \,.
-\end{equation}
-Since $\chi^2_\nu$ is Gamma distribution $\Gamma(\tfrac\nu2, \tfrac12)$, its logarithmic
-moment $
-  \mathbb{E}_{W\sim \chi^2_\nu} \log W
-$ is $
-  \psi\bigl(\tfrac\nu{2}\bigr) - \log \tfrac12
-$, where $\psi(x)$ is the digamma function. Hence
-\begin{equation}  \label{eq:exp_digamma}
-  \mathbb{E}_{W\sim \chi^2_k(\lambda)} \log W
-    = \log2 + \mathbb{E}_{J\sim {\mathcal{P}ois}(\tfrac\lambda2)}
-      \psi\bigl(\tfrac{m + 2 J}{2}\bigr)
-    % = \log2
-    % + \sum_{j\geq 0}
-    %     e^{- \tfrac{\lambda}2}
-    %     \frac{\bigl(\tfrac{\lambda}2\bigr)^j}{j!}
-    %   \psi\bigl(\tfrac{m+2J}{2}\bigr)
-    \,.
-\end{equation}
-We can use REINFORCE method to compute the derivative of \eqref{eq:exp_digamma} with respect
-to $\lambda$ \citep{williams_simple_1992}. Since Poisson $\log$-probability is $
-  \log p_\lambda(J)
-    = - \tfrac{\lambda}2
-      + J \log \tfrac{\lambda}2
-      - \log J!
-$, we get
-\begin{equation}  \label{eq:exp_reinforce}
-  \frac{d \eqref{eq:exp_digamma}}{d \lambda}
-    =
-    \mathbb{E}_{J\sim {\mathcal{P}ois}(\tfrac\lambda2)}
-      \psi\bigl(\tfrac{m + 2 J}{2}\bigr)
-      \tfrac{d}{d \lambda} \log p_\lambda(J)
-    % = \mathbb{E}_{J}
-    %   \bigl(
-    %     \tfrac2\lambda J - 1
-    %   \bigr)
-    %   \frac{\psi\bigl(\tfrac{m + 2 J}{2}\bigr)}2
-    = \frac12 g_m\bigl(\tfrac\lambda2\bigr)
-    \,,
-\end{equation}
-where
-\begin{equation}  \label{eq:g_m_series}
-  g_m(x)
-    =
-    \mathbb{E}_{J\sim {\mathcal{P}ois}(x)}
-      \bigl( \tfrac{J}x - 1 \bigr)
-      \psi\bigl(\tfrac{m + 2 J}{2}\bigr)
-    =
-    e^{- x} \sum_{j \geq 0}
-      \frac{x^j}{j!} \bigl( \tfrac{J}x - 1 \bigr)
-      \psi\bigl(\tfrac{m + 2 j}{2}\bigr)
-    \,.
-\end{equation}
-By manipulating the partial sums within $g_m(x)$ and making use of the property $
-  \psi(x + 1) = \psi(x) + \tfrac1x
-  % \psi(1 + J + \tfrac{m}2) = \tfrac2{m + 2J} + \psi(J + \tfrac{m}2)
-$ of the digamma funciton for $x > 0$, we get
-\begin{equation}  \label{eq:g_m_series_int}
-  g_m(x)
-    = e^{- x} \sum_{j \geq 0}
-      \frac{x^j}{j!} \frac1{j + \tfrac{m}2}
-    = e^{- x} x^{- \tfrac{m}2} \sum_{j \geq 0}
-      \frac1{j!}
-      \frac{x^{j + \tfrac{m}2}}{j + \tfrac{m}2}
-    = e^{- x} x^{- \tfrac{m}2} \sum_{j \geq 0}
-      \frac1{j!} \int_0^x t^{j + \tfrac{m}2 - 1} dt
-    \,.
-\end{equation}
-Since for any $J$ the functions $
-  t \mapsto \sum_{j=0}^J \frac1{j!} t^{j + \tfrac{m}2 - 1}
-$ are positive on $(0, x)$ and upper bounded by integrable $
-  t^{\tfrac{m}2 - 1} e^t
-$, which turns out to be the limit of the partial sums, the Dominated Convergence
-theorem implies
-\begin{equation}  \label{eq:g_m_integral}
-  g_m(x)
-    = e^{- x} x^{- \tfrac{m}2}
-      \int_0^x \sum_{j \geq 0}
-        \frac1{j!} t^{j + \tfrac{m}2 - 1} dt
-    = e^{- x} x^{- \tfrac{m}2}
-      \int_0^x e^t t^{(\tfrac{m}2 - 1)} dt
-    \,.
-\end{equation}
-Substituting $u^2 = t$ on $[0, \infty]$ with $2u du = dt$ and letting $
-  F_m
-  % \colon \mathbb{R} \to \mathbb{R}
-  \colon x \mapsto e^{-x^2} \int_0^x u^{m - 1} e^{u^2} du
-$ yields
-\begin{equation}  \label{eq:g_m_integral-sub}
-  \frac{d \eqref{eq:exp_digamma}}{d \lambda}
-    = \frac12 g_m\bigl(\tfrac\lambda2\bigr)
-    % = x^{-\tfrac{m}2} e^{-x}
-    %     \int_0^x t^{\tfrac{m}2 - 1} e^t dt
-    = e^{-x}
-      x^{-\tfrac{m}2}
-      \int_0^{\sqrt{x}} u^{m - 1} e^{u^2} du
-        \bigg\vert_{x=\tfrac\lambda2}
-    % = e^{-x}
-    %   \frac1{\sqrt{x}}
-    %   \int_0^{\sqrt{x}} e^{u^2} du
-    %     \bigg\vert_{x=\tfrac\lambda2}
-    = \Bigl(\sqrt{\tfrac2\lambda}\Bigr)^m F\Bigl(\sqrt{\tfrac\lambda2}\Bigr)
-    \,.
-\end{equation}
-Since $\alpha$ is non-negative, it is typically parameterized via its logarithm, whence
-the derivative of \eqref{eq:kl-div-appendix} with respect to $\log\alpha$ follows from
-\eqref{eq:g_m_integral-sub} for $m=1$ and $\lambda = \tfrac1\alpha$:
-\begin{equation}  \label{eq:real-kl-div-deriv-log}
-  \frac{d K(\alpha)}{d\log \alpha}
-    % = \tfrac12 \sqrt{\tfrac2\lambda} F\Bigl(\sqrt{\tfrac\lambda2}\Bigr)
-    % for \lambda = \tfrac1\alpha
-    %   \tfrac{d\lambda}{d\alpha} = - \alpha^{-2}
-    %   \tfrac{d\alpha}{d\log \alpha} = \alpha
-    % = - \alpha \frac1{\alpha\sqrt{2\alpha}} F\Bigl(\tfrac1{\sqrt{2\alpha}}\Bigr)
-    = - \frac1{\sqrt{2\alpha}} F\bigl(\tfrac1{\sqrt{2\alpha}}\bigr)
-    \,.
-\end{equation}
-
-We compute the Monte-Carlo estimator of \eqref{eq:improper-kl-div-real} on a sample of $10^7$
-draws over an equally spaced grid of $\log \alpha$ in $[-12, +12]$ of size $4096$. The
-coefficients of the approximation, proposed by \citet{molchanov_variational_2017}, are
-within $1\%$ relative tolerance of the reported therein. An equivalent expression of the
-approximation is given in \eqref{eq:improper-kl-div-real-approx}.
-% see eq.~(14): flit overall sign, use $C = -k_1$, $1-\sigma(x) = \sigma(-x)$
-\begin{equation}  \label{eq:improper-kl-div-real-approx}
-  \eqref{eq:improper-kl-div-real}
-% - KL(\mathcal{N}(w \mid \mu, \alpha \mu^2) \|
-%     \tfrac1{\lvert w \rvert})
-%   \approx
-%     k_1 \sigma(k_2 + k_3 \log \alpha)
-%     + C \big\vert_{C = -k1}
-%     - \tfrac12 \log (1 + e^{-\log \alpha})
-  % = \tfrac12 \log \alpha
-  %   - \mathbb{E}_{\varepsilon \sim \mathcal{N}(1, \alpha)}
-  %   \log{\lvert \varepsilon \rvert} + C
-  \approx
-    \frac12 \log{\bigl(1 + e^{-\log \alpha}\bigr)}
-    + k_1 \sigma\bigl(- (k_2 + k_3 \log \alpha)\bigr)
-    % - k_1 \bigl(1 - \sigma(k_2 + k_3 \log \alpha)\bigr)
-  \,,
-\end{equation}
-% in parctial implementations we suggest using softplus to numerically comptue the last
-% term, since it is typically implemented in a floating-point stable fashion.
-The numerically estimated derivative of the penalty term with respect to $\log \alpha$ using
-forward differences seems to be following \eqref{eq:real-kl-div-deriv-log} very closely (up to
-sampling error), see fig.~\ref{fig:molchanov-derivative-replica}. The derivative of
-\eqref{eq:improper-kl-div-real-approx} with respect to $\log \alpha$ appears to be very
-close to \eqref{eq:real-kl-div-deriv-log}. For sake of completeness, we compute a similar
-Monte-Carlo estimate for $\cplx$ variational dropout KL divergence term in \eqref{eq:c-vd-kl-div}
-with $\beta = 2$, fit the best approximation \eqref{eq:improper-kl-div-real-approx}, and
-compare it against the exact $\log \alpha$ derivative $
-  \frac{d \eqref{eq:c-vd-kl-div}}{d\log \alpha}
-    % = \frac{d \alpha}{d\log \alpha} \frac{d}{d\alpha} \bigl(
-    %   \log \tfrac1\alpha - \mathop{Ei}\bigl(-\tfrac1\alpha\bigr)
-    % = \alpha \bigl(
-    %   - \tfrac1\alpha
-    %   - \tfrac{e^x}{x} \bigg\vert_{x=-\tfrac1\alpha} \alpha^{-2}
-    % \bigr)
-    = e^{-\tfrac1\alpha} - 1
-$.
-
-\begin{figure}[!t]
-  \centering
-  \includegraphics[width=\columnwidth]{grad_log.pdf}
-  \caption{$\tfrac{d K(\alpha)}{d \log{\alpha}}$ of the approximation
-  \eqref{eq:improper-kl-div-real-approx}, MC estimate of \eqref{eq:improper-kl-div-real},
-  and the exact derivative using \eqref{eq:real-kl-div-deriv-log}.}
-  \label{fig:molchanov-derivative-replica}
-\end{figure}
-
-% section real-chisq-grad (end)
-
 \section{MNIST-like experiments} % (fold)
@@
   \label{fig:appendix__cmp__mnist-like__trade-off__VD__raw}
-\end{figure}
-
-\begin{figure}[b]
-  \centering
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/legacy__VD__emnist_letters__fft__-0.5.pdf}
-  \end{subfigure}%
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/legacy__VD__kmnist__fft__-0.5.pdf}
-  \end{subfigure} \\%
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/legacy__VD__fashionmnist__fft__-0.5.pdf}
-  \end{subfigure}%
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/legacy__VD__mnist__fft__-0.5.pdf}
-  \end{subfigure}
-  \caption{%
-    The trade-off of VD method for $\real$ and $\cplx$ models using Fourier features (main text).
-  }
-  \label{fig:paper__mnist-like__trade-off__VD__fft}
-\end{figure}
-
-\begin{figure}[b]
-  \centering
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/legacy__VD__emnist_letters__raw__-0.5.pdf}
-  \end{subfigure}%
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/legacy__VD__kmnist__raw__-0.5.pdf}
-  \end{subfigure} \\%
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/legacy__VD__fashionmnist__raw__-0.5.pdf}
-  \end{subfigure}%
-  \begin{subfigure}[b]{0.5\columnwidth}
-    \centering
-    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/legacy__VD__mnist__raw__-0.5.pdf}
-  \end{subfigure}
-  \caption{%
-    The trade-off of VD method for $\real$ and $\cplx$ models using raw features (main text).
-  }
-  \label{fig:paper__mnist-like__trade-off__VD__raw}
 \end{figure}
@@
 
-\section{$\cplx$-Linear operator representation} % (fold)
-\label{sec:c-linear_operator_representation}
-
-% proof that such operators exist and are unique (well this is an obvious statement)
-Consider $L \colon \cplx^m \to \cplx^n$ -- linear in $\cplx$. Then $
-  L(u + jv) = L u + \iu L v
-$ for any $u, v \in \real^m$, which implies that the effect of $L$ as $\cplx$-linear
-operator is determined by its restriction onto $\real^n$. Let $
-  F = L\vert_{\real^m}
-  \colon \real^m \to \cplx^n
-$ and observe that $F_r = \Re \circ F$ and $F_i = \Im \circ F$ are $\real$-linear operators
-such that $F = F_r + \iu F_i$ (pointwise). Indeed,
-$$
-  F_r(a + \lambda b)
-  % = \Re F(a + \lambda b)
-  = \Re L(a + \lambda b)
-  % = \Re \bigl( L a + \lambda L b \bigr)
-  = \Re L a + \lambda \Re L b
-  % = \Re F a + \lambda \Re F b
-  = F_r a + \lambda F_r b
-  \,. $$
-Therefore for any $\cplx$-linear operator $L$ there are $\real$-linear operators $U, V$
-such that
-$$
-L z 
-  = (U + \iu V) (\Re z + \iu \Im z)
-  % = (U + \iu V) \Re z + \iu (U + \iu V) \Im z
-  % = U \Re z + \iu V \Re z + \iu \bigl(U \Im z + \iu V \Im z \bigr)
-  = U \Re z - V \Im z + \iu \bigl( V \Re z + U \Im z \bigr)
-  % = (U + \iu V) z
-  \,. $$
-Uniqueness of these operators follows, if this decomposition is applied to any $z$ with
-$\Im z = 0$.
-
-% section c-linear_operator_representation (end)
+\section{Gradient of the KL-divergence in $\real$ case} % (fold)
+\label{sec:real-chisq-grad}  % gradient_of_the_kl_divergence_in_R_case
+
+In this appendix we study the approximation proposed by \citet{molchanov_variational_2017}
+for the KL divergence term \eqref{eq:improper-kl-div-real} for $\real$ Sparse Variational
+Dropout. Following the logic of \citet{lapidoth_capacity_2003} we derive the expression
+for $
+  \tfrac{d}{d\log \alpha} K(\alpha)
+$. Acknowledging that the same result was obtained by \citet[eq.~(5)]{hron_variational_2018},
+we provide this appendix for the sake of completeness.
+% The derivation in this section different from \citet{lapidoth_capacity_2003}.
+% The results are identical: they use DCT to establish interchangeability of limits
+% (sum-integral-derivative), whilst we allude to calculus theorems on differentiation
+% and integration of power series within the radius of their convergence (which are
+% essentially corollaries to the DCT).
+
+% \citet{pav_moments_2015} correctly notice that \cite[p. 2466]{lapidoth_capacity_2003} has a missing $\log{2}$ term.
+
+For $(z_i)_{i=1}^m \sim \mathcal{N}(0, 1)$ iid and $
+  (\mu_i)_{i=1}^m \in \mathbb{R}
+$, the random variable $W = \sum_i (\mu_i + z_i)^2$ has non-central $\chi^2$ distribution
+with shape $m$ and non-centrality parameter $\lambda = \sum_i \mu_i^2$, i.e. $
+  W\sim \chi^2_m(\lambda)
+$. Therefore, the divergence \eqref{eq:improper-kl-div-real} has the form
+\begin{equation}  \label{eq:kl-div-appendix}
+  K(\alpha)
+    \propto \frac12 \mathbb{E}_{
+        W\sim \chi^2_1\bigl(\tfrac1{\alpha}\bigr)
+      } \log W
+    \tag{\ref{eq:improper-kl-div-real}'}
+  \,.
+\end{equation}
+$W$ can alternatively be represented as a Poisson mixture of ordinary $\chi^2$
+distributions: if $Z_{\mid J} \sim \chi^2_{m + 2J}$ for $
+  J \sim \mathcal{P}ois(\tfrac{\lambda}2)
+$ then $W \sim Z$. Therefore, expanding the conditional expectation gives
+\begin{equation}  \label{eq:cond_exp_expansion}
+  \mathbb{E}_{W\sim \chi^2_m(\lambda)} \log W
+    = \mathbb{E}\Bigl(
+        \mathbb{E} \bigl( \log W \mid J)
+      \Bigr)
+    = \mathbb{E}_{J\sim {\mathcal{P}ois}(\tfrac\lambda2)}
+      \Bigl(
+        \mathbb{E}_{W\sim \chi^2_{m + 2 J}} \log W
+      \Bigr)
+    \,.
+\end{equation}
+Since $\chi^2_\nu$ is Gamma distribution $\Gamma(\tfrac\nu2, \tfrac12)$, it can be shown
+that the logarithmic moment $
+  \mathbb{E}_{W\sim \chi^2_\nu} \log W
+$ is $
+  \psi\bigl(\tfrac\nu{2}\bigr) - \log \tfrac12
+$, where $\psi$ is the digamma function ($\psi(x) = \tfrac{d}{dx} \log \Gamma(x)$).
+% \begin{equation}  \label{eq:digamma}
+%   \psi(x)
+%     % = \frac{d}{dx} \log \Gamma(x)
+%     = \frac1{\Gamma(x)}
+%       \int_0^\infty
+%         u^{x-1} e^{-u} \log{u}
+%       \, du
+%     \,.
+% \end{equation}
+By expanding expectation of a Poisson random variable we get $
+  \mathbb{E}_{W\sim \chi^2_m(\lambda)} \log W
+    = \log2 + g_m\bigl(\tfrac\lambda2\bigr)
+$, where
+\begin{equation}  \label{eq:exp_digamma}
+  g_m(x)
+    % = \mathbb{E}_{J\sim {\mathcal{P}ois}(x)}
+    %   \psi\bigl(\tfrac{m + 2 J}{2}\bigr)
+    = e^{- x} \sum_{j\geq 0}
+        \frac{x^j}{j!}
+          \psi\bigl(\tfrac{m + 2 J}{2}\bigr)
+    \,.
+\end{equation}
+Making use of the property $
+  \psi(z + 1) = \psi(z) + \tfrac1z
+  % \psi(1 + J + \tfrac{m}2) = \tfrac2{m + 2J} + \psi(J + \tfrac{m}2)
+$ of the digamma funciton for $z > 0$, we conclude that the power series in \eqref{eq:exp_digamma}
+converges for any $x \geq 0$. Therefore the derivative of \eqref{eq:exp_digamma} is
+given by
+\begin{equation}  \label{eq:g_m_series}
+  \frac{d}{dx} g_m(x)
+    % = \mathbb{E}_{J\sim {\mathcal{P}ois}(x)}
+    %     \bigl( \tfrac{J}x - 1 \bigr)
+    %   \psi\bigl(\tfrac{m + 2 J}{2}\bigr)
+    = - g_m(x)
+      + e^{- x} \sum_{j \geq 0}
+          \frac{x^j}{j!}
+        \biggl(
+          \psi\bigl(\tfrac{m + 2 j}{2}\bigr)
+          + \frac{2}{m + 2 j}
+        \biggr)
+    % = e^{- x} \sum_{j \geq 0}
+    %     \frac{x^j}{j!} \frac{2}{m + 2 j}
+    \,.
+\end{equation}
+By manipulating the partial sums within \eqref{eq:g_m_series} we get
+\begin{equation}  \label{eq:g_m_series_int}
+  \frac{d}{dx} g_m(x)
+    = e^{- x} \sum_{j \geq 0}
+      \frac{x^j}{j!} \frac1{j + \tfrac{m}2}
+    % = e^{- x} x^{- \tfrac{m}2} \sum_{j \geq 0}
+    %   \frac1{j!}
+    %   \frac{x^{j + \tfrac{m}2}}{j + \tfrac{m}2}
+    = e^{- x} x^{- \tfrac{m}2} \sum_{j \geq 0}
+      \frac1{j!} \int_0^x t^{j + \tfrac{m}2 - 1} dt
+    \,.
+\end{equation}
+Furthermore, the functions $
+  t \mapsto \sum_{j=0}^J \frac1{j!} t^{j + \tfrac{m}2 - 1}
+$ are non-decreasing on $(0, x)$ with growing $J$ and converge to $
+  t^{\tfrac{m}2 - 1} e^t
+$, which implies by the Monotone Convergence Theorem that
+\begin{equation}  \label{eq:g_m_integral}
+  \frac{d}{dx} g_m(x)
+    = e^{- x} x^{- \tfrac{m}2}
+      \int_0^x \sum_{j \geq 0}
+        \frac1{j!} t^{j + \tfrac{m}2 - 1} dt
+    = e^{- x} x^{- \tfrac{m}2}
+      \int_0^x t^{\bigl(\tfrac{m}2 - 1\bigr)} e^t dt
+    \,.
+\end{equation}
+Substituting $u^2 = t$ on $[0, \infty]$ with $2u du = dt$ and letting $
+  I_m
+  % \colon \mathbb{R} \to \mathbb{R}
+  \colon x \mapsto e^{-x^2} \int_0^x u^{m - 1} e^{u^2} du
+$ yields
+\begin{equation}  \label{eq:g_m_integral-sub}
+  \frac{d \eqref{eq:cond_exp_expansion}}{d \lambda}
+    = \frac12 \frac{d}{dx} g_m(x)
+        \bigg\vert_{x=\tfrac\lambda2}
+    % = x^{-\tfrac{m}2} e^{-x}
+    %     \int_0^x t^{\tfrac{m}2 - 1} e^t dt
+    = e^{-x}
+      x^{-\tfrac{m}2}
+      \int_0^{\sqrt{x}} u^{m - 1} e^{u^2} du
+        \bigg\vert_{x=\tfrac\lambda2}
+    % = e^{-x}
+    %   \frac1{\sqrt{x}}
+    %   \int_0^{\sqrt{x}} e^{u^2} du
+    %     \bigg\vert_{x=\tfrac\lambda2}
+    = \Bigl(\sqrt{\tfrac2\lambda}\Bigr)^m I_m\Bigl(\sqrt{\tfrac\lambda2}\Bigr)
+    \,.
+\end{equation}
+Since $\alpha$ is non-negative, it is typically parameterized via its logarithm, whence
+the derivative of \eqref{eq:kl-div-appendix} with respect to $\log\alpha$ follows from
+\eqref{eq:g_m_integral-sub} for $m=1$ and $\lambda = \tfrac1\alpha$:
+\begin{equation}  \label{eq:real-kl-div-deriv-log}
+  \frac{d K(\alpha)}{d\log \alpha}
+    % = \tfrac12 \sqrt{\tfrac2\lambda} F\Bigl(\sqrt{\tfrac\lambda2}\Bigr)
+    % for \lambda = \tfrac1\alpha
+    %   \tfrac{d\lambda}{d\alpha} = - \alpha^{-2}
+    %   \tfrac{d\alpha}{d\log \alpha} = \alpha
+    % = - \alpha \frac1{\alpha\sqrt{2\alpha}} F\Bigl(\tfrac1{\sqrt{2\alpha}}\Bigr)
+    = - \frac1{\sqrt{2\alpha}} I_1\bigl(\tfrac1{\sqrt{2\alpha}}\bigr)
+    \,.
+\end{equation}
+
+We compute the Monte-Carlo estimate of \eqref{eq:improper-kl-div-real} on a sample
+of $10^7$ draws over an equally spaced grid of $\log \alpha$ in $[-12, +12]$ of size
+$4096$. The approximation proposed by \citet{molchanov_variational_2017} is given in
+\eqref{eq:improper-kl-div-real-approx}, with coefficients $
+  k_1 = 0.63576
+$, $
+  k_2 = 1.8732
+$, and $
+  k_3 = 1.48695
+$. The derivative of the approximation with respect to $\log \alpha$ follows
+\eqref{eq:real-kl-div-deriv-log} within $4\%$ of relative tolerance, see
+fig.~\ref{fig:molchanov-derivative-replica}. 
+% see eq.~(14): flit overall sign, use $C = -k_1$, $1-\sigma(x) = \sigma(-x)$
+\begin{equation}  \label{eq:improper-kl-div-real-approx}
+  \eqref{eq:improper-kl-div-real}
+% - KL(\mathcal{N}(w \mid \mu, \alpha \mu^2) \|
+%     \tfrac1{\lvert w \rvert})
+%   \approx
+%     k_1 \sigma(k_2 + k_3 \log \alpha)
+%     + C \big\vert_{C = -k1}
+%     - \tfrac12 \log (1 + e^{-\log \alpha})
+  % = \tfrac12 \log \alpha
+  %   - \mathbb{E}_{\varepsilon \sim \mathcal{N}(1, \alpha)}
+  %   \log{\lvert \varepsilon \rvert} + C
+  \approx
+    \frac12 \log{\bigl(1 + e^{-\log \alpha}\bigr)}
+    + k_1 \sigma\bigl(- (k_2 + k_3 \log \alpha)\bigr)
+    % - k_1 \bigl(1 - \sigma(k_2 + k_3 \log \alpha)\bigr)
+  \,,
+\end{equation}
+% in parctial implementations we suggest using softplus to numerically comptue the last
+% term, since it is typically implemented in a floating-point stable fashion.
+Similarly, the forward difference estimate of the derivative \eqref{eq:real-kl-div-deriv-log}
+very closely (up to sampling error). For sake of completeness, we compute a similar
+Monte-Carlo estimate for the KL divergence term in \eqref{eq:c-vd-kl-div} for $\cplx$-valued
+Variational Dropout with $\beta = 2$, fit the best approximation \eqref{eq:improper-kl-div-real-approx},
+and compare it against the exact $\log \alpha$ derivative $
+  \frac{d \eqref{eq:c-vd-kl-div}}{d\log \alpha}
+    % = \frac{d \alpha}{d\log \alpha} \frac{d}{d\alpha} \bigl(
+    %   \log \tfrac1\alpha - \mathop{Ei}\bigl(-\tfrac1\alpha\bigr)
+    % = \alpha \bigl(
+    %   - \tfrac1\alpha
+    %   - \tfrac{e^x}{x} \bigg\vert_{x=-\tfrac1\alpha} \alpha^{-2}
+    % \bigr)
+    = e^{-\tfrac1\alpha} - 1
+$.
+
+\begin{figure}[!t]
+  \centering
+  \includegraphics[width=\columnwidth]{grad_log.pdf}
+  \caption{$\tfrac{d K(\alpha)}{d \log{\alpha}}$ of the approximation
+  \eqref{eq:improper-kl-div-real-approx}, MC estimate of \eqref{eq:improper-kl-div-real},
+  and the exact derivative using \eqref{eq:real-kl-div-deriv-log}.}
+  \label{fig:molchanov-derivative-replica}
+\end{figure}
+
+% section real-chisq-grad (end)
 

### 2020-06-23 paper/paper.tex
dropped appendix about linearops

@@
 \eqref{eq:sgvb_estimator} would require that the \emph{entire} set of network's parameters
-$\omega$ be independently drawn for each element in the mini-batch. Since that the
-parameters in a network naturally split into subsets with non-overlapping layer-wise
-effects, it is standard to assume that the approximation $
+$\omega$ be independently drawn for each element in the mini-batch. Since the parameters
+in a network naturally split into subsets with non-overlapping layer-wise effects, it is
+standard to assume that the approximation $
   q_\theta(\omega)
@@
 $, where $C_{ij} = \Sigma_{ij} \xi_{ij}$ and the complex modulus and square are applied
-elementwise. \eqref{sub:c_gauss_and_local_rep} can be applied to any layer, the output
+elementwise. Equation \eqref{eq:cplx-gauss-trick} can be applied to any layer, the output
 of which depends linearly on its parameters, such as convolutional, affine, and bilinear

### 2020-06-24 setup.py
version bump

@@ -1,8 +1,8 @@
-from distutils.core import setup, Extension
+from distutils.core import setup
 
 setup(
     name="cplxpaper",
-    version="2020.3",
+    version="2020.6",
     description="""Backend for experiments presented in Bayesian"""
                 """ Sparsification of Deep Complex-valued Networks.""",
     license="MIT License",

### 2020-06-24 paper/paper.tex
onecolumn

--- 2020-06-23 paper/paper.tex
@@
 \onecolumn
-
-\section{Gradient of the KL-divergence in $\real$ case} % (fold)
-\label{sec:real-chisq-grad}  % gradient_of_the_kl_divergence_in_R_case
-
-In this appendix we study the approximation proposed by \citet{molchanov_variational_2017}
-for the KL divergence term \eqref{eq:improper-kl-div-real}. We show empirically that
-the gradient feedback provided by the approximation is sufficiently close to $
-  \tfrac{d}{d\log \alpha} K(\alpha)
-$, making it a viable alternative to exact gradients, computed in \citet{hron_variational_2018}.
-% The derivation in this section different from \citet{lapidoth_capacity_2003}.
-% The results are identical: they use DCT to establish interchangeability of limits
-% (sum-integral-derivative), whilst we allude to calculus theorems on differentiation
-% and integration of power series within the radius of their convergence (which are
-% essentially corollaries to the DCT).
-
-% \citet{pav_moments_2015} correctly notice that \cite[p. 2466]{lapidoth_capacity_2003} has a missing $\log{2}$ term.
-
-For $(z_i)_{i=1}^m \sim \mathcal{N}(0, 1)$ iid and $
-  (\mu_i)_{i=1}^m \in \mathbb{R}
-$, the random variable $W = \sum_i (\mu_i + z_i)^2$ has non-central $\chi^2$ distribution
-with shape $m$ and non-centrality parameter $\lambda = \sum_i \mu_i^2$, i.e. $
-  W\sim \chi^2_m(\lambda)
-$. The divergence \eqref{eq:improper-kl-div-real} has the form
-\begin{equation}  \label{eq:kl-div-appendix}
-  K(\alpha)
-    \propto \frac12 \mathbb{E}_{
-        W\sim \chi^2_1\bigl(\tfrac1{\alpha}\bigr)
-      } \log W
-    \tag{\ref{eq:improper-kl-div-real}'}
-  \,,
-\end{equation}
-$W$ can alternatively be represented as a Poisson mixture of ordinary $\chi^2$
-distributions: if $Z_{\mid J} \sim \chi^2_{k + 2J}$ for $
-  J \sim \mathcal{P}ois(\tfrac{\lambda}2)
-$ then $W \sim Z$. Therefore, expanding the conditional expectation gives
-\begin{equation}  \label{eq:cond_exp_expansion}
-  \mathbb{E}_{W\sim \chi^2_k(\lambda)} \log W
-    = \mathbb{E}\Bigl(
-        \mathbb{E} \bigl( \log W \mid J)
-      \Bigr)
-    = \mathbb{E}_{J\sim {\mathcal{P}ois}(\tfrac\lambda2)}
-      \Bigl(
-        \mathbb{E}_{W\sim \chi^2_{m + 2 J}} \log W
-      \Bigr)
-    \,.
-\end{equation}
-Since $\chi^2_\nu$ is Gamma distribution $\Gamma(\tfrac\nu2, \tfrac12)$, its logarithmic
-moment $
-  \mathbb{E}_{W\sim \chi^2_\nu} \log W
-$ is $
-  \psi\bigl(\tfrac\nu{2}\bigr) - \log \tfrac12
-$, where $\psi(x)$ is the digamma function. Hence
-\begin{equation}  \label{eq:exp_digamma}
-  \mathbb{E}_{W\sim \chi^2_k(\lambda)} \log W
-    = \log2 + \mathbb{E}_{J\sim {\mathcal{P}ois}(\tfrac\lambda2)}
-      \psi\bigl(\tfrac{m + 2 J}{2}\bigr)
-    % = \log2
-    % + \sum_{j\geq 0}
-    %     e^{- \tfrac{\lambda}2}
-    %     \frac{\bigl(\tfrac{\lambda}2\bigr)^j}{j!}
-    %   \psi\bigl(\tfrac{m+2J}{2}\bigr)
-    \,.
-\end{equation}
-We can use REINFORCE method to compute the derivative of \eqref{eq:exp_digamma} with respect
-to $\lambda$ \citep{williams_simple_1992}. Since Poisson $\log$-probability is $
-  \log p_\lambda(J)
-    = - \tfrac{\lambda}2
-      + J \log \tfrac{\lambda}2
-      - \log J!
-$, we get
-\begin{equation}  \label{eq:exp_reinforce}
-  \frac{d \eqref{eq:exp_digamma}}{d \lambda}
-    =
-    \mathbb{E}_{J\sim {\mathcal{P}ois}(\tfrac\lambda2)}
-      \psi\bigl(\tfrac{m + 2 J}{2}\bigr)
-      \tfrac{d}{d \lambda} \log p_\lambda(J)
-    % = \mathbb{E}_{J}
-    %   \bigl(
-    %     \tfrac2\lambda J - 1
-    %   \bigr)
-    %   \frac{\psi\bigl(\tfrac{m + 2 J}{2}\bigr)}2
-    = \frac12 g_m\bigl(\tfrac\lambda2\bigr)
-    \,,
-\end{equation}
-where
-\begin{equation}  \label{eq:g_m_series}
-  g_m(x)
-    =
-    \mathbb{E}_{J\sim {\mathcal{P}ois}(x)}
-      \bigl( \tfrac{J}x - 1 \bigr)
-      \psi\bigl(\tfrac{m + 2 J}{2}\bigr)
-    =
-    e^{- x} \sum_{j \geq 0}
-      \frac{x^j}{j!} \bigl( \tfrac{J}x - 1 \bigr)
-      \psi\bigl(\tfrac{m + 2 j}{2}\bigr)
-    \,.
-\end{equation}
-By manipulating the partial sums within $g_m(x)$ and making use of the property $
-  \psi(x + 1) = \psi(x) + \tfrac1x
-  % \psi(1 + J + \tfrac{m}2) = \tfrac2{m + 2J} + \psi(J + \tfrac{m}2)
-$ of the digamma funciton for $x > 0$, we get
-\begin{equation}  \label{eq:g_m_series_int}
-  g_m(x)
-    = e^{- x} \sum_{j \geq 0}
-      \frac{x^j}{j!} \frac1{j + \tfrac{m}2}
-    = e^{- x} x^{- \tfrac{m}2} \sum_{j \geq 0}
-      \frac1{j!}
-      \frac{x^{j + \tfrac{m}2}}{j + \tfrac{m}2}
-    = e^{- x} x^{- \tfrac{m}2} \sum_{j \geq 0}
-      \frac1{j!} \int_0^x t^{j + \tfrac{m}2 - 1} dt
-    \,.
-\end{equation}
-Since for any $J$ the functions $
-  t \mapsto \sum_{j=0}^J \frac1{j!} t^{j + \tfrac{m}2 - 1}
-$ are positive on $(0, x)$ and upper bounded by integrable $
-  t^{\tfrac{m}2 - 1} e^t
-$, which turns out to be the limit of the partial sums, the Dominated Convergence
-theorem implies
-\begin{equation}  \label{eq:g_m_integral}
-  g_m(x)
-    = e^{- x} x^{- \tfrac{m}2}
-      \int_0^x \sum_{j \geq 0}
-        \frac1{j!} t^{j + \tfrac{m}2 - 1} dt
-    = e^{- x} x^{- \tfrac{m}2}
-      \int_0^x e^t t^{(\tfrac{m}2 - 1)} dt
-    \,.
-\end{equation}
-Substituting $u^2 = t$ on $[0, \infty]$ with $2u du = dt$ and letting $
-  F_m
-  % \colon \mathbb{R} \to \mathbb{R}
-  \colon x \mapsto e^{-x^2} \int_0^x u^{m - 1} e^{u^2} du
-$ yields
-\begin{equation}  \label{eq:g_m_integral-sub}
-  \frac{d \eqref{eq:exp_digamma}}{d \lambda}
-    = \frac12 g_m\bigl(\tfrac\lambda2\bigr)
-    % = x^{-\tfrac{m}2} e^{-x}
-    %     \int_0^x t^{\tfrac{m}2 - 1} e^t dt
-    = e^{-x}
-      x^{-\tfrac{m}2}
-      \int_0^{\sqrt{x}} u^{m - 1} e^{u^2} du
-        \bigg\vert_{x=\tfrac\lambda2}
-    % = e^{-x}
-    %   \frac1{\sqrt{x}}
-    %   \int_0^{\sqrt{x}} e^{u^2} du
-    %     \bigg\vert_{x=\tfrac\lambda2}
-    = \Bigl(\sqrt{\tfrac2\lambda}\Bigr)^m F\Bigl(\sqrt{\tfrac\lambda2}\Bigr)
-    \,.
-\end{equation}
-Since $\alpha$ is non-negative, it is typically parameterized via its logarithm, whence
-the derivative of \eqref{eq:kl-div-appendix} with respect to $\log\alpha$ follows from
-\eqref{eq:g_m_integral-sub} for $m=1$ and $\lambda = \tfrac1\alpha$:
-\begin{equation}  \label{eq:real-kl-div-deriv-log}
-  \frac{d K(\alpha)}{d\log \alpha}
-    % = \tfrac12 \sqrt{\tfrac2\lambda} F\Bigl(\sqrt{\tfrac\lambda2}\Bigr)
-    % for \lambda = \tfrac1\alpha
-    %   \tfrac{d\lambda}{d\alpha} = - \alpha^{-2}
-    %   \tfrac{d\alpha}{d\log \alpha} = \alpha
-    % = - \alpha \frac1{\alpha\sqrt{2\alpha}} F\Bigl(\tfrac1{\sqrt{2\alpha}}\Bigr)
-    = - \frac1{\sqrt{2\alpha}} F\bigl(\tfrac1{\sqrt{2\alpha}}\bigr)
-    \,.
-\end{equation}
-
-We compute the Monte-Carlo estimator of \eqref{eq:improper-kl-div-real} on a sample of $10^7$
-draws over an equally spaced grid of $\log \alpha$ in $[-12, +12]$ of size $4096$. The
-coefficients of the approximation, proposed by \citet{molchanov_variational_2017}, are
-within $1\%$ relative tolerance of the reported therein. An equivalent expression of the
-approximation is given in \eqref{eq:improper-kl-div-real-approx}.
-% see eq.~(14): flit overall sign, use $C = -k_1$, $1-\sigma(x) = \sigma(-x)$
-\begin{equation}  \label{eq:improper-kl-div-real-approx}
-  \eqref{eq:improper-kl-div-real}
-% - KL(\mathcal{N}(w \mid \mu, \alpha \mu^2) \|
-%     \tfrac1{\lvert w \rvert})
-%   \approx
-%     k_1 \sigma(k_2 + k_3 \log \alpha)
-%     + C \big\vert_{C = -k1}
-%     - \tfrac12 \log (1 + e^{-\log \alpha})
-  % = \tfrac12 \log \alpha
-  %   - \mathbb{E}_{\varepsilon \sim \mathcal{N}(1, \alpha)}
-  %   \log{\lvert \varepsilon \rvert} + C
-  \approx
-    \frac12 \log{\bigl(1 + e^{-\log \alpha}\bigr)}
-    + k_1 \sigma\bigl(- (k_2 + k_3 \log \alpha)\bigr)
-    % - k_1 \bigl(1 - \sigma(k_2 + k_3 \log \alpha)\bigr)
-  \,,
-\end{equation}
-% in parctial implementations we suggest using softplus to numerically comptue the last
-% term, since it is typically implemented in a floating-point stable fashion.
-The numerically estimated derivative of the penalty term with respect to $\log \alpha$ using
-forward differences seems to be following \eqref{eq:real-kl-div-deriv-log} very closely (up to
-sampling error), see fig.~\ref{fig:molchanov-derivative-replica}. The derivative of
-\eqref{eq:improper-kl-div-real-approx} with respect to $\log \alpha$ appears to be very
-close to \eqref{eq:real-kl-div-deriv-log}. For sake of completeness, we compute a similar
-Monte-Carlo estimate for $\cplx$ variational dropout KL divergence term in \eqref{eq:c-vd-kl-div}
-with $\beta = 2$, fit the best approximation \eqref{eq:improper-kl-div-real-approx}, and
-compare it against the exact $\log \alpha$ derivative $
-  \frac{d \eqref{eq:c-vd-kl-div}}{d\log \alpha}
-    % = \frac{d \alpha}{d\log \alpha} \frac{d}{d\alpha} \bigl(
-    %   \log \tfrac1\alpha - \mathop{Ei}\bigl(-\tfrac1\alpha\bigr)
-    % = \alpha \bigl(
-    %   - \tfrac1\alpha
-    %   - \tfrac{e^x}{x} \bigg\vert_{x=-\tfrac1\alpha} \alpha^{-2}
-    % \bigr)
-    = e^{-\tfrac1\alpha} - 1
-$.
-
-\begin{figure}[!t]
-  \centering
-  \includegraphics[width=\columnwidth]{grad_log.pdf}
-  \caption{$\tfrac{d K(\alpha)}{d \log{\alpha}}$ of the approximation
-  \eqref{eq:improper-kl-div-real-approx}, MC estimate of \eqref{eq:improper-kl-div-real},
-  and the exact derivative using \eqref{eq:real-kl-div-deriv-log}.}
-  \label{fig:molchanov-derivative-replica}
-\end{figure}
-
-% section real-chisq-grad (end)
 
@@
 
+\section{Gradient of the KL-divergence in $\real$ case} % (fold)
+\label{sec:real-chisq-grad}  % gradient_of_the_kl_divergence_in_R_case
+
+In this appendix we study the approximation proposed by \citet{molchanov_variational_2017}
+for the KL divergence term \eqref{eq:improper-kl-div-real} for $\real$ Sparse Variational
+Dropout. Following the logic of \citet{lapidoth_capacity_2003} we derive the expression
+for $
+  \tfrac{d}{d\log \alpha} K(\alpha)
+$. Acknowledging that the same result was obtained by \citet[eq.~(5)]{hron_variational_2018},
+we provide this appendix for the sake of completeness.
+% The derivation in this section different from \citet{lapidoth_capacity_2003}.
+% The results are identical: they use DCT to establish interchangeability of limits
+% (sum-integral-derivative), whilst we allude to calculus theorems on differentiation
+% and integration of power series within the radius of their convergence (which are
+% essentially corollaries to the DCT).
+
+% \citet{pav_moments_2015} correctly notice that \cite[p. 2466]{lapidoth_capacity_2003} has a missing $\log{2}$ term.
+
+For $(z_i)_{i=1}^m \sim \mathcal{N}(0, 1)$ iid and $
+  (\mu_i)_{i=1}^m \in \mathbb{R}
+$, the random variable $W = \sum_i (\mu_i + z_i)^2$ has non-central $\chi^2$ distribution
+with shape $m$ and non-centrality parameter $\lambda = \sum_i \mu_i^2$, i.e. $
+  W\sim \chi^2_m(\lambda)
+$. Therefore, the divergence \eqref{eq:improper-kl-div-real} has the form
+\begin{equation}  \label{eq:kl-div-appendix}
+  K(\alpha)
+    \propto \frac12 \mathbb{E}_{
+        W\sim \chi^2_1\bigl(\tfrac1{\alpha}\bigr)
+      } \log W
+    \tag{\ref{eq:improper-kl-div-real}'}
+  \,.
+\end{equation}
+$W$ can alternatively be represented as a Poisson mixture of ordinary $\chi^2$
+distributions: if $Z_{\mid J} \sim \chi^2_{m + 2J}$ for $
+  J \sim \mathcal{P}ois(\tfrac{\lambda}2)
+$ then $W \sim Z$. Therefore, expanding the conditional expectation gives
+\begin{equation}  \label{eq:cond_exp_expansion}
+  \mathbb{E}_{W\sim \chi^2_m(\lambda)} \log W
+    = \mathbb{E}\Bigl(
+        \mathbb{E} \bigl( \log W \mid J)
+      \Bigr)
+    = \mathbb{E}_{J\sim {\mathcal{P}ois}(\tfrac\lambda2)}
+      \Bigl(
+        \mathbb{E}_{W\sim \chi^2_{m + 2 J}} \log W
+      \Bigr)
+    \,.
+\end{equation}
+Since $\chi^2_\nu$ is Gamma distribution $\Gamma(\tfrac\nu2, \tfrac12)$, it can be shown
+that the logarithmic moment $
+  \mathbb{E}_{W\sim \chi^2_\nu} \log W
+$ is $
+  \psi\bigl(\tfrac\nu{2}\bigr) - \log \tfrac12
+$, where $\psi$ is the digamma function ($\psi(x) = \tfrac{d}{dx} \log \Gamma(x)$).
+% \begin{equation}  \label{eq:digamma}
+%   \psi(x)
+%     % = \frac{d}{dx} \log \Gamma(x)
+%     = \frac1{\Gamma(x)}
+%       \int_0^\infty
+%         u^{x-1} e^{-u} \log{u}
+%       \, du
+%     \,.
+% \end{equation}
+By expanding expectation of a Poisson random variable we get $
+  \mathbb{E}_{W\sim \chi^2_m(\lambda)} \log W
+    = \log2 + g_m\bigl(\tfrac\lambda2\bigr)
+$, where
+\begin{equation}  \label{eq:exp_digamma}
+  g_m(x)
+    % = \mathbb{E}_{J\sim {\mathcal{P}ois}(x)}
+    %   \psi\bigl(\tfrac{m + 2 J}{2}\bigr)
+    = e^{- x} \sum_{j\geq 0}
+        \frac{x^j}{j!}
+          \psi\bigl(\tfrac{m + 2 J}{2}\bigr)
+    \,.
+\end{equation}
+Making use of the property $
+  \psi(z + 1) = \psi(z) + \tfrac1z
+  % \psi(1 + J + \tfrac{m}2) = \tfrac2{m + 2J} + \psi(J + \tfrac{m}2)
+$ of the digamma funciton for $z > 0$, we conclude that the power series in \eqref{eq:exp_digamma}
+converges for any $x \geq 0$. Therefore the derivative of \eqref{eq:exp_digamma} is
+given by
+\begin{equation}  \label{eq:g_m_series}
+  \frac{d}{dx} g_m(x)
+    % = \mathbb{E}_{J\sim {\mathcal{P}ois}(x)}
+    %     \bigl( \tfrac{J}x - 1 \bigr)
+    %   \psi\bigl(\tfrac{m + 2 J}{2}\bigr)
+    = - g_m(x)
+      + e^{- x} \sum_{j \geq 0}
+          \frac{x^j}{j!}
+        \biggl(
+          \psi\bigl(\tfrac{m + 2 j}{2}\bigr)
+          + \frac{2}{m + 2 j}
+        \biggr)
+    % = e^{- x} \sum_{j \geq 0}
+    %     \frac{x^j}{j!} \frac{2}{m + 2 j}
+    \,.
+\end{equation}
+By manipulating the partial sums within \eqref{eq:g_m_series} we get
+\begin{equation}  \label{eq:g_m_series_int}
+  \frac{d}{dx} g_m(x)
+    = e^{- x} \sum_{j \geq 0}
+      \frac{x^j}{j!} \frac1{j + \tfrac{m}2}
+    % = e^{- x} x^{- \tfrac{m}2} \sum_{j \geq 0}
+    %   \frac1{j!}
+    %   \frac{x^{j + \tfrac{m}2}}{j + \tfrac{m}2}
+    = e^{- x} x^{- \tfrac{m}2} \sum_{j \geq 0}
+      \frac1{j!} \int_0^x t^{j + \tfrac{m}2 - 1} dt
+    \,.
+\end{equation}
+Furthermore, the functions $
+  t \mapsto \sum_{j=0}^J \frac1{j!} t^{j + \tfrac{m}2 - 1}
+$ are non-decreasing on $(0, x)$ with growing $J$ and converge to $
+  t^{\tfrac{m}2 - 1} e^t
+$, which implies by the Monotone Convergence Theorem that
+\begin{equation}  \label{eq:g_m_integral}
+  \frac{d}{dx} g_m(x)
+    = e^{- x} x^{- \tfrac{m}2}
+      \int_0^x \sum_{j \geq 0}
+        \frac1{j!} t^{j + \tfrac{m}2 - 1} dt
+    = e^{- x} x^{- \tfrac{m}2}
+      \int_0^x t^{\bigl(\tfrac{m}2 - 1\bigr)} e^t dt
+    \,.
+\end{equation}
+Substituting $u^2 = t$ on $[0, \infty]$ with $2u du = dt$ and letting $
+  I_m
+  % \colon \mathbb{R} \to \mathbb{R}
+  \colon x \mapsto e^{-x^2} \int_0^x u^{m - 1} e^{u^2} du
+$ yields
+\begin{equation}  \label{eq:g_m_integral-sub}
+  \frac{d \eqref{eq:cond_exp_expansion}}{d \lambda}
+    = \frac12 \frac{d}{dx} g_m(x)
+        \bigg\vert_{x=\tfrac\lambda2}
+    % = x^{-\tfrac{m}2} e^{-x}
+    %     \int_0^x t^{\tfrac{m}2 - 1} e^t dt
+    = e^{-x}
+      x^{-\tfrac{m}2}
+      \int_0^{\sqrt{x}} u^{m - 1} e^{u^2} du
+        \bigg\vert_{x=\tfrac\lambda2}
+    % = e^{-x}
+    %   \frac1{\sqrt{x}}
+    %   \int_0^{\sqrt{x}} e^{u^2} du
+    %     \bigg\vert_{x=\tfrac\lambda2}
+    = \Bigl(\sqrt{\tfrac2\lambda}\Bigr)^m I_m\Bigl(\sqrt{\tfrac\lambda2}\Bigr)
+    \,.
+\end{equation}
+Since $\alpha$ is non-negative, it is typically parameterized via its logarithm, whence
+the derivative of \eqref{eq:kl-div-appendix} with respect to $\log\alpha$ follows from
+\eqref{eq:g_m_integral-sub} for $m=1$ and $\lambda = \tfrac1\alpha$:
+\begin{equation}  \label{eq:real-kl-div-deriv-log}
+  \frac{d K(\alpha)}{d\log \alpha}
+    % = \tfrac12 \sqrt{\tfrac2\lambda} F\Bigl(\sqrt{\tfrac\lambda2}\Bigr)
+    % for \lambda = \tfrac1\alpha
+    %   \tfrac{d\lambda}{d\alpha} = - \alpha^{-2}
+    %   \tfrac{d\alpha}{d\log \alpha} = \alpha
+    % = - \alpha \frac1{\alpha\sqrt{2\alpha}} F\Bigl(\tfrac1{\sqrt{2\alpha}}\Bigr)
+    = - \frac1{\sqrt{2\alpha}} I_1\bigl(\tfrac1{\sqrt{2\alpha}}\bigr)
+    \,.
+\end{equation}
+
+We compute the Monte-Carlo estimate of \eqref{eq:improper-kl-div-real} on a sample
+of $10^7$ draws over an equally spaced grid of $\log \alpha$ in $[-12, +12]$ of size
+$4096$. The approximation proposed by \citet{molchanov_variational_2017} is given in
+\eqref{eq:improper-kl-div-real-approx}, with coefficients $
+  k_1 = 0.63576
+$, $
+  k_2 = 1.8732
+$, and $
+  k_3 = 1.48695
+$. The derivative of the approximation with respect to $\log \alpha$ follows
+\eqref{eq:real-kl-div-deriv-log} within $4\%$ of relative tolerance, see
+fig.~\ref{fig:molchanov-derivative-replica}. 
+% see eq.~(14): flit overall sign, use $C = -k_1$, $1-\sigma(x) = \sigma(-x)$
+\begin{equation}  \label{eq:improper-kl-div-real-approx}
+  \eqref{eq:improper-kl-div-real}
+% - KL(\mathcal{N}(w \mid \mu, \alpha \mu^2) \|
+%     \tfrac1{\lvert w \rvert})
+%   \approx
+%     k_1 \sigma(k_2 + k_3 \log \alpha)
+%     + C \big\vert_{C = -k1}
+%     - \tfrac12 \log (1 + e^{-\log \alpha})
+  % = \tfrac12 \log \alpha
+  %   - \mathbb{E}_{\varepsilon \sim \mathcal{N}(1, \alpha)}
+  %   \log{\lvert \varepsilon \rvert} + C
+  \approx
+    \frac12 \log{\bigl(1 + e^{-\log \alpha}\bigr)}
+    + k_1 \sigma\bigl(- (k_2 + k_3 \log \alpha)\bigr)
+    % - k_1 \bigl(1 - \sigma(k_2 + k_3 \log \alpha)\bigr)
+  \,,
+\end{equation}
+% in parctial implementations we suggest using softplus to numerically comptue the last
+% term, since it is typically implemented in a floating-point stable fashion.
+Similarly, the forward difference estimate of the derivative \eqref{eq:real-kl-div-deriv-log}
+very closely (up to sampling error). For sake of completeness, we compute a similar
+Monte-Carlo estimate for the KL divergence term in \eqref{eq:c-vd-kl-div} for $\cplx$-valued
+Variational Dropout with $\beta = 2$, fit the best approximation \eqref{eq:improper-kl-div-real-approx},
+and compare it against the exact $\log \alpha$ derivative $
+  \frac{d \eqref{eq:c-vd-kl-div}}{d\log \alpha}
+    % = \frac{d \alpha}{d\log \alpha} \frac{d}{d\alpha} \bigl(
+    %   \log \tfrac1\alpha - \mathop{Ei}\bigl(-\tfrac1\alpha\bigr)
+    % = \alpha \bigl(
+    %   - \tfrac1\alpha
+    %   - \tfrac{e^x}{x} \bigg\vert_{x=-\tfrac1\alpha} \alpha^{-2}
+    % \bigr)
+    = e^{-\tfrac1\alpha} - 1
+$.
+
+\begin{figure}[!t]
+  \centering
+  \includegraphics[width=\columnwidth]{grad_log.pdf}
+  \caption{$\tfrac{d K(\alpha)}{d \log{\alpha}}$ of the approximation
+  \eqref{eq:improper-kl-div-real-approx}, MC estimate of \eqref{eq:improper-kl-div-real},
+  and the exact derivative using \eqref{eq:real-kl-div-deriv-log}.}
+  \label{fig:molchanov-derivative-replica}
+\end{figure}
+
+% section real-chisq-grad (end)
+
 \section{$\cplx$-Linear operator representation} % (fold)

### 2020-06-25 paper/paper.tex
paragraph split in VI review and missing "as" in CVNN review

--- 2020-06-24 paper/paper.tex
@@
 \onecolumn
+
+\section{Gradient of the KL-divergence in $\real$ case} % (fold)
+\label{sec:real-chisq-grad}  % gradient_of_the_kl_divergence_in_R_case
+
+In this appendix we study the approximation proposed by \citet{molchanov_variational_2017}
+for the KL divergence term \eqref{eq:improper-kl-div-real}. We show empirically that
+the gradient feedback provided by the approximation is sufficiently close to $
+  \tfrac{d}{d\log \alpha} K(\alpha)
+$, making it a viable alternative to exact gradients, computed in \citet{hron_variational_2018}.
+% The derivation in this section different from \citet{lapidoth_capacity_2003}.
+% The results are identical: they use DCT to establish interchangeability of limits
+% (sum-integral-derivative), whilst we allude to calculus theorems on differentiation
+% and integration of power series within the radius of their convergence (which are
+% essentially corollaries to the DCT).
+
+% \citet{pav_moments_2015} correctly notice that \cite[p. 2466]{lapidoth_capacity_2003} has a missing $\log{2}$ term.
+
+For $(z_i)_{i=1}^m \sim \mathcal{N}(0, 1)$ iid and $
+  (\mu_i)_{i=1}^m \in \mathbb{R}
+$, the random variable $W = \sum_i (\mu_i + z_i)^2$ has non-central $\chi^2$ distribution
+with shape $m$ and non-centrality parameter $\lambda = \sum_i \mu_i^2$, i.e. $
+  W\sim \chi^2_m(\lambda)
+$. The divergence \eqref{eq:improper-kl-div-real} has the form
+\begin{equation}  \label{eq:kl-div-appendix}
+  K(\alpha)
+    \propto \frac12 \mathbb{E}_{
+        W\sim \chi^2_1\bigl(\tfrac1{\alpha}\bigr)
+      } \log W
+    \tag{\ref{eq:improper-kl-div-real}'}
+  \,,
+\end{equation}
+$W$ can alternatively be represented as a Poisson mixture of ordinary $\chi^2$
+distributions: if $Z_{\mid J} \sim \chi^2_{k + 2J}$ for $
+  J \sim \mathcal{P}ois(\tfrac{\lambda}2)
+$ then $W \sim Z$. Therefore, expanding the conditional expectation gives
+\begin{equation}  \label{eq:cond_exp_expansion}
+  \mathbb{E}_{W\sim \chi^2_k(\lambda)} \log W
+    = \mathbb{E}\Bigl(
+        \mathbb{E} \bigl( \log W \mid J)
+      \Bigr)
+    = \mathbb{E}_{J\sim {\mathcal{P}ois}(\tfrac\lambda2)}
+      \Bigl(
+        \mathbb{E}_{W\sim \chi^2_{m + 2 J}} \log W
+      \Bigr)
+    \,.
+\end{equation}
+Since $\chi^2_\nu$ is Gamma distribution $\Gamma(\tfrac\nu2, \tfrac12)$, its logarithmic
+moment $
+  \mathbb{E}_{W\sim \chi^2_\nu} \log W
+$ is $
+  \psi\bigl(\tfrac\nu{2}\bigr) - \log \tfrac12
+$, where $\psi(x)$ is the digamma function. Hence
+\begin{equation}  \label{eq:exp_digamma}
+  \mathbb{E}_{W\sim \chi^2_k(\lambda)} \log W
+    = \log2 + \mathbb{E}_{J\sim {\mathcal{P}ois}(\tfrac\lambda2)}
+      \psi\bigl(\tfrac{m + 2 J}{2}\bigr)
+    % = \log2
+    % + \sum_{j\geq 0}
+    %     e^{- \tfrac{\lambda}2}
+    %     \frac{\bigl(\tfrac{\lambda}2\bigr)^j}{j!}
+    %   \psi\bigl(\tfrac{m+2J}{2}\bigr)
+    \,.
+\end{equation}
+We can use REINFORCE method to compute the derivative of \eqref{eq:exp_digamma} with respect
+to $\lambda$ \citep{williams_simple_1992}. Since Poisson $\log$-probability is $
+  \log p_\lambda(J)
+    = - \tfrac{\lambda}2
+      + J \log \tfrac{\lambda}2
+      - \log J!
+$, we get
+\begin{equation}  \label{eq:exp_reinforce}
+  \frac{d \eqref{eq:exp_digamma}}{d \lambda}
+    =
+    \mathbb{E}_{J\sim {\mathcal{P}ois}(\tfrac\lambda2)}
+      \psi\bigl(\tfrac{m + 2 J}{2}\bigr)
+      \tfrac{d}{d \lambda} \log p_\lambda(J)
+    % = \mathbb{E}_{J}
+    %   \bigl(
+    %     \tfrac2\lambda J - 1
+    %   \bigr)
+    %   \frac{\psi\bigl(\tfrac{m + 2 J}{2}\bigr)}2
+    = \frac12 g_m\bigl(\tfrac\lambda2\bigr)
+    \,,
+\end{equation}
+where
+\begin{equation}  \label{eq:g_m_series}
+  g_m(x)
+    =
+    \mathbb{E}_{J\sim {\mathcal{P}ois}(x)}
+      \bigl( \tfrac{J}x - 1 \bigr)
+      \psi\bigl(\tfrac{m + 2 J}{2}\bigr)
+    =
+    e^{- x} \sum_{j \geq 0}
+      \frac{x^j}{j!} \bigl( \tfrac{J}x - 1 \bigr)
+      \psi\bigl(\tfrac{m + 2 j}{2}\bigr)
+    \,.
+\end{equation}
+By manipulating the partial sums within $g_m(x)$ and making use of the property $
+  \psi(x + 1) = \psi(x) + \tfrac1x
+  % \psi(1 + J + \tfrac{m}2) = \tfrac2{m + 2J} + \psi(J + \tfrac{m}2)
+$ of the digamma funciton for $x > 0$, we get
+\begin{equation}  \label{eq:g_m_series_int}
+  g_m(x)
+    = e^{- x} \sum_{j \geq 0}
+      \frac{x^j}{j!} \frac1{j + \tfrac{m}2}
+    = e^{- x} x^{- \tfrac{m}2} \sum_{j \geq 0}
+      \frac1{j!}
+      \frac{x^{j + \tfrac{m}2}}{j + \tfrac{m}2}
+    = e^{- x} x^{- \tfrac{m}2} \sum_{j \geq 0}
+      \frac1{j!} \int_0^x t^{j + \tfrac{m}2 - 1} dt
+    \,.
+\end{equation}
+Since for any $J$ the functions $
+  t \mapsto \sum_{j=0}^J \frac1{j!} t^{j + \tfrac{m}2 - 1}
+$ are positive on $(0, x)$ and upper bounded by integrable $
+  t^{\tfrac{m}2 - 1} e^t
+$, which turns out to be the limit of the partial sums, the Dominated Convergence
+theorem implies
+\begin{equation}  \label{eq:g_m_integral}
+  g_m(x)
+    = e^{- x} x^{- \tfrac{m}2}
+      \int_0^x \sum_{j \geq 0}
+        \frac1{j!} t^{j + \tfrac{m}2 - 1} dt
+    = e^{- x} x^{- \tfrac{m}2}
+      \int_0^x e^t t^{(\tfrac{m}2 - 1)} dt
+    \,.
+\end{equation}
+Substituting $u^2 = t$ on $[0, \infty]$ with $2u du = dt$ and letting $
+  F_m
+  % \colon \mathbb{R} \to \mathbb{R}
+  \colon x \mapsto e^{-x^2} \int_0^x u^{m - 1} e^{u^2} du
+$ yields
+\begin{equation}  \label{eq:g_m_integral-sub}
+  \frac{d \eqref{eq:exp_digamma}}{d \lambda}
+    = \frac12 g_m\bigl(\tfrac\lambda2\bigr)
+    % = x^{-\tfrac{m}2} e^{-x}
+    %     \int_0^x t^{\tfrac{m}2 - 1} e^t dt
+    = e^{-x}
+      x^{-\tfrac{m}2}
+      \int_0^{\sqrt{x}} u^{m - 1} e^{u^2} du
+        \bigg\vert_{x=\tfrac\lambda2}
+    % = e^{-x}
+    %   \frac1{\sqrt{x}}
+    %   \int_0^{\sqrt{x}} e^{u^2} du
+    %     \bigg\vert_{x=\tfrac\lambda2}
+    = \Bigl(\sqrt{\tfrac2\lambda}\Bigr)^m F\Bigl(\sqrt{\tfrac\lambda2}\Bigr)
+    \,.
+\end{equation}
+Since $\alpha$ is non-negative, it is typically parameterized via its logarithm, whence
+the derivative of \eqref{eq:kl-div-appendix} with respect to $\log\alpha$ follows from
+\eqref{eq:g_m_integral-sub} for $m=1$ and $\lambda = \tfrac1\alpha$:
+\begin{equation}  \label{eq:real-kl-div-deriv-log}
+  \frac{d K(\alpha)}{d\log \alpha}
+    % = \tfrac12 \sqrt{\tfrac2\lambda} F\Bigl(\sqrt{\tfrac\lambda2}\Bigr)
+    % for \lambda = \tfrac1\alpha
+    %   \tfrac{d\lambda}{d\alpha} = - \alpha^{-2}
+    %   \tfrac{d\alpha}{d\log \alpha} = \alpha
+    % = - \alpha \frac1{\alpha\sqrt{2\alpha}} F\Bigl(\tfrac1{\sqrt{2\alpha}}\Bigr)
+    = - \frac1{\sqrt{2\alpha}} F\bigl(\tfrac1{\sqrt{2\alpha}}\bigr)
+    \,.
+\end{equation}
+
+We compute the Monte-Carlo estimator of \eqref{eq:improper-kl-div-real} on a sample of $10^7$
+draws over an equally spaced grid of $\log \alpha$ in $[-12, +12]$ of size $4096$. The
+coefficients of the approximation, proposed by \citet{molchanov_variational_2017}, are
+within $1\%$ relative tolerance of the reported therein. An equivalent expression of the
+approximation is given in \eqref{eq:improper-kl-div-real-approx}.
+% see eq.~(14): flit overall sign, use $C = -k_1$, $1-\sigma(x) = \sigma(-x)$
+\begin{equation}  \label{eq:improper-kl-div-real-approx}
+  \eqref{eq:improper-kl-div-real}
+% - KL(\mathcal{N}(w \mid \mu, \alpha \mu^2) \|
+%     \tfrac1{\lvert w \rvert})
+%   \approx
+%     k_1 \sigma(k_2 + k_3 \log \alpha)
+%     + C \big\vert_{C = -k1}
+%     - \tfrac12 \log (1 + e^{-\log \alpha})
+  % = \tfrac12 \log \alpha
+  %   - \mathbb{E}_{\varepsilon \sim \mathcal{N}(1, \alpha)}
+  %   \log{\lvert \varepsilon \rvert} + C
+  \approx
+    \frac12 \log{\bigl(1 + e^{-\log \alpha}\bigr)}
+    + k_1 \sigma\bigl(- (k_2 + k_3 \log \alpha)\bigr)
+    % - k_1 \bigl(1 - \sigma(k_2 + k_3 \log \alpha)\bigr)
+  \,,
+\end{equation}
+% in parctial implementations we suggest using softplus to numerically comptue the last
+% term, since it is typically implemented in a floating-point stable fashion.
+The numerically estimated derivative of the penalty term with respect to $\log \alpha$ using
+forward differences seems to be following \eqref{eq:real-kl-div-deriv-log} very closely (up to
+sampling error), see fig.~\ref{fig:molchanov-derivative-replica}. The derivative of
+\eqref{eq:improper-kl-div-real-approx} with respect to $\log \alpha$ appears to be very
+close to \eqref{eq:real-kl-div-deriv-log}. For sake of completeness, we compute a similar
+Monte-Carlo estimate for $\cplx$ variational dropout KL divergence term in \eqref{eq:c-vd-kl-div}
+with $\beta = 2$, fit the best approximation \eqref{eq:improper-kl-div-real-approx}, and
+compare it against the exact $\log \alpha$ derivative $
+  \frac{d \eqref{eq:c-vd-kl-div}}{d\log \alpha}
+    % = \frac{d \alpha}{d\log \alpha} \frac{d}{d\alpha} \bigl(
+    %   \log \tfrac1\alpha - \mathop{Ei}\bigl(-\tfrac1\alpha\bigr)
+    % = \alpha \bigl(
+    %   - \tfrac1\alpha
+    %   - \tfrac{e^x}{x} \bigg\vert_{x=-\tfrac1\alpha} \alpha^{-2}
+    % \bigr)
+    = e^{-\tfrac1\alpha} - 1
+$.
+
+\begin{figure}[!t]
+  \centering
+  \includegraphics[width=\columnwidth]{grad_log.pdf}
+  \caption{$\tfrac{d K(\alpha)}{d \log{\alpha}}$ of the approximation
+  \eqref{eq:improper-kl-div-real-approx}, MC estimate of \eqref{eq:improper-kl-div-real},
+  and the exact derivative using \eqref{eq:real-kl-div-deriv-log}.}
+  \label{fig:molchanov-derivative-replica}
+\end{figure}
+
+% section real-chisq-grad (end)
 
@@
 
-\section{Gradient of the KL-divergence in $\real$ case} % (fold)
-\label{sec:real-chisq-grad}  % gradient_of_the_kl_divergence_in_R_case
-
-In this appendix we study the approximation proposed by \citet{molchanov_variational_2017}
-for the KL divergence term \eqref{eq:improper-kl-div-real} for $\real$ Sparse Variational
-Dropout. Following the logic of \citet{lapidoth_capacity_2003} we derive the expression
-for $
-  \tfrac{d}{d\log \alpha} K(\alpha)
-$. Acknowledging that the same result was obtained by \citet[eq.~(5)]{hron_variational_2018},
-we provide this appendix for the sake of completeness.
-% The derivation in this section different from \citet{lapidoth_capacity_2003}.
-% The results are identical: they use DCT to establish interchangeability of limits
-% (sum-integral-derivative), whilst we allude to calculus theorems on differentiation
-% and integration of power series within the radius of their convergence (which are
-% essentially corollaries to the DCT).
-
-% \citet{pav_moments_2015} correctly notice that \cite[p. 2466]{lapidoth_capacity_2003} has a missing $\log{2}$ term.
-
-For $(z_i)_{i=1}^m \sim \mathcal{N}(0, 1)$ iid and $
-  (\mu_i)_{i=1}^m \in \mathbb{R}
-$, the random variable $W = \sum_i (\mu_i + z_i)^2$ has non-central $\chi^2$ distribution
-with shape $m$ and non-centrality parameter $\lambda = \sum_i \mu_i^2$, i.e. $
-  W\sim \chi^2_m(\lambda)
-$. Therefore, the divergence \eqref{eq:improper-kl-div-real} has the form
-\begin{equation}  \label{eq:kl-div-appendix}
-  K(\alpha)
-    \propto \frac12 \mathbb{E}_{
-        W\sim \chi^2_1\bigl(\tfrac1{\alpha}\bigr)
-      } \log W
-    \tag{\ref{eq:improper-kl-div-real}'}
-  \,.
-\end{equation}
-$W$ can alternatively be represented as a Poisson mixture of ordinary $\chi^2$
-distributions: if $Z_{\mid J} \sim \chi^2_{m + 2J}$ for $
-  J \sim \mathcal{P}ois(\tfrac{\lambda}2)
-$ then $W \sim Z$. Therefore, expanding the conditional expectation gives
-\begin{equation}  \label{eq:cond_exp_expansion}
-  \mathbb{E}_{W\sim \chi^2_m(\lambda)} \log W
-    = \mathbb{E}\Bigl(
-        \mathbb{E} \bigl( \log W \mid J)
-      \Bigr)
-    = \mathbb{E}_{J\sim {\mathcal{P}ois}(\tfrac\lambda2)}
-      \Bigl(
-        \mathbb{E}_{W\sim \chi^2_{m + 2 J}} \log W
-      \Bigr)
-    \,.
-\end{equation}
-Since $\chi^2_\nu$ is Gamma distribution $\Gamma(\tfrac\nu2, \tfrac12)$, it can be shown
-that the logarithmic moment $
-  \mathbb{E}_{W\sim \chi^2_\nu} \log W
-$ is $
-  \psi\bigl(\tfrac\nu{2}\bigr) - \log \tfrac12
-$, where $\psi$ is the digamma function ($\psi(x) = \tfrac{d}{dx} \log \Gamma(x)$).
-% \begin{equation}  \label{eq:digamma}
-%   \psi(x)
-%     % = \frac{d}{dx} \log \Gamma(x)
-%     = \frac1{\Gamma(x)}
-%       \int_0^\infty
-%         u^{x-1} e^{-u} \log{u}
-%       \, du
-%     \,.
-% \end{equation}
-By expanding expectation of a Poisson random variable we get $
-  \mathbb{E}_{W\sim \chi^2_m(\lambda)} \log W
-    = \log2 + g_m\bigl(\tfrac\lambda2\bigr)
-$, where
-\begin{equation}  \label{eq:exp_digamma}
-  g_m(x)
-    % = \mathbb{E}_{J\sim {\mathcal{P}ois}(x)}
-    %   \psi\bigl(\tfrac{m + 2 J}{2}\bigr)
-    = e^{- x} \sum_{j\geq 0}
-        \frac{x^j}{j!}
-          \psi\bigl(\tfrac{m + 2 J}{2}\bigr)
-    \,.
-\end{equation}
-Making use of the property $
-  \psi(z + 1) = \psi(z) + \tfrac1z
-  % \psi(1 + J + \tfrac{m}2) = \tfrac2{m + 2J} + \psi(J + \tfrac{m}2)
-$ of the digamma funciton for $z > 0$, we conclude that the power series in \eqref{eq:exp_digamma}
-converges for any $x \geq 0$. Therefore the derivative of \eqref{eq:exp_digamma} is
-given by
-\begin{equation}  \label{eq:g_m_series}
-  \frac{d}{dx} g_m(x)
-    % = \mathbb{E}_{J\sim {\mathcal{P}ois}(x)}
-    %     \bigl( \tfrac{J}x - 1 \bigr)
-    %   \psi\bigl(\tfrac{m + 2 J}{2}\bigr)
-    = - g_m(x)
-      + e^{- x} \sum_{j \geq 0}
-          \frac{x^j}{j!}
-        \biggl(
-          \psi\bigl(\tfrac{m + 2 j}{2}\bigr)
-          + \frac{2}{m + 2 j}
-        \biggr)
-    % = e^{- x} \sum_{j \geq 0}
-    %     \frac{x^j}{j!} \frac{2}{m + 2 j}
-    \,.
-\end{equation}
-By manipulating the partial sums within \eqref{eq:g_m_series} we get
-\begin{equation}  \label{eq:g_m_series_int}
-  \frac{d}{dx} g_m(x)
-    = e^{- x} \sum_{j \geq 0}
-      \frac{x^j}{j!} \frac1{j + \tfrac{m}2}
-    % = e^{- x} x^{- \tfrac{m}2} \sum_{j \geq 0}
-    %   \frac1{j!}
-    %   \frac{x^{j + \tfrac{m}2}}{j + \tfrac{m}2}
-    = e^{- x} x^{- \tfrac{m}2} \sum_{j \geq 0}
-      \frac1{j!} \int_0^x t^{j + \tfrac{m}2 - 1} dt
-    \,.
-\end{equation}
-Furthermore, the functions $
-  t \mapsto \sum_{j=0}^J \frac1{j!} t^{j + \tfrac{m}2 - 1}
-$ are non-decreasing on $(0, x)$ with growing $J$ and converge to $
-  t^{\tfrac{m}2 - 1} e^t
-$, which implies by the Monotone Convergence Theorem that
-\begin{equation}  \label{eq:g_m_integral}
-  \frac{d}{dx} g_m(x)
-    = e^{- x} x^{- \tfrac{m}2}
-      \int_0^x \sum_{j \geq 0}
-        \frac1{j!} t^{j + \tfrac{m}2 - 1} dt
-    = e^{- x} x^{- \tfrac{m}2}
-      \int_0^x t^{\bigl(\tfrac{m}2 - 1\bigr)} e^t dt
-    \,.
-\end{equation}
-Substituting $u^2 = t$ on $[0, \infty]$ with $2u du = dt$ and letting $
-  I_m
-  % \colon \mathbb{R} \to \mathbb{R}
-  \colon x \mapsto e^{-x^2} \int_0^x u^{m - 1} e^{u^2} du
-$ yields
-\begin{equation}  \label{eq:g_m_integral-sub}
-  \frac{d \eqref{eq:cond_exp_expansion}}{d \lambda}
-    = \frac12 \frac{d}{dx} g_m(x)
-        \bigg\vert_{x=\tfrac\lambda2}
-    % = x^{-\tfrac{m}2} e^{-x}
-    %     \int_0^x t^{\tfrac{m}2 - 1} e^t dt
-    = e^{-x}
-      x^{-\tfrac{m}2}
-      \int_0^{\sqrt{x}} u^{m - 1} e^{u^2} du
-        \bigg\vert_{x=\tfrac\lambda2}
-    % = e^{-x}
-    %   \frac1{\sqrt{x}}
-    %   \int_0^{\sqrt{x}} e^{u^2} du
-    %     \bigg\vert_{x=\tfrac\lambda2}
-    = \Bigl(\sqrt{\tfrac2\lambda}\Bigr)^m I_m\Bigl(\sqrt{\tfrac\lambda2}\Bigr)
-    \,.
-\end{equation}
-Since $\alpha$ is non-negative, it is typically parameterized via its logarithm, whence
-the derivative of \eqref{eq:kl-div-appendix} with respect to $\log\alpha$ follows from
-\eqref{eq:g_m_integral-sub} for $m=1$ and $\lambda = \tfrac1\alpha$:
-\begin{equation}  \label{eq:real-kl-div-deriv-log}
-  \frac{d K(\alpha)}{d\log \alpha}
-    % = \tfrac12 \sqrt{\tfrac2\lambda} F\Bigl(\sqrt{\tfrac\lambda2}\Bigr)
-    % for \lambda = \tfrac1\alpha
-    %   \tfrac{d\lambda}{d\alpha} = - \alpha^{-2}
-    %   \tfrac{d\alpha}{d\log \alpha} = \alpha
-    % = - \alpha \frac1{\alpha\sqrt{2\alpha}} F\Bigl(\tfrac1{\sqrt{2\alpha}}\Bigr)
-    = - \frac1{\sqrt{2\alpha}} I_1\bigl(\tfrac1{\sqrt{2\alpha}}\bigr)
-    \,.
-\end{equation}
-
-We compute the Monte-Carlo estimate of \eqref{eq:improper-kl-div-real} on a sample
-of $10^7$ draws over an equally spaced grid of $\log \alpha$ in $[-12, +12]$ of size
-$4096$. The approximation proposed by \citet{molchanov_variational_2017} is given in
-\eqref{eq:improper-kl-div-real-approx}, with coefficients $
-  k_1 = 0.63576
-$, $
-  k_2 = 1.8732
-$, and $
-  k_3 = 1.48695
-$. The derivative of the approximation with respect to $\log \alpha$ follows
-\eqref{eq:real-kl-div-deriv-log} within $4\%$ of relative tolerance, see
-fig.~\ref{fig:molchanov-derivative-replica}. 
-% see eq.~(14): flit overall sign, use $C = -k_1$, $1-\sigma(x) = \sigma(-x)$
-\begin{equation}  \label{eq:improper-kl-div-real-approx}
-  \eqref{eq:improper-kl-div-real}
-% - KL(\mathcal{N}(w \mid \mu, \alpha \mu^2) \|
-%     \tfrac1{\lvert w \rvert})
-%   \approx
-%     k_1 \sigma(k_2 + k_3 \log \alpha)
-%     + C \big\vert_{C = -k1}
-%     - \tfrac12 \log (1 + e^{-\log \alpha})
-  % = \tfrac12 \log \alpha
-  %   - \mathbb{E}_{\varepsilon \sim \mathcal{N}(1, \alpha)}
-  %   \log{\lvert \varepsilon \rvert} + C
-  \approx
-    \frac12 \log{\bigl(1 + e^{-\log \alpha}\bigr)}
-    + k_1 \sigma\bigl(- (k_2 + k_3 \log \alpha)\bigr)
-    % - k_1 \bigl(1 - \sigma(k_2 + k_3 \log \alpha)\bigr)
-  \,,
-\end{equation}
-% in parctial implementations we suggest using softplus to numerically comptue the last
-% term, since it is typically implemented in a floating-point stable fashion.
-Similarly, the forward difference estimate of the derivative \eqref{eq:real-kl-div-deriv-log}
-very closely (up to sampling error). For sake of completeness, we compute a similar
-Monte-Carlo estimate for the KL divergence term in \eqref{eq:c-vd-kl-div} for $\cplx$-valued
-Variational Dropout with $\beta = 2$, fit the best approximation \eqref{eq:improper-kl-div-real-approx},
-and compare it against the exact $\log \alpha$ derivative $
-  \frac{d \eqref{eq:c-vd-kl-div}}{d\log \alpha}
-    % = \frac{d \alpha}{d\log \alpha} \frac{d}{d\alpha} \bigl(
-    %   \log \tfrac1\alpha - \mathop{Ei}\bigl(-\tfrac1\alpha\bigr)
-    % = \alpha \bigl(
-    %   - \tfrac1\alpha
-    %   - \tfrac{e^x}{x} \bigg\vert_{x=-\tfrac1\alpha} \alpha^{-2}
-    % \bigr)
-    = e^{-\tfrac1\alpha} - 1
-$.
-
-\begin{figure}[!t]
-  \centering
-  \includegraphics[width=\columnwidth]{grad_log.pdf}
-  \caption{$\tfrac{d K(\alpha)}{d \log{\alpha}}$ of the approximation
-  \eqref{eq:improper-kl-div-real-approx}, MC estimate of \eqref{eq:improper-kl-div-real},
-  and the exact derivative using \eqref{eq:real-kl-div-deriv-log}.}
-  \label{fig:molchanov-derivative-replica}
-\end{figure}
-
-% section real-chisq-grad (end)
-
 \section{$\cplx$-Linear operator representation} % (fold)

### 2020-06-26 paper/paper.tex
remove the silly appendix about lin ops

--- 2020-06-24 paper/paper.tex
@@
 
-\section{$\cplx$-Linear operator representation} % (fold)
-\label{sec:c-linear_operator_representation}
-
-% proof that such operators exist and are unique (well this is an obvious statement)
-Consider $L \colon \cplx^m \to \cplx^n$ -- linear in $\cplx$. Then $
-  L(u + jv) = L u + \iu L v
-$ for any $u, v \in \real^m$, which implies that the effect of $L$ as $\cplx$-linear
-operator is determined by its restriction onto $\real^n$. Let $
-  F = L\vert_{\real^m}
-  \colon \real^m \to \cplx^n
-$ and observe that $F_r = \Re \circ F$ and $F_i = \Im \circ F$ are $\real$-linear operators
-such that $F = F_r + \iu F_i$ (pointwise). Indeed,
-$$
-  F_r(a + \lambda b)
-  % = \Re F(a + \lambda b)
-  = \Re L(a + \lambda b)
-  % = \Re \bigl( L a + \lambda L b \bigr)
-  = \Re L a + \lambda \Re L b
-  % = \Re F a + \lambda \Re F b
-  = F_r a + \lambda F_r b
-  \,. $$
-Therefore for any $\cplx$-linear operator $L$ there are $\real$-linear operators $U, V$
-such that
-$$
-L z 
-  = (U + \iu V) (\Re z + \iu \Im z)
-  % = (U + \iu V) \Re z + \iu (U + \iu V) \Im z
-  % = U \Re z + \iu V \Re z + \iu \bigl(U \Im z + \iu V \Im z \bigr)
-  = U \Re z - V \Im z + \iu \bigl( V \Re z + U \Im z \bigr)
-  % = (U + \iu V) z
-  \,. $$
-Uniqueness of these operators follows, if this decomposition is applied to any $z$ with
-$\Im z = 0$.
-
-% section c-linear_operator_representation (end)
-
 % section appendix (end)

### 2020-06-26 paper/paper.tex
removed references to legacy stuff

@@
   \begin{subfigure}[b]{1.\columnwidth}  % imcl2019-style swears at this
-    % \includegraphics[width=\columnwidth]{figure__cifar__trade-off/legacy__augmentedcifar10__raw__-0.5.pdf}
     \includegraphics[width=\columnwidth]{figure__cifar__trade-off/appendix__augmentedcifar10__raw__-0.5.pdf}

### 2020-06-27 paper/paper.tex
reordered the appendix

--- 2020-06-26 paper/paper.tex
@@
 In this appendix we study the approximation proposed by \citet{molchanov_variational_2017}
-for the KL divergence term \eqref{eq:improper-kl-div-real} for $\real$ Sparse Variational
-Dropout. Following the logic of \citet{lapidoth_capacity_2003} we derive the expression
-for $
+for the KL divergence term \eqref{eq:improper-kl-div-real}. We show empirically that
+the gradient feedback provided by the approximation is sufficiently close to $
   \tfrac{d}{d\log \alpha} K(\alpha)
-$. Acknowledging that the same result was obtained by \citet[eq.~(5)]{hron_variational_2018},
-we provide this appendix for the sake of completeness.
+$, making it a viable alternative to exact gradients, computed in \citet{hron_variational_2018}.
 % The derivation in this section different from \citet{lapidoth_capacity_2003}.
@@
   W\sim \chi^2_m(\lambda)
-$. Therefore, the divergence \eqref{eq:improper-kl-div-real} has the form
+$. The divergence \eqref{eq:improper-kl-div-real} has the form
 \begin{equation}  \label{eq:kl-div-appendix}
@@
     \tag{\ref{eq:improper-kl-div-real}'}
-  \,.
+  \,,
 \end{equation}
 $W$ can alternatively be represented as a Poisson mixture of ordinary $\chi^2$
-distributions: if $Z_{\mid J} \sim \chi^2_{m + 2J}$ for $
+distributions: if $Z_{\mid J} \sim \chi^2_{k + 2J}$ for $
   J \sim \mathcal{P}ois(\tfrac{\lambda}2)
@@
 \begin{equation}  \label{eq:cond_exp_expansion}
-  \mathbb{E}_{W\sim \chi^2_m(\lambda)} \log W
+  \mathbb{E}_{W\sim \chi^2_k(\lambda)} \log W
     = \mathbb{E}\Bigl(
@@
 \end{equation}
-Since $\chi^2_\nu$ is Gamma distribution $\Gamma(\tfrac\nu2, \tfrac12)$, it can be shown
-that the logarithmic moment $
+Since $\chi^2_\nu$ is Gamma distribution $\Gamma(\tfrac\nu2, \tfrac12)$, its logarithmic
+moment $
   \mathbb{E}_{W\sim \chi^2_\nu} \log W
@@
   \psi\bigl(\tfrac\nu{2}\bigr) - \log \tfrac12
-$, where $\psi$ is the digamma function ($\psi(x) = \tfrac{d}{dx} \log \Gamma(x)$).
-% \begin{equation}  \label{eq:digamma}
-%   \psi(x)
-%     % = \frac{d}{dx} \log \Gamma(x)
-%     = \frac1{\Gamma(x)}
-%       \int_0^\infty
-%         u^{x-1} e^{-u} \log{u}
-%       \, du
-%     \,.
-% \end{equation}
-By expanding expectation of a Poisson random variable we get $
-  \mathbb{E}_{W\sim \chi^2_m(\lambda)} \log W
-    = \log2 + g_m\bigl(\tfrac\lambda2\bigr)
-$, where
+$, where $\psi(x)$ is the digamma function. Hence
 \begin{equation}  \label{eq:exp_digamma}
+  \mathbb{E}_{W\sim \chi^2_k(\lambda)} \log W
+    = \log2 + \mathbb{E}_{J\sim {\mathcal{P}ois}(\tfrac\lambda2)}
+      \psi\bigl(\tfrac{m + 2 J}{2}\bigr)
+    % = \log2
+    % + \sum_{j\geq 0}
+    %     e^{- \tfrac{\lambda}2}
+    %     \frac{\bigl(\tfrac{\lambda}2\bigr)^j}{j!}
+    %   \psi\bigl(\tfrac{m+2J}{2}\bigr)
+    \,.
+\end{equation}
+We can use REINFORCE method to compute the derivative of \eqref{eq:exp_digamma} with respect
+to $\lambda$ \citep{williams_simple_1992}. Since Poisson $\log$-probability is $
+  \log p_\lambda(J)
+    = - \tfrac{\lambda}2
+      + J \log \tfrac{\lambda}2
+      - \log J!
+$, we get
+\begin{equation}  \label{eq:exp_reinforce}
+  \frac{d \eqref{eq:exp_digamma}}{d \lambda}
+    =
+    \mathbb{E}_{J\sim {\mathcal{P}ois}(\tfrac\lambda2)}
+      \psi\bigl(\tfrac{m + 2 J}{2}\bigr)
+      \tfrac{d}{d \lambda} \log p_\lambda(J)
+    % = \mathbb{E}_{J}
+    %   \bigl(
+    %     \tfrac2\lambda J - 1
+    %   \bigr)
+    %   \frac{\psi\bigl(\tfrac{m + 2 J}{2}\bigr)}2
+    = \frac12 g_m\bigl(\tfrac\lambda2\bigr)
+    \,,
+\end{equation}
+where
+\begin{equation}  \label{eq:g_m_series}
   g_m(x)
-    % = \mathbb{E}_{J\sim {\mathcal{P}ois}(x)}
-    %   \psi\bigl(\tfrac{m + 2 J}{2}\bigr)
-    = e^{- x} \sum_{j\geq 0}
-        \frac{x^j}{j!}
+    =
+    \mathbb{E}_{J\sim {\mathcal{P}ois}(x)}
+      \bigl( \tfrac{J}x - 1 \bigr)
       \psi\bigl(\tfrac{m + 2 J}{2}\bigr)
+    =
+    e^{- x} \sum_{j \geq 0}
+      \frac{x^j}{j!} \bigl( \tfrac{J}x - 1 \bigr)
+      \psi\bigl(\tfrac{m + 2 j}{2}\bigr)
     \,.
 \end{equation}
-Making use of the property $
-  \psi(z + 1) = \psi(z) + \tfrac1z
+By manipulating the partial sums within $g_m(x)$ and making use of the property $
+  \psi(x + 1) = \psi(x) + \tfrac1x
   % \psi(1 + J + \tfrac{m}2) = \tfrac2{m + 2J} + \psi(J + \tfrac{m}2)
-$ of the digamma funciton for $z > 0$, we conclude that the power series in \eqref{eq:exp_digamma}
-converges for any $x \geq 0$. Therefore the derivative of \eqref{eq:exp_digamma} is
-given by
-\begin{equation}  \label{eq:g_m_series}
-  \frac{d}{dx} g_m(x)
-    % = \mathbb{E}_{J\sim {\mathcal{P}ois}(x)}
-    %     \bigl( \tfrac{J}x - 1 \bigr)
-    %   \psi\bigl(\tfrac{m + 2 J}{2}\bigr)
-    = - g_m(x)
-      + e^{- x} \sum_{j \geq 0}
-          \frac{x^j}{j!}
-        \biggl(
-          \psi\bigl(\tfrac{m + 2 j}{2}\bigr)
-          + \frac{2}{m + 2 j}
-        \biggr)
-    % = e^{- x} \sum_{j \geq 0}
-    %     \frac{x^j}{j!} \frac{2}{m + 2 j}
-    \,.
-\end{equation}
-By manipulating the partial sums within \eqref{eq:g_m_series} we get
+$ of the digamma funciton for $x > 0$, we get
 \begin{equation}  \label{eq:g_m_series_int}
-  \frac{d}{dx} g_m(x)
+  g_m(x)
     = e^{- x} \sum_{j \geq 0}
       \frac{x^j}{j!} \frac1{j + \tfrac{m}2}
-    % = e^{- x} x^{- \tfrac{m}2} \sum_{j \geq 0}
-    %   \frac1{j!}
-    %   \frac{x^{j + \tfrac{m}2}}{j + \tfrac{m}2}
+    = e^{- x} x^{- \tfrac{m}2} \sum_{j \geq 0}
+      \frac1{j!}
+      \frac{x^{j + \tfrac{m}2}}{j + \tfrac{m}2}
     = e^{- x} x^{- \tfrac{m}2} \sum_{j \geq 0}
@@
 \end{equation}
-Furthermore, the functions $
+Since for any $J$ the functions $
   t \mapsto \sum_{j=0}^J \frac1{j!} t^{j + \tfrac{m}2 - 1}
-$ are non-decreasing on $(0, x)$ with growing $J$ and converge to $
+$ are positive on $(0, x)$ and upper bounded by integrable $
   t^{\tfrac{m}2 - 1} e^t
-$, which implies by the Monotone Convergence Theorem that
+$, which turns out to be the limit of the partial sums, the Dominated Convergence
+theorem implies
 \begin{equation}  \label{eq:g_m_integral}
-  \frac{d}{dx} g_m(x)
+  g_m(x)
     = e^{- x} x^{- \tfrac{m}2}
@@
     = e^{- x} x^{- \tfrac{m}2}
-      \int_0^x t^{\bigl(\tfrac{m}2 - 1\bigr)} e^t dt
+      \int_0^x e^t t^{(\tfrac{m}2 - 1)} dt
     \,.
@@
 Substituting $u^2 = t$ on $[0, \infty]$ with $2u du = dt$ and letting $
-  I_m
+  F_m
   % \colon \mathbb{R} \to \mathbb{R}
@@
 \begin{equation}  \label{eq:g_m_integral-sub}
-  \frac{d \eqref{eq:cond_exp_expansion}}{d \lambda}
-    = \frac12 \frac{d}{dx} g_m(x)
-        \bigg\vert_{x=\tfrac\lambda2}
+  \frac{d \eqref{eq:exp_digamma}}{d \lambda}
+    = \frac12 g_m\bigl(\tfrac\lambda2\bigr)
     % = x^{-\tfrac{m}2} e^{-x}
@@
     %     \bigg\vert_{x=\tfrac\lambda2}
-    = \Bigl(\sqrt{\tfrac2\lambda}\Bigr)^m I_m\Bigl(\sqrt{\tfrac\lambda2}\Bigr)
+    = \Bigl(\sqrt{\tfrac2\lambda}\Bigr)^m F\Bigl(\sqrt{\tfrac\lambda2}\Bigr)
     \,.
@@
     % = - \alpha \frac1{\alpha\sqrt{2\alpha}} F\Bigl(\tfrac1{\sqrt{2\alpha}}\Bigr)
-    = - \frac1{\sqrt{2\alpha}} I_1\bigl(\tfrac1{\sqrt{2\alpha}}\bigr)
+    = - \frac1{\sqrt{2\alpha}} F\bigl(\tfrac1{\sqrt{2\alpha}}\bigr)
     \,.
@@
 
-We compute the Monte-Carlo estimate of \eqref{eq:improper-kl-div-real} on a sample
-of $10^7$ draws over an equally spaced grid of $\log \alpha$ in $[-12, +12]$ of size
-$4096$. The approximation proposed by \citet{molchanov_variational_2017} is given in
-\eqref{eq:improper-kl-div-real-approx}, with coefficients $
-  k_1 = 0.63576
-$, $
-  k_2 = 1.8732
-$, and $
-  k_3 = 1.48695
-$. The derivative of the approximation with respect to $\log \alpha$ follows
-\eqref{eq:real-kl-div-deriv-log} within $4\%$ of relative tolerance, see
-fig.~\ref{fig:molchanov-derivative-replica}. 
+We compute the Monte-Carlo estimator of \eqref{eq:improper-kl-div-real} on a sample of $10^7$
+draws over an equally spaced grid of $\log \alpha$ in $[-12, +12]$ of size $4096$. The
+coefficients of the approximation, proposed by \citet{molchanov_variational_2017}, are
+within $1\%$ relative tolerance of the reported therein. An equivalent expression of the
+approximation is given in \eqref{eq:improper-kl-div-real-approx}.
 % see eq.~(14): flit overall sign, use $C = -k_1$, $1-\sigma(x) = \sigma(-x)$
@@
 % term, since it is typically implemented in a floating-point stable fashion.
-Similarly, the forward difference estimate of the derivative \eqref{eq:real-kl-div-deriv-log}
-very closely (up to sampling error). For sake of completeness, we compute a similar
-Monte-Carlo estimate for the KL divergence term in \eqref{eq:c-vd-kl-div} for $\cplx$-valued
-Variational Dropout with $\beta = 2$, fit the best approximation \eqref{eq:improper-kl-div-real-approx},
-and compare it against the exact $\log \alpha$ derivative $
+The numerically estimated derivative of the penalty term with respect to $\log \alpha$ using
+forward differences seems to be following \eqref{eq:real-kl-div-deriv-log} very closely (up to
+sampling error), see fig.~\ref{fig:molchanov-derivative-replica}. The derivative of
+\eqref{eq:improper-kl-div-real-approx} with respect to $\log \alpha$ appears to be very
+close to \eqref{eq:real-kl-div-deriv-log}. For sake of completeness, we compute a similar
+Monte-Carlo estimate for $\cplx$ variational dropout KL divergence term in \eqref{eq:c-vd-kl-div}
+with $\beta = 2$, fit the best approximation \eqref{eq:improper-kl-div-real-approx}, and
+compare it against the exact $\log \alpha$ derivative $
   \frac{d \eqref{eq:c-vd-kl-div}}{d\log \alpha}
@@
 
+\section{$\cplx$-Linear operator representation} % (fold)
+\label{sec:c-linear_operator_representation}
+
+% proof that such operators exist and are unique (well this is an obvious statement)
+Consider $L \colon \cplx^m \to \cplx^n$ -- linear in $\cplx$. Then $
+  L(u + jv) = L u + \iu L v
+$ for any $u, v \in \real^m$, which implies that the effect of $L$ as $\cplx$-linear
+operator is determined by its restriction onto $\real^n$. Let $
+  F = L\vert_{\real^m}
+  \colon \real^m \to \cplx^n
+$ and observe that $F_r = \Re \circ F$ and $F_i = \Im \circ F$ are $\real$-linear operators
+such that $F = F_r + \iu F_i$ (pointwise). Indeed,
+$$
+  F_r(a + \lambda b)
+  % = \Re F(a + \lambda b)
+  = \Re L(a + \lambda b)
+  % = \Re \bigl( L a + \lambda L b \bigr)
+  = \Re L a + \lambda \Re L b
+  % = \Re F a + \lambda \Re F b
+  = F_r a + \lambda F_r b
+  \,. $$
+Therefore for any $\cplx$-linear operator $L$ there are $\real$-linear operators $U, V$
+such that
+$$
+L z 
+  = (U + \iu V) (\Re z + \iu \Im z)
+  % = (U + \iu V) \Re z + \iu (U + \iu V) \Im z
+  % = U \Re z + \iu V \Re z + \iu \bigl(U \Im z + \iu V \Im z \bigr)
+  = U \Re z - V \Im z + \iu \bigl( V \Re z + U \Im z \bigr)
+  % = (U + \iu V) z
+  \,. $$
+Uniqueness of these operators follows, if this decomposition is applied to any $z$ with
+$\Im z = 0$.
+
+% section c-linear_operator_representation (end)
+
 % section appendix (end)

### 2020-06-28 paper/paper.tex
13 merged older and newer versions of the appendix

--- 2020-06-26 paper/paper.tex
@@
   \begin{subfigure}[b]{1.\columnwidth}  % imcl2019-style swears at this
+    % \includegraphics[width=\columnwidth]{figure__cifar__trade-off/legacy__augmentedcifar10__raw__-0.5.pdf}
     \includegraphics[width=\columnwidth]{figure__cifar__trade-off/appendix__augmentedcifar10__raw__-0.5.pdf}
@@
   \label{fig:appendix__cmp__mnist-like__trade-off__VD__raw}
+\end{figure}
+
+\begin{figure}[b]
+  \centering
+  \begin{subfigure}[b]{0.5\columnwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/legacy__VD__emnist_letters__fft__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\columnwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/legacy__VD__kmnist__fft__-0.5.pdf}
+  \end{subfigure} \\%
+  \begin{subfigure}[b]{0.5\columnwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/legacy__VD__fashionmnist__fft__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\columnwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/legacy__VD__mnist__fft__-0.5.pdf}
+  \end{subfigure}
+  \caption{%
+    The trade-off of VD method for $\real$ and $\cplx$ models using Fourier features (main text).
+  }
+  \label{fig:paper__mnist-like__trade-off__VD__fft}
+\end{figure}
+
+\begin{figure}[b]
+  \centering
+  \begin{subfigure}[b]{0.5\columnwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/legacy__VD__emnist_letters__raw__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\columnwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/legacy__VD__kmnist__raw__-0.5.pdf}
+  \end{subfigure} \\%
+  \begin{subfigure}[b]{0.5\columnwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/legacy__VD__fashionmnist__raw__-0.5.pdf}
+  \end{subfigure}%
+  \begin{subfigure}[b]{0.5\columnwidth}
+    \centering
+    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/legacy__VD__mnist__raw__-0.5.pdf}
+  \end{subfigure}
+  \caption{%
+    The trade-off of VD method for $\real$ and $\cplx$ models using raw features (main text).
+  }
+  \label{fig:paper__mnist-like__trade-off__VD__raw}
 \end{figure}

### 2020-06-28 paper/paper.tex
hardcode the path to no-type-3 assets

--- 2020-06-26 paper/paper.tex
@@
-\documentclass[a4paper,10pt,onecolumn]{article}
+\documentclass{article}
 
@@
 
-\graphicspath{{../assets/}}
-
-\usepackage{subcaption}
+\graphicspath{{../miscellaneous/assets-no-type-3/}}
+
+\usepackage{subfigure}
 
@@
   \centering
-  \begin{subfigure}[b]{1.\columnwidth}  % imcl2019-style swears at this
+  % \includegraphics[width=\columnwidth]{figure__cifar__trade-off/legacy__augmentedcifar10__raw__-0.5.pdf}
   \includegraphics[width=\columnwidth]{figure__cifar__trade-off/appendix__augmentedcifar10__raw__-0.5.pdf}
-  \end{subfigure}
   \caption{%

### 2020-08-06 setup.py
version retro-update

@@ -1,8 +1,8 @@
-from distutils.core import setup, Extension
+from distutils.core import setup
 
 setup(
     name="cplxpaper",
-    version="2020.3",
+    version="2020.6",
     description="""Backend for experiments presented in Bayesian"""
                 """ Sparsification of Deep Complex-valued Networks.""",
     license="MIT License",
@@ -24,7 +24,7 @@ setup(
     ],
     install_requires=[
         "torch>=1.4",
-        "cplxmodule @ https://github.com/ivannz/cplxmodule/archive/v2020.03.tar.gz",
+        "cplxmodule @ https://github.com/ivannz/cplxmodule/archive/v2020.6rc.tar.gz",
         "numpy",
         "pandas",
         "sklearn",

### 2020-11-09 paper/paper.tex
typo fixes

@@
 \citep{wan_regularization_2013}, and Gaussian Dropout \citep{wang_fast_2013} through
-the lens of Variational Inference and propose \emph{Variational Dropout}. They argued
+the lens of Variational Inference and proposed \emph{Variational Dropout}. They argued
 that the multiplicative noise introduced by Dropout methods induces a distribution
@@
 final compression rate since it directly affects the feedback from sparsifying prior.
-So, during the $50$ epoch allotted for ``sparsify'' stage, low $C$ prevents the sparsity
+So, during the $50$ epochs allotted for ``sparsify'' stage, low $C$ prevents the sparsity
 inducing prior from pulling the posterior sufficiently away from the likelihood-maximizing
